### 2019-04-04 initial/notes.tex
initial

    \documentclass[11pt,
        usenames, % allows access to some tikz colors
        dvipsnames % more colors: https://en.wikibooks.org/wiki/LaTeX/Colors
    ]{article}
    \usepackage{
        amsmath,
        amssymb,
        fouriernc, % fourier font w/ new century book
        fancyhdr, % page styling
        lastpage, % footer fanciness
        hyperref, % various links
        setspace, % line spacing
        amsthm, % newtheorem and proof environment
        mathtools, % \Aboxed for boxing inside aligns, among others
        float, % Allow [H] figure env alignment
        enumerate, % Allow custom enumerate numbering
        graphicx, % allow includegraphics with more filetypes
        wasysym, % \smiley!
        upgreek, % \upmu for \mum macro
        listings, % writing TrueType fonts and including code prettily
        tikz, % drawing things
        booktabs, % \bottomrule instead of hline apparently
        cancel % can cancel things out!
    }
    \usepackage[margin=1in]{geometry} % page geometry
    \usepackage[
        labelfont=bf, % caption names are labeled in bold
        font=scriptsize % smaller font for captions
    ]{caption}
    \usepackage[font=scriptsize]{subcaption} % subfigures

    \newcommand*{\scinot}[2]{#1\times10^{#2}}
    \newcommand*{\dotp}[2]{\left<#1\,\middle|\,#2\right>}
    \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
    \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
    \newcommand*{\rtd}[2]{\frac{\mathrm{d}^2#1}{\mathrm{d}#2^2}}
    \newcommand*{\ptd}[2]{\frac{\partial^2 #1}{\partial#2^2}}
    \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
    \newcommand*{\pvec}[1]{\vec{#1}^{\,\prime}}
    \newcommand*{\svec}[1]{\vec{#1}\;\!}
    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
    \newcommand*{\ang}[0]{\;\text{\AA}}
    \newcommand*{\mum}[0]{\;\upmu \mathrm{m}}
    \newcommand*{\at}[1]{\left.#1\right|}

    \newtheorem{theorem}{Theorem}[section]

    \let\Re\undefined
    \let\Im\undefined
    \DeclareMathOperator{\Res}{Res}
    \DeclareMathOperator{\Re}{Re}
    \DeclareMathOperator{\Im}{Im}
    \DeclareMathOperator{\Log}{Log}
    \DeclareMathOperator{\Arg}{Arg}
    \DeclareMathOperator{\Tr}{Tr}
    \DeclareMathOperator{\E}{E}
    \DeclareMathOperator{\Var}{Var}
    \DeclareMathOperator*{\argmin}{argmin}
    \DeclareMathOperator*{\argmax}{argmax}
    \DeclareMathOperator{\sgn}{sgn}
    \DeclareMathOperator{\diag}{diag\;}

    \DeclarePairedDelimiter\bra{\langle}{\rvert}
    \DeclarePairedDelimiter\ket{\lvert}{\rangle}
    \DeclarePairedDelimiter\abs{\lvert}{\rvert}
    \DeclarePairedDelimiter\ev{\langle}{\rangle}
    \DeclarePairedDelimiter\p{\lparen}{\rparen}
    \DeclarePairedDelimiter\s{\lbrack}{\rbrack}
    \DeclarePairedDelimiter\z{\lbrace}{\rbrace}

    % \everymath{\displaystyle} % biggify limits of inline sums and integrals
    \tikzstyle{circ} % usage: \node[circ, placement] (label) {text};
        = [draw, circle, fill=white, node distance=3cm, minimum height=2em]
    \definecolor{commentgreen}{rgb}{0,0.6,0}
    \lstset{
        basicstyle=\ttfamily\footnotesize,
        frame=single,
        numbers=left,
        showstringspaces=false,
        keywordstyle=\color{blue},
        stringstyle=\color{purple},
        commentstyle=\color{commentgreen},
        morecomment=[l][\color{magenta}]{\#}
    }

\begin{document}

\def\Snospace~{\S{}} % hack to remove the space left after autorefs
\renewcommand*{\sectionautorefname}{\Snospace}
\renewcommand*{\appendixautorefname}{\Snospace}
\renewcommand*{\figureautorefname}{Fig.}
\renewcommand*{\equationautorefname}{Eq.}
\renewcommand*{\tableautorefname}{Tab.}

\section{Hamiltonians and EOM}

\subsection{Toy Problem}

Consider simplest spin Hamiltonian $H = -\vec{B} \cdot \vec{s}$. It's clear that
if we set up initial conditions $\vec{s}$ misaligned from $\vec{B}$, it will
simply spin around $\vec{B}$, which is fixed. Thus, let $\hat{B} \cdot \hat{s} =
\cos \theta$ the angle between the two, and let $\phi$ measure the azimuthal
angle.

We claim that $\cos \theta, \phi$ are canonical variables. Since $\phi$ is
ignorable, immediately $\rd{\theta}{t} = \rd{\cos \theta}{t} = -\pd{H}{\phi} =
0$, while $\rd{\phi}{t} = \pd{H}{(\cos \theta)} = Bs$ tells us the rate at which
the spin precesses around $\vec{B}$.

\subsection{Cassini State Hamilttonian}

This Hamiltonian is Kassandras Eq.\ 13, in the co-rotating frame with the
perturber's angular momentum:
\begin{equation}
    \mathcal{H} = \frac{1}{2}\p*{\hat{s} \cdot \hat{l}}^2
        - \eta \p*{\hat{s} \cdot \hat{l}_p}.
\end{equation}
In this frame, we can choose $\hat{l} \equiv \hat{z}$ fixed, and $\hat{l}_p =
\cos I\hat{z} + \sin I\hat{x}$ fixed as well. Then
\begin{equation*}
    \hat{s} = \cos\theta \hat{z}
        - \sin\theta\p*{\sin \phi \hat{y} + \cos \phi \hat{x}}.
\end{equation*}
We can choose the convention for $\phi = \phi$ azimuthal angle requiring $\phi =
0, \pi$ mean coplanarity between $\hat{s}, \hat{l}, \hat{l}_p$ in the $\hat{x},
\hat{z}$ plane such that $\hat{l}_p, \hat{s}$ lie on the same side of
$\hat{l}$. Then we can evaluate in coordinates
\begin{align*}
    \hat{s} \cdot \hat{l} &= \cos \theta,\\
    \hat{s} \cdot \hat{l}_p
        &= \cos \theta \cos I - \sin I \sin \theta \cos \phi,\\
    \mathcal{H} &= \frac{1}{2}\cos^2\theta
        - \eta \p*{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
\end{align*}
Note that if we take $\cos\theta$ to be our canonical variable, $\sin\theta =
\sqrt{1 - \cos^2\theta}$ can be used.

\end{document}

### 2019-04-09 initial/notes.tex
maybe?

@@
 
+\subsection{Equation of Motion}
+
+Consider Hamilton's equations applied to the Hamiltonian
+\begin{align}
+    \pd{\phi}{t} = -\pd{\mathcal{H}}{(\cos\theta)}
+        &= -\cos\theta + \eta\p*{\cos I + \sin I \cot \theta \cos \phi},\\
+    \pd{\theta}{t} = +\pd{\mathcal{H}}{\phi}
+        &= -\eta \sin I \sin \theta \sin \phi.
+\end{align}
+This can be compared to the original EOM given in Kassandra's Eq.\ 12,
+\begin{equation}
+    \rd{\hat{s}}{t} =
+        \p*{\hat{s} \cdot \hat{l}}\p*{\hat{s} \times \hat{l}}
+            -\eta\p*{\hat{s} \times \hat{l}_p}.
+\end{equation}
+Recalling that $\abs*{\hat{\phi}} = \sin\theta$ (the differential geometry
+result), we can verify the expressions are equivalent for $\phi = \pi$,
+alignment with $\hat{s}, \hat{l}_p$ on the same side of $\hat{l}$ as in her
+Fig.\ 2, checks our signs.
+
 \end{document}

### 2019-04-09 initial/plots/1contours.py

@@ -1,0 +1,37 @@
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif', size=14)
+from utils import roots
+
+def plot_H_for_eta(eta, I=np.radians(20)):
+    '''
+    Hamiltonian is H = 1/2 cos^2(theta) + eta * sin(phi)
+    canonical variables are x = phi, y = cos(theta)
+    '''
+    _x = np.linspace(0, 2 * np.pi, 50)
+    _y = np.linspace(-1, 1, 50)
+    x = np.outer(_x, np.ones_like(_y))
+    y = np.outer(np.ones_like(_x), _y)
+    H = 0.5 * y**2 - eta * (
+        y * np.cos(I) -
+        np.sqrt(1 - y**2) * np.sin(I) * np.cos(x))
+    plt.contour(x, y, H, cmap='RdBu_r')
+
+    thetas, phis = roots(eta, I)
+    colors = ['b', 'g', 'r', 'y'] if len(thetas) == 4 else ['b', 'y']
+    for color, theta, phi in zip(colors, thetas, phis):
+        phi_arr = [phi] if theta > 0 else [phi, phi + 2 * np.pi]
+        for phi in phi_arr:
+            plt.plot(phi, np.cos(theta), '%so' % color, markersize=16)
+    plt.xlabel(r'$\phi$')
+    plt.ylabel(r'$\cos \theta$')
+    plt.savefig('1contour%s.png' % (('%.2f' % eta).replace('.', '_')))
+    plt.clf()
+
+if __name__ == '__main__':
+    # Figures 3b-3e of Kassandra's paper
+    for eta in [0.1, 0.5, 0.561, 2]:
+        plot_H_for_eta(eta)

### 2019-04-09 initial/plots/1countours.py

@@ -1,65 +1,0 @@
-import math
-import numpy as np
-import matplotlib
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-plt.rc('text', usetex=True)
-plt.rc('font', family='serif', size=14)
-import scipy.optimize as opt
-
-def roots(eta, I):
-    ''' returns theta roots from EOM '''
-    f = lambda q: -eta * np.sin(q - I) + np.sin(q) * np.cos(q)
-    try:
-        roots = []
-        # try to root find w/ 4 intervals
-        args_4_arr = [
-            (-np.pi, -np.pi / 2),
-            (-np.pi/2, -np.pi / 4),
-            (-np.pi / 4, 0),
-            (0, np.pi),
-        ]
-        for args in args_4_arr:
-            roots.append(opt.brentq(f, *args))
-        return ['b', 'g', 'r', 'y'], np.array(roots)
-
-    # throws ValueError when no zero in brackets
-    except ValueError:
-        roots = []
-        # if not, fallback to only 2
-        args_2_arr = [
-            (-np.pi, 0),
-            (0, np.pi),
-        ]
-        for args in args_2_arr:
-            roots.append(opt.brentq(f, *args))
-        return ['b', 'y'], np.array(roots)
-
-def plot_H_for_eta(eta, I=math.radians(20)):
-    '''
-    Hamiltonian is H = 1/2 cos^2(theta) + eta * sin(phi)
-    canonical variables are x = phi, y = cos(theta)
-    '''
-    _x = np.linspace(0, 2 * np.pi, 50)
-    _y = np.linspace(-1, 1, 50)
-    x = np.outer(_x, np.ones_like(_y))
-    y = np.outer(np.ones_like(_x), _y)
-    H = 0.5 * y**2 - eta * (
-        y * np.cos(I) -
-        np.sqrt(1 - y**2) * np.sin(I) * np.cos(x))
-    plt.contour(x, y, H, cmap='RdBu_r')
-
-    colors, fixed_thetas = roots(eta, I)
-    for color, theta in zip(colors, fixed_thetas):
-        phis = [np.pi] if theta > 0 else [0, 2 * np.pi]
-        for phi in phis:
-            plt.plot(phi, np.cos(theta), '%so' % color, markersize=16)
-    plt.xlabel(r'$\phi$')
-    plt.ylabel(r'$\cos \theta$')
[…]

### 2019-04-09 initial/plots/utils.py

@@ -1,0 +1,33 @@
+import numpy as np
+import scipy.optimize as opt
+
+def get_phis(thetas):
+    return [np.pi if q > 0 else 0 for q in thetas]
+
+def roots(eta, I):
+    ''' returns theta roots from EOM '''
+    f = lambda q: -eta * np.sin(q - I) + np.sin(q) * np.cos(q)
+    try:
+        roots = []
+        # try to root find w/ 4 intervals
+        args_4_arr = [
+            (-np.pi, -np.pi / 2),
+            (-np.pi/2, -np.pi / 4),
+            (-np.pi / 4, 0),
+            (0, np.pi),
+        ]
+        for args in args_4_arr:
+            roots.append(opt.brentq(f, *args))
+        return np.array(roots), get_phis(roots)
+
+    # throws ValueError when no zero in brackets
+    except ValueError:
+        roots = []
+        # if not, fallback to only 2
+        args_2_arr = [
+            (-np.pi, 0),
+            (0, np.pi),
+        ]
+        for args in args_2_arr:
+            roots.append(opt.brentq(f, *args))
+        return np.array(roots), get_phis(roots)

### 2019-04-09 initial/plots/1contours.py
EOM seems to be correct

@@ -26,7 +26,7 @@ def plot_H_for_eta(ax, eta, I=np.radians(20)):
         phi_arr = [phi] if theta > 0 else [phi, phi + 2 * np.pi]
         for phi in phi_arr:
             ax.plot(phi, np.cos(theta), '%so' % color, markersize=10)
-    ax.set_title('(I, Eta)=($%d^\circ$, %.3f)' % (np.degrees(I), eta),
+    ax.set_title(r'(I, $\eta$)=($%d^\circ$, %.3f)' % (np.degrees(I), eta),
                  fontsize=8)
     ax.set_xticks([0, np.pi, 2 * np.pi])
 

### 2019-04-09 initial/notes.tex
EOM seems to be correct
foo

--- 2019-04-04 initial/notes.tex
@@
 
+\subsection{Equation of Motion}
+
+The correct EOM comes from Kassandra's Eq.\ 12:
+\begin{align*}
+    \rd{\hat{s}}{t} ={}&
+        \p*{\hat{s} \cdot \hat{l}}\p*{\hat{s} \times \hat{l}}
+            -\eta\p*{\hat{s} \times \hat{l}_p},\\
+        ={}& \cos\theta \s*{
+            \hat{x}\p*{-\sin\theta \sin\phi}
+            - \hat{y}\p*{-\sin\theta \cos\phi}}\\
+            &- \eta \s*{
+                \hat{x}\p*{-\sin\theta \sin \phi \cos I}
+                - \hat{y}\p*{-\sin \theta \cos \phi \cos I
+                    - \cos \theta\sin I}
+                + \hat{z}\p*{+\sin\theta \sin \phi \sin I}},\\
+        ={}& \s*{-\sin\theta \sin\phi \cos\theta
+            + \eta \sin \theta \sin \phi \cos I}\hat{x}
+            + \s*{\cos\theta \sin\theta \cos\phi
+                - \eta\p*{\sin\theta \cos\phi \cos I
+                    + \cos\theta \sin I}}\hat{y}\\
+            &+ \s*{-\eta\sin\theta \sin\phi \sin I}\hat{z}.
+\end{align*}
+
+Alternatively, consider Hamilton's equations applied to the Hamiltonian:
+\begin{align}
+    \pd{\phi}{t} = \pd{\mathcal{H}}{(\cos\theta)}
+        &= \cos\theta - \eta\p*{\cos I + \sin I \cot \theta \cos \phi},\\
+    \pd{(\cos \theta)}{t} = -\pd{\mathcal{H}}{\phi}
+        &= +\eta \sin I \sin \theta \sin \phi.
+\end{align}
+This seems to produce the same trajectories as Kassandra's EOM\@!
+
+We can check the stability of each of the equilibria of the EOM, there should be
+four corresponding to the four Cassini states:
+
 \end{document}

### 2019-04-11 initial/notes.tex
check in notes including tidal

@@
 \end{align}
-This seems to produce the same trajectories as Kassandra's EOM\@!
+This produces the same trajectories as the Cartesian EOM, so this is correct.
+However, since $\pd{\phi}{t} \propto 1/\sin\theta$, this is not a desirable
+system of equations to use, as they are very stiff near $\theta \approx 0$.
 
@@
 
+\subsection{Tidal Dissipation}
+
+We can add a tidal dissipation term; we write it in form
+$\p*{\rd{\hat{s}}{t}}_{tide} = \epsilon \hat{s} \times \p*{\hat{l} \times
+\hat{s}}$. Expanding, $\p*{\rd{\hat{s}}{t}}_{tide} = \epsilon \p*{\hat{z} -
+s_z\hat{s}}$.
+
 \end{document}

### 2019-04-16 initial/notes.tex
update notes

@@
 \begin{align*}
-    \rd{\hat{s}}{t} ={}&
+    \rd{\hat{s}}{t} &=
         \p*{\hat{s} \cdot \hat{l}}\p*{\hat{s} \times \hat{l}}
             -\eta\p*{\hat{s} \times \hat{l}_p},\\
-        ={}& \cos\theta \s*{
-            \hat{x}\p*{-\sin\theta \sin\phi}
-            - \hat{y}\p*{-\sin\theta \cos\phi}}\\
-            &- \eta \s*{
-                \hat{x}\p*{-\sin\theta \sin \phi \cos I}
-                - \hat{y}\p*{-\sin \theta \cos \phi \cos I
-                    - \cos \theta\sin I}
-                + \hat{z}\p*{+\sin\theta \sin \phi \sin I}},\\
-        ={}& \s*{-\sin\theta \sin\phi \cos\theta
-            + \eta \sin \theta \sin \phi \cos I}\hat{x}
-            + \s*{\cos\theta \sin\theta \cos\phi
-                - \eta\p*{\sin\theta \cos\phi \cos I
-                    + \cos\theta \sin I}}\hat{y}\\
-            &+ \s*{-\eta\sin\theta \sin\phi \sin I}\hat{z}.
+        &= \p*{s_ys_z - \eta s_y\cos(I)}\hat{x}
+            - \p*{s_xs_z + \eta \p*{s_x\cos I - s_z\sin I}}\hat{y}
+            + \eta s_y \sin(I)\hat{z}.
 \end{align*}
@@
 
-We can check the stability of each of the equilibria of the EOM, there should be
-four corresponding to the four Cassini states:
-
 \subsection{Tidal Dissipation}
@@
 $\p*{\rd{\hat{s}}{t}}_{tide} = \epsilon \hat{s} \times \p*{\hat{l} \times
-\hat{s}}$. Expanding, $\p*{\rd{\hat{s}}{t}}_{tide} = \epsilon \p*{\hat{z} -
-s_z\hat{s}}$.
+\hat{s}}$. Expanding,
+\begin{align}
+    \p*{\rd{\hat{s}}{t}}_{tide} &= \epsilon \p*{\hat{z} - s_z\hat{s}}
+        ,\nonumber\\
+        &= \epsilon \p*{-s_z s_x\hat{x} - s_zs_y\hat{y} + \p*{1 - s_z^2}
+            \hat{z}}.
+\end{align}
+We run numerical simulations for weaker $\epsilon \ll \eta \ll 1$ and stronger
+$\epsilon \lesssim \eta \ll 1$.
+
+We can seek equilibria of the the system including tides, which requires
+\begin{align*}
+    0 &= s_ys_z - \eta s_y\cos I - \epsilon s_zs_x,\\
+    0 &= -s_xs_z - \eta\p*{s_x \cos I - s_z \sin I} - \epsilon s_zs_y,\\
+    0 &= \eta s_y\sin(I) + \epsilon \p*{1 - s_z^2}.
+\end{align*}
+We expect at least two equilibria, based on the simulations: one near $s_z
+\approx 1$ and one $s_z \approx 0$.
+
+For near alignment/near Cassini state $1$, $1 - s_z \sim 1 - s_{\perp}^2$, so we
+can set $s_z = 1$ to first order: $s_y - \epsilon s_x - \eta s_y \cos I = -s_x -
+\eta\p*{s_x \cos I - \sin I} - \epsilon s_y = \eta s_y \sin I = 0$. This can be
+satisfied if we set $s_x = \tan(I) \ll 1, s_y = \mathcal{O}\p*{\epsilon s_x}$;
+this coarsely corresponds to Cassini state $1$.
+
+The other solution should be near Cassini state $2$, where $s_x \approx 1$;
+dropping second order terms forces $\eta s_y + \epsilon s_z = -s_z -
+\eta\p*{\cos I - s_z\sin I} = \eta s_y \sin(I) + \epsilon = 0$. This can thus be
+satisfied for $s_y \approx -\frac{\epsilon}{\eta \sin(I)}$. Thus, this explains
+why as $\epsilon$ is increased, we first start to get points that don't converge
+to Cassini state $2$ in the absence of tides, before starting to see points that
+fail to converge to Cassini state $1$.
 

### 2019-04-19 initial/notes.tex
group meeting presentation

@@
 
+\section{Separatrix Hopping}
+
+Inspired by G\&H, heteroclinic orbits are topologically unstable for any nonzero
+perturbation, but opened width $\sim$ perturbation parameter.
+
+We zoom in on Cassini State $4$, which has $\cos \theta \approx 0, \phi = 0$. In
+particular, by using equations of motion
+\begin{align}
+    \pd{\phi}{t} &= \cos \theta - \eta\p*{\cos I + \sin I \cot \theta \cos \phi}
+        ,\\
+    \pd{\theta}{t} &= -\eta \sin I \sin \phi - \s*{\epsilon \sin \theta},
+\end{align}
+we can compute $\theta_4 \approx -\frac{\pi}{2} +\frac{\eta \sin I}{1 + \eta
+\cos I}, \phi_4 = 0$ in the $\epsilon = 0$ limit (the other solution is
+$\theta_2 \approx +\frac{\pi}{2} - (\dots)$). Indeed the signs are correct:
+near $\theta \approx \frac{\pi}{2}, \phi \approx 0$ we have EOM
+$\dot{\delta\phi}_4 \approx -\delta \theta_4$ while $\dot{\delta \theta_4}
+\approx -\eta \sin I \delta \phi_4$ which is unstable.
+
+Substituting in perturbatively for nonzero $\epsilon$ in $\pd{\theta}{t}$ gives
+$\delta \phi_4 = +\frac{\epsilon}{\eta \sin I}, \delta \theta_4 = 0$. This is in
+agreement with Dong's result. Note that $\delta \theta_2 = -\frac{\epsilon}{\eta
+\sin I}$, which I saw in my simulations.
+
+This implies that the stable manifolds of the two saddle points, which once
+overlapped with each other's unstable manifolds (creating a heteroclinic orbit)
+now are offset from one another by distance $D \sim \frac{\epsilon}{\eta \sin
+I}$. The question is how likely it is to thread the needle.
+
+Consider that, very near CS4, the angle of incidence on the desired gap is
+roughly $\tan \psi \approx \psi = \frac{\Delta \theta}{\Delta \phi}$. Over the
+course of one orbit, $\Delta \phi$ changes by $2\pi$, while $\Delta \theta \sim
+\epsilon \sin \theta T$ where $T$ is the period of an orbit. Examining the data,
+$T \sim 50$, and so $\frac{\Delta \theta}{\Delta \phi} \sim \frac{2\pi}{\epsilon
+(50)}$.
+
+The effective probability of threading the opened gap between the
+stable/unstable manifolds is then just $P \propto D\sin \psi \sim
+\frac{2\pi}{T\p*{\eta \sin I}}$. Plugging in some observational values $T \sim
+50, \eta = 0.1, I = 20^\circ$ gives $P \propto 0.13$. In reality, I find it
+asymptotes to $\sim 0.08$, so the constant of proportionality is of order unity.
+Not bad given the really crappy $\psi \sim
+\frac{\ev*{\dot{\theta}}}{\dot{\phi}}$ argument.
+
 \end{document}

### 2019-04-19 initial/plots/3stats.py

@@ -147,8 +147,8 @@ def run_for_tide(tide=1e-3,
     for q, phi, belows, conv_pts, ax in\
             zip(qs, phis, below_convs, conv_data, axs):
         ax.set_title(
-            r'$(\phi_0, \theta_0, P_T, P_<) = (%.2f, %.2f) (%.3f, %.3f)$'
-            % (get_phi(q), q, len(conv_pts) / tot_pts, belows / tot_belows),
+            r'$(P_T, P_<) = (%.3f, %.3f)$'
+            % (len(conv_pts) / tot_pts, belows / tot_belows),
             fontsize=8)
 
     for (q0, _phi0), (x, y, z) in zeros:
@@ -164,9 +164,8 @@ def run_for_tide(tide=1e-3,
                    'mo',
                     markersize=4)
         axs[3].set_title(
-            r'$(\phi_0, \theta_0, P_T, P_<) = (%.2f, %.2f) (%.3f, %.3f)$'
-            % (get_phi(qs[3]), qs[3],
-               len(zeros) / tot_pts, belows_zero / tot_belows),
+            r'$(P_T, P_<) = (%.3f, %.3f)$'
+            % (len(zeros) / tot_pts, belows_zero / tot_belows),
             fontsize=8)
         ln1 = mlines.Line2D([], [], color='b', marker='o', markersize=0.5,
                             linewidth=0, label='Init')
@@ -181,13 +180,13 @@ def run_for_tide(tide=1e-3,
     plt.savefig('3stats%s.png' % prefix, dpi=400)
 
 if __name__ == '__main__':
-    # run_for_tide(tide=3e-2)
-    # run_for_tide(tide=1e-2)
-    # run_for_tide(tide=3e-3)
-    # run_for_tide(tide=1e-3)
-    # run_for_tide(tide=3e-4, NUM_RUNS=10000)
-    # run_for_tide(tide=1e-4, NUM_RUNS=10000)
-    # run_for_tide(tide=3e-5, NUM_RUNS=10000)
+    run_for_tide(tide=3e-2)
+    run_for_tide(tide=1e-2)
+    run_for_tide(tide=3e-3)
+    run_for_tide(tide=1e-3)
+    run_for_tide(tide=3e-4, NUM_RUNS=10000)
+    run_for_tide(tide=1e-4, NUM_RUNS=10000)
[…]

### 2019-04-22 initial/notes.tex
update notes

@@
 
+\subsection{Separatrix Area}
+
+We can estimate the area enclosed by the separatrix, as shown in
+\autoref{fig:1contours}. Note that the separatrix joins Cassini State 4 to its
+$+ 2\pi$ image.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.6\textwidth]{plots/1contours.png}
+    \caption{Separatrix for various values of $\eta$.}\label{fig:1contours}
+\end{figure}
+
+We notate $\mu = \cos\theta$; note that CS4 is $\mu_4 \approx \frac{\eta \cos
+I}{1 + \eta \sin I} \approx \eta \cos I$. Setting the Hamiltonian equal to its
+value at CS4 gives
+\begin{align*}
+    H_4 &\equiv H\p*{\mu_4, \phi_4}
+        \approx \frac{\mu_4^2}{2} - \eta \mu_4 \cos I + \eta \sin I,\\
+        &= -\eta^2\cos^2 I + \eta \sin I,\\
+    H(\mu_{sep}, \phi_{sep})
+        &= H_4 = \eta \sin I \cos \phi + \frac{\mu^2}{2} - \eta \mu \cos I
+            + \mathcal{O}(\eta^3),\\
+    0 &\approx \frac{\mu_{sep}^2}{2} - \eta \mu_{sep} \cos I
+        - \eta \sin I\p*{1 - \cos \phi_{sep}} + \eta^2\cos^2I,\\
+    \mu_{sep}\p*{\phi} &\approx \sqrt{2\eta \sin I\p*{1 - \cos \phi}}
+        + \mathcal{O}(\eta).
+\end{align*}
+
+We can then easily compute the area enclosed by the separatrix
+\begin{align}
+    A_{sep} &= \int\limits_0^{2\pi}2\mu_{sep}\;\mathrm{d}\phi,\nonumber\\
+        &\approx 16\sqrt{\eta \sin I}.
+\end{align}
+For $\eta = 0.1, I = 20^\circ$, this predicts $\frac{A_{sep}}{A_{T}} \approx
+0.235$, which is pretty close to my numerically calculated $\frac{A_{sep}}{A_T}
+= 0.229$.
+
 \subsection{Tidal Dissipation}
@@
 \end{align}
-we can compute $\theta_4 \approx -\frac{\pi}{2} +\frac{\eta \sin I}{1 + \eta
-\cos I}, \phi_4 = 0$ in the $\epsilon = 0$ limit (the other solution is
+we can compute $\theta_4 \approx -\frac{\pi}{2} +\frac{\eta \cos I}{1 + \eta
+\sin I}, \phi_4 = 0$ in the $\epsilon = 0$ limit (the other solution is
 $\theta_2 \approx +\frac{\pi}{2} - (\dots)$). Indeed the signs are correct:
@@
 
+\subsection{Melnikov Distance}
+
+We notice that the separatrix is a heteroclinic orbit, or a saddle connection,
+in the dissipation free problem. Introducing dissipation breaks the saddle
+connection by a distance that can be estimated with the Melnikov distance. This
+is G\&H Equation 4.5.11 or something:
+\begin{align}
+    d(t_0) &= \frac{\epsilon M(t_0)}{\abs*{f(q^0(0))}} + \mathcal{O}(\epsilon^2)
+        ,\\
+    M(t_0) &= \int\limits_{-\infty}^\infty
+        \s*{f \times g}_{hetero}\;\mathrm{d}t.
+\end{align}
+We evaluate the Melnikov integral $M(t_0)$ on the heteroclinic orbit. Note that
+since in our problem our perturbation $g$ is time-independent, so too is the
+Melnikov integral $M(t_0) = M$.
+
+Let's apply this to the Cassini state Hamiltonian w/ dissipation. We first write
+down our EOM in Melnikov form (we use canonical variables $\mu, \phi$):
+\begin{align}
+    \rd{\hat{s}}{t}
+        &= \underbrace{
+            \pd{\mathcal{H}}{\mu}\hat{\phi} - \pd{\mathcal{H}}{\phi}\hat{\mu}}_f
+            + \epsilon \underbrace{\p*{1 - \mu^2}\hat{\mu}}_g.
+\end{align}
+Then $f \times g = f_\phi g_\mu = \pd{\mathcal{H}}{\mu}\p*{1 - \mu^2}$. We then
+want to integrate this along the heteroclinic orbit. We can make change of
+variables
+\begin{equation}
+    M = \int\limits_0^{2\pi}\pd{\mathcal{H}}{\mu}
+        \p*{1 - \mu^2}\p*{\pd{\phi}{t}}^{-1}\;\mathrm{d}\phi.
+\end{equation}
+But thankfully, $\pd{\mathcal{H}}{\mu} = \pd{\phi}{t}$ in the absence of
+dissipation, and so $M = 2\pi\p*{1 - \mu^2} \approx 2\pi\p*{1 - 2\eta \sin I}$.
+Thus, the Melnikov distance at point $q^0$, a point on the heteroclinic
+orbit of the unperturbed Hamiltonian, is just
+\begin{equation}
+    d(q^0) = \frac{2\pi \epsilon\p*{1 - 2\eta \sin I}}{\abs*{f(q^0)}}.
+\end{equation}
+
 \end{document}

### 2019-04-22 initial/notes.tex
more update notes

@@
 stable/unstable manifolds is then just $P \propto D\sin \psi \sim
-\frac{2\pi}{T\p*{\eta \sin I}}$. Plugging in some observational values $T \sim
-50, \eta = 0.1, I = 20^\circ$ gives $P \propto 0.13$. In reality, I find it
-asymptotes to $\sim 0.08$, so the constant of proportionality is of order unity.
-Not bad given the really crappy $\psi \sim
-\frac{\ev*{\dot{\theta}}}{\dot{\phi}}$ argument.
+\frac{2\pi}{T\p*{\eta \sin I}}$. According to later analysis, this should really
+be $\frac{2\pi}{T}$. Plugging in some observational values $T \sim 50$ for $\eta
+= 0.1$gives $P \propto 0.13$. In reality, I find it asymptotes to $\sim 0.08$,
+so the constant of proportionality is of order unity. Not bad given the really
+crappy $\psi \sim \frac{\ev*{\dot{\theta}}}{\dot{\phi}}$ argument.
 
@@
 
+We compute the maximum $\abs*{f(q^0)}$, which occurs at $\phi = \pi$, and we
+find the expected $f \approx \sqrt{4\eta \sin I}$.
+
 \end{document}

### 2019-04-23 initial/notes.tex
maybe

@@
         &= \cos \theta \cos I - \sin I \sin \theta \cos \phi,\\
-    \mathcal{H} &= \frac{1}{2}\cos^2\theta
-        - \eta \p*{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
+    \mathcal{H} &= -\frac{1}{2}\cos^2\theta
+        + \eta \p*{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
 \end{align*}
@@
     \pd{\phi}{t} = \pd{\mathcal{H}}{(\cos\theta)}
-        &= \cos\theta - \eta\p*{\cos I + \sin I \cot \theta \cos \phi},\\
+        &= -\cos\theta + \eta\p*{\cos I + \sin I \cot \theta \cos \phi},\\
     \pd{(\cos \theta)}{t} = -\pd{\mathcal{H}}{\phi}
-        &= +\eta \sin I \sin \theta \sin \phi.
+        &= -\eta \sin I \sin \theta \sin \phi.\label{eq:H_eom}
 \end{align}
@@
 system of equations to use, as they are very stiff near $\theta \approx 0$.
+
+\subsection{Cassini States}
+
+The zeros to \autoref{eq:H_eom} are the Cassini states; we will go to canonical
+variables $\mu = \cos\theta$. We can immediately see that $\sin\phi = 0$ is
+necessary, so $\cos \phi = \pm 1$ and we need only solve for $\pd{\phi}{t} = 0$.
+We can furthermore separate the problem into two regimes, $\eta \ll 1$ and $\eta
+\gg 1$.
+
+For $\eta \ll 1$, it is clear that there will be two solutions near $\mu^2 = 1$
+and two solutions near $\mu = 0$:
+\begin{itemize}
+    \item For $\mu = 1 - \frac{\theta^2}{2}$, the dominant terms are
+        $\pd{\phi}{t} \approx -1 + \eta \sin I \frac{1}{\theta} = 0$,
+        where we've taken $\cos \phi = +1$ and $\phi = 0$. This forces $\theta
+        = \eta \sin I$.
+
+    \item Similarly, for $\mu = -1 + \frac{\epsilon^2}{2}$, $\phi = 0$ and
+        $\epsilon = \eta \sin I$ again. This actually corresponds to $\theta =
+        \pi - \eta \sin I$.
+
+    \item For $\mu \approx 0$, we have instead $\pd{\phi}{t} = -\mu\p*{1 - \eta
+        \sin I \cos \phi} + \eta \cos I = 0$. This forces $\mu_\pm = \frac{\eta
+        \cos I}{1 \pm \eta \sin I}$, where $\phi_{\pm} = \pi, 0$ respectively.
+
+        Note that $\phi = 0, \mu \approx 0$ is conventionally CS4. The
+        linearization locally has form $\pd{\delta \phi}{t} = -\delta \mu\p*{1 -
+        \eta \sin I}$ and $\pd{\mu}{t} = -\eta \sin I$, so the eigenvalues are
+        $\approx \mp \sqrt{\eta \sin I}$, and the two eigenvectors are $\p*{1,
+        \pm \sqrt{\eta \sin I}}$.
+\end{itemize}
+
+For $\eta \gg 1$, the solutions obviously just come from $\cos I \pm \sin I \cot
+\theta = 0$, which are just $\sin (I \pm \theta) = 0$
 
@@
 We notate $\mu = \cos\theta$; note that CS4 is $\mu_4 \approx \frac{\eta \cos
-I}{1 + \eta \sin I} \approx \eta \cos I$. Setting the Hamiltonian equal to its
+I}{1 - \eta \sin I} \approx \eta \cos I$. Setting the Hamiltonian equal to its
 value at CS4 gives
@@
     H_4 &\equiv H\p*{\mu_4, \phi_4}
-        \approx \frac{\mu_4^2}{2} - \eta \mu_4 \cos I + \eta \sin I,\\
-        &= -\eta^2\cos^2 I + \eta \sin I,\\
+        \approx -\frac{\mu_4^2}{2} + \eta \mu_4 \cos I - \eta \sin I,\\
+        &= +\eta^2\cos^2 I - \eta \sin I,\\
     H(\mu_{sep}, \phi_{sep})
-        &= H_4 = \eta \sin I \cos \phi + \frac{\mu^2}{2} - \eta \mu \cos I
-            + \mathcal{O}(\eta^3),\\
+        &= H_4 = -\eta \sin I \cos \phi_{sep} - \frac{\mu_{sep}^2}{2} + \eta
+            \mu_{sep} \cos I + \mathcal{O}(\eta^3),\\
     0 &\approx \frac{\mu_{sep}^2}{2} - \eta \mu_{sep} \cos I
@@
 
-We zoom in on Cassini State $4$, which has $\cos \theta \approx 0, \phi = 0$. In
-particular, by using equations of motion
+\subsection{Try 1: Qualitative}
+
+We zoom in on Cassini State $4$, which has $\theta_4 =
+-\frac{\pi}{2} + \frac{\eta \cos I}{1 - \eta \sin I}, \mu_4 = \frac{\eta \cos
+I}{1 - \eta \sin I}, \phi_4 = 0$. Then, using
+equations of motion
 \begin{align}
-    \pd{\phi}{t} &= \cos \theta - \eta\p*{\cos I + \sin I \cot \theta \cos \phi}
-        ,\\
-    \pd{\theta}{t} &= -\eta \sin I \sin \phi - \s*{\epsilon \sin \theta},
+    \pd{\phi}{t} &= \mu - \eta\p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}}
+        \cos \phi} ,\\
+    \pd{\mu}{t} &= -\eta \sin I \sin \phi + \s*{\epsilon \p*{1 - \mu^2}},
 \end{align}
-we can compute $\theta_4 \approx -\frac{\pi}{2} +\frac{\eta \cos I}{1 + \eta
-\sin I}, \phi_4 = 0$ in the $\epsilon = 0$ limit (the other solution is
-$\theta_2 \approx +\frac{\pi}{2} - (\dots)$). Indeed the signs are correct:
-near $\theta \approx \frac{\pi}{2}, \phi \approx 0$ we have EOM
-$\dot{\delta\phi}_4 \approx -\delta \theta_4$ while $\dot{\delta \theta_4}
-\approx -\eta \sin I \delta \phi_4$ which is unstable.
-
-Substituting in perturbatively for nonzero $\epsilon$ in $\pd{\theta}{t}$ gives
-$\delta \phi_4 = +\frac{\epsilon}{\eta \sin I}, \delta \theta_4 = 0$. This is in
-agreement with Dong's result. Note that $\delta \theta_2 = -\frac{\epsilon}{\eta
-\sin I}$, which I saw in my simulations.
+we can perturbatively require $\pd{\theta}{t} = 0$ for $\epsilon \neq 0$. This
+corresponds to $\eta \sin I \sin \p*{\phi_4 + \delta \phi} \approx \epsilon$, or
+$\delta \phi_4 = +\frac{\epsilon}{\eta \sin I}$. This is in agreement with
+Dong's result. Note that $\delta \theta_2 = -\frac{\epsilon}{\eta \sin I}$,
+which I saw in my simulations.
 
@@
 
-\subsection{Melnikov Distance}
+\subsection{Try 2: Melnikov Distance}
 
@@
 \end{align}
+
+This is not a hard formula to understand; along the separatrix, motion is
+dominated by $f$, but the perpendicular component adds up to contribute to a
+total ``perpendicular distance away from the original separatrix'' necessary to
+hit the saddle point, at least intuitively.
+
 We evaluate the Melnikov integral $M(t_0)$ on the heteroclinic orbit. Note that
@@
 \end{equation}
+Note that the maximum value $\abs*{f(q^0)}$, which occurs at $\phi = \pi$, is
+just $f \approx \sqrt{4\eta \sin I}$.
 
-We compute the maximum $\abs*{f(q^0)}$, which occurs at $\phi = \pi$, and we
-find the expected $f \approx \sqrt{4\eta \sin I}$.
+It proves to be a bit difficult to make quantitative predictions though, since
+the phase diagram is very smushed where $f$ is large, and $d$ is rather
+inaccurate where $f$ is small. Let's think about a Poincar\'e map instead.
+
+\subsection{Try 3: Poincar\'e Section}
+
+Let's consider the Poincar\'e section every time $\phi = \phi_4$ as the
+trajectory subject to tidal dissipation is moving $\theta < \theta_4 \to
+\theta_4$. To provide an estimate of $\Delta \theta(\theta) = \theta_{n - 1} -
+\theta_n$, this is just $\epsilon T$ where $T$ is the time elapsed between
+$\theta_n, \theta_{n + 1}$, the period of the orbit. $T$ is dominated by when
+$\pd{\phi}{t} \ll 1$ though, or where the orbit is close to the saddle point.
+
+Consider when $\mu = \mu_4 - \delta \mu$
 

### 2019-04-23 initial/plots/5poincare.py

@@ -17,17 +17,18 @@ from utils import to_cart, get_dydt, to_ang, is_below, get_phis, get_phi,\
 from scipy.integrate import solve_ivp
 from scipy.optimize import brentq
 
-def get_poincare(t, sol, interp):
+def get_poincare(I, eta, tide, t, sol, interp):
     '''
-    cos(theta, phi = 0) is equivalent to z(y = 0), x = -1
+    cos(theta, phi = phi_cross) is equivalent to z(y = y_cross), x = -1
     '''
     x, y, z = sol
+    y_cross = np.sin(tide / (eta * np.sin(I)))
 
     cross_zs = []
     for idx in range(len(y) - 1):
-        if y[idx] > 0 and y[idx + 1] < 0 and x[idx] < 0:
-            y_interp = lambda t: interp(t)[1]
-            t0 = brentq(y_interp, t[idx], t[idx + 1])
+        if y[idx] > -y_cross and y[idx + 1] < -y_cross and x[idx] < 0:
+            zero_interp = lambda t: interp(t)[1] + y_cross
+            t0 = brentq(zero_interp, t[idx], t[idx + 1])
             z_exact = interp(t0)[2]
             cross_zs.append(z_exact)
     return cross_zs
@@ -77,7 +78,8 @@ def plot_map(eta, nbins, n_thresh=10):
                   (sim_num, len(hop_idxs) + len(q_zeros)))
 
             if s[2] > q[3]:
-                q_poincare.append(get_poincare(ret.t, ret.y, ret.sol))
+                q_poincare.append(
+                    get_poincare(I, eta, tide, ret.t, ret.y, ret.sol))
             else:
                 print('(%.5f, %.5f, %.5f) did not converge' %
                       (s[0], s[1], s[2]))
@@ -97,14 +99,17 @@ def plot_map(eta, nbins, n_thresh=10):
                        if len(l) >= 2 and l[-1] > lf])
 
     # compute the smallest element in the first bin w/ a reasonable number
-    def plot_and_get_minmax(q_arr, label):
-        n, bins, _ = plt.hist(q_arr.flatten(), bins=nbins, label=label)
+    def plot_and_get_minmax(q_arr, label, **kwargs):
+        n, bins, _ = plt.hist(q_arr.flatten(), bins=nbins, label=label,
[…]

### 2019-04-26 initial/notes.tex
stash

@@
         linearization locally has form $\pd{\delta \phi}{t} = -\delta \mu\p*{1 -
-        \eta \sin I}$ and $\pd{\mu}{t} = -\eta \sin I$, so the eigenvalues are
-        $\approx \mp \sqrt{\eta \sin I}$, and the two eigenvectors are $\p*{1,
-        \pm \sqrt{\eta \sin I}}$.
+        \eta \sin I}$ and $\pd{\delta \mu}{t} = -\eta \sin I \delta \phi$, so
+        the eigenvalues are $\approx \mp \sqrt{\eta \sin I}$, and the two
+        eigenvectors are $\p*{1, \pm \sqrt{\eta \sin I}}$.
 \end{itemize}
@@
 
-Consider when $\mu = \mu_4 - \delta \mu$
+Note that $T$ is dominated by the time it spends near the saddle point. We
+showed earlier that near CS4, $\pd{\phi}{t} \approx \delta \mu$ where $\delta
+\mu = \mu - \mu_4$. Thus, we might surmise $\Delta \theta(\theta) \propto
+\theta^{-1}$ for sufficiently small $\theta - \theta_4$. Far away, $T$ is
+roughly constant and $\Delta \theta(\theta)$ is roughly constant.
+
+What is ``far away''? Well, it probably depends on how affected our trajectory
+is by the separatrix; far away from the saddle point, we go along contours of
+roughly constant $\theta$, while close by we follow the separatrix pretty well.
+We computed earlier that $\mu_{sep} \sim \sqrt{4\eta \sin I}$, so we might
+expect $\mu > \mu_{sep}, \Delta \mu \sim C$, while $\mu < \mu_{sep}, \Delta
+\mu \sim \delta \mu^{-1}$.
+
+My $\mu > \mu_{sep}$ simulations don't seem to work very well, so I'll focus on
+the $\delta \mu^{-1}$ case. In this case, define $\delta \mu_c: \Delta
+\mu\p*{\delta \mu_c} = -\delta \mu_c$, i.e.\ the point that jumps immediately to
+the saddle point. Furthermore, assume the inbound distribution is flat between
+$\delta \mu_c, f^{-1}\p*{\delta \mu_c}$. TODO\@: empirically, $\mu_c \sim
+\epsilon T$ is \emph{flat} with $\eta$, probably just because we're not getting
+sufficiently close to the saddle point for the $\propto \sqrt{\eta}$ to kick in.
+
+Then, we can compare the empirical Poincar\'e section of the points that cross
+the separatrix versus the total predicted interval width $\delta \mu_c,
+f^{-1}\p*{\delta \mu_c}$; this would predict $7.2\%, 18\%$. This does alright!
+
+Now, one final way to think about this, and I think this is the important one:
+consider if we are some $\delta \mu_0$ at $\phi = 0$ such that we barely hop the
+separatrix; this corresponds to $P_{hop} = \frac{\delta \mu_0}{\mu_c}$. In order
+for $\delta \mu_0$ to be hopping, $\delta \mu_\phi$ must be within $d_\phi
+\approx \frac{2\pi \epsilon}{\mu}$ of the separatrix. We can compute the ratio
+between $\delta \mu_0, \delta \mu_\phi$ by setting their Hamiltonian variations
+equal:
+\begin{align*}
+    \delta H_0 &\approx -\mu_4 \delta \mu_0 + \eta \cos I \delta \mu_0
+        \approx \eta^2 \cos I \sin I \delta \mu_0,\\
+    \delta H_\phi &\approx -\sqrt{4\eta \sin I} \delta \mu_\phi,\\
+    \frac{\delta \mu_\phi}{\delta \mu_0} &\propto
+        \eta^{3/2}\cos I \sqrt{\sin I}.
+\end{align*}
+We can assemble
 

### 2019-04-26 initial/plots/5poincare.py

@@ -33,14 +33,12 @@ def get_poincare(I, eta, tide, t, sol, interp):
             cross_zs.append(z_exact)
     return cross_zs
 
-def plot_map(eta, nbins, n_thresh=10):
+def plot_map(eta, nbins, n_thresh=10, tf=5000, max_sim=20):
     suffix = str(eta).replace('.', '_')
     filename = '3stats3_5_%s.pkl' % suffix
     out_file = '5poincare_%s.pkl' % suffix
     I = np.radians(20)
     tide = 3e-4
-    tf = 5000
-    max_sim = 20
     q, _ = roots(I, eta)
 
     if not os.path.exists(out_file):
@@ -69,15 +67,17 @@ def plot_map(eta, nbins, n_thresh=10):
         dydt = get_dydt(I, eta, tide)
         for sim_num, angs in enumerate(inits):
             s = to_cart(*angs)
+            qsol, phisol = to_ang(*s)
             for i in range(max_sim):
-                ret = solve_ivp(dydt, [0, tf], s, max_step=0.1, dense_output=True)
+                ret = solve_ivp(dydt, [0, tf], s, rtol=1e-6, dense_output=True)
                 s = ret.y[:, -1]
-                if s[2] > q[3]: # if z coord > CS4's z coord
+                qsol, phisol = to_ang(*s)
+                if is_inside(I, eta, [qsol], [phisol]):
                     break
             print('Finishing sim num %d/%d' %
                   (sim_num, len(hop_idxs) + len(q_zeros)))
 
-            if s[2] > q[3]:
+            if is_inside(I, eta, [qsol], [phisol]):
                 q_poincare.append(
                     get_poincare(I, eta, tide, ret.t, ret.y, ret.sol))
             else:
@@ -107,9 +107,9 @@ def plot_map(eta, nbins, n_thresh=10):
             q_arr.max(), max(n), sum(n[first_idx: ])
 
     min1, max1, max_ct1, n_tot1 = plot_and_get_minmax(
-        q_arr, 'Last', color='r')
+        q_arr, 'Last', color='tab:blue')
     min2, max2, max_ct2, n_tot2 = plot_and_get_minmax(
-        q2_arr, 'Penult.', color='b')
+        q2_arr, 'Penult.', color='tab:orange')
     xmin = min(min1, min2)
[…]

### 2019-05-02 initial/notes.tex
rename folder
ansatz

@@
     \centering
-    \includegraphics[width=0.6\textwidth]{plots/1contours.png}
+    \includegraphics[width=0.6\textwidth]{0_eta/1contours.png}
     \caption{Separatrix for various values of $\eta$.}\label{fig:1contours}
@@
 $\p*{\rd{\hat{s}}{t}}_{tide} = \epsilon \hat{s} \times \p*{\hat{l} \times
-\hat{s}}$. Expanding,
+\hat{s}} = \epsilon\p*{\vec{l} - \p*{\vec{s} \cdot \vec{l}}\vec{s}}$. Expanding,
 \begin{align}
@@
 
-Now, one final way to think about this, and I think this is the important one:
-consider if we are some $\delta \mu_0$ at $\phi = 0$ such that we barely hop the
-separatrix; this corresponds to $P_{hop} = \frac{\delta \mu_0}{\mu_c}$. In order
-for $\delta \mu_0$ to be hopping, $\delta \mu_\phi$ must be within $d_\phi
-\approx \frac{2\pi \epsilon}{\mu}$ of the separatrix. We can compute the ratio
-between $\delta \mu_0, \delta \mu_\phi$ by setting their Hamiltonian variations
-equal:
-\begin{align*}
-    \delta H_0 &\approx -\mu_4 \delta \mu_0 + \eta \cos I \delta \mu_0
-        \approx \eta^2 \cos I \sin I \delta \mu_0,\\
-    \delta H_\phi &\approx -\sqrt{4\eta \sin I} \delta \mu_\phi,\\
-    \frac{\delta \mu_\phi}{\delta \mu_0} &\propto
-        \eta^{3/2}\cos I \sqrt{\sin I}.
-\end{align*}
-We can assemble
+Abandoning the rest of this for the time being.
+
+\section{Weak Tidal Friction, changing $\eta$}
+
+Previously, we took the effect of tides to simply be $\rd{\hat{s}}{t} = \epsilon
+\hat{s} \times \p*{\hat{l} \times \hat{s}}$, but in reality, tides will spin
+down the body (in our case, planet) at the same rate as aligning $\hat{s}$ to
+$\hat{l}$. We must treat more carefully.
+
+\subsection{Equations of Motion}
+
+We first write out the full forms of the EOM without tidal friction. These are
+taken from Kassandra's Equations 1--3 except I replace subscript $\star$ with
+subscript $s$ since we are interested in the case where the spin of planet $1$
+evolves with its coupling to its orbital angular momentum and perturber. We
+obtain (maybe?)
+\begin{align}
+    \rd{\hat{s}}{t}
+        &= \omega_{s1}\p*{\hat{s} \cdot \hat{l}_1}\p*{\hat{s} \times \hat{l}_1}
+            - \omega_{1p}\cos(I)\p*{\hat{s} \times \hat{l}_p},\\
+    \omega_{s1} &= \frac{3k_q}{2k} \p*{\frac{R_1}{a_1}}^3 s,\\
+    \omega_{1p} &= \frac{3m_p}{4m_1}\p*{\frac{a_1}{a_p\p*{1 - e_p^2}}} \Omega_1.
+\end{align}
+Note here that $s$ is the spin frequency and $\Omega_1 =
+\sqrt{GM_1/a_1^3}$ is the Keplerian orbital frequency.
+
+In the presence of tides, and further assuming $s \ll l_1$, we may write (Lai
+2012, Equations 43--44, also Ward 1975 Equation 9 \& 13)
+\begin{align}
+    \frac{1}{s}\rd{s}{t}
+        = \frac{1}{s}\rd{s}{t}
+        &= \frac{1}{t_s}\frac{L}{2S}\s*{\cos\theta
+            - \frac{s}{2\Omega_1}\p*{1 + \cos^2\theta}},\\
+    \rd{\theta}{t} &= -\frac{1}{t_s}\frac{L}{2S}
+        \sin\theta\p*{1 - \frac{s}{2\Omega_1}\cos\theta}.
+\end{align}
+
+It is perhaps easiest to define $\frac{s}{s_c} =
+\frac{\omega_{s1}}{\omega_{1p}\cos I}$ and $\epsilon = \frac{L}{2St_s
+\omega_{1p}\cos I}$ while rescaling time $\tau = \omega_{1p}\cos(I) t$, so that
+we obtain equations of motion
+\begin{align}
+    \rd{\hat{s}}{\tau}
+        &= \frac{s}{s_c}\p*{\hat{s} \cdot \hat{l}_1}\p*{\hat{s} \times \hat{l}_1}
+            - \hat{s} \times \hat{l}_p
+            + \epsilon \p*{1 - \frac{s}{2\Omega_1}\p*{\hat{l}_1 \cdot \hat{s}}}
+                \hat{s} \times \p*{\hat{l}_1 \times \hat{s}},\\
+    \rd{s}{\tau}
+        &= \epsilon s \p*{\hat{s} \cdot \hat{l}_1 - \frac{s}{2\Omega_1}\p*{1
+            + \p*{\hat{s} \cdot \hat{l}_1}^2}}.
+\end{align}
+$s_c$ has the interpretation of being the critical spin such that the $s1$
+coupling is roughly equal strength to the $1p$ coupling. There then seem to be a
+few outcomes that we might expect:
+\begin{itemize}
+    \item Fast evolution towards CS1, then tides will slowly change $s$ without
+        changing $\hat{s}$.
+
+    \item Fast evolution towards CS2, then tides are strong while state lives
+        inside separatrix maybe? Then will spin down rapidly near CS2 until
+        spin-orbit coupling is weak.
+
+    \item Slow evolution that trails behind separatrix, expect state to converge
+        somewhere below separatrix? Would probably stay on level curve of
+        high-$\eta$ $H$ from earlier? Includes anything that doesn't make it to
+        separatrix, including almost fully anti-aligned.
+\end{itemize}
+
+\subsection{Crude Analytic Estimate}
+
+To make the equations more anemable to analytic analysis (not simulation), let's
+write down the EOM in $(\mu, \phi)$ coordinates again. The $\phi$ EOM does not
+change from the tide-free case, so we can reuse earlier equation:
+\begin{align}
+    \pd{\phi}{\tau} &= \frac{s}{s_c}\mu
+        - \p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}} \cos \phi} ,\\
+    \pd{\mu}{\tau} &= -\sin I \sin \phi +
+        \epsilon \p*{1 - \mu^2}
+            \p*{1 - \frac{s}{2\Omega_1}\mu},\\
+    \rd{s}{\tau}
+        &= \epsilon s \p*{\mu - \frac{s}{2\Omega_1}\p*{1 + \mu^2}}.
+\end{align}
+Assuming $s \gg s_c$ the strong spin-orbit coupling regime, let's first try
+assuming $\mu$ is roughly constant over the course of a precession period, then
+we can average out the $\phi$ dependencies. Then $\phi$ drops out of the EOM,
+and we have approximate averaged equations
+\begin{align}
+    \pd{\mu}{(\epsilon\tau)} &\approx \p*{1 - \mu^2}
+            \p*{1 - \frac{s}{2\Omega_1}\mu},\nonumber\\
+        &\approx \p*{1 - \mu^2}
+            \p*{- \frac{s}{2\Omega_1}\mu},\\
+    \frac{1}{s}\rd{s}{(\epsilon\tau)}
+        &\approx \mu - \frac{s}{2\Omega_1}\p*{1 + \mu^2},\nonumber\\
+        &\approx - \frac{s}{2\Omega_1}.
+\end{align}
+In the last term, we note $s \gtrsim 2\Omega_1$ initially, while $\mu \leq 1$,
+so we drop both the linear contribution from $\mu$ and approximate $\p*{1 +
+\mu^2} \approx 1$.
+
+Making all these approximations, we identify approximate analytic solution
+$s(\epsilon \tau) \approx \frac{2\Omega_1}{\epsilon \tau + C}$ with constant of
+integration $C$ set by initial conditions, or more precisely
+\begin{equation}
+    s(\epsilon \tau) \approx \frac{2\Omega_1}{\epsilon \tau +
+        \frac{2\Omega_1}{s(0)}}.
+\end{equation}
+The critical timescale is clearly $\epsilon \tau \sim 1$ (since $2\Omega_1/s(0)
+\ll 1$) at which $\frac{s}{2\Omega_1} \sim 1$ and synchronization sets in.
+
+The other timescale of interest is how long it takes $\hat{s}$ to reach a
+Cassini State. We may present crude estimates in the $s \gg s_c$ strong
+spin-orbit coupling limit; consider starting $\mu = -1 + \delta$, then to
+leading order
+\begin{align}
+    \pd{\delta}{(\epsilon\tau)} &\approx 2\delta \frac{s}{2\Omega_1},\nonumber\\
+    \delta(\epsilon\tau) &\approx
+        \delta_0\exp\s*{\frac{\epsilon \tau}{s/\Omega_1}}.
+\end{align}
+Setting $\delta \sim 1$ gives $\p*{\epsilon\tau}_{CS} \sim
+-\frac{\Omega_1}{s}\ln \delta_0$ the timescale it takes to reach $\mu = 0$ which
+is of order the timescale to reach the CS\@. This tells us that at displacements
+of $\delta_0 \gtrsim e^{-s/\Omega_1}$ is where states will be able to reach
+Cassini States. So for any respectable $s/\Omega_1$, the CS timescale will be
+short compared to the synchronization timescale, so we should expect the
+adiabatic evolution near CS1, CS2 as $\frac{s}{s_c}$ changes governs the
+long-term observed states. Specifically, states that end up near CS1 should
+(slowly!) hit the resonant obliquity excitation that Kassandra studied, while
+states near CS2 should stay on CS2 as $\eta$ grows past $\eta_{crit}$, since it
+is far from bifurcation.
+
+Under this assumption, it would appear that points that start inside the
+separatrix (rare) stay inside the separatrix, points that start above the
+separatrix stay above and undergo resonant obliquity excitation ($\sim 50\%$),
+and finally points that start outside the separatrix probably end up at either
+CS1 or CS2 probabilistically depending on $\eta(\Delta T(\mu_0))$ where $\Delta
+T(\mu_0)$ is the arrival time for a state starting at $\mu_0$.
 

### 2019-05-03 initial/notes.tex
maybe?

@@
 \end{align}
+Note that $L = \mu a^2\Omega_1, S = Is$ are the orbital and spin angular momenta
+espectively.
 
 It is perhaps easiest to define $\frac{s}{s_c} =
-\frac{\omega_{s1}}{\omega_{1p}\cos I}$ and $\epsilon = \frac{L}{2St_s
-\omega_{1p}\cos I}$ while rescaling time $\tau = \omega_{1p}\cos(I) t$, so that
-we obtain equations of motion
+\frac{\omega_{s1}}{\omega_{1p}\cos I}$ and $\epsilon\frac{\Omega_1}{s} =
+\frac{L}{2St_s \omega_{1p}\cos I}$ while rescaling time $\tau =
+\omega_{1p}\cos(I) t$, so that we obtain equations of motion
 \begin{align}
@@
             - \hat{s} \times \hat{l}_p
-            + \epsilon \p*{1 - \frac{s}{2\Omega_1}\p*{\hat{l}_1 \cdot \hat{s}}}
+            + \frac{\epsilon \Omega_1}{s}
+                \p*{1 - \frac{s}{2\Omega_1}\p*{\hat{l}_1 \cdot \hat{s}}}
                     \hat{s} \times \p*{\hat{l}_1 \times \hat{s}},\\
     \rd{s}{\tau}
-        &= \epsilon s \p*{\hat{s} \cdot \hat{l}_1 - \frac{s}{2\Omega_1}\p*{1
+        &= \epsilon \Omega_1 \p*{\hat{s} \cdot \hat{l}_1 - \frac{s}{2\Omega_1}\p*{1
             + \p*{\hat{s} \cdot \hat{l}_1}^2}}.
@@
     \pd{\mu}{\tau} &= -\sin I \sin \phi +
-        \epsilon \p*{1 - \mu^2}
+        \epsilon \frac{\Omega_1}{s}\p*{1 - \mu^2}
             \p*{1 - \frac{s}{2\Omega_1}\mu},\\
     \rd{s}{\tau}
-        &= \epsilon s \p*{\mu - \frac{s}{2\Omega_1}\p*{1 + \mu^2}}.
+        &= \epsilon \Omega_1 \p*{\mu - \frac{s}{2\Omega_1}\p*{1 + \mu^2}}.
 \end{align}
@@
 \begin{align}
-    \pd{\mu}{(\epsilon\tau)} &\approx \p*{1 - \mu^2}
+    \pd{\mu}{(\epsilon\tau)} &\approx \frac{\Omega_1}{s}\p*{1 - \mu^2}
             \p*{1 - \frac{s}{2\Omega_1}\mu},\nonumber\\
         &\approx \p*{1 - \mu^2}
-            \p*{- \frac{s}{2\Omega_1}\mu},\\
-    \frac{1}{s}\rd{s}{(\epsilon\tau)}
+            \p*{\frac{\Omega_1}{s} - \frac{1}{2}\mu},\\
+    \frac{1}{\Omega_1}\rd{s}{(\epsilon\tau)}
         &\approx \mu - \frac{s}{2\Omega_1}\p*{1 + \mu^2},\nonumber\\
@@
 
-Making all these approximations, we identify approximate analytic solution
-$s(\epsilon \tau) \approx \frac{2\Omega_1}{\epsilon \tau + C}$ with constant of
-integration $C$ set by initial conditions, or more precisely
-\begin{equation}
-    s(\epsilon \tau) \approx \frac{2\Omega_1}{\epsilon \tau +
-        \frac{2\Omega_1}{s(0)}}.
-\end{equation}
-The critical timescale is clearly $\epsilon \tau \sim 1$ (since $2\Omega_1/s(0)
-\ll 1$) at which $\frac{s}{2\Omega_1} \sim 1$ and synchronization sets in.
+With all these approximations, we clearly obtain $s(\tau) \approx
+s(0)e^{-\frac{\epsilon}{2}\tau}$, so the critical synchronization
+timescale is $\tau_{sync} \sim \frac{2}{\epsilon}$.
 
@@
 \begin{align}
-    \pd{\delta}{(\epsilon\tau)} &\approx 2\delta \frac{s}{2\Omega_1},\nonumber\\
-    \delta(\epsilon\tau) &\approx
-        \delta_0\exp\s*{\frac{\epsilon \tau}{s/\Omega_1}}.
+    \pd{\delta}{\tau} &\approx +\epsilon \delta,\nonumber\\
+    \delta(\epsilon\tau) &\approx \delta_0e^{\epsilon \tau}
 \end{align}
-Setting $\delta \sim 1$ gives $\p*{\epsilon\tau}_{CS} \sim
--\frac{\Omega_1}{s}\ln \delta_0$ the timescale it takes to reach $\mu = 0$ which
-is of order the timescale to reach the CS\@. This tells us that at displacements
-of $\delta_0 \gtrsim e^{-s/\Omega_1}$ is where states will be able to reach
-Cassini States. So for any respectable $s/\Omega_1$, the CS timescale will be
-short compared to the synchronization timescale, so we should expect the
-adiabatic evolution near CS1, CS2 as $\frac{s}{s_c}$ changes governs the
-long-term observed states. Specifically, states that end up near CS1 should
-(slowly!) hit the resonant obliquity excitation that Kassandra studied, while
-states near CS2 should stay on CS2 as $\eta$ grows past $\eta_{crit}$, since it
-is far from bifurcation.
+Setting $\delta \sim 1$ gives $\tau_{CS} = -\frac{1}{\epsilon}\ln \delta_0$ the
+timescale it takes to reach $\mu = 0$ which is of order the timescale to reach
+the CS\@. This tells us that at displacements of $\delta_0 \gtrsim
+e^{-2}$ is where states will be able to reach Cassini States before
+synchronization happens. This reinforces our expectation that synchronization is
+probably no faster than reaching the Cassini state, but that a significant
+fraction of initial conditions below the separatrix should be able to reach a
+Cassini State before tides synchronize.
 

### 2019-05-09 initial/notes.tex
plot manifolds

@@
 It is perhaps easiest to define $\frac{s}{s_c} =
-\frac{\omega_{s1}}{\omega_{1p}\cos I}$ and $\epsilon\frac{\Omega_1}{s} =
+\frac{\omega_{s1}}{\omega_{1p}\cos I}$ and $\epsilon\frac{2\Omega_1}{s} =
 \frac{L}{2St_s \omega_{1p}\cos I}$ while rescaling time $\tau =
@@
             - \hat{s} \times \hat{l}_p
-            + \frac{\epsilon \Omega_1}{s}
+            + \frac{\epsilon 2\Omega_1}{s}
                 \p*{1 - \frac{s}{2\Omega_1}\p*{\hat{l}_1 \cdot \hat{s}}}
@@
     \rd{s}{\tau}
-        &= \epsilon \Omega_1 \p*{\hat{s} \cdot \hat{l}_1 - \frac{s}{2\Omega_1}\p*{1
+        &= \epsilon 2\Omega_1 \p*{\hat{s} \cdot \hat{l}_1 - \frac{s}{2\Omega_1}\p*{1
             + \p*{\hat{s} \cdot \hat{l}_1}^2}}.
@@
     \pd{\mu}{\tau} &= -\sin I \sin \phi +
-        \epsilon \frac{\Omega_1}{s}\p*{1 - \mu^2}
+        \epsilon \frac{2\Omega_1}{s}\p*{1 - \mu^2}
             \p*{1 - \frac{s}{2\Omega_1}\mu},\\
     \rd{s}{\tau}
-        &= \epsilon \Omega_1 \p*{\mu - \frac{s}{2\Omega_1}\p*{1 + \mu^2}}.
+        &= \epsilon 2\Omega_1 \p*{\mu - \frac{s}{2\Omega_1}\p*{1 + \mu^2}}.
 \end{align}
@@
 \begin{align}
-    \pd{\mu}{(\epsilon\tau)} &\approx \frac{\Omega_1}{s}\p*{1 - \mu^2}
+    \pd{\mu}{(\epsilon\tau)} &\approx \frac{2\Omega_1}{s}\p*{1 - \mu^2}
             \p*{1 - \frac{s}{2\Omega_1}\mu},\nonumber\\
         &\approx \p*{1 - \mu^2}
-            \p*{\frac{\Omega_1}{s} - \frac{1}{2}\mu},\\
-    \frac{1}{\Omega_1}\rd{s}{(\epsilon\tau)}
+            \p*{\frac{2\Omega_1}{s} - \mu},\\
+    \frac{1}{2\Omega_1}\rd{s}{(\epsilon\tau)}
         &\approx \mu - \frac{s}{2\Omega_1}\p*{1 + \mu^2},\nonumber\\
@@
 With all these approximations, we clearly obtain $s(\tau) \approx
-s(0)e^{-\frac{\epsilon}{2}\tau}$, so the critical synchronization
-timescale is $\tau_{sync} \sim \frac{2}{\epsilon}$.
+s(0)e^{-\epsilon \tau}$, so the critical synchronization
+timescale is $\tau_{sync} \sim \frac{1}{\epsilon}$.
 
@@
 timescale it takes to reach $\mu = 0$ which is of order the timescale to reach
-the CS\@. This tells us that at displacements of $\delta_0 \gtrsim
-e^{-2}$ is where states will be able to reach Cassini States before
-synchronization happens. This reinforces our expectation that synchronization is
-probably no faster than reaching the Cassini state, but that a significant
-fraction of initial conditions below the separatrix should be able to reach a
-Cassini State before tides synchronize.
+the CS\@. This reinforces our expectation that synchronization is probably no
+faster than reaching the Cassini state, but that a significant fraction of
+initial conditions below the separatrix should be able to reach a Cassini State
+before tides synchronize.
 
 Under this assumption, it would appear that points that start inside the
-separatrix (rare) stay inside the separatrix, points that start above the
+separatrix (small) stay inside the separatrix, points that start above the
 separatrix stay above and undergo resonant obliquity excitation ($\sim 50\%$),

### 2019-05-09 initial/notes.tex
okay get Phop correctly

@@
 
-\section{Hamiltonians and EOM}
+\section{Constant $\eta$}
 
@@
 
-\subsection{Try 1: Qualitative}
+\subsection{Consideration 1: Qualitative}
 
@@
 $\delta \phi_4 = +\frac{\epsilon}{\eta \sin I}$. This is in agreement with
-Dong's result. Note that $\delta \theta_2 = -\frac{\epsilon}{\eta \sin I}$,
-which I saw in my simulations.
+Dong's result.
 
@@
 now are offset from one another by distance $D \sim \frac{\epsilon}{\eta \sin
-I}$. The question is how likely it is to thread the needle.
+I}$. But since $\epsilon$ also sets $\dot{\mu}$ in a precession orbit-averaged
+sense, the effective cross section is constant in some sense: there will be one
+orbit where $\mu$ goes from below CS4 to above CS4, during which it will make
+jump of size $\epsilon$, and if it hits a particular interval of size $\epsilon$
+then it will enter the separatrix. Thus, separatrix hopping should $\propto
+\epsilon^0$.
 
-Consider that, very near CS4, the angle of incidence on the desired gap is
-roughly $\tan \psi \approx \psi = \frac{\Delta \theta}{\Delta \phi}$. Over the
-course of one orbit, $\Delta \phi$ changes by $2\pi$, while $\Delta \theta \sim
-\epsilon \sin \theta T$ where $T$ is the period of an orbit. Examining the data,
-$T \sim 50$, and so $\frac{\Delta \theta}{\Delta \phi} \sim \frac{2\pi}{\epsilon
-(50)}$.
-
-The effective probability of threading the opened gap between the
-stable/unstable manifolds is then just $P \propto D\sin \psi \sim
-\frac{2\pi}{T\p*{\eta \sin I}}$. According to later analysis, this should really
-be $\frac{2\pi}{T}$. Plugging in some observational values $T \sim 50$ for $\eta
-= 0.1$gives $P \propto 0.13$. In reality, I find it asymptotes to $\sim 0.08$,
-so the constant of proportionality is of order unity. Not bad given the really
-crappy $\psi \sim \frac{\ev*{\dot{\theta}}}{\dot{\phi}}$ argument.
-
-\subsection{Try 2: Melnikov Distance}
+\subsection{Consideration 2: Melnikov Distance}
 
@@
 But thankfully, $\pd{\mathcal{H}}{\mu} = \pd{\phi}{t}$ in the absence of
-dissipation, and so $M = 2\pi\p*{1 - \mu^2} \approx 2\pi\p*{1 - 2\eta \sin I}$.
+dissipation, and so $M = 2\pi\p*{1 - \mu^2} \approx 2\pi$.
 Thus, the Melnikov distance at point $q^0$, a point on the heteroclinic
@@
 \begin{equation}
-    d(q^0) = \frac{2\pi \epsilon\p*{1 - 2\eta \sin I}}{\abs*{f(q^0)}}.
+    d(q^0) = \frac{2\pi \epsilon}{\abs*{f(q^0)}}.
 \end{equation}
 Note that the maximum value $\abs*{f(q^0)}$, which occurs at $\phi = \pi$, is
-just $f \approx \sqrt{4\eta \sin I}$.
+just $f_{\max} \approx \sqrt{4\eta \sin I}$.
 
@@
 
-\subsection{Try 3: Poincar\'e Section}
+\subsection{Consideration 3: Poincar\'e Section}
 
@@
 
-Abandoning the rest of this for the time being.
+\subsection{Consideration 4: Plotting Stable/Unstable manifolds}
+
+We can plot the stable/unstable manifolds of two Cassini States as in
+\autoref{fig:CS4s}. Then, since phase space is roughly flat near $\phi = \pi$
+(near $\phi = 0$, $\dot{\phi}$ varies drastically and so phase space is
+``squished'' a bit via Liouville's Theorem), we just need to compare the
+distance between $\mathcal{W}^{(0)}_S$ and $W_U^{(0)}$, the capture gap, to the
+distance between $\mathcal{W}^{(1)}_S$ and $W_U^{(0)}$ the Melnikov gap, to
+estimate the capture probability.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.6\textwidth]{0_eta/6manifolds0_10.png}
+    \caption{Stable/Unstable manifolds of the two Cassini State
+    4s.}\label{fig:CS4s}
+\end{figure}
+
+The Melnikov gap is predicted above as $d(q^0)$ or approximately
+\begin{equation}
+    \Delta_{M} \approx \frac{2\pi \epsilon}{\sqrt{4\eta\sin I}}.
+\end{equation}
+
+The capture gap is much trickier to predict, since it depends on the separation
+between $\mathcal{W}^{(0)}_S$ \emph{after passing through} CS$_4^{(1)}$.
+Instead, let's consider the closed orbit in the absence of dissipation that
+starts at CS4', the modified CS\@. This orbit has a finite period set by
+equating $\int\limits_0^T \pd{\phi}{t}\;\mathrm{d}t =
+\int\limits_0^{2\pi}\;\mathrm{d}\phi + \int\limits_{2\pi}^0\;\mathrm{d}\phi$.
+
+Now, let's reconsider the Melnikov integral when perturbing this finite
+(non-homoclinic orbit); this may no longer be an exact result but should give
+the correct scaling:
+\begin{equation}
+    M_c = \int\limits_0^T \pd{\phi}{t}\epsilon \p*{1 - \mu^2}\;\mathrm{d}t.
+\end{equation}
+Naively, we might claim that, since $\pd{\phi}{t}$ changes signs halfway through
+the interval of integration, that the only surviving component is $2\epsilon
+\bar{\mu}\mu'$, where $\bar{\mu} = \mu_4$ is the average value of $\mu$ and
+$\mu'$ is the fluctuation. This gives
+\begin{equation}
+    M_c = 2\int\limits_0^{2\pi}2\epsilon \frac{\eta \cos I}{1 + \eta \sin I}
+        \sqrt{2\eta \sin I \p*{1 - \cos \phi}}\;\mathrm{d}\phi.
+\end{equation}
+Note that $M_c \propto \eta^{3/2}$, and since the gap opened $\Delta_c =
+\frac{M_c}{\pd{\phi}{t}} \propto \eta$, it seems like we're on the right track.
+Specifically:
+\begin{align}
+    M_c &\approx \epsilon 2\eta \cos I A_{sep},\\
+    \Delta_c &\approx 2\epsilon \eta \cos I \p*{16 \sqrt{\eta \sin I}}
+        \frac{1}{\sqrt{4\eta \sin I}},\\
+        &\approx 8\epsilon \eta \cos I.
+\end{align}
+This also agrees exceedingly well with our simulations This then gives us
+hopping probability
+\begin{equation}
+    P_{hop} = \frac{\Delta_c}{\Delta_M} \approx
+        \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi}.
+\end{equation}
+This agrees perfectly with the cases we've run.
 

### 2019-05-09 initial/0_eta/6manifolds.py

@@ -37,8 +37,7 @@ def plot_manifolds(eta):
     q1, _phi1 = to_ang(*s1)
     phi1 = np.unwrap(_phi1 + np.pi) - 2 * np.pi
     term1 = np.where(phi1 < 0)[0][0]
-    plt.plot(phi1[ :term1], s1[2, :term1],
-             label=r'$W_s^{(0)}(%.2f)$' % abs(t1[term1]))
+    plt.plot(phi1[ :term1], s1[2, :term1], label=r'$W_s^{(0)}$', linewidth=0.6)
 
     # forwards from CS4^0
     init = get_displaced(-1, 1)
@@ -47,11 +46,10 @@ def plot_manifolds(eta):
     phi2 = np.unwrap(_phi2 + np.pi) - 2 * np.pi
     phi2_grad = np.gradient(phi2) / np.gradient(t2)
     term2 = np.where(np.logical_and(
-        abs(phi2_grad) < 2 * min(abs(phi2_grad)),
+        abs(phi2_grad) < 5 * min(abs(phi2_grad)),
         phi2 < 1,
     ))[0][0]
-    plt.plot(phi2[ :term2], s2[2, :term2],
-             label=r'$W_u^{(0)}(%.2f)$' % abs(t2[term2]))
+    plt.plot(phi2[ :term2], s2[2, :term2], label=r'$W_u^{(0)}$', linewidth=0.6)
 
     # backwards from CS4^1
     init = get_displaced(-1, -1)
@@ -59,8 +57,7 @@ def plot_manifolds(eta):
     q3, _phi3 = to_ang(*s3)
     phi3 = np.unwrap(_phi3 + np.pi)
     term3 = np.where(phi3 < 0)[0][0]
-    plt.plot(phi3[ :term3], s3[2, :term3],
-             label=r'$W_s^{(1)}(%.2f)$' % abs(t3[term3]))
+    plt.plot(phi3[ :term3], s3[2, :term3], label=r'$W_s^{(1)}$', linewidth=0.6)
 
     # forwards from CS4^1
     init = get_displaced(1, -1)
@@ -68,20 +65,20 @@ def plot_manifolds(eta):
     q4, _phi4 = to_ang(*s4)
     phi4 = np.unwrap(_phi4 + np.pi)
     term4 = np.where(phi4 < 0)[0][0]
-    plt.plot(phi4[ :term4], s4[2, :term4],
[…]

### 2019-05-10 initial/notes.tex
first try at weaktides

@@
         \frac{1}{\sqrt{4\eta \sin I}},\\
-        &\approx 8\epsilon \eta \cos I.
+        &\approx 16\epsilon \eta \cos I.
 \end{align}
@@
             \p*{\frac{2\Omega_1}{s} - \mu},\\
-    \frac{1}{2\Omega_1}\rd{s}{(\epsilon\tau)}
-        &\approx \mu - \frac{s}{2\Omega_1}\p*{1 + \mu^2},\nonumber\\
-        &\approx - \frac{s}{2\Omega_1}.
+    \frac{1}{\Omega_1}\rd{s}{(\epsilon\tau)}
+        &\approx 2\mu - \frac{s}{\Omega_1}\p*{1 + \mu^2}.
 \end{align}
+These EOM produce roughly the phase portrait \autoref{fig:phi_avg}.
+\begin{figure}[t]
+    \centering
+    \begin{tikzpicture}
+        \draw[<->] (0, 0) -- (8, 0);
+        \draw[<->] (0, 0) -- (0, 5);
+        \node[below right] at (8, 0) {$s$};
+        \node[above left] at (0, 5) {$\mu$};
+        \draw (0, 4) -- (2, 4) -- (4, 4);
+        \draw[dashed] (4, 4) -- (8, 4);
+        \draw (0, 4) -- (2, 4);
+        \draw[domain=0:2] plot({\x}, {\x * \x / 2 + 2});
+        \node[left] at (0, 4) {$1$};
+        \node[left] at (0, 2) {$0$};
+        \node[left] at (0, 0) {$-1$};
+        \node[below] at (0, 0) {$0$};
+        \node[below] at (2, 0) {$\Omega_1$};
+        \node[below] at (4, 0) {$2\Omega_1$};
+        \draw[domain=4:8] plot({\x}, {8 / (\x - 2)});
+        \draw[->] (2, 2) -- (1.5, 2.5);
+        \draw[->] (4, 2) -- (3.5, 2.5);
+        \draw[->] (6, 0.5) -- (5.5, 1);
+        \draw[->] (7, 3.5) -- (6.5, 3);
+        \draw[->] (0.5, 3) -- (1, 3.5);
+    \end{tikzpicture}
+    \caption{Rough phase portrait of $\phi$-averaged equations. Dashed lines
+    indicate unstable zeros of at least one of the EOM, while solid lines
+    indicate stable zeros of at least one of the EOM\@. The zeros are $\mu = 1$,
+    which becomes unstable at $s = 2\Omega_1$, $s = 2\Omega_1/\mu$ and $s' = 0$.
+    The only fixed point is $\mu = 1, s = \Omega_1$.}\label{fig:phi_avg}
+\end{figure}
 In the last term, we note $s \gtrsim 2\Omega_1$ initially, while $\mu \leq 1$,
 so we drop both the linear contribution from $\mu$ and approximate $\p*{1 +
-\mu^2} \approx 1$.
+\mu^2} \approx 1$ so that $\rd{(s/\Omega_1)}{(\epsilon\tau)} \approx
+-s/\Omega_1$.
 

### 2019-05-10 initial/1_weaktide/1sim.py

@@ -1,0 +1,36 @@
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif')
+
+from utils import solve_ic, to_ang
+
+if __name__ == '__main__':
+    tf = 1000
+    I = np.radians(20)
+    s_c = 0.1
+    eps = 1e-3
+
+    _init = np.array([-1, 0, -0.9])
+    mu0 = -0.9
+    s0 = 10
+
+    init = [-np.sqrt(1 - mu0**2), 0, mu0, s0]
+
+    t, svec, s = solve_ic(I, s_c, eps, init, tf)
+    q, phi = to_ang(*svec)
+    plt.plot(phi, np.cos(q), 'bo', markersize=2)
+    plt.xlabel(r'$\phi$')
+    plt.ylabel(r'$\cos\theta$')
+    plt.title(r'$(s_c, s_0, \cos \theta_0) = (%.2f, %d, %.2f)$' %
+              (s_c, s0, mu0))
+    plt.savefig('1traj.png')
+    plt.clf()
+
+    plt.plot(t, s_c / s)
+    plt.xlabel(r'$t$')
+    plt.ylabel(r'$\eta$')
+    plt.title(r'$\eta(t)$')
+    plt.savefig('1eta.png')

### 2019-05-10 initial/notes.tex
stash

@@
 The other timescale of interest is how long it takes $\hat{s}$ to reach a
-Cassini State. We may present crude estimates in the $s \gg s_c$ strong
-spin-orbit coupling limit; consider starting $\mu = -1 + \delta$, then to
-leading order
-\begin{align}
-    \pd{\delta}{\tau} &\approx +\epsilon \delta,\nonumber\\
-    \delta(\epsilon\tau) &\approx \delta_0e^{\epsilon \tau}
-\end{align}
-Setting $\delta \sim 1$ gives $\tau_{CS} = -\frac{1}{\epsilon}\ln \delta_0$ the
-timescale it takes to reach $\mu = 0$ which is of order the timescale to reach
-the CS\@. This reinforces our expectation that synchronization is probably no
-faster than reaching the Cassini state, but that a significant fraction of
-initial conditions below the separatrix should be able to reach a Cassini State
-before tides synchronize.
-
-Under this assumption, it would appear that points that start inside the
-separatrix (small) stay inside the separatrix, points that start above the
-separatrix stay above and undergo resonant obliquity excitation ($\sim 50\%$),
-and finally points that start outside the separatrix probably end up at either
-CS1 or CS2 probabilistically depending on $\eta(\Delta T(\mu_0))$ where $\Delta
-T(\mu_0)$ is the arrival time for a state starting at $\mu_0$.
+Cassini State. We may present some crude estimates; note that the Cassini state
+is located at $\mu_4 = \frac{\eta \cos I}{1 + \eta \sin I} \approx
+\frac{s_c}{s}\cos I$. Thus,
+\begin{align*}
+    \rd{\mu_4}{(\epsilon \tau)} &= -\frac{s_c}{s^2}\cos I
+            \rd{s}{(\epsilon\tau)},\\
+        &\approx \frac{s_c}{s}\cos I.
+\end{align*}
+At the same time, $\rd{\mu}{\p*{\epsilon\sigma}} < \frac{2\Omega_1}{s}$, so in
+order for $\mu < \mu_4$ to approach the Cassini state, we need $\Omega_1 \gtrsim
+s_c$ by a reasonable margin.
 

### 2019-05-10 initial/1_weaktide/1sim.py

@@ -7,30 +7,40 @@ plt.rc('font', family='serif')
 
 from utils import solve_ic, to_ang
 
-if __name__ == '__main__':
-    tf = 1000
-    I = np.radians(20)
-    s_c = 0.1
-    eps = 1e-3
+def get_name(s_c, eps, mu0):
+    epspow = -np.log10(eps)
+    return ('%.1fx%.1fx%.1f' % (s_c, epspow, -mu0)).replace('.', '_')
 
-    _init = np.array([-1, 0, -0.9])
-    mu0 = -0.9
-    s0 = 10
-
+def run_for_sc(I, s_c, eps, mu0, s0, tf=2500):
     init = [-np.sqrt(1 - mu0**2), 0, mu0, s0]
 
     t, svec, s = solve_ic(I, s_c, eps, init, tf)
     q, phi = to_ang(*svec)
-    plt.plot(phi, np.cos(q), 'bo', markersize=2)
+    plt.plot(phi, np.cos(q), 'bo', markersize=0.3)
+    plt.plot(phi[-1], np.cos(q)[-1], 'ro', markersize=1.5)
     plt.xlabel(r'$\phi$')
     plt.ylabel(r'$\cos\theta$')
     plt.title(r'$(s_c, s_0, \cos \theta_0) = (%.2f, %d, %.2f)$' %
               (s_c, s0, mu0))
-    plt.savefig('1traj.png')
+    plt.savefig('1traj_%s.png' % get_name(s_c, eps, mu0))
     plt.clf()
 
-    plt.plot(t, s_c / s)
+    eta = s_c / s
+    plt.plot(t, eta * np.cos(I) / (1 + eta * np.sin(I)), 'b', label=r'$\mu_4$')
+    plt.plot(t, svec[2, :], 'go', label=r'$\mu$', markersize=0.3)
     plt.xlabel(r'$t$')
-    plt.ylabel(r'$\eta$')
-    plt.title(r'$\eta(t)$')
-    plt.savefig('1eta.png')
+    plt.ylabel(r'$\mu$')
+    plt.title(r'$\mu(t), \mu_4(t)$')
+    plt.legend()
+    plt.savefig('1eta_%s.png' % get_name(s_c, eps, mu0))
+    plt.clf()
+
+if __name__ == '__main__':
+    I = np.radians(20)
+    eps = 1e-3
+    s0 = 10
+
[…]

### 2019-05-13 initial/notes.tex
stash

@@
     \centering
-    \includegraphics[width=0.6\textwidth]{0_eta/1contours.png}
+    \includegraphics[width=0.8\textwidth]{0_eta/1contours.png}
     \caption{Separatrix for various values of $\eta$.}\label{fig:1contours}
@@
 = 0.229$.
+
+\section{Separatrix Hopping}
+
+Inspired by G\&H, heteroclinic orbits are topologically unstable for any nonzero
+perturbation, but opened width $\sim$ perturbation parameter. Thus, if we
+introduce a small and constant tidal dissipation, we should get a
+\emph{asymptotically constant} probability of hopping the separatrix.
 
@@
 fail to converge to Cassini state $1$.
-
-\section{Separatrix Hopping}
-
-Inspired by G\&H, heteroclinic orbits are topologically unstable for any nonzero
-perturbation, but opened width $\sim$ perturbation parameter.
 
@@
 and we have approximate averaged equations
+\begin{subequations}\label{se:prec_avg}
     \begin{align}
@@
     \end{align}
+\end{subequations}
 These EOM produce roughly the phase portrait \autoref{fig:phi_avg}.
@@
         \node[below] at (4, 0) {$2\Omega_1$};
-        \draw[domain=4:8] plot({\x}, {8 / (\x - 2)});
+        \draw[domain=4:8] plot({\x}, {16 / \x});
         \draw[->] (2, 2) -- (1.5, 2.5);
@@
 
-The other timescale of interest is how long it takes $\hat{s}$ to reach a
-Cassini State. We may present some crude estimates; note that the Cassini state
-is located at $\mu_4 = \frac{\eta \cos I}{1 + \eta \sin I} \approx
-\frac{s_c}{s}\cos I$. Thus,
+\subsection{Reaching a Cassini State}
+
+As already stated above, the hypothesis is that starting above the separatrix
+results in obliquity excitation at secular resonance/bifurcation when $\eta =
+\eta_{crit}$, while starting inside the separatrix probably means the point will
+stay on CS2 past (saddle-node) bifurcation. We will eventually run numerical
+simulations to confirm this; we should probably derive modified Cassini states
+under weak tides to determine exactly where CS1, CS2 lie in this regime.
+
+Finally, if the IC starts below the separatrix, it will evolve to either CS1 or
+CS2 if it can \emph{catch up} to CS4, else it will stay below the separatrix up
+until bifurcation and slowly tidally align in the small $\eta$ limit. Note that
+CS4 is located at $\mu_4 = \frac{\eta \cos I}{1 + \eta \sin I} \approx
+\frac{s_c}{s}\cos I$, so we can compute $\rd{\mu_4}{(\epsilon\tau)}$ and compare
+to $\rd{\mu}{(\epsilon\tau)}$ in the precession-averaged equations. Thus,
 \begin{align*}
@@
 \end{align*}
-At the same time, $\rd{\mu}{\p*{\epsilon\sigma}} < \frac{2\Omega_1}{s}$, so in
-order for $\mu < \mu_4$ to approach the Cassini state, we need $\Omega_1 \gtrsim
-s_c$ by a reasonable margin.
+The precession averaged equations bound $\rd{\mu}{\p*{\epsilon\sigma}} <
+\frac{2\Omega_1}{s}$, so in order for $\mu < \mu_4$ to approach the Cassini
+state, we need $\Omega_1 \gtrsim s_c$ by a reasonable margin.
+
+To be more precise, $\mu_4$ disappears at
+\begin{equation}
+    \eta = \eta_c \equiv \p*{\sin^{2/3}I + \cos^{2/3}I}^{-3/2}.
+\end{equation}
+Thus, we can set $s = \frac{s_c}{\eta_c}$ and $\mu = \mu_4$ and integrate
+backwards \autoref{se:prec_avg} backwards in time to determine exactly where
+$\mu, s$ cross the separatrix. Physically, we never expect $s < \Omega_1$
+though, so the minimum $s_c$ we can use and still expect to see a strong
+spin-orbit coupling regime appear is $s_c \geq \Omega_1 \eta_c$.
+
+At the same time though, looking at the phase portrait \autoref{fig:phi_avg}, we
+can expect that running backwards in time will easily take us towards the upper
+right quadrant, where $\mu \to 1$ backwards in time. To start from a misaligned
+state, the final $s_f$ has a maximum $s_{f, \max}$, and therefore $s_c$ cannot
+be so large that $s_{f, \max} \eta_c < s_c$, otherwise the bifurcation will
+arrive before $\rd{\mu}{t}$ can catch up.
+
+This implies that $s_c$ is bound from both directions in order to get separatrix
+hopping before the bifurcation disappears.
 

### 2019-05-13 initial/1_weaktide/1sim.py

@@ -5,34 +5,48 @@ import matplotlib.pyplot as plt
 plt.rc('text', usetex=True)
 plt.rc('font', family='serif')
 
-from utils import solve_ic, to_ang, get_crits, get_etac, get_upper_sc
+from utils import solve_ic, solve_ic_avg, to_ang, backwards_solve,\
+    get_etac, get_upper_sc, get_mu4
 
 def get_name(s_c, eps, mu0):
     epspow = -np.log10(eps)
     return ('%.1fx%.1fx%.1f' % (s_c, epspow, -mu0)).replace('.', '_')
 
 def traj_for_sc(I, s_c, eps, mu0, s0, tf=2500):
+    fig, (ax1, ax2) = plt.subplots(2, 1)
     init = [-np.sqrt(1 - mu0**2), 0, mu0, s0]
 
     t, svec, s = solve_ic(I, s_c, eps, init, tf)
-    q, phi = to_ang(*svec)
-    plt.plot(phi, np.cos(q), 'bo', markersize=0.3)
-    plt.plot(phi[-1], np.cos(q)[-1], 'ro', markersize=1.5)
-    plt.xlabel(r'$\phi$')
-    plt.ylabel(r'$\cos\theta$')
-    plt.title(r'$(s_c, s_0, \cos \theta_0) = (%.2f, %d, %.2f)$' %
-              (s_c, s0, mu0))
-    plt.savefig('1traj_%s.png' % get_name(s_c, eps, mu0))
-    plt.clf()
+    t_avg, mu_avg, s_avg = solve_ic_avg(I, s_c, eps, [mu0, s0], tf)
+    # mu, s, mu4 = backwards_solve(I, s_f)
 
-    eta = s_c / s
-    plt.plot(t, eta * np.cos(I) / (1 + eta * np.sin(I)), 'b', label=r'$\mu_4$')
-    plt.plot(t, svec[2, :], 'go', label=r'$\mu$', markersize=0.3)
-    plt.xlabel(r'$t$')
-    plt.ylabel(r'$\mu$')
-    plt.title(r'$\mu(t), \mu_4(t)$')
-    plt.legend()
-    plt.savefig('1eta_%s.png' % get_name(s_c, eps, mu0))
+    q, phi = to_ang(*svec)
+
+    ax1.plot(t, svec[2, :], 'go', label=r'$\mu$', markersize=0.3)
[…]

### 2019-05-14 initial/notes.tex
better plotting, phase portraits

@@
 Thus, we can set $s = \frac{s_c}{\eta_c}$ and $\mu = \mu_4$ and integrate
-backwards \autoref{se:prec_avg} backwards in time to determine exactly where
-$\mu, s$ cross the separatrix. Physically, we never expect $s < \Omega_1$
-though, so the minimum $s_c$ we can use and still expect to see a strong
-spin-orbit coupling regime appear is $s_c \geq \Omega_1 \eta_c$.
+backwards \autoref{se:prec_avg} backwards in time to determine $\mu, s$ that are
+exactly sufficient for separatrix crossing. Physically, we never expect $s <
+\Omega_1$ though, so the minimum $s_c$ we can use and still expect to see a
+strong spin-orbit coupling regime appear is $s_c \geq \Omega_1 \eta_c$.
 

### 2019-05-14 initial/1_weaktide/2phase_portrait.py

@@ -1,0 +1,63 @@
+import numpy as np
+from scipy.integrate import solve_ivp
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif')
+
+from utils import get_inf_avg_sol, get_mu4, dmu_ds, stringify
+
+N_PTS = 50
+
+def plot_portrait(I=np.radians(20), s_c=1.5):
+    '''
+    plot phase portrait of cos(q), s in weak tide limit
+    '''
+    smax = 10
+    _mu = np.linspace(-1, 1, N_PTS)
+    _s = np.linspace(0.5, smax, N_PTS)
+    s2 = np.linspace(2, smax, N_PTS)
+
+    # plot where dmu changes signs
+    plt.plot(s2, 2 / s2, 'r', label=r'$d\mu = 0$')
+
+    # plot bounding (t -> -\infty, mu = 0, s = infty)
+    mu, s, _ = get_inf_avg_sol(smax)
+    plt.plot(s, mu, 'b', label=r'$(\mu_0, s_0) = (0, \infty)$')
+
+    # plot mu_4 for a fiducial s_c
+    mu4 = get_mu4(I, s_c, _s)
+    idx4 = np.where(mu4 > 0)[0]
+    plt.plot(_s[idx4], mu4[idx4], 'g', label=r'$\cos \theta_4$')
+
+    # flow entire mu_4 curve backwards in time to find cross section
+    sols = []
+    bounds = []
+    for idx in idx4:
+        s_curr = _s[idx]
+        ret = solve_ivp(dmu_ds, [s_curr, smax], [mu4[idx]], max_step=0.1,
+                        dense_output=True)
+        sols.append(ret.sol)
+        sols_at_curr = [sol(s_curr) for sol in sols]
+        bounds.append([np.max(sols_at_curr), np.min(sols_at_curr)])
+    mu4_min, mu4_max = np.array(bounds).T
+    plt.fill_between(_s[idx4], mu4_min, mu4_max, color='g', alpha=0.3)
+
+    # fill out ~ mu4 +- sqrt(eta * cos(I))
+    cass_width = np.sqrt(s_c / _s[idx4] * np.cos(I))
+    plt.fill_between(_s[idx4], mu4[idx4] + cass_width, mu4[idx4] - cass_width,
[…]

### 2019-05-14 initial/1_weaktide/utils.py

@@ -2,6 +2,9 @@ import numpy as np
 from scipy.integrate import solve_ivp
 import scipy.optimize as opt
 
+def stringify(*args):
+    return 'x'.join(['%.1f' % arg for arg in args]).replace('.', '_')
+
 def to_cart(q, phi):
     return [
         np.sin(q) * np.cos(phi),
@@ -32,15 +35,12 @@ def get_dydt(I, s_c, eps):
         ]
     return dydt
 
-def dydt_avg(t, y):
+def dmu_ds(s, y):
     '''
-    evolves dmu/dt, ds/dt forwards in time, precession-averaged
+    solves for mu(s) without ever introducing t
     '''
-    mu, s = y
-    return [
-        (1 - mu**2) * (2 / s - mu),
-        2 * mu - s * (1 + mu**2),
-    ]
+    mu = y[0]
+    return [((1 - mu**2) * (2 / s - mu)) / (2 * mu - s * (1 + mu**2))]
 
 def solve_ic(I, s_c, eps, y0, tf, method='RK45', rtol=1e-6, **kwargs):
     '''
@@ -49,11 +49,6 @@ def solve_ic(I, s_c, eps, y0, tf, method='RK45', rtol=1e-6, **kwargs):
     dydt = get_dydt(I, s_c, eps)
     ret = solve_ivp(dydt, [0, tf], y0, rtol=rtol, method=method, **kwargs)
     return ret.t, ret.y[0:3, :], ret.y[3, :]
-
-def solve_ic_avg(I, s_c, eps, y0, tf, method='RK45', rtol=1e-6, **kwargs):
-    ret = solve_ivp(dydt_avg, [0, eps * tf], y0,
-                    rtol=rtol, method=method, max_step=0.1 * eps, **kwargs)
-    return ret.t / eps, ret.y[0], ret.y[1]
 
 def find_cs(I, eta, q0):
     f = lambda q: -eta * np.sin(q - I) + np.sin(q) * np.cos(q)
@@ -86,24 +81,10 @@ def get_mu4(I, s_c, s):
             mu4.append(find_cs(I, eta_i, -np.pi / 2))
     return np.array(mu4)
 
-def backwards_solve(I, s_c):
+def get_inf_avg_sol(smax=10):
     '''
-    solve EOM backwards to find where separatrix hopping occurs
+    solve averaged equations for IC mu = 0, s >> 1
     '''
[…]

### 2019-05-20 initial/1_weaktide/2phase_portrait.py
technically correct quiver

@@ -6,7 +6,8 @@ import matplotlib.pyplot as plt
 plt.rc('text', usetex=True)
 plt.rc('font', family='serif')
 
-from utils import get_inf_avg_sol, get_mu4, dmu_ds, stringify
+from utils import get_inf_avg_sol, stringify, get_mu4, dmu_ds_nocs, dydt_nocs,\
+    get_dydt_num_avg
 
 N_PTS = 50
 
@@ -16,27 +17,58 @@ def plot_portrait(I=np.radians(20), s_c=1.5):
     '''
     smax = 10
     _mu = np.linspace(-1, 1, N_PTS)
-    _s = np.linspace(0.5, smax, N_PTS)
+    _s = np.linspace(2, smax, N_PTS)
     s2 = np.linspace(2, smax, N_PTS)
 
-    # plot where dmu changes signs
-    plt.plot(s2, 2 / s2, 'r', label=r'$d\mu = 0$')
+    def plot_shareds():
+        ''' few lines are shared on phase portrait and quiver'''
 
-    # plot bounding (t -> -\infty, mu = 0, s = infty)
-    mu, s, _ = get_inf_avg_sol(smax)
-    plt.plot(s, mu, 'b', label=r'$(\mu_0, s_0) = (0, \infty)$')
+        # plot where dmu changes signs
+        plt.plot(s2, 2 / s2, 'r', label=r'$d\mu = 0$')
 
-    # plot mu_4 for a fiducial s_c
-    mu4 = get_mu4(I, s_c, _s)
-    idx4 = np.where(mu4 > 0)[0]
-    plt.plot(_s[idx4], mu4[idx4], 'g', label=r'$\cos \theta_4$')
+        # plot bounding (t -> -\infty, mu = 0, s = infty)
+        mu, s, _ = get_inf_avg_sol(smax)
+        plt.plot(s, mu, 'b', label=r'$(\mu_0, s_0) = (0, \infty)$')
 
+        # plot mu_4 for a fiducial s_c
+        mu4 = get_mu4(I, s_c, _s)
+        idx4 = np.where(mu4 > 0)[0]
+        plt.plot(_s[idx4], mu4[idx4], 'g', label=r'$\mu_4$')
+        return mu4, idx4
+
+    s, mu = np.meshgrid(_s, _mu)
+    # fewer arrows
+    s = s[::2, ::2]
+    mu = mu[::2, ::2]
+
+    # no_cs approximation
+    ds, dmu = dydt_nocs(s, mu)
[…]

### 2019-05-28 initial/notes.tex
check in some new equations + plots to notes

@@
 
-\subsection{Cassini State Hamilttonian}
+\subsection{Cassini State Hamiltonian}
 
@@
 
+\section{Weak Tidal Friction, Take 2}
+
+I did a bunch of work w/o writing it up, so this is the basic gist.
+
+\begin{itemize}
+    \item We can still reuse the same equations as earlier, and the key point to
+        notice is that for a given trajectory, only times $\phi = 0$ are
+        important for determining the final fate of the system. Call these
+        $\mu_0$, then the dynamics of the system can be described by a map
+        $\mu_{0, i + 1}\p*{\mu_{0, i}, s}$. The reason $\mu_0$ is important is
+        that only when $\mu_0 = \mu_4(s)$ CS4 can separatrix hopping occur.
+        Thus, whenever $\mu_0$ crosses $\mu_4(s)$, there is some probability of
+        entering the separatrix and some probability of hopping over it.
+
+    \item The dynamics of the system are then governed by the dynamics of the
+        map near $\mu_4$. In the limit where $\phi$ is approximately constant
+        over a precession ($\mu_0$ is far from $\mu_4$ compared to $\sqrt{\eta
+        \sin I}$ the separatrix width), then the map obeys nearly the same
+        dynamics as the continuous flow in $(\mu, s)$ space for tidal friction.
+
+    \item However, when we are sufficiently close to $\mu_4$, we enter the
+        $\mu_0 - \mu_4 \lesssim \sqrt{2\eta \sin I}$ regime. Here, let's note
+        that the map takes on dynamics:
+        \begin{align}
+            \rd{\mu_0}{t} &= \pd{\mu_0}{H}\rd{H}{t},\nonumber\\
+                &= \frac{\dot{\phi}}{\dot{\phi}(\phi = 0)}
+                    \p*{\epsilon\p*{1 - \mu^2}\p*{\frac{2\Omega_1}{s}
+                        - \mu}},\nonumber\\
+            \ev*{\rd{\mu_0}{t}} &=
+                \frac{1}{T}\int\limits_0^T
+                    \frac{\dot{\phi}}{\dot{\phi}_0}
+                        \epsilon\p*{1 - \mu^2}\p*{\frac{2\Omega_1}{s} - \mu}
+                            \;\mathrm{d}t,\nonumber\\
+                &= \frac{1}{T}\int\limits_0^{2\pi}
+                    \frac{1}{\dot{\phi}_0}
+                        \epsilon\p*{1 - \mu^2}\p*{\frac{2\Omega_1}{s} - \mu}
+                            \;\mathrm{d}\phi,\nonumber\\
+                &\sim \frac{\sqrt{\eta \cos I}}{2\pi}
+                    \frac{1}{\dot{\phi}(\phi = 0)}
+                    \int\limits_0^{2\pi}
+                        \epsilon\p*{1 - \mu^2}\p*{\frac{2\Omega_1}{s} - \mu}
+                        \;\mathrm{d}\phi.\label{eq:final_approx}
+        \end{align}
+        We have substituted $\cos I/2\pi \sim 1/T$ a rough estimate
+        for the period. But now, $\frac{1}{\dot{\phi}(\phi = 0)}$ near $\mu_4$
+        obeys the linearization about the saddle point, and importantly it is
+        small. Near $\mu_4$, the linearization we computed above tells us that
+        $\dot{\phi} \approx - \sin I \Delta \mu$, and so we can imagine the
+        true map dynamics by a flow with $\rd{\mu_0}{t}$ of form
+        \begin{equation}
+            \rd{\mu_0}{t} =
+                \begin{cases}
+                    \rd{\mu_0}{t} & \abs*{\Delta \mu} \gtrsim
+                        2\sqrt{\eta \sin I},\\
+                    -\frac{\cot I}{2\pi \Delta \mu}
+                        \epsilon\p*{1 - \mu_{eff}^2}
+                            \p*{\frac{2\Omega_1}{s} - \mu_{eff}}
+                            & \text{otherwise}.
+                \end{cases}
+        \end{equation}
+        We've defined $\Delta \mu = \mu_0 - \mu_4$ for convenience. $\mu_{eff}$
+        reflects the fact that the $\epsilon$ integral in
+        \autoref{eq:final_approx} is taken over a curve of very non-constant
+        $\mu$, roughly following the separatrix boundary. In fact, $\mu_{eff}
+        \sim \sqrt{2\eta \sin I}$ the separatrix width, likely.
+
+        Our approximation near $\mu_4$ is probably only accurate up to scaling,
+        we should ensure this piecewise definition is smooth. Thus, we choose
+        $\mu_{eff} \equiv \mu_0 + 2\sqrt{\eta \sin I}$ and change the close-in
+        term to be $\frac{\Delta \mu_{eff}}{\Delta
+        \mu}\at{\rd{\mu_0}{t}}_{\mu_{eff}}$.
+
+        We can compare these predictions qualitatively to the actual integrated
+        map. By integrating the true $(\mu, \phi, s)$ system over a period, we
+        can derive an effective $\frac{\Delta \mu}{\Delta t}$ and compare to the
+        scaling we obtain above. The coefficients are not perfect, but the
+        $1/\Delta \mu$ scaling is correct: \autoref{fig:pw}.
+        \begin{figure}[t]
+            \centering
+            \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{1_weaktide/3diags0_7.png}
+                \caption{$\frac{\Delta \mu}{\Delta t}$ computed using the pure
+                weak tide prescription (ignoring $\mu(\phi)$ variations),
+                computed using an integral of the full system and computed using
+                the piecewise definition above.}
+            \end{subfigure}
+            \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{1_weaktide/3diags_loglog0_7.png}
+                \caption{Loglog plot of $\Delta \mu/\Delta t$ above $\mu_4$ for
+                the integrated and piecewise solutions.}
+            \end{subfigure}
+            \caption{Agreement of piecewise with integrated,
+            qualitatively.}\label{fig:pw}
+        \end{figure}
+
+    \item The thing that is interesting now is that $\mu_{eff}$ is evaluated
+        relatively farther away from $\mu_4$, and since $\rd{\mu}{t}$ in the
+        weak tidal limit for $s > 2$ can be negative, it is possible for a point
+        above $\mu_4$ to be \emph{sucked in} to CS4 \emph{from both above and
+        below}. This is an extremely important feature, and indeed in
+        \autoref{fig:pw} we see such behavior. If we are in this regime, then
+        any nonzero separatrix hopping probability will drive 100\% of points
+        incident on CS4 to enter the separatrix, since repeated hoppings must be
+        observed!
+
+        Qualitatively, we can use our piecewise definition to see the behavior
+        of this transition; it occurs when $\rd{\mu}{t}$ evaulated at the
+        $\mu_{eff}$ above $\mu_4$ is negative, i.e.\ above
+        $\frac{2\Omega_1}{s}$. Thus, this boils down to $\mu_4 + 2\sqrt{\eta
+        \sin I} \gtrsim \frac{2\Omega_1}{s}$. Since $\mu_4 \approx \eta \cos I
+        = \frac{s_c\cos I}{s}$, we see that for smaller $s_c$ than some critical
+        threshold, $\mu_4$ is no longer attracting on both sides. We can
+        numerically solve for this transition using the full integrated
+        equations: \autoref{fig:3crits}.
+        \begin{figure}[t]
+            \centering
+            \includegraphics[width=0.6\textwidth]{1_weaktide/3crits.png}
+            \caption{Critical values of $s_c$ below which $\mu_4$ is no longer
+            strongly attracting.}\label{fig:3crits}
+        \end{figure}
+
+    \item Indeed, \autoref{fig:3crits} shows that the critical $s_c$ is a fairly
+        flat function of $s$ in our parameter regime of interest. Call this
+        critical $s_c$ $S_0$ owing to unfortunate notation. We can thus identify
+        two regimes:
+        \begin{itemize}
+            \item $s_c < S_{0}$: points above CS4 will be driven away from CS4,
+                and so only points below the separatrix will experience a single
+                chance to separatrix hop. Thus, in this regime, points initially
+                above the separatrix will tidally synchronize, while points
+                below the separatrix will probabilistically either synchronize
+                or go to CS2.
+
+            \item $s_c > S_0$: CS4 becomes \emph{attracting}, and so two
+                consequences: points initially above the separatrix are sucked
+                downwards, and all encounters go to CS2 after 100\% separatrix
+                entry probability.
+        \end{itemize}
+        Since $S_0$ is some function of $s$, it is clear that for intermediate
+        values of $s_C$, we will see single separatrix hopping at early times
+        while separatrix attraction at late times.
+\end{itemize}
+
 \end{document}

### 2019-05-28 initial/notes.tex
check in histograms into notes

@@
         while separatrix attraction at late times.
+
+    \item Finally, we may compare histograms of outcomes when $s_c > S_0, s_c <
+        S_0$. For $s_c > S_0$, all points get attracted into CS2, which then
+        synchronizes quickly; this is illustrated poorly in
+        \autoref{fig:1hist07}.
+
+        On the other hand, when $s_c < S_0$, points below CS4 only get one
+        chance at hopping. We can perform similar Melnikov calculation to above
+        by integrating the true tidal term $\pd{\mu^{(1)}}{t} = \epsilon\p*{1 -
+        \mu^2}\p*{2\Omega_1/s - \mu}$ and find that the hopping probability
+        $P_{hop} \propto \frac{\mu}{2\Omega_1/s} \propto \sqrt{s}$ or in fact
+        scaling with $\eta^{-1/2}$; the difference comes in the $1/s$ dependence
+        in the single-leg integral and the $-\mu$ factor in the double-leg
+        integral. Thus, points closer to the initial separatrix actually should
+        experience higher entry probability, also observed in
+        \autoref{fig:1hist02}.
+
+        Finally, we can somewhat see what the transition regime looks like in
+        \autoref{fig:1hist03}. Points close to the separatrix experience
+        attracting dynamics and all hop, while points far away from the
+        separatrix experience the $\sqrt{s}$ hopping probability.
+        \begin{figure}[t]
+            \centering
+            \begin{subfigure}{0.32\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{1_weaktide/1hist_0_7.png}
+                \caption{Outcomes when $s_c = 0.7 > S_0$.}\label{fig:1hist07}
+            \end{subfigure}
+            \begin{subfigure}{0.32\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{1_weaktide/1hist_0_2.png}
+                \caption{Outcomes when $s_c = 0.2 > S_0$.}\label{fig:1hist02}
+            \end{subfigure}
+            \begin{subfigure}{0.32\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{1_weaktide/1hist_0_3.png}
+                \caption{Outcomes when $s_c = 0.3 \sim S_0$.}\label{fig:1hist03}
+            \end{subfigure}
+            \caption{Outcome hists.}
+        \end{figure}
 \end{itemize}

### 2019-05-31 initial/1_weaktide/4sim_v2.py
check in for GM

@@ -8,7 +8,7 @@ import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 plt.rc('text', usetex=True)
-plt.rc('font', family='serif')
+plt.rc('font', family='serif', size=14)
 
 from utils import solve_ic, to_ang, to_cart, get_etac, get_mu4, get_mu2,\
     stringify, H, roots, get_H4
@@ -310,7 +310,7 @@ if __name__ == '__main__':
     I = np.radians(20)
     eps = 1e-3
 
-    # plot_individual(I, eps)
+    plot_individual(I, eps)
     statistics(I, eps, 0.2)
     statistics(I, eps, 0.3)
     statistics(I, eps, 0.4)

### 2019-06-03 initial/notes.tex
add Melnikov for full weak tides

@@
 
-\subsection{Consideration 4: Plotting Stable/Unstable manifolds}
+\subsection{Consideration 4: Plotting Stable/Unstable
+manifolds}\label{ss:melnikov_success}
 
@@
 
+\subsection{Weak Perturber Hopping Distribution}
+
+We consider in the weak perturber (strong coupling) regime, where $s_c < S_0$.
+We will re-apply \autoref{ss:melnikov_success} to the weak tidal friction
+equations to compute $P_{hop}(s_\star)$ where $\star$ denotes at separatrix
+crossing. We will then seek an approximate form for $s_{\star}$ given arbitrary
+initial conditions to predict the hopping probability distribution over initial
+conditions. We only seek to solve Zone III (below separatrix) initial
+conditions.
+
+First, we note that the two integrals that I earlier called $\Delta_m, \Delta_c$
+(garbage notation sorry) can be evaluated for the new weak tidal friction
+integrals as follows:
+\begin{align}
+    \Delta_M &= \int\limits_0^{2\pi}\epsilon\p*{1 - \mu^2}
+            \p*{\frac{2\Omega}{s} - \mu} \;\mathrm{d}\phi,\nonumber\\
+        &\approx 2\pi \epsilon \frac{2\Omega}{s},\\
+    \Delta_c &= \oint \epsilon \p*{1 - \mu^2}\p*{\frac{2\Omega}{s} - \mu}
+            \;\mathrm{d}\phi,\nonumber\\
+        &= 2\int\limits_0^{2\pi}
+            \epsilon\sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi
+            ,\nonumber\\
+        &= 16\epsilon\sqrt{\eta \sin I}.
+\end{align}
+Recalling that $\eta = s_c/s$, we arrive at
+\begin{equation}
+    P_{hop} = \frac{4\sqrt{ss_c\sin I}}{\pi \Omega}.
+\end{equation}
+
+We evaluate the above at $s = s_\star$ for a given trajectory; we now want to
+compute an analytical approximation to $s_\star$. Under a familiar set of
+approximations, we can write
+\begin{align*}
+    \rd{s}{t} &\approx -s\epsilon,&
+    \rd{\mu^{(1)}}{t} &\approx
+    \begin{cases}
+        -\epsilon\mu & \mu \gtrsim \frac{2\Omega}{s},\\
+        \epsilon\frac{2\Omega}{s} & \mu \lesssim \frac{2\Omega}{s}.
+    \end{cases}
+\end{align*}
+We have taken $\mu \ll \frac{s}{2\Omega}, 1 + \mu^2 \sim 1$ to arrive at the
+first expression. The second expression hinges on the dominant term in
+$\frac{2\Omega}{s} - \mu$; since $\mu < 0$ in Zone III, this term is always
+positive.
+
+Now, recall that we won't get a sensible answer this way, since the dynamics
+near the separatrix $\abs*{\mu - \mu_4} \sim \sqrt{2\eta \sin I}$ are governed
+by the piecewise map we defined before. However, if $s_c$ is truly small, then
+the majority of the separatrix approach will be governed by the above flow. If
+we also adopt the $\mu \lesssim \frac{2\Omega}{s}$ limit, in this spirit, then
+an analytical solution can be approximated: we first observe that $\rd{\ln s}{t}
+\gtrsim \rd{\mu^{(1)}}{t}$ in this limit by a factor of $\frac{s}{2\Omega}$, so
+we approximate $s \approx s_0e^{-\epsilon t}$. This gives us
+\begin{equation*}
+    \mu(t) \approx \mu_0 + \frac{2\Omega}{s_0}\p*{e^{\epsilon t} - 1}.
+\end{equation*}
+If $\epsilon t \lesssim 1$, we can arrive at closed form $t_\star \approx
+\frac{s_0 \Delta \mu}{2\Omega \epsilon}$. Note that $\Delta \mu$ here should be
+calculated at $\phi = \pi$ since phase space is not flat there, unlike near the
+saddle point (same motivation as usual). This gives us $s_\star = s_0
+e^{-\frac{s_0 \Delta \mu}{2\Omega}}$. For a sample run at $s_0 = 10, s_c =
+0.03, \mu_0 = -0.3, \phi_0 = 0$, this estimates $t_\star \sim 500$ which is
+reasonably close to the measured $t_\star = 575$.
+
+If we are to use this prescription, then we can obtain
+\begin{equation}
+    P_{hop}\p*{\mu_\pi(t = 0)}
+        = \frac{4\sqrt{s_c \sin I s_0}}{\pi \Omega}
+            e^{-\frac{s_0}{4\Omega}\Delta \mu_\pi}.
+\end{equation}
+What is noteworthy is the \emph{exponential} dependence on $\Delta \mu_\pi$; we
+might expect similar behavior to manifest elsewhere thanks to the $\rd{\ln s}{t}
+\sim \epsilon, \rd{\mu}{t} \propto \z*{-\epsilon \mu, \epsilon/s}$ in both
+regimes of $\rd{\mu}{t}$. Further numerical testing to be performed.
+
 \end{document}

### 2019-06-10 initial/notes.tex
update notes slightly

@@
 
-\subsection{Weak Perturber Hopping Distribution}
+\subsection{Weak Perturber Hopping Distribution (Probably incorrect?)}
 
@@
 
+\textbf{Note:} This section's calculation may be inaccurate because $H$ is not
+an adiabatic invariant. I thought that maybe $s$ could be imagined to be
+approximately constant over the final orbit, I'm not sure how accurate that is
+though.
+
+\subsection{Relation to Henrard 1982}
+
+Henrard's \emph{Capture into resonance: An extension of the use of adiabatic
+invariants} is somewhat similar to our work but covers a slightly different
+scenario. We summarize the similarities below:
+\begin{itemize}
+    \item Henrard considers a dissipation-free system where $H^{(0)}$ slowly
+        changes in time due to a varying parameter $\lambda$. Contrast this to
+        our two considered problems, both of which have dissipation.
+
+    \item His result for hopping probabilities is the same as ours though:
+        consider $K = H - H^*$, which for us is $\Delta H = H - H_4$, then
+        we can write down expressions for the evolution of $\Delta H$ along the
+        heteroclinic orbit. Henrard calls these $B_i$ for energy balance.
+
+    \item Consider then an inbound trajectory on one of the two legs of the
+        separatrix, call this leg $1$ and the other leg $2$. Furthermore, adopt
+        convention whereby the separatrix has $K < 0$. Then, upon the final
+        orbit prior to separatrix crossing, the trajectory experiences some
+        $\Delta H = B_1$. Subsequently, it will hop onto the second leg of the
+        separatrix, where it further experiences some $\Delta H = B_2$. Note
+        that $B_1 < 0$ is necessary to experience separatrix crossing, otherwise
+        trajectories will be repelled from the separatrix.
+
+    \item Henrard then enumerates three possible cases: $B_2 < 0$ produces
+        guaranteed capture, $B_2 > 0, B_1 + B_2 > 0$ produces guaranteed
+        crossing, and $B_2 > 0, B_1 + B_2 < 0$ is effectively probabilistic.
+
+    \item These conclusions mirror ours, if we replace $\Delta_M = B_1, \Delta_c
+        = B_1 + B_2$; one may immediately see that $\Delta_c$ has the same sign
+        as $\Delta_M$ in the probabilistic case, and in the $s_c > S_{0}$ case
+        we have exactly $B_1, B_2 < 0$ attraction.
+\end{itemize}
+
+In our problem, we have both dissipation thanks to $\rd{\mu^{(1)}}{t}$ and
+parameter variation $\rd{s}{t}$. Paralleling Equation 41 of Henrard's paper, we
+may expand:
+\begin{align}
+    \rd{H}{t} &= \pd{H}{t} + \pd{H}{\phi}\rd{\phi}{t} + \pd{H}{\mu}\rd{\mu}{t}
+            + \pd{H}{s}\pd{s}{t},\nonumber\\
+        &= \dot{\mu}^{(1)} \dot{\phi}^{(0)} + \pd{H}{s}\rd{s}{t},\\
+    \rd{H_4}{t} &= \pd{H_4}{s}\rd{s}{t},\\
+    \rd{K}{\phi} &=
+        \dot{\mu}^{(1)} + \frac{\dot{s}^{(1)}}{\dot{\phi}^{(0)}}
+            \p*{\pd{H}{s} - \pd{H_4}{s}},\\
+    \Delta K_i &= \oint_{\mathcal{C}_i}
+        \dot{\mu}^{(1)} + \frac{\dot{s}^{(1)}}{\dot{\phi}^{(0)}}
+            \p*{\pd{H}{s} - \pd{H_4}{s}}\;\mathrm{d}\phi.
+\end{align}
+We have arbitrarily added superscripts to indicate to what order in $\epsilon$
+our expansions proceed. Note the resemblance of this formula to Equation 41 of
+Henrard's paper, but also to our earlier work in the constant tides case. Again,
+$\Delta K_i = H - H_4$ over path $\mathcal{C}_i$, which in our case can be either
+the bottom half of the separatrix or the entire separatrix (in which case
+$\Delta K_1 = B_1 = \Delta_M, \Delta K_2 = B_1 + B_2 = \Delta_c$).
+
+\subsection{Weak Perturber Hopping Revisited}
+
+First, let's examine our $t_{\star}$ plot (TODO add). We observe that there is a
+roughly linear slope $\rd{t_{\star}}{(\Delta H)} \sim \frac{600}{s_0/2s_c}$
+where $-s_0/2s_c$ is the minimum value of $H$ on the domain and so is the
+maximum value for $\Delta H = H_4 - H_0$. Note that
+\begin{align*}
+    H(\mu, \phi; s) &= -\frac{s}{s_c}\frac{\mu^2}{2}
+        + \mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi, &
+    H_4(s) &= -\sin I + \frac{s_c}{2s}\cos^2 I.
+\end{align*}
+While $s$ is actually a dynamical variable, it is a parameter to the 1D
+Hamiltonian. Plugging these expressions ino our above expression for $\rd{K}{t}
+= -\rd{(\Delta H)}{t}$, we obtain
+\begin{align}
+    \rd{(\Delta H)}{t} &= -\dot{\mu}^{(1)}\dot{\phi}^{(0)} - \dot{s}^{(1)}
+            \rd{(\Delta H)}{s},\\
+    -\rd{(\Delta H)}{(\epsilon t)} &= (1 - \mu^2)\p*{\frac{2\Omega}{s} - \mu}
+            \dot{\phi}^{(0)} + 2\Omega\p*{1 + \frac{s}{2\Omega}(1 + \mu^2)}
+            \s*{\frac{\mu^2}{2s_c} + \sin I + \frac{s_c}{2s^2}\cos^2 I}.
+\end{align}
+Now, if we evaluate far from the separatrix and for large $s$, similar to most
+of our initial conditions, we obtain $\rd{(\Delta H)}{t} \approx \epsilon
+\frac{s\mu^2}{s_c}\p*{1 - \mu^2 + \frac{1 + \mu^2}{2}} \sim
+-\epsilon\frac{s\mu^2}{s_c}$. Comparing to our plot, we would predict that this
+derivative should be close to $\frac{s/s_c}{1200}$ (assuming $s \sim s_0$
+initially), so it seems like we at least have the scaling correct.
+
+This allows for a rudimentary prediction of $t_{\star}, s_{\star}$ at separatrix
+crossing; we next want to compute the separatrix crossing probabilities.
+
 \end{document}

### 2019-06-10 initial/notes.tex
figured small out
add one extra line for ref

@@
         we have exactly $B_1, B_2 < 0$ attraction.
+
+    \item Henrard in a later paper cites the formula $\Pr\p*{i \to j} =
+        \abs*{\pd{J_j}{t} / \pd{J_i}{t}}$. This can be related to the above
+        $B_i, \Delta_H$ by:
+        \begin{equation}
+            \Delta H = \int \pd{H}{\lambda}\dot{\lambda}\mathrm{d}t
+                = \int \pd{J}{\lambda}\pd{H}{J}\dot{\lambda}\mathrm{d}t
+                = 2\pi \dot{\lambda}\pd{J}{\lambda},
+        \end{equation}
+        where $J$ is the action variable; this is easy to see since $\pd{H}{J}$
+        is just the angular velocity of the corresponding angle variable to $J$.
 \end{itemize}
@@
 Now, if we evaluate far from the separatrix and for large $s$, similar to most
-of our initial conditions, we obtain $\rd{(\Delta H)}{t} \approx \epsilon
+of our initial conditions, we approximate $\dot{\phi} \approx \frac{s_c}{s}$ and
+we obtain
+\begin{equation}
+    \rd{(\Delta H)}{t} \approx \epsilon
         \frac{s\mu^2}{s_c}\p*{1 - \mu^2 + \frac{1 + \mu^2}{2}} \sim
--\epsilon\frac{s\mu^2}{s_c}$. Comparing to our plot, we would predict that this
-derivative should be close to $\frac{s/s_c}{1200}$ (assuming $s \sim s_0$
-initially), so it seems like we at least have the scaling correct.
+        -\epsilon\frac{s\mu^2}{s_c}.
+\end{equation}
+Comparing to our plot, we would predict that this derivative should be close to
+$\frac{s/s_c}{1200}$ (assuming $s \sim s_0$ initially), so it seems like we at
+least have the scaling correct.
 
 This allows for a rudimentary prediction of $t_{\star}, s_{\star}$ at separatrix
-crossing; we next want to compute the separatrix crossing probabilities.
+crossing; we next want to compute the separatrix crossing probabilities. It's
+not immediately obvious whether the dissipation or adiabatic invariance term
+should dominate the crossing probability or the $\Delta H$ evolution: since
+$\pd{H}{s} \propto \mu^2$ but also $\dot{\phi}^{(0)} \to 0$ for much of the
+trajectory, it will require some careful statistics/simulation to disentangle
+the two.
 

### 2019-06-11 initial/notes.tex
stash

@@
 
-\section{Weak Tidal Friction, changing $\eta$}
+\section{Parametric Separatrix Hopping: Only changing $\eta$}
+
+Though this section is located before the weak tidal friction section, we
+actually return to this second toy problem to get some practice on the Henrard
+paper, to confirm the accuracy of our simulations compared to analytical
+predictions, and to get some practice doing these new integrals. Consider the
+dissipation-free Cassini state system with a small but constant $\pd{\eta}{t} =
+\epsilon$. For clarity, the Hamiltonian is
+\begin{equation}
+    H = -\frac{\mu^2}{2} + \eta
+        \p*{\mu \cos I - \sin I \sqrt{1 - \mu^2} \theta \cos \phi}.
+\end{equation}
+
+For an arbitrary initial condition outside of the separatrix, we want: (i) to
+know when it will encounter the separatrix, and (ii) what its fate will be. We
+will begin with (ii) since it is the more fun problem. We know that this boils
+down to the Melnikov-like formula
+\begin{equation}
+    B_i = \int_{\mathcal{C}_i} \dot{\eta}\pd{\Delta H}{\eta}
+        \;\mathrm{d}t.
+\end{equation}
+$B_i$ is the change in $\Delta H = H_4 - H$ over contour $\mathcal{C}_i$.
+
+\section{Weak Tidal Friction, changing $\eta$ and $\theta$}
 
@@
             \p*{\frac{2\Omega}{s} - \mu} \;\mathrm{d}\phi,\nonumber\\
-        &\approx 2\pi \epsilon \frac{2\Omega}{s},\\
+        &\sim 2\pi \epsilon \p*{\frac{2\Omega}{s}
+            - \sqrt{2\frac{s_c}{s}\sin I}},\\
     \Delta_c &= \oint \epsilon \p*{1 - \mu^2}\p*{\frac{2\Omega}{s} - \mu}
@@
 \begin{equation}
-    P_{hop} = \frac{4\sqrt{ss_c\sin I}}{\pi \Omega}.
+    P_{hop} = \frac{4\sqrt{ss_c\sin I}}{\pi \Omega}
+        \p*{1 + \sqrt{\frac{s_cs\sin I}{2}}}.\label{eq:p_hop_sqrt_s}
 \end{equation}
@@
 
-First, let's examine our $t_{\star}$ plot (TODO add). We observe that there is a
-roughly linear slope $\rd{t_{\star}}{(\Delta H)} \sim \frac{600}{s_0/2s_c}$
-where $-s_0/2s_c$ is the minimum value of $H$ on the domain and so is the
-maximum value for $\Delta H = H_4 - H_0$. Note that
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.7\textwidth]{../initial/1_weaktide/4_cross0_20.png}
+    \caption{$t_\star, s_\star$ for $s_c = 0.2$. Red line is a by-eye linear
+    fit.}\label{fig:4_cross0_20}
+\end{figure}
+
+First, let's examine our $t_{\star}$ plot e.g.\ \autoref{fig:4_cross0_20}. We
+observe that there is a roughly linear slope $\rd{t_{\star}}{(\Delta H)} \sim
+\frac{600}{s_0/2s_c}$ where $-s_0/2s_c$ is the minimum value of $H$ on the
+domain and so is the maximum value for $\Delta H = H_4 - H_0$. Note that
 \begin{align*}
@@
 While $s$ is actually a dynamical variable, it is a parameter to the 1D
-Hamiltonian. Plugging these expressions ino our above expression for $\rd{K}{t}
+Hamiltonian. Plugging these expressions into our above expression for $\rd{K}{t}
 = -\rd{(\Delta H)}{t}$, we obtain
@@
     \rd{(\Delta H)}{t} &= -\dot{\mu}^{(1)}\dot{\phi}^{(0)} - \dot{s}^{(1)}
-            \rd{(\Delta H)}{s},\\
+            \pd{(\Delta H)}{s},\\
     -\rd{(\Delta H)}{(\epsilon t)} &= (1 - \mu^2)\p*{\frac{2\Omega}{s} - \mu}
             \dot{\phi}^{(0)} + 2\Omega\p*{1 + \frac{s}{2\Omega}(1 + \mu^2)}
-            \s*{\frac{\mu^2}{2s_c} + \sin I + \frac{s_c}{2s^2}\cos^2 I}.
-\end{align}
-Now, if we evaluate far from the separatrix and for large $s$, similar to most
-of our initial conditions, we approximate $\dot{\phi} \approx \frac{s_c}{s}$ and
-we obtain
-\begin{equation}
-    \rd{(\Delta H)}{t} \approx \epsilon
-        \frac{s\mu^2}{s_c}\p*{1 - \mu^2 + \frac{1 + \mu^2}{2}} \sim
-        -\epsilon\frac{s\mu^2}{s_c}.
-\end{equation}
-Comparing to our plot, we would predict that this derivative should be close to
-$\frac{s/s_c}{1200}$ (assuming $s \sim s_0$ initially), so it seems like we at
-least have the scaling correct.
+            \s*{\frac{\mu^2}{2s_c} - \frac{s_c}{2s^2}\cos^2 I}.
+\end{align}
+Note that this expression is encouraging since both $\dot{\phi}^{(0)},
+\pd{\p*{\Delta H}}{s}$ vanish near CS4 (where $\mu_4 \approx \frac{s_c}{s}\cos
+I$), which corresponds to separatrix approach slowing down (also consistent w/
+our plots). Now, if we evaluate far from the separatrix and for large $s$,
+similar to most of our initial conditions, we approximate $\dot{\phi} \approx
+\frac{s_c}{s}$ and we obtain
+\begin{align}
+    \rd{(\Delta H)}{(\epsilon t)} &\approx
+            \p*{1 - \mu^2}\p*{\frac{2\Omega}{s} - \mu}\frac{s}{s_c}\mu
+                + s\p*{1 + \mu^2}\p*{\frac{\mu^2}{2s_c}},\nonumber\\
+        &\approx -\frac{s\mu^2}{2s_c} \p*{2(1 - \mu^2) - 1 + \mu^2}
+            ,\nonumber\\
+        &= -\frac{s\mu^2}{2s_c}\p*{3 - \mu^2}.
+\end{align}
+The linear fit by eye on the plot corresponds to a slope of $-\rd{(\Delta H)}{t}
+\approx \frac{s_0/s_c}{1200}$ which is of the right order $-\epsilon
+\frac{3s\mu^2}{2s_c}$, so it seems like we at least have the scaling correct.
+The intercept offset is given by the dynamics near $\Delta H$ small, or
+sufficiently small that $\dot{\phi}^{(0)} \approx \frac{s}{s_c}$ is no longer
+accurate (where phase space begins to be distorted by the separatrix); we will
+analyze this separately later/never.
+
+\subsection{$P_{hop}$ More Carefully}
 
@@
 
+It bears noting that the formula \autoref{eq:p_hop_sqrt_s} only holds under the
+following assumptions: (i) the Melnikov splitting is stronger than the adiabatic
+invariant effect described by Henrard, and (ii) $\frac{2\Omega}{s} \gtrsim \mu$
+along the separatrix. Condition (ii) is expected to hold in the weak perturber
+regime $s_c$ small, and indeed it seems to give the correct prediction, as seen
+in \autoref{fig:4_cross_hist0_05} (a few other trials also seem to suggest
+this).
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.7\textwidth]{../initial/1_weaktide/4_cross_hist0_05.png}
+    \caption{Histogram of $P_{hop}(s_\star)$ with prediction of
+    \autoref{eq:p_hop_sqrt_s} overlaid. Anal indicates just the prefactor, while
+    corrected analytic denotes including the estimated corrective term. We see
+    that the true curve lies somewhere in between.}\label{fig:4_cross_hist0_05}
+\end{figure}
+
+Can we analytically show that the Melnikov splitting dominates, and that in
+particular the seeming small excess of $P_{hop}$ is predictable?
+
 \end{document}

### 2019-06-13 initial/notes.tex
okok understand what's going on now

@@
 \begin{equation}
-    H = -\frac{\mu^2}{2} + \eta
-        \p*{\mu \cos I - \sin I \sqrt{1 - \mu^2} \theta \cos \phi}.
-\end{equation}
+    H = -\alpha\frac{\mu^2}{2} +
+        \mu \cos I - \sin I \sqrt{1 - \mu^2} \theta \cos \phi.
+\end{equation}
+This proves to be the algebraically easiest formulation, instead of using
+$\eta$.
 
@@
 \begin{equation}
-    B_i = \int_{\mathcal{C}_i} \dot{\eta}\pd{\Delta H}{\eta}
+    B_i = \int_{\mathcal{C}_i} \dot{\alpha}\pd{\Delta H}{\alpha}
         \;\mathrm{d}t.
@@
 $B_i$ is the change in $\Delta H = H_4 - H$ over contour $\mathcal{C}_i$.
+
+In order to probe the relevant physics here, we firsst cite without proof (refer
+to \autoref{ss:revisited} for this) that $\pd{\Delta H}{\alpha} =
+\frac{\mu^2}{2} - \frac{1}{2\alpha^2}\cos^2 I$. This implies that
+\begin{equation}
+    B_i = \int_{\mathcal{C}_i} \dot{\alpha}\s*{
+        \frac{\mu^2}{2} - \frac{1}{2\alpha^2}\cos^2 I}
+        \;\mathrm{d}t.
+\end{equation}
+Recall that the capture probability is $\frac{B_1 + B_2}{B_1}$ when this
+expression is $\in [0, 1]$. However, we immediately see a problem: the first
+term will dominate the second term, since $\alpha \gg 1$, but the first term is
+also positive semidefinite. This implies $B_1, B_2$ will always have the same
+sign unless $\dot{\alpha}$ has different signs over the two trajectories!
+
+Thus, in our toy model, we \emph{cannot} choose a simple form e.g.\
+$\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
+$\mathcal{C}_i$.
 
@@
 
-\subsection{Weak Perturber Hopping Revisited}
+\subsection{Weak Perturber Hopping Revisited}\label{ss:revisited}
 

### 2019-06-17 initial/notes.tex
update notes w/ algebra

@@
 
-\subsection{Separatrix Area}
+\subsection{Separatrix Area}\label{ss:sep_area}
 
@@
         \approx -\frac{\mu_4^2}{2} + \eta \mu_4 \cos I - \eta \sin I,\\
-        &= +\eta^2\cos^2 I - \eta \sin I,\\
+        &= +\frac{\eta^2\cos^2 I}{2} - \eta \sin I,\\
     H(\mu_{sep}, \phi_{sep})
@@
     0 &\approx \frac{\mu_{sep}^2}{2} - \eta \mu_{sep} \cos I
-        - \eta \sin I\p*{1 - \cos \phi_{sep}} + \eta^2\cos^2I,\\
+        - \eta \sin I\p*{1 - \cos \phi_{sep}} + \frac{\eta^2\cos^2I}{2},\\
     \mu_{sep}\p*{\phi} &\approx \sqrt{2\eta \sin I\p*{1 - \cos \phi}}
@@
 
-\section{Parametric Separatrix Hopping: Only changing $\eta$}
+\section{Parametric Separatrix Hopping: Only changing $\eta$}\label{s:p2}
 
@@
 
-In order to probe the relevant physics here, we firsst cite without proof (refer
+In order to probe the relevant physics here, we first cite without proof (refer
 to \autoref{ss:revisited} for this) that $\pd{\Delta H}{\alpha} =
@@
     H(\mu, \phi; s) &= -\frac{s}{s_c}\frac{\mu^2}{2}
-        + \mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi, &
+        + \mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi,&
     H_4(s) &= -\sin I + \frac{s_c}{2s}\cos^2 I.
 \end{align*}
+
+I accidentally did some extra algebra and computed to one extra order in
+$\frac{s_c}{s}$, so I might as well leave it in. We will compute carefully,
+noting that $\mu_4 = \frac{\cos I}{\alpha - \sin I}, \phi_4 = 0$ is exact (where
+$\alpha = s/s_c$ for brevity and compatibility with \autoref{s:p2}).
+\begin{align*}
+    H_4 &= -\alpha \frac{\mu_4^2}{2} + \mu_4 \cos I - \sin I \sqrt{1 - \mu_4^2}
+            \cos \phi_4,\\
+        &= -\frac{\alpha \cos^2 I}{2(\alpha - \sin I)^2}
+            + \frac{\cos^2 I}{\alpha - \sin I}
+            - \sin I \frac{\sqrt{(\alpha - \sin I)^2 - \cos^2 I}}{
+                \alpha - \sin I},\\
+        &= \frac{1}{\p*{\alpha - \sin I}^2}
+            \s*{-\alpha \cos^2 I + \p*{\alpha - \sin I}
+                \p*{\cos^2 I - \sin I \sqrt{
+                    (\alpha - \sin I)^2 - \cos^2 I}}},\\
+        &\approx \frac{1}{\p*{\alpha - \sin I}^2}
+            \s*{\frac{\alpha \cos^2 I}{2} -\sin I \cos^2 I - \alpha^2 \sin I
+                \p*{1 - \frac{2\alpha \sin I + \cos^2 I - \sin^2 I}{2\alpha^2}}
+                + \sin^2 I\alpha\p*{1 - \frac{2\alpha \sin I}{2\alpha^2}}},\\
+        &\approx \frac{1}{\alpha^2}\p*{1 + \frac{2\sin I}{\alpha}
+            + \frac{3\sin^2 I}{\alpha^2}}\p*{
+                -\alpha^2 \sin I + 2\sin^2 I\alpha
+                    + \frac{\alpha \cos^2 I}{2}
+                    - \frac{(\cos^2 I + 3\sin^2 I)\sin I}{2}},\\
+        &\approx -\sin I + \frac{\cos^2 I}{2\alpha}
+            + \frac{1}{\alpha^2}\s*{
+                -3\sin^3 I - \frac{\p*{\cos^2 I + 3\sin^2 I}\sin I}{2}
+                    + 4\sin^3 I + \sin I \cos^2 I},\\
+        &= -\sin I + \frac{\cos^2 I}{2\alpha}
+            + \frac{\p*{\cos^2 I - \sin^2 I}\sin I}{2\alpha^2}.
+\end{align*}
+
 While $s$ is actually a dynamical variable, it is a parameter to the 1D

### 2019-06-17 initial/notes.tex
check in notes

@@
 $\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
-$\mathcal{C}_i$.
+$\mathcal{C}_i$. Let's consider a model where $\dot{\eta} = +\epsilon \eta \mu$.
+It should be noted that, upon careful calculation, $\dot{\eta} = -\epsilon \eta
+\mu$ will \emph{not} result in any captures! We will see this below.
+
+Our expression then becomes (using our usual decomposition $\mu = \bar{\mu} +
+\mu'$ where $\bar{\mu} = \mu_4 \approx \cos I/\alpha$)
+\begin{align*}
+    B_i &= \int -\frac{\epsilon \mu}{\alpha}\frac{\mu^2}{2}\;\mathrm{d}t,\\
+        &\approx \int \frac{\epsilon \mu^3}{2\alpha \mu'}.
+\end{align*}
+It may be tempting now to predict $B_{top} = -\frac{2\pi \epsilon 4\sin
+I/\alpha}{2\alpha^2}$, by directly substituting $\mu \approx \mu'$, and use the
+same $\mu^3 = \mu'\p*{2\bar{\mu}\mu'}$ trick as in toy problem 1 to get an
+antisymmetric term and obtain
+\begin{equation}
+    B_{tot} = -\frac{4\pi \epsilon 2\sqrt{\frac{\sin I}{\alpha}}\frac{\cos
+        I}{\alpha}}{2\alpha^2}.
+\end{equation}
+This predicts a capture probability $P_c = \frac{\cos I}{\sqrt{\sin
+I}}\sqrt{\eta}$ where again $\eta\alpha = 1$. We note that this is \emph{not} in
+accordance with our calculations, which predict $P_{c} \propto \eta^0$! Further
+investigation necessary.
 

### 2019-06-18 initial/notes.tex
check in WIP

--- 2019-06-17 initial/notes.tex
@@
 $\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
-$\mathcal{C}_i$.
+$\mathcal{C}_i$. Let's consider a model where $\dot{\eta} = +\epsilon \eta \mu$.
+It should be noted that, upon careful calculation, $\dot{\eta} = -\epsilon \eta
+\mu$ will \emph{not} result in any captures! Our choice only permits captures
+\emph{from top down}. We will see this below.
+
+Our expression then becomes:
+\begin{align*}
+    B_i &= \int -\frac{\epsilon \mu}{2\alpha^2}\s*{
+        \alpha^2 \mu^2 - \cos^2 I}\;\mathrm{d}t,\\
+        &\approx -\frac{\epsilon}{2\alpha^2} \int
+            \mu \frac{\alpha^2 \mu^2 - \cos^2 I}{
+                -\alpha \mu + \cos I}\;\mathrm{d}\phi,\\
+        &\approx +\frac{\epsilon}{2\alpha^2}\int
+            \mu\p*{\alpha \mu + \cos I}\;\mathrm{d}\phi.
+\end{align*}
+Now, we can evaluate our two integrals. The first integral is just over the top
+leg, which is roughly
+\begin{align*}
+    \frac{B_{top}(2\alpha^2)}{\epsilon} &\approx
+            \int\limits_{2\pi}^{0}\alpha \mu^2\;\mathrm{d}\phi,\\
+        &\approx -2\pi \alpha \eta \sin I.
+\end{align*}
+The second integral around the full curve has two antisymmetric components, and
+so (borrowing the old $\mu = \bar{\mu} + \mu'$ notation, where $\bar{\mu} =
+\mu_4$ and $\mu'$ is antisymmetric over the two legs)
+\begin{align*}
+    \frac{B_{tot}(2\alpha^2)}{\epsilon} &\approx
+        2\int\limits_{2\pi}^0 \alpha \bar{\mu}\mu'
+            + \mu'\cos I\;\mathrm{d}\phi,\\
+        &= -2\cos I A_{sep},\\
+        &= -32\sqrt{\eta \sin I}\cos I.
+\end{align*}
+This predicts capture probability $P_c = \frac{16\cos I}{\pi \sqrt{\sin
+I}}\sqrt{\eta}$. This doesn't seem to agree with our numerical integrations,
+which suggest $P_c \propto \eta^1 I^0$, no dependence on $I$! There's a bit of
+interpretation still, but that is WIP\@.
+
+We can repeat this calculation using $\eta$ instead of $\alpha$ if desired, but
+it doesn't give us any qualitatively different result.
 

### 2019-06-18 initial/notes.tex
Toy Problem 2 seems solved

--- 2019-06-17 initial/notes.tex
@@
 $\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
-$\mathcal{C}_i$.
+$\mathcal{C}_i$. Let's consider a model where $\dot{\eta} = +\epsilon \eta \mu$.
+It should be noted that, upon careful calculation, $\dot{\eta} = -\epsilon \eta
+\mu$ will \emph{not} result in any captures! Our choice only permits captures
+\emph{from top down}. We will see this below.
+
+Our expression then becomes:
+\begin{align*}
+    B_i &= \int -\frac{\epsilon \mu}{2\alpha^2}\s*{
+        \alpha^2 \mu^2 - \cos^2 I}\;\mathrm{d}t,\\
+        &\approx -\frac{\epsilon}{2\alpha^2} \int
+            \mu \frac{\alpha^2 \mu^2 - \cos^2 I}{
+                -\alpha \mu + \cos I}\;\mathrm{d}\phi,\\
+        &\approx +\frac{\epsilon}{2\alpha^2}\int
+            \mu\p*{\alpha \mu + \cos I}\;\mathrm{d}\phi.
+\end{align*}
+Now, we can evaluate our two integrals. For some reason my usual arguments
+(taking symmetric/antisymmetric part etc.) don't seem to do too well here, there
+are too many terms, so we will keep as many terms as possible.
+
+First, we tackle the top integral. Here, the integrand is evaluated at
+$\mu_+(\phi) = \eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}$, so we can
+plug this in and compute
+\begin{align*}
+    B_{top}\frac{2\alpha^2}{\epsilon} &= \int\limits_{2\pi}^{0}
+            \mu(\alpha \mu + \cos I)\;\mathrm{d}\phi,\\
+        &= -\int\limits_0^{2\pi}
+            \p*{\eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}}
+                \p*{2\cos I + \sqrt{2\sin I\p*{1 - \cos \phi}/\eta}}
+                \;\mathrm{d}\phi.
+\end{align*}
+Let's track the four terms in FOIL (first, outer, inner, last) order. (F)
+evaluates to just $4\pi \eta \cos^2 I$. (O) evaluates to $\frac{\cos
+I}{2}A_{sep} = 8\cos I\sqrt{\eta \sin I}$, and (I) twice that. Lastly, (L)
+evaluates to $4\pi \sin I$. This agrees with our numerical check.
+
+We now track the bottom integral. Here, the integrand is instead evaluated at
+$\mu_-(\phi) = \eta \cos I - \sqrt{2\eta \sin I\p*{1 - \cos \phi}}$. This flips
+the signs of the (O) and (I) terms above. Furthermore, the $\mathrm{d}\phi$
+direction changes, and so we arrive at capture probability
+\begin{equation}
+    P_{c} = \frac{48\cos I \sqrt{\eta \sin I}}{
+        4\pi \sin I + 24\cos I \sqrt{\eta \sin I} + 4\pi \eta \cos^2 I}.
+\end{equation}
+The issue compared to the analytical computation comes in because $\cos I$ gives
+an extra factor of $1.5$ to the antisymmetric term, which gives a large enough
+prefactor that the $\sqrt{\eta}$ term is competitive with the $\eta^0$ term in
+the denominator; my earlier work showed $P_c = \frac{8\cos
+I\sqrt{\eta}}{\pi \sqrt{\sin I}}$. The last term in the denominator is
+negligible though, as one might expect.
 

### 2019-06-18 initial/2_toy2/1sim.py

@@ -185,14 +185,17 @@ def run_stats(I_deg):
     ax2.set_xlabel(r'$\eta_\star$')
     ax2.legend()
 
-    x_vals = (bins[ :-1] + bins[1: ]) / 2
-    # ax1.plot(x_vals, n[0] / n[1])
-    ax1.errorbar(x_vals, n[0] / n[1], yerr = np.sqrt(n[0]) / n[1],
+    eta_vals = (bins[ :-1] + bins[1: ]) / 2
+    # ax1.plot(eta_vals, n[0] / n[1])
+    ax1.errorbar(eta_vals, n[0] / n[1], yerr = np.sqrt(n[0]) / n[1],
                  fmt='o', label='Data')
     mean_p = np.mean(n[0] / n[1])
     ax1.axhline(mean_p, c='r', label='Mean')
-    ax1.plot(x_vals, 22.25 * x_vals, 'g:', linewidth=2,
-             label='Not-Fit')
+    fit = lambda eta: 48 * np.cos(I) * np.sqrt(eta * np.sin(I)) / (
+        4 * np.pi * np.sin(I)
+            + 24 * np.cos(I) * np.sqrt(eta * np.sin(I))
+            + 4 * np.pi * eta * np.cos(I)**2)
+    ax1.plot(eta_vals, fit(eta_vals), 'g:', linewidth=2, label='Fit')
     ax1.set_title(r'$I = %d^\circ, \langle \eta_\star \rangle = %.3f$'
                   % (I_deg, mean_p))
     ax1.set_ylabel('Capture Probability')
@@ -210,3 +213,4 @@ if __name__ == '__main__':
 
     run_stats(20)
     run_stats(10)
+    run_stats(25)

### 2019-06-18 initial/2_toy2/2_numcheck.py

@@ -1,0 +1,36 @@
+'''
+quick script, just need to store somewhere
+
+Numerically validate the integrals for Phop in toy problem 2, using the known
+eta_star values
+'''
+import numpy as np
+from scipy import integrate
+
+I = np.radians(20)
+eta = 0.029
+
+def mu_up(phi):
+    return eta * np.cos(I) + np.sqrt(2 * eta * np.sin(I) * (1 - np.cos(phi)))
+
+def mu_down(phi):
+    return eta * np.cos(I) - np.sqrt(2 * eta * np.sin(I) * (1 - np.cos(phi)))
+
+def arg(phi):
+    m = mu_up(phi)
+    return m * (m / eta + np.cos(I))
+
+def arg_bot(phi):
+    m = mu_down(phi)
+    return m * (m / eta + np.cos(I))
+
+if __name__ == '__main__':
+    top = integrate.quad(arg, 0, 2 * np.pi)[0]
+    bot = integrate.quad(arg_bot, 0, 2 * np.pi)[0]
+    tot = top - bot
+    top_anal = (4 * np.pi * np.sin(I) +
+        4 * np.pi * eta * np.cos(I)**2 +
+          24 * np.cos(I) * np.sqrt(eta * np.sin(I)))
+    tot_anal = (48 * np.cos(I) * np.sqrt(eta * np.sin(I)))
+    print(top_anal, top)
+    print(tot_anal, tot)

### 2019-06-18 initial/notes.tex
add correct eta calc

@@
     H = -\alpha\frac{\mu^2}{2} +
-        \mu \cos I - \sin I \sqrt{1 - \mu^2} \theta \cos \phi.
+        \mu \cos I - \sin I \sqrt{1 - \mu^2} \cos \phi.
 \end{equation}
@@
 negligible though, as one might expect.
+
+\subsection{Retry without changing Hamiltonian}
+
+Of course, it should be noted that modifying the Hamiltonian by dividing through
+by $\eta$ and defining $\alpha = 1/\eta$ actually changes the dynamics; we can
+see this since $\pd{(H/\eta)}{t}\dot{\eta} \neq
+\pd{H}{t}\frac{\dot{\eta}}{\eta}$. Since my simulated system actually uses the
+same Hamiltonian as toy problem 1, we should probably update the above algebra
+to use the correct term. Note that the correction should be small, of order
+$\frac{H/\eta^2}{\pd{H}{\eta}/\eta}$.
+
+For clarity, $H$ and $H_4$ are now
+\begin{align*}
+    H &= -\frac{\mu^2}{2}
+            + \eta\p*{\mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi}, &
+    H_4 &= -\eta \sin I + \frac{\eta^2 \cos^2 I}{2}.
+\end{align*}
+Thus, our $B_i$ are
+\begin{align*}
+    B_i &= \int_{\mathcal{C}_i} \epsilon \mu \eta
+            \s*{-\sin I + \eta \cos^2 I -
+                \p*{\mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi}}
+            \;\mathrm{d}t,\\
+        &\approx \int_{\mathcal{C}_i} \epsilon \mu \eta
+            \frac{\eta \cos^2 I - \mu \cos I
+                + \sin I\p*{\cos \phi \sqrt{1 - \mu^2} - 1}}{-\mu + \eta \cos I}
+            \;\mathrm{d}\phi,\\
+        &= \int_{\mathcal{C}_i} \epsilon \mu \eta
+            \p*{-\cos I + \sin I \frac{\cos \phi \sqrt{1 - \mu^2} - 1}{-\mu +
+            \eta \cos I}} \;\mathrm{d}\phi.
+\end{align*}
+That the second term does not diverge requires some careful work:
+\begin{align*}
+    \frac{\cos \phi\sqrt{1 - \mu^2} - 1}{\mu - \eta \cos I}
+        &\approx \frac{\sqrt{1 - 2\eta \sin I\p*{1 - \cos \phi}}\cos \phi
+            - 1}{\mu - \eta \cos I},\\
+        &\approx \frac{(1 - \eta \sin I(1 - \cos \phi))\cos \phi - 1}{
+            \mu - \eta \cos I},\\
+        &\approx \pm\frac{(1 + \eta \sin I)(\cos \phi - 1)}{\sqrt{2\eta \sin I
+            (1 - \cos \phi)}},\\
+        &\approx \mp\sqrt{\frac{1 - \cos \phi}{2\eta \sin I}},\\
+    B_i &= \int_{\mathcal{C}_i} \epsilon \mu \eta
+            \p*{-\cos I \pm \sin I
+                \sqrt{\frac{1 - \cos \phi}{2\eta \sin I}}} \;\mathrm{d}\phi.
+\end{align*}
+Note that the plus sign corresponds to the top integral, where $\mu - \eta \cos
+I > 0$. The top integral evaluates easily
+\begin{align*}
+    B_{top} &= \int\limits_{2\pi}^0 -\epsilon \mu \eta \cos I\;\mathrm{d}\phi
+            + \frac{\epsilon}{2}\int\limits_{2\pi}^0
+                \mu\sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
+        &= \epsilon \eta \cos I\p*{2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
+            + \frac{\epsilon}{2}\p*{\eta \cos I (8\sqrt{\eta \sin I})
+            + 4\pi \eta \sin I},\\
+        &= \epsilon \eta \s*{
+            2\pi \sin I + 12\sqrt{\eta \sin I}\cos I + 2\pi \eta \cos^2 I}.
+\end{align*}
+The bottom integral just flips the signs of the cross terms (the $\sqrt{\eta}$
+terms), since the integration path changes, which changes the sign inside the
+$B_i$ expression and $\mu$. The total integral is the difference between the top
+and bottom integrals, which is just twice the sign-changed terms, and so we
+obtain
+\begin{equation}
+    P_c = \frac{24\cos I \sqrt{\eta \sin I}}{
+            2\pi \sin I + 12\sqrt{\eta \sin I}\cos I + 2\pi \eta \cos^2 I}.
+\end{equation}
+Indeed we get the same expression; this is probably since the approximations we
+made in writing down $B_i$ washed out the extra $\eta$ dependence.
 

### 2019-06-24 initial/notes.tex

@@
 \begin{equation}
-    \mathcal{H} = \frac{1}{2}\p*{\hat{s} \cdot \hat{l}}^2
-        - \eta \p*{\hat{s} \cdot \hat{l}_p}.
+    \mathcal{H} = -\frac{1}{2}\p*{\hat{s} \cdot \hat{l}}^2
+        + \eta \p*{\hat{s} \cdot \hat{l}_p}.
 \end{equation}
@@
 \end{equation*}
-We can choose the convention for $\phi = \phi$ azimuthal angle requiring $\phi =
+We can choose the convention for $\phi$ azimuthal angle requiring $\phi =
 0, \pi$ mean coplanarity between $\hat{s}, \hat{l}, \hat{l}_p$ in the $\hat{x},

### 2019-06-25 writeups/paper.tex
stash writeup

    \documentclass[
        fleqn,
        usenatbib,
    ]{mnras}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        ae, aecompl,
        graphicx,
        booktabs,
    }
    \usepackage[T1]{fontenc}
    \usepackage[
        labelfont=bf, % caption names are labeled in bold
        font=scriptsize % smaller font for captions
    ]{caption}

    \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
    \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
    \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
    \newcommand*{\at}[1]{\left.#1\right|}
    \newcommand*{\abs}[1]{\left|#1\right|}
    \newcommand*{\ev}[1]{\langle#1\rangle}
    \newcommand*{\p}[1]{\left(#1\right)}
    \newcommand*{\s}[1]{\left[#1\right]}
    \newcommand*{\z}[1]{\left\{#1\right\}}
    \DeclareMathOperator*{\argmin}{argmin}
    \DeclareMathOperator*{\argmax}{argmax}
    \DeclareMathOperator*{\med}{med}

\title[Cassini State Capture]{Cassini State Capture}
\author[Y. Su et\ al.]{
Yubo Su$^1$,
Dong Lai$^1$
\\
$^1$ Cornell Center for Astrophysics and Planetary Science, Department of
Astronomy, Cornell University, Ithaca, NY 14853, USA
}

\date{Accepted XXX\@. Received YYY\@; in original form ZZZ}

\pubyear{2019}

\begin{document}\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\renewcommand*{\sectionautorefname}{Section}
\maketitle

\begin{abstract}
    Abstract
\end{abstract}

\begin{keywords}
planet--star interactions % chktex 8
\end{keywords}

\section{Introduction}

Introduction, test citation \citep{henrard1982}.

\section{Cassini States}\label{s:cs}

Denote $\hat{s}$ spin of planet, $\hat{l}$ angular momentum of planet, and
$\hat{l}_p$ angular momentum of perturber. The Cassini state Hamiltonian in the
frame corotating with $\hat{l}_p$ about $\hat{l}$ is:
\begin{equation}
    H = -\frac{\alpha}{2}\p{\hat{s} \cdot \hat{l}}^2
        -g \p{\hat{s} \cdot \hat{l}_p}.
\end{equation}
$\alpha > 0, g < 0$ depend on the particular dynamics of the system. Frequently,
parameter
\begin{equation}
    \eta \equiv \frac{\abs*{g}}{\alpha} \label{eq:eta}
\end{equation}
is defined; we refrain from doing so immediately.

Choose $\hat{l} = \hat{z}$ and $\hat{l}_p = \cos I \hat{z} + \sin I \hat{x}$.
Furthermore, choose standard convention where $\phi = 0$ corresponds to
$\hat{l}_p, \hat{s}$ lying on \emph{opposite} sides of $\hat{l}$. This allows us
to evaluate Hamiltonian
\begin{equation}
    H = -\frac{\alpha}{2}\cos^2\theta
        + \abs{g} \p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}
        \label{eq:H}
\end{equation}
Here, $\mu \equiv \cos \theta, \phi$ are canonically conjugate.

\subsection{Equilibria}

The evolution of $\hat{s}$ in this corotating frame is governed by:
\begin{equation}
    \rd{\hat{s}}{t} = \alpha \p{\hat{s} \cdot \hat{l}}
            \p{\hat{s} \times \hat{l}}
        - \abs{g}\p{\hat{s} \times \hat{l}_p}.
        \label{eq:dsdt_base}
\end{equation}

Spin states satisfying $\rd{\hat{s}}{t} = 0$ are referred to as \emph{Cassini
States} (CS). When $\eta < \eta_c$, there are four CSs, and when $\eta > \eta_c$
there are only two; $\eta_c$ is
\begin{equation}
    \eta_c \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{3/2}.
\end{equation}
Using the standard numbering given in \autoref{fig:0_1contours}, CSs 1, 2, 3 are
stable while CS4 is unstable.

\subsection{Separatrix}

In the four-CS regime, one of the CSs is a saddle point, conventionally denoted
Cassini State 4 (CS4). On the cylindrical phase space parameterized by $(\mu,
\phi)$, all trajectories are periodic with finite period except two critical (or
heteroclinic) trajectories. These are asymptotic in the past and future to CS4.
Together, these two heteroclinic are referred to as the \emph{separatrix} and
divide phase space into three zones.

The area enclosed by the separatrix is known exactly in literature
\citep{henrard1987}, but a serviceable approximation for small $\eta$ can be
derived as follows. Call $H_4$ the value of $H$ at CS4, then the separatrix is
defined implicitly by solutions to $H\p{\mu_{sep}(\phi), \phi} = H_4$. This may
be evaluated and we obtain
\begin{equation}
    \mu_{sep}(\phi) \approx \pm \sqrt{2\eta \sin I \p{1 - \cos \phi}}
        + \eta \cos I + \mathcal{O}\p{\eta^{3/2}}.\label{eq:mu_sep}
\end{equation}
The enclosed area between the two solutions can be obtained via explicit
integration. It can be expressed as a fraction of the total phase space area:
\begin{equation}
    \frac{A_{sep}}{4\pi} \approx \frac{4\sqrt{\eta \sin I}}{\pi}
        + \mathcal{O}\p{\eta^{3/2}}.\label{eq:a_sep}
\end{equation}

Contours of equal $H$, CSs and the separatrix are plotted in
\autoref{fig:0_1contours}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/0_eta/1contours.png}
    \caption{Contours of equal $H$, given by \autoref{eq:H}, at different values
    of $\eta \equiv \frac{\abs{g}}{\alpha}$. Labeled are CS1 (red), CS2
    (purple), CS3 (green) and CS4 (cyan). The thick black dashed line is the
    separatrix (which disappears for $\eta > \eta_c$). Finally, the fractional
    area enclosed by the separatrix is noted in the plot subtitles, in good
    agreement with \autoref{eq:a_sep}.}\label{fig:0_1contours}
\end{figure}

\section{Separatrix Crossing: Theory}\label{s:sep_cross}

In an exactly Hamiltonian system, $H$ is a conserved quantity and trajectories
in phase space coincide with level curves of $H$. If a system is only slightly
non-Hamiltonian, trajectories will generally cross level curves. Of particular
interest is the behavior of trajectories near the separatrix (also a level
curve), as it frequently governs the dynamics of resonance capture (CITE MMR,
Cassini, others). The intersection of system trajectories with the separatrix is
referred to as \emph{separatrix crossing}.

In previous work by~\cite{henrard1982}, separatrix crossing was studied for systems
that are Hamiltonian save for an adiabatically-varying parameter. In related work
surveyed by~\cite{g_and_h}, the impact of small perturbations to the equations
of motion of a Hamiltonian system are studied (referred to as \emph{saddle
connection bifurcations}). However, in some astrophysical systems of interest,
leading-order perturbations to a Hamiltonian system contribute in both of the
above ways. Such systems resist characterization via either existing technique.
We suggest a possible generalization unifying the above techniques. [Probably
eventually move this paragraph to the introduction]

\subsection{Derivation}\label{ss:henrard}

Consider our Hamiltonian described in \autoref{eq:H} as a unperturbed
Hamiltonian $H^{(0)}(\mu, \phi; \eta)$ where $\eta$ is to be varied
adiabatically. As $\eta$ varies, the location of the separatrix also changes. We
follow~\cite{henrard1982} by defining
\begin{equation}
    h(\mu, \phi; \eta) \equiv H^{(0)}(\mu, \phi; \eta) - H_4(\eta).
\end{equation}
The significance of $h$ is that it always vanishes along the separatrix. Note
that $h$ corresponds to $K$ in~\cite{henrard1982}, though in our problem
$H^{(0)} > H_4$ corresponds to the \emph{interior} of the separatrix. The
evolution of $h$ over time then determines whether and when a trajectory
experiences separatrix crossing. Denoting time derivatives with dots, we write
\begin{align}
    \rd{h}{t} &= \rd{H^{(0)}}{t} - \pd{H_4}{\eta}\dot{\eta},\nonumber\\
        &= \s{\pd{H^{(0)}}{\mu}\dot{\mu}
                + \pd{H^{(0)}}{\phi}\dot{\phi}
                + \pd{H^{(0)}}{\eta}\dot{\eta}}
            - \pd{H_4}{\eta}\dot{\eta},\nonumber\\
        &= \s{\pd{H^{(0)}}{\mu}\dot{\mu}
                + \pd{H^{(0)}}{\phi}\dot{\phi}
                + \pd{H^{(0)}}{\eta}\dot{\eta}}
            - \pd{H_4}{\eta}\dot{\eta},\nonumber\\
        &= \s{\dot{\phi}^{(0)}\dot{\mu}^{(1)}
                - \dot{\mu}^{(0)}\dot{\phi}^{(1)}
                + \pd{H^{(0)}}{\eta}\dot{\eta}} -
            \pd{H_4}{\eta}\dot{\eta}.\label{eq:dhdt}
\end{align}
We've notated $\dot{\phi}^{(0)} \equiv \pd{H^{(0)}}{\mu}$ and $\dot{\phi}^{(1)}
= \dot{\phi} - \dot{\phi}^{(0)}$ and similarly for $\mu$. The scenario studied
in~\cite{henrard1982} corresponds to $\dot{\mu}^{(1)} = \dot{\phi}^{(1)} = 0$
while that in~\cite{g_and_h} sets $\dot{\eta} = 0$.

In the neighborhood of $\mathcal{C}_{\pm}$, $\rd{h}{t}$ can be
approximated by its value on $\mathcal{C}_{\pm}$. This is the \emph{guiding
orbit} approximation; its accuracy is proven in~\cite{henrard1982} for their
specific application, while we will take it on good faith in ours. Denote then
\begin{equation}
    \Delta_{\pm} \equiv \int_{\mathcal{C}_{\pm}} \rd{h}{t}\;\mathrm{d}t.
        \label{eq:delta}
\end{equation}
These approximate $\Delta h$ for trajectories near $\mathcal{C}_{\pm}$ over one
orbit. They are identical to the $B_i$ defined in~\cite{henrard1982}.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/1_weaktide/3zones.png}
    \caption{Nomenclature of the two legs of the separatrix $\mathcal{C}_{\pm}$
    and three zones of the domain. For both $\mathcal{C}_{\pm}$, we will take
    the positive direction to be anti-clockwise.}\label{fig:1_3zones}
\end{figure}
For concreteness, we consider a specific example first. We assign labels to our
phase space as shown in \autoref{fig:1_3zones}. Consider a trajectory that
begins in zone III, which is circulating with $\dot{\phi} > 0$ and has $h < 0$,
and consider if $\rd{h}{t} > 0$ in all of zone III, such that the trajectory
eventually experiences separatrix crossing at $\mathcal{C}_-$. The following
sequence of events unfolds:
\begin{enumerate}
    \item[\textbf{(i)}] At the beginning ($\phi = 0$) of its separatrix-crossing
        orbit, $h_i \equiv h(\mu, \phi = 0; \eta) \in (\Delta_-, 0)$. Note
        that $h_i < 0$ to still be in zone III at the start of the orbit, while
        $h_i > \Delta_-$ to be separatrix crossing during the final orbit.

    \item[\textbf{(ii)}] After traversing the length of $\mathcal{C}_-$, the
        value of $h$ is now $h_i + \Delta_- > 0$ (recall $\Delta_- > 0$), and so
        the trajectory has entered zone II\@. Since zone II hosts only librating
        solutions, the trajectory will then ``turn around'' and track
        $\mathcal{C}_+$ from inside zone II\@.

    \item[\textbf{(iii)}] At the end of following $\mathcal{C}_+$, $h$ now takes
        value $h_f \equiv h_i + \Delta_- + \Delta_+$. There are now two
        possibilities:

    \item[\textbf{(iii-a)}] If $h_f > 0$, the trajectory remains inside zone II
        accrues further multiples of $\Delta_- + \Delta_+ = h_f - h_i > 0$.
        Thus, the trajectory must securely enter zone II\@. This outcome
        commonly corresponds to \emph{resonance capture}, a transition into zone
        II\@.

    \item[\textbf{(iii-b)}] If $h_f < 0$, the trajectory exits zone II and
        enters zone I\@. Since $\Delta_+ = h_f - h_i - \Delta_- < 0$ (as $h_f
        < 0, h_i + \Delta_- > 0$), the trajectory will continue circulation in
        zone I and accrue further multiples of $\Delta_+$, securely entering
        zone I\@. This corresponds to a zone III-zone I transition,
        \emph{escape}.
\end{enumerate}

Thus, the result of separatrix crossing depends on the sign of $h_i +
\Delta_- + \Delta_+$ where $\Delta_{\pm}$ are given by \autoref{eq:delta} and
$h_i \in [-\Delta_-, 0]$. The result of this analysis reproduces the conclusion
of~\cite{henrard1982}:
\begin{itemize}
    \item If $\Delta_+ < -\Delta_-$, then $h_f < 0$ necessarily, secure escape
        ensues.

    \item If $\Delta_+ > 0$, then $h_f > 0$ necessarily, and secure capture
        ensues.

    \item If $\Delta_+ + \Delta_- \in [0, \Delta_-]$, then it is clear that the
        sign of $h_f$ depends on the precise value of $h_i$. Generally,
        $\Delta_-$ can be assumed to be small as perturbations are weak, and
        so $\Delta_-$ is usually much smaller than the range of $h$ of interest.
        Thus, $h_i$ can be treated as uniformly distributed on interval
        $[-\Delta_-, 0]$, and a probability of resonance capture can be
        computed:

        \begin{equation}
            P_c \equiv \frac{\Delta_+ + \Delta_-}{\Delta_-}.
                \label{eq:p_c_gen}
        \end{equation}
\end{itemize}
With the exception of \autoref{eq:dhdt}, the above outlines the argument given
in~\cite{henrard1982}.

Similar derivations can be given for trajectories originating in zone I.
TODO say something about zone-II originating systems.

\subsection{Equivalence to Stable/Unstable Manifold Splitting}\label{ss:meln}

We now establish equivalence to an alternative formulation popular in dynamical
systems that is more graphically intuitive. For simplicity, we will take
$\dot{\eta} = 0$.

If we return to the unperturbed Hamiltonian system, recall that CS4 is joined to
itself by an infinite-period orbit. For a given saddle point, we may define the
\emph{stable manifold} $W_s$ of a saddle point to be the set of points whose
forward evolution converges to the saddle point. Similarly, we may define the
\emph{unstable manifold} $W_u$ of a saddle point to be the set of points that
originated \emph{from} the saddle point, or whose backwards evolution converges
to the saddle point. A \emph{saddle connection} is when the unstable manifold of
one saddle point and the unstable manifold of another saddle point are
degenerate. It is evident that the separatrix is formed of two saddle
connections: $\mathcal{C}_+$ is the unstable manifold of CS4 at $\phi = 2\pi$
and the stable manifold of CS4 at $\phi = 0$.

In the presence of a small perturbation, the stable and unstable manifolds
generally separate, as the perturbations along the saddle connection will
generally be different going forwards and backwards in time. The separation
distance as a function of time along the \emph{unperturbed} trajectory can be
computed via \emph{Melnikov's Method}
\begin{equation}
    d(t_0) = \frac{\epsilon}{\abs{f(q^0(-t_0))}}
        \int\limits_{-\infty}^\infty
            f(q^0(t - t_0)) \wedge g(q^0(t - t_0), t)\;\mathrm{d}t.
\end{equation}
The notation used here is that of~\cite{g_and_h}, where $d(t_0)$ is the distance
between the stable/unstable manifolds at time $t_0$ along the heteroclinic
orbit, $f = \p{\dot{\mu}^{(0)}, \dot{\phi}^{(0)}}$, $\epsilon g =
\p{\dot{\mu}^{(1)}, \dot{\phi}^{(1)}}$ a general time-dependent perturbation,
$q^0(t)$ is the unperturbed trajectory along the saddle connection (time
coordinate defined such that $t = 0$ coincides with the ``middle'' of the
infinite trajectory), and $\wedge$ is the wedge product.

We will assume $\epsilon g$ is not explicitly time-dependent, characteristic of
secular/averaged equations in astrophysics, then the integral above is simply
the familiar
\begin{equation}
    d(t_0) \abs{\vec{\nabla}H^{(0)}}(t_0) = \epsilon \int\limits_{-\infty}^\infty
        \dot{\mu}^{(0)}\dot{\phi}^{(1)} - \dot{\phi}^{(0)}\dot{\mu}^{(1)}
            \;\mathrm{d}t.\label{eq:melnikov}
\end{equation}
The right hand side is just the total change in $H^{(0)}$ over the saddle
connection though, equivalent to our \autoref{eq:delta} in the $\dot{\eta} = 0$
limit. The left hand side on the other hand is exactly $\abs{\vec{d} \cdot
\vec{\nabla}H^{(0)}}$ where the displacement is along $\vec{\nabla}H^{(0)}$.
Thus, the effect of the $\Delta_{\pm}$ is to split the stable/unstable manifolds
along the saddle connections.

Visually, this is depicted in \autoref{fig:0_6manifolds}. Note that:
trajectories starting in zone III below $W_s^{(1)}$ fail to separatrix cross;
those between $W_s^{(1)}$ and $W_s^{(0)}$ continue between $W_u^{(1)}$ and
$W_s^{(0)}$, eventually escaping; those between $W_s^{(0)}$ and $W_u^{(0)}$ are
securely captured, and no trajectories can begin above $W_u^{(0)}$ at $\phi =
0$.

The saddle connection splitting is easiest to measure where $\vec{\nabla}H^{(0)}
\propto \hat{\phi}$, where $\dot{\mu} = 0$, and \autoref{eq:melnikov} reduces to
just $\Delta \mu \pd{H^{(0)}}{\mu} = \Delta H^{(0)}$. Then the capture
probability must be given by ratio of $\Delta \mu$ separating $W_s^{(0)},
W_u^{(0)}$ to $\Delta \mu$ separating $W_s^{(1)}, W_u^{(0)}$. These $\Delta \mu$
values are those given in the title, and the resultant $P_c$ capture probability
is also quoted.
\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{../initial/0_eta/6manifolds0_20.png}
    \caption{Sample plot of saddle connection breaking in the presence of weakly
    non-Hamiltonian dissipation. Equations are used from \autoref{s:p1}. Stable
    and unstable manifolds are indexed such that superscript $(0)$/$(1)$
    belongs to the saddle point at left/right. $\Delta \mu$ represent the
    manifold separations, resulting in capture probability $P_c$
    prediction per \autoref{eq:p_c_dmu}. Numerical simulations predict $P_c
    \approx 0.252$.}\label{fig:0_6manifolds}
\end{figure}

Finally, the connection between \autoref{ss:henrard} and \autoref{ss:meln} is
evident: the ratio of the $\Delta \mu$ values is simply
\begin{align}
    P_c &= \frac{\Delta \mu(W_s^{(0)}, W_u^{(0)})}{
            \Delta \mu\p{W_s^{(1)}, W_u^{(0)}}},\label{eq:p_c_dmu},\\
        &= \frac{\Delta H^{(0)}_- + \Delta H^{(0)}_+}{\Delta H^{(0)}_-}.
\end{align}
This is exactly \autoref{eq:p_c_gen} when $\dot{\eta} = 0$.

\section{Problem 1: Weakly Dissipitive Hamiltonian}\label{s:p1}

We first consider a toy separatrix crossing problem in the $\dot{\eta} = 0$
limit, the case discussed in \autoref{ss:meln}. Consider adding to the
Hamiltonian Cassini State problem an additional aligning term
$\p{\rd{\theta}{t}}^{(1)} = -\frac{1}{t_s}\sin\theta$ that favors alignment
$\theta = 0$ on synchronization timescale $t_s$. This translates to equation of
motion
\begin{equation}
    \rd{\hat{s}}{\tau} = \p{\hat{s} \cdot \hat{l}}\p{\hat{s} \times \hat{l}}
        - \eta\p{\hat{s} \times \hat{l}_p}
        - \epsilon \sin \theta \hat{\theta}.
\end{equation}
We have divided \autoref{eq:dsdt_base} by $\alpha$ and defined $\tau \equiv
\alpha t, \epsilon \equiv \frac{1}{\alpha t_s}$. The equations of motion for
canonical variables $\mu \equiv \cos\theta, \phi$ are
\begin{subequations}\label{se:p1_eom}
    \begin{align}
        \mu' &= -\cos\theta
            + \eta\p{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}} \cos \phi},\\
        \mu' &= -\eta \sin I \sin \theta \sin \phi
            \s{+ \epsilon\p{1 - \mu^2}}.
    \end{align}
\end{subequations}
Primes denote $\rd{}{\tau}$. The bracketed term in $\mu'$ is the perturbation
component.

With a dissipitive term that favors alignment, we expect that separatrix
encounters can only occur from zone II and zone III\@. We will focus on the
outcomes of trajectories origiating in zone III for now. We now aim to compute
\autoref{eq:p_c_gen}, for which we need:
\begin{subequations}
    \begin{align}
        \Delta_- &= \int\limits_{\mathcal{C}_-}
                \phi'\epsilon\p{1 - \mu^2}\;\mathrm{d}t,\nonumber\\
            &= \int\limits_{\mathcal{C}_s}
                \p{1 - \mu^2}\;\mathrm{d}\phi,\\
        \Delta_- + \Delta_+ &= \int\limits_{\mathcal{C}_- + \mathcal{C}_+}
            \epsilon\p{1 - \mu^2}\;\mathrm{d}\phi.
    \end{align}
\end{subequations}
Note that along $\mathcal{C}_{\pm}$ that $\mathrm{d}\phi$ has sign $\mp$
respectively, thanks to our sign convention. We proceed to integrate:
\begin{itemize}
    \item $\Delta_-$: Recalling the parameterization for the separatrix
        $\mu_{sep}(\phi)$ given by \autoref{eq:mu_sep}, we can approximate the
        integrand as $1 + \mathcal{O}(\eta^1)$. This yields simply $\Delta_-
        \approx 2\pi \epsilon + \mathcal{O}(\eta^1)$.

    \item $\Delta_- + \Delta_+$: Since $\mathrm{d}\phi$ changes signs from
        $\mathcal{C}_-$ to $\mathcal{C}_+$, only terms in $(1 - \mu^2)$ that
        also change sign over $\mathcal{C}_{\mp}$ contribute to the integral.
        The leading order term that does so can be read off of
        \autoref{eq:mu_sep}, so the integral evaluates as
        \begin{align}
            \Delta_- + \Delta_+ &\approx
                2\int\limits_0^{2\pi}
                    \s{(\eta \cos I) \sqrt{2\eta \sin I(1 - \cos \phi)}
                        + \mathcal{O}(\eta^{5/2})} \;\mathrm{d}\phi,\\
                &\approx 32\epsilon \eta^{3/2} \cos I \sqrt{\sin I}
                    + \mathcal{O}(\eta^{5/2}).
        \end{align}
\end{itemize}
From these two integrals, we obtain
\begin{equation}
    P_c = \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi}.\label{eq:p1pc}
\end{equation}

As evidence, we provide the following table of separatrix capture probabilities
in \autoref{tab:p_c_num} (TODO make a plot and more robust parameter
exploration):
\begin{table*}
    \centering
    \begin{tabular}{c|c c c c}
        $\eta$ & $0.025$ & $0.05$ & $0.1$ & $0.2$\\\midrule
        Numerical $P_c$ & $0.010 \pm 0.002$ & $0.028 \pm 0.003$
            & $0.085 \pm 0.004$ & $0.251 \pm 0.006$ \\
        Analytical $P_c$ & $0.0111$ & $0.0313$ & $0.0886$ & $0.2503$.
    \end{tabular}
    \caption{Capture probability for four different values of $\eta$, all using
    $\epsilon = 3 \times 10^{-4}$. Different values of $\epsilon$ were tried
    $\epsilon \in 10^{[-2, -4]}$ with no effect on $P_c$. $10000$ random initial
    conditions were used for the numerical calculations, of which roughly $1/2$
    experience separatrix crossing. Numerical uncertainties are estimated as
    $\sqrt{N}$ errors.}\label{tab:p_c_num}
\end{table*}

For trajectories originating in zone II, numerical simulations indicate they can
never leave the separatrix. This can be intuited by considering trajectories
that are near the separatrix; over one orbit, they accumulate $\Delta h =
\Delta_+ + \Delta_- > 0$, which acts to drive them \emph{towards} CS2 and away
from the separatrix. Thus, separatrix crossing is forbidden in zone II, and our
above characterization of separatrix encounters with $P_c$ in \autoref{eq:p1pc}
is complete.

TODO prove the above completely.

\section{Problem 2: Adiabatic Capture}\label{s:p2}

Here, instead of introducing an aligning perturbation, we will instead
adiabatically vary $\eta$.

\subsection{Spindown Model}

We may first consider the unperturbed Hamiltonian
system with $\rd{\eta}{t} = \frac{\eta}{t_\eta}$ growth with characteristic
timescale $t_\eta$. Again rescaling time $\tau \equiv \alpha t$ and defining
$\epsilon \equiv \frac{1}{\alpha t_\eta}$, we obtain $\eta' = \epsilon
\eta$, where $\epsilon > 0$. Such a model is motivated e.g.\ when a planet's
spin $\hat{s}$ orbits a host star with angular momentum $\hat{l}$ while the star
spins down; $\dot{\alpha} < 0$ here, and $\eta' > 0$.

We then seek $\Delta_{\pm}$, determined by
\begin{align}
    \Delta_{\pm} &= \int\limits_{\mathcal{C}_{\pm}}
            \pd{h}{\eta}\eta'\;\mathrm{d}\tau,\nonumber\\
        &= \int\limits_{\mathcal{C}_{\pm}}
            \frac{\pd{h}{\eta}}{\phi'}\eta'\;\mathrm{d}\phi.
\end{align}
We must proceed carefully since $\phi' \to 0$ at the endpoints of
$\mathcal{C}_{\pm}$; careful work shows these zeros cancel against zeros of
$\pd{h}{\eta}$, and
\begin{equation}
    \Delta_{\pm} = \int\limits_{\mathcal{C}_{\pm}} \eta'
        \p{\cos I \mp \sin I \sqrt{\frac{1 - \cos \phi}{2\eta\sin I}}}
            \;\mathrm{d}\phi.\label{eq:p2_delta}
\end{equation}
Immediately, we see that if we use $\eta' = \epsilon \eta$, then $\Delta_{\pm} >
0$ and \emph{all separatrix encounters result in capture} regardless of whether
the trajectory originates in zone I or zone III\@. Since increasing $\eta$
results in larger separatrix, zone II trajectories will not experience
separatrix crossing. Indeed, an example of such a simulation is presented in
\autoref{fig:2_1testo4}. Further simulations with other initial conditions
support the guaranteed capture prediction in this system.
\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{../initial/2_toy2/1testo4.png}
    \caption{Simulation with initial condition in zone I subject to $\eta' =
    \epsilon \eta$, where $\epsilon = 10^{-4}$. The top panel shows the
    trajectory (red) and separatrix at separatrix crossing (dashed black) in
    the labelled coordinates. The bottom panel shows the evolution of the
    enclosed area by the trajectory (red dots), area of the separatrix (blue)
    and $\eta$ (dotted green) over time.}\label{fig:2_1testo4}
\end{figure}

If instead $\epsilon < 0$, then only zone II initial conditions experience
separatrix encounter, and since $\Delta_{\pm} < 0$, all trajectories are
ejected as the separatrix shrinks.

\subsection{Toy Model}

It is clear that $\eta'$ in \autoref{eq:p2_delta} being the same sign along both
$\mathcal{C}_{\pm}$ is the source of this guaranteed capture. To assess the
accuracy of our formalism, we choose to further study $\eta' = \epsilon \eta
\mu$. Straightforward evaluation of \autoref{eq:p2_delta} yields
\begin{equation}
    \Delta_{\pm} = \pm \epsilon \eta_\star \s{
        2\pi \sin I \pm 12 \sqrt{\eta_\star \sin I}\cos I
            + 2\pi \eta_\star \cos^2 I}.
\end{equation}
It bears noting that we must evaluate these integrals at $\eta = \eta_\star$ the
value at separatrix crossing. Since $\eta$ evolves over time, $\eta_{\star}$
depends on initial conditions. While one might expect the adiabatic invariance
of the action variable determines $\eta_\star$, this turns out to not be the
case; we address this in \autoref{ss:noncons}.

Since $\abs{\Delta_+} > \abs{\Delta_-}$, separatrix encounters originating in
zone III always result in capture. However, encounters originating in zone I
experience capture probability
\begin{equation}
    P_c = \frac{24\cos I \sqrt{\eta_\star \sin I}}{
        2\pi \sin I + 12\sqrt{\eta_\star \sin I}\cos I
            + 2\pi \eta_\star \cos^2 I}.
\end{equation}
This is in good agreement
% TODOYUBO plots

\subsection{Non-conservation of Adiabatic Invariant}\label{ss:noncons}

Best evidence is $\eta_{\star}$ when changing $I$, blatantly wrong scaling

\section{Problem 3: Weak Tidal Dissipation}\label{s:p3}

% TODOYUBO show that zone II stays in zone II?

\bibliographystyle{mnras}
\bibliography{paper}

% \clearpage
% \onecolumn
% \appendix

\label{lastpage} % chktex 24
\end{document}

### 2019-06-25 initial/2_toy2/1sim.py

@@ -12,7 +12,7 @@ plt.rc('font', family='serif', size=12)
 
 PLOT_DIR = '1plots'
 from utils import to_cart, to_ang, solve_ic, get_areas, get_plot_coords,\
-    roots, H, get_mu4
+    roots, H, get_mu4, solve_ic_base
 
 def plot_traj(I, ret, filename):
     ''' convention: -np.pi / 2 < q4 < 0 '''
@@ -21,7 +21,10 @@ def plot_traj(I, ret, filename):
     y = ret.y
     lw = 1
 
-    fig, (ax1, ax2) = plt.subplots(2, 1, gridspec_kw={'height_ratios': [2, 1]})
+    fig, (ax1, ax2) = plt.subplots(2, 1,
+                                   figsize=(6, 8),
+                                   gridspec_kw={'height_ratios': [3, 1]})
+    ax1.set_aspect('equal')
 
     # plot projection
     q, phi = to_ang(*y[0:3])
@@ -35,18 +38,21 @@ def plot_traj(I, ret, filename):
     bound_y = np.sin(bound_phi)
     ax1.plot(bound_x, bound_y, 'k', linewidth=5)
 
-    # plot separatrix @ end
+    # plot separatrix @ cross
     t_areas, areas, t_cross, ends_circ = get_areas(ret)
     # print('Initial area', areas[0])
-    eta_f = y[3, -1]
-    cs_qs = roots(I, eta_f)
+    circ_idxs = np.where(t <= t_cross)[0]
+    post_idxs = np.where(t > t_cross)[0]
+    cross_idx = circ_idxs[-1]
+    eta_cross = y[3, cross_idx]
+    cs_qs = roots(I, eta_cross)
     q4 = cs_qs[-1]
 
     phi_sep = np.linspace(0, 2 * np.pi, n_pts)[1: -1] # omit endpoints
     q_sep_top, q_sep_bot = np.zeros_like(phi_sep), np.zeros_like(phi_sep)
     for idx, phi in enumerate(phi_sep):
         def dH(q):
-            return H(I, eta_f, q, phi) - H(I, eta_f, q4, 0)
+            return H(I, eta_cross, q, phi) - H(I, eta_cross, q4, 0)
         q_sep_bot[idx] = opt.brentq(dH, -np.pi, q4)
         q_sep_top[idx] = opt.brentq(dH, q4, 0)
 
[…]

### 2019-06-25 initial/2_toy2/utils.py

@@ -178,5 +178,26 @@ def solve_ic(I, eps, y0, tf, rtol=1e-6, **kwargs):
 
     return ret
 
+def solve_ic_base(I, eps, y0, tf, rtol=1e-6, **kwargs):
+    '''
+    get dy/dt for (x, y, z, eta)
+
+    returns (t, y, sep areas, ret)
+    '''
+    def dydt(t, s):
+        x, y, z, eta = s
+        return [
+            y * z - eta * y * np.cos(I),
+            -x * z + eta * (x * np.cos(I) - z * np.sin(I)),
+            eta * y * np.sin(I),
+            eps * eta,
+        ]
+    event = lambda t, y: y[1]
+    ret = solve_ivp(dydt, [0, tf], y0,
+                    rtol=rtol, dense_output=True, events=[event],
+                    **kwargs)
+
+    return ret
+
 def get_plot_coords(q, phi):
     return np.sin(q / 2) * np.cos(phi), np.sin(q / 2) * np.sin(phi)

### 2019-06-26 initial/notes.tex
stash writeup
stash

@@
 
+\textbf{NB:} Our convention is that $\phi = 0$ for CS1, 3, 4, all of which are
+on opposite sides of $\hat{l}$ from $\hat{l}_p$.
+
 \subsection{Equation of Motion}
@@
 This agrees perfectly with the cases we've run.
+
+\textbf{Note:} The full formula, by actually evaluating all the terms, comes out
+to be
+\begin{equation}
+    P_{hop} = \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi
+        \p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
+        + 8\eta^{3/2}\cos I \sqrt{\sin I}}.
+\end{equation}
+It bears noting this formula slightly overpredicts $P_{hop}$ compared to the
+actual simulation values; this comes down to ICs too near the separatrix being
+necessarily escape-bound (can see \autoref{fig:CS4s} for more evidence).
 
@@
 
-Can we analytically show that the Melnikov splitting dominates, and that in
-particular the seeming small excess of $P_{hop}$ is predictable?
+\textbf{Revisited:} We should be able to evaluate this integral analytically.
+We've already mostly done the $\dot{\mu}\;\mathrm{d}\phi$ integral, let's now
+consider the $\frac{\dot{s}}{\dot{\phi}}\Delta H_{,s}\;\mathrm{d}\phi$
+component. This is just (we change sign convention, $\Delta H = H - H_4$ now,
+per recent developments)
+\begin{align*}
+    \int_{\mathcal{C}_{\pm}} \frac{\dot{s}}{\dot{\phi}^{(0)}}
+            \pd{\Delta H}{s}\;\mathrm{d}\phi &=
+        \int \dot{s}\frac{-\frac{\mu^2}{2s_c} + \frac{\cos^2 Is_c}{2s^2}}{
+            -\frac{s}{s_c}\mu + \cos I}\;\mathrm{d}\phi,\\
+        &= \int \frac{\dot{s}s_c}{2s^2}\s*{\frac{s\mu}{s_c} + \cos
+            I}\;\mathrm{d}\phi,\\
+        &= \pm \int \epsilon 2\Omega_1
+            \p*{\mu_{\pm} - \frac{s}{2\Omega_1}\p*{1 + \mu_{\pm}^2}}
+                \frac{s_c}{2s^2} \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}}
+                \;\mathrm{d}\phi,\\
+        &\approx \pm \frac{\epsilon \Omega_1 s_c}{s^2}
+            \int \p*{\mu_{\pm} - \frac{s}{2\Omega_1}}
+            \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}} \;\mathrm{d}\phi,\\
+        &\approx \pm\frac{\epsilon \Omega_1 s_c}{s^2}
+            \int \p*{\mu_4 - \frac{s}{2\Omega_1} \pm
+                \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}}}
+            \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}} \;\mathrm{d}\phi,\\
+        &= \frac{\epsilon \Omega_1 s_c}{s^2}\s*{
+            \pm \p*{\mu_4 - \frac{s}{2\Omega_1}}\p*{-8\sqrt{\eta \sin I}}
+                + 4\pi \frac{s_c}{s}\sin I}.
+\end{align*}
+Indeed, the sum over the two legs is positive, which is expected: during
+spindown, the separatrix expands, so the separatrix must have $\Delta H > 0$
+owing just to adiabatic expansion.
+
+For the $\dot{\mu}$ integral, the integrand is $\p*{\frac{2\Omega}{s} - \mu}$
+times the original integrand; this means the final result is $\frac{2\Omega}{s}$
+times the old result plus a contribution approximately $-\int \epsilon \mu
+\;\mathrm{d}\phi$. This latter term is a purely antisymmetric contribution, so
+we may approximate
+\begin{align*}
+    \int_{\mathcal{C}_{\pm}}\dot{\mu}^{(1)}\;\mathrm{d}\phi
+        &\approx \epsilon\frac{2\Omega}{s}\p{\mp 2\pi
+            + 16\cos I \eta^{3/2}\sqrt{\sin I}}
+            + 8\epsilon\sqrt{\eta \sin I},\\
+        &\approx \mp \frac{4\pi\epsilon \Omega}{s} + 8\sqrt{\eta \sin I}.
+\end{align*}
+This is in agreement with our work from 5.1. Thus, the total expression is
 

### 2019-06-26 writeups/paper.tex
stash

@@
     ]{caption}
+    \usepackage[font=scriptsize]{subcaption} % subfigures
+    \captionsetup{compatibility=false}
 
@@
     \item $\Delta_-$: Recalling the parameterization for the separatrix
-        $\mu_{sep}(\phi)$ given by \autoref{eq:mu_sep}, we can approximate the
-        integrand as $1 + \mathcal{O}(\eta^1)$. This yields simply $\Delta_-
-        \approx 2\pi \epsilon + \mathcal{O}(\eta^1)$.
+        $\mu_{sep}(\phi)$ given by \autoref{eq:mu_sep}, we can evaluate
+        explicitly over $\mathcal{C}_-$. This gives result
+        \begin{equation}
+            \Delta_- = 2\pi\p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
+                + 16\cos I \eta^{3/2}\sqrt{\sin I}.
+        \end{equation}
 
-    \item $\Delta_- + \Delta_+$: Since $\mathrm{d}\phi$ changes signs from
-        $\mathcal{C}_-$ to $\mathcal{C}_+$, only terms in $(1 - \mu^2)$ that
-        also change sign over $\mathcal{C}_{\mp}$ contribute to the integral.
-        The leading order term that does so can be read off of
-        \autoref{eq:mu_sep}, so the integral evaluates as
+    \item $\Delta_- + \Delta_+$: Note $\mathrm{d}\phi$ changes signs between
+        $\mathcal{C}_-$ and $\mathcal{C}_+$. Thus, only terms in $\Delta_-$ that
+        also change signs on $\mathcal{C}_+$ contribute to the integral. This
+        allows us to evaluate
         \begin{align}
-            \Delta_- + \Delta_+ &\approx
-                2\int\limits_0^{2\pi}
-                    \s{(\eta \cos I) \sqrt{2\eta \sin I(1 - \cos \phi)}
-                        + \mathcal{O}(\eta^{5/2})} \;\mathrm{d}\phi,\\
-                &\approx 32\epsilon \eta^{3/2} \cos I \sqrt{\sin I}
-                    + \mathcal{O}(\eta^{5/2}).
+            \Delta_- + \Delta_+ &= 32\epsilon \eta^{3/2} \cos I \sqrt{\sin I}.
         \end{align}
@@
 \begin{equation}
-    P_c = \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi}.\label{eq:p1pc}
+    P_c = \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi
+        \p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
+        + 8\eta^{3/2}\cos I \sqrt{\sin I}}.\label{eq:p1pc}
 \end{equation}
 
-As evidence, we provide the following table of separatrix capture probabilities
-in \autoref{tab:p_c_num} (TODO make a plot and more robust parameter
-exploration):
 \begin{table*}
@@
         $\eta$ & $0.025$ & $0.05$ & $0.1$ & $0.2$\\\midrule
-        Numerical $P_c$ & $0.010 \pm 0.002$ & $0.028 \pm 0.003$
-            & $0.085 \pm 0.004$ & $0.251 \pm 0.006$ \\
-        Analytical $P_c$ & $0.0111$ & $0.0313$ & $0.0886$ & $0.2503$.
+        Numerical $P_c$ & $0.010 \pm 0.002$ & $0.029 \pm 0.003$
+            & $0.082 \pm 0.004$ & $0.256 \pm 0.006$ \\
+        Analytical $P_c$ & $0.0112$ & $0.0320$ & $0.0915$ & $0.2627$.
     \end{tabular}
@@
     $\epsilon \in 10^{[-2, -4]}$ with no effect on $P_c$. $10000$ random initial
-    conditions were used for the numerical calculations, of which roughly $1/2$
-    experience separatrix crossing. Numerical uncertainties are estimated as
-    $\sqrt{N}$ errors.}\label{tab:p_c_num}
+    conditions uniformly distributed in $(\mu, \phi)$ were used for the
+    numerical calculations, of which roughly $1/2$ experience separatrix
+    crossing. Numerical uncertainties are estimated as $\sqrt{N}$ where $N$ is
+    the count per bin.}\label{tab:p_c_num}
 \end{table*}
+As evidence, we provide the following table of separatrix capture probabilities
+in \autoref{tab:p_c_num}.
+
+It may be noted that the numerical $P_c$ are systematically low compared to
+their analytical estimates. This has a clean explanation: initial conditions
+that start too close to the separatrix violate the assumption where $h_i$ is
+uniformly distributed on $[-\Delta_-, 0]$. In particular, most of the points
+near the separatrix and in zone III are escaping points, as can be visually seen
+in \autoref{fig:0_6manifolds}. A systematic underdensity of points converging to
+CS2 (separatrix capture) can be seen on the right hand side of the plot near the
+separatrix in \autoref{fig:0_3stats}.
+
+A further interesting feature in \autoref{fig:0_3stats} is a small portion of
+points in zone II near CS4  at $\phi = 2\pi$ that escape. These points accrue
+$\Delta_+$ on their first orbit and escape without librating. Visually, this
+zone is obvious in \autoref{fig:0_6manifolds} as the separation between
+$W_s^{(1)} \cup W_u^{(1)}$ and $W_s^{(0)} \cup W_u^{(0)}$ near $\phi = 2\pi$.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/0_eta/3stats3_5_0_1.png}
+    \caption{Plot of the CSs that initial conditions converge to. Each subplot
+    has a set of initial conditions (black dots) and the CS (red dot) that each
+    of these initial conditions converge to. Initial conditions are chosen
+    uniformly in $(\mu, \phi)$ coordinates. The parameters for the simulation
+    are in the title.}\label{fig:0_3stats}
+\end{figure}
 
 For trajectories originating in zone II, numerical simulations indicate they can
-never leave the separatrix. This can be intuited by considering trajectories
-that are near the separatrix; over one orbit, they accumulate $\Delta h =
-\Delta_+ + \Delta_- > 0$, which acts to drive them \emph{towards} CS2 and away
-from the separatrix. Thus, separatrix crossing is forbidden in zone II, and our
-above characterization of separatrix encounters with $P_c$ in \autoref{eq:p1pc}
-is complete.
-
-TODO prove the above completely.
+never leave the separatrix. This can be understood quantitatively (excepting the
+few initial conditions in \autoref{fig:0_3stats} discussed above). For any orbit
+in zone II that completes a full libration over contour $\mathcal{C}$, the total
+change in $h$ is given
+\begin{equation}
+    \Delta h = \epsilon \oint_{\mathcal{C}} (1 - \mu^2)\;\mathrm{d}\phi.
+\end{equation}
+Since $\mathcal{C}$ is a closed contour, any terms that are symmetric on the top
+and bottom legs of $\mathcal{C}$ vanish. If we decompose $\mu(\phi) \equiv
+\bar{\mu} \pm \mu'(\phi)$ where $\bar{\mu}$ is the average value of $\mu(\phi)$
+over $\mathcal{C}$ and $\mu'(\phi) \geq 0$ everywhere, then it is clear
+\begin{equation}
+    \Delta h = 2\epsilon \int\limits_0^{2\pi} 2\bar{\mu}\mu'(\phi)
+            \;\mathrm{d}\phi.
+\end{equation}
+Now, since $\mu'(\phi) \geq 0$ everywhere, and $\bar{\mu} \in [\mu_2, \mu_4] >
+0$ as well, $\Delta h > 0$ necessarily, and \emph{all full librations in zone II
+will be driven towards CS2} (the point of maximum $h$ and maximum $H^{(0)}$).
 
@@
 
-\subsection{Spindown Model}
+\subsection{Spindown Model}\label{ss:p2_spindown}
 
@@
 timescale $t_\eta$. Again rescaling time $\tau \equiv \alpha t$ and defining
-$\epsilon \equiv \frac{1}{\alpha t_\eta}$, we obtain $\eta' = \epsilon
-\eta$, where $\epsilon > 0$. Such a model is motivated e.g.\ when a planet's
+$\epsilon \equiv \frac{1}{\alpha t_\eta}$, we obtain
+\begin{equation}
+    \rd{\eta}{t} = \epsilon \eta,
+\end{equation}
+where $\epsilon > 0$. Such a model is motivated e.g.\ when a planet's
 spin $\hat{s}$ orbits a host star with angular momentum $\hat{l}$ while the star
@@
     \epsilon \eta$, where $\epsilon = 10^{-4}$. The top panel shows the
-    trajectory (red) and separatrix at separatrix crossing (dashed black) in
-    the labelled coordinates. The bottom panel shows the evolution of the
-    enclosed area by the trajectory (red dots), area of the separatrix (blue)
-    and $\eta$ (dotted green) over time.}\label{fig:2_1testo4}
+    trajectory (red) starting with initial condition $\mu_0 = 0.140, \phi_0 = 0$
+    (green dot) and separatrix at separatrix crossing (dashed black) in
+    the labelled coordinates. The end of the simulation is labelled in the blue
+    cyan dot. The bottom panel shows the evolution of the enclosed area by the
+    trajectory (red dots), area of the separatrix (blue) and $\eta$ (dotted
+    green) over time.}\label{fig:2_1testo4}
 \end{figure}
@@
 
-\subsection{Toy Model}
+\subsection{Nontrivial Test Problem}\label{ss:p2_toy}
 
@@
 $\mathcal{C}_{\pm}$ is the source of this guaranteed capture. To assess the
-accuracy of our formalism, we choose to further study $\eta' = \epsilon \eta
-\mu$. Straightforward evaluation of \autoref{eq:p2_delta} yields
+accuracy of our formalism, we propose instead test problem where $\eta$ is
+varied following
+\begin{equation}
+    \eta' = \epsilon \eta \mu.
+\end{equation}
+Straightforward evaluation of \autoref{eq:p2_delta} yields
 \begin{equation}
@@
 \begin{equation}
-    P_c = \frac{24\cos I \sqrt{\eta_\star \sin I}}{
+    P_c(\eta_\star) = \frac{24\cos I \sqrt{\eta_\star \sin I}}{
         2\pi \sin I + 12\sqrt{\eta_\star \sin I}\cos I
-            + 2\pi \eta_\star \cos^2 I}.
+            + 2\pi \eta_\star \cos^2 I}.\label{eq:p_c_p2}
 \end{equation}
-This is in good agreement
-% TODOYUBO plots
 
-\subsection{Non-conservation of Adiabatic Invariant}\label{ss:noncons}
+To test this capture probability, we adopt a slightly different testing
+methodology than in \autoref{s:p1}. For fixed initial condition $(\mu_0,
+\phi_0)$ in zone I, we vary the initial $\eta \in [0.01, 0.02]$ and $\epsilon
+\in 10^{[-3, -2]}$. In this way, every simulation experiences probabilistic
+separatrix crossing at roughly comparable times. We then repeated this procedure
+for three different values $I = 10^\circ, 20^\circ, 25^\circ$. A natural spread
+in $\eta_\star$ was observed at each $I$ value, which permitted comparison to
+\autoref{eq:p_c_p2} independently. The results for the three $I$ values are
+presented in \autoref{fig:2_1hist}, where good agreement with
+\autoref{eq:p_c_p2} is shown.
+\begin{figure}
+    \centering
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/1hist10.png}
+    \end{subfigure}
 
-Best evidence is $\eta_{\star}$ when changing $I$, blatantly wrong scaling
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/1hist20.png}
+    \end{subfigure}
+
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/1hist25.png}
+    \end{subfigure}
+    \caption{Simulations depicting $P_c(\eta_\star)$ at three different values
+    $I = 10^\circ, 20^\circ, 25^\circ$. The top panel represents the binned
+    outcomes as a function of $\eta_\star$, and the resulting estimates of $P_c$
+    are compared with the analytical curve (red) from \autoref{eq:p_c_p2} in the
+    bottom panel. Uncertainties in $P_c(\eta_\star)$ from data are estimated as
+    $\sqrt{N}$ where $N$ is the count per bin. Also reported is the average
+    value of $\eta_\star$.}\label{fig:2_1hist}
+\end{figure}
+
+\subsection{Conservation of Adiabatic Invariant}\label{ss:noncons}
+
+Under the theory of adiabatic invariants (see e.g.\ \cite{henrard1982,
+l_and_l}), trajectories following Hamiltonian equations of motion save for small
+$\eta'$ conserve action variable $I$ except at separatrix crossing, where
+\begin{equation}
+    I \equiv \frac{1}{2\pi}\oint p\;\mathrm{d}q.
+\end{equation}
+$I$ has physical interpretation the enclosed phase space area of trajectories.
+Its evolution can be seen in \autoref{fig:2_1testo4}. Under the assumption $I$
+is conserved except at separatrix crossing, $\eta_\star$ is fixed implicitly by
+$I = A_{sep}(\eta_\star)$ for $I$ the initial value of the action variable.
+Since $A_{sep}$ is given by \autoref{eq:a_sep}, it would appear $\eta_\star$ can
+be predicted exactly.
+
+\textbf{NOTE:} The rest of this section is not very complete.
+
+This turns out to be accurate in \autoref{ss:p2_spindown} but not in
+\autoref{ss:p2_toy}, so it's probably non-physical/has to do with $\eta' = 0$
+when $\mu = 0$. Not sure whether this is physically useful. Useful formulas for
+$\rd{I}{t}$ can be taken from~\cite{henrard1982, l_and_l}:
+\begin{equation}
+    \rd{I}{\tau} = \s{\pd{H}{\eta}T(\eta) - \int\limits_0^{T(\eta)}
+            \pd{H}{\eta}\;\mathrm{d}\tau} \eta'
+        = -\pd{}{w}\p{\pd{S}{\eta}}\eta'.
+\end{equation}
+Here, $T(\eta)$ is the period of the orbit, $w$ is the angle variable conjugate
+to $I$, and $S$ is the generating function for canonical transformation $\mu =
+\pd{S}{\phi}, w = \pd{S}{I}$. These expressions are hard to evaluate, but maybe
+they will tell us how much to expect $\rd{I}{\tau}$ to deviate from zero near
+the separatrix?
 
@@
 
-% TODOYUBO show that zone II stays in zone II?
+\subsection{Solution}
+
+We consider now the full Cassini State system with under weak tidal friction
+(see e.g.\ \cite{lai2012}). Note that generally $\abs{g}$ is a constant under
+weak tidal friction, as it is an orbit-orbit coupling term, while $\alpha
+\propto s$. Defining then $s_c$ critical spin such that $\frac{s}{s_c} \equiv
+\frac{\alpha}{\abs{g}}$\footnote{$s_c$ has interpretation \emph{critical spin}
+such that $\alpha, \abs{g}$ are equal.} and $\Omega_1$ the spin that $\hat{s}$
+is coupled to, we can write down fully coupled evolution equations for $(\mu,
+\phi, s)$:
+\begin{subequations}\label{se:p3_eom}
+    \begin{align}
+        \pd{\phi}{\tau} &= \frac{s}{s_c}\mu
+            - \p{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}} \cos \phi},\\
+        \pd{\mu}{\tau} &= -\sin I \sin \phi +
+            \epsilon \p{1 - \mu^2} \p{\frac{2\Omega_1}{s} - \mu},\\
+        \rd{s}{\tau}
+            &= \epsilon 2\Omega_1 \p{\mu - \frac{s}{2\Omega_1}\p{1 + \mu^2}}.
+    \end{align}
+\end{subequations}
+The expressions for $H^{(0)}, H_4$ can also be written down
+\begin{align}
+    H(\mu, \phi; s) &= -\frac{s}{s_c}\frac{\mu^2}{2}
+        + \mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi.\\
+    H_4(s) &= -\sin I + \frac{s_c}{2s}\cos^2 I.
+\end{align}
+
+Note that here $s$ takes the role of adiabatically-varying parameter. Thus, when
+computing $\Delta_{\pm}$ along the separatrix using \autoref{eq:delta}, there
+are two contributions. In particular, we write
+\begin{equation}
+    \Delta_{\pm} = \int_{\mathcal{C}_{\pm}} \dot{\mu}^{(1)} +
+        \frac{\dot{s}}{\dot{\phi}^{(0)}} \pd{h}{s}
+        \;\mathrm{d}\phi.
+\end{equation}
+Both of these integrals were performed in preceeding sections, and we may
+express in closed form (dropping some terms for simplicity)
+\begin{align}
+    \Delta_{\pm} \approx{}& \epsilon\z{
+            \mp \frac{4\pi  \Omega_1}{s} + 8\sqrt{\frac{s_c}{s}\sin I}
+            }\nonumber\\
+        &+\epsilon\z{\frac{ \Omega_1 s_c}{s^2}
+            \s{\pm 8\sqrt{\frac{s_c}{s} \sin I}
+            \p{\frac{s}{2\Omega_1} - \frac{s_c\cos I}{s}}
+                + 4\pi \frac{s_c}{s}\sin I}}.\label{eq:delta_p3}
+\end{align}
+We can then compute separatrix capture probability from zone III (which is $P_c
+= \frac{\Delta_+ + \Delta_-}{\Delta_-}$), again evaluating at $s = s_\star$:
+\begin{equation}
+    P_c(s_\star) = \frac{16\sqrt{\frac{s_c}{s_\star}\sin I} +
+        8\pi\frac{s_c}{s_\star}\sin I}{
+            \frac{4\pi \Omega_1}{s_\star} - \frac{8\Omega_1
+            s_c}{s_\star^2}\sqrt{\frac{s_c}{s_\star}\sin I}
+            \p{\frac{s_\star}{2\Omega_1} - \frac{s_c \cos I}{s_\star}}}.
+            \label{eq:p_c_p3}
+\end{equation}
+Note that for $\frac{s_c}{s_\star} < \eta_c$ that no separatrix (or resonance)
+exists anymore, so we will generally assume $s_\star \gtrsim s_c, \Omega_1$.
+
+To test \autoref{eq:p_c_p3}, we generate an evenly spaced grid of initial
+conditions $(\mu_0, \phi_0)$ and initialize $s_0 = 10$. We then record $s_\star$
+and the final ooutcome of the trajectory over many simulations. The agreement of
+\autoref{eq:p_c_p3} with data can be observed in \autoref{fig:1_4stats}.
+\begin{figure}
+    \centering
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/1_weaktide/4_cross_hist0_05.png}
+    \end{subfigure}
+
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/1_weaktide/4_cross_hist0_20.png}
+    \end{subfigure}
+
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/1_weaktide/4_cross_hist0_40.png}
+    \end{subfigure}
+
+    \caption{Histogram of simulation and inferred $P_c(s_\star)$ compared with
+    \autoref{eq:p_c_p3}. $s_c$ used are numbered at the top of each plot. $10^4$
+    simulations were used for each plot, and a single $I = 20^\circ$ was
+    used.}\label{fig:1_4stats}
+\end{figure}
+
+\subsection{Estimating $s_\star$}
+
+In \autoref{s:p2}, the capture probability $P_c(\eta_\star)$ depended on
+$\eta_\star$ which could be determined by conservation of the action varible
+$I$. Such an argument is not possible in the weak tidal prescription as the
+system is dissipitive thanks to $\dot{\mu}^{(1)}$ (see \autoref{se:p3_eom}).
+
+However, instead we can write down $\rd{h}{\tau}$, just as \autoref{eq:dhdt}.
+Since the initial value of $h$ can be computed from initial conditions, the ODE
+can simply be integrated numerically to find $\tau_\star$ the separatrix
+crossing time. In fact, for $\mu$ far from the separatrix, $\rd{h}{\tau} \approx
+\frac{3s\mu^2}{2s_c}$, predicting
+\begin{equation}
+    \tau_\star = \frac{h(t = 0)}{3s\mu^2/2s_c} + C,
+\end{equation}
+where $C$ depends on the detairs of $\rd{h}{\tau}$ near the separatrix. This is
+in good agreement with measurement (see top panel of \autoref{fig:1_4cross}).
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/4_cross0_20.png}
+    \caption{TODO make this plot actually look reasonable. The top and bottom
+    panels show $t_\star, s_\star$ as a function of $-h = H_4 - H$. The dotted
+    red line in the top panel is $t_\star = \frac{h}{3s\mu^2/2s_c} + C$ where
+    $C$ is a fitting parameter determined by the behavior of $\rd{h}{\tau}$ near
+    the separatrix.}\label{fig:1_4cross}
+\end{figure}
+
+\subsection{High Misalignment as an Attractor}
+
+Careful examination of \autoref{eq:delta_p3} reveals that for sufficiently large
+$s_c$, $\Delta_+$ changes sign and becomes positive. When $\Delta_+ < 0$,
+trajectories in zone I above the separatrix cannot enter the separatrix, as $h$
+decreases over an orbit. However, if $\Delta_+ > 0$, then trajectories in zone I
+can also enter the separatrix. The critical value of $s_c$ where $\Delta_+$
+changes sign as a function of $s$ can thus be determined analytically. TODO
+write down the formula and check it against my numerical solution earlier.
+
+Furthermore, $\rd{\mu}{\tau} < 0$ for $\mu > \frac{2\Omega_1}{s}$, it is clear
+that if $s$ is initially large, then aligned states $\mu > 0$ are driven towards
+misalignment and the separatrix, where they may then be captured for
+sufficiently large $s_c$. We find that $s_c \gtrsim 0.5 \Omega_1$ is sufficient
+that an initial spin of $s_0 = 10$ will \emph{always} be captured into CS2. TODO
+could shore this up a bit, find a good way to plot.
+
+TODO find a clean plot to demonstrate this, I have the data already.
 

### 2019-06-26 initial/2_toy2/1sim.py

@@ -40,7 +40,6 @@ def plot_traj(I, ret, filename):
 
     # plot separatrix @ cross
     t_areas, areas, t_cross, ends_circ = get_areas(ret)
-    # print('Initial area', areas[0])
     circ_idxs = np.where(t <= t_cross)[0]
     post_idxs = np.where(t > t_cross)[0]
     cross_idx = circ_idxs[-1]
@@ -82,6 +81,7 @@ def plot_traj(I, ret, filename):
         + 8 * np.sqrt(eta[circ_idxs] * np.sin(I))
     ln2 = ax2.plot(t[circ_idxs], circ_area / (4 * np.pi),
                    'b', linewidth=lw, label=r'$A_{sep}$')
+    print('Initial area, cross area', areas[0], circ_area[-1])
     # account for post_idxs depending on ends_circ (whether ends circulating)
     if ends_circ:
         mu4_post = get_mu4(I, eta[post_idxs])
@@ -106,7 +106,7 @@ def plot_traj(I, ret, filename):
     q_f, phi_f = to_ang(y[0][-1], y[1][-1], y[2][-1])
     eta_f = y[3, -1]
     dH_f = H(I, eta_f, q_f, phi_f) - H(I, eta_f, q4, 0)
-    ax1.set_title(r'$\mu_0 = %.3f$ (%s)' %
+    ax1.set_title(r'$(\mu_0, \phi_0) = (%.3f, 0)$ (%s)' %
                   (y[2][0], 'Capture' if dH_f > 0 else 'Escape'))
     fig.tight_layout()
     fig.savefig(filename, dpi=400)
@@ -181,7 +181,8 @@ def run_stats(I_deg):
             else:
                 escapes.append(etaf)
 
-    fig, (ax1, ax2) = plt.subplots(2, 1, sharex=True)
+    # swap order HACK
+    fig, (ax2, ax1) = plt.subplots(2, 1, sharex=True)
     fig.subplots_adjust(hspace=0)
     n, bins, _ = ax2.hist([captures, escapes],
                            bins=40,
@@ -200,10 +201,11 @@ def run_stats(I_deg):
         4 * np.pi * np.sin(I)
             + 24 * np.cos(I) * np.sqrt(eta * np.sin(I))
             + 4 * np.pi * eta * np.cos(I)**2)
[…]

### 2019-07-18 initial/notes.tex
toy problem 3 seems to have plausible agreement

@@
         &= \epsilon \p*{-s_z s_x\hat{x} - s_zs_y\hat{y} + \p*{1 - s_z^2}
-            \hat{z}}.
+            \hat{z}}.\label{eq:p1_eom}
 \end{align}
@@
 
+\subsection{Using $\alpha = 1/\eta$}
+
 Though this section is located before the weak tidal friction section, we
@@
 predictions, and to get some practice doing these new integrals. Consider the
-dissipation-free Cassini state system with a small but constant $\pd{\eta}{t} =
-\epsilon$. For clarity, the Hamiltonian is
+dissipation-free Cassini state system with a small but constant
+\begin{equation}
+    \pd{\eta}{t} = \epsilon.\label{eq:p2_eom}
+\end{equation}
+For clarity, the Hamiltonian is
 \begin{equation}
@@
 made in writing down $B_i$ washed out the extra $\eta$ dependence.
+
+For reference, let's also write down the $B_i$ in the $\dot{\eta} = \epsilon
+\eta$ case. First, $B_{+}$:
+\begin{align*}
+    B_{top} &= \int\limits_{2\pi}^0 -\epsilon \eta \cos I\;\mathrm{d}\phi
+            + \frac{\epsilon}{2}\int\limits_{2\pi}^0
+                \sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
+        &= 2\pi \epsilon \eta \cos I - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
+\end{align*}
+Along the bottom leg, the first term changes signs (both integrals have their
+paths flipped, but the sign of the second integral also changes), and so
+\begin{equation}
+    B_{\pm} = \pm 2\pi \epsilon \eta \cos I
+        - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
+\end{equation}
+Generally, since $\eta$ is small, $B_{+} + B_- < -\abs*{B_+}, -\abs*{B_-}$ which
+implies guaranteed capture from both sides, as expected (note that in our actual
+paper, we compute changes for $h \equiv H^{(0)} - H_4$, while here we compute
+changes in $H_4 - H^{(0)}$, accounting for the change in sign).
+
+\subsection{Toy Problem 3: Including Toy Tides}
+
+Consider now the extended toy problem where we both include the tidal term
+\autoref{eq:p1_eom} and adiabatic parameter variation \autoref{eq:p2_eom}. In
+the interest of generality, we replace
+\begin{equation}
+    \rd{\eta}{\tau} = f \epsilon \eta,
+\end{equation}
+such that the two $\epsilon$-fast terms have a tunable relative strength
+$f \sim 1$.
+
+We can now compute the $\Delta_{\pm}$ changes in $h \equiv H^{(0)} - H_4$
+(following my paper's convention, rather than those earlier in these notes),
+which are:
+\begin{equation}
+    \Delta_{\pm} = \epsilon\s*{\mp 2\pi \p{1 - 2\eta \sin I - \eta^2 \cos^2 I} +
+        16\cos I\eta^{3/2}\sqrt{\sin I}} + f\epsilon
+            \s*{\mp 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
+\end{equation}
+The two contributions are bracketed.
 

### 2019-07-18 initial/3_toy3/1sim.py

@@ -1,0 +1,120 @@
+import os
+import scipy.optimize as opt
+import numpy as np
+import multiprocessing as mp
+
+import matplotlib
+import pickle
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif', size=12)
+
+PLOT_DIR = '1plots'
+from utils import to_cart, to_ang, solve_ic, get_areas, get_plot_coords,\
+    roots, H, get_mu4
+
+EPS = 3e-4
+
+def my_fmt(I_deg, delta):
+    return '%d_%s' % (I_deg, ('%.2f' % delta).replace('.', '_'))
+
+def run_single(I, tf, eta0, q0, delta):
+    q4 = roots(I, eta0)[3]
+
+    y0 = [*to_cart(q0, 0.2), eta0]
+    return solve_ic(I, EPS, delta, y0, tf)
+
+def stats_runner(I, q0, delta):
+    tf = 3000
+    n_eta = 151
+
+    def result_single(tf, eta0):
+        ret = run_single(I, tf, eta0, q0, delta)
+
+        q_f, phi_f = to_ang(ret.y[0][-1], ret.y[1][-1], ret.y[2][-1])
+        eta_f = ret.y[3, -1]
+        q4 = roots(I, eta_f)[3]
+        dH_f = H(I, eta_f, q_f, phi_f) - H(I, eta_f, q4, 0)
+
+        _, _, t_cross, _ = get_areas(ret)
+        crossed_idxs = np.where(ret.t > t_cross)[0]
+        if len(crossed_idxs) == 0:
+            return dH_f > 0, -1
+        return dH_f > 0, ret.y[3, crossed_idxs[0]], ret.y[2, -1]
+
+    counts = 0
+    res = []
+    for eta0 in np.linspace(0.1, 0.2, n_eta):
+        capture, eta_f, z_f = result_single(tf, eta0)
+        print('\t', '%.3f' % q0, 'Finished', '%.3f' % (eta_f - eta0), capture,
+              '%.3f' % z_f)
+        res.append((eta_f, capture))
+        if capture:
+                counts += 1
+    return res
+
+def run_stats(I_deg, delta, p=None):
+    I = np.radians(I_deg)
+    n_q = 151
+
+    PKL_FN = '1dat%s.pkl' % my_fmt(I_deg, delta)
[…]

### 2019-07-18 initial/3_toy3/utils.py

@@ -1,0 +1,182 @@
+'''
+utils functions for toy problem 2
+
+since we're only concerned w/ separatrix hopping cases, we will ignore ICs
+inside the separatrix or that start too close to CS1/CS3
+'''
+import numpy as np
+import scipy.optimize as opt
+from scipy.integrate import solve_ivp
+
+########
+# COPIED
+########
+
+def to_cart(q, phi):
+    return [
+        np.sin(q) * np.cos(phi),
+        np.sin(q) * np.sin(phi),
+        np.cos(q),
+    ]
+
+def to_ang(x, y, z):
+    r = np.sqrt(x**2 + y**2 + z**2)
+    q = np.arccos(z / r)
+    phi = (np.arctan2(y / np.sin(q), x / np.sin(q)) + np.pi)\
+        % (2 * np.pi)
+    return q, phi
+
+def get_etac(I):
+    return (np.sin(I)**(2/3) + np.cos(I)**(2/3))**(-3/2)
+
+def roots(I, eta):
+    '''
+    returns theta roots from EOM, not phi (otherwise same as 0_eta func)
+    '''
+    eta_c = get_etac(I)
+
+    # function to minimize and derivatives
+    f = lambda q: -eta * np.sin(q - I) + np.sin(q) * np.cos(q)
+    fp = lambda q: -eta * np.cos(q - I) + np.cos(2 * q)
+
+    if eta < eta_c:
+        roots = []
+        inits = [0, np.pi / 2, -np.pi, -np.pi / 2]
+        for qi in inits:
+            roots.append(opt.newton(f, qi, fprime=fp))
+        return np.array(roots)
+
+    else:
+        roots = []
+        inits = [np.pi / 2 - I, -np.pi + I]
+        for qi in inits:
+            roots.append(opt.newton(f, qi, fprime=fp))
+        return np.array(roots)
+
+def H(I, eta, q, phi):
+    mu = np.cos(q)
+    return -0.5 * mu**2 + eta * (
+        mu * np.cos(I) -
+        np.sqrt(1 - mu**2) * np.sin(I) * np.cos(phi))
+
+def get_mu4(I, eta):
+    '''
+    gets mu4 for a list of spins s, returning -1 if no CS4 for given s
+    '''
+    eta_c = get_etac(I)
+    mu4 = np.full(np.shape(eta), -1.0)
+
+    valid_idxs = np.where(eta < eta_c)
+
[…]

### 2019-07-23 initial/notes.tex
stash

@@
 The two contributions are bracketed.
+
+Now, this turns out to be slightly inaccurate for $f > 0$, probably because
+$\mathcal{C}_{\pm}$ is a function of $\eta$ and changes over the course of
+orbit. The two possible solutions are: compute $\eta_\star$ averaged over the
+trajectory (for numerical purposes) or to compute the analytical correction for
+a given $\eta$. The latter seems hard, so we'll go with the former.
 

### 2019-07-23 initial/3_toy3/1sim.py

@@ -27,7 +27,7 @@ def run_single(I, tf, eta0, q0, delta):
 
 def stats_runner(I, q0, delta):
     tf = 3000
-    n_eta = 151
+    n_eta = 201
 
     def result_single(tf, eta0):
         ret = run_single(I, tf, eta0, q0, delta)
@@ -40,12 +40,13 @@ def stats_runner(I, q0, delta):
         _, _, t_cross, _ = get_areas(ret)
         crossed_idxs = np.where(ret.t > t_cross)[0]
         if len(crossed_idxs) == 0:
-            return dH_f > 0, -1
-        return dH_f > 0, ret.y[3, crossed_idxs[0]], ret.y[2, -1]
+            return dH_f > 0, eta0, -1
+        eta_cross = ret.sol(t_cross)[3]
+        return dH_f > 0, eta_cross, ret.y[2, -1]
 
     counts = 0
     res = []
-    for eta0 in np.linspace(0.1, 0.2, n_eta):
+    for eta0 in np.linspace(0.05, 0.2, n_eta):
         capture, eta_f, z_f = result_single(tf, eta0)
         print('\t', '%.3f' % q0, 'Finished', '%.3f' % (eta_f - eta0), capture,
               '%.3f' % z_f)
@@ -74,11 +75,11 @@ def run_stats(I_deg, delta, p=None):
 
     captures, escapes = [], []
     for res in res_arr:
-        for etaf, capture in res:
+        for eta_cross, capture in res:
             if capture:
-                captures.append(etaf)
+                captures.append(eta_cross)
             else:
-                escapes.append(etaf)
+                escapes.append(eta_cross)
 
     fig, (ax1, ax2) = plt.subplots(2, 1, sharex=True)
     fig.subplots_adjust(hspace=0)

### 2019-08-07 initial/notes.tex
temp checkpoint

--- 2019-07-18 initial/notes.tex
@@
 The two contributions are bracketed.
+
+Now, this turns out to be slightly inaccurate for $f > 0$ simply because our
+$\mu_{sep}$ approximation is not so accurate for $\eta \gtrsim 0.2$, where the
+top leg is significantly lower than the symmetric $\mu_{sep} = \eta \cos I \pm
+\dots$ would predict. This would mean the two legs don't cancel as exactly, and
+the capture probability increases, which is observed.
 

### 2019-08-07 writeups/Su_sep_cross.tex
temp checkpoint

--- 2019-06-26 writeups/paper.tex
@@
 \begin{equation}
-    \eta \equiv \frac{\abs*{g}}{\alpha} \label{eq:eta}
+    \eta \equiv \frac{\abs{g}}{\alpha} \label{eq:eta}
 \end{equation}
@@
 \citep{henrard1987}, but a serviceable approximation for small $\eta$ can be
-derived as follows. Call $H_4$ the value of $H$ at CS4, then the separatrix is
-defined implicitly by solutions to $H\p{\mu_{sep}(\phi), \phi} = H_4$. This may
-be evaluated and we obtain
+derived as follows. Call $H_{sep}$ the value of $H$ along the separatrix (also
+the value of $H$ at CS4), then the separatrix is defined implicitly by solutions
+to $H\p{\mu_{sep}(\phi), \phi} = H_{sep}$. This may be evaluated and we obtain
 \begin{equation}
@@
 \begin{equation}
-    h(\mu, \phi; \eta) \equiv H^{(0)}(\mu, \phi; \eta) - H_4(\eta).
+    h(\mu, \phi; \eta) \equiv H^{(0)}(\mu, \phi; \eta) - H_{sep}(\eta).
 \end{equation}
@@
 that $h$ corresponds to $K$ in~\cite{henrard1982}, though in our problem
-$H^{(0)} > H_4$ corresponds to the \emph{interior} of the separatrix. The
+$H^{(0)} > H_{sep}$ corresponds to the \emph{interior} of the separatrix. The
 evolution of $h$ over time then determines whether and when a trajectory
@@
 \begin{align}
-    \rd{h}{t} &= \rd{H^{(0)}}{t} - \pd{H_4}{\eta}\dot{\eta},\nonumber\\
+    \rd{h}{t} &= \rd{H^{(0)}}{t} - \pd{H_{sep}}{\eta}\dot{\eta},\nonumber\\
         &= \s{\pd{H^{(0)}}{\mu}\dot{\mu}
@@
                 + \pd{H^{(0)}}{\eta}\dot{\eta}}
-            - \pd{H_4}{\eta}\dot{\eta},\nonumber\\
+            - \pd{H_{sep}}{\eta}\dot{\eta},\nonumber\\
         &= \s{\pd{H^{(0)}}{\mu}\dot{\mu}
@@
                 + \pd{H^{(0)}}{\eta}\dot{\eta}}
-            - \pd{H_4}{\eta}\dot{\eta},\nonumber\\
+            - \pd{H_{sep}}{\eta}\dot{\eta},\nonumber\\
         &= \s{\dot{\phi}^{(0)}\dot{\mu}^{(1)}
@@
                 + \pd{H^{(0)}}{\eta}\dot{\eta}} -
-            \pd{H_4}{\eta}\dot{\eta}.\label{eq:dhdt}
+            \pd{H_{sep}}{\eta}\dot{\eta}.\label{eq:dhdt}
 \end{align}
@@
 \end{figure}
+
+\subsection{Zone I/III Initial Conditions}\label{ss:z_out_ic}
+
 For concreteness, we consider a specific example first. We assign labels to our
@@
 With the exception of \autoref{eq:dhdt}, the above outlines the argument given
-in~\cite{henrard1982}.
+in~\cite{henrard1982}. Similar conclusions can be drawn for trajectories
+originating in zone I.
 
-Similar derivations can be given for trajectories originating in zone I.
-TODO say something about zone-II originating systems.
+\subsection{Zone II Initial Conditions}\label{ss:z2_ic}
+
+The fates of trajectories originating in zone II, which librate about the
+CS2, also depend on $\Delta_{\pm}$. This implies $h_i > 0$. We identify the
+following possibilities:
+\begin{itemize}
+    \item $\Delta_{+} + \Delta_- > 0$: trajectories near the separatrix are
+        driven back into zone II over the course of a full libration, therefore
+        any trajectory originating in zone II is bound to zone II\@. Note that
+        this alone need not imply convergence to CS2, e.g.\ for a
+        non-dissipative system.
+
+    \item $\Delta_+ + \Delta_- < 0, \Delta_+ > 0, \Delta_- < 0$: trajectories
+        near the separatrix are driven back into zone II along $\mathcal{C}_+$
+        but out of zone II along $\mathcal{C}_-$, the net effect amounting to
+        expulsion. Since expulsion cannot occur along $\mathcal{C}_+$, the only
+        permitted transition is II $\to$ III\@. Vice versa of course if the signs
+        of $\Delta_{\pm}$ are swapped while still satisfying $\Delta_+ +
+        \Delta_- < 0$.
+
+    \item $\Delta_\pm < 0$: trajectories near the separatrix tend to be
+        ejected along both $\mathcal{C}_{\pm}$. Which zone the trajectory enters
+        is then probabilistic: it enters zone I with probability
+        $\frac{\Delta_+}{\Delta_+ + \Delta_-}$ and zone III with probability
+        $\frac{\Delta_-}{\Delta_+ + \Delta_-}$.
+
+        It bears noting that in the non-dissipative limit, this result is
+        equivalent to \citep{henrard1987}, which computes these probabilities
+        using change in enclosed phase space area.
+\end{itemize}
 
@@
 Visually, this is depicted in \autoref{fig:0_6manifolds}. Note that:
-trajectories starting in zone III below $W_s^{(1)}$ fail to separatrix cross;
-those between $W_s^{(1)}$ and $W_s^{(0)}$ continue between $W_u^{(1)}$ and
-$W_s^{(0)}$, eventually escaping; those between $W_s^{(0)}$ and $W_u^{(0)}$ are
-securely captured, and no trajectories can begin above $W_u^{(0)}$ at $\phi =
-0$.
+trajectories starting in zone III below $W_s^{R}$ fail to separatrix cross;
+those between $W_s^{R}$ and $W_s^{L}$ continue between $W_u^{R}$ and $W_s^{L}$,
+eventually escaping; those between $W_s^{L}$ and $W_u^{L}$ are securely
+captured, and no trajectories can begin above $W_u^{L}$ at $\phi = 0$.
 
@@
 just $\Delta \mu \pd{H^{(0)}}{\mu} = \Delta H^{(0)}$. Then the capture
-probability must be given by ratio of $\Delta \mu$ separating $W_s^{(0)},
-W_u^{(0)}$ to $\Delta \mu$ separating $W_s^{(1)}, W_u^{(0)}$. These $\Delta \mu$
+probability must be given by ratio of $\Delta \mu$ separating $W_s^{L},
+W_u^{L}$ to $\Delta \mu$ separating $W_s^{R}, W_u^{L}$. These $\Delta \mu$
 values are those given in the title, and the resultant $P_c$ capture probability
@@
     \caption{Sample plot of saddle connection breaking in the presence of weakly
-    non-Hamiltonian dissipation. Equations are used from \autoref{s:p1}. Stable
-    and unstable manifolds are indexed such that superscript $(0)$/$(1)$
-    belongs to the saddle point at left/right. $\Delta \mu$ represent the
-    manifold separations, resulting in capture probability $P_c$
-    prediction per \autoref{eq:p_c_dmu}. Numerical simulations predict $P_c
-    \approx 0.252$.}\label{fig:0_6manifolds}
+    non-Hamiltonian dissipation. Equations are used from \autoref{s:p2}. Stable
+    and unstable manifolds are indexed such that superscript $L/R$ belongs to
+    the saddle point at left/right. $\Delta \mu$ represent the manifold
+    separations, resulting in capture probability $P_c$ prediction per
+    \autoref{eq:p_c_dmu}. Numerical simulations predict $P_c \approx
+    0.252$.}\label{fig:0_6manifolds}
 \end{figure}
@@
 \begin{align}
-    P_c &= \frac{\Delta \mu(W_s^{(0)}, W_u^{(0)})}{
-            \Delta \mu\p{W_s^{(1)}, W_u^{(0)}}},\label{eq:p_c_dmu},\\
+    P_c &= \frac{\Delta \mu(W_s^{L}, W_u^{L})}{
+            \Delta \mu\p{W_s^{R}, W_u^{L}}},\label{eq:p_c_dmu},\\
         &= \frac{\Delta H^{(0)}_- + \Delta H^{(0)}_+}{\Delta H^{(0)}_-}.
@@
 
-\section{Problem 1: Weakly Dissipitive Hamiltonian}\label{s:p1}
+\section{Problem 1: Adiabatic Capture}\label{s:p1}
 
-We first consider a toy separatrix crossing problem in the $\dot{\eta} = 0$
+Here we will adiabatically vary $\eta$. This problem is extensively covered in
+existing work e.g.\ \citep{henrard1987}.
+
+\subsection{Spindown Model, $\dot{\eta} > 0$ (few sims)}\label{ss:p1_spindown}
+
+We may first consider the unperturbed Hamiltonian
+system with $\rd{\eta}{t} = \frac{\eta}{t_\eta}$ growth with characteristic
+timescale $t_\eta$. Again rescaling time $\tau \equiv \alpha t$ and defining
+$\epsilon \equiv \frac{1}{\alpha t_\eta}$, we obtain
+\begin{equation}
+    \rd{\eta}{\tau} = \epsilon \eta,\label{eq:p1_eom}
+\end{equation}
+where $\epsilon > 0$. Such a model is motivated e.g.\ when a planet's
+spin $\hat{s}$ orbits a host star with angular momentum $\hat{l}$ while the star
+spins down; $\dot{\alpha} < 0$ here, and $\eta' > 0$.
+
+We then seek $\Delta_{\pm}$, determined by
+\begin{align}
+    \Delta_{\pm} &= \int\limits_{\mathcal{C}_{\pm}}
+            \pd{h}{\eta}\eta'\;\mathrm{d}\tau,\nonumber\\
+        &= \int\limits_{\mathcal{C}_{\pm}}
+            \frac{\pd{h}{\eta}}{\phi'}\eta'\;\mathrm{d}\phi.
+\end{align}
+We must proceed carefully since $\phi' \to 0$ at the endpoints of
+$\mathcal{C}_{\pm}$; careful work shows these zeros cancel against zeros of
+$\pd{h}{\eta}$, and
+\begin{align}
+    \Delta_{\pm} &= \int\limits_{\mathcal{C}_{\pm}} \eta'
+        \p{\cos I \mp \sin I \sqrt{\frac{1 - \cos \phi}{2\eta\sin I}}}
+            \;\mathrm{d}\phi,\label{eq:p1_delta_eq}\\
+        &= \mp 2\pi \epsilon \eta \cos I
+            + 4\epsilon\sqrt{\eta \sin I}.\label{eq:p1_delta}
+\end{align}
+Call $\eta_\star$ the value of $\eta$ at which a trajectory encounters the
+separatrix. There are then three possibilities:
+\begin{itemize}
+    \item For $\eta_\star < \frac{4\sin I}{\pi^2 \cos^2 I}$, we obtain
+        $\Delta_{\pm} > 0$. In this regime, all separatrix encounters
+        originating in zones I/III result in secure capture (see
+        \autoref{ss:z_out_ic}), while all trajectories originating in zone II do
+        not experience separatrix encounter. For $I = 20^\circ$, this condition
+        equates to $\eta_\star \lesssim 0.16$. This condition is not to be taken
+        too exactly, as all our calculations are performed in the small $\eta$
+        limit. Select simulations in $\eta_\star \lesssim 0.1$ are in agreement
+        with the secure capture prediction. An example of such a simulation is
+        presented in \autoref{fig:2_1testo4}.
+        \begin{figure}[t]
+            \centering
+            \includegraphics[width=\columnwidth]{../initial/2_toy2/1testo4.png}
+            \caption{Simulation with initial condition in zone I subject to
+            $\eta' = \epsilon \eta$, where $\epsilon = 10^{-4}$. The top panel
+            shows the trajectory (red) starting with initial condition $\mu_0 =
+            0.140, \phi_0 = 0$ (green dot) and separatrix at separatrix crossing
+            (dashed black) in the labelled coordinates. The end of the
+            simulation is labelled in the blue cyan dot. The bottom panel shows
+            the evolution of the enclosed area by the trajectory (red dots),
+            area of the separatrix (blue) and $\eta$ (dotted green) over
+            time.}\label{fig:2_1testo4}
+        \end{figure}
+
+    \item If $\eta_\star > \frac{4\sin I}{\pi^2 \cos^2 I}, \eta_\star < \eta_c$,
+        then the separatrix still exists, and $\Delta_+ < 0, \Delta_- > 0$,
+        $\Delta_+ + \Delta_- > 0$. This implies: zone I + zone II trajectories
+        do not experience separatrix encounters, while zone III trajectories are
+        captured into zone II with probability
+        \begin{equation}
+            P_c = \frac{8\sqrt{\eta_\star \sin I}}{2\pi \eta_\star \cos I +
+                4\sqrt{\eta_\star \sin I}}.
+        \end{equation}
+
+    \item Further evolution from either of the above two cases, as well as the
+        case where no separatrix encounter occurs before $\eta > \eta_c$, is
+        governed simply by conservation of adiabatic invariant/action variable
+        \begin{equation}
+            I \equiv \oint \cos \theta \;\mathrm{d}\phi.
+        \end{equation}
+\end{itemize}
+
+\subsection{Spinup Model, $\dot{\eta} < 0$ (no sims)}\label{ss:p1_spinup}
+
+If instead $\epsilon < 0$, then the separatrix area shrinks over time. For
+initial values $\eta > \eta_c$, the separatrix appears over time and the
+scenario is analyzed in \citep{anderson2018teeter}.
+
+If $\eta$ decreases past critical value $\frac{4\sin I}{\pi^2 \cos^2 I}$, i.e.\
+$\Delta_{\pm} < 0$, then the separatrix appears. Here, trajectories in zones
+I/III do not experience separatrix encounter while trajectories in zone II
+transition into zones I/III with probabilities given respectively (see
+\autoref{ss:z2_ic}):
+\begin{equation}
+    \begin{split}
+        P_{II \to I} &= \frac{2\pi \eta_\star \cos I + 4\sqrt{\eta_\star \sin I}}
+            {8\sqrt{\eta_\star \sin I}}, \\
+        P_{II \to III} &= \frac{-2\pi \eta_\star \cos I + 4\sqrt{\eta_\star \sin
+            I}} {8\sqrt{\eta_\star \sin I}}.
+    \end{split}
+\end{equation}
+
+\subsection{Nontrivial Test Problem, ``Problem 1.5'' (sims)}\label{ss:p1_toy}
+
+It is clear that $\eta'$ in \autoref{eq:p1_delta_eq} being the same sign along
+both $\mathcal{C}_{\pm}$ is the source of guaranteed capture during
+spindown. In order to test that \autoref{eq:p_c_gen} is not only qualitatively
+correct but also quantitatively exact, we seek to simulate a problem with
+probabilistic behavior. \textbf{Note: This section is probably superceded by
+\autoref{ss:p1_spinup} or \autoref{s:p3}.}. We investigate test problem where
+$\eta$ is varied following
+\begin{equation}
+    \eta' = \epsilon \eta \mu.
+\end{equation}
+This is a pure mathematical exercise, but resembles weak tidal friction in the
+subsynchronous rotation regime.
+
+Straightforward evaluation of \autoref{eq:p1_delta_eq} yields
+\begin{equation}
+    \Delta_{\pm} = \pm \epsilon \eta_\star \s{
+        2\pi \sin I \pm 12 \sqrt{\eta_\star \sin I}\cos I
+            + 2\pi \eta_\star \cos^2 I}.
+\end{equation}
+It bears noting that we must evaluate these integrals at $\eta = \eta_\star$ the
+value at separatrix crossing. Since $\eta$ evolves over time, $\eta_{\star}$
+depends on initial conditions. While one might expect the adiabatic invariance
+of the action variable determines $\eta_\star$, this turns out to be slightly
+inaccurate for reasons (I haven't worked this out convincingly yet).
+% not be the case; we address this in \autoref{ss:noncons}.
+
+Since $\abs{\Delta_+} > \abs{\Delta_-}$, separatrix encounters originating in
+zone III always result in capture. However, encounters originating in zone I
+experience capture probability
+\begin{equation}
+    P_c(\eta_\star) = \frac{24\cos I \sqrt{\eta_\star \sin I}}{
+        2\pi \sin I + 12\sqrt{\eta_\star \sin I}\cos I
+            + 2\pi \eta_\star \cos^2 I}.\label{eq:p_c_p1}
+\end{equation}
+
+To test this capture probability, we test capture probability at a variety of
+$I$ for similar ICs. For fixed initial condition $(\mu_0, \phi_0)$ in zone I, we
+vary the initial $\eta \in [0.01, 0.02]$ and $\epsilon \in 10^{[-3, -2]}$. In
+this way, every simulation experiences probabilistic separatrix crossing at
+roughly comparable times. We then repeated this procedure for three different
+values $I = 10^\circ, 20^\circ, 25^\circ$. A natural spread in $\eta_\star$ was
+observed at each $I$ value, which permitted comparison to \autoref{eq:p_c_p1}
+independently. The results for the three $I$ values are presented in
+\autoref{fig:2_1hist}, where good agreement with
+\autoref{eq:p_c_p1} is shown.
+\begin{figure}
+    \centering
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/1hist10.png}
+    \end{subfigure}
+
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/1hist20.png}
+    \end{subfigure}
+
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/1hist25.png}
+    \end{subfigure}
+    \caption{Simulations depicting $P_c(\eta_\star)$ at three different values
+    $I = 10^\circ, 20^\circ, 25^\circ$ compared to analytical estimate
+    \autoref{eq:p_c_p1}. The top panel is a stacked histogram showing the
+    capture (into separatrix) and escape occurence counts at each $\eta_\star$.
+    The bottom panel are the inferred estimates of $P_c(\eta_{\star})$ (capture
+    probability) in blue and analytical curve in red. Uncertainties in
+    $P_c(\eta_\star)$ from data are estimated as $\sqrt{N}$ where $N$ is the
+    number of captures per bin. Also reported is the average value of
+    $\eta_\star$.}\label{fig:2_1hist}
+\end{figure}
+
+% \subsection{Conservation of Adiabatic Invariant}\label{ss:noncons}
+
+% Under the theory of adiabatic invariants (see e.g.\ \cite{henrard1982,
+% l_and_l}), trajectories following Hamiltonian equations of motion save for small
+% $\eta'$ conserve action variable $I$ except at separatrix crossing, where
+% \begin{equation}
+%     I \equiv \frac{1}{2\pi}\oint p\;\mathrm{d}q.
+% \end{equation}
+% $I$ has physical interpretation the enclosed phase space area of trajectories.
+% Its evolution can be seen in \autoref{fig:2_1testo4}. Under the assumption $I$
+% is conserved except at separatrix crossing, $\eta_\star$ is fixed implicitly by
+% $I = A_{sep}(\eta_\star)$ for $I$ the initial value of the action variable.
+% Since $A_{sep}$ is given by \autoref{eq:a_sep}, it would appear $\eta_\star$ can
+% be predicted exactly.
+
+% \textbf{NOTE:} The rest of this section is not very complete.
+
+% This turns out to be accurate in \autoref{ss:p1_spindown} but not in
+% \autoref{ss:p1_toy}, so it's probably non-physical/has to do with $\eta' = 0$
+% when $\mu = 0$. Not sure whether this is physically useful. Useful formulas for
+% $\rd{I}{t}$ can be taken from~\cite{henrard1982, l_and_l}:
+% \begin{equation}
+%     \rd{I}{\tau} = \s{\pd{H}{\eta}T(\eta) - \int\limits_0^{T(\eta)}
+%             \pd{H}{\eta}\;\mathrm{d}\tau} \eta'
+%         = -\pd{}{w}\p{\pd{S}{\eta}}\eta'.
+% \end{equation}
+% Here, $T(\eta)$ is the period of the orbit, $w$ is the angle variable conjugate
+% to $I$, and $S$ is the generating function for canonical transformation $\mu =
+% \pd{S}{\phi}, w = \pd{S}{I}$. These expressions are hard to evaluate, but maybe
+% they will tell us how much to expect $\rd{I}{\tau}$ to deviate from zero near
+% the separatrix?
+
+\section{Problem 2: Weakly Dissipitive Hamiltonian}\label{s:p2}
+
+\subsection{$\eta < \eta_c$, Separatrix Encounters (sims)}\label{ss:p2_lt}
+
+We next consider a toy separatrix crossing problem in the $\dot{\eta} = 0$
 limit, the case discussed in \autoref{ss:meln}. Consider adding to the
@@
 canonical variables $\mu \equiv \cos\theta, \phi$ are
-\begin{subequations}\label{se:p1_eom}
+\begin{subequations}\label{se:p2_eom}
     \begin{align}
-        \mu' &= -\cos\theta
+        \phi' &= -\cos\theta
             + \eta\p{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}} \cos \phi},\\
@@
 Primes denote $\rd{}{\tau}$. The bracketed term in $\mu'$ is the perturbation
-component.
+component. We will take $\alpha, \epsilon > 0$, which will result in separatrix
+encounters originating in zone III, but an identical procedure for $\epsilon <
+0$ describes separatrix encounters originating in zone I.
 
@@
 \autoref{eq:p_c_gen}, for which we need:
-\begin{subequations}
 \begin{align}
-        \Delta_- &= \int\limits_{\mathcal{C}_-}
+    \Delta_\pm &= \int\limits_{\mathcal{C}_\pm}
             \phi'\epsilon\p{1 - \mu^2}\;\mathrm{d}t,\nonumber\\
-            &= \int\limits_{\mathcal{C}_s}
-                \p{1 - \mu^2}\;\mathrm{d}\phi,\\
-        \Delta_- + \Delta_+ &= \int\limits_{\mathcal{C}_- + \mathcal{C}_+}
-            \epsilon\p{1 - \mu^2}\;\mathrm{d}\phi.
+        &= \mp 2\pi\p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
+                + 16\cos I \eta^{3/2}\sqrt{\sin I}.\label{eq:p2_delta}
 \end{align}
-\end{subequations}
 Note that along $\mathcal{C}_{\pm}$ that $\mathrm{d}\phi$ has sign $\mp$
-respectively, thanks to our sign convention. We proceed to integrate:
-\begin{itemize}
-    \item $\Delta_-$: Recalling the parameterization for the separatrix
-        $\mu_{sep}(\phi)$ given by \autoref{eq:mu_sep}, we can evaluate
-        explicitly over $\mathcal{C}_-$. This gives result
-        \begin{equation}
-            \Delta_- = 2\pi\p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
-                + 16\cos I \eta^{3/2}\sqrt{\sin I}.
-        \end{equation}
-
-    \item $\Delta_- + \Delta_+$: Note $\mathrm{d}\phi$ changes signs between
-        $\mathcal{C}_-$ and $\mathcal{C}_+$. Thus, only terms in $\Delta_-$ that
-        also change signs on $\mathcal{C}_+$ contribute to the integral. This
-        allows us to evaluate
-        \begin{align}
-            \Delta_- + \Delta_+ &= 32\epsilon \eta^{3/2} \cos I \sqrt{\sin I}.
-        \end{align}
-\end{itemize}
-From these two integrals, we obtain
+respectively. From these two integrals, we obtain
 \begin{equation}
@@
     of these initial conditions converge to. Initial conditions are chosen
-    uniformly in $(\mu, \phi)$ coordinates. The parameters for the simulation
-    are in the title.}\label{fig:0_3stats}
+    uniformly in $(\mu, \phi)$ coordinates. Key features to note are secure
+    convergence to CS1 for all zone I initial conditions, probabilistic
+    convergence to CS1 or CS2 for zone III initial conditions (first half of
+    \autoref{ss:p2_lt}), and secure convergence to CS2 for all zone II initial
+    conditions (second half of \autoref{ss:p2_lt}). The parameters for the
+    simulation are in the title.}\label{fig:0_3stats}
 \end{figure}
@@
 Now, since $\mu'(\phi) \geq 0$ everywhere, and $\bar{\mu} \in [\mu_2, \mu_4] >
-0$ as well, $\Delta h > 0$ necessarily, and \emph{all full librations in zone II
-will be driven towards CS2} (the point of maximum $h$ and maximum $H^{(0)}$).
+0$ as well, $\Delta h \geq  0$ necessarily, equality only exactly at CS2. And
+so, \emph{all full librations in zone II will be driven towards CS2} (the point
+of maximum $h$ and $H^{(0)}$).
 
-\section{Problem 2: Adiabatic Capture}\label{s:p2}
+\subsection{$\eta > \eta_c$, Convergence to CS2 (no sims)}
 
-Here, instead of introducing an aligning perturbation, we will instead
-adiabatically vary $\eta$.
+While not strictly within the purview of this paper, we can also prove that once
+$\eta > \eta_c$ and the separatrix vanishes, all trajectories converge to CS2.
+This follows naturally by considering the change $\Delta H^{(0)}$ over any orbit
+\begin{equation}
+    \Delta H^{(0)} = \oint \epsilon\p{1 - \mu^2}\;\mathrm{d}\phi.
+\end{equation}
+Visual inspection of \autoref{fig:0_1contours} shows that all orbits either
+circulate $\phi' > 0$ or librate counterclockwise very near CS2. For any
+circulating $\phi' > 0$ orbit, $\Delta H^{(0)} > 0$ is enforced. For any
+counterclockwise libration near CS2, the same argument as the zone II initial
+conditions from \autoref{ss:p2_lt} above apply, where $\Delta H^{(0)} \geq 0$
+with equality only at CS2 itself.
 
-\subsection{Spindown Model}\label{ss:p2_spindown}
+\section{Problem 3: Combined Perturbations (sims)}\label{s:p3}
 
-We may first consider the unperturbed Hamiltonian
-system with $\rd{\eta}{t} = \frac{\eta}{t_\eta}$ growth with characteristic
-timescale $t_\eta$. Again rescaling time $\tau \equiv \alpha t$ and defining
-$\epsilon \equiv \frac{1}{\alpha t_\eta}$, we obtain
+We now consider the combined problem, where the EOMs for Problem 2
+(\autoref{se:p2_eom}) are used in conjunction with the simplest $\eta' = \delta
+\eta$, the same as \autoref{eq:p1_eom}. Evaluation of $\Delta h$ along
+$\mathcal{C}_{\pm}$ is simply combining the results of \autoref{eq:p1_delta} and
+\autoref{eq:p2_delta}. The result is
+\begin{align}
+    \Delta_{\pm} ={}& \epsilon\s{
+        \mp 2\pi \p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
+            + 16\cos I\eta^{3/2}\sqrt{\sin I}}\nonumber\\
+        &+ \delta \s{\mp 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
+\end{align}
+Thus, the capture probability from a zone III initial condition into the
+separatrix is
 \begin{equation}
-    \rd{\eta}{t} = \epsilon \eta,
+    P_c \approx \frac{\p{32 \eta_\star \cos I + 8f}\sqrt{\eta_\star \sin I}}{
+        2\pi\p{1 - 2\eta_{\star}\sin I + f\eta_\star \cos I}
+            + \p{16\eta_\star\cos I + 4f} \sqrt{\eta_\star\sin I}}.
+            \label{eq:p3_p_c}
 \end{equation}
-where $\epsilon > 0$. Such a model is motivated e.g.\ when a planet's
-spin $\hat{s}$ orbits a host star with angular momentum $\hat{l}$ while the star
-spins down; $\dot{\alpha} < 0$ here, and $\eta' > 0$.
+An $\eta_\star^2$ term has been dropped from the denominator, and $f \equiv
+\frac{\delta}{\epsilon}$ measures the relative strength of the two
+perturbations. Note that $f = 0$ reduces to \autoref{s:p2}.
 
-We then seek $\Delta_{\pm}$, determined by
-\begin{align}
-    \Delta_{\pm} &= \int\limits_{\mathcal{C}_{\pm}}
-            \pd{h}{\eta}\eta'\;\mathrm{d}\tau,\nonumber\\
-        &= \int\limits_{\mathcal{C}_{\pm}}
-            \frac{\pd{h}{\eta}}{\phi'}\eta'\;\mathrm{d}\phi.
-\end{align}
-We must proceed carefully since $\phi' \to 0$ at the endpoints of
-$\mathcal{C}_{\pm}$; careful work shows these zeros cancel against zeros of
-$\pd{h}{\eta}$, and
-\begin{equation}
-    \Delta_{\pm} = \int\limits_{\mathcal{C}_{\pm}} \eta'
-        \p{\cos I \mp \sin I \sqrt{\frac{1 - \cos \phi}{2\eta\sin I}}}
-            \;\mathrm{d}\phi.\label{eq:p2_delta}
-\end{equation}
-Immediately, we see that if we use $\eta' = \epsilon \eta$, then $\Delta_{\pm} >
-0$ and \emph{all separatrix encounters result in capture} regardless of whether
-the trajectory originates in zone I or zone III\@. Since increasing $\eta$
-results in larger separatrix, zone II trajectories will not experience
-separatrix crossing. Indeed, an example of such a simulation is presented in
-\autoref{fig:2_1testo4}. Further simulations with other initial conditions
-support the guaranteed capture prediction in this system.
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/1testo4.png}
-    \caption{Simulation with initial condition in zone I subject to $\eta' =
-    \epsilon \eta$, where $\epsilon = 10^{-4}$. The top panel shows the
-    trajectory (red) starting with initial condition $\mu_0 = 0.140, \phi_0 = 0$
-    (green dot) and separatrix at separatrix crossing (dashed black) in
-    the labelled coordinates. The end of the simulation is labelled in the blue
-    cyan dot. The bottom panel shows the evolution of the enclosed area by the
-    trajectory (red dots), area of the separatrix (blue) and $\eta$ (dotted
-    green) over time.}\label{fig:2_1testo4}
-\end{figure}
-
-If instead $\epsilon < 0$, then only zone II initial conditions experience
-separatrix encounter, and since $\Delta_{\pm} < 0$, all trajectories are
-ejected as the separatrix shrinks.
-
-\subsection{Nontrivial Test Problem}\label{ss:p2_toy}
-
-It is clear that $\eta'$ in \autoref{eq:p2_delta} being the same sign along both
-$\mathcal{C}_{\pm}$ is the source of this guaranteed capture. To assess the
-accuracy of our formalism, we propose instead test problem where $\eta$ is
-varied following
-\begin{equation}
-    \eta' = \epsilon \eta \mu.
-\end{equation}
-Straightforward evaluation of \autoref{eq:p2_delta} yields
-\begin{equation}
-    \Delta_{\pm} = \pm \epsilon \eta_\star \s{
-        2\pi \sin I \pm 12 \sqrt{\eta_\star \sin I}\cos I
-            + 2\pi \eta_\star \cos^2 I}.
-\end{equation}
-It bears noting that we must evaluate these integrals at $\eta = \eta_\star$ the
-value at separatrix crossing. Since $\eta$ evolves over time, $\eta_{\star}$
-depends on initial conditions. While one might expect the adiabatic invariance
-of the action variable determines $\eta_\star$, this turns out to not be the
-case; we address this in \autoref{ss:noncons}.
-
-Since $\abs{\Delta_+} > \abs{\Delta_-}$, separatrix encounters originating in
-zone III always result in capture. However, encounters originating in zone I
-experience capture probability
-\begin{equation}
-    P_c(\eta_\star) = \frac{24\cos I \sqrt{\eta_\star \sin I}}{
-        2\pi \sin I + 12\sqrt{\eta_\star \sin I}\cos I
-            + 2\pi \eta_\star \cos^2 I}.\label{eq:p_c_p2}
-\end{equation}
-
-To test this capture probability, we adopt a slightly different testing
-methodology than in \autoref{s:p1}. For fixed initial condition $(\mu_0,
-\phi_0)$ in zone I, we vary the initial $\eta \in [0.01, 0.02]$ and $\epsilon
-\in 10^{[-3, -2]}$. In this way, every simulation experiences probabilistic
-separatrix crossing at roughly comparable times. We then repeated this procedure
-for three different values $I = 10^\circ, 20^\circ, 25^\circ$. A natural spread
-in $\eta_\star$ was observed at each $I$ value, which permitted comparison to
-\autoref{eq:p_c_p2} independently. The results for the three $I$ values are
-presented in \autoref{fig:2_1hist}, where good agreement with
-\autoref{eq:p_c_p2} is shown.
+The accuracy of \autoref{eq:p3_p_c} is illustrated in \autoref{fig:p3_hist}. A
+small deviation can be noticed at larger $\eta_\star$ values as $f$ is
+increased. This is attributed to the separatrix becoming significantly
+asymmetric around $\eta \sim 0.15$, therefore our \autoref{eq:mu_sep} is no
+longer an accurate approximation. When $f = 0$, the small deviations are
+significantly suppressed as the numerator scales with $\eta_\star^{3/2}$
+compared to when $f \sim 1$, where the numerator instead scales with
+$\eta_{\star}^{1/2}$.
 \begin{figure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/1hist10.png}
+        \includegraphics[width=\textwidth]{../initial/3_toy3/1hist20_0_00.png}
+        \caption{$\delta/\epsilon = 0$}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/1hist20.png}
+        \includegraphics[width=\textwidth]{../initial/3_toy3/1hist20_0_30.png}
+        \caption{$\delta/\epsilon = 0.3$}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/1hist25.png}
+        \includegraphics[width=\textwidth]{../initial/3_toy3/1hist20_0_70.png}
+        \caption{$\delta/\epsilon = 0.7$}
     \end{subfigure}
-    \caption{Simulations depicting $P_c(\eta_\star)$ at three different values
-    $I = 10^\circ, 20^\circ, 25^\circ$. The top panel represents the binned
-    outcomes as a function of $\eta_\star$, and the resulting estimates of $P_c$
-    are compared with the analytical curve (red) from \autoref{eq:p_c_p2} in the
-    bottom panel. Uncertainties in $P_c(\eta_\star)$ from data are estimated as
-    $\sqrt{N}$ where $N$ is the count per bin. Also reported is the average
-    value of $\eta_\star$.}\label{fig:2_1hist}
+    \caption{Histogram of simulation and inferred $P_c(s_\star)$ compared with
+    \autoref{eq:p3_p_c}, where $f = \delta/\epsilon$ is varied. $3 \times 10^4$
+    initial conditions were used for both plots. While the $f = 0$ case
+    indicates perfect agreement, the other two cases show increasingly large
+    deviations at larger $\eta_\star$.}\label{fig:p3_hist}
 \end{figure}
 
-\subsection{Conservation of Adiabatic Invariant}\label{ss:noncons}
-
-Under the theory of adiabatic invariants (see e.g.\ \cite{henrard1982,
-l_and_l}), trajectories following Hamiltonian equations of motion save for small
-$\eta'$ conserve action variable $I$ except at separatrix crossing, where
-\begin{equation}
-    I \equiv \frac{1}{2\pi}\oint p\;\mathrm{d}q.
-\end{equation}
-$I$ has physical interpretation the enclosed phase space area of trajectories.
-Its evolution can be seen in \autoref{fig:2_1testo4}. Under the assumption $I$
-is conserved except at separatrix crossing, $\eta_\star$ is fixed implicitly by
-$I = A_{sep}(\eta_\star)$ for $I$ the initial value of the action variable.
-Since $A_{sep}$ is given by \autoref{eq:a_sep}, it would appear $\eta_\star$ can
-be predicted exactly.
-
-\textbf{NOTE:} The rest of this section is not very complete.
-
-This turns out to be accurate in \autoref{ss:p2_spindown} but not in
-\autoref{ss:p2_toy}, so it's probably non-physical/has to do with $\eta' = 0$
-when $\mu = 0$. Not sure whether this is physically useful. Useful formulas for
-$\rd{I}{t}$ can be taken from~\cite{henrard1982, l_and_l}:
-\begin{equation}
-    \rd{I}{\tau} = \s{\pd{H}{\eta}T(\eta) - \int\limits_0^{T(\eta)}
-            \pd{H}{\eta}\;\mathrm{d}\tau} \eta'
-        = -\pd{}{w}\p{\pd{S}{\eta}}\eta'.
-\end{equation}
-Here, $T(\eta)$ is the period of the orbit, $w$ is the angle variable conjugate
-to $I$, and $S$ is the generating function for canonical transformation $\mu =
-\pd{S}{\phi}, w = \pd{S}{I}$. These expressions are hard to evaluate, but maybe
-they will tell us how much to expect $\rd{I}{\tau}$ to deviate from zero near
-the separatrix?
-
-\section{Problem 3: Weak Tidal Dissipation}\label{s:p3}
+\section{Problem 4: Weak Tidal Dissipation (sims)}\label{s:p4}
 
@@
 \phi, s)$:
-\begin{subequations}\label{se:p3_eom}
+\begin{subequations}\label{se:p4_eom}
     \begin{align}
-        \pd{\phi}{\tau} &= \frac{s}{s_c}\mu
+        \rd{\phi}{\tau} &= \frac{s}{s_c}\mu
             - \p{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}} \cos \phi},\\
-        \pd{\mu}{\tau} &= -\sin I \sin \phi +
+        \rd{\mu}{\tau} &= -\sin I \sin \phi +
             \epsilon \p{1 - \mu^2} \p{\frac{2\Omega_1}{s} - \mu},\\
@@
 \end{subequations}
-The expressions for $H^{(0)}, H_4$ can also be written down
+The expressions for $H^{(0)}, H_{sep}$ can also be written down
 \begin{align}
@@
         + \mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi.\\
-    H_4(s) &= -\sin I + \frac{s_c}{2s}\cos^2 I.
+    H_{sep}(s) &= -\sin I + \frac{s_c}{2s}\cos^2 I.
 \end{align}
@@
             \p{\frac{s}{2\Omega_1} - \frac{s_c\cos I}{s}}
-                + 4\pi \frac{s_c}{s}\sin I}}.\label{eq:delta_p3}
+                + 4\pi \frac{s_c}{s}\sin I}}.\label{eq:delta_p4}
 \end{align}
@@
             \p{\frac{s_\star}{2\Omega_1} - \frac{s_c \cos I}{s_\star}}}.
-            \label{eq:p_c_p3}
+            \label{eq:p_c_p4}
 \end{equation}
@@
 
-To test \autoref{eq:p_c_p3}, we generate an evenly spaced grid of initial
+To test \autoref{eq:p_c_p4}, we generate an evenly spaced grid of initial
 conditions $(\mu_0, \phi_0)$ and initialize $s_0 = 10$. We then record $s_\star$
-and the final ooutcome of the trajectory over many simulations. The agreement of
-\autoref{eq:p_c_p3} with data can be observed in \autoref{fig:1_4stats}.
+and the final outcome of the trajectory over many simulations. The agreement of
+\autoref{eq:p_c_p4} with data can be observed in \autoref{fig:1_4stats}.
 \begin{figure}
@@
     \caption{Histogram of simulation and inferred $P_c(s_\star)$ compared with
-    \autoref{eq:p_c_p3}. $s_c$ used are numbered at the top of each plot. $10^4$
+    \autoref{eq:p_c_p4}. $s_c$ used are numbered at the top of each plot. $10^4$
     simulations were used for each plot, and a single $I = 20^\circ$ was
@@
 
-In \autoref{s:p2}, the capture probability $P_c(\eta_\star)$ depended on
+In \autoref{s:p1}, the capture probability $P_c(\eta_\star)$ depended on
 $\eta_\star$ which could be determined by conservation of the action varible
 $I$. Such an argument is not possible in the weak tidal prescription as the
-system is dissipitive thanks to $\dot{\mu}^{(1)}$ (see \autoref{se:p3_eom}).
+system is dissipitive thanks to $\dot{\mu}^{(1)}$ (see \autoref{se:p4_eom}).
 
@@
 \begin{equation}
-    \tau_\star = \frac{h(t = 0)}{3s\mu^2/2s_c} + C,
+    \tau_\star = \frac{h(t = 0)}{3s\mu^2/2s_c} + C,\label{eq:tau_star}
 \end{equation}
@@
     \caption{TODO make this plot actually look reasonable. The top and bottom
-    panels show $t_\star, s_\star$ as a function of $-h = H_4 - H$. The dotted
-    red line in the top panel is $t_\star = \frac{h}{3s\mu^2/2s_c} + C$ where
-    $C$ is a fitting parameter determined by the behavior of $\rd{h}{\tau}$ near
-    the separatrix.}\label{fig:1_4cross}
+    panels show $t_\star, s_\star$ as a function of $-h = H_{sep} - H$. The
+    dotted red line in the top panel is $t_\star = \frac{h}{3s\mu^2/2s_c} + C$
+    where $C$ is a fitting parameter determined by the behavior of
+    $\rd{h}{\tau}$ near the separatrix. This demonstrates that the separatrix
+    arrival time is well-described by
+    \autoref{eq:tau_star}.}\label{fig:1_4cross}
 \end{figure}
@@
 
-Careful examination of \autoref{eq:delta_p3} reveals that for sufficiently large
+Careful examination of \autoref{eq:delta_p4} reveals that for sufficiently large
 $s_c$, $\Delta_+$ changes sign and becomes positive. When $\Delta_+ < 0$,
@@
 sufficiently large $s_c$. We find that $s_c \gtrsim 0.5 \Omega_1$ is sufficient
-that an initial spin of $s_0 = 10$ will \emph{always} be captured into CS2. TODO
-could shore this up a bit, find a good way to plot.
+that an initial spin of $s_0 = 10$ will \emph{always} be captured into CS2.
 
-TODO find a clean plot to demonstrate this, I have the data already.
+TODO Maybe this is worth a real plot?
 

### 2019-08-07 initial/0_eta/6manifolds.py

@@ -38,7 +38,7 @@ def plot_manifolds(eta):
     phi1 = np.unwrap(_phi1 + np.pi) - 2 * np.pi
     term1 = np.where(phi1 < 0)[0][0]
     plt.plot(phi1[ :term1], s1[2, :term1], 'g',
-             label=r'$W_s^{(0)}$', linewidth=0.6)
+             label=r'$W_s^{L}$', linewidth=0.6)
 
     # forwards from CS4^0
     init = get_displaced(-1, 1)
@@ -51,7 +51,7 @@ def plot_manifolds(eta):
         phi2 < 1,
     ))[0][0]
     plt.plot(phi2[ :term2], s2[2, :term2], 'r',
-             label=r'$W_u^{(0)}$', linewidth=0.6)
+             label=r'$W_u^{L}$', linewidth=0.6)
 
     # backwards from CS4^1
     init = get_displaced(-1, -1)
@@ -60,7 +60,7 @@ def plot_manifolds(eta):
     phi3 = np.unwrap(_phi3 + np.pi)
     term3 = np.where(phi3 < 0)[0][0]
     plt.plot(phi3[ :term3], s3[2, :term3], 'k',
-             label=r'$W_s^{(1)}$', linewidth=0.6)
+             label=r'$W_s^{R}$', linewidth=0.6)
 
     # forwards from CS4^1
     init = get_displaced(1, -1)
@@ -69,7 +69,7 @@ def plot_manifolds(eta):
     phi4 = np.unwrap(_phi4 + np.pi)
     term4 = np.where(phi4 < 0)[0][0]
     plt.plot(phi4[ :term4], s4[2, :term4], 'k',
-             label=r'$W_u^{(1)}$', linewidth=0.6)
+             label=r'$W_u^{R}$', linewidth=0.6)
 
     plt.xlim([0, 2 * np.pi])
     mu1, mu2, mu3 = min(s1[2, :term1]), min(s2[2, :term2]), min(s3[2, :term3])

### 2019-08-07 initial/1_weaktide/4sim_v2.py

@@ -435,10 +435,10 @@ def cross_times(trajs, I, eps, s_c, s0=10, tf=2500):
     p_hop = n_hop[valids] / (n_hop[valids] + n_cross[valids])
     p_hop_err = np.sqrt(n_hop[valids]) / (n_hop[valids] + n_cross[valids])
     ax2.errorbar(s_vals[valids], p_hop,
-                 yerr=p_hop_err, fmt='bo', label='Data')
+                 yerr=p_hop_err, fmt='C0o', label='Data')
     ax1.set_ylabel('Counts')
     ax2.set_xlabel(r'$s_\star$')
-    ax2.set_ylabel(r'$P_{hop}$')
+    ax2.set_ylabel(r'$P_{c}$')
 
     # overplot analytic estimate
     p_hop_top = 16 * np.sqrt(s_c / s_vals * np.sin(I))\

### 2019-08-07 initial/3_toy3/1sim.py

@@ -108,7 +108,7 @@ def run_stats(I_deg, delta, p=None):
                 + (16 * np.cos(I) * eta + 4 * delta) * np.sqrt(eta * np.sin(I)))
     ax2.plot(eta_vals, fit(eta_vals), 'r', linewidth=2, label='Analytical')
     ax1.set_title(r'$I = %d^\circ$' % I_deg)
-    ax2.set_ylabel('Capture Probability')
+    ax2.set_ylabel(r'$P_c$')
     ax1.set_ylabel('Counts')
     ax2.legend()
     plt.savefig('1hist%s.png' % my_fmt(I_deg, delta),

### 2019-08-27 writeups/Su_sep_cross.tex
typo fix
fix sign mistake, problem 3 looks good

@@
     \Delta_{\pm} &= \int\limits_{\mathcal{C}_{\pm}} \eta'
-        \p{\cos I \mp \sin I \sqrt{\frac{1 - \cos \phi}{2\eta\sin I}}}
+        \p{-\cos I \mp \sin I \sqrt{\frac{1 - \cos \phi}{2\eta\sin I}}}
             \;\mathrm{d}\phi,\label{eq:p1_delta_eq}\\
@@
     \item If $\eta_\star > \frac{4\sin I}{\pi^2 \cos^2 I}, \eta_\star < \eta_c$,
-        then the separatrix still exists, and $\Delta_+ < 0, \Delta_- > 0$,
-        $\Delta_+ + \Delta_- > 0$. This implies: zone I + zone II trajectories
-        do not experience separatrix encounters, while zone III trajectories are
+        then the separatrix still exists, and $\Delta_- < 0, \Delta_+ > 0$,
+        $\Delta_+ + \Delta_- > 0$. This implies: zone III + zone II trajectories
+        do not experience separatrix encounters, while zone I trajectories are
         captured into zone II with probability
@@
 If instead $\epsilon < 0$, then the separatrix area shrinks over time. For
-initial values $\eta > \eta_c$, the separatrix appears over time and the
-scenario is analyzed in \citep{anderson2018teeter}.
+initial values $\eta > \eta_c$, the separatrix is not initially present and only
+appears later in the simulation. This is analyzed in \citep{anderson2018teeter}.
 
@@
     \begin{split}
-        P_{II \to I} &= \frac{2\pi \eta_\star \cos I + 4\sqrt{\eta_\star \sin I}}
+        P_{II \to I} &= \frac{-2\pi \eta_\star \cos I + 4\sqrt{\eta_\star \sin I}}
             {8\sqrt{\eta_\star \sin I}}, \\
-        P_{II \to III} &= \frac{-2\pi \eta_\star \cos I + 4\sqrt{\eta_\star \sin
+        P_{II \to III} &= \frac{2\pi \eta_\star \cos I + 4\sqrt{\eta_\star \sin
             I}} {8\sqrt{\eta_\star \sin I}}.
@@
             + 16\cos I\eta^{3/2}\sqrt{\sin I}}\nonumber\\
-        &+ \delta \s{\mp 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
+        &+ \delta \s{\pm 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
 \end{align}
@@
     P_c \approx \frac{\p{32 \eta_\star \cos I + 8f}\sqrt{\eta_\star \sin I}}{
-        2\pi\p{1 - 2\eta_{\star}\sin I + f\eta_\star \cos I}
+        2\pi\p{1 - 2\eta_{\star}\sin I - f\eta_\star \cos I}
             + \p{16\eta_\star\cos I + 4f} \sqrt{\eta_\star\sin I}}.
@@
 \bibliographystyle{mnras}
-\bibliography{paper}
+\bibliography{Su_sep_cross}
 

### 2019-08-29 initial/notes.tex
fix sign mistake, problem 3 looks good
fix algebra on P3/4 Phops, now look really good

@@
     P_{hop} = \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi
-        \p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
+        \p*{1 - 2\eta \sin I - \eta^2 \cos^2 I}
         + 8\eta^{3/2}\cos I \sqrt{\sin I}}.
@@
         &= \int_{\mathcal{C}_i} \epsilon \mu \eta
-            \p*{-\cos I + \sin I \frac{\cos \phi \sqrt{1 - \mu^2} - 1}{-\mu +
+            \p*{\cos I + \sin I \frac{\cos \phi \sqrt{1 - \mu^2} - 1}{-\mu +
             \eta \cos I}} \;\mathrm{d}\phi.
@@
     B_i &= \int_{\mathcal{C}_i} \epsilon \mu \eta
-            \p*{-\cos I \pm \sin I
+            \p*{\cos I \pm \sin I
                 \sqrt{\frac{1 - \cos \phi}{2\eta \sin I}}} \;\mathrm{d}\phi.
@@
 \begin{align*}
-    B_{top} &= \int\limits_{2\pi}^0 -\epsilon \mu \eta \cos I\;\mathrm{d}\phi
+    B_{top} &= \int\limits_{2\pi}^0 \epsilon \mu \eta \cos I\;\mathrm{d}\phi
             + \frac{\epsilon}{2}\int\limits_{2\pi}^0
                 \mu\sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
-        &= \epsilon \eta \cos I\p*{2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
-            + \frac{\epsilon}{2}\p*{\eta \cos I (8\sqrt{\eta \sin I})
+        &= -\epsilon \eta \cos I\p*{2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
+            - \frac{\epsilon}{2}\p*{\eta \cos I (8\sqrt{\eta \sin I})
             + 4\pi \eta \sin I},\\
-        &= \epsilon \eta \s*{
+        &= -\epsilon \eta \s*{
             2\pi \sin I + 12\sqrt{\eta \sin I}\cos I + 2\pi \eta \cos^2 I}.
@@
 \begin{align*}
-    B_{top} &= \int\limits_{2\pi}^0 -\epsilon \eta \cos I\;\mathrm{d}\phi
+    B_{top} &= \int\limits_{2\pi}^0 \epsilon \eta \cos I\;\mathrm{d}\phi
             + \frac{\epsilon}{2}\int\limits_{2\pi}^0
                 \sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
-        &= 2\pi \epsilon \eta \cos I - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
+        &= -2\pi \epsilon \eta \cos I - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
 \end{align*}
@@
 \begin{equation}
-    B_{\pm} = \pm 2\pi \epsilon \eta \cos I
+    B_{\pm} = \mp 2\pi \epsilon \eta \cos I
         - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
@@
 \begin{equation}
-    \Delta_{\pm} = \epsilon\s*{\mp 2\pi \p{1 - 2\eta \sin I - \eta^2 \cos^2 I} +
+    \Delta_{\pm} = \epsilon\s*{\mp 2\pi \p*{1 - 2\eta \sin I - \eta^2 \cos^2 I} +
         16\cos I\eta^{3/2}\sqrt{\sin I}} + f\epsilon
-            \s*{\mp 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
+            \s*{\pm 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
 \end{equation}
@@
             I}\;\mathrm{d}\phi,\\
-        &= \pm \int \epsilon 2\Omega_1
+        &= \int \epsilon 2\Omega_1
             \p*{\mu_{\pm} - \frac{s}{2\Omega_1}\p*{1 + \mu_{\pm}^2}}
-                \frac{s_c}{2s^2} \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}}
+                \frac{s_c}{2s^2} \s*{
+                    2\cos I \pm
+                    \sqrt{2\frac{s}{s_c} \sin I\p*{1 - \cos \phi}}}
                 \;\mathrm{d}\phi,\\
-        &\approx \pm \frac{\epsilon \Omega_1 s_c}{s^2}
-            \int \p*{\mu_{\pm} - \frac{s}{2\Omega_1}}
-            \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}} \;\mathrm{d}\phi,\\
-        &\approx \pm\frac{\epsilon \Omega_1 s_c}{s^2}
-            \int \p*{\mu_4 - \frac{s}{2\Omega_1} \pm
-                \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}}}
-            \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}} \;\mathrm{d}\phi,\\
-        &= \frac{\epsilon \Omega_1 s_c}{s^2}\s*{
-            \pm \p*{\mu_4 - \frac{s}{2\Omega_1}}\p*{-8\sqrt{\eta \sin I}}
-                + 4\pi \frac{s_c}{s}\sin I}.
-\end{align*}
+        &\approx \epsilon \frac{s_c}{s^2} \int
+            \p*{\mu_{\pm} - \frac{s}{2}}
+                \s*{2\cos I \pm \sqrt{\frac{2 \sin I}{\eta}\p*{1 - \cos \phi}}}
+                \;\mathrm{d}\phi.
+\end{align*}
+At this point, the integral is rather messy, so we have approximated $1 +
+\mu_{\pm}^2 \approx 1$, set $\epsilon = \Omega_1 = 1$, then split $\mu_{\pm} -
+s/2$ into two terms, $\mu_4 - s/2$ and the square root. We further break down
+into three terms to evaluate the integral of the product: the $2\cos I$ term,
+the product of the two square root components. These three integrals are
+respectively
+\begin{align*}
+    \int_{\pm} 2\cos I \p*{\mu_{\pm} - \frac{s}{2}}\;\mathrm{d}\phi &=
+        -2\cos I\p*{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
+        \pm 2\pi s\cos I,\\
+    \pm \int_{\pm} \p*{\mu_4 - \frac{s}{2}}
+            \sqrt{\frac{2\sin I}{\eta}\p*{1 - \cos \phi}} \;\mathrm{d}\phi &=
+        \eta \cos I \p*{-8\sqrt{\sin I / \eta}}
+            + \frac{s}{2}8\sqrt{\sin I/\eta} ,\\
+    \int_{\pm} 2\sin I \p*{1 - \cos \phi}\;\mathrm{d}\phi &= \mp 4\pi \sin I.
+\end{align*}
+
 Indeed, the sum over the two legs is positive, which is expected: during
@@
 times the original integrand; this means the final result is $\frac{2\Omega}{s}$
-times the old result plus a contribution approximately $-\int \epsilon \mu
-\;\mathrm{d}\phi$. This latter term is a purely antisymmetric contribution, so
-we may approximate
+times the old result plus a contribution $\int \epsilon \p*{1 - \mu^2}\p*{-\mu}
+\;\mathrm{d}\phi$. This second term can be evaluated exactly, and we obtain
 \begin{align*}
     \int_{\mathcal{C}_{\pm}}\dot{\mu}^{(1)}\;\mathrm{d}\phi
-        &\approx \epsilon\frac{2\Omega}{s}\p{\mp 2\pi
+        &\approx \epsilon\frac{2\Omega}{s}\p*{\mp 2\pi\p*{1 - 2\eta \sin I}
             + 16\cos I \eta^{3/2}\sqrt{\sin I}}
-            + 8\epsilon\sqrt{\eta \sin I},\\
-        &\approx \mp \frac{4\pi\epsilon \Omega}{s} + 8\sqrt{\eta \sin I}.
+            + 8\epsilon\sqrt{\eta \sin I}
+            \pm 2 \pi \eta \cos I
+            - \frac{64}{3}\epsilon \p*{\eta \sin I}^{3/2}.
 \end{align*}
 This is in agreement with our work from 5.1. Thus, the total expression is
+\begin{align}
+    \frac{\Delta_{\pm}}{\epsilon} ={}&
+        -2\cos I\p*{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
+        \pm 2\pi s\cos I
+        + \eta \cos I \p*{-8\sqrt{\sin I / \eta}}
+            + \frac{s}{2}8\sqrt{\sin I/\eta}\nonumber\\
+        &+ \frac{2\Omega}{s}\p*{\mp 2\pi\p*{1 - 2\eta \sin I}
+            + 16\cos I \eta^{3/2}\sqrt{\sin I}}
+            + 8\sqrt{\eta \sin I}
+            \pm 2 \pi \eta \cos I
+            - \frac{64}{3} \p*{\eta \sin I}^{3/2},\\
+    P_c ={}& \frac{\Delta_+ + \Delta_-}{\Delta_-}.
+\end{align}
 

### 2019-08-29 writeups/Su_sep_cross.tex
fix algebra on P3/4 Phops, now look really good

@@
 
-The accuracy of \autoref{eq:p3_p_c} is illustrated in \autoref{fig:p3_hist}. A
-small deviation can be noticed at larger $\eta_\star$ values as $f$ is
-increased. This is attributed to the separatrix becoming significantly
-asymmetric around $\eta \sim 0.15$, therefore our \autoref{eq:mu_sep} is no
-longer an accurate approximation. When $f = 0$, the small deviations are
-significantly suppressed as the numerator scales with $\eta_\star^{3/2}$
-compared to when $f \sim 1$, where the numerator instead scales with
-$\eta_{\star}^{1/2}$.
+The good accuracy of \autoref{eq:p3_p_c} is illustrated in
+\autoref{fig:p3_hist}. Both a red line from \autoref{eq:p3_p_c} and a black line
+from numerically evaluating $\Delta h$ along the numerically-determined
+separatrix (obtained by solving $H(\mu_{sep}, \phi_{sep}) = H_4$) are presented.
+Good agreement is observed.
 \begin{figure}
@@
     \autoref{eq:p3_p_c}, where $f = \delta/\epsilon$ is varied. $3 \times 10^4$
-    initial conditions were used for both plots. While the $f = 0$ case
-    indicates perfect agreement, the other two cases show increasingly large
-    deviations at larger $\eta_\star$.}\label{fig:p3_hist}
+    initial conditions were used for both plots. The solid red line denotes the
+    prediction of \autoref{eq:p3_p_c}, while the black dotted line is estimated
+    via numerical integration instead.}\label{fig:p3_hist}
 \end{figure}
@@
 \begin{align}
-    \Delta_{\pm} \approx{}& \epsilon\z{
-            \mp \frac{4\pi  \Omega_1}{s} + 8\sqrt{\frac{s_c}{s}\sin I}
-            }\nonumber\\
-        &+\epsilon\z{\frac{ \Omega_1 s_c}{s^2}
-            \s{\pm 8\sqrt{\frac{s_c}{s} \sin I}
-            \p{\frac{s}{2\Omega_1} - \frac{s_c\cos I}{s}}
-                + 4\pi \frac{s_c}{s}\sin I}}.\label{eq:delta_p4}
+    \frac{\Delta_{\pm}}{\epsilon} ={}&
+        -2\cos I\p*{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
+        \pm 2\pi s\cos I\nonumber\\
+        &+ \eta \cos I \p*{-8\sqrt{\sin I / \eta}}
+            + \frac{s}{2}8\sqrt{\sin I/\eta}\nonumber\\
+        &+ \frac{2\Omega}{s}\p*{\mp 2\pi\p*{1 - 2\eta \sin I}
+            + 16\cos I \eta^{3/2}\sqrt{\sin I}}\nonumber\\
+        &+ 8\sqrt{\eta \sin I}
+            \pm 2 \pi \eta \cos I
+            - \frac{64}{3} \p*{\eta \sin I}^{3/2},\label{eq:delta_p4}\\
+    P_{c} &= \frac{\Delta_+ + \Delta_-}{\Delta_-}. \label{eq:p_c_p4}
 \end{align}
-We can then compute separatrix capture probability from zone III (which is $P_c
-= \frac{\Delta_+ + \Delta_-}{\Delta_-}$), again evaluating at $s = s_\star$:
-\begin{equation}
-    P_c(s_\star) = \frac{16\sqrt{\frac{s_c}{s_\star}\sin I} +
-        8\pi\frac{s_c}{s_\star}\sin I}{
-            \frac{4\pi \Omega_1}{s_\star} - \frac{8\Omega_1
-            s_c}{s_\star^2}\sqrt{\frac{s_c}{s_\star}\sin I}
-            \p{\frac{s_\star}{2\Omega_1} - \frac{s_c \cos I}{s_\star}}}.
-            \label{eq:p_c_p4}
-\end{equation}
-Note that for $\frac{s_c}{s_\star} < \eta_c$ that no separatrix (or resonance)
-exists anymore, so we will generally assume $s_\star \gtrsim s_c, \Omega_1$.
+Here, $P_c$ describes the separatrix capture probability from zone III\@. Note
+that for $\frac{s_c}{s_\star} < \eta_c$ that no separatrix (or resonance) exists
+anymore, so we will generally assume $s_\star \gtrsim s_c$ and correspeondingly
+$\Omega_1$.
 
@@
 and the final outcome of the trajectory over many simulations. The agreement of
-\autoref{eq:p_c_p4} with data can be observed in \autoref{fig:1_4stats}.
+\autoref{eq:p_c_p4} with data can be observed in \autoref{fig:1_4stats}. As
+before, a red solid line depicting \autoref{eq:p_c_p4} and a black dotted line
+using numerical evaluation of $\Delta h$ and a numerically-determined separatrix
+are depicted.
 \begin{figure}
@@
     simulations were used for each plot, and a single $I = 20^\circ$ was
-    used.}\label{fig:1_4stats}
+    used. The solid red and dotted black lines denote N\autoref{eq:p_c_p4} and a
+    full numerical evaluation of $P_c$ from $\Delta_{\pm}$ respectively. Note
+    that small values of $s$ cannot be evaluated as the separatrix has
+    disappeared $\eta > \eta_c$.}\label{fig:1_4stats}
 \end{figure}

### 2019-08-29 initial/1_weaktide/4sim_v2.py

@@ -7,6 +7,8 @@ detection/pretty plotting and t/s_cross statistics
 import os
 import numpy as np
 from multiprocessing import Pool
+import scipy.optimize as opt
+from scipy import integrate
 
 import pickle
 import matplotlib
@@ -20,6 +22,9 @@ from utils import solve_ic, to_ang, to_cart, get_etac, get_mu4, get_mu2,\
 PLOT_DIR = '4plots'
 PKL_FILE = '4dat%s.pkl'
 N_PTS = 100
+# eta higher than this, do not attempt phop matching; sep is hard to find
+# bit generous, otherwise sep is hard to find eta ~< 0.3
+ETA_CUTOFF = 0.3
 
 def get_name(s_c, eps, mu0, phi0):
     return stringify(s_c, mu0, phi0, strf='%.3f').replace('-', 'n')
@@ -441,17 +446,103 @@ def cross_times(trajs, I, eps, s_c, s0=10, tf=2500):
     ax2.set_ylabel(r'$P_{c}$')
 
     # overplot analytic estimate
-    p_hop_top = 16 * np.sqrt(s_c / s_vals * np.sin(I))\
-        + 8 * np.pi * s_c * np.sin(I) / s_vals
-    p_hop_bot = 4 * np.pi / s_vals \
-        - 8 * s_c / s_vals**2 * np.sqrt(s_c * np.sin(I) / s_vals)\
-        * (s_vals / 2 - s_c * np.cos(I) / s_vals)
-    p_hop_anal = p_hop_top / p_hop_bot
-    ax2.plot(s_vals, np.minimum(p_hop_anal, np.ones_like(p_hop_anal)),
-             'r', label='Anal')
+    def get_hop_approx(s):
+        ''' eta = scalar, approx mu(phi) '''
+        eta = s_c / s
+        if eta > ETA_CUTOFF:
+            return -1
+        [mu4] = get_mu4(I, s_c, np.array([s]))
+
+        def mu_up(phi):
+            def dH(mu):
+                return H(I, s_c, s, mu, phi) - H(I, s_c, s, mu4, 0)
+            return opt.brentq(dH, mu4, 1)
+        def mu_down(phi):
+            def dH(mu):
+                return H(I, s_c, s, mu, phi) - H(I, s_c, s, mu4, 0)
+            return opt.brentq(dH, -1, mu4)
+
+        def arg_top(phi):
+            m = mu_up(phi)
+            return (
[…]

### 2019-08-29 initial/3_toy3/1sim.py

@@ -68,7 +68,7 @@ def get_hop_anal(I, eta, delta):
     return (bot - top) / bot
 
 def get_hop_approx(I, eta, delta):
-    ''' eta = scalar, approximate mu(phi) '''
+    ''' eta = scalar, numerically integrate over approximate separatrix '''
     def mu_up(phi):
         return eta * np.cos(I) + np.sqrt(2 * eta * np.sin(I) * (1 - np.cos(phi)))
 
@@ -93,7 +93,7 @@ def get_hop_approx(I, eta, delta):
     return (bot - top) / bot
 
 def get_hop_num(I, eta, delta):
-    ''' eta = scalar, numerical mu(phi) '''
+    ''' eta = scalar, numerically integrate over exact separatrix '''
     q4 = roots(I, eta)[3]
     def mu_up(phi):
         def dH(q):
@@ -125,6 +125,7 @@ def get_hop_num(I, eta, delta):
     return (bot - top) / bot
 
 def get_hop_traj(I, eta_i, delta):
+    ''' eta = scalar, numerically integrate over IC-integrated trajectory '''
     tf = 150
     # quick heuristic calculation of Delta_-, to IC for evolve around sep
     q4 = roots(I, eta_i)[3]
@@ -246,11 +247,11 @@ def run_stats(I_deg, delta, p=None):
 
     # overplot fits
     fit_anal = get_hop_anal(I, eta_vals, delta)
-    ax2.plot(eta_vals, fit_anal, 'r', linewidth=2, label='An.')
+    ax2.plot(eta_vals, fit_anal, 'r', linewidth=2, label='Anal.')
     # fit_quad_approx = [get_hop_approx(I, eta, delta) for eta in eta_vals]
-    # ax2.plot(eta_vals, fit_quad_approx, 'g:', linewidth=2, label='Approx. Quad')
-    # fit_quad_num = [get_hop_num(I, eta, delta) for eta in eta_vals]
-    # ax2.plot(eta_vals, fit_quad_num, 'k:', linewidth=2, label='Full num')
+    # ax2.plot(eta_vals, fit_quad_approx, 'g:', linewidth=2, label='Num.')
+    fit_quad_num = [get_hop_num(I, eta, delta) for eta in eta_vals]
+    ax2.plot(eta_vals, fit_quad_num, 'k:', linewidth=2, label='Num.')
[…]

### 2019-09-04 initial/notes.tex
stash

@@
 \begin{align}
-    \pd{\phi}{t} &= \mu - \eta\p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}}
+    \pd{\phi}{t} &= -\mu + \eta\p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}}
         \cos \phi} ,\\
@@
 \begin{align}
-    \pd{\phi}{\tau} &= \frac{s}{s_c}\mu
-        - \p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}} \cos \phi} ,\\
+    \pd{\phi}{\tau} &= -\frac{s}{s_c}\mu
+        + \p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}} \cos \phi} ,\\
     \pd{\mu}{\tau} &= -\sin I \sin \phi +
@@
 
+\section{Misc}
+
+\subsection{Canonical Coordinates}
+
+Consider canonical coordinates $x = \sin \frac{\theta}{2}\cos \phi, y = \sin
+\frac{\theta}{2}\sin \phi$, then the Hamiltonian can be written
+\begin{align}
+    H &= -\frac{1}{2}\cos^2\theta
+        + \eta \p*{\cos \theta \cos I - \sin I \sin \theta \cos \phi}
+        ,\nonumber\\
+        &= -\frac{1}{2}\p*{1 - 2\sin^2\frac{\theta}{2}}^2
+            + \eta\p*{\p*{1 - 2\sin^2\frac{\theta}{2}}\cos I
+            - 2 \sin \frac{\theta}{2}\cos \phi \cos \frac{\theta}{2}\sin I}
+            ,\nonumber\\
+        &= -\frac{1}{2}\p*{1 - 2\p*{x^2 + y^2}}^2
+            + \eta\p*{\p*{1 - 2\p*{x^2 + y^2}}\cos I
+                - 2\sin I x\sqrt{1 - \p*{x^2 + y^2}}}.
+\end{align}
+
+\subsection{Destruction of CS via Tides}
+
+Let's return to the simple EOM considered in the constant $\eta$ tides case,
+where
+\begin{align}
+    \pd{\phi}{t} &= -\mu + \eta\p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}}
+        \cos \phi} ,\\
+    \pd{\mu}{t} &= -\eta \sin I \sin \phi + \s*{\epsilon \p*{1 - \mu^2}},
+\end{align}
+We want to determine where tides destroys CS2. We saw before that tides tends to
+shift CS2/CS4 towards each other. In fact, we can immediately see where they
+will collide: in the $\dot{\mu}$ equation, no $\phi$ is stationary if
+\begin{equation}
+    \epsilon > \frac{\eta \sin I}{1 - \mu^2}.
+\end{equation}
+We can substitute in $\mu_2, \mu_4 \sim \eta \cos I$ to obtain
+\begin{equation}
+    \epsilon_{c} \approx \frac{\eta \sin I}{1 - \eta^2\cos^2 I}.
+\end{equation}
+
+Of course, we can also solve perturbatively to higher order for the corrections
+to CS2/CS4 about their $\epsilon = 0$ values; we have already found before the
+first order correction to $\phi$
+\begin{equation}
+    \phi_{4, 2} = \z*{0, \pi} \pm \frac{\epsilon\p*{1 - \mu^2}}{\eta \sin I}
+        \approx \z*{0, \pi} \pm \frac{\epsilon}{\eta \sin I} +
+        \mathcal{O}\p*{\epsilon^2}.
+\end{equation}
+This can then be substituted back in to find the correction to $\mu_{4, 2}$
+\begin{equation}
+    \mu_{4, 2} \approx \frac{\eta \cos I}{1 \mp \eta \sin I}
+        \mp \frac{1}{2}\frac{\eta^2 \sin I \cos I}{1 \mp \eta \sin I}
+            \p*{\frac{\epsilon}{\eta \sin I}}^2 + \mathcal{O}\p*{\epsilon^3}.
+\end{equation}
+These corrections and $\epsilon_c$ can be found in good agreement w/ numerics in
+\lstinline{99_misc/0_stab.png}.
+
+Now, a slightly more subtle question: is it possible for CS2 to still exist but
+lose stability? Consider that for some $\epsilon\lesssim \epsilon_c$, the
+equilibria lie at $\phi_{2, 4} = \pi/2 \pm \Delta \phi$, where $\epsilon_c -
+\epsilon = \eta \sin I \frac{\Delta \phi^2}{2}$, then we consider perturbation
+about these equilibria $\phi_{2, 4} = \pi/2 \pm \Delta \phi + \delta \phi$. The
+linearized equations then read
+\begin{subequations}
+    \begin{align}
+        \dot{\phi} &\approx -\delta \mu \mp \eta^2 \sin I \cos I \delta \phi,\\
+        \dot{\mu} &\approx \pm\eta \sin I \Delta \phi \delta \phi.
+    \end{align}
+\end{subequations}
+The eigenvalue equation for this first-order system reads
+\begin{equation}
+    \lambda^2 \pm \eta^2 \sin I \cos I \pm \eta \sin I \Delta \phi = 0.
+\end{equation}
+This has real solutions if
+\begin{equation}
+    \p*{\eta^2 \sin I \cos I}^2 \mp \eta \sin I \Delta \phi > 0.
+\end{equation}
+If $\epsilon \sim \epsilon_c / 2$, i.e.\ not too close to critical, then
+$\Delta \phi^2 \sim 1$, so except for $\epsilon_c - \epsilon \ll \epsilon_c$,
+the second term dominates the first and we have one real and one imaginary root,
+corresponding to the two CSs. Otherwise, we can identify that for
+\begin{align*}
+    \Delta \phi &\leq \eta^3 \sin I \cos^2 I,\\
+    \epsilon_c - \epsilon &\leq \frac{\eta^7 \sin^3 I \cos^4 I}{2},
+\end{align*}
+that CS2 becomes unstable.
+
 \end{document}

### 2019-09-04 initial/99_misc/0_stab.py

@@ -1,0 +1,161 @@
+'''
+look for existence/stability of CS2 as tidal dissipation increases
+'''
+import numpy as np
+import scipy.optimize as opt
+
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif', size=12)
+
+I = np.radians(20)
+eta = 0.1
+mu2 = eta * np.cos(I) / (1 + eta * np.sin(I))
+mu4 = eta * np.cos(I) / (1 - eta * np.sin(I))
+eps_crit = eta * np.sin(I) / (1 - (eta * np.cos(I))**2)
+
+def get_dydt(tide):
+    def dydt(s):
+        x, y, z = s
+        return np.array([
+            y * z - eta * y * np.cos(I) - tide * z * x,
+            -x * z + eta * (x * np.cos(I) - z * np.sin(I)) - tide * z * y,
+            eta * y * np.sin(I) + tide * (1 - z**2),
+        ])
+    return dydt
+
+def get_jac(tide):
+    ''' get jacobian d(dy/dt)_i/dy_j for params '''
+    def jac(s):
+        x, y, z = s
+        return [
+            [-tide * z, z - eta * np.cos(I), y - tide * x],
+            [-z + eta * np.cos(I), -tide * z, -x - eta * np.sin(I) - tide * y],
+            [0, eta * np.sin(I), -2 * tide * z],
+        ]
+    return jac
+
+def to_ang(x, y, z):
+    r = np.sqrt(x**2 + y**2 + z**2)
+    q = np.arccos(z / r)
+    phi = (np.arctan2(y / np.sin(q), x / np.sin(q)) + np.pi)\
+        % (2 * np.pi)
+    return np.array([q, phi])
+
+def to_cart(q, phi):
+    return [
+        -np.sin(q) * np.cos(phi),
+        -np.sin(q) * np.sin(phi),
+        np.cos(q),
+    ]
+
+def get_cs2(eps):
+    cs2 = [np.sqrt(1 - mu2**2), 0, mu2]
+    return opt.root(get_dydt(eps), cs2, jac=get_jac(eps))
+
+def get_cs4(eps):
+    cs4 = [-np.sqrt(1 - mu4**2), 0, mu4]
+    return opt.root(get_dydt(eps), cs4, jac=get_jac(eps))
+
+def get_eps_crit_num():
+    left = 0
+    right = eps_crit
[…]

### 2019-09-04 initial/notes.tex
check in new canonical coords + eom

@@
 
-\subsection{Canonical Coordinates}
-
-Consider canonical coordinates $x = \sin \frac{\theta}{2}\cos \phi, y = \sin
-\frac{\theta}{2}\sin \phi$, then the Hamiltonian can be written
+\subsection{Another Set of Canonical Coordinates}
+
+Consider canonical coordinates $x = 2\sin \frac{\theta}{2}\cos \phi, y = 2\sin
+\frac{\theta}{2}\sin \phi$ (these can be verified to be canonical by evaluating
+PB $\z*{y, x}_{\cos \theta, \phi} = 1$), then the Hamiltonian can be written
 \begin{align}
@@
             ,\nonumber\\
-        &= -\frac{1}{2}\p*{1 - 2\p*{x^2 + y^2}}^2
-            + \eta\p*{\p*{1 - 2\p*{x^2 + y^2}}\cos I
-                - 2\sin I x\sqrt{1 - \p*{x^2 + y^2}}}.
-\end{align}
+        &= -\frac{1}{2}\p*{1 - \frac{x^2 + y^2}{2}}^2
+            + \eta\p*{\p*{1 - \frac{x^2 + y^2}{2}}\cos I
+                - \sin I x\sqrt{1 - \frac{x^2 + y^2}{4}}}.
+\end{align}
+This is in agreement w/ Millholland \& Batygin 2019's Eq.~26. These have EOM
+\begin{align*}
+    \dot{y} = -\pd{H}{x} &=
+        -x\p*{1 - \frac{x^2 + y^2}{2}} - \eta\p*{
+            -x \cos I + \frac{x^2\sin I}{4}\p*{1 - \frac{x^2 + y^2}{4}}^{-1/2}
+            - \sin I \sqrt{1 - \frac{x^2 + y^2}{4}}},\\
+    \dot{x} = \pd{H}{y} &=
+        y\p*{1 - \frac{x^2 + y^2}{2}} + \eta\p*{
+            -y \cos I + \frac{xy\sin I}{4}\p*{1 - \frac{x^2 + y^2}{4}}^{-1/2}
+            },\\
+\end{align*}
+The signs can be confirmed by considering that $\theta, x, y \approx 0$ in the
+$\eta \to 0$ limit results in $\dot{\phi} < 0$, or at $\phi \approx 0, y \propto
+\sin \phi \propto \phi$ and $\dot{y} < 0$. It bears noting that $x^2 + y^2 \in
+[0, 4]$, so the EOM diverge as $\theta \to \pi$. This is one fewer singularity
+than the naive $\p*{\cos\theta, \phi}$ covering, but full cartesian $\hat{s} =
+\p*{s_x, s_y, s_z}$ still has no singularities.
 

### 2019-09-04 initial/notes.tex
validated loss of stability
stash some notes

@@
 
+In fact, we can really do better: just let $\sin \phi = \frac{\epsilon\p*{1 -
+z_0^2}}{\eta \sin I}$, then $\mu = \frac{\eta \cos I}{1 - \eta \sin I \cos \phi
+\frac{1}{\sqrt{1 - z_0}}}$ where $z_0 = \eta \cos I$ is the zeroth order
+estimate. This is what is plotted in the aforementioned plot.
+
 Now, a slightly more subtle question: is it possible for CS2 to still exist but
@@
 \end{align*}
-that CS2 becomes unstable.
+that CS2 becomes unstable. We can also numerically validate this via
+\lstinline{99_misc/0_stab.py}.
+
+\subsection{Dissipating Disk: $\theta_f$ Distribution}
+
+Consider if $\eta$ crosses $\eta_c$ with $\eta(t = 0) > \eta_c$, and there is no
+dissipation, only variation of $\eta$. The area contained within the separatrix
+when it first forms is given in Ward \& Hamilton Paper I\@:
+\begin{equation}
+    A_{crit} = 4\pi \s*{1 - \p*{1 + \tan^{2/3}I}^{-3/2}}.
+\end{equation}
+We are interested in states that start nearly aligned w/ the disk, so in Zone II
+by our designation. Then, once three states appear, Zone II continues to shrink
+until separatrix crossing occurs. At the time of separatrix crossing, the
+trajectory is ejected into either Zone I/III (if Zone III is shrinking, then
+exclusively Zone I\@; can analytically state using Henrard \& Murigande 1987).
+The possible values for the new action of the ejected state are either $A_2 +
+A_3 - 2\pi$ or $A_3 - 2\pi$, when integrating $\mu\;\mathrm{d}\phi$. From here,
+the states will precess uniformly at some $\theta_f = A / 2\pi$.
 

### 2019-09-04 initial/99_misc/1_areas.py

@@ -1,0 +1,35 @@
+'''
+plot some areas
+'''
+import numpy as np
+
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif', size=12)
+
+def plot_A_crit():
+    '''
+    Plot area enclosed by separatrix at eta_crit
+    '''
+    I = np.linspace(0, 5, 21)**2
+    area_frac = 1 - (1 + np.tan(np.radians(I))**(2/3))**(-3/2)
+    fig, ax1 = plt.subplots(1, 1)
+    l1 = ax1.plot(I, area_frac, 'r', label='Areas')
+    ax1.set_xlabel(r'$I$ (deg)')
+    ax1.set_ylabel(r'$A_{crit}/4\pi$')
+    ax2 = ax1.twinx()
+
+    # @ cross, area is (A_3 - 2pi) / 2pi, while A_3 = 4pi * (1 - area_frac)
+    q_f = ((1 - area_frac) * 4 * np.pi - 2 * np.pi) / (2 * np.pi)
+    l2 = ax2.plot(I, q_f, 'b', label=r'$\cos\theta_f$') # TODO
+    ax2.set_ylabel(r'$\cos\theta$')
+
+    lns = l1 + l2
+    ax2.legend(lns, [l.get_label() for l in lns],
+               loc='upper left', fontsize=8)
+    plt.savefig('1_Acrit.png')
+
+if __name__ == '__main__':
+    plot_A_crit()

### 2019-09-05 initial/notes.tex
090519

@@
 \end{align*}
-that CS2 becomes unstable. We can also numerically validate this via
+the eigenvalues become real. However, for CS2, since the eigenvalue equation
+reads $\lambda^2 + b\lambda + c = 0$ and the eigenvalues take form $\p*{-b \pm
+\sqrt{b^2 - 4c}}/2$, no eigenvalue w/ positive real part ever appears, so it
+remains forever stable. We can also numerically validate this via
 \lstinline{99_misc/0_stab.py}.
@@
 by our designation. Then, once three states appear, Zone II continues to shrink
-until separatrix crossing occurs. At the time of separatrix crossing, the
-trajectory is ejected into either Zone I/III (if Zone III is shrinking, then
-exclusively Zone I\@; can analytically state using Henrard \& Murigande 1987).
-The possible values for the new action of the ejected state are either $A_2 +
-A_3 - 2\pi$ or $A_3 - 2\pi$, when integrating $\mu\;\mathrm{d}\phi$. From here,
-the states will precess uniformly at some $\theta_f = A / 2\pi$.
+until separatrix crossing occurs, which is at $J_i = A_2$. At the time of
+separatrix crossing, the trajectory is ejected into either Zone I/III (if Zone
+III is shrinking, then exclusively Zone I\@; can analytically state using
+Henrard \& Murigande 1987). The possible values for the new action of the
+ejected state are either $J_f = A_2 + A_3 - 2\pi$ or $J_f = A_3 - 2\pi$, when
+integrating $\mu\;\mathrm{d}\phi$. From here, the states will precess uniformly
+at some $\theta_f = J_f / 2\pi$.
+
+We can investigate two behaviors here then, the range of permitted $\theta_f$ as
+a function of $I$ (when $J_i = A_{crit}$), and the values of $\theta_f$ given
+some initial mutual inclination $\hat{s} \cdot \hat{l}_p$ ($J_i = 2\pi\p*{1 -
+\cos \epsilon}$ where $\epsilon$ is the initial mutual inclination).
 

### 2019-09-05 initial/99_misc/0_stab.py

@@ -10,7 +10,7 @@ import matplotlib.pyplot as plt
 plt.rc('text', usetex=True)
 plt.rc('font', family='serif', size=12)
 
-I = np.radians(20)
+I = np.radians(5)
 eta = 0.15
 mu2 = eta * np.cos(I) / (1 + eta * np.sin(I))
 mu4 = eta * np.cos(I) / (1 - eta * np.sin(I))
@@ -132,7 +132,7 @@ def plot_cs_pts():
     ax2.plot(eps_vals, phi4_th, 'b:')
 
     ax1.set_title(r'$\eta = %.1f$' % eta)
-    plt.savefig('0_stab.png')
+    plt.savefig('0_stab.png', dpi=400)
 
 def get_stab():
     eps_crit_exact = get_eps_crit_num()
@@ -169,5 +169,5 @@ def get_stab():
     get_eigens(1.1)
 
 if __name__ == '__main__':
-    # plot_cs_pts()
-    get_stab()
+    plot_cs_pts()
+    # get_stab()

### 2019-09-05 initial/notes.tex
add plot of locations of CS

@@
 First, we tackle the top integral. Here, the integrand is evaluated at
-$\mu_+(\phi) = \eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}$, so we can
-plug this in and compute
+$\mu_+(\phi) = \eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}$\footnote{
+Bears noting that $\mu_{\pm} = \frac{\eta \cos I}{1 - \eta \sin I} \pm \dots$
+significantly improves accuracy, it appears. Too many replacements to fix}, so
+we can plug this in and compute
 \begin{align*}
@@
 The two contributions are bracketed.
-
-Now, this turns out to be slightly inaccurate for $f > 0$ simply because our
-$\mu_{sep}$ approximation is not so accurate for $\eta \gtrsim 0.2$, where the
-top leg is significantly lower than the symmetric $\mu_{sep} = \eta \cos I \pm
-\dots$ would predict. This would mean the two legs don't cancel as exactly, and
-the capture probability increases, which is observed.
 

### 2019-09-05 initial/99_misc/2_rand_plots.py

@@ -1,0 +1,70 @@
+'''
+more random plots
+'''
+import numpy as np
+import scipy.optimize as opt
+
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif', size=12)
+
+def get_etac(I):
+    return (np.sin(I)**(2/3) + np.cos(I)**(2/3))**(-3/2)
+
+def roots(I, eta):
+    ''' returns theta roots from EOM '''
+    eta_c = get_etac(I)
+
+    # function to minimize and derivatives
+    f = lambda q: -eta * np.sin(q - I) + np.sin(q) * np.cos(q)
+    fp = lambda q: -eta * np.cos(q - I) + np.cos(2 * q)
+
+    if eta < eta_c:
+        roots = []
+        inits = [0, np.pi / 2, -np.pi, -np.pi / 2]
+        for qi in inits:
+            roots.append(opt.newton(f, qi, fprime=fp))
+        return np.cos(np.array(roots))
+
+    else:
+        roots = []
+        inits = [np.pi / 2 - I, -np.pi + I]
+        for qi in inits:
+            roots.append(opt.newton(f, qi, fprime=fp))
+        return np.cos(np.array(roots))
+
+def plot_cs(I=np.radians(5)):
+    etac = get_etac(I)
+    eps = 1e-5
+    min_eta, max_eta = etac / 30, etac * 30
+    etas = np.concatenate((
+        np.log(np.linspace(np.exp(min_eta), np.exp(etac - eps), 100)),
+        np.exp(np.linspace(np.log(etac + eps), np.log(max_eta), 100)),
+    ))
+    cs_vals = [[], [], [], []]
+
+    for eta_val in etas:
+        root_vals = roots(I, eta_val)
+        if eta_val > etac:
+            cs_vals[1].append(root_vals[0])
+            cs_vals[2].append(root_vals[1])
+        else:
+            for cs_lst, root_val in zip(cs_vals, root_vals):
+                cs_lst.append(root_val)
+
+    etas_four = etas[np.where(etas < etac)[0]]
+    plt.semilogx(etas_four, cs_vals[0], 'g', label='1')
+    plt.semilogx(etas, cs_vals[1], 'k', label='2')
+    plt.semilogx(etas, cs_vals[2], 'b', label='3')
[…]

### 2019-09-11 initial/notes.tex
stash first attempt overplot anal

@@
 
+We can illustrate the trajectories at $\phi_{2, \epsilon}$ when turning on
+$\epsilon$ by examining \lstinline{99_misc/3_trajs.py}.
+
 \subsection{Dissipating Disk: $\theta_f$ Distribution}
@@
 
-We can investigate two behaviors here then, the range of permitted $\theta_f$ as
-a function of $I$ (when $J_i = A_{crit}$), and the values of $\theta_f$ given
-some initial mutual inclination $\hat{s} \cdot \hat{l}_p$ ($J_i = 2\pi\p*{1 -
-\cos \epsilon}$ where $\epsilon$ is the initial mutual inclination).
+We can investigate the values of $\theta_f$ given some initial mutual
+inclination $\hat{s} \cdot \hat{l}_p$ ($J_i = 2\pi\p*{1 - \cos \epsilon}$ where
+$\epsilon$ is the initial mutual inclination). To do this, we need to understand
+what the possible transitions are. When the separatrix first appears to the
+final state, the transitions are $A_2 \to A_3, A_2 \to A_1, A_3 \to A_1, A_3 \to
+A_2 \to A_1, A_3 \to A_3$. Let's reproduce the analytical forms of these three
+areas below:
+
+%   z0 = eta * np.cos(I)
+%   chi = np.sqrt(-np.tan(q4)**3 / np.tan(I) - 1)
+%   rho = chi * np.sin(q4)**2 * np.cos(q4) / (
+%       chi**2 * np.cos(q4)**2 + 1)
+%   T = 2 * chi * np.cos(q4) / (
+%       chi**2 * np.cos(q4)**2 - 1)
+%   A2 = 8 * rho + 4 * np.arctan(T) - 8 * z0 * np.arctan(1 / chi)
+%   A1 = 2 * np.pi * (1 - z0) - A2 / 2
+%   A3 = 2 * np.pi * (1 + z0) - A2 / 2
+\begin{subequations}\label{se:}
+    \begin{align*}
+        z_0 &= \eta\cos I &
+        \chi &= \sqrt{-\frac{\tan^3\theta_4}{\tan I} - 1},\\
+        \rho &= \chi \frac{\sin^2 \theta_4\cos \theta_4}{
+            \chi^2 \cos^2\theta_4 + 1} &
+        T &= 2\chi \frac{\cos \theta_4}{
+            \chi^2 \cos^2\theta_4 - 1},
+    \end{align*}
+    \begin{align}
+        A_2 &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
+        A_1 &= 2\pi\p*{1 - z_0} - \frac{A_2}{2},\\
+        A_3 &= 2\pi\p*{1 + z_0} - \frac{A_2}{2}.
+    \end{align}
+\end{subequations}
 

### 2019-09-11 initial/2_toy2/3_disk_disp.py

@@ -261,6 +261,8 @@ def sim_for_many(I, eps=-1e-3, eta0_mult=10, etaf=1e-3, n_pts=21, n_dqs=51):
     filename = '3_ensemble_%02d.png' % I_deg
     inits_fn = '3_ensemble_inits%02d.png' % I_deg
     title = r'$I = %d^\circ$' % I_deg
+
+    # run/plot sim
     if not os.path.exists(PKL_FN):
         p = Pool(4)
         args = [(I, eps, eta0_mult, etaf, int(round(n_pt)), dq)
@@ -271,10 +273,32 @@ def sim_for_many(I, eps=-1e-3, eta0_mult=10, etaf=1e-3, n_pts=21, n_dqs=51):
     else:
         with open(PKL_FN, 'rb') as f:
             res_arr = pickle.load(f)
+
+    # first, plot some analytical curves (data overlaid on top)
+    # 4 curves: A2 -> A3, A2 -> A1, A3 -> A2, A3 -> A1
+    j_init = 2 * np.pi * (1 - np.cos(dqs))
+    # TODO use ward's formula instead
+    eta_c = (j_init / 16)**2 / np.sin(I)
+    A3 = 2 * np.pi * (1 + eta_c * np.cos(I)) - j_init / 2
+    # A2 -> A1, A2 -> A3
+    q_f_21 = np.arccos((
+        2 * np.pi * eta_c * np.cos(I) + 8 * np.sqrt(eta_c * np.sin(I))
+    ) / (2 * np.pi))
+    idx_23 = np.where(2 * np.sqrt(eta_c * np.sin(I)) >
+                            np.pi * eta_c * np.cos(I))[0]
+    eta_23 = eta_c[idx_23]
+    q_f_23 = np.arccos((
+        2 * np.pi * eta_23 * np.cos(I) - 8 * np.sqrt(eta_23 * np.sin(I))
+    ) / (2 * np.pi))
+    plt.plot(np.degrees(dqs), np.degrees(q_f_21), 'r')
+    plt.plot(np.degrees(dqs[idx_23]), np.degrees(q_f_23), 'r')
+
+    # plot data
     for dq, final_mus in zip(dqs, res_arr):
         final_q_deg = np.degrees(np.arccos(final_mus))
         plt.scatter(np.full_like(final_mus, np.degrees(dq)),
                     final_q_deg, c='b', s=0.5)
+
     plt.xlabel(r'$\mathrm{d}\theta$')
[…]

### 2019-09-12 initial/notes.tex
writeup WIP

@@
 We can investigate the values of $\theta_f$ given some initial mutual
-inclination $\hat{s} \cdot \hat{l}_p$ ($J_i = 2\pi\p*{1 - \cos \epsilon}$ where
-$\epsilon$ is the initial mutual inclination). To do this, we need to understand
-what the possible transitions are. When the separatrix first appears to the
-final state, the transitions are $A_2 \to A_3, A_2 \to A_1, A_3 \to A_1, A_3 \to
-A_2 \to A_1, A_3 \to A_3$. Let's reproduce the analytical forms of these three
-areas below:
-
-%   z0 = eta * np.cos(I)
-%   chi = np.sqrt(-np.tan(q4)**3 / np.tan(I) - 1)
-%   rho = chi * np.sin(q4)**2 * np.cos(q4) / (
-%       chi**2 * np.cos(q4)**2 + 1)
-%   T = 2 * chi * np.cos(q4) / (
-%       chi**2 * np.cos(q4)**2 - 1)
-%   A2 = 8 * rho + 4 * np.arctan(T) - 8 * z0 * np.arctan(1 / chi)
-%   A1 = 2 * np.pi * (1 - z0) - A2 / 2
-%   A3 = 2 * np.pi * (1 + z0) - A2 / 2
+inclination $\hat{s} \cdot \hat{l}_p \equiv \theta_{sp, i}$ ($J_i = 2\pi\p*{1 -
+\cos \epsilon}$ where $\epsilon$ is the initial mutual inclination). To do this,
+we need to understand what the possible transitions are. When the separatrix
+first appears to the final state, the transitions are $A_2 \to A_3, A_2 \to A_1,
+A_3 \to A_1, A_3 \to A_2 \to A_1, A_3 \to A_3$. Let's reproduce the analytical
+forms of these three areas below:
 \begin{subequations}\label{se:}
@@
 \end{subequations}
+To determine which of the transition histories we fall under (to get an
+analytical prediction for $\cos \theta_f$), we need to determine $\eta_\star$,
+so we know how the enclosed $J$ by the trajectory changes due to separatrix
+encounter. A guess for numerical root-finding can be put together for
+trajectories that encounter from $A_2$ via (inverting the separatrix area
+formula for small $\eta$)
+\begin{equation*}
+    \eta_\star\p*{A_2} = \p*{A_2/16}^2 / \sin I,
+\end{equation*}
+while for trajectories that encounter from $A_3$ we can solve the quadratic $A_3
+= 2\pi \eta \cos I - 8\sqrt{\eta \sin I} = 4\pi - J$ and obtain
+\begin{equation*}
+    \sqrt{\eta_\star} = \frac{4\sqrt{\sin I} + \sqrt{16\sin I + 2\pi \cos I
+        A_3}}{ 2\pi \cos I}.
+\end{equation*}
+This will often run over $\eta_c$, so we guess the smaller of $\eta_\star,
+\eta_c$.
+
+Finally, the $A_3 \to A_2 \to A_1$ pipeline only exists if $ \eta_{A2\max} <
+\eta_\star < \eta_c$, the $\eta$ at which $A_2$ is maximized (this maximization
+behavior is not captured in my linearized formulas, but can be seen in
+\lstinline{99_misc/1_areas.png}). Then, two separatrix crossings occur. Thus, for
+the five possible trajectories, we have the following transitions:
+\begin{itemize}
+    \item $A_2 \to A_3$: This transition happens with probability $\frac{-2\pi
+        \eta_{\star} \cos I + 4\sqrt{\eta_{\star}\sin
+        I}}{8\sqrt{\eta_{\star}\sin I}}$, so for $0 \leq \eta_{\star} \leq
+        \frac{4\sin I}{\pi^2 \cos^2 I}$ this transition is permitted. The
+        approximate $\mu_f$ can be estimated by conservation of adiabatic
+        invariant
+        \begin{align*}
+            \eta_\star &\approx \p*{\frac{2\pi\p*{1 - \cos \theta_{sp,i}}}{
+                        16}}^2 / \sin I&
+                    &\approx \p*{\frac{\pi \theta_{sp, i}^2}{16}}^2/\sin I,\\
+            \mu_{f, 23} &\approx \eta_\star \cos I
+                    - \frac{4\sqrt{\eta_\star \sin I}}{\pi} &
+                &\approx\p*{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
+                    - \frac{\theta_{sp, i}^2}{4}.
+        \end{align*}
+
+    \item $A_2 \to A_1$: This transition happens with probability $\frac{-2\pi
+        \eta_{\star} \cos I + 4\sqrt{\eta_{\star}\sin
+        I}}{8\sqrt{\eta_{\star}\sin I}}$ and can happen so long as $\theta_{sp,
+        i}$ is small enough to fit inside $A_{crit}$ when the separatrix first
+        appears, i.e.\ $2\pi\p*{1 - \cos \theta_{sl, i}} < A_{crit}$ (where
+        $\theta_{sl, i}$ is defined in the $\eta \to \infty$ limit, and since
+        there is no separatrix the enclosed area is conserved as $\eta$
+        approaches $\eta_c$ from above).
+
+        The resulting formulas for $\mu_{f, 21}$ are very similar to those above
+        \begin{align*}
+            \eta_\star &\approx \p*{\frac{2\pi\p*{1 - \cos \theta_{sp,i}}}{
+                        16}}^2 / \sin I&
+                    &\approx \p*{\frac{\pi \theta_{sp, i}^2}{16}}^2/\sin I,\\
+            \mu_{f, 21} &\approx \eta_\star \cos I
+                    + \frac{4\sqrt{\eta_\star \sin I}}{\pi} &
+                &\approx\p*{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
+                    + \frac{\theta_{sp, i}^2}{4}.
+        \end{align*}
+
+    \item $A_3 \to A_3$: This transition occurs if $J_i(\theta_{sl, i}) > 4\pi -
+        A_{3, \min}$. This implies the circulation never undergoes a separatrix
+        encounter at all, so it remains in $A_3$ forever.
+
+    \item $A_3 \to A_1$: This transition occurs when $\theta_{sl, i}$ satisfies
+        $2\pi\p*{1 - \cos \theta_{sl, i}} > A_{crit}$, so the trajectory starts
+        in $A_3$. It then has probability to hop to $A_1$ (TODO).
+
+    \item $A_3 \to A_2 \to A_1$: This transition also occurs when $J_i$ is
+        $> A_{crit}$, but has one further requirement, that $\eta_{\star} >
+        \argmax A_2(\eta)$, such that $A_2$ is expanding during the first
+        separatrix encounter. The bound on this is not exactly analytic though.
+\end{itemize}
 

### 2019-09-12 initial/2_toy2/3_disk_disp.py

@@ -18,6 +18,22 @@ PLOT_DIR = '1plots'
 from utils import to_cart, to_ang, roots, H, solve_ic_base,\
     get_etac
 
+def sep_areas_exact(I, eta):
+    mu4 = eta * np.cos(I) / (1 - eta * np.sin(I))
+    q4 = -np.arccos(mu4)
+
+    # WH2004 eq 11-13
+    z0 = eta * np.cos(I)
+    chi = np.sqrt(-np.tan(q4)**3 / np.tan(I) - 1)
+    rho = chi * np.sin(q4)**2 * np.cos(q4) / (
+        chi**2 * np.cos(q4)**2 + 1)
+    T = 2 * chi * np.cos(q4) / (
+        chi**2 * np.cos(q4)**2 - 1)
+    A2 = 8 * rho + 4 * np.arctan(T) - 8 * z0 * np.arctan(1 / chi)
+    A1 = 2 * np.pi * (1 - z0) - A2 / 2
+    A3 = 2 * np.pi * (1 + z0) - A2 / 2
+    return A1, A2, A3
+
 def plot_traj_colors(I, ret, filename):
     ''' scatter plot of (phi, mu) w/ colored time '''
     fix, ax1 = plt.subplots(1, 1)
@@ -54,7 +70,8 @@ def get_t_vals(t_i, t_f, int_n_pts=401):
 
 def get_areas_2(ret):
     '''
-    not get_areas in utils since this that assumes start -> ejection from sep
+    not get_areas in utils since this that assumes start -> ejection from sep,
+    but really assumes a very full featured trajectory
     '''
     t_events = ret.t_events[-1]
     x_events, _, z_events, eta_events = ret.sol(t_events)
@@ -84,21 +101,23 @@ def get_areas_2(ret):
             dphi = np.gradient(np.unwrap(phi))
             areas.append(np.sum((1 - np.cos(q)) * dphi))
     # truncate list of times during initial circulation
+    t_end_circ = t_areas[-1]
+    if t_end_circ > t_0[-1]: # pure circulating traj?
+        return np.inf, np.array(t_areas), np.array(areas)
     if len(areas):
-        t_end_circ = t_areas[-1]
         t_0 = t_0[np.where(t_0 > t_end_circ)[0][0]: ]
         t_pi = t_pi[np.where(t_pi > t_end_circ)[0][0]: ]
     # now solve librating period
     t_end_lib = max(t_pi) if len(t_0) == 0 else t_0[0]
[…]

### 2019-09-17 writeups/Su_disk_disp.tex
outlineish

    \documentclass[
        fleqn,
        usenatbib,
    ]{mnras}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        ae, aecompl,
        graphicx,
        booktabs,
    }
    \usepackage[T1]{fontenc}
    \usepackage[
        labelfont=bf, % caption names are labeled in bold
        font=scriptsize % smaller font for captions
    ]{caption}
    \usepackage[font=scriptsize]{subcaption} % subfigures
    \captionsetup{compatibility=false}

    \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
    \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
    \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
    \newcommand*{\at}[1]{\left.#1\right|}
    \newcommand*{\abs}[1]{\left|#1\right|}
    \newcommand*{\ev}[1]{\langle#1\rangle}
    \newcommand*{\p}[1]{\left(#1\right)}
    \newcommand*{\s}[1]{\left[#1\right]}
    \newcommand*{\z}[1]{\left\{#1\right\}}
    \DeclareMathOperator*{\argmin}{argmin}
    \DeclareMathOperator*{\argmax}{argmax}
    \DeclareMathOperator*{\med}{med}

\title[Cassini State Capture]{Cassini State Capture}
\author[Y. Su et\ al.]{
Yubo Su$^1$,
Dong Lai$^1$
\\
$^1$ Cornell Center for Astrophysics and Planetary Science, Department of
Astronomy, Cornell University, Ithaca, NY 14853, USA
}

\date{Accepted XXX\@. Received YYY\@; in original form ZZZ}

\pubyear{2019}

\begin{document}\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\renewcommand*{\sectionautorefname}{Section}
\maketitle

\begin{abstract}
    Abstract
\end{abstract}

\begin{keywords}
planet--star interactions % chktex 8
\end{keywords}

\section{Introduction}

\section{Equations}\label{s:eq}

Denote $\vec{S}$ spin of planet, $\vec{l}$ angular momentum of planet, and
$\vec{l}_d$ angular momentum of the surrounding disc. We approximate $S \ll L
\ll L_d$, so $\vec{l}_d$ is approximately constant. Much of this treatment
borrows from \citep{anderson2018teeter}. We consider equations in the corotating
frame
\begin{align}
    \rd{\hat{s}}{t} &= \omega_{sl} \p{\hat{s} \cdot \hat{l}_d}
        \p{\hat{s} \times \hat{l}_d},\\
    \rd{\hat{l}}{t} &= \omega_{ld}\p{\hat{l} \cdot \hat{l}_d}
        \p{\hat{l} \times \hat{l}_d},\\
    \omega_{sl} &= \frac{3k_q}{2k}\p{\frac{R_1}{a_1}}^3S,\\
    \omega_{ld} &= \dots.
\end{align}
(TODO get $\omega_{ld}$ from Millhollard \& Batygin).

We go to the corotating frame with $\vec{l}$ such that it is also fixed in time.
The evolution of $\hat{s}$ in this corotating frame is governed by:
\begin{equation}
    \rd{\hat{s}}{t} = \alpha \p{\hat{s} \cdot \hat{l}}
            \p{\hat{s} \times \hat{l}}
        - \abs{g}\p{\hat{s} \times \hat{l}_d}.
        \label{eq:dsdt_base}
\end{equation}
$\alpha = \omega_{sd} > 0, g \equiv -\omega_{ld}< 0$ follow traditional sign
conventions.

We divide through by $\alpha$ and define parameter $\eta$ and nondimensionalized
time $\tau$
\begin{align}
    \eta &\equiv \frac{\abs{g}}{\alpha}\label{eq:eta},\\
    \tau &\equiv \alpha t.
\end{align}

Following~\cite{millholland_disk}, we allow $g$ to vary in time owing to a
disk with decaying mass
\begin{equation}
    M_d(t) = M_d(0)e^{-t/t_d}.
\end{equation}
As $\alpha$ is held constant, this equates to $\eta$ decaying as $\rd{\eta}{t} =
-\frac{\eta}{t_d}$ for some decay time $t_\eta$. We nondimensionalize by
defining $\epsilon \equiv \frac{1}{\alpha t_\eta}$, so
\begin{equation}
    \rd{\eta}{\tau} = -\epsilon \eta.
\end{equation}

\subsection{Cassini States}\label{ss:cs}

The Cassini state Hamiltonian in the frame corotating with $\hat{l}_d$ about
$\hat{l}$ is:
\begin{equation}
    H = -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
        + \eta \p{\hat{s} \cdot \hat{l}_d}.
\end{equation}

Spin states satisfying $\rd{\hat{s}}{t} = 0$ are referred to as \emph{Cassini
States} (CS). When $\eta < \eta_c$, there are four CSs, and when $\eta > \eta_c$
there are only two; $\eta_c$ is \citep{henrard1987,ward2004I}
\begin{equation}
    \eta_c \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{3/2}.
\end{equation}
CSs 1, 2, 3 are stable while CS4 is unstable. A contour plot of $H\p{\phi, \cos
\theta}$ is
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/0_eta/1contours_flip.png}
    \caption{Contour plot of $H\p{\phi, \cos \theta}$. Black dotted line is the
    separatrix, which only exists for $\eta < \eta_c$.}\label{fig:eq_1contours}
\end{figure}

\subsection{Separatrix}

In the four-CS regime, one of the CSs is a saddle point, conventionally denoted
Cassini State 4 (CS4). All trajectories are periodic with finite period except
two critical trajectories asymptotic in the past and future to CS4. Together,
these two critical trajectories are referred to as the \emph{separatrix} and
divide phase space into three zones. We use notation described in
\autoref{fig:eq_3zones}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/1_weaktide/3zones.png}
    \caption{Nomenclature of the two legs of the separatrix $\mathcal{C}_{\pm}$
    and three zones of the domain. For both $\mathcal{C}_{\pm}$, we will take
    the positive direction to be anti-clockwise.}\label{fig:eq_3zones}
\end{figure}

The area enclosed by the separatrix is known exactly in literature
\citep{henrard1987,ward2004I}:
\begin{subequations}\label{se:area_ward}
    \begin{align*}
        z_0 &= \eta\cos I &
        \chi &= \sqrt{-\frac{\tan^3\theta_4}{\tan I} - 1},\\
        \rho &= \chi \frac{\sin^2 \theta_4\cos \theta_4}{
            \chi^2 \cos^2\theta_4 + 1} &
        T &= 2\chi \frac{\cos \theta_4}{
            \chi^2 \cos^2\theta_4 - 1},
    \end{align*}
    \begin{align}
        A_2 &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
        A_1 &= 2\pi\p{1 - z_0} - \frac{A_2}{2},\\
        A_3 &= 2\pi\p{1 + z_0} - \frac{A_2}{2}.
    \end{align}
\end{subequations}
These are plotted as a function of $\eta$ in \autoref{fig:eq_areas}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/99_misc/1_areas.png}
    \caption{Plot of $A_{i}(\eta)$ as given by \autoref{se:area_ward}. Dotted
    lines correspond to small $\eta$ approximations discussed in
    \autoref{ss:app_transition}.}\label{fig:eq_areas}
\end{figure}

\section{Adiabatic Evolution}\label{s:ad}

In the truly adiabatic limit, $\epsilon \to 0$; we use $\epsilon =
3 \times 10^{-4}$ in \autoref{ss:ad_fid} and vary $\epsilon$ in
\autoref{ss:ad_ensemble}. The adiabatic limit is quantified
in~\cite{millholland_disk} to be
\begin{equation}
    \dot{\eta} \lesssim \dots \label{eq:ad_constr}
\end{equation}

\subsection{Individual Simulations}\label{ss:ad_fid}

In the limit $\eta \to 0$, all trajectories circulate with constant
\begin{equation}
    \theta_{sl,f} \equiv \s{\arccos \hat{s} \cdot \hat{l}}_{\eta \to 0}.
\end{equation}
We run simulations that terminate at $\eta = 10^{-5}$ and measure
$\theta_{sl,f}$. We vary the initial
\begin{equation}
    \theta_{sd, i} \equiv \s{\arccos \hat{s} \cdot \hat{l}_d}_{t=0}.
\end{equation}
While complex at first sight, the outcomes of evolutionary
trajectories are only complicated by interactions with the separatrix (as phase
space area is conserved otherwise). Adopting the labels in
\autoref{fig:eq_3zones}, the five dynamical histories we observe in simulations
are described by their transitions between regions of phase space:
\begin{itemize}
    \item $A_2 \to A_1$ --- \autoref{fig:ad_21}.
    \item $A_2 \to A_3$ --- \autoref{fig:ad_23}.
    \item $A_3 \to A_1$ --- \autoref{fig:ad_31}.
    \item $A_3 \to A_2 \to A_1$ --- \autoref{fig:ad_321}.
    \item $A_3 \to A_3$ --- Trivial case, the initial enclosed area is too large
        to ever experience a separatrix encounter.
\end{itemize}

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo21.png}
        \caption{Top: Plot of $\cos \theta(t)$ (grey) over an example
        simulation. Overlaid are the locations of Cassini State 2 (blue), upper
        and lower bounds on the separatrix (dashed green), and value of
        $\theta_{sl,f}$ predicted in the adiabatic limit (horizontal red line).
        Bottom: Plot of the enclosed separatrix area obtained by integrating the
        simulated trajectory (blue dots) and fully adiabitic theory (red line).
        A small blip in the data area arises when the integration area crosses
        the coordinate singularity at the pole. Vertical red magenta lines
        denote the four snapshots depicted below; they correspond to the start
        of the simulation, the appearance of the separatrix, the separatrix
        encounter and the end of the simulation.}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo21_subplots.png}
        \caption{Snapshots in the $\p{\cos \theta, \phi}$ space of the
        simulation trajectories for two circulation/libration cycles around the
        $\eta$ values depicted above. Cycles are defined by the range of
        integration used to compute enclosed phase space area. Black dots denote
        the cycle immediately before the selected $\eta$ value, magenta dots the
        cycle immediately after, and grey denotes intermediate points that do
        not constitute a full cycle. Also labeled are the separatrix (green) and
        Cassini State 2 (blue).}
    \end{subfigure}
    \caption{Fiducial simulation following the $A_2 \to A_1$
    transition.}\label{fig:ad_21}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23_subplots.png}
    \end{subfigure}
    \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ history.
    }\label{fig:ad_23}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31_subplots.png}
    \end{subfigure}
    \caption{Same as \autoref{fig:ad_21} but for the $A_3 \to A_1$ history. TODO
    finish final areas plot.}\label{fig:ad_31}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321_subplots.png}
    \end{subfigure}
    \caption{Same as \autoref{fig:ad_21} but for the $A_3 \to A_2 \to A_1$
    history. The second snapshot, instead of depicting the appearance of the
    separatrix, captures the first of the two separatrix crossings. TODO finish
    final areas plot.}\label{fig:ad_321}
\end{figure}

\subsection{Dynamical Outcomes}\label{ss:ad_ensemble}

In the adiabatic limit, while separatrix encounters induce discontinuous changes
in enclosed phase space, the outcomes of these encounters are well understood in
pioneering work by Henrard \citep{henrard1982,henrard1987}. For a wide range of
$\theta_{sd, i}$, we run simulations over a ring of initial conditions at each
$\theta_{sd, i}$ and measure the final $\theta_{sl, f}$ values. We can also
predict the values of $\theta_{sl, f}$ for each of the dynamical histories as
well as their associated probabilities; refer to \autoref{ss:app_transition} for
details.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_35.png}
    \caption{Top: $\theta_{sl,f}\p{\theta_{sd, i}}$, overlaid with semi-analytic
    predictions of the $\theta_{sl, f}$ for each of the four nontrivial
    dynamical histories in colored lines. Bottom: Semi-analytic probabilities of
    each of the dynamical histories for each $\theta_{sd,
    i}$.}\label{fig:ad_ensemble}
\end{figure}

\section{Nonadiabatic Evolution}\label{s:nonad}

Here, we consider $\epsilon$ sufficiently large to violate the adiabiticity
constraint \autoref{eq:ad_constr}.

\subsection{Sample Trajectory}

A sample trajectory following in the style of \autoref{fig:ad_21} but for
$\epsilon = 0.1$ is provided in \autoref{fig:nonad_traj}.
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo_nonad.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo_nonad_subplots.png}
    \end{subfigure}
    \caption{Same as \autoref{fig:nonad_traj} but for a non-adiabatic $\epsilon =
    0.1$.}\label{fig:nonad_traj}
\end{figure}

\subsection{Dynamical Outcomes}

A formula for $\theta_{sl,f}$ assuming $\theta_{sd, i} = 0$ initially can be
given:
\begin{equation}
    \theta_{sl,f}\p{\theta_{sd, i} = 0} = \sqrt{\frac{2\pi \Omega}{\epsilon}}
        \tan I.\label{eq:nonad_q_f}
\end{equation}
We can naively generalize this by recognizing that any nonzero $\theta_{sd, i}$
manifests as obliquity variations as $\hat{s}$ librates about $\hat{l}_d$, and
these oscillations are ``frozen in'' when the disk dissipates. Thus,
\begin{equation}
    \theta_{sl,f}\p{\theta_{sd, i}} \in \sqrt{\frac{2\pi \Omega}{\epsilon}}
        \tan I \pm \theta_{sd, i}.\label{eq:nonad_q_f_dist}
\end{equation}

We present the results of simulations for using $\epsilon = 0.3$ in
\autoref{fig:nonad_3_ensemeble}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_05.png}
    \caption{$\theta_{sl, f}\p{\theta_{sd, i}}$ at $\epsilon = 0.3$, firmly in
    the non-adiabatic regime. Note the clear double-valuedeness has disappeared,
    as have distinct dynamical histories. The red dotted line presents the
    analytical prediction given by
    \autoref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemeble}
\end{figure}

\subsection{Transition from Adiabaticity}

The agreement of \autoref{eq:nonad_q_f} at fixed $I$ for varying $\epsilon$ is
shown in \autoref{fig:nonad_3_scan}. Note that $\epsilon \to 0$ recovers the
adiabatic regime.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/2_toy2/3scan.png}
    \caption{Plot of $\theta_{sl, f}\p{\theta_{sd, i} = 0}$ as a function of
    $\epsilon$, where $I = 5^\circ$. Overplotted in the red line is
    \autoref{eq:nonad_q_f}, which is in good agreement for $\epsilon \gtrsim
    0.1$ the non-adiabatic regime, while $\theta_{sl, f} \approx 90^\circ$ in
    the adiabatic regime.}\label{fig:nonad_3_scan}
\end{figure}

An example of an intermediate value $\epsilon = 10^{-2}$ between
\autoref{fig:ad_ensemble} and \autoref{fig:nonad_3_ensemeble} is shown in
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_20.png}
    \caption{Intermediate $\epsilon$ used in between those of
    \autoref{fig:ad_ensemble} and \autoref{fig:nonad_3_ensemeble}. Noticeable
    ``freezing-in'' of the obliquity variations over libration cycles is still
    visible, but the shapes of the adiabatic dynamical trajectories are
    beginning to appear.}\label{fig:nonad_3_ensemble_20}
\end{figure}

TODO compare to \autoref{eq:ad_constr}.

\bibliographystyle{mnras}
\bibliography{Su_sep_cross}

% \clearpage
% \onecolumn
\appendix

\section{Variation with $I$}

Plots of \autoref{fig:ad_ensemble} but for $I = 10^\circ, I=20^\circ$.

\section{Calculation of Transition Probabilities}\label{ss:app_transition}

Semi-analytic calculation probabilities, including naive line.

\label{lastpage} % chktex 24
\end{document}

### 2019-09-19 initial/notes.tex
Finalized plotting for now
0919 draft meeting w/ dong, wrote out adiabiticity constraint

@@
 
+\section{Non-adiabatic Regime}
+
+\subsection{Decaying Disk: Dong Notes}
+
+In the non-adiabatic regime, the Hamiltonian is much less useful, so we return
+to EOM in corotating frame (after dividing through by $\Omega_{sl}$ compared to
+Dong's notes)
+\begin{equation}
+    \rd{\hat{s}}{t} = \p*{\hat{s} \cdot \hat{l}}\p*{\hat{s} \times \hat{l}}
+        + \eta \cos I \p*{\hat{l}_d \times \hat{s}}.
+\end{equation}
+We adopt convention where $\Omega_{sl}, \Omega_{lp} > 0, \eta =
+\frac{\Omega_{ld}\cos I}{\Omega_{sl}}$, and time units are really $t \equiv
+\Omega_{sl}t$. In this decaying disk problem, $\eta\p*{-\infty} \gg 1,
+\eta\p*{+\infty} \ll 1$.
+
+Define again $\hat{l} = \hat{z}, \hat{l}_d = \hat{z} \cos I + \hat{x}\sin I$,
+then we go immediately into coordinates
+\begin{equation}
+    \rd{\hat{s}}{t} = \s*{
+        \p*{\eta \cos I - 1}\hat{z} + \eta \sin I \hat{x}} \times \hat{s}.
+\end{equation}
+
+Now, let's assume that $s_z \approx 1$ throughout the evolution of $\hat{s}$
+(maybe this can be relaxed later), which also requires $I \approx 0$. Then let's
+examine the evolution of quantity $S = s_x + is_y$ instead:
+\begin{equation}
+    \rd{S}{t} = i\p*{\eta\cos I - 1}S - i \eta \sin I.\label{eq:nonad_ode}
+\end{equation}
+Now this is a first-order ODE in $S$, albeit complex, which can be solved via
+an integrating factor
+\begin{align}
+    \Phi(t) &\equiv \int_{-\infty}^t \p*{1 - \eta(t') \cos I}
+        \mathrm{d}t',\\
+    \at{S(t) e^{i\Phi(t)}}_{-\infty}^t
+        &= \int\limits_{-\infty}^t e^{i\Phi(t')}
+            \p*{-i\eta(t')\sin I}\;\mathrm{d}t'\label{eq:nonad_int}
+\end{align}
+We now invoke stationary phase, asserting that $e^{i\Phi(t)}$ is dominated by
+its contribution where $\dot{\Phi} = 0$ (the phases add constructively). But
+$\dot{\Phi} = 0$ is where $1 - \eta\cos I = 0$, or where $\eta\cos I = 1$.
+
+Now at this point, let's choose $\eta(0) = 1/\cos I, \at{\rd{\eta}{t}}_{t=0} =
+-\epsilon/\cos I$. Then we expand near $t = 0$ so
+\begin{align*}
+    \Phi(t) &\approx \Phi(0) + \frac{1}{2}\ddot{\Phi}t^2,\\
+        &\approx \Phi(0) + \frac{1}{2}\epsilon t^2,\\
+    \int\limits_{-\infty}^t e^{i\Phi(t')}\eta(t')\;\mathrm{d}t'
+        &\approx
+        \begin{cases}
+            0 & t < 0,\\
+            \frac{1}{\cos I}e^{i\Phi(0)}\int\limits_{-\infty}^\infty
+                \exp\s*{\frac{i}{2}\epsilon t^2}\;\mathrm{d}t
+                & t > 0.
+        \end{cases}\\
+    \int\limits_{-\infty}^\infty
+                \exp\s*{\frac{i}{2}\epsilon t^2}\;\mathrm{d}t
+        &= \int\limits_{-\infty}^\infty e^{-\tau^2}\;\mathrm{d}\tau
+            \sqrt{\frac{2}{i\epsilon}},\\
+        &= \sqrt{\frac{2\pi}{i\epsilon}}.
+\end{align*}
+
+Now, it should be noted that $e^{i\Phi}$ is just a phase; all we really care
+about is $\abs*{S} = \sqrt{1 - s_z^2}$. Thus, taking the absolute value of both
+sides of \autoref{eq:nonad_int} we obtain
+\begin{align}
+    \abs*{S}(t) &= \tan I\sqrt{\frac{2\pi}{\epsilon}}\Theta(t).
+        \label{eq:nonad_dong}
+\end{align}
+It should be noted that $\theta_{sl, f} \approx \abs*{S}(\infty)$, and so we
+recover Dong's result $\theta_f = \sqrt{2\pi/\epsilon}\tan I$.
+
+To compare to data, let's define a few more things: $\theta_{sl, f} = \hat{s}
+\cdot \hat{l}(t \to \infty)$ and $\theta_{sd, i} = \hat{s} \cdot \hat{l}_d(t \to
+-\infty)$ (note that $I \equiv \theta_{ld}$ is constant). In our derivation
+above, we've sort of assumed $I \approx 0$, so $\theta_{sd, i} \approx
+\theta_{sl, i} = 0$ is the effective initial condition above.
+
+Then, for some $\theta_{sd, i} > 0$, we can intuit as follows: $\hat{s}$
+initially librates around $\hat{l}_d$ with oscillation amplitude $\theta_{sd,
+i}$. So if $\theta_{sd, i} = 0$ produces \autoref{eq:nonad_dong}, we might
+expect small deviations of amplitude $\theta_{sd, i}$ about CS2 to be ``frozen
+in'' as the disk dissipates non-adiabatically. Thus, $\theta_{sl, f} \in
+\theta_{sl, f, 0} + \s*{\pm \theta_{sd, i}}$.
+
+More importantly though, we want to find leading order corrections to the above
+result for: nonzero $I$, and somewhat smaller $\epsilon$. The problems with
+Dong's result can be seen in the two figures in \autoref{fig:nonad_scan}, which
+are derived for $\theta_{sd, i} \approx 0$. In this limit, $\theta_{sl, i} = I$,
+which explains why the predictions break down somewhat when $I$ is no longer
+small. Furthermore, for smaller $\epsilon$, the stationary phase approximation
+breaks down. We investigate the effect of these below.
+\begin{figure}[t]
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{2_toy2/3scan.png}
+    \end{subfigure}
+
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{2_toy2/3scan_20.png}
+    \end{subfigure}
+    \caption{$I = 5^\circ, 20^\circ$ distributions vs data. Red lines are the
+    result of Dong's calculation, blue are with my
+    improvements.}\label{fig:nonad_scan}
+\end{figure}
+
+\subsection{Extending Dong's result}
+
+Perhaps the easiest correction to make is, instead of assuming $s_z = 1$, to
+hold it constant at $s_z \approx \cos I$, which just changes the inhomogeneous
+term in \autoref{eq:nonad_ode} to $\p*{-i\eta \sin I \cos I}$; this is a very
+small change since $\cos I \approx 1$ for nearly all physical parameter space,
+but does improve the fit slightly.
+
+One other observation is that the LHS of \autoref{eq:nonad_int} should really be
+$\abs*{S\p*{t}e^{i\Phi(t)} - S\p*{-\infty}e^{i\Phi(-\infty)}}$, but we don't
+really know $e^{i\Phi}$ since it oscillates so quickly. Thus, only when $S\p*{t}
+\gg S\p*{-\infty}$ or $\theta_{sl, f} \gg I$ is the LHS easily evaluated. But at
+the very least we can claim that $\theta_{sl, f} = \max\p*{\abs*{S}, I}$, so
+that at very small $\abs*{S}$ we just use $I$ the approximate location of CS2.
+This seems to be in pretty good agreement if we look at
+\lstinline{2_toy2/3Iscan} plots.
+
+Somewhat surprisingly, using a proper $\theta_{sl, f} = \arccos 1 - S^2$
+actually hurts the fit; this would manifest in the larger $\theta_{sl, f}$
+regime, so it appears increasing adiabiticity dominates this correction.
+
+The other correction to consider is how the nonadiabatic assumption breaks down.
+In the stationary phase integral, we assumed that the phase could be integrated
+as an imaginary Gaussian.
+
+\textbf{Take 1 (fail):} This is only true if the in the
+vicinity of the minimum, $\Phi(t)$ is approximately symmetric. The ``vicinity''
+here is defined as where $\Phi(t) \lesssim \Phi_{\min} + 2\pi$, since that is
+where the phase begins to oscillate quickly again. To simplify, we can write
+$\eta = e^{-\epsilon t}/\cos I$, then we can integrate analytically:
+\begin{equation}
+    \Phi(t) = t + \frac{e^{-\epsilon t}}{\epsilon}
+        \approx \frac{1}{\epsilon} + t - te^{-\epsilon t} + \mathcal{O}(t^2).
+\end{equation}
+can be written down analytically, we can examine how symmetric $\Phi$ is about
+its minimum. It turns out though that $\Phi$ is actually \emph{more} symmetric
+for smaller $\epsilon$, so stationary phase should work \emph{better}. Hm.
+Similar arguments can be constructed for $\Phi$ being symmetric about $\pm
+\sigma \sim 1/\sqrt{\epsilon}$, or for the variation of $\eta$ across $t \in \pm
+1/\sqrt{\epsilon}$, but they all seem to favor smaller $\epsilon$ being more
+accurate.
+
+\textbf{Millholland Non-Adiabiticity:} The criterion for adiabiticity presented
+in Millholland \& Batygin \emph{Primordial Obliquities} is (their Equation 15)
+\begin{equation}
+    \dot{\alpha} - \dot{g} \lesssim \alpha g \sin \theta \sin I.
+\end{equation}
+Noting $\dot{\eta} = \p*{\frac{\dot{g}}{g} - \frac{\dot{\alpha}}{\alpha}}\eta$,
+where $\eta = \frac{g\cos I}{\alpha}$ ($g, \alpha$ follow their definitions),
+and that at crossing they define $g \approx \alpha$, then
+\begin{align*}
+    \frac{\dot{\alpha}}{\alpha} - \frac{\dot{g}}{g}
+        &\lesssim g\sin\theta\sin I,\\
+    -\s*{\frac{\dot{\alpha}}{\alpha} - \frac{\dot{g}}{g}}\cos I = \dot{\eta}
+        = -\epsilon \alpha \eta &\gtrsim -g\sin\theta\sin I\cos I,\\
+    \epsilon &\lesssim \frac{\sin \theta \sin I \cos I}{\eta}
+        \approx \sin\theta \sin I.
+\end{align*}
+This is overplotted in the vertical blue line in \autoref{fig:nonad_scan}.
+
 \section{Misc}
@@
 forms of these three areas below:
-\begin{subequations}\label{se:}
+\begin{subequations}
     \begin{align*}

### 2019-09-19 initial/2_toy2/3_disk_disp.py

@@ -44,11 +44,16 @@ def d_sep_areas(I, eta):
 
 def plot_traj_colors(I, ret, filename):
     ''' scatter plot of (phi, mu) w/ colored time '''
-    fix, ax1 = plt.subplots(1, 1)
-    mu_lim = 0.6
-    first_idx = np.where(abs(np.cos(q)) < mu_lim)[0][0]
+    fig, ax1 = plt.subplots(1, 1)
+    t = ret.t
+    etas = ret.y[3]
+    q, phi = to_ang(*ret.y[ :3])
+    # mu_lim = 0.6
+    # first_idx = np.where(abs(np.cos(q)) < mu_lim)[0][0]
+    first_idx = 0
     scat = ax1.scatter(phi[first_idx: ], np.cos(q[first_idx: ]),
                        c=t[first_idx: ], s=0.3, cmap='Spectral')
+    ylims = ax1.get_ylim()
     fig.colorbar(scat, ax=ax1)
     ax1.set_xlabel(r'$\phi$')
     ax1.set_xlim([0, 2 * np.pi])
@@ -63,6 +68,7 @@ def plot_traj_colors(I, ret, filename):
     ax1.plot(phi_arr, z4 + sep_diff, 'k', label='Final Sep')
     ax1.plot(phi_arr, z4 - sep_diff, 'k')
     ax1.legend()
+    ax1.set_ylim(ylims)
     plt.savefig(filename, dpi=dpi)
     print('Saved', filename)
     plt.clf()
@@ -638,17 +644,17 @@ def sim_for_many(I, eps=-1e-3, eta0_mult=10, etaf=1e-3, n_pts=21, n_dqs=51,
     # plt.savefig(inits_fn, dpi=dpi)
     # plt.clf()
 
-def eps_scan(I, filename='3scan', dq=0.01, n_pts=151, n_pts_ring=13,
+def eps_scan(I, filename='3scan', dq=0.01, n_pts=151, n_pts_ring=21,
              eps_min=1e-2, eps_max=0.5):
     '''
     scan for theta_sl,f for small dq @ various epsilons
     '''
     eta0 = 10 * get_etac(I)
     q2, _ = roots(I, eta0)
-    y0s = fetch_ring(I, eta0, dq, n_pts)
+    y0s = fetch_ring(I, eta0, dq, n_pts_ring)
     pts = []
+    eps_vals = np.exp(np.linspace(np.log(eps_max), np.log(eps_min), n_pts))
     for y0 in y0s.T:
[…]

### 2019-09-30 writeups/Su_disk_disp.tex
stash, bunch of new plots

@@
 \end{equation}
-$\alpha = \omega_{sd} > 0, g \equiv -\omega_{ld}< 0$ follow traditional sign
-conventions.
+$\alpha = \omega_{sd} > 0, g \equiv -\omega_{ld}\cos I < 0$ follow traditional
+sign conventions.
 
@@
 
+The locations of the $\cos\theta$ of the two/four CSs as a function of $\eta$ is
+provided in
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs.png}
+    \caption{Locations of the Cassini states over time, following the same
+    coloring scheme as \autoref{fig:eq_1contours}.}\label{fig:cs_locs}
+\end{figure}
+
 \subsection{Separatrix}
@@
 divide phase space into three zones. We use notation described in
-\autoref{fig:eq_3zones}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/3zones.png}
-    \caption{Nomenclature of the two legs of the separatrix $\mathcal{C}_{\pm}$
-    and three zones of the domain. For both $\mathcal{C}_{\pm}$, we will take
-    the positive direction to be anti-clockwise.}\label{fig:eq_3zones}
-\end{figure}
+\autoref{fig:eq_1contours}.
 
-The area enclosed by the separatrix is known exactly in literature
+The unsigned area enclosed by the separatrix is known exactly in literature
 \citep{henrard1987,ward2004I}:
 \begin{subequations}\label{se:area_ward}
-    \begin{align*}
-        z_0 &= \eta\cos I &
-        \chi &= \sqrt{-\frac{\tan^3\theta_4}{\tan I} - 1},\\
+    \begin{align}
+        z_0 &= \eta\cos I,\nonumber\\
+        \chi &= \sqrt{-\frac{\tan^3\theta_4}{\tan I} - 1},\nonumber\\
         \rho &= \chi \frac{\sin^2 \theta_4\cos \theta_4}{
-            \chi^2 \cos^2\theta_4 + 1} &
+            \chi^2 \cos^2\theta_4 + 1},\nonumber\\
         T &= 2\chi \frac{\cos \theta_4}{
-            \chi^2 \cos^2\theta_4 - 1},
-    \end{align*}
-    \begin{align}
-        A_2 &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
-        A_1 &= 2\pi\p{1 - z_0} - \frac{A_2}{2},\\
-        A_3 &= 2\pi\p{1 + z_0} - \frac{A_2}{2}.
+            \chi^2 \cos^2\theta_4 - 1},\nonumber\\
+        A_{II} &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
+        A_I &= 2\pi\p{1 - z_0} - \frac{A_2}{2},\\
+        A_{III} &= 2\pi\p{1 + z_0} - \frac{A_2}{2}.
     \end{align}
@@
 \begin{equation}
-    \theta_{sl,f} \equiv \s{\arccos \hat{s} \cdot \hat{l}}_{\eta \to 0}.
+    \theta_{f} \equiv \s{\arccos \hat{s} \cdot \hat{l}}_{\eta \to 0}.
 \end{equation}
 We run simulations that terminate at $\eta = 10^{-5}$ and measure
-$\theta_{sl,f}$. We vary the initial
+$\theta_{f}$. We vary the initial
 \begin{equation}
@@
 \end{equation}
-While complex at first sight, the outcomes of evolutionary
-trajectories are only complicated by interactions with the separatrix (as phase
-space area is conserved otherwise). Adopting the labels in
-\autoref{fig:eq_3zones}, the five dynamical histories we observe in simulations
-are described by their transitions between regions of phase space:
-\begin{itemize}
-    \item $A_2 \to A_1$ --- \autoref{fig:ad_21}.
-    \item $A_2 \to A_3$ --- \autoref{fig:ad_23}.
-    \item $A_3 \to A_1$ --- \autoref{fig:ad_31}.
-    \item $A_3 \to A_2 \to A_1$ --- \autoref{fig:ad_321}.
-    \item $A_3 \to A_3$ --- Trivial case, the initial enclosed area is too large
-        to ever experience a separatrix encounter.
-\end{itemize}
 
+Initially, in the $\eta > \eta_c$ regime, only zones $II, III$ exist.
+Conversely, at the end of the simulation when $\eta \to 0$, only zones $I, III$
+exist. Naively then, one might expect four sequences of transitions
+between zones (``zone transition histories'') to appear during simulations: (i)
+$II \to I$, (ii) $II \to III$, (iii) $III \to I$, and (iv) the trivial $III \to
+III$ where the trajectory never encounters the separatrix. In fact, (v) a fifth
+possible history involving two transitions is observed $III \to II \to I$.
+
+Between zone transitions, the adiabatic invariant $J \equiv \oint \cos\theta
+\;\mathrm{d}\phi$ is conserved. Here, we adopt convention $J$ is a \emph{signed}
+area
+\begin{equation}
+    J = \oint \p{1 - \cos \theta}\;\mathrm{d}\phi.
+\end{equation}
+This has the advantage of (i) having a removable singularity when the trajectory
+crosses $\cos \theta = 1$, and (ii) being easily expressible as combinations of
+the $A_i$ of \autoref{se:area_ward} without $2\pi$ offsets.
+
+Given this definition, the change in $J$ during a separatrix encounter is easily
+understood \citep{henrard1982}. We present in \autoref{fig:ad_21} a fiducial
+simulaiton undergoing the $II \to I$ zone transition. An initial condition in
+zone II with initial adiabatic invariant $J_i > 0$ librates about CS2 until
+$A_{II} = J_i$. At this point, it encounters the separatrix and moves into zone I
+with $J_f = -A_I$. Further simulations illustrating the other zone transition
+histories are depicted in \autoref{s:app_histories}.
 \begin{figure}
@@
         and lower bounds on the separatrix (dashed green), and value of
-        $\theta_{sl,f}$ predicted in the adiabatic limit (horizontal red line).
+        $\theta_{f}$ predicted in the adiabatic limit (horizontal red line).
         Bottom: Plot of the enclosed separatrix area obtained by integrating the
@@
 \end{figure}
+
+\subsection{Dynamical Outcomes}\label{ss:ad_ensemble}
+
+In the adiabatic limit, while separatrix encounters induce discontinuous changes
+in enclosed phase space, the outcomes of these encounters are well understood in
+pioneering work by Henrard \citep{henrard1982,henrard1987}. For a wide range of
+$\theta_{sd, i}$, we run simulations over a ring of initial conditions at each
+$\theta_{sd, i}$ and measure the final $\theta_{ f}$ values. We can also
+predict the values of $\theta_{ f}$ for each of the dynamical histories as
+well as their associated probabilities; refer to \autoref{ss:app_transition} for
+details.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_35.png}
+    \caption{Top: $\theta_{f}\p{\theta_{sd, i}}$, overlaid with semi-analytic
+    predictions of the $\theta_{ f}$ for each of the four nontrivial
+    dynamical histories in colored lines. Bottom: Semi-analytic probabilities of
+    each of the dynamical histories for each $\theta_{sd,
+    i}$.}\label{fig:ad_ensemble}
+\end{figure}
+
+\section{Nonadiabatic Evolution}\label{s:nonad}
+
+Here, we consider $\epsilon$ sufficiently large to violate the adiabiticity
+constraint \autoref{eq:ad_constr}.
+
+\subsection{Sample Trajectory}
+
+A sample trajectory following in the style of \autoref{fig:ad_21} but for
+$\epsilon = 0.1$ is provided in \autoref{fig:nonad_traj}.
+\begin{figure}
+    \centering
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo_nonad.png}
+    \end{subfigure}
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo_nonad_subplots.png}
+    \end{subfigure}
+    \caption{Same as \autoref{fig:nonad_traj} but for a non-adiabatic $\epsilon =
+    0.1$.}\label{fig:nonad_traj}
+\end{figure}
+
+\subsection{Dynamical Outcomes}
+
+A formula for $\theta_{f}$ assuming $\theta_{sd, i} = 0$ initially can be
+given:
+\begin{equation}
+    \theta_{f}\p{\theta_{sd, i} = 0} = \sqrt{\frac{2\pi \Omega}{\epsilon}}
+        \tan I.\label{eq:nonad_q_f}
+\end{equation}
+We can naively generalize this by recognizing that any nonzero $\theta_{sd, i}$
+manifests as obliquity variations as $\hat{s}$ librates about $\hat{l}_d$, and
+these oscillations are ``frozen in'' when the disk dissipates. Thus,
+\begin{equation}
+    \theta_{f}\p{\theta_{sd, i}} \in \sqrt{\frac{2\pi \Omega}{\epsilon}}
+        \tan I \pm \theta_{sd, i}.\label{eq:nonad_q_f_dist}
+\end{equation}
+
+We present the results of simulations for using $\epsilon = 0.3$ in
+\autoref{fig:nonad_3_ensemeble}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_05.png}
+    \caption{$\theta_{ f}\p{\theta_{sd, i}}$ at $\epsilon = 0.3$, firmly in
+    the non-adiabatic regime. Note the clear double-valuedeness has disappeared,
+    as have distinct dynamical histories. The red dotted line presents the
+    analytical prediction given by
+    \autoref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemeble}
+\end{figure}
+
+\subsection{Transition from Adiabaticity}
+
+The agreement of \autoref{eq:nonad_q_f} at fixed $I$ for varying $\epsilon$ is
+shown in \autoref{fig:nonad_3_scan}. Note that $\epsilon \to 0$ recovers the
+adiabatic regime.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/2_toy2/3scan.png}
+    \caption{Plot of $\theta_{ f}\p{\theta_{sd, i} = 0}$ as a function of
+    $\epsilon$, where $I = 5^\circ$. Overplotted in the red line is
+    \autoref{eq:nonad_q_f}, which is in good agreement for $\epsilon \gtrsim
+    0.1$ the non-adiabatic regime, while $\theta_{ f} \approx 90^\circ$ in
+    the adiabatic regime.}\label{fig:nonad_3_scan}
+\end{figure}
+
+An example of an intermediate value $\epsilon = 10^{-2}$ between
+\autoref{fig:ad_ensemble} and \autoref{fig:nonad_3_ensemeble} is shown in
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_20.png}
+    \caption{Intermediate $\epsilon$ used in between those of
+    \autoref{fig:ad_ensemble} and \autoref{fig:nonad_3_ensemeble}. Noticeable
+    ``freezing-in'' of the obliquity variations over libration cycles is still
+    visible, but the shapes of the adiabatic dynamical trajectories are
+    beginning to appear.}\label{fig:nonad_3_ensemble_20}
+\end{figure}
+
+TODO compare to \autoref{eq:ad_constr}.
+
+\bibliographystyle{mnras}
+\bibliography{Su_sep_cross}
+
+% \clearpage
+% \onecolumn
+\appendix
+
+\section{Dynamical Histories}\label{s:app_histories}
+
+\begin{itemize}
+    \item $A_2 \to A_1$ --- \autoref{fig:ad_21}.
+    \item $A_2 \to A_3$ --- \autoref{fig:ad_23}.
+    \item $A_3 \to A_1$ --- \autoref{fig:ad_31}.
+    \item $A_3 \to A_2 \to A_1$ --- \autoref{fig:ad_321}.
+    \item $A_3 \to A_3$ --- Trivial case, the initial enclosed area is too large
+        to ever experience a separatrix encounter.
+\end{itemize}
 \begin{figure}
@@
 
-\subsection{Dynamical Outcomes}\label{ss:ad_ensemble}
-
-In the adiabatic limit, while separatrix encounters induce discontinuous changes
-in enclosed phase space, the outcomes of these encounters are well understood in
-pioneering work by Henrard \citep{henrard1982,henrard1987}. For a wide range of
-$\theta_{sd, i}$, we run simulations over a ring of initial conditions at each
-$\theta_{sd, i}$ and measure the final $\theta_{sl, f}$ values. We can also
-predict the values of $\theta_{sl, f}$ for each of the dynamical histories as
-well as their associated probabilities; refer to \autoref{ss:app_transition} for
-details.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_35.png}
-    \caption{Top: $\theta_{sl,f}\p{\theta_{sd, i}}$, overlaid with semi-analytic
-    predictions of the $\theta_{sl, f}$ for each of the four nontrivial
-    dynamical histories in colored lines. Bottom: Semi-analytic probabilities of
-    each of the dynamical histories for each $\theta_{sd,
-    i}$.}\label{fig:ad_ensemble}
-\end{figure}
-
-\section{Nonadiabatic Evolution}\label{s:nonad}
-
-Here, we consider $\epsilon$ sufficiently large to violate the adiabiticity
-constraint \autoref{eq:ad_constr}.
-
-\subsection{Sample Trajectory}
-
-A sample trajectory following in the style of \autoref{fig:ad_21} but for
-$\epsilon = 0.1$ is provided in \autoref{fig:nonad_traj}.
-\begin{figure}
-    \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo_nonad.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo_nonad_subplots.png}
-    \end{subfigure}
-    \caption{Same as \autoref{fig:nonad_traj} but for a non-adiabatic $\epsilon =
-    0.1$.}\label{fig:nonad_traj}
-\end{figure}
-
-\subsection{Dynamical Outcomes}
-
-A formula for $\theta_{sl,f}$ assuming $\theta_{sd, i} = 0$ initially can be
-given:
-\begin{equation}
-    \theta_{sl,f}\p{\theta_{sd, i} = 0} = \sqrt{\frac{2\pi \Omega}{\epsilon}}
-        \tan I.\label{eq:nonad_q_f}
-\end{equation}
-We can naively generalize this by recognizing that any nonzero $\theta_{sd, i}$
-manifests as obliquity variations as $\hat{s}$ librates about $\hat{l}_d$, and
-these oscillations are ``frozen in'' when the disk dissipates. Thus,
-\begin{equation}
-    \theta_{sl,f}\p{\theta_{sd, i}} \in \sqrt{\frac{2\pi \Omega}{\epsilon}}
-        \tan I \pm \theta_{sd, i}.\label{eq:nonad_q_f_dist}
-\end{equation}
-
-We present the results of simulations for using $\epsilon = 0.3$ in
-\autoref{fig:nonad_3_ensemeble}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_05.png}
-    \caption{$\theta_{sl, f}\p{\theta_{sd, i}}$ at $\epsilon = 0.3$, firmly in
-    the non-adiabatic regime. Note the clear double-valuedeness has disappeared,
-    as have distinct dynamical histories. The red dotted line presents the
-    analytical prediction given by
-    \autoref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemeble}
-\end{figure}
-
-\subsection{Transition from Adiabaticity}
-
-The agreement of \autoref{eq:nonad_q_f} at fixed $I$ for varying $\epsilon$ is
-shown in \autoref{fig:nonad_3_scan}. Note that $\epsilon \to 0$ recovers the
-adiabatic regime.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3scan.png}
-    \caption{Plot of $\theta_{sl, f}\p{\theta_{sd, i} = 0}$ as a function of
-    $\epsilon$, where $I = 5^\circ$. Overplotted in the red line is
-    \autoref{eq:nonad_q_f}, which is in good agreement for $\epsilon \gtrsim
-    0.1$ the non-adiabatic regime, while $\theta_{sl, f} \approx 90^\circ$ in
-    the adiabatic regime.}\label{fig:nonad_3_scan}
-\end{figure}
-
-An example of an intermediate value $\epsilon = 10^{-2}$ between
-\autoref{fig:ad_ensemble} and \autoref{fig:nonad_3_ensemeble} is shown in
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_20.png}
-    \caption{Intermediate $\epsilon$ used in between those of
-    \autoref{fig:ad_ensemble} and \autoref{fig:nonad_3_ensemeble}. Noticeable
-    ``freezing-in'' of the obliquity variations over libration cycles is still
-    visible, but the shapes of the adiabatic dynamical trajectories are
-    beginning to appear.}\label{fig:nonad_3_ensemble_20}
-\end{figure}
-
-TODO compare to \autoref{eq:ad_constr}.
-
-\bibliographystyle{mnras}
-\bibliography{Su_sep_cross}
-
-% \clearpage
-% \onecolumn
-\appendix
-
 \section{Variation with $I$}

### 2019-09-30 initial/0_eta/1contours.py

@@ -12,47 +12,93 @@ def plot_H_for_eta(f, ax, eta, I):
     Hamiltonian is H = 1/2 cos^2(theta) + eta * sin(phi)
     canonical variables are (phi, x = cos(theta))
     '''
+    eta_c = get_etac(I)
     x_grid, phi_grid = get_grids()
     H_grid = H(I, eta, x_grid, phi_grid)
     cset = ax.contour(phi_grid, x_grid, H_grid,
-                      cmap='RdBu_r', linewidths=0.8, levels=20)
+                      cmap='RdBu_r', linewidths=0.8, levels=5)
 
     thetas, phis = roots(I, eta)
     colors = ['r', 'm', 'g', 'c'] if len(thetas) == 4 else ['m', 'g']
     for color, theta, phi in zip(colors, thetas, phis):
         plot_point(ax, theta, '%so' % color, markersize=6)
 
+    shade = '0.8' # shade interior of separatrix
+    font_height = 0.05 # ~font height so y loc is center of text, not base
     if len(thetas) == 4:
+        H4 = H(I, eta, np.cos(thetas[3]), phis[3])
         ax.contour(phi_grid,
                    x_grid,
                    H_grid,
-                   levels=[H(I, eta, np.cos(thetas[3]), phis[3])],
+                   levels=[H4],
                    colors=['k'],
-                   linewidths=1.6)
+                   linewidths=1.2,
+                   linestyles='solid')
+        ax.contourf(phi_grid,
+                    x_grid,
+                    H_grid,
+                    levels=[H4, np.max(H_grid)],
+                    colors=[shade])
 
-    ax.set_title(r'$(I, \eta)=(%d^\circ, %.3f)$'
-                 % (np.degrees(I), eta), fontsize=8)
+        if eta < 0.8 * eta_c:
+            # if Zone I is sufficiently large, place it inside zone
+            ax.text(0.3, np.cos(thetas[3]) + 0.4, 'I')
+        else:
+            # else draw an arrow
+            y = (4 * np.cos(thetas[0]) + np.cos(thetas[3])) / 5
+            x = 0.3
+            dx = np.pi / 3
+            ax.arrow(x + dx, y, -dx, 0,
+                     width=0.006, head_width=0.056, head_length=0.08)
[…]

### 2019-09-30 initial/99_misc/2_rand_plots.py

@@ -32,7 +32,10 @@ def roots(I, eta):
         roots = []
         inits = [np.pi / 2 - I, -np.pi + I]
         for qi in inits:
-            roots.append(opt.newton(f, qi, fprime=fp))
+            # newton doesn't seem to work very well here @ large eta
+            # roots.append(opt.newton(f, qi, fprime=fp))
+            dq = np.pi / 2
+            roots.append(opt.bisect(f, qi - dq, qi + dq))
         return np.cos(np.array(roots))
 
 def plot_cs(I=np.radians(5)):
@@ -55,10 +58,10 @@ def plot_cs(I=np.radians(5)):
                 cs_lst.append(root_val)
 
     etas_four = etas[np.where(etas < etac)[0]]
-    plt.semilogx(etas_four, cs_vals[0], 'g', label='1')
-    plt.semilogx(etas, cs_vals[1], 'k', label='2')
-    plt.semilogx(etas, cs_vals[2], 'b', label='3')
-    plt.semilogx(etas_four, cs_vals[3], 'r', label='4')
+    plt.semilogx(etas_four, cs_vals[0], 'r', label='1')
+    plt.semilogx(etas, cs_vals[1], 'm', label='2')
+    plt.semilogx(etas, cs_vals[2], 'g', label='3')
+    plt.semilogx(etas_four, cs_vals[3], 'c', label='4')
     plt.xlabel(r'$\eta$')
     plt.ylabel(r'$\cos\theta$')
     plt.legend()
@@ -67,4 +70,4 @@ def plot_cs(I=np.radians(5)):
     plt.savefig('2_cs_locs.png', dpi=400)
 
 if __name__ == '__main__':
-    plot_cs(np.radians(20))
+    plot_cs(np.radians(5))

### 2019-10-02 writeups/Su_disk_disp.tex
lunch presentation + stash paper WIP

@@
 \ll L_d$, so $\vec{l}_d$ is approximately constant. Much of this treatment
-borrows from \citep{anderson2018teeter}. We consider equations in the corotating
-frame
+borrows from \citep{anderson2018teeter}. We consider precession equations
 \begin{align}
     \rd{\hat{s}}{t} &= \omega_{sl} \p{\hat{s} \cdot \hat{l}_d}
-        \p{\hat{s} \times \hat{l}_d},\\
+        \p{\hat{s} \times \hat{l}_d},\label{eq:dsdt}\\
     \rd{\hat{l}}{t} &= \omega_{ld}\p{\hat{l} \cdot \hat{l}_d}
-        \p{\hat{l} \times \hat{l}_d},\\
-    \omega_{sl} &= \frac{3k_q}{2k}\p{\frac{R_1}{a_1}}^3S,\\
-    \omega_{ld} &= \dots.
+        \p{\hat{l} \times \hat{l}_d},\label{eq:dldt}\\
+    \omega_{sl} &\equiv \frac{3k_{qp}}{2k_p} \frac{M_\star}{m_p}
+        \p{\frac{R_p}{a_p}}^3 \Omega_p,\label{eq:wsl}\\
+    \omega_{ld} &\equiv \frac{3M_d}{4M_\star}\p{\frac{a_p}{r_d}}^3 n
+        .\label{eq:wld}
 \end{align}
-(TODO get $\omega_{ld}$ from Millhollard \& Batygin).
+In \autoref{eq:wsl}, $k_{qp}$ and $k_p$ are related to the planet's quadrupole
+moment and moment of inertia respectively \citep[see][]{lai2018}, $M_\star$ is
+the mass of the host star, and $M_p, R_p, a_p, \Omega_p$ are the mass, radius,
+semi-major axis and angular spin frequency of the planet respectively.
+\autoref{eq:wld} is written for a disk of mass $M_d$ located at characteristic
+distance $r_d$ from the host star \citep[see][for a power-law disk
+profile]{millholland_disk}, $n \equiv \sqrt{GM_\star/a_p^3}$ is the planet's
+orbital mean motion.
 
@@
 \end{equation}
-$\alpha = \omega_{sd} > 0, g \equiv -\omega_{ld}\cos I < 0$ follow traditional
+$\alpha = \omega_{sl} > 0, g \equiv -\omega_{ld}\cos I < 0$ follow traditional
 sign conventions.

### 2019-10-02 initial/2_toy2/3_disk_disp.py

@@ -181,12 +181,12 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
     # calculate times to plot for snapshots
     dAreas = abs((areas[1: ] - areas[ :-1]) / areas[1: ])
     peak_idxs = np.argsort(dAreas)
-    if num_snapshots == 1:
-        # plot @ sep appearance
-        cross_idx = np.where(eta_areas < eta_c)[0][0]
-        plot_idxs = [1, *sorted([cross_idx, peak_idxs[-1]]), -2]
-    else:
-        plot_idxs = [1, *sorted(peak_idxs[-num_snapshots: ]), -2]
+    # plot @ sep appearance
+    cross_idx = np.where(eta_areas < eta_c)[0][0]
+    sep_idxs = peak_idxs[-num_snapshots: ]
+    # 2 plots for every sep_idx
+    plot_idxs = sorted([1, cross_idx, *sep_idxs,
+                        *([i + 1 for i in sep_idxs])]) + [-2]
 
     fig, (ax1, ax3) = plt.subplots(2, 1,
                             sharex=True,
@@ -237,12 +237,12 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
     # will handle them in the plot_type branches below
     mu_dat = np.cos(q)
 
-    ax1.semilogx(etas, mu_dat, c='0.25', label='Sim')
+    ax1.semilogx(etas, mu_dat, c='y', label='Sim')
     max_valid_idxs = np.where(mu_max > 0)[0]
     ax1.semilogx(etas[idx4s][max_valid_idxs], mu_max[max_valid_idxs],
-             'g:', label='Sep')
-    ax1.semilogx(etas[idx4s], mu_min, 'g:')
-    ax1.semilogx(etas[idx4s], np.cos(q2s), 'b', label='CS2')
+             'k:', label='Sep')
+    ax1.semilogx(etas[idx4s], mu_min, 'k:')
+    ax1.semilogx(etas[idx4s], np.cos(q2s), 'm', label='CS2')
     ax1.set_xlabel(r'$t$')
     ax1.set_ylabel(r'$\cos\theta$')
 
@@ -310,7 +310,7 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
 
     for ax in [ax1, ax3]:
         for plt_idx in plot_idxs:
-            ax.axvline(eta_areas[plt_idx], c='m', lw=0.5)
[…]

### 2019-10-02 initial/2_toy2/3_disk_disp.py
small updates to presentation

@@ -168,10 +168,12 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
         ret = solve_ic_base(I, eps, y0, tf, events=events)
         t_end_lib, t_end_circ, t_areas, t_areas_f, areas = get_areas_2(ret)
         with open(PKL_FN, 'wb') as f:
-            pickle.dump((ret, t_end_lib, t_end_circ, t_areas, t_areas_f, areas), f)
+            pickle.dump((ret, t_end_lib, t_end_circ,
+                         t_areas, t_areas_f, areas), f)
     else:
         with open(PKL_FN, 'rb') as f:
-            ret, t_end_lib, t_end_circ, t_areas, t_areas_f, areas = pickle.load(f)
+            ret, t_end_lib, t_end_circ,\
+                t_areas, t_areas_f, areas = pickle.load(f)
     # get initial area
     eta_areas = ret.sol(t_areas)[3]
     a_init_int = areas[0]
@@ -328,19 +330,29 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
         fig.delaxes(axs[-1])
         del axs[-1]
     fig.subplots_adjust(wspace=0, hspace=0)
-    # let the first iteration set the ylims
+    # plot data to set the ylims
     for plot_idx, ax in zip(plot_idxs, axs):
         plt_step = 0.05
         t1 = np.arange(t_areas[plot_idx], t_areas_f[plot_idx], plt_step)
         q1, phi1 = to_ang(*ret.sol(t1)[ :3])
         ms = 1.0 if len(t1) < 50 else 0.2
         ax.plot(phi1, np.cos(q1), ls='', marker='o', c='y', markersize=ms)
-        # HACK plot q2 just once
+
+        # plot CS2 as well
         curr_roots = roots(I, eta_areas[plot_idx])
         q2 = curr_roots[0] if len(curr_roots) == 2 else curr_roots[1]
         ax.plot(np.pi, np.cos(q2), 'mo', ms=2)
 
-    # now use the ylims to compute the minimal separatrix pts necessary
+        # overplot an arrow
+        arrow_idx = len(t1) // 2
+        width_base = ax.get_ylim()[1] - ax.get_ylim()[0]
[…]

### 2019-10-02 initial/99_misc/1_areas.py

@@ -61,11 +61,11 @@ def plot_areas():
     A1ys = 2 * np.pi * (1 - eta * np.cos(I)) - A2ys / 2
     A3ys = 2 * np.pi * (1 + eta * np.cos(I)) - A2ys / 2
     plt.plot(eta, A1ys / (4 * np.pi), 'g:')
-    plt.plot(eta, A1w / (4 * np.pi), 'g', label='A1')
+    plt.plot(eta, A1w / (4 * np.pi), 'g', label=r'$A_{I}$')
     plt.plot(eta, A2ys / (4 * np.pi), 'k:')
-    plt.plot(eta, A2w / (4 * np.pi), 'k', label='A2')
+    plt.plot(eta, A2w / (4 * np.pi), 'k', label=r'$A_{II}$')
     plt.plot(eta, A3ys / (4 * np.pi), 'r:')
-    plt.plot(eta, A3w / (4 * np.pi), 'r', label='A3')
+    plt.plot(eta, A3w / (4 * np.pi), 'r', label=r'$A_{III}$')
 
     # dotted line continuation to show "analytic" continuation
     eta_cont = np.linspace(eta_c, 1.2 * eta_c, 21)

### 2019-10-03 writeups/Su_disk_disp.tex
tried to shade in subplots

@@
 
+The primary result of our paper is \autoref{fig:nonad_3_ensemeble}.
+
 \section{Equations}\label{s:eq}
 
-Denote $\vec{S}$ spin of planet, $\vec{l}$ angular momentum of planet, and
+Denote $\vec{s}$ spin of planet, $\vec{l}$ angular momentum of planet, and
 $\vec{l}_d$ angular momentum of the surrounding disc. We approximate $S \ll L
@@
 \begin{align}
-    \rd{\hat{s}}{t} &= \omega_{sl} \p{\hat{s} \cdot \hat{l}_d}
-        \p{\hat{s} \times \hat{l}_d},\label{eq:dsdt}\\
+    \rd{\hat{s}}{t} &= \omega_{sl} \p{\hat{s} \cdot \hat{l}}
+        \p{\hat{s} \times \hat{l}}\label{eq:dsdt}\\
     \rd{\hat{l}}{t} &= \omega_{ld}\p{\hat{l} \cdot \hat{l}_d}
-        \p{\hat{l} \times \hat{l}_d},\label{eq:dldt}\\
+        \p{\hat{l} \times \hat{l}_d},\label{eq:dldt},\\
+\end{align}
+where
+\begin{align}
     \omega_{sl} &\equiv \frac{3k_{qp}}{2k_p} \frac{M_\star}{m_p}
@@
 profile]{millholland_disk}, $n \equiv \sqrt{GM_\star/a_p^3}$ is the planet's
-orbital mean motion.
+orbital mean motion. The three angles formed by the three vectors are notated
+\begin{align}
+    \theta &\equiv \arccos \hat{s} \cdot \hat{l},\\
+    \theta_{sd} &\equiv \arccos \hat{s} \cdot \hat{l}_d,\\
+    I &\equiv \arccos \hat{l} \cdot \hat{l}_d.
+\end{align}
 
-We go to the corotating frame with $\vec{l}$ such that it is also fixed in time.
+We go to the corotating frame with $\hat{l}$ fixed such that $\hat{z} =
+\hat{l}$ ($\theta$ is now conveniently also the polar component of $\hat{s}$).
 The evolution of $\hat{s}$ in this corotating frame is governed by:
@@
         - \abs{g}\p{\hat{s} \times \hat{l}_d}.
-        \label{eq:dsdt_base}
 \end{equation}
@@
 \end{align}
+The redimensionalized equation of motion is then
+\begin{equation}
+    \rd{\hat{s}}{\tau} = \p{\hat{s} \cdot \hat{l}}
+            \p{\hat{s} \times \hat{l}}
+        - \eta\p{\hat{s} \times \hat{l}_d}. \label{eq:dsdt_base}
+\end{equation}
 
@@
 \begin{equation}
-    \rd{\eta}{\tau} = -\epsilon \eta.
+    \rd{\eta}{\tau} = -\epsilon \eta.\label{eq:deta_dt}
 \end{equation}
+Equations \autoref{eq:dsdt_base} and \autoref{eq:deta_dt} constitute our system
+of study.
+
+Finally, the Hamiltonian corresponding to the equation of motion
+\autoref{eq:dsdt_base} is
+\begin{equation}
+    H\p{\phi, \theta} = -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
+        + \eta \p{\hat{s} \cdot \hat{l}_d}.\label{eq:H}
+\end{equation}
+Here, we adopt a spherical coordinate system where $\hat{l} = \hat{z}$ and
+$\theta, \phi$ are the polar and azimuthal angle of $\hat{s}$. By convention, we
+choose $\hat{l}_z$ at coordinates $\theta = I, \phi = \pi$.
 
 \subsection{Cassini States}\label{ss:cs}
-
-The Cassini state Hamiltonian in the frame corotating with $\hat{l}_d$ about
-$\hat{l}$ is:
-\begin{equation}
-    H = -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
-        + \eta \p{\hat{s} \cdot \hat{l}_d}.
-\end{equation}
 
@@
 CSs 1, 2, 3 are stable while CS4 is unstable. A contour plot of $H\p{\phi, \cos
-\theta}$ is
+\theta}$ is provided in \autoref{fig:eq_1contours}.
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{../initial/0_eta/1contours_flip.png}
-    \caption{Contour plot of $H\p{\phi, \cos \theta}$. Black dotted line is the
-    separatrix, which only exists for $\eta < \eta_c$.}\label{fig:eq_1contours}
+    \caption{Contour plot of $H\p{\phi, \cos \theta}$, where warmer colors
+    denote more positive values. The black solid line is the separatrix, which
+    only exists for $\eta < \eta_c$. The three zones, divided by the separatrix,
+    are labeled. The interior of the separatrix, shaded in grey, is formally
+    only defined for $\eta < \eta_c$, but we may identify the phase space
+    trajectories that flow into zone II when evolved forward in time; this is
+    the shaded region in the top left plot, bounded by the dotted black
+    line.}\label{fig:eq_1contours}
 \end{figure}
@@
 The locations of the $\cos\theta$ of the two/four CSs as a function of $\eta$ is
-provided in
-\begin{figure}[t]
+provided in \autoref{fig:cs_locs}.
+\begin{figure}
     \centering
     \includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs.png}
-    \caption{Locations of the Cassini states over time, following the same
-    coloring scheme as \autoref{fig:eq_1contours}.}\label{fig:cs_locs}
+    \caption{$\theta$ values of the Cassini states over time, following the same
+    coloring scheme as \autoref{fig:eq_1contours}. Note that $\theta \in [-\pi,
+    \pi]$ is the traditional definition of the polar angle
+    \citep[see e.g.][]{colombo1966,peale1969,henrard1987}.}\label{fig:cs_locs}
 \end{figure}
@@
 these two critical trajectories are referred to as the \emph{separatrix} and
-divide phase space into three zones. We use notation described in
-\autoref{fig:eq_1contours}.
+divide phase space into three zones. We label these zones as illustrated in
+\autoref{fig:eq_1contours}. As trajectories of constant $\eta$ evolve along
+contours of constant $H$, it can be observed that trajectories in zone II
+librate about CS2 while those in zones I/III circulate.
 
-The unsigned area enclosed by the separatrix is known exactly in literature
-\citep{henrard1987,ward2004I}:
+The unsigned areas of the three zones are known exactly in literature
+\citep{henrard1987,ward2004I}. Defining
+\begin{align*}
+    z_0 &= \eta\cos I, &
+    \chi &= \sqrt{-\frac{\tan^3\theta_4}{\tan I} - 1},\\
+    \rho &= \chi \frac{\sin^2 \theta_4\cos \theta_4}{
+        \chi^2 \cos^2\theta_4 + 1},&
+    T &= 2\chi \frac{\cos \theta_4}{
+        \chi^2 \cos^2\theta_4 - 1},\\
+\end{align*}
+the areas for $\eta < \eta_c$ are given by
 \begin{subequations}\label{se:area_ward}
     \begin{align}
-        z_0 &= \eta\cos I,\nonumber\\
-        \chi &= \sqrt{-\frac{\tan^3\theta_4}{\tan I} - 1},\nonumber\\
-        \rho &= \chi \frac{\sin^2 \theta_4\cos \theta_4}{
-            \chi^2 \cos^2\theta_4 + 1},\nonumber\\
-        T &= 2\chi \frac{\cos \theta_4}{
-            \chi^2 \cos^2\theta_4 - 1},\nonumber\\
         A_{II} &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
@@
 \end{subequations}
-These are plotted as a function of $\eta$ in \autoref{fig:eq_areas}.
+These are plotted as a function of $\eta$ in \autoref{fig:eq_areas}. Note that
+the zones are not formally defined for $\eta > \eta_c$, but a natural extension
+exists: evolve an initial point $p$ under adiabatic decrease of $\eta > \eta_c$
+until the separatrix appears at $\eta = \eta_c$, then identify $p$ with the zone
+it is in at $\eta_c$. Since phase space area is conserved under adiabatic
+evolution, this implies $A_i\p{\eta > \eta_c} = A_i(\eta_c)$.
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{../initial/99_misc/1_areas.png}
-    \caption{Plot of $A_{i}(\eta)$ as given by \autoref{se:area_ward}. Dotted
-    lines correspond to small $\eta$ approximations discussed in
-    \autoref{ss:app_transition}.}\label{fig:eq_areas}
+    \caption{Plot of fractional $A_{i}(\eta)$ as given by
+    \autoref{se:area_ward}. Dotted lines correspond to small $\eta$
+    approximations discussed in \autoref{ss:app_transition}. Dashed lines denote
+    effective values of $A_{II}, A_{III}$ for $\eta > \eta_c$, denoting the
+    area of points that would flow into either area under adiabatic decrease of
+    $\eta$ to below $\eta_c$.}\label{fig:eq_areas}
 \end{figure}
@@
 
-In the truly adiabatic limit, $\epsilon \to 0$; we use $\epsilon =
-3 \times 10^{-4}$ in \autoref{ss:ad_fid} and vary $\epsilon$ in
-\autoref{ss:ad_ensemble}. The adiabatic limit is quantified
-in~\cite{millholland_disk} to be
+As $\eta$ decreases, the trajectory generally encounters the separatrix at some
+value $\eta_\star$ depending on its initial condition. If $\eta$ changes
+sufficiently little during this separatrix-crossing orbit, the evolution of the
+system is considered \emph{adiabatic}. In the truly adiabatic limit, $\epsilon
+\to 0$; we use $\epsilon = 3 \times 10^{-4}$ unless otherwise noted.
+
+One criterion for adiabaticity is that the separatrix crossing timescale be
+longer than the the resonant libration period \citep{ward2004I}. This is
+evaluated in~\cite{millholland_disk}, and in our problem reduces to
 \begin{equation}
-    \dot{\eta} \lesssim \dots \label{eq:ad_constr}
+    \at{\rd{\eta}{t}}_{cross} = -\epsilon\eta_\star \gtrsim
+        -\sin\theta \sin I \cos I.\label{eq:ad_constr}
 \end{equation}
+Note that this is a necessary but not sufficient criterion: the libration period
+is longer for trajectories nearer the separatrix and diverges at the separatrix
+for constant $\eta$.
 
-\subsection{Individual Simulations}\label{ss:ad_fid}
+\subsection{Fiducial Simulation: Zone Transition Histories}\label{ss:ad_fid}
 
-In the limit $\eta \to 0$, all trajectories circulate with constant
-\begin{equation}
-    \theta_{f} \equiv \s{\arccos \hat{s} \cdot \hat{l}}_{\eta \to 0}.
-\end{equation}
-We run simulations that terminate at $\eta = 10^{-5}$ and measure
-$\theta_{f}$. We vary the initial
-\begin{equation}
-    \theta_{sd, i} \equiv \s{\arccos \hat{s} \cdot \hat{l}_d}_{t=0}.
-\end{equation}
+In the limit $\eta \to 0$, zone II disappears and all trajectories circulate at
+constant final $\theta$ values, notated $\theta_f$. We run simulations that
+terminate at $\eta = 10^{-{-3.5}}$ and measure $\theta_{f}$. We vary the initial
+value of $\theta_{sd}$, notated $\theta_{sd, i}$, among our simulations.
 
@@
 exist. Naively then, one might expect four sequences of transitions
-between zones (``zone transition histories'') to appear during simulations: (i)
-$II \to I$, (ii) $II \to III$, (iii) $III \to I$, and (iv) the trivial $III \to
-III$ where the trajectory never encounters the separatrix. In fact, (v) a fifth
-possible history involving two transitions is observed $III \to II \to I$.
+between zones (we call these dynamical ``tracks'') to appear during simulations:
+(i) $II \to I$, (ii) $II \to III$, (iii) $III \to I$, and (iv) the trivial $III
+\to III$ where the trajectory never encounters the separatrix. In fact, (v) a
+fifth possible track involving two transitions is observed $III \to II \to I$.
 
-Between zone transitions, the adiabatic invariant $J \equiv \oint \cos\theta
-\;\mathrm{d}\phi$ is conserved. Here, we adopt convention $J$ is a \emph{signed}
-area
+Between zone transitions, the enclosed phase space area $A \equiv \oint \cos\theta
+\;\mathrm{d}\phi$ is an adiabatic invariant. Here, we adopt convention $A$ is a
+\emph{signed} area
 \begin{equation}
-    J = \oint \p{1 - \cos \theta}\;\mathrm{d}\phi.
+    A = \oint \p{1 - \cos \theta}\;\mathrm{d}\phi.
 \end{equation}
@@
 crosses $\cos \theta = 1$, and (ii) being easily expressible as combinations of
-the $A_i$ of \autoref{se:area_ward} without $2\pi$ offsets.
+the $A_i$ of \autoref{se:area_ward}. The bounds of the integral are either a
+libration or circulation cycle.
 
-Given this definition, the change in $J$ during a separatrix encounter is easily
+Given this definition, the change in $A$ during a separatrix encounter is easily
 understood \citep{henrard1982}. We present in \autoref{fig:ad_21} a fiducial
-simulaiton undergoing the $II \to I$ zone transition. An initial condition in
-zone II with initial adiabatic invariant $J_i > 0$ librates about CS2 until
-$A_{II} = J_i$. At this point, it encounters the separatrix and moves into zone I
-with $J_f = -A_I$. Further simulations illustrating the other zone transition
-histories are depicted in \autoref{s:app_histories}.
+simulation undergoing the $II \to I$ zone transition. An initial condition in
+zone II with initial adiabatic invariant $A_i > 0$ librates about CS2 until
+$A_{II} = A_i$. At this point, it encounters the separatrix and moves into zone
+I and the final enclosed phase space area is $A_f = -(A_{II} + A_{III})$.
+Further simulations illustrating the other tracks are depicted in
+\autoref{ss:app_tracks}.
 \begin{figure}
@@
         \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo21.png}
-        \caption{Top: Plot of $\cos \theta(t)$ (grey) over an example
-        simulation. Overlaid are the locations of Cassini State 2 (blue), upper
-        and lower bounds on the separatrix (dashed green), and value of
-        $\theta_{f}$ predicted in the adiabatic limit (horizontal red line).
-        Bottom: Plot of the enclosed separatrix area obtained by integrating the
-        simulated trajectory (blue dots) and fully adiabitic theory (red line).
-        A small blip in the data area arises when the integration area crosses
-        the coordinate singularity at the pole. Vertical red magenta lines
-        denote the four snapshots depicted below; they correspond to the start
-        of the simulation, the appearance of the separatrix, the separatrix
-        encounter and the end of the simulation.}
     \end{subfigure}
@@
         \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo21_subplots.png}
-        \caption{Snapshots in the $\p{\cos \theta, \phi}$ space of the
-        simulation trajectories for two circulation/libration cycles around the
-        $\eta$ values depicted above. Cycles are defined by the range of
-        integration used to compute enclosed phase space area. Black dots denote
-        the cycle immediately before the selected $\eta$ value, magenta dots the
-        cycle immediately after, and grey denotes intermediate points that do
-        not constitute a full cycle. Also labeled are the separatrix (green) and
-        Cassini State 2 (blue).}
     \end{subfigure}
-    \caption{Fiducial simulation following the $A_2 \to A_1$
-    transition.}\label{fig:ad_21}
+    \caption{Fiducial simulation following the $A_{II} \to A_{I}$ transition. Top
+    plot upper panel: plot of $\cos \theta(t)$ (gold) in an example simulation.
+    Overlaid are the locations of Cassini State 2 (magenta), and upper and lower
+    bounds on the separatrix (dashed black). Note that the trajectory
+    successfully tracks CS2 to a misalignment angle $\theta \approx 90^\circ$.
+    Vertical green lines denote times portrayed in bottom plot. Top plot lower
+    panel: plot of the enclosed separatrix area obtained by integrating the
+    simulated trajectory (blue dots) and adiabatic theory (red line). Lower
+    plot: snapshots in the $\p{\cos \theta, \phi}$ space of the simulation
+    trajectories for the times demarcated in green above, corresponding to the
+    start of the simulation, the appearance of the separatrix, two panels
+    depicting the separatrix crossing process, and a final snapshot at $\eta =
+    10^{-3.5}$. Gold dots denote a full circulation or libration cycle at the
+    selected time, while the separatrix at the start/end of the portrayed cycle
+    are shown in solid/dashed black lines respectively. Also labeled is CS2
+    (magenta).}\label{fig:ad_21}
 \end{figure}
@@
 $\theta_{sd, i}$ and measure the final $\theta_{ f}$ values. We can also
-predict the values of $\theta_{ f}$ for each of the dynamical histories as
+predict the values of $\theta_{ f}$ for each of the tracks as
 well as their associated probabilities; refer to \autoref{ss:app_transition} for
-details.
+details. The comparison of the final obliquities associated with these tracks
+and those obtained via simulation can be seen in \autoref{fig:ad_ensemble}. The
+same plot for $I = 10^\circ, I = 20^\circ$ can be found in
+\autoref{ss:varying_I}.
 \begin{figure}
@@
     predictions of the $\theta_{ f}$ for each of the four nontrivial
-    dynamical histories in colored lines. Bottom: Semi-analytic probabilities of
-    each of the dynamical histories for each $\theta_{sd,
+    dynamical tracks in colored lines. Bottom: Semi-analytic probabilities of
+    each of the dynamical tracks for each $\theta_{sd,
     i}$.}\label{fig:ad_ensemble}
+\end{figure}
+
+\subsection{Transition to Non-adiabaticity}
+
+To illustrate the transition to non-adiabaticity, we present three simulations
+with increasingly larger values of $\epsilon$ than \autoref{fig:ad_ensemble}
+below in \autoref{fig:transition_to_nonad}.
+
+At first non-adiabaticity manifests as a larger scatter of final obliquities
+near the tracks predicted from adiabatic evolution. These scatters first set in
+for trajectories starting in zone III, as these cross the separatrix at higher
+values of $\theta$ and have a stricter adiabaticity criterion (see
+\autoref{eq:ad_constr}).
+
+Later, these large scatters take on band-like structures that seem to persist
+across values of $\theta_{sd, i}$; we attribute these to the separatrix crossing
+process becoming sensitive to the \emph{phase} of the final
+libration/circulation orbit at separatrix crossing. This is equivalent to
+separatrix crossing no longer being significantly slower than orbit timescales
+and violating the adiabatic assumption.
+\begin{figure}
+    \centering
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_25.png}
+    \end{subfigure}
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_15.png}
+    \end{subfigure}
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_10.png}
+    \end{subfigure}
+    \caption{Increasingly larger $\epsilon$ used compared to those in
+    \autoref{fig:ad_ensemble}. The general evolutionary tracks in the adiabatic
+    limit deteriorate as $\epsilon$ is increased. Deviations from the adiabatic
+    predictions seem to be banded structures, which can be attributed to
+    non-adiabaticity ``freezing-in'' the phase of the obliquity variations over
+    the final libration/circulation orbit prior to separatrix
+    crossing.}\label{fig:transition_to_nonad}
 \end{figure}
@@
 
-Here, we consider $\epsilon$ sufficiently large to violate the adiabiticity
-constraint \autoref{eq:ad_constr}.
+Here, we consider $\epsilon \sim 0.2$ which significantly violates
+\autoref{eq:ad_constr}.
 
@@
     \caption{Same as \autoref{fig:nonad_traj} but for a non-adiabatic $\epsilon =
-    0.1$.}\label{fig:nonad_traj}
+    0.1$. In the top panel of the top plot, it is evident that the libration
+    cycle about CS2 is unable to keep up with the swift motion of CS2 as $\eta$
+    changes, decreasing the obliquity jump. In the bottom plot, we can see that
+    individual orbits do not lie along level curves of the Hamiltonian, a
+    further consequence of violating adiabaticity.}\label{fig:nonad_traj}
 \end{figure}
@@
 A formula for $\theta_{f}$ assuming $\theta_{sd, i} = 0$ initially can be
-given:
+given (see \autoref{ss:app_transition})
 \begin{equation}
@@
     the non-adiabatic regime. Note the clear double-valuedeness has disappeared,
-    as have distinct dynamical histories. The red dotted line presents the
+    as have distinct dynamical tracks. The red dotted line presents the
     analytical prediction given by
@@
 \end{figure}
-
-\subsection{Transition from Adiabaticity}
 
@@
 
-An example of an intermediate value $\epsilon = 10^{-2}$ between
-\autoref{fig:ad_ensemble} and \autoref{fig:nonad_3_ensemeble} is shown in
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_20.png}
-    \caption{Intermediate $\epsilon$ used in between those of
-    \autoref{fig:ad_ensemble} and \autoref{fig:nonad_3_ensemeble}. Noticeable
-    ``freezing-in'' of the obliquity variations over libration cycles is still
-    visible, but the shapes of the adiabatic dynamical trajectories are
-    beginning to appear.}\label{fig:nonad_3_ensemble_20}
-\end{figure}
-
-TODO compare to \autoref{eq:ad_constr}.
-
 \bibliographystyle{mnras}
@@
 
-\section{Dynamical Histories}\label{s:app_histories}
+\section{Adiabatic Evolution}
+
+\subsection{Adiabatic Dynamical Histories}\label{ss:app_tracks}
 
 \begin{itemize}
-    \item $A_2 \to A_1$ --- \autoref{fig:ad_21}.
-    \item $A_2 \to A_3$ --- \autoref{fig:ad_23}.
-    \item $A_3 \to A_1$ --- \autoref{fig:ad_31}.
-    \item $A_3 \to A_2 \to A_1$ --- \autoref{fig:ad_321}.
-    \item $A_3 \to A_3$ --- Trivial case, the initial enclosed area is too large
-        to ever experience a separatrix encounter.
+    \item $A_{II} \to A_{I}$ --- \autoref{fig:ad_21}.
+    \item $A_{II} \to A_{III}$ --- \autoref{fig:ad_23}.
+    \item $A_{III} \to A_{I}$ --- \autoref{fig:ad_31}.
+    \item $A_{III} \to A_{II} \to A_{I}$ --- \autoref{fig:ad_321}.
+    \item $A_{III} \to A_{III}$ --- Trivial case, the initial enclosed area is
+        too large to ever experience a separatrix encounter.
 \end{itemize}
@@
     \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ history.
+    \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ track.
     }\label{fig:ad_23}
@@
     \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_3 \to A_1$ history. TODO
-    finish final areas plot.}\label{fig:ad_31}
+    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_I$
+    track.}\label{fig:ad_31}
 \end{figure}
@@
     \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_3 \to A_2 \to A_1$
-    history. The second snapshot, instead of depicting the appearance of the
-    separatrix, captures the first of the two separatrix crossings. TODO finish
-    final areas plot.}\label{fig:ad_321}
+    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_{II} \to A_I$
+    track. Two separatrix crossings are shown.}\label{fig:ad_321}
 \end{figure}
 
-\section{Variation with $I$}
+\subsection{Adiabatic Tracks at Varying $I$}\label{ss:varying_I}
 
-Plots of \autoref{fig:ad_ensemble} but for $I = 10^\circ, I=20^\circ$.
+See \autoref{fig:varying_i}.
+\begin{figure}
+    \centering
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_10_35.png}
+    \end{subfigure}
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_20_35.png}
+    \end{subfigure}
+    \caption{Same as \autoref{fig:ad_ensemble} but for $I = 10^\circ$ (top) and
+    $I = 20^\circ$ (bottom).}\label{fig:varying_i}
+\end{figure}
 
-\section{Calculation of Transition Probabilities}\label{ss:app_transition}
+\subsection{$\theta_f$ for Adiabatic Tracks}\label{ss:app_transition}
 
-Semi-analytic calculation probabilities, including naive line.
+To understand how trajectories transition between zones, we must recall the
+result from \citep{henrard1982,henrard1987}: if a zone $i$ is shrinking and zone
+$j$ is expanding, the probability of transition from zone $i$ to zone $j$ is
+given
+\begin{equation}
+    \Pr_{i \Rightarrow j} = -\frac{\pd{A_j}{t}}{ \pd{A_i}{t}}
+        = -\frac{\pd{A_j}{\eta}}{ \pd{A_i}{\eta}}\label{eq:henrard_hop}
+\end{equation}
+This can be used directly in conjunction with \autoref{se:area_ward} to generate
+the probabilities in the bottom panel of \autoref{fig:ad_ensemble}.
+
+Next, we will compute an approximate closed form for the final obliquities for
+the initial conditions in zone II (which experience separatrix crossing at
+$\eta_\star \ll 1$), we first seek a simple parameterization for the separatrix.
+We first solve for equilibria of the equation of motion \autoref{eq:dsdt_base}
+to compute the coordinates for Cassini State 4:
+\begin{equation}
+    \cos \theta_4 \approx \frac{\mu \cos I}{1 - \eta \sin I}.
+\end{equation}
+Note that $\phi_4 = 0$. Then, the separatrix is the level curve of the
+Hamiltonian intersecting CS4, so it satisfies $H\p{\theta_{sep}(\phi), \phi} =
+H\p{\theta_4, \phi_4}$. This solves to be approximately
+\begin{equation}
+    \cos \theta_{sep}(\phi) \approx \cos \theta_4 \pm
+        \sqrt{2\eta \sin I\p{1 - \cos \phi}}.
+\end{equation}
+Integration of the phase area enclosed by the two legs of the separatrix then
+yields
+\begin{equation}
+    A_{II}(\eta) \approx 16\sqrt{\eta \sin I}.\label{eq:a_approx}
+\end{equation}
+This, in conjunction with \autoref{eq:henrard_hop}, is sufficient to compute
+$\theta_f\p{\theta_{sd, i}}$ for zone II initial conditions.
+
+\begin{itemize}
+    \item For a given $\theta_{sd, i}$, we know that if $\eta \to \infty$ then
+        the trajectory executes simple libration about $\hat{l}_d$, and so $A =
+        2\pi\p{1 - \cos \theta_{sd, i}} \approx \pi \theta_{sd, i}^2$. This
+        then implies $\eta_\star$ must be the solution to $A_{II}(\eta_\star) =
+        A$, or
+        \begin{align}
+            \eta_\star &\approx \p{\frac{2\pi\p{1 - \cos \theta_{sd,i}}}{
+                        16}}^2 / \sin I,\nonumber\\
+                    &\approx \p{\frac{\pi \theta_{sd, i}^2}{16}}^2/\sin I.
+        \end{align}
+
+    \item Upon separatrix encounter, a transition to either zone I or zone III
+        occurs. These can be calculated to have associated probabilities (using
+        the approximate area \autoref{eq:a_approx})
+        \begin{align}
+            \Pr_{II \Rightarrow I} &\approx \frac{2\pi
+                \eta_{\star} \cos I + 4\sqrt{\eta_{\star}\sin
+                I}}{8\sqrt{\eta_{\star}\sin I}},\\
+            \Pr_{II \Rightarrow III} &\approx \frac{-2\pi
+                \eta_{\star} \cos I + 4\sqrt{\eta_{\star}\sin
+                I}}{8\sqrt{\eta_{\star}\sin I}}.
+        \end{align}
+
+    \item Upon a transition to zone I or zone III, the final obliquities can be
+        predicted by observing the final adiabatic invariant $A_f =
+        -A_I(\eta_\star)$ in the zone I case and $A_f = A_I(\eta_\star) +
+        A_II(\eta_\star)$ in the zone III case. As $\eta \to 0$, these
+        correspond to obliquities
+        \begin{align}
+            \cos \theta_{f, II \Rightarrow I} &\approx
+                &\approx\p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
+                    + \frac{\theta_{sp, i}^2}{4},\\
+            \cos \theta_{f, II \Rightarrow III} &\approx
+                &\approx\p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
+                    - \frac{\theta_{sp, i}^2}{4}.
+        \end{align}
+        These are the black dotted lines overplotted in
+        \autoref{fig:ad_ensemble}.
+\end{itemize}
+
+\section{Nonadiabatic Evolution}\label{s:nonad_app}
+
+We present a single result, the derivation of \autoref{eq:nonad_q_f}. We take
+\autoref{eq:dsdt_base} and choose coordinate axes such that $\hat{l} = \hat{z},
+\hat{l}_d = \hat{z} \cos I + \hat{x}\sin I$, then we obtain
+\begin{equation}
+    \rd{\hat{s}}{t} = \s{
+        \p{\eta \cos I - 1}\hat{z} + \eta \sin I \hat{x}} \times \hat{s}.
+\end{equation}
+
+Now, let's assume that $s_z \approx \cos I$ throughout the evolution of $\hat{s}$
+(note that $\theta_{sd, i} = 0$ implies the initial $s_z = \cos I$). Then let's
+examine the evolution of quantity $S = s_x + is_y$ instead:
+\begin{equation}
+    \rd{S}{t} = i\p{\eta\cos I - 1}S - i \eta \sin I\cos I.\label{eq:nonad_ode}
+\end{equation}
+Now this is a first-order ODE in $S$, albeit complex, which can be solved via
+an integrating factor
+\begin{align}
+    \Phi(t) &\equiv \int_{-\infty}^t \p{1 - \eta(t') \cos I}
+        \mathrm{d}t',\\
+    \at{S(t) e^{i\Phi(t)}}_{-\infty}^t
+        &= \int\limits_{-\infty}^t e^{i\Phi(t')}
+            \p{-i\eta(t')\sin I\cos I}\;\mathrm{d}t'\label{eq:nonad_int}
+\end{align}
+We now invoke stationary phase, asserting that $e^{i\Phi(t)}$ is dominated by
+its contribution where $\dot{\Phi} = 0$ (the phases add constructively). But
+$\dot{\Phi} = 0$ is where $1 - \eta\cos I = 0$, or where $\eta\cos I = 1$.
+
+Now at this point, let's choose $\eta(0) = 1/\cos I, \at{\rd{\eta}{t}}_{t=0} =
+-\epsilon/\cos I$. Then we expand near $t = 0$ so
+\begin{align*}
+    \Phi(t) &\approx \Phi(0) + \frac{1}{2}\ddot{\Phi}t^2,\\
+        &\approx \Phi(0) + \frac{1}{2}\epsilon t^2,\\
+    \int\limits_{-\infty}^t e^{i\Phi(t')}\eta(t')\;\mathrm{d}t'
+        &\approx
+        \begin{cases}
+            0 & t < 0,\\
+            \frac{1}{\cos I}e^{i\Phi(0)}\int\limits_{-\infty}^\infty
+                \exp\s{\frac{i}{2}\epsilon t^2}\;\mathrm{d}t
+                & t > 0.
+        \end{cases}\\
+    \int\limits_{-\infty}^\infty
+                \exp\s{\frac{i}{2}\epsilon t^2}\;\mathrm{d}t
+        &= \int\limits_{-\infty}^\infty e^{-\tau^2}\;\mathrm{d}\tau
+            \sqrt{\frac{2}{i\epsilon}},\\
+        &= \sqrt{\frac{2\pi}{i\epsilon}}.
+\end{align*}
+
+Now, it should be noted that $e^{i\Phi}$ is just a phase; all we really care
+about is $\abs{S} = \sqrt{1 - s_z^2}$. Thus, taking the absolute value of both
+sides of \autoref{eq:nonad_int}, assuming $S\p{-\infty} \ll S\p{+\infty}$ and
+noting $\theta_f \approx \abs{S}(+\infty)$, we obtain
+\begin{equation}
+    \theta_f = \tan I\cos I\sqrt{\frac{2\pi}{\epsilon}}.\label{eq:nonad_dong}
+\end{equation}
+
+It should be noted that this calculation breaks down in two ways:
+\begin{itemize}
+    \item If the evolution of $\hat{s}$ is adiabatic, then it is invalid to
+        assume $s_z$ is approximately constant in time, as many
+        circulation/libration orbits can ensue. Only when the driving is
+        sufficiently impulsive that the evolution dominates the change in $s_z$
+        is this calculation valid.
+
+    \item If $\abs{S\p{-\infty}} \sim \abs{S\p{+\infty}}$, then taking the
+        absolute value of both sides of \autoref{eq:nonad_int} no longer simply
+        yields $\abs{S}\p{+\infty}$. This corresponds to the extreme limit
+        where $\eta$ changes so suddenly that $\hat{s}$ has no time to respond
+        and remains roughly unchanged as $\eta \to 0$. This is accommodated by
+        noting $\theta_f \geq \theta_{sd, i}$, so the correct estimate can be
+        roughly amended
+        \begin{equation}
+            \theta_f \simeq \min\p{\tan I\cos I\sqrt{\frac{2\pi}{\epsilon}},
+                \theta_{sd, i}}.
+        \end{equation}
+\end{itemize}
 

### 2019-10-03 initial/2_toy2/3_disk_disp.py

@@ -8,6 +8,7 @@ import scipy.optimize as opt
 import numpy as np
 from multiprocessing import Pool
 from matplotlib import cm
+from scipy.interpolate import interp1d
 
 import matplotlib
 import pickle
@@ -333,28 +334,67 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
     # plot data to set the ylims
     for plot_idx, ax in zip(plot_idxs, axs):
         plt_step = 0.05
-        t1 = np.arange(t_areas[plot_idx], t_areas_f[plot_idx], plt_step)
-        q1, phi1 = to_ang(*ret.sol(t1)[ :3])
-        ms = 1.0 if len(t1) < 50 else 0.2
-        ax.plot(phi1, np.cos(q1), ls='', marker='o', c='y', markersize=ms)
+        t_vals = np.arange(t_areas[plot_idx], t_areas_f[plot_idx], plt_step)
+        q_vals, phi_vals = to_ang(*ret.sol(t_vals)[ :3])
+        ms = 1.0 if len(t_vals) < 50 else 0.2
+        ax.plot(phi_vals, np.cos(q_vals), ls='', marker='o', c='y', markersize=ms)
 
         # plot CS2 as well
         curr_roots = roots(I, eta_areas[plot_idx])
         q2 = curr_roots[0] if len(curr_roots) == 2 else curr_roots[1]
         ax.plot(np.pi, np.cos(q2), 'mo', ms=2)
 
-        # overplot an arrow
-        arrow_idx = len(t1) // 2
+        # overplot an arrow to show direction
+        arrow_idx = len(t_vals) // 2
         width_base = ax.get_ylim()[1] - ax.get_ylim()[0]
-        ax.arrow(phi1[arrow_idx], np.cos(q1[arrow_idx]),
-                 phi1[arrow_idx + 1] - phi1[arrow_idx],
-                 np.cos(q1[arrow_idx + 1]) - np.cos(q1[arrow_idx]),
+        ax.arrow(phi_vals[arrow_idx], np.cos(q_vals[arrow_idx]),
+                 phi_vals[arrow_idx + 1] - phi_vals[arrow_idx],
+                 np.cos(q_vals[arrow_idx + 1]) - np.cos(q_vals[arrow_idx]),
                  color='y', width=0,
                  head_width=0.056 * width_base, head_length=0.12)
+
+        # shade the enclosed phase space area
[…]

### 2019-10-03 initial/99_misc/1_areas.py

@@ -79,6 +79,7 @@ def plot_areas():
                [r'$0$', r'$0.3$', r'$0.6$', r'$\eta_c$', r'$0.9$'])
     old_ylims = plt.ylim()
     plt.ylim([0, old_ylims[1]])
+    plt.xlim([0, 1.2 * eta_c])
     plt.title(r'$I = %d^\circ, \eta_c = %.3f$' % (np.degrees(I), eta_c))
     plt.savefig('1_areas.png', dpi=400)
     plt.clf()

### 2019-10-10 writeups/Su_disk_disp.tex
stash draft for 10/10 meeting

@@
 
+% TODO
+% figure out whether can draw vertical lines on 3testo plots for regimes
+% run simulations up to III -> III (not today)
+
 \begin{abstract}
@@
 \ll L_d$, so $\vec{l}_d$ is approximately constant. Much of this treatment
-borrows from \citep{anderson2018teeter}. We consider precession equations
+borrows from \citealp{anderson2018teeter} and \citealp{millholland_disk}. We
+consider precession equations
 \begin{align}
@@
     \rd{\hat{l}}{t} &= \omega_{ld}\p{\hat{l} \cdot \hat{l}_d}
-        \p{\hat{l} \times \hat{l}_d},\label{eq:dldt},\\
+        \p{\hat{l} \times \hat{l}_d},\label{eq:dldt}\\
 \end{align}
@@
 \end{equation}
-CSs 1, 2, 3 are stable while CS4 is unstable. A contour plot of $H\p{\phi, \cos
-\theta}$ is provided in \autoref{fig:eq_1contours}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/0_eta/1contours_flip.png}
-    \caption{Contour plot of $H\p{\phi, \cos \theta}$, where warmer colors
-    denote more positive values. The black solid line is the separatrix, which
-    only exists for $\eta < \eta_c$. The three zones, divided by the separatrix,
-    are labeled. The interior of the separatrix, shaded in grey, is formally
-    only defined for $\eta < \eta_c$, but we may identify the phase space
-    trajectories that flow into zone II when evolved forward in time; this is
-    the shaded region in the top left plot, bounded by the dotted black
-    line.}\label{fig:eq_1contours}
-\end{figure}
+CSs 1, 2, 3 are stable while CS4 is unstable.
 
@@
 these two critical trajectories are referred to as the \emph{separatrix} and
-divide phase space into three zones. We label these zones as illustrated in
-\autoref{fig:eq_1contours}. As trajectories of constant $\eta$ evolve along
+divide phase space into three zones. The separatrix and three zones are most
+clearly shown via a contour plot of $H\p{\phi, \cos \theta}$ in
+\autoref{fig:eq_1contours}.
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.8\textwidth]{../initial/0_eta/1contours_flip.png}
+    \caption{Contour plot of $H\p{\phi, \cos \theta}$, where warmer colors
+    denote more positive values. The black solid line is the separatrix, which
+    only exists for $\eta < \eta_c$. The three zones, divided by the separatrix,
+    are labeled. The interior of the separatrix, shaded in grey, is formally
+    only defined for $\eta < \eta_c$, but we may identify the phase space
+    trajectories that flow into zone II when evolved forward in time; this is
+    the shaded region in the top left plot, bounded by the dotted black
+    line.}\label{fig:eq_1contours}
+\end{figure*}
+
+As trajectories of constant $\eta$ evolve along
 contours of constant $H$, it can be observed that trajectories in zone II
@@
 
-\subsection{Fiducial Simulation: Zone Transition Histories}\label{ss:ad_fid}
+\subsection{Separatrix Crossing and Evolutionary Tracks
+}\label{ss:zone_transitions}
 
@@
 
-Initially, in the $\eta > \eta_c$ regime, only zones $II, III$ exist.
-Conversely, at the end of the simulation when $\eta \to 0$, only zones $I, III$
-exist. Naively then, one might expect four sequences of transitions
-between zones (we call these dynamical ``tracks'') to appear during simulations:
-(i) $II \to I$, (ii) $II \to III$, (iii) $III \to I$, and (iv) the trivial $III
-\to III$ where the trajectory never encounters the separatrix. In fact, (v) a
-fifth possible track involving two transitions is observed $III \to II \to I$.
-
-Between zone transitions, the enclosed phase space area $A \equiv \oint \cos\theta
-\;\mathrm{d}\phi$ is an adiabatic invariant. Here, we adopt convention $A$ is a
-\emph{signed} area
+In the absence of separatrix encounters, the enclosed phase space area $A \equiv
+\oint \cos\theta \;\mathrm{d}\phi$ is an adiabatic invariant. Here, we adopt
+convention where $A$ is a \emph{signed} area
 \begin{equation}
@@
 the $A_i$ of \autoref{se:area_ward}. The bounds of the integral are either a
-libration or circulation cycle.
+libration ($\phi$ returns to its original value with the same $\dot{q\phi}$
+sign) or circulation cycle ($\phi$ advances to $\phi \pm 2\pi$). Note lastly
+that $A$ has simple physical interpretation of are enclosed on the unit sphere
+by $\hat{s}$ over one cycle measured relative to $+\hat{z}$:
+\begin{equation*}
+    \int \int\limits_{\cos \theta(\phi)}^1
+        \mathrm{d}\cos\theta\;\mathrm{d}\phi = \int \p{1 - \cos \theta(\phi)}
+            \;\mathrm{d}\phi.
+\end{equation*}
 
-Given this definition, the change in $A$ during a separatrix encounter is easily
-understood \citep{henrard1982}. We present in \autoref{fig:ad_21} a fiducial
-simulation undergoing the $II \to I$ zone transition. An initial condition in
-zone II with initial adiabatic invariant $A_i > 0$ librates about CS2 until
-$A_{II} = A_i$. At this point, it encounters the separatrix and moves into zone
-I and the final enclosed phase space area is $A_f = -(A_{II} + A_{III})$.
-Further simulations illustrating the other tracks are depicted in
-\autoref{ss:app_tracks}.
+When a trajectory encounters the separatrix, $A$ will change discontinuously as
+the trajectory moves between zones, but its change is easily understood
+\citep{henrard1982}. We can classify trajectories by the separatrix encounters
+they undergo. Initially, in the $\eta > \eta_c$ regime, only zones $II, III$
+exist. Conversely, at the end of the simulation when $\eta \to 0$, only zones
+$I, III$ exist. Most simply, one might expect four sequences of transitions
+between zones (we call these dynamical ``tracks'') to manifest: from one of
+$\z{I, III}$ to one of $\z{II, III}$. In addition to these four tracks, a
+fifth track $III \to II \to I$ is observed.
+
+Beyond simply identifying the possible tracks, we may clearly delineate the
+initial conditions for which each track can be encountered. Separatrix crossing
+is a probabilistic process whose outcomes are well understood by
+\citealp{henrard1982,henrard1987}. Their resultss may be simply summarized as
+follows: if a zone $i$ is shrinking and zone $j$ is expanding, the probability
+of transition from zone $i$ to zone $j$ is given
+\begin{equation}
+    \Pr_{i \Rightarrow j} = -\frac{\pd{A_j}{t}}{ \pd{A_i}{t}}
+        = -\frac{\pd{A_j}{\eta}}{ \pd{A_i}{\eta}}\label{eq:henrard_hop}
+\end{equation}
+This can be used directly in conjunction with \autoref{se:area_ward} to
+understand for what initial conditions each track can be observed and with what
+probabilities.
+
+Below, we will describe the evolution of $A$ throughout each of the five tracks,
+as well as determine the initial conditions and probabilities associated with
+each track:
+\begin{itemize}
+    \item $II \to I$ --- This track is depicted in \autoref{fig:ad_21}.
+        $\hat{s}$ starts librating about CS2 in zone II, enclosing some initial
+        phase space area $A_i$. The trajectory is able to librate without
+        separatrix encounter until $A_{II}(\eta_\star) = A_i$. At this point, as
+        the trajectory transitions to a circulating trajectory in zone I
+        immediately bordering the separatrix, it will encompass
+        $-A_I(\eta_\star)$ phase space area. Conservation of phase space area
+        then predicts that as $\eta \to 0$, the final enclosed phase space area
+        will still be $A_f = -A_I$, and the final obliquity $\theta_f$ must be
+        given by
+        \begin{equation}
+            2\pi\p{1 - \cos \theta_f} = A_f. \label{eq:qfaf}
+        \end{equation}
+
+        This transition can only occur when the initial condition begins in zone
+        II, requiring $A_i < A_{II}(\eta_c)$, where $A_{II}(\eta_c)$ is known in
+        closed form \citep{ward2004I}
+        \begin{equation}
+            A_{II}\p{\eta_c} = 4\pi \s{
+                1 - \p{1 + \tan^{2/3}I}^{-3/2}}.
+        \end{equation}
+        Then, at some known $\eta_\star$ satisfying $A_{II}(\eta_\star) = A_i$,
+        the trajectory is ejected from the separatrix and enters zone I with
+        probability
+        \begin{equation}
+            \Pr_{II \to I} = -\at{\frac{\pd{A_I}{\eta}}{\pd{A_{II}}{\eta}}}
+                _{\eta_\star}.
+        \end{equation}
+        Note that since $\pd{A_i}{\eta} < 0$ everywhere, while
+        $\pd{A_{II}}{\eta} > 0$ at all possible $\eta_\star$ for an initial
+        condition starting in zone II, this track always has nonzero
+        probability.
+
+    \item $II \to III$ --- This track is depicted in \autoref{fig:ad_23}. The
+        only difference from the previous track is that, upon separatrix
+        encounter, the trajectory follows the circulating trajectory in zone III
+        bordering the separatrix, upon which it will encompass $A_f =
+        A_I(\eta_\star) + A_{II}(\eta_\star)$. The final obliquity is still
+        given by \autoref{eq:qfaf}.
+
+        Again, this track can only occur when $A_i < A_{II}(\eta_c)$, and enters
+        zone III with probability
+        \begin{equation}
+            \Pr_{II \to III} = -\at{\frac{\pd{A_{III}}{\eta}}
+                {\pd{A_{II}}{\eta}}} _{\eta_\star}.
+        \end{equation}
+        Upon examination of \autoref{fig:eq_areas}, it is clear that
+        $\pd{A_{III}}{\eta} > 0$ for many $\eta$. Call
+        \begin{equation}
+            \eta_{\min, III} \equiv \argmin A_{III}(\eta),
+        \end{equation}
+        then if $\eta_\star > \eta_{\min, III}$ then $\Pr_{II \to III} < 0$.
+        This is interpreted as a forbidden transition, and so $II \to III$ is
+        only a permitted dynamical track if $\eta_\star \in 0, \eta_{\min,
+        III}$.
+
+    \item $III \to I$ --- This track is depicted in \autoref{fig:ad_31}.
+        The trajectory encounters the separatrix when $A_I(\eta_\star) +
+        A_{II}(\eta_\star) = A_i$, upon which it transitions to a zone I
+        trajectory enclosing $A_f = -A_I$.
+
+        This track can only occur if $A_i > A_{II}(\eta_c)$, but is also
+        constrained by requiring its $A_i$ is sufficiently small it will
+        encounter the separatrix at all (if it is too large, it will never
+        encounter the separatrix, which we classify as a $III \to III$
+        transition below). This is written $A_i < \max A_I + A_{II} = 4\pi -
+        \min A_{III}$. Within these constraints, the zone transition occurs with
+        probability
+        \begin{equation}
+            \Pr_{III \to I} = -\at{\frac{\pd{A_I}{\eta}}{\pd{A_{III}}{\eta}}}
+                _{\eta_\star}.
+        \end{equation}
+        Note that since $\pd{A_I}{\eta} < 0$ always while $\pd{A_{III}}{\eta} >
+        0$ for all accessible $\eta_{\star}$, this track is always permitted.
+
+    \item $III \to II \to I$ --- This track is depicted in
+        \autoref{fig:ad_321}. The first separatrix encounter occurs at $\eta_1$
+        when $A_I(\eta_1) + A_{II}(\eta_1) = A_i$, upon which the trajectory
+        moves into zone II enclosing intermediate phase space area $A_m =
+        A_{II}(\eta_1)$. Examining \autoref{fig:eq_areas}, there exist values
+        $A$ for which $A_{II}(\eta) = A$ has multiple solutions. These are the
+        only values for which the $III \to II \to I$ transition is permitted.
+        Thus, as $\eta$ continues to decrease, a second $\eta_2$ value exists
+        for which $A_m = A_II(\eta_2)$, upon which the trajectory is ejected to
+        zone I and $A_f = -A_I(\eta_2)$. The final obliquity again then obeys
+        \autoref{eq:qfaf}.
+
+        Similar to the $III \to I$ track, the $III \to II \to I$ track can only
+        occur over the same $A_{II}(\eta_c) < A_i < \max A_I + A_{II}$ interval.
+        Here, the transition probability for the initial $III \to II$ transition
+        is simply
+        \begin{equation}
+            \Pr_{III \to II} = -\at{\frac{\pd{A_II}{\eta}}{\pd{A_{III}}{\eta}}}
+                _{\eta_1}.
+        \end{equation}
+        It bears noting that this expression is only nonzero for a very small
+        fraction of $A_i$ values, since it requires $\pd{A_{II}}{\eta}$ and
+        $\pd{A_{III}}{\eta}$ to have different signs; this occurs only if
+        $A_{II}\p{\eta_c} < A_i < A_{II, \max}$. Outside of these bounds,
+        $\Pr_{III \to II} < 0$ which is interpreted again as a forbidden
+        transition.
+
+        Then, once a $III \to II$ transition occurs, the second $II \to I$
+        transition occurs for some $\eta_2$ satisfying $A_{II}(\eta_2) =
+        A_{II}(\eta_1), \eta_2 < \eta_1$. Graphical inspection shows that
+        $\pd{A_{II}}{\eta}$ has the same sign as $\pd{A_{III}}{\eta}$ over all
+        possible values, so the second $II \to I$ transition is guaranteed,
+        completing the $III \to II \to I$ track.
+
+    \item $III \to III$ --- This track depicts the trivial case where no
+        separatrix encounter ever occurs, and $A$ is constant throughout the
+        evolution. This constraint equates to $A_i > \max A_I + A_{II}$,
+        whereupon no separatrix encounter occurs at all.
+\end{itemize}
+In summary, the five regimes of track possibilities in increasing order of $A_i$
+are:
+\begin{itemize}
+    \item $II \to III, II \to I$ both possible, $A_i < A_{II}\p{\eta_{\min,
+        III}}$.
+
+    \item $II \to I$ only, $A_{II}\p{\eta_{\min, III}} < A_i < A_{II}(\eta_c)$.
+
+    \item $III \to I, III \to II \to I$ both possible, $A_{II}(\eta_c) < A_i <
+        A_{II, \max}$.
+
+    \item $III \to I$ only, $A_{II, \max} < A_i < \max A_I + A_{II}$.
+
+    \item $III \to III$ only, $A_i > \max A_I + A_{II}$.
+\end{itemize}
 \begin{figure}
@@
     \end{subfigure}
-    \caption{Fiducial simulation following the $A_{II} \to A_{I}$ transition. Top
-    plot upper panel: plot of $\cos \theta(t)$ (gold) in an example simulation.
-    Overlaid are the locations of Cassini State 2 (magenta), and upper and lower
-    bounds on the separatrix (dashed black). Note that the trajectory
+    \caption{Fiducial simulation following the $A_{II} \to A_{I}$ transition.
+    Top plot upper panel: plot of $\cos \theta(t)$ (gold) in an example
+    simulation. Overlaid are the locations of Cassini State 2 (magenta), and
+    upper and lower bounds on the separatrix (black). Note that the trajectory
     successfully tracks CS2 to a misalignment angle $\theta \approx 90^\circ$.
@@
     are shown in solid/dashed black lines respectively. Also labeled is CS2
-    (magenta).}\label{fig:ad_21}
+    (magenta). Finally, the enclosed phase space area is shaded in grey ($A >
+    0$) and red ($A < 0$).}\label{fig:ad_21}
+\end{figure}
+\begin{figure}
+    \centering
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23.png}
+    \end{subfigure}
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23_subplots.png}
+    \end{subfigure}
+    \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ track.
+    }\label{fig:ad_23}
+\end{figure}
+\begin{figure}
+    \centering
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31.png}
+    \end{subfigure}
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31_subplots.png}
+    \end{subfigure}
+    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_I$
+    track.}\label{fig:ad_31}
+\end{figure}
+\begin{figure}
+    \centering
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321.png}
+    \end{subfigure}
+    \begin{subfigure}{\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321_subplots.png}
+    \end{subfigure}
+    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_{II} \to A_I$
+    track. Two separatrix crossings are shown.}\label{fig:ad_321}
 \end{figure}
@@
 
-In the adiabatic limit, while separatrix encounters induce discontinuous changes
-in enclosed phase space, the outcomes of these encounters are well understood in
-pioneering work by Henrard \citep{henrard1982,henrard1987}. For a wide range of
-$\theta_{sd, i}$, we run simulations over a ring of initial conditions at each
-$\theta_{sd, i}$ and measure the final $\theta_{ f}$ values. We can also
-predict the values of $\theta_{ f}$ for each of the tracks as
-well as their associated probabilities; refer to \autoref{ss:app_transition} for
-details. The comparison of the final obliquities associated with these tracks
-and those obtained via simulation can be seen in \autoref{fig:ad_ensemble}. The
-same plot for $I = 10^\circ, I = 20^\circ$ can be found in
-\autoref{ss:varying_I}.
+Next, we will consider the evolution of a system with arbitrary $\theta_{sd, i}$
+starting in the $\eta \gg 1$ regime. By evolving such systems until $\eta \ll
+1$, we can measure the final $\theta_f$ values and make comparisons with those
+obtained via the dynamical tracks above. Observe that when $\eta \gg 1$,
+trajectories librate with approximately constant $\theta_{sd}$, meaning they
+enclose phase space area
+\begin{equation}
+    A_i = 2\pi\p{1 - \cos \theta_{sd, i}}.\label{eq:ai_qsd}
+\end{equation}
+Thus, for a given $\theta_{sd, i}$, we know immediately which tracks are
+accessible and with what probability following the results of
+\autoref{ss:zone_transitions}.
+
+We run simulations over a ring of initial conditions at each $\theta_{sd, i}$
+and measure the final $\theta_{f}$ values. We use \autoref{eq:ai_qsd} to predict
+the final obliquities $\theta_f$ according to each of the dynamical tracks. The
+agreement of these predictions for $I = 5^\circ, 10^\circ, 20^\circ$ can be seen
+in \autoref{fig:ad_ensemble}, \autoref{fig:3_ensemble_10_35}, and
+\autoref{fig:3_ensemble_20_35}.
 \begin{figure}
@@
     dynamical tracks in colored lines. Bottom: Semi-analytic probabilities of
-    each of the dynamical tracks for each $\theta_{sd,
-    i}$.}\label{fig:ad_ensemble}
+    each of the dynamical tracks for each $\theta_{sd, i}$. The five regimes of
+    $\theta_{sd, i}$ values correspond to the five regimes of $A_i$ discussed in
+    \autoref{ss:zone_transitions} when using \autoref{eq:ai_qsd} to relate
+    $A_i\p{\theta_{sd, i}}$. }\label{fig:ad_ensemble}
 \end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_10_35.png}
+    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
+    10^\circ$.}\label{fig:3_ensemble_10_35}
+\end{figure}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_20_35.png}
+    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
+    10^\circ$.}\label{fig:3_ensemble_20_35}
+\end{figure}
+
+\section{Nonadiabatic Effects}\label{s:nonad}
 
@@
 with increasingly larger values of $\epsilon$ than \autoref{fig:ad_ensemble}
-below in \autoref{fig:transition_to_nonad}.
+below in \autoref{fig:3_ensemble_05_25} and \autoref{fig:3_ensemble_05_15}.
 
@@
     \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
     \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_25.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
+    \caption{Same as \autoref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$.
+    A larger spread from the dynamical tracks is observed in the
+    data.}\label{fig:3_ensemble_05_25}
+\end{figure}
+\begin{figure}
     \centering
     \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_15.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_10.png}
-    \end{subfigure}
-    \caption{Increasingly larger $\epsilon$ used compared to those in
-    \autoref{fig:ad_ensemble}. The general evolutionary tracks in the adiabatic
-    limit deteriorate as $\epsilon$ is increased. Deviations from the adiabatic
-    predictions seem to be banded structures, which can be attributed to
+    \caption{Same as \autoref{fig:ad_ensemble} but for $\epsilon = 10^{-1.5}$.
+    Some small semblance of the evolutionary tracks remains, and the deviations
+    appear to have a banded structure. This can be attributed to
     non-adiabaticity ``freezing-in'' the phase of the obliquity variations over
     the final libration/circulation orbit prior to separatrix
-    crossing.}\label{fig:transition_to_nonad}
+    crossing.}\label{fig:3_ensemble_05_15}
 \end{figure}
 
-\section{Nonadiabatic Evolution}\label{s:nonad}
-
-Here, we consider $\epsilon \sim 0.2$ which significantly violates
-\autoref{eq:ad_constr}.
-
-\subsection{Sample Trajectory}
+\subsection{Strongly Nonadiabatic Fiducial Trajectory}
 
@@
 shown in \autoref{fig:nonad_3_scan}. Note that $\epsilon \to 0$ recovers the
-adiabatic regime.
+adiabatic regime. The deviation of $\theta_f$ from the analytical prediction
+within the adiabatic regime is indeed due to adiabatic effects becoming
+dominant; compare to \autoref{fig:nonad_3_scan_20} where little deviation is
+observed until $\theta_f \approx 90^\circ$.
 \begin{figure}
@@
     the adiabatic regime.}\label{fig:nonad_3_scan}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/2_toy2/3scan_20.png}
+    \caption{Same as \autoref{fig:nonad_3_scan} but for $I=20^\circ$. Note that
+    the analytical prediction is accurate until $\theta_f \approx 90^\circ$,
+    which occurs before the transition to the adiabatic
+    regime.}\label{fig:nonad_3_scan_20}
 \end{figure}
@@
 
-\subsection{Adiabatic Dynamical Histories}\label{ss:app_tracks}
+\subsection{Analytic $\theta_f$ for small $\theta_{sd,
+i}$}\label{ss:app_transition}
 
-\begin{itemize}
-    \item $A_{II} \to A_{I}$ --- \autoref{fig:ad_21}.
-    \item $A_{II} \to A_{III}$ --- \autoref{fig:ad_23}.
-    \item $A_{III} \to A_{I}$ --- \autoref{fig:ad_31}.
-    \item $A_{III} \to A_{II} \to A_{I}$ --- \autoref{fig:ad_321}.
-    \item $A_{III} \to A_{III}$ --- Trivial case, the initial enclosed area is
-        too large to ever experience a separatrix encounter.
-\end{itemize}
-\begin{figure}
-    \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23_subplots.png}
-    \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ track.
-    }\label{fig:ad_23}
-\end{figure}
-\begin{figure}
-    \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31_subplots.png}
-    \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_I$
-    track.}\label{fig:ad_31}
-\end{figure}
-\begin{figure}
-    \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321_subplots.png}
-    \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_{II} \to A_I$
-    track. Two separatrix crossings are shown.}\label{fig:ad_321}
-\end{figure}
+In this section, we will use approximations valid for small $\eta$ to derive
+analytic expressions for the final obliquities and associated probabilities for
+the $II \to I, II \to III$ tracks that govern behavior at small $\theta_{sd,
+i}$.
 
-\subsection{Adiabatic Tracks at Varying $I$}\label{ss:varying_I}
-
-See \autoref{fig:varying_i}.
-\begin{figure}
-    \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_10_35.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_20_35.png}
-    \end{subfigure}
-    \caption{Same as \autoref{fig:ad_ensemble} but for $I = 10^\circ$ (top) and
-    $I = 20^\circ$ (bottom).}\label{fig:varying_i}
-\end{figure}
-
-\subsection{$\theta_f$ for Adiabatic Tracks}\label{ss:app_transition}
-
-To understand how trajectories transition between zones, we must recall the
-result from \citep{henrard1982,henrard1987}: if a zone $i$ is shrinking and zone
-$j$ is expanding, the probability of transition from zone $i$ to zone $j$ is
-given
-\begin{equation}
-    \Pr_{i \Rightarrow j} = -\frac{\pd{A_j}{t}}{ \pd{A_i}{t}}
-        = -\frac{\pd{A_j}{\eta}}{ \pd{A_i}{\eta}}\label{eq:henrard_hop}
-\end{equation}
-This can be used directly in conjunction with \autoref{se:area_ward} to generate
-the probabilities in the bottom panel of \autoref{fig:ad_ensemble}.
-
-Next, we will compute an approximate closed form for the final obliquities for
-the initial conditions in zone II (which experience separatrix crossing at
-$\eta_\star \ll 1$), we first seek a simple parameterization for the separatrix.
-We first solve for equilibria of the equation of motion \autoref{eq:dsdt_base}
-to compute the coordinates for Cassini State 4:
+We first seek a simple parameterization for the separatrix. We first solve for
+equilibria of the equation of motion \autoref{eq:dsdt_base} to compute the
+coordinates for Cassini State 4:
 \begin{equation}
@@
             \cos \theta_{f, II \Rightarrow I} &\approx
-                &\approx\p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
+                \p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
                     + \frac{\theta_{sp, i}^2}{4},\\
             \cos \theta_{f, II \Rightarrow III} &\approx
-                &\approx\p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
+                \p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
                     - \frac{\theta_{sp, i}^2}{4}.

### 2019-10-10 initial/2_toy2/3_disk_disp.py

@@ -15,7 +15,7 @@ import pickle
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 plt.rc('text', usetex=True)
-plt.rc('font', family='serif', size=12)
+plt.rc('font', family='serif', size=18)
 
 PLOT_DIR = '1plots'
 from utils import to_cart, to_ang, roots, H, solve_ic_base,\
@@ -193,8 +193,8 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
 
     fig, (ax1, ax3) = plt.subplots(2, 1,
                             sharex=True,
+                            figsize=(6, 5),
                             gridspec_kw={'height_ratios': [3, 2]})
-    fig.subplots_adjust(hspace=0)
     t = ret.t
     etas = ret.y[3]
     q, phi = to_ang(*ret.y[0:3])
@@ -218,13 +218,13 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
                 f = lambda mu: -mu**2 / 2 + eta4s[i] * (
                     mu * np.cos(I) + np.sin(I) * np.sqrt(1 - mu**2))\
                     - H4s[i]
-                # mu_min always exists
+                # mu_min will always be < mu4, mu_max > mu4
                 mu_min[i] = opt.bisect(f, -1, mu4s[i])
-                # mu_max may not always exist
-                guess = mu4s[i] + np.sqrt(4 * eta4s[i] * np.sin(I))
-                res = opt.newton(f, guess)
-                if abs(res - mu_min[i]) > 1e-5: # not the same root
-                    mu_max[i] = res
+                # note mu_max may not exist, so push -1 if not
+                try:
+                    mu_max[i] = opt.bisect(f, mu4s[i], 1)
+                except ValueError:
+                    mu_max[i] = -1
             except:
                 pass
 
@@ -243,8 +243,8 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
     ax1.semilogx(etas, mu_dat, c='y', label='Sim')
     max_valid_idxs = np.where(mu_max > 0)[0]
     ax1.semilogx(etas[idx4s][max_valid_idxs], mu_max[max_valid_idxs],
-             'k:', label='Sep')
-    ax1.semilogx(etas[idx4s], mu_min, 'k:')
+             'k', label='Sep')
[…]

### 2019-10-10 writeups/Su_disk_disp.tex
oops needed to address a few more TODOs

@@
     \end{subfigure}
-    \caption{Fiducial simulation following the $A_{II} \to A_{I}$ transition.
-    Top plot upper panel: plot of $\cos \theta(t)$ (gold) in an example
-    simulation. Overlaid are the locations of Cassini State 2 (magenta), and
-    upper and lower bounds on the separatrix (black). Note that the trajectory
-    successfully tracks CS2 to a misalignment angle $\theta \approx 90^\circ$.
-    Vertical green lines denote times portrayed in bottom plot. Top plot lower
-    panel: plot of the enclosed separatrix area obtained by integrating the
-    simulated trajectory (blue dots) and adiabatic theory (red line). Lower
-    plot: snapshots in the $\p{\cos \theta, \phi}$ space of the simulation
-    trajectories for the times demarcated in green above, corresponding to the
-    start of the simulation, the appearance of the separatrix, two panels
-    depicting the separatrix crossing process, and a final snapshot at $\eta =
-    10^{-3.5}$. Gold dots denote a full circulation or libration cycle at the
-    selected time, while the separatrix at the start/end of the portrayed cycle
-    are shown in solid/dashed black lines respectively. Also labeled is CS2
-    (magenta). Finally, the enclosed phase space area is shaded in grey ($A >
-    0$) and red ($A < 0$).}\label{fig:ad_21}
+    \caption{Fiducial simulation following the $A_{II} \to A_{I}$ transition. An
+    initial $\theta_{sd, i} = 0.3\;\mathrm{rad} \approx 17.2^\circ$ was used, as
+    well as $\epsilon = 3 \times 10^{-4}$. Top plot upper panel: plot of $\cos
+    \theta(t)$ (gold) in an example simulation. Overlaid are the locations of
+    Cassini State 2 (magenta), and upper and lower bounds on the separatrix
+    (black). Note that the trajectory successfully tracks CS2 to a misalignment
+    angle $\theta \approx 90^\circ$. Vertical green lines denote times portrayed
+    in bottom plot. Top plot lower panel: plot of the enclosed separatrix area
+    obtained by integrating the simulated trajectory (blue dots) and adiabatic
+    theory (red line). Lower plot: snapshots in the $\p{\cos \theta, \phi}$
+    space of the simulation trajectories for the times demarcated in green
+    above, corresponding to the start of the simulation, the appearance of the
+    separatrix, two panels depicting the separatrix crossing process, and a
+    final snapshot at $\eta = 10^{-3.5}$. Gold dots denote a full circulation or
+    libration cycle at the selected time, while the separatrix at the start/end
+    of the portrayed cycle are shown in solid/dashed black lines respectively.
+    Also labeled is CS2 (magenta). Finally, the enclosed phase space area is
+    shaded in grey ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
 \end{figure}
@@
     \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ track.
-    }\label{fig:ad_23}
+    $\theta_{sd, i} = 0.3\;\mathrm{rad} \approx 17.2^\circ$, and $\epsilon =
+    3.01 \times 10^{-4}$.}\label{fig:ad_23}
 \end{figure}
@@
     \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_I$
-    track.}\label{fig:ad_31}
+    track. $\theta_{sd, i} = 89.1^\circ$, and $\epsilon = 3.01 \times
+    10^{-4}$.}\label{fig:ad_31}
 \end{figure}
@@
     \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_{II} \to A_I$
-    track. Two separatrix crossings are shown.}\label{fig:ad_321}
+    track. $\theta_{sd, i} = 60^\circ$, and $\epsilon = 3.14 \times 10^{-4}$.
+    Two separatrix crossings are shown.}\label{fig:ad_321}
 \end{figure}
@@
 obtained via the dynamical tracks above. Observe that when $\eta \gg 1$,
-trajectories librate with approximately constant $\theta_{sd}$, meaning they
-enclose phase space area
+trajectories librate about $\hat{l}_d$, or equivalently CS2, with approximately
+constant $\theta_{sd}$, meaning they enclose phase space area
 \begin{equation}
@@
 We run simulations over a ring of initial conditions at each $\theta_{sd, i}$
-and measure the final $\theta_{f}$ values. We use \autoref{eq:ai_qsd} to predict
-the final obliquities $\theta_f$ according to each of the dynamical tracks. The
-agreement of these predictions for $I = 5^\circ, 10^\circ, 20^\circ$ can be seen
-in \autoref{fig:ad_ensemble}, \autoref{fig:3_ensemble_10_35}, and
-\autoref{fig:3_ensemble_20_35}.
+and measure the final $\theta_{f}$ values. Since we start with finite $\eta$, we
+use the angular distance to CS2 as a proxy for $\theta_{sd, i}$, as it is the
+correct quantity to use to make \autoref{eq:ai_qsd} hold exactly. We use
+\autoref{eq:ai_qsd} to predict the final obliquities $\theta_f$ according to
+each of the dynamical tracks. The agreement of these predictions for $I =
+5^\circ, 10^\circ, 20^\circ$ can be seen in \autoref{fig:ad_ensemble},
+\autoref{fig:3_ensemble_10_35}, and \autoref{fig:3_ensemble_20_35}.
 \begin{figure}

### 2019-10-10 initial/2_toy2/3_disk_disp.py

@@ -200,12 +200,16 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
     q, phi = to_ang(*ret.y[0:3])
 
     # calculate separatrix min/max mu @ phi = pi
-    idx4s = np.where(etas < get_etac(I))[0]
-    eta4s = etas[idx4s]
-    q4s, q2s = np.zeros_like(eta4s), np.zeros_like(eta4s)
+    eta4s = etas[np.where(etas < get_etac(I))[0]]
+    eta2s = etas[np.where(etas > get_etac(I))[0]]
+    q4s = np.zeros_like(eta4s)
+    q2s = np.zeros_like(etas)
+    for i, eta in enumerate(eta2s):
+        q2, _ = roots(I, eta)
+        q2s[i] = q2
     for i, eta in enumerate(eta4s):
         _, q2, _, q4 = roots(I, eta)
-        q2s[i] = q2
+        q2s[i + len(eta2s)] = q2
         q4s[i] = q4
     mu4s = np.cos(q4s)
     H4s = H(I, eta4s, q4s, 0)
@@ -242,10 +246,10 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
 
     ax1.semilogx(etas, mu_dat, c='y', label='Sim')
     max_valid_idxs = np.where(mu_max > 0)[0]
-    ax1.semilogx(etas[idx4s][max_valid_idxs], mu_max[max_valid_idxs],
+    ax1.semilogx(eta4s[max_valid_idxs], mu_max[max_valid_idxs],
              'k', label='Sep')
-    ax1.semilogx(etas[idx4s], mu_min, 'k')
-    ax1.semilogx(etas[idx4s], np.cos(q2s), 'm', label='CS2')
+    ax1.semilogx(eta4s, mu_min, 'k')
+    ax1.semilogx(etas, np.cos(q2s), 'm', label='CS2')
     ax1.set_xlabel(r'$t$')
     ax1.set_ylabel(r'$\cos\theta$')
 

### 2019-10-15 writeups/Su_disk_disp.tex
new adiabaticity criterion?

@@
 \begin{equation}
-    H\p{\phi, \theta} = -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
+    \mathcal{H}\p{\theta, \phi} = -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
         + \eta \p{\hat{s} \cdot \hat{l}_d}.\label{eq:H}
@@
 $\theta, \phi$ are the polar and azimuthal angle of $\hat{s}$. By convention, we
-choose $\hat{l}_z$ at coordinates $\theta = I, \phi = \pi$.
+choose $\hat{l}_z$ at coordinates $\theta = I, \phi = \pi$, in which case the
+Hamiltonian can be written
+\begin{equation}
+    \mathcal{H} = -\frac{1}{2}\cos^2\theta
+        + \eta \p*{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
+\end{equation}
+
+Note that $\p{\cos \theta, \phi}$ form a canonically conjugate pair of variables
+describing $\hat{s}$. The equations of motion for these variables can be derived
+by taking derivatives of $\mathcal{H}$ given by \autoref{eq:H} and agree with
+\autoref{eq:dsdt_base}:
+\begin{subequations}\label{se:H_eom}
+    \begin{align}
+        \pd{\phi}{t} = \pd{\mathcal{H}}{(\cos\theta)}
+            &= -\cos\theta + \eta\p{\cos I + \sin I \cot \theta \cos \phi},\\
+        \pd{(\cos \theta)}{t} = -\pd{\mathcal{H}}{\phi}
+            &= -\eta \sin I \sin \theta \sin \phi.
+    \end{align}
+\end{subequations}
+While these equations are numerically stiff owing to the $\cot\theta$ term, they
+are the most intuitive description for analytical work.
 
@@
 Spin states satisfying $\rd{\hat{s}}{t} = 0$ are referred to as \emph{Cassini
-States} (CS). When $\eta < \eta_c$, there are four CSs, and when $\eta > \eta_c$
-there are only two; $\eta_c$ is \citep{henrard1987,ward2004I}
+States} (CSs). There are either two or four solutions, depending on the values
+of $\eta, I$. Following standard convention and nomenclature (see
+\autoref{fig:cs_locs}), CSs 1, 3, 4 have $\phi = 0, \theta < 0$ and CS2 has
+$\phi = \pi, \theta > 0$. Of these, CSs 1, 2, 3 are stable while CS4 is
+unstable.
+
+When $\eta < \eta_c$, where
 \begin{equation}
-    \eta_c \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{3/2}.
+    \eta_c \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{-3/2},
 \end{equation}
-CSs 1, 2, 3 are stable while CS4 is unstable.
-
-The locations of the $\cos\theta$ of the two/four CSs as a function of $\eta$ is
+all four CSs exist, and when $\eta > \eta_c$, only CSs 2, 3 exist
+\citep{henrard1987,ward2004I}. The CS obliquities as a function of $\eta$ are
 provided in \autoref{fig:cs_locs}.
@@
 
-In the four-CS regime, one of the CSs is a saddle point, conventionally denoted
-Cassini State 4 (CS4). All trajectories are periodic with finite period except
-two critical trajectories asymptotic in the past and future to CS4. Together,
-these two critical trajectories are referred to as the \emph{separatrix} and
-divide phase space into three zones. The separatrix and three zones are most
-clearly shown via a contour plot of $H\p{\phi, \cos \theta}$ in
+When $\eta < \eta_c$, CS4 exists and is a saddle point. All trajectories are
+periodic with finite period except two critical trajectories asymptotic in the
+past and future to CS4. Together, these two critical trajectories are referred
+to as the \emph{separatrix} and divide phase space into three zones. The
+separatrix, three zones, and their relations to the CSs are most clearly shown
+via a contour plot of $\mathcal{H}\p{\phi, \cos \theta}$ in
 \autoref{fig:eq_1contours}.
@@
     \includegraphics[width=0.8\textwidth]{../initial/0_eta/1contours_flip.png}
-    \caption{Contour plot of $H\p{\phi, \cos \theta}$, where warmer colors
-    denote more positive values. The black solid line is the separatrix, which
-    only exists for $\eta < \eta_c$. The three zones, divided by the separatrix,
-    are labeled. The interior of the separatrix, shaded in grey, is formally
-    only defined for $\eta < \eta_c$, but we may identify the phase space
-    trajectories that flow into zone II when evolved forward in time; this is
-    the shaded region in the top left plot, bounded by the dotted black
+    \caption{Contour plot of $\mathcal{H}\p{\phi, \cos \theta}$, where warmer
+    colors denote more positive values. The black solid line is the separatrix,
+    which only exists for $\eta < \eta_c$. The three zones, divided by the
+    separatrix, are labeled. The interior of the separatrix, shaded in grey, is
+    formally only defined for $\eta < \eta_c$, but we may identify the phase
+    space trajectories that flow into zone II when evolved forward in time; this
+    is the shaded region in the top left plot, bounded by the dotted black
     line.}\label{fig:eq_1contours}
@@
 
-As trajectories of constant $\eta$ evolve along
-contours of constant $H$, it can be observed that trajectories in zone II
-librate about CS2 while those in zones I/III circulate.
+As trajectories of constant $\eta$ evolve along contours of constant
+$\mathcal{H}$, it can be observed that trajectories in zone II librate about CS2
+while those in zones I/III circulate.
 
-The unsigned areas of the three zones are known exactly in literature
+The unsigned areas of the three zones are known exactly
 \citep{henrard1987,ward2004I}. Defining
@@
 
-One criterion for adiabaticity is that the separatrix crossing timescale be
-longer than the the resonant libration period \citep{ward2004I}. This is
-evaluated in~\cite{millholland_disk}, and in our problem reduces to
-\begin{equation}
-    \at{\rd{\eta}{t}}_{cross} = -\epsilon\eta_\star \gtrsim
-        -\sin\theta \sin I \cos I.\label{eq:ad_constr}
-\end{equation}
+One necessary criterion for adiabaticity is that the separatrix crossing
+timescale be longer than the the resonant libration period \citep{ward2004I}.
+The resonant libration period is just the libration period about CS2, which can
+be found by linearizing \autoref{se:H_eom} about $\phi \approx \pi, \theta
+\approx \theta_2$. The resulting criterion is
+\begin{align}
+    -\at{\frac{1}{\eta}\rd{\eta}{\tau}}_{cross} = \epsilon &\lesssim
+            \frac{2\pi}{T_{lib}},\\
+        &\lesssim \sqrt{\eta_\star\sin\theta \sin I
+            \p{1 + \eta_\star \frac{\sin I}{\sin^3\theta}}}.\label{eq:ad_constr}
+\end{align}
 Note that this is a necessary but not sufficient criterion: the libration period
 is longer for trajectories nearer the separatrix and diverges at the separatrix
-for constant $\eta$.
+for constant $\eta$. This formula also is in slight disagreement with that
+presented in \citealt{millholland_disk}
 
@@
 Note that $\phi_4 = 0$. Then, the separatrix is the level curve of the
-Hamiltonian intersecting CS4, so it satisfies $H\p{\theta_{sep}(\phi), \phi} =
-H\p{\theta_4, \phi_4}$. This solves to be approximately
+Hamiltonian intersecting CS4, so it satisfies $\mathcal{H}\p{\theta_{sep}(\phi),
+\phi} = \mathcal{H}\p{\theta_4, \phi_4}$. This solves to be approximately
 \begin{equation}

### 2019-10-15 initial/2_toy2/3_disk_disp.py

@@ -702,7 +702,8 @@ def plot_ICs(I, eta0, dqs, n_pts):
 
 def sim_for_many(I, eps=-1e-3, eta0_mult=10, etaf=1e-3, n_pts=21, n_dqs=51,
                  adiabatic=True, two_panel=True,
-                 dqmin=0.05, dqmax = 0.99 * np.pi / 2):
+                 dqmin=0.05, dqmax = 0.99 * np.pi / 2, dqmax2 = np.pi,
+                 extra_plot=False):
     '''
     variable number of points per ring,
     starting from n_pts/4 to n_pts linearly over dqs
@@ -712,22 +713,36 @@ def sim_for_many(I, eps=-1e-3, eta0_mult=10, etaf=1e-3, n_pts=21, n_dqs=51,
     I_deg = round(np.degrees(I))
     eps_log = 10 * (-np.log10(-eps))
     eta0 = eta0_mult * get_etac(I)
-    dqs = np.linspace(dqmin, dqmax, n_dqs)
+    dqs1 = np.linspace(dqmin, dqmax, n_dqs)
+    dqs2 = np.linspace(dqmax, dqmax2, n_dqs)[1: ]
 
     PKL_FN = '3dat%02d_%02d.pkl' % (I_deg, eps_log)
+    PKL_FN2 = '3dat%02d_%02d_2.pkl' % (I_deg, eps_log)
     filename = '3_ensemble_%02d_%02d' % (I_deg, eps_log)
     title = r'$I = %d^\circ, \epsilon = 10^{-%.1f}$' % (I_deg, eps_log / 10)
 
-    # run/plot sim
+    # run sim (HACK HACK two separate saves since I ran them separately)
     if not os.path.exists(PKL_FN):
         p = Pool(4)
-        args = [(I, eps, eta0_mult, etaf, n_pts, dq) for dq in dqs]
-        res_arr = p.starmap(sim_for_dq, args)
+        args = [(I, eps, eta0_mult, etaf, n_pts, dq) for dq in dqs1]
+        res_arr1 = p.starmap(sim_for_dq, args)
         with open(PKL_FN, 'wb') as f:
-            pickle.dump(res_arr, f)
+            pickle.dump(res_arr1, f)
     else:
         with open(PKL_FN, 'rb') as f:
-            res_arr = pickle.load(f)
+            res_arr1 = pickle.load(f)
+    if extra_plot:
+        if not os.path.exists(PKL_FN2):
+            p = Pool(4)
[…]

### 2019-10-15 writeups/Su_disk_disp.tex
probabilities are now being overplotted, as well as III -> III

@@
 
-\section{Equations}\label{s:eq}
+\section{Theory}\label{s:eq}
 
-Denote $\vec{s}$ spin of planet, $\vec{l}$ angular momentum of planet, and
-$\vec{l}_d$ angular momentum of the surrounding disc. We approximate $S \ll L
-\ll L_d$, so $\vec{l}_d$ is approximately constant. Much of this treatment
-borrows from \citealp{anderson2018teeter} and \citealp{millholland_disk}. We
-consider precession equations
+\subsection{Equations of Motion}
+
+Denote $\hat{s}$ spin of planet, $\hat{l}$ angular momentum of planet, and
+$\hat{l}_d$ angular momentum of the surrounding disc. We approximate $S \ll L
+\ll L_d$, so $\hat{l}_d$ is approximately constant and $\hat{l}$ experiences
+negligible backreaction torque from $\hat{s}$. Much of this treatment borrows
+from \citealp{anderson2018teeter} and \citealp{millholland_disk}. We consider
+precession equations
 \begin{align}
@@
     \rd{\hat{l}}{t} &= \omega_{ld}\p{\hat{l} \cdot \hat{l}_d}
-        \p{\hat{l} \times \hat{l}_d},\label{eq:dldt}\\
+        \p{\hat{l} \times \hat{l}_d}\label{eq:dldt}.
 \end{align}
@@
 
-We go to the corotating frame with $\hat{l}$ fixed such that $\hat{z} =
-\hat{l}$ ($\theta$ is now conveniently also the polar component of $\hat{s}$).
-The evolution of $\hat{s}$ in this corotating frame is governed by:
+Let us transform to frame rotating about $\hat{l}_p$ with frequency $g \equiv
+-\omega_{ld}\cos I < 0$, where $\hat{l}$ fixed. In this frame, $\hat{l}_p$
+also remains fixed and $\hat{s}$ evolves as:
 \begin{equation}
@@
             \p{\hat{s} \times \hat{l}}
-        - \abs{g}\p{\hat{s} \times \hat{l}_d}.
+        + g\p{\hat{s} \times \hat{l}_d},
 \end{equation}
-$\alpha = \omega_{sl} > 0, g \equiv -\omega_{ld}\cos I < 0$ follow traditional
-sign conventions.
-
-We divide through by $\alpha$ and define parameter $\eta$ and nondimensionalized
-time $\tau$
+where $\alpha \equiv \omega_{sl} > 0$ follows standard notation. By defining
+$\eta$ and nondimensionalized time $\tau$ as
 \begin{align}
     \eta &\equiv \frac{\abs{g}}{\alpha}\label{eq:eta},\\
-    \tau &\equiv \alpha t.
+    \tau &\equiv \alpha t,
 \end{align}
-The redimensionalized equation of motion is then
+we can non-dimensionalize the equation of motion as
 \begin{equation}
@@
 \end{equation}
-Equations \autoref{eq:dsdt_base} and \autoref{eq:deta_dt} constitute our system
+\autoref{eq:dsdt_base} and \autoref{eq:deta_dt} together constitute our system
 of study.
 
-Finally, the Hamiltonian corresponding to the equation of motion
-\autoref{eq:dsdt_base} is
-\begin{equation}
-    \mathcal{H}\p{\theta, \phi} = -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
-        + \eta \p{\hat{s} \cdot \hat{l}_d}.\label{eq:H}
-\end{equation}
-Here, we adopt a spherical coordinate system where $\hat{l} = \hat{z}$ and
-$\theta, \phi$ are the polar and azimuthal angle of $\hat{s}$. By convention, we
-choose $\hat{l}_z$ at coordinates $\theta = I, \phi = \pi$, in which case the
-Hamiltonian can be written
-\begin{equation}
-    \mathcal{H} = -\frac{1}{2}\cos^2\theta
-        + \eta \p*{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
-\end{equation}
+For analytical work, we adopt spherical coordinate system where $\hat{l} =
+\hat{z}$ and $\theta, \phi$ are the polar and azimuthal angle of $\hat{s}$. By
+convention, we choose $\hat{l}_z$ at coordinates $\theta = I, \phi = \pi$.
+Note that $\p{\cos \theta, \phi}$ form a canonically conjugate pair of variables
+describing $\hat{s}$. To derive equations of motion for these canonical
+coordinates, we introduce Hamiltonian
+\begin{align}
+    \mathcal{H}\p{\theta, \phi} &= -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
+            + \eta \p{\hat{s} \cdot \hat{l}_d}.\label{eq:H}\\
+        &= -\frac{1}{2}\cos^2\theta
+            + \eta \p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
+\end{align}
 
-Note that $\p{\cos \theta, \phi}$ form a canonically conjugate pair of variables
-describing $\hat{s}$. The equations of motion for these variables can be derived
-by taking derivatives of $\mathcal{H}$ given by \autoref{eq:H} and agree with
-\autoref{eq:dsdt_base}:
+The equations of motion follow by taking derivatives of $\mathcal{H}$ and agree
+with \autoref{eq:dsdt_base}:
 \begin{subequations}\label{se:H_eom}
@@
 \autoref{fig:cs_locs}), CSs 1, 3, 4 have $\phi = 0, \theta < 0$ and CS2 has
-$\phi = \pi, \theta > 0$. Of these, CSs 1, 2, 3 are stable while CS4 is
-unstable.
-
-When $\eta < \eta_c$, where
+$\phi = \pi, \theta > 0$. Of these, CSs 1, 2, 3 are stable while CS4 is unstable
+(this follows from linearization of \autoref{se:H_eom}). When $\eta < \eta_c$,
+where
 \begin{equation}
@@
 \citep{henrard1987,ward2004I}. The CS obliquities as a function of $\eta$ are
-provided in \autoref{fig:cs_locs}.
+shown in \autoref{fig:cs_locs}.
 \begin{figure}
@@
 
-When $\eta < \eta_c$, CS4 exists and is a saddle point. All trajectories are
-periodic with finite period except two critical trajectories asymptotic in the
-past and future to CS4. Together, these two critical trajectories are referred
-to as the \emph{separatrix} and divide phase space into three zones. The
-separatrix, three zones, and their relations to the CSs are most clearly shown
-via a contour plot of $\mathcal{H}\p{\phi, \cos \theta}$ in
-\autoref{fig:eq_1contours}.
+When $\eta < \eta_c$, CS4 exists and is a saddle point. The two trajectories
+originating and ending at CS4 are the only two infinite-period orbits in phase
+space. Together, these two critical trajectories are referred to as the
+\emph{separatrix} and divide phase space into three zones. The separatrix, three
+zones, and their relations to the CSs are shown in \autoref{fig:eq_1contours}.
+Note that trajectories in zone II librate about CS2 while those in zones I/III
+circulate.
 \begin{figure*}
@@
 \end{figure*}
-
-As trajectories of constant $\eta$ evolve along contours of constant
-$\mathcal{H}$, it can be observed that trajectories in zone II librate about CS2
-while those in zones I/III circulate.
 
@@
 it is in at $\eta_c$. Since phase space area is conserved under adiabatic
-evolution, this implies $A_i\p{\eta > \eta_c} = A_i(\eta_c)$.
+evolution, this implies $A_i\p{\eta > \eta_c} = A_i(\eta_c)$. This extension is
+also reflected in the dashed boundary in \autoref{fig:eq_1contours}.
 \begin{figure}
@@
 
-As $\eta$ decreases, the trajectory generally encounters the separatrix at some
-value $\eta_\star$ depending on its initial condition. If $\eta$ changes
-sufficiently little during this separatrix-crossing orbit, the evolution of the
-system is considered \emph{adiabatic}. In the truly adiabatic limit, $\epsilon
-\to 0$; we use $\epsilon = 3 \times 10^{-4}$ unless otherwise noted.
+A perturbation to a Hamiltonian system is considered \emph{adiabatic} if it is
+sufficiently slow compared to all other relevant time scales in the problem.
+In the current problem, the slowest time scale is the \emph{separatrix crossing
+time scale}: as $\eta$ evolves, a trajectory may encounter the separatrix at
+some value $\eta_\star$ which varies depending on its initial condition. If
+$\eta$ changes sufficiently little during the separatrix-crossing orbit, the
+evolution of the system may be considered adiabatic. The truly adiabatic limit
+corresponds to $\epsilon \to 0$; we take $\epsilon = 3 \times 10^{-4}$ unless
+otherwise noted.
 
-One necessary criterion for adiabaticity is that the separatrix crossing
-timescale be longer than the the resonant libration period \citep{ward2004I}.
-The resonant libration period is just the libration period about CS2, which can
-be found by linearizing \autoref{se:H_eom} about $\phi \approx \pi, \theta
-\approx \theta_2$. The resulting criterion is
+One criterion for adiabaticity is that the separatrix crossing timescale be
+longer than the the resonant libration period \citep{ward2004I}. The resonant
+libration period is just the libration period about CS2, which can be found by
+linearizing \autoref{se:H_eom} about CS2. This results in constraint
 \begin{align}
     -\at{\frac{1}{\eta}\rd{\eta}{\tau}}_{cross} = \epsilon &\lesssim
-            \frac{2\pi}{T_{lib}},\\
-        &\lesssim \sqrt{\eta_\star\sin\theta \sin I
+            \frac{1}{T_{lib}},\\
+        &\lesssim \frac{1}{2\pi}\sqrt{\eta_\star\sin\theta \sin I
             \p{1 + \eta_\star \frac{\sin I}{\sin^3\theta}}}.\label{eq:ad_constr}
 \end{align}
-Note that this is a necessary but not sufficient criterion: the libration period
-is longer for trajectories nearer the separatrix and diverges at the separatrix
-for constant $\eta$. This formula also is in slight disagreement with that
-presented in \citealt{millholland_disk}
+This formula differs from that presented in \citealt{millholland_disk}.
+
+\subsection{Dynamical Outcomes}\label{ss:ad_ensemble}
+
+We consider the evolution of a system with arbitrary initial $\theta_{sd, i}
+\equiv \theta_{sd}\p{t = 0}$ and $\eta_i \gg 1$. We are interested in the
+distribution of final $\theta_f$ values after $\eta$ decreases to $\eta_f \ll 1$
+(after the disk has dissipated to negligible mass). While it is likely that
+$\theta_{sd, i} \approx 0$ as the planet forms in the disk, we explore all
+$\theta_{sd, i} \in [0, \pi]$ for completeness.
+
+We evenly sample $101$ values of $\theta_{sd, i}$, and for each $\theta_{sd, i}$
+value, we pick $101$ $\hat{s}$ initial conditions on the ring fixed by
+$\theta_{sd, i}$. To be concrete, we choose $\eta_i = 10\eta_c$. For each
+initial condition, we evolve Equations~\ref{eq:dsdt_base} and~\ref{eq:deta_dt}
+until $\eta \leq 10^{-5}$, where $\hat{s}$ precesses about $\hat{l}$ with
+uniform final obliquity $\theta_f$. This transfer function
+$\theta_f\p{\theta_{sd, i}}$ is our primary result, and is shown for $I =
+5^\circ, 10^\circ, 20^\circ$ in \autoref{fig:ad_ensemble},
+\autoref{fig:3_ensemble_10_35}, and \autoref{fig:3_ensemble_20_35} respectively.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_35.png}
+    \caption{Top: $\theta_{f}\p{\theta_{sd, i}}$, overlaid with semi-analytic
+    predictions of the $\theta_{ f}$ for each of the four nontrivial
+    dynamical tracks in colored lines. Bottom: Semi-analytic probabilities of
+    each of the dynamical tracks for each $\theta_{sd, i}$. The five regimes of
+    $\theta_{sd, i}$ values correspond to the five regimes of $A_i$ discussed in
+    \autoref{ss:zone_transitions} when using \autoref{eq:ai_qsd} to relate
+    $A_i\p{\theta_{sd, i}}$. }\label{fig:ad_ensemble}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_10_35.png}
+    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
+    10^\circ$.}\label{fig:3_ensemble_10_35}
+\end{figure}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_20_35.png}
+    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
+    10^\circ$.}\label{fig:3_ensemble_20_35}
+\end{figure}
 
@@
 \end{equation*}
+
+Observe that when $\eta \gg 1$, trajectories librate about $\hat{l}_d$, or
+equivalently CS2, with approximately constant $\theta_{sd}$, meaning they
+enclose phase space area
+\begin{equation}
+    A_i = 2\pi\p{1 - \cos \theta_{sd, i}}.\label{eq:ai_qsd}
+\end{equation}
+In our simulations, we start with finite $\eta$, so we use the angular distance
+to CS2 instead of $\theta_{sd, i}$ above, as the trajectory initially librates
+about CS2 and not $\hat{l}_p$.
 
@@
     Two separatrix crossings are shown.}\label{fig:ad_321}
-\end{figure}
-
-\subsection{Dynamical Outcomes}\label{ss:ad_ensemble}
-
-Next, we will consider the evolution of a system with arbitrary $\theta_{sd, i}$
-starting in the $\eta \gg 1$ regime. By evolving such systems until $\eta \ll
-1$, we can measure the final $\theta_f$ values and make comparisons with those
-obtained via the dynamical tracks above. Observe that when $\eta \gg 1$,
-trajectories librate about $\hat{l}_d$, or equivalently CS2, with approximately
-constant $\theta_{sd}$, meaning they enclose phase space area
-\begin{equation}
-    A_i = 2\pi\p{1 - \cos \theta_{sd, i}}.\label{eq:ai_qsd}
-\end{equation}
-Thus, for a given $\theta_{sd, i}$, we know immediately which tracks are
-accessible and with what probability following the results of
-\autoref{ss:zone_transitions}.
-
-We run simulations over a ring of initial conditions at each $\theta_{sd, i}$
-and measure the final $\theta_{f}$ values. Since we start with finite $\eta$, we
-use the angular distance to CS2 as a proxy for $\theta_{sd, i}$, as it is the
-correct quantity to use to make \autoref{eq:ai_qsd} hold exactly. We use
-\autoref{eq:ai_qsd} to predict the final obliquities $\theta_f$ according to
-each of the dynamical tracks. The agreement of these predictions for $I =
-5^\circ, 10^\circ, 20^\circ$ can be seen in \autoref{fig:ad_ensemble},
-\autoref{fig:3_ensemble_10_35}, and \autoref{fig:3_ensemble_20_35}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_35.png}
-    \caption{Top: $\theta_{f}\p{\theta_{sd, i}}$, overlaid with semi-analytic
-    predictions of the $\theta_{ f}$ for each of the four nontrivial
-    dynamical tracks in colored lines. Bottom: Semi-analytic probabilities of
-    each of the dynamical tracks for each $\theta_{sd, i}$. The five regimes of
-    $\theta_{sd, i}$ values correspond to the five regimes of $A_i$ discussed in
-    \autoref{ss:zone_transitions} when using \autoref{eq:ai_qsd} to relate
-    $A_i\p{\theta_{sd, i}}$. }\label{fig:ad_ensemble}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_10_35.png}
-    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
-    10^\circ$.}\label{fig:3_ensemble_10_35}
-\end{figure}
-\begin{figure}
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_20_35.png}
-    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
-    10^\circ$.}\label{fig:3_ensemble_20_35}
 \end{figure}

### 2019-10-17 writeups/Su_disk_disp.tex
Modified a ton more plots

@@
 
-% TODO
-% figure out whether can draw vertical lines on 3testo plots for regimes
-% run simulations up to III -> III (not today)
-
 \begin{abstract}
@@
 \end{align}
+% = 1/(152600 yr) (kp = 6kqp, Mstar = msun, mp = mJ, Rp = RJ, ap = AU, Wp = 2pi
+% / (10 days))
+% = 1 / (573362 yr) (Md/Mstar = 0.01, ap/rd = 1/30)
 In \autoref{eq:wsl}, $k_{qp}$ and $k_p$ are related to the planet's quadrupole
@@
 \begin{align}
-    \eta &\equiv \frac{\abs{g}}{\alpha}\label{eq:eta},\\
-    \tau &\equiv \alpha t,
+    \eta \equiv{}& \frac{\abs{g}}{\alpha}\label{eq:eta},\\
+        ={}& 3.75 \p{\frac{k_p}{6k_{qp}}}
+            \p{\frac{m_p}{0.001 M_\star}}
+            \p{\frac{a_p}{1\;\mathrm{AU}}\frac{R_J}{R_p}}^3
+            \p{\frac{2\pi/\p{10\;\mathrm{days}}}{\Omega_p}}\nonumber\\
+        &\p{\frac{M_d}{0.01 M_{\star}}}
+            \p{\frac{30 a_p}{r_d}}^3
+            \p{\frac{n}{2\pi / \p{1\;\mathrm{yr}}}}
+            \p{\frac{\cos I}{\cos 5^\circ}},\nonumber\\
+    \tau \equiv{}& \alpha t,
 \end{align}
@@
 As $\alpha$ is held constant, this equates to $\eta$ decaying as $\rd{\eta}{t} =
--\frac{\eta}{t_d}$ for some decay time $t_\eta$. We nondimensionalize by
-defining $\epsilon \equiv \frac{1}{\alpha t_\eta}$, so
-\begin{equation}
-    \rd{\eta}{\tau} = -\epsilon \eta.\label{eq:deta_dt}
-\end{equation}
+-\frac{\eta}{t_d}$ as well. We nondimensionalize:
+\begin{align}
+    \epsilon \equiv{}& \frac{1}{\alpha t_d},\\
+        ={}& 0.015 \p{\frac{k_p}{6k_{qp}}}
+            \p{\frac{m_p}{0.001 M_\star}}
+            \p{\frac{a_p}{1\;\mathrm{AU}}\frac{R_J}{R_p}}^3\nonumber\\
+        &\p{\frac{2\pi/\p{10\;\mathrm{days}}}{\Omega_p}}
+            \p{\frac{10\;\mathrm{Myr}}{t_d}},\\
+    \rd{\eta}{\tau} ={}& -\epsilon \eta.\label{eq:deta_dt}
+\end{align}
 \autoref{eq:dsdt_base} and \autoref{eq:deta_dt} together constitute our system
@@
     \includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs.png}
-    \caption{$\theta$ values of the Cassini states over time, following the same
-    coloring scheme as \autoref{fig:eq_1contours}. Note that $\theta \in [-\pi,
-    \pi]$ is the traditional definition of the polar angle
+    \caption{Cassini state obliquities as a function of $\eta$. Note that
+    $\theta \in [-\pi, \pi]$ is the traditional definition of the polar angle
     \citep[see e.g.][]{colombo1966,peale1969,henrard1987}.}\label{fig:cs_locs}
@@
 zones, and their relations to the CSs are shown in \autoref{fig:eq_1contours}.
-Note that trajectories in zone II librate about CS2 while those in zones I/III
-circulate.
+Note that trajectories in zone $II$ librate about CS2 while those in zones
+$I$/$III$ circulate.
 \begin{figure*}
@@
     which only exists for $\eta < \eta_c$. The three zones, divided by the
-    separatrix, are labeled. The interior of the separatrix, shaded in grey, is
-    formally only defined for $\eta < \eta_c$, but we may identify the phase
-    space trajectories that flow into zone II when evolved forward in time; this
-    is the shaded region in the top left plot, bounded by the dotted black
-    line.}\label{fig:eq_1contours}
+    separatrix, are labeled. The Cassini states are labeled and have the same
+    colors as \autoref{fig:cs_locs}. The interior of the separatrix, shaded in
+    grey, is formally only defined for $\eta < \eta_c$, but we may identify the
+    phase space trajectories that flow into zone $II$ when evolved forward in
+    time; this is the shaded region in the top left plot, bounded by the dotted
+    black line.}\label{fig:eq_1contours}
 \end{figure*}
@@
     \autoref{se:area_ward}. Dotted lines correspond to small $\eta$
-    approximations discussed in \autoref{ss:app_transition}. Dashed lines denote
-    effective values of $A_{II}, A_{III}$ for $\eta > \eta_c$, denoting the
-    area of points that would flow into either area under adiabatic decrease of
-    $\eta$ to below $\eta_c$.}\label{fig:eq_areas}
+    approximations discussed in \autoref{s:app_transition}. Dashed lines for
+    $\eta > \eta_c$ effective values of $A_{II}, A_{III}$ for $\eta > \eta_c$,
+    denoting the area of points that would flow into either area under adiabatic
+    decrease of $\eta$ to below $\eta_c$.}\label{fig:eq_areas}
 \end{figure}
@@
     -\at{\frac{1}{\eta}\rd{\eta}{\tau}}_{cross} = \epsilon &\lesssim
-            \frac{1}{T_{lib}},\\
+            \frac{1}{T_{lib}},\nonumber\\
         &\lesssim \frac{1}{2\pi}\sqrt{\eta_\star\sin\theta \sin I
@@
 
-\subsection{Dynamical Outcomes}\label{ss:ad_ensemble}
+\subsection{Adiabatic Evolution Outcomes}\label{ss:ad_ensemble}
 
 We consider the evolution of a system with arbitrary initial $\theta_{sd, i}
-\equiv \theta_{sd}\p{t = 0}$ and $\eta_i \gg 1$. We are interested in the
-distribution of final $\theta_f$ values after $\eta$ decreases to $\eta_f \ll 1$
-(after the disk has dissipated to negligible mass). While it is likely that
-$\theta_{sd, i} \approx 0$ as the planet forms in the disk, we explore all
-$\theta_{sd, i} \in [0, \pi]$ for completeness.
+\equiv \at{\theta_{sd}}_{t = 0}$ and $\eta_i \equiv \at{\eta}_{t = 0} \gg 1$. We
+are interested in the distribution of final obliquities after $\eta$ decreases
+to $\eta_f \ll 1$ (after the disk has dissipated to negligible mass). While it
+is likely that $\theta_{sd, i} \approx 0$ as the planet forms in the disk, we
+explore all $\theta_{sd, i} \in [0, \pi]$ for completeness.
 
 We evenly sample $101$ values of $\theta_{sd, i}$, and for each $\theta_{sd, i}$
-value, we pick $101$ $\hat{s}$ initial conditions on the ring fixed by
-$\theta_{sd, i}$. To be concrete, we choose $\eta_i = 10\eta_c$. For each
-initial condition, we evolve Equations~\ref{eq:dsdt_base} and~\ref{eq:deta_dt}
-until $\eta \leq 10^{-5}$, where $\hat{s}$ precesses about $\hat{l}$ with
-uniform final obliquity $\theta_f$. This transfer function
-$\theta_f\p{\theta_{sd, i}}$ is our primary result, and is shown for $I =
-5^\circ, 10^\circ, 20^\circ$ in \autoref{fig:ad_ensemble},
-\autoref{fig:3_ensemble_10_35}, and \autoref{fig:3_ensemble_20_35} respectively.
+value, we pick $101$ $\hat{s}$ initial conditions approximately on the ring
+fixed by $\theta_{sd, i}$\footnote{For each $\theta_{sd, i}$ we choose an
+initial condition on the libration cycle with initial condition $\p{\theta_2 +
+\theta_{sd, i}, \phi_2}$ (where $\p{\theta_2, \phi_2}$ are the coordinates of
+CS2), such that all initial conditions for a given $\theta_{sd, i}$ enclose the
+same initial phase space; see \autoref{sss:a_evo}.}. To be concrete, we choose
+$\eta_i = 10\eta_c$. For each initial condition, we evolve
+Equations~\ref{eq:dsdt_base} and~\ref{eq:deta_dt} until $\eta = 10^{-5}$. For
+such small $\eta$, $\hat{s}$ precesses about $\hat{l}$ with uniform final
+obliquity $\theta_f$. This transfer function $\theta_f\p{\theta_{sd, i}}$ is our
+primary result, and is shown for $I = 5^\circ, 10^\circ, 20^\circ$ in
+\autoref{fig:ad_ensemble}, \autoref{fig:3_ensemble_10_35}, and
+\autoref{fig:3_ensemble_20_35} respectively. The blue dots represent the results
+of the simulation, which are in excellent agreement with the colored tracks.
+These colored tracks are calculated semi-analytically using methods explained in
+the following section.
 
@@
     predictions of the $\theta_{ f}$ for each of the four nontrivial
-    dynamical tracks in colored lines. Bottom: Semi-analytic probabilities of
-    each of the dynamical tracks for each $\theta_{sd, i}$. The five regimes of
-    $\theta_{sd, i}$ values correspond to the five regimes of $A_i$ discussed in
-    \autoref{ss:zone_transitions} when using \autoref{eq:ai_qsd} to relate
-    $A_i\p{\theta_{sd, i}}$. }\label{fig:ad_ensemble}
+    dynamical tracks in colored lines. Black dotted lines correspond to
+    small-$\theta_{sd, i}$ predictions derived in \autoref{s:app_transition}.
+    Bottom: Semi-analytic probabilities of each of the dynamical tracks for each
+    $\theta_{sd, i}$. The five regimes of $\theta_{sd, i}$ values correspond to
+    the five regimes of $A_i$ discussed in \autoref{ss:zone_transitions}. Again,
+    black dotted lines correspond to simple analytic estimates. Vertical black
+    dashed lines correspond to the analytical predictions of where each
+    dynamical track is accessible, as described in
+    \autoref{ss:zone_transitions}.}\label{fig:ad_ensemble}
 \end{figure}
@@
     \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_20_35.png}
-    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
-    10^\circ$.}\label{fig:3_ensemble_20_35}
+    \caption{Same as \autoref{fig:ad_ensemble} but for $I = 20^\circ$. The $III
+    \to II \to I$ track is not visible since the maximum $A_{II}$ is very near
+    $\eta_c$ for $I = 20^\circ$.}\label{fig:3_ensemble_20_35}
 \end{figure}
 
-\subsection{Separatrix Crossing and Evolutionary Tracks
-}\label{ss:zone_transitions}
+\subsection{Adiabatic Evolution Theory}\label{ss:zone_transitions}
 
-In the limit $\eta \to 0$, zone II disappears and all trajectories circulate at
-constant final $\theta$ values, notated $\theta_f$. We run simulations that
-terminate at $\eta = 10^{-{-3.5}}$ and measure $\theta_{f}$. We vary the initial
-value of $\theta_{sd}$, notated $\theta_{sd, i}$, among our simulations.
+The evolutionary tracks that govern the behavior of $\theta_f\p{\theta_{sd,
+i}}$ correspond to particular sequences of separatrix crossings. Coarsely, they
+can be understood using a combination of (i) how the enclosed phase space area
+by the trajectory evolves across each separatrix crossing, and (ii) the
+associated probabilities with each separatrix crossing.
 
-In the absence of separatrix encounters, the enclosed phase space area $A \equiv
-\oint \cos\theta \;\mathrm{d}\phi$ is an adiabatic invariant. Here, we adopt
-convention where $A$ is a \emph{signed} area
+\subsubsection{Governing Principles: Evolution of $A$}\label{sss:a_evo}
+
+First, we consider how the enclosed phase space area by a trajectory evolves
+over time. In the absence of separatrix encounters, the enclosed phase space
+area $\oint \cos\theta \;\mathrm{d}\phi$ is an adiabatic invariant. In
+particular, we adopt convention where
 \begin{equation}
-    A = \oint \p{1 - \cos \theta}\;\mathrm{d}\phi.
+    A \equiv \oint \p{1 - \cos \theta}\;\mathrm{d}\phi.\label{eq:a_oint}
 \end{equation}
-This has the advantage of (i) having a removable singularity when the trajectory
-crosses $\cos \theta = 1$, and (ii) being easily expressible as combinations of
-the $A_i$ of \autoref{se:area_ward}. The bounds of the integral are either a
-libration ($\phi$ returns to its original value with the same $\dot{q\phi}$
-sign) or circulation cycle ($\phi$ advances to $\phi \pm 2\pi$). Note lastly
-that $A$ has simple physical interpretation of are enclosed on the unit sphere
-by $\hat{s}$ over one cycle measured relative to $+\hat{z}$:
+This definition of $A$ has the advantage of (i) being continuous at $\cos \theta
+= 1$, and (ii) being easily expressible as combinations of the $A_i$ of
+\autoref{se:area_ward}. The bounds of the integral are either a libration
+($\phi$ returns to its original value with the same $\dot{q\phi}$ sign) or
+circulation cycle ($\phi$ advances to $\phi \pm 2\pi$). Note lastly that $A$ has
+simple physical interpretation of are enclosed on the unit sphere by $\hat{s}$
+over one cycle measured relative to $+\hat{z}$:
 \begin{equation*}
@@
 
-Observe that when $\eta \gg 1$, trajectories librate about $\hat{l}_d$, or
-equivalently CS2, with approximately constant $\theta_{sd}$, meaning they
-enclose phase space area
+Observe that when $\eta_i \gg 1$, trajectories librate about $\hat{l}_d$ with
+constant $\theta_{sd}$, meaning they enclose initial phase space area
 \begin{equation}
-    A_i = 2\pi\p{1 - \cos \theta_{sd, i}}.\label{eq:ai_qsd}
+    A_i \equiv \at{A}_{t = 0}
+        = 2\pi\p{1 - \cos \theta_{sd, i}}.\label{eq:ai_qsd}
 \end{equation}
-In our simulations, we start with finite $\eta$, so we use the angular distance
-to CS2 instead of $\theta_{sd, i}$ above, as the trajectory initially librates
-about CS2 and not $\hat{l}_p$.
+Complications arise when considering finite $\eta_i$, as trajectories near CS2 or
+CS3 librate about these equilibria respectively, rather than $\hat{l}_d$, and
+\autoref{eq:ai_qsd} is no longer exact. In practice, \autoref{eq:ai_qsd} holds
+very well when defining $\theta_{sd, i}$ as the angular distance to CS2; an
+exception is discussed in \autoref{sss:evol_traj}.
 
-When a trajectory encounters the separatrix, $A$ will change discontinuously as
-the trajectory moves between zones, but its change is easily understood
-\citep{henrard1982}. We can classify trajectories by the separatrix encounters
-they undergo. Initially, in the $\eta > \eta_c$ regime, only zones $II, III$
-exist. Conversely, at the end of the simulation when $\eta \to 0$, only zones
-$I, III$ exist. Most simply, one might expect four sequences of transitions
-between zones (we call these dynamical ``tracks'') to manifest: from one of
-$\z{I, III}$ to one of $\z{II, III}$. In addition to these four tracks, a
-fifth track $III \to II \to I$ is observed.
-
-Beyond simply identifying the possible tracks, we may clearly delineate the
-initial conditions for which each track can be encountered. Separatrix crossing
-is a probabilistic process whose outcomes are well understood by
-\citealp{henrard1982,henrard1987}. Their resultss may be simply summarized as
-follows: if a zone $i$ is shrinking and zone $j$ is expanding, the probability
-of transition from zone $i$ to zone $j$ is given
-\begin{equation}
-    \Pr_{i \Rightarrow j} = -\frac{\pd{A_j}{t}}{ \pd{A_i}{t}}
-        = -\frac{\pd{A_j}{\eta}}{ \pd{A_i}{\eta}}\label{eq:henrard_hop}
-\end{equation}
-This can be used directly in conjunction with \autoref{se:area_ward} to
-understand for what initial conditions each track can be observed and with what
-probabilities.
-
-Below, we will describe the evolution of $A$ throughout each of the five tracks,
-as well as determine the initial conditions and probabilities associated with
-each track:
-\begin{itemize}
-    \item $II \to I$ --- This track is depicted in \autoref{fig:ad_21}.
-        $\hat{s}$ starts librating about CS2 in zone II, enclosing some initial
-        phase space area $A_i$. The trajectory is able to librate without
-        separatrix encounter until $A_{II}(\eta_\star) = A_i$. At this point, as
-        the trajectory transitions to a circulating trajectory in zone I
-        immediately bordering the separatrix, it will encompass
-        $-A_I(\eta_\star)$ phase space area. Conservation of phase space area
-        then predicts that as $\eta \to 0$, the final enclosed phase space area
-        will still be $A_f = -A_I$, and the final obliquity $\theta_f$ must be
-        given by
+Beginning at the last separatrix crossing, the final enclosed phase space area
+$A_f$ will be conserved for all time. As $\eta \to 0$, trajectories circulate at
+constant obliquity $\theta_f$, related to $A_f$ by
 \begin{equation}
@@
 
+$A$ is not conserved when the trajectory encounters the separatrix. Howover,
+its change is easily understood \citep{henrard1982}. In essence, when the
+trajectory crosses the separatrix, it continues to evolve adjacent to the
+separatrix. So if a separatrix crossing results in a zone I trajectory, the
+resultant $A$ can be approximated by integrating \autoref{eq:a_oint} along the
+upper leg of the separatrix. Pictorally, this can be seen in the bottom plots of
+\autoref{fig:ad_21}.
+
+\subsubsection{Governing Principles: Probabilistic Separatrix Crossing}
+
+When a trajectory experiences separatrix crossing, it transitions into nearby
+zones probabilistically. This process is well understood by
+\citealp{henrard1982,henrard1987}. Their results may be simply summarized as
+follows: if a zone $i$ is shrinking while adjacent zones $j, k$ are expanding
+such that the sum of their areas is constant, the probability of transition from
+zone $i$ to zone $j$ is given
+\begin{align}
+    \Pr\p{i \to j} = -\frac{\pd{A_j}{t}}{ \pd{A_i}{t}}
+        = -\frac{\pd{A_j}{\eta}}{ \pd{A_i}{\eta}},\\
+    \Pr\p{i \to k}
+        = -\frac{\pd{A_k}{\eta}}{ \pd{A_i}{\eta}}.\label{eq:henrard_hop}
+\end{align}
+Note that $\Pr \p{i \to j} + \Pr\p{i \to k} = 1$. This can be used directly in
+conjunction with \autoref{se:area_ward} to understand for what initial
+conditions each track can be observed and with what probabilities.
+
+As a particular example, consider a system in zone $II$ in panel (d) of
+\autoref{fig:eq_1contours}. As $\eta$ decreases, zone $II$ will shrink while
+zones $I$ and $III$ will expand until the trajectory. Suppose the trajectory
+exits zone $II$ at some $\eta_\star$, then the probability of a $II \to I$
+transition is $\Pr\p{II \to I} = -\frac{\dot{A}_{I}}{\dot{A}_{II}}$, while a $II
+\to III$ transition occurs with probability $\Pr\p{II \to III} =
+-\frac{\dot{A}_{III}}{\dot{A}_{II}}$.
+
+\subsubsection{Evolutionary Trajectories}\label{sss:evol_traj}
+
+Returning to the evolution of $\hat{s}$, we can classify trajectories by the
+separatrix encounters experienced. Initially, in the $\eta > \eta_c$ regime,
+only zones $II, III$ exist. Conversely, at the end of the simulation when $\eta
+\to 0$, only zones $I, III$ exist. Most simply, one might expect four sequences
+of transitions between zones (we call these dynamical ``tracks'') to manifest:
+from one of $\z{I, III}$ to one of $\z{II, III}$, where $III \to III$ is a
+trivial case (no separatrix encounter). In addition to these four tracks, a
+fifth track $III \to II \to I$ is observed. Below, we will describe the
+evolution of $A$ throughout each of the five tracks, as well as determine the
+initial conditions and probabilities associated with each track:
+\begin{itemize}
+    \item $II \to I$ --- An example trajectory following this track is depicted
+        in \autoref{fig:ad_21}. $\hat{s}$ starts librating about CS2 in zone
+        $II$, enclosing some initial phase space area $A_i$. The trajectory is
+        able to librate without separatrix encounter until $A_{II}(\eta_\star) =
+        A_i$. As the trajectory transitions to a circulating trajectory in zone
+        $I$ immediately bordering the separatrix, it will encompass
+        $-A_I(\eta_\star)$ phase space area. The final $\theta_f$ is then given
+        by \autoref{eq:qfaf}.
+
         This transition can only occur when the initial condition begins in zone
-        II, requiring $A_i < A_{II}(\eta_c)$, where $A_{II}(\eta_c)$ is known in
-        closed form \citep{ward2004I}
-        \begin{equation}
-            A_{II}\p{\eta_c} = 4\pi \s{
-                1 - \p{1 + \tan^{2/3}I}^{-3/2}}.
-        \end{equation}
-        Then, at some known $\eta_\star$ satisfying $A_{II}(\eta_\star) = A_i$,
-        the trajectory is ejected from the separatrix and enters zone I with
-        probability
-        \begin{equation}
-            \Pr_{II \to I} = -\at{\frac{\pd{A_I}{\eta}}{\pd{A_{II}}{\eta}}}
-                _{\eta_\star}.
-        \end{equation}
-        Note that since $\pd{A_i}{\eta} < 0$ everywhere, while
-        $\pd{A_{II}}{\eta} > 0$ at all possible $\eta_\star$ for an initial
-        condition starting in zone II, this track always has nonzero
-        probability.
+        II, requiring $A_i < A_{II}(\eta_c)$. Note $A_{II}(\eta_c)$ is given in
+        closed form in \citealt{ward2004I} but appears to be incorrect. Then, at
+        some known $\eta_\star$ satisfying $A_{II}(\eta_\star) = A_i$, the
+        trajectory is ejected from the separatrix following
+        \autoref{eq:henrard_hop}. Note that since $\pd{A_i}{\eta} < 0$
+        everywhere, while $\pd{A_{II}}{\eta} > 0$ at all possible $\eta_\star$
+        for an initial condition starting in zone $II$, this track always has
+        nonzero probability.
 
-    \item $II \to III$ --- This track is depicted in \autoref{fig:ad_23}. The
-        only difference from the previous track is that, upon separatrix
-        encounter, the trajectory follows the circulating trajectory in zone III
-        bordering the separatrix, upon which it will encompass $A_f =
-        A_I(\eta_\star) + A_{II}(\eta_\star)$. The final obliquity is still
-        given by \autoref{eq:qfaf}.
+    \item $II \to III$ --- An example trajectory following this track is
+        depicted in \autoref{fig:ad_23}. The only difference from the previous
+        track is that, upon separatrix encounter, the trajectory follows the
+        circulating trajectory in zone $III$ bordering the separatrix, upon
+        which it will encompass $A_f = A_I(\eta_\star) + A_{II}(\eta_\star)$.
+        The final obliquity is still given by \autoref{eq:qfaf}.
 
-        Again, this track can only occur when $A_i < A_{II}(\eta_c)$, and enters
-        zone III with probability
-        \begin{equation}
-            \Pr_{II \to III} = -\at{\frac{\pd{A_{III}}{\eta}}
-                {\pd{A_{II}}{\eta}}} _{\eta_\star}.
-        \end{equation}
-        Upon examination of \autoref{fig:eq_areas}, it is clear that
-        $\pd{A_{III}}{\eta} > 0$ for many $\eta$. Call
+        Again, this track can only occur when $A_i < A_{II}(\eta_c)$, but a
+        further constraint arises when we consider the transition probability
+        given by \autoref{eq:henrard_hop}. Upon examination of
+        \autoref{fig:eq_areas}, it is clear that $\pd{A_{III}}{\eta} > 0$ for
+        many $\eta$. Call
         \begin{equation}
@@
         then if $\eta_\star > \eta_{\min, III}$ then $\Pr_{II \to III} < 0$.
-        This is interpreted as a forbidden transition, and so $II \to III$ is
-        only a permitted dynamical track if $\eta_\star \in 0, \eta_{\min,
-        III}$.
+        This is understood as a forbidden transition, and so $II \to III$ is
+        only a permitted dynamical track if $\eta_\star <, \eta_{\min,
+        III}$, or $A_i < \min A_{III}$.
 
@@
         The trajectory encounters the separatrix when $A_I(\eta_\star) +
-        A_{II}(\eta_\star) = A_i$, upon which it transitions to a zone I
-        trajectory enclosing $A_f = -A_I$.
+        A_{II}(\eta_\star) = A_i$, upon which it transitions to a zone $I$
+        trajectory enclosing $A_f = -A_I$. Then, as always, the final obliquity
+        is given by \autoref{eq:qfaf}.
 
@@
         constrained by requiring its $A_i$ is sufficiently small it will
-        encounter the separatrix at all (if it is too large, it will never
-        encounter the separatrix, which we classify as a $III \to III$
-        transition below). This is written $A_i < \max A_I + A_{II} = 4\pi -
-        \min A_{III}$. Within these constraints, the zone transition occurs with
-        probability
-        \begin{equation}
-            \Pr_{III \to I} = -\at{\frac{\pd{A_I}{\eta}}{\pd{A_{III}}{\eta}}}
-                _{\eta_\star}.
-        \end{equation}
+        encounter the separatrix (if it is too large, it will never encounter
+        the separatrix, which is a $III \to III$ transition). This is written
+        $A_i < \max A_I + A_{II} = 4\pi - \min A_{III}$.
+
         Note that since $\pd{A_I}{\eta} < 0$ always while $\pd{A_{III}}{\eta} >
@@
 
-    \item $III \to II \to I$ --- This track is depicted in
-        \autoref{fig:ad_321}. The first separatrix encounter occurs at $\eta_1$
-        when $A_I(\eta_1) + A_{II}(\eta_1) = A_i$, upon which the trajectory
-        moves into zone II enclosing intermediate phase space area $A_m =
-        A_{II}(\eta_1)$. Examining \autoref{fig:eq_areas}, there exist values
-        $A$ for which $A_{II}(\eta) = A$ has multiple solutions. These are the
-        only values for which the $III \to II \to I$ transition is permitted.
-        Thus, as $\eta$ continues to decrease, a second $\eta_2$ value exists
-        for which $A_m = A_II(\eta_2)$, upon which the trajectory is ejected to
-        zone I and $A_f = -A_I(\eta_2)$. The final obliquity again then obeys
-        \autoref{eq:qfaf}.
+    \item $III \to II \to I$ --- This track is depicted in \autoref{fig:ad_321}.
+        The first separatrix encounter occurs at $\eta_1$ when $A_I(\eta_1) +
+        A_{II}(\eta_1) = A_i$, upon which the trajectory moves into zone $II$
+        enclosing intermediate phase space area $A_m = A_{II}(\eta_1)$.
+        Examining \autoref{fig:eq_areas}, there exist values $A$ for which
+        $A_{II}(\eta) = A$ has multiple solutions. These are the only values for
+        which the $III \to II \to I$ transition is permitted. Thus, as $\eta$
+        continues to decrease, a second $\eta_2$ value exists for which $A_m =
+        A_II(\eta_2)$, upon which the trajectory is ejected to zone $I$ and $A_f
+        = -A_I(\eta_2)$. The final obliquity again then obeys \autoref{eq:qfaf}.
 
@@
         occur over the same $A_{II}(\eta_c) < A_i < \max A_I + A_{II}$ interval.
-        Here, the transition probability for the initial $III \to II$ transition
-        is simply
-        \begin{equation}
-            \Pr_{III \to II} = -\at{\frac{\pd{A_II}{\eta}}{\pd{A_{III}}{\eta}}}
-                _{\eta_1}.
-        \end{equation}
-        It bears noting that this expression is only nonzero for a very small
-        fraction of $A_i$ values, since it requires $\pd{A_{II}}{\eta}$ and
-        $\pd{A_{III}}{\eta}$ to have different signs; this occurs only if
-        $A_{II}\p{\eta_c} < A_i < A_{II, \max}$. Outside of these bounds,
-        $\Pr_{III \to II} < 0$ which is interpreted again as a forbidden
-        transition.
+        The probability of encountering this track is set by the initial $III
+        \to II$ transition. It bears noting that this probability is only
+        nonnegative for a very small fraction of $A_i$ values, since it requires
+        $\pd{A_{II}}{\eta}$ and $\pd{A_{III}}{\eta}$ to have different signs;
+        this occurs only if $A_{II}\p{\eta_c} < A_i < A_{II, \max}$. Outside of
+        these bounds, $\Pr_{III \to II} < 0$ which is interpreted again as a
+        forbidden transition.
 
@@
         evolution. This constraint equates to $A_i > \max A_I + A_{II}$,
-        whereupon no separatrix encounter occurs at all.
+        whereupon no separatrix encounter occurs at all, and $A_f = A_i$, which
+        for $\eta_i \to \infty, \eta_f \to 0$ results in $\theta = \theta_{sd,
+        i}$.
+
+        Note that a small deviation from $\theta = \theta_{sd, i}$ occurs
+        because we use finite $\eta_i$, as hinted at in \autoref{sss:a_evo}.
+        This is because for $\theta_{sd, i} \gtrsim \pi/2$, trajectories are
+        better described as librating about CS3. Nevertheless, we can still
+        approximate $A_i$ to good accuracy as the solid angle enclosed by
+        libration about CS3 with polar angle $2\pi + \theta_3 - \theta_2 -
+        \theta_{sd, i}$. This recovers the correct transfer function
+        $\theta_f\p{\theta_{sd, i}}$ for the $III \to III$ regime, as can be
+        seen visibly in \autoref{fig:3_ensemble_20_35}.
 \end{itemize}
@@
 \begin{itemize}
-    \item $II \to III, II \to I$ both possible, $A_i < A_{II}\p{\eta_{\min,
-        III}}$.
+    \item $A_i \in \s{0, A_{II}\p{\eta_{\min, III}}}$: $II \to III, II \to I$
+        both possible.
 
-    \item $II \to I$ only, $A_{II}\p{\eta_{\min, III}} < A_i < A_{II}(\eta_c)$.
+    \item $A_i \in \s{A_{II}\p{\eta_{\min, III}}, A_{II}(\eta_c)}$: $II \to I$
+        only.
 
-    \item $III \to I, III \to II \to I$ both possible, $A_{II}(\eta_c) < A_i <
-        A_{II, \max}$.
+    \item $A_i \in \s{A_{II}(\eta_c), A_{II, \max}}$: $III \to I, III \to II \to
+        I$ both possible.
 
-    \item $III \to I$ only, $A_{II, \max} < A_i < \max A_I + A_{II}$.
+    \item $A_i \in \s{A_{II, \max}, \max A_I + A_{II}}$: $III \to I$ only.
 
-    \item $III \to III$ only, $A_i > \max A_I + A_{II}$.
+    \item $A_i > \max A_I + A_{II}$: $III \to III$ only.
 \end{itemize}
+The corresponding ranges for for $\theta_{sd,i}$ can be computed via
+\autoref{eq:ai_qsd}. The boundaries between these ranges are overplotted in
+\autoref{fig:ad_ensemble}, where they can be seen to agree well with numerical
+results.
 \begin{figure}
@@
     well as $\epsilon = 3 \times 10^{-4}$. Top plot upper panel: plot of $\cos
-    \theta(t)$ (gold) in an example simulation. Overlaid are the locations of
-    Cassini State 2 (magenta), and upper and lower bounds on the separatrix
-    (black). Note that the trajectory successfully tracks CS2 to a misalignment
-    angle $\theta \approx 90^\circ$. Vertical green lines denote times portrayed
+    \theta(t)$ (green) in an example simulation. Overlaid are the locations of
+    Cassini State 2 (red), and upper and lower bounds on the separatrix (black).
+    Note that the trajectory successfully tracks CS2 to a misalignment angle
+    $\theta \approx 90^\circ$. Light vertical blue lines denote times portrayed
     in bottom plot. Top plot lower panel: plot of the enclosed separatrix area
@@
     separatrix, two panels depicting the separatrix crossing process, and a
-    final snapshot at $\eta = 10^{-3.5}$. Gold dots denote a full circulation or
-    libration cycle at the selected time, while the separatrix at the start/end
-    of the portrayed cycle are shown in solid/dashed black lines respectively.
-    Also labeled is CS2 (magenta). Finally, the enclosed phase space area is
-    shaded in grey ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
+    final snapshot at $\eta = 10^{-3.5}$. The green line denotes a full
+    circulation or libration cycle at the selected time, including an arrow for
+    directionality. The separatrix at the start/end of the portrayed cycle are
+    shown in solid/dashed black lines respectively. Also labeled is CS2 at the
+    start of the cycle (red). Finally, the enclosed phase space area is shaded
+    in grey ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
 \end{figure}
@@
     \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ track.
-    $\theta_{sd, i} = 0.3\;\mathrm{rad} \approx 17.2^\circ$, and $\epsilon =
-    3.01 \times 10^{-4}$.}\label{fig:ad_23}
+    $\theta_{sd, i} = 0.3\;\mathrm{rad}$ and $\epsilon = 3.01 \times
+    10^{-4}$.}\label{fig:ad_23}
 \end{figure}
@@
 
-To illustrate the transition to non-adiabaticity, we present three simulations
+To illustrate the transition to non-adiabaticity, we present two simulations
 with increasingly larger values of $\epsilon$ than \autoref{fig:ad_ensemble}
@@
 near the tracks predicted from adiabatic evolution. These scatters first set in
-for trajectories starting in zone III, as these cross the separatrix at higher
+for trajectories starting in zone $III$, as these cross the separatrix at higher
 values of $\theta$ and have a stricter adiabaticity criterion (see
@@
 libration/circulation orbit at separatrix crossing. This is equivalent to
-separatrix crossing no longer being significantly slower than orbit timescales
-and violating the adiabatic assumption.
+separatrix crossing no longer being significantly slower than the resonant
+libration period and violating the adiabatic assumption.
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_25.png}
-    \caption{Same as \autoref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$.
-    A larger spread from the dynamical tracks is observed in the
-    data.}\label{fig:3_ensemble_05_25}
+    \caption{Same as \autoref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$,
+    and restricting $\theta_{sd, i} < 90^\circ$. A larger spread from the
+    dynamical tracks is observed in the data.}\label{fig:3_ensemble_05_25}
 \end{figure}
@@
     \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_15.png}
-    \caption{Same as \autoref{fig:ad_ensemble} but for $\epsilon = 10^{-1.5}$.
-    Some small semblance of the evolutionary tracks remains, and the deviations
-    appear to have a banded structure. This can be attributed to
+    \caption{Same as \autoref{fig:3_ensemble_05_25} but for $\epsilon =
+    10^{-1.5}$. Some small semblance of the evolutionary tracks remains, and the
+    deviations appear to have a banded structure. This can be attributed to
     non-adiabaticity ``freezing-in'' the phase of the obliquity variations over
@@
 
-\subsection{Strongly Nonadiabatic Fiducial Trajectory}
-
 A sample trajectory following in the style of \autoref{fig:ad_21} but for
-$\epsilon = 0.1$ is provided in \autoref{fig:nonad_traj}.
+$\epsilon = 0.3$ is provided in \autoref{fig:nonad_traj}. It is clear the
+trajectory does not track level curves of the Hamiltonian during each individual
+snapshot (e.g.\ the third snapshot).
 \begin{figure}
@@
     \end{subfigure}
-    \caption{Same as \autoref{fig:nonad_traj} but for a non-adiabatic $\epsilon =
-    0.1$. In the top panel of the top plot, it is evident that the libration
+    \caption{Same as \autoref{fig:ad_21} but for a non-adiabatic $\epsilon =
+    0.3$. In the top panel of the top plot, it is evident that the libration
     cycle about CS2 is unable to keep up with the swift motion of CS2 as $\eta$
@@
 
-\subsection{Dynamical Outcomes}
+\subsection{Non-adiabatic Evolution Outcomes}
 
 A formula for $\theta_{f}$ assuming $\theta_{sd, i} = 0$ initially can be
-given (see \autoref{ss:app_transition})
+given (see \autoref{s:app_transition})
 \begin{equation}
-    \theta_{f}\p{\theta_{sd, i} = 0} = \sqrt{\frac{2\pi \Omega}{\epsilon}}
-        \tan I.\label{eq:nonad_q_f}
+    \theta_{f}\p{\theta_{sd, i} = 0} = \sqrt{\frac{2\pi}{\epsilon}}
+        \tan I\cos I.\label{eq:nonad_q_f}
 \end{equation}
 We can naively generalize this by recognizing that any nonzero $\theta_{sd, i}$
-manifests as obliquity variations as $\hat{s}$ librates about $\hat{l}_d$, and
-these oscillations are ``frozen in'' when the disk dissipates. Thus,
+manifests as obliquity variations as $\hat{s}$ librates about $\hat{l}_d$. These
+can be accounted for by simply allowing the final obliquity to vary over the
+same range as the initial obliquity, or,
 \begin{equation}
-    \theta_{f}\p{\theta_{sd, i}} \in \sqrt{\frac{2\pi \Omega}{\epsilon}}
-        \tan I \pm \theta_{sd, i}.\label{eq:nonad_q_f_dist}
+    \theta_{f}\p{\theta_{sd, i}} - \sqrt{\frac{2\pi}{\epsilon}}
+        \tan I\cos I\in \s{-\theta_{sd, i}, \theta_{sd,i}}
+        .\label{eq:nonad_q_f_dist}
 \end{equation}
@@
     \caption{Plot of $\theta_{ f}\p{\theta_{sd, i} = 0}$ as a function of
-    $\epsilon$, where $I = 5^\circ$. Overplotted in the red line is
+    $\epsilon$, where $I = 5^\circ$. The shaded area, bordered by the black
+    line, corresponds to the adiabatic regime estimated by
+    \autoref{eq:ad_constr}. Overplotted in the red line is
     \autoref{eq:nonad_q_f}, which is in good agreement for $\epsilon \gtrsim
-    0.1$ the non-adiabatic regime, while $\theta_{ f} \approx 90^\circ$ in
-    the adiabatic regime.}\label{fig:nonad_3_scan}
+    0.1$ the non-adiabatic regime, while $\theta_{f} \approx 90^\circ$ in the
+    adiabatic regime.}\label{fig:nonad_3_scan}
 \end{figure}
@@
     \caption{Same as \autoref{fig:nonad_3_scan} but for $I=20^\circ$. Note that
-    the analytical prediction is accurate until $\theta_f \approx 90^\circ$,
-    which occurs before the transition to the adiabatic
+    \autoref{eq:nonad_q_f} is accurate until $\theta_f \approx 90^\circ$, which
+    occurs before the transition to the adiabatic
     regime.}\label{fig:nonad_3_scan_20}
@@
 
-\section{Adiabatic Evolution}
-
-\subsection{Analytic $\theta_f$ for small $\theta_{sd,
-i}$}\label{ss:app_transition}
+\section{Approximate Adiabatic Evolution}\label{s:app_transition}
 
 In this section, we will use approximations valid for small $\eta$ to derive
-analytic expressions for the final obliquities and associated probabilities for
-the $II \to I, II \to III$ tracks that govern behavior at small $\theta_{sd,
-i}$.
+analytic expressions for the final obliquities at small $\theta_{sd, i}$ and
+associated probabilities for the $II \to I, II \to III$ tracks that are
+accessible.
 
@@
 This, in conjunction with \autoref{eq:henrard_hop}, is sufficient to compute
-$\theta_f\p{\theta_{sd, i}}$ for zone II initial conditions.
+$\theta_f\p{\theta_{sd, i}}$ for zone $II$ initial conditions.
 
@@
 
-    \item Upon separatrix encounter, a transition to either zone I or zone III
-        occurs. These can be calculated to have associated probabilities (using
-        the approximate area \autoref{eq:a_approx})
+    \item Upon separatrix encounter, a transition to either zone $I$ or zone
+        $III$ occurs. These can be calculated to have associated probabilities
+        (using the approximate area \autoref{eq:a_approx})
         \begin{align}
@@
 
-    \item Upon a transition to zone I or zone III, the final obliquities can be
+    \item Upon a transition to zone $I$ or zone $III$, the final obliquities can be
         predicted by observing the final adiabatic invariant $A_f =
-        -A_I(\eta_\star)$ in the zone I case and $A_f = A_I(\eta_\star) +
-        A_II(\eta_\star)$ in the zone III case. As $\eta \to 0$, these
+        -A_I(\eta_\star)$ in the zone $I$ case and $A_f = A_I(\eta_\star) +
+        A_II(\eta_\star)$ in the zone $III$ case. As $\eta \to 0$, these
         correspond to obliquities
@@
 
-\section{Nonadiabatic Evolution}\label{s:nonad_app}
+\section{Derivation of Nonadiabatic Evolution}\label{s:nonad_app}
 

### 2019-10-17 initial/0_eta/1contours.py

@@ -7,7 +7,8 @@ plt.rc('font', family='serif', size=16)
 from utils import roots, get_four_subplots, plot_point, H, get_grids, get_etac,\
     get_sep_area
 
-def plot_H_for_eta(f, ax, eta, I):
+letters = ['a', 'b', 'c', 'd']
+def plot_H_for_eta(f, ax, eta, I, idx):
     '''
     Hamiltonian is H = 1/2 cos^2(theta) + eta * sin(phi)
     canonical variables are (phi, x = cos(theta))
@@ -19,7 +20,7 @@ def plot_H_for_eta(f, ax, eta, I):
                       cmap='RdBu_r', linewidths=0.8, levels=5)
 
     thetas, phis = roots(I, eta)
-    colors = ['r', 'm', 'g', 'c'] if len(thetas) == 4 else ['m', 'g']
+    colors = ['y', 'r', 'm', 'c'] if len(thetas) == 4 else ['r', 'm']
     for color, theta, phi in zip(colors, thetas, phis):
         plot_point(ax, theta, '%so' % color, markersize=6)
 
@@ -76,7 +77,7 @@ def plot_H_for_eta(f, ax, eta, I):
         ax.text(2 * np.pi / 3, np.cos(thetas[0]) - 0.1 - font_height, 'II')
         ax.text(0.3, np.cos(thetas[1]) + 0.6, 'III')
 
-    ax.set_title(r'$\eta = %.2f$' % eta, fontsize=14)
+    ax.set_title(r'(%s) $\eta = %.2f$' % (letters[idx], eta), fontsize=14)
 
     plt.suptitle(r'$I = %d^\circ, \eta_c = %.3f$' %
                  (np.degrees(I), eta_c))
@@ -93,8 +94,8 @@ if __name__ == '__main__':
     # plt.clf()
 
     f, axs = get_four_subplots()
-    for ax, eta in zip(axs, [2, 0.73, 0.4, 0.1]):
-        plot_H_for_eta(f, ax, eta, I)
+    for idx, (ax, eta) in enumerate(zip(axs, [2, 0.73, 0.4, 0.1])):
+        plot_H_for_eta(f, ax, eta, I, idx)
 
     plt.savefig('1contours_flip.png', dpi=400)
     plt.clf()

### 2019-10-17 initial/99_misc/2_rand_plots.py

@@ -58,14 +58,24 @@ def plot_cs(I=np.radians(5)):
                 cs_lst.append(root_val)
 
     etas_four = etas[np.where(etas < etac)[0]]
-    plt.semilogx(etas_four, np.degrees(cs_vals[0]), 'r', label='1')
-    plt.semilogx(etas, np.degrees(cs_vals[1]), 'm', label='2')
-    plt.semilogx(etas, np.degrees(cs_vals[2]), 'g', label='3')
+    plt.semilogx(etas_four, np.degrees(cs_vals[0]), 'y', label='1')
+    plt.semilogx(etas, np.degrees(cs_vals[1]), 'r', label='2')
+    plt.semilogx(etas, np.degrees(cs_vals[2]), 'm', label='3')
     plt.semilogx(etas_four, np.degrees(cs_vals[3]), 'c', label='4')
     plt.xlabel(r'$\eta$')
     plt.ylabel(r'$\theta$ (deg)')
     plt.legend(loc='lower right')
     plt.xlim([min_eta, max_eta])
+    plt.yticks([-180 + np.degrees(I),
+                -90,
+                np.degrees(I),
+                90],
+               [r'$%d$' % (np.degrees(I) - 180),
+                r'$-90$',
+                r'$%d$' % np.degrees(I),
+                r'$90$'])
+    plt.axhline(np.degrees(I), lw=0.8, c='k', ls='dashed')
+    plt.axhline(-180 + np.degrees(I), lw=0.8, c='k', ls='dashed')
     plt.axvline(etac, c='k', lw='0.8', ls='dashed')
     plt.title(r'$I = %d^\circ, \eta_c = %.3f$' % (np.degrees(I), etac))
     plt.tight_layout()

### 2019-10-24 writeups/Su_disk_disp.tex
okay full draft kinda

@@
         usenatbib,
+        referee,
     ]{mnras}
@@
         newtxmath,
+        graphicx,
         ae, aecompl,
-        graphicx,
         booktabs,
+        caption,
+        subcaption,
     }
     \usepackage[T1]{fontenc}
-    \usepackage[
-        labelfont=bf, % caption names are labeled in bold
-        font=scriptsize % smaller font for captions
-    ]{caption}
-    \usepackage[font=scriptsize]{subcaption} % subfigures
     \captionsetup{compatibility=false}
@@
     \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
+    \newcommand*{\rtd}[2]{\frac{\mathrm{d}^2#1}{\mathrm{d}#2^2}}
     \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
@@
 
-\title[Cassini State Capture]{Cassini State Capture}
+\title[Analytical Exoplanet Obliquities]{Analytical Predictions of Explanet
+Obliquities Generated by Planet-Disk Interactions}
 \author[Y. Su et\ al.]{
@@
 \renewcommand*{\sectionautorefname}{Section}
+% \renewcommand*{\subsectionautorefname}{Subsection}
 \maketitle
@@
 \begin{abstract}
-    Abstract
+    Large planetary spin-orbit misalignments (obliquities) are thought to play a
+    key role in some planets' atmospheric circulation and tidal heating. A
+    promising avenue to generate high obliquities is via spin-orbit resonances,
+    where the spin and orbital precession frequencies of the planet become and
+    remain commensurate as the system evolves. One such proposed mechanism
+    involves a dissipating protoplanetary disk driving orbital precession of an
+    interior planet \citep{millholland_disk}. This previous work is limited to
+    small initial misalignment angles between the spin axis of the planet and
+    orbital axis of the massive disk. In the present paper, this scenario is
+    analytically characterized and extended to arbitrary misalignment angles. It
+    is shown that (i) under adiabatic evolution, final planetary obliquities
+    bifurcate into distinct tracks governed by interactions with the resonance,
+    while (ii) under non-adiabatic evolution, a broad range of obliquities can
+    be excited. Analytical formulae are provided for most interesting regimes of
+    parameter space.
 \end{abstract}
@@
 
-The primary result of our paper is \autoref{fig:nonad_3_ensemeble}.
+Substantial planetary obliquities, defined as the angle between a planet's spin
+and orbital axes, have featured in many astrophysical scenarios. They lie at the
+heart of the obliquity tides scenario of radius enhancement in hot Jupiters
+\citep{winn_otides, fabrycky_otides, millholland_wasp12b}. They have also been
+invoked to explain peculiar thermal phase curves in hot Jupiters \citep[see
+e.g.][]{millholland_signatures, ohno_infer_obl}. While exoplanet obliquities
+have yet to be directly detected, techniques have been proposed to constrain
+them \citep[see e.g.][]{schwarz_infer_obl, rauscher_infer_obl}.
+
+Many mechanisms have been proposed to generate large planetary obliquities.
+Giant impacts are traditionally used to generate the large obliquities of the
+solar system ice giants \citep{original_gi, morbidelli_gi}. More recently,
+obliquity excitations have been achieved via \emph{spin-orbit resonances}, where
+the spin and orbital precession frequencies of the planet become and remain
+commensurate as the system evolves (sometimes called \emph{resonance
+advection}). Spin-orbit resonances have been studied extensively in solar system
+dynamics as \emph{Cassini States} and are responsible for the significant
+nonzero obliquities of both Jupiter ($3.1^\circ$) and Saturn ($26.7^\circ$)
+\citep{colombo1966, henrard1987, ward2004I, ward_jupiter}. Recent work has
+attempted to apply this mechanism to the ice giants as well
+\citep{hamilton_tilting_ice}.
+
+Producing exoplanet obliquities via spin-orbit resonances was the subject of
+\citet{millholland_disk}, where a dissipating protoplanetary disk causes
+resonance capture and advection. In their work, they begin with a planet whose
+spin is nearly aligned with the angular momentum vector of the protoplanetary
+disk. After the disk dissipates, the resulting planetary obliquity is generally
+substantial, reaching $90^\circ$ for what they characterize as adiabatic
+resonance crossings.
+
+However, their study was limited to small initial misalignment angles between
+the spin vector of the planet and the orbital angular momentum of the
+protoplanetary disk. Such an assumption is intuitive, since the planet forms
+from the disk, but prospects for it to be violated exist. In particular, giant
+and planetesimal impacts are expected to be abundant during planet formation and
+may perturb the spin axis of the protoplanet from its primordial value
+\citep{yalinewich2019atmospheric, schlichting2015atmospheric}. Furthermore, the
+abundance of compact multi-planet systems provides support for possible
+scattering between close-in, newly-formed planets \citep{usp_compact1,
+usp_review}. It is conceivable that such processes could generate significant
+spin-disk misalignment within the lifetime of the disk.
+
+In our work, we provide an analytical framework for understanding the final
+planetary obliquity for arbitrary initial spin-disk misalignment angles. Our
+analytical work and independent numerical simulations are in agreement with
+\citet{millholland_disk} but provide a more complete characterization of
+possible behavior.
+
+The paper is organized as follows. In \autoref{s:eq}, we review relevant
+spin-orbit dynamics and present the equations studied in the rest of the paper.
+In \autoref{s:ad} and \autoref{s:nonad}, we study the evolution of the system
+when the disk either dissipates adiabatically or non-adiabatically respectively.
+Exhaustive yet simple analytical arguments are able to explain completely the
+numerical results in both limits. We discuss potential consequences in
+\autoref{s:disc}. Our primary physical results consist of
+\autoref{fig:ad_ensemble} in the adiabatic limit and
+\autoref{fig:3_ensemble_05_15} in the non-adiabatic limit. Longer mathematical
+calculations are relegated to the appendicies, including a leading-order
+estimate of final planetary obliquities given small initial spin-disk
+misalignment angles in \autoref{s:ad_approx}.
 
@@
 
-Denote $\hat{s}$ spin of planet, $\hat{l}$ angular momentum of planet, and
-$\hat{l}_d$ angular momentum of the surrounding disc. We approximate $S \ll L
-\ll L_d$, so $\hat{l}_d$ is approximately constant and $\hat{l}$ experiences
-negligible backreaction torque from $\hat{s}$. Much of this treatment borrows
-from \citealp{anderson2018teeter} and \citealp{millholland_disk}. We consider
-precession equations
+Much of this treatment parallels that of \citet{anderson2018teeter} and
+\citet{millholland_disk}. We consider an oblate star of mass $M_\star$ hosting a
+planet of mass $M_p$, radius $R_p$, at semimajor axis $a_p$, and with spin
+angular frequency $\Omega_p$, and a protoplanetary disk of mass $M_d$ at some
+characteristic distance $r_d$ from the host star \citep[see][for a power-law
+disk profile]{millholland_disk}. Denote $\hat{s} \equiv \vec{S} / S$ spin unit
+vector of planet, $\hat{l} \equiv \vec{L} / L$ orbital angular momentum unit
+vector of planet, and $\hat{l}_d \equiv \vec{L}_d / L_d$ angular momentum of the
+surrounding disc. We approximate $S \ll L \ll L_d$, so $\hat{l}_d$ is
+approximately constant and $\hat{l}$ experiences negligible backreaction torque
+from $\hat{s}$. The quadrupole-order secular equations of motion for $\hat{s}$,
+$\hat{l}$ and $\hat{l}_d$ then become very simple
 \begin{align}
     \rd{\hat{s}}{t} &= \omega_{sl} \p{\hat{s} \cdot \hat{l}}
-        \p{\hat{s} \times \hat{l}}\label{eq:dsdt}\\
+        \p{\hat{s} \times \hat{l}},\label{eq:dsdt}\\
     \rd{\hat{l}}{t} &= \omega_{ld}\p{\hat{l} \cdot \hat{l}_d}
@@
 In \autoref{eq:wsl}, $k_{qp}$ and $k_p$ are related to the planet's quadrupole
-moment and moment of inertia respectively \citep[see][]{lai2018}, $M_\star$ is
-the mass of the host star, and $M_p, R_p, a_p, \Omega_p$ are the mass, radius,
-semi-major axis and angular spin frequency of the planet respectively.
-\autoref{eq:wld} is written for a disk of mass $M_d$ located at characteristic
-distance $r_d$ from the host star \citep[see][for a power-law disk
-profile]{millholland_disk}, $n \equiv \sqrt{GM_\star/a_p^3}$ is the planet's
-orbital mean motion. The three angles formed by the three vectors are notated
+moment and moment of inertia respectively \citep[see][]{lai2018}, and $n \equiv
+\sqrt{GM_\star/a_p^3}$ is the planet's orbital mean motion. The three angles
+formed by the three vectors are denoted
 \begin{align}
@@
 Let us transform to frame rotating about $\hat{l}_p$ with frequency $g \equiv
--\omega_{ld}\cos I < 0$, where $\hat{l}$ fixed. In this frame, $\hat{l}_p$
+-\omega_{ld}\cos I < 0$, then $\hat{l}$ is fixed. In this frame, $\hat{l}_p$
 also remains fixed and $\hat{s}$ evolves as:
@@
         ={}& 3.75 \p{\frac{k_p}{6k_{qp}}}
-            \p{\frac{m_p}{0.001 M_\star}}
-            \p{\frac{a_p}{1\;\mathrm{AU}}\frac{R_J}{R_p}}^3
-            \p{\frac{2\pi/\p{10\;\mathrm{days}}}{\Omega_p}}\nonumber\\
-        &\p{\frac{M_d}{0.01 M_{\star}}}
-            \p{\frac{30 a_p}{r_d}}^3
-            \p{\frac{n}{2\pi / \p{1\;\mathrm{yr}}}}
-            \p{\frac{\cos I}{\cos 5^\circ}},\nonumber\\
+            \p{\frac{m_p}{0.001 M_\odot}}
+            \p{\frac{R_p}{R_J}}^{-3}
+            \p{\frac{\Omega_p}{2\pi/\p{10\;\mathrm{days}}}}^{-1}\nonumber\\
+        &\p{\frac{M_d}{0.01 M_{\odot}}}
+            \p{\frac{a_p}{1\;\mathrm{AU}}}^{9/2}
+            \p{\frac{r_d}{30 \;\mathrm{AU}}}^{-3}
+            \p{\frac{M_\star}{1M_{\odot}}}^{-3/2}
+            \cos I,\\
     \tau \equiv{}& \alpha t,
@@
         ={}& 0.015 \p{\frac{k_p}{6k_{qp}}}
-            \p{\frac{m_p}{0.001 M_\star}}
-            \p{\frac{a_p}{1\;\mathrm{AU}}\frac{R_J}{R_p}}^3\nonumber\\
-        &\p{\frac{2\pi/\p{10\;\mathrm{days}}}{\Omega_p}}
-            \p{\frac{10\;\mathrm{Myr}}{t_d}},\\
+            \p{\frac{m_p/M_\star}{0.001}}
+            \p{\frac{a_p}{1\;\mathrm{AU}}}^3\nonumber\\
+        &\p{\frac{R_p}{R_J}}^{-3}
+            \p{\frac{\Omega_p}{2\pi/\p{10\;\mathrm{days}}}}
+            \p{\frac{t_d}{10\;\mathrm{Myr}}}^{-1},\\
     \rd{\eta}{\tau} ={}& -\epsilon \eta.\label{eq:deta_dt}
@@
 of study.
-
-For analytical work, we adopt spherical coordinate system where $\hat{l} =
-\hat{z}$ and $\theta, \phi$ are the polar and azimuthal angle of $\hat{s}$. By
-convention, we choose $\hat{l}_z$ at coordinates $\theta = I, \phi = \pi$.
-Note that $\p{\cos \theta, \phi}$ form a canonically conjugate pair of variables
-describing $\hat{s}$. To derive equations of motion for these canonical
-coordinates, we introduce Hamiltonian
-\begin{align}
-    \mathcal{H}\p{\theta, \phi} &= -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
-            + \eta \p{\hat{s} \cdot \hat{l}_d}.\label{eq:H}\\
-        &= -\frac{1}{2}\cos^2\theta
-            + \eta \p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
-\end{align}
-
-The equations of motion follow by taking derivatives of $\mathcal{H}$ and agree
-with \autoref{eq:dsdt_base}:
-\begin{subequations}\label{se:H_eom}
-    \begin{align}
-        \pd{\phi}{t} = \pd{\mathcal{H}}{(\cos\theta)}
-            &= -\cos\theta + \eta\p{\cos I + \sin I \cot \theta \cos \phi},\\
-        \pd{(\cos \theta)}{t} = -\pd{\mathcal{H}}{\phi}
-            &= -\eta \sin I \sin \theta \sin \phi.
-    \end{align}
-\end{subequations}
-While these equations are numerically stiff owing to the $\cot\theta$ term, they
-are the most intuitive description for analytical work.
 
@@
 $\phi = \pi, \theta > 0$. Of these, CSs 1, 2, 3 are stable while CS4 is unstable
-(this follows from linearization of \autoref{se:H_eom}). When $\eta < \eta_c$,
-where
+(see \autoref{s:local_dynamics}). When $\eta < \eta_c$, where
 \begin{equation}
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs.png}
+    \includegraphics[width=0.5\textwidth]{../initial/99_misc/2_cs_locs.png}
     \caption{Cassini state obliquities as a function of $\eta$. Note that
@@
 \emph{separatrix} and divide phase space into three zones. The separatrix, three
-zones, and their relations to the CSs are shown in \autoref{fig:eq_1contours}.
-Note that trajectories in zone $II$ librate about CS2 while those in zones
-$I$/$III$ circulate.
+zones, and their relations to the CSs are shown via a contour plot of the
+Hamiltonian of the system
+\begin{equation}
+    \mathcal{H} = -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
+            + \eta \p{\hat{s} \cdot \hat{l}_d}.\label{eq:H}
+\end{equation}
+Such a contour plot is given in \autoref{fig:eq_1contours}. Note that
+trajectories in zone $II$ librate about CS2 while those in zones $I$/$III$
+circulate.
 \begin{figure*}
@@
     \includegraphics[width=0.8\textwidth]{../initial/0_eta/1contours_flip.png}
-    \caption{Contour plot of $\mathcal{H}\p{\phi, \cos \theta}$, where warmer
-    colors denote more positive values. The black solid line is the separatrix,
-    which only exists for $\eta < \eta_c$. The three zones, divided by the
-    separatrix, are labeled. The Cassini states are labeled and have the same
-    colors as \autoref{fig:cs_locs}. The interior of the separatrix, shaded in
-    grey, is formally only defined for $\eta < \eta_c$, but we may identify the
-    phase space trajectories that flow into zone $II$ when evolved forward in
-    time; this is the shaded region in the top left plot, bounded by the dotted
-    black line.}\label{fig:eq_1contours}
+    \caption{Contour plot of $\mathcal{H}\p{\phi, \cos \theta}$ as given in
+    \autoref{eq:H}, where warmer colors denote more positive values. The black
+    solid line is the separatrix, which only exists for $\eta < \eta_c$. The
+    three zones, divided by the separatrix, are labeled. The Cassini states are
+    labeled and have the same colors as \autoref{fig:cs_locs}. The interior of
+    the separatrix, shaded in grey, is formally only defined for $\eta <
+    \eta_c$, but we may identify the phase space trajectories that flow into
+    zone $II$ when evolved forward in time; this is the shaded region in the top
+    left plot, bounded by the dotted black line.}\label{fig:eq_1contours}
 \end{figure*}
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/99_misc/1_areas.png}
-    \caption{Plot of fractional $A_{i}(\eta)$ as given by
-    \autoref{se:area_ward}. Dotted lines correspond to small $\eta$
-    approximations discussed in \autoref{s:app_transition}. Dashed lines for
-    $\eta > \eta_c$ effective values of $A_{II}, A_{III}$ for $\eta > \eta_c$,
-    denoting the area of points that would flow into either area under adiabatic
-    decrease of $\eta$ to below $\eta_c$.}\label{fig:eq_areas}
+    \includegraphics[width=0.5\textwidth]{../initial/99_misc/1_areas.png}
+    \caption{Plot of fractional areas of each of the zones $A_{i}(\eta) / 4\pi$
+    as given by \autoref{se:area_ward}. Dotted lines correspond to small $\eta$
+    approximations discussed in \autoref{s:ad_approx}. Dashed lines for $\eta >
+    \eta_c$ effective values of $A_{II}, A_{III}$ for $\eta > \eta_c$, denoting
+    the area of points that would flow into either area under adiabatic decrease
+    of $\eta$ from $\eta > \eta_c$.}\label{fig:eq_areas}
 \end{figure}
@@
 One criterion for adiabaticity is that the separatrix crossing timescale be
-longer than the the resonant libration period \citep{ward2004I}. The resonant
-libration period is just the libration period about CS2, which can be found by
-linearizing \autoref{se:H_eom} about CS2. This results in constraint
+longer than the the resonant libration period \citep{ward2004II}. The resonant
+libration period for a nearly separatrix-crossing orbit can be approximated by
+the libration period near CS2, resulting in constraint
 \begin{align}
     -\at{\frac{1}{\eta}\rd{\eta}{\tau}}_{cross} = \epsilon &\lesssim
-            \frac{1}{T_{lib}},\nonumber\\
-        &\lesssim \frac{1}{2\pi}\sqrt{\eta_\star\sin\theta \sin I
-            \p{1 + \eta_\star \frac{\sin I}{\sin^3\theta}}}.\label{eq:ad_constr}
-\end{align}
-This formula differs from that presented in \citealt{millholland_disk}.
+            \frac{1}{T_{lib}},\\
+        &\lesssim \frac{1}{2\pi}\sqrt{\eta_\star\sin I \sin \theta_2
+            \p{1 + \eta_\star \sin I \csc^3 \theta_2}},
+            \label{eq:ad_constr}
+\end{align}
+where $\theta_2$ is the obliquity at CS2. This formula differs from that
+presented in \citet{millholland_disk}, where the $\csc^3\theta_2$ term is
+neglected and a square root is missing. See \autoref{s:local_dynamics} for a
+detailed derivation of $T_{lib}$ and comparison to existing work.
 
@@
 fixed by $\theta_{sd, i}$\footnote{For each $\theta_{sd, i}$ we choose an
-initial condition on the libration cycle with initial condition $\p{\theta_2 +
+initial condition on the libration cycle going through $\p{\theta_2 +
 \theta_{sd, i}, \phi_2}$ (where $\p{\theta_2, \phi_2}$ are the coordinates of
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_35.png}
+    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_35.png}
     \caption{Top: $\theta_{f}\p{\theta_{sd, i}}$, overlaid with semi-analytic
@@
     dynamical tracks in colored lines. Black dotted lines correspond to
-    small-$\theta_{sd, i}$ predictions derived in \autoref{s:app_transition}.
+    small-$\theta_{sd, i}$ predictions derived in \autoref{s:ad_approx}.
     Bottom: Semi-analytic probabilities of each of the dynamical tracks for each
-    $\theta_{sd, i}$. The five regimes of $\theta_{sd, i}$ values correspond to
-    the five regimes of $A_i$ discussed in \autoref{ss:zone_transitions}. Again,
-    black dotted lines correspond to simple analytic estimates. Vertical black
-    dashed lines correspond to the analytical predictions of where each
-    dynamical track is accessible, as described in
-    \autoref{ss:zone_transitions}.}\label{fig:ad_ensemble}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_10_35.png}
+    $\theta_{sd, i}$. The five regimes of $\theta_{sd, i}$ values demarcated by
+    the vertical dashed black lines correspond to the five regimes of $A_i$
+    calculated in \autoref{ss:zone_transitions}. Black dotted lines correspond to
+    simple analytic estimates given in
+    \autoref{s:ad_approx}.}\label{fig:ad_ensemble}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_10_35.png}
     \caption{Same as \autoref{fig:ad_ensemble} but for $I =
-    10^\circ$.}\label{fig:3_ensemble_10_35}
-\end{figure}
-\begin{figure}
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_20_35.png}
-    \caption{Same as \autoref{fig:ad_ensemble} but for $I = 20^\circ$. The $III
-    \to II \to I$ track is not visible since the maximum $A_{II}$ is very near
-    $\eta_c$ for $I = 20^\circ$.}\label{fig:3_ensemble_20_35}
+    10^\circ$ and with fewer annotations.}\label{fig:3_ensemble_10_35}
+\end{figure}
+\begin{figure}
+    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_20_35.png}
+    \caption{Same as \autoref{fig:3_ensemble_10_35} but for $I = 20^\circ$. The
+    $III \to II \to I$ track is very short since the maximum $A_{II}$ is very
+    near $\eta_c$ for $I = 20^\circ$.}\label{fig:3_ensemble_20_35}
 \end{figure}
@@
 initial conditions and probabilities associated with each track:
-\begin{itemize}
+\begin{enumerate}
     \item $II \to I$ --- An example trajectory following this track is depicted
@@
         $-A_I(\eta_\star)$ phase space area. The final $\theta_f$ is then given
-        by \autoref{eq:qfaf}.
+        by \autoref{eq:qfaf}. An analytical approximation to $\theta_f$ is
+        derived in \autoref{s:ad_approx} and is
+        \begin{equation}
+            \cos \theta_{f, II \Rightarrow I} \approx
+                \p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
+                    + \frac{\theta_{sp, i}^2}{4}.\label{eq:qf_21_approx}
+        \end{equation}
 
@@
         II, requiring $A_i < A_{II}(\eta_c)$. Note $A_{II}(\eta_c)$ is given in
-        closed form in \citealt{ward2004I} but appears to be incorrect. Then, at
+        closed form in \citet{ward2004I} but appears to be incorrect. Then, at
         some known $\eta_\star$ satisfying $A_{II}(\eta_\star) = A_i$, the
@@
         which it will encompass $A_f = A_I(\eta_\star) + A_{II}(\eta_\star)$.
-        The final obliquity is still given by \autoref{eq:qfaf}.
+        The final obliquity is still given by \autoref{eq:qfaf}, and the
+        analytical approximation derived in \autoref{s:ad_approx} is
+        \begin{equation}
+            \cos \theta_{f, II \Rightarrow III} \approx
+                \p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
+                    - \frac{\theta_{sp, i}^2}{4}.\label{eq:qf_23_approx}
+        \end{equation}
 
@@
         \end{equation}
-        then if $\eta_\star > \eta_{\min, III}$ then $\Pr_{II \to III} < 0$.
-        This is understood as a forbidden transition, and so $II \to III$ is
-        only a permitted dynamical track if $\eta_\star <, \eta_{\min,
-        III}$, or $A_i < \min A_{III}$.
+        which is labeled in \autoref{fig:eq_areas}, then if $\eta_\star >
+        \eta_{\min, III}$ then $\Pr_{II \to III} < 0$. This is understood as a
+        forbidden transition, and so $II \to III$ is only a permitted dynamical
+        track if $\eta_\star <, \eta_{\min, III}$.
 
@@
         Examining \autoref{fig:eq_areas}, there exist values $A$ for which
-        $A_{II}(\eta) = A$ has multiple solutions. These are the only values for
-        which the $III \to II \to I$ transition is permitted. Thus, as $\eta$
-        continues to decrease, a second $\eta_2$ value exists for which $A_m =
-        A_II(\eta_2)$, upon which the trajectory is ejected to zone $I$ and $A_f
-        = -A_I(\eta_2)$. The final obliquity again then obeys \autoref{eq:qfaf}.
+        $A_{II}(\eta) = A$ has multiple solutions, and $\eta_1 > \eta_{II,
+        \max}$ as labeled. These are the only values for which the $III \to II
+        \to I$ transition is permitted. Thus, as $\eta$ continues to decrease, a
+        second $\eta_2$ value exists for which $A_m = A_{II}(\eta_2)$, upon
+        which the trajectory is ejected to zone $I$ and $A_f = -A_I(\eta_2)$.
+        The final obliquity again then obeys \autoref{eq:qfaf}.
 
@@
         seen visibly in \autoref{fig:3_ensemble_20_35}.
-\end{itemize}
+\end{enumerate}
 In summary, the five regimes of track possibilities in increasing order of $A_i$
 are:
-\begin{itemize}
-    \item $A_i \in \s{0, A_{II}\p{\eta_{\min, III}}}$: $II \to III, II \to I$
+\begin{enumerate}
+    \item $A_i \in \s{0, A_{II}\p{\eta_{\min, III}}}$ --- $II \to III, II \to I$
         both possible.
 
-    \item $A_i \in \s{A_{II}\p{\eta_{\min, III}}, A_{II}(\eta_c)}$: $II \to I$
-        only.
-
-    \item $A_i \in \s{A_{II}(\eta_c), A_{II, \max}}$: $III \to I, III \to II \to
-        I$ both possible.
-
-    \item $A_i \in \s{A_{II, \max}, \max A_I + A_{II}}$: $III \to I$ only.
-
-    \item $A_i > \max A_I + A_{II}$: $III \to III$ only.
-\end{itemize}
+    \item $A_i \in \s{A_{II}\p{\eta_{\min, III}}, A_{II}(\eta_c)}$ --- $II \to
+        I$ only.
+
+    \item $A_i \in \s{A_{II}(\eta_c), A_{II, \max}}$ --- $III \to I, III \to II
+        \to I$ both possible.
+
+    \item $A_i \in \s{A_{II, \max}, \max A_I + A_{II}}$ --- $III \to I$ only.
+
+    \item $A_i > \max A_I + A_{II}$ --- $III \to III$ only.
+\end{enumerate}
 The corresponding ranges for for $\theta_{sd,i}$ can be computed via
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo21.png}
+        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo21.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo21_subplots.png}
+        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo21_subplots.png}
     \end{subfigure}
@@
     Cassini State 2 (red), and upper and lower bounds on the separatrix (black).
-    Note that the trajectory successfully tracks CS2 to a misalignment angle
-    $\theta \approx 90^\circ$. Light vertical blue lines denote times portrayed
-    in bottom plot. Top plot lower panel: plot of the enclosed separatrix area
+    Note that the trajectory successfully tracks CS2 to an obliquity $\theta
+    \approx 90^\circ$. Light vertical blue lines denote times portrayed in
+    bottom plot. Top plot lower panel: plot of the enclosed separatrix area
     obtained by integrating the simulated trajectory (blue dots) and adiabatic
-    theory (red line). Lower plot: snapshots in the $\p{\cos \theta, \phi}$
-    space of the simulation trajectories for the times demarcated in green
-    above, corresponding to the start of the simulation, the appearance of the
-    separatrix, two panels depicting the separatrix crossing process, and a
-    final snapshot at $\eta = 10^{-3.5}$. The green line denotes a full
-    circulation or libration cycle at the selected time, including an arrow for
-    directionality. The separatrix at the start/end of the portrayed cycle are
-    shown in solid/dashed black lines respectively. Also labeled is CS2 at the
-    start of the cycle (red). Finally, the enclosed phase space area is shaded
-    in grey ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
+    theory (red line). Even though the enclosed area jumps at separatrix
+    crossing, the resultant $A$ is still accurately predicted. Lower plot:
+    snapshots in the $\p{\cos \theta, \phi}$ space of the simulation
+    trajectories for the vertical blue lines in the top plots. These times
+    correspond to the start of the simulation, the appearance of the separatrix,
+    two panels depicting the separatrix crossing process, and a final snapshot
+    at $\eta = 10^{-3.5}$. The green line denotes a full circulation or
+    libration cycle at the selected time, including an arrow for directionality.
+    The separatrix at the start/end of the portrayed cycle are shown in
+    solid/dashed black lines respectively. Also labeled is CS2 at the start of
+    the cycle (red). Finally, the enclosed phase space area is shaded in grey
+    ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
 \end{figure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23.png}
+        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo23.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23_subplots.png}
+        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo23_subplots.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31.png}
+        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo31.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31_subplots.png}
+        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo31_subplots.png}
     \end{subfigure}
     \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_I$
-    track. $\theta_{sd, i} = 89.1^\circ$, and $\epsilon = 3.01 \times
+    track. $\theta_{sd, i} = 89.1^\circ$, and $\epsilon = 3 \times
     10^{-4}$.}\label{fig:ad_31}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321.png}
+        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo321.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321_subplots.png}
+        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo321_subplots.png}
     \end{subfigure}
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_25.png}
+    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_25.png}
     \caption{Same as \autoref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$,
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_15.png}
+    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_15.png}
     \caption{Same as \autoref{fig:3_ensemble_05_25} but for $\epsilon =
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo_nonad.png}
+        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo_nonad.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo_nonad_subplots.png}
+        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo_nonad_subplots.png}
     \end{subfigure}
@@
     changes, decreasing the obliquity jump. In the bottom plot, we can see that
-    individual orbits do not lie along level curves of the Hamiltonian, a
-    further consequence of violating adiabaticity.}\label{fig:nonad_traj}
+    individual orbits do not lie along level curves of the Hamiltonian, as the
+    Hamiltonian phase space changes quickly compared to the period of
+    circulation cycles.}\label{fig:nonad_traj}
 \end{figure}
@@
 A formula for $\theta_{f}$ assuming $\theta_{sd, i} = 0$ initially can be
-given (see \autoref{s:app_transition})
+given (see \autoref{s:ad_approx})
 \begin{equation}
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_05.png}
+    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_05.png}
     \caption{$\theta_{ f}\p{\theta_{sd, i}}$ at $\epsilon = 0.3$, firmly in
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3scan.png}
+    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3scan.png}
     \caption{Plot of $\theta_{ f}\p{\theta_{sd, i} = 0}$ as a function of
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/2_toy2/3scan_20.png}
+    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3scan_20.png}
     \caption{Same as \autoref{fig:nonad_3_scan} but for $I=20^\circ$. Note that
     \autoref{eq:nonad_q_f} is accurate until $\theta_f \approx 90^\circ$, which
-    occurs before the transition to the adiabatic
-    regime.}\label{fig:nonad_3_scan_20}
-\end{figure}
+    is much closer to the transition to adiabaticity. Comparison with
+    \autoref{fig:nonad_3_scan} suggests that the breakdown of
+    \autoref{eq:nonad_q_f} indeed is caused by the breakdown of the
+    non-adiabatic assumption.}\label{fig:nonad_3_scan_20}
+\end{figure}
+
+\section{Summary and Discussion}\label{s:disc}
+
+In this paper, we have studied the excitation of planetary obliquities by a
+dissipating protoplanetary disk for arbitrary initial misalignment angles. This
+is described by transfer function $\theta_f\p{\theta_{sd, i}}$, where $\theta_f$
+is the final planetary obliquity and $\theta_{sd, i}$ is the initial
+misalignment angle between the planet's spin axis and the disk's orbital angular
+momentum. We have presented analytical results that capture the behavior of
+$\theta_f\p{\theta_{sd, i}}$ in both the adiabatic and nonadiabatic limits:
+\begin{enumerate}
+    \item In the adiabatic limit, we are able to reproduce the known result
+        $\theta(0) \approx 90^\circ$ \citep{millholland_disk}. We demonstrate
+        via numerical simulation the dual-valued behavior of $\theta$ as nonzero
+        values of $\theta_{sd, i}$ are permitted (see
+        \autoref{fig:ad_ensemble}). We are able to capture both the exact final
+        $\theta$ values and the probabilities of observing each value via
+        careful accounting of enclosed phase space area and separatrix crossing
+        dynamics \citep{henrard1982,henrard1987}.
+
+    \item As the system transitions more abruptly, the adiabatic prediction
+        breaks down when criterion \autoref{eq:ad_constr} is violated. We find a
+        broad range of $\theta$ values can be excited for a given $\theta_{sd,
+        i}$ (see \autoref{fig:nonad_3_ensemeble}). We provide an analytical
+        expression of the bounds on $\theta_f\p{\theta_{sd, i}}$ in
+        \autoref{eq:nonad_q_f_dist}.
+\end{enumerate}
+
+It is of interest to note the leading order behavior of $\theta$ in the
+small $\theta_{sd, i}$ limit given by \autoref{eq:qf_21_approx} and
+\autoref{eq:qf_23_approx}. Therefore, if $\theta_{sd, i}$ is generally small, as
+would be expected for peacefully forming planets, resonance capture induced by
+an adiabatically dissipating protoplanetary disk is expected to significantly
+narrow the final $\theta$ spread compared to the initial $\theta_{sd, i}$
+spread.
 
@@
 
-\section{Approximate Adiabatic Evolution}\label{s:app_transition}
+\section{Cassini State Local Dynamics}\label{s:local_dynamics}
+
+In this section, we perform local linearizations about the CSs to determine the
+stability of each CS and, when stable, the local libration frequencies.
+
+\subsection{Canonical Equations of Motion and Solutions}
+
+For analytical work, we adopt spherical coordinate system where $\hat{l} =
+\hat{z}$ and $\theta, \phi$ are the polar and azimuthal angle of $\hat{s}$. By
+convention, we choose $\hat{l}_z$ at coordinates $\theta = I, \phi = \pi$.
+Note that $\p{\cos \theta, \phi}$ form a canonically conjugate pair of variables
+describing $\hat{s}$. To derive equations of motion for these canonical
+coordinates, we rewrite \autoref{eq:H}
+\begin{equation}
+    \mathcal{H}\p{\theta, \phi} = -\frac{1}{2}\cos^2\theta
+            + \eta \p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
+\end{equation}
+
+The equations of motion follow by taking derivatives of $\mathcal{H}$ and agree
+with \autoref{eq:dsdt_base}:
+\begin{subequations}\label{se:H_eom}
+    \begin{align}
+        \rd{\phi}{t} = \pd{\mathcal{H}}{(\cos\theta)}
+            &= -\cos\theta + \eta\p{\cos I + \sin I \cot \theta \cos \phi},
+                \label{seq:H_eom_phi_t}\\
+        \rd{(\cos \theta)}{t} = -\pd{\mathcal{H}}{\phi}
+            &= -\eta \sin I \sin \theta \sin \phi.
+                \label{seq:H_eom_mu_t}
+    \end{align}
+\end{subequations}
+While these equations are numerically stiff owing to the $\cot\theta$ term, they
+are the most intuitive description for analytical work.
+
+We next develop some approximate forms for the CS obliquities that will be
+useful for guiding later discussion.
+\begin{enumerate}
+    \item $\eta \ll 1, \cos \theta_{CS} \ll 1$ --- This is the limiting case for
+        CS2 and CS4 when $\eta \ll \eta_c$. We examine \autoref{seq:H_eom_phi_t}
+        and approximate $\cot \theta \approx \cos \theta$ to find
+        \begin{equation}
+            \cos \theta_{CS} \approx \frac{\eta \cos I}
+                {1 \mp \eta \sin I}.
+        \end{equation}
+        The two signs correspond to choices of $\cos \phi$. Each sign
+        corresponds to one of CS2 and CS4.
+
+    \item $\sin \theta_{CS} \ll 1$ --- The $\eta \ll 1, \eta \gg 1$ cases can be
+        solved together, and are the limiting cases both for CS1 and CS3 when
+        $\eta \ll \eta_c$, and for CS2 and CS3 when $\eta \gg \eta_c$. It proves
+        easiest to rewrite \autoref{seq:H_eom_phi_t} as
+        \begin{equation}
+            0 = \cos \theta_{CS}\p{-1 + 2\eta
+                \frac{\sin \p{I \pm \theta_{CS}}}{\sin \p{2\theta_{CS}}}}.
+                \label{eq:rewritten_dphi}
+        \end{equation}
+        The $\pm$ choice again comes from choice of $\cos \phi$. Then assuming
+        $\theta_{CS}, I \ll 1$, we obtain $\frac{I \pm
+        \theta_{CS}}{2\theta_{CS}} = \frac{1}{2\eta}$ or
+        \begin{equation}
+            \theta_{CS} = \frac{\eta I}{1 \mp \eta}.
+        \end{equation}
+
+        In the limit $\eta \ll \eta_c$, these two solutions describe CS1 and
+        CS3, while in the limit $\eta \gg \eta_c$ these two solutions describe
+        CS2 and CS3.
+\end{enumerate}
+Note that the $\theta_{CS}$ values derived here do not follow the same
+convention as \autoref{fig:cs_locs}, because the previous $\theta$ conventions
+presume $\cos \phi = -1$ for all states and let $-\pi \leq \theta < \pi$.
+
+\subsection{Stability}
+
+To examine stability of each CS, it proves very easy to handle them generally.
+We linearize about an equilibrium located at $\bar{\phi} = 0, \pi$ but arbitrary
+$\bar{\theta}$. Linearizing \autoref{se:H_eom} about $\phi = \bar{\phi} + \delta
+\phi, \theta = \bar{\theta} + \delta \theta$ gives
+\begin{subequations}\label{se:H_eom_lin}
+    \begin{align}
+        \rd{\delta \phi}{t} &= \sin \bar{\theta} \delta \theta
+            \mp \eta \frac{\sin I}{\sin^2\bar{\theta}} \delta \theta,\\
+        \rd{\delta \theta}{t} &= \pm \eta \sin I \delta \phi.
+    \end{align}
+\end{subequations}
+Note that the positive sign corresponds to $\cos \bar{\phi} = +1, \bar{\phi} =
+0$. Eliminating $\delta \theta$ gives
+\begin{align}
+    \rtd{\delta \phi}{t} &= \p{\sin \bar{\theta}
+        \mp \eta \sin I\csc^2\theta}\p{\pm \eta \sin I} \delta
+            \phi,\\
+        &\equiv \lambda^2\delta \phi.\label{eq:lambda2}
+\end{align}
+A plot of $\lambda^2$ for each of the CSs is given in \autoref{fig:lambda2}.
+From the plot, it is clear that only CS4 is a saddle point, while the other
+three are centers (stable). The local libration frequency for these points is
+just
+\begin{align}
+    \omega_{lib} &= \sqrt{-\lambda^2},\\
+        &= \sqrt{\p{\sin \bar{\theta}
+            \mp \eta \sin I \csc^2\theta}\p{\mp \eta \sin I}}.
+\end{align}
+The libration period is related simply $T_{lib} = \frac{2\pi}{\omega_{lib}}$.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.5\textwidth]{../initial/99_misc/2_lambdas.png}
+    \caption{Plot of $\lambda^2$ per \autoref{eq:lambda2} evaluated at each
+    of the Cassini States. It is clear that CS4 is a saddle point when it
+    exists while all others are centers.}\label{fig:lambda2}
+\end{figure}
+
+Note that our expression is somewhat more complicated than in existing
+literature \citep{millholland_disk,ward2004II}. This seems to stem from the
+approximation $\theta \gg I$ made in deriving Equation 3 of
+\citet{ward2004II}. This is invalid in the $\eta \gtrsim \eta_c$ limit for
+CS2, since $\theta_{CS} \approx I$ in this regime as was shown above.
+
+\subsection{Consequences for Adiabaticity}\label{ss:careful_ad}
+
+In \autoref{s:ad}, we said the adiabaticity criterion is given by comparison of
+the separatrix crossing timescale to the resonant libration period
+\citep{ward2004II}, and we corrected the formula presented by
+\citet{millholland_disk}. Two further comments can be made:
+\begin{enumerate}
+    \item The adiabaticity criterion compares how quickly the
+        separatrix-crossing orbit is completed to how quickly the separatrix
+        location shifts. However, it's not obvious that the libration period
+        about CS2 captures the duration of the separatrix-crossing orbit, which
+        as $\epsilon \to 0$ formally diverges. Thus, this criterion can only be
+        taken as a necessary but not sufficient criterion to guarantee accurate
+        predictions of $A$ post-encounter.
+
+        We speculate a formally sufficient criterion may be able to be
+        formulated as $\Delta t \lesssim \frac{\Delta \eta}{\dot{\eta}}$, where
+        $\Delta t$ is the length of the separatrix-crossing orbit, and $\Delta
+        \eta$ is the change in $\eta$ over the separatrix-crossing orbit. Note
+        for all $\epsilon > 0$ that $\Delta t < \infty$. The exact form of such
+        a criterion is inessential to our result.
+
+    \item A different adiabaticity criterion can be defined for
+        $III$-originating trajectories, as the separatrix-crossing orbit is much
+        shorter (see e.g.\ \autoref{fig:ad_31}). However, the resultant
+        criterion becomes extremely strict for the $III \to I$ track, as it goes
+        through very small $\theta$. That this track is least adiabatic track
+        can be seen by comparing \autoref{fig:ad_ensemble} and
+        \autoref{fig:3_ensemble_05_25}, where the $III \to I$ track develops the
+        largest spread about the analytical prediction.
+\end{enumerate}
+
+\section{Approximate Adiabatic Evolution}\label{s:ad_approx}
 
@@
 
-\begin{itemize}
+\begin{enumerate}
     \item For a given $\theta_{sd, i}$, we know that if $\eta \to \infty$ then
@@
             \eta_\star &\approx \p{\frac{2\pi\p{1 - \cos \theta_{sd,i}}}{
-                        16}}^2 / \sin I,\nonumber\\
+                        16}}^2 / \sin I,\\
                     &\approx \p{\frac{\pi \theta_{sd, i}^2}{16}}^2/\sin I.
@@
         (using the approximate area \autoref{eq:a_approx})
+        \begin{subequations}
             \begin{align}
@@
             \end{align}
+        \end{subequations}
 
@@
         correspond to obliquities
+        \begin{subequations}\label{se:q_f_approx}
             \begin{align}
@@
             \end{align}
+        \end{subequations}
         These are the black dotted lines overplotted in
         \autoref{fig:ad_ensemble}.
-\end{itemize}
+\end{enumerate}
 
@@
 It should be noted that this calculation breaks down in two ways:
-\begin{itemize}
+\begin{enumerate}
     \item If the evolution of $\hat{s}$ is adiabatic, then it is invalid to
@@
         \end{equation}
-\end{itemize}
-
+\end{enumerate}
+
+\bsp
 \label{lastpage} % chktex 24

### 2019-10-24 writeups/Su_disk_disp.tex
10/24 meeting

@@
     \newcommand*{\ev}[1]{\langle#1\rangle}
+    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
     \newcommand*{\p}[1]{\left(#1\right)}
@@
 \citet{millholland_disk} but provide a more complete characterization of
-possible behavior.
+possible behavior. While we solve a specific dynamics problem, our analysis
+is general and has a wide range of applicability to general resonance
+encounters.
 
@@
 \citet{millholland_disk}. We consider an oblate star of mass $M_\star$ hosting a
-planet of mass $M_p$, radius $R_p$, at semimajor axis $a_p$, and with spin
-angular frequency $\Omega_p$, and a protoplanetary disk of mass $M_d$ at some
-characteristic distance $r_d$ from the host star \citep[see][for a power-law
-disk profile]{millholland_disk}. Denote $\hat{s} \equiv \vec{S} / S$ spin unit
-vector of planet, $\hat{l} \equiv \vec{L} / L$ orbital angular momentum unit
-vector of planet, and $\hat{l}_d \equiv \vec{L}_d / L_d$ angular momentum of the
-surrounding disc. We approximate $S \ll L \ll L_d$, so $\hat{l}_d$ is
-approximately constant and $\hat{l}$ experiences negligible backreaction torque
-from $\hat{s}$. The quadrupole-order secular equations of motion for $\hat{s}$,
-$\hat{l}$ and $\hat{l}_d$ then become very simple
-\begin{align}
-    \rd{\hat{s}}{t} &= \omega_{sl} \p{\hat{s} \cdot \hat{l}}
+planet of mass $M_{\rm p}$, radius $R_{\rm p}$, at semimajor axis $a_{\rm p}$,
+and with spin angular frequency $\Omega_{\rm p}$, and a protoplanetary disk of
+mass $M_{\rm d}$ at some characteristic distance $r_{\rm d}$ from the host star
+\citep[see][for a power-law disk profile]{millholland_disk}. Denote $\hat{s}
+\equiv \bm{S} / S$ spin unit vector of planet, $\hat{l} \equiv \bm{L} / L$
+orbital angular momentum unit vector of planet, and $\hat{l}_{\rm d} \equiv
+\bm{L}_{\rm d} / L_{\rm d}$ angular momentum of the surrounding disc. We
+approximate $S \ll L \ll L_{\rm d}$, so $\hat{l}_{\rm d}$ is approximately
+constant and $\hat{l}$ experiences negligible backreaction torque from
+$\hat{s}$. The quadrupole-order secular equations of motion for $\hat{s}$,
+$\hat{l}$ and $\hat{l}_{\rm d}$ then become very simple
+\begin{align}
+    \rd{\hat{s}}{t} &= \omega_{\rm sl} \p{\hat{s} \cdot \hat{l}}
         \p{\hat{s} \times \hat{l}},\label{eq:dsdt}\\
-    \rd{\hat{l}}{t} &= \omega_{ld}\p{\hat{l} \cdot \hat{l}_d}
-        \p{\hat{l} \times \hat{l}_d}\label{eq:dldt}.
+    \rd{\hat{l}}{t} &= \omega_{\rm ld}\p{\hat{l} \cdot \hat{l}_{\rm d}}
+        \p{\hat{l} \times \hat{l}_{\rm d}}\label{eq:dldt}.
 \end{align}
@@
 \begin{align}
-    \omega_{sl} &\equiv \frac{3k_{qp}}{2k_p} \frac{M_\star}{m_p}
-        \p{\frac{R_p}{a_p}}^3 \Omega_p,\label{eq:wsl}\\
-    \omega_{ld} &\equiv \frac{3M_d}{4M_\star}\p{\frac{a_p}{r_d}}^3 n
-        .\label{eq:wld}
+    \omega_{\rm sl} &\equiv \frac{3k_{\rm qp}}{2k_{\rm p}} \frac{M_\star}{m_{\rm
+        p}} \p{\frac{R_{\rm p}}{a_{\rm p}}}^3 \Omega_{\rm p},\label{eq:wsl}\\
+    \omega_{\rm ld} &\equiv \frac{3M_{\rm d}}{4M_\star}\p{\frac{a_{\rm
+        p}}{r_{\rm d}}}^3 n .\label{eq:wld}
 \end{align}
@@
 % = 1 / (573362 yr) (Md/Mstar = 0.01, ap/rd = 1/30)
-In \autoref{eq:wsl}, $k_{qp}$ and $k_p$ are related to the planet's quadrupole
-moment and moment of inertia respectively \citep[see][]{lai2018}, and $n \equiv
-\sqrt{GM_\star/a_p^3}$ is the planet's orbital mean motion. The three angles
-formed by the three vectors are denoted
+In \autoref{eq:wsl}, $k_{\rm qp}$ and $k_{\rm }$ are related to the planet's
+quadrupole moment and moment of inertia respectively \citep[see][]{lai2018}, and
+$n \equiv \sqrt{GM_\star/a_{\rm p}^3}$ is the planet's orbital mean motion. The
+three angles formed by the three vectors are denoted
 \begin{align}
     \theta &\equiv \arccos \hat{s} \cdot \hat{l},\\
-    \theta_{sd} &\equiv \arccos \hat{s} \cdot \hat{l}_d,\\
-    I &\equiv \arccos \hat{l} \cdot \hat{l}_d.
-\end{align}
-
-Let us transform to frame rotating about $\hat{l}_p$ with frequency $g \equiv
--\omega_{ld}\cos I < 0$, then $\hat{l}$ is fixed. In this frame, $\hat{l}_p$
-also remains fixed and $\hat{s}$ evolves as:
+    \theta_{\rm sd} &\equiv \arccos \hat{s} \cdot \hat{l}_{\rm d},\\
+    I &\equiv \arccos \hat{l} \cdot \hat{l}_{\rm d}.
+\end{align}
+
+Let us transform to frame rotating about $\hat{l}_{\rm p}$ with frequency $g
+\equiv -\omega_{\rm ld}\cos I < 0$, then $\hat{l}$ is fixed. In this frame,
+$\hat{l}_{\rm p}$ also remains fixed and $\hat{s}$ evolves as:
 \begin{equation}
@@
             \p{\hat{s} \times \hat{l}}
-        + g\p{\hat{s} \times \hat{l}_d},
-\end{equation}
-where $\alpha \equiv \omega_{sl} > 0$ follows standard notation. By defining
+        + g\p{\hat{s} \times \hat{l}_{\rm d}},
+\end{equation}
+where $\alpha \equiv \omega_{\rm sl} > 0$ follows standard notation. By defining
 $\eta$ and nondimensionalized time $\tau$ as
@@
     \eta \equiv{}& \frac{\abs{g}}{\alpha}\label{eq:eta},\\
-        ={}& 3.75 \p{\frac{k_p}{6k_{qp}}}
-            \p{\frac{m_p}{0.001 M_\odot}}
-            \p{\frac{R_p}{R_J}}^{-3}
-            \p{\frac{\Omega_p}{2\pi/\p{10\;\mathrm{days}}}}^{-1}\nonumber\\
-        &\p{\frac{M_d}{0.01 M_{\odot}}}
-            \p{\frac{a_p}{1\;\mathrm{AU}}}^{9/2}
-            \p{\frac{r_d}{30 \;\mathrm{AU}}}^{-3}
+        ={}& 3.75 \p{\frac{k_{\rm p}}{6k_{\rm qp}}}
+            \p{\frac{m_{\rm p}}{0.001 M_\odot}}
+            \p{\frac{R_{\rm p}}{R_J}}^{-3}
+        &\p{\frac{M_{\rm d}}{0.01 M_{\odot}}}
+            \p{\frac{a_{\rm p}}{1\;\mathrm{AU}}}^{9/2}
+            \p{\frac{r_{\rm d}}{30 \;\mathrm{AU}}}^{-3}
             \p{\frac{M_\star}{1M_{\odot}}}^{-3/2}
@@
             \p{\hat{s} \times \hat{l}}
-        - \eta\p{\hat{s} \times \hat{l}_d}. \label{eq:dsdt_base}
+        - \eta\p{\hat{s} \times \hat{l}_{\rm d}}. \label{eq:dsdt_base}
 \end{equation}
@@
 \begin{equation}
-    M_d(t) = M_d(0)e^{-t/t_d}.
+    M_{\rm d}(t) = M_{\rm d}(0)e^{-t/t_{\rm d}}.
 \end{equation}
 As $\alpha$ is held constant, this equates to $\eta$ decaying as $\rd{\eta}{t} =
--\frac{\eta}{t_d}$ as well. We nondimensionalize:
-\begin{align}
-    \epsilon \equiv{}& \frac{1}{\alpha t_d},\\
-        ={}& 0.015 \p{\frac{k_p}{6k_{qp}}}
-            \p{\frac{m_p/M_\star}{0.001}}
-            \p{\frac{a_p}{1\;\mathrm{AU}}}^3\nonumber\\
-        &\p{\frac{R_p}{R_J}}^{-3}
-            \p{\frac{\Omega_p}{2\pi/\p{10\;\mathrm{days}}}}
-            \p{\frac{t_d}{10\;\mathrm{Myr}}}^{-1},\\
+-\frac{\eta}{t_{\rm d}}$ as well. We nondimensionalize:
+\begin{align}
+    \epsilon \equiv{}& \frac{1}{\alpha t_{\rm d}},\\
+        ={}& 0.015 \p{\frac{k_{\rm p}}{6k_{\rm qp}}}
+            \p{\frac{m_{\rm p}/M_\star}{0.001}}
+            \p{\frac{a_{\rm p}}{1\;\mathrm{AU}}}^3\nonumber\\
+        &\p{\frac{R_{\rm p}}{R_J}}^{-3}
+            \p{\frac{\Omega_{\rm p}}{2\pi/\p{10\;\mathrm{days}}}}
+            \p{\frac{t_{\rm d}}{10\;\mathrm{Myr}}}^{-1},\\
     \rd{\eta}{\tau} ={}& -\epsilon \eta.\label{eq:deta_dt}
@@
 of study.
+
+In the next two subsections, we further discuss theoretical background relevant
+to our analysis of the evolution of this system. They are not essential to
+reproducing the results presented in \autoref{ss:ad_ensemble}.
 
@@
 $\phi = \pi, \theta > 0$. Of these, CSs 1, 2, 3 are stable while CS4 is unstable
-(see \autoref{s:local_dynamics}). When $\eta < \eta_c$, where
-\begin{equation}
-    \eta_c \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{-3/2},
-\end{equation}
-all four CSs exist, and when $\eta > \eta_c$, only CSs 2, 3 exist
+(see \autoref{s:local_dynamics}). When $\eta < \eta_{\rm c}$, where
+\begin{equation}
+    \eta_{\rm c} \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{-3/2},
+\end{equation}
+all four CSs exist, and when $\eta > \eta_{\rm c}$, only CSs 2, 3 exist
 \citep{henrard1987,ward2004I}. The CS obliquities as a function of $\eta$ are
@@
     $\theta \in [-\pi, \pi]$ is the traditional definition of the polar angle
-    \citep[see e.g.][]{colombo1966,peale1969,henrard1987}.}\label{fig:cs_locs}
+    \citep[see e.g.][]{colombo1966,peale1969,henrard1987}. The vertical dashed
+    line indicates $\eta_{\rm c}$, where CS1 and CS4 merge and annihilate, and the
+    horizontal dashed lines indicate $\theta = I, 180^\circ - I$ the asymptotic
+    behavior for CS2, 3 for $\eta \gg \eta_{\rm c}$.}\label{fig:cs_locs}
 \end{figure}
@@
 
-When $\eta < \eta_c$, CS4 exists and is a saddle point. The two trajectories
+When $\eta < \eta_{\rm c}$, CS4 exists and is a saddle point. The two trajectories
 originating and ending at CS4 are the only two infinite-period orbits in phase
@@
     \mathcal{H} = -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
-            + \eta \p{\hat{s} \cdot \hat{l}_d}.\label{eq:H}
+            + \eta \p{\hat{s} \cdot \hat{l}_{\rm d}}.\label{eq:H}
 \end{equation}
@@
     \autoref{eq:H}, where warmer colors denote more positive values. The black
-    solid line is the separatrix, which only exists for $\eta < \eta_c$. The
+    solid line is the separatrix, which only exists for $\eta < \eta_{\rm c}$. The
     three zones, divided by the separatrix, are labeled. The Cassini states are
@@
     the separatrix, shaded in grey, is formally only defined for $\eta <
-    \eta_c$, but we may identify the phase space trajectories that flow into
+    \eta_{\rm c}$, but we may identify the phase space trajectories that flow into
     zone $II$ when evolved forward in time; this is the shaded region in the top
@@
 \citep{henrard1987,ward2004I}. Defining
-\begin{align*}
+\begin{subequations}\label{se:area_ward}
+    \begin{align}
         z_0 &= \eta\cos I, &
@@
             \chi^2 \cos^2\theta_4 - 1},\\
-\end{align*}
-the areas for $\eta < \eta_c$ are given by
-\begin{subequations}\label{se:area_ward}
-    \begin{align}
-        A_{II} &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
-        A_I &= 2\pi\p{1 - z_0} - \frac{A_2}{2},\\
-        A_{III} &= 2\pi\p{1 + z_0} - \frac{A_2}{2}.
+    \end{align}
+    the areas for $\eta < \eta_{\rm c}$ are given by
+    \begin{align}
+        A_{\rm II} &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
+        A_{\rm I} &= 2\pi\p{1 - z_0} - \frac{A_2}{2},\\
+        A_{\rm III} &= 2\pi\p{1 + z_0} - \frac{A_2}{2}.
     \end{align}
@@
 These are plotted as a function of $\eta$ in \autoref{fig:eq_areas}. Note that
-the zones are not formally defined for $\eta > \eta_c$, but a natural extension
-exists: evolve an initial point $p$ under adiabatic decrease of $\eta > \eta_c$
-until the separatrix appears at $\eta = \eta_c$, then identify $p$ with the zone
-it is in at $\eta_c$. Since phase space area is conserved under adiabatic
-evolution, this implies $A_i\p{\eta > \eta_c} = A_i(\eta_c)$. This extension is
-also reflected in the dashed boundary in \autoref{fig:eq_1contours}.
+the zones are not formally defined for $\eta > \eta_{\rm c}$, but a natural
+extension exists: evolve an initial point $p$ under adiabatic decrease of $\eta
+> \eta_{\rm c}$ until the separatrix appears at $\eta = \eta_{\rm c}$, then
+identify $p$ with the zone it is in at $\eta_{\rm c}$. Since phase space area is
+conserved under adiabatic evolution, this implies $A_i\p{\eta > \eta_{\rm c}} =
+A_i(\eta_{\rm c})$. This extension is also reflected in the dashed boundary in
+\autoref{fig:eq_1contours}.
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{../initial/99_misc/1_areas.png}
-    \caption{Plot of fractional areas of each of the zones $A_{i}(\eta) / 4\pi$
-    as given by \autoref{se:area_ward}. Dotted lines correspond to small $\eta$
-    approximations discussed in \autoref{s:ad_approx}. Dashed lines for $\eta >
-    \eta_c$ effective values of $A_{II}, A_{III}$ for $\eta > \eta_c$, denoting
-    the area of points that would flow into either area under adiabatic decrease
-    of $\eta$ from $\eta > \eta_c$.}\label{fig:eq_areas}
+    \caption{Plot of fractional areas of each of the zones $A_{\rm i}(\eta) /
+    4\pi$ as given by \autoref{se:area_ward}. Dotted lines correspond to small
+    $\eta$ approximations discussed in \autoref{s:ad_approx}. Dashed lines for
+    $\eta > \eta_{\rm c}$ effective values of $A_{\rm II}, A_{\rm III}$ for
+    $\eta > \eta_{\rm c}$, denoting the area of points that would flow into
+    either area under adiabatic decrease of $\eta$ from $\eta > \eta_{\rm
+    c}$.}\label{fig:eq_areas}
 \end{figure}
@@
 longer than the the resonant libration period \citep{ward2004II}. The resonant
-libration period for a nearly separatrix-crossing orbit can be approximated by
-the libration period near CS2, resulting in constraint
-\begin{align}
-    -\at{\frac{1}{\eta}\rd{\eta}{\tau}}_{cross} = \epsilon &\lesssim
-            \frac{1}{T_{lib}},\\
+libration period for a nearly separatrix-crossing orbit is approximated by
+the libration period near CS2 in \citet{millholland_disk}. We find that this
+criterion performs remarkably well despire the expectation that the separatrix
+crossing orbit should be much longer than libration near CS2 (approaching
+infinity as $\epsilon \to 0$). One justification for this is that the libration
+period about CS2 is the longest timescale in the system (see
+\autoref{fig:lambda2})
+
+This constraint can be computed
+\begin{align}
+    -\at{\frac{1}{\eta}\rd{\eta}{\tau}}_{\rm cross} = \epsilon &\lesssim
+            \frac{1}{T_{\rm lib}},\\
         &\lesssim \frac{1}{2\pi}\sqrt{\eta_\star\sin I \sin \theta_2
@@
 presented in \citet{millholland_disk}, where the $\csc^3\theta_2$ term is
-neglected and a square root is missing. See \autoref{s:local_dynamics} for a
-detailed derivation of $T_{lib}$ and comparison to existing work.
+neglected and a square root is missing.
 
@@
 
-We consider the evolution of a system with arbitrary initial $\theta_{sd, i}
-\equiv \at{\theta_{sd}}_{t = 0}$ and $\eta_i \equiv \at{\eta}_{t = 0} \gg 1$. We
-are interested in the distribution of final obliquities after $\eta$ decreases
-to $\eta_f \ll 1$ (after the disk has dissipated to negligible mass). While it
-is likely that $\theta_{sd, i} \approx 0$ as the planet forms in the disk, we
-explore all $\theta_{sd, i} \in [0, \pi]$ for completeness.
-
-We evenly sample $101$ values of $\theta_{sd, i}$, and for each $\theta_{sd, i}$
-value, we pick $101$ $\hat{s}$ initial conditions approximately on the ring
-fixed by $\theta_{sd, i}$\footnote{For each $\theta_{sd, i}$ we choose an
-initial condition on the libration cycle going through $\p{\theta_2 +
-\theta_{sd, i}, \phi_2}$ (where $\p{\theta_2, \phi_2}$ are the coordinates of
-CS2), such that all initial conditions for a given $\theta_{sd, i}$ enclose the
-same initial phase space; see \autoref{sss:a_evo}.}. To be concrete, we choose
-$\eta_i = 10\eta_c$. For each initial condition, we evolve
+We consider the evolution of a system with arbitrary initial $\theta_{\rm sd, i}
+\equiv \at{\theta_{\rm sd}}_{t = 0}$ and $\eta_i \equiv \at{\eta}_{t = 0} \gg
+1$. We are interested in the distribution of final obliquities after $\eta$
+decreases to $\eta_f \ll 1$ (after the disk has dissipated to negligible mass).
+While it is likely that $\theta_{\rm sd, i} \approx 0$ as the planet forms in
+the disk, we explore all $\theta_{\rm sd, i} \in [0, \pi]$ for completeness.
+
+We evenly sample $101$ values of $\theta_{\rm sd, i}$, and for each $\theta_{\rm
+sd, i}$ value, we pick $101$ $\hat{s}$ initial conditions approximately on the
+ring fixed by $\theta_{\rm sd, i}$\footnote{For each $\theta_{\rm sd, i}$ we
+choose an initial condition on the libration cycle going through $\p{\theta_2 +
+\theta_{\rm sd, i}, \phi_2}$ (where $\p{\theta_2, \phi_2}$ are the coordinates
+of CS2), such that all initial conditions for a given $\theta_{\rm sd, i}$
+enclose the same initial phase space; see \autoref{sss:a_evo}.}. To be concrete,
+we choose $\eta_i = 10\eta_{\rm c}$. For each initial condition, we evolve
 Equations~\ref{eq:dsdt_base} and~\ref{eq:deta_dt} until $\eta = 10^{-5}$. For
 such small $\eta$, $\hat{s}$ precesses about $\hat{l}$ with uniform final
-obliquity $\theta_f$. This transfer function $\theta_f\p{\theta_{sd, i}}$ is our
-primary result, and is shown for $I = 5^\circ, 10^\circ, 20^\circ$ in
-\autoref{fig:ad_ensemble}, \autoref{fig:3_ensemble_10_35}, and
+obliquity $\theta_{\rm f}$. This transfer function $\theta_{\rm f}\p{\theta_{\rm
+sd, i}}$ is our primary result, and is shown for $I = 5^\circ, 10^\circ,
+20^\circ$ in \autoref{fig:ad_ensemble}, \autoref{fig:3_ensemble_10_35}, and
 \autoref{fig:3_ensemble_20_35} respectively. The blue dots represent the results
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_35.png}
-    \caption{Top: $\theta_{f}\p{\theta_{sd, i}}$, overlaid with semi-analytic
-    predictions of the $\theta_{ f}$ for each of the four nontrivial
-    dynamical tracks in colored lines. Black dotted lines correspond to
-    small-$\theta_{sd, i}$ predictions derived in \autoref{s:ad_approx}.
+    \caption{Top: $\theta_{\rm f}\p{\theta_{\rm sd, i}}$, overlaid with
+    semi-analytic predictions of the $\theta_{\rm  f}$ for each of the four
+    nontrivial dynamical tracks in colored lines. Black dotted lines correspond
+    to small-$\theta_{\rm sd, i}$ predictions derived in \autoref{s:ad_approx}.
     Bottom: Semi-analytic probabilities of each of the dynamical tracks for each
-    $\theta_{sd, i}$. The five regimes of $\theta_{sd, i}$ values demarcated by
-    the vertical dashed black lines correspond to the five regimes of $A_i$
-    calculated in \autoref{ss:zone_transitions}. Black dotted lines correspond to
-    simple analytic estimates given in
+    $\theta_{\rm sd, i}$. The five regimes of $\theta_{\rm sd, i}$ values
+    demarcated by the vertical dashed black lines correspond to the five regimes
+    of $A_i$ calculated in \autoref{ss:zone_transitions}. Black dotted lines
+    correspond to simple analytic estimates given in
     \autoref{s:ad_approx}.}\label{fig:ad_ensemble}
@@
 \begin{figure}
+    \centering
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_20_35.png}
     \caption{Same as \autoref{fig:3_ensemble_10_35} but for $I = 20^\circ$. The
-    $III \to II \to I$ track is very short since the maximum $A_{II}$ is very
-    near $\eta_c$ for $I = 20^\circ$.}\label{fig:3_ensemble_20_35}
+    $III \to II \to I$ track is very short since the maximum $A_{\rm II}$ is very
+    near $\eta_{\rm c}$ for $I = 20^\circ$.}\label{fig:3_ensemble_20_35}
 \end{figure}
@@
 
-The evolutionary tracks that govern the behavior of $\theta_f\p{\theta_{sd,
-i}}$ correspond to particular sequences of separatrix crossings. Coarsely, they
-can be understood using a combination of (i) how the enclosed phase space area
-by the trajectory evolves across each separatrix crossing, and (ii) the
-associated probabilities with each separatrix crossing.
-
-\subsubsection{Governing Principles: Evolution of $A$}\label{sss:a_evo}
+The evolutionary tracks that govern the behavior of $\theta_{\rm
+f}\p{\theta_{\rm sd, i}}$ correspond to particular sequences of separatrix
+crossings. Coarsely, they can be understood using a combination of (i) how the
+enclosed phase space area by the trajectory evolves across each separatrix
+crossing, and (ii) the associated probabilities with each separatrix crossing.
+
+\subsubsection{Governing Principles: Evolution of Enclosed Phase Space
+Area}\label{sss:a_evo}
 
@@
 over one cycle measured relative to $+\hat{z}$:
-\begin{equation*}
+\begin{equation}
     \int \int\limits_{\cos \theta(\phi)}^1
@@
             \;\mathrm{d}\phi.
-\end{equation*}
-
-Observe that when $\eta_i \gg 1$, trajectories librate about $\hat{l}_d$ with
-constant $\theta_{sd}$, meaning they enclose initial phase space area
+\end{equation}
+
+Observe that when $\eta_i \gg 1$, trajectories librate about $\hat{l}_{\rm d}$
+with constant $\theta_{\rm sd}$, meaning they enclose initial phase space area
 \begin{equation}
     A_i \equiv \at{A}_{t = 0}
-        = 2\pi\p{1 - \cos \theta_{sd, i}}.\label{eq:ai_qsd}
-\end{equation}
-Complications arise when considering finite $\eta_i$, as trajectories near CS2 or
-CS3 librate about these equilibria respectively, rather than $\hat{l}_d$, and
-\autoref{eq:ai_qsd} is no longer exact. In practice, \autoref{eq:ai_qsd} holds
-very well when defining $\theta_{sd, i}$ as the angular distance to CS2; an
-exception is discussed in \autoref{sss:evol_traj}.
+        = 2\pi\p{1 - \cos \theta_{\rm sd, i}}.\label{eq:ai_qsd}
+\end{equation}
+Complications arise when considering finite $\eta_i$, as trajectories near CS2
+or CS3 librate about these equilibria respectively, rather than $\hat{l}_{\rm
+d}$, and \autoref{eq:ai_qsd} is no longer exact. In practice,
+\autoref{eq:ai_qsd} holds very well when defining $\theta_{\rm sd, i}$ as the
+angular distance to CS2; an exception is discussed in \autoref{sss:evol_traj}.
 
@@
 $A_f$ will be conserved for all time. As $\eta \to 0$, trajectories circulate at
-constant obliquity $\theta_f$, related to $A_f$ by
-\begin{equation}
-    2\pi\p{1 - \cos \theta_f} = A_f. \label{eq:qfaf}
+constant obliquity $\theta_{\rm f}$, related to $A_f$ by
+\begin{equation}
+    2\pi\p{1 - \cos \theta_{\rm f}} = A_f. \label{eq:qfaf}
 \end{equation}
@@
 exits zone $II$ at some $\eta_\star$, then the probability of a $II \to I$
-transition is $\Pr\p{II \to I} = -\frac{\dot{A}_{I}}{\dot{A}_{II}}$, while a $II
-\to III$ transition occurs with probability $\Pr\p{II \to III} =
--\frac{\dot{A}_{III}}{\dot{A}_{II}}$.
+transition is $\Pr\p{II \to I} = -\frac{\dot{A}_{\rm I}}{\dot{A}_{\rm II}}$,
+while a $II \to III$ transition occurs with probability $\Pr\p{II \to III} =
+-\frac{\dot{A}_{\rm III}}{\dot{A}_{\rm II}}$.
 
@@
 Returning to the evolution of $\hat{s}$, we can classify trajectories by the
-separatrix encounters experienced. Initially, in the $\eta > \eta_c$ regime,
+separatrix encounters experienced. Initially, in the $\eta > \eta_{\rm c}$ regime,
 only zones $II, III$ exist. Conversely, at the end of the simulation when $\eta
@@
         $II$, enclosing some initial phase space area $A_i$. The trajectory is
-        able to librate without separatrix encounter until $A_{II}(\eta_\star) =
-        A_i$. As the trajectory transitions to a circulating trajectory in zone
-        $I$ immediately bordering the separatrix, it will encompass
-        $-A_I(\eta_\star)$ phase space area. The final $\theta_f$ is then given
-        by \autoref{eq:qfaf}. An analytical approximation to $\theta_f$ is
-        derived in \autoref{s:ad_approx} and is
-        \begin{equation}
-            \cos \theta_{f, II \Rightarrow I} \approx
-                \p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
-                    + \frac{\theta_{sp, i}^2}{4}.\label{eq:qf_21_approx}
+        able to librate without separatrix encounter until $A_{\rm
+        II}(\eta_\star) = A_i$. As the trajectory transitions to a circulating
+        trajectory in zone $I$ immediately bordering the separatrix, it will
+        encompass $-A_{\rm I}(\eta_\star)$ phase space area. The final
+        $\theta_{\rm f}$ is then given by \autoref{eq:qfaf}. An analytical
+        approximation to $\theta_{\rm f}$ is derived in \autoref{s:ad_approx}
+        and is
+        \begin{equation}
+            \cos \theta_{\rm f, II \Rightarrow I} \approx
+                \p{\frac{\pi \theta_{\rm sp, i}^2}{16}}^2 \cot I
+                    + \frac{\theta_{\rm sp, i}^2}{4}.\label{eq:qf_21_approx}
         \end{equation}
@@
         This transition can only occur when the initial condition begins in zone
-        II, requiring $A_i < A_{II}(\eta_c)$. Note $A_{II}(\eta_c)$ is given in
-        closed form in \citet{ward2004I} but appears to be incorrect. Then, at
-        some known $\eta_\star$ satisfying $A_{II}(\eta_\star) = A_i$, the
-        trajectory is ejected from the separatrix following
+        II, requiring $A_i < A_{\rm II}(\eta_{\rm c})$. Note $A_{\rm II}(\eta_{\rm c})$ is
+        given in closed form in \citet{ward2004I} but appears to be incorrect.
+        Then, at some known $\eta_\star$ satisfying $A_{\rm II}(\eta_\star) =
+        A_i$, the trajectory is ejected from the separatrix following
         \autoref{eq:henrard_hop}. Note that since $\pd{A_i}{\eta} < 0$
-        everywhere, while $\pd{A_{II}}{\eta} > 0$ at all possible $\eta_\star$
-        for an initial condition starting in zone $II$, this track always has
-        nonzero probability.
+        everywhere, while $\pd{A_{\rm II}}{\eta} > 0$ at all possible
+        $\eta_\star$ for an initial condition starting in zone $II$, this track
+        always has nonzero probability.
 
@@
         circulating trajectory in zone $III$ bordering the separatrix, upon
-        which it will encompass $A_f = A_I(\eta_\star) + A_{II}(\eta_\star)$.
-        The final obliquity is still given by \autoref{eq:qfaf}, and the
-        analytical approximation derived in \autoref{s:ad_approx} is
-        \begin{equation}
-            \cos \theta_{f, II \Rightarrow III} \approx
-                \p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
-                    - \frac{\theta_{sp, i}^2}{4}.\label{eq:qf_23_approx}
-        \end{equation}
-
-        Again, this track can only occur when $A_i < A_{II}(\eta_c)$, but a
+        which it will encompass $A_f = A_{\rm I}(\eta_\star) + A_{\rm
+        II}(\eta_\star)$. The final obliquity is still given by
+        \autoref{eq:qfaf}, and the analytical approximation derived in
+        \autoref{s:ad_approx} is
+        \begin{equation}
+            \cos \theta_{\rm f, II \Rightarrow III} \approx
+                \p{\frac{\pi \theta_{\rm sp, i}^2}{16}}^2 \cot I
+                    - \frac{\theta_{\rm sp, i}^2}{4}.\label{eq:qf_23_approx}
+        \end{equation}
+
+        Again, this track can only occur when $A_i < A_{\rm II}(\eta_{\rm c})$, but a
         further constraint arises when we consider the transition probability
         given by \autoref{eq:henrard_hop}. Upon examination of
-        \autoref{fig:eq_areas}, it is clear that $\pd{A_{III}}{\eta} > 0$ for
+        \autoref{fig:eq_areas}, it is clear that $\pd{A_{\rm III}}{\eta} > 0$ for
         many $\eta$. Call
         \begin{equation}
-            \eta_{\min, III} \equiv \argmin A_{III}(\eta),
+            \eta_{\min, III} \equiv \argmin A_{\rm III}(\eta),
         \end{equation}
         which is labeled in \autoref{fig:eq_areas}, then if $\eta_\star >
-        \eta_{\min, III}$ then $\Pr_{II \to III} < 0$. This is understood as a
+        \eta_{\rm \min, III}$ then $\Pr_{\rm II \to III} < 0$. This is understood as a
         forbidden transition, and so $II \to III$ is only a permitted dynamical
-        track if $\eta_\star <, \eta_{\min, III}$.
+        track if $\eta_\star <, \eta_{\rm \min, III}$.
 
     \item $III \to I$ --- This track is depicted in \autoref{fig:ad_31}.
-        The trajectory encounters the separatrix when $A_I(\eta_\star) +
-        A_{II}(\eta_\star) = A_i$, upon which it transitions to a zone $I$
-        trajectory enclosing $A_f = -A_I$. Then, as always, the final obliquity
-        is given by \autoref{eq:qfaf}.
-
-        This track can only occur if $A_i > A_{II}(\eta_c)$, but is also
+        The trajectory encounters the separatrix when $A_{\rm I}(\eta_\star) +
+        A_{\rm II}(\eta_\star) = A_i$, upon which it transitions to a zone $I$
+        trajectory enclosing $A_f = -A_{\rm I}$. Then, as always, the final
+        obliquity is given by \autoref{eq:qfaf}.
+
+        This track can only occur if $A_i > A_{\rm II}(\eta_{\rm c})$, but is also
         constrained by requiring its $A_i$ is sufficiently small it will
@@
         the separatrix, which is a $III \to III$ transition). This is written
-        $A_i < \max A_I + A_{II} = 4\pi - \min A_{III}$.
-
-        Note that since $\pd{A_I}{\eta} < 0$ always while $\pd{A_{III}}{\eta} >
-        0$ for all accessible $\eta_{\star}$, this track is always permitted.
+        $A_i < \max A_{\rm I} + A_{\rm II} = 4\pi - \min A_{\rm III}$.
+
+        Note that since $\pd{A_{\rm I}}{\eta} < 0$ always while $\pd{A_{\rm
+        III}}{\eta} > 0$ for all accessible $\eta_{\star}$, this track is always
+        permitted.
 
     \item $III \to II \to I$ --- This track is depicted in \autoref{fig:ad_321}.
-        The first separatrix encounter occurs at $\eta_1$ when $A_I(\eta_1) +
-        A_{II}(\eta_1) = A_i$, upon which the trajectory moves into zone $II$
-        enclosing intermediate phase space area $A_m = A_{II}(\eta_1)$.
-        Examining \autoref{fig:eq_areas}, there exist values $A$ for which
-        $A_{II}(\eta) = A$ has multiple solutions, and $\eta_1 > \eta_{II,
-        \max}$ as labeled. These are the only values for which the $III \to II
-        \to I$ transition is permitted. Thus, as $\eta$ continues to decrease, a
-        second $\eta_2$ value exists for which $A_m = A_{II}(\eta_2)$, upon
-        which the trajectory is ejected to zone $I$ and $A_f = -A_I(\eta_2)$.
-        The final obliquity again then obeys \autoref{eq:qfaf}.
+        The first separatrix encounter occurs at $\eta_1$ when $A_{\rm
+        I}(\eta_1) + A_{\rm II}(\eta_1) = A_i$, upon which the trajectory moves
+        into zone $II$ enclosing intermediate phase space area $A_m = A_{\rm
+        II}(\eta_1)$. Examining \autoref{fig:eq_areas}, there exist values $A$
+        for which $A_{\rm II}(\eta) = A$ has multiple solutions, and $\eta_1 >
+        \eta_{\rm II, \max}$ as labeled. These are the only values for which the
+        $III \to II \to I$ transition is permitted. Thus, as $\eta$ continues to
+        decrease, a second $\eta_2$ value exists for which $A_m = A_{\rm
+        II}(\eta_2)$, upon which the trajectory is ejected to zone $I$ and $A_f
+        = -A_{\rm I}(\eta_2)$. The final obliquity again then obeys
+        \autoref{eq:qfaf}.
 
         Similar to the $III \to I$ track, the $III \to II \to I$ track can only
-        occur over the same $A_{II}(\eta_c) < A_i < \max A_I + A_{II}$ interval.
-        The probability of encountering this track is set by the initial $III
-        \to II$ transition. It bears noting that this probability is only
-        nonnegative for a very small fraction of $A_i$ values, since it requires
-        $\pd{A_{II}}{\eta}$ and $\pd{A_{III}}{\eta}$ to have different signs;
-        this occurs only if $A_{II}\p{\eta_c} < A_i < A_{II, \max}$. Outside of
-        these bounds, $\Pr_{III \to II} < 0$ which is interpreted again as a
-        forbidden transition.
+        occur over the same $A_{\rm II}(\eta_{\rm c}) < A_i < \max A_{\rm I} + A_{\rm
+        II}$ interval. The probability of encountering this track is set by the
+        initial $III \to II$ transition. It bears noting that this probability
+        is only nonnegative for a very small fraction of $A_i$ values, since it
+        requires $\pd{A_{\rm II}}{\eta}$ and $\pd{A_{\rm III}}{\eta}$ to have
+        different signs; this occurs only if $A_{\rm II}\p{\eta_{\rm c}} < A_i <
+        A_{\rm II, \max}$. Outside of these bounds, $\Pr_{\rm III \to II} < 0$
+        which is interpreted again as a forbidden transition.
 
         Then, once a $III \to II$ transition occurs, the second $II \to I$
-        transition occurs for some $\eta_2$ satisfying $A_{II}(\eta_2) =
-        A_{II}(\eta_1), \eta_2 < \eta_1$. Graphical inspection shows that
-        $\pd{A_{II}}{\eta}$ has the same sign as $\pd{A_{III}}{\eta}$ over all
-        possible values, so the second $II \to I$ transition is guaranteed,
-        completing the $III \to II \to I$ track.
+        transition occurs for some $\eta_2$ satisfying $A_{\rm II}(\eta_2) =
+        A_{\rm II}(\eta_1), \eta_2 < \eta_1$. Graphical inspection shows that
+        $\pd{A_{\rm II}}{\eta}$ has the same sign as $\pd{A_{\rm III}}{\eta}$
+        over all possible values, so the second $II \to I$ transition is
+        guaranteed, completing the $III \to II \to I$ track.
 
@@
         separatrix encounter ever occurs, and $A$ is constant throughout the
-        evolution. This constraint equates to $A_i > \max A_I + A_{II}$,
-        whereupon no separatrix encounter occurs at all, and $A_f = A_i$, which
-        for $\eta_i \to \infty, \eta_f \to 0$ results in $\theta = \theta_{sd,
-        i}$.
-
-        Note that a small deviation from $\theta = \theta_{sd, i}$ occurs
+        evolution. This constraint equates to $A_i > \max A_{\rm I} + A_{\rm
+        II}$, whereupon no separatrix encounter occurs at all, and $A_f = A_i$,
+        which for $\eta_i \to \infty, \eta_f \to 0$ results in $\theta =
+        \theta_{\rm sd, i}$.
+
+        Note that a small deviation from $\theta = \theta_{\rm sd, i}$ occurs
         because we use finite $\eta_i$, as hinted at in \autoref{sss:a_evo}.
-        This is because for $\theta_{sd, i} \gtrsim \pi/2$, trajectories are
+        This is because for $\theta_{\rm sd, i} \gtrsim \pi/2$, trajectories are
         better described as librating about CS3. Nevertheless, we can still
@@
         libration about CS3 with polar angle $2\pi + \theta_3 - \theta_2 -
-        \theta_{sd, i}$. This recovers the correct transfer function
-        $\theta_f\p{\theta_{sd, i}}$ for the $III \to III$ regime, as can be
-        seen visibly in \autoref{fig:3_ensemble_20_35}.
+        \theta_{\rm sd, i}$. This recovers the correct transfer function
+        $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for the $III \to III$ regime, as
+        can be seen visibly in \autoref{fig:3_ensemble_20_35}.
 \end{enumerate}
@@
 \begin{enumerate}
-    \item $A_i \in \s{0, A_{II}\p{\eta_{\min, III}}}$ --- $II \to III, II \to I$
-        both possible.
-
-    \item $A_i \in \s{A_{II}\p{\eta_{\min, III}}, A_{II}(\eta_c)}$ --- $II \to
-        I$ only.
-
-    \item $A_i \in \s{A_{II}(\eta_c), A_{II, \max}}$ --- $III \to I, III \to II
-        \to I$ both possible.
-
-    \item $A_i \in \s{A_{II, \max}, \max A_I + A_{II}}$ --- $III \to I$ only.
-
-    \item $A_i > \max A_I + A_{II}$ --- $III \to III$ only.
+    \item $A_i \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$ --- $II \to III,
+        II \to I$ both possible.
+
+    \item $A_i \in \s{A_{\rm II}\p{\eta_{\rm \min, III}}, A_{\rm II}(\eta_{\rm c})}$
+        --- $II \to I$ only.
+
+    \item $A_i \in \s{A_{\rm II}(\eta_{\rm c}), A_{\rm II, \max}}$ --- $III \to I, III
+        \to II \to I$ both possible.
+
+    \item $A_i \in \s{A_{\rm II, \max}, \max A_{\rm I} + A_{\rm II}}$ --- $III
+        \to I$ only.
+
+    \item $A_i > \max A_{\rm I} + A_{\rm II}$ --- $III \to III$ only.
 \end{enumerate}
-The corresponding ranges for for $\theta_{sd,i}$ can be computed via
+The corresponding ranges for for $\theta_{\rm sd,i}$ can be computed via
 \autoref{eq:ai_qsd}. The boundaries between these ranges are overplotted in
@@
     \end{subfigure}
-    \caption{Fiducial simulation following the $A_{II} \to A_{I}$ transition. An
-    initial $\theta_{sd, i} = 0.3\;\mathrm{rad} \approx 17.2^\circ$ was used, as
-    well as $\epsilon = 3 \times 10^{-4}$. Top plot upper panel: plot of $\cos
-    \theta(t)$ (green) in an example simulation. Overlaid are the locations of
-    Cassini State 2 (red), and upper and lower bounds on the separatrix (black).
-    Note that the trajectory successfully tracks CS2 to an obliquity $\theta
-    \approx 90^\circ$. Light vertical blue lines denote times portrayed in
-    bottom plot. Top plot lower panel: plot of the enclosed separatrix area
-    obtained by integrating the simulated trajectory (blue dots) and adiabatic
-    theory (red line). Even though the enclosed area jumps at separatrix
-    crossing, the resultant $A$ is still accurately predicted. Lower plot:
-    snapshots in the $\p{\cos \theta, \phi}$ space of the simulation
-    trajectories for the vertical blue lines in the top plots. These times
-    correspond to the start of the simulation, the appearance of the separatrix,
-    two panels depicting the separatrix crossing process, and a final snapshot
-    at $\eta = 10^{-3.5}$. The green line denotes a full circulation or
-    libration cycle at the selected time, including an arrow for directionality.
-    The separatrix at the start/end of the portrayed cycle are shown in
-    solid/dashed black lines respectively. Also labeled is CS2 at the start of
-    the cycle (red). Finally, the enclosed phase space area is shaded in grey
-    ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
+    \caption{Fiducial simulation following the $A_{\rm II} \to A_{\rm I}$
+    transition. An initial $\theta_{\rm sd, i} = 0.3\;\mathrm{rad} \approx
+    17.2^\circ$ was used, as well as $\epsilon = 3 \times 10^{-4}$. Top plot
+    upper panel: plot of $\cos \theta(t)$ (green) in an example simulation.
+    Overlaid are the locations of Cassini State 2 (red), and upper and lower
+    bounds on the separatrix (black). Note that the trajectory successfully
+    tracks CS2 to an obliquity $\theta \approx 90^\circ$. Light vertical blue
+    lines denote times portrayed in bottom plot. Top plot lower panel: plot of
+    the enclosed separatrix area obtained by integrating the simulated
+    trajectory (blue dots) and adiabatic theory (red line). Even though the
+    enclosed area jumps at separatrix crossing, the resultant $A$ is still
+    accurately predicted. Lower plot: snapshots in the $\p{\cos \theta, \phi}$
+    space of the simulation trajectories for the vertical blue lines in the top
+    plots. These times correspond to the start of the simulation, the appearance
+    of the separatrix, two panels depicting the separatrix crossing process, and
+    a final snapshot at $\eta = 10^{-3.5}$. The green line denotes a full
+    circulation or libration cycle at the selected time, including an arrow for
+    directionality. The separatrix at the start/end of the portrayed cycle are
+    shown in solid/dashed black lines respectively. Also labeled is CS2 at the
+    start of the cycle (red). Finally, the enclosed phase space area is shaded
+    in grey ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
 \end{figure}
@@
     \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ track.
-    $\theta_{sd, i} = 0.3\;\mathrm{rad}$ and $\epsilon = 3.01 \times
+    $\theta_{\rm sd, i} = 0.3\;\mathrm{rad}$ and $\epsilon = 3.01 \times
     10^{-4}$.}\label{fig:ad_23}
@@
     \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_I$
-    track. $\theta_{sd, i} = 89.1^\circ$, and $\epsilon = 3 \times
+    \caption{Same as \autoref{fig:ad_21} but for the $A_{\rm III} \to A_{\rm I}$
+    track. $\theta_{\rm sd, i} = 89.1^\circ$, and $\epsilon = 3 \times
     10^{-4}$.}\label{fig:ad_31}
@@
     \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_{II} \to A_I$
-    track. $\theta_{sd, i} = 60^\circ$, and $\epsilon = 3.14 \times 10^{-4}$.
-    Two separatrix crossings are shown.}\label{fig:ad_321}
+    \caption{Same as \autoref{fig:ad_21} but for the $A_{\rm III} \to A_{\rm II}
+    \to A_{\rm I}$ track. $\theta_{\rm sd, i} = 60^\circ$, and $\epsilon = 3.14
+    \times 10^{-4}$. Two separatrix crossings are shown.}\label{fig:ad_321}
 \end{figure}
@@
 Later, these large scatters take on band-like structures that seem to persist
-across values of $\theta_{sd, i}$; we attribute these to the separatrix crossing
-process becoming sensitive to the \emph{phase} of the final
+across values of $\theta_{\rm sd, i}$; we attribute these to the separatrix
+crossing process becoming sensitive to the \emph{phase} of the final
 libration/circulation orbit at separatrix crossing. This is equivalent to
@@
     \caption{Same as \autoref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$,
-    and restricting $\theta_{sd, i} < 90^\circ$. A larger spread from the
+    and restricting $\theta_{\rm sd, i} < 90^\circ$. A larger spread from the
     dynamical tracks is observed in the data.}\label{fig:3_ensemble_05_25}
@@
 
-A formula for $\theta_{f}$ assuming $\theta_{sd, i} = 0$ initially can be
-given (see \autoref{s:ad_approx})
-\begin{equation}
-    \theta_{f}\p{\theta_{sd, i} = 0} = \sqrt{\frac{2\pi}{\epsilon}}
-        \tan I\cos I.\label{eq:nonad_q_f}
-\end{equation}
-We can naively generalize this by recognizing that any nonzero $\theta_{sd, i}$
-manifests as obliquity variations as $\hat{s}$ librates about $\hat{l}_d$. These
-can be accounted for by simply allowing the final obliquity to vary over the
-same range as the initial obliquity, or,
-\begin{equation}
-    \theta_{f}\p{\theta_{sd, i}} - \sqrt{\frac{2\pi}{\epsilon}}
-        \tan I\cos I\in \s{-\theta_{sd, i}, \theta_{sd,i}}
+A formula for $\theta_{\rm f}$ assuming $\theta_{\rm sd, i} = 0$ initially can
+be given (see \autoref{s:ad_approx})
+\begin{equation}
+    \theta_{\rm f}\p{\theta_{\rm sd, i} = 0} = \sqrt{\frac{2\pi}{\epsilon}} \tan
+        I\cos I.\label{eq:nonad_q_f}
+\end{equation}
+We can naively generalize this by recognizing that any nonzero $\theta_{\rm sd,
+i}$ manifests as obliquity variations as $\hat{s}$ librates about $\hat{l}_{\rm
+d}$. These can be accounted for by simply allowing the final obliquity to vary
+over the same range as the initial obliquity, or,
+\begin{equation}
+    \theta_{\rm f}\p{\theta_{\rm sd, i}} - \sqrt{\frac{2\pi}{\epsilon}} \tan
+        I\cos I\in \s{-\theta_{\rm sd, i}, \theta_{\rm sd,i}}
         .\label{eq:nonad_q_f_dist}
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_05.png}
-    \caption{$\theta_{ f}\p{\theta_{sd, i}}$ at $\epsilon = 0.3$, firmly in
-    the non-adiabatic regime. Note the clear double-valuedeness has disappeared,
-    as have distinct dynamical tracks. The red dotted line presents the
-    analytical prediction given by
+    \caption{$\theta_{\rm  f}\p{\theta_{\rm sd, i}}$ at $\epsilon = 0.3$, firmly
+    in the non-adiabatic regime. Note the clear double-valuedeness has
+    disappeared, as have distinct dynamical tracks. The red dotted line presents
+    the analytical prediction given by
     \autoref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemeble}
@@
 shown in \autoref{fig:nonad_3_scan}. Note that $\epsilon \to 0$ recovers the
-adiabatic regime. The deviation of $\theta_f$ from the analytical prediction
-within the adiabatic regime is indeed due to adiabatic effects becoming
-dominant; compare to \autoref{fig:nonad_3_scan_20} where little deviation is
-observed until $\theta_f \approx 90^\circ$.
+adiabatic regime. The deviation of $\theta_{\rm f}$ from the analytical
+prediction within the adiabatic regime is indeed due to adiabatic effects
+becoming dominant; compare to \autoref{fig:nonad_3_scan_20} where little
+deviation is observed until $\theta_{\rm f} \approx 90^\circ$.
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3scan.png}
-    \caption{Plot of $\theta_{ f}\p{\theta_{sd, i} = 0}$ as a function of
-    $\epsilon$, where $I = 5^\circ$. The shaded area, bordered by the black
+    \caption{Plot of $\theta_{\rm  f}\p{\theta_{\rm sd, i} = 0}$ as a function
+    of $\epsilon$, where $I = 5^\circ$. The shaded area, bordered by the black
     line, corresponds to the adiabatic regime estimated by
@@
     \autoref{eq:nonad_q_f}, which is in good agreement for $\epsilon \gtrsim
-    0.1$ the non-adiabatic regime, while $\theta_{f} \approx 90^\circ$ in the
-    adiabatic regime.}\label{fig:nonad_3_scan}
+    0.1$ the non-adiabatic regime, while $\theta_{\rm f} \approx 90^\circ$ in
+    the adiabatic regime.}\label{fig:nonad_3_scan}
 \end{figure}
@@
     \caption{Same as \autoref{fig:nonad_3_scan} but for $I=20^\circ$. Note that
-    \autoref{eq:nonad_q_f} is accurate until $\theta_f \approx 90^\circ$, which
-    is much closer to the transition to adiabaticity. Comparison with
+    \autoref{eq:nonad_q_f} is accurate until $\theta_{\rm f} \approx 90^\circ$,
+    which is much closer to the transition to adiabaticity. Comparison with
     \autoref{fig:nonad_3_scan} suggests that the breakdown of
@@
 dissipating protoplanetary disk for arbitrary initial misalignment angles. This
-is described by transfer function $\theta_f\p{\theta_{sd, i}}$, where $\theta_f$
-is the final planetary obliquity and $\theta_{sd, i}$ is the initial
-misalignment angle between the planet's spin axis and the disk's orbital angular
-momentum. We have presented analytical results that capture the behavior of
-$\theta_f\p{\theta_{sd, i}}$ in both the adiabatic and nonadiabatic limits:
+is described by transfer function $\theta_{\rm f}\p{\theta_{\rm sd, i}}$, where
+$\theta_{\rm f}$ is the final planetary obliquity and $\theta_{\rm sd, i}$ is
+the initial misalignment angle between the planet's spin axis and the disk's
+orbital angular momentum. We have presented analytical results that capture the
+behavior of $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ in both the adiabatic and
+nonadiabatic
+limits:
 \begin{enumerate}
@@
         via numerical simulation the dual-valued behavior of $\theta$ as nonzero
-        values of $\theta_{sd, i}$ are permitted (see
+        values of $\theta_{\rm sd, i}$ are permitted (see
         \autoref{fig:ad_ensemble}). We are able to capture both the exact final
@@
         breaks down when criterion \autoref{eq:ad_constr} is violated. We find a
-        broad range of $\theta$ values can be excited for a given $\theta_{sd,
-        i}$ (see \autoref{fig:nonad_3_ensemeble}). We provide an analytical
-        expression of the bounds on $\theta_f\p{\theta_{sd, i}}$ in
+        broad range of $\theta$ values can be excited for a given $\theta_{\rm
+        sd, i}$ (see \autoref{fig:nonad_3_ensemeble}). We provide an analytical
+        expression of the bounds on $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ in
         \autoref{eq:nonad_q_f_dist}.
@@
 
-It is of interest to note the leading order behavior of $\theta$ in the
-small $\theta_{sd, i}$ limit given by \autoref{eq:qf_21_approx} and
-\autoref{eq:qf_23_approx}. Therefore, if $\theta_{sd, i}$ is generally small, as
-would be expected for peacefully forming planets, resonance capture induced by
-an adiabatically dissipating protoplanetary disk is expected to significantly
-narrow the final $\theta$ spread compared to the initial $\theta_{sd, i}$
-spread.
+It is of interest to note the leading order behavior of $\theta$ in the small
+$\theta_{\rm sd, i}$ limit given by \autoref{eq:qf_21_approx} and
+\autoref{eq:qf_23_approx}. Therefore, if $\theta_{\rm sd, i}$ is generally
+small, as would be expected for peacefully forming planets, resonance capture
+induced by an adiabatically dissipating protoplanetary disk is expected to
+significantly narrow the final $\theta$ spread compared to the initial
+$\theta_{\rm sd, i}$ spread.
 
@@
 We next develop some approximate forms for the CS obliquities that will be
-useful for guiding later discussion.
+useful for guiding later discussion. Denote $\theta_{\rm cs}$ the obliquity of
+some Cassini State (fixed point of \autoref{se:H_eom}).
 \begin{enumerate}
-    \item $\eta \ll 1, \cos \theta_{CS} \ll 1$ --- This is the limiting case for
-        CS2 and CS4 when $\eta \ll \eta_c$. We examine \autoref{seq:H_eom_phi_t}
-        and approximate $\cot \theta \approx \cos \theta$ to find
-        \begin{equation}
-            \cos \theta_{CS} \approx \frac{\eta \cos I}
+    \item $\eta \ll 1, \cos \theta_{\rm cs} \ll 1$ --- This is the limiting case
+        for CS2 and CS4 when $\eta \ll \eta_{\rm c}$. We examine
+        \autoref{seq:H_eom_phi_t} and approximate $\cot \theta \approx \cos
+        \theta$ to find
+        \begin{equation}
+            \cos \theta_{\rm cs} \approx \frac{\eta \cos I}
                 {1 \mp \eta \sin I}.
@@
 
-    \item $\sin \theta_{CS} \ll 1$ --- The $\eta \ll 1, \eta \gg 1$ cases can be
-        solved together, and are the limiting cases both for CS1 and CS3 when
-        $\eta \ll \eta_c$, and for CS2 and CS3 when $\eta \gg \eta_c$. It proves
-        easiest to rewrite \autoref{seq:H_eom_phi_t} as
-        \begin{equation}
-            0 = \cos \theta_{CS}\p{-1 + 2\eta
-                \frac{\sin \p{I \pm \theta_{CS}}}{\sin \p{2\theta_{CS}}}}.
-                \label{eq:rewritten_dphi}
+    \item $\sin \theta_{\rm cs} \ll 1$ --- The $\eta \ll 1, \eta \gg 1$ cases
+        can be solved together, and are the limiting cases both for CS1 and CS3
+        when $\eta \ll \eta_{\rm c}$, and for CS2 and CS3 when $\eta \gg
+        \eta_{\rm c}$. It proves easiest to rewrite \autoref{seq:H_eom_phi_t} as
+        \begin{equation}
+            0 = \cos \theta_{\rm cs}\p{-1 + 2\eta
+                \frac{\sin \p{I \pm \theta_{\rm cs}}}{\sin \p{2\theta_{\rm
+                    cs}}}}.\label{eq:rewritten_dphi}
         \end{equation}
         The $\pm$ choice again comes from choice of $\cos \phi$. Then assuming
-        $\theta_{CS}, I \ll 1$, we obtain $\frac{I \pm
-        \theta_{CS}}{2\theta_{CS}} = \frac{1}{2\eta}$ or
-        \begin{equation}
-            \theta_{CS} = \frac{\eta I}{1 \mp \eta}.
-        \end{equation}
-
-        In the limit $\eta \ll \eta_c$, these two solutions describe CS1 and
-        CS3, while in the limit $\eta \gg \eta_c$ these two solutions describe
-        CS2 and CS3.
+        $\theta_{\rm cs}, I \ll 1$, we obtain $\frac{I \pm
+        \theta_{\rm cs}}{2\theta_{\rm cs}} = \frac{1}{2\eta}$ or
+        \begin{equation}
+            \theta_{\rm cs} = \frac{\eta I}{1 \mp \eta}.
+        \end{equation}
+
+        In the limit $\eta \ll \eta_{\rm c}$, these two solutions describe CS1
+        and CS3, while in the limit $\eta \gg \eta_{\rm c}$ these two solutions
+        describe CS2 and CS3.
 \end{enumerate}
-Note that the $\theta_{CS}$ values derived here do not follow the same
+Note that the $\theta_{\rm cs}$ values derived here do not follow the same
 convention as \autoref{fig:cs_locs}, because the previous $\theta$ conventions
@@
 To examine stability of each CS, it proves very easy to handle them generally.
-We linearize about an equilibrium located at $\bar{\phi} = 0, \pi$ but arbitrary
-$\bar{\theta}$. Linearizing \autoref{se:H_eom} about $\phi = \bar{\phi} + \delta
-\phi, \theta = \bar{\theta} + \delta \theta$ gives
+We linearize about an equilibrium located at $\phi_{\rm cs} = 0, \pi$ but
+arbitrary $\theta_{\rm cs}$. Linearizing \autoref{se:H_eom} about $\phi =
+\phi_{\rm cs} + \delta \phi, \theta = \theta_{\rm cs} + \delta \theta$ gives
 \begin{subequations}\label{se:H_eom_lin}
     \begin{align}
-        \rd{\delta \phi}{t} &= \sin \bar{\theta} \delta \theta
-            \mp \eta \frac{\sin I}{\sin^2\bar{\theta}} \delta \theta,\\
+        \rd{\delta \phi}{t} &= \sin \theta_{\rm cs} \delta \theta
+            \mp \eta \frac{\sin I}{\sin^2\theta_{\rm cs}} \delta \theta,\\
         \rd{\delta \theta}{t} &= \pm \eta \sin I \delta \phi.
@@
 \end{subequations}
-Note that the positive sign corresponds to $\cos \bar{\phi} = +1, \bar{\phi} =
-0$. Eliminating $\delta \theta$ gives
-\begin{align}
-    \rtd{\delta \phi}{t} &= \p{\sin \bar{\theta}
+Note that the positive sign corresponds to $\phi_{\rm cs} = 0$. Eliminating
+$\delta \theta$ gives
+\begin{align}
+    \rtd{\delta \phi}{t} &= \p{\sin \theta_{\rm cs}
         \mp \eta \sin I\csc^2\theta}\p{\pm \eta \sin I} \delta
@@
 \begin{align}
-    \omega_{lib} &= \sqrt{-\lambda^2},\\
-        &= \sqrt{\p{\sin \bar{\theta}
+    \omega_{\rm lib} &= \sqrt{-\lambda^2},\\
+        &= \sqrt{\p{\sin \theta_{\rm cs}
             \mp \eta \sin I \csc^2\theta}\p{\mp \eta \sin I}}.
 \end{align}
-The libration period is related simply $T_{lib} = \frac{2\pi}{\omega_{lib}}$.
+The libration period is related simply $T_{\rm lib} = \frac{2\pi}{\omega_{\rm
+lib}}$.
 \begin{figure}[t]
@@
     \caption{Plot of $\lambda^2$ per \autoref{eq:lambda2} evaluated at each
-    of the Cassini States. It is clear that CS4 is a saddle point when it
-    exists while all others are centers.}\label{fig:lambda2}
+    of the Cassini States. The vertical axis is rescaled to limit the vertical
+    extent of the plot. Note that CS4 is a saddle point ($\lambda^2 > 0$) when
+    it exists while all others are centers ($\lambda^2 < 0$). The horizontal
+    dashed line is $\lambda^2 = 0$ the instability boundary while $\eta_c$ is
+    labered in the vertical dashed line.}\label{fig:lambda2}
 \end{figure}
@@
 approximation $\theta \gg I$ made in deriving Equation 3 of
-\citet{ward2004II}. This is invalid in the $\eta \gtrsim \eta_c$ limit for
-CS2, since $\theta_{CS} \approx I$ in this regime as was shown above.
+\citet{ward2004II}. This is invalid in the $\eta \gtrsim \eta_{\rm c}$ limit for
+CS2, since $\theta_{\rm cs} \approx I$ in this regime as was shown above.
 
@@
 In this section, we will use approximations valid for small $\eta$ to derive
-analytic expressions for the final obliquities at small $\theta_{sd, i}$ and
+analytic expressions for the final obliquities at small $\theta_{\rm sd, i}$ and
 associated probabilities for the $II \to I, II \to III$ tracks that are
@@
 Note that $\phi_4 = 0$. Then, the separatrix is the level curve of the
-Hamiltonian intersecting CS4, so it satisfies $\mathcal{H}\p{\theta_{sep}(\phi),
-\phi} = \mathcal{H}\p{\theta_4, \phi_4}$. This solves to be approximately
-\begin{equation}
-    \cos \theta_{sep}(\phi) \approx \cos \theta_4 \pm
+Hamiltonian intersecting CS4, so it satisfies $\mathcal{H}\p{\theta_{\rm
+sep}(\phi), \phi} = \mathcal{H}\p{\theta_4, \phi_4}$. This solves to be
+approximately
+\begin{equation}
+    \cos \theta_{\rm sep}(\phi) \approx \cos \theta_4 \pm
         \sqrt{2\eta \sin I\p{1 - \cos \phi}}.
@@
 \begin{equation}
-    A_{II}(\eta) \approx 16\sqrt{\eta \sin I}.\label{eq:a_approx}
+    A_{\rm II}(\eta) \approx 16\sqrt{\eta \sin I}.\label{eq:a_approx}
 \end{equation}
 This, in conjunction with \autoref{eq:henrard_hop}, is sufficient to compute
-$\theta_f\p{\theta_{sd, i}}$ for zone $II$ initial conditions.
+$\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for zone $II$ initial conditions.
 
 \begin{enumerate}
-    \item For a given $\theta_{sd, i}$, we know that if $\eta \to \infty$ then
-        the trajectory executes simple libration about $\hat{l}_d$, and so $A =
-        2\pi\p{1 - \cos \theta_{sd, i}} \approx \pi \theta_{sd, i}^2$. This
-        then implies $\eta_\star$ must be the solution to $A_{II}(\eta_\star) =
-        A$, or
-        \begin{align}
-            \eta_\star &\approx \p{\frac{2\pi\p{1 - \cos \theta_{sd,i}}}{
+    \item For a given $\theta_{\rm sd, i}$, we know that if $\eta \to \infty$
+        then the trajectory executes simple libration about $\hat{l}_{\rm d}$,
+        and so $A = 2\pi\p{1 - \cos \theta_{\rm sd, i}} \approx \pi \theta_{\rm
+        sd, i}^2$. This then implies $\eta_\star$ must be the solution to
+        $A_{\rm II}(\eta_\star) = A$, or
+        \begin{align}
+            \eta_\star &\approx \p{\frac{2\pi\p{1 - \cos \theta_{\rm sd,i}}}{
                         16}}^2 / \sin I,\\
-                    &\approx \p{\frac{\pi \theta_{sd, i}^2}{16}}^2/\sin I.
+                    &\approx \p{\frac{\pi \theta_{\rm sd, i}^2}{16}}^2/\sin I.
         \end{align}
@@
             \begin{align}
-                \Pr_{II \Rightarrow I} &\approx \frac{2\pi
+                \Pr_{\rm II \Rightarrow I} &\approx \frac{2\pi
                     \eta_{\star} \cos I + 4\sqrt{\eta_{\star}\sin
                     I}}{8\sqrt{\eta_{\star}\sin I}},\\
-                \Pr_{II \Rightarrow III} &\approx \frac{-2\pi
+                \Pr_{\rm II \Rightarrow III} &\approx \frac{-2\pi
                     \eta_{\star} \cos I + 4\sqrt{\eta_{\star}\sin
@@
 
-    \item Upon a transition to zone $I$ or zone $III$, the final obliquities can be
-        predicted by observing the final adiabatic invariant $A_f =
-        -A_I(\eta_\star)$ in the zone $I$ case and $A_f = A_I(\eta_\star) +
-        A_II(\eta_\star)$ in the zone $III$ case. As $\eta \to 0$, these
+    \item Upon a transition to zone $I$ or zone $III$, the final obliquities can
+        be predicted by observing the final adiabatic invariant $A_f = -A_{\rm
+        I}(\eta_\star)$ in the zone $I$ case and $A_f = A_{\rm I}(\eta_\star) +
+        A_{\rm I}I(\eta_\star)$ in the zone $III$ case. As $\eta \to 0$, these
         correspond to obliquities
@@
             \begin{align}
-                \cos \theta_{f, II \Rightarrow I} &\approx
-                    \p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
-                        + \frac{\theta_{sp, i}^2}{4},\\
-                \cos \theta_{f, II \Rightarrow III} &\approx
-                    \p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
-                        - \frac{\theta_{sp, i}^2}{4}.
+                \cos \theta_{\rm f, II \Rightarrow I} &\approx
+                    \p{\frac{\pi \theta_{\rm sp, i}^2}{16}}^2 \cot I
+                        + \frac{\theta_{\rm sp, i}^2}{4},\\
+                \cos \theta_{\rm f, II \Rightarrow III} &\approx
+                    \p{\frac{\pi \theta_{\rm sp, i}^2}{16}}^2 \cot I
+                        - \frac{\theta_{\rm sp, i}^2}{4}.
             \end{align}
@@
 \autoref{eq:dsdt_base} and choose coordinate axes such that $\hat{l} = \hat{z},
-\hat{l}_d = \hat{z} \cos I + \hat{x}\sin I$, then we obtain
+\hat{l}_{\rm d} = \hat{z} \cos I + \hat{x}\sin I$, then we obtain
 \begin{equation}
@@
 
-Now, let's assume that $s_z \approx \cos I$ throughout the evolution of $\hat{s}$
-(note that $\theta_{sd, i} = 0$ implies the initial $s_z = \cos I$). Then let's
-examine the evolution of quantity $S = s_x + is_y$ instead:
+Now, let's assume that $s_z \approx \cos I$ throughout the evolution of
+$\hat{s}$ (note that $\theta_{\rm sd, i} = 0$ implies the initial $s_z = \cos
+I$). Then let's examine the evolution of quantity $S = s_x + is_y$ instead:
 \begin{equation}
@@
 -\epsilon/\cos I$. Then we expand near $t = 0$ so
-\begin{align*}
+\begin{align}
     \Phi(t) &\approx \Phi(0) + \frac{1}{2}\ddot{\Phi}t^2,\\
@@
         &= \sqrt{\frac{2\pi}{i\epsilon}}.
-\end{align*}
+\end{align}
 
@@
 sides of \autoref{eq:nonad_int}, assuming $S\p{-\infty} \ll S\p{+\infty}$ and
-noting $\theta_f \approx \abs{S}(+\infty)$, we obtain
-\begin{equation}
-    \theta_f = \tan I\cos I\sqrt{\frac{2\pi}{\epsilon}}.\label{eq:nonad_dong}
+noting $\theta_{\rm f} \approx \abs{S}(+\infty)$, we obtain
+\begin{equation}
+    \theta_{\rm f} = \tan I\cos I\sqrt{\frac{2\pi}{\epsilon}}.
+        \label{eq:nonad_dong}
 \end{equation}
@@
         and remains roughly unchanged as $\eta \to 0$. This is accommodated by
-        noting $\theta_f \geq \theta_{sd, i}$, so the correct estimate can be
+        noting $\theta_{\rm f} \geq \theta_{\rm sd, i}$, so the correct estimate can be
         roughly amended
         \begin{equation}
-            \theta_f \simeq \min\p{\tan I\cos I\sqrt{\frac{2\pi}{\epsilon}},
-                \theta_{sd, i}}.
+            \theta_{\rm f} \simeq \min\p{\tan I\cos
+                I\sqrt{\frac{2\pi}{\epsilon}}, \theta_{\rm sd, i}}.
         \end{equation}

### 2019-10-24 initial/2_toy2/3_disk_disp.py

@@ -385,7 +385,8 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
         # shade the enclosed phase space area
         ylims = ax.get_ylim()
         # give a small bit of extra space
-        ylims = (max(ylims[0] - 0.05, -1), min(ylims[1] + 0.05, 1))
+        ylims = (max(ylims[0] - 0.1 * abs(ylims[0]), -1),
+                 min(ylims[1] + 0.1 * abs(ylims[1]), 1))
         ax.set_ylim(ylims)
         if abs(phi_uw[-1] - phi_uw[0]) > np.pi:
             # circulating, if phi increasing, shade grey, else red
@@ -1023,7 +1024,7 @@ def plot_manys(I):
 
 if __name__ == '__main__':
     I = np.radians(5)
-    # plot_singles(I)
+    plot_singles(I)
     # plot_manys(I)
 
     # testing high epsilon

### 2019-11-08 initial/notes.tex
I should have known this lol

@@
             - \omega_{1p}\cos(I)\p*{\hat{s} \times \hat{l}_p},\\
-    \omega_{s1} &= \frac{3k_q}{2k} \p*{\frac{R_1}{a_1}}^3 s,\\
-    \omega_{1p} &= \frac{3m_p}{4m_1}\p*{\frac{a_1}{a_p\p*{1 - e_p^2}}} \Omega_1.
-\end{align}
-Note here that $s$ is the spin frequency and $\Omega_1 =
-\sqrt{GM_1/a_1^3}$ is the Keplerian orbital frequency.
+    \omega_{s1} &= \frac{3k_q}{2k}\frac{M_*}{m_1}\p*{\frac{R_1}{a_1}}^3 s,\\
+    \omega_{1p} &= \frac{3m_p}{4m_*}\p*{\frac{a_1}{a_p\sqrt{1 - e_p^2}}}^3 \Omega_1.
+\end{align}
+Note here that $s$ is the spin frequency and $\Omega_1 = \sqrt{GM_1/a_1^3}$ is
+the Keplerian orbital frequency. We may verify that these scalings are correct:
+\begin{itemize}
+    \item $\omega_{1p}$ comes from the perturber being a ring that generates a
+        gravitational field that is out-of-plane from the host star. We estimate
+        the scalings by comparing their relative gravitational strengths. For
+        this, we need that the gravitational potential of a ring inside the ring
+        scales $\Phi'(r) \sim \frac{Gm_p}{a_p}\p*{\frac{r}{a_p}}^2$, and so
+        \begin{equation}
+            \omega_{1p} \sim \frac{\Phi'}{\Phi_0}n
+                \sim \frac{m_p}{m}\p*{\frac{a_1}{a_p}}^3n.
+        \end{equation}
+
+        Recall the idea here is that we can compute some potential $\Phi(r)$ due
+        to the disk $m_d$, which generally takes on form $\Phi(r, \theta) =
+        -\frac{Gm_d}{a_d}\sum\limits_l a_l(\theta) \frac{r}{a_d}^l$ power
+        series, and the $a_l$ are generally Legendre polynomials/spherical
+        harmonics. Then, if we want the energy of an inner ring in this $\Phi$,
+        we get energy $U = \int \Phi(r) m_1(r) \;\mathrm{d}r$, and if $m_1$ only
+        has $l$-multipole moments then $U$ only has to be computed against
+        limited terms of the expansion of $\Phi$. The way we get the expansion
+        of $\Phi$ is just by expanding $\frac{1}{\abs*{\vec{r} - \vec{r}_d}}
+        \sim \frac{1}{\p*{r^2 - rr_d\cos\theta + r_d^2}^{1/2}}$ as a Taylor
+        series for small $\vec{r}_d$.
+
+        I think that the vertical component of the inner ring, out of the plane
+        of the disk, is not as important as the squeezing once we project it
+        into the plane of the disk, but that's conjecture. It is clear that the
+        quadrupole expansion of the disk potential is what drives precession,
+        which gives us our scaling.
+
+    \item $\omega_{s1}$ comes from the action of the central star on the
+        quadrupole moment of the planet. This comes from applying the
+        quadrupolar torque to the spin angular momentum of the planet, or
+        \begin{align}
+            \omega_{s1} &\sim \frac{GM_* J_2 m_1 R_1^2/a^3}{k_p m_1 R_1^2s},\\
+                &\sim \frac{k_{qp}}{k_p}\frac{M_*}{m_1} \p*{\frac{R_1}{a}}^3.
+        \end{align}
+        Note that $J_2 = \frac{k_{qp}s^2}{Gm_1/R_1^3}$, some constant times the
+        spin frequency relative to breakup. This captures the scalings.
+
+        The argument for why this precession frequency scales like
+        $\omega_{s1}\cos \theta$ is also then clear: we have some quadrupolar
+        distortion of the planet, in the potential generated by the host star
+        going around in a circle, so the planet projected into the plane of the
+        ecliptic looks like a triaxial ellipsoid (rather than axisymmetric), and
+        so will have a quadrupole moment and experience a torque that induces
+        precession.
+\end{itemize}
 
@@
 
+\subsection{Physical Parameters}
+
+Note that for Jupiter, $k_p \sim 0.27$ while $J_2 \sim \scinot{1.4}{-2}$ giving
+$k_{qp} \sim 0.0467$ since $k_{qp} \frac{\Omega}{\sqrt{GM_p/R_p^3}} = J_2$.
+Consider again the precession frequencies
+\begin{align}
+    \omega_{s1} &= \frac{3k_{qp}}{2k_p}\p*{\frac{R_1}{a_1}}^3s,\\
+        &\approx 0.011\;\mathrm{yr^{-1}}
+            \p*{\frac{5.5 k_{qp}}{k_p}}\p*{\frac{R_1}{2R_J}}^3
+                \p*{\frac{a_1}{0.05\;\mathrm{AU}}}^{-3}
+                \p*{\frac{s}{2\pi / 10\;\mathrm{hr}}},\\
+    \omega_{1p} &= \frac{3m_p}{4m_1} \frac{a_1}{a_p\p*{1 - e_p^2}} \Omega_1,\\
+        &\approx 0.017\;\mathrm{yr^{-1}}
+            \frac{m_p/m_1}{0.003}
+            \p*{\frac{a_1/a_p}{0.01}}
+            \frac{\Omega_1}{2\pi / 3\;\mathrm{days}}
+            \frac{1}{1 - e_p^2}.
+\end{align}
+So with a bit of tweaking, we can barely get $\omega_{1p} \lesssim \omega_{s1}$.
+Recall that $\eta = \frac{\omega_{1p}\cos I}{\omega_{s1}}$, which here $\sim 1$.
+We simulated above for initial conditions $\frac{s_c}{s} = \eta \sim 0.1$, which
+grows as $s$ spins down. This implies $\frac{s_c}{\Omega_1} \sim 1000$
+though\dots
+
+Let's also evaluate
+\begin{align}
+    \rd{\theta}{t} &\approx -\frac{1}{t_a}\frac{L}{2S}\sin \theta\p*{1 -
+        \frac{s}{2\Omega_1}\cos \theta},\\
+        &\approx 14\;\mathrm{Myr}\p*{\frac{P}{3\;\mathrm{d}}}^{16/3}
+            \p*{\frac{Q_p'}{10^7}}
+            \p*{\frac{M_*}{10^3M_p}}
+            \p*{\frac{a/r}{100}}^2
+            \p*{\frac{s}{2\pi / 10\;\mathrm{h}}}^{-1}
+            \p*{\frac{k_p}{0.25}}^{-1}
+            \sin \theta\p*{1 - \frac{s}{2\Omega_1}\cos \theta}.
+\end{align}
+Note that typically, when trapped in CS2 and $\eta \ll 1$, $\sin \theta \approx
+1$, while when at CS1, $\sin \theta \approx \sin I$. For reference, $\sin
+5^\circ \approx 0.087$.
+
+Again though, we see that if $s > \frac{2\Omega_1}{\cos\theta}$, then
+$\rd{\theta}{t}$ drives towards CS2.
+
 \section{Non-adiabatic Regime}

### 2019-11-12 initial/notes.tex
add a new pop synth for weak tides b/c didn't run old ones long enough

@@
 \begin{align}
-    \omega_{s1} &= \frac{3k_{qp}}{2k_p}\p*{\frac{R_1}{a_1}}^3s,\\
-        &\approx 0.011\;\mathrm{yr^{-1}}
+    \omega_{s1} &= \frac{3k_{qp}}{2k_p}\frac{M_*}{m_1}
+            \p*{\frac{R_1}{a_1}}^3s,\\
+        &\approx 10\;\mathrm{yr^{-1}}
+            \p*{\frac{M_*/m_1}{300}}
             \p*{\frac{5.5 k_{qp}}{k_p}}\p*{\frac{R_1}{2R_J}}^3
@@
     \omega_{1p} &= \frac{3m_p}{4m_1} \frac{a_1}{a_p\p*{1 - e_p^2}} \Omega_1,\\
-        &\approx 0.017\;\mathrm{yr^{-1}}
+        &\approx 0.0625\;\mathrm{yr^{-1}}
             \frac{m_p/m_1}{0.003}
-            \p*{\frac{a_1/a_p}{0.01}}
-            \frac{\Omega_1}{2\pi / 3\;\mathrm{days}}
+            \p*{\frac{a_1/a_p}{0.05}}
+            \frac{\Omega_1}{2\pi / 4\;\mathrm{days}}
             \frac{1}{1 - e_p^2}.
 \end{align}
-So with a bit of tweaking, we can barely get $\omega_{1p} \lesssim \omega_{s1}$.
-Recall that $\eta = \frac{\omega_{1p}\cos I}{\omega_{s1}}$, which here $\sim 1$.
-We simulated above for initial conditions $\frac{s_c}{s} = \eta \sim 0.1$, which
-grows as $s$ spins down. This implies $\frac{s_c}{\Omega_1} \sim 1000$
-though\dots
+Let's note that the effective initial $\eta = \frac{\omega_{1p}\cos
+I}{\omega_{s1}} \sim 0.006$. Furthermore, the smallest $\eta$ we can get at
+small final obliquities is just when $s = \Omega_1$, which is roughly a factor
+of $10$ increase so $\eta_f \sim 0.06$. Recall that $\eta = \frac{s_c}{s}
+\approx \frac{s_c}{\Omega_1}0.1$ since $\Omega_1/s \approx 0.1$, then $s_c
+\approx 0.06$ as well.
 

### 2019-11-12 initial/1_weaktide/4sim_v2.py

@@ -353,6 +353,29 @@ def statistics(trajs, I, eps, s_c, s0=10, tf=2500):
     plt.savefig('4_stats%s.png' % s_c_str(s_c), dpi=400)
     plt.close(fig)
 
+def plot_final_dists(trajs, I, eps, s_c, s0=10, tf=2500):
+    fig, ((ax1, ax2), (ax3, ax4)) = plt.subplots(2, 2)
+    titles = ['No hop, CS1', 'No hop, CS2', 'Cross to CS1', 'Hop to CS2']
+    for ax, outcome_trajs, title in\
+            zip([ax1, ax2, ax3, ax4], trajs, titles):
+        ax.set_title(title)
+        ax.set_xlabel(r'$s_f$')
+        ax.set_ylabel(r'$\cos \theta_f$')
+        if not outcome_trajs:
+            continue
+        s_f = []
+        mu_f = []
+        for _, _, _, mu_pi, s_pi, _, _, _, _ in outcome_trajs:
+            s_f.append(s_pi[-1])
+            mu_f.append(mu_pi[-1])
+        ax.scatter(s_f, mu_f, s=0.5**2, c='k')
+    plt.suptitle(r'$I = %d^\circ, s_c = %.2f, T_f = %d$' %
+                 (np.degrees(I), s_c, tf))
+    plt.tight_layout()
+    plt.subplots_adjust(top=0.85)
+    plt.savefig('4outcomes%s.png' % s_c_str(s_c), dpi=400)
+    plt.clf()
+
 def cross_times(trajs, I, eps, s_c, s0=10, tf=2500):
     '''
     plot t_cross and s_cross(H_4 - H_0) (H4 > H0 for all these, H4 evaluated at
@@ -566,5 +589,6 @@ if __name__ == '__main__':
 
     for s_c in s_c_vals:
         trajs = run_sim(I, eps, s_c, num_threads=4)
-        statistics(trajs, I, eps, s_c)
-        cross_times(trajs, I, eps, s_c)
+        # statistics(trajs, I, eps, s_c)
+        # cross_times(trajs, I, eps, s_c)
+        plot_final_dists(trajs, I, eps, s_c)

### 2019-11-12 initial/1_weaktide/5pop.py

@@ -1,0 +1,219 @@
+'''
+plot distributions of s, q_f for the three populations Z1/Z2/Z3-cross/Z3-hop
+'''
+import os
+import numpy as np
+from multiprocessing import Pool
+import scipy.optimize as opt
+from scipy import integrate
+
+import pickle
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif', size=14)
+
+from utils import solve_ic, to_ang, to_cart, get_etac, get_mu4, get_mu2,\
+    stringify, H, roots, get_H4
+PKL_FILE = '5dat%s.pkl'
+N_PTS = 1000
+TF = 8000
+TIMES = np.exp(np.linspace(0, np.log(TF), 100))
+
+def s_c_str(s_c):
+    return ('%.2f' % s_c).replace('.', '_')
+
+def solve_with_events(I, s_c, eps, mu0, phi0, s0):
+    '''
+    solves IVP then returns (mu, s, t) at phi=0, pi + others
+    '''
+    init_xy = np.sqrt(1 - mu0**2)
+    init = [-init_xy * np.cos(phi0), -init_xy * np.sin(phi0), mu0, s0]
+
+    event = lambda t, y: y[1]
+    t, _, _, ret = solve_ic(I, s_c, eps, init, TF,
+                            rtol=1e-4,
+                            events=[event], dense_output=True)
+    sol_times = ret.sol(TIMES)
+    q, phi = to_ang(*sol_times[0:3])
+    s = sol_times[3]
+
+    [t_events] = ret.t_events
+    x_events, _, mu_events, s_events = ret.sol(t_events)
+    # phi = 0 means x < 0
+    idxs_0 = np.where(x_events < 0)
+    idxs_pi = np.where(x_events > 0)
+    mu_0, s_0, t_0 = mu_events[idxs_0], s_events[idxs_0], t_events[idxs_0]
+    mu_pi, s_pi, t_pi = mu_events[idxs_pi], s_events[idxs_pi], t_events[idxs_pi]
+
+    shat_f = np.sqrt(np.sum(ret.y[ :3, -1]**2))
+    return (mu_0, s_0, t_0, mu_pi, s_pi, t_pi), np.cos(q), phi, s
+
+def get_sep_hop(t_0, s_0, mu_0, t_pi, s_pi, mu_pi):
+    '''
[…]

### 2019-11-26 writeups/Su_disk_disp.tex
small notes changes

@@
 Obliquities Generated by Planet-Disk Interactions}
-\author[Y. Su et\ al.]{
+\author[Y. Su and D. Lai]{
 Yubo Su$^1$,
@@
 Substantial planetary obliquities, defined as the angle between a planet's spin
-and orbital axes, have featured in many astrophysical scenarios. They lie at the
-heart of the obliquity tides scenario of radius enhancement in hot Jupiters
+and orbital axes, have been proposed in many exoplanetary systems. They lie at
+the heart of the obliquity tides mechanism of radius enhancement in hot Jupiters
 \citep{winn_otides, fabrycky_otides, millholland_wasp12b}. They have also been
@@
 to our analysis of the evolution of this system. They are not essential to
-reproducing the results presented in \autoref{ss:ad_ensemble}.
+reproducing the results of \autoref{s:ad} and \autoref{s:nonad}.
 
@@
 space. Together, these two critical trajectories are referred to as the
-\emph{separatrix} and divide phase space into three zones. The separatrix, three
-zones, and their relations to the CSs are shown via a contour plot of the
-Hamiltonian of the system
+\emph{separatrix} and divide phase space into three zones. In
+\autoref{fig:eq_1contours}, we show the separatrix, the three zones, and their
+relations to the CSs via a contour plot of the Hamiltonian of the system
 \begin{equation}
@@
 \end{equation}
-Such a contour plot is given in \autoref{fig:eq_1contours}. Note that
-trajectories in zone $II$ librate about CS2 while those in zones $I$/$III$
-circulate.
+Note that trajectories in zone $II$ librate about CS2 while those in zones
+$I$/$III$ circulate.
 \begin{figure*}
@@
     \autoref{eq:H}, where warmer colors denote more positive values. The black
-    solid line is the separatrix, which only exists for $\eta < \eta_{\rm c}$. The
-    three zones, divided by the separatrix, are labeled. The Cassini states are
-    labeled and have the same colors as \autoref{fig:cs_locs}. The interior of
-    the separatrix, shaded in grey, is formally only defined for $\eta <
-    \eta_{\rm c}$, but we may identify the phase space trajectories that flow into
+    solid line is the separatrix, which only exists for $\eta < \eta_{\rm c}$.
+    The three zones, divided by the separatrix, are labeled. The Cassini states
+    are labeled and have the same colors as \autoref{fig:cs_locs}. The interior
+    of the separatrix, shaded in grey, is formally only defined for $\eta <
+    \eta_{\rm c}$, but we may identify the points in phase space that flow into
     zone $II$ when evolved forward in time; this is the shaded region in the top
@@
 \citep{henrard1987,ward2004I}. Defining
-\begin{subequations}\label{se:area_ward}
+\begin{subequations}
     \begin{align}
@@
     \end{align}
+\end{subequations}
 the areas for $\eta < \eta_{\rm c}$ are given by
+\begin{subequations}\label{se:area_ward}
     \begin{align}
@@
 the zones are not formally defined for $\eta > \eta_{\rm c}$, but a natural
-extension exists: evolve an initial point $p$ under adiabatic decrease of $\eta
-> \eta_{\rm c}$ until the separatrix appears at $\eta = \eta_{\rm c}$, then
-identify $p$ with the zone it is in at $\eta_{\rm c}$. Since phase space area is
-conserved under adiabatic evolution, this implies $A_i\p{\eta > \eta_{\rm c}} =
-A_i(\eta_{\rm c})$. This extension is also reflected in the dashed boundary in
-\autoref{fig:eq_1contours}.
+extension exists: evolve an initial point $p$ under adiabatic decrease of $\eta$
+until the separatrix appears at $\eta = \eta_{\rm c}$, then identify $p$ with
+the zone it is in at $\eta_{\rm c}$. Since phase space area is conserved under
+adiabatic evolution, this implies $A_i\p{\eta > \eta_{\rm c}} = A_i(\eta_{\rm
+c})$. The boundary between these extended zones is denoted by the dashed black
+line in the top left panel of \autoref{fig:eq_1contours}, where otherwise no
+separatrix should exist since $\eta > \eta_{\rm c}$.
 \begin{figure}
@@
 
-A perturbation to a Hamiltonian system is considered \emph{adiabatic} if it is
-sufficiently slow compared to all other relevant time scales in the problem.
-In the current problem, the slowest time scale is the \emph{separatrix crossing
-time scale}: as $\eta$ evolves, a trajectory may encounter the separatrix at
-some value $\eta_\star$ which varies depending on its initial condition. If
-$\eta$ changes sufficiently little during the separatrix-crossing orbit, the
-evolution of the system may be considered adiabatic. The truly adiabatic limit
-corresponds to $\epsilon \to 0$; we take $\epsilon = 3 \times 10^{-4}$ unless
-otherwise noted.
-
-One criterion for adiabaticity is that the separatrix crossing timescale be
-longer than the the resonant libration period \citep{ward2004II}. The resonant
-libration period for a nearly separatrix-crossing orbit is approximated by
-the libration period near CS2 in \citet{millholland_disk}. We find that this
-criterion performs remarkably well despire the expectation that the separatrix
-crossing orbit should be much longer than libration near CS2 (approaching
-infinity as $\epsilon \to 0$). One justification for this is that the libration
-period about CS2 is the longest timescale in the system (see
-\autoref{fig:lambda2})
-
-This constraint can be computed
-\begin{align}
-    -\at{\frac{1}{\eta}\rd{\eta}{\tau}}_{\rm cross} = \epsilon &\lesssim
+If a Hamiltonian system is parameterized by some parameter that is varied, its
+evolution is considered \emph{adiabatic} if the parameter's variation is slow
+compared to the Hamiltonian dynamics. In the current problem, the period of the
+longest orbit of the constant-$\eta$ Hamiltonian system is infinite, namely
+along the separatrix. This is an essential feature of the problem, as otherwise
+trajectories would never be able to experience separatrix crossings. But this
+seemingly implies adiabaticity is impossible to define.
+
+Instead of requiring the variation of $\eta$ be slower than all timescales in
+the Hamiltonian dynamics, we seek a weaker but nevertheless effective criterion.
+In practice, trajectories only cross the separatrix once, while they spend many
+orbits inside one of the three zones and far from the separatrix as $\eta$
+evolves. Thus, a \emph{weak adiabaticity criterion} is that the variation of
+$\eta$ be slower than all circulation/libration timescales in the Hamiltonian
+system. If this criterion is satisfied, then a given trajectory will be
+adiabatic for almost all of its evolution save one or two separatrix-crossing
+orbits.
+
+As is shown in \autoref{ss:eigens}, the libration frequency about CS2 is slower
+than that about CS1 or CS3. As such, it is the slowest characteristic frequency
+in the system. The weak adiabaticity criterion can be recast as requiring that
+$\eta$ vary more slowly than this libration period; this is exactly the
+criterion used in \citep{ward2004II,millholland_disk}. This constraint can be
+computed
+\begin{align}
+    -\at{\frac{1}{\eta}\rd{\eta}{\tau}} = \epsilon &\lesssim
             \frac{1}{T_{\rm lib}},\\
-        &\lesssim \frac{1}{2\pi}\sqrt{\eta_\star\sin I \sin \theta_2
-            \p{1 + \eta_\star \sin I \csc^3 \theta_2}},
+        &\lesssim \frac{1}{2\pi}\sqrt{\eta\sin I \sin \theta_2
+            \p{1 + \eta \sin I \csc^3 \theta_2}},
             \label{eq:ad_constr}
 \end{align}
-where $\theta_2$ is the obliquity at CS2. This formula differs from that
-presented in \citet{millholland_disk}, where the $\csc^3\theta_2$ term is
+where $\theta_2$ is the obliquity at CS2. This formula differs somewhat from
+that presented in \citet{millholland_disk}, where the $\csc^3\theta_2$ term is
 neglected and a square root is missing.
+
+For $I = 5^\circ$, $\eta \sim \eta_c$ we compute $\epsilon \lesssim 0.085$ is
+the requirement for weak adiabaticity. Since our criterion is only a weak
+constraint on adiabaticity, we use $\epsilon = 3 \times 10^{-4}$ in our
+``adiabatic'' simulations. We explore the consequences of increasingly
+nonadiabatic evolution in \autoref{ss:transition}.
 
@@
 
-\subsection{Transition to Non-adiabaticity}
+\subsection{Transition to Non-adiabaticity}\label{ss:transition}
 
@@
 crossing process becoming sensitive to the \emph{phase} of the final
-libration/circulation orbit at separatrix crossing. This is equivalent to
-separatrix crossing no longer being significantly slower than the resonant
-libration period and violating the adiabatic assumption.
+libration/circulation orbit at separatrix crossing, which implies that $\eta$
+changes substantially over the separatrix crossing orbit. This is clearly a
+non-adiabatic effect but is permitted by the weak adiabaticity criterion,
+which only compares $\eta$ evolution to dynamics far from the separatrix.
 \begin{figure}
@@
 A sample trajectory following in the style of \autoref{fig:ad_21} but for
-$\epsilon = 0.3$ is provided in \autoref{fig:nonad_traj}. It is clear the
-trajectory does not track level curves of the Hamiltonian during each individual
-snapshot (e.g.\ the third snapshot).
+$\epsilon = 0.3$ (violating even weak adiabaticity) is provided in
+\autoref{fig:nonad_traj}. It is clear the trajectory does not track level curves
+of the Hamiltonian during each individual snapshot (e.g.\ the third snapshot).
+This manifests when CS2 migrates more quickly than the trajectory can librate
+about CS2, precisely a violation of the weak adiabaticity criterion.
 \begin{figure}
@@
 
-A formula for $\theta_{\rm f}$ assuming $\theta_{\rm sd, i} = 0$ initially can
-be given (see \autoref{s:ad_approx})
+We now consider the general problem of how a state evolves when $\eta$ changes
+non-adiabatically. In \autoref{s:ad_approx}, we derive a formula for
+$\theta_{\rm f}$ assuming no initial spin-disk misalignment:
 \begin{equation}
@@
 \end{equation}
-We can naively generalize this by recognizing that any nonzero $\theta_{\rm sd,
-i}$ manifests as obliquity variations as $\hat{s}$ librates about $\hat{l}_{\rm
-d}$. These can be accounted for by simply allowing the final obliquity to vary
-over the same range as the initial obliquity, or,
+
+An intuitive guess at generalizing this assumes that any nonzero $\theta_{\rm
+sd, i}$ manifests as obliquity variations as $\hat{s}$ librates about
+$\hat{l}_{\rm d}$. These can be accounted for by simply allowing the final
+obliquity to vary over the same range as the initial obliquity, or,
 \begin{equation}
@@
 \end{equation}
-
-We present the results of simulations for using $\epsilon = 0.3$ in
-\autoref{fig:nonad_3_ensemeble}.
+In \autoref{fig:nonad_3_ensemeble}, we show that this proves a remarkably
+accurate when taking $\epsilon = 0.3$.
 \begin{figure}
@@
 \autoref{eq:qf_23_approx}. Therefore, if $\theta_{\rm sd, i}$ is generally
-small, as would be expected for peacefully forming planets, resonance capture
-induced by an adiabatically dissipating protoplanetary disk is expected to
-significantly narrow the final $\theta$ spread compared to the initial
-$\theta_{\rm sd, i}$ spread.
+small, as might be expected for planets that do not experience strong collisions
+or scattering, resonance capture induced by an adiabatically dissipating
+protoplanetary disk is expected to significantly narrow the final $\theta$
+spread compared to the initial $\theta_{\rm sd, i}$ spread.
 
@@
 
-\subsection{Stability}
+\subsection{Stability and Frequency of Local Oscillations}\label{ss:eigens}
 
@@
 CS2, since $\theta_{\rm cs} \approx I$ in this regime as was shown above.
-
-\subsection{Consequences for Adiabaticity}\label{ss:careful_ad}
-
-In \autoref{s:ad}, we said the adiabaticity criterion is given by comparison of
-the separatrix crossing timescale to the resonant libration period
-\citep{ward2004II}, and we corrected the formula presented by
-\citet{millholland_disk}. Two further comments can be made:
-\begin{enumerate}
-    \item The adiabaticity criterion compares how quickly the
-        separatrix-crossing orbit is completed to how quickly the separatrix
-        location shifts. However, it's not obvious that the libration period
-        about CS2 captures the duration of the separatrix-crossing orbit, which
-        as $\epsilon \to 0$ formally diverges. Thus, this criterion can only be
-        taken as a necessary but not sufficient criterion to guarantee accurate
-        predictions of $A$ post-encounter.
-
-        We speculate a formally sufficient criterion may be able to be
-        formulated as $\Delta t \lesssim \frac{\Delta \eta}{\dot{\eta}}$, where
-        $\Delta t$ is the length of the separatrix-crossing orbit, and $\Delta
-        \eta$ is the change in $\eta$ over the separatrix-crossing orbit. Note
-        for all $\epsilon > 0$ that $\Delta t < \infty$. The exact form of such
-        a criterion is inessential to our result.
-
-    \item A different adiabaticity criterion can be defined for
-        $III$-originating trajectories, as the separatrix-crossing orbit is much
-        shorter (see e.g.\ \autoref{fig:ad_31}). However, the resultant
-        criterion becomes extremely strict for the $III \to I$ track, as it goes
-        through very small $\theta$. That this track is least adiabatic track
-        can be seen by comparing \autoref{fig:ad_ensemble} and
-        \autoref{fig:3_ensemble_05_25}, where the $III \to I$ track develops the
-        largest spread about the analytical prediction.
-\end{enumerate}
 

### 2020-01-16 writeups/Su_disk_disp.tex
stash, finished all S2

@@
 \pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\renewcommand*{\sectionautorefname}{Section}
-% \renewcommand*{\subsectionautorefname}{Subsection}
 \maketitle
@@
 
-The paper is organized as follows. In \autoref{s:eq}, we review relevant
+The paper is organized as follows. In Section~\ref{s:eq}, we review relevant
 spin-orbit dynamics and present the equations studied in the rest of the paper.
-In \autoref{s:ad} and \autoref{s:nonad}, we study the evolution of the system
+In Sections~\ref{s:ad} and~\ref{s:nonad}, we study the evolution of the system
 when the disk either dissipates adiabatically or non-adiabatically respectively.
@@
 numerical results in both limits. We discuss potential consequences in
-\autoref{s:disc}. Our primary physical results consist of
-\autoref{fig:ad_ensemble} in the adiabatic limit and
-\autoref{fig:3_ensemble_05_15} in the non-adiabatic limit. Longer mathematical
+Section~\ref{s:disc}. Our primary physical results consist of
+Fig.~\ref{fig:ad_ensemble} in the adiabatic limit and
+Fig.~\ref{fig:3_ensemble_05_15} in the non-adiabatic limit. Longer mathematical
 calculations are relegated to the appendicies, including a leading-order
 estimate of final planetary obliquities given small initial spin-disk
-misalignment angles in \autoref{s:ad_approx}.
+misalignment angles in Appendix~\ref{s:ad_approx}.
 
@@
 Much of this treatment parallels that of \citet{anderson2018teeter} and
-\citet{millholland_disk}. We consider an oblate star of mass $M_\star$ hosting a
+\citet{millholland_disk}. We consider a star of mass $M_\star$ hosting an oblate
 planet of mass $M_{\rm p}$, radius $R_{\rm p}$, at semimajor axis $a_{\rm p}$,
@@
 \bm{L}_{\rm d} / L_{\rm d}$ angular momentum of the surrounding disc. We
-approximate $S \ll L \ll L_{\rm d}$, so $\hat{l}_{\rm d}$ is approximately
-constant and $\hat{l}$ experiences negligible backreaction torque from
-$\hat{s}$. The quadrupole-order secular equations of motion for $\hat{s}$,
-$\hat{l}$ and $\hat{l}_{\rm d}$ then become very simple
+assume $S \ll L \ll L_{\rm d}$, so $\vec{l}_{\rm d}$ is approximately
+constant and $\vec{l}$ experiences negligible backreaction torque from
+$\hat{s}$. The equations of motion for $\hat{s}$, $\hat{l}$ and $\hat{l}_{\rm
+d}$ are
 \begin{align}
     \rd{\hat{s}}{t} &= \omega_{\rm sl} \p{\hat{s} \cdot \hat{l}}
+            \p{\hat{s} \times \hat{l}}
+        \equiv \alpha \p{\hat{s} \cdot \hat{l}}
             \p{\hat{s} \times \hat{l}},\label{eq:dsdt}\\
     \rd{\hat{l}}{t} &= \omega_{\rm ld}\p{\hat{l} \cdot \hat{l}_{\rm d}}
-        \p{\hat{l} \times \hat{l}_{\rm d}}\label{eq:dldt}.
+            \p{\hat{l} \times \hat{l}_{\rm d}}
+        \equiv -g\p{\hat{l} \times \hat{l}_{\rm d}},
+            \label{eq:dldt}
 \end{align}
@@
 \begin{align}
-    \omega_{\rm sl} &\equiv \frac{3k_{\rm qp}}{2k_{\rm p}} \frac{M_\star}{m_{\rm
+    \omega_{\rm sl} &= \frac{3k_{\rm qp}}{2k_{\rm p}} \frac{M_\star}{m_{\rm
         p}} \p{\frac{R_{\rm p}}{a_{\rm p}}}^3 \Omega_{\rm p},\label{eq:wsl}\\
-    \omega_{\rm ld} &\equiv \frac{3M_{\rm d}}{4M_\star}\p{\frac{a_{\rm
+    \omega_{\rm ld} &= \frac{3M_{\rm d}}{4M_\star}\p{\frac{a_{\rm
         p}}{r_{\rm d}}}^3 n .\label{eq:wld}
@@
 % = 1 / (573362 yr) (Md/Mstar = 0.01, ap/rd = 1/30)
-In \autoref{eq:wsl}, $k_{\rm qp}$ and $k_{\rm }$ are related to the planet's
-quadrupole moment and moment of inertia respectively \citep[see][]{lai2018}, and
-$n \equiv \sqrt{GM_\star/a_{\rm p}^3}$ is the planet's orbital mean motion. The
-three angles formed by the three vectors are denoted
+In Eq.~\eqref{eq:wsl}, $k_{\rm qp}$ and $k_{\rm p}$ are related to the planet's
+rotation-induced quadrupole moment and moment of inertia respectively
+\citep[see][]{lai2018}, and $n \equiv \sqrt{GM_\star/a_{\rm p}^3}$ is the
+planet's orbital mean motion. The three angles formed by the three vectors are
+denoted
 \begin{align}
@@
 \end{align}
-
-Let us transform to frame rotating about $\hat{l}_{\rm p}$ with frequency $g
-\equiv -\omega_{\rm ld}\cos I < 0$, then $\hat{l}$ is fixed. In this frame,
-$\hat{l}_{\rm p}$ also remains fixed and $\hat{s}$ evolves as:
-\begin{equation}
-    \rd{\hat{s}}{t} = \alpha \p{\hat{s} \cdot \hat{l}}
+Following standard notation \citep[e.g.][]{colombo1966,peale1969,ward_jupiter},
+we have defined $\alpha \equiv \omega_{\rm sl}$ and $g = -\omega_{\rm ld}\cos
+I$.
+
+We can combine Eqs.~\eqref{eq:dsdt}--\eqref{eq:dldt} into a single equation by
+transforming into a frame rotating about $\hat{l}_{\rm d}$ with frequency $g$.
+In this frame, $\hat{l}_{\rm d}$ and $\hat{l}$ are fixed, and $\hat{s}$ evolves
+as:
+\begin{equation}
+    \at{\rd{\hat{s}}{t}}_{\rm rot} = \alpha \p{\hat{s} \cdot \hat{l}}
             \p{\hat{s} \times \hat{l}}
-        + g\p{\hat{s} \times \hat{l}_{\rm d}},
-\end{equation}
-where $\alpha \equiv \omega_{\rm sl} > 0$ follows standard notation. By defining
-$\eta$ and nondimensionalized time $\tau$ as
-\begin{align}
-    \eta \equiv{}& \frac{\abs{g}}{\alpha}\label{eq:eta},\\
+        + g\p{\hat{s} \times \hat{l}_{\rm d}}.\label{eq:dsdt_rot}
+\end{equation}
+
+We define the frequency ratio $\eta$ and dimensionless time $\tau$ as
+\begin{align}
+    \eta \equiv{}& -\frac{g}{\alpha}\label{eq:eta},\\
         ={}& 3.75 \p{\frac{k_{\rm p}}{6k_{\rm qp}}}
@@
             \cos I,\\
-    \tau \equiv{}& \alpha t,
-\end{align}
-we can non-dimensionalize the equation of motion as
-\begin{equation}
-    \rd{\hat{s}}{\tau} = \p{\hat{s} \cdot \hat{l}}
+    \tau \equiv{}& \alpha t.
+\end{align}
+Then Eq.~\eqref{eq:dsdt_rot} becomes
+\begin{equation}
+    \at{\rd{\hat{s}}{t}}_{\rm rot} = \p{\hat{s} \cdot \hat{l}}
             \p{\hat{s} \times \hat{l}}
@@
 
-Following~\cite{millholland_disk}, we allow $g$ to vary in time owing to a
-disk with decaying mass
-\begin{equation}
-    M_{\rm d}(t) = M_{\rm d}(0)e^{-t/t_{\rm d}}.
-\end{equation}
-As $\alpha$ is held constant, this equates to $\eta$ decaying as $\rd{\eta}{t} =
--\frac{\eta}{t_{\rm d}}$ as well. We nondimensionalize:
+Throughout this paper, we consider $\alpha$ constant, but allow $g$ to vary in
+time. In the dispersing disk scenario of \citet{millholland_disk}, $\abs{g}$
+decreases in time due to the decreasing disk mass. We consider a simple
+exponential decay model
+\begin{equation}
+    M_{\rm d}(t) = M_{\rm d}(0)e^{-t/t_{\rm d}},
+\end{equation}
+with $t_d$ constant.
+
+Tihs implies $\rd{\eta}{t} = -\frac{\eta}{t_{\rm d}}$. In dimenisonless units,
+we have
+\begin{equation}
+    \rd{\eta}{\tau} = -\epsilon \eta\label{eq:deta_dt},
+\end{equation}
+where
 \begin{align}
@@
             \p{\frac{\Omega_{\rm p}}{2\pi/\p{10\;\mathrm{days}}}}
-            \p{\frac{t_{\rm d}}{10\;\mathrm{Myr}}}^{-1},\\
-    \rd{\eta}{\tau} ={}& -\epsilon \eta.\label{eq:deta_dt}
-\end{align}
-\autoref{eq:dsdt_base} and \autoref{eq:deta_dt} together constitute our system
+            \p{\frac{t_{\rm d}}{10\;\mathrm{Myr}}}^{-1}.
+\end{align}
+Eqs.~\eqref{eq:dsdt_base} and~\eqref{eq:deta_dt} together constitute our system
 of study.
 
-In the next two subsections, we further discuss theoretical background relevant
-to our analysis of the evolution of this system. They are not essential to
-reproducing the results of \autoref{s:ad} and \autoref{s:nonad}.
+In the next two subsections, we discuss and review the theoretical background
+relevant to our analysis of the evolution of the system.
 
@@
 
-Spin states satisfying $\rd{\hat{s}}{t} = 0$ are referred to as \emph{Cassini
-States} (CSs). There are either two or four solutions, depending on the values
-of $\eta, I$. Following standard convention and nomenclature (see
-\autoref{fig:cs_locs}), CSs 1, 3, 4 have $\phi = 0, \theta < 0$ and CS2 has
-$\phi = \pi, \theta > 0$. Of these, CSs 1, 2, 3 are stable while CS4 is unstable
-(see \autoref{s:local_dynamics}). When $\eta < \eta_{\rm c}$, where
+Spin states satisfying $\at{\rd{\hat{s}}{t}}_{\rm rot} = 0$ are referred to as
+\emph{Cassini States} (CSs). They require that $\hat{s}$, $\hat{l}$, and
+$\hat{l}_{\rm d}$ be coplanar. There are either two or four solutions, depending
+on the values of $\eta, I$. They are specified by the obliquity $\theta$ and the
+precessional phase of $\hat{s}$ around $\hat{l}$, denoted $\phi$. Following
+standard convention and nomenclature (see Fig.~\ref{fig:cs_locs}), CSs 1, 3, 4
+have $\phi = 0$ and $\theta < 0$, corresponding to $\hat{s}$ and $\hat{l}_{\rm
+d}$ being on opposite sides of $\hat{l}$, while CS2 has $\phi = \pi$ and $\theta
+> 0$, corresponding to $\hat{s}$ and $\hat{l}_{\rm d}$ being on the same side of
+$\hat{l}$. When $\eta < \eta_{\rm c}$, where
 \begin{equation}
@@
 \end{equation}
-all four CSs exist, and when $\eta > \eta_{\rm c}$, only CSs 2, 3 exist
-\citep{henrard1987,ward2004I}. The CS obliquities as a function of $\eta$ are
-shown in \autoref{fig:cs_locs}.
+all four CSs exist, and when $\eta > \eta_{\rm c}$, only CSs 2, 3 exist. The CS
+obliquities as a function of $\eta$ are shown in Fig.~\ref{fig:cs_locs}.
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{../initial/99_misc/2_cs_locs.png}
-    \caption{Cassini state obliquities as a function of $\eta$. Note that
-    $\theta \in [-\pi, \pi]$ is the traditional definition of the polar angle
-    \citep[see e.g.][]{colombo1966,peale1969,henrard1987}. The vertical dashed
-    line indicates $\eta_{\rm c}$, where CS1 and CS4 merge and annihilate, and the
-    horizontal dashed lines indicate $\theta = I, 180^\circ - I$ the asymptotic
-    behavior for CS2, 3 for $\eta \gg \eta_{\rm c}$.}\label{fig:cs_locs}
-\end{figure}
+    \caption{Cassini state obliquities as a function of $\eta$ at $I = 5^\circ$.
+    Note that $\theta \in [-\pi, \pi]$ is the traditional definition of the
+    polar angle. The vertical dashed line indicates $\eta_{\rm c}$, where CS1
+    and CS4 merge and annihilate, and the horizontal dashed lines indicate
+    $\theta = I$ and $180^\circ - I$, the asymptotic behavior for CSs 2 and 3
+    for $\eta \gg \eta_{\rm c}$.}\label{fig:cs_locs}
+\end{figure}
+
+Of the four CSs, 1, 2, 3 are stable while 4 is unstable.
+Appendix~\ref{s:local_dynamics} gives the libration frequencies and growth rates
+respectively near these CSs.
 
@@
 
-When $\eta < \eta_{\rm c}$, CS4 exists and is a saddle point. The two trajectories
-originating and ending at CS4 are the only two infinite-period orbits in phase
-space. Together, these two critical trajectories are referred to as the
-\emph{separatrix} and divide phase space into three zones. In
-\autoref{fig:eq_1contours}, we show the separatrix, the three zones, and their
+When $\eta < \eta_{\rm c}$, CS4 exists and is a saddle point. The two
+trajectories originating and ending at CS4 are the only two infinite-period
+orbits in the phase space. Together, these two critical trajectories are
+referred to as the \emph{separatrix} and divide phase space into three zones. In
+Eq.~\eqref{fig:eq_1contours}, we show the separatrix, the three zones, and their
 relations to the CSs via a contour plot of the Hamiltonian of the system
-\begin{equation}
-    \mathcal{H} = -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
-            + \eta \p{\hat{s} \cdot \hat{l}_{\rm d}}.\label{eq:H}
-\end{equation}
+\begin{align}
+    \mathcal{H} &= -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
+            + \eta \p{\hat{s} \cdot \hat{l}_{\rm d}},\label{eq:H}\\
+        &= -\frac{1}{2}\cos^2\theta
+            + \eta \p*{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
+\end{align}
 Note that trajectories in zone $II$ librate about CS2 while those in zones
-$I$/$III$ circulate.
+$I$ and $III$ circulate.
 \begin{figure*}
@@
     \caption{Contour plot of $\mathcal{H}\p{\phi, \cos \theta}$ as given in
-    \autoref{eq:H}, where warmer colors denote more positive values. The black
+    Eq.~\eqref{eq:H}, where warmer colors denote more positive values. The black
     solid line is the separatrix, which only exists for $\eta < \eta_{\rm c}$.
     The three zones, divided by the separatrix, are labeled. The Cassini states
-    are labeled and have the same colors as \autoref{fig:cs_locs}. The interior
-    of the separatrix, shaded in grey, is formally only defined for $\eta <
-    \eta_{\rm c}$, but we may identify the points in phase space that flow into
-    zone $II$ when evolved forward in time; this is the shaded region in the top
-    left plot, bounded by the dotted black line.}\label{fig:eq_1contours}
+    are labeled and have the same colors as in Fig.~\ref{fig:cs_locs}. The
+    interior of the separatrix, shaded in grey, is formally only defined for
+    $\eta < \eta_{\rm c}$, but we may identify the points in phase space that
+    flow into zone $II$ when evolved forward in time (decreasing $\eta$
+    adiabatically); this is the shaded region in the top left panel, bounded by
+    the black dotted line.}\label{fig:eq_1contours}
 \end{figure*}
 
-The unsigned areas of the three zones are known exactly
-\citep{henrard1987,ward2004I}. Defining
+The unsigned areas $\p{\abs{\int \cos \theta \;\mathrm{d}\phi}}$ of the three
+zones can be computed analytically \citep{henrard1987,ward2004I}. Defining
 \begin{subequations}
@@
 \end{subequations}
-These are plotted as a function of $\eta$ in \autoref{fig:eq_areas}. Note that
-the zones are not formally defined for $\eta > \eta_{\rm c}$, but a natural
-extension exists: evolve an initial point $p$ under adiabatic decrease of $\eta$
-until the separatrix appears at $\eta = \eta_{\rm c}$, then identify $p$ with
-the zone it is in at $\eta_{\rm c}$. Since phase space area is conserved under
-adiabatic evolution, this implies $A_i\p{\eta > \eta_{\rm c}} = A_i(\eta_{\rm
-c})$. The boundary between these extended zones is denoted by the dashed black
-line in the top left panel of \autoref{fig:eq_1contours}, where otherwise no
-separatrix should exist since $\eta > \eta_{\rm c}$.
+These are plotted as a function of $\eta$ in Fig.~\ref{fig:eq_areas}. Note that
+the zones are not formally defined for $\eta > \eta_{\rm c}$ since the
+separatrix disappears, but a natural extension exists: evolve an initial phase
+space point $p$ under adiabatic decrease of $\eta$ until the separatrix appears
+at $\eta = \eta_{\rm c}$, then identify $p$ with the zone it is in at $\eta_{\rm
+c}$. Since phase space area is conserved under adiabatic evolution, this implies
+$A_i\p{\eta > \eta_{\rm c}} = A_i(\eta_{\rm c})$. The boundary between these
+extended zones is denoted by the dashed black line in the top left panel of
+Fig.~\ref{fig:eq_1contours}, where otherwise no separatrix exists.
 \begin{figure}
@@
     \caption{Plot of fractional areas of each of the zones $A_{\rm i}(\eta) /
-    4\pi$ as given by \autoref{se:area_ward}. Dotted lines correspond to small
-    $\eta$ approximations discussed in \autoref{s:ad_approx}. Dashed lines for
-    $\eta > \eta_{\rm c}$ effective values of $A_{\rm II}, A_{\rm III}$ for
-    $\eta > \eta_{\rm c}$, denoting the area of points that would flow into
-    either area under adiabatic decrease of $\eta$ from $\eta > \eta_{\rm
+    4\pi$ as given by Eqs.~\eqref{se:area_ward}. Dotted lines correspond to
+    small $\eta$ approximations discussed in Appendix~\ref{s:ad_approx}. Dashed
+    lines for $\eta > \eta_{\rm c}$ effective values of $A_{\rm II}, A_{\rm
+    III}$ for $\eta > \eta_{\rm c}$, denoting the area of points that would flow
+    into either area under adiabatic decrease of $\eta$ from $\eta > \eta_{\rm
     c}$.}\label{fig:eq_areas}
@@
 
-As is shown in \autoref{ss:eigens}, the libration frequency about CS2 is slower
+As is shown in Appendix~\ref{ss:eigens}, the libration frequency about CS2 is slower
 than that about CS1 or CS3. As such, it is the slowest characteristic frequency
@@
 ``adiabatic'' simulations. We explore the consequences of increasingly
-nonadiabatic evolution in \autoref{ss:transition}.
+nonadiabatic evolution in Section~\ref{ss:transition}.
 
@@
 of CS2), such that all initial conditions for a given $\theta_{\rm sd, i}$
-enclose the same initial phase space; see \autoref{sss:a_evo}.}. To be concrete,
+enclose the same initial phase space; see Section~\ref{sss:a_evo}.}. To be concrete,
 we choose $\eta_i = 10\eta_{\rm c}$. For each initial condition, we evolve
@@
 sd, i}}$ is our primary result, and is shown for $I = 5^\circ, 10^\circ,
-20^\circ$ in \autoref{fig:ad_ensemble}, \autoref{fig:3_ensemble_10_35}, and
-\autoref{fig:3_ensemble_20_35} respectively. The blue dots represent the results
+20^\circ$ in Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
+and~\ref{fig:3_ensemble_20_35} respectively. The blue dots represent the results
 of the simulation, which are in excellent agreement with the colored tracks.
@@
     nontrivial dynamical tracks in colored lines. Black dotted lines correspond
-    to small-$\theta_{\rm sd, i}$ predictions derived in \autoref{s:ad_approx}.
-    Bottom: Semi-analytic probabilities of each of the dynamical tracks for each
-    $\theta_{\rm sd, i}$. The five regimes of $\theta_{\rm sd, i}$ values
-    demarcated by the vertical dashed black lines correspond to the five regimes
-    of $A_i$ calculated in \autoref{ss:zone_transitions}. Black dotted lines
-    correspond to simple analytic estimates given in
-    \autoref{s:ad_approx}.}\label{fig:ad_ensemble}
+    to small-$\theta_{\rm sd, i}$ predictions derived in
+    Appendix~\ref{s:ad_approx}. Bottom: Semi-analytic probabilities of each of
+    the dynamical tracks for each $\theta_{\rm sd, i}$. The five regimes of
+    $\theta_{\rm sd, i}$ values demarcated by the vertical dashed black lines
+    correspond to the five regimes of $A_i$ calculated in
+    Section~\ref{ss:zone_transitions}.}\label{fig:ad_ensemble}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_10_35.png}
-    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
+    \caption{Same as Fig.~\ref{fig:ad_ensemble} but for $I =
     10^\circ$ and with fewer annotations.}\label{fig:3_ensemble_10_35}
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_20_35.png}
-    \caption{Same as \autoref{fig:3_ensemble_10_35} but for $I = 20^\circ$. The
+    \caption{Same as Fig.~\ref{fig:3_ensemble_10_35} but for $I = 20^\circ$. The
     $III \to II \to I$ track is very short since the maximum $A_{\rm II}$ is very
@@
 = 1$, and (ii) being easily expressible as combinations of the $A_i$ of
-\autoref{se:area_ward}. The bounds of the integral are either a libration
+Eqs.~\eqref{se:area_ward}. The bounds of the integral are either a libration
 ($\phi$ returns to its original value with the same $\dot{q\phi}$ sign) or
@@
 or CS3 librate about these equilibria respectively, rather than $\hat{l}_{\rm
-d}$, and \autoref{eq:ai_qsd} is no longer exact. In practice,
-\autoref{eq:ai_qsd} holds very well when defining $\theta_{\rm sd, i}$ as the
-angular distance to CS2; an exception is discussed in \autoref{sss:evol_traj}.
+d}$, and Eq.~\eqref{eq:ai_qsd} is no longer exact. In practice,
+Eq.~\eqref{eq:ai_qsd} holds very well when defining $\theta_{\rm sd, i}$ as the
+angular distance to CS2; an exception is discussed in Section~\ref{sss:evol_traj}.
 
@@
 
-$A$ is not conserved when the trajectory encounters the separatrix. Howover,
-its change is easily understood \citep{henrard1982}. In essence, when the
-trajectory crosses the separatrix, it continues to evolve adjacent to the
-separatrix. So if a separatrix crossing results in a zone I trajectory, the
-resultant $A$ can be approximated by integrating \autoref{eq:a_oint} along the
-upper leg of the separatrix. Pictorally, this can be seen in the bottom plots of
-\autoref{fig:ad_21}.
+$A$ is not conserved when the trajectory encounters the separatrix. Howover, its
+change is easily understood \citep{henrard1982}. In essence, when the trajectory
+crosses the separatrix, it continues to evolve adjacent to the separatrix. So if
+a separatrix crossing results in a zone I trajectory, the resultant $A$ can be
+approximated by integrating Eq.~\eqref{eq:a_oint} along the upper leg of the
+separatrix. Pictorally, this can be seen in the bottom plots of
+Fig.~\ref{fig:ad_21}.
 
@@
 Note that $\Pr \p{i \to j} + \Pr\p{i \to k} = 1$. This can be used directly in
-conjunction with \autoref{se:area_ward} to understand for what initial
+conjunction with Eqs.~\eqref{se:area_ward} to understand for what initial
 conditions each track can be observed and with what probabilities.
@@
 As a particular example, consider a system in zone $II$ in panel (d) of
-\autoref{fig:eq_1contours}. As $\eta$ decreases, zone $II$ will shrink while
+Fig.~\ref{fig:eq_1contours}. As $\eta$ decreases, zone $II$ will shrink while
 zones $I$ and $III$ will expand until the trajectory. Suppose the trajectory
@@
     \item $II \to I$ --- An example trajectory following this track is depicted
-        in \autoref{fig:ad_21}. $\hat{s}$ starts librating about CS2 in zone
+        in Fig.~\ref{fig:ad_21}. $\hat{s}$ starts librating about CS2 in zone
         $II$, enclosing some initial phase space area $A_i$. The trajectory is
@@
         encompass $-A_{\rm I}(\eta_\star)$ phase space area. The final
-        $\theta_{\rm f}$ is then given by \autoref{eq:qfaf}. An analytical
-        approximation to $\theta_{\rm f}$ is derived in \autoref{s:ad_approx}
-        and is
+        $\theta_{\rm f}$ is then given by Eq.~\eqref{eq:qfaf}. An analytical
+        approximation to $\theta_{\rm f}$ is derived in
+        Appendix~\ref{s:ad_approx} and is
         \begin{equation}
@@
         A_i$, the trajectory is ejected from the separatrix following
-        \autoref{eq:henrard_hop}. Note that since $\pd{A_i}{\eta} < 0$
+        Eq.~\eqref{eq:henrard_hop}. Note that since $\pd{A_i}{\eta} < 0$
         everywhere, while $\pd{A_{\rm II}}{\eta} > 0$ at all possible
@@
     \item $II \to III$ --- An example trajectory following this track is
-        depicted in \autoref{fig:ad_23}. The only difference from the previous
+        depicted in Fig.~\ref{fig:ad_23}. The only difference from the previous
         track is that, upon separatrix encounter, the trajectory follows the
@@
         II}(\eta_\star)$. The final obliquity is still given by
-        \autoref{eq:qfaf}, and the analytical approximation derived in
-        \autoref{s:ad_approx} is
+        Eq.~\eqref{eq:qfaf}, and the analytical approximation derived in
+        Appendix~\ref{s:ad_approx} is
         \begin{equation}
@@
         further constraint arises when we consider the transition probability
-        given by \autoref{eq:henrard_hop}. Upon examination of
-        \autoref{fig:eq_areas}, it is clear that $\pd{A_{\rm III}}{\eta} > 0$ for
+        given by Eq.~\eqref{eq:henrard_hop}. Upon examination of
+        Fig.~\ref{fig:eq_areas}, it is clear that $\pd{A_{\rm III}}{\eta} > 0$ for
         many $\eta$. Call
@@
         \end{equation}
-        which is labeled in \autoref{fig:eq_areas}, then if $\eta_\star >
+        which is labeled in Fig.~\ref{fig:eq_areas}, then if $\eta_\star >
         \eta_{\rm \min, III}$ then $\Pr_{\rm II \to III} < 0$. This is understood as a
@@
 
-    \item $III \to I$ --- This track is depicted in \autoref{fig:ad_31}.
+    \item $III \to I$ --- This track is depicted in Fig.~\ref{fig:ad_31}.
         The trajectory encounters the separatrix when $A_{\rm I}(\eta_\star) +
@@
         trajectory enclosing $A_f = -A_{\rm I}$. Then, as always, the final
-        obliquity is given by \autoref{eq:qfaf}.
+        obliquity is given by Eq.~\eqref{eq:qfaf}.
 
@@
 
-    \item $III \to II \to I$ --- This track is depicted in \autoref{fig:ad_321}.
+    \item $III \to II \to I$ --- This track is depicted in Fig.~\ref{fig:ad_321}.
         The first separatrix encounter occurs at $\eta_1$ when $A_{\rm
@@
         into zone $II$ enclosing intermediate phase space area $A_m = A_{\rm
-        II}(\eta_1)$. Examining \autoref{fig:eq_areas}, there exist values $A$
+        II}(\eta_1)$. Examining Fig.~\ref{fig:eq_areas}, there exist values $A$
         for which $A_{\rm II}(\eta) = A$ has multiple solutions, and $\eta_1 >
@@
         = -A_{\rm I}(\eta_2)$. The final obliquity again then obeys
-        \autoref{eq:qfaf}.
+        Eq.~\eqref{eq:qfaf}.
 
@@
         Note that a small deviation from $\theta = \theta_{\rm sd, i}$ occurs
-        because we use finite $\eta_i$, as hinted at in \autoref{sss:a_evo}.
+        because we use finite $\eta_i$, as hinted at in Section~\ref{sss:a_evo}.
         This is because for $\theta_{\rm sd, i} \gtrsim \pi/2$, trajectories are
@@
         $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for the $III \to III$ regime, as
-        can be seen visibly in \autoref{fig:3_ensemble_20_35}.
+        can be seen visibly in Fig.~\ref{fig:3_ensemble_20_35}.
 \end{enumerate}
@@
 The corresponding ranges for for $\theta_{\rm sd,i}$ can be computed via
-\autoref{eq:ai_qsd}. The boundaries between these ranges are overplotted in
-\autoref{fig:ad_ensemble}, where they can be seen to agree well with numerical
+Eq.~\eqref{eq:ai_qsd}. The boundaries between these ranges are overplotted in
+Fig.~\ref{fig:ad_ensemble}, where they can be seen to agree well with numerical
 results.
@@
     \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ track.
+    \caption{Same as Fig.~\ref{fig:ad_21} but for the $A_2 \to A_3$ track.
     $\theta_{\rm sd, i} = 0.3\;\mathrm{rad}$ and $\epsilon = 3.01 \times
@@
     \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_{\rm III} \to A_{\rm I}$
+    \caption{Same as Fig.~\ref{fig:ad_21} but for the $A_{\rm III} \to A_{\rm I}$
     track. $\theta_{\rm sd, i} = 89.1^\circ$, and $\epsilon = 3 \times
@@
     \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for the $A_{\rm III} \to A_{\rm II}
+    \caption{Same as Fig.~\ref{fig:ad_21} but for the $A_{\rm III} \to A_{\rm II}
     \to A_{\rm I}$ track. $\theta_{\rm sd, i} = 60^\circ$, and $\epsilon = 3.14
@@
 
-To illustrate the transition to non-adiabaticity, we present two simulations
-with increasingly larger values of $\epsilon$ than \autoref{fig:ad_ensemble}
-below in \autoref{fig:3_ensemble_05_25} and \autoref{fig:3_ensemble_05_15}.
+To illustrate the transition to non-adiabaticity, we present below two
+simulations with larger $\epsilon$ than used for Fig.~\ref{fig:ad_ensemble} in
+Figs.~\ref{fig:3_ensemble_05_25} and~\ref{fig:3_ensemble_05_15}.
 
@@
 values of $\theta$ and have a stricter adiabaticity criterion (see
-\autoref{eq:ad_constr}).
+Eq.~\eqref{eq:ad_constr}).
 
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_25.png}
-    \caption{Same as \autoref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$,
+    \caption{Same as Fig.~\ref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$,
     and restricting $\theta_{\rm sd, i} < 90^\circ$. A larger spread from the
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_15.png}
-    \caption{Same as \autoref{fig:3_ensemble_05_25} but for $\epsilon =
+    \caption{Same as Fig.~\ref{fig:3_ensemble_05_25} but for $\epsilon =
     10^{-1.5}$. Some small semblance of the evolutionary tracks remains, and the
@@
 
-A sample trajectory following in the style of \autoref{fig:ad_21} but for
+A sample trajectory following in the style of Fig.~\ref{fig:ad_21} but for
 $\epsilon = 0.3$ (violating even weak adiabaticity) is provided in
-\autoref{fig:nonad_traj}. It is clear the trajectory does not track level curves
+Fig.~\ref{fig:nonad_traj}. It is clear the trajectory does not track level curves
 of the Hamiltonian during each individual snapshot (e.g.\ the third snapshot).
@@
     \end{subfigure}
-    \caption{Same as \autoref{fig:ad_21} but for a non-adiabatic $\epsilon =
+    \caption{Same as Fig.~\ref{fig:ad_21} but for a non-adiabatic $\epsilon =
     0.3$. In the top panel of the top plot, it is evident that the libration
@@
 We now consider the general problem of how a state evolves when $\eta$ changes
-non-adiabatically. In \autoref{s:ad_approx}, we derive a formula for
+non-adiabatically. In Appendix~\ref{s:ad_approx}, we derive a formula for
 $\theta_{\rm f}$ assuming no initial spin-disk misalignment:
@@
 \end{equation}
-In \autoref{fig:nonad_3_ensemeble}, we show that this proves a remarkably
+In Fig.~\ref{fig:nonad_3_ensemeble}, we show that this proves a remarkably
 accurate when taking $\epsilon = 0.3$.
@@
     the analytical prediction given by
-    \autoref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemeble}
-\end{figure}
-
-The agreement of \autoref{eq:nonad_q_f} at fixed $I$ for varying $\epsilon$ is
-shown in \autoref{fig:nonad_3_scan}. Note that $\epsilon \to 0$ recovers the
+    Eq.~\eqref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemeble}
+\end{figure}
+
+The agreement of Eq.~\eqref{eq:nonad_q_f} at fixed $I$ for varying $\epsilon$ is
+shown in Fig.~\ref{fig:nonad_3_scan}. Note that $\epsilon \to 0$ recovers the
 adiabatic regime. The deviation of $\theta_{\rm f}$ from the analytical
 prediction within the adiabatic regime is indeed due to adiabatic effects
-becoming dominant; compare to \autoref{fig:nonad_3_scan_20} where little
+becoming dominant; compare to Fig.~\ref{fig:nonad_3_scan_20} where little
 deviation is observed until $\theta_{\rm f} \approx 90^\circ$.
@@
     line, corresponds to the adiabatic regime estimated by
-    \autoref{eq:ad_constr}. Overplotted in the red line is
-    \autoref{eq:nonad_q_f}, which is in good agreement for $\epsilon \gtrsim
+    Eq.~\eqref{eq:ad_constr}. Overplotted in the red line is
+    Eq.~\eqref{eq:nonad_q_f}, which is in good agreement for $\epsilon \gtrsim
     0.1$ the non-adiabatic regime, while $\theta_{\rm f} \approx 90^\circ$ in
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3scan_20.png}
-    \caption{Same as \autoref{fig:nonad_3_scan} but for $I=20^\circ$. Note that
-    \autoref{eq:nonad_q_f} is accurate until $\theta_{\rm f} \approx 90^\circ$,
+    \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$. Note that
+    Eq.~\eqref{eq:nonad_q_f} is accurate until $\theta_{\rm f} \approx 90^\circ$,
     which is much closer to the transition to adiabaticity. Comparison with
-    \autoref{fig:nonad_3_scan} suggests that the breakdown of
-    \autoref{eq:nonad_q_f} indeed is caused by the breakdown of the
+    Fig.~\ref{fig:nonad_3_scan} suggests that the breakdown of
+    Eq.~\eqref{eq:nonad_q_f} indeed is caused by the breakdown of the
     non-adiabatic assumption.}\label{fig:nonad_3_scan_20}
@@
         values of $\theta_{\rm sd, i}$ are permitted (see
-        \autoref{fig:ad_ensemble}). We are able to capture both the exact final
+        Fig.~\ref{fig:ad_ensemble}). We are able to capture both the exact final
         $\theta$ values and the probabilities of observing each value via
@@
     \item As the system transitions more abruptly, the adiabatic prediction
-        breaks down when criterion \autoref{eq:ad_constr} is violated. We find a
+        breaks down when criterion Eq.~\eqref{eq:ad_constr} is violated. We find a
         broad range of $\theta$ values can be excited for a given $\theta_{\rm
-        sd, i}$ (see \autoref{fig:nonad_3_ensemeble}). We provide an analytical
+        sd, i}$ (see Fig.~\ref{fig:nonad_3_ensemeble}). We provide an analytical
         expression of the bounds on $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ in
-        \autoref{eq:nonad_q_f_dist}.
+        Eq.~\eqref{eq:nonad_q_f_dist}.
 \end{enumerate}
@@
 It is of interest to note the leading order behavior of $\theta$ in the small
-$\theta_{\rm sd, i}$ limit given by \autoref{eq:qf_21_approx} and
-\autoref{eq:qf_23_approx}. Therefore, if $\theta_{\rm sd, i}$ is generally
+$\theta_{\rm sd, i}$ limit given by Eq.~\eqref{eq:qf_21_approx} and
+Eq.~\eqref{eq:qf_23_approx}. Therefore, if $\theta_{\rm sd, i}$ is generally
 small, as might be expected for planets that do not experience strong collisions
@@
 describing $\hat{s}$. To derive equations of motion for these canonical
-coordinates, we rewrite \autoref{eq:H}
+coordinates, we rewrite Eq.~\eqref{eq:H}
 \begin{equation}
@@
 The equations of motion follow by taking derivatives of $\mathcal{H}$ and agree
-with \autoref{eq:dsdt_base}:
+with Eq.~\eqref{eq:dsdt_base}:
 \begin{subequations}\label{se:H_eom}
@@
 useful for guiding later discussion. Denote $\theta_{\rm cs}$ the obliquity of
-some Cassini State (fixed point of \autoref{se:H_eom}).
+some Cassini State (fixed point of Eqs.~\eqref{se:H_eom}).
 \begin{enumerate}
@@
         for CS2 and CS4 when $\eta \ll \eta_{\rm c}$. We examine
-        \autoref{seq:H_eom_phi_t} and approximate $\cot \theta \approx \cos
+        Eqs.~\eqref{seq:H_eom_phi_t} and approximate $\cot \theta \approx \cos
         \theta$ to find
@@
         when $\eta \ll \eta_{\rm c}$, and for CS2 and CS3 when $\eta \gg
-        \eta_{\rm c}$. It proves easiest to rewrite \autoref{seq:H_eom_phi_t} as
+        \eta_{\rm c}$. It proves easiest to rewrite Eqs.~\eqref{seq:H_eom_phi_t}
+        as
         \begin{equation}
@@
 Note that the $\theta_{\rm cs}$ values derived here do not follow the same
-convention as \autoref{fig:cs_locs}, because the previous $\theta$ conventions
+convention as Fig.~\ref{fig:cs_locs}, because the previous $\theta$ conventions
 presume $\cos \phi = -1$ for all states and let $-\pi \leq \theta < \pi$.
@@
 We linearize about an equilibrium located at $\phi_{\rm cs} = 0, \pi$ but
-arbitrary $\theta_{\rm cs}$. Linearizing \autoref{se:H_eom} about $\phi =
+arbitrary $\theta_{\rm cs}$. Linearizing Eqs.~\eqref{se:H_eom} about $\phi =
 \phi_{\rm cs} + \delta \phi, \theta = \theta_{\rm cs} + \delta \theta$ gives
@@
 \end{align}
-A plot of $\lambda^2$ for each of the CSs is given in \autoref{fig:lambda2}.
+A plot of $\lambda^2$ for each of the CSs is given in Fig.~\ref{fig:lambda2}.
 From the plot, it is clear that only CS4 is a saddle point, while the other
@@
     \includegraphics[width=0.5\textwidth]{../initial/99_misc/2_lambdas.png}
-    \caption{Plot of $\lambda^2$ per \autoref{eq:lambda2} evaluated at each
+    \caption{Plot of $\lambda^2$ per Eq.~\eqref{eq:lambda2} evaluated at each
     of the Cassini States. The vertical axis is rescaled to limit the vertical
@@
 We first seek a simple parameterization for the separatrix. We first solve for
-equilibria of the equation of motion \autoref{eq:dsdt_base} to compute the
+equilibria of the equation of motion Eq.~\eqref{eq:dsdt_base} to compute the
 coordinates for Cassini State 4:
@@
 \end{equation}
-This, in conjunction with \autoref{eq:henrard_hop}, is sufficient to compute
+This, in conjunction with Eq.~\eqref{eq:henrard_hop}, is sufficient to compute
 $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for zone $II$ initial conditions.
@@
         $III$ occurs. These can be calculated to have associated probabilities
-        (using the approximate area \autoref{eq:a_approx})
+        (using the approximate area Eq.~\eqref{eq:a_approx})
         \begin{subequations}
@@
         These are the black dotted lines overplotted in
-        \autoref{fig:ad_ensemble}.
+        Fig.~\ref{fig:ad_ensemble}.
 \end{enumerate}
@@
 
-We present a single result, the derivation of \autoref{eq:nonad_q_f}. We take
-\autoref{eq:dsdt_base} and choose coordinate axes such that $\hat{l} = \hat{z},
+We present a single result, the derivation of Eq.~\eqref{eq:nonad_q_f}. We take
+Eq.~\eqref{eq:dsdt_base} and choose coordinate axes such that $\hat{l} = \hat{z},
 \hat{l}_{\rm d} = \hat{z} \cos I + \hat{x}\sin I$, then we obtain
@@
 about is $\abs{S} = \sqrt{1 - s_z^2}$. Thus, taking the absolute value of both
-sides of \autoref{eq:nonad_int}, assuming $S\p{-\infty} \ll S\p{+\infty}$ and
+sides of Eq.~\eqref{eq:nonad_int}, assuming $S\p{-\infty} \ll S\p{+\infty}$ and
 noting $\theta_{\rm f} \approx \abs{S}(+\infty)$, we obtain
@@
     \item If $\abs{S\p{-\infty}} \sim \abs{S\p{+\infty}}$, then taking the
-        absolute value of both sides of \autoref{eq:nonad_int} no longer simply
-        yields $\abs{S}\p{+\infty}$. This corresponds to the extreme limit
-        where $\eta$ changes so suddenly that $\hat{s}$ has no time to respond
-        and remains roughly unchanged as $\eta \to 0$. This is accommodated by
-        noting $\theta_{\rm f} \geq \theta_{\rm sd, i}$, so the correct estimate can be
-        roughly amended
+        absolute value of both sides of Eq.~\eqref{eq:nonad_int} no longer
+        simply yields $\abs{S}\p{+\infty}$. This corresponds to the extreme
+        limit where $\eta$ changes so suddenly that $\hat{s}$ has no time to
+        respond and remains roughly unchanged as $\eta \to 0$. This is
+        accommodated by noting $\theta_{\rm f} \geq \theta_{\rm sd, i}$, so the
+        correct estimate can be roughly amended
         \begin{equation}

### 2020-01-16 initial/0_eta/utils.py

@@ -93,7 +93,7 @@ def get_four_subplots():
     for ax in axs:
         ax.set_xlim([0, 2 * np.pi])
         ax.set_ylim([-1, 1])
-    f.subplots_adjust(wspace=0.07)
+    f.subplots_adjust(wspace=0.15)
     ax1.set_ylabel(r'$\cos \theta$')
     ax3.set_xlabel(r'$\phi$')
     ax.set_xticks([0, np.pi, 2 * np.pi])

### 2020-01-16 initial/99_misc/1_areas.py

@@ -78,7 +78,7 @@ def plot_areas(I=np.radians(5), filename='1_areas'):
     ax1.plot(eta_cont, np.full_like(eta_cont, A3w[-1] / (4 * np.pi)), 'r--')
     ax1.legend(loc='upper left')
     ax1.set_xlabel(r'$\eta$')
-    ax1.set_ylabel(r'$A_{sep} / 4\pi$')
+    ax1.set_ylabel(r'$A / 4\pi$')
     ax1.set_xticks([0, 0.3, 0.6, 0.9])
     ax1.set_xticklabels([r'$0$', r'$0.3$', r'$0.6$', r'$0.9$'])
     old_ylims = ax1.get_ylim()

### 2020-01-22 writeups/Su_disk_disp.tex
stash work

@@
 
-It should be noted that this calculation breaks down in two ways:
+We note the resemblance to a similar result given by \citet{malhotra_calc}
+describing the impact of a secular resonance sweeping through a system. Both
+results have the scaling with repsect to $\epsilon$, despite the vastly
+different calculation.
+
+It should be noted that this result breaks down in two ways:
 \begin{enumerate}

### 2020-01-22 writeups/Su_weak_tides.tex
stash work

    \documentclass[
        fleqn,
        usenatbib,
        referee,
    ]{mnras}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        graphicx,
        ae, aecompl,
        booktabs,
        caption,
        subcaption,
    }
    \usepackage[T1]{fontenc}
    \captionsetup{compatibility=false}

    \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
    \newcommand*{\rtd}[2]{\frac{\mathrm{d}^2#1}{\mathrm{d}#2^2}}
    \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
    \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
    \newcommand*{\at}[1]{\left.#1\right|}
    \newcommand*{\abs}[1]{\left|#1\right|}
    \newcommand*{\ev}[1]{\langle#1\rangle}
    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
    \newcommand*{\p}[1]{\left(#1\right)}
    \newcommand*{\s}[1]{\left[#1\right]}
    \newcommand*{\z}[1]{\left\{#1\right\}}
    \DeclareMathOperator*{\argmin}{argmin}
    \DeclareMathOperator*{\argmax}{argmax}
    \DeclareMathOperator*{\med}{med}

\title[Analytical Exoplanet Obliquities]{Analytical Predictions of Explanet
Obliquities Generated by Planet-Disk Interactions}
\author[Y. Su and D. Lai]{
Yubo Su$^1$,
Dong Lai$^1$
\\
$^1$ Cornell Center for Astrophysics and Planetary Science, Department of
Astronomy, Cornell University, Ithaca, NY 14853, USA
}

\date{Accepted XXX\@. Received YYY\@; in original form ZZZ}

\pubyear{2020}

\begin{document}\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
    Abstract here
\end{abstract}

\begin{keywords}
planet--star interactions % chktex 8
\end{keywords}

\section{Introduction}

Separatrix crossing was studied by \citep{henrard1982}.

\section{Theory and Equations}\label{s:theory}

We study an oblate planet orbiting around a star hosting a further out planet.
The equations of motion in the absence of dissipation are:

We define $s_c$ to be the critical spin where the precession frequencies
$\omega_{s1}$ and $\omega_{21}$ are equal, or:

Throughout this paper, we often set the orbital frequency of the inner planet
$\Omega_1 = 1$.

\subsection{Cassini States}\label{ss:cs_theory}

Equilibria of spin dynamics are \emph{Cassini States} (CSs). Refer to Su \& Lai
2020 for more detailed discussion. In the notation of the previous paper,
\begin{equation}
    \eta = s_c / s.
\end{equation}

Plots of CS locations as always.

Note that $\phi$ is conjugate to $\cos \theta$, and thus the spin dynamics
exhibit Hamiltonian:

Plot of level curves of Hamiltonian, including $\mathcal{C}_{\pm}$ notation.

\subsection{Weak Tidal Friction}\label{ss:weak_tides}

We use the weak tidal friction model \citep{lai2012}. The EOM for $\theta, s$
become:

The phase portrait for these EOM in $\p{s, \theta}$ space is shown in
Fig.~flow-diagram.

% \label{fig:flow-diagram}

TODO overplot CS1, CS2 for two values of $s_c$. TODO show on plot the location
where tides are so strong that CS2 ecomes unstable (is the only
$\epsilon$-dependent result of the paper).

\subsection{Stable Equilibria of Tidal Friction}\label{ss:tidal_eqs}

Generally, these EOM have equilibria at the points that are both a CS and
satisfy $\dot{s} = 0$ under weak tidal friction. These are stable as $\epsilon
\to 0$, see Appendix~\ref{app:cs_stab}. On Fig.~flow-diagram, these are the
intersection of the locations of CS1 and CS2 with the line $\dot{s} = 0$. It is
clear that the locations of these equilibria depend on the value of $s_c$. Call
these generalized equilibria \emph{tidal Cassini States} (tCS), and number them
tCS1 and tCS2 depending on whether they are CS1 or CS2 states.

Furthermore, if tides are too strong (large $\epsilon$), CS2 can become
unstable (cite Fabrycky). This can be quantified as:

\section{Probability Distribution of Outcomes}\label{s:sim}

The general question of the dynamics is then as follows: given problem
parameters (including $s_c$) and an initial planet spin and obliquity $(s,
\theta)$, what are the possible outcomes and their associated probabilities? We
study this first at fixed $s_c$ as a function of $\theta$ in
Section~\ref{ss:q_dist}, then as a function of $s_c$ for an isotropic initial
spin $\hat{s}$ in Section~\ref{ss:s_c_dist}.

\subsection{Distribution As a Function of $\theta$}\label{ss:q_dist}

As a result of \autoref{ss:tidal_eqs}, the tCS are the only possible final
outcomes. We generate initial spin vectors $\hat{s}$ for isotropic initial
distribution $\p{\cos \theta, \phi}$, and marginalize over $\phi$ (which
generally cannot be fixed by any formation mechanism) in histograms:

% Three primary regimes: $s_c \ll 1$ (CS2 rare), $\simeq 1$ (CS2 is substantial
% and probable), $\gg 1$ (CS2 = I, uninteresting)

The governing mechanism for these probabilities is probabilistic separatrix
crossing, which is covered in Appendix~\ref{app:probs}. The calculation is
difficult analytically, but can be performed semi-analytically (describe
procedure here, calculate $\eta_{\star}$ numerically etc.). The agreement of
this curve with the histograms is examined for the same three $s_c$ values
below:

\subsection{Distribution As a Function of $s_c$}\label{ss:s_c_dist}

Assuming that $\hat{s}$ is drawn from an isotropic distribution, we may then
calculate the probabilities of going to either tCS as a function of $s_c$. This
is shown below:

Note that while only the results for an isotropic distribution of initial
$\hat{s}$ are shown, in principle arbitrary distributions $P\p{\theta_i}$ can be
convolved against the $P_{tCS2}\p{\theta_i}$ distributions shown in
\autoref{ss:q_dist}.

\section{Summary and Discussion}\label{s:summary}

\bibliographystyle{mnras}
\bibliography{Su_sep_cross}

\appendix
\section{Proof of Stability of Cassini States 1 \& 2}\label{app:cs_stab}

Insert here.

\section{Separatrix Crossing Dynamics}

\subsection{Theory}\label{app:sep_crossing_dynamics}

\subsubsection{Application of Adiabatic Invariance: Henrard Theory}

Review Henrard result, is already very successful e.g.\ MMR capture.

\subsubsection{Melnikov Integral}\label{sss:Melnikov}

The first substantial new result.

\subsection{Example: Constant $s$}

``Toy problem 1'', the nice $P_c \propto \eta^{3/2}$ result. Application of
Section~\ref{sss:Melnikov}.

\subsection{Separatrix Crossing Probability: Tidal Friction}\label{app:probs}

Application of the full formula presented in
Section~\ref{app:sep_crossing_dynamics}. The key result is that one integrates

% $\Delta_{\pm}$ equation

The capture probabilities are then

% $P_c = \Delta \pm \dots$

An analytical form that holds when $s \gg s_c$ is:

% ugly approximate form

\bsp
\label{lastpage} % chktex 24
\end{document}

### 2020-01-22 writeups/Su_disk_disp.tex
stash DL first half comments

@@
 
-\section{Introduction}
+\section{Introduction}\label{s:intro}
 
@@
             \p{\frac{m_{\rm p}}{0.001 M_\odot}}
-            \p{\frac{R_{\rm p}}{R_J}}^{-3}
+            \p{\frac{R_{\rm p}}{R_{\rm J}}}^{-3}
         &\p{\frac{M_{\rm d}}{0.01 M_{\odot}}}
@@
 \begin{equation}
-    M_{\rm d}(t) = M_{\rm d}(0)e^{-t/t_{\rm d}},
-\end{equation}
-with $t_d$ constant.
+    M_{\rm d}(t) = M_{\rm d}(0)e^{-t/t_{\rm d}},\label{eq:dmd_dt}
+\end{equation}
+with $t_{\rm d}$ constant.
 
@@
 \begin{align}
-    \epsilon \equiv{}& \frac{1}{\alpha t_{\rm d}},\\
+    \epsilon \equiv{}& \frac{1}{\alpha t_{\rm d}},\label{eq:eps_def}\\
         ={}& 0.015 \p{\frac{k_{\rm p}}{6k_{\rm qp}}}
@@
             \p{\frac{a_{\rm p}}{1\;\mathrm{AU}}}^3\nonumber\\
-        &\p{\frac{R_{\rm p}}{R_J}}^{-3}
+        &\p{\frac{R_{\rm p}}{R_{\rm J}}}^{-3}
             \p{\frac{\Omega_{\rm p}}{2\pi/\p{10\;\mathrm{days}}}}
@@
 \begin{equation}
-    \eta_{\rm c} \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{-3/2},
+    \eta_{\rm c} \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{-3/2},\label{eq:etac}
 \end{equation}
@@
 c}$. Since phase space area is conserved under adiabatic evolution, this implies
-$A_i\p{\eta > \eta_{\rm c}} = A_i(\eta_{\rm c})$. The boundary between these
+$A_{\rm i}\p{\eta > \eta_{\rm c}} = A_{\rm i}(\eta_{\rm c})$. The boundary between these
 extended zones is denoted by the dashed black line in the top left panel of
@@
 
-If a Hamiltonian system is parameterized by some parameter that is varied, its
-evolution is considered \emph{adiabatic} if the parameter's variation is slow
-compared to the Hamiltonian dynamics. In the current problem, the period of the
-longest orbit of the constant-$\eta$ Hamiltonian system is infinite, namely
-along the separatrix. This is an essential feature of the problem, as otherwise
-trajectories would never be able to experience separatrix crossings. But this
-seemingly implies adiabaticity is impossible to define.
-
-Instead of requiring the variation of $\eta$ be slower than all timescales in
-the Hamiltonian dynamics, we seek a weaker but nevertheless effective criterion.
-In practice, trajectories only cross the separatrix once, while they spend many
-orbits inside one of the three zones and far from the separatrix as $\eta$
-evolves. Thus, a \emph{weak adiabaticity criterion} is that the variation of
-$\eta$ be slower than all circulation/libration timescales in the Hamiltonian
-system. If this criterion is satisfied, then a given trajectory will be
-adiabatic for almost all of its evolution save one or two separatrix-crossing
-orbits.
-
-As is shown in Appendix~\ref{ss:eigens}, the libration frequency about CS2 is slower
-than that about CS1 or CS3. As such, it is the slowest characteristic frequency
-in the system. The weak adiabaticity criterion can be recast as requiring that
-$\eta$ vary more slowly than this libration period; this is exactly the
-criterion used in \citep{ward2004II,millholland_disk}. This constraint can be
-computed
-\begin{align}
-    -\at{\frac{1}{\eta}\rd{\eta}{\tau}} = \epsilon &\lesssim
-            \frac{1}{T_{\rm lib}},\\
-        &\lesssim \frac{1}{2\pi}\sqrt{\eta\sin I \sin \theta_2
+In this section, we study the evolution of the planetary obliquity $\theta$ when
+the parameter $\eta$ (or the disk mass $M_{\rm d}$; see Eq.~\eqref{eq:eta})
+decreases sufficiently slowly that the evolution is adiabatic. Strictly
+speaking, this requires the disk evolution timescale $t_{\rm d}$
+(Eq.~\eqref{eq:dmd_dt}) be much larger than all timesccales of the dynamical
+system governed by the Hamiltonian~\eqref{eq:H}. This is of course not possible
+in all cases, as the motion along the separatrix has an infinite period.
+
+In practice, as $\eta$ evolves, the system only crosses the separatrix once or
+twice, while it spends many orbits inside one of the three zones and far from
+the separatrix. Thus, a \emph{weak adiabaticity criterion} is that the variation
+timescale of $\eta$ be slower than all circulation/libration timescales near the
+equilibria/fixed points. If this criterion is satisfied, then the system will
+evolve adiabatically for most of its evolution save one or two separatrix
+crossings.
+
+As is shown in Appendix~\ref{ss:eigens}, libration about CS2 is slower than that
+about CS1 or CS3. As such, it is the slowest characteristic frequency in the
+system. The weak adiabaticity criterion can be recast as requiring that $\eta$
+vary more slowly than this libration frequency
+\citep[see][]{ward2004II,millholland_disk}, i.e.\ $t_{\rm d}^{-1} \lesssim
+\omega_{\rm lib} / 2\pi$. In terms of the dimensionless parameter $\epsilon$
+(Eq.~\eqref{eq:eps_def}), this adiabaticity condition is
+\begin{equation}
+    \epsilon = \frac{1}{\alpha t_{\rm d}}
+        \lesssim \frac{1}{2\pi}\sqrt{\eta\sin I \sin \theta_2
             \p{1 + \eta \sin I \csc^3 \theta_2}},
             \label{eq:ad_constr}
-\end{align}
+\end{equation}
 where $\theta_2$ is the obliquity at CS2. This formula differs somewhat from
@@
 
-For $I = 5^\circ$, $\eta \sim \eta_c$ we compute $\epsilon \lesssim 0.085$ is
-the requirement for weak adiabaticity. Since our criterion is only a weak
-constraint on adiabaticity, we use $\epsilon = 3 \times 10^{-4}$ in our
-``adiabatic'' simulations. We explore the consequences of increasingly
-nonadiabatic evolution in Section~\ref{ss:transition}.
+For $I = 5^\circ$, $\eta \sim \eta_{\rm c}$ Eq.~\eqref{eq:ad_constr} gives $\epsilon
+\lesssim 0.085$. Since our criterion is only a weak condition for adiabaticity,
+we use $\epsilon = 3 \times 10^{-4}$ in our ``adiabatic'' simulations below
+(Section~\autoref{ss:ad_ensemble}). We explore the consequences of nonadiabatic
+evolution in Section~\ref{s:nonad}.
 
@@
 
-We consider the evolution of a system with arbitrary initial $\theta_{\rm sd, i}
-\equiv \at{\theta_{\rm sd}}_{t = 0}$ and $\eta_i \equiv \at{\eta}_{t = 0} \gg
-1$. We are interested in the distribution of final obliquities after $\eta$
-decreases to $\eta_f \ll 1$ (after the disk has dissipated to negligible mass).
-While it is likely that $\theta_{\rm sd, i} \approx 0$ as the planet forms in
-the disk, we explore all $\theta_{\rm sd, i} \in [0, \pi]$ for completeness.
-
-We evenly sample $101$ values of $\theta_{\rm sd, i}$, and for each $\theta_{\rm
-sd, i}$ value, we pick $101$ $\hat{s}$ initial conditions approximately on the
-ring fixed by $\theta_{\rm sd, i}$\footnote{For each $\theta_{\rm sd, i}$ we
-choose an initial condition on the libration cycle going through $\p{\theta_2 +
-\theta_{\rm sd, i}, \phi_2}$ (where $\p{\theta_2, \phi_2}$ are the coordinates
-of CS2), such that all initial conditions for a given $\theta_{\rm sd, i}$
-enclose the same initial phase space; see Section~\ref{sss:a_evo}.}. To be concrete,
-we choose $\eta_i = 10\eta_{\rm c}$. For each initial condition, we evolve
-Equations~\ref{eq:dsdt_base} and~\ref{eq:deta_dt} until $\eta = 10^{-5}$. For
-such small $\eta$, $\hat{s}$ precesses about $\hat{l}$ with uniform final
-obliquity $\theta_{\rm f}$. This transfer function $\theta_{\rm f}\p{\theta_{\rm
-sd, i}}$ is our primary result, and is shown for $I = 5^\circ, 10^\circ,
+We consider the evolution of a system with arbitrary initial spin-disk
+misalignment angle $\theta_{\rm sd, i}$ and initial $\eta_{\rm i} \gg 1$. We are
+interested in the final spin obliquities $\theta_{\rm f}$ after $\eta$ gradually
+decreases to $\eta_{\rm f} \ll 1$ (i.e.\ after the disk has dissipated to a
+negligible mass). Note that when $\eta_{\rm i} \gg 1$, $\hat{l}$ precesses
+around $\hat{l}_{\rm d}$ much faster than the spin-orbit precession
+($\abs{\omega_{\rm ld}} \gg \abs{\omega_{\rm sl}}$), and the spin obliquity
+$\theta$ is not well defined. So it is more appropriate to use $\theta_{\rm sd}$
+rather than $\theta$ to specify the initial spin orientation.
+
+As discussed in Section~\ref{s:intro}, we explore $\theta_{\rm sd, i} \in [0,
+\pi]$. We choose $\epsilon = 3 \times 10^{-4}$ so that the system evolves almost
+adiabatically (see above).
+
+To obtain the distribution of the final obliquities $\theta_{\rm f}$, we evenly
+sample $101$ values of $\theta_{\rm sd, i}$, and for each $\theta_{\rm sd, i}$
+value, we pick $101$ $\hat{s}$ initial conditions approximately on the ring
+fixed by $\theta_{\rm sd, i}$%
+%
+\footnote{For each $\theta_{\rm sd, i}$ we choose an initial condition on the
+libration cycle going through $\p{\theta_2 + \theta_{\rm sd, i}, \phi_2}$ (where
+$\p{\theta_2, \phi_2}$ are the coordinates of CS2), such that all initial
+conditions for a given $\theta_{\rm sd, i}$ enclose the same initial phase
+space; see Section~\ref{sss:a_evo}.}.
+%
+To be concrete, we choose $\eta_{\rm i} = 10\eta_{\rm c}$ where $\eta_{\rm c}$
+is given by Eq.~\eqref{eq:etac} and evolve Equations~\ref{eq:dsdt_base}
+and~\ref{eq:deta_dt} until $\eta$ reaches its final value $10^{-5}$. At such a
+small $\eta$, $\hat{s}$ is strongly coupled to $\hat{l}$ and the final obliquity
+$\theta_{rm f}$ is frozen. The mapping between $\theta_{\rm sd, i}$ and
+$\theta_{\rm f}$ is our primary result, and is shown for $I = 5^\circ, 10^\circ,
 20^\circ$ in Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
 and~\ref{fig:3_ensemble_20_35} respectively. The blue dots represent the results
-of the simulation, which are in excellent agreement with the colored tracks.
-These colored tracks are calculated semi-analytically using methods explained in
-the following section.
+of the numerical calculation. The colored tracks are calculated
+semi-analytically using the method discussed in the following subsection.
 
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_35.png}
-    \caption{Top: $\theta_{\rm f}\p{\theta_{\rm sd, i}}$, overlaid with
-    semi-analytic predictions of the $\theta_{\rm  f}$ for each of the four
-    nontrivial dynamical tracks in colored lines. Black dotted lines correspond
-    to small-$\theta_{\rm sd, i}$ predictions derived in
-    Appendix~\ref{s:ad_approx}. Bottom: Semi-analytic probabilities of each of
-    the dynamical tracks for each $\theta_{\rm sd, i}$. The five regimes of
-    $\theta_{\rm sd, i}$ values demarcated by the vertical dashed black lines
-    correspond to the five regimes of $A_i$ calculated in
-    Section~\ref{ss:zone_transitions}.}\label{fig:ad_ensemble}
+    \caption{Top: The final spin obliquity $\theta_{\rm f}$ as a function of the
+    initial spin-disk misalignment angle $\theta_{\rm sd, i}$ for systems
+    evolving from initial $\eta_{\rm i} \gg 1$ to $\eta_{\rm i} \ll 1$. The dots
+    are results of numerical calculations (Section~\ref{ss:ad_ensemble}), and
+    the colored tracks are semi-analytical results
+    (Section~\ref{ss:zone_transitions}). The black dotted lines represent
+    analytical approximations valid in the small-$\theta_{\rm sd, i}$ limit (see
+    Appendix~\ref{s:ad_approx}). Bottom: Where a particular $\theta_{\rm sd, i}$
+    corresponds to multiple tracks, the system evolves probabilistically.
+    The track that a particular system evolves along in a numerical simulation
+    can be measured by examining its final obliquity. The dots represent the
+    inferred probabilities from measured final obliquities in our simulations,
+    while the colored tracks denote the semi-analytic probability of the system
+    evolving along each track. There are five regimes of $\theta_{\rm sd, i}$
+    values for which different tracks are accessible. Semi-analytical
+    calculations of the boundaries of these regimes are denoted via the vertical
+    dashed black lines (see
+    Section~\ref{ss:zone_transitions}).}\label{fig:ad_ensemble}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_20_35.png}
-    \caption{Same as Fig.~\ref{fig:3_ensemble_10_35} but for $I = 20^\circ$. The
-    $III \to II \to I$ track is very short since the maximum $A_{\rm II}$ is very
-    near $\eta_{\rm c}$ for $I = 20^\circ$.}\label{fig:3_ensemble_20_35}
-\end{figure}
-
-\subsection{Adiabatic Evolution Theory}\label{ss:zone_transitions}
-
-The evolutionary tracks that govern the behavior of $\theta_{\rm
-f}\p{\theta_{\rm sd, i}}$ correspond to particular sequences of separatrix
-crossings. Coarsely, they can be understood using a combination of (i) how the
-enclosed phase space area by the trajectory evolves across each separatrix
+    \caption{Same as Fig.~\ref{fig:3_ensemble_10_35} but for $I = 20^\circ$.
+    % Note that the $III \to II \to I$ track is very short since the maximum
+    % $A_{\rm II}$ is very near $\eta_{\rm c}$ for $I = 20^\circ$. (not a
+    % clear/useful observation - yubo)
+    }\label{fig:3_ensemble_20_35}
+\end{figure}
+
+\subsection{Analytical Theory for Adiabatic Evolution}\label{ss:zone_transitions}
+
+The evolutionary tracks that govern the $\theta_{\rm f}$-$\theta_{\rm sd, i}$
+mapping correspond to various sequences of separatrix crossings. They can be
+understood using the principle of adiabatic invariance, combined with (i) how
+the enclosed phase space area by the trajectory evolves across each separatrix
 crossing, and (ii) the associated probabilities with each separatrix crossing.
@@
 This definition of $A$ has the advantage of (i) being continuous at $\cos \theta
-= 1$, and (ii) being easily expressible as combinations of the $A_i$ of
+= 1$, and (ii) being easily expressible as combinations of the $A_{\rm i}$ of
 Eqs.~\eqref{se:area_ward}. The bounds of the integral are either a libration
@@
 
-Observe that when $\eta_i \gg 1$, trajectories librate about $\hat{l}_{\rm d}$
+Observe that when $\eta_{\rm i} \gg 1$, trajectories librate about $\hat{l}_{\rm d}$
 with constant $\theta_{\rm sd}$, meaning they enclose initial phase space area
 \begin{equation}
-    A_i \equiv \at{A}_{t = 0}
+    A_{\rm i} \equiv \at{A}_{t = 0}
         = 2\pi\p{1 - \cos \theta_{\rm sd, i}}.\label{eq:ai_qsd}
 \end{equation}
-Complications arise when considering finite $\eta_i$, as trajectories near CS2
+Complications arise when considering finite $\eta_{\rm i}$, as trajectories near CS2
 or CS3 librate about these equilibria respectively, rather than $\hat{l}_{\rm
@@
 Beginning at the last separatrix crossing, the final enclosed phase space area
-$A_f$ will be conserved for all time. As $\eta \to 0$, trajectories circulate at
-constant obliquity $\theta_{\rm f}$, related to $A_f$ by
-\begin{equation}
-    2\pi\p{1 - \cos \theta_{\rm f}} = A_f. \label{eq:qfaf}
+$A_{\rm f}$ will be conserved for all time. As $\eta \to 0$, trajectories circulate at
+constant obliquity $\theta_{\rm f}$, related to $A_{\rm f}$ by
+\begin{equation}
+    2\pi\p{1 - \cos \theta_{\rm f}} = A_{\rm f}. \label{eq:qfaf}
 \end{equation}
@@
 \begin{align}
-    \Pr\p{i \to j} = -\frac{\pd{A_j}{t}}{ \pd{A_i}{t}}
-        = -\frac{\pd{A_j}{\eta}}{ \pd{A_i}{\eta}},\\
+    \Pr\p{i \to j} = -\frac{\pd{A_{\rm j}}{t}}{ \pd{A_{\rm i}}{t}}
+        = -\frac{\pd{A_{\rm j}}{\eta}}{ \pd{A_{\rm i}}{\eta}},\\
     \Pr\p{i \to k}
-        = -\frac{\pd{A_k}{\eta}}{ \pd{A_i}{\eta}}.\label{eq:henrard_hop}
+        = -\frac{\pd{A_{\rm k}}{\eta}}{ \pd{A_{\rm i}}{\eta}}.\label{eq:henrard_hop}
 \end{align}
@@
         in Fig.~\ref{fig:ad_21}. $\hat{s}$ starts librating about CS2 in zone
-        $II$, enclosing some initial phase space area $A_i$. The trajectory is
+        $II$, enclosing some initial phase space area $A_{\rm i}$. The trajectory is
         able to librate without separatrix encounter until $A_{\rm
-        II}(\eta_\star) = A_i$. As the trajectory transitions to a circulating
+        II}(\eta_\star) = A_{\rm i}$. As the trajectory transitions to a circulating
         trajectory in zone $I$ immediately bordering the separatrix, it will
@@
         This transition can only occur when the initial condition begins in zone
-        II, requiring $A_i < A_{\rm II}(\eta_{\rm c})$. Note $A_{\rm II}(\eta_{\rm c})$ is
+        II, requiring $A_{\rm i} < A_{\rm II}(\eta_{\rm c})$. Note $A_{\rm II}(\eta_{\rm c})$ is
         given in closed form in \citet{ward2004I} but appears to be incorrect.
         Then, at some known $\eta_\star$ satisfying $A_{\rm II}(\eta_\star) =
-        A_i$, the trajectory is ejected from the separatrix following
-        Eq.~\eqref{eq:henrard_hop}. Note that since $\pd{A_i}{\eta} < 0$
+        A_{\rm i}$, the trajectory is ejected from the separatrix following
+        Eq.~\eqref{eq:henrard_hop}. Note that since $\pd{A_{\rm i}}{\eta} < 0$
         everywhere, while $\pd{A_{\rm II}}{\eta} > 0$ at all possible
@@
         circulating trajectory in zone $III$ bordering the separatrix, upon
-        which it will encompass $A_f = A_{\rm I}(\eta_\star) + A_{\rm
+        which it will encompass $A_{\rm f} = A_{\rm I}(\eta_\star) + A_{\rm
         II}(\eta_\star)$. The final obliquity is still given by
@@
 
-        Again, this track can only occur when $A_i < A_{\rm II}(\eta_{\rm c})$, but a
+        Again, this track can only occur when $A_{\rm i} < A_{\rm II}(\eta_{\rm c})$, but a
         further constraint arises when we consider the transition probability
@@
         The trajectory encounters the separatrix when $A_{\rm I}(\eta_\star) +
-        A_{\rm II}(\eta_\star) = A_i$, upon which it transitions to a zone $I$
-        trajectory enclosing $A_f = -A_{\rm I}$. Then, as always, the final
+        A_{\rm II}(\eta_\star) = A_{\rm i}$, upon which it transitions to a zone $I$
+        trajectory enclosing $A_{\rm f} = -A_{\rm I}$. Then, as always, the final
         obliquity is given by Eq.~\eqref{eq:qfaf}.
 
-        This track can only occur if $A_i > A_{\rm II}(\eta_{\rm c})$, but is also
-        constrained by requiring its $A_i$ is sufficiently small it will
+        This track can only occur if $A_{\rm i} > A_{\rm II}(\eta_{\rm c})$, but is also
+        constrained by requiring its $A_{\rm i}$ is sufficiently small it will
         encounter the separatrix (if it is too large, it will never encounter
         the separatrix, which is a $III \to III$ transition). This is written
-        $A_i < \max A_{\rm I} + A_{\rm II} = 4\pi - \min A_{\rm III}$.
+        $A_{\rm i} < \max A_{\rm I} + A_{\rm II} = 4\pi - \min A_{\rm III}$.
 
@@
         The first separatrix encounter occurs at $\eta_1$ when $A_{\rm
-        I}(\eta_1) + A_{\rm II}(\eta_1) = A_i$, upon which the trajectory moves
-        into zone $II$ enclosing intermediate phase space area $A_m = A_{\rm
+        I}(\eta_1) + A_{\rm II}(\eta_1) = A_{\rm i}$, upon which the trajectory moves
+        into zone $II$ enclosing intermediate phase space area $A_{\rm m} = A_{\rm
         II}(\eta_1)$. Examining Fig.~\ref{fig:eq_areas}, there exist values $A$
@@
         $III \to II \to I$ transition is permitted. Thus, as $\eta$ continues to
-        decrease, a second $\eta_2$ value exists for which $A_m = A_{\rm
+        decrease, a second $\eta_2$ value exists for which $A_{\rm m} = A_{\rm
         II}(\eta_2)$, upon which the trajectory is ejected to zone $I$ and $A_f
@@
         Similar to the $III \to I$ track, the $III \to II \to I$ track can only
-        occur over the same $A_{\rm II}(\eta_{\rm c}) < A_i < \max A_{\rm I} + A_{\rm
+        occur over the same $A_{\rm II}(\eta_{\rm c}) < A_{\rm i} < \max A_{\rm I} + A_{\rm
         II}$ interval. The probability of encountering this track is set by the
         initial $III \to II$ transition. It bears noting that this probability
-        is only nonnegative for a very small fraction of $A_i$ values, since it
+        is only nonnegative for a very small fraction of $A_{\rm i}$ values, since it
         requires $\pd{A_{\rm II}}{\eta}$ and $\pd{A_{\rm III}}{\eta}$ to have
-        different signs; this occurs only if $A_{\rm II}\p{\eta_{\rm c}} < A_i <
+        different signs; this occurs only if $A_{\rm II}\p{\eta_{\rm c}} <
+        A_{\rm i} <
         A_{\rm II, \max}$. Outside of these bounds, $\Pr_{\rm III \to II} < 0$
@@
         separatrix encounter ever occurs, and $A$ is constant throughout the
-        evolution. This constraint equates to $A_i > \max A_{\rm I} + A_{\rm
-        II}$, whereupon no separatrix encounter occurs at all, and $A_f = A_i$,
-        which for $\eta_i \to \infty, \eta_f \to 0$ results in $\theta =
+        evolution. This constraint equates to $A_{\rm i} > \max A_{\rm I} + A_{\rm
+        II}$, whereupon no separatrix encounter occurs at all, and $A_{\rm f} =
+        A_{\rm i}$,
+        which for $\eta_{\rm i} \to \infty, \eta_{\rm f} \to 0$ results in $\theta =
         \theta_{\rm sd, i}$.
@@
         Note that a small deviation from $\theta = \theta_{\rm sd, i}$ occurs
-        because we use finite $\eta_i$, as hinted at in Section~\ref{sss:a_evo}.
+        because we use finite $\eta_{\rm i}$, as hinted at in Section~\ref{sss:a_evo}.
         This is because for $\theta_{\rm sd, i} \gtrsim \pi/2$, trajectories are
         better described as librating about CS3. Nevertheless, we can still
-        approximate $A_i$ to good accuracy as the solid angle enclosed by
+        approximate $A_{\rm i}$ to good accuracy as the solid angle enclosed by
         libration about CS3 with polar angle $2\pi + \theta_3 - \theta_2 -
@@
 \end{enumerate}
-In summary, the five regimes of track possibilities in increasing order of $A_i$
+In summary, the five regimes of track possibilities in increasing order of
+$A_{\rm i}$
 are:
 \begin{enumerate}
-    \item $A_i \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$ --- $II \to III,
+    \item $A_{\rm i} \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$ --- $II \to III,
         II \to I$ both possible.
 
-    \item $A_i \in \s{A_{\rm II}\p{\eta_{\rm \min, III}}, A_{\rm II}(\eta_{\rm c})}$
+    \item $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm \min, III}}, A_{\rm II}(\eta_{\rm c})}$
         --- $II \to I$ only.
 
-    \item $A_i \in \s{A_{\rm II}(\eta_{\rm c}), A_{\rm II, \max}}$ --- $III \to I, III
+    \item $A_{\rm i} \in \s{A_{\rm II}(\eta_{\rm c}), A_{\rm II, \max}}$ --- $III \to I, III
         \to II \to I$ both possible.
 
-    \item $A_i \in \s{A_{\rm II, \max}, \max A_{\rm I} + A_{\rm II}}$ --- $III
+    \item $A_{\rm i} \in \s{A_{\rm II, \max}, \max A_{\rm I} + A_{\rm II}}$ --- $III
         \to I$ only.
 
-    \item $A_i > \max A_{\rm I} + A_{\rm II}$ --- $III \to III$ only.
+    \item $A_{\rm i} > \max A_{\rm I} + A_{\rm II}$ --- $III \to III$ only.
 \end{enumerate}
@@
 \hat{z}$ and $\theta, \phi$ are the polar and azimuthal angle of $\hat{s}$. By
-convention, we choose $\hat{l}_z$ at coordinates $\theta = I, \phi = \pi$.
+convention, we choose $\hat{l}_{\rm z}$ at coordinates $\theta = I, \phi = \pi$.
 Note that $\p{\cos \theta, \phi}$ form a canonically conjugate pair of variables
@@
     it exists while all others are centers ($\lambda^2 < 0$). The horizontal
-    dashed line is $\lambda^2 = 0$ the instability boundary while $\eta_c$ is
+    dashed line is $\lambda^2 = 0$ the instability boundary while $\eta_{\rm c}$ is
     labered in the vertical dashed line.}\label{fig:lambda2}
@@
     \item Upon a transition to zone $I$ or zone $III$, the final obliquities can
-        be predicted by observing the final adiabatic invariant $A_f = -A_{\rm
-        I}(\eta_\star)$ in the zone $I$ case and $A_f = A_{\rm I}(\eta_\star) +
+        be predicted by observing the final adiabatic invariant $A_{\rm f} = -A_{\rm
+        I}(\eta_\star)$ in the zone $I$ case and $A_{\rm f} = A_{\rm I}(\eta_\star) +
         A_{\rm I}I(\eta_\star)$ in the zone $III$ case. As $\eta \to 0$, these
@@
 
-Now, let's assume that $s_z \approx \cos I$ throughout the evolution of
-$\hat{s}$ (note that $\theta_{\rm sd, i} = 0$ implies the initial $s_z = \cos
-I$). Then let's examine the evolution of quantity $S = s_x + is_y$ instead:
+Now, let's assume that $s_{\rm z} \approx \cos I$ throughout the evolution of
+$\hat{s}$ (note that $\theta_{\rm sd, i} = 0$ implies the initial $s_{\rm z} = \cos
+I$). Then let's examine the evolution of quantity $S = s_{\rm x} + is_{\rm y}$ instead:
 \begin{equation}
@@
 Now, it should be noted that $e^{i\Phi}$ is just a phase; all we really care
-about is $\abs{S} = \sqrt{1 - s_z^2}$. Thus, taking the absolute value of both
+about is $\abs{S} = \sqrt{1 - s_{\rm z}^2}$. Thus, taking the absolute value of both
 sides of Eq.~\eqref{eq:nonad_int}, assuming $S\p{-\infty} \ll S\p{+\infty}$ and
@@
     \item If the evolution of $\hat{s}$ is adiabatic, then it is invalid to
-        assume $s_z$ is approximately constant in time, as many
+        assume $s_{\rm z}$ is approximately constant in time, as many
         circulation/libration orbits can ensue. Only when the driving is
-        sufficiently impulsive that the evolution dominates the change in $s_z$
+        sufficiently impulsive that the evolution dominates the change in
+        $s_{\rm z}$
         is this calculation valid.

### 2020-01-23 writeups/Su_disk_disp.tex
fix plots, plus footnote for DL first half review

@@
 sample $101$ values of $\theta_{\rm sd, i}$, and for each $\theta_{\rm sd, i}$
-value, we pick $101$ $\hat{s}$ initial conditions approximately on the ring
-fixed by $\theta_{\rm sd, i}$%
+value, we pick $101$ $\hat{s}$ approximately from the ring of initial conditions
+having angular distance $\theta_{\rm sd, i}$ to $\hat{l}_{\rm d}$%
 %
-\footnote{For each $\theta_{\rm sd, i}$ we choose an initial condition on the
-libration cycle going through $\p{\theta_2 + \theta_{\rm sd, i}, \phi_2}$ (where
-$\p{\theta_2, \phi_2}$ are the coordinates of CS2), such that all initial
-conditions for a given $\theta_{\rm sd, i}$ enclose the same initial phase
-space; see Section~\ref{sss:a_evo}.}.
+\footnote{
+The procedure we adopted for choosing initial conditions is the natural
+extension of this for finite $\eta_{\rm i}$. Note that the center of $\hat{s}$'s
+libration is CS2, which, since $\eta_{\rm i}$ is finite, is different than
+$\hat{l}_{\rm d}$. Furthermore, the libration is not exactly circular. Thus,
+initial conditions on the circular ring of points having angular distance
+$\theta_{\rm sd, i}$ from $\hat{l}_{\rm d}$ do not lie \emph{exactly} along each
+others' trajectories, and will each enclose slightly different initial phase
+space areas $A_{\rm i}$. Since our analytical theory assumes exact conservation
+of phase space area $A_{\rm i}$ derived from $\theta_{\rm sd, i}$ (see
+Section~\ref{ss:zone_transitions}), this discrepancy introduces an extra
+deviation from the analytical prediction. To guarantee all points for a
+particular $\theta_{\rm sd, i}$ have the same $A_{\rm i}$, we instead choose
+initial conditions on the libration cycle going through $\p{\theta_2 +
+\theta_{\rm sd, i}, \phi_2}$ (where $\p{\theta_2, \phi_2}$ are the coordinates
+of CS2). This ensures that all initial conditions for a given $\theta_{\rm sd,
+i}$ enclose the same initial $A_{\rm i}$. Note that as $\eta_{\rm i} \to
+\infty$, CS2 becomes coincident with $\hat{l}_{\rm d}$ and the libration cycle
+becomes exactly circular, recovering the procedure given in the text.}.
 %

### 2020-01-23 writeups/Su_weak_tides.tex
put a few prelim plots into outline

@@
 Yubo Su$^1$,
-Dong Lai$^1$
+Dong Lai$^{1,2}$
 \\
@@
 Astronomy, Cornell University, Ithaca, NY 14853, USA
+\\
+$^2$ Tsung-Dao Lee Institute, 800 Dongchuan Road, Shanghai, 200240, China
 }
@@
 The phase portrait for these EOM in $\p{s, \theta}$ space is shown in
-Fig.~flow-diagram.
+Fig.~\ref{fig:quiver}.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/2quiver0_2.png}
+    \caption{Phase portrait.}\label{fig:quiver}
+\end{figure}
 
-% \label{fig:flow-diagram}
-
-TODO overplot CS1, CS2 for two values of $s_c$. TODO show on plot the location
+TODO overplot CS1, CS2 for \emph{two} values of $s_c$. TODO show on plot the location
 where tides are so strong that CS2 ecomes unstable (is the only
@@
 satisfy $\dot{s} = 0$ under weak tidal friction. These are stable as $\epsilon
-\to 0$, see Appendix~\ref{app:cs_stab}. On Fig.~flow-diagram, these are the
+\to 0$, see Appendix~\ref{app:cs_stab}. On Fig.~\ref{fig:quiver}, these are the
 intersection of the locations of CS1 and CS2 with the line $\dot{s} = 0$. It is
@@
 distribution $\p{\cos \theta, \phi}$, and marginalize over $\phi$ (which
-generally cannot be fixed by any formation mechanism) in histograms:
-
-% Three primary regimes: $s_c \ll 1$ (CS2 rare), $\simeq 1$ (CS2 is substantial
-% and probable), $\gg 1$ (CS2 = I, uninteresting)
+generally cannot be fixed by any formation mechanism) in histograms. This gives
+histograms in Figs.~\ref{fig:Hhists_0_06,fig:Hhists_0_20,fig:Hhists_0_70}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
+    \caption{$s_c = 0.06$. Note that it is difficult to reach
+    tCS2.}\label{fig:Hhists_0_06}
+\end{figure}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
+    \caption{$s_c = 0.2$. Note that tCS2 is both reached with substantial
+    probability and has substantial obliquity.}\label{fig:Hhists_0_20}
+\end{figure}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_60_5.png}
+    \caption{$s_c = 0.6$. Note that tCS2 becomes attracting over tCS1, but will
+    have obliquity $\approx I$ and is uninteresting.}\label{fig:Hhists_0_70}
+\end{figure}
 
@@
 this curve with the histograms is examined for the same three $s_c$ values
-below:
+in Figs.~\ref{fig:pc_fits_0_06,fig:pc_fits_0_20,fig:pc_fits_0_70}.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_06_5.png}
+    \caption{$s_c = 0.06$ fit to histogram.}\label{fig:pc_fits_0_06}
+\end{figure}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_20_5.png}
+    \caption{$s_c = 0.20$ fit to histogram.}\label{fig:pc_fits_0_20}
+\end{figure}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_70_5.png}
+    \caption{$s_c = 0.70$ fit to histogram.}\label{fig:pc_fits_0_70}
+\end{figure}
 
@@
 calculate the probabilities of going to either tCS as a function of $s_c$. This
-is shown below:
+is shown below for $I = 5^\circ$
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5probs_5.png}
+    \caption{Total probabilities of ending up in either tCS and their ossicated
+    final obliquities.}\label{fig:probs}
+\end{figure}
 

### 2020-01-23 initial/1_weaktide/utils.py

@@ -291,7 +291,16 @@ def get_crit_mus(I, s_c):
             return opt.bisect(dmu_cs1_equil, s_etac, 1), cs2_equil_mu
     return None, cs2_equil_mu
 
-ETA_CUTOFF = 0.65
+def get_eta_cutoff(I):
+    '''
+    if the separatrix isn't double valued for phi (i.e. it touches (np.pi, +1)),
+    then the calculations of the probabilities is somewhat different; above this
+    eta, finding the separatrix to integrate is somewhat tricky. We will ad-hoc
+    this cutoff since we only use two I values...
+    '''
+    if I > np.radians(10):
+        return 0.4
+    return 0.65
 def get_ps_anal(I, s_c, s, *args):
     ''' analytical capture probabilities '''
     eta = s_c / s
@@ -341,8 +350,8 @@ def get_ps_anal(I, s_c, s, *args):
         )
     top = get_top()
     bot = get_bot()
-    top[np.where(eta > ETA_CUTOFF)[0]] = -1
-    bot[np.where(eta > ETA_CUTOFF)[0]] = -1
+    top[np.where(eta > get_eta_cutoff(I))[0]] = -1
+    bot[np.where(eta > get_eta_cutoff(I))[0]] = -1
     return top, bot
 
 def get_ps_numinterp(I, s_c, s_arr):
@@ -351,7 +360,7 @@ def get_ps_numinterp(I, s_c, s_arr):
     def getter(s):
         ''' gets probability for a single spin s '''
         eta = s_c / s
-        if eta > ETA_CUTOFF:
+        if eta > get_eta_cutoff(I):
             return -1, -1
         [mu4] = get_mu4(I, s_c, np.array([s]))
 
@@ -418,7 +427,7 @@ def get_anal_caps(I, s_c, cross_dat, mu_vals,
         else:
             p_caps[idx, cross_idxs] = (top + bot) / top
 
-        # ETA_CUTOFF values above sep are zero
+        # eta cutoff values above sep are zero
         cutoff_expr = np.logical_and(top == -1, bot == -1)
         cutoff_idxs_above = np.where(np.logical_and(
             cutoff_expr,

### 2020-01-30 initial/notes.tex
overplot vertical lines for slowest spin such that CS2 is still stable to tides

@@
 \end{equation}
+Note that we can invert this to find, for a given $\epsilon$, the smallest value
+of $\eta$ for which CS2 is still stable, which must satisfy $\eta \sin I =
+\epsilon\p*{1 - \eta^2\cos^2 I}$, or
+\begin{equation}
+    \eta_{\min} \equiv \frac{\sin I + \sqrt{\sin^2I
+        + 4\epsilon^2 \cos^2 I}}{2\epsilon \cos^2 I}.
+\end{equation}
+
 We can substitute in $\mu_2, \mu_4 \sim \eta \cos I$ to obtain

### 2020-01-30 initial/1_weaktide/utils.py

@@ -446,3 +446,20 @@ def get_anal_caps(I, s_c, cross_dat, mu_vals,
 
 def get_num_caps(I, s_c, cross_dat, mu_vals):
     return get_anal_caps(I, s_c, cross_dat, mu_vals, getter=get_ps_num)
+
+def get_areas_ward(I, s_c, s):
+    eta = s_c / s
+    mu4 = eta * np.cos(I) / (1 - eta * np.sin(I))
+    q4 = -np.arccos(mu4)
+
+    # WH2004 eq 11-13
+    z0 = eta * np.cos(I)
+    chi = np.sqrt(-np.tan(q4)**3 / np.tan(I) - 1)
+    rho = chi * np.sin(q4)**2 * np.cos(q4) / (
+        chi**2 * np.cos(q4)**2 + 1)
+    T = 2 * chi * np.cos(q4) / (
+        chi**2 * np.cos(q4)**2 - 1)
+    A2 = 8 * rho + 4 * np.arctan(T) - 8 * z0 * np.arctan(1 / chi)
+    A1 = 2 * np.pi * (1 - z0) - A2 / 2
+    A3 = 2 * np.pi * (1 + z0) - A2 / 2
+    return A1, A2, A3

### 2020-02-05 writeups/Su_weak_tides.tex
overplot the inside-separatrix probability
add a bit to draft

@@
 The equations of motion in the absence of dissipation are:
+\begin{align}
+    \rd{\hat{s}}{t}
+        &= \omega_{s1}\p{\hat{s} \cdot \hat{l}_1}\p{\hat{s} \times \hat{l}_1}
+            - \omega_{1p}\cos I\p{\hat{s} \times \hat{l}_p},\\
+    \omega_{s1} &= \frac{3k_q}{2k}\frac{M_*}{m_1}\p{\frac{R_1}{a_1}}^3 s,\\
+    \omega_{1p} &= \frac{3m_p}{4m_*}\p{\frac{a_1}{a_p\sqrt{1 - e_p^2}}}^3 \Omega_1.
+\end{align}
 
 We define $s_c$ to be the critical spin where the precession frequencies
-$\omega_{s1}$ and $\omega_{21}$ are equal, or:
-
-Throughout this paper, we often set the orbital frequency of the inner planet
+$\omega_{s1}$ and $\omega_{1p}$ are equal, or
+\begin{equation}
+    \at{\omega_{s1}}_{s = s_c} = \omega_{1p}\cos I.
+\end{equation}
+rhroughout this paper, we often set the orbital frequency of the inner planet
 $\Omega_1 = 1$.
@@
 \begin{equation}
-    \eta = s_c / s.
+    \eta \equiv -\frac{g}{\alpha} = s_c / s.
 \end{equation}
 
-Plots of CS locations as always.
+Plots of CS locations as always in \autoref{fig:cs_locs}.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/99_misc/2_cs_locs.png}
+    \caption{CS locations, TODO change axis labels etc.}\label{fig:cs_locs}
+\end{figure}
 
@@
 exhibit Hamiltonian:
+\begin{equation}
+    H(\mu, \phi; s) = -\frac{s}{s_c}\frac{\mu^2}{2}
+        + \mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi.
+\end{equation}
 
-Plot of level curves of Hamiltonian, including $\mathcal{C}_{\pm}$ notation.
+Plot of level curves of Hamiltonian as before, including $\mathcal{C}_{\pm}$
+notation in \autoref{fig:1contours}.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/0_eta/1contours.png}
+    \caption{TODO label $\mathcal{C}_{\pm}$.}\label{fig:1contours}
+\end{figure}
 
@@
 become:
+\begin{align}
+    \rd{\hat{s}}{\tau}
+        &= \frac{s}{s_c}\p{\hat{s} \cdot \hat{l}_1}\p{\hat{s} \times
+                \hat{l}_1} - \hat{s} \times \hat{l}_p
+            + \frac{\epsilon 2\Omega_1}{s}
+                \p{1 - \frac{s}{2\Omega_1}\p{\hat{l}_1 \cdot \hat{s}}}
+                    \hat{s} \times \p{\hat{l}_1 \times \hat{s}},\\
+    \rd{s}{\tau}
+        &= \epsilon 2\Omega_1 \p{\hat{s} \cdot \hat{l}_1 -
+            \frac{s}{2\Omega_1}\p{1 + \p{\hat{s} \cdot \hat{l}_1}^2}}.
+\end{align}
 
@@
 Fig.~\ref{fig:quiver}.
-\begin{figure}[t]
+\begin{figure}
     \centering
@@
 \end{figure}
-
-TODO overplot CS1, CS2 for \emph{two} values of $s_c$. TODO show on plot the location
-where tides are so strong that CS2 ecomes unstable (is the only
-$\epsilon$-dependent result of the paper).
 
@@
 these generalized equilibria \emph{tidal Cassini States} (tCS), and number them
-tCS1 and tCS2 depending on whether they are CS1 or CS2 states.
+tCS1 and tCS2 depending on whether they are CS1 or CS2 states. Shown
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/6equils0_06.png}
+    \caption{Location of tCS\@. Vertical line is spin rate below which tCS is
+    destroyed.}\label{fig:6equils}
+\end{figure}
 
-Furthermore, if tides are too strong (large $\epsilon$), CS2 can become
-unstable (cite Fabrycky). This can be quantified as:
+Furthermore, if tides are too strong (large $\epsilon$), tCS2 can become
+unstable (cite Fabrycky). The required $\epsilon$ for stability of tCS2 is given
+by
+\begin{equation}
+    \epsilon \leq \frac{\eta_2 \sin I}{1 - \mu_2^2},
+\end{equation}
+where $\eta_2$ and $\mu_2$ are evaluated at tCS2.
 
@@
 histograms in Figs.~\ref{fig:Hhists_0_06,fig:Hhists_0_20,fig:Hhists_0_70}
-\begin{figure}[t]
+\begin{figure}
     \centering
@@
 \end{figure}
-\begin{figure}[t]
+\begin{figure}
     \centering
@@
 in Figs.~\ref{fig:pc_fits_0_06,fig:pc_fits_0_20,fig:pc_fits_0_70}.
-\begin{figure}[t]
+\begin{figure}
     \centering
     \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_06_5.png}
-    \caption{$s_c = 0.06$ fit to histogram.}\label{fig:pc_fits_0_06}
+    \caption{$s_c = 0.06$ prediction vs histogram.}\label{fig:pc_fits_0_06}
 \end{figure}
-\begin{figure}[t]
+\begin{figure}
     \centering
     \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_20_5.png}
-    \caption{$s_c = 0.20$ fit to histogram.}\label{fig:pc_fits_0_20}
+    \caption{$s_c = 0.20$ prediction vs histogram.}\label{fig:pc_fits_0_20}
 \end{figure}
-\begin{figure}[t]
+\begin{figure}
     \centering
     \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_70_5.png}
-    \caption{$s_c = 0.70$ fit to histogram.}\label{fig:pc_fits_0_70}
+    \caption{$s_c = 0.70$ prediction vs histogram.}\label{fig:pc_fits_0_70}
 \end{figure}
@@
 is shown below for $I = 5^\circ$
-\begin{figure}[t]
+\begin{figure}
     \centering
     \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5probs_5.png}
-    \caption{Total probabilities of ending up in either tCS and their ossicated
-    final obliquities.}\label{fig:probs}
+    \caption{Top: total probability of ending up in tCS2 (blue dots) and the
+    prediction ignoring separatrix capture (red line). Bottom:
+    obliquities of the tCSs.}\label{fig:probs}
 \end{figure}
@@
 
-\subsection{Example: Constant $s$}
+\subsubsection{Example: Constant $s$}
 
@@
 Section~\ref{sss:Melnikov}.
+
+\subsubsection{Combined Result}
+
+Thus, the natural extension of the two above results should be
+\begin{align}
+    \Delta_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}\;\mathrm{d}t,\\
+        &= \oint_{\mathcal{C}_{\pm}}
+            \dot{\mu}^{(1)} + \frac{\dot{s}^{(1)}}{\dot{\phi}^{(0)}}
+                \p{\pd{H}{s} - \pd{H_4}{s}}\;\mathrm{d}\phi.
+\end{align}
 
@@
 Section~\ref{app:sep_crossing_dynamics}. The key result is that one integrates
-
-% $\Delta_{\pm}$ equation
-
-The capture probabilities are then
-
-% $P_c = \Delta \pm \dots$
+\begin{equation}
+    \rd{(\Delta H)}{(\epsilon t)} \approx
+            (1 - \mu^2)\p{\frac{2\Omega}{s} - \mu}
+                \dot{\phi}^{(0)} + 2\Omega\p{1 + \frac{s}{2\Omega}(1 + \mu^2)}
+                \s{\frac{\mu^2}{2s_c} - \frac{s_c}{2s^2}\cos^2 I}.
+\end{equation}
 
 An analytical form that holds when $s \gg s_c$ is:
-
-% ugly approximate form
+\begin{align}
+    \frac{\Delta_{\pm}}{\epsilon} ={}&
+        -2\cos I\p{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
+        \pm 2\pi s\cos I
+        + \eta \cos I \p{-8\sqrt{\sin I / \eta}}
+            + \frac{s}{2}8\sqrt{\sin I/\eta}\nonumber\\
+        &+ \frac{2\Omega}{s}\p{\mp 2\pi\p{1 - 2\eta \sin I}
+            + 16\cos I \eta^{3/2}\sqrt{\sin I}}
+            + 8\sqrt{\eta \sin I}
+            \pm 2 \pi \eta \cos I
+            - \frac{64}{3} \p{\eta \sin I}^{3/2}.
+\end{align}
+The capture probability is then just
+\begin{equation}
+    P_c = \frac{\Delta_+ + \Delta_-}{\Delta_-}.
+\end{equation}
 

### 2020-02-17 writeups/Su_disk_disp.tex
Forgot to check in work at home, this updates through end of S2

@@
 
+The Hamiltonian (in the rotating frame) of the system is
+\begin{align}
+    \mathcal{H} &= -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
+            + \eta \p{\hat{s} \cdot \hat{l}_{\rm d}}\label{eq:H}\nonumber\\
+        &= -\frac{1}{2}\cos^2\theta
+            + \eta \p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
+\end{align}
+Trajectories in the phase space $\p{\phi, \cos \theta}$ satisfy $H = $ constant
+(see Fig.~\autoref{fig:eq_1contours}).
+
 When $\eta < \eta_{\rm c}$, CS4 exists and is a saddle point. The two
@@
 referred to as the \emph{separatrix} and divide phase space into three zones. In
-Eq.~\eqref{fig:eq_1contours}, we show the separatrix, the three zones, and their
-relations to the CSs via a contour plot of the Hamiltonian of the system
-\begin{align}
-    \mathcal{H} &= -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
-            + \eta \p{\hat{s} \cdot \hat{l}_{\rm d}},\label{eq:H}\\
-        &= -\frac{1}{2}\cos^2\theta
-            + \eta \p*{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
-\end{align}
-Note that trajectories in zone $II$ librate about CS2 while those in zones
-$I$ and $III$ circulate.
+Fig.~\ref{fig:eq_1contours}, we show the separatrix, the three zones, and their
+relations to the CSs. Note that trajectories in zone II librate about CS2
+while those in zones I and III circulate.
 \begin{figure*}
@@
     \includegraphics[width=0.8\textwidth]{../initial/0_eta/1contours_flip.png}
-    \caption{Contour plot of $\mathcal{H}\p{\phi, \cos \theta}$ as given in
-    Eq.~\eqref{eq:H}, where warmer colors denote more positive values. The black
-    solid line is the separatrix, which only exists for $\eta < \eta_{\rm c}$.
-    The three zones, divided by the separatrix, are labeled. The Cassini states
-    are labeled and have the same colors as in Fig.~\ref{fig:cs_locs}. The
-    interior of the separatrix, shaded in grey, is formally only defined for
-    $\eta < \eta_{\rm c}$, but we may identify the points in phase space that
-    flow into zone $II$ when evolved forward in time (decreasing $\eta$
-    adiabatically); this is the shaded region in the top left panel, bounded by
-    the black dotted line.}\label{fig:eq_1contours}
+    \caption{Level curves plot of $\mathcal{H}\p{\phi, \cos \theta}$
+    (Eq.~\eqref{eq:H}) for $I = 5^\circ$, where warmer colors denote more
+    positive values. The black solid line is the separatrix, which only exists
+    for $\eta < \eta_{\rm c} = 0.766$. The three zones (I, II, III), divided by
+    the separatrix, are labeled. The Cassini states are denoted by filled
+    circles and have the same colors as in Fig.~\ref{fig:cs_locs}. The interior
+    of the separatrix, shaded in grey, is formally only defined for $\eta <
+    \eta_{\rm c}$, but we may identify the points in phase space that flow into
+    zone II when evolved forward in time (decreasing $\eta$ adiabatically); this
+    is the shaded region in the top left panel, bounded by the black dotted
+    line.}\label{fig:eq_1contours}
 \end{figure*}
 
-The unsigned areas $\p{\abs{\int \cos \theta \;\mathrm{d}\phi}}$ of the three
-zones can be computed analytically \citep{henrard1987,ward2004I}. Defining
+Since $\p*{\phi, \cos \theta}$ form a set of canonical variables, the integral
+$\oint \cos \theta\;\mathrm{d}\phi$ along a trajectory is an adiabatic invariant
+(see Section~\autoref{s:ad}). The unsigned areas $\p{\abs{\int \cos \theta
+\;\mathrm{d}\phi}}$ of the three zones (as defined in
+Fig.~\autoref{fig:eq_1contours}) can be computed analytically
+\citep{henrard1987,ward2004I}. Define
 \begin{subequations}
@@
         T &= 2\chi \frac{\cos \theta_4}{
-            \chi^2 \cos^2\theta_4 - 1},\\
+            \chi^2 \cos^2\theta_4 - 1}.
     \end{align}
 \end{subequations}
-the areas for $\eta < \eta_{\rm c}$ are given by
+The areas for $\eta < \eta_{\rm c}$ are given by
 \begin{subequations}\label{se:area_ward}
     \begin{align}
+        A_{\rm I} &= 2\pi\p{1 - z_0} - \frac{A_2}{2},\\
         A_{\rm II} &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
-        A_{\rm I} &= 2\pi\p{1 - z_0} - \frac{A_2}{2},\\
         A_{\rm III} &= 2\pi\p{1 + z_0} - \frac{A_2}{2}.
@@
 at $\eta = \eta_{\rm c}$, then identify $p$ with the zone it is in at $\eta_{\rm
-c}$. Since phase space area is conserved under adiabatic evolution, this implies
-$A_{\rm i}\p{\eta > \eta_{\rm c}} = A_{\rm i}(\eta_{\rm c})$. The boundary between these
-extended zones is denoted by the dashed black line in the top left panel of
-Fig.~\ref{fig:eq_1contours}, where otherwise no separatrix exists.
+c}$. Since phase space area is conserved under adiabatic evolution, this
+extension implies $A_{\rm i}\p{\eta > \eta_{\rm c}} = A_{\rm i}(\eta_{\rm c})$.
+The boundary between these extended zones is denoted by the dashed black line in
+the top left panel of Fig.~\ref{fig:eq_1contours}, where otherwise no separatrix
+exists.
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{../initial/99_misc/1_areas.png}
-    \caption{Plot of fractional areas of each of the zones $A_{\rm i}(\eta) /
-    4\pi$ as given by Eqs.~\eqref{se:area_ward}. Dotted lines correspond to
-    small $\eta$ approximations discussed in Appendix~\ref{s:ad_approx}. Dashed
-    lines for $\eta > \eta_{\rm c}$ effective values of $A_{\rm II}, A_{\rm
-    III}$ for $\eta > \eta_{\rm c}$, denoting the area of points that would flow
-    into either area under adiabatic decrease of $\eta$ from $\eta > \eta_{\rm
-    c}$.}\label{fig:eq_areas}
+    \caption{Fractional areas of each of the zones $A_{\rm i}(\eta) /
+    4\pi$ as given by Eqs.~\eqref{se:area_ward}. The dotted lines correspond to
+    small $\eta$ approximations discussed in Appendix~\ref{s:ad_approx}. The
+    dashed lines for $\eta > \eta_{\rm c}$ are the effective values of $A_{\rm
+    II}, A_{\rm III}$ for $\eta > \eta_{\rm c}$, denoting the points that would
+    flow into either area under adiabatic decrease of $\eta$ from $\eta >
+    \eta_{\rm c}$. The vertical lines correspond to $\eta = \eta_{\rm c}$
+    (Eq.\eqref{eq:etac}) and the values of $\eta$ for which $A_{\rm II}$ is
+    maximized ($\eta_{\rm \max, II}$) and for which $A_{\rm III}$ is minimized
+    ($\eta_{\rm \min, III}$, Eq.~\eqref{eq:eta_minIII}).}\label{fig:eq_areas}
 \end{figure}
@@
 
-As a particular example, consider a system in zone $II$ in panel (d) of
-Fig.~\ref{fig:eq_1contours}. As $\eta$ decreases, zone $II$ will shrink while
-zones $I$ and $III$ will expand until the trajectory. Suppose the trajectory
-exits zone $II$ at some $\eta_\star$, then the probability of a $II \to I$
-transition is $\Pr\p{II \to I} = -\frac{\dot{A}_{\rm I}}{\dot{A}_{\rm II}}$,
-while a $II \to III$ transition occurs with probability $\Pr\p{II \to III} =
+As a particular example, consider a system in zone II in panel (d) of
+Fig.~\ref{fig:eq_1contours}. As $\eta decreases, zone II$ will shrink while
+zones I and III will expand until the trajectory. Suppose the trajectory
+exits zone II at some $\eta_\star$, then the probability of a II $\to$ I
+transition is $\Pr\p{\rm II \to I} = -\frac{\dot{A}_{\rm I}}{\dot{A}_{\rm II}}$,
+while a II $\to$ III transition occurs with probability $\Pr\p{\rm II \to III} =
 -\frac{\dot{A}_{\rm III}}{\dot{A}_{\rm II}}$.
@@
 separatrix encounters experienced. Initially, in the $\eta > \eta_{\rm c}$ regime,
-only zones $II, III$ exist. Conversely, at the end of the simulation when $\eta
-\to 0$, only zones $I, III$ exist. Most simply, one might expect four sequences
+only zones II and III exist. Conversely, at the end of the simulation when $\eta
+\to 0$, only zones I and III exist. Most simply, one might expect four sequences
 of transitions between zones (we call these dynamical ``tracks'') to manifest:
-from one of $\z{I, III}$ to one of $\z{II, III}$, where $III \to III$ is a
+from one of $\z{I, III}$ to one of $\z{II, III}$, where III $\to$ III is a
 trivial case (no separatrix encounter). In addition to these four tracks, a
-fifth track $III \to II \to I$ is observed. Below, we will describe the
+fifth track III $\to$ II $\to$ I is observed. Below, we will describe the
 evolution of $A$ throughout each of the five tracks, as well as determine the
@@
 \begin{enumerate}
-    \item $II \to I$ --- An example trajectory following this track is depicted
+    \item II $\to$ I --- An example trajectory following this track is depicted
         in Fig.~\ref{fig:ad_21}. $\hat{s}$ starts librating about CS2 in zone
-        $II$, enclosing some initial phase space area $A_{\rm i}$. The trajectory is
+        II, enclosing some initial phase space area $A_{\rm i}$. The trajectory is
         able to librate without separatrix encounter until $A_{\rm
         II}(\eta_\star) = A_{\rm i}$. As the trajectory transitions to a circulating
-        trajectory in zone $I$ immediately bordering the separatrix, it will
+        trajectory in zone I immediately bordering the separatrix, it will
         encompass $-A_{\rm I}(\eta_\star)$ phase space area. The final
@@
         everywhere, while $\pd{A_{\rm II}}{\eta} > 0$ at all possible
-        $\eta_\star$ for an initial condition starting in zone $II$, this track
+        $\eta_\star$ for an initial condition starting in zone II, this track
         always has nonzero probability.
 
-    \item $II \to III$ --- An example trajectory following this track is
+    \item II $\to$ III --- An example trajectory following this track is
         depicted in Fig.~\ref{fig:ad_23}. The only difference from the previous
         track is that, upon separatrix encounter, the trajectory follows the
-        circulating trajectory in zone $III$ bordering the separatrix, upon
+        circulating trajectory in zone III bordering the separatrix, upon
         which it will encompass $A_{\rm f} = A_{\rm I}(\eta_\star) + A_{\rm
@@
         \begin{equation}
-            \eta_{\min, III} \equiv \argmin A_{\rm III}(\eta),
+            \eta_{\min, III} \equiv \argmin A_{\rm III}(\eta)
+                \label{eq:eta_minIII},
         \end{equation}
         which is labeled in Fig.~\ref{fig:eq_areas}, then if $\eta_\star >
-        \eta_{\rm \min, III}$ then $\Pr_{\rm II \to III} < 0$. This is understood as a
-        forbidden transition, and so $II \to III$ is only a permitted dynamical
-        track if $\eta_\star <, \eta_{\rm \min, III}$.
-
-    \item $III \to I$ --- This track is depicted in Fig.~\ref{fig:ad_31}.
+        \eta_{\rm \min, III}$ then $\Pr_{\rm II \to III} < 0$. This is
+        understood as a forbidden transition, and so II $\to$ III is only a
+        permitted dynamical track if $\eta_\star <, \eta_{\rm \min, III}$.
+
+    \item III $\to$ I --- This track is depicted in Fig.~\ref{fig:ad_31}.
         The trajectory encounters the separatrix when $A_{\rm I}(\eta_\star) +
-        A_{\rm II}(\eta_\star) = A_{\rm i}$, upon which it transitions to a zone $I$
-        trajectory enclosing $A_{\rm f} = -A_{\rm I}$. Then, as always, the final
-        obliquity is given by Eq.~\eqref{eq:qfaf}.
+        A_{\rm II}(\eta_\star) = A_{\rm i}$, upon which it transitions to a zone
+        I trajectory enclosing $A_{\rm f} = -A_{\rm I}$. Then, as always, the
+        final obliquity is given by Eq.~\eqref{eq:qfaf}.
 
@@
         encounter the separatrix (if it is too large, it will never encounter
-        the separatrix, which is a $III \to III$ transition). This is written
+        the separatrix, which is a III $\to$ III transition). This is written
         $A_{\rm i} < \max A_{\rm I} + A_{\rm II} = 4\pi - \min A_{\rm III}$.
@@
 
-    \item $III \to II \to I$ --- This track is depicted in Fig.~\ref{fig:ad_321}.
-        The first separatrix encounter occurs at $\eta_1$ when $A_{\rm
-        I}(\eta_1) + A_{\rm II}(\eta_1) = A_{\rm i}$, upon which the trajectory moves
-        into zone $II$ enclosing intermediate phase space area $A_{\rm m} = A_{\rm
-        II}(\eta_1)$. Examining Fig.~\ref{fig:eq_areas}, there exist values $A$
-        for which $A_{\rm II}(\eta) = A$ has multiple solutions, and $\eta_1 >
-        \eta_{\rm II, \max}$ as labeled. These are the only values for which the
-        $III \to II \to I$ transition is permitted. Thus, as $\eta$ continues to
-        decrease, a second $\eta_2$ value exists for which $A_{\rm m} = A_{\rm
-        II}(\eta_2)$, upon which the trajectory is ejected to zone $I$ and $A_f
-        = -A_{\rm I}(\eta_2)$. The final obliquity again then obeys
+    \item III $\to$ II $\to$ I --- This track is depicted in
+        Fig.~\ref{fig:ad_321}. The first separatrix encounter occurs at $\eta_1$
+        when $A_{\rm I}(\eta_1) + A_{\rm II}(\eta_1) = A_{\rm i}$, upon which
+        the trajectory moves into zone II enclosing intermediate phase space
+        area $A_{\rm m} = A_{\rm II}(\eta_1)$. Examining
+        Fig.~\ref{fig:eq_areas}, there exist values $A$ for which $A_{\rm
+        II}(\eta) = A$ has multiple solutions, and $\eta_1 > \eta_{\rm II,
+        \max}$ as labeled. These are the only values for which the III $\to$ II
+        $\to$ I transition is permitted. Thus, as $\eta$ continues to decrease,
+        a second $\eta_2$ value exists for which $A_{\rm m} = A_{\rm
+        II}(\eta_2)$, upon which the trajectory is ejected to zone I and $A_f =
+        -A_{\rm I}(\eta_2)$. The final obliquity again then obeys
         Eq.~\eqref{eq:qfaf}.
 
-        Similar to the $III \to I$ track, the $III \to II \to I$ track can only
-        occur over the same $A_{\rm II}(\eta_{\rm c}) < A_{\rm i} < \max A_{\rm I} + A_{\rm
-        II}$ interval. The probability of encountering this track is set by the
-        initial $III \to II$ transition. It bears noting that this probability
-        is only nonnegative for a very small fraction of $A_{\rm i}$ values, since it
-        requires $\pd{A_{\rm II}}{\eta}$ and $\pd{A_{\rm III}}{\eta}$ to have
-        different signs; this occurs only if $A_{\rm II}\p{\eta_{\rm c}} <
-        A_{\rm i} <
-        A_{\rm II, \max}$. Outside of these bounds, $\Pr_{\rm III \to II} < 0$
-        which is interpreted again as a forbidden transition.
-
-        Then, once a $III \to II$ transition occurs, the second $II \to I$
+        Similar to the III $\to$ I track, the III $\to$ II $\to$ I track can
+        only occur over the same $A_{\rm II}(\eta_{\rm c}) < A_{\rm i} < \max
+        A_{\rm I} + A_{\rm II}$ interval. The probability of encountering this
+        track is set by the initial III $\to$ II transition. It bears noting
+        that this probability is only nonnegative for a very small fraction of
+        $A_{\rm i}$ values, since it requires $\pd{A_{\rm II}}{\eta}$ and
+        $\pd{A_{\rm III}}{\eta}$ to have different signs; this occurs only if
+        $A_{\rm II}\p{\eta_{\rm c}} < A_{\rm i} < A_{\rm II, \max}$. Outside of
+        these bounds, $\Pr_{\rm III \to II} < 0$ which is interpreted again as a
+        forbidden transition.
+
+        Then, once a III $\to$ II transition occurs, the second II $\to$ I
         transition occurs for some $\eta_2$ satisfying $A_{\rm II}(\eta_2) =
@@
         $\pd{A_{\rm II}}{\eta}$ has the same sign as $\pd{A_{\rm III}}{\eta}$
-        over all possible values, so the second $II \to I$ transition is
-        guaranteed, completing the $III \to II \to I$ track.
-
-    \item $III \to III$ --- This track depicts the trivial case where no
+        over all possible values, so the second II $\to$ I transition is
+        guaranteed, completing the III $\to$ II $\to$ I track.
+
+    \item III $\to$ III --- This track depicts the trivial case where no
         separatrix encounter ever occurs, and $A$ is constant throughout the
@@
         \theta_{\rm sd, i}$. This recovers the correct transfer function
-        $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for the $III \to III$ regime, as
+        $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for the III $\to$ III regime, as
         can be seen visibly in Fig.~\ref{fig:3_ensemble_20_35}.
@@
 \begin{enumerate}
-    \item $A_{\rm i} \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$ --- $II \to III,
-        II \to I$ both possible.
-
-    \item $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm \min, III}}, A_{\rm II}(\eta_{\rm c})}$
-        --- $II \to I$ only.
-
-    \item $A_{\rm i} \in \s{A_{\rm II}(\eta_{\rm c}), A_{\rm II, \max}}$ --- $III \to I, III
-        \to II \to I$ both possible.
-
-    \item $A_{\rm i} \in \s{A_{\rm II, \max}, \max A_{\rm I} + A_{\rm II}}$ --- $III
-        \to I$ only.
-
-    \item $A_{\rm i} > \max A_{\rm I} + A_{\rm II}$ --- $III \to III$ only.
+    \item $A_{\rm i} \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$ --- II $\to$
+        III and II $\to$ I both possible.
+
+    \item $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm \min, III}}, A_{\rm
+        II}(\eta_{\rm c})}$ --- II $\to$ I only.
+
+    \item $A_{\rm i} \in \s{A_{\rm II}(\eta_{\rm c}), A_{\rm II, \max}}$ ---
+        III $\to$ I and III $\to$ II $\to$ I both possible.
+
+    \item $A_{\rm i} \in \s{A_{\rm II, \max}, \max A_{\rm I} + A_{\rm II}}$ ---
+        III $\to$ I only.
+
+    \item $A_{\rm i} > \max A_{\rm I} + A_{\rm II}$ --- III $\to$ III only.
 \end{enumerate}
@@
 near the tracks predicted from adiabatic evolution. These scatters first set in
-for trajectories starting in zone $III$, as these cross the separatrix at higher
+for trajectories starting in zone III, as these cross the separatrix at higher
 values of $\theta$ and have a stricter adiabaticity criterion (see
@@
 
-The agreement of Eq.~\eqref{eq:nonad_q_f} at fixed $I$ for varying $\epsilon$ is
+The agreement of Eq.~\eqref{eq:nonad_q_f} at fixed I for varying $\epsilon$ is
 shown in Fig.~\ref{fig:nonad_3_scan}. Note that $\epsilon \to 0$ recovers the
@@
 analytic expressions for the final obliquities at small $\theta_{\rm sd, i}$ and
-associated probabilities for the $II \to I, II \to III$ tracks that are
+associated probabilities for the II $\to$ I and II $\to$ III tracks that are
 accessible.
@@
 This, in conjunction with Eq.~\eqref{eq:henrard_hop}, is sufficient to compute
-$\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for zone $II$ initial conditions.
+$\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for zone II initial conditions.
 
@@
 
-    \item Upon separatrix encounter, a transition to either zone $I$ or zone
-        $III$ occurs. These can be calculated to have associated probabilities
+    \item Upon separatrix encounter, a transition to either zone I or zone
+        III occurs. These can be calculated to have associated probabilities
         (using the approximate area Eq.~\eqref{eq:a_approx})
@@
 
-    \item Upon a transition to zone $I$ or zone $III$, the final obliquities can
+    \item Upon a transition to zone I or zone III, the final obliquities can
         be predicted by observing the final adiabatic invariant $A_{\rm f} = -A_{\rm
-        I}(\eta_\star)$ in the zone $I$ case and $A_{\rm f} = A_{\rm I}(\eta_\star) +
-        A_{\rm I}I(\eta_\star)$ in the zone $III$ case. As $\eta \to 0$, these
+        I}(\eta_\star)$ in the zone I case and $A_{\rm f} = A_{\rm I}(\eta_\star) +
+        A_{\rm I}I(\eta_\star)$ in the zone III case. As $\eta \to 0$, these
         correspond to obliquities

### 2020-02-17 initial/99_misc/1_areas.py

@@ -7,6 +7,7 @@ import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 plt.rc('text', usetex=True)
+plt.rc('lines', lw=3.0)
 plt.rc('font', family='serif', size=16)
 
 def plot_A_crit():
@@ -28,8 +29,7 @@ def plot_A_crit():
     ax2.set_ylabel(r'$\theta$')
 
     lns = l1 + l2
-    ax2.legend(lns, [l.get_label() for l in lns],
-               loc='upper left', fontsize=8)
+    ax2.legend(lns, [l.get_label() for l in lns], loc='upper left', fontsize=8)
     plt.savefig('1_Acrit.png', dpi=400)
     plt.clf()
 
@@ -65,18 +65,20 @@ def plot_areas(I=np.radians(5), filename='1_areas'):
     ax3 = ax1.twinx()
     ax4 = ax1.twiny()
     ax1.plot(eta, A1ys / (4 * np.pi), 'g:')
-    ax1.plot(eta, A1w / (4 * np.pi), 'g', label=r'$A_{I}$')
+    ax1.plot(eta, A1w / (4 * np.pi), 'g', label=r'$A_{\rm I}$')
     ax1.plot(eta, A2ys / (4 * np.pi), 'k:')
-    ax1.plot(eta, A2w / (4 * np.pi), 'k', label=r'$A_{II}$')
+    ax1.plot(eta, A2w / (4 * np.pi), 'k', label=r'$A_{\rm II}$')
     ax1.plot(eta, A3ys / (4 * np.pi), 'r:')
-    ax1.plot(eta, A3w / (4 * np.pi), 'r', label=r'$A_{III}$')
+    ax1.plot(eta, A3w / (4 * np.pi), 'r', label=r'$A_{\rm III}$')
 
     # dotted line continuation to show "analytic" continuation
     eta_cont = np.linspace(eta_c, 1.2 * eta_c, 21)
     ax1.plot(eta_cont, np.full_like(eta_cont, A1w[-1] / (4 * np.pi)), 'g--')
     ax1.plot(eta_cont, np.full_like(eta_cont, A2w[-1] / (4 * np.pi)), 'k--')
     ax1.plot(eta_cont, np.full_like(eta_cont, A3w[-1] / (4 * np.pi)), 'r--')
-    ax1.legend(loc='upper left')
+    xlims = ax1.get_xlim()
+    ax1.legend(loc='upper left', fontsize=14,
[…]

### 2020-02-17 writeups/Su_disk_disp.tex
recolor plots for clarity

@@
     \includegraphics[width=0.5\textwidth]{../initial/99_misc/1_areas.png}
-    \caption{Fractional areas of each of the zones $A_{\rm i}(\eta) /
-    4\pi$ as given by Eqs.~\eqref{se:area_ward}. The dotted lines correspond to
-    small $\eta$ approximations discussed in Appendix~\ref{s:ad_approx}. The
-    dashed lines for $\eta > \eta_{\rm c}$ are the effective values of $A_{\rm
-    II}, A_{\rm III}$ for $\eta > \eta_{\rm c}$, denoting the points that would
-    flow into either area under adiabatic decrease of $\eta$ from $\eta >
-    \eta_{\rm c}$. The vertical lines correspond to $\eta = \eta_{\rm c}$
-    (Eq.\eqref{eq:etac}) and the values of $\eta$ for which $A_{\rm II}$ is
-    maximized ($\eta_{\rm \max, II}$) and for which $A_{\rm III}$ is minimized
-    ($\eta_{\rm \min, III}$, Eq.~\eqref{eq:eta_minIII}).}\label{fig:eq_areas}
+    \caption{The solid lines show the fractional areas of each of the zones
+    $A_{\rm i}(\eta) / 4\pi$ as given by Eqs.~\eqref{se:area_ward}. The colored
+    dashed lines correspond to small $\eta$ approximations used in
+    Appendix~\ref{s:ad_approx}. The colored dashed lines for $\eta > \eta_{\rm
+    c}$ are the effective values of $A_{\rm II}, A_{\rm III}$ for $\eta >
+    \eta_{\rm c}$, denoting the points that would flow into either area under
+    adiabatic decrease of $\eta$ from $\eta > \eta_{\rm c}$. The vertical black
+    dashed lines correspond to $\eta = \eta_{\rm c}$ (Eq.\eqref{eq:etac}) and
+    the values of $\eta$ for which $A_{\rm II}$ is maximized ($\eta_{\rm \max,
+    II}$) and for which $A_{\rm III}$ is minimized ($\eta_{\rm \min, III}$,
+    Eq.~\eqref{eq:eta_minIII}). The horizontal black dashed line illustrates the
+    fraction of phase space occupied by zone II at separatrix appearance.
+    }\label{fig:eq_areas}
 \end{figure}

### 2020-02-17 initial/99_misc/1_areas.py

@@ -66,8 +66,8 @@ def plot_areas(I=np.radians(5), filename='1_areas'):
     ax4 = ax1.twiny()
     ax1.plot(eta, A1ys / (4 * np.pi), 'g:')
     ax1.plot(eta, A1w / (4 * np.pi), 'g', label=r'$A_{\rm I}$')
-    ax1.plot(eta, A2ys / (4 * np.pi), 'k:')
-    ax1.plot(eta, A2w / (4 * np.pi), 'k', label=r'$A_{\rm II}$')
+    ax1.plot(eta, A2ys / (4 * np.pi), 'b:')
+    ax1.plot(eta, A2w / (4 * np.pi), 'b', label=r'$A_{\rm II}$')
     ax1.plot(eta, A3ys / (4 * np.pi), 'r:')
     ax1.plot(eta, A3w / (4 * np.pi), 'r', label=r'$A_{\rm III}$')
 

### 2020-02-18 writeups/Su_disk_disp.tex
check in work from home that I forgot

@@
     \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
+    \newcommand*{\uv}[1]{\hat{\bm{#1}}}
     \newcommand*{\p}[1]{\left(#1\right)}
@@
 
-Much of this treatment parallels that of \citet{anderson2018teeter} and
-\citet{millholland_disk}. We consider a star of mass $M_\star$ hosting an oblate
-planet of mass $M_{\rm p}$, radius $R_{\rm p}$, at semimajor axis $a_{\rm p}$,
-and with spin angular frequency $\Omega_{\rm p}$, and a protoplanetary disk of
-mass $M_{\rm d}$ at some characteristic distance $r_{\rm d}$ from the host star
-\citep[see][for a power-law disk profile]{millholland_disk}. Denote $\hat{s}
-\equiv \bm{S} / S$ spin unit vector of planet, $\hat{l} \equiv \bm{L} / L$
-orbital angular momentum unit vector of planet, and $\hat{l}_{\rm d} \equiv
-\bm{L}_{\rm d} / L_{\rm d}$ angular momentum of the surrounding disc. We
-assume $S \ll L \ll L_{\rm d}$, so $\vec{l}_{\rm d}$ is approximately
-constant and $\vec{l}$ experiences negligible backreaction torque from
-$\hat{s}$. The equations of motion for $\hat{s}$, $\hat{l}$ and $\hat{l}_{\rm
-d}$ are
-\begin{align}
-    \rd{\hat{s}}{t} &= \omega_{\rm sl} \p{\hat{s} \cdot \hat{l}}
-            \p{\hat{s} \times \hat{l}}
-        \equiv \alpha \p{\hat{s} \cdot \hat{l}}
-            \p{\hat{s} \times \hat{l}},\label{eq:dsdt}\\
-    \rd{\hat{l}}{t} &= \omega_{\rm ld}\p{\hat{l} \cdot \hat{l}_{\rm d}}
-            \p{\hat{l} \times \hat{l}_{\rm d}}
-        \equiv -g\p{\hat{l} \times \hat{l}_{\rm d}},
+We consider a star of mass $M_\star$ hosting an oblate planet of mass $M_{\rm
+p}$, radius $R_{\rm p}$, at semimajor axis $a_{\rm p}$, and with spin angular
+frequency $\Omega_{\rm p}$, and a protoplanetary disk of mass $M_{\rm d}$. For
+simplicity, we treat the disk as a ring of radius $r_d$, but it is simple to
+generalize to a disk with finite extent \citep[see][]{millholland_disk}.
+Denote $\bm{S}$ the spin angular momentum and $\bm{L}$ the orbital angular
+momentum of the planet, and $\bm{L}_{\rm d}$ the angular momentum of the disk.
+The corresponding unit vectors are $\uv{s} \equiv \bm{S} / S$,
+$\uv{l} \equiv \bm{L} / L$, and $\uv{l}_{\rm d} \equiv \bm{L}_{\rm
+d} / L_d$.
+
+We assume $S \ll L \ll L_{\rm d}$, so $\uv{l}_{\rm d}$ is approximately
+constant and $\uv{l}$ experiences negligible backreaction torque from
+$\uv{s}$. The equations of motion for $\uv{s}$ and $\uv{l}$
+are
+\begin{align}
+    \rd{\uv{s}}{t} &= \omega_{\rm sl} \p{\uv{s} \cdot \uv{l}}
+            \p{\uv{s} \times \uv{l}}
+        \equiv \alpha \p{\uv{s} \cdot \uv{l}}
+            \p{\uv{s} \times \uv{l}},\label{eq:dsdt}\\
+    \rd{\uv{l}}{t} &= \omega_{\rm ld}\p{\uv{l} \cdot \uv{l}_{\rm d}}
+            \p{\uv{l} \times \uv{l}_{\rm d}}
+        \equiv -g\p{\uv{l} \times \uv{l}_{\rm d}},
             \label{eq:dldt}
@@
 \begin{align}
-    \theta &\equiv \arccos \hat{s} \cdot \hat{l},\\
-    \theta_{\rm sd} &\equiv \arccos \hat{s} \cdot \hat{l}_{\rm d},\\
-    I &\equiv \arccos \hat{l} \cdot \hat{l}_{\rm d}.
+    \theta &\equiv \arccos \p{\uv{s} \cdot \uv{l}},\\
+    \theta_{\rm sd} &\equiv \arccos \p{\uv{s} \cdot \uv{l}_{\rm d}},\\
+    I &\equiv \arccos \p{\uv{l} \cdot \uv{l}_{\rm d}}.
 \end{align}
 Following standard notation \citep[e.g.][]{colombo1966,peale1969,ward_jupiter},
-we have defined $\alpha \equiv \omega_{\rm sl}$ and $g = -\omega_{\rm ld}\cos
-I$.
-
-We can combine Eqs.~\eqref{eq:dsdt}--\eqref{eq:dldt} into a single equation by
-transforming into a frame rotating about $\hat{l}_{\rm d}$ with frequency $g$.
-In this frame, $\hat{l}_{\rm d}$ and $\hat{l}$ are fixed, and $\hat{s}$ evolves
-as:
-\begin{equation}
-    \at{\rd{\hat{s}}{t}}_{\rm rot} = \alpha \p{\hat{s} \cdot \hat{l}}
-            \p{\hat{s} \times \hat{l}}
-        + g\p{\hat{s} \times \hat{l}_{\rm d}}.\label{eq:dsdt_rot}
+we have defined $\alpha \equiv \omega_{\rm sl}$ and $g \equiv -\omega_{\rm
+ld}\cos I$.
+
+We can combine Eqs.~\eqref{eq:dsdt} and~\eqref{eq:dldt} into a single equation
+by transforming into a frame rotating about $\uv{l}_{\rm d}$ with
+frequency $(-g)$. In this frame, $\uv{l}_{\rm d}$ and $\uv{l}$ are fixed, and
+$\uv{s}$ evolves as:
+\begin{equation}
+    \p{\rd{\uv{s}}{t}}_{\rm rot} = \alpha \p{\uv{s} \cdot \uv{l}}
+            \p{\uv{s} \times \uv{l}}
+        + g\p{\uv{s} \times \uv{l}_{\rm d}}.\label{eq:dsdt_rot}
 \end{equation}
@@
 \begin{align}
-    \eta \equiv{}& -\frac{g}{\alpha}\label{eq:eta},\\
+    \eta \equiv{}& -\frac{g}{\alpha}\nonumber\\
         ={}& 3.75 \p{\frac{k_{\rm p}}{6k_{\rm qp}}}
             \p{\frac{m_{\rm p}}{0.001 M_\odot}}
-            \p{\frac{R_{\rm p}}{R_{\rm J}}}^{-3}
-        &\p{\frac{M_{\rm d}}{0.01 M_{\odot}}}
+            \p{\frac{R_{\rm p}}{R_{\rm J}}}^{-3}\nonumber\\
+        &\times \p{\frac{M_{\rm d}}{0.01 M_{\odot}}}
             \p{\frac{a_{\rm p}}{1\;\mathrm{AU}}}^{9/2}
@@
             \p{\frac{M_\star}{1M_{\odot}}}^{-3/2}
-            \cos I,\\
+            \cos I,\label{eq:eta}\\
     \tau \equiv{}& \alpha t.
 \end{align}
-Then Eq.~\eqref{eq:dsdt_rot} becomes
-\begin{equation}
-    \at{\rd{\hat{s}}{t}}_{\rm rot} = \p{\hat{s} \cdot \hat{l}}
-            \p{\hat{s} \times \hat{l}}
-        - \eta\p{\hat{s} \times \hat{l}_{\rm d}}. \label{eq:dsdt_base}
+In Eq.~\eqref{eq:eta}, we have introduced the fiducial values of variable
+parameters for the appciation considered in this paper. Eq.~\eqref{eq:dsdt_rot}
+then becomes
+\begin{equation}
+    \p{\rd{\uv{s}}{\tau}}_{\rm rot} = \p{\uv{s} \cdot \uv{l}}
+            \p{\uv{s} \times \uv{l}}
+        - \eta\p{\uv{s} \times \uv{l}_{\rm d}}. \label{eq:dsdt_base}
 \end{equation}
@@
 \end{equation}
-with $t_{\rm d}$ constant.
-
-Tihs implies $\rd{\eta}{t} = -\frac{\eta}{t_{\rm d}}$. In dimenisonless units,
-we have
+with $t_{\rm d}$ constant. This implies $\mathrm{d}\eta / \mathrm{d}t = -\eta /
+t_{\rm d}$. In dimensionless units, we have
 \begin{equation}
@@
             \p{\frac{a_{\rm p}}{1\;\mathrm{AU}}}^3\nonumber\\
-        &\p{\frac{R_{\rm p}}{R_{\rm J}}}^{-3}
+        &\times \p{\frac{R_{\rm p}}{R_{\rm J}}}^{-3}
             \p{\frac{\Omega_{\rm p}}{2\pi/\p{10\;\mathrm{days}}}}
@@
 
-In the next two subsections, we discuss and review the theoretical background
-relevant to our analysis of the evolution of the system.
+In the next two subsections, we summarize the theoretical background relevant to
+our analysis of the evolution of the system.
 
@@
 
-Spin states satisfying $\at{\rd{\hat{s}}{t}}_{\rm rot} = 0$ are referred to as
-\emph{Cassini States} (CSs). They require that $\hat{s}$, $\hat{l}$, and
-$\hat{l}_{\rm d}$ be coplanar. There are either two or four solutions, depending
-on the values of $\eta, I$. They are specified by the obliquity $\theta$ and the
-precessional phase of $\hat{s}$ around $\hat{l}$, denoted $\phi$. Following
-standard convention and nomenclature (see Fig.~\ref{fig:cs_locs}), CSs 1, 3, 4
-have $\phi = 0$ and $\theta < 0$, corresponding to $\hat{s}$ and $\hat{l}_{\rm
-d}$ being on opposite sides of $\hat{l}$, while CS2 has $\phi = \pi$ and $\theta
-> 0$, corresponding to $\hat{s}$ and $\hat{l}_{\rm d}$ being on the same side of
-$\hat{l}$. When $\eta < \eta_{\rm c}$, where
+Spin states satisfying $\p{\rd{\uv{s}}{t}}_{\rm rot} = 0$ are referred to as
+\emph{Cassini States} (CSs). They require that $\uv{s}$, $\uv{l}$, and
+$\uv{l}_{\rm d}$ be coplanar. There are either two or four CSs, depending
+on the values of $\eta$. They are specified by the obliquity $\theta$ and the
+precessional phase of $\uv{s}$ around $\uv{l}$, denoted by $\phi$. Following
+the standard convention and nomenclature (see Fig.~\ref{fig:cs_locs}), CSs 1, 3, 4
+have $\phi = 0$ and $\theta < 0$, corresponding to $\uv{s}$ and $\uv{l}_{\rm
+d}$ being on opposite sides of $\uv{l}$, while CS2 has $\phi = \pi$ and $\theta
+> 0$, corresponding to $\uv{s}$ and $\uv{l}_{\rm d}$ being on the same side of
+$\uv{l}$. When $\eta < \eta_{\rm c}$, where
 \begin{equation}
@@
     \includegraphics[width=0.5\textwidth]{../initial/99_misc/2_cs_locs.png}
-    \caption{Cassini state obliquities as a function of $\eta$ at $I = 5^\circ$.
-    Note that $\theta \in [-\pi, \pi]$ is the traditional definition of the
-    polar angle. The vertical dashed line indicates $\eta_{\rm c}$, where CS1
-    and CS4 merge and annihilate, and the horizontal dashed lines indicate
-    $\theta = I$ and $180^\circ - I$, the asymptotic behavior for CSs 2 and 3
-    for $\eta \gg \eta_{\rm c}$.}\label{fig:cs_locs}
+    \caption{Cassini state obliquities as a function of $\eta$ for $I =
+    5^\circ$. Note that $\theta \in [-\pi, \pi]$ is the traditional definition
+    of the polar angle. The vertical dashed line indicates $\eta_{\rm c}$ ($=
+    0.766$ for $I = 5^\circ$), where CS1 and CS4 merge and annihilate, and the
+    horizontal dashed lines indicate $\theta = I$ and $I - 180^\circ$, the
+    asymptotic values for CSs 2 and 3 for $\eta \gg \eta_{\rm
+    c}$.}\label{fig:cs_locs}
 \end{figure}
@@
 \begin{align}
-    \mathcal{H} &= -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
-            + \eta \p{\hat{s} \cdot \hat{l}_{\rm d}}\label{eq:H}\nonumber\\
+    \mathcal{H} &= -\frac{1}{2}\p{\uv{s} \cdot \uv{l}}^2
+            + \eta \p{\uv{s} \cdot \uv{l}_{\rm d}}\nonumber\\
         &= -\frac{1}{2}\cos^2\theta
-            + \eta \p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
+            + \eta \p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}
+                \label{eq:H}.
 \end{align}
@@
 decreases to $\eta_{\rm f} \ll 1$ (i.e.\ after the disk has dissipated to a
-negligible mass). Note that when $\eta_{\rm i} \gg 1$, $\hat{l}$ precesses
-around $\hat{l}_{\rm d}$ much faster than the spin-orbit precession
+negligible mass). Note that when $\eta_{\rm i} \gg 1$, $\uv{l}$ precesses
+around $\uv{l}_{\rm d}$ much faster than the spin-orbit precession
 ($\abs{\omega_{\rm ld}} \gg \abs{\omega_{\rm sl}}$), and the spin obliquity
@@
 sample $101$ values of $\theta_{\rm sd, i}$, and for each $\theta_{\rm sd, i}$
-value, we pick $101$ $\hat{s}$ approximately from the ring of initial conditions
-having angular distance $\theta_{\rm sd, i}$ to $\hat{l}_{\rm d}$%
+value, we pick $101$ $\uv{s}$ approximately from the ring of initial conditions
+having angular distance $\theta_{\rm sd, i}$ to $\uv{l}_{\rm d}$%
 %
@@
 The procedure we adopted for choosing initial conditions is the natural
-extension of this for finite $\eta_{\rm i}$. Note that the center of $\hat{s}$'s
+extension of this for finite $\eta_{\rm i}$. Note that the center of $\uv{s}$'s
 libration is CS2, which, since $\eta_{\rm i}$ is finite, is different than
-$\hat{l}_{\rm d}$. Furthermore, the libration is not exactly circular. Thus,
+$\uv{l}_{\rm d}$. Furthermore, the libration is not exactly circular. Thus,
 initial conditions on the circular ring of points having angular distance
-$\theta_{\rm sd, i}$ from $\hat{l}_{\rm d}$ do not lie \emph{exactly} along each
+$\theta_{\rm sd, i}$ from $\uv{l}_{\rm d}$ do not lie \emph{exactly} along each
 others' trajectories, and will each enclose slightly different initial phase
@@
 i}$ enclose the same initial $A_{\rm i}$. Note that as $\eta_{\rm i} \to
-\infty$, CS2 becomes coincident with $\hat{l}_{\rm d}$ and the libration cycle
+\infty$, CS2 becomes coincident with $\uv{l}_{\rm d}$ and the libration cycle
 becomes exactly circular, recovering the procedure given in the text.}.
@@
 and~\ref{eq:deta_dt} until $\eta$ reaches its final value $10^{-5}$. At such a
-small $\eta$, $\hat{s}$ is strongly coupled to $\hat{l}$ and the final obliquity
+small $\eta$, $\uv{s}$ is strongly coupled to $\uv{l}$ and the final obliquity
 $\theta_{rm f}$ is frozen. The mapping between $\theta_{\rm sd, i}$ and
@@
     \caption{Same as Fig.~\ref{fig:3_ensemble_10_35} but for $I = 20^\circ$.
-    % Note that the $III \to II \to I$ track is very short since the maximum
-    % $A_{\rm II}$ is very near $\eta_{\rm c}$ for $I = 20^\circ$. (not a
-    % clear/useful observation - yubo)
     }\label{fig:3_ensemble_20_35}
@@
 circulation cycle ($\phi$ advances to $\phi \pm 2\pi$). Note lastly that $A$ has
-simple physical interpretation of are enclosed on the unit sphere by $\hat{s}$
-over one cycle measured relative to $+\hat{z}$:
+simple physical interpretation of are enclosed on the unit sphere by $\uv{s}$
+over one cycle measured relative to $+\uv{z}$:
 \begin{equation}
@@
 
-Observe that when $\eta_{\rm i} \gg 1$, trajectories librate about $\hat{l}_{\rm d}$
+Observe that when $\eta_{\rm i} \gg 1$, trajectories librate about $\uv{l}_{\rm d}$
 with constant $\theta_{\rm sd}$, meaning they enclose initial phase space area
@@
 Complications arise when considering finite $\eta_{\rm i}$, as trajectories near CS2
-or CS3 librate about these equilibria respectively, rather than $\hat{l}_{\rm
+or CS3 librate about these equilibria respectively, rather than $\uv{l}_{\rm
 d}$, and Eq.~\eqref{eq:ai_qsd} is no longer exact. In practice,
@@
 
-Returning to the evolution of $\hat{s}$, we can classify trajectories by the
+Returning to the evolution of $\uv{s}$, we can classify trajectories by the
 separatrix encounters experienced. Initially, in the $\eta > \eta_{\rm c}$ regime,
@@
     \item II $\to$ I --- An example trajectory following this track is depicted
-        in Fig.~\ref{fig:ad_21}. $\hat{s}$ starts librating about CS2 in zone
-        II, enclosing some initial phase space area $A_{\rm i}$. The trajectory is
+        in Fig.~\ref{fig:ad_21}. $\uv{s}$ starts librating about CS2 in zone II,
+        enclosing some initial phase space area $A_{\rm i}$. The trajectory is
         able to librate without separatrix encounter until $A_{\rm
-        II}(\eta_\star) = A_{\rm i}$. As the trajectory transitions to a circulating
-        trajectory in zone I immediately bordering the separatrix, it will
-        encompass $-A_{\rm I}(\eta_\star)$ phase space area. The final
+        II}(\eta_\star) = A_{\rm i}$. As the trajectory transitions to a
+        circulating trajectory in zone I immediately bordering the separatrix,
+        it will encompass $-A_{\rm I}(\eta_\star)$ phase space area. The final
         $\theta_{\rm f}$ is then given by Eq.~\eqref{eq:qfaf}. An analytical
@@
 An intuitive guess at generalizing this assumes that any nonzero $\theta_{\rm
-sd, i}$ manifests as obliquity variations as $\hat{s}$ librates about
-$\hat{l}_{\rm d}$. These can be accounted for by simply allowing the final
+sd, i}$ manifests as obliquity variations as $\uv{s}$ librates about
+$\uv{l}_{\rm d}$. These can be accounted for by simply allowing the final
 obliquity to vary over the same range as the initial obliquity, or,
@@
 
-For analytical work, we adopt spherical coordinate system where $\hat{l} =
-\hat{z}$ and $\theta, \phi$ are the polar and azimuthal angle of $\hat{s}$. By
-convention, we choose $\hat{l}_{\rm z}$ at coordinates $\theta = I, \phi = \pi$.
+For analytical work, we adopt spherical coordinate system where $\uv{l} =
+\uv{z}$ and $\theta, \phi$ are the polar and azimuthal angle of $\uv{s}$. By
+convention, we choose $\uv{l}_{\rm z}$ at coordinates $\theta = I, \phi = \pi$.
 Note that $\p{\cos \theta, \phi}$ form a canonically conjugate pair of variables
-describing $\hat{s}$. To derive equations of motion for these canonical
+describing $\uv{s}$. To derive equations of motion for these canonical
 coordinates, we rewrite Eq.~\eqref{eq:H}
@@
     \item For a given $\theta_{\rm sd, i}$, we know that if $\eta \to \infty$
-        then the trajectory executes simple libration about $\hat{l}_{\rm d}$,
+        then the trajectory executes simple libration about $\uv{l}_{\rm d}$,
         and so $A = 2\pi\p{1 - \cos \theta_{\rm sd, i}} \approx \pi \theta_{\rm
@@
 We present a single result, the derivation of Eq.~\eqref{eq:nonad_q_f}. We take
-Eq.~\eqref{eq:dsdt_base} and choose coordinate axes such that $\hat{l} = \hat{z},
-\hat{l}_{\rm d} = \hat{z} \cos I + \hat{x}\sin I$, then we obtain
-\begin{equation}
-    \rd{\hat{s}}{t} = \s{
-        \p{\eta \cos I - 1}\hat{z} + \eta \sin I \hat{x}} \times \hat{s}.
+Eq.~\eqref{eq:dsdt_base} and choose coordinate axes such that $\uv{l} = \uv{z},
+\uv{l}_{\rm d} = \uv{z} \cos I + \uv{x}\sin I$, then we obtain
+\begin{equation}
+    \rd{\uv{s}}{t} = \s{
+        \p{\eta \cos I - 1}\uv{z} + \eta \sin I \uv{x}} \times \uv{s}.
 \end{equation}
@@
 Now, let's assume that $s_{\rm z} \approx \cos I$ throughout the evolution of
-$\hat{s}$ (note that $\theta_{\rm sd, i} = 0$ implies the initial $s_{\rm z} = \cos
+$\uv{s}$ (note that $\theta_{\rm sd, i} = 0$ implies the initial $s_{\rm z} = \cos
 I$). Then let's examine the evolution of quantity $S = s_{\rm x} + is_{\rm y}$ instead:
@@
 \begin{enumerate}
-    \item If the evolution of $\hat{s}$ is adiabatic, then it is invalid to
+    \item If the evolution of $\uv{s}$ is adiabatic, then it is invalid to
         assume $s_{\rm z}$ is approximately constant in time, as many
@@
         simply yields $\abs{S}\p{+\infty}$. This corresponds to the extreme
-        limit where $\eta$ changes so suddenly that $\hat{s}$ has no time to
+        limit where $\eta$ changes so suddenly that $\uv{s}$ has no time to
         respond and remains roughly unchanged as $\eta \to 0$. This is

### 2020-02-19 writeups/Su_disk_disp.tex
continued a small bit respond DL comments

@@
 
-\title[Analytical Exoplanet Obliquities]{Analytical Predictions of Explanet
+\title[Analytical Exoplanet Obliquities]{Analytical Predictions of Exoplanet
 Obliquities Generated by Planet-Disk Interactions}
@@
 Trajectories in the phase space $\p{\phi, \cos \theta}$ satisfy $H = $ constant
-(see Fig.~\autoref{fig:eq_1contours}).
+(see Fig.~\ref{fig:eq_1contours}).
 
@@
     \caption{Level curves plot of $\mathcal{H}\p{\phi, \cos \theta}$
-    (Eq.~\eqref{eq:H}) for $I = 5^\circ$, where warmer colors denote more
+    [Eq.~\eqref{eq:H}] for $I = 5^\circ$, where warmer colors denote more
     positive values. The black solid line is the separatrix, which only exists
@@
 
-Since $\p*{\phi, \cos \theta}$ form a set of canonical variables, the integral
+Since $\p{\phi, \cos \theta}$ form a set of canonical variables, the integral
 $\oint \cos \theta\;\mathrm{d}\phi$ along a trajectory is an adiabatic invariant
-(see Section~\autoref{s:ad}). The unsigned areas $\p{\abs{\int \cos \theta
+(see Section~\ref{s:ad}). The unsigned areas $\p{\abs{\int \cos \theta
 \;\mathrm{d}\phi}}$ of the three zones (as defined in
-Fig.~\autoref{fig:eq_1contours}) can be computed analytically
+Fig.~\ref{fig:eq_1contours}) can be computed analytically
 \citep{henrard1987,ward2004I}. Define
@@
     adiabatic decrease of $\eta$ from $\eta > \eta_{\rm c}$. The vertical black
-    dashed lines correspond to $\eta = \eta_{\rm c}$ (Eq.\eqref{eq:etac}) and
+    dashed lines correspond to $\eta = \eta_{\rm c}$ [Eq.\eqref{eq:etac}] and
     the values of $\eta$ for which $A_{\rm II}$ is maximized ($\eta_{\rm \max,
@@
 In this section, we study the evolution of the planetary obliquity $\theta$ when
-the parameter $\eta$ (or the disk mass $M_{\rm d}$; see Eq.~\eqref{eq:eta})
-decreases sufficiently slowly that the evolution is adiabatic. Strictly
-speaking, this requires the disk evolution timescale $t_{\rm d}$
-(Eq.~\eqref{eq:dmd_dt}) be much larger than all timesccales of the dynamical
-system governed by the Hamiltonian~\eqref{eq:H}. This is of course not possible
-in all cases, as the motion along the separatrix has an infinite period.
+the parameter $\eta$ (or the disk mass $M_{\rm d}$; see Eqs.~\eqref{eq:eta}
+and~\eqref{eq:deta_dt}) decreases sufficiently slowly that the evolution is
+adiabatic. Strictly speaking, this requires the disk evolution timescale $t_{\rm
+d}$ [Eq.~\eqref{eq:dmd_dt}] be much larger than all timesccales of the dynamical
+system governed by the Hamiltonian [Eq.~\eqref{eq:H}]. This is of course not
+possible in all cases, as the motion along the separatrix has an infinite
+period.
 
@@
 
-As is shown in Appendix~\ref{ss:eigens}, libration about CS2 is slower than that
+As shown in Appendix~\ref{ss:eigens}, libration about CS2 is slower than that
 about CS1 or CS3. As such, it is the slowest characteristic frequency in the
@@
 \omega_{\rm lib} / 2\pi$. In terms of the dimensionless parameter $\epsilon$
-(Eq.~\eqref{eq:eps_def}), this adiabaticity condition is
+[Eq.~\eqref{eq:eps_def}], this adiabaticity condition is
 \begin{equation}
@@
 \end{equation}
-where $\theta_2$ is the obliquity at CS2. This formula differs somewhat from
-that presented in \citet{millholland_disk}, where the $\csc^3\theta_2$ term is
-neglected and a square root is missing.
+where $\theta_2$ is the obliquity at CS2. This formula differs from that given
+in \citet{millholland_disk}, where the $\csc^3\theta_2$ term is neglected and
+the square root is missing.
 
 For $I = 5^\circ$, $\eta \sim \eta_{\rm c}$ Eq.~\eqref{eq:ad_constr} gives $\epsilon
-\lesssim 0.085$. Since our criterion is only a weak condition for adiabaticity,
+\lesssim 0.085$. Since our criterion is only a weak condition for diabaticity,
 we use $\epsilon = 3 \times 10^{-4}$ in our ``adiabatic'' simulations below
-(Section~\autoref{ss:ad_ensemble}). We explore the consequences of nonadiabatic
+(Section~\ref{ss:ad_ensemble}). We explore the consequences of nonadiabatic
 evolution in Section~\ref{s:nonad}.
@@
 ($\abs{\omega_{\rm ld}} \gg \abs{\omega_{\rm sl}}$), and the spin obliquity
-$\theta$ is not well defined. So it is more appropriate to use $\theta_{\rm sd}$
-rather than $\theta$ to specify the initial spin orientation.
-
-As discussed in Section~\ref{s:intro}, we explore $\theta_{\rm sd, i} \in [0,
-\pi]$. We choose $\epsilon = 3 \times 10^{-4}$ so that the system evolves almost
-adiabatically (see above).
+$\theta$ varies rapidly. So it is more appropriate to use $\theta_{\rm sd}$
+rather than $\theta$ to specify the initial spin orientation. We explore the
+entire range $\theta_{\rm sd, i} \in [0, \pi]$ and choose $\epsilon = 3 \times
+10^{-4}$ so that the system evolves almost adiabatically (see above).
 
@@
 sample $101$ values of $\theta_{\rm sd, i}$, and for each $\theta_{\rm sd, i}$
-value, we pick $101$ $\uv{s}$ approximately from the ring of initial conditions
-having angular distance $\theta_{\rm sd, i}$ to $\uv{l}_{\rm d}$%
+value, we pick $101$ orientations of $\uv{s}$ approximately from the ring of
+initial conditions having angular distance $\theta_{\rm sd, i}$ to $\uv{l}_{\rm
+d}$%
 %
-\footnote{
-The procedure we adopted for choosing initial conditions is the natural
-extension of this for finite $\eta_{\rm i}$. Note that the center of $\uv{s}$'s
-libration is CS2, which, since $\eta_{\rm i}$ is finite, is different than
-$\uv{l}_{\rm d}$. Furthermore, the libration is not exactly circular. Thus,
-initial conditions on the circular ring of points having angular distance
-$\theta_{\rm sd, i}$ from $\uv{l}_{\rm d}$ do not lie \emph{exactly} along each
-others' trajectories, and will each enclose slightly different initial phase
-space areas $A_{\rm i}$. Since our analytical theory assumes exact conservation
-of phase space area $A_{\rm i}$ derived from $\theta_{\rm sd, i}$ (see
-Section~\ref{ss:zone_transitions}), this discrepancy introduces an extra
+\footnote{The procedure we adopted for choosing the initial conditions is the
+natural extension of this for finite $\eta_{\rm i}$. Note that the center of
+libration of $\uv{s}$ is CS2, which, since $\eta_{\rm i}$ is finite, is
+different from $\uv{l}_{\rm d}$. Furthermore, the libration is not exactly
+circular. As a result, the libration trajectories for initial conditions on the
+circular ring of points having angular distance $\theta_{\rm sd, i}$ from
+$\uv{l}_{\rm d}$ are not the same and will each enclose slightly different
+initial phase space areas $A_{\rm i}$. Since our analytical theory assumes exact
+conservation of phase space area $A_{\rm i}$ derived from $\theta_{\rm sd, i}$
+(see Section~\ref{ss:zone_transitions}), this discrepancy introduces an extra
 deviation from the analytical prediction. To guarantee all points for a
@@
 initial conditions on the libration cycle going through $\p{\theta_2 +
-\theta_{\rm sd, i}, \phi_2}$ (where $\p{\theta_2, \phi_2}$ are the coordinates
-of CS2). This ensures that all initial conditions for a given $\theta_{\rm sd,
+\theta_{\rm sd, i}, \phi_2}$ [where $\p{\theta_2, \phi_2}$ are the coordinates
+of CS2]. This ensures that all initial conditions for a given $\theta_{\rm sd,
 i}$ enclose the same initial $A_{\rm i}$. Note that as $\eta_{\rm i} \to
@@
 To be concrete, we choose $\eta_{\rm i} = 10\eta_{\rm c}$ where $\eta_{\rm c}$
-is given by Eq.~\eqref{eq:etac} and evolve Equations~\ref{eq:dsdt_base}
-and~\ref{eq:deta_dt} until $\eta$ reaches its final value $10^{-5}$. At such a
+is given by Eq.~\eqref{eq:etac} and evolve Eqs.~\eqref{eq:dsdt_base}
+and~\eqref{eq:deta_dt} until $\eta$ reaches its final value $10^{-5}$. At such a
 small $\eta$, $\uv{s}$ is strongly coupled to $\uv{l}$ and the final obliquity
-$\theta_{rm f}$ is frozen. The mapping between $\theta_{\rm sd, i}$ and
+$\theta_{\rm f}$ is frozen. The mapping between $\theta_{\rm sd, i}$ and
 $\theta_{\rm f}$ is our primary result, and is shown for $I = 5^\circ, 10^\circ,
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_35.png}
-    \caption{Top: The final spin obliquity $\theta_{\rm f}$ as a function of the
-    initial spin-disk misalignment angle $\theta_{\rm sd, i}$ for systems
-    evolving from initial $\eta_{\rm i} \gg 1$ to $\eta_{\rm i} \ll 1$. The dots
-    are results of numerical calculations (Section~\ref{ss:ad_ensemble}), and
-    the colored tracks are semi-analytical results
-    (Section~\ref{ss:zone_transitions}). The black dotted lines represent
-    analytical approximations valid in the small-$\theta_{\rm sd, i}$ limit (see
-    Appendix~\ref{s:ad_approx}). Bottom: Where a particular $\theta_{\rm sd, i}$
-    corresponds to multiple tracks, the system evolves probabilistically.
-    The track that a particular system evolves along in a numerical simulation
-    can be measured by examining its final obliquity. The dots represent the
-    inferred probabilities from measured final obliquities in our simulations,
-    while the colored tracks denote the semi-analytic probability of the system
-    evolving along each track. There are five regimes of $\theta_{\rm sd, i}$
-    values for which different tracks are accessible. Semi-analytical
-    calculations of the boundaries of these regimes are denoted via the vertical
-    dashed black lines (see
-    Section~\ref{ss:zone_transitions}).}\label{fig:ad_ensemble}
+    \caption{Top: Shown are the final spin obliquity $\theta_{\rm f}$ as a
+    function of the initial spin-disk misalignment angle $\theta_{\rm sd, i}$
+    for systems evolving from initial $\eta_{\rm i} \gg 1$ to $\eta_{\rm f} \ll
+    1$. The blue dots are results of numerical calculations
+    (Section~\ref{ss:ad_ensemble}), and the colored tracks are semi-analytical
+    results (Section~\ref{ss:zone_transitions}). The black dotted lines
+    represent analytical approximations valid in the small-$\theta_{\rm sd, i}$
+    limit (see Appendix~\ref{s:ad_approx}). Bottom: Shown are the probabilities
+    of different outcomes. Where a particular $\theta_{\rm sd, i}$ corresponds
+    to multiple tracks, the system evolves probabilistically. The track that a
+    particular system evolves along in a numerical simulation can be measured by
+    examining its final obliquity. The dots represent the inferred probabilities
+    from measured final obliquities in our simulations, while the colored tracks
+    denote the semi-analytic probability of the system evolving along each
+    track. There are five regimes of $\theta_{\rm sd, i}$ values for which
+    different tracks are accessible. Semi-analytical calculations of the
+    boundaries of these regimes are denoted via the vertical dashed black lines
+    (see Section~\ref{ss:zone_transitions}).}\label{fig:ad_ensemble}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_10_35.png}
-    \caption{Same as Fig.~\ref{fig:ad_ensemble} but for $I =
+    \caption{Same as the top panel of Fig.~\ref{fig:ad_ensemble} but for $I =
     10^\circ$ and with fewer annotations.}\label{fig:3_ensemble_10_35}
@@
     \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_20_35.png}
-    \caption{Same as Fig.~\ref{fig:3_ensemble_10_35} but for $I = 20^\circ$.
-    }\label{fig:3_ensemble_20_35}
+    \caption{Same as the top panel of Fig.~\ref{fig:3_ensemble_10_35} but for $I
+    = 20^\circ$ and with fewer annotations.}\label{fig:3_ensemble_20_35}
 \end{figure}

### 2020-02-19 writeups/Su_disk_disp.tex
stash

@@
 
-\subsubsection{Governing Principles: Evolution of Enclosed Phase Space
+\subsubsection{Governing Principle: Evolution of Enclosed Phase Space
 Area}\label{sss:a_evo}
@@
 over time. In the absence of separatrix encounters, the enclosed phase space
-area $\oint \cos\theta \;\mathrm{d}\phi$ is an adiabatic invariant. In
-particular, we adopt convention where
+area $\oint \cos\theta \;\mathrm{d}\phi$ is an adiabatic invariant. We adopt
+convention where
 \begin{equation}
@@
 \end{equation}
-This definition of $A$ has the advantage of (i) being continuous at $\cos \theta
-= 1$, and (ii) being easily expressible as combinations of the $A_{\rm i}$ of
-Eqs.~\eqref{se:area_ward}. The bounds of the integral are either a libration
-($\phi$ returns to its original value with the same $\dot{q\phi}$ sign) or
-circulation cycle ($\phi$ advances to $\phi \pm 2\pi$). Note lastly that $A$ has
-simple physical interpretation of are enclosed on the unit sphere by $\uv{s}$
-over one cycle measured relative to $+\uv{z}$:
-\begin{equation}
-    \int \int\limits_{\cos \theta(\phi)}^1
-        \mathrm{d}\cos\theta\;\mathrm{d}\phi = \int \p{1 - \cos \theta(\phi)}
-            \;\mathrm{d}\phi.
-\end{equation}
-
-Observe that when $\eta_{\rm i} \gg 1$, trajectories librate about $\uv{l}_{\rm d}$
-with constant $\theta_{\rm sd}$, meaning they enclose initial phase space area
-\begin{equation}
-    A_{\rm i} \equiv \at{A}_{t = 0}
-        = 2\pi\p{1 - \cos \theta_{\rm sd, i}}.\label{eq:ai_qsd}
-\end{equation}
-Complications arise when considering finite $\eta_{\rm i}$, as trajectories near CS2
-or CS3 librate about these equilibria respectively, rather than $\uv{l}_{\rm
-d}$, and Eq.~\eqref{eq:ai_qsd} is no longer exact. In practice,
-Eq.~\eqref{eq:ai_qsd} holds very well when defining $\theta_{\rm sd, i}$ as the
-angular distance to CS2; an exception is discussed in Section~\ref{sss:evol_traj}.
+This definition of $A$ has the advantage of (i) being continuous across
+transitions from circulating to librating that cross the North pole
+($\cos \theta = 1$), and (ii) being easily expressible as combinations of the
+$A_{\rm i}$ of Eqs.~\eqref{se:area_ward}. The bounds of the integral are either
+a libration or circulation cycle. Note that when $\eta_{\rm i} \gg 1$,
+trajectories librate about $\uv{l}_{\rm d}$ with constant $\theta_{\rm sd}$,
+meaning they enclose initial phase space area
+\begin{equation}
+    A_{\rm i} = 2\pi\p{1 - \cos \theta_{\rm sd, i}}.\label{eq:ai_qsd}
+\end{equation}
+Complications arise when considering finite $\eta_{\rm i}$, as trajectories near
+CS2 or CS3 librate about these equilibria, rather than $\uv{l}_{\rm d}$, and
+Eq.~\eqref{eq:ai_qsd} is no longer exact. In practice, Eq.~\eqref{eq:ai_qsd}
+holds very well when defining $\theta_{\rm sd, i}$ as the angular distance to
+CS2; an exception is discussed in Section~\ref{sss:evol_traj}.
 

### 2020-02-20 writeups/Su_weak_tides.tex
stash dong feedback on weak tCS draft

@@
+% label C_\pm on fig 2
+% unify 3 & 4, choose consistent q/cos q
     \documentclass[
@@
 clear that the locations of these equilibria depend on the value of $s_c$. Call
-these generalized equilibria \emph{tidal Cassini States} (tCS), and number them
-tCS1 and tCS2 depending on whether they are CS1 or CS2 states. Shown
+these generalized equilibria \emph{tidal Cassini Equilibria} (tCE), and number
+them tCE1 and tCE2 depending on whether they are CS1 or CS2 states. Shown
 \begin{figure}
@@
     \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/6equils0_06.png}
-    \caption{Location of tCS\@. Vertical line is spin rate below which tCS is
+    \caption{Location of tCE\@. Vertical line is spin rate below which tCE is
     destroyed.}\label{fig:6equils}
@@
 
-Furthermore, if tides are too strong (large $\epsilon$), tCS2 can become
-unstable (cite Fabrycky). The required $\epsilon$ for stability of tCS2 is given
+Furthermore, if tides are too strong (large $\epsilon$), tCE2 can become
+unstable (cite Fabrycky). The required $\epsilon$ for stability of tCE2 is given
 by
@@
 \end{equation}
-where $\eta_2$ and $\mu_2$ are evaluated at tCS2.
+where $\eta_2$ and $\mu_2$ are evaluated at tCE2.
 
@@
 
-As a result of \autoref{ss:tidal_eqs}, the tCS are the only possible final
+As a result of \autoref{ss:tidal_eqs}, the tCE are the only possible final
 outcomes. We generate initial spin vectors $\hat{s}$ for isotropic initial
@@
     \caption{$s_c = 0.06$. Note that it is difficult to reach
-    tCS2.}\label{fig:Hhists_0_06}
+    tCE2.}\label{fig:Hhists_0_06}
 \end{figure}
@@
     \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
-    \caption{$s_c = 0.2$. Note that tCS2 is both reached with substantial
+    \caption{$s_c = 0.2$. Note that tCE2 is both reached with substantial
     probability and has substantial obliquity.}\label{fig:Hhists_0_20}
@@
     \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_60_5.png}
-    \caption{$s_c = 0.6$. Note that tCS2 becomes attracting over tCS1, but will
+    \caption{$s_c = 0.6$. Note that tCE2 becomes attracting over tCE1, but will
     have obliquity $\approx I$ and is uninteresting.}\label{fig:Hhists_0_70}
@@
 Assuming that $\hat{s}$ is drawn from an isotropic distribution, we may then
-calculate the probabilities of going to either tCS as a function of $s_c$. This
+calculate the probabilities of going to either tCE as a function of $s_c$. This
 is shown below for $I = 5^\circ$
@@
     \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5probs_5.png}
-    \caption{Top: total probability of ending up in tCS2 (blue dots) and the
+    \caption{Top: total probability of ending up in tCE2 (blue dots) and the
     prediction ignoring separatrix capture (red line). Bottom:
-    obliquities of the tCSs.}\label{fig:probs}
+    obliquities of the tCEs.}\label{fig:probs}
 \end{figure}
@@
 $\hat{s}$ are shown, in principle arbitrary distributions $P\p{\theta_i}$ can be
-convolved against the $P_{tCS2}\p{\theta_i}$ distributions shown in
+convolved against the $P_{tCE2}\p{\theta_i}$ distributions shown in
 \autoref{ss:q_dist}.

### 2020-02-20 initial/notes.tex
fix sign error, actually plot tidal breakdown criterion

@@
             \omega_{s1} &\sim \frac{GM_* J_2 m_1 R_1^2/a^3}{k_p m_1 R_1^2s},\\
-                &\sim \frac{k_{qp}}{k_p}\frac{M_*}{m_1} \p*{\frac{R_1}{a}}^3.
+                &\sim \frac{k_{qp}}{k_p}\frac{M_*}{m_1} \p*{\frac{R_1}{a}}^3s.
         \end{align}
@@
 $k_{qp} \sim 0.0467$ since $k_{qp} \frac{\Omega}{\sqrt{GM_p/R_p^3}} = J_2$.
-Consider again the precession frequencies
+Consider again the precession frequencies (we will take a hot Jupiter at
+$0.1\;\mathrm{AU}$ and a cold Earth at $1\;\mathrm{AU}$, roughly)
 \begin{align}
@@
             \p*{\frac{R_1}{a_1}}^3s,\\
-        &\approx 10\;\mathrm{yr^{-1}}
+        &\approx 0.062\;\mathrm{yr^{-1}}
             \p*{\frac{M_*/m_1}{300}}
-            \p*{\frac{5.5 k_{qp}}{k_p}}\p*{\frac{R_1}{2R_J}}^3
-                \p*{\frac{a_1}{0.05\;\mathrm{AU}}}^{-3}
-                \p*{\frac{s}{2\pi / 10\;\mathrm{hr}}},\\
-    \omega_{1p} &= \frac{3m_p}{4m_1} \frac{a_1}{a_p\p*{1 - e_p^2}} \Omega_1,\\
-        &\approx 0.0625\;\mathrm{yr^{-1}}
+            \p*{\frac{5.5 k_{qp}}{k_p}}\p*{\frac{R_1}{R_J}}^3
+                \p*{\frac{a_1}{0.1\;\mathrm{AU}}}^{-9/2}
+                \p*{\frac{s/\Omega_1}{10}},\\
+    \omega_{1p} &= \frac{3m_p}{4m_1} \p*{\frac{a_1}{a_p\p*{1 - e_p^2}}}^3
+            \Omega_1,\\
+        &\approx 0.0047\;\mathrm{yr^{-1}}
             \frac{m_p/m_1}{0.003}
-            \p*{\frac{a_1/a_p}{0.05}}
-            \frac{\Omega_1}{2\pi / 4\;\mathrm{days}}
-            \frac{1}{1 - e_p^2}.
-\end{align}
-Let's note that the effective initial $\eta = \frac{\omega_{1p}\cos
-I}{\omega_{s1}} \sim 0.006$. Furthermore, the smallest $\eta$ we can get at
-small final obliquities is just when $s = \Omega_1$, which is roughly a factor
-of $10$ increase so $\eta_f \sim 0.06$. Recall that $\eta = \frac{s_c}{s}
-\approx \frac{s_c}{\Omega_1}0.1$ since $\Omega_1/s \approx 0.1$, then $s_c
-\approx 0.06$ as well.
+            \p*{\frac{a_1/a_p}{0.1}}
+            \frac{\Omega_1}{2\pi / 11.54\;\mathrm{days}}
+            \frac{1}{\p*{1 - e_p^2}^3}.
+\end{align}
+Note then that $s_c$ is where $\omega_{s1} = \omega_{1p}$, which is satisfied
+for $s_c \approx 0.76$.
 
@@
 \begin{equation}
-    \eta_{\min} \equiv \frac{\sin I + \sqrt{\sin^2I
-        + 4\epsilon^2 \cos^2 I}}{2\epsilon \cos^2 I}.
+    \eta_{\min} \equiv \frac{-\sin I + \sqrt{\sin^2I
+            + 4\epsilon^2 \cos^2 I}}{2\epsilon \cos^2 I}
+        \approx \frac{2\epsilon^2 \cos^2 I / \sin^2 I}{
+            2\epsilon \cos^2 I}
+        = \frac{\epsilon}{\sin^2 I}.
 \end{equation}

### 2020-02-24 writeups/Su_disk_disp.tex
move most plots into writeup folder, almost finished Dong first pass

@@
+%TODO
+% rework 3->2->1 ??? part, probably also the 3 -> 3 part
+% Fig 7 caption lol
     \documentclass[
@@
     \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
+    \newcommand*{\pdil}[2]{\partial#1 / \partial#2}
     \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
@@
     \begin{align}
-        A_{\rm I} &= 2\pi\p{1 - z_0} - \frac{A_2}{2},\\
-        A_{\rm II} &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
-        A_{\rm III} &= 2\pi\p{1 + z_0} - \frac{A_2}{2}.
+        A_{\rm I} &= 2\pi\p{1 - z_0} - \frac{A_2}{2}, \label{eq:A1}\\
+        A_{\rm II} &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},
+            \label{eq:A2}\\
+        A_{\rm III} &= 2\pi\p{1 + z_0} - \frac{A_2}{2}\label{eq:A3}.
     \end{align}
@@
 Beginning at the last separatrix crossing, the final enclosed phase space area
-$A_{\rm f}$ will be conserved for all time. As $\eta \to 0$, trajectories circulate at
-constant obliquity $\theta_{\rm f}$, related to $A_{\rm f}$ by
+$A_{\rm f}$ will be conserved for all time. As $\eta \to 0$, trajectories
+circulate about $\hat{l}$ at constant obliquity $\theta_{\rm f}$, related to
+$A_{\rm f}$ by
 \begin{equation}
@@
 
-$A$ is not conserved when the trajectory encounters the separatrix. Howover, its
-change is easily understood \citep{henrard1982}. In essence, when the trajectory
-crosses the separatrix, it continues to evolve adjacent to the separatrix. So if
-a separatrix crossing results in a zone I trajectory, the resultant $A$ can be
-approximated by integrating Eq.~\eqref{eq:a_oint} along the upper leg of the
-separatrix. Pictorally, this can be seen in the bottom plots of
-Fig.~\ref{fig:ad_21}.
-
-\subsubsection{Governing Principles: Probabilistic Separatrix Crossing}
+The enclosed phase space area is not conserved when the trajectory encounters
+the separatrix. Howover, the change is easily understood \citep{henrard1982}. In
+essence, when the trajectory crosses the separatrix, it continues to evolve
+adjacent to the separatrix. So if a separatrix crossing results in a zone I
+trajectory (see Fig.~\ref{fig:eq_1contours}), the new area can be approximated
+by integrating Eq.~\eqref{eq:a_oint} along the upper leg of the separatrix.
+Pictorally, this can be seen in the bottom panels of Fig.~\ref{fig:ad_21}.
+
+\subsubsection{Governing Principle: Probabilistic Separatrix Crossing}
 
 When a trajectory experiences separatrix crossing, it transitions into nearby
-zones probabilistically. This process is well understood by
-\citealp{henrard1982,henrard1987}. Their results may be simply summarized as
-follows: if a zone $i$ is shrinking while adjacent zones $j, k$ are expanding
-such that the sum of their areas is constant, the probability of transition from
-zone $i$ to zone $j$ is given
-\begin{align}
-    \Pr\p{i \to j} = -\frac{\pd{A_{\rm j}}{t}}{ \pd{A_{\rm i}}{t}}
-        = -\frac{\pd{A_{\rm j}}{\eta}}{ \pd{A_{\rm i}}{\eta}},\\
-    \Pr\p{i \to k}
-        = -\frac{\pd{A_{\rm k}}{\eta}}{ \pd{A_{\rm i}}{\eta}}.\label{eq:henrard_hop}
-\end{align}
-Note that $\Pr \p{i \to j} + \Pr\p{i \to k} = 1$. This can be used directly in
-conjunction with Eqs.~\eqref{se:area_ward} to understand for what initial
-conditions each track can be observed and with what probabilities.
-
-As a particular example, consider a system in zone II in panel (d) of
+zones probabilistically. This process is studied by \citet{henrard1982} and
+\citet{henrard1987}. Their results may be summarized as follows: if zone $i$
+is shrinking while adjacent zones $j, k$ are expanding such that the sum of
+their areas is constant, the probabilities of transition from zone $i$ to zones
+$j$ and $k$ are given by
+\begin{subequations}\label{eq:henrard_hop}
+    \begin{align}
+        \Pr\p{i \to j} = -\frac{\pdil{A_{\rm j}}{\eta}}{\pdil{A_{\rm i}}{\eta}},
+                \\
+        \Pr\p{i \to k} = -\frac{\pdil{A_{\rm k}}{\eta}}{\pdil{A_{\rm i}}{\eta}}.
+    \end{align}
+\end{subequations}
+Note that $\Pr \p{i \to j} + \Pr\p{i \to k} = 1$.
+Eqs.~\eqref{eq:henrard_hop} can be used directly in conjunction with
+Eqs.~\eqref{se:area_ward} to understand for what initial conditions each track
+can be observed and with what probabilities.
+
+As an example, consider a system in zone II in panel (d) of
 Fig.~\ref{fig:eq_1contours}. As $\eta decreases, zone II$ will shrink while
-zones I and III will expand until the trajectory. Suppose the trajectory
-exits zone II at some $\eta_\star$, then the probability of a II $\to$ I
-transition is $\Pr\p{\rm II \to I} = -\frac{\dot{A}_{\rm I}}{\dot{A}_{\rm II}}$,
-while a II $\to$ III transition occurs with probability $\Pr\p{\rm II \to III} =
--\frac{\dot{A}_{\rm III}}{\dot{A}_{\rm II}}$.
+zones I and III will expand until the trajectory crosses the separatrix. Suppose
+the trajectory exits zone II at some $\eta_\star$, then the probability of the
+II $\to$ I transition is $\Pr\p{\rm II \to I} = -\dot{A}_{\rm I} / \dot{A}_{\rm
+II}$, while the II $\to$ III transition occurs with probability $\Pr\p{\rm II
+\to III} = -\dot{A}_{\rm III} / \dot{A}_{\rm II}$.
 
@@
 Returning to the evolution of $\uv{s}$, we can classify trajectories by the
-separatrix encounters experienced. Initially, in the $\eta > \eta_{\rm c}$ regime,
-only zones II and III exist. Conversely, at the end of the simulation when $\eta
-\to 0$, only zones I and III exist. Most simply, one might expect four sequences
-of transitions between zones (we call these dynamical ``tracks'') to manifest:
-from one of $\z{I, III}$ to one of $\z{II, III}$, where III $\to$ III is a
-trivial case (no separatrix encounter). In addition to these four tracks, a
-fifth track III $\to$ II $\to$ I is observed. Below, we will describe the
-evolution of $A$ throughout each of the five tracks, as well as determine the
-initial conditions and probabilities associated with each track:
+sequence of separatrix encounters. Initially, in the $\eta > \eta_{\rm c}$
+regime, only zones II and III exist; as $\eta \to 0$, only zones I and III exist
+(see Fig.~\ref{fig:eq_1contours}). There are five distinct evolutionary tracks:
 \begin{enumerate}
-    \item II $\to$ I --- An example trajectory following this track is depicted
-        in Fig.~\ref{fig:ad_21}. $\uv{s}$ starts librating about CS2 in zone II,
-        enclosing some initial phase space area $A_{\rm i}$. The trajectory is
-        able to librate without separatrix encounter until $A_{\rm
-        II}(\eta_\star) = A_{\rm i}$. As the trajectory transitions to a
+    \item II $\to$ I (see Fig.~\ref{fig:ad_21} for an example). The spin axis
+        $\uv{s}$ initially circulates in zone II (see a), and then starts
+        librating about CS2 as $\eta$ decreases (b), enclosing some initial
+        phase space area $A_{\rm i}$. This libration continues until the
+        separatrix expands (due to decreasing $\eta$) to ``touch'' the
+        trajectory (see c), at which $A_{\rm II}(\eta_\star) = A_{\rm i}$.
+        As $\hat{s}$ to a
         circulating trajectory in zone I immediately bordering the separatrix,
         it will encompass $-A_{\rm I}(\eta_\star)$ phase space area. The final
-        $\theta_{\rm f}$ is then given by Eq.~\eqref{eq:qfaf}. An analytical
-        approximation to $\theta_{\rm f}$ is derived in
-        Appendix~\ref{s:ad_approx} and is
-        \begin{equation}
-            \cos \theta_{\rm f, II \Rightarrow I} \approx
-                \p{\frac{\pi \theta_{\rm sp, i}^2}{16}}^2 \cot I
-                    + \frac{\theta_{\rm sp, i}^2}{4}.\label{eq:qf_21_approx}
-        \end{equation}
-
-        This transition can only occur when the initial condition begins in zone
-        II, requiring $A_{\rm i} < A_{\rm II}(\eta_{\rm c})$. Note $A_{\rm II}(\eta_{\rm c})$ is
-        given in closed form in \citet{ward2004I} but appears to be incorrect.
-        Then, at some known $\eta_\star$ satisfying $A_{\rm II}(\eta_\star) =
-        A_{\rm i}$, the trajectory is ejected from the separatrix following
-        Eq.~\eqref{eq:henrard_hop}. Note that since $\pd{A_{\rm i}}{\eta} < 0$
-        everywhere, while $\pd{A_{\rm II}}{\eta} > 0$ at all possible
-        $\eta_\star$ for an initial condition starting in zone II, this track
-        always has nonzero probability.
-
-    \item II $\to$ III --- An example trajectory following this track is
-        depicted in Fig.~\ref{fig:ad_23}. The only difference from the previous
-        track is that, upon separatrix encounter, the trajectory follows the
-        circulating trajectory in zone III bordering the separatrix, upon
-        which it will encompass $A_{\rm f} = A_{\rm I}(\eta_\star) + A_{\rm
-        II}(\eta_\star)$. The final obliquity is still given by
-        Eq.~\eqref{eq:qfaf}, and the analytical approximation derived in
-        Appendix~\ref{s:ad_approx} is
-        \begin{equation}
-            \cos \theta_{\rm f, II \Rightarrow III} \approx
-                \p{\frac{\pi \theta_{\rm sp, i}^2}{16}}^2 \cot I
-                    - \frac{\theta_{\rm sp, i}^2}{4}.\label{eq:qf_23_approx}
-        \end{equation}
-
-        Again, this track can only occur when $A_{\rm i} < A_{\rm II}(\eta_{\rm c})$, but a
-        further constraint arises when we consider the transition probability
-        given by Eq.~\eqref{eq:henrard_hop}. Upon examination of
-        Fig.~\ref{fig:eq_areas}, it is clear that $\pd{A_{\rm III}}{\eta} > 0$ for
-        many $\eta$. Call
+        obliquity $\theta_{\rm f}$ is then given by Eq.~\eqref{eq:qfaf}, with
+        $A_{\rm f} = -A_{\rm I}\p{\eta_\star}$. An analytical approximation to
+        $\theta_{\rm f}$ is derived in Appendix~\ref{s:ad_approx} and is
+        \begin{equation}
+            \p{\cos \theta_{\rm f}}_{\rm II \to I} \approx
+                \p{\frac{\pi \theta_{\rm sd, i}^2}{16}}^2 \cot I
+                    + \frac{\theta_{\rm sd, i}^2}{4}.\label{eq:qf_21_approx}
+        \end{equation}
+        The transition probability is
+        \begin{equation}
+            \Pr\p{\mathrm{II} \to \mathrm{I}} = -\p{
+                \frac{\pdil{A_{\rm I}}{\eta}}{\pdil{A_{\rm II}}{\eta}}}
+                    _{\eta = \eta_{\star}}.
+        \end{equation}
+
+        This track can only occur when the initial condition begins in zone II,
+        requiring $A_{\rm i} < A_{\rm II}(\eta_{\rm c})$, where
+        \begin{equation}
+            A_{\rm II}\p{\eta_c} = 4\pi\s{1 - \p{1 + \tan^{2/3}I}^{-3/2}},
+        \end{equation}
+        is given by Eq.~\eqref{eq:A2} evaluated at $\eta = \eta_c$
+        \citep{ward2004I}.
+
+        Also, note that since $\pdil{A_{\rm I}}{\eta} < 0$ everywhere, while
+        $\pdil{A_{\rm II}}{\eta} > 0$ at all possible $\eta_\star$ for an
+        initial condition starting in zone II, this track always has nonzero
+        probability.
+
+    \item II $\to$ III (see Fig.~\ref{fig:ad_23}) This track is similar to the
+        II $\to$ I track; the only difference is that, upon separatrix
+        encounter, the trajectory follows the circulating trajectory in zone III
+        bordering the separatrix, upon which it will encompass area $A_{\rm
+        I}(\eta_\star) + A_{\rm II}(\eta_\star) = A_{\rm f}$. The final
+        obliquity is still given by Eq.~\eqref{eq:qfaf}, and the analytical
+        approximation derived in Appendix~\ref{s:ad_approx} is
+        \begin{equation}
+            \p{\cos \theta_{\rm f}}_{\rm II \to III} \approx
+                \p{\frac{\pi \theta_{\rm sd, i}^2}{16}}^2 \cot I
+                    - \frac{\theta_{\rm sd, i}^2}{4}.\label{eq:qf_23_approx}
+        \end{equation}
+        The transition probability is
+        \begin{equation}
+            \Pr\p{\mathrm{II} \to \mathrm{III}} = -\p{
+                \frac{\pdil{A_{\rm III}}{\eta}}{\pdil{A_{\rm II}}{\eta}}}
+                    _{\eta = \eta_{\star}}.
+        \end{equation}
+
+        Again, this track can only occur when $A_{\rm i} < A_{\rm II}(\eta_{\rm
+        c})$, but a further constraint arises when we consider the transition
+        probability. Upon examination of Fig.~\ref{fig:eq_areas}, it is clear
+        that $\pd{A_{\rm III}}{\eta} > 0$ for a large range of $\eta$, which
+        would give a negative transition probability---implying a forbidden
+        transition. Define
         \begin{equation}
@@
         \end{equation}
-        which is labeled in Fig.~\ref{fig:eq_areas}, then if $\eta_\star >
-        \eta_{\rm \min, III}$ then $\Pr_{\rm II \to III} < 0$. This is
-        understood as a forbidden transition, and so II $\to$ III is only a
-        permitted dynamical track if $\eta_\star <, \eta_{\rm \min, III}$.
-
-    \item III $\to$ I --- This track is depicted in Fig.~\ref{fig:ad_31}.
-        The trajectory encounters the separatrix when $A_{\rm I}(\eta_\star) +
-        A_{\rm II}(\eta_\star) = A_{\rm i}$, upon which it transitions to a zone
-        I trajectory enclosing $A_{\rm f} = -A_{\rm I}$. Then, as always, the
-        final obliquity is given by Eq.~\eqref{eq:qfaf}.
-
-        This track can only occur if $A_{\rm i} > A_{\rm II}(\eta_{\rm c})$, but is also
-        constrained by requiring its $A_{\rm i}$ is sufficiently small it will
-        encounter the separatrix (if it is too large, it will never encounter
-        the separatrix, which is a III $\to$ III transition). This is written
-        $A_{\rm i} < \max A_{\rm I} + A_{\rm II} = 4\pi - \min A_{\rm III}$.
-
-        Note that since $\pd{A_{\rm I}}{\eta} < 0$ always while $\pd{A_{\rm
+        which is labeled in Fig.~\ref{fig:eq_areas}. Thus, the II $\to$ III
+        track is permitted only if $\eta_\star <, \eta_{\rm \min, III}$.
+
+    \item III $\to$ I (see Fig.~\ref{fig:ad_31}) The trajectory encounters the
+        separatrix when $A_{\rm I}(\eta_\star) + A_{\rm II}(\eta_\star) = A_{\rm
+        i}$, upon which it transitions to a zone I trajectory enclosing $A_{\rm
+        f} = -A_{\rm I}$. The final obliquity is again given by
+        Eq.~\eqref{eq:qfaf}.
+
+        This track can only occur if $A_{\rm i} > A_{\rm II}(\eta_{\rm c})$, but
+        is also constrained by requiring $A_{\rm i}$ be sufficiently small so
+        that it will encounter the separatrix (if $A_{\rm i}$ is too large, it
+        will never encounter the separatrix, and we simply have a III $\to$ III
+        transition). This condition is $A_{\rm i} < \max \p{A_{\rm I} + A_{\rm
+        II}} = 4\pi - \min \p{A_{\rm III}}$.
+
+        Note that since $\pdil{A_{\rm I}}{\eta} < 0$ while $\pdil{A_{\rm
         III}}{\eta} > 0$ for all accessible $\eta_{\star}$, this track is always
@@
 
-    \item III $\to$ II $\to$ I --- This track is depicted in
-        Fig.~\ref{fig:ad_321}. The first separatrix encounter occurs at $\eta_1$
-        when $A_{\rm I}(\eta_1) + A_{\rm II}(\eta_1) = A_{\rm i}$, upon which
-        the trajectory moves into zone II enclosing intermediate phase space
-        area $A_{\rm m} = A_{\rm II}(\eta_1)$. Examining
-        Fig.~\ref{fig:eq_areas}, there exist values $A$ for which $A_{\rm
-        II}(\eta) = A$ has multiple solutions, and $\eta_1 > \eta_{\rm II,
-        \max}$ as labeled. These are the only values for which the III $\to$ II
-        $\to$ I transition is permitted. Thus, as $\eta$ continues to decrease,
-        a second $\eta_2$ value exists for which $A_{\rm m} = A_{\rm
-        II}(\eta_2)$, upon which the trajectory is ejected to zone I and $A_f =
-        -A_{\rm I}(\eta_2)$. The final obliquity again then obeys
+    \item III $\to$ II $\to$ I (see Fig.~\ref{fig:ad_321}) The first separatrix
+        encounter occurs at $\eta_1$ when $A_{\rm I}(\eta_1) + A_{\rm
+        II}(\eta_1) = A_{\rm i}$, upon which the trajectory moves into zone II
+        enclosing intermediate phase space area $A_{\rm m} = A_{\rm
+        II}(\eta_1)$. Examining Fig.~\ref{fig:eq_areas}, there exist values $A$
+        for which $A_{\rm II}(\eta) = A$ has multiple solutions, and $\eta_1 >
+        \eta_{\rm II, \max}$ as labeled. These are the only values for which the
+        III $\to$ II $\to$ I transition is permitted. Thus, as $\eta$ continues
+        to decrease, a second $\eta_2$ value exists for which $A_{\rm m} =
+        A_{\rm II}(\eta_2)$, upon which the trajectory is ejected to zone I and
+        $A_f = -A_{\rm I}(\eta_2)$. The final obliquity again then obeys
         Eq.~\eqref{eq:qfaf}.
@@
     \item III $\to$ III --- This track depicts the trivial case where no
-        separatrix encounter ever occurs, and $A$ is constant throughout the
-        evolution. This constraint equates to $A_{\rm i} > \max A_{\rm I} + A_{\rm
-        II}$, whereupon no separatrix encounter occurs at all, and $A_{\rm f} =
-        A_{\rm i}$,
-        which for $\eta_{\rm i} \to \infty, \eta_{\rm f} \to 0$ results in $\theta =
-        \theta_{\rm sd, i}$.
+        separatrix encounter occurs, and $A$ is constant throughout the
+        evolution ($A_{\rm f} = A_{\rm i}$). This requires $A_{\rm i} > \max
+        \p{A_{\rm I} + A_{\rm II}}$. In the limit of $\eta_{\rm i} \to \infty$
+        and $ \eta_{\rm f} \to 0$ we have $\theta_{\rm f} = \theta_{\rm sd, i}$.
 
         Note that a small deviation from $\theta = \theta_{\rm sd, i}$ occurs
-        because we use finite $\eta_{\rm i}$, as hinted at in Section~\ref{sss:a_evo}.
-        This is because for $\theta_{\rm sd, i} \gtrsim \pi/2$, trajectories are
-        better described as librating about CS3. Nevertheless, we can still
-        approximate $A_{\rm i}$ to good accuracy as the solid angle enclosed by
-        libration about CS3 with polar angle $2\pi + \theta_3 - \theta_2 -
-        \theta_{\rm sd, i}$. This recovers the correct transfer function
-        $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for the III $\to$ III regime, as
-        can be seen visibly in Fig.~\ref{fig:3_ensemble_20_35}.
+        because we use finite $\eta_{\rm i}$, as hinted at in
+        Section~\ref{sss:a_evo}. This is because for $\theta_{\rm sd, i} \gtrsim
+        \pi/2$, trajectories are better described as librating about CS3.
+        Nevertheless, we can still approximate $A_{\rm i}$ to good accuracy as
+        the solid angle enclosed by libration about CS3 with polar angle $2\pi +
+        \theta_3 - \theta_2 - \theta_{\rm sd, i}$. This recovers the correct
+        transfer function $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for the III
+        $\to$ III regime, as can be seen visibly in
+        Fig.~\ref{fig:3_ensemble_20_35}.
 \end{enumerate}
-In summary, the five regimes of track possibilities in increasing order of
-$A_{\rm i}$
-are:
+In summary, starting from an initial condition with phase space area $A_{\rm i}$
+at $\eta = \eta_{\rm i} \gg 1$, the five evolutionary tracks are:
 \begin{enumerate}
-    \item $A_{\rm i} \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$ --- II $\to$
-        III and II $\to$ I both possible.
+    \item $A_{\rm i} \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$. Both the II
+        $\to$ III and the II $\to$ I tracks are possible.
 
     \item $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm \min, III}}, A_{\rm
-        II}(\eta_{\rm c})}$ --- II $\to$ I only.
-
-    \item $A_{\rm i} \in \s{A_{\rm II}(\eta_{\rm c}), A_{\rm II, \max}}$ ---
-        III $\to$ I and III $\to$ II $\to$ I both possible.
-
-    \item $A_{\rm i} \in \s{A_{\rm II, \max}, \max A_{\rm I} + A_{\rm II}}$ ---
-        III $\to$ I only.
-
-    \item $A_{\rm i} > \max A_{\rm I} + A_{\rm II}$ --- III $\to$ III only.
+        II}(\eta_{\rm c})}$. Only the II $\to$ I track.
+
+    \item $A_{\rm i} \in \s{A_{\rm II}(\eta_{\rm c}), A_{\rm II, \max}}$.
+        Both the III $\to$ I and III $\to$ II $\to$ I  are possible.
+
+    \item $A_{\rm i} \in \s{A_{\rm II, \max}, \max \p{A_{\rm I} + A_{\rm II}}}$.
+        Only the III $\to$ I track.
+
+    \item $A_{\rm i} > \max \p{A_{\rm I} + A_{\rm II}}$. Only the III $\to$ III
+        track.
 \end{enumerate}
-The corresponding ranges for for $\theta_{\rm sd,i}$ can be computed via
+In all cases, the corresponding ranges for $\theta_{\rm sd,i}$ can be computed via
 Eq.~\eqref{eq:ai_qsd}. The boundaries between these ranges are overplotted in
-Fig.~\ref{fig:ad_ensemble}, where they can be seen to agree well with numerical
-results.
+Fig.~\ref{fig:ad_ensemble}, where they can be seen to agree well with the
+numerical results.
 \begin{figure}
@@
 \end{equation}
-This, in conjunction with Eq.~\eqref{eq:henrard_hop}, is sufficient to compute
+This, in conjunction with Eqs.~\eqref{eq:henrard_hop}, is sufficient to compute
 $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for zone II initial conditions.

### 2020-02-24 initial/99_misc/2_rand_plots.py

@@ -7,6 +7,7 @@ import scipy.optimize as opt
 import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
+import matplotlib.patches as patches
 plt.rc('text', usetex=True)
 plt.rc('font', family='serif', size=20)
 LW=3.5
@@ -138,6 +139,77 @@ def plot_eigens(I=np.radians(5)):
     plt.savefig('2_lambdas.png', dpi=400)
     plt.clf()
 
+def plot_3vec():
+    ''' plots the relative orientations of the three vectors '''
+    offset = 0.02 # offset for text from arrow tip
+    alpha = 0.8
+
+    fig, ax = plt.subplots(1, 1, figsize=(6, 6))
+    plt.axis('off')
+    ax.set_xlim(0.2, 1.1)
+    ax.set_ylim(-0.1, 1.1)
+    def get_xy(angle):
+        return 1 - np.sin(np.radians(angle)), np.cos(np.radians(angle))
+
+    # central dot
+    ax.plot(1, 0, 'ko', ms=8, zorder=np.inf)
+    arrowprops = lambda c: {'fc': c, 'alpha': alpha, 'lw': 0,
+                            'width': 3, 'headwidth': 12}
+
+    # draw three arrows
+    l_xy = get_xy(0)
+    l_c = 'b'
+    ax.annotate('', xy=l_xy, xytext=(1, 0),
+                 arrowprops=arrowprops(l_c))
+    ax.text(l_xy[0] - offset / 3, l_xy[1] + offset, r'$\hat{\mathbf{l}}$',
+             fontdict={'c': l_c})
+
+    ld_q = 20
+    ld_xy = get_xy(ld_q)
+    ld_c = 'darkslategray'
+    ax.annotate('', xy=ld_xy, xytext=(1, 0),
+                 arrowprops=arrowprops(ld_c))
+    ax.text(ld_xy[0] - offset / 2, ld_xy[1] + offset,
+            r'$\hat{\mathbf{l}}_{\rm d}$', fontdict={'c': ld_c})
+
+    s_q = 50
+    s_xy = get_xy(s_q)
+    s_c = 'r'
+    ax.annotate('', xy=s_xy, xytext=(1, 0),
+                 arrowprops=arrowprops(s_c))
+    ax.text(s_xy[0] - offset, s_xy[1] + offset, r'$\hat{\mathbf{s}}$',
+             fontdict={'c': s_c})
+
[…]

### 2020-02-24 writeups/Su_disk_disp.tex
oops forgot to check in updated writeup

@@
         usenatbib,
-        referee,
+        % referee,
     ]{mnras}
@@
 
+% for i in ../initial/99_misc/2_3vec.png ../initial/99_misc/2_cs_locs.png ../initial/0_eta/1contours_flip.png ../initial/99_misc/1_areas.png ../initial/2_toy2/3_ensemble_05_35.png ../initial/2_toy2/3_ensemble_10_35.png ../initial/2_toy2/3_ensemble_20_35.png ../initial/2_toy2/3testo21.png ../initial/2_toy2/3testo21_subplots.png ../initial/2_toy2/3testo23.png ../initial/2_toy2/3testo23_subplots.png ../initial/2_toy2/3testo31.png ../initial/2_toy2/3testo31_subplots.png ../initial/2_toy2/3testo321.png ../initial/2_toy2/3testo321_subplots.png ../initial/2_toy2/3_ensemble_05_25.png ../initial/2_toy2/3_ensemble_05_15.png ../initial/2_toy2/3testo_nonad.png ../initial/2_toy2/3testo_nonad_subplots.png ../initial/2_toy2/3_ensemble_05_05.png ../initial/2_toy2/3scan.png ../initial/2_toy2/3scan_20.png ../initial/99_misc/2_lambdas.png; do cp $i plots_diskdisp; done
+
 \date{Accepted XXX\@. Received YYY\@; in original form ZZZ}
 
-\pubyear{2019}
+\pubyear{2020}
 
@@
 obliquities as a function of $\eta$ are shown in Fig.~\ref{fig:cs_locs}.
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{../initial/99_misc/2_cs_locs.png}
-    \caption{Cassini state obliquities as a function of $\eta$ for $I =
-    5^\circ$. Note that $\theta \in [-\pi, \pi]$ is the traditional definition
-    of the polar angle. The vertical dashed line indicates $\eta_{\rm c}$ ($=
-    0.766$ for $I = 5^\circ$), where CS1 and CS4 merge and annihilate, and the
-    horizontal dashed lines indicate $\theta = I$ and $I - 180^\circ$, the
-    asymptotic values for CSs 2 and 3 for $\eta \gg \eta_{\rm
-    c}$.}\label{fig:cs_locs}
-\end{figure}
+\begin{figure*}
+    \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_3vec.png}\hfil
+    %
+    \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_cs_locs.png}
+    \caption{Left: Definition of angles in the Cassini state configuration and
+    the adopted sign convention for $\theta$. Right: Cassini state obliquities
+    as a function of $\eta$ for $I = 5^\circ$, where $\theta \in [-\pi, \pi]$
+    is the traditional definition of the polar angle. The vertical dashed line
+    indicates $\eta_{\rm c}$ ($= 0.766$ for $I = 5^\circ$), where CS1 and CS4
+    merge and annihilate, and the horizontal dashed lines indicate $\theta = I$
+    and $I - 180^\circ$, the asymptotic values for CSs 2 and 3 for $\eta \gg
+    \eta_{\rm c}$.}\label{fig:cs_locs}
+\end{figure*}
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{../initial/0_eta/1contours_flip.png}
+    \includegraphics[width=0.8\textwidth]{plots_diskdisp/1contours_flip.png}
     \caption{Level curves plot of $\mathcal{H}\p{\phi, \cos \theta}$
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../initial/99_misc/1_areas.png}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/1_areas.png}
     \caption{The solid lines show the fractional areas of each of the zones
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_35.png}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_35.png}
     \caption{Top: Shown are the final spin obliquity $\theta_{\rm f}$ as a
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_10_35.png}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_10_35.png}
     \caption{Same as the top panel of Fig.~\ref{fig:ad_ensemble} but for $I =
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_20_35.png}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_20_35.png}
     \caption{Same as the top panel of Fig.~\ref{fig:3_ensemble_10_35} but for $I
@@
         \end{equation}
-
         This track can only occur when the initial condition begins in zone II,
-        requiring $A_{\rm i} < A_{\rm II}(\eta_{\rm c})$, where
-        \begin{equation}
-            A_{\rm II}\p{\eta_c} = 4\pi\s{1 - \p{1 + \tan^{2/3}I}^{-3/2}},
-        \end{equation}
-        is given by Eq.~\eqref{eq:A2} evaluated at $\eta = \eta_c$
-        \citep{ward2004I}.
-
-        Also, note that since $\pdil{A_{\rm I}}{\eta} < 0$ everywhere, while
+        requiring $A_{\rm i} < A_{\rm II}(\eta_{\rm c})$, where $A_{\rm
+        II}\p{\eta_c}$ is given by Eq.~\eqref{eq:A2} evaluated at $\eta =
+        \eta_c$. Note that since $\pdil{A_{\rm I}}{\eta} < 0$ everywhere, while
         $\pdil{A_{\rm II}}{\eta} > 0$ at all possible $\eta_\star$ for an
@@
     \item III $\to$ I (see Fig.~\ref{fig:ad_31}) The trajectory encounters the
-        separatrix when $A_{\rm I}(\eta_\star) + A_{\rm II}(\eta_\star) = A_{\rm
-        i}$, upon which it transitions to a zone I trajectory enclosing $A_{\rm
-        f} = -A_{\rm I}$. The final obliquity is again given by
+        separatrix when $A_{\rm I}(\eta_\star) + A_{\rm II}(\eta_\star) =
+        A_{\rm i}$, upon which it transitions to a zone I trajectory enclosing
+        $A_{\rm f} = -A_{\rm I}$. The final obliquity is again given by
         Eq.~\eqref{eq:qfaf}.
 
-        This track can only occur if $A_{\rm i} > A_{\rm II}(\eta_{\rm c})$, but
-        is also constrained by requiring $A_{\rm i}$ be sufficiently small so
-        that it will encounter the separatrix (if $A_{\rm i}$ is too large, it
-        will never encounter the separatrix, and we simply have a III $\to$ III
-        transition). This condition is $A_{\rm i} < \max \p{A_{\rm I} + A_{\rm
-        II}} = 4\pi - \min \p{A_{\rm III}}$.
+        This track can only occur if $A_{\rm i} > A_{\rm II}(\eta_{\rm c})$,
+        but is also constrained by requiring $A_{\rm i}$ be sufficiently small
+        so that it will encounter the separatrix (if $A_{\rm i}$ is too large,
+        it will never encounter the separatrix, and we simply have a III $\to$
+        III transition). This condition is $A_{\rm i} < \max \p{A_{\rm I} +
+        A_{\rm II}} = 4\pi - \min \p{A_{\rm III}}$.
 
         Note that since $\pdil{A_{\rm I}}{\eta} < 0$ while $\pdil{A_{\rm
-        III}}{\eta} > 0$ for all accessible $\eta_{\star}$, this track is always
-        permitted.
-
-    \item III $\to$ II $\to$ I (see Fig.~\ref{fig:ad_321}) The first separatrix
-        encounter occurs at $\eta_1$ when $A_{\rm I}(\eta_1) + A_{\rm
-        II}(\eta_1) = A_{\rm i}$, upon which the trajectory moves into zone II
-        enclosing intermediate phase space area $A_{\rm m} = A_{\rm
-        II}(\eta_1)$. Examining Fig.~\ref{fig:eq_areas}, there exist values $A$
-        for which $A_{\rm II}(\eta) = A$ has multiple solutions, and $\eta_1 >
-        \eta_{\rm II, \max}$ as labeled. These are the only values for which the
-        III $\to$ II $\to$ I transition is permitted. Thus, as $\eta$ continues
-        to decrease, a second $\eta_2$ value exists for which $A_{\rm m} =
-        A_{\rm II}(\eta_2)$, upon which the trajectory is ejected to zone I and
-        $A_f = -A_{\rm I}(\eta_2)$. The final obliquity again then obeys
-        Eq.~\eqref{eq:qfaf}.
-
-        Similar to the III $\to$ I track, the III $\to$ II $\to$ I track can
-        only occur over the same $A_{\rm II}(\eta_{\rm c}) < A_{\rm i} < \max
-        A_{\rm I} + A_{\rm II}$ interval. The probability of encountering this
-        track is set by the initial III $\to$ II transition. It bears noting
-        that this probability is only nonnegative for a very small fraction of
-        $A_{\rm i}$ values, since it requires $\pd{A_{\rm II}}{\eta}$ and
-        $\pd{A_{\rm III}}{\eta}$ to have different signs; this occurs only if
-        $A_{\rm II}\p{\eta_{\rm c}} < A_{\rm i} < A_{\rm II, \max}$. Outside of
-        these bounds, $\Pr_{\rm III \to II} < 0$ which is interpreted again as a
-        forbidden transition.
-
-        Then, once a III $\to$ II transition occurs, the second II $\to$ I
-        transition occurs for some $\eta_2$ satisfying $A_{\rm II}(\eta_2) =
-        A_{\rm II}(\eta_1), \eta_2 < \eta_1$. Graphical inspection shows that
-        $\pd{A_{\rm II}}{\eta}$ has the same sign as $\pd{A_{\rm III}}{\eta}$
-        over all possible values, so the second II $\to$ I transition is
-        guaranteed, completing the III $\to$ II $\to$ I track.
-
-    \item III $\to$ III --- This track depicts the trivial case where no
-        separatrix encounter occurs, and $A$ is constant throughout the
-        evolution ($A_{\rm f} = A_{\rm i}$). This requires $A_{\rm i} > \max
-        \p{A_{\rm I} + A_{\rm II}}$. In the limit of $\eta_{\rm i} \to \infty$
-        and $ \eta_{\rm f} \to 0$ we have $\theta_{\rm f} = \theta_{\rm sd, i}$.
+        III}}{\eta} > 0$ for all accessible $\eta_{\star}$, this track is
+        always permitted.
+
+    \item III $\to$ II $\to$ I (see Fig.~\ref{fig:ad_321}) That $A_{\rm II}
+        \p{\eta_c}$ is not monotonic is key to the existence of this track.
+        Consider a trajectory originating in zone III that first encounters the
+        separatrix at $\eta_1$, when $A_{\rm I}(\eta_1) + A_{\rm II}(\eta_1) =
+        A_{\rm i}$, such that it transitions into zone II enclosing
+        intermediate phase space area $A_{\rm m} = A_{\rm II}(\eta_1)$. Such a
+        transition has probability
+        \begin{equation}
+            \Pr\p{\rm III \to II} = -\p{
+                \frac{\pdil{A_{\rm II}}{\eta}}{\pdil{A_{\rm III}}{\eta}}}
+                    _{\eta = \eta_1},
+        \end{equation}
+        which is nonnegative (i.e.\ the transition is permitted) if $\eta_1
+        \in [\eta_{\rm \max, II}, \eta_c]$. Equivalently, this requires
+        $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm c}} , A_{\rm II, \max}}$.
+
+        Then, as $\eta$ continues to decrease, a second $\eta_2$ value exists
+        for which $A_{\rm m} = A_{\rm II}(\eta_2)$, upon which the trajectory
+        is ejected to zone I and $A_f = -A_{\rm I}(\eta_2)$. Note that $\eta_2
+        < \eta_{\rm \max, II}$ necessarily, as zone II must be shrinking in
+        order for the trajectory to be ejected. The final obliquity is again
+        given by Eq.~\eqref{eq:qfaf}.
+
+        Graphical inspection of Fig.~\ref{fig:eq_areas} shows that
+        $\pdil{A_{\rm II}}{\eta}$ and $\pdil{A_{\rm I}}{\eta}$ have opposite
+        signs for $\eta_2 < \eta_{\rm \max, II}$, and therefore the second II
+        $\to$ I transition is guaranteed. In summary, the III $\to$ II $\to$ I
+        track is permitted so long as the first transition is permitted, or
+        $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm c}} , A_{\rm II, \max}}$.
+
+    \item III $\to$ III --- This track is the trivial case where no separatrix
+        encounter occurs, and $A$ is constant throughout the evolution ($A_{\rm
+        f} = A_{\rm i}$). This requires $A_{\rm i} > \max \p{A_{\rm I} + A_{\rm
+        II}}$. In the limit of $\eta_{\rm i} \to \infty$ and $ \eta_{\rm f} \to
+        0$ we have $\theta_{\rm f} = \theta_{\rm sd, i}$.
 
@@
         because we use finite $\eta_{\rm i}$, as hinted at in
-        Section~\ref{sss:a_evo}. This is because for $\theta_{\rm sd, i} \gtrsim
-        \pi/2$, trajectories are better described as librating about CS3.
-        Nevertheless, we can still approximate $A_{\rm i}$ to good accuracy as
-        the solid angle enclosed by libration about CS3 with polar angle $2\pi +
-        \theta_3 - \theta_2 - \theta_{\rm sd, i}$. This recovers the correct
-        transfer function $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for the III
-        $\to$ III regime, as can be seen visibly in
+        Section~\ref{sss:a_evo}. This is because for $\theta_{\rm sd, i}
+        \gtrsim \pi/2$, trajectories are better described as librating about
+        CS3. Nevertheless, we can still approximate $A_{\rm i}$ to good
+        accuracy as the solid angle enclosed by libration about CS3 with polar
+        angle $2\pi + \theta_3 - \theta_2 - \theta_{\rm sd, i}$. This recovers
+        the correct $\theta_{\rm f}$-$\p{\theta_{\rm sd, i}}$ mapping for the
+        III $\to$ III regime, as can be seen visibly in
         Fig.~\ref{fig:3_ensemble_20_35}.
@@
     \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo21.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo21_subplots.png}
-    \end{subfigure}
-    \caption{Fiducial simulation following the $A_{\rm II} \to A_{\rm I}$
-    transition. An initial $\theta_{\rm sd, i} = 0.3\;\mathrm{rad} \approx
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo21.png}
+
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo21_subplots.png}
+    \caption{Fiducial simulation following the II $\to$ I
+    track. An initial $\theta_{\rm sd, i} = 0.3\;\mathrm{rad} \approx
     17.2^\circ$ was used, as well as $\epsilon = 3 \times 10^{-4}$. Top plot
@@
     \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo23.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo23_subplots.png}
-    \end{subfigure}
-    \caption{Same as Fig.~\ref{fig:ad_21} but for the $A_2 \to A_3$ track.
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo23.png}
+
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo23_subplots.png}
+    \caption{Same as Fig.~\ref{fig:ad_21} but for the II $\to$ III track.
     $\theta_{\rm sd, i} = 0.3\;\mathrm{rad}$ and $\epsilon = 3.01 \times
@@
     \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo31.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo31_subplots.png}
-    \end{subfigure}
-    \caption{Same as Fig.~\ref{fig:ad_21} but for the $A_{\rm III} \to A_{\rm I}$
-    track. $\theta_{\rm sd, i} = 89.1^\circ$, and $\epsilon = 3 \times
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo31.png}
+
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo31_subplots.png}
+    \caption{Same as Fig.~\ref{fig:ad_21} but for the III $\to$ I track.
+    $\theta_{\rm sd, i} = 89.1^\circ$, and $\epsilon = 3 \times
     10^{-4}$.}\label{fig:ad_31}
@@
     \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo321.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo321_subplots.png}
-    \end{subfigure}
-    \caption{Same as Fig.~\ref{fig:ad_21} but for the $A_{\rm III} \to A_{\rm II}
-    \to A_{\rm I}$ track. $\theta_{\rm sd, i} = 60^\circ$, and $\epsilon = 3.14
-    \times 10^{-4}$. Two separatrix crossings are shown.}\label{fig:ad_321}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo321.png}
+
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo321_subplots.png}
+    \caption{Same as Fig.~\ref{fig:ad_21} but for the III $\to$ II $\to$ I
+    track. $\theta_{\rm sd, i} = 60^\circ$, and $\epsilon = 3.14 \times
+    10^{-4}$. Two separatrix crossings are shown.}\label{fig:ad_321}
 \end{figure}
@@
 
+In Section~\autoref{s:ad}, we have examined the spin axis evolution in the limit
+where $\epsilon \ll 1$ and the evolution is mostly adiabatic (except at
+separatrix crossings). We now consider nonadiabatic effects.
+
 \subsection{Transition to Non-adiabaticity}\label{ss:transition}
 
-To illustrate the transition to non-adiabaticity, we present below two
-simulations with larger $\epsilon$ than used for Fig.~\ref{fig:ad_ensemble} in
-Figs.~\ref{fig:3_ensemble_05_25} and~\ref{fig:3_ensemble_05_15}.
-
-At first non-adiabaticity manifests as a larger scatter of final obliquities
-near the tracks predicted from adiabatic evolution. These scatters first set in
-for trajectories starting in zone III, as these cross the separatrix at higher
-values of $\theta$ and have a stricter adiabaticity criterion (see
-Eq.~\eqref{eq:ad_constr}).
-
-Later, these large scatters take on band-like structures that seem to persist
-across values of $\theta_{\rm sd, i}$; we attribute these to the separatrix
-crossing process becoming sensitive to the \emph{phase} of the final
-libration/circulation orbit at separatrix crossing, which implies that $\eta$
-changes substantially over the separatrix crossing orbit. This is clearly a
-non-adiabatic effect but is permitted by the weak adiabaticity criterion,
-which only compares $\eta$ evolution to dynamics far from the separatrix.
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_25.png}
+To illustrate the transition to non-adiabaticity, we carried out a suite of
+simulations for several values of $\epsilon$. The results for two of these
+values are shown in Figs.~\ref{fig:3_ensemble_05_25}
+and~\ref{fig:3_ensemble_05_15}.
+
+As $\epsilon$ increases (see Fig.~\ref{fig:3_ensemble_05_25}), non-adiabaticity
+manifests as a larger scatter of final obliquities near the tracks predicted
+from adiabatic evolution. This scatter first sets in for trajectories starting
+in zone III, as the obliquity of CS2 at separatrix crossing is higher for these
+trajectories than those starting in zone II\@. As such, the adiabaticity criterion
+is stricter for zone III initial conditions [see Eq.~\eqref{eq:ad_constr}].
+
+As $\epsilon$ increases further (see Fig.~\ref{fig:3_ensemble_05_15}) but still
+satisfies the weak adiabaticity criterion [Eq.~\eqref{eq:ad_constr}], these
+large scatters take on band-like structures that seem to persist across all
+values of $\theta_{\rm sd, i}$. We attribute these to the separatrix crossing
+process becoming sensitive to the \emph{phase} of the final
+libration/circulation orbit at the crossing. This suggests that $\eta$
+changes substantially over the separatrix crossing orbit and is clearly a
+non-adiabatic effect. The weak adiabaticity criterion permits this, as it only
+compares the rate of change of $\eta$ to dynamics far from the separatrix.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_25.png}
     \caption{Same as Fig.~\ref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$,
     and restricting $\theta_{\rm sd, i} < 90^\circ$. A larger spread from the
-    dynamical tracks is observed in the data.}\label{fig:3_ensemble_05_25}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_15.png}
+    dynamical tracks is observed in the numerical results.
+    }\label{fig:3_ensemble_05_25}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_15.png}
     \caption{Same as Fig.~\ref{fig:3_ensemble_05_25} but for $\epsilon =
-    10^{-1.5}$. Some small semblance of the evolutionary tracks remains, and the
-    deviations appear to have a banded structure. This can be attributed to
+    10^{-1.5}$. Some small resemblance to the evolutionary tracks remains, and
+    the deviations appear to have a banded structure. This can be attributed to
     non-adiabaticity ``freezing-in'' the phase of the obliquity variations over
@@
 $\epsilon = 0.3$ (violating even weak adiabaticity) is provided in
-Fig.~\ref{fig:nonad_traj}. It is clear the trajectory does not track level curves
-of the Hamiltonian during each individual snapshot (e.g.\ the third snapshot).
-This manifests when CS2 migrates more quickly than the trajectory can librate
-about CS2, precisely a violation of the weak adiabaticity criterion.
-\begin{figure}
-    \centering
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo_nonad.png}
-    \end{subfigure}
-    \begin{subfigure}{\columnwidth}
-        \centering
-        \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3testo_nonad_subplots.png}
-    \end{subfigure}
+Fig.~\ref{fig:nonad_traj}. It is clear that the trajectory does not track the
+level curves of the Hamiltonian during each individual snapshot. This manifests
+when CS2 migrates more quickly than the trajectory can librate about CS2, a
+violation of the weak adiabaticity criterion.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo_nonad.png}
+
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo_nonad_subplots.png}
     \caption{Same as Fig.~\ref{fig:ad_21} but for a non-adiabatic $\epsilon =
@@
 We now consider the general problem of how a state evolves when $\eta$ changes
-non-adiabatically. In Appendix~\ref{s:ad_approx}, we derive a formula for
-$\theta_{\rm f}$ assuming no initial spin-disk misalignment:
+non-adiabatically [i.e.\ $\epsilon \gtrsim \p*{\alpha t_{\rm d}}^{-1}$, see
+Eq.~\eqref{eq:ad_constr}]. In Appendix~\ref{s:nonad_app}, we derive a formula
+for the final obliquity $\theta_{\rm f}$ assuming no initial spin-disk
+misalignment:
 \begin{equation}
@@
 \end{equation}
-In Fig.~\ref{fig:nonad_3_ensemeble}, we show that this proves a remarkably
+In Fig.~\ref{fig:nonad_3_ensemeble}, we show that this proves to be remarkably
 accurate when taking $\epsilon = 0.3$.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3_ensemble_05_05.png}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_05.png}
     \caption{$\theta_{\rm  f}\p{\theta_{\rm sd, i}}$ at $\epsilon = 0.3$, firmly
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3scan.png}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3scan.png}
     \caption{Plot of $\theta_{\rm  f}\p{\theta_{\rm sd, i} = 0}$ as a function
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../initial/2_toy2/3scan_20.png}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3scan_20.png}
     \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$. Note that
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../initial/99_misc/2_lambdas.png}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/2_lambdas.png}
     \caption{Plot of $\lambda^2$ per Eq.~\eqref{eq:lambda2} evaluated at each
@@
             \begin{align}
-                \Pr_{\rm II \Rightarrow I} &\approx \frac{2\pi
+                \Pr\p{\rm II \to I} &\approx \frac{2\pi
                     \eta_{\star} \cos I + 4\sqrt{\eta_{\star}\sin
                     I}}{8\sqrt{\eta_{\star}\sin I}},\\
-                \Pr_{\rm II \Rightarrow III} &\approx \frac{-2\pi
+                \Pr\p{\rm II \to III} &\approx \frac{-2\pi
                     \eta_{\star} \cos I + 4\sqrt{\eta_{\star}\sin
@@
             \begin{align}
-                \cos \theta_{\rm f, II \Rightarrow I} &\approx
+                \p{\cos \theta_{\rm f}}_{\rm II \to I} &\approx
                     \p{\frac{\pi \theta_{\rm sp, i}^2}{16}}^2 \cot I
                         + \frac{\theta_{\rm sp, i}^2}{4},\\
-                \cos \theta_{\rm f, II \Rightarrow III} &\approx
+                \p{\cos \theta_{\rm f}}_{\rm II \to III} &\approx
                     \p{\frac{\pi \theta_{\rm sp, i}^2}{16}}^2 \cot I

### 2020-02-24 writeups/Su_disk_disp.tex
stash, I think almost finalized

@@
 %TODO
-% rework 3->2->1 ??? part, probably also the 3 -> 3 part
 % Fig 7 caption lol
@@
 \begin{align}
-    \epsilon \equiv{}& \frac{1}{\alpha t_{\rm d}},\label{eq:eps_def}\\
+    \epsilon \equiv{}& \frac{1}{\alpha t_{\rm d}},\nonumber\\
         ={}& 0.015 \p{\frac{k_{\rm p}}{6k_{\rm qp}}}
@@
             \p{\frac{\Omega_{\rm p}}{2\pi/\p{10\;\mathrm{days}}}}
-            \p{\frac{t_{\rm d}}{10\;\mathrm{Myr}}}^{-1}.
+            \p{\frac{t_{\rm d}}{10\;\mathrm{Myr}}}^{-1}.\label{eq:eps_def}
 \end{align}
@@
 precessional phase of $\uv{s}$ around $\uv{l}$, denoted by $\phi$. Following
-the standard convention and nomenclature (see Fig.~\ref{fig:cs_locs}), CSs 1, 3, 4
-have $\phi = 0$ and $\theta < 0$, corresponding to $\uv{s}$ and $\uv{l}_{\rm
-d}$ being on opposite sides of $\uv{l}$, while CS2 has $\phi = \pi$ and $\theta
-> 0$, corresponding to $\uv{s}$ and $\uv{l}_{\rm d}$ being on the same side of
-$\uv{l}$. When $\eta < \eta_{\rm c}$, where
+the standard convention and nomenclature (see Figs.~\ref{fig:cs_vecs}
+and~\ref{fig:cs_locs}), CSs 1, 3, 4 have $\phi = 0$ and $\theta < 0$,
+corresponding to $\uv{s}$ and $\uv{l}_{\rm d}$ being on opposite sides of
+$\uv{l}$, while CS2 has $\phi = \pi$ and $\theta > 0$, corresponding to $\uv{s}$
+and $\uv{l}_{\rm d}$ being on the same side of $\uv{l}$. When $\eta < \eta_{\rm
+c}$, where
 \begin{equation}
@@
 obliquities as a function of $\eta$ are shown in Fig.~\ref{fig:cs_locs}.
-\begin{figure*}
-    \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_3vec.png}\hfil
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_3vec.png}
+    \caption{Definition of angles in the Cassini state configuration and the
+    adopted sign convention for $\theta$. Traditionally, $\theta \in [-\pi,
+    pi]$.}\label{fig:cs_vecs}
+\end{figure}
+\begin{figure}
     %
     \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_cs_locs.png}
-    \caption{Left: Definition of angles in the Cassini state configuration and
-    the adopted sign convention for $\theta$. Right: Cassini state obliquities
-    as a function of $\eta$ for $I = 5^\circ$, where $\theta \in [-\pi, \pi]$
-    is the traditional definition of the polar angle. The vertical dashed line
-    indicates $\eta_{\rm c}$ ($= 0.766$ for $I = 5^\circ$), where CS1 and CS4
-    merge and annihilate, and the horizontal dashed lines indicate $\theta = I$
-    and $I - 180^\circ$, the asymptotic values for CSs 2 and 3 for $\eta \gg
-    \eta_{\rm c}$.}\label{fig:cs_locs}
-\end{figure*}
+    \caption{Cassini state obliquities as a function of $\eta$ for $I =
+    5^\circ$. The vertical dashed line indicates $\eta_{\rm c}$ ($= 0.766$ for
+    $I = 5^\circ$), where CS1 and CS4 merge and annihilate, and the horizontal
+    dashed lines indicate $\theta = I$ and $I - 180^\circ$, the asymptotic
+    values for CSs 2 and 3 for $\eta \gg \eta_{\rm c}$.}\label{fig:cs_locs}
+\end{figure}
 
@@
 As an example, consider a system in zone II in panel (d) of
-Fig.~\ref{fig:eq_1contours}. As $\eta decreases, zone II$ will shrink while
+Fig.~\ref{fig:eq_1contours}. As $\eta$ decreases, zone II will shrink while
 zones I and III will expand until the trajectory crosses the separatrix. Suppose
@@
         < \eta_{\rm \max, II}$ necessarily, as zone II must be shrinking in
-        order for the trajectory to be ejected. The final obliquity is again
+        order for the trajectory to be ejected. The final obliquity is finally
         given by Eq.~\eqref{eq:qfaf}.
@@
 
-        Note that a small deviation from $\theta = \theta_{\rm sd, i}$ occurs
-        because we use finite $\eta_{\rm i}$, as hinted at in
-        Section~\ref{sss:a_evo}. This is because for $\theta_{\rm sd, i}
-        \gtrsim \pi/2$, trajectories are better described as librating about
-        CS3. Nevertheless, we can still approximate $A_{\rm i}$ to good
-        accuracy as the solid angle enclosed by libration about CS3 with polar
-        angle $2\pi + \theta_3 - \theta_2 - \theta_{\rm sd, i}$. This recovers
-        the correct $\theta_{\rm f}$-$\p{\theta_{\rm sd, i}}$ mapping for the
-        III $\to$ III regime, as can be seen visibly in
-        Fig.~\ref{fig:3_ensemble_20_35}.
+        Note that for finite $\eta_{\rm i}$, the initial enclosed phase space
+        area for III $\to$ III trajectories is not given exactly by using
+        $\theta = \theta_{\rm sd, i}$ in Eq.~\eqref{eq:ai_qsd}. This is because
+        the initial orbits for these trajectories are better described as
+        librating about CS3 with angle of libration $\Delta \theta - \theta_{\rm
+        sd, i}$ rather than about CS2 with angle of libration $\theta_{\rm sd,
+        i}$. Here, $\Delta \theta$ is the angular distance between CS2 and CS3
+        and is not equal to $180^\circ$ except for $\eta_{\rm i} \to \infty$.
+
+        Using such an orbit to evaluate Eq.~\eqref{eq:a_oint} for these initial
+        conditions yields the correct enclosed phase space area that predicts
+        the $\theta_{\rm f}$-$\p{\theta_{\rm sd, i}}$ mapping for the III $\to$
+        III track in the simulation results. This correction is responsible for
+        the small cusp at the very right ($\theta_{\rm sd, i} \to 180^\circ$) of
+        all of Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
+        and~\ref{fig:3_ensemble_20_35}.
 \end{enumerate}
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo21_subplots.png}
-    \caption{Fiducial simulation following the II $\to$ I
-    track. An initial $\theta_{\rm sd, i} = 0.3\;\mathrm{rad} \approx
-    17.2^\circ$ was used, as well as $\epsilon = 3 \times 10^{-4}$. Top plot
-    upper panel: plot of $\cos \theta(t)$ (green) in an example simulation.
-    Overlaid are the locations of Cassini State 2 (red), and upper and lower
-    bounds on the separatrix (black). Note that the trajectory successfully
-    tracks CS2 to an obliquity $\theta \approx 90^\circ$. Light vertical blue
-    lines denote times portrayed in bottom plot. Top plot lower panel: plot of
-    the enclosed separatrix area obtained by integrating the simulated
-    trajectory (blue dots) and adiabatic theory (red line). Even though the
-    enclosed area jumps at separatrix crossing, the resultant $A$ is still
-    accurately predicted. Lower plot: snapshots in the $\p{\cos \theta, \phi}$
-    space of the simulation trajectories for the vertical blue lines in the top
-    plots. These times correspond to the start of the simulation, the appearance
-    of the separatrix, two panels depicting the separatrix crossing process, and
-    a final snapshot at $\eta = 10^{-3.5}$. The green line denotes a full
-    circulation or libration cycle at the selected time, including an arrow for
-    directionality. The separatrix at the start/end of the portrayed cycle are
-    shown in solid/dashed black lines respectively. Also labeled is CS2 at the
-    start of the cycle (red). Finally, the enclosed phase space area is shaded
-    in grey ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
+    % Even though the enclosed area jumps at
+    % separatrix crossing, the resultant $A$ is still accurately predicted.
+    \caption{An example of the II $\to$ I evolutionary track for $I = 5^\circ$
+    and $\theta_{\rm sd, i} = 17.2^\circ$. Upper panel: The green line shows
+    $\cos \theta$ as a function of $\eta$, obtained by numerical integration
+    (with $\epsilon = 3 \times 10^{-4}$). Overlaid are the location of Cassini
+    State 2 (red) and the upper and lower bounds on the separatrix (black). Note
+    that the trajectory tracks CS2 to a final obliquity of $88.57^\circ$. The
+    black vertical dashed lines denote instants in the simulation  portrayed in
+    bottom panels. Middle panel: The enclosed separatrix area obtained by
+    integrating the simulated trajectory (blue dots) and adiabatic theory (red
+    line). Lower plot: Snapshots in $\p{\cos \theta, \phi}$ phase space of one
+    circulation/libration cycle of the trajectory, shown in dark green with an
+    arrow indicating direction. The snapshots correspond to the start of the
+    simulation (a), the appearance of the separatrix (b), two panels depicting
+    the separatrix crossing process (c-d), and a final snapshot at $\eta =
+    10^{-3.5}$ (e). The separatricies at the beginning and end of the portrayed
+    orbit in each snapshot are shown in solid/dashed black lines respectively.
+    Also labeled is CS2 at the start of each orbit (red point). Finally, the
+    enclosed phase space area is shaded in grey ($A > 0$) and red ($A <
+    0$).}\label{fig:ad_21}
 \end{figure}
@@
     \caption{Same as Fig.~\ref{fig:ad_21} but for the II $\to$ III track.
-    $\theta_{\rm sd, i} = 0.3\;\mathrm{rad}$ and $\epsilon = 3.01 \times
+    $\theta_{\rm sd, i} = 17.2^\circ$ and $\epsilon = 3.01 \times
     10^{-4}$.}\label{fig:ad_23}
@@
     track. $\theta_{\rm sd, i} = 60^\circ$, and $\epsilon = 3.14 \times
-    10^{-4}$. Two separatrix crossings are shown.}\label{fig:ad_321}
+    10^{-4}$. Two separatrix crossings are shown [in panels (c-d) and (e-f)].
+    }\label{fig:ad_321}
 \end{figure}
@@
 
-In Section~\autoref{s:ad}, we have examined the spin axis evolution in the limit
+In Section~\ref{s:ad}, we have examined the spin axis evolution in the limit
 where $\epsilon \ll 1$ and the evolution is mostly adiabatic (except at
@@
 We now consider the general problem of how a state evolves when $\eta$ changes
-non-adiabatically [i.e.\ $\epsilon \gtrsim \p*{\alpha t_{\rm d}}^{-1}$, see
+non-adiabatically [i.e.\ $\epsilon \gtrsim \p{\alpha t_{\rm d}}^{-1}$, see
 Eq.~\eqref{eq:ad_constr}]. In Appendix~\ref{s:nonad_app}, we derive a formula
@@
 lib}}$.
-\begin{figure}[t]
+\begin{figure}
     \centering
@@
 
-We note the resemblance to a similar result given by \citet{malhotra_calc}
-describing the impact of a secular resonance sweeping through a system. Both
-results have the scaling with repsect to $\epsilon$, despite the vastly
-different calculation.
-
 It should be noted that this result breaks down in two ways:
@@
 
+We note the resemblance to the well-known eccentricity excitation of an asteroid
+sweeping through a secular resonance \citep{malhotra_calc}. Both results have
+the same scaling with repsect to the rate of change of secular frequency,
+$\epsilon$ in our notation and $\lambda$ in theirs.
+
 \bsp

### 2020-02-24 initial/2_toy2/3_disk_disp.py

@@ -16,14 +16,17 @@ matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 plt.rc('text', usetex=True)
 plt.rc('font', family='serif', size=18)
+plt.rc('xtick', direction='in', top=True, bottom=True)
+plt.rc('ytick', direction='in', left=True, right=True)
 
 PLOT_DIR = '1plots'
 from utils import to_cart, to_ang, roots, H, solve_ic_base,\
     get_etac
 dpi = 600
-my_ms = 3.5
-my_lw = 3.5
-my_alpha = 0.7
+my_lw = 4.5
+lw_single = 2.0
+my_ms = 2
+my_alpha = 0.5
 
 def sep_areas_exact(I, eta):
     mu4 = eta * np.cos(I) / (1 - eta * np.sin(I))
@@ -255,17 +258,20 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
     # will handle them in the plot_type branches below
     mu_dat = np.cos(q)
 
-    ax1.semilogx(etas, mu_dat, c='g', label='Sim')
+    if plot_type == 'nonad':
+        ax1.semilogx(etas, mu_dat, c='g', label='Sim')
+    else:
+        ax1.semilogx(etas, mu_dat, c='g', lw=0.5, label='Sim')
+        ax1.semilogx(etas, mu_dat, c='g', label='Sim')
     max_valid_idxs = np.where(mu_max > 0)[0]
     ax1.semilogx(eta4s[max_valid_idxs], mu_max[max_valid_idxs],
              'k', label='Sep')
     ax1.semilogx(eta4s, mu_min, 'k')
     ax1.semilogx(etas, np.cos(q2s), 'r', label='CS2')
-    ax1.set_xlabel(r'$t$')
     ax1.set_ylabel(r'$\cos\theta$')
 
-    ax1.set_title(r'$I = %d^\circ$' % np.degrees(I))
-    ax1.legend(loc='right')
+    # ax1.set_title(r'$I = %d^\circ$' % np.degrees(I))
+    # ax1.legend(loc='right')
 
     # plot areas
     etas_pre_cross = eta_areas[np.where(t_areas < t_end_lib)[0]]
@@ -273,23 +279,23 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
     # theory
     if plot_type == '23':
         ax3.semilogx(etas_pre_cross, np.full_like(etas_pre_cross, a_init_int),
[…]

### 2020-02-24 writeups/Su_disk_disp.tex
Dong first pass

@@
     bifurcate into distinct tracks governed by interactions with the resonance,
-    while (ii) under non-adiabatic evolution, a broad range of obliquities can
+    while (ii) under nonadiabatic evolution, a broad range of obliquities can
     be excited. Analytical formulae are provided for most interesting regimes of
@@
 advection}). Spin-orbit resonances have been studied extensively in solar system
-dynamics as \emph{Cassini States} and are responsible for the significant
-nonzero obliquities of both Jupiter ($3.1^\circ$) and Saturn ($26.7^\circ$)
-\citep{colombo1966, henrard1987, ward2004I, ward_jupiter}. Recent work has
-attempted to apply this mechanism to the ice giants as well
+dynamics as \emph{Cassini States} and are thought to be responsible for the
+significant nonzero obliquities of both Jupiter ($3.1^\circ$) and Saturn
+($26.7^\circ$) \citep{colombo1966, henrard1987, ward2004I, ward_jupiter}. Recent
+work has attempted to apply this mechanism to the ice giants as well
 \citep{hamilton_tilting_ice}.
@@
 protoplanetary disk. Such an assumption is intuitive, since the planet forms
-from the disk, but prospects for it to be violated exist. In particular, giant
-and planetesimal impacts are expected to be abundant during planet formation and
-may perturb the spin axis of the protoplanet from its primordial value
-\citep{yalinewich2019atmospheric, schlichting2015atmospheric}. Furthermore, the
-abundance of compact multi-planet systems provides support for possible
-scattering between close-in, newly-formed planets \citep{usp_compact1,
+from the disk, but evidence suggests it may not always be satisfied. In
+particular, giant and planetesimal impacts are expected to be abundant during
+planet formation and may perturb the spin axis of the protoplanet from its
+primordial value \citep{yalinewich2019atmospheric, schlichting2015atmospheric}.
+Furthermore, the prevalence of compact multi-planet systems provides support for
+possible scattering between close-in, newly-formed planets \citep{usp_compact1,
 usp_review}. It is conceivable that such processes could generate significant
@@
 In Sections~\ref{s:ad} and~\ref{s:nonad}, we study the evolution of the system
-when the disk either dissipates adiabatically or non-adiabatically respectively.
+when the disk either dissipates adiabatically or nonadiabatically respectively.
 Exhaustive yet simple analytical arguments are able to explain completely the
@@
 Fig.~\ref{fig:ad_ensemble} in the adiabatic limit and
-Fig.~\ref{fig:3_ensemble_05_15} in the non-adiabatic limit. Longer mathematical
+Fig.~\ref{fig:3_ensemble_05_15} in the nonadiabatic limit. Longer mathematical
 calculations are relegated to the appendicies, including a leading-order
@@
 frequency $\Omega_{\rm p}$, and a protoplanetary disk of mass $M_{\rm d}$. For
-simplicity, we treat the disk as a ring of radius $r_d$, but it is simple to
+simplicity, we treat the disk as a ring of radius $r_{\rm d}$, but it is simple to
 generalize to a disk with finite extent \citep[see][]{millholland_disk}.
@@
 $\uv{l} \equiv \bm{L} / L$, and $\uv{l}_{\rm d} \equiv \bm{L}_{\rm
-d} / L_d$.
+d} / L_{\rm d}$.
 
@@
 \end{align}
-Following standard notation \citep[e.g.][]{colombo1966,peale1969,ward_jupiter},
-we have defined $\alpha \equiv \omega_{\rm sl}$ and $g \equiv -\omega_{\rm
-ld}\cos I$.
+Following standard notation \citep[e.g.][]{colombo1966,peale1969,ward2004I}, we
+have defined $\alpha \equiv \omega_{\rm sl}$ and $g \equiv -\omega_{\rm ld}\cos
+I$.
 
@@
 
-Spin states satisfying $\p{\rd{\uv{s}}{t}}_{\rm rot} = 0$ are referred to as
+Spin states satisfying $\p{\rd{\uv{s}}{\tau}}_{\rm rot} = 0$ are referred to as
 \emph{Cassini States} (CSs). They require that $\uv{s}$, $\uv{l}$, and
 $\uv{l}_{\rm d}$ be coplanar. There are either two or four CSs, depending
-on the values of $\eta$. They are specified by the obliquity $\theta$ and the
+on the value of $\eta$. They are specified by the obliquity $\theta$ and the
 precessional phase of $\uv{s}$ around $\uv{l}$, denoted by $\phi$. Following
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_3vec.png}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/2_3vec.png}
     \caption{Definition of angles in the Cassini state configuration and the
     adopted sign convention for $\theta$. Traditionally, $\theta \in [-\pi,
-    pi]$.}\label{fig:cs_vecs}
-\end{figure}
-\begin{figure}
-    %
-    \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_cs_locs.png}
+    \pi]$.}\label{fig:cs_vecs}
+\end{figure}
+\begin{figure}
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/2_cs_locs.png}
     \caption{Cassini state obliquities as a function of $\eta$ for $I =
@@
 \begin{align}
-    \mathcal{H} &= -\frac{1}{2}\p{\uv{s} \cdot \uv{l}}^2
+    \mathcal{H}\p{\phi, \cos \theta} &= -\frac{1}{2}\p{\uv{s} \cdot \uv{l}}^2
             + \eta \p{\uv{s} \cdot \uv{l}_{\rm d}}\nonumber\\
@@
 \end{align}
-Trajectories in the phase space $\p{\phi, \cos \theta}$ satisfy $H = $ constant
-(see Fig.~\ref{fig:eq_1contours}).
+Here, $\phi$ and $\cos \theta$ are canonically conjugate variables. Trajectories
+in the phase space $\p{\phi, \cos \theta}$ satisfy $H = $ constant (see
+Fig.~\ref{fig:eq_1contours}).
 
@@
 Fig.~\ref{fig:eq_1contours}, we show the separatrix, the three zones, and their
-relations to the CSs. Note that trajectories in zone II librate about CS2
-while those in zones I and III circulate.
+relations to the CSs. Trajectories in zone II librate about CS2 while those in
+zones I and III circulate.
 \begin{figure*}
@@
     zone II when evolved forward in time (decreasing $\eta$ adiabatically); this
-    is the shaded region in the top left panel, bounded by the black dotted
+    is the shaded region in panel (a), bounded by the black dotted
     line.}\label{fig:eq_1contours}
@@
 
-Since $\p{\phi, \cos \theta}$ form a set of canonical variables, the integral
-$\oint \cos \theta\;\mathrm{d}\phi$ along a trajectory is an adiabatic invariant
-(see Section~\ref{s:ad}). The unsigned areas $\p{\abs{\int \cos \theta
+Since $\p{\phi, \cos \theta}$ are canonically conjugate, the integral $\oint
+\cos \theta\;\mathrm{d}\phi$ along a trajectory is an adiabatic invariant (see
+Section~\ref{s:ad}). The unsigned areas $\p{\abs{\int \cos \theta
 \;\mathrm{d}\phi}}$ of the three zones (as defined in
@@
 \end{subequations}
-These are plotted as a function of $\eta$ in Fig.~\ref{fig:eq_areas}. Note that
-the zones are not formally defined for $\eta > \eta_{\rm c}$ since the
-separatrix disappears, but a natural extension exists: evolve an initial phase
-space point $p$ under adiabatic decrease of $\eta$ until the separatrix appears
-at $\eta = \eta_{\rm c}$, then identify $p$ with the zone it is in at $\eta_{\rm
-c}$. Since phase space area is conserved under adiabatic evolution, this
-extension implies $A_{\rm i}\p{\eta > \eta_{\rm c}} = A_{\rm i}(\eta_{\rm c})$.
-The boundary between these extended zones is denoted by the dashed black line in
-the top left panel of Fig.~\ref{fig:eq_1contours}, where otherwise no separatrix
-exists.
+These are plotted as a function of $\eta$ in Fig.~\ref{fig:eq_areas}. While the
+zones are not formally defined for $\eta > \eta_{\rm c}$ since the separatrix
+disappears, a natural extension exists: evolve an initial phase space point $p$
+under adiabatic decrease of $\eta$ until the separatrix appears at $\eta =
+\eta_{\rm c}$, then identify $p$ with the zone it is in at $\eta_{\rm c}$. Since
+phase space area is conserved under adiabatic evolution, this extension implies
+$A_{\rm i}\p{\eta > \eta_{\rm c}} = A_{\rm i}(\eta_{\rm c})$. The boundary
+between these extended zones is denoted by the dashed black line in panel (a) of
+Fig.~\ref{fig:eq_1contours}, where no separatrix exists.
 \begin{figure}
@@
     II}$) and for which $A_{\rm III}$ is minimized ($\eta_{\rm \min, III}$,
-    Eq.~\eqref{eq:eta_minIII}). The horizontal black dashed line illustrates the
-    fraction of phase space occupied by zone II at separatrix appearance.
-    }\label{fig:eq_areas}
+    Eq.~\eqref{eq:eta_minIII}).}\label{fig:eq_areas}
 \end{figure}
@@
 In this section, we study the evolution of the planetary obliquity $\theta$ when
-the parameter $\eta$ (or the disk mass $M_{\rm d}$; see Eqs.~\eqref{eq:eta}
-and~\eqref{eq:deta_dt}) decreases sufficiently slowly that the evolution is
+the parameter $\eta$ [or the disk mass $M_{\rm d}$; see Eqs.~\eqref{eq:eta}
+and~\eqref{eq:deta_dt}] decreases sufficiently slowly that the evolution is
 adiabatic. Strictly speaking, this requires the disk evolution timescale $t_{\rm
@@
 in \citet{millholland_disk}, where the $\csc^3\theta_2$ term is neglected and
-the square root is missing.
-
-For $I = 5^\circ$, $\eta \sim \eta_{\rm c}$ Eq.~\eqref{eq:ad_constr} gives $\epsilon
-\lesssim 0.085$. Since our criterion is only a weak condition for diabaticity,
-we use $\epsilon = 3 \times 10^{-4}$ in our ``adiabatic'' simulations below
-(Section~\ref{ss:ad_ensemble}). We explore the consequences of nonadiabatic
-evolution in Section~\ref{s:nonad}.
+the square root is missing\footnote{The missing $\csc^3 \theta_2$ term can be
+traced to a $\theta \gg I$ approximation made in Eq.~(3) of \citet{ward2004II}.
+Since $\theta_2 \approx I$ for $\eta \gg 1$ (Fig.~\ref{fig:cs_locs}), this
+approximation is not always valid.}.
+
+For $I = 5^\circ$, $\eta \sim \eta_{\rm c}$ Eq.~\eqref{eq:ad_constr} gives
+$\epsilon \lesssim 0.085$. Since our criterion is only a weak condition for
+diabaticity, we use $\epsilon = 3 \times 10^{-4}$ in our ``adiabatic''
+simulations below. We explore the consequences of nonadiabatic evolution in
+Section~\ref{s:nonad}.
 
@@
 ($\abs{\omega_{\rm ld}} \gg \abs{\omega_{\rm sl}}$), and the spin obliquity
-$\theta$ varies rapidly. So it is more appropriate to use $\theta_{\rm sd}$
+$\theta$ varies rapidly. It is thus more appropriate to use $\theta_{\rm sd, i}$
 rather than $\theta$ to specify the initial spin orientation. We explore the
@@
 sample $101$ values of $\theta_{\rm sd, i}$, and for each $\theta_{\rm sd, i}$
-value, we pick $101$ orientations of $\uv{s}$ approximately from the ring of
-initial conditions having angular distance $\theta_{\rm sd, i}$ to $\uv{l}_{\rm
-d}$%
+value, we pick $101$ evenly spaced orientations of $\uv{s}$ approximately from
+the ring of initial conditions having angular distance $\theta_{\rm sd, i}$ to
+$\uv{l}_{\rm d}$%
 %
-\footnote{The procedure we adopted for choosing the initial conditions is the
-natural extension of this for finite $\eta_{\rm i}$. Note that the center of
-libration of $\uv{s}$ is CS2, which, since $\eta_{\rm i}$ is finite, is
-different from $\uv{l}_{\rm d}$. Furthermore, the libration is not exactly
+\footnote{The actual procedure we adopt to choose the initial conditions is the
+natural extension of this description to finite $\eta_{\rm i}$. Note that the
+center of libration of $\uv{s}$ is CS2, which, since $\eta_{\rm i}$ is finite,
+is different from $\uv{l}_{\rm d}$. Furthermore, the libration is not exactly
 circular. As a result, the libration trajectories for initial conditions on the
@@
 initial phase space areas $A_{\rm i}$. Since our analytical theory assumes exact
-conservation of phase space area $A_{\rm i}$ derived from $\theta_{\rm sd, i}$
-(see Section~\ref{ss:zone_transitions}), this discrepancy introduces an extra
-deviation from the analytical prediction. To guarantee all points for a
-particular $\theta_{\rm sd, i}$ have the same $A_{\rm i}$, we instead choose
-initial conditions on the libration cycle going through $\p{\theta_2 +
-\theta_{\rm sd, i}, \phi_2}$ [where $\p{\theta_2, \phi_2}$ are the coordinates
-of CS2]. This ensures that all initial conditions for a given $\theta_{\rm sd,
-i}$ enclose the same initial $A_{\rm i}$. Note that as $\eta_{\rm i} \to
-\infty$, CS2 becomes coincident with $\uv{l}_{\rm d}$ and the libration cycle
-becomes exactly circular, recovering the procedure given in the text.}.
+conservation of the initially enclosed phase space area $A_{\rm i}$ for each
+$\theta_{\rm sd, i}$ (see Section~\ref{ss:zone_transitions}), this discrepancy
+introduces an extra deviation from the analytical prediction. To guarantee all
+points for a particular $\theta_{\rm sd, i}$ have the same $A_{\rm i}$, we
+instead choose initial conditions on the libration cycle going through
+$\p{\theta_2 + \theta_{\rm sd, i}, \phi_2}$ [where $\p{\theta_2, \phi_2}$ are
+the coordinates of CS2]. This ensures that all initial conditions for a given
+$\theta_{\rm sd, i}$ enclose the same initial $A_{\rm i}$. As $\eta_{\rm i} \to
+\infty$, this procedure generates initial conditions on the ring having angular
+distance $\theta_{\rm sd, i}$ to $\uv{l}_{\rm d}$, recovering the procedure
+given in the text.}.
 %
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_35.png}
-    \caption{Top: Shown are the final spin obliquity $\theta_{\rm f}$ as a
-    function of the initial spin-disk misalignment angle $\theta_{\rm sd, i}$
-    for systems evolving from initial $\eta_{\rm i} \gg 1$ to $\eta_{\rm f} \ll
-    1$. The blue dots are results of numerical calculations
-    (Section~\ref{ss:ad_ensemble}), and the colored tracks are semi-analytical
-    results (Section~\ref{ss:zone_transitions}). The black dotted lines
-    represent analytical approximations valid in the small-$\theta_{\rm sd, i}$
-    limit (see Appendix~\ref{s:ad_approx}). Bottom: Shown are the probabilities
-    of different outcomes. Where a particular $\theta_{\rm sd, i}$ corresponds
-    to multiple tracks, the system evolves probabilistically. The track that a
-    particular system evolves along in a numerical simulation can be measured by
-    examining its final obliquity. The dots represent the inferred probabilities
-    from measured final obliquities in our simulations, while the colored tracks
+    \caption{Top: The final spin obliquity $\theta_{\rm f}$ as a function of the
+    initial spin-disk misalignment angle $\theta_{\rm sd, i}$ for systems
+    evolving from initial $\eta_{\rm i} \gg 1$ to $\eta_{\rm f} \ll 1$. The blue
+    dots are results of numerical calculations (Section~\ref{ss:ad_ensemble}),
+    and the colored tracks are semi-analytical results
+    (Section~\ref{ss:zone_transitions}). Bottom: The probabilities of different
+    outcomes. Where a particular $\theta_{\rm sd, i}$ corresponds to multiple
+    tracks, the system evolves probabilistically. The track that a particular
+    system evolves along in a numerical simulation can be measured by examining
+    its final obliquity. The dots represent the inferred probabilities from
+    measured final obliquities in our simulations, while the colored tracks
     denote the semi-analytic probability of the system evolving along each
     track. There are five regimes of $\theta_{\rm sd, i}$ values for which
-    different tracks are accessible. Semi-analytical calculations of the
-    boundaries of these regimes are denoted via the vertical dashed black lines
-    (see Section~\ref{ss:zone_transitions}).}\label{fig:ad_ensemble}
+    different tracks are accessible. In both plots, the vertical dashed black
+    lines denote semi-analytical calculations of the boundaries of these regimes
+    (see Section~\ref{ss:zone_transitions}), while the black dotted lines
+    represent analytical approximations valid in the small-$\theta_{\rm sd, i}$
+    limit (see Appendix~\ref{s:ad_approx}).}\label{fig:ad_ensemble}
 \end{figure}
@@
 This definition of $A$ has the advantage of (i) being continuous across
-transitions from circulating to librating that cross the North pole
-($\cos \theta = 1$), and (ii) being easily expressible as combinations of the
-$A_{\rm i}$ of Eqs.~\eqref{se:area_ward}. The bounds of the integral are either
-a libration or circulation cycle. Note that when $\eta_{\rm i} \gg 1$,
-trajectories librate about $\uv{l}_{\rm d}$ with constant $\theta_{\rm sd}$,
-meaning they enclose initial phase space area
+transitions from circulating to librating that cross the North pole ($\cos
+\theta = 1$), and (ii) the areas of the three zones are equal in absolute value
+to the expressions given in Eqs.~\eqref{se:area_ward}. The path over which the
+integral is taken is either a libration or circulation cycle. When $\eta_{\rm i}
+\gg 1$, trajectories librate about $\uv{l}_{\rm d}$ with constant $\theta_{\rm
+sd}$, meaning they enclose initial phase space area
 \begin{equation}
@@
 Note that $\Pr \p{i \to j} + \Pr\p{i \to k} = 1$.
-Eqs.~\eqref{eq:henrard_hop} can be used directly in conjunction with
+Eqs.~\eqref{eq:henrard_hop} can be used in conjunction with
 Eqs.~\eqref{se:area_ward} to understand for what initial conditions each track
@@
         II}\p{\eta_c}$ is given by Eq.~\eqref{eq:A2} evaluated at $\eta =
-        \eta_c$. Note that since $\pdil{A_{\rm I}}{\eta} < 0$ everywhere, while
+        \eta_c$. Since $\pdil{A_{\rm I}}{\eta} < 0$ everywhere, while
         $\pdil{A_{\rm II}}{\eta} > 0$ at all possible $\eta_\star$ for an
@@
 
-        Note that since $\pdil{A_{\rm I}}{\eta} < 0$ while $\pdil{A_{\rm
-        III}}{\eta} > 0$ for all accessible $\eta_{\star}$, this track is
-        always permitted.
+        Since $\pdil{A_{\rm I}}{\eta} < 0$ and $\pdil{A_{\rm III}}{\eta} > 0$
+        for all accessible $\eta_{\star}$, this track is always permitted.
 
     \item III $\to$ II $\to$ I (see Fig.~\ref{fig:ad_321}) That $A_{\rm II}
-        \p{\eta_c}$ is not monotonic is key to the existence of this track.
+        \p{\eta_{\rm c}}$ is not monotonic is key to the existence of this track.
         Consider a trajectory originating in zone III that first encounters the
@@
         which is nonnegative (i.e.\ the transition is permitted) if $\eta_1
-        \in [\eta_{\rm \max, II}, \eta_c]$. Equivalently, this requires
+        \in [\eta_{\rm \max, II}, \eta_{\rm c}]$. Equivalently, this requires
         $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm c}} , A_{\rm II, \max}}$.
@@
         for which $A_{\rm m} = A_{\rm II}(\eta_2)$, upon which the trajectory
-        is ejected to zone I and $A_f = -A_{\rm I}(\eta_2)$. Note that $\eta_2
-        < \eta_{\rm \max, II}$ necessarily, as zone II must be shrinking in
-        order for the trajectory to be ejected. The final obliquity is finally
-        given by Eq.~\eqref{eq:qfaf}.
+        is ejected to zone I and $A_{\rm f} = -A_{\rm I}(\eta_2)$. Note that
+        $\eta_2 < \eta_{\rm \max, II}$ necessarily, as zone II must be shrinking
+        in order for the trajectory to be ejected. The final obliquity is
+        finally given by Eq.~\eqref{eq:qfaf}.
 
         Graphical inspection of Fig.~\ref{fig:eq_areas} shows that
-        $\pdil{A_{\rm II}}{\eta}$ and $\pdil{A_{\rm I}}{\eta}$ have opposite
-        signs for $\eta_2 < \eta_{\rm \max, II}$, and therefore the second II
-        $\to$ I transition is guaranteed. In summary, the III $\to$ II $\to$ I
-        track is permitted so long as the first transition is permitted, or
+        $\pdil{A_{\rm II}}{\eta}$ and $\pdil{A_{\rm III}}{\eta}$ have the same
+        signs for $\eta < \eta_{\rm \max, II}$, and therefore the complementary
+        II $\to$ I transition is guaranteed. In summary, the III $\to$ II $\to$
+        I track is permitted so long as the first transition is permitted, or
         $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm c}} , A_{\rm II, \max}}$.
@@
         encounter occurs, and $A$ is constant throughout the evolution ($A_{\rm
-        f} = A_{\rm i}$). This requires $A_{\rm i} > \max \p{A_{\rm I} + A_{\rm
-        II}}$. In the limit of $\eta_{\rm i} \to \infty$ and $ \eta_{\rm f} \to
-        0$ we have $\theta_{\rm f} = \theta_{\rm sd, i}$.
-
-        Note that for finite $\eta_{\rm i}$, the initial enclosed phase space
-        area for III $\to$ III trajectories is not given exactly by using
-        $\theta = \theta_{\rm sd, i}$ in Eq.~\eqref{eq:ai_qsd}. This is because
-        the initial orbits for these trajectories are better described as
-        librating about CS3 with angle of libration $\Delta \theta - \theta_{\rm
-        sd, i}$ rather than about CS2 with angle of libration $\theta_{\rm sd,
-        i}$. Here, $\Delta \theta$ is the angular distance between CS2 and CS3
-        and is not equal to $180^\circ$ except for $\eta_{\rm i} \to \infty$.
-
-        Using such an orbit to evaluate Eq.~\eqref{eq:a_oint} for these initial
-        conditions yields the correct enclosed phase space area that predicts
-        the $\theta_{\rm f}$-$\p{\theta_{\rm sd, i}}$ mapping for the III $\to$
-        III track in the simulation results. This correction is responsible for
+        f} = A_{\rm i}$) except for a jump by $4\pi$ when crossing the South
+        pole ($\cos \theta = -1$) due to the coordinate singularity. This
+        requires $A_{\rm i} > \max \p{A_{\rm I} + A_{\rm II}}$. In the limit of
+        $\eta_{\rm i} \to \infty$ and $ \eta_{\rm f} \to 0$ we have $\theta_{\rm
+        f} = \theta_{\rm sd, i}$.
+
+        For finite $\eta_{\rm i}$, the initial enclosed phase space area for III
+        $\to$ III trajectories is not given exactly by using $\theta =
+        \theta_{\rm sd, i}$ in Eq.~\eqref{eq:ai_qsd}. This is because the
+        initial orbits for these trajectories are better described as librating
+        about CS3 with angle of libration $\Delta \theta - \theta_{\rm sd, i}$
+        rather than about CS2 with angle of libration $\theta_{\rm sd, i}$.
+        Here, $\Delta \theta$ is the angular distance between CS2 and CS3 and is
+        not equal to $180^\circ$ except when $\eta_{\rm i} \to \infty$.
+
+        Using such an orbit to evaluate Eq.~\eqref{eq:a_oint} for the initial
+        conditions for the III $\to$ III track yields the correct enclosed phase
+        space area that predicts the $\theta_{\rm f}$-$\p{\theta_{\rm sd, i}}$
+        mapping in the simulation results. This correction is responsible for
         the small cusp at the very right ($\theta_{\rm sd, i} \to 180^\circ$) of
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo21_subplots.png}
-    % Even though the enclosed area jumps at
-    % separatrix crossing, the resultant $A$ is still accurately predicted.
     \caption{An example of the II $\to$ I evolutionary track for $I = 5^\circ$
@@
     (with $\epsilon = 3 \times 10^{-4}$). Overlaid are the location of Cassini
-    State 2 (red) and the upper and lower bounds on the separatrix (black). Note
-    that the trajectory tracks CS2 to a final obliquity of $88.57^\circ$. The
-    black vertical dashed lines denote instants in the simulation  portrayed in
-    bottom panels. Middle panel: The enclosed separatrix area obtained by
-    integrating the simulated trajectory (blue dots) and adiabatic theory (red
-    line). Lower plot: Snapshots in $\p{\cos \theta, \phi}$ phase space of one
+    State 2 (red) and the upper and lower bounds on the separatrix (black). The
+    trajectory tracks CS2 to a final obliquity of $88.57^\circ$. The black
+    vertical dashed lines denote instants in the simulation  portrayed in bottom
+    panels. Middle panel: The enclosed separatrix area obtained by integrating
+    the simulated trajectory (blue dots) and adiabatic theory (red line). Lower
+    plot: Snapshots in $\p{\cos \theta, \phi}$ phase space of one
     circulation/libration cycle of the trajectory, shown in dark green with an
@@
     10^{-3.5}$ (e). The separatricies at the beginning and end of the portrayed
-    orbit in each snapshot are shown in solid/dashed black lines respectively.
-    Also labeled is CS2 at the start of each orbit (red point). Finally, the
-    enclosed phase space area is shaded in grey ($A > 0$) and red ($A <
+    cycle in each snapshot are shown in solid/dashed black lines respectively.
+    Also labeled is CS2 at the start of each cycle (filled red circle). Finally,
+    the enclosed phase space area is shaded in grey ($A > 0$) and red ($A <
     0$).}\label{fig:ad_21}
@@
     track. $\theta_{\rm sd, i} = 60^\circ$, and $\epsilon = 3.14 \times
-    10^{-4}$. Two separatrix crossings are shown [in panels (c-d) and (e-f)].
-    }\label{fig:ad_321}
+    10^{-4}$. Two separatrix crossings are shown, in panels (c-d) and
+    (e-f).}\label{fig:ad_321}
 \end{figure}
@@
 
-To illustrate the transition to non-adiabaticity, we carried out a suite of
+To illustrate the transition to nonadiabaticity, we carried out a suite of
 simulations for several values of $\epsilon$. The results for two of these
@@
 
-As $\epsilon$ increases (see Fig.~\ref{fig:3_ensemble_05_25}), non-adiabaticity
+As $\epsilon$ increases (see Fig.~\ref{fig:3_ensemble_05_25}), nonadiabaticity
 manifests as a larger scatter of final obliquities near the tracks predicted
@@
 process becoming sensitive to the \emph{phase} of the final
-libration/circulation orbit at the crossing. This suggests that $\eta$
+libration/circulation cycle at the crossing. This suggests that $\eta$
 changes substantially over the separatrix crossing orbit and is clearly a
-non-adiabatic effect. The weak adiabaticity criterion permits this, as it only
+nonadiabatic effect. The weak adiabaticity criterion permits this, as it only
 compares the rate of change of $\eta$ to dynamics far from the separatrix.
@@
     the deviations appear to have a banded structure. This can be attributed to
-    non-adiabaticity ``freezing-in'' the phase of the obliquity variations over
-    the final libration/circulation orbit prior to separatrix
+    nonadiabaticity ``freezing-in'' the phase of the obliquity variations over
+    the final libration/circulation cycle prior to separatrix
     crossing.}\label{fig:3_ensemble_05_15}
@@
 Fig.~\ref{fig:nonad_traj}. It is clear that the trajectory does not track the
-level curves of the Hamiltonian during each individual snapshot. This manifests
-when CS2 migrates more quickly than the trajectory can librate about CS2, a
-violation of the weak adiabaticity criterion.
+level curves of the Hamiltonian during each individual snapshot. This results
+from CS2 migrating more quickly than the trajectory can librate about CS2,
+violating the weak adiabaticity criterion.
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo_nonad_subplots.png}
-    \caption{Same as Fig.~\ref{fig:ad_21} but for a non-adiabatic $\epsilon =
-    0.3$. In the top panel of the top plot, it is evident that the libration
-    cycle about CS2 is unable to keep up with the swift motion of CS2 as $\eta$
-    changes, decreasing the obliquity jump. In the bottom plot, we can see that
-    individual orbits do not lie along level curves of the Hamiltonian, as the
-    Hamiltonian phase space changes quickly compared to the period of
-    circulation cycles.}\label{fig:nonad_traj}
+    \caption{Same as Fig.~\ref{fig:ad_21} but for a nonadiabatic $\epsilon =
+    0.3$. In the top panel, it is evident that the libration cycle about CS2 is
+    unable to keep up with the swift migration of CS2 as $\eta$ changes,
+    decreasing the obliquity excitation compared to the adiabatic simulation. In
+    the middle panel, the enclosed phase space area is evidently not conserved.
+    In the bottom panel, we can see that individual orbits do not lie along
+    level curves of the Hamiltonian, as the Hamiltonian phase space changes
+    quickly compared to the period of circulation cycles.}\label{fig:nonad_traj}
 \end{figure}
@@
 We now consider the general problem of how a state evolves when $\eta$ changes
-non-adiabatically [i.e.\ $\epsilon \gtrsim \p{\alpha t_{\rm d}}^{-1}$, see
+nonadiabatically [i.e.\ $\epsilon \gtrsim \p{\alpha t_{\rm d}}^{-1}$, see
 Eq.~\eqref{eq:ad_constr}]. In Appendix~\ref{s:nonad_app}, we derive a formula
@@
 \begin{equation}
-    \theta_{\rm f}\p{\theta_{\rm sd, i} = 0} = \sqrt{\frac{2\pi}{\epsilon}} \tan
+    \p{\theta_{\rm f}}_{\theta_{\rm sd, i} = 0} = \sqrt{\frac{2\pi}{\epsilon}} \tan
         I\cos I.\label{eq:nonad_q_f}
@@
 
-An intuitive guess at generalizing this assumes that any nonzero $\theta_{\rm
-sd, i}$ manifests as obliquity variations as $\uv{s}$ librates about
-$\uv{l}_{\rm d}$. These can be accounted for by simply allowing the final
-obliquity to vary over the same range as the initial obliquity, or,
-\begin{equation}
-    \theta_{\rm f}\p{\theta_{\rm sd, i}} - \sqrt{\frac{2\pi}{\epsilon}} \tan
+We can generalize this to nonzero $\theta_{\rm sd, i}$ by assuming the amplitude
+of libration of $\uv{s}$ about $\uv{l}_{\rm d}$ ($\theta_{\rm sd, i}$ namely)
+is equal to the range of final obliquities when the disk dissipates quickly.
+Intuitively, this corresponds to ``freezing in'' the variations in initial
+obliquity over a single libration cycle to the final obliquity. We obtain
+\begin{equation}
+    \theta_{\rm f} - \sqrt{\frac{2\pi}{\epsilon}} \tan
         I\cos I\in \s{-\theta_{\rm sd, i}, \theta_{\rm sd,i}}
@@
 \end{equation}
-In Fig.~\ref{fig:nonad_3_ensemeble}, we show that this proves to be remarkably
-accurate when taking $\epsilon = 0.3$.
+In Fig.~\ref{fig:nonad_3_ensemeble}, we show that this agrees with numerical
+simulations for $\epsilon = 0.3$.
 \begin{figure}
@@
     \caption{$\theta_{\rm  f}\p{\theta_{\rm sd, i}}$ at $\epsilon = 0.3$, firmly
-    in the non-adiabatic regime. Note the clear double-valuedeness has
-    disappeared, as have distinct dynamical tracks. The red dotted line presents
-    the analytical prediction given by
+    in the nonadiabatic regime. The clear double-valuedeness has disappeared,
+    as have distinct dynamical tracks. The red dotted line presents the
+    analytical prediction given by
     Eq.~\eqref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemeble}
@@
 
-The agreement of Eq.~\eqref{eq:nonad_q_f} at fixed I for varying $\epsilon$ is
-shown in Fig.~\ref{fig:nonad_3_scan}. Note that $\epsilon \to 0$ recovers the
-adiabatic regime. The deviation of $\theta_{\rm f}$ from the analytical
-prediction within the adiabatic regime is indeed due to adiabatic effects
-becoming dominant; compare to Fig.~\ref{fig:nonad_3_scan_20} where little
-deviation is observed until $\theta_{\rm f} \approx 90^\circ$.
+The agreement of Eq.~\eqref{eq:nonad_q_f} at fixed $I$ for varying $\epsilon$ is
+shown in Fig.~\ref{fig:nonad_3_scan}. In the limit $\epsilon \to 0$,
+$\theta_{\rm f} = 90^\circ$, in agreement with the adiabatic prediction (e.g.\
+Fig.~\ref{fig:ad_ensemble}). The deviation of $\theta_{\rm f}$ from the
+analytical prediction within the adiabatic regime is indeed due to adiabatic
+effects becoming dominant; compare to Fig.~\ref{fig:nonad_3_scan_20} where
+little deviation is observed until $\theta_{\rm f} \approx 90^\circ$.
 \begin{figure}
@@
     Eq.~\eqref{eq:nonad_q_f}, which is in good agreement for $\epsilon \gtrsim
-    0.1$ the non-adiabatic regime, while $\theta_{\rm f} \approx 90^\circ$ in
+    0.1$ the nonadiabatic regime, while $\theta_{\rm f} \approx 90^\circ$ in
     the adiabatic regime.}\label{fig:nonad_3_scan}
@@
     \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$. Note that
-    Eq.~\eqref{eq:nonad_q_f} is accurate until $\theta_{\rm f} \approx 90^\circ$,
-    which is much closer to the transition to adiabaticity. Comparison with
-    Fig.~\ref{fig:nonad_3_scan} suggests that the breakdown of
-    Eq.~\eqref{eq:nonad_q_f} indeed is caused by the breakdown of the
-    non-adiabatic assumption.}\label{fig:nonad_3_scan_20}
+    Eq.~\eqref{eq:nonad_q_f} is much higher final obliquities than
+    in for $I = 5^\circ$. This suggests the breakdown of
+    Eq.~\eqref{eq:nonad_q_f} is caused by the breakdown of the nonadiabatic
+    assumption rather than proximity to $\theta_f =
+    90^\circ$.}\label{fig:nonad_3_scan_20}
 \end{figure}
@@
 In this paper, we have studied the excitation of planetary obliquities by a
-dissipating protoplanetary disk for arbitrary initial misalignment angles. This
-is described by transfer function $\theta_{\rm f}\p{\theta_{\rm sd, i}}$, where
-$\theta_{\rm f}$ is the final planetary obliquity and $\theta_{\rm sd, i}$ is
-the initial misalignment angle between the planet's spin axis and the disk's
+dissipating protoplanetary disk for arbitrary initial misalignment angles. We
+present our result as a mapping from $\theta_{\rm sd, i}$ to $\theta_{\rm f}$,
+where $\theta_{\rm f}$ is the final planetary obliquity and $\theta_{\rm sd, i}$
+is the initial misalignment angle between the planet's spin axis and the disk's
 orbital angular momentum. We have presented analytical results that capture the
-behavior of $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ in both the adiabatic and
-nonadiabatic
-limits:
+behavior of this mapping in both the adiabatic and nonadiabatic limits:
 \begin{enumerate}
     \item In the adiabatic limit, we are able to reproduce the known result
-        $\theta(0) \approx 90^\circ$ \citep{millholland_disk}. We demonstrate
-        via numerical simulation the dual-valued behavior of $\theta$ as nonzero
-        values of $\theta_{\rm sd, i}$ are permitted (see
-        Fig.~\ref{fig:ad_ensemble}). We are able to capture both the exact final
-        $\theta$ values and the probabilities of observing each value via
-        careful accounting of enclosed phase space area and separatrix crossing
-        dynamics \citep{henrard1982,henrard1987}.
+        $\theta_{\rm f} = 90^\circ$ for $\theta_{\rm sd, i} \approx 0$
+        \citep{millholland_disk}. We demonstrate via numerical simulation and
+        analytical argument the dual-valued behavior of $\theta_{\rm f}$ as
+        nonzero initial spin-disk misalignment angles $\theta_{\rm sd, i}$ are
+        permitted (see Fig.~\ref{fig:ad_ensemble}). We are able to capture both
+        the exact final $\theta_{\rm f}$ values and the probabilities of
+        observing each value via careful accounting of enclosed phase space area
+        and separatrix crossing dynamics.
 
     \item As the system transitions more abruptly, the adiabatic prediction
-        breaks down when criterion Eq.~\eqref{eq:ad_constr} is violated. We find a
-        broad range of $\theta$ values can be excited for a given $\theta_{\rm
-        sd, i}$ (see Fig.~\ref{fig:nonad_3_ensemeble}). We provide an analytical
-        expression of the bounds on $\theta_{\rm f}\p{\theta_{\rm sd, i}}$ in
+        breaks down when criterion Eq.~\eqref{eq:ad_constr} is violated. We find
+        a broad range of final obliquities can be reached for a given
+        $\theta_{\rm sd, i}$ (see Fig.~\ref{fig:nonad_3_ensemeble}). We provide
+        an analytical expression of the bounds on $\theta_{\rm f}$ in
         Eq.~\eqref{eq:nonad_q_f_dist}.
@@
 
-It is of interest to note the leading order behavior of $\theta$ in the small
-$\theta_{\rm sd, i}$ limit given by Eq.~\eqref{eq:qf_21_approx} and
-Eq.~\eqref{eq:qf_23_approx}. Therefore, if $\theta_{\rm sd, i}$ is generally
-small, as might be expected for planets that do not experience strong collisions
-or scattering, resonance capture induced by an adiabatically dissipating
-protoplanetary disk is expected to significantly narrow the final $\theta$
-spread compared to the initial $\theta_{\rm sd, i}$ spread.
+It is of interest to note the leading order dependence of $\theta_{\rm f}$ on
+$\theta_{\rm sd, i}$ [given by Eq.~\eqref{eq:qf_21_approx} and
+Eq.~\eqref{eq:qf_23_approx}] is second order. Therefore, if $\theta_{\rm sd, i}$
+is generally small, as might be expected for planets that do not experience
+strong collisions or scattering, resonance passage induced by an adiabatically
+dissipating protoplanetary disk is expected to significantly narrow the final
+$\theta_{\rm f}$ spread compared to the initial $\theta_{\rm sd, i}$ spread.
 
@@
 
-In this section, we perform local linearizations about the CSs to determine the
-stability of each CS and, when stable, the local libration frequencies.
+In this section, we linearize the equations of motion near each CS\@. We
+determine the stability of each CS and the local libration frequencies of the
+stable CSs.
 
@@
 For analytical work, we adopt spherical coordinate system where $\uv{l} =
-\uv{z}$ and $\theta, \phi$ are the polar and azimuthal angle of $\uv{s}$. By
-convention, we choose $\uv{l}_{\rm z}$ at coordinates $\theta = I, \phi = \pi$.
-Note that $\p{\cos \theta, \phi}$ form a canonically conjugate pair of variables
-describing $\uv{s}$. To derive equations of motion for these canonical
-coordinates, we rewrite Eq.~\eqref{eq:H}
-\begin{equation}
-    \mathcal{H}\p{\theta, \phi} = -\frac{1}{2}\cos^2\theta
-            + \eta \p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
-\end{equation}
-
-The equations of motion follow by taking derivatives of $\mathcal{H}$ and agree
-with Eq.~\eqref{eq:dsdt_base}:
+\uv{z}$ and $\theta, \phi$ are the polar and azimuthal angle of $\uv{s}$. We
+choose $\uv{l}_{\rm z}$ at coordinates $\theta = I, \phi = \pi$ (see
+Figs.~\ref{fig:cs_vecs} and~\ref{fig:cs_locs}). Following modern mathematical
+convention, we will use
+$\theta \in [0, \pi)$% chktex 9
+and $\phi \in [0, 2\pi)$.% chktex 9
+
+The equations of motion in coordinates $\p{\phi, \cos \theta}$ follow by
+applying Hamilton's equations to the Hamiltonian [Eq.~\eqref{eq:H}]:
 \begin{subequations}\label{se:H_eom}
@@
 \end{subequations}
-While these equations are numerically stiff owing to the $\cot\theta$ term, they
-are the most intuitive description for analytical work.
+These agree with Eq.~\eqref{eq:dsdt_base}. While these equations are numerically
+stiff owing to the $\cot\theta$ term, they are the most intuitive description
+for analytical work.
 
@@
 \end{enumerate}
-Note that the $\theta_{\rm cs}$ values derived here do not follow the same
-convention as Fig.~\ref{fig:cs_locs}, because the previous $\theta$ conventions
-presume $\cos \phi = -1$ for all states and let $-\pi \leq \theta < \pi$.
+Again, the $\theta_{\rm cs}$ values derived here do not follow the same
+convention as Fig.~\ref{fig:cs_locs} due to our different $\theta, \phi$
+convention.
 
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/2_lambdas.png}
-    \caption{Plot of $\lambda^2$ per Eq.~\eqref{eq:lambda2} evaluated at each
-    of the Cassini States. The vertical axis is rescaled to limit the vertical
-    extent of the plot. Note that CS4 is a saddle point ($\lambda^2 > 0$) when
-    it exists while all others are centers ($\lambda^2 < 0$). The horizontal
-    dashed line is $\lambda^2 = 0$ the instability boundary while $\eta_{\rm c}$ is
-    labered in the vertical dashed line.}\label{fig:lambda2}
-\end{figure}
-
-Note that our expression is somewhat more complicated than in existing
-literature \citep{millholland_disk,ward2004II}. This seems to stem from the
-approximation $\theta \gg I$ made in deriving Equation 3 of
-\citet{ward2004II}. This is invalid in the $\eta \gtrsim \eta_{\rm c}$ limit for
-CS2, since $\theta_{\rm cs} \approx I$ in this regime as was shown above.
+    \caption{$\lambda^2$, given by Eq.~\eqref{eq:lambda2}, evaluated at each of
+    the Cassini States. The vertical axis is rescaled for clarity. Note that CS4
+    is a saddle point ($\lambda^2 > 0$) when it exists while all others are
+    stable ($\lambda^2 < 0$). The horizontal dashed line is the instability
+    boundary $\lambda^2 = 0$ while the vertical dashed line labels $\eta =
+    \eta_{\rm c}$.}\label{fig:lambda2}
+\end{figure}
 
@@
 Note that $\phi_4 = 0$. Then, the separatrix is the level curve of the
-Hamiltonian intersecting CS4, so it satisfies $\mathcal{H}\p{\theta_{\rm
-sep}(\phi), \phi} = \mathcal{H}\p{\theta_4, \phi_4}$. This solves to be
-approximately
+Hamiltonian intersecting CS4, so it satisfies $\mathcal{H}\p{\phi, \theta_{\rm
+sep}(\phi)} = \mathcal{H}\p{\phi_4, \theta_4}$. To leading order in $\eta$, this
+has simple expression
 \begin{equation}
@@
 \end{equation}
-Now this is a first-order ODE in $S$, albeit complex, which can be solved via
-an integrating factor
+This can be solved via an integrating factor
 \begin{align}
@@
 \end{align}
-We now invoke stationary phase, asserting that $e^{i\Phi(t)}$ is dominated by
-its contribution where $\dot{\Phi} = 0$ (the phases add constructively). But
-$\dot{\Phi} = 0$ is where $1 - \eta\cos I = 0$, or where $\eta\cos I = 1$.
-
-Now at this point, let's choose $\eta(0) = 1/\cos I, \at{\rd{\eta}{t}}_{t=0} =
--\epsilon/\cos I$. Then we expand near $t = 0$ so
+We now invoke the stationary phase approximation, asserting that $e^{i\Phi(t)}$
+is dominated by its contribution where $\dot{\Phi} = 0$ (the phases add
+constructively). This occurs where where $1 - \eta\cos I = 0$, or where
+$\eta\cos I = 1$. Choosing initial conditions $\eta(0) = 1/\cos I,
+\at{\rd{\eta}{t}}_{t=0} = -\epsilon/\cos I$, we can then expand near $t = 0$:
 \begin{align}
@@
                 & t > 0.
-        \end{cases}\\
+        \end{cases}\label{eq:app_phase}\\
     \int\limits_{-\infty}^\infty
@@
 
-Now, it should be noted that $e^{i\Phi}$ is just a phase; all we really care
-about is $\abs{S} = \sqrt{1 - s_{\rm z}^2}$. Thus, taking the absolute value of both
-sides of Eq.~\eqref{eq:nonad_int}, assuming $S\p{-\infty} \ll S\p{+\infty}$ and
-noting $\theta_{\rm f} \approx \abs{S}(+\infty)$, we obtain
+Now, it should be noted that $e^{i\Phi}$ in Eq.~\ref{eq:app_phase} is just a
+complex phase, and the obliquity excitation depends only on $\abs{S} = \sqrt{1 -
+s_{\rm z}^2}$. Thus, taking the absolute value of both sides of
+Eq.~\eqref{eq:nonad_int}, assuming $S\p{-\infty} \ll S\p{+\infty}$ and noting
+$\theta_{\rm f} \approx \abs{S}(+\infty)$, we obtain
 \begin{equation}
@@
         assume $s_{\rm z}$ is approximately constant in time, as many
-        circulation/libration orbits can ensue. Only when the driving is
-        sufficiently impulsive that the evolution dominates the change in
-        $s_{\rm z}$
-        is this calculation valid.
-
-    \item If $\abs{S\p{-\infty}} \sim \abs{S\p{+\infty}}$, then taking the
+        circulation/libration orbits can ensue. We can understand this as
+        requiring $\dot{\eta}$ be sufficiently impulsive that its response
+        dominate the adjustment in $s_{\rm z}$. This is supported by analysis of
+        Figs.~\ref{fig:nonad_3_scan} and~\ref{fig:nonad_3_scan}.
+
+    \item If $\abs{S\p{-\infty}} \gtrsim \abs{S\p{+\infty}}$, then taking the
         absolute value of both sides of Eq.~\eqref{eq:nonad_int} no longer
-        simply yields $\abs{S}\p{+\infty}$. This corresponds to the extreme
+        simply reduces to $\abs{S}\p{+\infty}$. This corresponds to the extreme
         limit where $\eta$ changes so suddenly that $\uv{s}$ has no time to
-        respond and remains roughly unchanged as $\eta \to 0$. This is
-        accommodated by noting $\theta_{\rm f} \geq \theta_{\rm sd, i}$, so the
-        correct estimate can be roughly amended
+        respond and remains roughly unchanged as $\eta \to 0$. However,
+        regardless of how quickly $\eta$ evolves, the final obliquity must
+        satisfy $\theta_{\rm f} \geq \theta_{\rm sd, i}$, so the correct
+        estimate can be roughly amended
         \begin{equation}
@@
 
-We note the resemblance to the well-known eccentricity excitation of an asteroid
-sweeping through a secular resonance \citep{malhotra_calc}. Both results have
-the same scaling with repsect to the rate of change of secular frequency,
-$\epsilon$ in our notation and $\lambda$ in theirs.
+Finally, we note the resemblance of this nonadiabatic result to the well-known
+eccentricity excitation of an asteroid sweeping through a secular resonance
+\citep{malhotra_calc}. Both results have the same scaling with repsect to the
+rate of change of secular frequency, $\epsilon$ in our notation and $\lambda$ in
+theirs.
 
@@
 \label{lastpage} % chktex 24
-\end{document}
+\end{document} % chktex 17

### 2020-02-24 initial/2_toy2/3_disk_disp.py

@@ -94,7 +94,7 @@ def get_t_vals(t_i, t_f, int_n_pts=401):
     # first/last elements overlap
     return np.concatenate((t1, t2[1: ]))
 
-def get_areas_2(ret):
+def get_areas_2(ret, plot_type):
     '''
     not get_areas in utils since this that assumes start -> ejection from sep,
     but really assumes a very full featured trajectory
@@ -116,42 +116,61 @@ def get_areas_2(ret):
     # can start either circulating or librating, but always eventually
     # transitions to librating about CS2, and ends up circulating again...
 
-    # if starts circulating, integrate (1 - mu) dphi for continuity... so many
-    # cases
-    for t_0_i, t_0_f, t_pi_f in zip(t_0, t_0[1: ], t_pi[1: ]):
-        if t_0_f < t_pi_f: # circulating
-            t_vals = get_t_vals(t_0_i, t_0_f)
-            t_areas.append(t_0_i)
-            t_areas_f.append(t_0_f)
+    # note that for plot_type = '33', the first and third loops are the relevant
+    # ones, since the first loop is *librating*. We just code this
+    # separately...
+    if plot_type != '33':
+        # if starts circulating, integrate (1 - mu) dphi for continuity... so
+        # many cases
+        for t_0_i, t_0_f, t_pi_f in zip(t_0, t_0[1: ], t_pi[1: ]):
+            if t_0_f < t_pi_f: # circulating
+                t_vals = get_t_vals(t_0_i, t_0_f)
+                t_areas.append(t_0_i)
+                t_areas_f.append(t_0_f)
+
+                x, y, z, _ = ret.sol(t_vals)
+                q, phi = to_ang(x, y, z)
+                dphi = np.gradient(np.unwrap(phi))
+                areas.append(np.sum((1 - np.cos(q)) * dphi))
+            else:
+                break
+        # truncate list of times during initial circulation
+        t_end_circ = t_0_f
+        if t_end_circ >= t_0[-1]: # pure circulating traj?
+            return np.inf, np.inf, np.array(t_areas), np.array(t_areas_f), np.array(areas)
+        if len(areas):
+            t_0 = t_0[np.where(t_0 >= t_end_circ)[0][0]: ]
[…]

### 2020-04-12 writeups/Su_disk_disp.tex
Dong feedback but not nonad section

@@
-%TODO
-% Fig 7 caption lol
     \documentclass[
@@
 
-\title[Analytical Exoplanet Obliquities]{Analytical Predictions of Exoplanet
-Obliquities Generated by Planet-Disk Interactions}
+\title[Exoplanet Obliquities]{Dynamics of Colombo's Top: Generating Exoplanet
+Obliquties from Planet-Disc Interactions}
 \author[Y. Su and D. Lai]{
@@
 \begin{abstract}
+%DL: Not done yet
     Large planetary spin-orbit misalignments (obliquities) are thought to play a
@@
 
-Substantial planetary obliquities, defined as the angle between a planet's spin
-and orbital axes, have been proposed in many exoplanetary systems. They lie at
-the heart of the obliquity tides mechanism of radius enhancement in hot Jupiters
-\citep{winn_otides, fabrycky_otides, millholland_wasp12b}. They have also been
-invoked to explain peculiar thermal phase curves in hot Jupiters \citep[see
-e.g.][]{millholland_signatures, ohno_infer_obl}. While exoplanet obliquities
-have yet to be directly detected, techniques have been proposed to constrain
-them \citep[see e.g.][]{schwarz_infer_obl, rauscher_infer_obl}.
-
-Many mechanisms have been proposed to generate large planetary obliquities.
-Giant impacts are traditionally used to generate the large obliquities of the
-solar system ice giants \citep{original_gi, morbidelli_gi}. More recently,
-obliquity excitations have been achieved via \emph{spin-orbit resonances}, where
-the spin and orbital precession frequencies of the planet become and remain
-commensurate as the system evolves (sometimes called \emph{resonance
-advection}). Spin-orbit resonances have been studied extensively in solar system
-dynamics as \emph{Cassini States} and are thought to be responsible for the
-significant nonzero obliquities of both Jupiter ($3.1^\circ$) and Saturn
-($26.7^\circ$) \citep{colombo1966, henrard1987, ward2004I, ward_jupiter}. Recent
-work has attempted to apply this mechanism to the ice giants as well
-\citep{hamilton_tilting_ice}.
-
-Producing exoplanet obliquities via spin-orbit resonances was the subject of
-\citet{millholland_disk}, where a dissipating protoplanetary disk causes
-resonance capture and advection. In their work, they begin with a planet whose
-spin is nearly aligned with the angular momentum vector of the protoplanetary
-disk. After the disk dissipates, the resulting planetary obliquity is generally
-substantial, reaching $90^\circ$ for what they characterize as adiabatic
-resonance crossings.
-
-However, their study was limited to small initial misalignment angles between
-the spin vector of the planet and the orbital angular momentum of the
-protoplanetary disk. Such an assumption is intuitive, since the planet forms
-from the disk, but evidence suggests it may not always be satisfied. In
-particular, giant and planetesimal impacts are expected to be abundant during
-planet formation and may perturb the spin axis of the protoplanet from its
-primordial value \citep{yalinewich2019atmospheric, schlichting2015atmospheric}.
-Furthermore, the prevalence of compact multi-planet systems provides support for
-possible scattering between close-in, newly-formed planets \citep{usp_compact1,
-usp_review}. It is conceivable that such processes could generate significant
-spin-disk misalignment within the lifetime of the disk.
-
-In our work, we provide an analytical framework for understanding the final
-planetary obliquity for arbitrary initial spin-disk misalignment angles. Our
-analytical work and independent numerical simulations are in agreement with
-\citet{millholland_disk} but provide a more complete characterization of
-possible behavior. While we solve a specific dynamics problem, our analysis
-is general and has a wide range of applicability to general resonance
-encounters.
-
-The paper is organized as follows. In Section~\ref{s:eq}, we review relevant
-spin-orbit dynamics and present the equations studied in the rest of the paper.
-In Sections~\ref{s:ad} and~\ref{s:nonad}, we study the evolution of the system
-when the disk either dissipates adiabatically or nonadiabatically respectively.
-Exhaustive yet simple analytical arguments are able to explain completely the
-numerical results in both limits. We discuss potential consequences in
+\subsection{Colombo's Top}
+
+A rotating planet is subjected to gravitational torque from its host star,
+making its spin axis precess around its orbital (angular momentum) axis.  Now
+suppose the orbital axis precesses around another fixed axis---such orbital
+precession could arise from gravitational interactions with other masses in the
+system (e.g.\ planets, external discs, or binary stellar companion). What is the
+dynamics of the planetary spin axis?  How does the spin axis evolve as the spin
+precession rate, the orbital precession rate, or their ratio, gradually changes
+in time?
+
+\citet{colombo1966} was the first to point out the importance of the above
+simple model in the study of the obliquity (the angle between the spin axis and
+orbital axis) of planets and satellites. Subsequent works
+\citep{peale1969,peale1974possible,ward1975tidal,henrard1987} have revealed rich
+dynamics of this model. With appropriate modification,
+% (e.g. including the nutation of the orbital axis and multi-frequency
+% precessions due to multiple planets),
+this model can be used as a basis for understanding the evolution of rotation
+axes of celestial bodies.  Indeed, many contemporary problems in
+planetary/exoplanetary dynamics can be casted into a form analogous to this
+simple model or its variant \citep[e.g.][]{ward2004I, fabrycky_otides,
+batygin2013magnetic, lai2014star, anderson2018teeter}.
+
+In this paper we present a systematic investigation on the secular evolution of
+Colombo's top, starting from general initial conditions. Our study includes
+several new analytical results that go beyond previous works. While our results
+are general, we frame our study in the context of generating exoplanet
+obliquities from planet-disc interaction with in a dissipating disc.
+
+\subsection{Planetary Obliquities from Planet-Disc Interaction}
+
+It is well recognized that the obliquity of a planet may provide important clue
+to its dynamical history. In the the Solar System, a wide range of planetary
+obliquities are observed, from nearly zero for Mercury and $3.1^\circ$ for
+Jupiter, to $23^\circ$ for Earth and $26.7^\circ$ for Saturn, to $98^\circ$ for
+Uranus. Multiple giant impacts are traditionally invoked to generate the large
+obliquities of ice giants \citep{original_gi, benz1989tilting,
+korycansky1990one, morbidelli_gi}. For gas giants, obliquity excitations may be
+achieved via spin-orbit resonances, where the spin and orbital precession
+frequencies of the planet become commensurate as the system evolves
+\citep{ward2004I, ward2004II, vokrouhlicky2015tilting}. Such resonances may also
+play a role in generating Uranus's obliquity \citep{hamilton_tilting_ice}. For
+terrestrial planets, multiple spin-orbit resonances and their overlaps can make
+the obliquity vary chaotically over a wide range
+\citep[e.g.][]{laskar1993chaotic, touma1993chaotic, correia2003long}
+
+Obliquities of extrasolar planets are difficult to measure. So far only loose
+constraints have been obtained for the obliquity of a faraway ($\gtrsim 50$~au)
+planetary-mass companion \citep{bryan2020obliquity}. But there are prospects for
+constraining exoplanetary obliquities in the coming years, such as using
+high-resolution spectroscopy to obtain $v\sin i$ of the planet
+\citep{snellen2014fast, bryan2018constraints} and using high-precision
+photometry to measure asphericity of the planet \citep{seager2002constraining}.
+Finite planetary obliquities have been indirectly inferred to explain the
+peculiar thermal phase curves \citep[see e.g.][]{millholland_signatures,
+ohno_infer_obl} and tidal dissipation in hot Jupiters
+\citep{millholland_wasp12b} and in super-Earths
+\citep{millholland2019obliquity}.
+
+It is natural to imagine some of the mechanisms that generate planetary
+obliquities in the Solar System may also operate in exoplanetary systems.
+Recently, \citet{millholland_disk} studied the production of planet obliquities
+via spin-orbit resonance, where a dissipating protoplanetary disk causes
+resonance capture and advection. In their work, a planet is accompanied by an
+inclined exterior disk; as the disk graduatelly dissipates, the resulting
+planetary obliquity is generally substantial, reaching $90^\circ$ for what they
+characterize as adiabatic resonance crossings.
+
+The Millholland \& Batygin study assumes a negligible initial planetary
+obliquity. This assumption is intuitive, since the planet attains its spin
+angular momentum from the disk. But it may not always be satisfied. In
+particular, the formation of rocky planets through planetesimal accretion can
+lead to a wide range of obliquities, especially if the final spin is imparted by
+a few large bodies \citep{dones1993does, lissauer1997accretion,
+miguel2010planet}. Such ``stocastic'' accretion likely happened for terrestrial
+planets in the Solar System. Giant impacts may have also played a role in the
+formation of the close-in multiple-planet systems discovered by the Kepler
+satellite \citep[e.g.][]{inamdar2015formation, izidoro2017breaking}.
+
+\subsection{Goal of This Paper}
+
+In this paper, we consider a wide range of initial planetary obliquities in the
+Millholland-Batygin dissipating disk scenario, and examine how the obliquity
+evolves toward the ``final'' value as the exterior disk dissipates. We provide
+an analytical framework for understanding the final planetary obliquity for
+arbitrary initial spin-disk misalignment angles. We also consider various
+dissipation timescales, and examine both ``adiabatic'' (slow disk dissipation)
+and ``non-adiabatic'' evolution. We calibrate our analytical results with
+numerical calculations.
+
+It is important to note that while we focus on a specific scenario of
+generating/modifying planetary obliquities from planet-disk interactions, our
+analysis and results have a wide range of applicability. For example, a
+dissipating disk is dynamically equivalent to an outward migrating external
+companion.
+
+The paper is organized as follows. In Section~\ref{s:eq}, we review the relevant
+spin-orbit dynamics, equations and key concepts that are used in the remainder
+of the paper. In Sections~\ref{s:ad} and~\ref{s:nonad}, we study the evolution
+of the system when the disk dissipates on different timescales, from highly
+adiabatic to nonadiabatic. Analytical results are presented to explain the
+numerical results in both limits. We discuss the implications of our results in
 Section~\ref{s:disc}. Our primary physical results consist of
 Fig.~\ref{fig:ad_ensemble} in the adiabatic limit and
-Fig.~\ref{fig:3_ensemble_05_15} in the nonadiabatic limit. Longer mathematical
+Fig.~\ref{fig:3_ensemble_05_15} in the nonadiabatic limit. Some detailed
 calculations are relegated to the appendicies, including a leading-order
-estimate of final planetary obliquities given small initial spin-disk
+estimate of the final planetary obliquities given small initial spin-disk
 misalignment angles in Appendix~\ref{s:ad_approx}.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Theory}\label{s:eq}
@@
 
-We consider a star of mass $M_\star$ hosting an oblate planet of mass $M_{\rm
-p}$, radius $R_{\rm p}$, at semimajor axis $a_{\rm p}$, and with spin angular
-frequency $\Omega_{\rm p}$, and a protoplanetary disk of mass $M_{\rm d}$. For
-simplicity, we treat the disk as a ring of radius $r_{\rm d}$, but it is simple to
-generalize to a disk with finite extent \citep[see][]{millholland_disk}.
-Denote $\bm{S}$ the spin angular momentum and $\bm{L}$ the orbital angular
-momentum of the planet, and $\bm{L}_{\rm d}$ the angular momentum of the disk.
-The corresponding unit vectors are $\uv{s} \equiv \bm{S} / S$,
-$\uv{l} \equiv \bm{L} / L$, and $\uv{l}_{\rm d} \equiv \bm{L}_{\rm
+We consider a star of mass $M_\star$ hosting an oblate planet (mass $M_{\rm p}$,
+radius $R_{\rm p}$ and spin angular frequency $\Omega_{\rm p}$) at semimajor
+axis $a_{\rm p}$, and a protoplanetary disk of mass $M_{\rm d}$. For simplicity,
+we treat the disk as a ring of radius $r_{\rm d}$, but it is simple to
+generalize to a disk with finite extent \citep[see][]{millholland_disk}. Denote
+$\bm{S}$ the spin angular momentum and $\bm{L}$ the orbital angular momentum of
+the planet, and $\bm{L}_{\rm d}$ the angular momentum of the disk. The
+corresponding unit vectors are $\uv{s} \equiv \bm{S} / S$, $\uv{l} \equiv \bm{L}
+/ L$, and $\uv{l}_{\rm d} \equiv \bm{L}_{\rm
 d} / L_{\rm d}$.
 
-We assume $S \ll L \ll L_{\rm d}$, so $\uv{l}_{\rm d}$ is approximately
-constant and $\uv{l}$ experiences negligible backreaction torque from
-$\uv{s}$. The equations of motion for $\uv{s}$ and $\uv{l}$
-are
+The spin axis $\uv{s}$ of the planet tends to precess around its orbital
+(angular momentum) axis $\uv{l}$, driven by the gravitational torque from the
+host star acting on the planet's rotational bulge. On the other hand, $\uv{l}$
+and the disc axis $\uv{l}_{\rm d}$ precess around each other due to
+gravitational interactions. We assume $S \ll L \ll L_{\rm d}$, so $\uv{l}_{\rm
+d}$ is nearly constant and $\uv{l}$ experiences negligible backreaction torque
+from $\uv{s}$. The
+equations of motion for $\uv{s}$ and $\uv{l}$ are
 \begin{align}
@@
 \begin{align}
-    \omega_{\rm sl} &= \frac{3k_{\rm qp}}{2k_{\rm p}} \frac{M_\star}{m_{\rm
-        p}} \p{\frac{R_{\rm p}}{a_{\rm p}}}^3 \Omega_{\rm p},\label{eq:wsl}\\
-    \omega_{\rm ld} &= \frac{3M_{\rm d}}{4M_\star}\p{\frac{a_{\rm
+    \omega_{\rm sl} &\equiv \frac{3GJ_2 M_pR_p^2 M_\star}{2a_p^3 I_p\Omega_p}
+        = \frac{3k_{\rm qp}}{2k_{\rm p}} \frac{M_\star}{m_{\rm p}}
+            \p{\frac{R_{\rm p}}{a_{\rm p}}}^3 \Omega_{\rm p},\label{eq:wsl}\\
+    \omega_{\rm ld} &\equiv \frac{3M_{\rm d}}{4M_\star}\p{\frac{a_{\rm
             p}}{r_{\rm d}}}^3 n .\label{eq:wld}
 \end{align}
-% = 1/(152600 yr) (kp = 6kqp, Mstar = msun, mp = mJ, Rp = RJ, ap = AU, Wp = 2pi
-% / (10 days))
-% = 1 / (573362 yr) (Md/Mstar = 0.01, ap/rd = 1/30)
-In Eq.~\eqref{eq:wsl}, $k_{\rm qp}$ and $k_{\rm p}$ are related to the planet's
-rotation-induced quadrupole moment and moment of inertia respectively
-\citep[see][]{lai2018}, and $n \equiv \sqrt{GM_\star/a_{\rm p}^3}$ is the
-planet's orbital mean motion. The three angles formed by the three vectors are
-denoted
-\begin{align}
-    \theta &\equiv \arccos \p{\uv{s} \cdot \uv{l}},\\
-    \theta_{\rm sd} &\equiv \arccos \p{\uv{s} \cdot \uv{l}_{\rm d}},\\
-    I &\equiv \arccos \p{\uv{l} \cdot \uv{l}_{\rm d}}.
-\end{align}
+In Eq.~\eqref{eq:wsl}, $I_p = k_p M_pR_p^2$ (with $k_p$ a constant) is the
+moment of inertia and $J_2=k_{\rm qp}\Omega_p^2 (R_p^3/GM_p)$ (with $k_{qp}$ a
+constant) the rotation-induced (dimensionless) quadrupole of the planet [for a
+body with uniform density, $k_p=0.4, k_{qp}=0.5$; for giant planets, $k_p\simeq
+0.25$ and $k_{qp}\simeq 0.17$ \citep[e.g.][]{lainey2016quantification}]. In
+Eq.~\eqref{eq:wld}, $n \equiv \sqrt{GM_\star/a_{\rm p}^3}$ is the planet's
+orbital mean motion, and we have assumed $r_d\gg a_p$ and included only the
+leading-order (quadrupole) interaction between the planet and disc. We define
+three relative inclination angles via
+\begin{equation}
+  \uv{s} \cdot \uv{l}\equiv \cos\theta,\quad
+  \uv{s} \cdot \uv{l}_{\rm d}\equiv \cos\theta_{\rm sd},\quad
+  \uv{l} \cdot \uv{l}_{\rm d}\equiv \cos I.
+\end{equation}
+In our model, $I$ is a constant.
 Following standard notation \citep[e.g.][]{colombo1966,peale1969,ward2004I}, we
-have defined $\alpha \equiv \omega_{\rm sl}$ and $g \equiv -\omega_{\rm ld}\cos
-I$.
+have defined $\alpha \equiv \omega_{\rm sl}$ and $g \equiv -\omega_{\rm ld}\cos I$.
 
 We can combine Eqs.~\eqref{eq:dsdt} and~\eqref{eq:dldt} into a single equation
-by transforming into a frame rotating about $\uv{l}_{\rm d}$ with
-frequency $(-g)$. In this frame, $\uv{l}_{\rm d}$ and $\uv{l}$ are fixed, and
+by transforming into a frame rotating about $\uv{l}_{\rm d}$ with frequency $g$.
+In this frame, $\uv{l}_{\rm d}$ and $\uv{l}$ are fixed, and
 $\uv{s}$ evolves as:
@@
 
-We define the frequency ratio $\eta$ and dimensionless time $\tau$ as
+We define the dimensionless time $\tau$ as
+\begin{equation}
+    \tau \equiv \alpha t,
+\end{equation}
+and the frequency ratio $\eta$
 \begin{align}
     \eta \equiv{}& -\frac{g}{\alpha}\nonumber\\
-        ={}& 3.75 \p{\frac{k_{\rm p}}{6k_{\rm qp}}}
-            \p{\frac{m_{\rm p}}{0.001 M_\odot}}
-            \p{\frac{R_{\rm p}}{R_{\rm J}}}^{-3}\nonumber\\
-        &\times \p{\frac{M_{\rm d}}{0.01 M_{\odot}}}
-            \p{\frac{a_{\rm p}}{1\;\mathrm{AU}}}^{9/2}
+        ={}& 2.08 \p{\frac{k_{\rm p}}{k_{\rm qp}}}
+            \p{\frac{\rho_{\rm p}}{\mathrm{g/cm}^3}}
+            \p{\frac{M_{\rm d}}{0.01 M_{\odot}}}
+            \p{\frac{a_{\rm p}}{5\;\mathrm{AU}}}^{9/2}\nonumber\\
+        &\times
             \p{\frac{r_{\rm d}}{30 \;\mathrm{AU}}}^{-3}
-            \p{\frac{M_\star}{1M_{\odot}}}^{-3/2}
-            \cos I,\label{eq:eta}\\
-    \tau \equiv{}& \alpha t.
-\end{align}
-In Eq.~\eqref{eq:eta}, we have introduced the fiducial values of variable
-parameters for the appciation considered in this paper. Eq.~\eqref{eq:dsdt_rot}
-then becomes
+            \p{\frac{M_\star}{M_{\odot}}}^{-3/2}
+            \p{\frac{P_p}{10\;\mathrm{hrs}}}
+            \cos I ,\label{eq:eta}
+\end{align}
+% g = 1 / (51249 yr) 1 / (3 / 4 * (0.01) / (30 AU)^3 * sqrt(G * (solar mass) * (5AU)^3))
+% alpha = 1/(106700 yr) 1 / (3/2 * (1 solar mass / (5AU)^3) / (4*pi / 3 * 1g/cm^3) * (2pi / (10 hours)))
+% ((3 * 0.01 / 4) * (1 / 30AU)^3 * (10 hours * sqrt(G * (solar mass)) / (2pi)) / (1.5 * (1 solar mass / (5AU)^(9/2)) / (4 * pi / 3 * (1g/cm^3))))
+where $\rho_p = 3M_p/(4\pi R_p^3)$ and $P_p = 2\pi/\Omega_p$ is the planet's
+rotation period. . In Eq.~\eqref{eq:eta}, we have introduced the fiducial values
+of variable parameters for the appciation considered in this paper.
+Eq.~\eqref{eq:dsdt_rot} then becomes
 \begin{equation}
@@
 \end{equation}
-with $t_{\rm d}$ constant. This implies $\mathrm{d}\eta / \mathrm{d}t = -\eta /
-t_{\rm d}$. In dimensionless units, we have
-\begin{equation}
+with $t_{\rm d}$ constant. This implies
+\begin{equation}
+    \rd{\eta}{t} = -\eta /t_{\rm d},\;\; \mathrm{or}\;\;
     \rd{\eta}{\tau} = -\epsilon \eta\label{eq:deta_dt},
@@
 where
-\begin{align}
-    \epsilon \equiv{}& \frac{1}{\alpha t_{\rm d}},\nonumber\\
-        ={}& 0.015 \p{\frac{k_{\rm p}}{6k_{\rm qp}}}
-            \p{\frac{m_{\rm p}/M_\star}{0.001}}
-            \p{\frac{a_{\rm p}}{1\;\mathrm{AU}}}^3\nonumber\\
-        &\times \p{\frac{R_{\rm p}}{R_{\rm J}}}^{-3}
-            \p{\frac{\Omega_{\rm p}}{2\pi/\p{10\;\mathrm{days}}}}
-            \p{\frac{t_{\rm d}}{10\;\mathrm{Myr}}}^{-1}.\label{eq:eps_def}
+% 1 / (1Myr * 3 / 4 * (0.01) / (30 AU)^3 * sqrt(G * (solar mass) * (5AU)^3))
+\begin{align}
+    \epsilon \equiv{}& \frac{1}{\alpha t_{\rm d}}\nonumber\\
+    ={}& 0.051 \p{\frac{k_{\rm p}}{k_{\rm qp}}}
+        \p{\frac{\rho_{\rm p}}{\mathrm{g/cm}^3}}
+        \p{\frac{a_{\rm p}}{5\;\mathrm{AU}}}^3
+        \p{\frac{P_{\rm p}}{10\;\mathrm{hrs}}}
+        \p{\frac{t_{\rm d}}{\mathrm{Myr}}}^{-1}.\label{eq:eps_def}
 \end{align}
@@
 
-Spin states satisfying $\p{\rd{\uv{s}}{\tau}}_{\rm rot} = 0$ are referred to as
-\emph{Cassini States} (CSs). They require that $\uv{s}$, $\uv{l}$, and
-$\uv{l}_{\rm d}$ be coplanar. There are either two or four CSs, depending
-on the value of $\eta$. They are specified by the obliquity $\theta$ and the
-precessional phase of $\uv{s}$ around $\uv{l}$, denoted by $\phi$. Following
-the standard convention and nomenclature (see Figs.~\ref{fig:cs_vecs}
-and~\ref{fig:cs_locs}), CSs 1, 3, 4 have $\phi = 0$ and $\theta < 0$,
-corresponding to $\uv{s}$ and $\uv{l}_{\rm d}$ being on opposite sides of
-$\uv{l}$, while CS2 has $\phi = \pi$ and $\theta > 0$, corresponding to $\uv{s}$
-and $\uv{l}_{\rm d}$ being on the same side of $\uv{l}$. When $\eta < \eta_{\rm
+Spin states satisfying $\p{d\uv{s}/d\uv{\tau}}_{\rm rot} = 0$ are referred to as
+\emph{Cassini States} (CSs) \citep{colombo1966,peale1969}. They require that
+$\uv{s}$, $\uv{l}$, and $\uv{l}_{\rm d}$ be coplanar. There are either two or
+four CSs, depending on the value of $\eta$. They are specified by the obliquity
+$\theta$ and the precessional phase of $\uv{s}$ around $\uv{l}$, denoted by
+$\phi$. Following the standard convention and nomenclature (see
+Figs.~\ref{fig:cs_vecs} and~\ref{fig:cs_locs}), CSs 1, 3, 4 have $\phi = 0$ and
+$\theta < 0$, corresponding to $\uv{s}$ and $\uv{l}_{\rm d}$ being on opposite
+sides of $\uv{l}$, while CS2 has $\phi = \pi$ and $\theta > 0$, corresponding to
+$\uv{s}$ and $\uv{l}_{\rm d}$ being on the same side of $\uv{l}$. When $\eta <
+\eta_{\rm
 c}$, where
 \begin{equation}
-    \eta_{\rm c} \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{-3/2},\label{eq:etac}
+    \eta_{\rm c} \equiv \p{\sin^{2/3}\!I + \cos^{2/3}\!I}^{-3/2},\label{eq:etac}
 \end{equation}
@@
 obliquities as a function of $\eta$ are shown in Fig.~\ref{fig:cs_locs}.
-\begin{figure}
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/2_3vec.png}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.3\textwidth]{plots_diskdisp/2_3vec.png}
     \caption{Definition of angles in the Cassini state configuration and the
@@
 \end{figure}
+
 \begin{figure}
@@
 Of the four CSs, 1, 2, 3 are stable while 4 is unstable.
-Appendix~\ref{s:local_dynamics} gives the libration frequencies and growth rates
-respectively near these CSs.
+Appendix~\ref{s:local_dynamics} gives the libration frequencies and growth rates,
+respectively, near these CSs.
 
@@
     \includegraphics[width=0.8\textwidth]{plots_diskdisp/1contours_flip.png}
-    \caption{Level curves plot of $\mathcal{H}\p{\phi, \cos \theta}$
+    \caption{Level curves of $\mathcal{H}\p{\phi, \cos \theta}$
     [Eq.~\eqref{eq:H}] for $I = 5^\circ$, where warmer colors denote more
@@
     \eta_{\rm c}$, denoting the points that would flow into either area under
-    adiabatic decrease of $\eta$ from $\eta > \eta_{\rm c}$. The vertical black
+    adiabatic decrease of $\eta$ from $\eta > \eta_{\rm c}$ (see the text). The vertical black
     dashed lines correspond to $\eta = \eta_{\rm c}$ [Eq.\eqref{eq:etac}] and
@@
 As shown in Appendix~\ref{ss:eigens}, libration about CS2 is slower than that
-about CS1 or CS3. As such, it is the slowest characteristic frequency in the
+about CS1 or CS3. As such, it has the smallest characteristic frequency in the
 system. The weak adiabaticity criterion can be recast as requiring that $\eta$
-vary more slowly than this libration frequency
-\citep[see][]{ward2004II,millholland_disk}, i.e.\ $t_{\rm d}^{-1} \lesssim
-\omega_{\rm lib} / 2\pi$. In terms of the dimensionless parameter $\epsilon$
+vary more slowly than this libration frequency \citep[see][]{ward2004II}, i.e.\
+$t_{\rm d}^{-1} \lesssim \omega_{\rm lib} / 2\pi$. In terms of the dimensionless
+parameter $\epsilon$
 [Eq.~\eqref{eq:eps_def}], this adiabaticity condition is
 \begin{equation}
-    \epsilon = \frac{1}{\alpha t_{\rm d}}
-        \lesssim \frac{1}{2\pi}\sqrt{\eta\sin I \sin \theta_2
+    \epsilon \lesssim \frac{1}{2\pi}\sqrt{\eta\sin I \sin \theta_2
             \p{1 + \eta \sin I \csc^3 \theta_2}},
@@
 where $\theta_2$ is the obliquity at CS2. This formula differs from that given
-in \citet{millholland_disk}, where the $\csc^3\theta_2$ term is neglected and
+in \citet{millholland_disk}, where the $\csc^3\!\theta_2$ term is neglected and
 the square root is missing\footnote{The missing $\csc^3 \theta_2$ term can be
@@
 diabaticity, we use $\epsilon = 3 \times 10^{-4}$ in our ``adiabatic''
-simulations below. We explore the consequences of nonadiabatic evolution in
+calculations below. We explore the consequences of nonadiabatic evolution in
 Section~\ref{s:nonad}.
@@
 \end{equation}
-This definition of $A$ has the advantage of (i) being continuous across
+This definition of $A$ has two advantages: (i) it is continuous across
 transitions from circulating to librating that cross the North pole ($\cos
@@
 $A_{\rm f}$ will be conserved for all time. As $\eta \to 0$, trajectories
-circulate about $\hat{l}$ at constant obliquity $\theta_{\rm f}$, related to
+circulate about $\uv{l}$ at constant obliquity $\theta_{\rm f}$, related to
 $A_{\rm f}$ by
@@
     \item II $\to$ I (see Fig.~\ref{fig:ad_21} for an example). The spin axis
-        $\uv{s}$ initially circulates in zone II (see a), and then starts
-        librating about CS2 as $\eta$ decreases (b), enclosing some initial
-        phase space area $A_{\rm i}$. This libration continues until the
+        $\uv{s}$ initially circulates in zone II (snapshot a), and then starts
+        librating about CS2 as $\eta$ decreases (snapshot b), enclosing some
+        initial phase space area $A_{\rm i}$. This libration continues until the
         separatrix expands (due to decreasing $\eta$) to ``touch'' the
-        trajectory (see c), at which $A_{\rm II}(\eta_\star) = A_{\rm i}$.
-        As $\hat{s}$ to a
-        circulating trajectory in zone I immediately bordering the separatrix,
-        it will encompass $-A_{\rm I}(\eta_\star)$ phase space area. The final
-        obliquity $\theta_{\rm f}$ is then given by Eq.~\eqref{eq:qfaf}, with
-        $A_{\rm f} = -A_{\rm I}\p{\eta_\star}$. An analytical approximation to
-        $\theta_{\rm f}$ is derived in Appendix~\ref{s:ad_approx} and is
-        \begin{equation}
-            \p{\cos \theta_{\rm f}}_{\rm II \to I} \approx
+        trajectory (snapshot c), at which $A_{\rm II}(\eta_\star) = A_{\rm i}$.
+        As $\hat{s}$ moves to a circulating trajectory in zone I immediately
+        bordering the separatrix, it will encompass $-A_{\rm I}(\eta_\star)$
+        phase space area. The final obliquity $\theta_{\rm f}$ is then given by
+        Eq.~\eqref{eq:qfaf}, with $A_{\rm f} = -A_{\rm I}\p{\eta_\star}$. An
+        analytical approximation to $\theta_{\rm f}$ is derived in
+        Appendix~\ref{s:ad_approx} and is
+        \begin{equation}
+            \p{\cos \theta_{\rm f}}_{\rm II \to I} \simeq
                 \p{\frac{\pi \theta_{\rm sd, i}^2}{16}}^2 \cot I
@@
 
-    \item II $\to$ III (see Fig.~\ref{fig:ad_23}) This track is similar to the
+    \item II $\to$ III (see Fig.~\ref{fig:ad_23}). This track is similar to the
         II $\to$ I track; the only difference is that, upon separatrix
@@
         \begin{equation}
-            \p{\cos \theta_{\rm f}}_{\rm II \to III} \approx
+            \p{\cos \theta_{\rm f}}_{\rm II \to III} \simeq
                 \p{\frac{\pi \theta_{\rm sd, i}^2}{16}}^2 \cot I
@@
         \end{equation}
-
         Again, this track can only occur when $A_{\rm i} < A_{\rm II}(\eta_{\rm
@@
         probability. Upon examination of Fig.~\ref{fig:eq_areas}, it is clear
-        that $\pd{A_{\rm III}}{\eta} > 0$ for a large range of $\eta$, which
-        would give a negative transition probability---implying a forbidden
-        transition. Define
+        that $\pdil{A_{\rm III}}{\partial \eta} > 0$ for a large range of
+        $\eta$, which would give a negative transition probability---implying
+        a forbidden transition. Define
         \begin{equation}
@@
 
-    \item III $\to$ I (see Fig.~\ref{fig:ad_31}) The trajectory encounters the
+    \item III $\to$ I (see Fig.~\ref{fig:ad_31}). The trajectory encounters the
         separatrix when $A_{\rm I}(\eta_\star) + A_{\rm II}(\eta_\star) =
@@
         A_{\rm II}} = 4\pi - \min \p{A_{\rm III}}$.
-
         Since $\pdil{A_{\rm I}}{\eta} < 0$ and $\pdil{A_{\rm III}}{\eta} > 0$
@@
 
-    \item III $\to$ II $\to$ I (see Fig.~\ref{fig:ad_321}) That $A_{\rm II}
-        \p{\eta_{\rm c}}$ is not monotonic is key to the existence of this track.
-        Consider a trajectory originating in zone III that first encounters the
+    \item III $\to$ II $\to$ I (see Fig.~\ref{fig:ad_321}). That $A_{\rm
+        II}(\eta)$ is not a monotonic function of $\eta$ (see
+        Fig.~\ref{fig:eq_areas}) is key to the existence of this track. Consider
+        a trajectory originating in zone III that first encounters the
         separatrix at $\eta_1$, when $A_{\rm I}(\eta_1) + A_{\rm II}(\eta_1) =
-        A_{\rm i}$, such that it transitions into zone II enclosing
-        intermediate phase space area $A_{\rm m} = A_{\rm II}(\eta_1)$. Such a
-        transition has probability
+        A_{\rm i}$, such that it transitions into zone II enclosing intermediate
+        phase space area $A_{\rm m} = A_{\rm II}(\eta_1)$. Such a transition has
+        probability
         \begin{equation}
@@
         \end{equation}
-        which is nonnegative (i.e.\ the transition is permitted) if $\eta_1
-        \in [\eta_{\rm \max, II}, \eta_{\rm c}]$. Equivalently, this requires
-        $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm c}} , A_{\rm II, \max}}$.
-
-        Then, as $\eta$ continues to decrease, a second $\eta_2$ value exists
-        for which $A_{\rm m} = A_{\rm II}(\eta_2)$, upon which the trajectory
-        is ejected to zone I and $A_{\rm f} = -A_{\rm I}(\eta_2)$. Note that
+        which is nonnegative (i.e.\ the transition is permitted) if $\eta_1 \in
+        [\eta_{\rm \max, II}, \eta_{\rm c}]$. Equivalently, this requires
+        $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm c}} , A_{\rm II, \max}}$. Then,
+        as $\eta$ continues to decrease, a second $\eta_2$ value exists for
+        which $A_{\rm m} = A_{\rm II}(\eta_2)$, upon which the trajectory is
+        ejected to zone I and $A_{\rm f} = -A_{\rm I}(\eta_2)$. Note that
         $\eta_2 < \eta_{\rm \max, II}$ necessarily, as zone II must be shrinking
-        in order for the trajectory to be ejected. The final obliquity is
-        finally given by Eq.~\eqref{eq:qfaf}.
-
-        Graphical inspection of Fig.~\ref{fig:eq_areas} shows that
-        $\pdil{A_{\rm II}}{\eta}$ and $\pdil{A_{\rm III}}{\eta}$ have the same
-        signs for $\eta < \eta_{\rm \max, II}$, and therefore the complementary
-        II $\to$ I transition is guaranteed. In summary, the III $\to$ II $\to$
-        I track is permitted so long as the first transition is permitted, or
-        $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm c}} , A_{\rm II, \max}}$.
-
-    \item III $\to$ III --- This track is the trivial case where no separatrix
+        in order for the trajectory to be ejected. The final obliquity is given
+        by Eq.~\eqref{eq:qfaf}. Graphical inspection of Fig.~\ref{fig:eq_areas}
+        shows that $\pdil{A_{\rm II}}{\eta}$ and $\pdil{A_{\rm III}}{\eta}$ have
+        the same signs for $\eta < \eta_{\rm \max, II}$, and therefore the
+        complementary II $\to$ I transition is guaranteed. Overall, the III
+        $\to$ II $\to$ I track is permitted so long as the first transition is
+        permitted, or $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm c}} , A_{\rm II,
+        \max}}$.
+
+    \item III $\to$ III\@. This track is the trivial case where no separatrix
         encounter occurs, and $A$ is constant throughout the evolution ($A_{\rm
@@
         $\eta_{\rm i} \to \infty$ and $ \eta_{\rm f} \to 0$ we have $\theta_{\rm
-        f} = \theta_{\rm sd, i}$.
-
-        For finite $\eta_{\rm i}$, the initial enclosed phase space area for III
-        $\to$ III trajectories is not given exactly by using $\theta =
-        \theta_{\rm sd, i}$ in Eq.~\eqref{eq:ai_qsd}. This is because the
-        initial orbits for these trajectories are better described as librating
-        about CS3 with angle of libration $\Delta \theta - \theta_{\rm sd, i}$
-        rather than about CS2 with angle of libration $\theta_{\rm sd, i}$.
-        Here, $\Delta \theta$ is the angular distance between CS2 and CS3 and is
-        not equal to $180^\circ$ except when $\eta_{\rm i} \to \infty$.
-
-        Using such an orbit to evaluate Eq.~\eqref{eq:a_oint} for the initial
-        conditions for the III $\to$ III track yields the correct enclosed phase
-        space area that predicts the $\theta_{\rm f}$-$\p{\theta_{\rm sd, i}}$
-        mapping in the simulation results. This correction is responsible for
-        the small cusp at the very right ($\theta_{\rm sd, i} \to 180^\circ$) of
-        all of Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
+        f} = \theta_{\rm sd, i}$. For finite $\eta_{\rm i}$, the initial
+        enclosed phase space area for III $\to$ III trajectories is not given
+        exactly by using $\theta = \theta_{\rm sd, i}$ in Eq.~\eqref{eq:ai_qsd}.
+        This is because the initial orbits for such trajectories are better
+        described as librating about CS3 with angle of libration $\Delta \theta
+        - \theta_{\rm sd, i}$ rather than about CS2 with angle of libration
+        $\theta_{\rm sd, i}$. Here, $\Delta \theta$ is the angular distance
+        between CS2 and CS3 and is not equal to $180^\circ$ except when
+        $\eta_{\rm i} \to \infty$. This finite-$\eta_{\rm i}$ effect is
+        responsible for the small cusp at the very right ($\theta_{\rm sd, i}
+        \to 180^\circ$) of
+        Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
         and~\ref{fig:3_ensemble_20_35}.
 \end{enumerate}
+
 In summary, starting from an initial condition with phase space area $A_{\rm i}$
@@
 \begin{enumerate}
-    \item $A_{\rm i} \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$. Both the II
+    \item $A_{\rm i} \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$: Both the II
         $\to$ III and the II $\to$ I tracks are possible.
@@
     \item $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm \min, III}}, A_{\rm
-        II}(\eta_{\rm c})}$. Only the II $\to$ I track.
-
-    \item $A_{\rm i} \in \s{A_{\rm II}(\eta_{\rm c}), A_{\rm II, \max}}$.
+        II}(\eta_{\rm c})}$: Only the II $\to$ I track.
+
+    \item $A_{\rm i} \in \s{A_{\rm II}(\eta_{\rm c}), A_{\rm II, \max}}$:
         Both the III $\to$ I and III $\to$ II $\to$ I are possible.
 
-    \item $A_{\rm i} \in \s{A_{\rm II, \max}, \max \p{A_{\rm I} + A_{\rm II}}}$.
+    \item $A_{\rm i} \in \s{A_{\rm II, \max}, \max \p{A_{\rm I} + A_{\rm II}}}$:
         Only the III $\to$ I track.
 
-    \item $A_{\rm i} > \max \p{A_{\rm I} + A_{\rm II}}$. Only the III $\to$ III
+    \item $A_{\rm i} > \max \p{A_{\rm I} + A_{\rm II}}$: Only the III $\to$ III
         track.
@@
     \caption{An example of the II $\to$ I evolutionary track for $I = 5^\circ$
-    and $\theta_{\rm sd, i} = 17.2^\circ$. Upper panel: The green line shows
+    and $\theta_{\rm sd, i} = 17.2^\circ$. Upper panel: The thin green line shows
     $\cos \theta$ as a function of $\eta$, obtained by numerical integration
     (with $\epsilon = 3 \times 10^{-4}$). Overlaid are the location of Cassini
-    State 2 (red) and the upper and lower bounds on the separatrix (black). The
-    trajectory tracks CS2 to a final obliquity of $88.57^\circ$. The black
-    vertical dashed lines denote instants in the simulation  portrayed in bottom
-    panels. Middle panel: The enclosed separatrix area obtained by integrating
-    the simulated trajectory (blue dots) and adiabatic theory (red line). Lower
-    plot: Snapshots in $\p{\cos \theta, \phi}$ phase space of one
-    circulation/libration cycle of the trajectory, shown in dark green with an
-    arrow indicating direction. The snapshots correspond to the start of the
-    simulation (a), the appearance of the separatrix (b), two panels depicting
-    the separatrix crossing process (c-d), and a final snapshot at $\eta =
-    10^{-3.5}$ (e). The separatricies at the beginning and end of the portrayed
-    cycle in each snapshot are shown in solid/dashed black lines respectively.
-    Also labeled is CS2 at the start of each cycle (filled red circle). Finally,
-    the enclosed phase space area is shaded in grey ($A > 0$) and red ($A <
-    0$).}\label{fig:ad_21}
+    State 2 (dashed red) and the upper and lower bounds on the separatrix
+    (dotted black). The trajectory tracks CS2 to a final obliquity of
+    $88.57^\circ$. The black vertical dashed lines denote instants in the
+    simulation  portrayed in bottom panels. Middle panel: The enclosed
+    separatrix area obtained by integrating the simulated trajectory (green
+    dots) and adiabatic theory (red line). Lower plot: Snapshots in $\p{\cos
+    \theta, \phi}$ phase space of one circulation/libration cycle of the
+    trajectory, shown in dark green with an arrow indicating direction. The
+    snapshots correspond to the start of the simulation (a), the appearance of
+    the separatrix (b), two panels depicting the separatrix crossing process
+    (c-d), and a final snapshot at $\eta = 10^{-3.5}$ (e). The separatricies at
+    the beginning and end of the portrayed cycle in each snapshot are shown in
+    solid/dashed black lines respectively. Also labeled is CS2 at the start of
+    each cycle (filled red circle). Finally, the enclosed phase space area is
+    shaded in grey ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
 \end{figure}
@@
 In Section~\ref{s:ad}, we have examined the spin axis evolution in the limit
-where $\epsilon \ll 1$ and the evolution is mostly adiabatic (except at
-separatrix crossings). We now consider nonadiabatic effects.
-
-\subsection{Transition to Non-adiabaticity}\label{ss:transition}
+where $\epsilon \ll 1$ [see Eq.~\eqref{eq:ad_constr}] and the evolution is
+mostly adiabatic (except at separatrix crossings). We now consider nonadiabatic
+effects.
+
+\subsection{Transition to Non-adiabaticity: Results for $\epsilon\lesssim
+1$}\label{ss:transition}
 
 To illustrate the transition to nonadiabaticity, we carried out a suite of
-simulations for several values of $\epsilon$. The results for two of these
+numerical calculations for several values of $\epsilon$. The results for two of these
 values are shown in Figs.~\ref{fig:3_ensemble_05_25}
@@
 from adiabatic evolution. This scatter first sets in for trajectories starting
-in zone III, as the obliquity of CS2 at separatrix crossing is higher for these
-trajectories than those starting in zone II\@. As such, the adiabaticity criterion
-is stricter for zone III initial conditions [see Eq.~\eqref{eq:ad_constr}].
+in zone III, as these trajectories encounter the separatrix at larger $\eta$
+compared to those originating in zone II\@. This means the obliquity of CS2
+$\theta_2$ is smaller for these trajectories, and the adiabaticity criterion is
+stricter [see Eq.~\eqref{eq:ad_constr}]. Physically, approaching the
+adiabaticity criterion corresponds to the separatrix crossing process becoming
+sensitive to the \emph{phase} of the libration/circulation cycle at the
+crossing: if the trajectory crosses the separatrix when the obliquity is at its
+maximum, the final obliquity will also be relatively larger.
 
 As $\epsilon$ increases further (see Fig.~\ref{fig:3_ensemble_05_15}) but still
-satisfies the weak adiabaticity criterion [Eq.~\eqref{eq:ad_constr}], these
-large scatters take on band-like structures that seem to persist across all
-values of $\theta_{\rm sd, i}$. We attribute these to the separatrix crossing
-process becoming sensitive to the \emph{phase} of the final
-libration/circulation cycle at the crossing. This suggests that $\eta$
-changes substantially over the separatrix crossing orbit and is clearly a
-nonadiabatic effect. The weak adiabaticity criterion permits this, as it only
-compares the rate of change of $\eta$ to dynamics far from the separatrix.
+marginally satisfies the weak adiabaticity criterion [Eq.~\eqref{eq:ad_constr}],
+the scatter in $\theta_{\rm f}$ continues to widen. The horizontal banded
+structure of the final obliquities is a consequence of even stronger phase
+sensitivity during separatrix crossing: trajectories cross the separatrix at
+similar phases evolve to similar final obliquities that only depend weakly on
+on $\theta_{\rm sd, i}$.
+
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_25.png}
-    \caption{Same as Fig.~\ref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$,
-    and restricting $\theta_{\rm sd, i} < 90^\circ$. A larger spread from the
-    dynamical tracks is observed in the numerical results.
+    \caption{Same as Fig.~\ref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$
+    and restricting $\theta_{\rm sd, i} < 90^\circ$ (blue dots). The colored
+    solid lines are analytical adiabatic results (same as shown in
+    Fig.~\ref{fig:ad_ensemble}). A larger spread from the adiabatic tracks is
+    observed in the numerical results due to the non-adiabaticity effect.
     }\label{fig:3_ensemble_05_25}
 \end{figure}
+
 \begin{figure}
@@
     \caption{Same as Fig.~\ref{fig:3_ensemble_05_25} but for $\epsilon =
-    10^{-1.5}$. Some small resemblance to the evolutionary tracks remains, and
-    the deviations appear to have a banded structure. This can be attributed to
-    nonadiabaticity ``freezing-in'' the phase of the obliquity variations over
-    the final libration/circulation cycle prior to separatrix
-    crossing.}\label{fig:3_ensemble_05_15}
+    10^{-1.5}$ (i.e.\ larger non-adiabaticity effect). Some small resemblance to
+    the adiabatic tracks remains, and the deviations appear to have a banded
+    structure. }\label{fig:3_ensemble_05_15}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo_nonad_subplots.png}
-    \caption{Same as Fig.~\ref{fig:ad_21} but for a nonadiabatic $\epsilon =
+    \caption{Same as Fig.~\ref{fig:ad_21} but for a nonadiabatic case, with $\epsilon =
     0.3$. In the top panel, it is evident that the libration cycle about CS2 is
@@
     decreasing the obliquity excitation compared to the adiabatic simulation. In
-    the middle panel, the enclosed phase space area is evidently not conserved.
-    In the bottom panel, we can see that individual orbits do not lie along
-    level curves of the Hamiltonian, as the Hamiltonian phase space changes
-    quickly compared to the period of circulation cycles.}\label{fig:nonad_traj}
-\end{figure}
-
-\subsection{Non-adiabatic Evolution Outcomes}
-
-We now consider the general problem of how a state evolves when $\eta$ changes
-nonadiabatically [i.e.\ $\epsilon \gtrsim \p{\alpha t_{\rm d}}^{-1}$, see
-Eq.~\eqref{eq:ad_constr}]. In Appendix~\ref{s:nonad_app}, we derive a formula
-for the final obliquity $\theta_{\rm f}$ assuming no initial spin-disk
-misalignment:
-\begin{equation}
-    \p{\theta_{\rm f}}_{\theta_{\rm sd, i} = 0} = \sqrt{\frac{2\pi}{\epsilon}} \tan
-        I\cos I.\label{eq:nonad_q_f}
-\end{equation}
-
-We can generalize this to nonzero $\theta_{\rm sd, i}$ by assuming the amplitude
-of libration of $\uv{s}$ about $\uv{l}_{\rm d}$ ($\theta_{\rm sd, i}$ namely)
+    the middle panel, the trajectory only undergoes six libration/circulation
+    cycles before $\eta < 10^{-5}$, and the enclosed phase space area is
+    clearly not conserved. In the bottom panel, we can see that individual
+    trajectories do not lie along level curves of the Hamiltonian, as the
+    Hamiltonian phase space changes quickly compared to the period of
+    circulation cycles.}\label{fig:nonad_traj}
+\end{figure}
+
+\subsection{Non-adiabatic Evolution: Result for $\epsilon\gtrsim 1$}
+
+In general, numerical calculations are needed to determine the non-adiabatic
+obliquity evolution ($\epsilon\gtrsim 1$). However, some analytical results can
+be still be obtained when the obliquity remains small throughout the evolution.
+
+We start from Eq.~\eqref{eq:dsdt_base}, which governs the evolution of the spin
+axis. We choose coordinate axes such that $\uv{l} = \uv{z}$ and $ \uv{l}_{\rm d}
+= \uv{z} \cos I + \uv{x}\sin I$, giving
+\begin{equation}
+    \rd{\uv{s}}{\tau} = \s{
+        \p{\eta \cos I - \cos\theta}\uv{z} + \eta \sin I \,\uv{x}} \times \uv{s}.
+\end{equation}
+%Now, let's assume that $s_{\rm z} \approx \cos I$ throughout the evolution of
+%$\uv{s}$ (note that $\theta_{\rm sd, i} = 0$ implies the initial $s_{\rm z} = \cos I$).
+Define $S = {\hat s}_{\rm x} + i{\hat s}_{\rm y}$, we find
+\begin{equation}
+    \rd{S}{\tau} = i\p{\eta\cos I - \cos\theta}S - i \eta \sin I\cos\theta.\label{eq:nonad_ode}
+\end{equation}
+To proceed, we assume $\theta$ is small and set $\cos\theta \simeq 1$. Equation
+(\ref{eq:nonad_ode}) can then be solved explicitly, starting from the initial
+value $S(\tau_{\rm i})$:
+\begin{equation}
+    S(\tau)e^{-i\Phi(\tau)} - S(\tau_{\rm i})
+        \simeq -i\sin I\int_{\tau_{\rm i}}^\tau \eta(\tau')
+            e^{-i\Phi(\tau')}\;\mathrm{d}\tau',
+\end{equation}
+where
+\begin{equation}
+    \Phi(\tau) \equiv \int_{\tau_{\rm i}}^\tau \p{\eta(\tau') \cos I -1}\;
+        \mathrm{d}\tau'.
+\end{equation}
+We now invoke the stationary phase approximation, so that $\Phi(\tau)\simeq
+\Phi(\tau_0) + (1/2)\ddot\Phi (\tau_0)(\tau - \tau_0)^2$, where $\tau_0$ is
+determined by $\dot\Phi=0$ or $\eta_0=1/\cos I$. We then find, for $\tau\gg
+\tau_0$,
+\begin{equation}
+    S(\tau)e^{-i\Phi(\tau)}-S(\tau_{\rm i})\simeq -i\sin I\,\eta(\tau_0)\, e^{-i\Phi(\tau_0)}
+    \p{\frac{2\pi}{i \ddot\Phi(\tau_0)}}^{1/2}.
+\end{equation}
+Using $\dot\eta = -\epsilon \eta$ [Eq.~\eqref{eq:deta_dt}] and
+$\ddot\Phi(\tau_0) = \dot\eta(\tau_0)\cos I = -\epsilon$, we have
+\begin{equation}
+    S(\tau)e^{-i\Phi(\tau)}-S(\tau_{\rm i})
+        \simeq -i^{3/2}\tan I\, e^{-i\Phi(\tau_0)}
+            \p{\frac{2\pi}{\epsilon}}^{1/2}.
+\end{equation}
+If the initial obliquity is negligible ($\theta_{\rm i} = \abs{S(\tau_{\rm
+i})} \ll 1$), the final obliquity is given by
+\begin{equation}
+    \theta_{\rm f}\simeq \sqrt{\frac{2\pi}{\epsilon}}\tan I.\label{eq:nonad_q_f}
+\end{equation}
+This expression is valid only if $\theta_f$ is small (recall that we have used
+the approximation $\cos\theta\simeq 1$ in the above derivation).
+
+We can generalize the above analytic result to nonzero initial spin-disc
+angle $\theta_{\rm sd, i}$ by assuming the amplitude
+of libration of $\uv{s}$ about $\uv{l}_{\rm d}$ (namely $\theta_{\rm sd, i}$)
 is equal to the range of final obliquities when the disk dissipates quickly.
 Intuitively, this corresponds to ``freezing in'' the variations in initial
-obliquity over a single libration cycle to the final obliquity. We obtain
-\begin{equation}
-    \theta_{\rm f} - \sqrt{\frac{2\pi}{\epsilon}} \tan
-        I\cos I\in \s{-\theta_{\rm sd, i}, \theta_{\rm sd,i}}
-        .\label{eq:nonad_q_f_dist}
-\end{equation}
-In Fig.~\ref{fig:nonad_3_ensemeble}, we show that this agrees with numerical
-simulations for $\epsilon = 0.3$.
+obliquity over a single libration cycle to the final obliquity. Thus we expect
+\begin{equation}
+  \theta_{\rm f} - \sqrt{\frac{2\pi}{\epsilon}} \tan I
+  \in \s{-\theta_{\rm sd, i}, \theta_{\rm sd,i}}.\label{eq:nonad_q_f_dist}
+\end{equation}
+
+In Fig.~\ref{fig:nonad_3_ensemble}, we show the numerical result of $\theta_f$
+vs $\theta_{\rm sd,i}$ for $I = 5^\circ$ and $\epsilon = 0.3$. We see that
+Eq.~(\ref{eq:nonad_q_f_dist}) provides good lower and upper bounds of the final
+obliquity for $\theta_{\rm sd,i} \lesssim 20^\circ$.
+
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_05.png}
-    \caption{$\theta_{\rm  f}\p{\theta_{\rm sd, i}}$ at $\epsilon = 0.3$, firmly
-    in the nonadiabatic regime. The clear double-valuedeness has disappeared,
-    as have distinct dynamical tracks. The red dotted line presents the
-    analytical prediction given by
-    Eq.~\eqref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemeble}
-\end{figure}
-
-The agreement of Eq.~\eqref{eq:nonad_q_f} at fixed $I$ for varying $\epsilon$ is
-shown in Fig.~\ref{fig:nonad_3_scan}. In the limit $\epsilon \to 0$,
-$\theta_{\rm f} = 90^\circ$, in agreement with the adiabatic prediction (e.g.\
-Fig.~\ref{fig:ad_ensemble}). The deviation of $\theta_{\rm f}$ from the
-analytical prediction within the adiabatic regime is indeed due to adiabatic
-effects becoming dominant; compare to Fig.~\ref{fig:nonad_3_scan_20} where
-little deviation is observed until $\theta_{\rm f} \approx 90^\circ$.
+    \caption{$\theta_{\rm  f}$ vs $\theta_{\rm sd, i}$ for $I=5^\circ$ and
+    $\epsilon = 0.3$ (firmly in the nonadiabatic regime). The blue dots
+    represent numerical result, and the two red lines show the analytical lower
+    and upper limits given by
+    Eq.~\eqref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemble}
+\end{figure}
+
+Figures~\ref{fig:nonad_3_scan} and~\ref{fig:nonad_3_scan_20} show $\theta_f$ as
+function of $\epsilon$ for $\theta_{\rm sd,i} = 0$ and $I = 5$, $20^\circ$. We
+see that the agreement between the numerical results and
+Eq.~\eqref{eq:nonad_q_f} is excellent, particularly for the $I = 5^\circ$ case.
+The agreement when $I = 20^\circ$ is poorer as the initial obliquity
+$\theta_{\rm i} = I$ is larger, violating one of our key assumptions. For
+$\epsilon \ll 1$, we find $\theta_f \simeq 90^\circ$, in agreement with the
+result of adiabatic evolution (see Fig.~\ref{fig:ad_ensemble}).
+
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3scan.png}
-    \caption{Plot of $\theta_{\rm  f}\p{\theta_{\rm sd, i} = 0}$ as a function
-    of $\epsilon$, where $I = 5^\circ$. The shaded area, bordered by the black
-    line, corresponds to the adiabatic regime estimated by
-    Eq.~\eqref{eq:ad_constr}. Overplotted in the red line is
-    Eq.~\eqref{eq:nonad_q_f}, which is in good agreement for $\epsilon \gtrsim
-    0.1$ the nonadiabatic regime, while $\theta_{\rm f} \approx 90^\circ$ in
-    the adiabatic regime.}\label{fig:nonad_3_scan}
+    \caption{Final obliquity $\theta_{\rm  f}$ as a function of $\epsilon$ for
+    $\theta_{\rm sd,i} = 0$ and $I = 5^\circ$. The shaded area, bordered by the
+    black line, corresponds to the adiabatic regime estimated by
+    Eq.~\eqref{eq:ad_constr}. The blue dots are numerical results, and the red
+    line corresponds to Eq.~\eqref{eq:nonad_q_f}, which is in good agreement
+    with numerical results for $\epsilon \gtrsim 0.1$ (the nonadiabatic regime);
+    $\theta_{\rm f} \simeq  90^\circ$ in the adiabatic regime ($\epsilon\ll
+    1$).}\label{fig:nonad_3_scan}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3scan_20.png}
-    \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$. Note that
-    Eq.~\eqref{eq:nonad_q_f} is much higher final obliquities than
-    in for $I = 5^\circ$. This suggests the breakdown of
-    Eq.~\eqref{eq:nonad_q_f} is caused by the breakdown of the nonadiabatic
-    assumption rather than proximity to $\theta_f =
-    90^\circ$.}\label{fig:nonad_3_scan_20}
+    \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$.
+    }\label{fig:nonad_3_scan_20}
 \end{figure}
@@
 \section{Summary and Discussion}\label{s:disc}
+
+%DL: Not done yet
 
@@
 \begin{enumerate}
-    \item In the adiabatic limit, we are able to reproduce the known result
-        $\theta_{\rm f} = 90^\circ$ for $\theta_{\rm sd, i} \approx 0$
-        \citep{millholland_disk}. We demonstrate via numerical simulation and
-        analytical argument the dual-valued behavior of $\theta_{\rm f}$ as
-        nonzero initial spin-disk misalignment angles $\theta_{\rm sd, i}$ are
-        permitted (see Fig.~\ref{fig:ad_ensemble}). We are able to capture both
-        the exact final $\theta_{\rm f}$ values and the probabilities of
-        observing each value via careful accounting of enclosed phase space area
-        and separatrix crossing dynamics.
+    \item In the adiabatic limit, we reproduce the known result $\theta_{\rm f}
+        = 90^\circ$ for $\theta_{\rm sd, i} \approx 0$ \citep{millholland_disk}.
+        We demonstrate via numerical simulation and analytical argument the
+        dual-valued behavior of $\theta_{\rm f}$ as nonzero initial spin-disk
+        misalignment angles $\theta_{\rm sd, i}$ are permitted (see
+        Fig.~\ref{fig:ad_ensemble}). We are able to capture both the exact final
+        $\theta_{\rm f}$ values and the probabilities of observing each value
+        via careful accounting of enclosed phase space area and separatrix
+        crossing dynamics.
 
@@
         a broad range of final obliquities can be reached for a given
-        $\theta_{\rm sd, i}$ (see Fig.~\ref{fig:nonad_3_ensemeble}). We provide
+        $\theta_{\rm sd, i}$ (see Fig.~\ref{fig:nonad_3_ensemble}). We provide
         an analytical expression of the bounds on $\theta_{\rm f}$ in
@@
 
-\section{Derivation of Nonadiabatic Evolution}\label{s:nonad_app}
-
-We present a single result, the derivation of Eq.~\eqref{eq:nonad_q_f}. We take
-Eq.~\eqref{eq:dsdt_base} and choose coordinate axes such that $\uv{l} = \uv{z},
-\uv{l}_{\rm d} = \uv{z} \cos I + \uv{x}\sin I$, then we obtain
-\begin{equation}
-    \rd{\uv{s}}{t} = \s{
-        \p{\eta \cos I - 1}\uv{z} + \eta \sin I \uv{x}} \times \uv{s}.
-\end{equation}
-
-Now, let's assume that $s_{\rm z} \approx \cos I$ throughout the evolution of
-$\uv{s}$ (note that $\theta_{\rm sd, i} = 0$ implies the initial $s_{\rm z} = \cos
-I$). Then let's examine the evolution of quantity $S = s_{\rm x} + is_{\rm y}$ instead:
-\begin{equation}
-    \rd{S}{t} = i\p{\eta\cos I - 1}S - i \eta \sin I\cos I.\label{eq:nonad_ode}
-\end{equation}
-This can be solved via an integrating factor
-\begin{align}
-    \Phi(t) &\equiv \int_{-\infty}^t \p{1 - \eta(t') \cos I}
-        \mathrm{d}t',\\
-    \at{S(t) e^{i\Phi(t)}}_{-\infty}^t
-        &= \int\limits_{-\infty}^t e^{i\Phi(t')}
-            \p{-i\eta(t')\sin I\cos I}\;\mathrm{d}t'\label{eq:nonad_int}
-\end{align}
-We now invoke the stationary phase approximation, asserting that $e^{i\Phi(t)}$
-is dominated by its contribution where $\dot{\Phi} = 0$ (the phases add
-constructively). This occurs where where $1 - \eta\cos I = 0$, or where
-$\eta\cos I = 1$. Choosing initial conditions $\eta(0) = 1/\cos I,
-\at{\rd{\eta}{t}}_{t=0} = -\epsilon/\cos I$, we can then expand near $t = 0$:
-\begin{align}
-    \Phi(t) &\approx \Phi(0) + \frac{1}{2}\ddot{\Phi}t^2,\\
-        &\approx \Phi(0) + \frac{1}{2}\epsilon t^2,\\
-    \int\limits_{-\infty}^t e^{i\Phi(t')}\eta(t')\;\mathrm{d}t'
-        &\approx
-        \begin{cases}
-            0 & t < 0,\\
-            \frac{1}{\cos I}e^{i\Phi(0)}\int\limits_{-\infty}^\infty
-                \exp\s{\frac{i}{2}\epsilon t^2}\;\mathrm{d}t
-                & t > 0.
-        \end{cases}\label{eq:app_phase}\\
-    \int\limits_{-\infty}^\infty
-                \exp\s{\frac{i}{2}\epsilon t^2}\;\mathrm{d}t
-        &= \int\limits_{-\infty}^\infty e^{-\tau^2}\;\mathrm{d}\tau
-            \sqrt{\frac{2}{i\epsilon}},\\
-        &= \sqrt{\frac{2\pi}{i\epsilon}}.
-\end{align}
-
-Now, it should be noted that $e^{i\Phi}$ in Eq.~\ref{eq:app_phase} is just a
-complex phase, and the obliquity excitation depends only on $\abs{S} = \sqrt{1 -
-s_{\rm z}^2}$. Thus, taking the absolute value of both sides of
-Eq.~\eqref{eq:nonad_int}, assuming $S\p{-\infty} \ll S\p{+\infty}$ and noting
-$\theta_{\rm f} \approx \abs{S}(+\infty)$, we obtain
-\begin{equation}
-    \theta_{\rm f} = \tan I\cos I\sqrt{\frac{2\pi}{\epsilon}}.
-        \label{eq:nonad_dong}
-\end{equation}
-
-It should be noted that this result breaks down in two ways:
-\begin{enumerate}
-    \item If the evolution of $\uv{s}$ is adiabatic, then it is invalid to
-        assume $s_{\rm z}$ is approximately constant in time, as many
-        circulation/libration orbits can ensue. We can understand this as
-        requiring $\dot{\eta}$ be sufficiently impulsive that its response
-        dominate the adjustment in $s_{\rm z}$. This is supported by analysis of
-        Figs.~\ref{fig:nonad_3_scan} and~\ref{fig:nonad_3_scan}.
-
-    \item If $\abs{S\p{-\infty}} \gtrsim \abs{S\p{+\infty}}$, then taking the
-        absolute value of both sides of Eq.~\eqref{eq:nonad_int} no longer
-        simply reduces to $\abs{S}\p{+\infty}$. This corresponds to the extreme
-        limit where $\eta$ changes so suddenly that $\uv{s}$ has no time to
-        respond and remains roughly unchanged as $\eta \to 0$. However,
-        regardless of how quickly $\eta$ evolves, the final obliquity must
-        satisfy $\theta_{\rm f} \geq \theta_{\rm sd, i}$, so the correct
-        estimate can be roughly amended
-        \begin{equation}
-            \theta_{\rm f} \simeq \min\p{\tan I\cos
-                I\sqrt{\frac{2\pi}{\epsilon}}, \theta_{\rm sd, i}}.
-        \end{equation}
-\end{enumerate}
-
-Finally, we note the resemblance of this nonadiabatic result to the well-known
-eccentricity excitation of an asteroid sweeping through a secular resonance
-\citep{malhotra_calc}. Both results have the same scaling with repsect to the
-rate of change of secular frequency, $\epsilon$ in our notation and $\lambda$ in
-theirs.
-
 \bsp

### 2020-04-12 initial/99_misc/1_areas.py

@@ -73,7 +73,7 @@ def plot_areas(I=np.radians(5), filename='1_areas'):
     A1ys = 2 * np.pi * (1 - eta * np.cos(I)) - A2ys / 2
     A3ys = 2 * np.pi * (1 + eta * np.cos(I)) - A2ys / 2
     fig, ax1 = plt.subplots(1, 1)
-    ax3 = ax1.twinx()
+    # ax3 = ax1.twinx()
     ax4 = ax1.twiny()
     ax1.plot(eta, A1ys / (4 * np.pi), 'g:', lw=LW/2)
     ax1.plot(eta, A1w / (4 * np.pi), 'g', label=r'$A_{\rm I}$')
@@ -96,7 +96,7 @@ def plot_areas(I=np.radians(5), filename='1_areas'):
     ax1.set_xticklabels([r'$0$', r'$0.3$', r'$0.6$', r'$0.9$'])
     old_ylims = ax1.get_ylim()
     ax1.set_ylim([0, old_ylims[1]])
-    ax3.set_ylim([0, old_ylims[1]])
+    # ax3.set_ylim([0, old_ylims[1]])
     ax1.set_xlim([0, 1.2 * eta_c])
     ax4.set_xlim([0, 1.2 * eta_c])
 
@@ -104,8 +104,8 @@ def plot_areas(I=np.radians(5), filename='1_areas'):
     crit_vals_y = [A_sep_crit]
     # for val in crit_vals_y:
     #     ax3.axhline(val, c='k', lw=2.0, ls='dashed')
-    ax3.set_yticks(crit_vals_y)
-    ax3.set_yticklabels([r'$A_{\rm II}(\eta_c)$'])
+    # ax3.set_yticks(crit_vals_y)
+    # ax3.set_yticklabels([r'$A_{\rm II}(\eta_c)$'])
     eta_2_max = eta[np.argmax(A2w)]
     eta_3_min = eta[np.argmin(A3w)]
     crit_vals_x = [eta_c, eta_2_max, eta_3_min]
@@ -116,9 +116,9 @@ def plot_areas(I=np.radians(5), filename='1_areas'):
                          r'$\eta_{\max,II}$',
                          r'$\eta_{\min,III}$'])
 
-    plt.title(r'$I = %d^\circ$' % np.degrees(I))
+    # plt.title(r'$I = %d^\circ$' % np.degrees(I))
     plt.tight_layout()
-    plt.savefig(filename, dpi=400)
[…]

### 2020-04-12 initial/99_misc/2_rand_plots.py

@@ -147,7 +147,7 @@ def plot_3vec():
     offset = 0.02 # offset for text from arrow tip
     alpha = 0.8
 
-    fig, ax = plt.subplots(1, 1, figsize=(6, 6))
+    fig, ax = plt.subplots(1, 1, figsize=(4, 4))
     plt.axis('off')
     ax.set_xlim(0.2, 1.1)
     ax.set_ylim(-0.1, 1.1)
@@ -198,7 +198,7 @@ def plot_3vec():
             np.cos(np.radians(ld_q * 0.6)) * 0.5 + offset,
             r'$I$',
             fontdict={'c': l_c})
-    ax.text(1 - np.sin(np.radians(0.8 * s_q)) * 0.3 - 2 * offset,
+    ax.text(1 - np.sin(np.radians(0.8 * s_q)) * 0.3 - 4 * offset,
             np.cos(np.radians(0.8 * s_q)) * 0.3 + 2 * offset,
             r'$+\theta$',
             fontdict={'c': s_c})
@@ -214,5 +214,5 @@ def plot_3vec():
 
 if __name__ == '__main__':
     # plot_cs(np.radians(5))
-    plot_eigens(np.radians(5))
-    # plot_3vec()
+    # plot_eigens(np.radians(5))
+    plot_3vec()

### 2020-04-13 writeups/Su_disk_disp.tex
check in draft 2 maybe?

@@
     \caption{Cassini state obliquities as a function of $\eta$ for $I =
-    5^\circ$. The vertical dashed line indicates $\eta_{\rm c}$ ($= 0.766$ for
-    $I = 5^\circ$), where CS1 and CS4 merge and annihilate, and the horizontal
-    dashed lines indicate $\theta = I$ and $I - 180^\circ$, the asymptotic
-    values for CSs 2 and 3 for $\eta \gg \eta_{\rm c}$.}\label{fig:cs_locs}
+    5^\circ$. The thin vertical dashed line indicates $\eta_{\rm c}$ ($= 0.766$
+    for $I = 5^\circ$), where CS1 and CS4 merge and annihilate, and the thin
+    horizontal dashed lines indicate $\theta = I$ and $I - 180^\circ$, the
+    asymptotic values for CSs 2 and 3 for $\eta \gg \eta_{\rm
+    c}$.}\label{fig:cs_locs}
 \end{figure}
@@
 \begin{equation}
-    \epsilon \lesssim \frac{1}{2\pi}\sqrt{\eta\sin I \sin \theta_2
+    \epsilon \lesssim \epsilon_{\rm c} \equiv
+        \frac{1}{2\pi}\sqrt{\eta\sin I \sin \theta_2
             \p{1 + \eta \sin I \csc^3 \theta_2}},
@@
 For $I = 5^\circ$, $\eta \sim \eta_{\rm c}$ Eq.~\eqref{eq:ad_constr} gives
-$\epsilon \lesssim 0.085$. Since our criterion is only a weak condition for
+$\epsilon_{\rm c} = 0.085$. Since our criterion is only a weak condition for
 diabaticity, we use $\epsilon = 3 \times 10^{-4}$ in our ``adiabatic''
@@
 entire range $\theta_{\rm sd, i} \in [0, \pi]$ and choose $\epsilon = 3 \times
-10^{-4}$ so that the system evolves almost adiabatically (see above).
+10^{-4}$ (see above).
 
@@
 In Section~\ref{s:ad}, we have examined the spin axis evolution in the limit
-where $\epsilon \ll 1$ [see Eq.~\eqref{eq:ad_constr}] and the evolution is
-mostly adiabatic (except at separatrix crossings). We now consider nonadiabatic
-effects.
+where $\epsilon \ll \epsilon_{\rm c}$ [see Eq.~\eqref{eq:ad_constr}] and the
+evolution is mostly adiabatic (except at separatrix crossings). We now consider
+nonadiabatic effects.
 
 \subsection{Transition to Non-adiabaticity: Results for $\epsilon\lesssim
-1$}\label{ss:transition}
+\epsilon_{\rm c}$}\label{ss:transition}
 
@@
 
-\subsection{Non-adiabatic Evolution: Result for $\epsilon\gtrsim 1$}
+\subsection{Non-adiabatic Evolution:
+Result for $\epsilon\gtrsim \epsilon_{\rm c}$}
 
 In general, numerical calculations are needed to determine the non-adiabatic
-obliquity evolution ($\epsilon\gtrsim 1$). However, some analytical results can
-be still be obtained when the obliquity remains small throughout the evolution.
+obliquity evolution ($\epsilon\gtrsim \epsilon_{\rm c}$). However, some
+analytical results can be still be obtained when the obliquity change is small.
 
@@
     \rd{\uv{s}}{\tau} = \s{
-        \p{\eta \cos I - \cos\theta}\uv{z} + \eta \sin I \,\uv{x}} \times \uv{s}.
-\end{equation}
-%Now, let's assume that $s_{\rm z} \approx \cos I$ throughout the evolution of
-%$\uv{s}$ (note that $\theta_{\rm sd, i} = 0$ implies the initial $s_{\rm z} = \cos I$).
+        \p{\eta \cos I - 1}\uv{z} + \eta \sin I \,\uv{x}} \times \uv{s}.
+\end{equation}
 Define $S = {\hat s}_{\rm x} + i{\hat s}_{\rm y}$, we find
 \begin{equation}
-    \rd{S}{\tau} = i\p{\eta\cos I - \cos\theta}S - i \eta \sin I\cos\theta.\label{eq:nonad_ode}
-\end{equation}
-To proceed, we assume $\theta$ is small and set $\cos\theta \simeq 1$. Equation
-(\ref{eq:nonad_ode}) can then be solved explicitly, starting from the initial
-value $S(\tau_{\rm i})$:
+    \rd{S}{\tau} = i\p{\eta\cos I - 1}S
+        - i \eta \sin I\cos\theta.\label{eq:nonad_ode}
+\end{equation}
+To proceed, we assume the obliquity is roughly constant, $\cos \theta \approx
+\cos \theta_{\rm i}$. Eq.~\eqref{eq:nonad_ode} can then be solved explicitly,
+starting from the initial value $S(\tau_{\rm i})$:
 \begin{equation}
     S(\tau)e^{-i\Phi(\tau)} - S(\tau_{\rm i})
-        \simeq -i\sin I\int_{\tau_{\rm i}}^\tau \eta(\tau')
+        \simeq -i\sin I \cos \theta_{\rm i}
+            \int_{\tau_{\rm i}}^\tau \eta(\tau')
             e^{-i\Phi(\tau')}\;\mathrm{d}\tau',
@@
 \begin{equation}
-    \Phi(\tau) \equiv \int_{\tau_{\rm i}}^\tau \p{\eta(\tau') \cos I -1}\;
-        \mathrm{d}\tau'.
+    \Phi(\tau) \equiv \int_{\tau_{\rm i}}^\tau \p{\eta(\tau') \cos I
+        - 1}\; \mathrm{d}\tau'.
 \end{equation}
 We now invoke the stationary phase approximation, so that $\Phi(\tau)\simeq
-\Phi(\tau_0) + (1/2)\ddot\Phi (\tau_0)(\tau - \tau_0)^2$, where $\tau_0$ is
-determined by $\dot\Phi=0$ or $\eta_0=1/\cos I$. We then find, for $\tau\gg
-\tau_0$,
-\begin{equation}
-    S(\tau)e^{-i\Phi(\tau)}-S(\tau_{\rm i})\simeq -i\sin I\,\eta(\tau_0)\, e^{-i\Phi(\tau_0)}
+\Phi(\tau_0) + (1/2)\ddot\Phi (\tau_0)(\tau - \tau_0)^2$ where $\tau_0$ is
+determined by $\dot\Phi = 0$, occuring when $\eta_0 = 1/\cos I$. We then find,
+for $\tau \gg \tau_0$,
+\begin{equation}
+    S(\tau)e^{-i\Phi(\tau)} - S(\tau_{\rm i})
+        \simeq -i \eta(\tau_0)\sin I \cos \theta_{\rm i} e^{-i\Phi(\tau_0)}
             \p{\frac{2\pi}{i \ddot\Phi(\tau_0)}}^{1/2}.
@@
 \begin{equation}
-    S(\tau)e^{-i\Phi(\tau)}-S(\tau_{\rm i})
-        \simeq -i^{3/2}\tan I\, e^{-i\Phi(\tau_0)}
+    S(\tau)e^{-i\Phi(\tau)} - S(\tau_{\rm i})
+        \simeq -i^{3/2}\tan I \cos \theta_{\rm i} e^{-i\Phi(\tau_0)}
             \p{\frac{2\pi}{\epsilon}}^{1/2}.
 \end{equation}
-If the initial obliquity is negligible ($\theta_{\rm i} = \abs{S(\tau_{\rm
-i})} \ll 1$), the final obliquity is given by
-\begin{equation}
-    \theta_{\rm f}\simeq \sqrt{\frac{2\pi}{\epsilon}}\tan I.\label{eq:nonad_q_f}
-\end{equation}
-This expression is valid only if $\theta_f$ is small (recall that we have used
-the approximation $\cos\theta\simeq 1$ in the above derivation).
-
-We can generalize the above analytic result to nonzero initial spin-disc
-angle $\theta_{\rm sd, i}$ by assuming the amplitude
-of libration of $\uv{s}$ about $\uv{l}_{\rm d}$ (namely $\theta_{\rm sd, i}$)
-is equal to the range of final obliquities when the disk dissipates quickly.
-Intuitively, this corresponds to ``freezing in'' the variations in initial
-obliquity over a single libration cycle to the final obliquity. Thus we expect
-\begin{equation}
-  \theta_{\rm f} - \sqrt{\frac{2\pi}{\epsilon}} \tan I
-  \in \s{-\theta_{\rm sd, i}, \theta_{\rm sd,i}}.\label{eq:nonad_q_f_dist}
-\end{equation}
+If the initial obliquity is much smaller than the final obliquity ($\theta_{\rm
+i} = \abs{S(\tau_{\rm i})} \ll \abs{S(\tau_{\rm f})}$), then we obtain
+\begin{equation}
+    \theta_{\rm f}\simeq \sqrt{\frac{2\pi}{\epsilon}}\tan I\cos \theta_{\rm i}.
+        \label{eq:nonad_q_f}
+\end{equation}
+This expression is valid only if $\cos \theta \approx \cos \theta_{\rm i}$
+throughout the evolution. This corresponds to the limit where $\theta_{\rm f}$
+is not too much larger than $\theta_{\rm i}$, which requires $\epsilon$ not to
+be too small. Numerically, we verify this is consistent with being in the
+nonadiabatic regime $\epsilon \gtrsim \epsilon_{\rm c}$ (see
+Figs.~\ref{fig:nonad_3_scan} and~\ref{fig:nonad_3_scan_20}).
+
+We must next understand the above results in terms of the initial spin-disk
+misalignment angle $\theta_{\rm sd, i}$. To do so, we first compute the final
+obliquity when $\theta_{\rm sd, i} = 0$, corresponding to initial obliquity
+$\theta_{\rm i} = \theta_2 \approx I$. The set of possible initial conditions
+for nonzero $\theta_{\rm sd, i}$ is a ring of angular width $\theta_{\rm sd, i}$
+about CS2. We find this ring evolves to a new ring of angular width $\theta_{\rm
+sd, i}$ about the $\theta_{\rm sd, i} = 0$ prediction, so the range of final
+obliquities is the $\theta$ range spanned by this final ring\footnote{The
+interpretation for this procedure is that the process generating the final
+obliquity predicted by Eq.~\eqref{eq:nonad_q_f} acts only on the \emph{center}
+of libration of the trajectory when $\eta \gg 1$ (CS2). This is not apparent
+from our derivation but reproduces the results of the numerical simulation.}.
+This procedure yields prediction
+\begin{equation}
+    \abs{\p{\sqrt{\frac{2\pi}{\epsilon}}\tan I\cos I - \theta_{\rm sd, i}}}
+    \leq \theta_{\rm f}
+    \leq
+    \sqrt{\frac{2\pi}{\epsilon}}\tan I\cos I + \theta_{\rm sd, i}
+    .\label{eq:nonad_q_f_dist}
+\end{equation}
+The absolute value in the lower bound is a result of the ring of final
+conditions crossing the North pole.
 
@@
 vs $\theta_{\rm sd,i}$ for $I = 5^\circ$ and $\epsilon = 0.3$. We see that
-Eq.~(\ref{eq:nonad_q_f_dist}) provides good lower and upper bounds of the final
-obliquity for $\theta_{\rm sd,i} \lesssim 20^\circ$.
+Eq.~\eqref{eq:nonad_q_f_dist} provides good lower and upper bounds of the final
+obliquity for $\theta_{\rm sd,i} \lesssim 45^\circ$.
 
@@
     $\epsilon = 0.3$ (firmly in the nonadiabatic regime). The blue dots
-    represent numerical result, and the two red lines show the analytical lower
+    represent numerical results, and the two red lines show the analytical lower
     and upper limits given by
@@
 Eq.~\eqref{eq:nonad_q_f} is excellent, particularly for the $I = 5^\circ$ case.
-The agreement when $I = 20^\circ$ is poorer as the initial obliquity
-$\theta_{\rm i} = I$ is larger, violating one of our key assumptions. For
-$\epsilon \ll 1$, we find $\theta_f \simeq 90^\circ$, in agreement with the
+The agreement when $I = 20^\circ$ is slightly poorer as $\theta_{\rm i}$ is
+larger and hence less negligible in Eq.~\eqref{eq:nonad_q_f}. For $\epsilon \ll
+\epsilon_{\rm c}$, we find $\theta_f \simeq 90^\circ$, in agreement with the
 result of adiabatic evolution (see Fig.~\ref{fig:ad_ensemble}).
@@
     Eq.~\eqref{eq:ad_constr}. The blue dots are numerical results, and the red
-    line corresponds to Eq.~\eqref{eq:nonad_q_f}, which is in good agreement
-    with numerical results for $\epsilon \gtrsim 0.1$ (the nonadiabatic regime);
-    $\theta_{\rm f} \simeq  90^\circ$ in the adiabatic regime ($\epsilon\ll
-    1$).}\label{fig:nonad_3_scan}
+    dashed line corresponds to Eq.~\eqref{eq:nonad_q_f}, which is in good
+    agreement with numerical results for $\epsilon > \epsilon_{\rm c} \approx
+    0.1$ (the nonadiabatic regime); $\theta_{\rm f} \simeq  90^\circ$ in the
+    adiabatic regime ($\epsilon\ll \epsilon_{\rm c}$).}\label{fig:nonad_3_scan}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3scan_20.png}
-    \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$.
-    }\label{fig:nonad_3_scan_20}
+    \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$. The right
+    shaded area is where $\theta_{\rm f}$ predicted by Eq.~\eqref{eq:nonad_q_f}
+    violates the assumption $\theta_{\rm f} \gg \theta_{\rm
+    i}$.}\label{fig:nonad_3_scan_20}
 \end{figure}
@@
     is a saddle point ($\lambda^2 > 0$) when it exists while all others are
-    stable ($\lambda^2 < 0$). The horizontal dashed line is the instability
-    boundary $\lambda^2 = 0$ while the vertical dashed line labels $\eta =
+    stable ($\lambda^2 < 0$). The thin horizontal dashed line is the instability
+    boundary $\lambda^2 = 0$ while the thin vertical dashed line labels $\eta =
     \eta_{\rm c}$.}\label{fig:lambda2}

### 2020-04-13 writeups/Su_disk_disp.tex
add theta_f definition

@@
 If the initial obliquity is much smaller than the final obliquity ($\theta_{\rm
-i} = \abs{S(\tau_{\rm i})} \ll \abs{S(\tau_{\rm f})}$), then we obtain
+i} = \abs{S(\tau_{\rm i})} \ll \theta_{\rm f} = \abs{S(\tau_{\rm f})}$), then we
+obtain
 \begin{equation}

### 2020-04-14 writeups/Su_disk_disp.tex
fix nonadiabatic calculation that I incorrectly 'fixed'

@@
 We start from Eq.~\eqref{eq:dsdt_base}, which governs the evolution of the spin
-axis. We choose coordinate axes such that $\uv{l} = \uv{z}$ and $ \uv{l}_{\rm d}
-= \uv{z} \cos I + \uv{x}\sin I$, giving
-\begin{equation}
-    \rd{\uv{s}}{\tau} = \s{
-        \p{\eta \cos I - 1}\uv{z} + \eta \sin I \,\uv{x}} \times \uv{s}.
-\end{equation}
-Define $S = {\hat s}_{\rm x} + i{\hat s}_{\rm y}$, we find
-\begin{equation}
-    \rd{S}{\tau} = i\p{\eta\cos I - 1}S
+axis in the rotating frame. We choose coordinate axes such that $\uv{l} =
+\uv{z}$ and $ \uv{l}_{\rm d} = \uv{z} \cos I + \uv{x}\sin I$, giving
+\begin{equation}
+    \p{\rd{\uv{s}}{\tau}}_{\rm rot} = \s{
+        \p{\eta \cos I - \cos \theta}\uv{z}
+            + \eta \sin I \,\uv{x}} \times \uv{s}.
+\end{equation}
+Defining $S = {\hat s}_{\rm x} + i{\hat s}_{\rm y}$ in the rotating frame, we
+find
+\begin{equation}
+    \rd{S}{\tau} = i\p{\eta\cos I - \cos \theta}S
         - i \eta \sin I\cos\theta.\label{eq:nonad_ode}
@@
     \Phi(\tau) \equiv \int_{\tau_{\rm i}}^\tau \p{\eta(\tau') \cos I
-        - 1}\; \mathrm{d}\tau'.
+        - \cos \theta_{\rm i}}\; \mathrm{d}\tau'.
 \end{equation}
@@
 \Phi(\tau_0) + (1/2)\ddot\Phi (\tau_0)(\tau - \tau_0)^2$ where $\tau_0$ is
-determined by $\dot\Phi = 0$, occuring when $\eta_0 = 1/\cos I$. We then find,
-for $\tau \gg \tau_0$,
+determined by $\dot\Phi = 0$, occuring when $\eta_0 = \cos \theta_i /\cos I$. We
+then find, for $\tau \gg \tau_0$,
 \begin{equation}
@@
     S(\tau)e^{-i\Phi(\tau)} - S(\tau_{\rm i})
-        \simeq -i^{3/2}\tan I \cos \theta_{\rm i} e^{-i\Phi(\tau_0)}
+        \simeq -i^{3/2}\tan I \cos^2\theta_{\rm i} e^{-i\Phi(\tau_0)}
             \p{\frac{2\pi}{\epsilon}}^{1/2}.
@@
 \begin{equation}
-    \theta_{\rm f}\simeq \sqrt{\frac{2\pi}{\epsilon}}\tan I\cos \theta_{\rm i}.
+    \theta_{\rm f}\simeq \sqrt{\frac{2\pi}{\epsilon}}\tan I\cos^2\theta_{\rm i}.
         \label{eq:nonad_q_f}
@@
 obliquity when $\theta_{\rm sd, i} = 0$, corresponding to initial obliquity
-$\theta_{\rm i} = \theta_2 \approx I$. The set of possible initial conditions
+$\theta_{\rm i} = I$. The set of possible initial conditions
 for nonzero $\theta_{\rm sd, i}$ is a ring of angular width $\theta_{\rm sd, i}$
-about CS2. We find this ring evolves to a new ring of angular width $\theta_{\rm
-sd, i}$ about the $\theta_{\rm sd, i} = 0$ prediction, so the range of final
-obliquities is the $\theta$ range spanned by this final ring\footnote{The
-interpretation for this procedure is that the process generating the final
-obliquity predicted by Eq.~\eqref{eq:nonad_q_f} acts only on the \emph{center}
-of libration of the trajectory when $\eta \gg 1$ (CS2). This is not apparent
-from our derivation but reproduces the results of the numerical simulation.}.
-This procedure yields prediction
-\begin{equation}
-    \abs{\p{\sqrt{\frac{2\pi}{\epsilon}}\tan I\cos I - \theta_{\rm sd, i}}}
+about $\uv{l}_{\rm d}$. We find this ring evolves to a new ring of angular width
+$\theta_{\rm sd, i}$ about the $\theta_{\rm sd, i} = 0$ prediction, so the range
+of final obliquities is the $\theta$ range spanned by this final
+ring\footnote{The interpretation for this procedure is that the process
+generating the final obliquity predicted by Eq.~\eqref{eq:nonad_q_f} acts only
+on the \emph{center} of libration of the trajectory when $\eta \gg 1$ (CS2).
+This is not apparent from our derivation but reproduces the results of the
+numerical simulation.}. This procedure yields prediction
+\begin{equation}
+    \abs{\sqrt{\frac{2\pi}{\epsilon}}\frac{\sin \p{2I}}{2}
+        - \theta_{\rm sd, i}}
     \leq \theta_{\rm f}
-    \leq
-    \sqrt{\frac{2\pi}{\epsilon}}\tan I\cos I + \theta_{\rm sd, i}
+    \leq \sqrt{\frac{2\pi}{\epsilon}}\frac{\sin\p{2I}}{2} + \theta_{\rm sd, i}
     .\label{eq:nonad_q_f_dist}

### 2020-04-15 writeups/Su_disk_disp.tex
another nonad thetasdi writeup

@@
 Recently, \citet{millholland_disk} studied the production of planet obliquities
-via spin-orbit resonance, where a dissipating protoplanetary disk causes
+via a spin-orbit resonance, where a dissipating protoplanetary disk causes
 resonance capture and advection. In their work, a planet is accompanied by an
-inclined exterior disk; as the disk graduatelly dissipates, the resulting
-planetary obliquity is generally substantial, reaching $90^\circ$ for what they
-characterize as adiabatic resonance crossings.
+inclined exterior disk; as the disk gradually dissipates, the planetary
+obliquity increases, reaching $90^\circ$ for what the authors characterize as
+adiabatic resonance crossings.
 
@@
 The paper is organized as follows. In Section~\ref{s:eq}, we review the relevant
-spin-orbit dynamics, equations and key concepts that are used in the remainder
-of the paper. In Sections~\ref{s:ad} and~\ref{s:nonad}, we study the evolution
-of the system when the disk dissipates on different timescales, from highly
-adiabatic to nonadiabatic. Analytical results are presented to explain the
-numerical results in both limits. We discuss the implications of our results in
+spin-orbit dynamics and key concepts that are used in the remainder of the
+paper. In Sections~\ref{s:ad} and~\ref{s:nonad}, we study the evolution of the
+system when the disk dissipates on different timescales, from highly adiabatic
+to nonadiabatic. Analytical results are presented to explain the numerical
+results in both limits. We discuss the implications of our results in
 Section~\ref{s:disc}. Our primary physical results consist of
@@
 corresponding unit vectors are $\uv{s} \equiv \bm{S} / S$, $\uv{l} \equiv \bm{L}
-/ L$, and $\uv{l}_{\rm d} \equiv \bm{L}_{\rm
-d} / L_{\rm d}$.
+/ L$, and $\uv{l}_{\rm d} \equiv \bm{L}_{\rm d} / L_{\rm d}$.
 
@@
 sides of $\uv{l}$, while CS2 has $\phi = \pi$ and $\theta > 0$, corresponding to
-$\uv{s}$ and $\uv{l}_{\rm d}$ being on the same side of $\uv{l}$. When $\eta <
-\eta_{\rm
-c}$, where
+$\uv{s}$ and $\uv{l}_{\rm d}$ being on the same side of $\uv{l}$.
+The CS obliquity satisfie
+\begin{equation}
+    \sin \theta \cos \theta - \eta \sin\p{\theta - I} = 0.
+\end{equation}
+When $\eta < \eta_{\rm c}$, where
 \begin{equation}
@@
     $A_{\rm i}(\eta) / 4\pi$ as given by Eqs.~\eqref{se:area_ward}. The colored
-    dashed lines correspond to small $\eta$ approximations used in
+    dotted lines correspond to small $\eta$ approximations used in
     Appendix~\ref{s:ad_approx}. The colored dashed lines for $\eta > \eta_{\rm
@@
     \eta_{\rm c}$, denoting the points that would flow into either area under
-    adiabatic decrease of $\eta$ from $\eta > \eta_{\rm c}$ (see the text). The vertical black
-    dashed lines correspond to $\eta = \eta_{\rm c}$ [Eq.\eqref{eq:etac}] and
-    the values of $\eta$ for which $A_{\rm II}$ is maximized ($\eta_{\rm \max,
-    II}$) and for which $A_{\rm III}$ is minimized ($\eta_{\rm \min, III}$,
-    Eq.~\eqref{eq:eta_minIII}).}\label{fig:eq_areas}
+    adiabatic decrease of $\eta$ from $\eta > \eta_{\rm c}$ (see the text). The
+    vertical black dashed lines correspond to $\eta = \eta_{\rm c}$
+    [Eq.\eqref{eq:etac}] and the values of $\eta$ for which $A_{\rm II}$ is
+    maximized ($\eta_{\rm \max, II}$) and for which $A_{\rm III}$ is minimized
+    ($\eta_{\rm \min, III}$, Eq.~\eqref{eq:eta_minIII}).}\label{fig:eq_areas}
 \end{figure}
@@
 
-In this section, we study the evolution of the planetary obliquity $\theta$ when
+In this appendix, we study the evolution of the planetary obliquity $\theta$ when
 the parameter $\eta$ [or the disk mass $M_{\rm d}$; see Eqs.~\eqref{eq:eta}
@@
 
-We must next understand the above results in terms of the initial spin-disk
-misalignment angle $\theta_{\rm sd, i}$. To do so, we first compute the final
-obliquity when $\theta_{\rm sd, i} = 0$, corresponding to initial obliquity
-$\theta_{\rm i} = I$. The set of possible initial conditions
-for nonzero $\theta_{\rm sd, i}$ is a ring of angular width $\theta_{\rm sd, i}$
-about $\uv{l}_{\rm d}$. We find this ring evolves to a new ring of angular width
-$\theta_{\rm sd, i}$ about the $\theta_{\rm sd, i} = 0$ prediction, so the range
-of final obliquities is the $\theta$ range spanned by this final
-ring\footnote{The interpretation for this procedure is that the process
-generating the final obliquity predicted by Eq.~\eqref{eq:nonad_q_f} acts only
-on the \emph{center} of libration of the trajectory when $\eta \gg 1$ (CS2).
-This is not apparent from our derivation but reproduces the results of the
-numerical simulation.}. This procedure yields prediction
+The above calculation is performed for initial condition $\theta_{\rm i}$, but,
+as discussed earlier in the text, the initial spin orientation is more
+appropriately described by $\theta_{\rm sd, i}$. The correct way to predict
+final obliquities for such initial conditions using Eq.~\eqref{eq:nonad_q_f} is
+somewhat indirect but yields good agreement with numerical results. We develop
+the procedure for two cases: (i) for $\theta_{\rm sd, i} = 0$, then (ii) for
+nonzero $\theta_{\rm sd, i}$. To simplify the discussion below, we consider the
+limit where $\eta_{\rm i} \to \infty$, and CS2 and $\uv{l}_d$ coincide. The
+nonadiabatic evolution is then described by:
+\begin{itemize}
+    \item When $\theta_{\rm sd, i} = 0$, the initial condition is just CS2, so
+        Eq.~\eqref{eq:nonad_q_f} can be directly applied setting $\theta_{\rm i}
+        = I$. This yields good agreement with numerical results (see
+        Figs.~\ref{fig:nonad_3_scan} and~\ref{fig:nonad_3_scan_20}). We denote
+        this final obliquity
+        \begin{equation}
+            \theta_{\rm f} = \sqrt{\frac{2\pi}{\epsilon}}\frac{\sin (2I)}{2}.
+                \label{eq:theta_2f}
+        \end{equation}
+        The azimuthal angle of the spin vector does not change and remains $\phi
+        = \pi$. Figures~\ref{fig:nonad_3_scan} and~\ref{fig:nonad_3_scan_20}
+        show the final obliquity as function of $\epsilon$ for $\theta_{\rm
+        sd,i} = 0$ and $I = 5$, $20^\circ$. We see that the agreement between
+        the numerical results and Eq.~\eqref{eq:nonad_q_f} is excellent,
+        particularly for the $I = 5^\circ$ case. The agreement when $I =
+        20^\circ$ is slightly poorer as $\theta_{\rm i}$ is larger and hence
+        less negligible in Eq.~\eqref{eq:nonad_q_f}. For $\epsilon \ll
+        \epsilon_{\rm c}$, we find $\theta_f \simeq 90^\circ$, in agreement with
+        the result of adiabatic evolution (see Fig.~\ref{fig:ad_ensemble}).
+
+    \item When $\theta_{\rm sd, i}$ is permitted to be nonzero, the set of
+        possible initial conditions forms a ring of angular width $\theta_{\rm
+        sd, i}$ about CS2. We find that this set of initial conditions
+        approximately evolves under nonadiabatic evolution to a ring of angular
+        width $\theta_{\rm sd, i}$ about the $\theta_{\rm sd, i} = 0$ prediction
+        given by Eq.~\eqref{eq:theta_2f}. The range of possible final
+        obliquities is the range of $\theta$ spanned by this ring of possible
+        outcomes. This can be solved in closed form, yielding generalization of
+        Eq.~\eqref{eq:theta_2f}
         \begin{equation}
@@
             \leq \theta_{\rm f}
-    \leq \sqrt{\frac{2\pi}{\epsilon}}\frac{\sin\p{2I}}{2} + \theta_{\rm sd, i}
-    .\label{eq:nonad_q_f_dist}
+            \leq \sqrt{\frac{2\pi}{\epsilon}}\frac{\sin\p{2I}}{2}
+                + \theta_{\rm sd, i} .\label{eq:nonad_q_f_dist}
         \end{equation}
         The absolute value in the lower bound is a result of the ring of final
-conditions crossing the North pole.
-
-In Fig.~\ref{fig:nonad_3_ensemble}, we show the numerical result of $\theta_f$
-vs $\theta_{\rm sd,i}$ for $I = 5^\circ$ and $\epsilon = 0.3$. We see that
-Eq.~\eqref{eq:nonad_q_f_dist} provides good lower and upper bounds of the final
-obliquity for $\theta_{\rm sd,i} \lesssim 45^\circ$.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_05.png}
-    \caption{$\theta_{\rm  f}$ vs $\theta_{\rm sd, i}$ for $I=5^\circ$ and
-    $\epsilon = 0.3$ (firmly in the nonadiabatic regime). The blue dots
-    represent numerical results, and the two red lines show the analytical lower
-    and upper limits given by
-    Eq.~\eqref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemble}
-\end{figure}
-
-Figures~\ref{fig:nonad_3_scan} and~\ref{fig:nonad_3_scan_20} show $\theta_f$ as
-function of $\epsilon$ for $\theta_{\rm sd,i} = 0$ and $I = 5$, $20^\circ$. We
-see that the agreement between the numerical results and
-Eq.~\eqref{eq:nonad_q_f} is excellent, particularly for the $I = 5^\circ$ case.
-The agreement when $I = 20^\circ$ is slightly poorer as $\theta_{\rm i}$ is
-larger and hence less negligible in Eq.~\eqref{eq:nonad_q_f}. For $\epsilon \ll
-\epsilon_{\rm c}$, we find $\theta_f \simeq 90^\circ$, in agreement with the
-result of adiabatic evolution (see Fig.~\ref{fig:ad_ensemble}).
+        conditions crossing the North pole. Fig.~\ref{fig:nonad_3_ensemble}
+        shows the numerical result of $\theta_f$ vs $\theta_{\rm sd,i}$ for $I =
+        5^\circ$ and $\epsilon = 0.3$. We see that Eq.~\eqref{eq:nonad_q_f_dist}
+        provides good lower and upper bounds of the final obliquity for
+        $\theta_{\rm sd,i} \lesssim 45^\circ$.
+\end{itemize}
 
@@
     i}$.}\label{fig:nonad_3_scan_20}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_05.png}
+    \caption{$\theta_{\rm  f}$ vs $\theta_{\rm sd, i}$ for $I=5^\circ$
+    and $\epsilon = 0.3$ (firmly in the nonadiabatic regime). The blue
+    dots represent numerical results, and the two red lines show the
+    analytical lower and upper limits given by
+    Eq.~\eqref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemble}
 \end{figure}
@@
 In this section, we linearize the equations of motion near each CS\@. We
-determine the stability of each CS and the local libration frequencies of the
-stable CSs.
-
-\subsection{Canonical Equations of Motion and Solutions}
-
-For analytical work, we adopt spherical coordinate system where $\uv{l} =
+determine the stability of each CS and the local libration frequencies or growth
+rates of the CSs.
+
+\subsection{Canonical Equations of Motion and Solutions}\label{ss:canonical}
+
+We adopt spherical coordinate system where $\uv{l} =
 \uv{z}$ and $\theta, \phi$ are the polar and azimuthal angle of $\uv{s}$. We
-choose $\uv{l}_{\rm z}$ at coordinates $\theta = I, \phi = \pi$ (see
-Figs.~\ref{fig:cs_vecs} and~\ref{fig:cs_locs}). Following modern mathematical
-convention, we will use
+choose $\uv{l}_{\rm d}$ at coordinates $\theta = I, \phi = \pi$ (see
+Figs.~\ref{fig:cs_vecs} and~\ref{fig:cs_locs}). We use the convention
 $\theta \in [0, \pi)$% chktex 9
@@
 
-The equations of motion in coordinates $\p{\phi, \cos \theta}$ follow by
+The equations of motion in $\p{\phi, \cos \theta}$ follow by
 applying Hamilton's equations to the Hamiltonian [Eq.~\eqref{eq:H}]:
@@
 \end{subequations}
-These agree with Eq.~\eqref{eq:dsdt_base}. While these equations are numerically
-stiff owing to the $\cot\theta$ term, they are the most intuitive description
-for analytical work.
-
-We next develop some approximate forms for the CS obliquities that will be
-useful for guiding later discussion. Denote $\theta_{\rm cs}$ the obliquity of
-some Cassini State (fixed point of Eqs.~\eqref{se:H_eom}).
-\begin{enumerate}
-    \item $\eta \ll 1, \cos \theta_{\rm cs} \ll 1$ --- This is the limiting case
-        for CS2 and CS4 when $\eta \ll \eta_{\rm c}$. We examine
-        Eqs.~\eqref{seq:H_eom_phi_t} and approximate $\cot \theta \approx \cos
-        \theta$ to find
-        \begin{equation}
-            \cos \theta_{\rm cs} \approx \frac{\eta \cos I}
-                {1 \mp \eta \sin I}.
-        \end{equation}
-        The two signs correspond to choices of $\cos \phi$. Each sign
-        corresponds to one of CS2 and CS4.
-
-    \item $\sin \theta_{\rm cs} \ll 1$ --- The $\eta \ll 1, \eta \gg 1$ cases
-        can be solved together, and are the limiting cases both for CS1 and CS3
-        when $\eta \ll \eta_{\rm c}$, and for CS2 and CS3 when $\eta \gg
-        \eta_{\rm c}$. It proves easiest to rewrite Eqs.~\eqref{seq:H_eom_phi_t}
-        as
-        \begin{equation}
-            0 = \cos \theta_{\rm cs}\p{-1 + 2\eta
-                \frac{\sin \p{I \pm \theta_{\rm cs}}}{\sin \p{2\theta_{\rm
-                    cs}}}}.\label{eq:rewritten_dphi}
-        \end{equation}
-        The $\pm$ choice again comes from choice of $\cos \phi$. Then assuming
-        $\theta_{\rm cs}, I \ll 1$, we obtain $\frac{I \pm
-        \theta_{\rm cs}}{2\theta_{\rm cs}} = \frac{1}{2\eta}$ or
-        \begin{equation}
-            \theta_{\rm cs} = \frac{\eta I}{1 \mp \eta}.
-        \end{equation}
-
-        In the limit $\eta \ll \eta_{\rm c}$, these two solutions describe CS1
-        and CS3, while in the limit $\eta \gg \eta_{\rm c}$ these two solutions
-        describe CS2 and CS3.
-\end{enumerate}
-Again, the $\theta_{\rm cs}$ values derived here do not follow the same
-convention as Fig.~\ref{fig:cs_locs} due to our different $\theta, \phi$
-convention.
+These agree with Eq.~\eqref{eq:dsdt_base}.
+% While these equations are numerically stiff owing to the $\cot\theta$ term, they
+% are the most intuitive description for analytical work.
+
+% We next develop some approximate forms for the CS obliquities that will be
+% useful for guiding later discussion. Denote $\theta_{\rm cs}$ the obliquity of
+% some Cassini State (fixed point of Eqs.~\eqref{se:H_eom}).
+% \begin{enumerate}
+%     \item $\eta \ll 1, \cos \theta_{\rm cs} \ll 1$ --- This is the limiting case
+%         for CS2 and CS4 when $\eta \ll \eta_{\rm c}$. We examine
+%         Eqs.~\eqref{seq:H_eom_phi_t} and approximate $\cot \theta \approx \cos
+%         \theta$ to find
+%         \begin{equation}
+%             \cos \theta_{\rm cs} \approx \frac{\eta \cos I}
+%                 {1 \mp \eta \sin I}.
+%         \end{equation}
+%         The two signs correspond to choices of $\cos \phi$. Each sign
+%         corresponds to one of CS2 and CS4.
+
+%     \item $\sin \theta_{\rm cs} \ll 1$ --- The $\eta \ll 1, \eta \gg 1$ cases
+%         can be solved together, and are the limiting cases both for CS1 and CS3
+%         when $\eta \ll \eta_{\rm c}$, and for CS2 and CS3 when $\eta \gg
+%         \eta_{\rm c}$. It proves easiest to rewrite Eqs.~\eqref{seq:H_eom_phi_t}
+%         as
+%         \begin{equation}
+%             0 = \cos \theta_{\rm cs}\p{-1 + 2\eta
+%                 \frac{\sin \p{I \pm \theta_{\rm cs}}}{\sin \p{2\theta_{\rm
+%                     cs}}}}.\label{eq:rewritten_dphi}
+%         \end{equation}
+%         The $\pm$ choice again comes from choice of $\cos \phi$. Then assuming
+%         $\theta_{\rm cs}, I \ll 1$, we obtain $\frac{I \pm
+%         \theta_{\rm cs}}{2\theta_{\rm cs}} = \frac{1}{2\eta}$ or
+%         \begin{equation}
+%             \theta_{\rm cs} = \frac{\eta I}{1 \mp \eta}.
+%         \end{equation}
+
+%         In the limit $\eta \ll \eta_{\rm c}$, these two solutions describe CS1
+%         and CS3, while in the limit $\eta \gg \eta_{\rm c}$ these two solutions
+%         describe CS2 and CS3.
+% \end{enumerate}
+% Again, the $\theta_{\rm cs}$ values derived here do not follow the same
+% convention as Fig.~\ref{fig:cs_locs} due to our different $\theta, \phi$
+% convention.
+
+The CSs satisfy $\dot{\phi} = \dot{\theta} = 0$. For convenience, we give
+approximate solutions for the CSs in the limits $\eta \ll 1$ and $\eta \gg 1$.
+For $\eta \ll 1$:
+\begin{itemize}
+    \item CS1: $\phi_1 = 0$, $\theta_1 \simeq \eta \sin I$.
+    \item CS2: $\phi_2 = \pi$, $\theta_2 \simeq \pi / 2 + \eta \cos I$.
+    \item CS3: $\phi_3 = 0$, $\theta_3 \simeq \pi - \eta \sin I$.
+    \item CS4: $\phi_4 = 0$, $\theta_4 \simeq \pi / 2 - \eta \cos I$.
+\end{itemize}
+For $\eta \gg 1$, only CS2 and CS3 exist and are given by:
+\begin{itemize}
+    \item CS2: $\phi_2 = \pi$, $\theta_2 \simeq I - \sin I \cos I / \eta$.
+    \item CS3: $\phi_3 = 0$, $\theta_3 \simeq \pi - I + \sin I \cos I / \eta$.
+\end{itemize}
 
@@
 
-To examine stability of each CS, it proves very easy to handle them generally.
-We linearize about an equilibrium located at $\phi_{\rm cs} = 0, \pi$ but
-arbitrary $\theta_{\rm cs}$. Linearizing Eqs.~\eqref{se:H_eom} about $\phi =
-\phi_{\rm cs} + \delta \phi, \theta = \theta_{\rm cs} + \delta \theta$ gives
+To examine stability of each CS, we linearize Eqs.~\eqref{se:H_eom} about an
+equilibrium located at $\phi_{\rm cs} = 0$ (CS 1, 3, 4) or $\pi$ (CS2) but
+arbitrary $\theta_{\rm cs}$. Setting $\phi = \phi_{\rm cs} + \delta \phi, \theta
+= \theta_{\rm cs} + \delta \theta$ gives
 \begin{subequations}\label{se:H_eom_lin}
@@
             \mp \eta \frac{\sin I}{\sin^2\theta_{\rm cs}} \delta \theta,\\
-        \rd{\delta \theta}{t} &= \pm \eta \sin I \delta \phi.
+        \rd{\delta \theta}{t} &= \pm \eta \sin I \delta \phi,
     \end{align}
 \end{subequations}
-Note that the positive sign corresponds to $\phi_{\rm cs} = 0$. Eliminating
-$\delta \theta$ gives
-\begin{align}
-    \rtd{\delta \phi}{t} &= \p{\sin \theta_{\rm cs}
-        \mp \eta \sin I\csc^2\theta}\p{\pm \eta \sin I} \delta
-            \phi,\\
-        &\equiv \lambda^2\delta \phi.\label{eq:lambda2}
-\end{align}
+where the upper sign corresponds to $\phi_{\rm cs} = 0$. Eliminating $\delta
+\theta$ gives
+\begin{equation}
+    \rtd{\delta \phi}{t} \equiv \lambda^2\delta \phi,\label{eq:lambda2}
+\end{equation}
+where
+\begin{equation}
+    \lambda^2 \equiv \p{\sin \theta_{\rm cs}
+        \mp \eta \sin I\csc^2\theta}\p{\pm \eta \sin I}.
+\end{equation}
 A plot of $\lambda^2$ for each of the CSs is given in Fig.~\ref{fig:lambda2}.
-From the plot, it is clear that only CS4 is a saddle point, while the other
-three are centers (stable). The local libration frequency for these points is
-just
-\begin{align}
-    \omega_{\rm lib} &= \sqrt{-\lambda^2},\\
-        &= \sqrt{\p{\sin \theta_{\rm cs}
-            \mp \eta \sin I \csc^2\theta}\p{\mp \eta \sin I}}.
-\end{align}
-The libration period is related simply $T_{\rm lib} = \frac{2\pi}{\omega_{\rm
-lib}}$.
+It is clear that CS4 is unstable while the other three are stable. The local
+libration frequency for these stable CSs is simply $\omega_{\rm lib} =
+\sqrt{-\lambda^2}$.
+
 \begin{figure}
@@
     the Cassini States. The vertical axis is rescaled for clarity. Note that CS4
-    is a saddle point ($\lambda^2 > 0$) when it exists while all others are
+    is unstable ($\lambda^2 > 0$) when it exists while all others are
     stable ($\lambda^2 < 0$). The thin horizontal dashed line is the instability
     boundary $\lambda^2 = 0$ while the thin vertical dashed line labels $\eta =
-    \eta_{\rm c}$.}\label{fig:lambda2}
+    \eta_{\rm c}$ [Eq.~\eqref{eq:etac}].}\label{fig:lambda2}
 \end{figure}
@@
 
-In this section, we will use approximations valid for small $\eta$ to derive
-analytic expressions for the final obliquities at small $\theta_{\rm sd, i}$ and
-associated probabilities for the II $\to$ I and II $\to$ III tracks that are
-accessible.
-
-We first seek a simple parameterization for the separatrix. We first solve for
-equilibria of the equation of motion Eq.~\eqref{eq:dsdt_base} to compute the
-coordinates for Cassini State 4:
-\begin{equation}
-    \cos \theta_4 \approx \frac{\mu \cos I}{1 - \eta \sin I}.
-\end{equation}
-Note that $\phi_4 = 0$. Then, the separatrix is the level curve of the
-Hamiltonian intersecting CS4, so it satisfies $\mathcal{H}\p{\phi, \theta_{\rm
-sep}(\phi)} = \mathcal{H}\p{\phi_4, \theta_4}$. To leading order in $\eta$, this
-has simple expression
+In this appendix, we will use approximations valid for small $\eta$ to derive
+the explicit analytic expressions for the final obliquities at small
+$\theta_{\rm sd, i}$ and the associated probabilities for the II $\to$ I and II
+$\to$ III tracks. These are the only possible tracks for small $\eta$.
+
+We first seek a simple parameterization for the separatrix, the level curve of
+the Hamiltonian intersecting the unstable equilibrium CS4. Points along the
+separatrix, parameterized by $\p{\phi, \theta_{\rm sep}(\phi)}$, satisfy
+$\mathcal{H}\p{\phi, \theta_{\rm sep}(\phi)} = \mathcal{H}\p{\phi_4, \theta_4}$
+where $\phi_4$ and $\theta_4$ are given in Appendix~\ref{ss:canonical}. We
+obtain two solutions for $\theta_{\rm sep}$, given to leading order in $\eta$
+by:
 \begin{equation}
@@
 \end{equation}
-Integration of the phase area enclosed by the two legs of the separatrix then
-yields
+These two solutions parameterize the two legs of the separatrix. Integration of
+the phase area enclosed by the separatrix yields then
 \begin{equation}
@@
 \end{equation}
-This, in conjunction with Eqs.~\eqref{eq:henrard_hop}, is sufficient to compute
-$\theta_{\rm f}\p{\theta_{\rm sd, i}}$ for zone II initial conditions.
-
+We can now compute the final obliquities and their associated probabilities for
+each track as follows:
 \begin{enumerate}
@@
         $A_{\rm II}(\eta_\star) = A$, or
-        \begin{align}
-            \eta_\star &\approx \p{\frac{2\pi\p{1 - \cos \theta_{\rm sd,i}}}{
-                        16}}^2 / \sin I,\\
-                    &\approx \p{\frac{\pi \theta_{\rm sd, i}^2}{16}}^2/\sin I.
-        \end{align}
+        \begin{equation}
+            \eta_\star \approx \p{\frac{2\pi\p{1 - \cos \theta_{\rm sd,i}}}{
+                        16}}^2 \frac{1}{\sin I}
+                    \approx \p{\frac{\pi \theta_{\rm sd,
+                    i}^2}{16}}^2\frac{1}{\sin I}.
+        \end{equation}
 
     \item Upon separatrix encounter, a transition to either zone I or zone
-        III occurs. These can be calculated to have associated probabilities
-        (using the approximate area Eq.~\eqref{eq:a_approx})
+        III occurs. These can be calculated to have the associated probabilities
+        [using the approximate area Eq.~\eqref{eq:a_approx} and
+        Eqs.~\eqref{eq:henrard_hop}]
         \begin{subequations}
@@
 
-    \item Upon a transition to zone I or zone III, the final obliquities can
-        be predicted by observing the final adiabatic invariant $A_{\rm f} = -A_{\rm
-        I}(\eta_\star)$ in the zone I case and $A_{\rm f} = A_{\rm I}(\eta_\star) +
-        A_{\rm I}I(\eta_\star)$ in the zone III case. As $\eta \to 0$, these
-        correspond to obliquities
+    \item Upon a transition to zone I or zone III, the final obliquity can be
+        predicted by observing the final adiabatic invariant $A_{\rm f} =
+        -A_{\rm I}(\eta_\star)$ in the zone I case and $A_{\rm f} = A_{\rm
+        I}(\eta_\star) + A_{\rm I}I(\eta_\star)$ in the zone III case. As $\eta
+        \to 0$, these correspond to obliquities
         \begin{subequations}\label{se:q_f_approx}
@@
                 \p{\cos \theta_{\rm f}}_{\rm II \to I} &\approx
-                    \p{\frac{\pi \theta_{\rm sp, i}^2}{16}}^2 \cot I
-                        + \frac{\theta_{\rm sp, i}^2}{4},\\
+                    \p{\frac{\pi \theta_{\rm sd, i}^2}{16}}^2 \cot I
+                        + \frac{\theta_{\rm sd, i}^2}{4},\\
                 \p{\cos \theta_{\rm f}}_{\rm II \to III} &\approx
-                    \p{\frac{\pi \theta_{\rm sp, i}^2}{16}}^2 \cot I
-                        - \frac{\theta_{\rm sp, i}^2}{4}.
+                    \p{\frac{\pi \theta_{\rm sd, i}^2}{16}}^2 \cot I
+                        - \frac{\theta_{\rm sd, i}^2}{4}.
             \end{align}

### 2020-04-15 initial/99_misc/1_areas.py

@@ -75,18 +75,20 @@ def plot_areas(I=np.radians(5), filename='1_areas'):
     fig, ax1 = plt.subplots(1, 1)
     # ax3 = ax1.twinx()
     ax4 = ax1.twiny()
-    ax1.plot(eta, A1ys / (4 * np.pi), 'g:', lw=LW/2)
-    ax1.plot(eta, A1w / (4 * np.pi), 'g', label=r'$A_{\rm I}$')
-    ax1.plot(eta, A2ys / (4 * np.pi), 'b:', lw=LW/2)
-    ax1.plot(eta, A2w / (4 * np.pi), 'b', label=r'$A_{\rm II}$')
-    ax1.plot(eta, A3ys / (4 * np.pi), 'r:', lw=LW/2)
-    ax1.plot(eta, A3w / (4 * np.pi), 'r', label=r'$A_{\rm III}$')
+    ax1.plot(eta, A1ys / (4 * np.pi), 'g:', lw=LW/2, alpha=0.7)
+    ax1.plot(eta, A1w / (4 * np.pi), 'g', label=r'$A_{\rm I}$', lw=LW/3)
+    ax1.plot(eta, A2ys / (4 * np.pi), 'b:', lw=LW/2, alpha=0.7)
+    ax1.plot(eta, A2w / (4 * np.pi), 'b', label=r'$A_{\rm II}$', lw=2*LW/3)
+    ax1.plot(eta, A3ys / (4 * np.pi), 'r:', lw=LW/2, alpha=0.7)
+    ax1.plot(eta, A3w / (4 * np.pi), 'r', label=r'$A_{\rm III}$', lw=LW)
 
     # dotted line continuation to show "analytic" continuation
     eta_cont = np.linspace(eta_c, 1.2 * eta_c, 21)
-    ax1.plot(eta_cont, np.full_like(eta_cont, A1w[-1] / (4 * np.pi)), 'g--')
-    ax1.plot(eta_cont, np.full_like(eta_cont, A2w[-1] / (4 * np.pi)), 'b--')
-    ax1.plot(eta_cont, np.full_like(eta_cont, A3w[-1] / (4 * np.pi)), 'r--')
+    # ax1.plot(eta_cont, np.full_like(eta_cont, A1w[-1] / (4 * np.pi)), 'g--')
+    ax1.plot(eta_cont, np.full_like(eta_cont, A2w[-1] / (4 * np.pi)), 'b--',
+             lw=2*LW/3)
[…]

### 2020-04-16 writeups/Su_disk_disp.tex
sigh

@@
 \title[Exoplanet Obliquities]{Dynamics of Colombo's Top: Generating Exoplanet
-Obliquties from Planet-Disc Interactions}
+Obliquities from Planet-Disc Interactions}
 \author[Y. Su and D. Lai]{
 Yubo Su$^1$,
-Dong Lai$^1$
+Dong Lai$^{1,2}$
 \\
@@
 Astronomy, Cornell University, Ithaca, NY 14853, USA
+\\
+$^2$ Tsung-Dao Lee Institute, Shanghai Jiao Tong University, Shanghai, 200240,
+China
 }
@@
 \begin{abstract}
-%DL: Not done yet
-    Large planetary spin-orbit misalignments (obliquities) are thought to play a
-    key role in some planets' atmospheric circulation and tidal heating. A
-    promising avenue to generate high obliquities is via spin-orbit resonances,
-    where the spin and orbital precession frequencies of the planet become and
-    remain commensurate as the system evolves. One such proposed mechanism
-    involves a dissipating protoplanetary disk driving orbital precession of an
-    interior planet \citep{millholland_disk}. This previous work is limited to
-    small initial misalignment angles between the spin axis of the planet and
-    orbital axis of the massive disk. In the present paper, this scenario is
-    analytically characterized and extended to arbitrary misalignment angles. It
-    is shown that (i) under adiabatic evolution, final planetary obliquities
-    bifurcate into distinct tracks governed by interactions with the resonance,
-    while (ii) under nonadiabatic evolution, a broad range of obliquities can
-    be excited. Analytical formulae are provided for most interesting regimes of
-    parameter space.
+Large planetary spin-orbit misalignments (obliquities) may strongly influence
+atmospheric circulation and tidal heating in the planet. A promising avenue to
+generate obliquities is via spin-orbit resonances, where the spin and orbital
+precession frequencies of the planet cross each other as the system evolves in
+time. One such mechanism involves a dissipating (mass-losing) protoplanetary
+disk driving orbital precession of an interior planet. We study this scenario
+analytically in this paper, and obtain the mapping between the initial spin
+orientation and the final obliquity. We show that (i) under adiabatic evolution
+(i.e.\ the disk dissipates at a sufficiently slow rate), the final planetary
+obliquities bifurcate into distinct tracks governed by interactions with the
+resonance; (ii) under nonadiabatic evolution, a broad range of obliquities can
+be excited. We obtain analytical expressions for the final obliquities for most
+interesting regimes of parameter space. The dynamical system studied in this
+paper is an example of ``Colombo's top'', and our analysis and results can be
+adapted for other applications.
 \end{abstract}
@@
 \citet{colombo1966} was the first to point out the importance of the above
-simple model in the study of the obliquity (the angle between the spin axis and
-orbital axis) of planets and satellites. Subsequent works
+simple model in the study of the obliquity (the angle between the spin and
+orbital axes) of planets and satellites. Subsequent works
 \citep{peale1969,peale1974possible,ward1975tidal,henrard1987} have revealed rich
-dynamics of this model. With appropriate modification,
-% (e.g. including the nutation of the orbital axis and multi-frequency
-% precessions due to multiple planets),
-this model can be used as a basis for understanding the evolution of rotation
-axes of celestial bodies.  Indeed, many contemporary problems in
-planetary/exoplanetary dynamics can be casted into a form analogous to this
-simple model or its variant \citep[e.g.][]{ward2004I, fabrycky_otides,
-batygin2013magnetic, lai2014star, anderson2018teeter}.
+dynamics of this model. With appropriate modification, this model can be used as
+a basis for understanding the evolution of rotation axes of celestial bodies.
+Indeed, many contemporary problems in planetary/exoplanetary dynamics can be
+cast into a form analogous to this simple model or its variants
+\citep[e.g.][]{ward2004I, fabrycky_otides, batygin2013magnetic, lai2014star,
+anderson2018teeter}.
 
@@
 are general, we frame our study in the context of generating exoplanet
-obliquities from planet-disc interaction with in a dissipating disc.
+obliquities from planet-disc interaction with a dissipating disc.
 
@@
 obliquities of ice giants \citep{original_gi, benz1989tilting,
-korycansky1990one, morbidelli_gi}. For gas giants, obliquity excitations may be
+korycansky1990one, morbidelli_gi}. For gas giants, obliquity excitation may be
 achieved via spin-orbit resonances, where the spin and orbital precession
@@
 \citep{ward2004I, ward2004II, vokrouhlicky2015tilting}. Such resonances may also
-play a role in generating Uranus's obliquity \citep{hamilton_tilting_ice}. For
-terrestrial planets, multiple spin-orbit resonances and their overlaps can make
-the obliquity vary chaotically over a wide range
-\citep[e.g.][]{laskar1993chaotic, touma1993chaotic, correia2003long}
+play a role in generating the obliquities of Uranus and Neptune
+\citep{hamilton_tilting_ice}. For terrestrial planets, multiple spin-orbit
+resonances and their overlaps can make the obliquity vary chaotically over a
+wide range \citep[e.g.][]{laskar1993chaotic, touma1993chaotic, correia2003long}
 
@@
 a few large bodies \citep{dones1993does, lissauer1997accretion,
-miguel2010planet}. Such ``stocastic'' accretion likely happened for terrestrial
+miguel2010planet}. Such ``stochastic'' accretion likely happened for terrestrial
 planets in the Solar System. Giant impacts may have also played a role in the
@@
 analysis and results have a wide range of applicability. For example, a
-dissipating disk is dynamically equivalent to an outward migrating external
+dissipating disk is dynamically equivalent to an outward-migrating external
 companion.
@@
 Fig.~\ref{fig:3_ensemble_05_15} in the nonadiabatic limit. Some detailed
-calculations are relegated to the appendicies, including a leading-order
+calculations are relegated to the appendices, including a leading-order
 estimate of the final planetary obliquities given small initial spin-disk
@@
 rotation period. . In Eq.~\eqref{eq:eta}, we have introduced the fiducial values
-of variable parameters for the appciation considered in this paper.
+of variable parameters for the application considered in this paper.
 Eq.~\eqref{eq:dsdt_rot} then becomes
@@
 sides of $\uv{l}$, while CS2 has $\phi = \pi$ and $\theta > 0$, corresponding to
-$\uv{s}$ and $\uv{l}_{\rm d}$ being on the same side of $\uv{l}$.
-The CS obliquity satisfie
+$\uv{s}$ and $\uv{l}_{\rm d}$ being on the same side of $\uv{l}$. The CS
+obliquity satisfies
 \begin{equation}
@@
 
-In this appendix, we study the evolution of the planetary obliquity $\theta$ when
+In this section, we study the evolution of the planetary obliquity $\theta$ when
 the parameter $\eta$ [or the disk mass $M_{\rm d}$; see Eqs.~\eqref{eq:eta}
@@
 adiabatic. Strictly speaking, this requires the disk evolution timescale $t_{\rm
-d}$ [Eq.~\eqref{eq:dmd_dt}] be much larger than all timesccales of the dynamical
+d}$ [Eq.~\eqref{eq:dmd_dt}] be much larger than all timescales of the dynamical
 system governed by the Hamiltonian [Eq.~\eqref{eq:H}]. This is of course not
@@
 $\epsilon_{\rm c} = 0.085$. Since our criterion is only a weak condition for
-diabaticity, we use $\epsilon = 3 \times 10^{-4}$ in our ``adiabatic''
+adiabaticity, we use $\epsilon = 3 \times 10^{-4}$ in our ``adiabatic''
 calculations below. We explore the consequences of nonadiabatic evolution in
@@
 The enclosed phase space area is not conserved when the trajectory encounters
-the separatrix. Howover, the change is easily understood \citep{henrard1982}. In
+the separatrix. However, the change is easily understood \citep{henrard1982}. In
 essence, when the trajectory crosses the separatrix, it continues to evolve
@@
 by integrating Eq.~\eqref{eq:a_oint} along the upper leg of the separatrix.
-Pictorally, this can be seen in the bottom panels of Fig.~\ref{fig:ad_21}.
+Pictorially, this can be seen in the bottom panels of Fig.~\ref{fig:ad_21}.
 
@@
     the separatrix (b), two panels depicting the separatrix crossing process
-    (c-d), and a final snapshot at $\eta = 10^{-3.5}$ (e). The separatricies at
+    (c-d), and a final snapshot at $\eta = 10^{-3.5}$ (e). The separatrices at
     the beginning and end of the portrayed cycle in each snapshot are shown in
@@
 obliquity evolution ($\epsilon\gtrsim \epsilon_{\rm c}$). However, some
-analytical results can be still be obtained when the obliquity change is small.
+analytical results can still be obtained when the obliquity change is small.
 
@@
 \end{equation}
-Defining $S = {\hat s}_{\rm x} + i{\hat s}_{\rm y}$ in the rotating frame, we
-find
+Defining $S = {\hat s}_{\rm x} + i{\hat s}_{\rm y}$, we find
 \begin{equation}
@@
 We now invoke the stationary phase approximation, so that $\Phi(\tau)\simeq
-\Phi(\tau_0) + (1/2)\ddot\Phi (\tau_0)(\tau - \tau_0)^2$ where $\tau_0$ is
-determined by $\dot\Phi = 0$, occuring when $\eta_0 = \cos \theta_i /\cos I$. We
-then find, for $\tau \gg \tau_0$,
+\Phi(\tau_0) + (1/2)\ddot\Phi (\tau_0)(\tau - \tau_0)^2$, where $\tau_0$ is
+determined by $\dot\Phi = 0$, occurring when $\eta_0 = \cos \theta_i /\cos I$.
+We then find, for $\tau \gg \tau_0$,
 \begin{equation}
     S(\tau)e^{-i\Phi(\tau)} - S(\tau_{\rm i})
-        \simeq -i \eta(\tau_0)\sin I \cos \theta_{\rm i} e^{-i\Phi(\tau_0)}
-            \p{\frac{2\pi}{i \ddot\Phi(\tau_0)}}^{1/2}.
+        \simeq -i \eta(\tau_0)\sin I \cos \theta_{\rm i}\,e^{-i\Phi(\tau_0)}
+            \sqrt{\frac{2\pi}{i \ddot\Phi(\tau_0)}}.
 \end{equation}
 Using $\dot\eta = -\epsilon \eta$ [Eq.~\eqref{eq:deta_dt}] and
-$\ddot\Phi(\tau_0) = \dot\eta(\tau_0)\cos I = -\epsilon$, we have
+$\ddot\Phi(\tau_0) = \dot\eta(\tau_0)\cos I = -\epsilon \cos\theta_i$,
+we have
 \begin{equation}
   S(\tau)e^{-i\Phi(\tau)} - S(\tau_{\rm i})
-        \simeq -i^{3/2}\tan I \cos^2\theta_{\rm i} e^{-i\Phi(\tau_0)}
-            \p{\frac{2\pi}{\epsilon}}^{1/2}.
-\end{equation}
-If the initial obliquity is much smaller than the final obliquity ($\theta_{\rm
-i} = \abs{S(\tau_{\rm i})} \ll \theta_{\rm f} = \abs{S(\tau_{\rm f})}$), then we
-obtain
-\begin{equation}
-    \theta_{\rm f}\simeq \sqrt{\frac{2\pi}{\epsilon}}\tan I\cos^2\theta_{\rm i}.
+        \simeq -i^{3/2}\tan I (\cos\theta_{\rm i})^{3/2} e^{-i\Phi(\tau_0)}
+            \sqrt{\frac{2\pi}{\epsilon}}.
+\end{equation}
+The final obliquity $\theta_{\rm f}$ is then given by
+\begin{equation}
+    \sin\theta_{\rm f}\simeq \abs{
+        \sin\theta_i+ e^{-i\varphi_0}\tan I (\cos\theta_{\rm i})^{3/2}
+            \sqrt{\frac{2\pi}{\epsilon}}},
+\label{eq:thetaf}
+\end{equation}
+where $\varphi_0=\Phi(\tau_0)+\pi/4$ is a constant phase. If the initial
+obliquity is much smaller than the final obliquity ($\sin\theta_{\rm i} \ll
+\sin\theta_{\rm f}$), we obtain
+\begin{equation}
+    \sin\theta_{\rm f}\simeq \sqrt{\frac{2\pi}{\epsilon}}
+        \tan I (\cos\theta_{\rm i})^{3/2}.
             \label{eq:nonad_q_f}
@@
 throughout the evolution. This corresponds to the limit where $\theta_{\rm f}$
-is not too much larger than $\theta_{\rm i}$, which requires $\epsilon$ not to
-be too small. Numerically, we verify this is consistent with being in the
+is not much larger than $\theta_{\rm i}$, which requires $\epsilon$ not to be
+too small. Numerically, this is consistent with the system being in the
 nonadiabatic regime $\epsilon \gtrsim \epsilon_{\rm c}$ (see
-Figs.~\ref{fig:nonad_3_scan} and~\ref{fig:nonad_3_scan_20}).
-
-The above calculation is performed for initial condition $\theta_{\rm i}$, but,
-as discussed earlier in the text, the initial spin orientation is more
-appropriately described by $\theta_{\rm sd, i}$. The correct way to predict
-final obliquities for such initial conditions using Eq.~\eqref{eq:nonad_q_f} is
-somewhat indirect but yields good agreement with numerical results. We develop
-the procedure for two cases: (i) for $\theta_{\rm sd, i} = 0$, then (ii) for
-nonzero $\theta_{\rm sd, i}$. To simplify the discussion below, we consider the
-limit where $\eta_{\rm i} \to \infty$, and CS2 and $\uv{l}_d$ coincide. The
-nonadiabatic evolution is then described by:
-\begin{itemize}
-    \item When $\theta_{\rm sd, i} = 0$, the initial condition is just CS2, so
-        Eq.~\eqref{eq:nonad_q_f} can be directly applied setting $\theta_{\rm i}
-        = I$. This yields good agreement with numerical results (see
-        Figs.~\ref{fig:nonad_3_scan} and~\ref{fig:nonad_3_scan_20}). We denote
-        this final obliquity
-        \begin{equation}
-            \theta_{\rm f} = \sqrt{\frac{2\pi}{\epsilon}}\frac{\sin (2I)}{2}.
+Fig.~\ref{fig:nonad_3_scan}).
+
+The above calculation applies for a specific initial $\theta_{\rm i}$, but, as
+discussed at the beginning of Section~\ref{ss:ad_ensemble}, the initial spin
+orientation is more appropriately described by $\theta_{\rm sd, i}$ since
+$\eta_i\gg 1$. The correct way to predict the final obliquity for a given
+$\theta_{\rm sd, i}$ using Eq.~\eqref{eq:thetaf}
+is somewhat indirect but yields good agreement with numerical results.
+
+First consider the case with $\theta_{\rm sd, i} = 0$. This corresponds to a
+well-defined initial obliquity $\theta_i = I$ (more precisely, the initial
+condition is CS2). Thus
+\begin{align}
+    \sin\theta_{\rm f} &\simeq \sin I \abs{1 + e^{-i\varphi_0}
+            \sqrt{\frac{2\pi \cos I}{\epsilon}}},\nonumber\\
+        &\approx \sin I \sqrt{\frac{2\pi \cos I}{\epsilon}},
             \label{eq:theta_2f}
-        \end{equation}
-        The azimuthal angle of the spin vector does not change and remains $\phi
-        = \pi$. Figures~\ref{fig:nonad_3_scan} and~\ref{fig:nonad_3_scan_20}
-        show the final obliquity as function of $\epsilon$ for $\theta_{\rm
-        sd,i} = 0$ and $I = 5$, $20^\circ$. We see that the agreement between
-        the numerical results and Eq.~\eqref{eq:nonad_q_f} is excellent,
-        particularly for the $I = 5^\circ$ case. The agreement when $I =
-        20^\circ$ is slightly poorer as $\theta_{\rm i}$ is larger and hence
-        less negligible in Eq.~\eqref{eq:nonad_q_f}. For $\epsilon \ll
-        \epsilon_{\rm c}$, we find $\theta_f \simeq 90^\circ$, in agreement with
-        the result of adiabatic evolution (see Fig.~\ref{fig:ad_ensemble}).
-
-    \item When $\theta_{\rm sd, i}$ is permitted to be nonzero, the set of
-        possible initial conditions forms a ring of angular width $\theta_{\rm
-        sd, i}$ about CS2. We find that this set of initial conditions
-        approximately evolves under nonadiabatic evolution to a ring of angular
-        width $\theta_{\rm sd, i}$ about the $\theta_{\rm sd, i} = 0$ prediction
-        given by Eq.~\eqref{eq:theta_2f}. The range of possible final
-        obliquities is the range of $\theta$ spanned by this ring of possible
-        outcomes. This can be solved in closed form, yielding generalization of
-        Eq.~\eqref{eq:theta_2f}
-        \begin{equation}
-            \abs{\sqrt{\frac{2\pi}{\epsilon}}\frac{\sin \p{2I}}{2}
-                - \theta_{\rm sd, i}}
-            \leq \theta_{\rm f}
-            \leq \sqrt{\frac{2\pi}{\epsilon}}\frac{\sin\p{2I}}{2}
-                + \theta_{\rm sd, i} .\label{eq:nonad_q_f_dist}
-        \end{equation}
-        The absolute value in the lower bound is a result of the ring of final
-        conditions crossing the North pole. Fig.~\ref{fig:nonad_3_ensemble}
-        shows the numerical result of $\theta_f$ vs $\theta_{\rm sd,i}$ for $I =
-        5^\circ$ and $\epsilon = 0.3$. We see that Eq.~\eqref{eq:nonad_q_f_dist}
-        provides good lower and upper bounds of the final obliquity for
-        $\theta_{\rm sd,i} \lesssim 45^\circ$.
-\end{itemize}
+\end{align}
+where the second equality assumes $\sqrt{2\pi/\epsilon}\gg 1$.
+Fig.~\ref{fig:nonad_3_scan} shows the final obliquity as function of $\epsilon$
+for $\theta_{\rm sd,i} = 0$ and $I = 5^\circ$. We see that the agreement between
+the numerical results and Eq.~\eqref{eq:theta_2f} is excellent. For $\epsilon
+\ll \epsilon_{\rm c}$, we find $\theta_{\rm f} \simeq 90^\circ$, in agreement
+with the result of adiabatic evolution (see Fig.~\ref{fig:ad_ensemble}).
+
+For $\theta_{\rm sd, i}\neq 0$, the set of possible initial conditions forms a
+ring of angular radius $\theta_{\rm sd, i}$ about $\uv{l}_{\rm d}$ (or CS2). We
+find that this set of initial conditions approximately evolves under
+nonadiabatic evolution to a ring of angular width $\theta_{\rm sd, i}$ about the
+$\theta_{\rm sd, i} = 0$ result given by Eq.~\eqref{eq:theta_2f}. Intuitively,
+because of the rapid precession of $\uv{l}$ around $\uv{l}_d$ at $\eta = \eta_i
+\gg 1$, the initial $\theta_i$ varies rapidly but is centered around $\theta_i
+\simeq I$. Thus the final obliquity spans in the range
+\begin{equation}
+    \abs{\sqrt{\frac{2\pi \cos I}{\epsilon}}\sin I
+            - \sin\theta_{\rm sd, i}}
+        \lesssim \sin\theta_{\rm f}
+        \lesssim
+            \sqrt{\frac{2\pi \cos I}{\epsilon}}\sin I + \sin \theta_{\rm sd, i}
+    .\label{eq:nonad_q_f_dist}
+\end{equation}
+Fig.~\ref{fig:nonad_3_ensemble} shows the numerical result of $\theta_f$ vs
+$\theta_{\rm sd,i}$ for $I =5^\circ$ and $\epsilon = 0.3$. We see that
+Eq.~\eqref{eq:nonad_q_f_dist} provides good lower and upper bounds of the final
+obliquity for $\theta_{\rm sd,i} \lesssim 45^\circ$.
 
@@
     Eq.~\eqref{eq:ad_constr}. The blue dots are numerical results, and the red
-    dashed line corresponds to Eq.~\eqref{eq:nonad_q_f}, which is in good
+    dashed line corresponds to Eq.~\eqref{eq:theta_2f}, which is in good
     agreement with numerical results for $\epsilon > \epsilon_{\rm c} \approx
-    0.1$ (the nonadiabatic regime); $\theta_{\rm f} \simeq  90^\circ$ in the
-    adiabatic regime ($\epsilon\ll \epsilon_{\rm c}$).}\label{fig:nonad_3_scan}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3scan_20.png}
-    \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$. The right
-    shaded area is where $\theta_{\rm f}$ predicted by Eq.~\eqref{eq:nonad_q_f}
-    violates the assumption $\theta_{\rm f} \gg \theta_{\rm
-    i}$.}\label{fig:nonad_3_scan_20}
-\end{figure}
+    0.1$ (the nonadiabatic regime). Note that $\theta_{\rm f} \simeq  90^\circ$
+    in the adiabatic regime ($\epsilon\ll \epsilon_{\rm
+    c}$).}\label{fig:nonad_3_scan}
+\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3scan_20.png}
+%     \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$. The right
+%     shaded area is where $\theta_{\rm f}$ predicted by Eq.~\eqref{eq:theta_2f}
+%     violates the assumption $\theta_{\rm f} \gtrsim \theta_{\rm
+%     i}$.}\label{fig:nonad_3_scan_20}
+% \end{figure}
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_05.png}
-    \caption{$\theta_{\rm  f}$ vs $\theta_{\rm sd, i}$ for $I=5^\circ$
-    and $\epsilon = 0.3$ (firmly in the nonadiabatic regime). The blue
-    dots represent numerical results, and the two red lines show the
-    analytical lower and upper limits given by
+    \caption{Final obliquity $\theta_{\rm  f}$ vs $\theta_{\rm sd, i}$ for
+    $I=5^\circ$ and $\epsilon = 0.3$ (firmly in the nonadiabatic regime). The
+    blue dots represent numerical results, and the two red lines show the
+    analytical lower and upper bounds given by
     Eq.~\eqref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemble}
@@
 
-\section{Summary and Discussion}\label{s:disc}
-
-%DL: Not done yet
-
-In this paper, we have studied the excitation of planetary obliquities by a
-dissipating protoplanetary disk for arbitrary initial misalignment angles. We
-present our result as a mapping from $\theta_{\rm sd, i}$ to $\theta_{\rm f}$,
-where $\theta_{\rm f}$ is the final planetary obliquity and $\theta_{\rm sd, i}$
-is the initial misalignment angle between the planet's spin axis and the disk's
-orbital angular momentum. We have presented analytical results that capture the
-behavior of this mapping in both the adiabatic and nonadiabatic limits:
+\section{Summary}\label{s:disc}
+
+In this paper, we have studied the excitation of planetary obliquities due to
+gravitational interaction with an exterior, dissipating (mass-losing)
+protoplanetary disk. Obliquity excitation occurs as the system passes through a
+secular resonance between spin precession and orbital (nodal) precession. This
+scenario was recently studied by \citet{millholland_disk}, who focused on the
+special case of small initial obliquities.  In contrast, we consider arbitrary
+initial misalignment angles in this paper, motivated by the fact that planet
+formation through core accretion can lead to a wide range of initial spin
+orientations.  We present our result as a mapping from $\theta_{\rm sd, i}$ to
+$\theta_{\rm f}$, where $\theta_{\rm sd, i}$ is the initial misalignment angle
+between the planet's spin axis and the disk's orbital angular momentum axis, and
+$\theta_{\rm f}$ is the final planetary obliquity. We have derived analytical
+results that capture the behavior of this mapping in both the adiabatic and
+nonadiabatic limits:
 \begin{enumerate}
-    \item In the adiabatic limit, we reproduce the known result $\theta_{\rm f}
-        = 90^\circ$ for $\theta_{\rm sd, i} \approx 0$ \citep{millholland_disk}.
-        We demonstrate via numerical simulation and analytical argument the
-        dual-valued behavior of $\theta_{\rm f}$ as nonzero initial spin-disk
-        misalignment angles $\theta_{\rm sd, i}$ are permitted (see
-        Fig.~\ref{fig:ad_ensemble}). We are able to capture both the exact final
-        $\theta_{\rm f}$ values and the probabilities of observing each value
-        via careful accounting of enclosed phase space area and separatrix
-        crossing dynamics.
-
-    \item As the system transitions more abruptly, the adiabatic prediction
-        breaks down when criterion Eq.~\eqref{eq:ad_constr} is violated. We find
-        a broad range of final obliquities can be reached for a given
-        $\theta_{\rm sd, i}$ (see Fig.~\ref{fig:nonad_3_ensemble}). We provide
-        an analytical expression of the bounds on $\theta_{\rm f}$ in
-        Eq.~\eqref{eq:nonad_q_f_dist}.
+    \item In the adiabatic limit (i.e.\ the disk dissipates at a
+        sufficiently slow rate), we reproduce the known result $\theta_{\rm f}
+        \simeq 90^\circ$ for $\theta_{\rm sd, i} \simeq 0$. We demonstrate via
+        numerical calculation and analytical argument the dual-valued behavior
+        of $\theta_{\rm f}$ for nonzero initial spin-disk misalignment angles
+        $\theta_{\rm sd, i}$ (see Fig.~\ref{fig:ad_ensemble}). We are able to
+        capture both the exact final $\theta_{\rm f}$ values and the
+        probabilities of achieving each value via careful accounting of
+        adiabatic invariance and separatrix crossing dynamics.
+    \item As the disk dissipates more rapidly, the adiabatic condition
+        [Eq.~\eqref{eq:ad_constr}] breaks down, we find that a broad range of
+        final obliquities can be reached for a given $\theta_{\rm sd, i}$ (see
+        Fig.~\ref{fig:nonad_3_ensemble}). We provide an analytical expression of
+        the bounds on $\theta_{\rm f}$ in Eq.~\eqref{eq:nonad_q_f_dist}.
 \end{enumerate}
 
-It is of interest to note the leading order dependence of $\theta_{\rm f}$ on
-$\theta_{\rm sd, i}$ [given by Eq.~\eqref{eq:qf_21_approx} and
-Eq.~\eqref{eq:qf_23_approx}] is second order. Therefore, if $\theta_{\rm sd, i}$
-is generally small, as might be expected for planets that do not experience
-strong collisions or scattering, resonance passage induced by an adiabatically
-dissipating protoplanetary disk is expected to significantly narrow the final
-$\theta_{\rm f}$ spread compared to the initial $\theta_{\rm sd, i}$ spread.
+As noted in Section 1, while in this paper we have examined a specific scenario
+of generating/modifying planetary obliquities from planet-disk interactions, the
+dynamical problem have studied is more general
+\citep{colombo1966,peale1969,peale1974possible,ward1975tidal,henrard1987}. Our
+work goes beyond these previous works and provides the most general solution to
+the evolution of ``Colombo's top'' as the system evolves from the ``weak
+spin-orbit coupling'' regime ($\eta\gg 1$) to the ``strong spin-orbit coupling''
+regime ($\eta\ll 1$).  The new analytical results presented in this paper can be
+adapted for other applications.
+
+\section*{Acknowledgements}
+
+We thank Kassandra Anderson for discussion and assistance in the early phase of
+this work. DL thanks the Dept.\ of Astronomy and the Miller Institute for Basic
+Science at UC Berkeley for hospitality while part of this work was carried out.
+This work has been supported in part by the NSF grant AST-17152 and NASA grant
+80NSSC19K0444. YS is supported by the NASA FINESST grant
+19-ASTRO19-0041.% chktex 8
 
@@
 
-In this section, we linearize the equations of motion near each CS\@. We
-determine the stability of each CS and the local libration frequencies or growth
-rates of the CSs.
+In this appendix, we linearize the equations of motion near each CS and
+determine its stability. We derive the local libration frequency or growth
+rate for perturbations around each CS\@.
 
@@
 Figs.~\ref{fig:cs_vecs} and~\ref{fig:cs_locs}). We use the convention
-$\theta \in [0, \pi)$% chktex 9
+$\theta \in [0, \pi)$ % chktex 9
 and $\phi \in [0, 2\pi)$.% chktex 9
@@
     \item CS1: $\phi_1 = 0$, $\theta_1 \simeq \eta \sin I$.
-    \item CS2: $\phi_2 = \pi$, $\theta_2 \simeq \pi / 2 + \eta \cos I$.
+    \item CS2: $\phi_2 = \pi$, $\theta_2 \simeq \pi / 2 - \eta \cos I$.
     \item CS3: $\phi_3 = 0$, $\theta_3 \simeq \pi - \eta \sin I$.
@@
 \begin{itemize}
-    \item CS2: $\phi_2 = \pi$, $\theta_2 \simeq I - \sin I \cos I / \eta$.
-    \item CS3: $\phi_3 = 0$, $\theta_3 \simeq \pi - I + \sin I \cos I / \eta$.
+    \item CS2: $\phi_2 = \pi$, $\theta_2 \simeq I + \eta^{-1}\sin I \cos I$.
+    \item CS3: $\phi_3 = 0$, $\theta_3 \simeq \pi - I + \eta^{-1}\sin I \cos I$.
 \end{itemize}
+Note that in the convention of Fig.~\ref{fig:cs_locs}, CS1, CS3 and CS4 have
+negative $\theta$ values since $\phi=0$.
 
@@
 arbitrary $\theta_{\rm cs}$. Setting $\phi = \phi_{\rm cs} + \delta \phi, \theta
-= \theta_{\rm cs} + \delta \theta$ gives
+= \theta_{\rm cs} + \delta \theta$ yields
 \begin{subequations}\label{se:H_eom_lin}

### 2020-04-23 writeups/Su_disk_disp.tex
check in new explanation for nonad sdi > 0 case

@@
         subcaption,
+        xcolor,
     }
@@
     \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
+    \newcommand*{\rdil}[2]{\mathrm{d}#1 / \mathrm{d}#2}
     \newcommand*{\pdil}[2]{\partial#1 / \partial#2}
@@
 
+    \colorlet{Corr}{red}
+
 \title[Exoplanet Obliquities]{Dynamics of Colombo's Top: Generating Exoplanet
@@
 
-% for i in ../initial/99_misc/2_3vec.png ../initial/99_misc/2_cs_locs.png ../initial/0_eta/1contours_flip.png ../initial/99_misc/1_areas.png ../initial/2_toy2/3_ensemble_05_35.png ../initial/2_toy2/3_ensemble_10_35.png ../initial/2_toy2/3_ensemble_20_35.png ../initial/2_toy2/3testo21.png ../initial/2_toy2/3testo21_subplots.png ../initial/2_toy2/3testo23.png ../initial/2_toy2/3testo23_subplots.png ../initial/2_toy2/3testo31.png ../initial/2_toy2/3testo31_subplots.png ../initial/2_toy2/3testo321.png ../initial/2_toy2/3testo321_subplots.png ../initial/2_toy2/3_ensemble_05_25.png ../initial/2_toy2/3_ensemble_05_15.png ../initial/2_toy2/3testo_nonad.png ../initial/2_toy2/3testo_nonad_subplots.png ../initial/2_toy2/3_ensemble_05_05.png ../initial/2_toy2/3scan.png ../initial/2_toy2/3scan_20.png ../initial/99_misc/2_lambdas.png; do cp $i plots_diskdisp; done
+% for i in ../initial/99_misc/2_nonad_rot.png ../initial/99_misc/2_3vec.png ../initial/99_misc/2_cs_locs.png ../initial/0_eta/1contours_flip.png ../initial/99_misc/1_areas.png ../initial/2_toy2/3_ensemble_05_35.png ../initial/2_toy2/3_ensemble_10_35.png ../initial/2_toy2/3_ensemble_20_35.png ../initial/2_toy2/3testo21.png ../initial/2_toy2/3testo21_subplots.png ../initial/2_toy2/3testo23.png ../initial/2_toy2/3testo23_subplots.png ../initial/2_toy2/3testo31.png ../initial/2_toy2/3testo31_subplots.png ../initial/2_toy2/3testo321.png ../initial/2_toy2/3testo321_subplots.png ../initial/2_toy2/3_ensemble_05_25.png ../initial/2_toy2/3_ensemble_05_15.png ../initial/2_toy2/3testo_nonad.png ../initial/2_toy2/3testo_nonad_subplots.png ../initial/2_toy2/3_ensemble_05_05.png ../initial/2_toy2/3scan.png ../initial/2_toy2/3scan_20.png ../initial/99_misc/2_lambdas.png; do cp $i plots_diskdisp; done
 
@@
 \begin{equation}
-    \sin \theta \cos \theta - \eta \sin\p{\theta - I} = 0.
+    \sin \theta \cos \theta - \eta \sin\p{\theta - I} = 0.\label{eq:cs_zero}
 \end{equation}
@@
 twice, while it spends many orbits inside one of the three zones and far from
-the separatrix. Thus, a \emph{weak adiabaticity criterion} is that the variation
-timescale of $\eta$ be slower than all circulation/libration timescales near the
-equilibria/fixed points. If this criterion is satisfied, then the system will
-evolve adiabatically for most of its evolution save one or two separatrix
-crossings.
+the separatrix. Thus, a \emph{weak adiabaticity criterion} is
+that\textcolor{Corr}{, for all equilibria/fixed points, the local
+circulation/libration timescales are much shorter than motion of the
+equilibrium}. If this criterion is satisfied, then the system will evolve
+adiabatically for most of its evolution save one or two separatrix crossings.
 
@@
 about CS1 or CS3. As such, it has the smallest characteristic frequency in the
-system. The weak adiabaticity criterion can be recast as requiring that $\eta$
-vary more slowly than this libration frequency \citep[see][]{ward2004II}, i.e.\
-$t_{\rm d}^{-1} \lesssim \omega_{\rm lib} / 2\pi$. In terms of the dimensionless
-parameter $\epsilon$
-[Eq.~\eqref{eq:eps_def}], this adiabaticity condition is
-\begin{equation}
-    \epsilon \lesssim \epsilon_{\rm c} \equiv
-        \frac{1}{2\pi}\sqrt{\eta\sin I \sin \theta_2
-            \p{1 + \eta \sin I \csc^3 \theta_2}},
-            \label{eq:ad_constr}
-\end{equation}
-where $\theta_2$ is the obliquity at CS2. This formula differs from that given
-in \citet{millholland_disk}, where the $\csc^3\!\theta_2$ term is neglected and
-the square root is missing\footnote{The missing $\csc^3 \theta_2$ term can be
-traced to a $\theta \gg I$ approximation made in Eq.~(3) of \citet{ward2004II}.
-Since $\theta_2 \approx I$ for $\eta \gg 1$ (Fig.~\ref{fig:cs_locs}), this
-approximation is not always valid.}.
-
-For $I = 5^\circ$, $\eta \sim \eta_{\rm c}$ Eq.~\eqref{eq:ad_constr} gives
-$\epsilon_{\rm c} = 0.085$. Since our criterion is only a weak condition for
-adiabaticity, we use $\epsilon = 3 \times 10^{-4}$ in our ``adiabatic''
-calculations below. We explore the consequences of nonadiabatic evolution in
-Section~\ref{s:nonad}.
+system. The weak adiabaticity criterion \textcolor{Corr}{is equivalent to
+requiring that, for all times other than separatrix crossing, the obliquity of
+CS2 ($\theta_2$) evolve over longer timescales than the local libration period
+about CS2, or
+\begin{equation}
+    \rd{\theta_2(t)}{t} \lesssim \frac{\omega_{\rm lib}(t)}{2\pi},\label{eq:ad_base}
+\end{equation}
+where
+\begin{equation}
+    \omega_{\rm lib}(t) = \sqrt{\eta(t)\sin I \sin \theta_2(t)
+            \p{1 + \eta \sin I \csc^3 \theta_2(t)}},\label{eq:w_lib}
+\end{equation}
+is the libration frequency about CS2 at time $t$ (Appendix~\ref{ss:eigens}).}
+This formula differs from that given in \citet{millholland_disk}, where the
+$\csc^3\!\theta_2$ term is neglected and the square root is missing\footnote{The
+missing $\csc^3\!\theta_2$ term can be traced to a $\theta \gg I$ approximation
+made in Eq.~(3) of \citet{ward2004II}. Since $\theta_2 \sim I$ for $\eta \sim 1$
+(Fig.~\ref{fig:cs_locs}), this approximation is not always valid.}.
+\textcolor{Corr}{Differentiating Eq.~\eqref{eq:cs_zero} gives
+\begin{equation}
+    \rd{\theta_2}{t} = \epsilon \frac{\eta \sin\p{\theta_2(t) - I}}{
+        \cos\p{2\theta_2(t)} - \eta \cos\p{\theta_2(t) - I}},\label{eq:dq2dt}
+\end{equation}
+where $\epsilon = -\rdil{(\ln \eta)}{t}$ [Eq.~\eqref{eq:eps_def}]. For a given
+$\epsilon$, Eqs.~(\ref{eq:ad_base}--\ref{eq:dq2dt}) will be satisfied for all
+times if they are satisfied near $\eta \simeq 1$, where $\dot{\theta}_2 \simeq
+\epsilon$. Thus, weak adiabiticity requires
+\begin{equation}
+    \epsilon \lesssim \epsilon_{\rm c},\label{eq:ad_constr}
+\end{equation}
+where
+\begin{equation}
+    \epsilon_{\rm c} \equiv \p{\frac{\omega_{\rm lib}}{t}}_{\eta = 1} =
+        \frac{1}{2\pi}\sqrt{\sin I \sin \theta_{\rm 2c}
+            \p{1 + \sin I \csc^3 \theta_{\rm 2c}}},
+\end{equation}
+where $\theta_{\rm 2c}$ is the location of CS2 for $\eta = 1$.
+% theta_{2c} = 31^\circ$
+} For $I = 5^\circ$, we find $\epsilon_{\rm c} = 0.0431$. Since our criterion is
+only a weak condition for adiabaticity, we use $\epsilon = 3 \times 10^{-4}$ in
+our ``adiabatic'' calculations below. We explore the consequences of
+nonadiabatic evolution in Section~\ref{s:nonad}.
 
@@
 $\theta_{\rm sd, i}$ using Eq.~\eqref{eq:thetaf}
-is somewhat indirect but yields good agreement with numerical results.
+is somewhat \textcolor{Corr}{subtle} but yields good agreement with numerical
+results.
 
@@
 well-defined initial obliquity $\theta_i = I$ (more precisely, the initial
-condition is CS2). Thus
+condition is CS2). \textcolor{Corr}{The final obliquity in this case, denoted
+$\theta_{\rm 0f}$, is given by}
 \begin{align}
-    \sin\theta_{\rm f} &\simeq \sin I \abs{1 + e^{-i\varphi_0}
+    \sin\theta_{\rm 0f} &\simeq \sin I \abs{1 + e^{-i\varphi_0}
             \sqrt{\frac{2\pi \cos I}{\epsilon}}},\nonumber\\
@@
 
-For $\theta_{\rm sd, i}\neq 0$, the set of possible initial conditions forms a
-ring of angular radius $\theta_{\rm sd, i}$ about $\uv{l}_{\rm d}$ (or CS2). We
-find that this set of initial conditions approximately evolves under
-nonadiabatic evolution to a ring of angular width $\theta_{\rm sd, i}$ about the
-$\theta_{\rm sd, i} = 0$ result given by Eq.~\eqref{eq:theta_2f}. Intuitively,
-because of the rapid precession of $\uv{l}$ around $\uv{l}_d$ at $\eta = \eta_i
-\gg 1$, the initial $\theta_i$ varies rapidly but is centered around $\theta_i
-\simeq I$. Thus the final obliquity spans in the range
-\begin{equation}
-    \abs{\sqrt{\frac{2\pi \cos I}{\epsilon}}\sin I
-            - \sin\theta_{\rm sd, i}}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\columnwidth]{plots_diskdisp/2_nonad_rot.png}
+    \caption{\textcolor{Corr}{Schematic depicting the calculation of
+    $\theta_{\rm f}$ for nonadiabatic evolution when $\theta_{\rm sd, i} > 0$,
+    where $\theta_{\rm 0f}$ is given by Eq.~\eqref{eq:theta_2f}. The figure
+    shows a projection onto the $x$-$z$ plane. For a given $\theta_{\rm sd, i}$,
+    the set of initial conditions forms a ring about CS2 (solid red area) and
+    evolves to a ring about $\theta_{\rm 0f}$ (hatched red area) under
+    nonadiabatic evolution. The final obliquities are the projection of this
+    final cone onto the $\uv{l}$ axis (horizontal green
+    lines).}}\label{fig:2nonadrot}
+\end{figure}
+\textcolor{Corr}{
+When $\theta_{\rm sd, i}\neq 0$, the calculation of final obliquities is best
+described by Fig.~\ref{fig:2nonadrot}, and yields the range of obliquities
+\begin{equation}
+    \abs{\theta_{\rm 0f} - \theta_{\rm sd, i}}
         \lesssim \sin\theta_{\rm f}
-        \lesssim
-            \sqrt{\frac{2\pi \cos I}{\epsilon}}\sin I + \sin \theta_{\rm sd, i}
+        \lesssim \theta_{\rm 0f} + \theta_{\rm sd, i}
     .\label{eq:nonad_q_f_dist}
 \end{equation}
+The absolute value in the lower bound is necessary to capture the behavior of
+the projected obliquities in Fig.~\ref{fig:2nonadrot} when the hatched area
+encloses $\uv{l}$.}
+
+\textcolor{Corr}{
+The process depicted in Fig.~\ref{fig:2nonadrot} has a physically clear
+interpretation as a two-step process: (i) when $\eta$ is sufficiently large, the
+evolution of the system is always adiabatic [$\dot{\theta}_2 \to 0$,
+Eq.~\eqref{eq:dq2dt}], so $\uv{s}$ precesses around CS2 with constant angle
+$\theta_{\rm sd, i}$ as $\eta$ decreases; (ii) when $\eta$ has decreased
+sufficiently that the system becomes nonadiabatic [violating
+Eq.~\eqref{eq:ad_base}], the obliquity of the system at that instant is frozen
+in as the final obliquity.}
+
 Fig.~\ref{fig:nonad_3_ensemble} shows the numerical result of $\theta_f$ vs

### 2020-04-23 initial/2_toy2/3_disk_disp.py

@@ -22,7 +22,7 @@ plt.rc('ytick', direction='in', left=True, right=True)
 PLOT_DIR = '1plots'
 from utils import to_cart, to_ang, roots, H, solve_ic_base,\
     get_etac
-dpi = 600
+dpi = 200
 my_lw = 4.5
 lw_single = 2.0
 my_ms = 2
@@ -996,6 +996,19 @@ def sim_for_many(I, eps=-1e-3, eta0_mult=10, etaf=1e-3, n_pts=21, n_dqs=51,
                  'r',
                  zorder=1)
 
+        # alternative fit: use theta_i = [abs(theta_sdi - I), theta_sdi + I]
+        # bound_1_deg = []
+        # bound_2_deg = []
+        # for dq in dqs:
+        #     bound_1_deg.append(np.degrees(
+        #         np.sqrt(2 * np.pi / (-eps))
+        #         * np.tan(I) * np.cos(abs(dq - I))**(3/2)))
+        #     bound_2_deg.append(np.degrees(
+        #         np.sqrt(2 * np.pi / (-eps))
+        #         * np.tan(I) * np.cos(dq + I)**(3/2)))
+        # ax1.plot(dqs_d, bound_1_deg, 'g:', zorder=1,)
+        # ax1.plot(dqs_d, bound_2_deg, 'g:', zorder=1,)
+
         # ax1.set_title(title)
         ax1.set_ylim(ymin=0)
         ax1.set_xlim([0, 90])
@@ -1083,7 +1096,7 @@ def eps_scan(I, filename='3scan', dq=0.01, n_pts=151, n_pts_ring=21,
                [r'$%d$' % np.degrees(I), r'$90$'])
     plt.ylim(ylims)
     plt.xlabel(r'$\epsilon$')
-    plt.ylabel(r'$\theta_{\rm f}$')
+    plt.ylabel(r'$\theta_{\rm 0f}$')
     # plt.title(r'$I = %d^\circ$' % np.degrees(I))
     plt.tight_layout()
     # plt.legend()
@@ -1177,7 +1190,7 @@ def plot_manys():
 if __name__ == '__main__':
     I = np.radians(5)
     # plot_singles(I)
-    # plot_manys()
+    plot_manys()
 
     # testing high epsilon
     # eta_c = get_etac(I)
@@ -1187,7 +1200,7 @@ if __name__ == '__main__':
[…]

### 2020-04-28 writeups/Su_disk_disp.tex
convert to ApJ style, rewrite the comment yet again

@@
-    \documentclass[
-        fleqn,
-        usenatbib,
-        % referee,
-    ]{mnras}
+%%  twocolumn   : two text columns, 10 point font, single spaced article.
+%%                This is the most compact and represent the final published
+%%                derived PDF copy of the accepted manuscript from the publisher
+%%  manuscript  : one text column, 12 point font, double spaced article.
+%%  preprint    : one text column, 12 point font, single spaced article.
+%%  preprint2   : two text columns, 12 point font, single spaced article.
+%%  modern      : a stylish, single text column, 12 point font, article with
+%%        wider left and right margins. This uses the Daniel
+%%        Foreman-Mackey and David Hogg design.
+%%  RNAAS       : Preferred style for Research Notes which are by design
+%%                lacking an abstract and brief. DO NOT use \begin{abstract}
+%%                and \end{abstract} with this style.
+    \documentclass[twocolumn]{aastex63}
     \usepackage{
@@
     \newcommand*{\ev}[1]{\langle#1\rangle}
-    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
-    \newcommand*{\uv}[1]{\hat{\bm{#1}}}
+    \newcommand*{\bsmb}[1]{\boldsymbol{\mathbf{#1}}}
+    \newcommand*{\uv}[1]{\hat{\bsmb{#1}}}
     \newcommand*{\p}[1]{\left(#1\right)}
@@
 
-\title[Exoplanet Obliquities]{Dynamics of Colombo's Top: Generating Exoplanet
-Obliquities from Planet-Disc Interactions}
-\author[Y. Su and D. Lai]{
-Yubo Su$^1$,
-Dong Lai$^{1,2}$
-\\
-$^1$ Cornell Center for Astrophysics and Planetary Science, Department of
-Astronomy, Cornell University, Ithaca, NY 14853, USA
-\\
-$^2$ Tsung-Dao Lee Institute, Shanghai Jiao Tong University, Shanghai, 200240,
-China
-}
+    \newcommand{\vdag}{(v)^\dagger}
+    \newcommand\aastex{AAS\TeX}
+    \newcommand\latex{La\TeX}
+
+    \received{XXXX}
+    \revised{XXXX}
+    \accepted{XXXX}
+    \submitjournal{ApJ}
 
 % for i in ../initial/99_misc/2_nonad_rot.png ../initial/99_misc/2_3vec.png ../initial/99_misc/2_cs_locs.png ../initial/0_eta/1contours_flip.png ../initial/99_misc/1_areas.png ../initial/2_toy2/3_ensemble_05_35.png ../initial/2_toy2/3_ensemble_10_35.png ../initial/2_toy2/3_ensemble_20_35.png ../initial/2_toy2/3testo21.png ../initial/2_toy2/3testo21_subplots.png ../initial/2_toy2/3testo23.png ../initial/2_toy2/3testo23_subplots.png ../initial/2_toy2/3testo31.png ../initial/2_toy2/3testo31_subplots.png ../initial/2_toy2/3testo321.png ../initial/2_toy2/3testo321_subplots.png ../initial/2_toy2/3_ensemble_05_25.png ../initial/2_toy2/3_ensemble_05_15.png ../initial/2_toy2/3testo_nonad.png ../initial/2_toy2/3testo_nonad_subplots.png ../initial/2_toy2/3_ensemble_05_05.png ../initial/2_toy2/3scan.png ../initial/2_toy2/3scan_20.png ../initial/99_misc/2_lambdas.png; do cp $i plots_diskdisp; done
-
-\date{Accepted XXX\@. Received YYY\@; in original form ZZZ}
-
-\pubyear{2020}
-
-\begin{document}\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
+\shorttitle{Exoplanet Obliquities}
+\shortauthors{Y.\ Su and D.\ Lai}
+
+\begin{document}
+
+\title{Template \aastex Article with Examples:
+v6.3\footnote{Released on June, 10th, 2019}}
+
+\title{Dynamics of Colombo's Top: Generating Exoplanet Obliquities from
+Planet-Disc Interactions}
+
+\correspondingauthor{Yubo Su}
+\email{yubosu@astro.cornell.edu}
+
+\author[0000-0001-8283-3425]{Yubo Su}% chktex 8
+\affiliation{Cornell Center for Astrophysics and Planetary Science, Department
+of Astronomy, Cornell University, Ithaca, NY 14853, USA}
+
+\author[0000-0002-1934-6250]{Dong Lai}% chktex 8
+\affiliation{Cornell Center for Astrophysics and Planetary Science, Department
+of Astronomy, Cornell University, Ithaca, NY 14853, USA}
+\affiliation{Tsung-Dao Lee Institute, Shanghai Jiao Tong University, Shanghai, 200240,
+China}
 
 \begin{abstract}
+
 Large planetary spin-orbit misalignments (obliquities) may strongly influence
@@
 adapted for other applications.
+
 \end{abstract}
-
-\begin{keywords}
-planet--star interactions % chktex 8
-\end{keywords}
 
@@
 generalize to a disk with finite extent \citep[see][]{millholland_disk}. Denote
-$\bm{S}$ the spin angular momentum and $\bm{L}$ the orbital angular momentum of
-the planet, and $\bm{L}_{\rm d}$ the angular momentum of the disk. The
-corresponding unit vectors are $\uv{s} \equiv \bm{S} / S$, $\uv{l} \equiv \bm{L}
-/ L$, and $\uv{l}_{\rm d} \equiv \bm{L}_{\rm d} / L_{\rm d}$.
+$\bsmb{S}$ the spin angular momentum and $\bsmb{L}$ the orbital angular momentum of
+the planet, and $\bsmb{L}_{\rm d}$ the angular momentum of the disk. The
+corresponding unit vectors are $\uv{s} \equiv \bsmb{S} / S$, $\uv{l} \equiv \bsmb{L}
+/ L$, and $\uv{l}_{\rm d} \equiv \bsmb{L}_{\rm d} / L_{\rm d}$.
 
@@
 \begin{figure}
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/2_cs_locs.png}
+    \centering
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/2_cs_locs.png}
     \caption{Cassini state obliquities as a function of $\eta$ for $I =
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/1_areas.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/1_areas.png}
     \caption{The solid lines show the fractional areas of each of the zones
@@
 and~\eqref{eq:deta_dt}] decreases sufficiently slowly that the evolution is
-adiabatic. Strictly speaking, this requires the disk evolution timescale $t_{\rm
-d}$ [Eq.~\eqref{eq:dmd_dt}] be much larger than all timescales of the dynamical
-system governed by the Hamiltonian [Eq.~\eqref{eq:H}]. This is of course not
-possible in all cases, as the motion along the separatrix has an infinite
-period.
-
-In practice, as $\eta$ evolves, the system only crosses the separatrix once or
-twice, while it spends many orbits inside one of the three zones and far from
-the separatrix. Thus, a \emph{weak adiabaticity criterion} is
-that\textcolor{Corr}{, for all equilibria/fixed points, the local
-circulation/libration timescales are much shorter than motion of the
-equilibrium}. If this criterion is satisfied, then the system will evolve
-adiabatically for most of its evolution save one or two separatrix crossings.
+adiabatic. \textcolor{Corr}{Intuitively, this requires the disk evolution time
+$t_{\rm d}$ [Eq.~\eqref{eq:dmd_dt}] be larger than the spin precession period,
+$2\pi / \alpha$, i.e.\ $\epsilon = 1 / (\alpha t_{\rm d}) \lesssim 1/ (2\pi)$.}
+
+Strictly speaking, \textcolor{Corr}{adiabaticity} requires $t_{\rm d}$ be much
+larger than all timescales of the dynamical system governed by the Hamiltonian
+[Eq.~\eqref{eq:H}]. This is of course not possible in all cases, as the motion
+along the separatrix has an infinite period. In practice, as $\eta$ evolves, the
+system only crosses the separatrix once or twice, while it spends many orbits
+inside one of the three zones and far from the separatrix. Thus, a \emph{weak
+adiabaticity criterion} is that, for all equilibria/fixed points, the local
+circulation/libration periods are much shorter than the
+\textcolor{Corr}{timescale for the} motion of the equilibria
+\textcolor{Corr}{due to changing $\eta$}. If this criterion is satisfied, then
+the system will evolve adiabatically for most of its
+evolution save one or two separatrix crossings.
 
@@
 about CS1 or CS3. As such, it has the smallest characteristic frequency in the
-system. The weak adiabaticity criterion \textcolor{Corr}{is equivalent to
-requiring that, for all times other than separatrix crossing, the obliquity of
-CS2 ($\theta_2$) evolve over longer timescales than the local libration period
-about CS2, or
-\begin{equation}
-    \rd{\theta_2(t)}{t} \lesssim \frac{\omega_{\rm lib}(t)}{2\pi},\label{eq:ad_base}
+system. The weak adiabaticity criterion is equivalent to
+requiring that, at all times other than separatrix crossing, the obliquity of
+CS2 ($\theta_2$) evolve over a longer timescale than the local libration period
+about CS2, i.e.
+\begin{equation}
+    \abs{\rd{\theta_2}{\tau}} \lesssim
+        \frac{\omega_{\rm lib}}{2\pi},\label{eq:ad_base}
 \end{equation}
@@
 \begin{equation}
-    \omega_{\rm lib}(t) = \sqrt{\eta(t)\sin I \sin \theta_2(t)
-            \p{1 + \eta \sin I \csc^3 \theta_2(t)}},\label{eq:w_lib}
-\end{equation}
-is the libration frequency about CS2 at time $t$ (Appendix~\ref{ss:eigens}).}
-This formula differs from that given in \citet{millholland_disk}, where the
-$\csc^3\!\theta_2$ term is neglected and the square root is missing\footnote{The
-missing $\csc^3\!\theta_2$ term can be traced to a $\theta \gg I$ approximation
-made in Eq.~(3) of \citet{ward2004II}. Since $\theta_2 \sim I$ for $\eta \sim 1$
-(Fig.~\ref{fig:cs_locs}), this approximation is not always valid.}.
-\textcolor{Corr}{Differentiating Eq.~\eqref{eq:cs_zero} gives
-\begin{equation}
-    \rd{\theta_2}{t} = \epsilon \frac{\eta \sin\p{\theta_2(t) - I}}{
-        \cos\p{2\theta_2(t)} - \eta \cos\p{\theta_2(t) - I}},\label{eq:dq2dt}
-\end{equation}
-where $\epsilon = -\rdil{(\ln \eta)}{t}$ [Eq.~\eqref{eq:eps_def}]. For a given
-$\epsilon$, Eqs.~(\ref{eq:ad_base}--\ref{eq:dq2dt}) will be satisfied for all
-times if they are satisfied near $\eta \simeq 1$, where $\dot{\theta}_2 \simeq
-\epsilon$. Thus, weak adiabiticity requires
-\begin{equation}
-    \epsilon \lesssim \epsilon_{\rm c},\label{eq:ad_constr}
-\end{equation}
-where
-\begin{equation}
-    \epsilon_{\rm c} \equiv \p{\frac{\omega_{\rm lib}}{t}}_{\eta = 1} =
-        \frac{1}{2\pi}\sqrt{\sin I \sin \theta_{\rm 2c}
-            \p{1 + \sin I \csc^3 \theta_{\rm 2c}}},
-\end{equation}
-where $\theta_{\rm 2c}$ is the location of CS2 for $\eta = 1$.
-% theta_{2c} = 31^\circ$
-} For $I = 5^\circ$, we find $\epsilon_{\rm c} = 0.0431$. Since our criterion is
-only a weak condition for adiabaticity, we use $\epsilon = 3 \times 10^{-4}$ in
-our ``adiabatic'' calculations below. We explore the consequences of
-nonadiabatic evolution in Section~\ref{s:nonad}.
+    \omega_{\rm lib} = \sqrt{\eta\sin I \sin \theta_2
+        \p{1 + \eta \sin I \csc^3 \theta_2}},\label{eq:w_lib}
+\end{equation}
+is the libration frequency about CS2 \textcolor{Corr}{for a given $\eta$}
+(Appendix~\ref{ss:eigens}). This formula differs from that given in
+\citet{millholland_disk}, where the $\csc^3\!\theta_2$ term is neglected and the
+square root is missing\footnote{The missing $\csc^3\!\theta_2$ term can be
+traced to a $\theta \gg I$ approximation made in Eq.~(3) of \citet{ward2004II}.
+Since $\theta_2 \sim I$ for $\eta \gtrsim 1$ (Fig.~\ref{fig:cs_locs}), this
+approximation is not always valid.}. Differentiating Eq.~\eqref{eq:cs_zero}
+gives
+\begin{equation}
+    \rd{\theta_2}{\tau} = -\epsilon \frac{\eta \sin\p{\theta_2 - I}}{
+        \cos\p{2\theta_2} - \eta \cos\p{\theta_2 - I}},\label{eq:dq2dt}
+\end{equation}
+where $\epsilon = -\rdil{(\ln \eta)}{\tau}$ [Eq.~\eqref{eq:eps_def}].
+\textcolor{Corr}{Eq.~\eqref{eq:ad_base} is most constraining at $\eta \sim 1$,
+i.e.\ it is satisfied for all $\eta$ if it is satisfied near $\eta \sim 1$,
+$\abs{\rdil{\theta_2}{\tau}} \sim \epsilon$}. Thus, weak adiabiticity requires
+\textcolor{Corr}{
+\begin{equation}
+    \epsilon \lesssim \epsilon_{\rm c}
+        \equiv \p{\frac{\omega_{\rm lib}}{2\pi}}_{\eta = 1}
+            % =\frac{1}{2\pi}\sqrt{\sin I \sin \theta_{\rm 2c}
+            %     \p{1 + \sin I \csc^3 \theta_{\rm 2c}}}
+            \sim 0.0433,\label{eq:ad_constr}
+\end{equation}
+where we have used $\sin \theta_{\rm 2} \sim 1/2$ when $\eta =
+1$ (for $I = 5^\circ$ and $\eta = 1$, $\theta_{\rm 2} \approx 31^\circ$)}. Since
+our criterion is only a weak condition for adiabaticity, we use $\epsilon = 3
+\times 10^{-4}$ in our ``adiabatic'' calculations below. We explore the
+consequences of nonadiabatic evolution in Section~\ref{s:nonad}.
 
@@
 $\theta_{\rm f}$ is frozen. The mapping between $\theta_{\rm sd, i}$ and
-$\theta_{\rm f}$ is our primary result, and is shown for $I = 5^\circ, 10^\circ,
-20^\circ$ in Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
+$\theta_{\rm f}$ is our primary result, and is shown for $I = 5^\circ$,
+$10^\circ$, and $20^\circ$ in
+Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
 and~\ref{fig:3_ensemble_20_35} respectively. The blue dots represent the results
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_35.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3_ensemble_05_35.png}
     \caption{Top: The final spin obliquity $\theta_{\rm f}$ as a function of the
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_10_35.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3_ensemble_10_35.png}
     \caption{Same as the top panel of Fig.~\ref{fig:ad_ensemble} but for $I =
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_20_35.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3_ensemble_20_35.png}
     \caption{Same as the top panel of Fig.~\ref{fig:3_ensemble_10_35} but for $I
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo21.png}
-
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo21_subplots.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3testo21.png}
+
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3testo21_subplots.png}
     \caption{An example of the II $\to$ I evolutionary track for $I = 5^\circ$
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo23.png}
-
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo23_subplots.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3testo23.png}
+
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3testo23_subplots.png}
     \caption{Same as Fig.~\ref{fig:ad_21} but for the II $\to$ III track.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo31.png}
-
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo31_subplots.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3testo31.png}
+
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3testo31_subplots.png}
     \caption{Same as Fig.~\ref{fig:ad_21} but for the III $\to$ I track.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo321.png}
-
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo321_subplots.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3testo321.png}
+
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3testo321_subplots.png}
     \caption{Same as Fig.~\ref{fig:ad_21} but for the III $\to$ II $\to$ I
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_25.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3_ensemble_05_25.png}
     \caption{Same as Fig.~\ref{fig:ad_ensemble} but for $\epsilon = 10^{-2.5}$
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_15.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3_ensemble_05_15.png}
     \caption{Same as Fig.~\ref{fig:3_ensemble_05_25} but for $\epsilon =
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo_nonad.png}
-
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo_nonad_subplots.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3testo_nonad.png}
+
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3testo_nonad_subplots.png}
     \caption{Same as Fig.~\ref{fig:ad_21} but for a nonadiabatic case, with $\epsilon =
@@
 $\eta_i\gg 1$. The correct way to predict the final obliquity for a given
-$\theta_{\rm sd, i}$ using Eq.~\eqref{eq:thetaf}
-is somewhat \textcolor{Corr}{subtle} but yields good agreement with numerical
-results.
+$\theta_{\rm sd, i}$ using Eq.~\eqref{eq:thetaf} is somewhat subtle but yields
+good agreement with numerical results.
 
@@
 well-defined initial obliquity $\theta_i = I$ (more precisely, the initial
-condition is CS2). \textcolor{Corr}{The final obliquity in this case, denoted
-$\theta_{\rm 0f}$, is given by}
+condition is CS2). The final obliquity in this case, denoted
+$\theta_{\rm 0f}$, is given by
 \begin{align}
@@
     \centering
-    \includegraphics[width=0.6\columnwidth]{plots_diskdisp/2_nonad_rot.png}
-    \caption{\textcolor{Corr}{Schematic depicting the calculation of
-    $\theta_{\rm f}$ for nonadiabatic evolution when $\theta_{\rm sd, i} > 0$,
-    where $\theta_{\rm 0f}$ is given by Eq.~\eqref{eq:theta_2f}. The figure
-    shows a projection onto the $x$-$z$ plane. For a given $\theta_{\rm sd, i}$,
-    the set of initial conditions forms a ring about CS2 (solid red area) and
-    evolves to a ring about $\theta_{\rm 0f}$ (hatched red area) under
-    nonadiabatic evolution. The final obliquities are the projection of this
-    final cone onto the $\uv{l}$ axis (horizontal green
-    lines).}}\label{fig:2nonadrot}
-\end{figure}
-\textcolor{Corr}{
-When $\theta_{\rm sd, i}\neq 0$, the calculation of final obliquities is best
-described by Fig.~\ref{fig:2nonadrot}, and yields the range of obliquities
+    \includegraphics[width=0.7\columnwidth]{plots_diskdisp/2_nonad_rot_cropped.png}
+    \caption{\textcolor{Corr}{Schematic depicting nonadiabatic obliquity
+    evolution when $\theta_{\rm sd, i} > 0$ assuming $\eta_{\rm i} \gg 1$. The
+    figure shows a projection onto the plane containing both $\uv{l}$ and
+    $\uv{l}_{\rm d}$. When $\theta_{\rm sd, i} = 0$, the initial spin vector
+    points along $\uv{l}_{\rm d}$ and evolves into the final spin vector (grey),
+    which has obliquity $\theta_{\rm 0f}$ [Eq.~\eqref{eq:theta_2f}]. When
+    $\theta_{\rm sd, i} \neq 0$, the set of initial conditions for the spin
+    vector forms a cone (solid red area) centered on $\uv{l}_{\rm d}$ with
+    opening half-angle $\theta_{\rm sd, i}$. Under nonadiabatic evolution, the
+    set of final spin vectors forms a new cone, still with opening half-angle
+    $\theta_{\rm sd, i}$, centered on $\theta_{\rm 0f}$ (light red
+    area).}}\label{fig:2nonadrot}
+\end{figure}
+
+When $\theta_{\rm sd, i}\neq 0$, \textcolor{Corr}{we find that the final
+obliquity $\theta_{\rm f}$ varies over a range of values for a given
+$\theta_{\rm sd, i}$, as can be seen in Fig.~\ref{fig:nonad_3_ensemble}. The
+range can be described by}
 \begin{equation}
     \abs{\theta_{\rm 0f} - \theta_{\rm sd, i}}
-        \lesssim \sin\theta_{\rm f}
+        \lesssim \theta_{\rm f}
         \lesssim \theta_{\rm 0f} + \theta_{\rm sd, i}
@@
 \end{equation}
-The absolute value in the lower bound is necessary to capture the behavior of
-the projected obliquities in Fig.~\ref{fig:2nonadrot} when the hatched area
-encloses $\uv{l}$.}
-
 \textcolor{Corr}{
-The process depicted in Fig.~\ref{fig:2nonadrot} has a physically clear
-interpretation as a two-step process: (i) when $\eta$ is sufficiently large, the
-evolution of the system is always adiabatic [$\dot{\theta}_2 \to 0$,
-Eq.~\eqref{eq:dq2dt}], so $\uv{s}$ precesses around CS2 with constant angle
-$\theta_{\rm sd, i}$ as $\eta$ decreases; (ii) when $\eta$ has decreased
-sufficiently that the system becomes nonadiabatic [violating
-Eq.~\eqref{eq:ad_base}], the obliquity of the system at that instant is frozen
-in as the final obliquity.}
+This can be understood as follows (see Fig.~\ref{fig:2nonadrot}). In the
+beginning ($\eta = \eta_{\rm i} \gg 1$), the initial spin vector precesses
+around $\uv{l}_{\rm d}$ on a cone with opening half-angle $\theta_{\rm sd, i}$
+(more precisely, the cone is centered on CS2, which coincides with $\uv{l}_{\rm
+d}$ as $\eta_{\rm i} \to \infty$). Note that for $\eta \gg 1$, the adiabaticity
+condition is easily satisfied: Eq.~\eqref{eq:w_lib} gives $\omega_{\rm lib}
+\simeq \eta$ while Eq.~\eqref{eq:dq2dt} gives $\abs{\rdil{\theta_2}{\tau}} \sim
+\epsilon \tan\p{\theta_2 - I} \ll \eta$. As $\eta$ decreases, the system will
+transition from being adiabatic to being nonadiabatic, since $\epsilon \gtrsim
+\epsilon_{\rm c}$. The evolution of the system can thus be decomposed into
+two phases: (i) when the evolution is adiabatic, the spin vector will precess
+around the slowly-moving CS2, then (ii) when the evolution becomes nonadiabatic,
+the spin vector stops tracking the quickly-evolving CS2. During the adiabatic
+evolution of phase (i), the angle between CS2 and the spin vector is
+approximately unchanged due to conservation of phase space area}\footnote{
+\textcolor{Corr}{This approximation assumes sufficiently small $\theta_{\rm sd,
+i}$ such that libration about CS2 remains approximately circular throughout
+phase (i). Deviations from this approximation occur when $\theta_{\rm sd, i}$ is
+sufficiently large that libration cycles become non-circular as $\eta$ decreases
+(Fig.~\ref{fig:eq_1contours} illustrates that libration cycles farther from CS2
+are less circular).
+% Such deformations decrease the obliquity spanned by the cone (see
+% Fig.~\ref{fig:eq_1contours} for decreasing $\eta$; note that level curves of $H$
+% correspond to bases of cones), which causes the observed range of final
+% obliquities in Fig.~\ref{fig:nonad_3_ensemble} to be smaller than predicted by
+% Eq.~\eqref{eq:nonad_q_f_dist} when $\theta_{\rm sd, i} \gtrsim 45^\circ$.
+This causes the deviation of the data in Fig.~\ref{fig:nonad_3_ensemble} from
+Eq.~\eqref{eq:nonad_q_f_dist} for $\theta_{\rm sd, i} \gtrsim 45^\circ$.
+}}.
+\textcolor{Corr}{Once the evolution enters phase (ii), the precession axis
+quickly (on timescale $\ll 1 / \omega_{\rm lib}$) changes to $\uv{l}$ (as $\eta
+\to \eta_{\rm f} \ll 1$). Precession about $\uv{l}$ does not change the
+obliquity, so the range of obliquities when the spin vector stops tracking CS2
+is frozen in as the range of final obliquities.}
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3scan.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3scan.png}
     \caption{Final obliquity $\theta_{\rm  f}$ as a function of $\epsilon$ for
@@
 %     \centering
-%     \includegraphics[width=0.5\textwidth]{plots_diskdisp/3scan_20.png}
+%     \includegraphics[width=0.47\textwidth]{plots_diskdisp/3scan_20.png}
 %     \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$. The right
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3_ensemble_05_05.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3_ensemble_05_05.png}
     \caption{Final obliquity $\theta_{\rm  f}$ vs $\theta_{\rm sd, i}$ for
@@
 
-\bibliographystyle{mnras}
 \bibliography{Su_sep_cross}
-
-% \clearpage
-% \onecolumn
+\bibliographystyle{aasjournal}
+
 \appendix
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots_diskdisp/2_lambdas.png}
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/2_lambdas.png}
     \caption{$\lambda^2$, given by Eq.~\eqref{eq:lambda2}, evaluated at each of
@@
 
-\bsp
-\label{lastpage} % chktex 24
-\end{document} % chktex 17
+\end{document}
+% chktex 17

### 2020-04-28 initial/99_misc/2_rand_plots.py

@@ -1,6 +1,7 @@
 '''
 more random plots
 '''
+# convert 2_nonad_rot.png -crop 650x700+100+75 2_nonad_rot_cropped.png
 import numpy as np
 import scipy.optimize as opt
 
@@ -67,10 +68,10 @@ def get_cs(I):
 def plot_cs(I=np.radians(5)):
     etas, cs_vals, etas_four, etac = get_cs(I)
 
-    plt.semilogx(etas_four, np.degrees(cs_vals[0]), 'y:', lw=LW, label='1')
+    plt.semilogx(etas_four, np.degrees(cs_vals[0]), 'y', lw=LW, label='1')
     plt.semilogx(etas, np.degrees(cs_vals[1]), 'r', lw=LW, label='2')
-    plt.semilogx(etas, np.degrees(cs_vals[2]), 'm--', lw=LW, label='3')
-    plt.semilogx(etas_four, np.degrees(cs_vals[3]), 'c-.', lw=LW, label='4')
+    plt.semilogx(etas, np.degrees(cs_vals[2]), 'm', lw=LW, label='3')
+    plt.semilogx(etas_four, np.degrees(cs_vals[3]), 'c', lw=LW, label='4')
     plt.xlabel(r'$\eta$', fontsize=22)
     plt.ylabel(r'$\theta$ (deg)', fontsize=22)
     plt.xlim([min(etas), max(etas)])
@@ -116,7 +117,7 @@ def plot_eigens(I=np.radians(5)):
     plt.semilogx(etas_four,
                  [lambda2(e, q, -1)
                   for e, q in zip(etas_four, cs_vals[0])],
-                 'y:', label='1', lw=LW)
+                 'y', label='1', lw=LW)
     plt.semilogx(etas,
                  [lambda2(e, q, -1)
                   for e, q in zip(etas, cs_vals[1])],
@@ -124,11 +125,11 @@ def plot_eigens(I=np.radians(5)):
     plt.semilogx(etas,
                  [lambda2(e, q, -1)
                   for e, q in zip(etas, cs_vals[2])],
-                  'm--', label='3', lw=LW)
+                  'm', label='3', lw=LW)
     plt.semilogx(etas_four,
                  [lambda2(e, q, -1)
                   for e, q in zip(etas_four, cs_vals[3])],
[…]

### 2020-04-28 writeups/Su_disk_disp.tex
redo even more plots

@@
 i}$ such that libration about CS2 remains approximately circular throughout
-phase (i). Deviations from this approximation occur when $\theta_{\rm sd, i}$ is
-sufficiently large that libration cycles become non-circular as $\eta$ decreases
-(Fig.~\ref{fig:eq_1contours} illustrates that libration cycles farther from CS2
-are less circular).
+phase (i) (initially, when $\eta \to \infty$, all librations are circular about
+$\uv{l}_{\rm d}$). This assumption breaks down when $\theta_{\rm sd, i}$ is
+sufficiently large that librating orbits become non-circular as $\eta$ decreases
+before the end of phase (i) (Fig.~\ref{fig:eq_1contours} illustrates that
+libration cycles farther from CS2, corresponding to a larger $\theta_{\rm sd,
+i}$, are less circular for a given $\eta$).
 % Such deformations decrease the obliquity spanned by the cone (see
@@
 \to \eta_{\rm f} \ll 1$). Precession about $\uv{l}$ does not change the
-obliquity, so the range of obliquities when the spin vector stops tracking CS2
-is frozen in as the range of final obliquities.}
+obliquity, so the range of obliquities at the end of phase (i) is frozen in as
+the range of final obliquities.}
 

### 2020-04-28 initial/2_toy2/3_disk_disp.py

@@ -287,9 +287,9 @@ def plot_single(I, eps, tf, eta0, q0, filename, dq=0.3,
         ax1.semilogx(etas, mu_dat, c='g', lw=0.5, alpha=0.7, label='Sim')
     max_valid_idxs = np.where(mu_max > 0)[0]
     ax1.semilogx(eta4s[max_valid_idxs], mu_max[max_valid_idxs],
-                 'k:', label='Sep')
-    ax1.semilogx(eta4s, mu_min, 'k:')
-    ax1.semilogx(etas, np.cos(q2s), 'r--', label='CS2')
+                 'k', label='Sep')
+    ax1.semilogx(eta4s, mu_min, 'k')
+    ax1.semilogx(etas, np.cos(q2s), 'r', label='CS2')
     ax1.set_ylabel(r'$\cos\theta$')
 
     # ax1.set_title(r'$I = %d^\circ$' % np.degrees(I))
@@ -1189,8 +1189,8 @@ def plot_manys():
 
 if __name__ == '__main__':
     I = np.radians(5)
-    # plot_singles(I)
-    plot_manys()
+    plot_singles(I)
+    # plot_manys()
 
     # testing high epsilon
     # eta_c = get_etac(I)

### 2020-04-29 writeups/Su_disk_disp.tex
final Dong review

--- 2020-04-28 writeups/Su_disk_disp.tex
@@
 %%                and \end{abstract} with this style.
-    \documentclass[twocolumn]{aastex63}
+    \documentclass[twocolumn,twocolappendix]{aastex63}
     \usepackage{
@@
 time. One such mechanism involves a dissipating (mass-losing) protoplanetary
-disk driving orbital precession of an interior planet. We study this scenario
-analytically in this paper, and obtain the mapping between the initial spin
-orientation and the final obliquity. We show that (i) under adiabatic evolution
-(i.e.\ the disk dissipates at a sufficiently slow rate), the final planetary
-obliquities bifurcate into distinct tracks governed by interactions with the
-resonance; (ii) under nonadiabatic evolution, a broad range of obliquities can
-be excited. We obtain analytical expressions for the final obliquities for most
-interesting regimes of parameter space. The dynamical system studied in this
-paper is an example of ``Colombo's top'', and our analysis and results can be
-adapted for other applications.
+disk that drives orbital precession of an interior planet. We study this
+scenario analytically in this paper, and obtain the mapping between the general
+initial spin orientation and the final obliquity. We show that (i) under
+adiabatic evolution (i.e.\ the disk dissipates at a sufficiently slow rate), the
+final planetary obliquity as a function of the initial spin orientation
+bifurcates into distinct tracks governed by interactions with the resonance;
+(ii) under nonadiabatic evolution, a broad range of obliquities can be excited.
+We obtain analytical expressions for the final obliquities for various
+regimes of parameter space. The dynamical system studied in this paper is an
+example of ``Colombo's top'', and our analysis and results can be adapted to
+other applications.
 
 \end{abstract}
+
+\keywords{planet---star interactions}
 
@@
 precession could arise from gravitational interactions with other masses in the
-system (e.g.\ planets, external discs, or binary stellar companion). What is the
+system (e.g.\ planets, external disks, or binary stellar companion). What is the
 dynamics of the planetary spin axis?  How does the spin axis evolve as the spin
@@
 \citep[e.g.][]{ward2004I, fabrycky_otides, batygin2013magnetic, lai2014star,
-anderson2018teeter}.
+anderson2018teeter,zanazzi2018planet}.
 
@@
 are general, we frame our study in the context of generating exoplanet
-obliquities from planet-disc interaction with a dissipating disc.
+obliquities from planet-disk interaction with a dissipating disk.
 
@@
 planets in the Solar System. Giant impacts may have also played a role in the
-formation of the close-in multiple-planet systems discovered by the Kepler
+formation of the close-in multiple-planet systems diskovered by the Kepler
 satellite \citep[e.g.][]{inamdar2015formation, izidoro2017breaking}.
@@
 to nonadiabatic. Analytical results are presented to explain the numerical
-results in both limits. We discuss the implications of our results in
-Section~\ref{s:disc}. Our primary physical results consist of
+results in both limits. We diskuss the implications of our results in
+Section~\ref{s:disk}. Our primary physical results consist of
 Fig.~\ref{fig:ad_ensemble} in the adiabatic limit and
@@
 host star acting on the planet's rotational bulge. On the other hand, $\uv{l}$
-and the disc axis $\uv{l}_{\rm d}$ precess around each other due to
+and the disk axis $\uv{l}_{\rm d}$ precess around each other due to
 gravitational interactions. We assume $S \ll L \ll L_{\rm d}$, so $\uv{l}_{\rm
@@
 orbital mean motion, and we have assumed $r_d\gg a_p$ and included only the
-leading-order (quadrupole) interaction between the planet and disc. We define
+leading-order (quadrupole) interaction between the planet and disk. We define
 three relative inclination angles via
@@
 and~\eqref{eq:deta_dt}] decreases sufficiently slowly that the evolution is
-adiabatic. \textcolor{Corr}{Intuitively, this requires the disk evolution time
-$t_{\rm d}$ [Eq.~\eqref{eq:dmd_dt}] be larger than the spin precession period,
-$2\pi / \alpha$, i.e.\ $\epsilon = 1 / (\alpha t_{\rm d}) \lesssim 1/ (2\pi)$.}
-
-Strictly speaking, \textcolor{Corr}{adiabaticity} requires $t_{\rm d}$ be much
-larger than all timescales of the dynamical system governed by the Hamiltonian
+adiabatic. Intuitively, this requires the disk evolution time
+$t_{\rm d}$ [Eq.~\eqref{eq:dmd_dt}] be much larger than the spin precession
+period, $2\pi / \alpha$, i.e.\ $\epsilon = 1 / (\alpha t_{\rm d}) \ll 1/
+(2\pi)$.
+
+More rigorously, adiabaticity requires $t_{\rm d}$ be much larger than all
+timescales of the dynamical system governed by the Hamiltonian
 [Eq.~\eqref{eq:H}]. This is of course not possible in all cases, as the motion
@@
 adiabaticity criterion} is that, for all equilibria/fixed points, the local
-circulation/libration periods are much shorter than the
-\textcolor{Corr}{timescale for the} motion of the equilibria
-\textcolor{Corr}{due to changing $\eta$}. If this criterion is satisfied, then
-the system will evolve adiabatically for most of its
-evolution save one or two separatrix crossings.
+circulation/libration periods are much shorter than the timescale for the motion
+of the equilibria due to changing $\eta$. If this criterion is satisfied, then
+the system will evolve adiabatically for most of its evolution save one or two
+separatrix crossings.
 
@@
 \begin{equation}
-    \abs{\rd{\theta_2}{\tau}} \lesssim
+    \abs{\rd{\theta_2}{\tau}} \ll
         \frac{\omega_{\rm lib}}{2\pi},\label{eq:ad_base}
@@
 \end{equation}
-is the libration frequency about CS2 \textcolor{Corr}{for a given $\eta$}
+is the libration frequency about CS2 for a given $\eta$
 (Appendix~\ref{ss:eigens}). This formula differs from that given in
@@
 traced to a $\theta \gg I$ approximation made in Eq.~(3) of \citet{ward2004II}.
-Since $\theta_2 \sim I$ for $\eta \gtrsim 1$ (Fig.~\ref{fig:cs_locs}), this
+Since $\theta_2 \sim I$ for $\eta \gg 1$ (Fig.~\ref{fig:cs_locs}), this
 approximation is not always valid.}. Differentiating Eq.~\eqref{eq:cs_zero}
@@
 where $\epsilon = -\rdil{(\ln \eta)}{\tau}$ [Eq.~\eqref{eq:eps_def}].
-\textcolor{Corr}{Eq.~\eqref{eq:ad_base} is most constraining at $\eta \sim 1$,
-i.e.\ it is satisfied for all $\eta$ if it is satisfied near $\eta \sim 1$,
-$\abs{\rdil{\theta_2}{\tau}} \sim \epsilon$}. Thus, weak adiabiticity requires
-\textcolor{Corr}{
-\begin{equation}
-    \epsilon \lesssim \epsilon_{\rm c}
+Eq.~\eqref{eq:ad_base} is most constraining at $\eta \sim 1$, i.e.\ it will be
+satisfied for all $\eta$ if it is satisfied near $\eta \sim 1$, where
+$\abs{\rdil{\theta_2}{\tau}} \sim \epsilon$. Thus, weak adiabiticity requires
+\begin{equation}
+    \epsilon \ll \epsilon_{\rm c}
         \equiv \p{\frac{\omega_{\rm lib}}{2\pi}}_{\eta = 1}
+            \simeq \frac{1}{2\pi\sqrt{2}}\sqrt{\sin I\p{1 + 8\sin I}},
             % =\frac{1}{2\pi}\sqrt{\sin I \sin \theta_{\rm 2c}
             %     \p{1 + \sin I \csc^3 \theta_{\rm 2c}}}
-            \sim 0.0433,\label{eq:ad_constr}
-\end{equation}
-where we have used $\sin \theta_{\rm 2} \sim 1/2$ when $\eta =
-1$ (for $I = 5^\circ$ and $\eta = 1$, $\theta_{\rm 2} \approx 31^\circ$)}. Since
-our criterion is only a weak condition for adiabaticity, we use $\epsilon = 3
-\times 10^{-4}$ in our ``adiabatic'' calculations below. We explore the
+            % \approx 0.0433,
+            \label{eq:ad_constr}
+\end{equation}
+where in the last equality we have used $\sin \theta_{\rm 2} \simeq 1/2$ at
+$\eta = 1$ (e.g.\ when $I = 5^\circ$ and $\eta = 1$, $\theta_{\rm 2} \approx
+31^\circ$). For $I = 5^\circ$, we obtain $\epsilon_{\rm c} \approx 0.0433$.
+Since our criterion is only a weak condition for adiabaticity, we use $\epsilon
+= 3 \times 10^{-4}$ in our ``adiabatic'' calculations below. We explore the
 consequences of nonadiabatic evolution in Section~\ref{s:nonad}.
@@
 conservation of the initially enclosed phase space area $A_{\rm i}$ for each
-$\theta_{\rm sd, i}$ (see Section~\ref{ss:zone_transitions}), this discrepancy
+$\theta_{\rm sd, i}$ (see Section~\ref{ss:zone_transitions}), this diskrepancy
 introduces an extra deviation from the analytical prediction. To guarantee all
@@
 of the numerical calculation. The colored tracks are calculated
-semi-analytically using the method discussed in the following subsection.
+semi-analytically using the method diskussed in the following subsection.
 
@@
 holds very well when defining $\theta_{\rm sd, i}$ as the angular distance to
-CS2; an exception is discussed in Section~\ref{sss:evol_traj}.
+CS2; an exception is diskussed in Section~\ref{sss:evol_traj}.
 
@@
 The above calculation applies for a specific initial $\theta_{\rm i}$, but, as
-discussed at the beginning of Section~\ref{ss:ad_ensemble}, the initial spin
+diskussed at the beginning of Section~\ref{ss:ad_ensemble}, the initial spin
 orientation is more appropriately described by $\theta_{\rm sd, i}$ since
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{plots_diskdisp/2_nonad_rot_cropped.png}
-    \caption{\textcolor{Corr}{Schematic depicting nonadiabatic obliquity
+When $\theta_{\rm sd, i}\neq 0$, we find that the final obliquity $\theta_{\rm
+f}$ spans a range of values for a given $\theta_{\rm sd, i}$, as can be
+seen in Fig.~\ref{fig:nonad_3_ensemble}. The range can be described by
+\begin{equation}
+    \abs{\theta_{\rm 0f} - \theta_{\rm sd, i}}
+        \lesssim \theta_{\rm f}
+        \lesssim \theta_{\rm 0f} + \theta_{\rm sd, i}
+    .\label{eq:nonad_q_f_dist}
+\end{equation}
+Eq.~\eqref{eq:nonad_q_f_dist} can be understood as follows (see
+Fig.~\ref{fig:2nonadrot}). In the beginning ($\eta = \eta_{\rm i} \gg 1$), the
+initial spin vector precesses around $\uv{l}_{\rm d}$ on a cone with opening
+half-angle $\theta_{\rm sd, i}$ (more precisely, the cone is centered on CS2,
+which coincides with $\uv{l}_{\rm d}$ as $\eta_{\rm i} \to \infty$). Note that
+for $\eta \gg 1$, the adiabaticity condition is easily satisfied: using
+$\theta_2 \simeq I + \eta^{-1}\sin I \cos I$ (see
+Section~\ref{s:s:local_dynamics}), Eq.~\eqref{eq:w_lib} gives $\omega_{\rm lib}
+\simeq \eta$ while Eq.~\eqref{eq:dq2dt} gives $\abs{\rdil{\theta_2}{\tau}}
+\simeq \p{\epsilon / \eta} \sin I \cos I \ll \omega_{\rm lib}$. As $\eta$
+decreases, the system will transition from being adiabatic to being
+nonadiabatic, since $\epsilon \gtrsim \epsilon_{\rm c}$. The evolution of the
+system can thus be decomposed into two phases: (i) when the evolution is
+adiabatic, the spin vector will precess around the slowly-moving CS2; (ii) when
+the evolution becomes nonadiabatic, the spin vector stops tracking the
+quickly-evolving CS2. During the adiabatic evolution of phase (i), the angle
+between CS2 and the spin vector is approximately unchanged due to conservation
+of phase space area\footnote{ This approximation assumes sufficiently small
+$\theta_{\rm sd, i}$ such that libration about CS2 remains approximately
+circular throughout phase (i) (initially, when $\eta \to \infty$, all librations
+are circular about $\uv{l}_{\rm d}$). This assumption breaks down when
+$\theta_{\rm sd, i}$ is sufficiently large that librating orbits become
+non-circular as $\eta$ decreases before the end of phase (i)
+(Fig.~\ref{fig:eq_1contours} illustrates that the libration cycles farther from
+CS2, corresponding to a larger $\theta_{\rm sd, i}$, are less circular for a
+given $\eta$).
+% Such deformations decrease the obliquity spanned by the cone (see
+% Fig.~\ref{fig:eq_1contours} for decreasing $\eta$; note that level curves of $H$
+% correspond to bases of cones), which causes the observed range of final
+% obliquities in Fig.~\ref{fig:nonad_3_ensemble} to be smaller than predicted by
+% Eq.~\eqref{eq:nonad_q_f_dist} when $\theta_{\rm sd, i} \gtrsim 45^\circ$.
+This causes the deviation of the numerical results in
+Fig.~\ref{fig:nonad_3_ensemble} from Eq.~\eqref{eq:nonad_q_f_dist} for
+$\theta_{\rm sd, i} \gtrsim 45^\circ$. }.
+Once the evolution enters phase (ii), the precession axis
+quickly (on timescale $\ll 1 / \omega_{\rm lib}$) changes to $\uv{l}$ (as $\eta$
+decreases to $\eta_{\rm f} \ll 1$). Precession about $\uv{l}$ does not change the
+obliquity, so the range of obliquities at the end of phase (i) is frozen in as
+the range of final obliquities.
+
+Fig.~\ref{fig:nonad_3_ensemble} shows the numerical result of $\theta_{\rm f}$
+vs $\theta_{\rm sd,i}$ for $I =5^\circ$ and $\epsilon = 0.3$. We see that
+Eq.~\eqref{eq:nonad_q_f_dist} provides good lower and upper bounds of the final
+obliquity for $\theta_{\rm sd,i} \lesssim 45^\circ$ (see footnote 3).
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3scan.png}
+    \caption{Final obliquity $\theta_{\rm  f}$ as a function of $\epsilon$ for
+    $\theta_{\rm sd,i} = 0$ and $I = 5^\circ$. The shaded area, bordered by the
+    black line, corresponds to the adiabatic regime estimated by
+    Eq.~\eqref{eq:ad_constr}. The blue dots are numerical results, and the red
+    dashed line corresponds to Eq.~\eqref{eq:theta_2f}, which is in good
+    agreement with numerical results for $\epsilon > \epsilon_{\rm c} \approx
+    0.1$ (the nonadiabatic regime). Note that $\theta_{\rm f} \simeq 90^\circ$
+    in the adiabatic regime ($\epsilon\ll \epsilon_{\rm
+    c}$).}\label{fig:nonad_3_scan}
+\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.47\textwidth]{plots_diskdisp/3scan_20.png}
+%     \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$. The right
+%     shaded area is where $\theta_{\rm f}$ predicted by Eq.~\eqref{eq:theta_2f}
+%     violates the assumption $\theta_{\rm f} \gtrsim \theta_{\rm
+%     i}$.}\label{fig:nonad_3_scan_20}
+% \end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3_ensemble_05_05.png}
+    \caption{Final obliquity $\theta_{\rm  f}$ vs $\theta_{\rm sd, i}$ for
+    $I=5^\circ$ and $\epsilon = 0.3$ (firmly in the nonadiabatic regime). The
+    blue dots represent numerical results, and the two red lines show the
+    analytical lower and upper bounds given by
+    Eq.~\eqref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemble}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.47\textwidth]{plots_diskdisp/2_nonad_rot_cropped.png}
+    \caption{Schematic picture for understanding nonadiabatic obliquity
     evolution when $\theta_{\rm sd, i} > 0$ assuming $\eta_{\rm i} \gg 1$. The
@@
     $\theta_{\rm sd, i}$, centered on $\theta_{\rm 0f}$ (light red
-    area).}}\label{fig:2nonadrot}
-\end{figure}
-
-When $\theta_{\rm sd, i}\neq 0$, \textcolor{Corr}{we find that the final
-obliquity $\theta_{\rm f}$ varies over a range of values for a given
-$\theta_{\rm sd, i}$, as can be seen in Fig.~\ref{fig:nonad_3_ensemble}. The
-range can be described by}
-\begin{equation}
-    \abs{\theta_{\rm 0f} - \theta_{\rm sd, i}}
-        \lesssim \theta_{\rm f}
-        \lesssim \theta_{\rm 0f} + \theta_{\rm sd, i}
-    .\label{eq:nonad_q_f_dist}
-\end{equation}
-\textcolor{Corr}{
-This can be understood as follows (see Fig.~\ref{fig:2nonadrot}). In the
-beginning ($\eta = \eta_{\rm i} \gg 1$), the initial spin vector precesses
-around $\uv{l}_{\rm d}$ on a cone with opening half-angle $\theta_{\rm sd, i}$
-(more precisely, the cone is centered on CS2, which coincides with $\uv{l}_{\rm
-d}$ as $\eta_{\rm i} \to \infty$). Note that for $\eta \gg 1$, the adiabaticity
-condition is easily satisfied: Eq.~\eqref{eq:w_lib} gives $\omega_{\rm lib}
-\simeq \eta$ while Eq.~\eqref{eq:dq2dt} gives $\abs{\rdil{\theta_2}{\tau}} \sim
-\epsilon \tan\p{\theta_2 - I} \ll \eta$. As $\eta$ decreases, the system will
-transition from being adiabatic to being nonadiabatic, since $\epsilon \gtrsim
-\epsilon_{\rm c}$. The evolution of the system can thus be decomposed into
-two phases: (i) when the evolution is adiabatic, the spin vector will precess
-around the slowly-moving CS2, then (ii) when the evolution becomes nonadiabatic,
-the spin vector stops tracking the quickly-evolving CS2. During the adiabatic
-evolution of phase (i), the angle between CS2 and the spin vector is
-approximately unchanged due to conservation of phase space area}\footnote{
-\textcolor{Corr}{This approximation assumes sufficiently small $\theta_{\rm sd,
-i}$ such that libration about CS2 remains approximately circular throughout
-phase (i). Deviations from this approximation occur when $\theta_{\rm sd, i}$ is
-sufficiently large that libration cycles become non-circular as $\eta$ decreases
-(Fig.~\ref{fig:eq_1contours} illustrates that libration cycles farther from CS2
-are less circular).
-% Such deformations decrease the obliquity spanned by the cone (see
-% Fig.~\ref{fig:eq_1contours} for decreasing $\eta$; note that level curves of $H$
-% correspond to bases of cones), which causes the observed range of final
-% obliquities in Fig.~\ref{fig:nonad_3_ensemble} to be smaller than predicted by
-% Eq.~\eqref{eq:nonad_q_f_dist} when $\theta_{\rm sd, i} \gtrsim 45^\circ$.
-This causes the deviation of the data in Fig.~\ref{fig:nonad_3_ensemble} from
-Eq.~\eqref{eq:nonad_q_f_dist} for $\theta_{\rm sd, i} \gtrsim 45^\circ$.
-}}.
-\textcolor{Corr}{Once the evolution enters phase (ii), the precession axis
-quickly (on timescale $\ll 1 / \omega_{\rm lib}$) changes to $\uv{l}$ (as $\eta
-\to \eta_{\rm f} \ll 1$). Precession about $\uv{l}$ does not change the
-obliquity, so the range of obliquities when the spin vector stops tracking CS2
-is frozen in as the range of final obliquities.}
-
-Fig.~\ref{fig:nonad_3_ensemble} shows the numerical result of $\theta_f$ vs
-$\theta_{\rm sd,i}$ for $I =5^\circ$ and $\epsilon = 0.3$. We see that
-Eq.~\eqref{eq:nonad_q_f_dist} provides good lower and upper bounds of the final
-obliquity for $\theta_{\rm sd,i} \lesssim 45^\circ$.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3scan.png}
-    \caption{Final obliquity $\theta_{\rm  f}$ as a function of $\epsilon$ for
-    $\theta_{\rm sd,i} = 0$ and $I = 5^\circ$. The shaded area, bordered by the
-    black line, corresponds to the adiabatic regime estimated by
-    Eq.~\eqref{eq:ad_constr}. The blue dots are numerical results, and the red
-    dashed line corresponds to Eq.~\eqref{eq:theta_2f}, which is in good
-    agreement with numerical results for $\epsilon > \epsilon_{\rm c} \approx
-    0.1$ (the nonadiabatic regime). Note that $\theta_{\rm f} \simeq 90^\circ$
-    in the adiabatic regime ($\epsilon\ll \epsilon_{\rm
-    c}$).}\label{fig:nonad_3_scan}
-\end{figure}
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.47\textwidth]{plots_diskdisp/3scan_20.png}
-%     \caption{Same as Fig.~\ref{fig:nonad_3_scan} but for $I=20^\circ$. The right
-%     shaded area is where $\theta_{\rm f}$ predicted by Eq.~\eqref{eq:theta_2f}
-%     violates the assumption $\theta_{\rm f} \gtrsim \theta_{\rm
-%     i}$.}\label{fig:nonad_3_scan_20}
-% \end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3_ensemble_05_05.png}
-    \caption{Final obliquity $\theta_{\rm  f}$ vs $\theta_{\rm sd, i}$ for
-    $I=5^\circ$ and $\epsilon = 0.3$ (firmly in the nonadiabatic regime). The
-    blue dots represent numerical results, and the two red lines show the
-    analytical lower and upper bounds given by
-    Eq.~\eqref{eq:nonad_q_f_dist}.}\label{fig:nonad_3_ensemble}
-\end{figure}
-
-\section{Summary}\label{s:disc}
+    area).}\label{fig:2nonadrot}
+\end{figure}
+
+\section{Summary}\label{s:disk}
 
@@
         sufficiently slow rate), we reproduce the known result $\theta_{\rm f}
-        \simeq 90^\circ$ for $\theta_{\rm sd, i} \simeq 0$. We demonstrate via
-        numerical calculation and analytical argument the dual-valued behavior
-        of $\theta_{\rm f}$ for nonzero initial spin-disk misalignment angles
-        $\theta_{\rm sd, i}$ (see Fig.~\ref{fig:ad_ensemble}). We are able to
-        capture both the exact final $\theta_{\rm f}$ values and the
-        probabilities of achieving each value via careful accounting of
-        adiabatic invariance and separatrix crossing dynamics.
+        \simeq 90^\circ$ for $\theta_{\rm sd, i} \simeq 0$. We demonstrate (via
+        numerical calculation and analytical argument) the dual-valued behavior
+        of $\theta_{\rm f}$ for nonzero $\theta_{\rm sd, i}$ (see
+        Fig.~\ref{fig:ad_ensemble}). We analytically calculate both the exact
+        final $\theta_{\rm f}$ values and the probabilities of achieving each
+        value via careful accounting of adiabatic invariance and separatrix
+        crossing dynamics.
     \item As the disk dissipates more rapidly, the adiabatic condition
@@
 regime ($\eta\ll 1$).  The new analytical results presented in this paper can be
-adapted for other applications.
+adapted to other applications.
 
@@
 
-We thank Kassandra Anderson for discussion and assistance in the early phase of
+We thank Kassandra Anderson for diskussion and assistance in the early phase of
 this work. DL thanks the Dept.\ of Astronomy and the Miller Institute for Basic
@@
 % We next develop some approximate forms for the CS obliquities that will be
-% useful for guiding later discussion. Denote $\theta_{\rm cs}$ the obliquity of
+% useful for guiding later diskussion. Denote $\theta_{\rm cs}$ the obliquity of
 % some Cassini State (fixed point of Eqs.~\eqref{se:H_eom}).

### 2020-04-29 writeups/Su_disk_disp.tex
new bib file (need same name for arxiv)

@@
-%%  twocolumn   : two text columns, 10 point font, single spaced article.
-%%                This is the most compact and represent the final published
-%%                derived PDF copy of the accepted manuscript from the publisher
-%%  manuscript  : one text column, 12 point font, double spaced article.
-%%  preprint    : one text column, 12 point font, single spaced article.
-%%  preprint2   : two text columns, 12 point font, single spaced article.
-%%  modern      : a stylish, single text column, 12 point font, article with
-%%        wider left and right margins. This uses the Daniel
-%%        Foreman-Mackey and David Hogg design.
-%%  RNAAS       : Preferred style for Research Notes which are by design
-%%                lacking an abstract and brief. DO NOT use \begin{abstract}
-%%                and \end{abstract} with this style.
     \documentclass[twocolumn,twocolappendix]{aastex63}
@@
         booktabs,
-        caption,
-        subcaption,
-        xcolor,
     }
     \usepackage[T1]{fontenc}
-    \captionsetup{compatibility=false}
 
@@
 
-    \colorlet{Corr}{red}
-
-    \newcommand{\vdag}{(v)^\dagger}
     \newcommand\aastex{AAS\TeX}
@@
 $\theta_2 \simeq I + \eta^{-1}\sin I \cos I$ (see
-Section~\ref{s:s:local_dynamics}), Eq.~\eqref{eq:w_lib} gives $\omega_{\rm lib}
+Section~\ref{s:local_dynamics}), Eq.~\eqref{eq:w_lib} gives $\omega_{\rm lib}
 \simeq \eta$ while Eq.~\eqref{eq:dq2dt} gives $\abs{\rdil{\theta_2}{\tau}}
@@
 
-\bibliography{Su_sep_cross}
+\bibliography{Su_disk_disp}
 \bibliographystyle{aasjournal}

### 2020-05-11 initial/notes.tex
stash for princeton presentation

@@
     \newcommand*{\at}[1]{\left.#1\right|}
+    \newcommand*{\bra}[1]{\left<#1\right|}
+    \newcommand*{\ket}[1]{\left|#1\right>}
+    \newcommand*{\abs}[1]{\left|#1\right|}
+    \newcommand*{\ev}[1]{\langle#1\rangle}
+    \newcommand*{\p}[1]{\left(#1\right)}
+    \newcommand*{\s}[1]{\left[#1\right]}
+    \newcommand*{\z}[1]{\left\{#1\right\}}
 
@@
 
-    \DeclarePairedDelimiter\bra{\langle}{\rvert}
-    \DeclarePairedDelimiter\ket{\lvert}{\rangle}
-    \DeclarePairedDelimiter\abs{\lvert}{\rvert}
-    \DeclarePairedDelimiter\ev{\langle}{\rangle}
-    \DeclarePairedDelimiter\p{\lparen}{\rparen}
-    \DeclarePairedDelimiter\s{\lbrack}{\rbrack}
-    \DeclarePairedDelimiter\z{\lbrace}{\rbrace}
-
     % \everymath{\displaystyle} % biggify limits of inline sums and integrals
@@
 \begin{equation}
-    \mathcal{H} = -\frac{1}{2}\p*{\hat{s} \cdot \hat{l}}^2
-        + \eta \p*{\hat{s} \cdot \hat{l}_p}.
+    \mathcal{H} = -\frac{1}{2}\p{\hat{s} \cdot \hat{l}}^2
+        + \eta \p{\hat{s} \cdot \hat{l}_p}.
 \end{equation}
@@
     \hat{s} = \cos\theta \hat{z}
-        - \sin\theta\p*{\sin \phi \hat{y} + \cos \phi \hat{x}}.
+        - \sin\theta\p{\sin \phi \hat{y} + \cos \phi \hat{x}}.
 \end{equation*}
@@
     \mathcal{H} &= -\frac{1}{2}\cos^2\theta
-        + \eta \p*{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
+        + \eta \p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}.
 \end{align*}
@@
     \rd{\hat{s}}{t} &=
-        \p*{\hat{s} \cdot \hat{l}}\p*{\hat{s} \times \hat{l}}
-            -\eta\p*{\hat{s} \times \hat{l}_p},\\
-        &= \p*{s_ys_z - \eta s_y\cos(I)}\hat{x}
-            - \p*{s_xs_z + \eta \p*{s_x\cos I - s_z\sin I}}\hat{y}
+        \p{\hat{s} \cdot \hat{l}}\p{\hat{s} \times \hat{l}}
+            -\eta\p{\hat{s} \times \hat{l}_p},\\
+        &= \p{s_ys_z - \eta s_y\cos(I)}\hat{x}
+            - \p{s_xs_z + \eta \p{s_x\cos I - s_z\sin I}}\hat{y}
             + \eta s_y \sin(I)\hat{z}.
@@
     \pd{\phi}{t} = \pd{\mathcal{H}}{(\cos\theta)}
-        &= -\cos\theta + \eta\p*{\cos I + \sin I \cot \theta \cos \phi},\\
+        &= -\cos\theta + \eta\p{\cos I + \sin I \cot \theta \cos \phi},\\
     \pd{(\cos \theta)}{t} = -\pd{\mathcal{H}}{\phi}
@@
 
-    \item For $\mu \approx 0$, we have instead $\pd{\phi}{t} = -\mu\p*{1 - \eta
+    \item For $\mu \approx 0$, we have instead $\pd{\phi}{t} = -\mu\p{1 - \eta
         \sin I \cos \phi} + \eta \cos I = 0$. This forces $\mu_\pm = \frac{\eta
@@
         Note that $\phi = 0, \mu \approx 0$ is conventionally CS4. The
-        linearization locally has form $\pd{\delta \phi}{t} = -\delta \mu\p*{1 -
+        linearization locally has form $\pd{\delta \phi}{t} = -\delta \mu\p{1 -
         \eta \sin I}$ and $\pd{\delta \mu}{t} = -\eta \sin I \delta \phi$, so
         the eigenvalues are $\approx \mp \sqrt{\eta \sin I}$, and the two
-        eigenvectors are $\p*{1, \pm \sqrt{\eta \sin I}}$.
+        eigenvectors are $\p{1, \pm \sqrt{\eta \sin I}}$.
 \end{itemize}
@@
 \begin{align*}
-    H_4 &\equiv H\p*{\mu_4, \phi_4}
+    H_4 &\equiv H\p{\mu_4, \phi_4}
         \approx -\frac{\mu_4^2}{2} + \eta \mu_4 \cos I - \eta \sin I,\\
@@
     0 &\approx \frac{\mu_{sep}^2}{2} - \eta \mu_{sep} \cos I
-        - \eta \sin I\p*{1 - \cos \phi_{sep}} + \frac{\eta^2\cos^2I}{2},\\
-    \mu_{sep}\p*{\phi} &\approx \sqrt{2\eta \sin I\p*{1 - \cos \phi}}
+        - \eta \sin I\p{1 - \cos \phi_{sep}} + \frac{\eta^2\cos^2I}{2},\\
+    \mu_{sep}\p{\phi} &\approx \sqrt{2\eta \sin I\p{1 - \cos \phi}}
         + \mathcal{O}(\eta).
@@
 We can add a tidal dissipation term; we write it in form
-$\p*{\rd{\hat{s}}{t}}_{tide} = \epsilon \hat{s} \times \p*{\hat{l} \times
-\hat{s}} = \epsilon\p*{\vec{l} - \p*{\vec{s} \cdot \vec{l}}\vec{s}}$. Expanding,
-\begin{align}
-    \p*{\rd{\hat{s}}{t}}_{tide} &= \epsilon \p*{\hat{z} - s_z\hat{s}}
+$\p{\rd{\hat{s}}{t}}_{tide} = \epsilon \hat{s} \times \p{\hat{l} \times
+\hat{s}} = \epsilon\p{\vec{l} - \p{\vec{s} \cdot \vec{l}}\vec{s}}$. Expanding,
+\begin{align}
+    \p{\rd{\hat{s}}{t}}_{tide} &= \epsilon \p{\hat{z} - s_z\hat{s}}
         ,\nonumber\\
-        &= \epsilon \p*{-s_z s_x\hat{x} - s_zs_y\hat{y} + \p*{1 - s_z^2}
+        &= \epsilon \p{-s_z s_x\hat{x} - s_zs_y\hat{y} + \p{1 - s_z^2}
             \hat{z}}.\label{eq:p1_eom}
@@
     0 &= s_ys_z - \eta s_y\cos I - \epsilon s_zs_x,\\
-    0 &= -s_xs_z - \eta\p*{s_x \cos I - s_z \sin I} - \epsilon s_zs_y,\\
-    0 &= \eta s_y\sin(I) + \epsilon \p*{1 - s_z^2}.
+    0 &= -s_xs_z - \eta\p{s_x \cos I - s_z \sin I} - \epsilon s_zs_y,\\
+    0 &= \eta s_y\sin(I) + \epsilon \p{1 - s_z^2}.
 \end{align*}
@@
 can set $s_z = 1$ to first order: $s_y - \epsilon s_x - \eta s_y \cos I = -s_x -
-\eta\p*{s_x \cos I - \sin I} - \epsilon s_y = \eta s_y \sin I = 0$. This can be
-satisfied if we set $s_x = \tan(I) \ll 1, s_y = \mathcal{O}\p*{\epsilon s_x}$;
+\eta\p{s_x \cos I - \sin I} - \epsilon s_y = \eta s_y \sin I = 0$. This can be
+satisfied if we set $s_x = \tan(I) \ll 1, s_y = \mathcal{O}\p{\epsilon s_x}$;
 this coarsely corresponds to Cassini state $1$.
@@
 dropping second order terms forces $\eta s_y + \epsilon s_z = -s_z -
-\eta\p*{\cos I - s_z\sin I} = \eta s_y \sin(I) + \epsilon = 0$. This can thus be
+\eta\p{\cos I - s_z\sin I} = \eta s_y \sin(I) + \epsilon = 0$. This can thus be
 satisfied for $s_y \approx -\frac{\epsilon}{\eta \sin(I)}$. Thus, this explains
@@
 \begin{align}
-    \pd{\phi}{t} &= -\mu + \eta\p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}}
+    \pd{\phi}{t} &= -\mu + \eta\p{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}}
         \cos \phi} ,\\
-    \pd{\mu}{t} &= -\eta \sin I \sin \phi + \s*{\epsilon \p*{1 - \mu^2}},
+    \pd{\mu}{t} &= -\eta \sin I \sin \phi + \s{\epsilon \p{1 - \mu^2}},
 \end{align}
 we can perturbatively require $\pd{\theta}{t} = 0$ for $\epsilon \neq 0$. This
-corresponds to $\eta \sin I \sin \p*{\phi_4 + \delta \phi} \approx \epsilon$, or
+corresponds to $\eta \sin I \sin \p{\phi_4 + \delta \phi} \approx \epsilon$, or
 $\delta \phi_4 = +\frac{\epsilon}{\eta \sin I}$. This is in agreement with
@@
 \begin{align}
-    d(t_0) &= \frac{\epsilon M(t_0)}{\abs*{f(q^0(0))}} + \mathcal{O}(\epsilon^2)
+    d(t_0) &= \frac{\epsilon M(t_0)}{\abs{f(q^0(0))}} + \mathcal{O}(\epsilon^2)
         ,\\
     M(t_0) &= \int\limits_{-\infty}^\infty
-        \s*{f \times g}_{hetero}\;\mathrm{d}t.
+        \s{f \times g}_{hetero}\;\mathrm{d}t.
 \end{align}
@@
             \pd{\mathcal{H}}{\mu}\hat{\phi} - \pd{\mathcal{H}}{\phi}\hat{\mu}}_f
-            + \epsilon \underbrace{\p*{1 - \mu^2}\hat{\mu}}_g.
-\end{align}
-Then $f \times g = f_\phi g_\mu = \pd{\mathcal{H}}{\mu}\p*{1 - \mu^2}$. We then
+            + \epsilon \underbrace{\p{1 - \mu^2}\hat{\mu}}_g.
+\end{align}
+Then $f \times g = f_\phi g_\mu = \pd{\mathcal{H}}{\mu}\p{1 - \mu^2}$. We then
 want to integrate this along the heteroclinic orbit. We can make change of
@@
     M = \int\limits_0^{2\pi}\pd{\mathcal{H}}{\mu}
-        \p*{1 - \mu^2}\p*{\pd{\phi}{t}}^{-1}\;\mathrm{d}\phi.
+        \p{1 - \mu^2}\p{\pd{\phi}{t}}^{-1}\;\mathrm{d}\phi.
 \end{equation}
 But thankfully, $\pd{\mathcal{H}}{\mu} = \pd{\phi}{t}$ in the absence of
-dissipation, and so $M = 2\pi\p*{1 - \mu^2} \approx 2\pi$.
+dissipation, and so $M = 2\pi\p{1 - \mu^2} \approx 2\pi$.
 Thus, the Melnikov distance at point $q^0$, a point on the heteroclinic
@@
 \begin{equation}
-    d(q^0) = \frac{2\pi \epsilon}{\abs*{f(q^0)}}.
-\end{equation}
-Note that the maximum value $\abs*{f(q^0)}$, which occurs at $\phi = \pi$, is
+    d(q^0) = \frac{2\pi \epsilon}{\abs{f(q^0)}}.
+\end{equation}
+Note that the maximum value $\abs{f(q^0)}$, which occurs at $\phi = \pi$, is
 just $f_{\max} \approx \sqrt{4\eta \sin I}$.
@@
 the $\delta \mu^{-1}$ case. In this case, define $\delta \mu_c: \Delta
-\mu\p*{\delta \mu_c} = -\delta \mu_c$, i.e.\ the point that jumps immediately to
+\mu\p{\delta \mu_c} = -\delta \mu_c$, i.e.\ the point that jumps immediately to
 the saddle point. Furthermore, assume the inbound distribution is flat between
-$\delta \mu_c, f^{-1}\p*{\delta \mu_c}$. TODO\@: empirically, $\mu_c \sim
+$\delta \mu_c, f^{-1}\p{\delta \mu_c}$. TODO\@: empirically, $\mu_c \sim
 \epsilon T$ is \emph{flat} with $\eta$, probably just because we're not getting
@@
 the separatrix versus the total predicted interval width $\delta \mu_c,
-f^{-1}\p*{\delta \mu_c}$; this would predict $7.2\%, 18\%$. This does alright!
+f^{-1}\p{\delta \mu_c}$; this would predict $7.2\%, 18\%$. This does alright!
 
@@
 \begin{equation}
-    M_c = \int\limits_0^T \pd{\phi}{t}\epsilon \p*{1 - \mu^2}\;\mathrm{d}t.
+    M_c = \int\limits_0^T \pd{\phi}{t}\epsilon \p{1 - \mu^2}\;\mathrm{d}t.
 \end{equation}
@@
     M_c = 2\int\limits_0^{2\pi}2\epsilon \frac{\eta \cos I}{1 + \eta \sin I}
-        \sqrt{2\eta \sin I \p*{1 - \cos \phi}}\;\mathrm{d}\phi.
+        \sqrt{2\eta \sin I \p{1 - \cos \phi}}\;\mathrm{d}\phi.
 \end{equation}
@@
     M_c &\approx \epsilon 2\eta \cos I A_{sep},\\
-    \Delta_c &\approx 2\epsilon \eta \cos I \p*{16 \sqrt{\eta \sin I}}
+    \Delta_c &\approx 2\epsilon \eta \cos I \p{16 \sqrt{\eta \sin I}}
         \frac{1}{\sqrt{4\eta \sin I}},\\
@@
     P_{hop} = \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi
-        \p*{1 - 2\eta \sin I - \eta^2 \cos^2 I}
+        \p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
         + 8\eta^{3/2}\cos I \sqrt{\sin I}}.
@@
 \begin{equation}
-    B_i = \int_{\mathcal{C}_i} \dot{\alpha}\s*{
+    B_i = \int_{\mathcal{C}_i} \dot{\alpha}\s{
         \frac{\mu^2}{2} - \frac{1}{2\alpha^2}\cos^2 I}
@@
 \begin{align*}
-    B_i &= \int -\frac{\epsilon \mu}{2\alpha^2}\s*{
+    B_i &= \int -\frac{\epsilon \mu}{2\alpha^2}\s{
         \alpha^2 \mu^2 - \cos^2 I}\;\mathrm{d}t,\\
@@
         &\approx +\frac{\epsilon}{2\alpha^2}\int
-            \mu\p*{\alpha \mu + \cos I}\;\mathrm{d}\phi.
+            \mu\p{\alpha \mu + \cos I}\;\mathrm{d}\phi.
 \end{align*}
@@
 First, we tackle the top integral. Here, the integrand is evaluated at
-$\mu_+(\phi) = \eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}$\footnote{
+$\mu_+(\phi) = \eta \cos I + \sqrt{2\eta \sin I\p{1 - \cos \phi}}$\footnote{
 Bears noting that $\mu_{\pm} = \frac{\eta \cos I}{1 - \eta \sin I} \pm \dots$
@@
         &= -\int\limits_0^{2\pi}
-            \p*{\eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}}
-                \p*{2\cos I + \sqrt{2\sin I\p*{1 - \cos \phi}/\eta}}
+            \p{\eta \cos I + \sqrt{2\eta \sin I\p{1 - \cos \phi}}}
+                \p{2\cos I + \sqrt{2\sin I\p{1 - \cos \phi}/\eta}}
                 \;\mathrm{d}\phi.
@@
 We now track the bottom integral. Here, the integrand is instead evaluated at
-$\mu_-(\phi) = \eta \cos I - \sqrt{2\eta \sin I\p*{1 - \cos \phi}}$. This flips
+$\mu_-(\phi) = \eta \cos I - \sqrt{2\eta \sin I\p{1 - \cos \phi}}$. This flips
 the signs of the (O) and (I) terms above. Furthermore, the $\mathrm{d}\phi$
@@
     H &= -\frac{\mu^2}{2}
-            + \eta\p*{\mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi}, &
+            + \eta\p{\mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi}, &
     H_4 &= -\eta \sin I + \frac{\eta^2 \cos^2 I}{2}.
@@
     B_i &= \int_{\mathcal{C}_i} \epsilon \mu \eta
-            \s*{-\sin I + \eta \cos^2 I -
-                \p*{\mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi}}
+            \s{-\sin I + \eta \cos^2 I -
+                \p{\mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi}}
             \;\mathrm{d}t,\\
@@
             \frac{\eta \cos^2 I - \mu \cos I
-                + \sin I\p*{\cos \phi \sqrt{1 - \mu^2} - 1}}{-\mu + \eta \cos I}
+                + \sin I\p{\cos \phi \sqrt{1 - \mu^2} - 1}}{-\mu + \eta \cos I}
             \;\mathrm{d}\phi,\\
         &= \int_{\mathcal{C}_i} \epsilon \mu \eta
-            \p*{\cos I + \sin I \frac{\cos \phi \sqrt{1 - \mu^2} - 1}{-\mu +
+            \p{\cos I + \sin I \frac{\cos \phi \sqrt{1 - \mu^2} - 1}{-\mu +
             \eta \cos I}} \;\mathrm{d}\phi.
@@
     \frac{\cos \phi\sqrt{1 - \mu^2} - 1}{\mu - \eta \cos I}
-        &\approx \frac{\sqrt{1 - 2\eta \sin I\p*{1 - \cos \phi}}\cos \phi
+        &\approx \frac{\sqrt{1 - 2\eta \sin I\p{1 - \cos \phi}}\cos \phi
             - 1}{\mu - \eta \cos I},\\
@@
     B_i &= \int_{\mathcal{C}_i} \epsilon \mu \eta
-            \p*{\cos I \pm \sin I
+            \p{\cos I \pm \sin I
                 \sqrt{\frac{1 - \cos \phi}{2\eta \sin I}}} \;\mathrm{d}\phi.
@@
             + \frac{\epsilon}{2}\int\limits_{2\pi}^0
-                \mu\sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
-        &= -\epsilon \eta \cos I\p*{2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
-            - \frac{\epsilon}{2}\p*{\eta \cos I (8\sqrt{\eta \sin I})
+                \mu\sqrt{2\eta \sin I\p{1 - \cos \phi}}\;\mathrm{d}\phi,\\
+        &= -\epsilon \eta \cos I\p{2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
+            - \frac{\epsilon}{2}\p{\eta \cos I (8\sqrt{\eta \sin I})
             + 4\pi \eta \sin I},\\
-        &= -\epsilon \eta \s*{
+        &= -\epsilon \eta \s{
             2\pi \sin I + 12\sqrt{\eta \sin I}\cos I + 2\pi \eta \cos^2 I}.
@@
             + \frac{\epsilon}{2}\int\limits_{2\pi}^0
-                \sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
+                \sqrt{2\eta \sin I\p{1 - \cos \phi}}\;\mathrm{d}\phi,\\
         &= -2\pi \epsilon \eta \cos I - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
@@
 \end{equation}
-Generally, since $\eta$ is small, $B_{+} + B_- < -\abs*{B_+}, -\abs*{B_-}$ which
+Generally, since $\eta$ is small, $B_{+} + B_- < -\abs{B_+}, -\abs{B_-}$ which
 implies guaranteed capture from both sides, as expected (note that in our actual
@@
 \begin{equation}
-    \Delta_{\pm} = \epsilon\s*{\mp 2\pi \p*{1 - 2\eta \sin I - \eta^2 \cos^2 I} +
+    \Delta_{\pm} = \epsilon\s{\mp 2\pi \p{1 - 2\eta \sin I - \eta^2 \cos^2 I} +
         16\cos I\eta^{3/2}\sqrt{\sin I}} + f\epsilon
-            \s*{\pm 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
+            \s{\pm 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
 \end{equation}
@@
 Previously, we took the effect of tides to simply be $\rd{\hat{s}}{t} = \epsilon
-\hat{s} \times \p*{\hat{l} \times \hat{s}}$, but in reality, tides will spin
+\hat{s} \times \p{\hat{l} \times \hat{s}}$, but in reality, tides will spin
 down the body (in our case, planet) at the same rate as aligning $\hat{s}$ to
@@
     \rd{\hat{s}}{t}
-        &= \omega_{s1}\p*{\hat{s} \cdot \hat{l}_1}\p*{\hat{s} \times \hat{l}_1}
-            - \omega_{1p}\cos(I)\p*{\hat{s} \times \hat{l}_p},\\
-    \omega_{s1} &= \frac{3k_q}{2k}\frac{M_*}{m_1}\p*{\frac{R_1}{a_1}}^3 s,\\
-    \omega_{1p} &= \frac{3m_p}{4m_*}\p*{\frac{a_1}{a_p\sqrt{1 - e_p^2}}}^3 \Omega_1.
+        &= \omega_{s1}\p{\hat{s} \cdot \hat{l}_1}\p{\hat{s} \times \hat{l}_1}
+            - \omega_{1p}\cos(I)\p{\hat{s} \times \hat{l}_p},\\
+    \omega_{s1} &= \frac{3k_q}{2k}\frac{M_*}{m_1}\p{\frac{R_1}{a_1}}^3 s,\\
+    \omega_{1p} &= \frac{3m_p}{4m_*}\p{\frac{a_1}{a_p\sqrt{1 - e_p^2}}}^3 \Omega_1.
 \end{align}
@@
         this, we need that the gravitational potential of a ring inside the ring
-        scales $\Phi'(r) \sim \frac{Gm_p}{a_p}\p*{\frac{r}{a_p}}^2$, and so
+        scales $\Phi'(r) \sim \frac{Gm_p}{a_p}\p{\frac{r}{a_p}}^2$, and so
         \begin{equation}
             \omega_{1p} \sim \frac{\Phi'}{\Phi_0}n
-                \sim \frac{m_p}{m}\p*{\frac{a_1}{a_p}}^3n.
+                \sim \frac{m_p}{m}\p{\frac{a_1}{a_p}}^3n.
         \end{equation}
@@
         limited terms of the expansion of $\Phi$. The way we get the expansion
-        of $\Phi$ is just by expanding $\frac{1}{\abs*{\vec{r} - \vec{r}_d}}
-        \sim \frac{1}{\p*{r^2 - rr_d\cos\theta + r_d^2}^{1/2}}$ as a Taylor
+        of $\Phi$ is just by expanding $\frac{1}{\abs{\vec{r} - \vec{r}_d}}
+        \sim \frac{1}{\p{r^2 - rr_d\cos\theta + r_d^2}^{1/2}}$ as a Taylor
         series for small $\vec{r}_d$.
@@
             \omega_{s1} &\sim \frac{GM_* J_2 m_1 R_1^2/a^3}{k_p m_1 R_1^2s},\\
-                &\sim \frac{k_{qp}}{k_p}\frac{M_*}{m_1} \p*{\frac{R_1}{a}}^3s.
+                &\sim \frac{k_{qp}}{k_p}\frac{M_*}{m_1} \p{\frac{R_1}{a}}^3s.
         \end{align}
@@
         = \frac{1}{s}\rd{s}{t}
-        &= \frac{1}{t_s}\frac{L}{2S}\s*{\cos\theta
-            - \frac{s}{2\Omega_1}\p*{1 + \cos^2\theta}},\\
+        &= \frac{1}{t_s}\frac{L}{2S}\s{\cos\theta
+            - \frac{s}{2\Omega_1}\p{1 + \cos^2\theta}},\\
     \rd{\theta}{t} &= -\frac{1}{t_s}\frac{L}{2S}
-        \sin\theta\p*{1 - \frac{s}{2\Omega_1}\cos\theta}.
+        \sin\theta\p{1 - \frac{s}{2\Omega_1}\cos\theta}.
 \end{align}
@@
     \rd{\hat{s}}{\tau}
-        &= \frac{s}{s_c}\p*{\hat{s} \cdot \hat{l}_1}\p*{\hat{s} \times \hat{l}_1}
+        &= \frac{s}{s_c}\p{\hat{s} \cdot \hat{l}_1}\p{\hat{s} \times \hat{l}_1}
             - \hat{s} \times \hat{l}_p
             + \frac{\epsilon 2\Omega_1}{s}
-                \p*{1 - \frac{s}{2\Omega_1}\p*{\hat{l}_1 \cdot \hat{s}}}
-                    \hat{s} \times \p*{\hat{l}_1 \times \hat{s}},\\
+                \p{1 - \frac{s}{2\Omega_1}\p{\hat{l}_1 \cdot \hat{s}}}
+                    \hat{s} \times \p{\hat{l}_1 \times \hat{s}},\\
     \rd{s}{\tau}
-        &= \epsilon 2\Omega_1 \p*{\hat{s} \cdot \hat{l}_1 - \frac{s}{2\Omega_1}\p*{1
-            + \p*{\hat{s} \cdot \hat{l}_1}^2}}.
+        &= \epsilon 2\Omega_1 \p{\hat{s} \cdot \hat{l}_1 - \frac{s}{2\Omega_1}\p{1
+            + \p{\hat{s} \cdot \hat{l}_1}^2}}.
 \end{align}
@@
     \pd{\phi}{\tau} &= -\frac{s}{s_c}\mu
-        + \p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}} \cos \phi} ,\\
+        + \p{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}} \cos \phi} ,\\
     \pd{\mu}{\tau} &= -\sin I \sin \phi +
-        \epsilon \frac{2\Omega_1}{s}\p*{1 - \mu^2}
-            \p*{1 - \frac{s}{2\Omega_1}\mu},\\
+        \epsilon \frac{2\Omega_1}{s}\p{1 - \mu^2}
+            \p{1 - \frac{s}{2\Omega_1}\mu},\\
     \rd{s}{\tau}
-        &= \epsilon 2\Omega_1 \p*{\mu - \frac{s}{2\Omega_1}\p*{1 + \mu^2}}.
+        &= \epsilon 2\Omega_1 \p{\mu - \frac{s}{2\Omega_1}\p{1 + \mu^2}}.
 \end{align}
@@
     \begin{align}
-        \pd{\mu}{(\epsilon\tau)} &\approx \frac{2\Omega_1}{s}\p*{1 - \mu^2}
-                \p*{1 - \frac{s}{2\Omega_1}\mu},\nonumber\\
-            &\approx \p*{1 - \mu^2}
-                \p*{\frac{2\Omega_1}{s} - \mu},\\
+        \pd{\mu}{(\epsilon\tau)} &\approx \frac{2\Omega_1}{s}\p{1 - \mu^2}
+                \p{1 - \frac{s}{2\Omega_1}\mu},\nonumber\\
+            &\approx \p{1 - \mu^2}
+                \p{\frac{2\Omega_1}{s} - \mu},\\
         \frac{1}{\Omega_1}\rd{s}{(\epsilon\tau)}
-            &\approx 2\mu - \frac{s}{\Omega_1}\p*{1 + \mu^2}.
+            &\approx 2\mu - \frac{s}{\Omega_1}\p{1 + \mu^2}.
     \end{align}
@@
 In the last term, we note $s \gtrsim 2\Omega_1$ initially, while $\mu \leq 1$,
-so we drop both the linear contribution from $\mu$ and approximate $\p*{1 +
+so we drop both the linear contribution from $\mu$ and approximate $\p{1 +
 \mu^2} \approx 1$ so that $\rd{(s/\Omega_1)}{(\epsilon\tau)} \approx
@@
 \end{align*}
-The precession averaged equations bound $\rd{\mu}{\p*{\epsilon\sigma}} <
+The precession averaged equations bound $\rd{\mu}{\p{\epsilon\sigma}} <
 \frac{2\Omega_1}{s}$, so in order for $\mu < \mu_4$ to approach the Cassini
@@
 \begin{equation}
-    \eta = \eta_c \equiv \p*{\sin^{2/3}I + \cos^{2/3}I}^{-3/2}.
+    \eta = \eta_c \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{-3/2}.
 \end{equation}
@@
         $\mu_0$, then the dynamics of the system can be described by a map
-        $\mu_{0, i + 1}\p*{\mu_{0, i}, s}$. The reason $\mu_0$ is important is
+        $\mu_{0, i + 1}\p{\mu_{0, i}, s}$. The reason $\mu_0$ is important is
         that only when $\mu_0 = \mu_4(s)$ CS4 can separatrix hopping occur.
@@
                 &= \frac{\dot{\phi}}{\dot{\phi}(\phi = 0)}
-                    \p*{\epsilon\p*{1 - \mu^2}\p*{\frac{2\Omega_1}{s}
+                    \p{\epsilon\p{1 - \mu^2}\p{\frac{2\Omega_1}{s}
                         - \mu}},\nonumber\\
-            \ev*{\rd{\mu_0}{t}} &=
+            \ev{\rd{\mu_0}{t}} &=
                 \frac{1}{T}\int\limits_0^T
                     \frac{\dot{\phi}}{\dot{\phi}_0}
-                        \epsilon\p*{1 - \mu^2}\p*{\frac{2\Omega_1}{s} - \mu}
+                        \epsilon\p{1 - \mu^2}\p{\frac{2\Omega_1}{s} - \mu}
                             \;\mathrm{d}t,\nonumber\\
@@
                     \frac{1}{\dot{\phi}_0}
-                        \epsilon\p*{1 - \mu^2}\p*{\frac{2\Omega_1}{s} - \mu}
+                        \epsilon\p{1 - \mu^2}\p{\frac{2\Omega_1}{s} - \mu}
                             \;\mathrm{d}\phi,\nonumber\\
@@
                     \int\limits_0^{2\pi}
-                        \epsilon\p*{1 - \mu^2}\p*{\frac{2\Omega_1}{s} - \mu}
+                        \epsilon\p{1 - \mu^2}\p{\frac{2\Omega_1}{s} - \mu}
                         \;\mathrm{d}\phi.\label{eq:final_approx}
@@
                 \begin{cases}
-                    \rd{\mu_0}{t} & \abs*{\Delta \mu} \gtrsim
+                    \rd{\mu_0}{t} & \abs{\Delta \mu} \gtrsim
                         2\sqrt{\eta \sin I},\\
                     -\frac{\cot I}{2\pi \Delta \mu}
-                        \epsilon\p*{1 - \mu_{eff}^2}
-                            \p*{\frac{2\Omega_1}{s} - \mu_{eff}}
+                        \epsilon\p{1 - \mu_{eff}^2}
+                            \p{\frac{2\Omega_1}{s} - \mu_{eff}}
                             & \text{otherwise}.
@@
         chance at hopping. We can perform similar Melnikov calculation to above
-        by integrating the true tidal term $\pd{\mu^{(1)}}{t} = \epsilon\p*{1 -
-        \mu^2}\p*{2\Omega_1/s - \mu}$ and find that the hopping probability
+        by integrating the true tidal term $\pd{\mu^{(1)}}{t} = \epsilon\p{1 -
+        \mu^2}\p{2\Omega_1/s - \mu}$ and find that the hopping probability
         $P_{hop} \propto \frac{\mu}{2\Omega_1/s} \propto \sqrt{s}$ or in fact
@@
 \begin{align}
-    \Delta_M &= \int\limits_0^{2\pi}\epsilon\p*{1 - \mu^2}
-            \p*{\frac{2\Omega}{s} - \mu} \;\mathrm{d}\phi,\nonumber\\
-        &\sim 2\pi \epsilon \p*{\frac{2\Omega}{s}
+    \Delta_M &= \int\limits_0^{2\pi}\epsilon\p{1 - \mu^2}
+            \p{\frac{2\Omega}{s} - \mu} \;\mathrm{d}\phi,\nonumber\\
+        &\sim 2\pi \epsilon \p{\frac{2\Omega}{s}
             - \sqrt{2\frac{s_c}{s}\sin I}},\\
-    \Delta_c &= \oint \epsilon \p*{1 - \mu^2}\p*{\frac{2\Omega}{s} - \mu}
+    \Delta_c &= \oint \epsilon \p{1 - \mu^2}\p{\frac{2\Omega}{s} - \mu}
             \;\mathrm{d}\phi,\nonumber\\
         &= 2\int\limits_0^{2\pi}
-            \epsilon\sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi
+            \epsilon\sqrt{2\eta \sin I\p{1 - \cos \phi}}\;\mathrm{d}\phi
             ,\nonumber\\
@@
     P_{hop} = \frac{4\sqrt{ss_c\sin I}}{\pi \Omega}
-        \p*{1 + \sqrt{\frac{s_cs\sin I}{2}}}.\label{eq:p_hop_sqrt_s}
+        \p{1 + \sqrt{\frac{s_cs\sin I}{2}}}.\label{eq:p_hop_sqrt_s}
 \end{equation}
@@
 Now, recall that we won't get a sensible answer this way, since the dynamics
-near the separatrix $\abs*{\mu - \mu_4} \sim \sqrt{2\eta \sin I}$ are governed
+near the separatrix $\abs{\mu - \mu_4} \sim \sqrt{2\eta \sin I}$ are governed
 by the piecewise map we defined before. However, if $s_c$ is truly small, then
@@
 \begin{equation*}
-    \mu(t) \approx \mu_0 + \frac{2\Omega}{s_0}\p*{e^{\epsilon t} - 1}.
+    \mu(t) \approx \mu_0 + \frac{2\Omega}{s_0}\p{e^{\epsilon t} - 1}.
 \end{equation*}
@@
 \begin{equation}
-    P_{hop}\p*{\mu_\pi(t = 0)}
+    P_{hop}\p{\mu_\pi(t = 0)}
         = \frac{4\sqrt{s_c \sin I s_0}}{\pi \Omega}
@@
 might expect similar behavior to manifest elsewhere thanks to the $\rd{\ln s}{t}
-\sim \epsilon, \rd{\mu}{t} \propto \z*{-\epsilon \mu, \epsilon/s}$ in both
+\sim \epsilon, \rd{\mu}{t} \propto \z{-\epsilon \mu, \epsilon/s}$ in both
 regimes of $\rd{\mu}{t}$. Further numerical testing to be performed.
@@
 
-    \item Henrard in a later paper cites the formula $\Pr\p*{i \to j} =
-        \abs*{\pd{J_j}{t} / \pd{J_i}{t}}$. This can be related to the above
+    \item Henrard in a later paper cites the formula $\Pr\p{i \to j} =
+        \abs{\pd{J_j}{t} / \pd{J_i}{t}}$. This can be related to the above
         $B_i, \Delta_H$ by:
@@
         \dot{\mu}^{(1)} + \frac{\dot{s}^{(1)}}{\dot{\phi}^{(0)}}
-            \p*{\pd{H}{s} - \pd{H_4}{s}},\\
+            \p{\pd{H}{s} - \pd{H_4}{s}},\\
     \Delta K_i &= \oint_{\mathcal{C}_i}
         \dot{\mu}^{(1)} + \frac{\dot{s}^{(1)}}{\dot{\phi}^{(0)}}
-            \p*{\pd{H}{s} - \pd{H_4}{s}}\;\mathrm{d}\phi.
+            \p{\pd{H}{s} - \pd{H_4}{s}}\;\mathrm{d}\phi.
 \end{align}
@@
                 \alpha - \sin I},\\
-        &= \frac{1}{\p*{\alpha - \sin I}^2}
-            \s*{-\alpha \cos^2 I + \p*{\alpha - \sin I}
-                \p*{\cos^2 I - \sin I \sqrt{
+        &= \frac{1}{\p{\alpha - \sin I}^2}
+            \s{-\alpha \cos^2 I + \p{\alpha - \sin I}
+                \p{\cos^2 I - \sin I \sqrt{
                     (\alpha - \sin I)^2 - \cos^2 I}}},\\
-        &\approx \frac{1}{\p*{\alpha - \sin I}^2}
-            \s*{\frac{\alpha \cos^2 I}{2} -\sin I \cos^2 I - \alpha^2 \sin I
-                \p*{1 - \frac{2\alpha \sin I + \cos^2 I - \sin^2 I}{2\alpha^2}}
-                + \sin^2 I\alpha\p*{1 - \frac{2\alpha \sin I}{2\alpha^2}}},\\
-        &\approx \frac{1}{\alpha^2}\p*{1 + \frac{2\sin I}{\alpha}
-            + \frac{3\sin^2 I}{\alpha^2}}\p*{
+        &\approx \frac{1}{\p{\alpha - \sin I}^2}
+            \s{\frac{\alpha \cos^2 I}{2} -\sin I \cos^2 I - \alpha^2 \sin I
+                \p{1 - \frac{2\alpha \sin I + \cos^2 I - \sin^2 I}{2\alpha^2}}
+                + \sin^2 I\alpha\p{1 - \frac{2\alpha \sin I}{2\alpha^2}}},\\
+        &\approx \frac{1}{\alpha^2}\p{1 + \frac{2\sin I}{\alpha}
+            + \frac{3\sin^2 I}{\alpha^2}}\p{
                 -\alpha^2 \sin I + 2\sin^2 I\alpha
@@
         &\approx -\sin I + \frac{\cos^2 I}{2\alpha}
-            + \frac{1}{\alpha^2}\s*{
-                -3\sin^3 I - \frac{\p*{\cos^2 I + 3\sin^2 I}\sin I}{2}
+            + \frac{1}{\alpha^2}\s{
+                -3\sin^3 I - \frac{\p{\cos^2 I + 3\sin^2 I}\sin I}{2}
                     + 4\sin^3 I + \sin I \cos^2 I},\\
         &= -\sin I + \frac{\cos^2 I}{2\alpha}
-            + \frac{\p*{\cos^2 I - \sin^2 I}\sin I}{2\alpha^2}.
+            + \frac{\p{\cos^2 I - \sin^2 I}\sin I}{2\alpha^2}.
 \end{align*}
@@
             \pd{(\Delta H)}{s},\\
-    -\rd{(\Delta H)}{(\epsilon t)} &= (1 - \mu^2)\p*{\frac{2\Omega}{s} - \mu}
-            \dot{\phi}^{(0)} + 2\Omega\p*{1 + \frac{s}{2\Omega}(1 + \mu^2)}
-            \s*{\frac{\mu^2}{2s_c} - \frac{s_c}{2s^2}\cos^2 I}.
+    -\rd{(\Delta H)}{(\epsilon t)} &= (1 - \mu^2)\p{\frac{2\Omega}{s} - \mu}
+            \dot{\phi}^{(0)} + 2\Omega\p{1 + \frac{s}{2\Omega}(1 + \mu^2)}
+            \s{\frac{\mu^2}{2s_c} - \frac{s_c}{2s^2}\cos^2 I}.
 \end{align}
 Note that this expression is encouraging since both $\dot{\phi}^{(0)},
-\pd{\p*{\Delta H}}{s}$ vanish near CS4 (where $\mu_4 \approx \frac{s_c}{s}\cos
+\pd{\p{\Delta H}}{s}$ vanish near CS4 (where $\mu_4 \approx \frac{s_c}{s}\cos
 I$), which corresponds to separatrix approach slowing down (also consistent w/
@@
     \rd{(\Delta H)}{(\epsilon t)} &\approx
-            \p*{1 - \mu^2}\p*{\frac{2\Omega}{s} - \mu}\frac{s}{s_c}\mu
-                + s\p*{1 + \mu^2}\p*{\frac{\mu^2}{2s_c}},\nonumber\\
-        &\approx -\frac{s\mu^2}{2s_c} \p*{2(1 - \mu^2) - 1 + \mu^2}
+            \p{1 - \mu^2}\p{\frac{2\Omega}{s} - \mu}\frac{s}{s_c}\mu
+                + s\p{1 + \mu^2}\p{\frac{\mu^2}{2s_c}},\nonumber\\
+        &\approx -\frac{s\mu^2}{2s_c} \p{2(1 - \mu^2) - 1 + \mu^2}
             ,\nonumber\\
-        &= -\frac{s\mu^2}{2s_c}\p*{3 - \mu^2}.
+        &= -\frac{s\mu^2}{2s_c}\p{3 - \mu^2}.
 \end{align}
@@
             -\frac{s}{s_c}\mu + \cos I}\;\mathrm{d}\phi,\\
-        &= \int \frac{\dot{s}s_c}{2s^2}\s*{\frac{s\mu}{s_c} + \cos
+        &= \int \frac{\dot{s}s_c}{2s^2}\s{\frac{s\mu}{s_c} + \cos
             I}\;\mathrm{d}\phi,\\
         &= \int \epsilon 2\Omega_1
-            \p*{\mu_{\pm} - \frac{s}{2\Omega_1}\p*{1 + \mu_{\pm}^2}}
-                \frac{s_c}{2s^2} \s*{
+            \p{\mu_{\pm} - \frac{s}{2\Omega_1}\p{1 + \mu_{\pm}^2}}
+                \frac{s_c}{2s^2} \s{
                     2\cos I \pm
-                    \sqrt{2\frac{s}{s_c} \sin I\p*{1 - \cos \phi}}}
+                    \sqrt{2\frac{s}{s_c} \sin I\p{1 - \cos \phi}}}
                 \;\mathrm{d}\phi,\\
         &\approx \epsilon \frac{s_c}{s^2} \int
-            \p*{\mu_{\pm} - \frac{s}{2}}
-                \s*{2\cos I \pm \sqrt{\frac{2 \sin I}{\eta}\p*{1 - \cos \phi}}}
+            \p{\mu_{\pm} - \frac{s}{2}}
+                \s{2\cos I \pm \sqrt{\frac{2 \sin I}{\eta}\p{1 - \cos \phi}}}
                 \;\mathrm{d}\phi.
@@
 \begin{align*}
-    \int_{\pm} 2\cos I \p*{\mu_{\pm} - \frac{s}{2}}\;\mathrm{d}\phi &=
-        -2\cos I\p*{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
+    \int_{\pm} 2\cos I \p{\mu_{\pm} - \frac{s}{2}}\;\mathrm{d}\phi &=
+        -2\cos I\p{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
         \pm 2\pi s\cos I,\\
-    \pm \int_{\pm} \p*{\mu_4 - \frac{s}{2}}
-            \sqrt{\frac{2\sin I}{\eta}\p*{1 - \cos \phi}} \;\mathrm{d}\phi &=
-        \eta \cos I \p*{-8\sqrt{\sin I / \eta}}
+    \pm \int_{\pm} \p{\mu_4 - \frac{s}{2}}
+            \sqrt{\frac{2\sin I}{\eta}\p{1 - \cos \phi}} \;\mathrm{d}\phi &=
+        \eta \cos I \p{-8\sqrt{\sin I / \eta}}
             + \frac{s}{2}8\sqrt{\sin I/\eta} ,\\
-    \int_{\pm} 2\sin I \p*{1 - \cos \phi}\;\mathrm{d}\phi &= \mp 4\pi \sin I.
+    \int_{\pm} 2\sin I \p{1 - \cos \phi}\;\mathrm{d}\phi &= \mp 4\pi \sin I.
 \end{align*}
@@
 
-For the $\dot{\mu}$ integral, the integrand is $\p*{\frac{2\Omega}{s} - \mu}$
+For the $\dot{\mu}$ integral, the integrand is $\p{\frac{2\Omega}{s} - \mu}$
 times the original integrand; this means the final result is $\frac{2\Omega}{s}$
-times the old result plus a contribution $\int \epsilon \p*{1 - \mu^2}\p*{-\mu}
+times the old result plus a contribution $\int \epsilon \p{1 - \mu^2}\p{-\mu}
 \;\mathrm{d}\phi$. This second term can be evaluated exactly, and we obtain
@@
     \int_{\mathcal{C}_{\pm}}\dot{\mu}^{(1)}\;\mathrm{d}\phi
-        &\approx \epsilon\frac{2\Omega}{s}\p*{\mp 2\pi\p*{1 - 2\eta \sin I}
+        &\approx \epsilon\frac{2\Omega}{s}\p{\mp 2\pi\p{1 - 2\eta \sin I}
             + 16\cos I \eta^{3/2}\sqrt{\sin I}}
@@
             \pm 2 \pi \eta \cos I
-            - \frac{64}{3}\epsilon \p*{\eta \sin I}^{3/2}.
+            - \frac{64}{3}\epsilon \p{\eta \sin I}^{3/2}.
 \end{align*}
@@
     \frac{\Delta_{\pm}}{\epsilon} ={}&
-        -2\cos I\p*{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
+        -2\cos I\p{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
         \pm 2\pi s\cos I
-        + \eta \cos I \p*{-8\sqrt{\sin I / \eta}}
+        + \eta \cos I \p{-8\sqrt{\sin I / \eta}}
             + \frac{s}{2}8\sqrt{\sin I/\eta}\nonumber\\
-        &+ \frac{2\Omega}{s}\p*{\mp 2\pi\p*{1 - 2\eta \sin I}
+        &+ \frac{2\Omega}{s}\p{\mp 2\pi\p{1 - 2\eta \sin I}
             + 16\cos I \eta^{3/2}\sqrt{\sin I}}
@@
             \pm 2 \pi \eta \cos I
-            - \frac{64}{3} \p*{\eta \sin I}^{3/2},\\
+            - \frac{64}{3} \p{\eta \sin I}^{3/2},\\
     P_c ={}& \frac{\Delta_+ + \Delta_-}{\Delta_-}.
@@
 
-Note that for Jupiter, $k_p \sim 0.27$ while $J_2 \sim \scinot{1.4}{-2}$ giving
-$k_{qp} \sim 0.0467$ since $k_{qp} \frac{\Omega}{\sqrt{GM_p/R_p^3}} = J_2$.
-Consider again the precession frequencies (we will take a hot Jupiter at
-$0.1\;\mathrm{AU}$ and a cold Earth at $1\;\mathrm{AU}$, roughly)
-\begin{align}
-    \omega_{s1} &= \frac{3k_{qp}}{2k_p}\frac{M_*}{m_1}
-            \p*{\frac{R_1}{a_1}}^3s,\\
-        &\approx 0.062\;\mathrm{yr^{-1}}
-            \p*{\frac{M_*/m_1}{300}}
-            \p*{\frac{5.5 k_{qp}}{k_p}}\p*{\frac{R_1}{R_J}}^3
-                \p*{\frac{a_1}{0.1\;\mathrm{AU}}}^{-9/2}
-                \p*{\frac{s/\Omega_1}{10}},\\
-    \omega_{1p} &= \frac{3m_p}{4m_1} \p*{\frac{a_1}{a_p\p*{1 - e_p^2}}}^3
-            \Omega_1,\\
-        &\approx 0.0047\;\mathrm{yr^{-1}}
-            \frac{m_p/m_1}{0.003}
-            \p*{\frac{a_1/a_p}{0.1}}
-            \frac{\Omega_1}{2\pi / 11.54\;\mathrm{days}}
-            \frac{1}{\p*{1 - e_p^2}^3}.
-\end{align}
-Note then that $s_c$ is where $\omega_{s1} = \omega_{1p}$, which is satisfied
-for $s_c \approx 0.76$.
-
-Let's also evaluate
-\begin{align}
-    \rd{\theta}{t} &\approx -\frac{1}{t_a}\frac{L}{2S}\sin \theta\p*{1 -
-        \frac{s}{2\Omega_1}\cos \theta},\\
-        &\approx 14\;\mathrm{Myr}\p*{\frac{P}{3\;\mathrm{d}}}^{16/3}
-            \p*{\frac{Q_p'}{10^7}}
-            \p*{\frac{M_*}{10^3M_p}}
-            \p*{\frac{a/r}{100}}^2
-            \p*{\frac{s}{2\pi / 10\;\mathrm{h}}}^{-1}
-            \p*{\frac{k_p}{0.25}}^{-1}
-            \sin \theta\p*{1 - \frac{s}{2\Omega_1}\cos \theta}.
-\end{align}
-Note that typically, when trapped in CS2 and $\eta \ll 1$, $\sin \theta \approx
-1$, while when at CS1, $\sin \theta \approx \sin I$. For reference, $\sin
-5^\circ \approx 0.087$.
-
-Again though, we see that if $s > \frac{2\Omega_1}{\cos\theta}$, then
-$\rd{\theta}{t}$ drives towards CS2.
+The two key constraints we want are: (i) $\sim \frac{1}{5\omega_{\rm
+1p}\epsilon}$ the tidal synchronization timescale (we will now use $t_a$ to
+follow DL12 notation) should be faster than $\sim$ Gyr, (ii) $s_c$ ideally
+should not be too small to forbid separatrix crossings. Note that $3 / Q' = 2k_2
+/ Q$ ranges from around $10^{-2}$ for rocky Earths to $10^{-5}$ for Jupiters. We
+can then write down the following dimensionless scalings (checked against the
+dissipating disks paper w/ Dong):
+% in paper 1, s_c = 2.04e4, for m_p = 0.01 Msun, a1=5AU, rho1=1g/cm^3, ap=30AU
+\begin{align}
+    \frac{s_c}{\Omega_1} &= \frac{
+        \frac{3m_p}{4M_\star}\p{\frac{a_1}{\tilde{a}_{\rm p}}}^3
+            }{\frac{3k_{\rm qp}}{2k_{\rm p}}
+            \frac{M_\star}{M_1}\p{\frac{R_1}{a_1}}^3},\\
+        &= \frac{m_{\rm p}m_1}{2M_{\star}^2}
+            \p{\frac{k_{\rm p}}{k_{\rm qp}}}
+            \p{\frac{a_1^6}{R_1^3 \tilde{a}_p^3}},\\
+    \epsilon &=\frac{L}{2S}\frac{s}{2\Omega}\frac{1}{\omega_{\rm 1p}\cos I t_a}
+            ,\\
+    \frac{1}{t_a} &= \frac{9}{2Q'}\frac{M_\star}{m_{\rm 1}}
+        \p{\frac{R_1}{a_1}}^5\Omega,\\
+    \epsilon &= \frac{m_1a_1^2\Omega}{2(m_1R_1^2/4)s}\frac{s}{2\Omega}
+        \frac{1}{\cos I}\p{\frac{9}{2Q'}\frac{M_\star}{m_1}
+            \p{\frac{R_1}{a_1}}^5}
+            \p{\frac{4M_\star a_p^3}{3m_pa_1^3}},\\
+        &= \frac{1}{\cos I}
+            \frac{6}{Q'}\p{\frac{M_\star^2}{m_1m_p}}
+            \p{\frac{R_1^3a_p^3}{a_1^6}},\\
+        &= \frac{1}{\cos I}\frac{3}{Q'}\frac{\Omega_1}{s_c},\\
+% use paper I formula, change rho_1, mp, ap, a1
+    \frac{s_c}{n_1} &= 0.06 \p{\frac{k_{\rm 1}}{k_{\rm q1}}}
+            \p{\frac{m_{\rm p}}{0.001 M_{\odot}}}
+            \p{\frac{a_{\rm p}}{5 \;\mathrm{AU}}}^{-3}
+            \p{\frac{a_{\rm 1}}{0.3\;\mathrm{AU}}}^{6}
+            \p{\frac{\rho_{\rm 1}}{3 \; \mathrm{g/cm}^3}}
+            \p{\frac{M_\star}{M_{\odot}}}^{-2},\\
+    \epsilon &\sim 10^{-2} \p{\frac{2k_2/Q}{10^{-3}}}.
+\end{align}
+Note that $2k_2/Q = 3/Q'$ in Dong's notation. The timescales now work since
+$\omega_{\rm 1p} \sim 1.6\;\mathrm{Myr}$, so obliquities are driven to their
+extreme values in around $0.8\;\mathrm{Gyr}$.
 
@@
 \begin{equation}
-    \rd{\hat{s}}{t} = \p*{\hat{s} \cdot \hat{l}}\p*{\hat{s} \times \hat{l}}
-        + \eta \cos I \p*{\hat{l}_d \times \hat{s}}.
+    \rd{\hat{s}}{t} = \p{\hat{s} \cdot \hat{l}}\p{\hat{s} \times \hat{l}}
+        + \eta \cos I \p{\hat{l}_d \times \hat{s}}.
 \end{equation}
@@
 \frac{\Omega_{ld}\cos I}{\Omega_{sl}}$, and time units are really $t \equiv
-\Omega_{sl}t$. In this decaying disk problem, $\eta\p*{-\infty} \gg 1,
-\eta\p*{+\infty} \ll 1$.
+\Omega_{sl}t$. In this decaying disk problem, $\eta\p{-\infty} \gg 1,
+\eta\p{+\infty} \ll 1$.
 
@@
 \begin{equation}
-    \rd{\hat{s}}{t} = \s*{
-        \p*{\eta \cos I - 1}\hat{z} + \eta \sin I \hat{x}} \times \hat{s}.
+    \rd{\hat{s}}{t} = \s{
+        \p{\eta \cos I - 1}\hat{z} + \eta \sin I \hat{x}} \times \hat{s}.
 \end{equation}
@@
 \begin{equation}
-    \rd{S}{t} = i\p*{\eta\cos I - 1}S - i \eta \sin I.\label{eq:nonad_ode}
+    \rd{S}{t} = i\p{\eta\cos I - 1}S - i \eta \sin I.\label{eq:nonad_ode}
 \end{equation}
@@
 \begin{align}
-    \Phi(t) &\equiv \int_{-\infty}^t \p*{1 - \eta(t') \cos I}
+    \Phi(t) &\equiv \int_{-\infty}^t \p{1 - \eta(t') \cos I}
         \mathrm{d}t',\\
@@
         &= \int\limits_{-\infty}^t e^{i\Phi(t')}
-            \p*{-i\eta(t')\sin I}\;\mathrm{d}t'\label{eq:nonad_int}
+            \p{-i\eta(t')\sin I}\;\mathrm{d}t'\label{eq:nonad_int}
 \end{align}
@@
             \frac{1}{\cos I}e^{i\Phi(0)}\int\limits_{-\infty}^\infty
-                \exp\s*{\frac{i}{2}\epsilon t^2}\;\mathrm{d}t
+                \exp\s{\frac{i}{2}\epsilon t^2}\;\mathrm{d}t
                 & t > 0.
@@
     \int\limits_{-\infty}^\infty
-                \exp\s*{\frac{i}{2}\epsilon t^2}\;\mathrm{d}t
+                \exp\s{\frac{i}{2}\epsilon t^2}\;\mathrm{d}t
         &= \int\limits_{-\infty}^\infty e^{-\tau^2}\;\mathrm{d}\tau
@@
 Now, it should be noted that $e^{i\Phi}$ is just a phase; all we really care
-about is $\abs*{S} = \sqrt{1 - s_z^2}$. Thus, taking the absolute value of both
+about is $\abs{S} = \sqrt{1 - s_z^2}$. Thus, taking the absolute value of both
 sides of \autoref{eq:nonad_int} we obtain
 \begin{align}
-    \abs*{S}(t) &= \tan I\sqrt{\frac{2\pi}{\epsilon}}\Theta(t).
+    \abs{S}(t) &= \tan I\sqrt{\frac{2\pi}{\epsilon}}\Theta(t).
         \label{eq:nonad_dong}
 \end{align}
-It should be noted that $\theta_{sl, f} \approx \abs*{S}(\infty)$, and so we
+It should be noted that $\theta_{sl, f} \approx \abs{S}(\infty)$, and so we
 recover Dong's result $\theta_f = \sqrt{2\pi/\epsilon}\tan I$.
@@
 in'' as the disk dissipates non-adiabatically. Thus, $\theta_{sl, f} \in
-\theta_{sl, f, 0} + \s*{\pm \theta_{sd, i}}$.
+\theta_{sl, f, 0} + \s{\pm \theta_{sd, i}}$.
 
@@
 hold it constant at $s_z \approx \cos I$, which just changes the inhomogeneous
-term in \autoref{eq:nonad_ode} to $\p*{-i\eta \sin I \cos I}$; this is a very
+term in \autoref{eq:nonad_ode} to $\p{-i\eta \sin I \cos I}$; this is a very
 small change since $\cos I \approx 1$ for nearly all physical parameter space,
@@
 One other observation is that the LHS of \autoref{eq:nonad_int} should really be
-$\abs*{S\p*{t}e^{i\Phi(t)} - S\p*{-\infty}e^{i\Phi(-\infty)}}$, but we don't
-really know $e^{i\Phi}$ since it oscillates so quickly. Thus, only when $S\p*{t}
-\gg S\p*{-\infty}$ or $\theta_{sl, f} \gg I$ is the LHS easily evaluated. But at
-the very least we can claim that $\theta_{sl, f} = \max\p*{\abs*{S}, I}$, so
-that at very small $\abs*{S}$ we just use $I$ the approximate location of CS2.
+$\abs{S\p{t}e^{i\Phi(t)} - S\p{-\infty}e^{i\Phi(-\infty)}}$, but we don't
+really know $e^{i\Phi}$ since it oscillates so quickly. Thus, only when $S\p{t}
+\gg S\p{-\infty}$ or $\theta_{sl, f} \gg I$ is the LHS easily evaluated. But at
+the very least we can claim that $\theta_{sl, f} = \max\p{\abs{S}, I}$, so
+that at very small $\abs{S}$ we just use $I$ the approximate location of CS2.
 This seems to be in pretty good agreement if we look at
@@
 \end{equation}
-Noting $\dot{\eta} = \p*{\frac{\dot{g}}{g} - \frac{\dot{\alpha}}{\alpha}}\eta$,
+Noting $\dot{\eta} = \p{\frac{\dot{g}}{g} - \frac{\dot{\alpha}}{\alpha}}\eta$,
 where $\eta = \frac{g\cos I}{\alpha}$ ($g, \alpha$ follow their definitions),
@@
         &\lesssim g\sin\theta\sin I,\\
-    -\s*{\frac{\dot{\alpha}}{\alpha} - \frac{\dot{g}}{g}}\cos I = \dot{\eta}
+    -\s{\frac{\dot{\alpha}}{\alpha} - \frac{\dot{g}}{g}}\cos I = \dot{\eta}
         = -\epsilon \alpha \eta &\gtrsim -g\sin\theta\sin I\cos I,\\
@@
 \frac{\theta}{2}\sin \phi$ (these can be verified to be canonical by evaluating
-PB $\z*{y, x}_{\cos \theta, \phi} = 1$), then the Hamiltonian can be written
+PB $\z{y, x}_{\cos \theta, \phi} = 1$), then the Hamiltonian can be written
 \begin{align}
     H &= -\frac{1}{2}\cos^2\theta
-        + \eta \p*{\cos \theta \cos I - \sin I \sin \theta \cos \phi}
+        + \eta \p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}
         ,\nonumber\\
-        &= -\frac{1}{2}\p*{1 - 2\sin^2\frac{\theta}{2}}^2
-            + \eta\p*{\p*{1 - 2\sin^2\frac{\theta}{2}}\cos I
+        &= -\frac{1}{2}\p{1 - 2\sin^2\frac{\theta}{2}}^2
+            + \eta\p{\p{1 - 2\sin^2\frac{\theta}{2}}\cos I
             - 2 \sin \frac{\theta}{2}\cos \phi \cos \frac{\theta}{2}\sin I}
             ,\nonumber\\
-        &= -\frac{1}{2}\p*{1 - \frac{x^2 + y^2}{2}}^2
-            + \eta\p*{\p*{1 - \frac{x^2 + y^2}{2}}\cos I
+        &= -\frac{1}{2}\p{1 - \frac{x^2 + y^2}{2}}^2
+            + \eta\p{\p{1 - \frac{x^2 + y^2}{2}}\cos I
                 - \sin I x\sqrt{1 - \frac{x^2 + y^2}{4}}}.
@@
     \dot{y} = -\pd{H}{x} &=
-        -x\p*{1 - \frac{x^2 + y^2}{2}} - \eta\p*{
-            -x \cos I + \frac{x^2\sin I}{4}\p*{1 - \frac{x^2 + y^2}{4}}^{-1/2}
+        -x\p{1 - \frac{x^2 + y^2}{2}} - \eta\p{
+            -x \cos I + \frac{x^2\sin I}{4}\p{1 - \frac{x^2 + y^2}{4}}^{-1/2}
             - \sin I \sqrt{1 - \frac{x^2 + y^2}{4}}},\\
     \dot{x} = \pd{H}{y} &=
-        y\p*{1 - \frac{x^2 + y^2}{2}} + \eta\p*{
-            -y \cos I + \frac{xy\sin I}{4}\p*{1 - \frac{x^2 + y^2}{4}}^{-1/2}
+        y\p{1 - \frac{x^2 + y^2}{2}} + \eta\p{
+            -y \cos I + \frac{xy\sin I}{4}\p{1 - \frac{x^2 + y^2}{4}}^{-1/2}
             },\\
@@
 [0, 4]$, so the EOM diverge as $\theta \to \pi$. This is one fewer singularity
-than the naive $\p*{\cos\theta, \phi}$ covering, but full cartesian $\hat{s} =
-\p*{s_x, s_y, s_z}$ still has no singularities.
+than the naive $\p{\cos\theta, \phi}$ covering, but full cartesian $\hat{s} =
+\p{s_x, s_y, s_z}$ still has no singularities.
 
@@
 \begin{align}
-    \pd{\phi}{t} &= -\mu + \eta\p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}}
+    \pd{\phi}{t} &= -\mu + \eta\p{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}}
         \cos \phi} ,\\
-    \pd{\mu}{t} &= -\eta \sin I \sin \phi + \s*{\epsilon \p*{1 - \mu^2}},
+    \pd{\mu}{t} &= -\eta \sin I \sin \phi + \s{\epsilon \p{1 - \mu^2}},
 \end{align}
@@
 of $\eta$ for which CS2 is still stable, which must satisfy $\eta \sin I =
-\epsilon\p*{1 - \eta^2\cos^2 I}$, or
+\epsilon\p{1 - \eta^2\cos^2 I}$, or
 \begin{equation}
@@
 \begin{equation}
-    \phi_{4, 2} = \z*{0, \pi} \pm \frac{\epsilon\p*{1 - \mu^2}}{\eta \sin I}
-        \approx \z*{0, \pi} \pm \frac{\epsilon}{\eta \sin I} +
-        \mathcal{O}\p*{\epsilon^2}.
+    \phi_{4, 2} = \z{0, \pi} \pm \frac{\epsilon\p{1 - \mu^2}}{\eta \sin I}
+        \approx \z{0, \pi} \pm \frac{\epsilon}{\eta \sin I} +
+        \mathcal{O}\p{\epsilon^2}.
 \end{equation}
@@
         \mp \frac{1}{2}\frac{\eta^2 \sin I \cos I}{1 \mp \eta \sin I}
-            \p*{\frac{\epsilon}{\eta \sin I}}^2 + \mathcal{O}\p*{\epsilon^3}.
+            \p{\frac{\epsilon}{\eta \sin I}}^2 + \mathcal{O}\p{\epsilon^3}.
 \end{equation}
@@
 
-In fact, we can really do better: just let $\sin \phi = \frac{\epsilon\p*{1 -
+In fact, we can really do better: just let $\sin \phi = \frac{\epsilon\p{1 -
 z_0^2}}{\eta \sin I}$, then $\mu = \frac{\eta \cos I}{1 - \eta \sin I \cos \phi
@@
 \begin{equation}
-    \p*{\eta^2 \sin I \cos I}^2 \mp \eta \sin I \Delta \phi > 0.
+    \p{\eta^2 \sin I \cos I}^2 \mp \eta \sin I \Delta \phi > 0.
 \end{equation}
@@
 the eigenvalues become real. However, for CS2, since the eigenvalue equation
-reads $\lambda^2 + b\lambda + c = 0$ and the eigenvalues take form $\p*{-b \pm
+reads $\lambda^2 + b\lambda + c = 0$ and the eigenvalues take form $\p{-b \pm
 \sqrt{b^2 - 4c}}/2$, no eigenvalue w/ positive real part ever appears, so it
@@
 \begin{equation}
-    A_{crit} = 4\pi \s*{1 - \p*{1 + \tan^{2/3}I}^{-3/2}}.
+    A_{crit} = 4\pi \s{1 - \p{1 + \tan^{2/3}I}^{-3/2}}.
 \end{equation}
@@
 We can investigate the values of $\theta_f$ given some initial mutual
-inclination $\hat{s} \cdot \hat{l}_p \equiv \theta_{sp, i}$ ($J_i = 2\pi\p*{1 -
+inclination $\hat{s} \cdot \hat{l}_p \equiv \theta_{sp, i}$ ($J_i = 2\pi\p{1 -
 \cos \epsilon}$ where $\epsilon$ is the initial mutual inclination). To do this,
@@
         A_2 &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},\\
-        A_1 &= 2\pi\p*{1 - z_0} - \frac{A_2}{2},\\
-        A_3 &= 2\pi\p*{1 + z_0} - \frac{A_2}{2}.
+        A_1 &= 2\pi\p{1 - z_0} - \frac{A_2}{2},\\
+        A_3 &= 2\pi\p{1 + z_0} - \frac{A_2}{2}.
     \end{align}
@@
 \begin{equation*}
-    \eta_\star\p*{A_2} = \p*{A_2/16}^2 / \sin I,
+    \eta_\star\p{A_2} = \p{A_2/16}^2 / \sin I,
 \end{equation*}
@@
         \begin{align*}
-            \eta_\star &\approx \p*{\frac{2\pi\p*{1 - \cos \theta_{sp,i}}}{
+            \eta_\star &\approx \p{\frac{2\pi\p{1 - \cos \theta_{sp,i}}}{
                         16}}^2 / \sin I&
-                    &\approx \p*{\frac{\pi \theta_{sp, i}^2}{16}}^2/\sin I,\\
+                    &\approx \p{\frac{\pi \theta_{sp, i}^2}{16}}^2/\sin I,\\
             \mu_{f, 23} &\approx \eta_\star \cos I
                     - \frac{4\sqrt{\eta_\star \sin I}}{\pi} &
-                &\approx\p*{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
+                &\approx\p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
                     - \frac{\theta_{sp, i}^2}{4}.
@@
         i}$ is small enough to fit inside $A_{crit}$ when the separatrix first
-        appears, i.e.\ $2\pi\p*{1 - \cos \theta_{sl, i}} < A_{crit}$ (where
+        appears, i.e.\ $2\pi\p{1 - \cos \theta_{sl, i}} < A_{crit}$ (where
         $\theta_{sl, i}$ is defined in the $\eta \to \infty$ limit, and since
@@
         \begin{align*}
-            \eta_\star &\approx \p*{\frac{2\pi\p*{1 - \cos \theta_{sp,i}}}{
+            \eta_\star &\approx \p{\frac{2\pi\p{1 - \cos \theta_{sp,i}}}{
                         16}}^2 / \sin I&
-                    &\approx \p*{\frac{\pi \theta_{sp, i}^2}{16}}^2/\sin I,\\
+                    &\approx \p{\frac{\pi \theta_{sp, i}^2}{16}}^2/\sin I,\\
             \mu_{f, 21} &\approx \eta_\star \cos I
                     + \frac{4\sqrt{\eta_\star \sin I}}{\pi} &
-                &\approx\p*{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
+                &\approx\p{\frac{\pi \theta_{sp, i}^2}{16}}^2 \cot I
                     + \frac{\theta_{sp, i}^2}{4}.
@@
     \item $A_3 \to A_1$: This transition occurs when $\theta_{sl, i}$ satisfies
-        $2\pi\p*{1 - \cos \theta_{sl, i}} > A_{crit}$, so the trajectory starts
+        $2\pi\p{1 - \cos \theta_{sl, i}} > A_{crit}$, so the trajectory starts
         in $A_3$. It then has probability to hop to $A_1$ (TODO).

### 2020-05-11 initial/1_weaktide/6misc.py

@@ -123,8 +123,8 @@ def get_cross_dat(I, s_c, s0, eps, tf, mu0, phi0):
 
 def plot_equil_dist_anal(I, s_c, s0, eps, tf=8000):
     pkl_fn = '6pc_dist%s.pkl' % s_c_str(s_c)
-    n_mu = 101
-    n_phi = 60
+    n_mu = 501
+    n_phi = 50
     mu_vals =  np.linspace(-0.99, 0.99, n_mu)
     phi_vals = np.linspace(0, 2 * np.pi, n_phi, endpoint=False)
 
@@ -168,14 +168,14 @@ def plot_equil_dist_anal(I, s_c, s0, eps, tf=8000):
 if __name__ == '__main__':
     eps = 1e-3
     I = np.radians(5)
-    plot_equils(I, 0.2)
-    plot_equils(I, 0.2, verbose=False, fn_str='6equils_half%s')
-    plot_equils(I, 0.06)
-    plot_equils(I, 0.6)
+    # plot_equils(I, 0.2)
+    # plot_equils(I, 0.2, verbose=False, fn_str='6equils_half%s')
+    # plot_equils(I, 0.06)
+    # plot_equils(I, 0.6)
     # plot_phop(I, 0.2)
-    # plot_equil_dist_anal(I, 0.06, 10, eps)
-    # plot_equil_dist_anal(I, 0.2, 10, eps)
-    # plot_equil_dist_anal(I, 0.7, 10, eps)
+    plot_equil_dist_anal(I, 0.06, 10, eps)
+    plot_equil_dist_anal(I, 0.2, 10, eps)
+    plot_equil_dist_anal(I, 0.7, 10, eps)
 
     # test cases
     # print(get_cross_dat(I, 0.7, 10, 1e-3, 8000, 0.9, np.pi)) # no cross

### 2020-08-07 writeups/response.txt
half of ref responses

> This paper explores the dynamics of "Colombo's top" problem, which involves the motion of a planet's spin axis while its orbit undergoes uniform orbital precession due to a perturber. The dynamics are envisioned to take place early on in the system's lifetime, and the perturber is the protoplanetary disk. As the disk loses mass, a spin-orbit resonance is crossed, and the planetary obliquity is excited. While Colombo's top is not a new set-up, this paper presents several new and interesting components of the general problem. Overall, I think the authors do a great job with their analytical explorations, as all components are very thorough, and they appear correct as far as I can tell. My comments here are generally minor and are mostly directed at enhancing clarity for the readers, since the paper is fairly technically-challenging. I will present the most substantial comments first, before moving onto the more minor ones.

We thank the reviewer for their encouraging and insightful comments. We give our responses to each of the reviewer's concerns below, and mark changes to the text in red text (except for the change in notation A => \mathcal{A} for the unsigned areas of Zones I-III).

> 1) Given that Colombo's top problem has been studied in much previous literature, it would be helpful to specify more explicitly which parts of this paper are completely novel (particularly regarding the phase space area evolution in the adiabatic regime).

We have added sentences to the introduction and summary describing the parts of the paper that are novel.

> 2) This is primarily a matter of preference, but I suggest considering the usage of the polar depiction of the phase space, as opposed to using \phi and \cos\theta as the x and y axes. The polar view can assist in seeing where and when the separatrix emerges. In addition, the calculations of phase space areas tend to be more intuitive, and it could also help the reader better interpret the scenarios in Figures 8-11.

Yes, there are definitely many advantages to the polar depiction of phase space. However, we tried in this paper to highlight the detailed behavior near separatrix crossing, and it seems much easier to zoom in to the vicinity of the separatrix in (\phi, \cos\theta) coordinates. There is precedent using these coordinates for this reason, e.g. https://doi.org/10.1093/mnras/stw3018.

> 3) There is an interesting difference between separatrix crossings that change the obliquity with an impulsive and large jump (e.g. III->I, III->II->I) versus those that do not affect the obliquity evolution in a significant way (e.g. II->I, II->III). Is this distinction fundamental enough to be emphasized in the text?

This is an interesting observation and distinction, and we have added a few sentences to discuss this.

> 4) The whole set-up assumes a single planet in the disk. Can the authors comment (briefly) on what changes when multiple planets are present? Similarly, are there any interesting dependencies on the timing at which the resonance encounter occurs? (E.g. closer planets encounter the resonance earlier than more distant ones.)

This is a great comment, and we have added a paragraph to the discussion outlining the possible consequences of multiple interior planets.

Smaller comments:
> - State references for equations 3 and 4.

* Added

> - In equation 3 and 4, it is more customary in previous literature to label k_2 = 3 k_{qp}, where k_2 is the Love number. In addition, conventional notation for k_p is \lambda or C.

* Our notation follows the notation used in our references, though we have added equivalences and references for the more common choices of notation

> - In equations 17, A_2 should be labeled A_{II}.

* Fixed

> - Please cite the references you used for equations 14, 15, 16, and 17. Much of equations 16 and 17, for example, are written in the notation of Ward & Hamilton (2004).

* Added

> - Add a legend with the colors of the Cassini states in Figure 3. (It's not easy to remember them from the previous figure.)

* Added

> - Figure 4 is plotted for I=5 deg, correct? Can you please include this in the figure caption? Also in Figure 4, it would be helpful to label the allowed regions for each of the separatrix crossing sequences, as delineated/summarized in the left column of page 9. Finally, it would also be helpful to include an additional y-axis label in Figure 4 for \theta_sd, given the equation 23 relation between \theta_sd and the initial phase space area. This can help the reader understand why each evolutionary track can only occur for a distinct range of \theta_sd.

* Added inclination to captions for Figs 4 & 5

Regarding the final two points, the unsigned areas A_{I,II,III} and the signed phase space areas cannot be easily directly compared, so such a y-axis label would be misleading (and the allowed regions difficult to label). This confusion seems to arise from our use of A for both quantities. We have changed the notation to use \mathcal{A} for unsigned areas, and A for signed areas, as well as a note describing this change. This also addresses a later concern from the reviewer.

> - Figures 6 and 7 look very similar, and it does not seem to add much to have both of them. I would suggest either removing one or making Figure 7 an even larger angle than I=20 deg.

* removed Figure 6, leaving only I = 20

> - In section 3.2.2, whenever the probability is between 0 and 1, how does the phase factor into determining which track the system ends up following? Is the phase the only factor that influences which side the trajectory will come out on?

This is a great question. Strictly speaking, in the pure adiabatic limit, the phase cannot affect the evolution of the system. Instead, the result from Henrard 1982 (Eqs. 25) shows that the true outcome depends on the value of the Hamiltonian modulo a small quantity ~epsilon, e.g. whether H \mod epsilon = 0.2 epsilon or H \mod epsilon = 0.8 epsilon dictates whether the system ends up in one track or the other. When epsilon is sufficiently small, this is effectively probabilistic, rather than deterministic. We have added a footnote summarizing this relavant result.

> - There is an extra partial derivative at the top of page 8 shortly before equation 30.

* Removed

> - Whether the area A_I is positive or negative depends on the direction of the trajectory in the phase space. It would be helpful to clarify this in a couple areas in Section 3.2.3. It is understandable upon examination of the figures, but at first look at the text, it is confusing why area A_I is sometimes denoted as negative (e.g. just before equation 26) and other times positive (e.g. just before equation 28).

* We believe this confusion is largely remedied by the change in notation to differentiate between unsigned areas (a la Ward & Hamilton) and signed phase space areas, c.f. 6th small comment

> - On Figures 8-11 and 14, it might be helpful to maintain a uniform y-axis range, since the evolution of the phase space and separatrix crossings would be clearer.

We believe a very narrow y-axis is necessary to show the evolution of the trajectory relative to the changing separatrix and how separatrix crossing is executed. However, we note the reviewer's concern that the plots do not convey the phase space area evolution very well, so we choose to zoom the plots out slightly, to better convey the message that the shaded areas extend to the poles.

> - In Figure 13, why does the vertical banding not extend all the way to the green III->I track? Is it because the libration cycles deviate more strongly from circular in this regime?

This is a great observation. Firstly, our calculations only assume the libration cycles are circular initially; at later times, we use conservation of phase space area to compare the phase space area at any time to the analytical A_{I,II,III}s. Instead, since this plot describes the messy intermediate regime, we have two possible explanations for the observed deviation: (i) it is likely that phase space area conservation is simply imperfect, and (ii) since the separatrix is changing so much during the separatrix-crossing orbit, approximating eta_star as a constant during this orbit is invalid. This hurts the accuracy of our calculations, as we calculate analytical phase space areas using eta from the start of the separatrix crossing orbit. This observation illustrates the caveats of our calculations well, so we have made note of it in the manuscript.

### 2020-08-07 writeups/Su_disk_disp.tex
half of ref responses

@@
+% rm -f plots_diskdisp/*.png; for i in ../initial/99_misc/2_nonad_rot.png ../initial/99_misc/2_3vec.png ../initial/99_misc/2_cs_locs.png ../initial/0_eta/1contours_flip.png ../initial/99_misc/1_areas.png ../initial/2_toy2/3_ensemble_05_35.png ../initial/2_toy2/3_ensemble_20_35.png ../initial/2_toy2/3testo21.png ../initial/2_toy2/3testo21_subplots.png ../initial/2_toy2/3testo23.png ../initial/2_toy2/3testo23_subplots.png ../initial/2_toy2/3testo31.png ../initial/2_toy2/3testo31_subplots.png ../initial/2_toy2/3testo321.png ../initial/2_toy2/3testo321_subplots.png ../initial/2_toy2/3_ensemble_05_25.png ../initial/2_toy2/3_ensemble_05_15.png ../initial/2_toy2/3testo_nonad.png ../initial/2_toy2/3testo_nonad_subplots.png ../initial/2_toy2/3_ensemble_05_05.png ../initial/2_toy2/3scan.png ../initial/2_toy2/3scan_20.png ../initial/99_misc/2_lambdas.png; do cp $i plots_diskdisp; done
     \documentclass[twocolumn,twocolappendix]{aastex63}
@@
 
-    \received{XXXX}
+    \colorlet{Corr}{red}
+    \received{Apr 29, 2020}
     \revised{XXXX}
@@
 
-% for i in ../initial/99_misc/2_nonad_rot.png ../initial/99_misc/2_3vec.png ../initial/99_misc/2_cs_locs.png ../initial/0_eta/1contours_flip.png ../initial/99_misc/1_areas.png ../initial/2_toy2/3_ensemble_05_35.png ../initial/2_toy2/3_ensemble_10_35.png ../initial/2_toy2/3_ensemble_20_35.png ../initial/2_toy2/3testo21.png ../initial/2_toy2/3testo21_subplots.png ../initial/2_toy2/3testo23.png ../initial/2_toy2/3testo23_subplots.png ../initial/2_toy2/3testo31.png ../initial/2_toy2/3testo31_subplots.png ../initial/2_toy2/3testo321.png ../initial/2_toy2/3testo321_subplots.png ../initial/2_toy2/3_ensemble_05_25.png ../initial/2_toy2/3_ensemble_05_15.png ../initial/2_toy2/3testo_nonad.png ../initial/2_toy2/3testo_nonad_subplots.png ../initial/2_toy2/3_ensemble_05_05.png ../initial/2_toy2/3scan.png ../initial/2_toy2/3scan_20.png ../initial/99_misc/2_lambdas.png; do cp $i plots_diskdisp; done
 \shorttitle{Exoplanet Obliquities}
@@
 
-\title{Template \aastex Article with Examples:
-v6.3\footnote{Released on June, 10th, 2019}}
-
 \title{Dynamics of Colombo's Top: Generating Exoplanet Obliquities from
-Planet-Disc Interactions}
+Planet-Disk Interactions}
 
@@
 of Astronomy, Cornell University, Ithaca, NY 14853, USA}
-\affiliation{Tsung-Dao Lee Institute, Shanghai Jiao Tong University, Shanghai, 200240,
-China}
 
@@
 
-\subsection{Planetary Obliquities from Planet-Disc Interaction}
-
-It is well recognized that the obliquity of a planet may provide important clue
+\subsection{Planetary Obliquities from Planet-Disk Interaction}
+
+It is well recognized that the obliquity of a planet may provide important clues
 to its dynamical history. In the the Solar System, a wide range of planetary
@@
 dissipation timescales, and examine both ``adiabatic'' (slow disk dissipation)
-and ``non-adiabatic'' evolution. We calibrate our analytical results with
-numerical calculations.
+and ``non-adiabatic'' evolution. \textcolor{Corr}{Our chief results include
+that: (i) careful accounting of phase space area across separatrix
+crossings is able to explain the rich dynamics of adiabatic evolution, and (ii)
+the concept of ``partial adiabatic resonance advection'' fully explains dynamics
+in the non-adiabatic limit.} We calibrate our analytical results with numerical
+calculations.
 
@@
 to nonadiabatic. Analytical results are presented to explain the numerical
-results in both limits. We diskuss the implications of our results in
+results in both limits. We discuss the implications of our results in
 Section~\ref{s:disk}. Our primary physical results consist of
@@
 d}$ is nearly constant and $\uv{l}$ experiences negligible backreaction torque
-from $\uv{s}$. The
-equations of motion for $\uv{s}$ and $\uv{l}$ are
+from $\uv{s}$. The equations of motion for $\uv{s}$ and $\uv{l}$ in this limit
+are \textcolor{Corr}{\citep{anderson2018teeter}}
 \begin{align}
@@
 body with uniform density, $k_p=0.4, k_{qp}=0.5$; for giant planets, $k_p\simeq
-0.25$ and $k_{qp}\simeq 0.17$ \citep[e.g.][]{lainey2016quantification}]. In
-Eq.~\eqref{eq:wld}, $n \equiv \sqrt{GM_\star/a_{\rm p}^3}$ is the planet's
-orbital mean motion, and we have assumed $r_d\gg a_p$ and included only the
-leading-order (quadrupole) interaction between the planet and disk. We define
-three relative inclination angles via
+0.25$ and $k_{qp}\simeq 0.17$ \citep[e.g.][]{lainey2016quantification}].
+\textcolor{Corr}{In other studies, $3k_{\rm qp} / 2 k_{\rm p}$ is often notated
+$k_2 / 2C$ \citep[e.g.][]{millholland_disk}}. In Eq.~\eqref{eq:wld}, $n \equiv
+\sqrt{GM_\star/a_{\rm p}^3}$ is the planet's orbital mean motion, and we have
+assumed $r_d\gg a_p$ and included only the leading-order (quadrupole)
+interaction between the planet and disk. We define three relative inclination
+angles via
 \begin{equation}
@@
 where
-% 1 / (1Myr * 3 / 4 * (0.01) / (30 AU)^3 * sqrt(G * (solar mass) * (5AU)^3))
+% 2.08 / (1Myr * 3 / 4 * (0.01) / (30 AU)^3 * sqrt(G * (solar mass) * (5AU)^3))
 \begin{align}
     \epsilon \equiv{}& \frac{1}{\alpha t_{\rm d}}\nonumber\\
-    ={}& 0.051 \p{\frac{k_{\rm p}}{k_{\rm qp}}}
+    ={}& 0.106 \p{\frac{k_{\rm p}}{k_{\rm qp}}}
         \p{\frac{\rho_{\rm p}}{\mathrm{g/cm}^3}}
@@
 
-Spin states satisfying $\p{d\uv{s}/d\uv{\tau}}_{\rm rot} = 0$ are referred to as
+Spin states satisfying $\p{\rdil{\uv{s}}{\tau}}_{\rm rot} = 0$ are referred to as
 \emph{Cassini States} (CSs) \citep{colombo1966,peale1969}. They require that
@@
 Fig.~\ref{fig:eq_1contours}) can be computed analytically
-\citep{henrard1987,ward2004I}. Define
+\citep{henrard1987,ward2004I}. \textcolor{Corr}{As given in
+\citet{ward2004I}, if we define}
 \begin{subequations}
@@
         T &= 2\chi \frac{\cos \theta_4}{
-            \chi^2 \cos^2\theta_4 - 1}.
+            \chi^2 \cos^2\theta_4 - 1},
     \end{align}
 \end{subequations}
-The areas for $\eta < \eta_{\rm c}$ are given by
+\textcolor{Corr}{then} the areas for $\eta < \eta_{\rm c}$ are given by
 \begin{subequations}\label{se:area_ward}
     \begin{align}
-        A_{\rm I} &= 2\pi\p{1 - z_0} - \frac{A_2}{2}, \label{eq:A1}\\
-        A_{\rm II} &= 8\rho + 4\arctan T - 8z_0 \arctan \frac{1}{\chi},
-            \label{eq:A2}\\
-        A_{\rm III} &= 2\pi\p{1 + z_0} - \frac{A_2}{2}\label{eq:A3}.
+        \mathcal{A}_{\rm I} &= 2\pi\p{1 - z_0} - \frac{\mathcal{A}_{\rm II}}{2},
+            \label{eq:A1}\\
+        \mathcal{A}_{\rm II} &= 8\rho + 4\arctan T - 8z_0 \arctan
+            \frac{1}{\chi}, \label{eq:A2}\\
+        \mathcal{A}_{\rm III} &= 2\pi\p{1 + z_0} - \frac{\mathcal{A}_{\rm
+            II}}{2}\label{eq:A3}.
     \end{align}
@@
 phase space area is conserved under adiabatic evolution, this extension implies
-$A_{\rm i}\p{\eta > \eta_{\rm c}} = A_{\rm i}(\eta_{\rm c})$. The boundary
-between these extended zones is denoted by the dashed black line in panel (a) of
-Fig.~\ref{fig:eq_1contours}, where no separatrix exists.
+$\mathcal{A}_{\rm j}\p{\eta > \eta_{\rm c}} = \mathcal{A}_{\rm j}(\eta_{\rm
+c})$. The boundary between these extended zones is denoted by the dashed black
+line in panel (a) of Fig.~\ref{fig:eq_1contours}, where no separatrix exists.
 \begin{figure}
@@
     \includegraphics[width=0.47\textwidth]{plots_diskdisp/1_areas.png}
-    \caption{The solid lines show the fractional areas of each of the zones
-    $A_{\rm i}(\eta) / 4\pi$ as given by Eqs.~\eqref{se:area_ward}. The colored
-    dotted lines correspond to small $\eta$ approximations used in
-    Appendix~\ref{s:ad_approx}. The colored dashed lines for $\eta > \eta_{\rm
-    c}$ are the effective values of $A_{\rm II}, A_{\rm III}$ for $\eta >
-    \eta_{\rm c}$, denoting the points that would flow into either area under
-    adiabatic decrease of $\eta$ from $\eta > \eta_{\rm c}$ (see the text). The
-    vertical black dashed lines correspond to $\eta = \eta_{\rm c}$
-    [Eq.\eqref{eq:etac}] and the values of $\eta$ for which $A_{\rm II}$ is
-    maximized ($\eta_{\rm \max, II}$) and for which $A_{\rm III}$ is minimized
-    ($\eta_{\rm \min, III}$, Eq.~\eqref{eq:eta_minIII}).}\label{fig:eq_areas}
+    \caption{Plot of fractional areas of each of the zones
+    $\mathcal{A}_{\rm i}(\eta) / 4\pi$ as given by Eqs.~\eqref{se:area_ward} for
+    $I = 5^\circ$. The colored dotted lines correspond to small $\eta$
+    approximations used in Appendix~\ref{s:ad_approx}. The colored dashed lines
+    for $\eta > \eta_{\rm c}$ are the effective values of $\mathcal{A}_{\rm II},
+    \mathcal{A}_{\rm III}$ for $\eta > \eta_{\rm c}$, denoting the points that
+    would flow into either area under adiabatic decrease of $\eta$ from $\eta >
+    \eta_{\rm c}$ (see the text). The vertical black dashed lines correspond to
+    $\eta = \eta_{\rm c}$ [Eq.\eqref{eq:etac}] and the values of $\eta$ for
+    which $\mathcal{A}_{\rm II}$ is maximized ($\eta_{\rm \max, II}$) and for
+    which $\mathcal{A}_{\rm III}$ is minimized ($\eta_{\rm \min, III}$,
+    Eq.~\eqref{eq:eta_minIII}).}\label{fig:eq_areas}
 \end{figure}
@@
 $\theta_{\rm f}$ is our primary result, and is shown for $I = 5^\circ$,
-$10^\circ$, and $20^\circ$ in
-Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
+$10^\circ$, and $20^\circ$ in Figs.~\ref{fig:ad_ensemble}
 and~\ref{fig:3_ensemble_20_35} respectively. The blue dots represent the results
 of the numerical calculation. The colored tracks are calculated
-semi-analytically using the method diskussed in the following subsection.
+semi-analytically using the method discussed in the following subsection.
 
@@
     initial spin-disk misalignment angle $\theta_{\rm sd, i}$ for systems
-    evolving from initial $\eta_{\rm i} \gg 1$ to $\eta_{\rm f} \ll 1$. The blue
-    dots are results of numerical calculations (Section~\ref{ss:ad_ensemble}),
-    and the colored tracks are semi-analytical results
-    (Section~\ref{ss:zone_transitions}). Bottom: The probabilities of different
-    outcomes. Where a particular $\theta_{\rm sd, i}$ corresponds to multiple
-    tracks, the system evolves probabilistically. The track that a particular
-    system evolves along in a numerical simulation can be measured by examining
-    its final obliquity. The dots represent the inferred probabilities from
-    measured final obliquities in our simulations, while the colored tracks
+    evolving from initial $\eta_{\rm i} \gg 1$ to $\eta_{\rm f} \ll 1$, for $I =
+    5^\circ$. The blue dots are results of numerical calculations
+    (Section~\ref{ss:ad_ensemble}), and the colored tracks are semi-analytical
+    results (Section~\ref{ss:zone_transitions}). Bottom: The probabilities of
+    different outcomes. Where a particular $\theta_{\rm sd, i}$ corresponds to
+    multiple tracks, the system evolves probabilistically. The track that a
+    particular system evolves along in a numerical simulation can be measured by
+    examining its final obliquity. The dots represent the inferred probabilities
+    from measured final obliquities in our simulations, while the colored tracks
     denote the semi-analytic probability of the system evolving along each
@@
     \centering
-    \includegraphics[width=0.47\textwidth]{plots_diskdisp/3_ensemble_10_35.png}
-    \caption{Same as the top panel of Fig.~\ref{fig:ad_ensemble} but for $I =
-    10^\circ$ and with fewer annotations.}\label{fig:3_ensemble_10_35}
-\end{figure}
-\begin{figure}
-    \centering
     \includegraphics[width=0.47\textwidth]{plots_diskdisp/3_ensemble_20_35.png}
-    \caption{Same as the top panel of Fig.~\ref{fig:3_ensemble_10_35} but for $I
+    \caption{Same as the top panel of Fig.~\ref{fig:ad_ensemble} but for $I
     = 20^\circ$ and with fewer annotations.}\label{fig:3_ensemble_20_35}
@@
 holds very well when defining $\theta_{\rm sd, i}$ as the angular distance to
-CS2; an exception is diskussed in Section~\ref{sss:evol_traj}.
+CS2; an exception is discussed in Section~\ref{sss:evol_traj}.
 
@@
     \begin{align}
-        \Pr\p{i \to j} = -\frac{\pdil{A_{\rm j}}{\eta}}{\pdil{A_{\rm i}}{\eta}},
-                \\
-        \Pr\p{i \to k} = -\frac{\pdil{A_{\rm k}}{\eta}}{\pdil{A_{\rm i}}{\eta}}.
+        \Pr\p{i \to j} = -\frac{\pdil{\mathcal{A}_{\rm
+            j}}{\eta}}{\pdil{\mathcal{A}_{\rm i}}{\eta}}, \\
+        \Pr\p{i \to k} = -\frac{\pdil{\mathcal{A}_{\rm
+            k}}{\eta}}{\pdil{\mathcal{A}_{\rm i}}{\eta}}.
     \end{align}
@@
         separatrix expands (due to decreasing $\eta$) to ``touch'' the
-        trajectory (snapshot c), at which $A_{\rm II}(\eta_\star) = A_{\rm i}$.
-        As $\hat{s}$ moves to a circulating trajectory in zone I immediately
-        bordering the separatrix, it will encompass $-A_{\rm I}(\eta_\star)$
-        phase space area. The final obliquity $\theta_{\rm f}$ is then given by
-        Eq.~\eqref{eq:qfaf}, with $A_{\rm f} = -A_{\rm I}\p{\eta_\star}$. An
-        analytical approximation to $\theta_{\rm f}$ is derived in
-        Appendix~\ref{s:ad_approx} and is
+        trajectory (snapshot c), at which $\mathcal{A}_{\rm II}(\eta_\star) =
+        A_{\rm i}$. As $\hat{s}$ moves to a circulating trajectory in zone I
+        immediately bordering the separatrix, it will encompass
+        $-\mathcal{A}_{\rm I}(\eta_\star)$ phase space area. The final obliquity
+        $\theta_{\rm f}$ is then given by Eq.~\eqref{eq:qfaf}, with $A_{\rm f} =
+        -\mathcal{A}_{\rm I}\p{\eta_\star}$. An analytical approximation to
+        $\theta_{\rm f}$ is derived in Appendix~\ref{s:ad_approx} and is
         \begin{equation}
@@
             \Pr\p{\mathrm{II} \to \mathrm{I}} = -\p{
-                \frac{\pdil{A_{\rm I}}{\eta}}{\pdil{A_{\rm II}}{\eta}}}
-                    _{\eta = \eta_{\star}}.
+                \frac{\pdil{\mathcal{A}_{\rm I}}{\eta}}{\pdil{\mathcal{A}_{\rm
+                    II}}{\eta}}} _{\eta = \eta_{\star}}.
         \end{equation}
         This track can only occur when the initial condition begins in zone II,
-        requiring $A_{\rm i} < A_{\rm II}(\eta_{\rm c})$, where $A_{\rm
-        II}\p{\eta_c}$ is given by Eq.~\eqref{eq:A2} evaluated at $\eta =
-        \eta_c$. Since $\pdil{A_{\rm I}}{\eta} < 0$ everywhere, while
-        $\pdil{A_{\rm II}}{\eta} > 0$ at all possible $\eta_\star$ for an
-        initial condition starting in zone II, this track always has nonzero
-        probability.
+        requiring $A_{\rm i} < \mathcal{A}_{\rm II}(\eta_{\rm c})$, where
+        $\mathcal{A}_{\rm II}\p{\eta_c}$ is given by Eq.~\eqref{eq:A2} evaluated
+        at $\eta = \eta_c$. Since $\pdil{\mathcal{A}_{\rm I}}{\eta} < 0$
+        everywhere, while $\pdil{\mathcal{A}_{\rm II}}{\eta} > 0$ at all
+        possible $\eta_\star$ for an initial condition starting in zone II, this
+        track always has nonzero probability.
 
@@
         encounter, the trajectory follows the circulating trajectory in zone III
-        bordering the separatrix, upon which it will encompass area $A_{\rm
-        I}(\eta_\star) + A_{\rm II}(\eta_\star) = A_{\rm f}$. The final
-        obliquity is still given by Eq.~\eqref{eq:qfaf}, and the analytical
-        approximation derived in Appendix~\ref{s:ad_approx} is
+        bordering the separatrix, upon which it will encompass area
+        $\mathcal{A}_{\rm I}(\eta_\star) + \mathcal{A}_{\rm II}(\eta_\star) =
+        A_{\rm f}$. The final obliquity is still given by Eq.~\eqref{eq:qfaf},
+        and the analytical approximation derived in Appendix~\ref{s:ad_approx}
+        is
         \begin{equation}
@@
             \Pr\p{\mathrm{II} \to \mathrm{III}} = -\p{
-                \frac{\pdil{A_{\rm III}}{\eta}}{\pdil{A_{\rm II}}{\eta}}}
-                    _{\eta = \eta_{\star}}.
-        \end{equation}
-        Again, this track can only occur when $A_{\rm i} < A_{\rm II}(\eta_{\rm
-        c})$, but a further constraint arises when we consider the transition
-        probability. Upon examination of Fig.~\ref{fig:eq_areas}, it is clear
-        that $\pdil{A_{\rm III}}{\partial \eta} > 0$ for a large range of
-        $\eta$, which would give a negative transition probability---implying
+                \frac{\pdil{\mathcal{A}_{\rm III}}{\eta}}{\pdil{\mathcal{A}_{\rm
+                    II}}{\eta}}} _{\eta = \eta_{\star}}.
+        \end{equation}
+        Again, this track can only occur when $A_{\rm i} < \mathcal{A}_{\rm
+        II}(\eta_{\rm c})$, but a further constraint arises when we consider the
+        transition probability. Upon examination of Fig.~\ref{fig:eq_areas}, it
+        is clear that $\pdil{\mathcal{A}_{\rm III}}{\eta} > 0$ for a large range
+        of $\eta$, which would give a negative transition probability---implying
         a forbidden transition. Define
         \begin{equation}
-            \eta_{\min, III} \equiv \argmin A_{\rm III}(\eta)
+            \eta_{\min, III} \equiv \argmin \mathcal{A}_{\rm III}(\eta)
                 \label{eq:eta_minIII},
@@
     \item III $\to$ I (see Fig.~\ref{fig:ad_31}). The trajectory encounters the
-        separatrix when $A_{\rm I}(\eta_\star) + A_{\rm II}(\eta_\star) =
-        A_{\rm i}$, upon which it transitions to a zone I trajectory enclosing
-        $A_{\rm f} = -A_{\rm I}$. The final obliquity is again given by
-        Eq.~\eqref{eq:qfaf}.
-
-        This track can only occur if $A_{\rm i} > A_{\rm II}(\eta_{\rm c})$,
-        but is also constrained by requiring $A_{\rm i}$ be sufficiently small
-        so that it will encounter the separatrix (if $A_{\rm i}$ is too large,
-        it will never encounter the separatrix, and we simply have a III $\to$
-        III transition). This condition is $A_{\rm i} < \max \p{A_{\rm I} +
-        A_{\rm II}} = 4\pi - \min \p{A_{\rm III}}$.
-        Since $\pdil{A_{\rm I}}{\eta} < 0$ and $\pdil{A_{\rm III}}{\eta} > 0$
-        for all accessible $\eta_{\star}$, this track is always permitted.
-
-    \item III $\to$ II $\to$ I (see Fig.~\ref{fig:ad_321}). That $A_{\rm
-        II}(\eta)$ is not a monotonic function of $\eta$ (see
+        separatrix when $\mathcal{A}_{\rm I}(\eta_\star) + \mathcal{A}_{\rm
+        II}(\eta_\star) = A_{\rm i}$, upon which it transitions to a zone I
+        trajectory enclosing $A_{\rm f} = -\mathcal{A}_{\rm I}$. The final
+        obliquity is again given by Eq.~\eqref{eq:qfaf}.
+
+        This track can only occur if $A_{\rm i} > \mathcal{A}_{\rm II}(\eta_{\rm
+        c})$, but is also constrained by requiring $A_{\rm i}$ be sufficiently
+        small so that it will encounter the separatrix (if $A_{\rm i}$ is too
+        large, it will never encounter the separatrix, and we simply have a III
+        $\to$ III transition). This condition is $A_{\rm i} < \max
+        \p{\mathcal{A}_{\rm I} + \mathcal{A}_{\rm II}} = 4\pi - \min
+        \p{\mathcal{A}_{\rm III}}$. Since $\pdil{\mathcal{A}_{\rm I}}{\eta} < 0$
+        and $\pdil{\mathcal{A}_{\rm III}}{\eta} > 0$ for all accessible
+        $\eta_{\star}$, this track is always permitted.
+
+    \item III $\to$ II $\to$ I (see Fig.~\ref{fig:ad_321}). That
+        $\mathcal{A}_{\rm II}(\eta)$ is not a monotonic function of $\eta$ (see
         Fig.~\ref{fig:eq_areas}) is key to the existence of this track. Consider
         a trajectory originating in zone III that first encounters the
-        separatrix at $\eta_1$, when $A_{\rm I}(\eta_1) + A_{\rm II}(\eta_1) =
-        A_{\rm i}$, such that it transitions into zone II enclosing intermediate
-        phase space area $A_{\rm m} = A_{\rm II}(\eta_1)$. Such a transition has
-        probability
+        separatrix at $\eta_1$, when $\mathcal{A}_{\rm I}(\eta_1) +
+        \mathcal{A}_{\rm II}(\eta_1) = A_{\rm i}$, such that it transitions into
+        zone II enclosing intermediate phase space area $A_{\rm m} =
+        \mathcal{A}_{\rm II}(\eta_1)$. Such a transition has probability
         \begin{equation}
             \Pr\p{\rm III \to II} = -\p{
-                \frac{\pdil{A_{\rm II}}{\eta}}{\pdil{A_{\rm III}}{\eta}}}
-                    _{\eta = \eta_1},
+                \frac{\pdil{\mathcal{A}_{\rm II}}{\eta}}{\pdil{\mathcal{A}_{\rm
+                    III}}{\eta}}} _{\eta = \eta_1},
         \end{equation}
@@
         [\eta_{\rm \max, II}, \eta_{\rm c}]$. Equivalently, this requires
-        $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm c}} , A_{\rm II, \max}}$. Then,
-        as $\eta$ continues to decrease, a second $\eta_2$ value exists for
-        which $A_{\rm m} = A_{\rm II}(\eta_2)$, upon which the trajectory is
-        ejected to zone I and $A_{\rm f} = -A_{\rm I}(\eta_2)$. Note that
-        $\eta_2 < \eta_{\rm \max, II}$ necessarily, as zone II must be shrinking
-        in order for the trajectory to be ejected. The final obliquity is given
-        by Eq.~\eqref{eq:qfaf}. Graphical inspection of Fig.~\ref{fig:eq_areas}
-        shows that $\pdil{A_{\rm II}}{\eta}$ and $\pdil{A_{\rm III}}{\eta}$ have
-        the same signs for $\eta < \eta_{\rm \max, II}$, and therefore the
-        complementary II $\to$ I transition is guaranteed. Overall, the III
-        $\to$ II $\to$ I track is permitted so long as the first transition is
-        permitted, or $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm c}} , A_{\rm II,
+        $A_{\rm i} \in \s{\mathcal{A}_{\rm II}\p{\eta_{\rm c}} ,
+        \mathcal{A}_{\rm II, \max}}$. Then, as $\eta$ continues to decrease, a
+        second $\eta_2$ value exists for which $A_{\rm m} = \mathcal{A}_{\rm
+        II}(\eta_2)$, upon which the trajectory is ejected to zone I and $A_{\rm
+        f} = -\mathcal{A}_{\rm I}(\eta_2)$. Note that $\eta_2 < \eta_{\rm \max,
+        II}$ necessarily, as zone II must be shrinking in order for the
+        trajectory to be ejected. The final obliquity is given by
+        Eq.~\eqref{eq:qfaf}. Graphical inspection of Fig.~\ref{fig:eq_areas}
+        shows that $\pdil{\mathcal{A}_{\rm II}}{\eta}$ and
+        $\pdil{\mathcal{A}_{\rm III}}{\eta}$ have the same signs for $\eta <
+        \eta_{\rm \max, II}$, and therefore the complementary II $\to$ I
+        transition is guaranteed. Overall, the III $\to$ II $\to$ I track is
+        permitted so long as the first transition is permitted, or $A_{\rm i}
+        \in \s{\mathcal{A}_{\rm II}\p{\eta_{\rm c}} , \mathcal{A}_{\rm II,
         \max}}$.
@@
         pole ($\cos \theta = -1$) due to the coordinate singularity. This
-        requires $A_{\rm i} > \max \p{A_{\rm I} + A_{\rm II}}$. In the limit of
-        $\eta_{\rm i} \to \infty$ and $ \eta_{\rm f} \to 0$ we have $\theta_{\rm
-        f} = \theta_{\rm sd, i}$. For finite $\eta_{\rm i}$, the initial
-        enclosed phase space area for III $\to$ III trajectories is not given
-        exactly by using $\theta = \theta_{\rm sd, i}$ in Eq.~\eqref{eq:ai_qsd}.
-        This is because the initial orbits for such trajectories are better
-        described as librating about CS3 with angle of libration $\Delta \theta
-        - \theta_{\rm sd, i}$ rather than about CS2 with angle of libration
-        $\theta_{\rm sd, i}$. Here, $\Delta \theta$ is the angular distance
-        between CS2 and CS3 and is not equal to $180^\circ$ except when
-        $\eta_{\rm i} \to \infty$. This finite-$\eta_{\rm i}$ effect is
-        responsible for the small cusp at the very right ($\theta_{\rm sd, i}
-        \to 180^\circ$) of
-        Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
+        requires $A_{\rm i} > \max \p{\mathcal{A}_{\rm I} + \mathcal{A}_{\rm
+        II}}$. In the limit of $\eta_{\rm i} \to \infty$ and $ \eta_{\rm f} \to
+        0$ we have $\theta_{\rm f} = \theta_{\rm sd, i}$. For finite $\eta_{\rm
+        i}$, the initial enclosed phase space area for III $\to$ III
+        trajectories is not given exactly by using $\theta = \theta_{\rm sd, i}$
+        in Eq.~\eqref{eq:ai_qsd}. This is because the initial orbits for such
+        trajectories are better described as librating about CS3 with angle of
+        libration $\Delta \theta - \theta_{\rm sd, i}$ rather than about CS2
+        with angle of libration $\theta_{\rm sd, i}$. Here, $\Delta \theta$ is
+        the angular distance between CS2 and CS3 and is not equal to $180^\circ$
+        except when $\eta_{\rm i} \to \infty$. This finite-$\eta_{\rm i}$ effect
+        is responsible for the small cusp at the very right ($\theta_{\rm sd, i}
+        \to 180^\circ$) of Figs.~\ref{fig:ad_ensemble}
         and~\ref{fig:3_ensemble_20_35}.
@@
 \begin{enumerate}
-    \item $A_{\rm i} \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$: Both the II
-        $\to$ III and the II $\to$ I tracks are possible.
-
-    \item $A_{\rm i} \in \s{A_{\rm II}\p{\eta_{\rm \min, III}}, A_{\rm
-        II}(\eta_{\rm c})}$: Only the II $\to$ I track.
-
-    \item $A_{\rm i} \in \s{A_{\rm II}(\eta_{\rm c}), A_{\rm II, \max}}$:
-        Both the III $\to$ I and III $\to$ II $\to$ I are possible.
-
-    \item $A_{\rm i} \in \s{A_{\rm II, \max}, \max \p{A_{\rm I} + A_{\rm II}}}$:
-        Only the III $\to$ I track.
-
-    \item $A_{\rm i} > \max \p{A_{\rm I} + A_{\rm II}}$: Only the III $\to$ III
-        track.
+    \item $A_{\rm i} \in \s{0, \mathcal{A}_{\rm II}\p{\eta_{\rm \min, III}}}$:
+        Both the II $\to$ III and the II $\to$ I tracks are possible.
+
+    \item $A_{\rm i} \in \s{\mathcal{A}_{\rm II}\p{\eta_{\rm \min, III}},
+        \mathcal{A}_{\rm II}(\eta_{\rm c})}$: Only the II $\to$ I track.
+
+    \item $A_{\rm i} \in \s{\mathcal{A}_{\rm II}(\eta_{\rm c}), \mathcal{A}_{\rm
+        II, \max}}$: Both the III $\to$ I and III $\to$ II $\to$ I are possible.
+
+    \item $A_{\rm i} \in \s{\mathcal{A}_{\rm II, \max}, \max \p{\mathcal{A}_{\rm
+        I} + \mathcal{A}_{\rm II}}}$: Only the III $\to$ I track.
+
+    \item $A_{\rm i} > \max \p{\mathcal{A}_{\rm I} + \mathcal{A}_{\rm II}}$:
+        Only the III $\to$ III track.
 \end{enumerate}
@@
 The above calculation applies for a specific initial $\theta_{\rm i}$, but, as
-diskussed at the beginning of Section~\ref{ss:ad_ensemble}, the initial spin
+discussed at the beginning of Section~\ref{ss:ad_ensemble}, the initial spin
 orientation is more appropriately described by $\theta_{\rm sd, i}$ since
@@
 
-As noted in Section 1, while in this paper we have examined a specific scenario
-of generating/modifying planetary obliquities from planet-disk interactions, the
-dynamical problem have studied is more general
+As noted in Section~\ref{s:intro}, while in this paper we have examined a
+specific scenario of generating/modifying planetary obliquities from planet-disk
+interactions, the dynamical problem have studied is more general
 \citep{colombo1966,peale1969,peale1974possible,ward1975tidal,henrard1987}. Our
@@
 
-We thank Kassandra Anderson for diskussion and assistance in the early phase of
-this work. DL thanks the Dept.\ of Astronomy and the Miller Institute for Basic
-Science at UC Berkeley for hospitality while part of this work was carried out.
-This work has been supported in part by the NSF grant AST-17152 and NASA grant
-80NSSC19K0444. YS is supported by the NASA FINESST grant
-19-ASTRO19-0041.% chktex 8
+We thank \textcolor{Corr}{the anonymous reviewer for their detailed and
+insightful comments that improved this work, and} Kassandra Anderson for
+discussion and assistance in the early phase of this work. DL thanks the Dept.\
+of Astronomy and the Miller Institute for Basic Science at UC Berkeley for
+hospitality while part of this work was carried out. This work has been
+supported in part by the NSF grant AST-17152 and NASA grant 80NSSC19K0444. YS is
+supported by the NASA FINESST grant 19-ASTRO19-0041.% chktex 8
 
@@
 % We next develop some approximate forms for the CS obliquities that will be
-% useful for guiding later diskussion. Denote $\theta_{\rm cs}$ the obliquity of
+% useful for guiding later discussion. Denote $\theta_{\rm cs}$ the obliquity of
 % some Cassini State (fixed point of Eqs.~\eqref{se:H_eom}).
@@
 \begin{equation}
-    A_{\rm II}(\eta) \approx 16\sqrt{\eta \sin I}.\label{eq:a_approx}
+    \mathcal{A}_{\rm II}(\eta) \approx 16\sqrt{\eta \sin I}.\label{eq:a_approx}
 \end{equation}
@@
         sd, i}^2$. This then implies $\eta_\star$ must be the solution to
-        $A_{\rm II}(\eta_\star) = A$, or
+        $\mathcal{A}_{\rm II}(\eta_\star) = A$, or
         \begin{equation}
@@
         predicted by observing the final adiabatic invariant $A_{\rm f} =
-        -A_{\rm I}(\eta_\star)$ in the zone I case and $A_{\rm f} = A_{\rm
-        I}(\eta_\star) + A_{\rm I}I(\eta_\star)$ in the zone III case. As $\eta
+        -\mathcal{A}_{\rm I}(\eta_\star)$ in the zone I case and $A_{\rm f} =
+        \mathcal{A}_{\rm I}(\eta_\star) + \mathcal{A}_{\rm I}I(\eta_\star)$ in
+        the zone III case. As $\eta
         \to 0$, these correspond to obliquities

### 2020-08-07 initial/0_eta/utils.py

@@ -86,9 +86,10 @@ def solve_ic(I, eta, tide, y0, tf, method='RK45', rtol=1e-6, **kwargs):
                         rtol=rtol, method=method, jac=jac, **kwargs)
     return time.time() - time_i, ret.t, ret.y
 
-def get_four_subplots():
+def get_four_subplots(**kwargs):
     ''' keep using four subplots w/ same settings '''
-    f, ((ax1, ax2), (ax3, ax4)) = plt.subplots(2, 2, sharex=True, sharey=True)
+    f, ((ax1, ax2), (ax3, ax4)) = plt.subplots(2, 2, sharex=True, sharey=True,
+                                               **kwargs)
     axs = [ax1, ax2, ax3, ax4]
     for ax in axs:
         ax.set_xlim([0, 2 * np.pi])
@@ -107,8 +108,12 @@ def plot_point(ax, q, *args, **kwargs):
     ''' plot Cassini state including wrap around logic '''
     phi = get_phi(q)
     phi_arr = [phi] if abs(phi % (2 * np.pi)) > 0.5 else [phi, phi + 2 * np.pi]
-    for phi_plot in phi_arr:
-        ax.plot(phi_plot, np.cos(q), *args, **kwargs)
+    for idx, phi_plot in enumerate(phi_arr):
+        if idx == 0:
+            ax.plot(phi_plot, np.cos(q), *args, **kwargs)
+        else:
+            del kwargs['label']
+            ax.plot(phi_plot, np.cos(q), *args, **kwargs)
 
 def H(I, eta, x, phi):
     return -0.5 * x**2 + eta * (

### 2020-08-07 initial/2_toy2/3_disk_disp.py

@@ -1172,16 +1172,17 @@ def plot_manys():
     # sim_for_many(np.radians(5), eps=-3e-4, n_pts=101, n_dqs=51, extra_plot=True)
     # sim_for_many(np.radians(10), eps=-3e-4, n_pts=101, n_dqs=51,
     #              two_panel=False, extra_plot=True)
-    # sim_for_many(np.radians(20), eps=-3e-4, n_pts=101, n_dqs=51, #              two_panel=False, extra_plot=True)
+    # sim_for_many(np.radians(20), eps=-3e-4, n_pts=101, n_dqs=51,
+    #              two_panel=False, extra_plot=True)
     # sim_for_many(I, eps=-1e-3, n_pts=101, n_dqs=51, two_panel=False)
     # sim_for_many(I, eps=-3e-3, n_pts=101, n_dqs=51, two_panel=False)
     # sim_for_many(I, eps=-1e-2, n_pts=101, n_dqs=101, dqmin=0.01,
     #              two_panel=False)
-    # sim_for_many(I, eps=-3e-2, n_pts=101, n_dqs=101,
-    #              two_panel=False, dqmin=0.01)
+    sim_for_many(I, eps=-3e-2, n_pts=101, n_dqs=101,
+                 two_panel=False, dqmin=0.01)
 
-    sim_for_many(I, eps=-3e-1, n_pts=101, n_dqs=101,
-                 adiabatic=False, dqmin=0.01)
+    # sim_for_many(I, eps=-3e-1, n_pts=101, n_dqs=101,
+    #              adiabatic=False, dqmin=0.01)
     # sim_for_many(I, eps=-2e-1, n_pts=101, n_dqs=101,
     #              adiabatic=False, dqmin=0.01)
     # sim_for_many(I, eps=-1e-1, n_pts=101, n_dqs=101,
@@ -1189,8 +1190,8 @@ def plot_manys():
 
 if __name__ == '__main__':
     I = np.radians(5)
-    plot_singles(I)
-    # plot_manys()
+    # plot_singles(I)
+    plot_manys()
 
     # testing high epsilon
     # eta_c = get_etac(I)

### 2020-08-13 writeups/response.txt
finished paper response

@@
 https://doi.org/10.1093/mnras/stw3018.
+So we choose to retain the current coordinate system.
 
@@
 
-This is an interesting observation and distinction, and we have added a few sentences to discuss this.
+This largely arises due to the choices of parameters used for Figs 7-8; a larger \theta_{sd, i} would show that II -> I,III crossings also impulsively change the obliquity behavior.
+As such, we choose not to remark on this in the paper.
 
@@
 
-This is a great comment, and we have added a paragraph to the discussion outlining the possible consequences of multiple interior planets.
+We have added a brief discussion on multiple planet configurations, focusing on aspects for which our analysis differs from that of Millholland & Batygin 2018.
 
@@
 
-* Added
+Added.
 
@@
 
-* Our notation follows the notation used in our references, though we have added equivalences and references for the more common choices of notation
+Our notation follows the notation used in our references, though we have added equivalences to the common choices of notation.
 
@@
 
-* Fixed
+Fixed.
 
@@
 
-* Added inclination to captions for Figs 4 & 5
+Added inclination to captions for Figs 4 & 5.
 
@@
 
-* removed Figure 6, leaving only I = 20
+Removed Figure 6, leaving only I = 20.
 
@@
 Instead, the result from Henrard 1982 (Eqs.
-25) shows that the true outcome depends on the value of the Hamiltonian modulo a small quantity ~epsilon, e.g.
-whether H \mod epsilon = 0.2 epsilon or H \mod epsilon = 0.8 epsilon dictates whether the system ends up in one track or the other.
+25) shows that the true outcome depends on the value of the Hamiltonian modulo a small quantity ~epsilon.
 When epsilon is sufficiently small, this is effectively probabilistic, rather than deterministic.
@@
 
-* Removed
+Removed.
 
@@
 
-* We believe this confusion is largely remedied by the change in notation to differentiate between unsigned areas (a la Ward & Hamilton) and signed phase space areas, c.f. 6th small comment
+We have added such a clarification.
+We believe this confusion is further remedied by the change in notation to differentiate between unsigned areas (a la Ward & Hamilton) and signed phase space areas, c.f.
+6th small comment.
 
@@
 This is a great observation.
-Firstly, our calculations only assume the libration cycles are circular initially; at later times, we use conservation of phase space area to compare the phase space area at any time to the analytical A_{I,II,III}s.
-Instead, since this plot describes the messy intermediate regime, we have two possible explanations for the observed deviation: (i) it is likely that phase space area conservation is simply imperfect, and (ii) since the separatrix is changing so much during the separatrix-crossing orbit, approximating eta_star as a constant during this orbit is invalid.
-This hurts the accuracy of our calculations, as we calculate analytical phase space areas using eta from the start of the separatrix crossing orbit.
-This observation illustrates the caveats of our calculations well, so we have made note of it in the manuscript.
+Our calculations only assume the libration cycles are circular initially; at later times, we use conservation of phase space area to compare the phase space area at any time to the analytical A_{I,II,III}s.
+Instead, this is because the separatrix is changing so much during the separatrix-crossing orbit, approximating eta_star as a constant during this orbit is invalid.
+We have made note of it in the manuscript.

### 2020-08-13 writeups/Su_disk_disp.tex
typos
finished paper response

@@
-% rm -f plots_diskdisp/*.png; for i in ../initial/99_misc/2_nonad_rot.png ../initial/99_misc/2_3vec.png ../initial/99_misc/2_cs_locs.png ../initial/0_eta/1contours_flip.png ../initial/99_misc/1_areas.png ../initial/2_toy2/3_ensemble_05_35.png ../initial/2_toy2/3_ensemble_20_35.png ../initial/2_toy2/3testo21.png ../initial/2_toy2/3testo21_subplots.png ../initial/2_toy2/3testo23.png ../initial/2_toy2/3testo23_subplots.png ../initial/2_toy2/3testo31.png ../initial/2_toy2/3testo31_subplots.png ../initial/2_toy2/3testo321.png ../initial/2_toy2/3testo321_subplots.png ../initial/2_toy2/3_ensemble_05_25.png ../initial/2_toy2/3_ensemble_05_15.png ../initial/2_toy2/3testo_nonad.png ../initial/2_toy2/3testo_nonad_subplots.png ../initial/2_toy2/3_ensemble_05_05.png ../initial/2_toy2/3scan.png ../initial/2_toy2/3scan_20.png ../initial/99_misc/2_lambdas.png; do cp $i plots_diskdisp; done
+% rm -f plots_diskdisp/*.png; for i in ../initial/99_misc/2_nonad_rot_cropped.png ../initial/99_misc/2_nonad_rot.png ../initial/99_misc/2_3vec.png ../initial/99_misc/2_cs_locs.png ../initial/0_eta/1contours_flip.png ../initial/99_misc/1_areas.png ../initial/2_toy2/3_ensemble_05_35.png ../initial/2_toy2/3_ensemble_20_35.png ../initial/2_toy2/3testo21.png ../initial/2_toy2/3testo21_subplots.png ../initial/2_toy2/3testo23.png ../initial/2_toy2/3testo23_subplots.png ../initial/2_toy2/3testo31.png ../initial/2_toy2/3testo31_subplots.png ../initial/2_toy2/3testo321.png ../initial/2_toy2/3testo321_subplots.png ../initial/2_toy2/3_ensemble_05_25.png ../initial/2_toy2/3_ensemble_05_15.png ../initial/2_toy2/3testo_nonad.png ../initial/2_toy2/3testo_nonad_subplots.png ../initial/2_toy2/3_ensemble_05_05.png ../initial/2_toy2/3scan.png ../initial/2_toy2/3scan_20.png ../initial/99_misc/2_lambdas.png; do cp $i plots_diskdisp; done
     \documentclass[twocolumn,twocolappendix]{aastex63}
@@
 dissipation timescales, and examine both ``adiabatic'' (slow disk dissipation)
-and ``non-adiabatic'' evolution. \textcolor{Corr}{Our chief results include
-that: (i) careful accounting of phase space area across separatrix
-crossings is able to explain the rich dynamics of adiabatic evolution, and (ii)
-the concept of ``partial adiabatic resonance advection'' fully explains dynamics
-in the non-adiabatic limit.} We calibrate our analytical results with numerical
+and ``non-adiabatic'' evolution. \textcolor{Corr}{Our chief new results include
+that: (i) careful accounting of phase space area across separatrix crossings can
+analytically describe the rich dynamics of adiabatic evolution, and (ii) the
+concept of ``partial adiabatic resonance advection'' fully captures dynamics in
+the non-adiabatic limit.} We calibrate our analytical results with numerical
 calculations.
@@
 where $\rho_p = 3M_p/(4\pi R_p^3)$ and $P_p = 2\pi/\Omega_p$ is the planet's
-rotation period. . In Eq.~\eqref{eq:eta}, we have introduced the fiducial values
+rotation period. In Eq.~\eqref{eq:eta}, we have introduced the fiducial values
 of variable parameters for the application considered in this paper.
@@
     \caption{Level curves of $\mathcal{H}\p{\phi, \cos \theta}$
-    [Eq.~\eqref{eq:H}] for $I = 5^\circ$, where warmer colors denote more
-    positive values. The black solid line is the separatrix, which only exists
-    for $\eta < \eta_{\rm c} = 0.766$. The three zones (I, II, III), divided by
-    the separatrix, are labeled. The Cassini states are denoted by filled
-    circles and have the same colors as in Fig.~\ref{fig:cs_locs}. The interior
-    of the separatrix, shaded in grey, is formally only defined for $\eta <
-    \eta_{\rm c}$, but we may identify the points in phase space that flow into
-    zone II when evolved forward in time (decreasing $\eta$ adiabatically); this
-    is the shaded region in panel (a), bounded by the black dotted
-    line.}\label{fig:eq_1contours}
+    [Eq.~\eqref{eq:H}] \textcolor{Corr}{for $I = 5^\circ$}, where warmer colors
+    denote more positive values. The black solid line is the separatrix, which
+    only exists for $\eta < \eta_{\rm c} = 0.766$. The three zones (I, II, III),
+    divided by the separatrix, are labeled. The Cassini states are denoted by
+    filled circles and have the same colors as in Fig.~\ref{fig:cs_locs}. The
+    interior of the separatrix, shaded in grey, is formally only defined for
+    $\eta < \eta_{\rm c}$, but we may identify the points in phase space that
+    flow into zone II when evolved forward in time (decreasing $\eta$
+    adiabatically); this is the shaded region in panel (a), bounded by the black
+    dotted line.}\label{fig:eq_1contours}
 \end{figure*}
@@
 \;\mathrm{d}\phi}}$ of the three zones (as defined in
-Fig.~\ref{fig:eq_1contours}) can be computed analytically
-\citep{henrard1987,ward2004I}. \textcolor{Corr}{As given in
-\citet{ward2004I}, if we define}
+Fig.~\ref{fig:eq_1contours}) can be computed analytically. If we define
 \begin{subequations}
@@
 \end{subequations}
-\textcolor{Corr}{then} the areas for $\eta < \eta_{\rm c}$ are given by
+\textcolor{Corr}{then the areas for $\eta < \eta_{\rm c}$ are given by
+\citep{ward2004I}}
 \begin{subequations}\label{se:area_ward}
@@
     \caption{Plot of fractional areas of each of the zones
-    $\mathcal{A}_{\rm i}(\eta) / 4\pi$ as given by Eqs.~\eqref{se:area_ward} for
-    $I = 5^\circ$. The colored dotted lines correspond to small $\eta$
-    approximations used in Appendix~\ref{s:ad_approx}. The colored dashed lines
-    for $\eta > \eta_{\rm c}$ are the effective values of $\mathcal{A}_{\rm II},
-    \mathcal{A}_{\rm III}$ for $\eta > \eta_{\rm c}$, denoting the points that
-    would flow into either area under adiabatic decrease of $\eta$ from $\eta >
-    \eta_{\rm c}$ (see the text). The vertical black dashed lines correspond to
-    $\eta = \eta_{\rm c}$ [Eq.\eqref{eq:etac}] and the values of $\eta$ for
-    which $\mathcal{A}_{\rm II}$ is maximized ($\eta_{\rm \max, II}$) and for
-    which $\mathcal{A}_{\rm III}$ is minimized ($\eta_{\rm \min, III}$,
-    Eq.~\eqref{eq:eta_minIII}).}\label{fig:eq_areas}
+    $\mathcal{A}_{\rm j}(\eta) / 4\pi$ as given by Eqs.~\eqref{se:area_ward}
+    \textcolor{Corr}{for $I = 5^\circ$}. The colored dotted lines correspond to
+    small $\eta$ approximations used in Appendix~\ref{s:ad_approx}. The colored
+    dashed lines for $\eta > \eta_{\rm c}$ are the effective values of
+    $\mathcal{A}_{\rm II}, \mathcal{A}_{\rm III}$ for $\eta > \eta_{\rm c}$,
+    denoting the points that would flow into either area under adiabatic
+    decrease of $\eta$ from $\eta > \eta_{\rm c}$ (see the text). The vertical
+    black dashed lines correspond to $\eta = \eta_{\rm c}$ [Eq.\eqref{eq:etac}]
+    and the values of $\eta$ for which $\mathcal{A}_{\rm II}$ is maximized
+    ($\eta_{\rm \max, II}$) and for which $\mathcal{A}_{\rm III}$ is minimized
+    ($\eta_{\rm \min, III}$, Eq.~\eqref{eq:eta_minIII}).}\label{fig:eq_areas}
 \end{figure}
@@
     initial spin-disk misalignment angle $\theta_{\rm sd, i}$ for systems
-    evolving from initial $\eta_{\rm i} \gg 1$ to $\eta_{\rm f} \ll 1$, for $I =
-    5^\circ$. The blue dots are results of numerical calculations
-    (Section~\ref{ss:ad_ensemble}), and the colored tracks are semi-analytical
-    results (Section~\ref{ss:zone_transitions}). Bottom: The probabilities of
-    different outcomes. Where a particular $\theta_{\rm sd, i}$ corresponds to
-    multiple tracks, the system evolves probabilistically. The track that a
-    particular system evolves along in a numerical simulation can be measured by
-    examining its final obliquity. The dots represent the inferred probabilities
-    from measured final obliquities in our simulations, while the colored tracks
-    denote the semi-analytic probability of the system evolving along each
-    track. There are five regimes of $\theta_{\rm sd, i}$ values for which
-    different tracks are accessible. In both plots, the vertical dashed black
-    lines denote semi-analytical calculations of the boundaries of these regimes
-    (see Section~\ref{ss:zone_transitions}), while the black dotted lines
-    represent analytical approximations valid in the small-$\theta_{\rm sd, i}$
-    limit (see Appendix~\ref{s:ad_approx}).}\label{fig:ad_ensemble}
+    evolving from initial $\eta_{\rm i} \gg 1$ to $\eta_{\rm f} \ll 1$,
+    \textcolor{Corr}{for $I = 5^\circ$}. The blue dots are results of numerical
+    calculations (Section~\ref{ss:ad_ensemble}), and the colored tracks are
+    semi-analytical results (Section~\ref{ss:zone_transitions}). Bottom: The
+    probabilities of different outcomes. Where a particular $\theta_{\rm sd, i}$
+    corresponds to multiple tracks, the system evolves probabilistically. The
+    track that a particular system evolves along in a numerical simulation can
+    be measured by examining its final obliquity. The dots represent the
+    inferred probabilities from measured final obliquities in our simulations,
+    while the colored tracks denote the semi-analytic probability of the system
+    evolving along each track. There are five regimes of $\theta_{\rm sd, i}$
+    values for which different tracks are accessible. In both plots, the
+    vertical dashed black lines denote semi-analytical calculations of the
+    boundaries of these regimes (see Section~\ref{ss:zone_transitions}), while
+    the black dotted lines represent analytical approximations valid in the
+    small-$\theta_{\rm sd, i}$ limit (see
+    Appendix~\ref{s:ad_approx}).}\label{fig:ad_ensemble}
 \end{figure}
@@
 \end{equation}
-This definition of $A$ has two advantages: (i) it is continuous across
-transitions from circulating to librating that cross the North pole ($\cos
-\theta = 1$), and (ii) the areas of the three zones are equal in absolute value
-to the expressions given in Eqs.~\eqref{se:area_ward}. The path over which the
-integral is taken is either a libration or circulation cycle. When $\eta_{\rm i}
-\gg 1$, trajectories librate about $\uv{l}_{\rm d}$ with constant $\theta_{\rm
-sd}$, meaning they enclose initial phase space area
+\textcolor{Corr}{Note that $A$ can be negative when $\rdil{\phi}{t} < 0$, unlike
+the unsigned areas $\mathcal{A}_{\rm i}$ [Eqs.~\eqref{se:area_ward}] which are
+positive by definition.} This definition
+of $A$ has two advantages: (i) it is continuous across transitions from
+circulating to librating that cross the North pole ($\cos \theta = 1$), and (ii)
+the areas of the three zones are equal in absolute value to the expressions
+given in Eqs.~\eqref{se:area_ward}. The path over which the integral is taken is
+either a libration or circulation cycle. When $\eta_{\rm i} \gg 1$, trajectories
+librate about $\uv{l}_{\rm d}$ with constant $\theta_{\rm sd}$, meaning they
+enclose initial phase space area
 \begin{equation}
@@
 When a trajectory experiences separatrix crossing, it transitions into nearby
-zones probabilistically. This process is studied by \citet{henrard1982} and
-\citet{henrard1987}. Their results may be summarized as follows: if zone $i$
-is shrinking while adjacent zones $j, k$ are expanding such that the sum of
-their areas is constant, the probabilities of transition from zone $i$ to zones
-$j$ and $k$ are given by
+zones probabilistically. This process is studied \textcolor{Corr}{in the
+adiabatic limit} by \citet{henrard1982} and \citet{henrard1987}. Their results
+may be summarized as follows: if zone $i$ is shrinking while adjacent zones $j,
+k$ are expanding such that the sum of their areas is constant, the probabilities
+of transition from zone $i$ to zones $j$ and $k$ are given by\footnote{
+\textcolor{Corr}{Interestingly, the probabilistic nature of separatrix crossing
+is not because the outcome depends on the phase $\phi$ of the system at
+crossing. Instead, the transition the system takes is determined by the value of
+$H$ at the start of a separatrix-crossing orbit \citep{henrard1982}. Since $H$
+only changes by $\propto \epsilon$ over a circulation/libration cycle, $\sim
+\epsilon$ changes to initial conditions affect the final outcome. As such, as
+$\epsilon \to 0$, the outcome effectively becomes probabilistic.}}
 \begin{subequations}\label{eq:henrard_hop}
@@
 To illustrate the transition to nonadiabaticity, we carried out a suite of
-numerical calculations for several values of $\epsilon$. The results for two of these
-values are shown in Figs.~\ref{fig:3_ensemble_05_25}
+numerical calculations for several values of $\epsilon$. The results for two of
+these values are shown in Figs.~\ref{fig:3_ensemble_05_25}
 and~\ref{fig:3_ensemble_05_15}.
@@
 sensitive to the \emph{phase} of the libration/circulation cycle at the
-crossing: if the trajectory crosses the separatrix when the obliquity is at its
-maximum, the final obliquity will also be relatively larger.
+crossing \textcolor{Corr}{(as noted in Section~3.2.2, the phase does not affect
+separatrix crossing in the adiabatic limit)}: if the trajectory crosses the
+separatrix when the obliquity is at its maximum, the final obliquity will also
+be relatively larger.
 
@@
 similar phases evolve to similar final obliquities that only depend weakly on
-on $\theta_{\rm sd, i}$.
+on $\theta_{\rm sd, i}$. \textcolor{Corr}{Finally, the bottom edge
+of the data and the III $\to$ I track deviate very noticeably. This
+non-adiabatic effect is the result of the separatrix evolving significantly
+within the separatrix-crossing orbit, as the tracks computed in
+Section~\ref{s:ad} assume $\eta$ is constant throughout the separatrix-crossing
+orbit.}
 
@@
     the adiabatic tracks remains, and the deviations appear to have a banded
-    structure. }\label{fig:3_ensemble_05_15}
+    structure.}\label{fig:3_ensemble_05_15}
 \end{figure}
@@
 obliquity, so the range of obliquities at the end of phase (i) is frozen in as
-the range of final obliquities.
+the range of final obliquities. \textcolor{Corr}{We refer to this two-phase
+evolution as \emph{partial adiabatic resonance advection}.}
 
@@
         of $\theta_{\rm f}$ for nonzero $\theta_{\rm sd, i}$ (see
-        Fig.~\ref{fig:ad_ensemble}). We analytically calculate both the exact
-        final $\theta_{\rm f}$ values and the probabilities of achieving each
-        value via careful accounting of adiabatic invariance and separatrix
-        crossing dynamics.
+        Fig.~\ref{fig:ad_ensemble}). We \textcolor{Corr}{show for the first time
+        that} both the final $\theta_{\rm f}$ values and the probabilities of
+        achieving each value \textcolor{Corr}{can be understood analytically}
+        via careful accounting of adiabatic invariance and separatrix crossing
+        dynamics.
+
     \item As the disk dissipates more rapidly, the adiabatic condition
@@
         final obliquities can be reached for a given $\theta_{\rm sd, i}$ (see
-        Fig.~\ref{fig:nonad_3_ensemble}). We provide an analytical expression of
-        the bounds on $\theta_{\rm f}$ in Eq.~\eqref{eq:nonad_q_f_dist}.
+        Fig.~\ref{fig:nonad_3_ensemble}). We \textcolor{Corr}{understand this
+        via the novel concept of partial adiabatic resonance advection and}
+        provide an analytical expression of the bounds on $\theta_{\rm f}$ in
+        Eq.~\eqref{eq:nonad_q_f_dist}.
 \end{enumerate}
@@
 
+\textcolor{Corr}{In practice, planets are not expected to form in isolation.
+\citet{millholland_disk} point out that one effect of a companion planet is that
+$g$ and $\eta$ for the planet of interest never decay below the Laplace-Lagrange
+secular nodal precession frequency. This does not affect the methodology of our
+analysis, but has some small effects on our detailed results: (i) the
+adiabaticity criterion must be modified slightly as $\rdil{\ln \eta}{t}$ is no
+longer constant but asymptotes to zero as $\eta$ decreases, (ii) the planet may
+never undergo separatrix crossing if their $\eta_{\star}$ (which depends on
+$\theta_{\rm sd, i}$) in the absence of the companions is too small, and (iii)
+the planetary obliquities will oscillate even when the disk has fully evaporated
+(as $\uv{l}$ is no longer constant). An interesting consequence of (ii) is that
+an outer planet may experience separatrix crossing before an inner planet does.
+The dynamics can be even more complex if the two planets are in mean motion
+resonance \citep[e.g.][]{millholland2019obliquity}.}
+
 \section*{Acknowledgements}
@@
 We thank \textcolor{Corr}{the anonymous reviewer for their detailed and
-insightful comments that improved this work, and} Kassandra Anderson for
+insightful comments that improved this work and} Kassandra Anderson for
 discussion and assistance in the early phase of this work. DL thanks the Dept.\

### 2020-08-13 initial/99_misc/1_areas.py

@@ -9,7 +9,8 @@ import matplotlib.pyplot as plt
 plt.rc('text', usetex=True)
 LW=2.0
 plt.rc('lines', lw=LW)
-plt.rc('font', family='serif', size=20)
+plt.rc('font', family='serif', size=16)
+plt.rc('text.latex', preamble=r'\usepackage{newtxmath}')
 
 def get_etac(I):
     return (np.sin(I)**(2/3) + np.cos(I)**(2/3))**(-3/2)
@@ -93,7 +94,7 @@ def plot_areas(I=np.radians(5), filename='1_areas'):
     ax1.legend(loc='upper left', fontsize=12,
                bbox_to_anchor=(0.05, xlims[1] + 0.035))
     ax1.set_xlabel(r'$\eta$')
-    ax1.set_ylabel(r'$A / 4\pi$')
+    ax1.set_ylabel(r'$\mathcal{A} / 4\pi$')
     ax1.set_xticks([0, 0.3, 0.6, 0.9])
     ax1.set_xticklabels([r'$0$', r'$0.3$', r'$0.6$', r'$0.9$'])
     old_ylims = ax1.get_ylim()

### 2020-08-17 writeups/Su_disk_disp.tex
small typos

@@
 \citet{millholland_disk} point out that one effect of a companion planet is that
-$g$ and $\eta$ for the planet of interest never decay below the Laplace-Lagrange
-secular nodal precession frequency. This does not affect the methodology of our
-analysis, but has some small effects on our detailed results: (i) the
-adiabaticity criterion must be modified slightly as $\rdil{\ln \eta}{t}$ is no
-longer constant but asymptotes to zero as $\eta$ decreases, (ii) the planet may
-never undergo separatrix crossing if their $\eta_{\star}$ (which depends on
-$\theta_{\rm sd, i}$) in the absence of the companions is too small, and (iii)
-the planetary obliquities will oscillate even when the disk has fully evaporated
-(as $\uv{l}$ is no longer constant). An interesting consequence of (ii) is that
-an outer planet may experience separatrix crossing before an inner planet does.
-The dynamics can be even more complex if the two planets are in mean motion
-resonance \citep[e.g.][]{millholland2019obliquity}.}
+$g$ for the planet of interest never decays below the Laplace-Lagrange
+secular nodal precession frequency. Therefore, $\eta$ has a minimum value at
+late times. This does not affect the methodology of our analysis, but has some
+small effects on our detailed results: (i) the adiabaticity criterion must be
+modified slightly as $\rdil{\ln \eta}{t}$ is no longer constant but asymptotes
+to zero as $\eta$ decreases, (ii) the planet may never undergo separatrix
+crossing if their $\eta_{\star}$ (which depends on $\theta_{\rm sd, i}$) in the
+absence of the companions is too small, and (iii) the planetary obliquities will
+oscillate even when the disk has fully evaporated (as $\uv{l}$ is no longer
+constant). An interesting consequence of (ii) is that an outer planet may
+experience separatrix crossing before an inner planet does. The dynamics can be
+even more complex if the two planets are in mean motion resonance
+\citep[e.g.][]{millholland2019obliquity}.}
 

### 2020-08-18 writeups/Su_disk_disp.tex
done response

@@
 dissipation timescales, and examine both ``adiabatic'' (slow disk dissipation)
-and ``non-adiabatic'' evolution. \textcolor{Corr}{Our chief new results include
-that: (i) careful accounting of phase space area across separatrix crossings can
-analytically describe the rich dynamics of adiabatic evolution, and (ii) the
-concept of ``partial adiabatic resonance advection'' fully captures dynamics in
-the non-adiabatic limit.} We calibrate our analytical results with numerical
-calculations.
+and ``non-adiabatic'' evolution. We calibrate these analytical results with
+numerical calculations. \textcolor{Corr}{ On the technical side, our paper
+extends previous works \citep[such as][]{henrard1982, henrard1987,
+millholland_disk} in several aspects. Two of our main results are: (i) a careful
+accounting of the phase space area across sepratrix to analytically describe the
+rich dynamics of adiabatic evolution, and (ii) using the concept of ``partial
+adiabatic resonance advection'' to fully capture the dynamics in the
+non-adiabatic limit.}
 
@@
 \textcolor{Corr}{In other studies, $3k_{\rm qp} / 2 k_{\rm p}$ is often notated
-$k_2 / 2C$ \citep[e.g.][]{millholland_disk}}. In Eq.~\eqref{eq:wld}, $n \equiv
-\sqrt{GM_\star/a_{\rm p}^3}$ is the planet's orbital mean motion, and we have
-assumed $r_d\gg a_p$ and included only the leading-order (quadrupole)
+as $k_2 / 2C$ \citep[e.g.][]{millholland_disk}}. In Eq.~\eqref{eq:wld}, $n
+\equiv \sqrt{GM_\star/a_{\rm p}^3}$ is the planet's orbital mean motion, and we
+have assumed $r_d\gg a_p$ and included only the leading-order (quadrupole)
 interaction between the planet and disk. We define three relative inclination
@@
 $H$ at the start of a separatrix-crossing orbit \citep{henrard1982}. Since $H$
-only changes by $\propto \epsilon$ over a circulation/libration cycle, $\sim
-\epsilon$ changes to initial conditions affect the final outcome. As such, as
-$\epsilon \to 0$, the outcome effectively becomes probabilistic.}}
+only changes by $\propto \epsilon$ over a circulation/libration cycle, an order
+$\sim \epsilon$ change to the initial condition affects the final outcome. As
+such, as $\epsilon \to 0$, the outcome effectively becomes probabilistic.}}
 \begin{subequations}\label{eq:henrard_hop}
@@
 similar phases evolve to similar final obliquities that only depend weakly on
-on $\theta_{\rm sd, i}$. \textcolor{Corr}{Finally, the bottom edge
-of the data and the III $\to$ I track deviate very noticeably. This
-non-adiabatic effect is the result of the separatrix evolving significantly
-within the separatrix-crossing orbit, as the tracks computed in
-Section~\ref{s:ad} assume $\eta$ is constant throughout the separatrix-crossing
-orbit.}
+on $\theta_{\rm sd, i}$. \textcolor{Corr}{Finally, in
+Fig.~\ref{fig:3_ensemble_05_15}, the bottom edge of the data and the III $\to$ I
+track deviate very noticeably. This non-adiabatic effect is the result of the
+separatrix evolving significantly within the separatrix-crossing orbit, as the
+tracks computed in Section~\ref{s:ad} assume that $\eta$ is constant throughout
+the separatrix-crossing orbit.}
 
@@
         Fig.~\ref{fig:nonad_3_ensemble}). We \textcolor{Corr}{understand this
-        via the novel concept of partial adiabatic resonance advection and}
-        provide an analytical expression of the bounds on $\theta_{\rm f}$ in
-        Eq.~\eqref{eq:nonad_q_f_dist}.
+        result via the novel concept of partial adiabatic resonance advection
+        and} provide an analytical expression of the bounds on $\theta_{\rm f}$
+        in Eq.~\eqref{eq:nonad_q_f_dist}.
 \end{enumerate}
@@
 
-\textcolor{Corr}{In practice, planets are not expected to form in isolation.
-\citet{millholland_disk} point out that one effect of a companion planet is that
-$g$ for the planet of interest never decays below the Laplace-Lagrange
-secular nodal precession frequency. Therefore, $\eta$ has a minimum value at
-late times. This does not affect the methodology of our analysis, but has some
-small effects on our detailed results: (i) the adiabaticity criterion must be
-modified slightly as $\rdil{\ln \eta}{t}$ is no longer constant but asymptotes
-to zero as $\eta$ decreases, (ii) the planet may never undergo separatrix
-crossing if their $\eta_{\star}$ (which depends on $\theta_{\rm sd, i}$) in the
-absence of the companions is too small, and (iii) the planetary obliquities will
-oscillate even when the disk has fully evaporated (as $\uv{l}$ is no longer
-constant). An interesting consequence of (ii) is that an outer planet may
-experience separatrix crossing before an inner planet does. The dynamics can be
-even more complex if the two planets are in mean motion resonance
+\textcolor{Corr}{Concerning the production of planetary obliquity with a
+dissipating disk, when there are multiple planets in a system, the nodal
+precession rate $g$ for the planet of interest never decays below the
+Laplace-Lagrange rate driven by planet-planet secular interactions
+\citep{millholland_disk}. Therefore, $\eta$ has a minimum value at late times.
+This does not affect the methodology of our analysis, but can affect the
+detailed results. For example, the adiabaticity criterion must be modified
+slightly as $\rdil{\ln \eta}{t}$ is no longer constant but asymptotes to zero as
+$\eta$ decreases; the planet may never undergo separatrix crossing if their
+$\eta_{\star}$ (which depends on $\theta_{\rm sd, i}$) in the absence of the
+companions is too small; the planetary obliquity will oscillate even when the
+disk has fully evaporated (as $\uv{l}$ is no longer constant). The spin dynamics
+can be even more complex if the two planets are in mean motion resonance
 \citep[e.g.][]{millholland2019obliquity}.}
@@
 
-We thank \textcolor{Corr}{the anonymous reviewer for their detailed and
-insightful comments that improved this work and} Kassandra Anderson for
-discussion and assistance in the early phase of this work. DL thanks the Dept.\
-of Astronomy and the Miller Institute for Basic Science at UC Berkeley for
-hospitality while part of this work was carried out. This work has been
-supported in part by the NSF grant AST-17152 and NASA grant 80NSSC19K0444. YS is
-supported by the NASA FINESST grant 19-ASTRO19-0041.% chktex 8
+We thank \textcolor{Corr}{the anonymous reviewer for detailed comments that
+improved this work and} Kassandra Anderson for discussion and assistance in the
+early phase of this work. DL thanks the Dept.\ of Astronomy and the Miller
+Institute for Basic Science at UC Berkeley for hospitality while part of this
+work was carried out. This work has been supported in part by the NSF grant
+AST-17152 and NASA grant 80NSSC19K0444. YS is supported by the NASA FINESST
+grant 19-ASTRO19-0041.% chktex 8
 

### 2020-08-18 writeups/Su_weak_tides.tex
done response

@@
 % unify 3 & 4, choose consistent q/cos q
-    \documentclass[
-        fleqn,
-        usenatbib,
-        referee,
-    ]{mnras}
+    \documentclass[twocolumn]{aastex63}
     \usepackage{
@@
         booktabs,
-        caption,
-        subcaption,
     }
     \usepackage[T1]{fontenc}
-    \captionsetup{compatibility=false}
 
@@
     \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
+    \newcommand*{\rdil}[2]{\mathrm{d}#1 / \mathrm{d}#2}
+    \newcommand*{\pdil}[2]{\partial#1 / \partial#2}
     \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
@@
     \newcommand*{\ev}[1]{\langle#1\rangle}
-    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
+    \newcommand*{\bsmb}[1]{\boldsymbol{\mathbf{#1}}}
+    \newcommand*{\uv}[1]{\hat{\bsmb{#1}}}
     \newcommand*{\p}[1]{\left(#1\right)}
@@
 
-\title[Analytical Exoplanet Obliquities]{Analytical Predictions of Explanet
-Obliquities Generated by Planet-Disk Interactions}
-\author[Y. Su and D. Lai]{
-Yubo Su$^1$,
-Dong Lai$^{1,2}$
-\\
-$^1$ Cornell Center for Astrophysics and Planetary Science, Department of
-Astronomy, Cornell University, Ithaca, NY 14853, USA
-\\
-$^2$ Tsung-Dao Lee Institute, 800 Dongchuan Road, Shanghai, 200240, China
-}
+    \newcommand\aastex{AAS\TeX}
+    \newcommand\latex{La\TeX}
 
-\date{Accepted XXX\@. Received YYY\@; in original form ZZZ}
+    \colorlet{Corr}{red}
+    \received{XXXX}
+    \revised{XXXX}
+    \accepted{XXXX}
+    \submitjournal{ApJ}
 
-\pubyear{2020}
+\shorttitle{Weak Tides and Cassini States}
+\shortauthors{Y.\ Su and D.\ Lai}
 
-\begin{document}\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
+\begin{document}
+
+\title{Dynamics of Colombo's Top: Tidal Dissipation and Resonance Capture}
+
+\correspondingauthor{Yubo Su}
+\email{yubosu@astro.cornell.edu}
+
+\author[0000-0001-8283-3425]{Yubo Su}% chktex 8
+\affiliation{Cornell Center for Astrophysics and Planetary Science, Department
+of Astronomy, Cornell University, Ithaca, NY 14853, USA}
+
+\author[0000-0002-1934-6250]{Dong Lai}% chktex 8
+\affiliation{Cornell Center for Astrophysics and Planetary Science, Department
+of Astronomy, Cornell University, Ithaca, NY 14853, USA}
 
@@
 
-\begin{keywords}
-planet--star interactions % chktex 8
-\end{keywords}
+\keywords{planet---star interactions}
 
@@
 \section{Theory and Equations}\label{s:theory}
+
+In this section, we first briefly lay out the spin dynamics of the planet,
+introducing the Cassini State spin-orbit resonance \citep[for more details,
+see][]{su2020}. We then introduce the equilibrium tide model of weak tidal
+friction used in this work, though much of our analysis does not depend on the
+detailed tidal model used.
+
+\subsection{Spin Dynamics Without Tidal Friction}\label{ss:theory_spin}
 
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/99_misc/2_cs_locs.png}
+    \includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs.png}
     \caption{CS locations, TODO change axis labels etc.}\label{fig:cs_locs}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/0_eta/1contours.png}
+    \includegraphics[width=\columnwidth]{../initial/0_eta/1contours.png}
     \caption{TODO label $\mathcal{C}_{\pm}$.}\label{fig:1contours}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/2quiver0_2.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/2quiver0_2.png}
     \caption{Phase portrait.}\label{fig:quiver}
 \end{figure}
+Note that the semimajor axis $a$ is not constant, but $\dot{a} / \dot{\theta}
+\sim S / L \ll 1$, and is negligible for our problem (but not always,
+Millholland tidal runaway cite).
 
@@
 Generally, these EOM have equilibria at the points that are both a CS and
-satisfy $\dot{s} = 0$ under weak tidal friction. These are stable as $\epsilon
-\to 0$, see Appendix~\ref{app:cs_stab}. On Fig.~\ref{fig:quiver}, these are the
+satisfy $\dot{s} = 0$ under weak tidal friction. These are stable when ignoring
+tidal friction \citep{su2020}. On Fig.~\ref{fig:quiver}, these are the
 intersection of the locations of CS1 and CS2 with the line $\dot{s} = 0$. It is
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/6equils0_06.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils0_06.png}
     \caption{Location of tCE\@. Vertical line is spin rate below which tCE is
@@
 outcomes. We generate initial spin vectors $\hat{s}$ for isotropic initial
-distribution $\p{\cos \theta, \phi}$, and marginalize over $\phi$ (which
-generally cannot be fixed by any formation mechanism) in histograms. This gives
-histograms in Figs.~\ref{fig:Hhists_0_06,fig:Hhists_0_20,fig:Hhists_0_70}
+distribution $\p{\cos \theta, \phi}$, and average over $\phi$ in histograms.
+This gives histograms in
+Figs.~\ref{fig:Hhists_0_06,fig:Hhists_0_20,fig:Hhists_0_70}
 \begin{figure}
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
     \caption{$s_c = 0.06$. Note that it is difficult to reach
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
     \caption{$s_c = 0.2$. Note that tCE2 is both reached with substantial
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_60_5.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_60_5.png}
     \caption{$s_c = 0.6$. Note that tCE2 becomes attracting over tCE1, but will
@@
 
-The governing mechanism for these probabilities is probabilistic separatrix
-crossing, which is covered in Appendix~\ref{app:probs}. The calculation is
-difficult analytically, but can be performed semi-analytically (describe
-procedure here, calculate $\eta_{\star}$ numerically etc.). The agreement of
-this curve with the histograms is examined for the same three $s_c$ values
-in Figs.~\ref{fig:pc_fits_0_06,fig:pc_fits_0_20,fig:pc_fits_0_70}.
+Similarly to \citet{su2020}, these probabilities are the result of separatrix
+crossings. However, the calculation differs from \citet{su2020}: since the
+perturbation is dissipative in phase space (i.e.\ it does not conserve phase
+space area), analysis following \citet{henrard1982} is not sufficient. A more
+general theory of separatrix crossing indeed lets us semi-analytically calculate
+the outcome probabilities. Appendix~\ref{app:probs} gives a more thorough
+overview of separatrix crossing dynamics, but the key result is:
+\begin{equation}
+    a^2 + b^2 = c^2.
+\end{equation}
+We can apply this curve to calculate the likelihood of the tCEs when a
+particular trajectory encounters the separatrix, and from this obtain a
+semi-analytical prediction of the distribution of outcomes. The semi-analytical
+nature of this calculation arises because $\eta_\star$ cannot be calculated
+\emph{a priori}. The agreement of this curve with the histograms is examined for
+the same three $s_c$ values in
+Figs.~\ref{fig:pc_fits_0_06,fig:pc_fits_0_20,fig:pc_fits_0_70}.
 \begin{figure}
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_06_5.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_06_5.png}
     \caption{$s_c = 0.06$ prediction vs histogram.}\label{fig:pc_fits_0_06}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_20_5.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_20_5.png}
     \caption{$s_c = 0.20$ prediction vs histogram.}\label{fig:pc_fits_0_20}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_70_5.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_70_5.png}
     \caption{$s_c = 0.70$ prediction vs histogram.}\label{fig:pc_fits_0_70}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5probs_5.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5probs_5.png}
     \caption{Top: total probability of ending up in tCE2 (blue dots) and the
@@
 
-\bibliographystyle{mnras}
-\bibliography{Su_sep_cross}
+\bibliography{Su_weak_tides}
+\bibliographystyle{aasjournal}
 
 \appendix
-\section{Proof of Stability of Cassini States 1 \& 2}\label{app:cs_stab}
-
-Insert here.
 
@@
 
-\bsp
-\label{lastpage} % chktex 24
 \end{document}

### 2020-09-03 writeups/Su_disk_disp.tex
rm bad footnote per ref request

@@
 and ``non-adiabatic'' evolution. We calibrate these analytical results with
-numerical calculations. \textcolor{Corr}{ On the technical side, our paper
+numerical calculations. On the technical side, our paper
 extends previous works \citep[such as][]{henrard1982, henrard1987,
@@
 adiabatic resonance advection'' to fully capture the dynamics in the
-non-adiabatic limit.}
+non-adiabatic limit.
 
@@
 from $\uv{s}$. The equations of motion for $\uv{s}$ and $\uv{l}$ in this limit
-are \textcolor{Corr}{\citep{anderson2018teeter}}
+are \citep{anderson2018teeter}
 \begin{align}
@@
 0.25$ and $k_{qp}\simeq 0.17$ \citep[e.g.][]{lainey2016quantification}].
-\textcolor{Corr}{In other studies, $3k_{\rm qp} / 2 k_{\rm p}$ is often notated
-as $k_2 / 2C$ \citep[e.g.][]{millholland_disk}}. In Eq.~\eqref{eq:wld}, $n
+In other studies, $3k_{\rm qp} / 2 k_{\rm p}$ is often notated
+as $k_2 / 2C$ \citep[e.g.][]{millholland_disk}. In Eq.~\eqref{eq:wld}, $n
 \equiv \sqrt{GM_\star/a_{\rm p}^3}$ is the planet's orbital mean motion, and we
@@
     \caption{Level curves of $\mathcal{H}\p{\phi, \cos \theta}$
-    [Eq.~\eqref{eq:H}] \textcolor{Corr}{for $I = 5^\circ$}, where warmer colors
+    [Eq.~\eqref{eq:H}] for $I = 5^\circ$, where warmer colors
     denote more positive values. The black solid line is the separatrix, which
@@
 \end{subequations}
-\textcolor{Corr}{then the areas for $\eta < \eta_{\rm c}$ are given by
-\citep{ward2004I}}
+then the areas for $\eta < \eta_{\rm c}$ are given by
+\citep{ward2004I}
 \begin{subequations}\label{se:area_ward}
@@
     $\mathcal{A}_{\rm j}(\eta) / 4\pi$ as given by Eqs.~\eqref{se:area_ward}
-    \textcolor{Corr}{for $I = 5^\circ$}. The colored dotted lines correspond to
+    for $I = 5^\circ$. The colored dotted lines correspond to
     small $\eta$ approximations used in Appendix~\ref{s:ad_approx}. The colored
@@
     evolving from initial $\eta_{\rm i} \gg 1$ to $\eta_{\rm f} \ll 1$,
-    \textcolor{Corr}{for $I = 5^\circ$}. The blue dots are results of numerical
+    for $I = 5^\circ$. The blue dots are results of numerical
     calculations (Section~\ref{ss:ad_ensemble}), and the colored tracks are
@@
 \end{equation}
-\textcolor{Corr}{Note that $A$ can be negative when $\rdil{\phi}{t} < 0$, unlike
+Note that $A$ can be negative when $\rdil{\phi}{t} < 0$, unlike
 the unsigned areas $\mathcal{A}_{\rm i}$ [Eqs.~\eqref{se:area_ward}] which are
-positive by definition.} This definition
+positive by definition. This definition
 of $A$ has two advantages: (i) it is continuous across transitions from
@@
 When a trajectory experiences separatrix crossing, it transitions into nearby
-zones probabilistically. This process is studied \textcolor{Corr}{in the
-adiabatic limit} by \citet{henrard1982} and \citet{henrard1987}. Their results
+zones probabilistically. This process is studied in the
+adiabatic limit by \citet{henrard1982} and \citet{henrard1987}. Their results
 may be summarized as follows: if zone $i$ is shrinking while adjacent zones $j,
 k$ are expanding such that the sum of their areas is constant, the probabilities
-of transition from zone $i$ to zones $j$ and $k$ are given by\footnote{
-\textcolor{Corr}{Interestingly, the probabilistic nature of separatrix crossing
-is not because the outcome depends on the phase $\phi$ of the system at
-crossing. Instead, the transition the system takes is determined by the value of
-$H$ at the start of a separatrix-crossing orbit \citep{henrard1982}. Since $H$
-only changes by $\propto \epsilon$ over a circulation/libration cycle, an order
-$\sim \epsilon$ change to the initial condition affects the final outcome. As
-such, as $\epsilon \to 0$, the outcome effectively becomes probabilistic.}}
+of transition from zone $i$ to zones $j$ and $k$ are given by
 \begin{subequations}\label{eq:henrard_hop}
@@
 sensitive to the \emph{phase} of the libration/circulation cycle at the
-crossing \textcolor{Corr}{(as noted in Section~3.2.2, the phase does not affect
-separatrix crossing in the adiabatic limit)}: if the trajectory crosses the
-separatrix when the obliquity is at its maximum, the final obliquity will also
-be relatively larger.
+crossing: if the trajectory crosses the separatrix when the obliquity is at its
+maximum, the final obliquity will also be relatively larger.
 
@@
 similar phases evolve to similar final obliquities that only depend weakly on
-on $\theta_{\rm sd, i}$. \textcolor{Corr}{Finally, in
+on $\theta_{\rm sd, i}$. Finally, in
 Fig.~\ref{fig:3_ensemble_05_15}, the bottom edge of the data and the III $\to$ I
@@
 tracks computed in Section~\ref{s:ad} assume that $\eta$ is constant throughout
-the separatrix-crossing orbit.}
+the separatrix-crossing orbit.
 
@@
 obliquity, so the range of obliquities at the end of phase (i) is frozen in as
-the range of final obliquities. \textcolor{Corr}{We refer to this two-phase
-evolution as \emph{partial adiabatic resonance advection}.}
+the range of final obliquities. We refer to this two-phase
+evolution as \emph{partial adiabatic resonance advection}.
 
@@
         of $\theta_{\rm f}$ for nonzero $\theta_{\rm sd, i}$ (see
-        Fig.~\ref{fig:ad_ensemble}). We \textcolor{Corr}{show for the first time
-        that} both the final $\theta_{\rm f}$ values and the probabilities of
-        achieving each value \textcolor{Corr}{can be understood analytically}
+        Fig.~\ref{fig:ad_ensemble}). We show for the first time
+        that both the final $\theta_{\rm f}$ values and the probabilities of
+        achieving each value can be understood analytically
         via careful accounting of adiabatic invariance and separatrix crossing
@@
         final obliquities can be reached for a given $\theta_{\rm sd, i}$ (see
-        Fig.~\ref{fig:nonad_3_ensemble}). We \textcolor{Corr}{understand this
+        Fig.~\ref{fig:nonad_3_ensemble}). We understand this
         result via the novel concept of partial adiabatic resonance advection
-        and} provide an analytical expression of the bounds on $\theta_{\rm f}$
+        and provide an analytical expression of the bounds on $\theta_{\rm f}$
         in Eq.~\eqref{eq:nonad_q_f_dist}.
@@
 
-\textcolor{Corr}{Concerning the production of planetary obliquity with a
+Concerning the production of planetary obliquity with a
 dissipating disk, when there are multiple planets in a system, the nodal
@@
 can be even more complex if the two planets are in mean motion resonance
-\citep[e.g.][]{millholland2019obliquity}.}
+\citep[e.g.][]{millholland2019obliquity}.
 
@@
 
-We thank \textcolor{Corr}{the anonymous reviewer for detailed comments that
-improved this work and} Kassandra Anderson for discussion and assistance in the
+We thank the anonymous reviewer for detailed comments that
+improved this work and Kassandra Anderson for discussion and assistance in the
 early phase of this work. DL thanks the Dept.\ of Astronomy and the Miller

### 2021-01-10 writeups/Su_weak_tides.tex
rm bad footnote per ref request
stash beginning work on weak tides

@@
 
+    \newcommand*{\uv}[1]{\hat{\bsmb{#1}}}
     \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
@@
     \newcommand*{\bsmb}[1]{\boldsymbol{\mathbf{#1}}}
-    \newcommand*{\uv}[1]{\hat{\bsmb{#1}}}
     \newcommand*{\p}[1]{\left(#1\right)}
@@
 
-Separatrix crossing was studied by \citep{henrard1982}.
+\begin{itemize}
+    \item Studying planetary obliquities is important. Cassini States are key.
+
+    \item In CS, resonance when two frequencies $g$ and $\alpha \cos \theta$
+        become commensurate, $g \simeq \alpha \cos \theta$, where $\theta$ is
+        the planetary obliquity.
+
+    \item Many works consider entry into a CS by having $g$ or $\alpha$ vary
+        over time to effect resonance capture \citep[e.g.][]{anderson2018teeter,
+        millholland_disk, su2020, anderson2020excitation}. However, a third
+        possibility exists: $\theta$ can evolve and sweep through a resonance,
+        e.g.\ under tidal friction.
+
+    \item Resonance capture via separatrix crossing was first considered by
+        \citep{henrard1982} for non-dissipative perturbations
+        \citep[e.g.][]{su2020}. However, tidal friction is dissipative, so this
+        formalism does not apply. We show that this generalizes.
+\end{itemize}
 
@@
 see][]{su2020}. We then introduce the equilibrium tide model of weak tidal
-friction used in this work, though much of our analysis does not depend on the
-detailed tidal model used.
+friction used in this work \citep{lai2012}. While there are many models of tidal
+dissipation that may be more accurate (e.g. CITE), our qualitative conclusions
+do not depend on the specific model used, so we use the equilibrium tide model
+for simplicity.
 
@@
 
-We study an oblate planet orbiting around a star hosting a further out planet.
-The equations of motion in the absence of dissipation are:
+We consider a star of mass $M_\star$ hosting an inner oblate planet of mass $m$
+and radius $R$ with semi-major axis $a$ and an outer planet of mass $m_{\rm p}$
+with semi-major axis $a_{\rm p}$ and eccentricity $e_{\rm p}$. Let the inner
+planet be spinning with spin $\bsmb{s}$ (with $s \equiv \abs{\bsmb{s}}$ the spin
+angular velocity and $\uv{s}$ the spin orientation), and call the unit angular
+momenta of the inner and outer planets' orbits $\uv{l}$ and $\uv{l}_{\rm p}$
+respectively. The equations of motion in the absence of tidal friction are:
 \begin{align}
-    \rd{\hat{s}}{t}
-        &= \omega_{s1}\p{\hat{s} \cdot \hat{l}_1}\p{\hat{s} \times \hat{l}_1}
-            - \omega_{1p}\cos I\p{\hat{s} \times \hat{l}_p},\\
-    \omega_{s1} &= \frac{3k_q}{2k}\frac{M_*}{m_1}\p{\frac{R_1}{a_1}}^3 s,\\
-    \omega_{1p} &= \frac{3m_p}{4m_*}\p{\frac{a_1}{a_p\sqrt{1 - e_p^2}}}^3 \Omega_1.
+    \rd{\uv{s}}{t}
+        &= \omega_{\rm sl}\p{\uv{s} \cdot \uv{l}}\p{\uv{s} \times \uv{l}}
+            - \omega_{\rm lp}\cos I\p{\uv{s} \times \uv{l}_{\rm p}},\\
+    \omega_{\rm sl} &\equiv \frac{3GJ_2 mR^2 M_\star}{2a^3 I\Omega}
+        = \frac{3k_q}{2k}\frac{M_\star}{m}\p{\frac{R}{a}}^3 s,
+            \label{eq:wsl}\\
+    \omega_{\rm lp} &= \frac{3m_p}{4M_\star}\p{\frac{a}{a_{\rm p}\sqrt{1 -
+            e_{\rm p}^2}}}^3 n.\label{eq:wlp}
 \end{align}
+In Eq.~\eqref{eq:wsl}, $I = k mR^2$ (with $k$ a constant) is the moment of
+inertia and $J_2=k_{\rm q}s^2 (R^3/Gm)$ (with $k_{q}$ a constant) the
+rotation-induced (dimensionless) quadrupole of the planet [for a body with
+uniform density, $k=0.4, k_{q}=0.5$; for rocky planets, $k\simeq 0.2$ and
+$k_{qp}\simeq 0.17$ \citep[e.g.][]{lainey2016quantification} \textcolor{Corr}{?
+not sure}]. In other studies, $3k_{\rm qp} / 2 k_{\rm p}$ is often notated as
+$k_2 / 2C$ \citep[e.g.][]{millholland_disk}. In Eq.~\eqref{eq:wlp}, $n \equiv
+\sqrt{GM_\star/a^3}$ is the inner planet's orbital mean motion, and we have
+assumed $a_{\rm p}\gg a$ and included only the leading-order (quadrupole)
+interaction between the planet and disk. Following standard notation, we define
+$\alpha = \omega_{\rm sl}$ and $g \equiv -\omega_{\rm 1p} \cos I$
+\citep[e.g.][]{colombo1966}.
 
-We define $s_c$ to be the critical spin where the precession frequencies
-$\omega_{s1}$ and $\omega_{1p}$ are equal, or
+We define $s_{\rm c}$ to be the critical spin where
 \begin{equation}
-    \at{\omega_{s1}}_{s = s_c} = \omega_{1p}\cos I.
+    \at{\alpha}_{s = s_{\rm c}} = -g.
 \end{equation}
-rhroughout this paper, we often set the orbital frequency of the inner planet
-$\Omega_1 = 1$.
 
@@
 \begin{equation}
-    \eta \equiv -\frac{g}{\alpha} = s_c / s.
+    \eta \equiv -\frac{g}{\alpha} = \frac{s_{\rm c}}{s}.
 \end{equation}
 
-Plots of CS locations as always in \autoref{fig:cs_locs}.
+Plots of CS locations as always in Fig.~\ref{fig:cs_locs}.
 \begin{figure}
@@
 Note that $\phi$ is conjugate to $\cos \theta$, and thus the spin dynamics
-exhibit Hamiltonian:
+obey Hamiltonian:
 \begin{equation}
-    H(\mu, \phi; s) = -\frac{s}{s_c}\frac{\mu^2}{2}
+    H(\mu, \phi; s) = -\frac{s}{s_{\rm c}}\frac{\mu^2}{2}
         + \mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi.
@@
 Plot of level curves of Hamiltonian as before, including $\mathcal{C}_{\pm}$
-notation in \autoref{fig:1contours}.
+notation in Fig.~\ref{fig:1contours}.
 \begin{figure}
@@
 
-We use the weak tidal friction model \citep{lai2012}. The EOM for $\theta, s$
-become:
+We implement the weak friction theory of equilibrium tides \citep{lai2012},
+under which both $\theta$ and $s$ evolve. We define the dimensionless time
+\begin{equation}
+    \tau \equiv gt.
+\end{equation}
+The full equations of motion including weak tidal friction are then
 \begin{align}
-    \rd{\hat{s}}{\tau}
-        &= \frac{s}{s_c}\p{\hat{s} \cdot \hat{l}_1}\p{\hat{s} \times
-                \hat{l}_1} - \hat{s} \times \hat{l}_p
-            + \frac{\epsilon 2\Omega_1}{s}
-                \p{1 - \frac{s}{2\Omega_1}\p{\hat{l}_1 \cdot \hat{s}}}
-                    \hat{s} \times \p{\hat{l}_1 \times \hat{s}},\\
+    \rd{\uv{s}}{\tau}
+        ={}& \frac{s}{s_c}\p{\uv{s} \cdot \uv{l}}\p{\uv{s} \times
+                \uv{l}} - \uv{s} \times \uv{l}_{\rm p}\nonumber\\
+            &+ \frac{\epsilon 2n}{s}
+                \p{1 - \frac{s}{2n}\p{\uv{l} \cdot \uv{s}}}
+                    \uv{s} \times \p{\uv{l} \times \uv{s}},\\
     \rd{s}{\tau}
-        &= \epsilon 2\Omega_1 \p{\hat{s} \cdot \hat{l}_1 -
-            \frac{s}{2\Omega_1}\p{1 + \p{\hat{s} \cdot \hat{l}_1}^2}}.
+        ={}& \epsilon 2n \p{\uv{s} \cdot \uv{l} -
+            \frac{s}{2n}\p{1 + \p{\uv{s} \cdot \uv{l}}^2}},
 \end{align}
+where $\epsilon$ measures the tidal dissipation rate and is given by
+\begin{align}
+    \epsilon &\equiv -\frac{1}{gt_a}\frac{L}{2S} \frac{s}{2n},\\
+    \frac{1}{t_a} &= \frac{3k_2}{Q}\p{\frac{m}{M}}\p{\frac{R}{a}}^5 n.
+\end{align}
+Here, $L$ and $S$ are the orbital and spin angular momenta of the inner planet,
+respectively.
 
@@
 
-As a result of \autoref{ss:tidal_eqs}, the tCE are the only possible final
+As a result of Section~\ref{ss:tidal_eqs}, the tCE are the only possible final
 outcomes. We generate initial spin vectors $\hat{s}$ for isotropic initial
@@
 space area), analysis following \citet{henrard1982} is not sufficient. A more
-general theory of separatrix crossing indeed lets us semi-analytically calculate
-the outcome probabilities. Appendix~\ref{app:probs} gives a more thorough
-overview of separatrix crossing dynamics, but the key result is:
+general theory of separatrix crossing is still able to predict the outcome
+probabilities. Appendix~\ref{app:probs} gives a more thorough overview of
+separatrix crossing dynamics, but the key result is:
 \begin{equation}
@@
 convolved against the $P_{tCE2}\p{\theta_i}$ distributions shown in
-\autoref{ss:q_dist}.
+Section~\ref{ss:q_dist}.
 

### 2021-04-19 writeups/Su_weak_tides.tex
stash 0419

--- 2020-02-20 writeups/Su_weak_tides.tex
@@
 % unify 3 & 4, choose consistent q/cos q
+
+% S2: CS stability
+% S3: How to reach CS
+% S3: toy problem, affords analytical understanding
+% S4: full problem
+% Discussion/conclusion: maybe 0.05 AU + SE? does this still work?
     \documentclass[
@@
         newtxmath,
+        ae, aecompl,
         graphicx,
-        ae, aecompl,
         booktabs,
-        caption,
-        subcaption,
+        xcolor,
     }
-    \usepackage[T1]{fontenc}
-    \captionsetup{compatibility=false}
 
+    \newcommand*{\scinot}[2]{#1\times10^{#2}}
     \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
@@
     \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
-    \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
+    \newcommand*{\ptd}[2]{\frac{\partial^2#1}{\partial#2^2}}
+    % inline
+    \newcommand*{\mdil}[2]{\mathrm{D}#1/\mathrm{D}#2}
+    \newcommand*{\pdil}[2]{\partial#1/\partial#2}
+    \newcommand*{\rdil}[2]{\mathrm{d}#1/\mathrm{d}#2}
     \newcommand*{\at}[1]{\left.#1\right|}
     \newcommand*{\abs}[1]{\left|#1\right|}
-    \newcommand*{\ev}[1]{\langle#1\rangle}
-    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
+    \newcommand*{\ev}[1]{\left\langle#1\right\rangle}
     \newcommand*{\p}[1]{\left(#1\right)}
@@
     \newcommand*{\z}[1]{\left\{#1\right\}}
-    \DeclareMathOperator*{\argmin}{argmin}
-    \DeclareMathOperator*{\argmax}{argmax}
+    \newcommand*{\bm}[1]{\mathbf{#1}}
+    \newcommand*{\uv}[1]{\hat{\mathbf{#1}}}
+    \newcommand*{\md}[0]{\mathrm{d}}
     \DeclareMathOperator*{\med}{med}
+    \DeclareMathOperator*{\erf}{erf}
 
-\title[Analytical Exoplanet Obliquities]{Analytical Predictions of Explanet
-Obliquities Generated by Planet-Disk Interactions}
-\author[Y. Su and D. Lai]{
-Yubo Su$^1$,
+\title[Weak Tides and Cassini States]{Dynamics of Colombo's Top: Tidal
+Dissipation and Resonance Capture}
+\author[Y. Su and D. Lai.]{
+Yubo Su,$^1$\thanks{E-mail: yubosu@astro.cornell.edu},
 Dong Lai$^{1,2}$
@@
 $^1$ Cornell Center for Astrophysics and Planetary Science, Department of
-Astronomy, Cornell University, Ithaca, NY 14853, USA
-\\
-$^2$ Tsung-Dao Lee Institute, 800 Dongchuan Road, Shanghai, 200240, China
+Astronomy, Cornell University, Ithaca, NY 14853, USA\\
+$^2$ Tsung-Dao Lee Institute \& School of Physics and Astronomy, Shanghai Jiao
+Tong University, 200240 Shanghai, China
 }
@@
 
-\pubyear{2020}
+\pubyear{2021}
 
@@
 \begin{keywords}
-planet--star interactions % chktex 8
+planet-star interactions
 \end{keywords}
@@
 
-Separatrix crossing was studied by \citep{henrard1982}.
+\begin{itemize}
+    \item Studying planetary obliquities (define) is important. Cassini States
+        are key. More introduction.
 
-\section{Theory and Equations}\label{s:theory}
+    \item Resonance capture via separatrix crossing was first considered by
+        \citep{henrard1982} for non-dissipative perturbations
+        \citep[e.g.][]{su2020}. However, tidal friction is dissipative, so this
+        formalism does not apply. We generalize this calculation and show that
+        it reproduces results.
+\end{itemize}
 
-We study an oblate planet orbiting around a star hosting a further out planet.
-The equations of motion in the absence of dissipation are:
+In Section XXX\dots
+
+\section{Spin Evolution Equations and Cassini States: Review}\label{s:theory}
+
+In this section, we first briefly lay out the spin dynamics of the planet,
+introducing the Cassini State spin-orbit resonance \citep[for more details,
+see][]{su2020}. We then introduce the weak friction theory of equilibrium tides
+used in this work \citep{lai2012}. While many different tidal effects may
+dominate in different planetary systems, our qualitative conclusions do not
+depend on the specific form of the tidal dissipation, so we use the classic weak
+friction theory for simplicity.
+
+\subsection{Spin Dynamics in the Absence of Tides}\label{ss:theory_spin}
+
+\subsubsection{Equations of Motion}
+
+We consider a star of mass $M_\star$ hosting an inner oblate planet of mass $m$
+and radius $R$ on a circular orbit with semi-major axis $a$ and an outer
+perturber of mass $m_{\rm p}$ on a circular orbit with semi-major axis $a_{\rm
+p}$. We assume that the two orbits are mildly misaligned with mutual inclination
+$I$. Denote $\bm{S}$ the spin angular momentum and $\bm{L}$ the orbital angular
+momentum of the planet, and $\bm{L}_{\rm p}$ the angular momentum of the
+perturber. The corresponding unit vectors are $\uv{s} \equiv \bm{S} / S$,
+$\uv{l} \equiv \bm{L} / L$, and $\uv{l}_{\rm p} \equiv \bm{L}_{\rm p} / L_{\rm
+p}$. The spin axis $\uv{s}$ of the planet tends to precess around its orbital
+(angular momentum) axis $\uv{l}$, driven by the gravitational torque from the
+host star acting on the planet's rotational bulge. On the other hand, $\uv{l}$
+and the disk axis $\uv{l}_{\rm p}$ precess around each other due to
+gravitational interactions. We assume $S \ll L \ll L_{\rm p}$, so $\uv{l}_{\rm
+p}$ and $\uv{l}$ are nearly constant. The equations of motion for $\uv{s}$ and
+$\uv{l}$ in this limit are \citep{anderson2018teeter, su2020}
 \begin{align}
-    \rd{\hat{s}}{t}
-        &= \omega_{s1}\p{\hat{s} \cdot \hat{l}_1}\p{\hat{s} \times \hat{l}_1}
-            - \omega_{1p}\cos I\p{\hat{s} \times \hat{l}_p},\\
-    \omega_{s1} &= \frac{3k_q}{2k}\frac{M_*}{m_1}\p{\frac{R_1}{a_1}}^3 s,\\
-    \omega_{1p} &= \frac{3m_p}{4m_*}\p{\frac{a_1}{a_p\sqrt{1 - e_p^2}}}^3 \Omega_1.
+    \rd{\uv{s}}{t}
+        &= \omega_{\rm sl}\p{\uv{s} \cdot \uv{l}}\p{\uv{s} \times \uv{l}}
+        \equiv \alpha\p{\uv{s} \cdot \uv{l}}\p{\uv{s} \times
+        \uv{l}},\label{eq:dsdt1}\\
+    \rd{\uv{l}}{t} &= \omega_{\rm lp}\p{\uv{l} \cdot \uv{l}_{\rm p}}\p{\uv{l}
+        \times \uv{l}_{\rm p}} \equiv -g\p{\uv{l} \times \uv{l}_{\rm p}},
+        \label{eq:dldt1}
+\end{align}
+where
+\begin{align}
+    \omega_{\rm sl} &\equiv \frac{3GJ_2 mR^2 M_\star}{2a^3 I\Omega_{\rm s}}
+        = \frac{3k_q}{2k}\frac{M_\star}{m}\p{\frac{R}{a}}^3 \Omega_{\rm s},
+            \label{eq:wsl}\\
+    \omega_{\rm lp} &= \frac{3m_p}{4M_\star}\p{\frac{a}{a_{\rm p}}}^3
+        n.\label{eq:wlp}
+\end{align}
+In Eq.~\eqref{eq:wsl}, $\Omega_{\rm s}$ is the spin frequency of the inner
+planet, $I = k mR^2$ (with $k$ a constant) is its moment of inertia and $J_2 =
+k_{\rm q}\Omega_{\rm s}^2 (R^3/Gm)$ (with $k_{q}$ a constant) is its rotation-induced
+(dimensionless) quadrupole moment [for a body with uniform density, $k=0.4,
+k_{\rm q}=0.5$; for rocky planets, $k\simeq 0.2$ and $k_{\rm q}\simeq 0.17$
+\citep[e.g.][]{lainey2016quantification} \textcolor{red}{? not sure}]. In other
+studies, $3k_{\rm q} / 2 k$ is often notated as $k_2 / 2C$
+\citep[e.g.][]{millholland_disk}. In Eq.~\eqref{eq:wlp}, $n \equiv
+\sqrt{GM_\star/a^3}$ is the inner planet's orbital mean motion,  and we have
+assumed $a_{\rm p}\gg a$ and included only the leading-order (quadrupole)
+interaction between the inner planet and perturber. Following standard notation,
+we define $\alpha = \omega_{\rm sl}$ and $g \equiv -\omega_{\rm 1p} \cos I$
+\citep[e.g.][]{colombo1966}.
+
+As in \citet{su2020}, we combine Eqs.~(\ref{eq:dsdt1}--\ref{eq:dldt1}) into a
+single equation by transforming into a frame rotating about $\uv{l}_{\rm p}$
+with frequency $g$. In this frame, $\uv{l}_{\rm p}$ and $\uv{l}$ are both fixed,
+and $\uv{s}$ evolves as:
+\begin{equation}
+    \p{\rd{\uv{s}}{t}}_{\rm rot}
+        = \alpha\p{\uv{s} \cdot \uv{l}}\p{\uv{s} \times \uv{l}}
+            + g\p{\uv{s} \times \uv{l}_{\rm p}}. \label{eq:dsdt_rot}
+\end{equation}
+In this reference frame, we choose the coordinate system such that $\uv{z} =
+\uv{l}$ and $\uv{l}_{\rm p}$ lies in the $\uv{x}$-$\uv{z}$ plane. We describe
+$\uv{s}$ in spherical coordinates using the polar angle $\theta$, the planet's
+obliquity, and $\phi$, the precessional phase of $\uv{s}$ about $\uv{l}$.
+
+The equilibria of Eq.~\eqref{eq:dsdt_rot} are referred to as \emph{Cassini
+States} \citep[CSs;][]{colombo1966, peale1969}. We follow the notation of
+\citet{su2020}, where the parameter
+\begin{equation}
+    \eta \equiv -\frac{g}{\alpha},\label{eq:def_eta}
+\end{equation}
+is used. For a given value of $\eta$, there can be either two or four CSs, all
+of which require $\uv{s}$ lie in the plane of $\uv{l}$ and $\uv{l}_{\rm p}$.
+Following the standard convention and nomenclature, CSs 1, 3, and 4 have $\phi =
+0$ and $\theta < 0$, while CS2 has $\phi = \pi$ and $\theta > 0$.
+Figure~\ref{fig:cs_locs} shows the CS obliquities as a function of $\eta$, each
+of which satisfies
+\begin{equation}
+    \sin \theta \cos \theta - \eta \sin\p{\theta - I} = 0.\label{eq:cs_zero}
+\end{equation}
+Note that there are four CSs when $\eta < \eta_{\rm c}$ and only two when $\eta
+> \eta_{\rm c}$, where
+\begin{equation}
+    \eta_{\rm c} \equiv \p{\sin^{2/3}\!I + \cos^{2/3}\!I}^{-3/2}.\label{eq:etac}
+\end{equation}
+\begin{figure}
+    \centering
+    %\includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs.png}
+    \caption{Cassini State obliquities $\theta$ as a function of $\eta \equiv
+    -g/\alpha$ (Eq.~\ref{eq:def_eta}) for $I = 5^\circ$. The vertical dashed
+    line denotes $\eta_{\rm c}$, where the number of Cassini States changes from
+    four to just two (Eq.~\ref{eq:etac}). The horizontal dashed line gives
+    $\theta = I$, the asymptotic value of Cassini State 2's obliquity when $\eta
+    \to \infty$.}\label{fig:cs_locs}
+\end{figure}
+
+The Hamiltonian corresponding to Eq.~\eqref{eq:dsdt_rot} is
+\begin{align}
+    H &= -\frac{\alpha}{2}\p{\uv{s} \cdot \uv{l}}^2
+            - g\p{\uv{s} \cdot \uv{l}_{\rm d}}\nonumber\\
+        &= -\frac{\alpha}{2} \cos^2\theta
+            - g\p{\cos\theta \cos I - \sin I \sin\theta \cos \phi}.\label{eq:H}
+\end{align}
+Here, $\cos \theta$ and $\phi$ form a canonically conjugate pair of variables.
+Figure~\ref{fig:1contours} shows the level curves of this Hamiltonian for $I =
+20^\circ$, for which $\eta_{\rm c} \approx 0.77$ (Eq.~\ref{eq:etac}). When $\eta
+< \eta_{\rm c}$, CS4 exists and is a saddle point. The two trajectories
+originating and ending at CS4 are the only two infinite-period orbits in the
+phase space. Together, these two critical trajectories are referred to as the
+\emph{separatrix} and divide phase space into three zones. Trajectories in zone
+II librate about CS2 while those in zones I and III circulate. On the other
+hand, when $\eta > \eta_{\rm c}$, all trajectories circulate. When the
+separatrix exists, we divide it into two curves: $\mathcal{C}_+$, the boundary
+between zones I and II, and $\mathcal{C}_-$, the boundary between zones II and
+III\@.
+\begin{figure}
+    \centering
+    %\includegraphics[width=\columnwidth]{../initial/0_eta/1contours.png}
+    \caption{Level curves of the Cassini State Hamiltonian (Eq.~\ref{eq:H}) for
+    $I = 5^\circ$, for which $\eta_{\rm c} \approx 0.77$ (Eq.~\ref{eq:etac}).
+    For $\eta < \eta_{\rm c}$, there are four Cassini States (labeled), while
+    for $\eta > \eta_{\rm c}$ there are only two. In the former case, the
+    existence of a \emph{separatrix} (solid black lines) separates phase space
+    into three numbered zones (I/II/III, labeled). Finally, we denote the upper
+    and lower legs of the separatrix by $\mathcal{C}_{\pm}$ respectively, as
+    shown in the upper two panels.}\label{fig:1contours}
+\end{figure}
+
+\section{Spin Evolution with Alignment Torque}\label{ss:toy_model}
+
+In this section, we consider a simplified model of equilibrium tides that
+isolates the important new phenomenon presented in this paper. We assume that
+the spin magnitude of the planet is constant, so $\alpha$ and $g$ are both
+fixed, while the spin orientation $\uv{s}$ experiences a torque that drives it
+towards alignment with $\uv{l}$ on the alignment timescale $t_{\rm s}$:
+\begin{equation}
+    \p{\rd{\uv{s}}{t}}_{\rm tide}
+        = \frac{1}{t_{\rm s}} \uv{s} \times \p{\uv{l} \times \uv{s}}.
+\end{equation}
+The full equations of motion for $\uv{s}$ in the coordinates $\theta$ and $\phi$
+can be written:
+\begin{align}
+    \rd{\theta}{t} &= -g\sin I \sin \phi - \frac{1}{t_{\rm s}} \sin \theta,
+        \label{eq:dqdt_toy}\\
+    \rd{\phi}{t} &= -\alpha \cos\theta
+        - g\p{\cos I + \sin I \cot \theta \cos \phi}.\label{eq:dfdt_toy}
 \end{align}
 
-We define $s_c$ to be the critical spin where the precession frequencies
-$\omega_{s1}$ and $\omega_{1p}$ are equal, or
+\subsection{Shifted Cassini States and Linear Stability
+Analysis}\label{ss:tidal_eqs}
+
+When $t_{\rm s}$ is finite, the CSs tilt out of the $\uv{l}$-$\uv{l}_{\rm p}$
+plane \citep[as was first pointed out for CS2 by][]{fabrycky_otides}. A simple
+expression for the degree of this tilt can be obtained by solving for $\phi_{\rm
+cs}$, the azimuthal angle of the modified CS, when setting Eq.~\eqref{eq:dqdt_toy} equal
+to zero. This gives
 \begin{equation}
-    \at{\omega_{s1}}_{s = s_c} = \omega_{1p}\cos I.
+    \sin \phi_{\rm cs} = \frac{\sin^2\theta_{\rm cs}}{\sin I \abs{g}t_{\rm s}}.
 \end{equation}
-rhroughout this paper, we often set the orbital frequency of the inner planet
-$\Omega_1 = 1$.
+Here, $\theta_{\rm cs}$ is the modified CS obliquity. Note that if $t_{\rm s}$
+is shorter than some critical value $t_{\rm s, c}$, which for a given CS is
+given by
+\begin{align}
+    t_{\rm s, c} &= \frac{\sin^2\theta_{\rm cs}}{\abs{g}\sin I},
+\end{align}
+then there are no solutions for $\phi_{\rm cs}$, and the CS is no longer a fixed
+point. This condition first breaks down for $\theta_{\rm cs} \approx 90^\circ$,
+i.e.\ for CS2 (and CS4) in the limit $\eta \ll 1$. Thus, as long as $t_{\rm s}
+\gtrsim \p{\abs{g}\sin I}^{-1}$, then all CSs will exist.
 
-\subsection{Cassini States}\label{ss:cs_theory}
+We next seek to characterize the stability of small perturbations about each of
+the CSs in the presence of the alignment torque. We can linearize
+Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) about a [modified] CS, yelding
+\begin{align}
+    \rd{}{\tau}\begin{bmatrix}
+        \theta\\ \phi
+    \end{bmatrix} &= \begin{bmatrix}
+        -\frac{\cos \theta}{t_{\rm s}} &
+        -g\sin I \cos \phi \\
+        \alpha \sin \theta + g\frac{\sin I \cos \phi}{\sin^2\theta} &
+        0
+    \end{bmatrix}_{\rm cs}\begin{bmatrix}
+        \Delta \theta \\ \Delta \phi
+    \end{bmatrix},\label{eq:dsdt_hessian}
+\end{align}
+where the cs subscript indicates evaluating at a CS, $\Delta \theta = \theta -
+\theta_{\rm cs}$, and the same for $\Delta \phi$. The eigenvalues $\lambda$ of
+Eq.~\eqref{eq:dsdt_hessian} satisfy the equation
+\begin{align}
+    0 &= \p{\lambda + \frac{\cos \theta_{\rm cs}}{t_{\rm s}}}\lambda - \lambda_0^2,\\
+    \lambda_0^2 &\equiv \p{\alpha
+        \sin \theta_{\rm cs} + g\sin I \csc^2\theta_{\rm cs}\cos \phi_{\rm cs}}
+            \p{- g \sin I \cos \phi_{\rm cs}},\\
+    \lambda &\approx -\frac{\cos \theta_{\rm cs}}{t_{\rm s}} \pm \sqrt{\lambda_0^2}.
+        \label{eq:lambda_approx}
+\end{align}
+The stability depends only on the real part of
+$\lambda$ in Eq.~\eqref{eq:lambda_approx}. If we assume that the torque-induced
+modification to $\phi_{\rm cs}$ is small, then $\lambda_0$ reduces to the
+product of the eigenvalues in the torque-free limit. In this limit, $\lambda_0^2
+< 0$ for each of CSs 1--3 and $\lambda_0^2 > 0$ for CS4 \citep[see Fig.~17
+of][]{su2020}. Thus, CS4 is always unstable, since there will always be a
+positive eigenvalue $\lambda$, while the stability of CSs 1--3 are solely
+determined by the sign of $\cos \theta_{\rm cs}$. From Fig.~\ref{fig:cs_locs},
+we see that CSs 1 and 2 are stable while CS3 is unstable under the alignment
+torque. These calculations justify results long used in CS literature
+\citep[e.g.][]{ward1975tidal}.
 
-Equilibria of spin dynamics are \emph{Cassini States} (CSs). Refer to Su \& Lai
-2020 for more detailed discussion. In the notation of the previous paper,
+\subsection{Spin Obliquity Evolution Driven by Alignment Torque}
+
+With the above results, we are equipped to ask the key question of this section:
+for a given initial $\theta_0$ and $\phi_0$, which of CS1 and CS2 does the
+system evolve into? For initial conditions in Zone I (see
+Fig.~\ref{fig:1contours}), an unperturbed trajectory circulates and returns to
+$(\theta_0, \phi_0 + 2\pi)$ after a single precession period. During this
+period, the effect of the dissipation is a negative $\theta'$ everywhere during
+the cycle. Thus, for initial conditions in Zone I, $\theta$ decreases until the
+trajectory has converged to CS1. This is intuitively reasonable, as CS1 is
+stable. For initial conditions in Zone II, an equivalent calculation to that in
+Section~\ref{sss:cs_stab2} shows that all trajectories converge to CS2.
+
+For illustrative purposes, we fix $\abs{g}t_{\rm s} = 10^{-3}$, and $\eta =
+-g / \alpha$ is varied among a few small values (small
+meaning much less than $\eta_{\rm c}$). We specialize to the case where $\eta
+< \eta_{\rm c}$ and there are four CSs.
+
+However, initial conditions in Zone III pose a puzzle. There are no stable CSs
+in Zone III, so the system must evolve through the separatrix to reach one of
+either CS1 or CS2. In Fig.~\ref{fig:toy_phop}, we find see that the outcome for
+initial conditions in Zone III is in fact \emph{probabilistic}. Intuitively,
+this can be understood as probabilistic resonance capture: since $\eta \ll
+\eta_{\rm c}$, $\alpha \gg -g$ (the spin-orbit precession rate,
+Eq.~\ref{eq:dsdt1}, and the orbit precession induced by the perturber,
+Eq.~\ref{eq:dldt1}, respectively), but $\alpha \cos \theta$ can become
+commensurate with $-g$ if $\cos \theta \sim \eta$. This is achieved as $\theta$
+evolves from an initially retrograde obliquity through $90^\circ$ towards
+$0^\circ$ under the influence of the dissipative term in
+Eq.~\eqref{eq:dqdt_toy}.
+\begin{figure}
+    \centering
+    %\includegraphics[width=\columnwidth]{../initial/0_eta/3stats3_5_0_2.png}
+    \caption{TODO generate a better plot. Ignore bottom two panels, top two
+    panels show which ICs end up in CS 1 (left) and CS2 (right). Probabilistic
+    behavior in Zone III is evident.}\label{fig:toy_phop}
+\end{figure}
+
+While similar in behavior to previous studies of probabilistic resonance capture
+\citep{henrard1982, su2020}, the mechanism at play here is necessarily
+different: here, the Hamiltonian and underlying phase structure is kept constant
+while a non-Hamiltonian, dissipative perturbation is introduced. The origin of
+this resonance crossing process is easy to visualize. In the absence of
+dissipative effects, the separatrix is both the set of points that flow into CS4
+and the set of points that flow away CS4, called the \emph{stable} and
+\emph{unstable} manifolds of the saddle point CS4 respectively \citep{g_and_h}.
+When the dissipative term is taken into account, these stable and unstable
+manifolds split and open a visible ``path'' from Zone III into both Zones I and
+II, as shown in Fig.~\ref{fig:toy_hop_manifolds}.
+\begin{figure}
+    \centering
+    %\includegraphics[width=\columnwidth]{../initial/0_eta/6manifolds0_05.png}
+    \caption{TODO overplot separatrix, remove bad labels, better legend. Stable
+    and unstable manifolds of CS4, showing how the separatrix splrits and gives
+    a ``path'' from Zone III into Zones I/II.}\label{fig:}
+\end{figure}
+
+The amount that the stable and unstable manifolds split can be calculated
+perturbatively using \emph{Melnikov's Method} \citep{g_and_h}. The essence of
+Melnikov's method lies at the heart of the perturbative approach used in
+Section~\ref{sss:cs_stab2}, where the evolution of $H$ along the perturbed
+trajectories can be evaluated by integration along their original
+\emph{unperturbed} trajectories. In particular: \textcolor{red}{TODO the rest of
+this section is copy pasted from notes without even notation changes, needs to
+be written up correctly} Now, let's reconsider the Melnikov integral when
+perturbing this finite (non-homoclinic orbit); this may no longer be an exact
+result but should give the correct scaling:
 \begin{equation}
-    \eta \equiv -\frac{g}{\alpha} = s_c / s.
+    M_c = \int\limits_0^T \pd{\phi}{t}\epsilon \p{1 - \mu^2}\;\mathrm{d}t.
+\end{equation}
+Naively, we might claim that, since $\pd{\phi}{t}$ changes signs halfway through
+the interval of integration, that the only surviving component is $2\epsilon
+\bar{\mu}\mu'$, where $\bar{\mu} = \mu_4$ is the average value of $\mu$ and
+$\mu'$ is the fluctuation. This gives
+\begin{equation}
+    M_c = 2\int\limits_0^{2\pi}2\epsilon \frac{\eta \cos I}{1 + \eta \sin I}
+        \sqrt{2\eta \sin I \p{1 - \cos \phi}}\;\mathrm{d}\phi.
+\end{equation}
+Note that $M_c \propto \eta^{3/2}$, and since the gap opened $\Delta_c =
+\frac{M_c}{\pd{\phi}{t}} \propto \eta$, it seems like we're on the right track.
+Specifically:
+\begin{align}
+    M_c &\approx \epsilon 2\eta \cos I A_{sep},\\
+    \Delta_c &\approx 2\epsilon \eta \cos I \p{16 \sqrt{\eta \sin I}}
+        \frac{1}{\sqrt{4\eta \sin I}},\\
+        &\approx 16\epsilon \eta \cos I.
+\end{align}
+This also agrees exceedingly well with our simulations This then gives us
+hopping probability
+\begin{equation}
+    P_{hop} = \frac{\Delta_c}{\Delta_M} \approx
+        \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi}.
+\end{equation}
+This agrees perfectly with the cases we've run.
+
+\textbf{Note:} The full formula, by actually evaluating all the terms, comes out
+to be
+\begin{equation}
+    P_{hop} = \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi
+        \p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
+        + 8\eta^{3/2}\cos I \sqrt{\sin I}}.
 \end{equation}
 
-Plots of CS locations as always in \autoref{fig:cs_locs}.
+\section{Spin Evolution with Weak Tidal Friction}\label{ss:full_tide_prob}
+
 \begin{figure}
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/99_misc/2_cs_locs.png}
-    \caption{CS locations, TODO change axis labels etc.}\label{fig:cs_locs}
+    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils0_06.png}
+    \caption{Schematic illustrating the evolution of the planet's spin due to
+    tidal friction. The green lines illustrate the directions of
+    Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}), while the black and blue
+    lines denote where the tidal $\Omega_{\rm s}'$ and $\theta'$ change signs
+    respectively. Overlaid are the obliquities of Cassini States 1 and 2, the
+    two Cassini States that are stable under tidal dissipation (see
+    Section~\ref{ss:tidal_eqs}). The points that are both Cassini States and
+    satisfy $\Omega_{\rm s}' = 0$ are the tidal Cassini Equilibria (tCE),
+    circled in green. Finally, the vertical red lines illustrate the
+    $\Omega_{\rm s}$ below which tides causes tCE2 to become unstable; the
+    dashed and dotted lines correspond to values of $\epsilon = 10^{-2}$ and
+    $10^{-1}$ respectively.
+    }\label{fig:6equils}
 \end{figure}
 
-Note that $\phi$ is conjugate to $\cos \theta$, and thus the spin dynamics
-exhibit Hamiltonian:
-\begin{equation}
-    H(\mu, \phi; s) = -\frac{s}{s_c}\frac{\mu^2}{2}
-        + \mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi.
-\end{equation}
+\subsection{Tidal Model: Equilibrium Tides}\label{sss:weaktide}
 
-Plot of level curves of Hamiltonian as before, including $\mathcal{C}_{\pm}$
-notation in \autoref{fig:1contours}.
+To model the dissipative effect of times, we use the weak friction theory of
+equilibrium tides \citep{lai2012}. In this model, tides cause both $\uv{s}$ and
+$\Omega_{\rm s}$ to evolve following:
+\begin{align}
+    \p{\rd{\uv{s}}{\tau}}_{\rm tide} &= \epsilon
+                \s{\frac{2n}{\Omega_{\rm s}} - \p{\uv{s} \cdot \uv{l}}}
+                    \uv{s} \times \p{\uv{l} \times \uv{s}}\label{eq:dsdt_tide},\\
+    \frac{1}{\Omega_{\rm s}}\p{\rd{\Omega_{\rm s}}{\tau}}_{\rm tide}
+        &= \epsilon \s{\frac{2n}{\Omega_{\rm s}}\p{\uv{s} \cdot
+            \uv{l}} - \p{1 + \p{\uv{s} \cdot \uv{l}}^2}},\label{eq:dWsdt_tide}
+\end{align}
+where $\epsilon$ is the dimensionless tidal evolution rate, given by
+\begin{align}
+    \epsilon \equiv{}& -\frac{1}{gt_a}\frac{L}{2S} \frac{\Omega_{\rm s}}{2n},\\
+        % = \frac{1}{\cos I} \frac{2k_2}{Q} \frac{n}{\Omega_{\rm c}},\\
+    \frac{1}{t_a} ={}& \frac{3k_2}{Q}\p{\frac{m}{M}}\p{\frac{R}{a}}^5 n,\\
+    \epsilon \approx{}& 0.003\frac{1}{\cos I}\p{\frac{2k_2/Q}{10^{-3}}}
+            \p{\frac{m_{\rm p}}{M_{\rm J}}}^{-1}
+            \p{\frac{a_{\rm p}}{5 \;\mathrm{AU}}}^{3}\nonumber\\
+        &\times \p{\frac{a}{0.4\;\mathrm{AU}}}^{-6}
+            \p{\frac{\rho}{3 \; \mathrm{g/cm}^3}}^{-1}
+            \p{\frac{M_\star}{M_{\odot}}}^{2}.
+\end{align}
+Here, $L = ma^2n$ and $S = kmR^2 \approx mR^2/4$ are the orbital and spin
+angular momenta of the inner planet, respectively. In Eq.~\eqref{eq:dsdt_tide},
+it is clear that tides only acts on the polar component of $\uv{s}$,
+i.e.\ $\theta$, and not the azimuthal component $\phi$. As such,
+the effect of tides on the dynamics of the system can be qualitatively
+understood in $(\Omega_{\rm s}, \theta)$ space. Figure~\ref{fig:6equils} shows
+the behavior of Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) in a few
+characteristic regions of $(\Omega_{\rm s}, \theta)$ space.
+
+Component form
+\begin{align}
+    \rd{\theta}{t} &= g\sin I \sin \phi -
+        \epsilon \sin \theta,\label{eq:ds_fullq}\\
+    \rd{\phi}{t} &= -\alpha\cos\theta
+        - g\p{\cos I + \sin I \cot \theta \cos \phi}\label{eq:ds_fullphi},\\
+    \rd{\Omega_{\rm s}}{t}
+        &= \epsilon \s{2n \cos \theta
+            - \Omega_{\rm s}\p{1 + \cos^2\theta}}\label{eq:ds_fulls}.
+\end{align}
+
+For the parameters considered here, the tidal evolution in $\Omega_{\rm s}$ and
+$\theta$ occurs over characteristic time scale $2 \times 10^8\;\mathrm{yr}$.
+Note that while the semimajor axis $a$ is not strictly constant under the
+influence of tidal dissipation, $\dot{a} / \dot{\theta} \sim S / L \ll 1$
+\citep{lai2012} and the evolution of $a$ can be safely neglected in this paper.
+
+Armed with the intuition provided by the toy model in
+Section~\ref{ss:toy_model}, we now study the equations of motion including the
+full weak tidal friction theory, given by
+Eqs.~(\ref{eq:ds_fullq}--\ref{eq:ds_fulls}). We imagine that the inner planet is
+born rapidly spinning, but for computational reasons, we restrict the initial
+spin to be $\Omega_{\rm s, i} = 10n$. The final results are not sensitive on the
+specific initial spin as long as $\Omega_{\rm s, i} \gg n$. The hierarchy of the
+system is determined by the parameter $\Omega_{\rm c}$, given by
+Eq.~\eqref{eq:def_Wc}, for which we choose a few representative values. Then,
+for a given initial $\theta_0$ and $\phi_0$, the final outcome (between tCE1 and
+tCE2) of the system can
+be calculated. In Fig.~\ref{fig:Hhists_0_06}, we show the final outcome for many
+randomly chosen $\theta_0$ and $\phi_0$ for $\Omega_{\rm c} = 0.06$ and $I =
+5^\circ$. We see that tCE1 is generally reached for spins initially in Zone I,
+tCE2 is generally reached for spins initially in Zone II, and a probabilistic
+outcome is observed for spins initially in Zone III, very similar to the results
+found for the toy model in Section~\ref{ss:toy_model}.
+Figures~\ref{fig:Hhists_0_20,fig:Hhists_0_70} show the same results but for
+$\Omega_{\rm c} = 0.2$ and $\Omega_{\rm c} = 0.7$. We see that more initial
+conditions are able to end up in tCE2, mostly because the initial Zone II is
+larger. In all three examples, probabilistic resonance capture for initial
+conditions in Zone III is responsible for a significant fraction of systems that
+end up in tCE2.
 \begin{figure}
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/0_eta/1contours.png}
-    \caption{TODO label $\mathcal{C}_{\pm}$.}\label{fig:1contours}
-\end{figure}
-
-\subsection{Weak Tidal Friction}\label{ss:weak_tides}
-
-We use the weak tidal friction model \citep{lai2012}. The EOM for $\theta, s$
-become:
-\begin{align}
-    \rd{\hat{s}}{\tau}
-        &= \frac{s}{s_c}\p{\hat{s} \cdot \hat{l}_1}\p{\hat{s} \times
-                \hat{l}_1} - \hat{s} \times \hat{l}_p
-            + \frac{\epsilon 2\Omega_1}{s}
-                \p{1 - \frac{s}{2\Omega_1}\p{\hat{l}_1 \cdot \hat{s}}}
-                    \hat{s} \times \p{\hat{l}_1 \times \hat{s}},\\
-    \rd{s}{\tau}
-        &= \epsilon 2\Omega_1 \p{\hat{s} \cdot \hat{l}_1 -
-            \frac{s}{2\Omega_1}\p{1 + \p{\hat{s} \cdot \hat{l}_1}^2}}.
-\end{align}
-
-The phase portrait for these EOM in $\p{s, \theta}$ space is shown in
-Fig.~\ref{fig:quiver}.
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/2quiver0_2.png}
-    \caption{Phase portrait.}\label{fig:quiver}
-\end{figure}
-
-\subsection{Stable Equilibria of Tidal Friction}\label{ss:tidal_eqs}
-
-Generally, these EOM have equilibria at the points that are both a CS and
-satisfy $\dot{s} = 0$ under weak tidal friction. These are stable as $\epsilon
-\to 0$, see Appendix~\ref{app:cs_stab}. On Fig.~\ref{fig:quiver}, these are the
-intersection of the locations of CS1 and CS2 with the line $\dot{s} = 0$. It is
-clear that the locations of these equilibria depend on the value of $s_c$. Call
-these generalized equilibria \emph{tidal Cassini Equilibria} (tCE), and number
-them tCE1 and tCE2 depending on whether they are CS1 or CS2 states. Shown
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/6equils0_06.png}
-    \caption{Location of tCE\@. Vertical line is spin rate below which tCE is
-    destroyed.}\label{fig:6equils}
-\end{figure}
-
-Furthermore, if tides are too strong (large $\epsilon$), tCE2 can become
-unstable (cite Fabrycky). The required $\epsilon$ for stability of tCE2 is given
-by
-\begin{equation}
-    \epsilon \leq \frac{\eta_2 \sin I}{1 - \mu_2^2},
-\end{equation}
-where $\eta_2$ and $\mu_2$ are evaluated at tCE2.
-
-\section{Probability Distribution of Outcomes}\label{s:sim}
-
-The general question of the dynamics is then as follows: given problem
-parameters (including $s_c$) and an initial planet spin and obliquity $(s,
-\theta)$, what are the possible outcomes and their associated probabilities? We
-study this first at fixed $s_c$ as a function of $\theta$ in
-Section~\ref{ss:q_dist}, then as a function of $s_c$ for an isotropic initial
-spin $\hat{s}$ in Section~\ref{ss:s_c_dist}.
-
-\subsection{Distribution As a Function of $\theta$}\label{ss:q_dist}
-
-As a result of \autoref{ss:tidal_eqs}, the tCE are the only possible final
-outcomes. We generate initial spin vectors $\hat{s}$ for isotropic initial
-distribution $\p{\cos \theta, \phi}$, and marginalize over $\phi$ (which
-generally cannot be fixed by any formation mechanism) in histograms. This gives
-histograms in Figs.~\ref{fig:Hhists_0_06,fig:Hhists_0_20,fig:Hhists_0_70}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
-    \caption{$s_c = 0.06$. Note that it is difficult to reach
-    tCE2.}\label{fig:Hhists_0_06}
+    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
+    \caption{\emph{Left:} Each dot indicates which tCE a given initial condition
+    $(\theta_{\rm i}, \phi_{\rm i})$ evolve towards (labeled in legend), for
+    $\Omega_{\rm c} = 0.06n$ and $I = 5^\circ$. The
+    separatrix is shown as the black line. Note that points above the
+    separatrix evolve towards tCE1, points inside the separatrix evolve towards
+    tCE2, and points below the separatrix have a probabilistic outcome.
+    \emph{Right:} Histogram of which tCE a given initial obliquity $\theta_{\rm
+    i}$ evolves towards.}\label{fig:Hhists_0_06}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
-    \caption{$s_c = 0.2$. Note that tCE2 is both reached with substantial
-    probability and has substantial obliquity.}\label{fig:Hhists_0_20}
+    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
+    \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\Omega_{\rm c} =
+    0.2n$.}\label{fig:Hhists_0_20}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_60_5.png}
-    \caption{$s_c = 0.6$. Note that tCE2 becomes attracting over tCE1, but will
-    have obliquity $\approx I$ and is uninteresting.}\label{fig:Hhists_0_70}
+    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_70_5.png}
+    \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\Omega_{\rm c} =
+    0.7n$. Note that even points above the separatrix can evolve towards tCE2
+    here.}\label{fig:Hhists_0_70}
 \end{figure}
 
-The governing mechanism for these probabilities is probabilistic separatrix
-crossing, which is covered in Appendix~\ref{app:probs}. The calculation is
-difficult analytically, but can be performed semi-analytically (describe
-procedure here, calculate $\eta_{\star}$ numerically etc.). The agreement of
-this curve with the histograms is examined for the same three $s_c$ values
-in Figs.~\ref{fig:pc_fits_0_06,fig:pc_fits_0_20,fig:pc_fits_0_70}.
+Similarly to \citet{su2020}, these probabilities are the result of separatrix
+crossings. However, the calculation differs from \citet{su2020}: since the
+perturbation is dissipative in phase space (i.e.\ it does not conserve phase
+space area), analysis following \citet{henrard1982} is not sufficient. A more
+general theory of separatrix crossing is still able to predict the outcome
+probabilities, extending the results in Section~\ref{ss:toy_model}.
+Appendix~\ref{app:probs} gives the appropriate generalization, which gives the
+resonance capture probability $P_{\rm III \to II}$ as a function of $\eta$ upon
+separatrix encounter.
+
+We can apply this probability to calculate the probabilities of the two outcomes
+when a numerically-integrated trajectory encounters the separatrix, and from
+this obtain a semi-analytical prediction of the distribution of outcomes. In
+Fig.~\ref{fig:pc_fits_0_06}, we show the same histogram as the vertical panel of
+Fig.~\ref{fig:Hhists_0_06} alongside the semi-analytical prediction. Good
+qualitative agreement is observed. Figs.~\ref{fig:pc_fits_0_20,fig:pc_fits_0_70}
+show the same for Figs.~\ref{fig:Hhists_0_20, fig:Hhists_0_70}.
 \begin{figure}
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_06_5.png}
-    \caption{$s_c = 0.06$ prediction vs histogram.}\label{fig:pc_fits_0_06}
+    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_06_5.png}
+    \caption{Comparison of the right hand panel of Fig.~\ref{fig:Hhists_0_06}
+    (red dots) with a semi-analytic calculation (blue line). The semi-analytic
+    calculation is performed by numerically integrating
+    Eqs.(~\ref{eq:ds_fullq}--\ref{eq:ds_fulls}) on a grid of initial
+    conditions uniform in $\cos \theta_{\rm i}$ and $\phi_{\rm i}$ until
+    separatrix encounter, then using the $\Omega_{\rm s}$ at separatrix
+    encounter to evaluate (TODO) to analytically compute the probability of
+    evolution into tCE2.}\label{fig:pc_fits_0_06}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_20_5.png}
-    \caption{$s_c = 0.20$ prediction vs histogram.}\label{fig:pc_fits_0_20}
+    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_20_5.png}
+    \caption{Same as Fig.~\ref{fig:pc_fits_0_06} but for $\Omega_{\rm c} =
+    0.2n$, shown in Fig.~\ref{fig:Hhists_0_20}.}\label{fig:pc_fits_0_20}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_70_5.png}
-    \caption{$s_c = 0.70$ prediction vs histogram.}\label{fig:pc_fits_0_70}
+    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_70_5.png}
+    \caption{Same as Fig.~\ref{fig:pc_fits_0_06} but for $\Omega_{\rm c} =
+    0.7n$, shown in Fig.~\ref{fig:Hhists_0_70}.}\label{fig:pc_fits_0_70}
 \end{figure}
 
-\subsection{Distribution As a Function of $s_c$}\label{ss:s_c_dist}
+\subsection{Outcomes for Distribution of Initial Spin Orientations
+}\label{ss:s_c_dist}
 
-Assuming that $\hat{s}$ is drawn from an isotropic distribution, we may then
-calculate the probabilities of going to either tCE as a function of $s_c$. This
-is shown below for $I = 5^\circ$
+Here, we define $\Omega_{\rm c}$ to be the critical spin where the
+precession frequencies are equal, i.e.
+% ((3 Mjup) / (4 Msun) * (0.4 / 5)^3) /
+%   (1.5 * Msun / (4 * pi / 3 * (3 g\cm#3)) / (0.4 AU)^3)
+\begin{align}
+    \Omega_{\rm c} \equiv{}& -\frac{g}{\alpha}\Omega_{\rm s},\\
+    \frac{\Omega_{\rm c}}{n} ={}& 0.33 \p{\frac{k}{k_{\rm q}}}
+            \p{\frac{m_{\rm p}}{M_{\rm J}}}
+            \p{\frac{a_{\rm p}}{5 \;\mathrm{AU}}}^{-3}\nonumber\\
+        &\times \p{\frac{a}{0.4\;\mathrm{AU}}}^{6}
+            \p{\frac{\rho}{3 \; \mathrm{g/cm}^3}}
+            \p{\frac{M_\star}{M_{\odot}}}^{-2}.\label{eq:def_Wc}
+\end{align}
+Here, $\rho = m / \p{4\pi R^3/3}$ is the average density of the inner planet,
+and $M_{\rm J}$ is the mass of Jupiter. Tides tend to drive $\Omega_{\rm s}$ to
+spin-orbit synchronization, where $\Omega_{\rm s} = n$ and thus $-g / \alpha =
+\Omega_{\rm c} / n$. As such, we see that the ratio $\Omega_{\rm c} / n$
+quantifies the strength of the perturber relative to the spin-orbit coupling at
+the tidal equilibrium.
+
+In the previous section, we considered the outcome as a function of the initial
+spin orientation, specified by $\theta_0$ and $\phi_0$. In this section, we
+consider the distribution of outcomes when averaging over a distribution of
+initial spin orientations. For simplicity, we just consider $\uv{s}$ being
+isotropically distributed. Figure~\ref{fig:probs} shows this for $I
+= 5^\circ$ as a function of $\Omega_{\rm c}$.
 \begin{figure}
     \centering
-    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5probs_5.png}
-    \caption{Top: total probability of ending up in tCE2 (blue dots) and the
-    prediction ignoring separatrix capture (red line). Bottom:
-    obliquities of the tCEs.}\label{fig:probs}
+    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5probs_5.png}
+    \caption{\emph{Top:} Total probability of ending up in tCE2 (red dots) for
+    $I = 5^\circ$ for a range of $\Omega_{\rm c}$. \emph{Bottom:}
+    obliquities of the two possible tCEs.}\label{fig:probs}
 \end{figure}
-
-Note that while only the results for an isotropic distribution of initial
-$\hat{s}$ are shown, in principle arbitrary distributions $P\p{\theta_i}$ can be
-convolved against the $P_{tCE2}\p{\theta_i}$ distributions shown in
-\autoref{ss:q_dist}.
 
@@
 
-\bibliographystyle{mnras}
-\bibliography{Su_sep_cross}
+\bibliography{Su_weak_tides}
+\bibliographystyle{aasjournal}
 
 \appendix
-\section{Proof of Stability of Cassini States 1 \& 2}\label{app:cs_stab}
 
-Insert here.
+\onecolumn
 
-\section{Separatrix Crossing Dynamics}
+\section{Convergence of Initial Conditions Inside the Separatrix to tCE2
+}\label{sss:cs_stab2}
 
-\subsection{Theory}\label{app:sep_crossing_dynamics}
+Based on the results from the previous section, we intuitively expect that all
+initial conditions in Zone II, i.e.\ inside the separatrix, will remain near
+CS2, and eventually converge to tCE2. However, this is not immediately
+justified, since not all points in Zone II are necessarily close enough to CS2
+for the linear analysis in Section~\ref{ss:tidal_eqs} to be valid. We present an
+alternative calculation illustrating that all points in Zone II remain near CS2.
+For simplicity, we neglect the evolution of $\Omega_{\rm s}$ here and take
+$\eta$ to be constant; the full calculation presented in
+Appendix~\ref{app:sep_crossing_dynamics} includes the evolution of $\Omega_{\rm
+s}$ and reproduces this result.
 
-\subsubsection{Application of Adiabatic Invariance: Henrard Theory}
+The objective is to determine the change in $H$, the value of the unperturbed
+Hamiltonian, over a single libration cycle. If the system's has initial $H_0
+\equiv H\p{\theta_0, \phi_0} = H_{\rm sep} + \Delta H$ where
+\begin{align}
+    H_{\rm sep} &\equiv H\p{\cos \theta_{\rm 4}, \phi_{\rm 4}},\\
+        &\approx -\sin I + \frac{\eta}{2}\cos^2 I +
+            \mathcal{O}\p{\eta^2},\label{eq:def_Hsep}
+\end{align}
+is the value of $H$ along the separatrix, and $\Delta H > 0$ for initial
+conditions inside the separatrix, then the unperturbed trajectory $\theta(\phi)$
+can then be written explicitly via:
+\begin{align}
+    H_{\rm sep} + \Delta H &= -\frac{\cos^2\theta}{2\eta} + \cos\theta \cos I
+            - \sin I \cos \phi,\\
+    % \cos \theta &=
+    %     \eta \cos I \pm \eta\sqrt{\cos^2 I - 2
+    %         \p{H_{\rm sep} + \Delta H + \sin I \cos \phi} / \eta},\\
+    \cos \theta_{\pm} &\approx
+        \eta \cos I \pm \sqrt{2\eta\s{\sin I\p{1 - \cos \phi} - \Delta H}}.
+        \label{eq:lib_cycle_toy}
+\end{align}
+We have taken $\sin \theta \approx 1$, a good approximation in Zone II since
+$\eta \ll 1$. When $\Delta H = 0$, this reproduces Eq.~(B5) of \citet{su2020}.
+When $\Delta H > 0$, there are some values of $\phi$ for which no solutions of
+$\theta$ exist, reflecting the fact that the libration does not extend over the
+full interval $\phi \in [0, 2\pi]$. During a libration cycle, $\theta_-$
+[$\theta_+$] is traversed while $\phi' > 0$ [$\phi' < 0$], i.e.\ the trajectory
+librates counterclockwise in $(\cos \theta, \phi)$ phase space (see
+Fig.~\ref{fig:1contours}).
 
-Review Henrard result, is already very successful e.g.\ MMR capture.
+The above calculation assumes $H$ is constant, yielding the unperturbed
+trajectory. The leading order change to $H$ can be computed by integrating
+$\rdil{H}{\tau}$ along this trajectory, where $\rdil{H}{\tau}$ is given by
+\begin{align}
+    \rd{H}{\tau} &=
+            \pd{H}{(\cos \theta)}\rd{(\cos \theta)}{\tau}
+            + \pd{H}{\phi}\rd{\phi}{\tau},\nonumber\\
+        &= -\p{\rd{(\cos\theta)}{\tau}}_{\rm tide} \rd{\phi}{\tau}.
+            \label{eq:dHdt_toyf}
+\end{align}
+We have used Hamilton's equations for the canonically conjugate variables $\cos
+\theta$ and $\phi$ to eliminate the non-tidal contributions. The total change in
+$H$ over a single cycle is then:
+\begin{align}
+    \oint \rd{H}{\tau}\;\mathrm{d}\tau ={}& \oint \rd{H}{\tau}
+        \rd{\tau}{\phi}\;\mathrm{d}\phi,\nonumber\\
+        ={}& \oint -\p{\rd{(\cos \theta)}{\tau}}_{\rm tide}
+            \;\mathrm{d}\phi,\nonumber\\
+        ={}&
+            \int\limits_{\phi_{\min}}^{\phi_{\max}}
+                \epsilon \p{\frac{2n}{\Omega_{\rm s}} - \cos \theta_-}
+                \sin^2\theta_- \;\mathrm{d}\phi\nonumber\\
+            &+ \int\limits_{\phi_{\min}}^{\phi_{\max}}
+                \epsilon \p{\frac{2n}{\Omega_{\rm s}} - \cos \theta_+}
+                \sin^2\theta_+ \;\mathrm{d}\phi,\nonumber\\
+        \approx{}&
+            \int\limits_{\phi_{\min}}^{\phi_{\max}}
+                \epsilon \p{\frac{2n}{\Omega_{\rm s}}\sin^2\theta_- - \cos \theta_-}
+                 \;\mathrm{d}\phi\nonumber\\
+            &+ \int\limits_{\phi_{\min}}^{\phi_{\max}}
+                \epsilon \p{\frac{2n}{\Omega_{\rm s}}\sin^2\theta_+ - \cos \theta_+}
+                \;\mathrm{d}\phi.
+\end{align}
+Finally, for every $\phi$, $\sin \theta_- \geq \sin \theta_+$ and $\cos \theta_-
+\leq \cos \theta_+$ with equality only at the endpoints of the libration cycle
+where $\theta_- = \theta_+$. As such, the total change in $H$ over a libration
+cycle is positive, and we conclude that every trajectory starting in Zone II
+remains near CS2 under the effect of tidal dissipation even when not
+infinitesimally close to CS2 initially.
 
-\subsubsection{Melnikov Integral}\label{sss:Melnikov}
-
-The first substantial new result.
-
-\subsubsection{Example: Constant $s$}
-
-``Toy problem 1'', the nice $P_c \propto \eta^{3/2}$ result. Application of
-Section~\ref{sss:Melnikov}.
-
-\subsubsection{Combined Result}
+\section{Separatrix Crossing Theory}\label{app:sep_crossing_dynamics}
 
@@
 \subsection{Separatrix Crossing Probability: Tidal Friction}\label{app:probs}
+\begin{align}
+    \rd{\p{\Delta H}}{\tau} &=
+            \pd{H}{(\cos \theta)}\rd{(\cos \theta)}{\tau}
+            + \pd{H}{\phi}\rd{\phi}{\tau}
+            + \pd{H}{\Omega_{\rm s}}\rd{\Omega_{\rm s}}{\tau}
+            - \pd{H_{\rm sep}}{\Omega_{\rm s}}\rd{\Omega_{\rm s}}{\tau}
+                    ,\nonumber\\
+        &= -\p{\rd{(\cos\theta)}{\tau}}_{\rm tide} \rd{\phi}{\tau}
+            + \p{\pd{H}{\Omega_{\rm s}} - \pd{H_{\rm sep}}{\Omega_{\rm s}}}
+            \rd{\Omega_{\rm s}}{\tau},\label{eq:dHdt_schematic}\\
+    \frac{1}{\epsilon}\rd{(\Delta H)}{\tau} &\approx
+            \sin^2\theta\p{\frac{2n}{\Omega_{\rm s}} - \cos\theta}
+                \rd{\phi}{\tau} +
+                \s{\frac{\cos^2\theta}{2\Omega_{\rm c}} - \frac{\Omega_{\rm
+                c}}{2\Omega_{\rm s}^2}\cos^2 I}\rd{\Omega_{\rm
+                s}}{\tau}.\label{eq:dHdt_final}
+\end{align}
 
@@
 
-\bsp
 \label{lastpage} % chktex 24
 \end{document}
+% chktex 17

### 2021-04-19 initial/1_weaktide/6misc.py

@@ -10,6 +10,8 @@ matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 plt.rc('text', usetex=True)
 plt.rc('font', family='serif', size=16)
+from scipy.optimize import brenth
+from scipy.interpolate import interp1d
 
 POOL_SIZE = 50
 
@@ -34,6 +36,7 @@ def get_cs_val(I, s_c, s):
 
 def plot_equils(I, s_c, verbose=True, fn_str='6equils%s'):
     ''' plot in (s, mu) space showing how the tCS arise '''
+    fig = plt.figure(figsize=(6, 6))
     s_lt = np.linspace(s_c / 10, 1, 200) # max eta = 10
     s_gt = np.linspace(1, 3, 200) # other interesting part of the interval
     s_tot = np.concatenate((s_lt, s_gt))
@@ -41,14 +44,11 @@ def plot_equils(I, s_c, verbose=True, fn_str='6equils%s'):
     cs1_qs, cs2_qs = get_cs_val(I, s_c, s_tot)
     cs1_exist_idx = np.where(cs1_qs > -1)[0]
     mu_equil_lt = [np.degrees(np.arccos(get_mu_equil(s))) for s in s_lt]
-    plt.plot(s_lt, mu_equil_lt, 'k', label=r'$\dot{s}=0$', lw=4)
 
     s_dq = np.linspace(2, 3, 200)
-    plt.plot(s_dq, np.degrees(np.arccos(2 / s_dq)), 'b',
-             label=r'$\dot{\theta} = 0$', lw=4)
 
-    plt.xlabel(r'$s / \Omega_1$')
-    plt.ylabel(r'$\theta$')
+    plt.xlabel(r'$\Omega_{\rm s} / n$')
+    plt.ylabel(r'$\theta$ (deg)')
     plt.ylim([0, 90])
     if verbose:
         plt.plot(s_tot, np.degrees(cs2_qs), 'r', label='CS2', lw=2.5)
@@ -62,19 +62,32 @@ def plot_equils(I, s_c, verbose=True, fn_str='6equils%s'):
             -np.sin(I) + np.sqrt(np.sin(I)**2 + 4 * eps_val**2 * np.cos(I)**2)
         ) / (2 * eps_val * np.cos(I)**2)
         xlims = plt.xlim()
-        plt.axvline(s_c / eta_crit(1e-2), c='r', ls=':', lw=0.6,
[…]

### 2021-04-19 initial/99_misc/2_rand_plots.py

@@ -324,7 +324,7 @@ def plot_nonad_diagram():
     plt.clf()
 
 if __name__ == '__main__':
-    # plot_cs(np.radians(5))
+    plot_cs(np.radians(5))
     # plot_eigens(np.radians(5))
-    plot_3vec()
+    # plot_3vec()
     # plot_nonad_diagram()

### 2021-04-19 initial/99_misc/4cs_stab_hessian.py

@@ -1,0 +1,197 @@
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif', size=20)
+plt.rc('lines', lw=2.5)
+plt.rc('xtick', direction='in', top=True, bottom=True)
+plt.rc('ytick', direction='in', left=True, right=True)
+import scipy.optimize as opt
+
+
+def get_etac(I):
+    return (np.sin(I)**(2/3) + np.cos(I)**(2/3))**(-3/2)
+
+def roots(I, s_c, s):
+    '''
+    returns theta roots from EOM, not phi (otherwise same as 0_eta func)
+    '''
+    eta_c = get_etac(I)
+    eta = s_c / s
+
+    # function to minimize and derivatives
+    f = lambda q: -eta * np.sin(q - I) + np.sin(q) * np.cos(q)
+    fp = lambda q: -eta * np.cos(q - I) + np.cos(2 * q)
+
+    if eta < eta_c:
+        roots = []
+        inits = [0, np.pi / 2, -np.pi, -np.pi / 2]
+        for qi in inits:
+            roots.append(opt.newton(f, qi, fprime=fp))
+        return np.array(roots)
+
+    else:
+        roots = []
+        inits = [np.pi / 2 - I, -np.pi + I]
+        for qi in inits:
+            # newton doesn't seem to work very well here @ large eta
+            # roots.append(opt.newton(f, qi, fprime=fp))
+            dq = np.pi / 2
+            roots.append(opt.bisect(f, qi - dq, qi + dq))
+        return np.array(roots)
+
+def plot_tCE_stab():
+    # TODO unused since inaccurate, but maybe can plot tCE stability as a
+    # function of s_c
+    I = np.radians(5)
+    s_c = 0.3
+
+    num_etas = 100
+    eigs = np.full((12, num_etas), -1000 + 0j, dtype=np.complex64)
+    # CS2, CS3, CS1, CS4
+    eps = 3e-3
+    eta_c = get_etac(I)
+    s_vals = np.geomspace(s_c / (1.3 * eta_c), s_c * 10, num_etas)
+
+    # convention: phi = 0
[…]

### 2021-04-26 writeups/Su_weak_tides.tex
made a decent amount of progress on weak tides draft...

@@
-% label C_\pm on fig 2
-% unify 3 & 4, choose consistent q/cos q
-
-% S2: CS stability
-% S3: How to reach CS
-% S3: toy problem, affords analytical understanding
-% S4: full problem
-% Discussion/conclusion: maybe 0.05 AU + SE? does this still work?
     \documentclass[
@@
 \begin{equation}
-    \eta_{\rm c} \equiv \p{\sin^{2/3}\!I + \cos^{2/3}\!I}^{-3/2}.\label{eq:etac}
+    \eta_{\rm c} \equiv \p{\sin^{2/3}\!I + \cos^{2/3}\!I}^{-3/2}.\label{eq:def_etac}
 \end{equation}
@@
     \centering
-    %\includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs.png}
+    \includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs.png}
     \caption{Cassini State obliquities $\theta$ as a function of $\eta \equiv
@@
     line denotes $\eta_{\rm c}$, where the number of Cassini States changes from
-    four to just two (Eq.~\ref{eq:etac}). The horizontal dashed line gives
+    four to just two (Eq.~\ref{eq:def_etac}). The horizontal dashed line gives
     $\theta = I$, the asymptotic value of Cassini State 2's obliquity when $\eta
@@
 Figure~\ref{fig:1contours} shows the level curves of this Hamiltonian for $I =
-20^\circ$, for which $\eta_{\rm c} \approx 0.77$ (Eq.~\ref{eq:etac}). When $\eta
+20^\circ$, for which $\eta_{\rm c} \approx 0.77$ (Eq.~\ref{eq:def_etac}). When $\eta
 < \eta_{\rm c}$, CS4 exists and is a saddle point. The two trajectories
@@
     \centering
-    %\includegraphics[width=\columnwidth]{../initial/0_eta/1contours.png}
+    \includegraphics[width=\columnwidth]{../initial/0_eta/1contours.png}
     \caption{Level curves of the Cassini State Hamiltonian (Eq.~\ref{eq:H}) for
-    $I = 5^\circ$, for which $\eta_{\rm c} \approx 0.77$ (Eq.~\ref{eq:etac}).
+    $I = 5^\circ$, for which $\eta_{\rm c} \approx 0.77$ (Eq.~\ref{eq:def_etac}).
     For $\eta < \eta_{\rm c}$, there are four Cassini States (labeled), while
@@
 
-\section{Spin Evolution with Alignment Torque}\label{ss:toy_model}
+\section{Spin Evolution with Alignment Torque}\label{s:toy_model}
 
@@
 the spin magnitude of the planet is constant, so $\alpha$ and $g$ are both
-fixed, while the spin orientation $\uv{s}$ experiences a torque that drives it
-towards alignment with $\uv{l}$ on the alignment timescale $t_{\rm s}$:
+fixed, while the spin orientation $\uv{s}$ experiences an alignment torque
+towards $\uv{l}$ on the alignment timescale $t_{\rm s}$:
 \begin{equation}
@@
         = \frac{1}{t_{\rm s}} \uv{s} \times \p{\uv{l} \times \uv{s}}.
+        \label{eq:dsdt_tide_toy}
 \end{equation}
@@
 \subsection{Shifted Cassini States and Linear Stability
-Analysis}\label{ss:tidal_eqs}
+Analysis}\label{ss:tidal_equils}
 
-When $t_{\rm s}$ is finite, the CSs tilt out of the $\uv{l}$-$\uv{l}_{\rm p}$
-plane \citep[as was first pointed out for CS2 by][]{fabrycky_otides}. A simple
-expression for the degree of this tilt can be obtained by solving for $\phi_{\rm
-cs}$, the azimuthal angle of the modified CS, when setting Eq.~\eqref{eq:dqdt_toy} equal
-to zero. This gives
+If the alignment torque is weak ($\abs{gt_{\rm s}} \gg 1$), then the fixed points of
+Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) are just slightly shifted CSs. This
+shift can be calculated cleanly to leading order: all of the CS obliquities
+$\theta_{\rm cs}$ are unchanged while the azimuthal angle $\phi_{\rm cs}$ for
+each CS now satisfies
 \begin{equation}
-    \sin \phi_{\rm cs} = \frac{\sin^2\theta_{\rm cs}}{\sin I \abs{g}t_{\rm s}}.
+    \sin \phi_{\rm cs} = \frac{\sin\theta_{\rm cs}}{\sin I \abs{g}t_{\rm s}}.
+        \label{eq:mcs_shift}
 \end{equation}
-Here, $\theta_{\rm cs}$ is the modified CS obliquity. Note that if $t_{\rm s}$
-is shorter than some critical value $t_{\rm s, c}$, which for a given CS is
-given by
+We can see that if $t_{\rm s} > t_{\rm s, c}$, where
 \begin{align}
-    t_{\rm s, c} &= \frac{\sin^2\theta_{\rm cs}}{\abs{g}\sin I},
+    t_{\rm s, c} &= \frac{1}{\abs{g}\sin I},
 \end{align}
-then there are no solutions for $\phi_{\rm cs}$, and the CS is no longer a fixed
-point. This condition first breaks down for $\theta_{\rm cs} \approx 90^\circ$,
-i.e.\ for CS2 (and CS4) in the limit $\eta \ll 1$. Thus, as long as $t_{\rm s}
-\gtrsim \p{\abs{g}\sin I}^{-1}$, then all CSs will exist.
+then Eq.~\eqref{eq:mcs_shift} will always have solutions for $\phi_{\rm cs}$,
+and the alignment torque never changes the number of fixed points of the system.
+If $t_{\rm s}$ is decreased below $t_{\rm s, c}$, CS2 and CS4 cease to be
+fixed points if $\eta \ll 1$ \citep[as first noted in][]{fabrycky_otides}, as
+$\theta_{\rm cs} \approx 90^\circ$ for these (see Fig.~\ref{fig:cs_locs}), while
+the other CSs have small $\sin \theta_{\rm cs}$ and are only slightly perturbed.
+Figure~\ref{fig:mcs} shows the obliquity and azimuthal angles for each of the
+CSs in the $\eta \ll 1$ case, where it can be seen that CS2 and CS4 collide and
+annihilate.. For the remainder of this section, we will consider the case where
+$t_{\rm s} \gg t_{\rm s, c}$ and the CSs only differ slightly from their
+unperturbed locations.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/99_misc/0_stab.png}
+    \caption{Modified CSs for $I = 5^\circ$ and $\eta = 0.2$, and the CS1 and
+    CS3 obliquities have been offset (labeled in legend) to improve clarity of
+    the plot.}\label{fig:mcs}
+\end{figure}
 
 We next seek to characterize the stability of small perturbations about each of
-the CSs in the presence of the alignment torque. We can linearize
-Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) about a [modified] CS, yelding
+the CSs in the presence of the weak tidal alignment torque. We can linearize
+Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) about a shifted CS, yelding
 \begin{align}
-    \rd{}{\tau}\begin{bmatrix}
+    \rd{}{t}\begin{bmatrix}
         \theta\\ \phi
@@
 where the cs subscript indicates evaluating at a CS, $\Delta \theta = \theta -
-\theta_{\rm cs}$, and the same for $\Delta \phi$. The eigenvalues $\lambda$ of
-Eq.~\eqref{eq:dsdt_hessian} satisfy the equation
+\theta_{\rm cs}$, and $\Delta \phi = \phi - \phi_{\rm cs}$. The eigenvalues
+$\lambda$ of Eq.~\eqref{eq:dsdt_hessian} satisfy the equation
 \begin{align}
@@
         \sin \theta_{\rm cs} + g\sin I \csc^2\theta_{\rm cs}\cos \phi_{\rm cs}}
-            \p{- g \sin I \cos \phi_{\rm cs}},\\
+            \p{- g \sin I \cos \phi_{\rm cs}},\label{eq:def_l0_sq}\\
     \lambda &\approx -\frac{\cos \theta_{\rm cs}}{t_{\rm s}} \pm \sqrt{\lambda_0^2}.
@@
 \end{align}
-The stability depends only on the real part of
-$\lambda$ in Eq.~\eqref{eq:lambda_approx}. If we assume that the torque-induced
-modification to $\phi_{\rm cs}$ is small, then $\lambda_0$ reduces to the
-product of the eigenvalues in the torque-free limit. In this limit, $\lambda_0^2
-< 0$ for each of CSs 1--3 and $\lambda_0^2 > 0$ for CS4 \citep[see Fig.~17
-of][]{su2020}. Thus, CS4 is always unstable, since there will always be a
-positive eigenvalue $\lambda$, while the stability of CSs 1--3 are solely
-determined by the sign of $\cos \theta_{\rm cs}$. From Fig.~\ref{fig:cs_locs},
-we see that CSs 1 and 2 are stable while CS3 is unstable under the alignment
-torque. These calculations justify results long used in CS literature
+The stability depends only on the real part of $\lambda$ in
+Eq.~\eqref{eq:lambda_approx}. $\lambda_0^2$ is a generalization of Eq.~(A4)
+in, \citet{su2020} and generally has the same behavior: it is negative for CSs
+1--3 and positive for CS4, as shown in Fig.~\ref{fig:lambda_full}. Thus, CS4 is
+always unstable, as there will always be at least one positive solution for
+$\lambda$, and the stability of CSs 1--3 are solely determined by the sign of
+$\cos \theta_{\rm cs}$. From Figs.~\ref{fig:cs_locs}, we thus see that CSs 1 and
+2 are stable while CS3 is unstable under the alignment torque. These
+calculations justify results long used in CS literature
 \citep[e.g.][]{ward1975tidal}.
-
-\subsection{Spin Obliquity Evolution Driven by Alignment Torque}
-
-With the above results, we are equipped to ask the key question of this section:
-for a given initial $\theta_0$ and $\phi_0$, which of CS1 and CS2 does the
-system evolve into? For initial conditions in Zone I (see
-Fig.~\ref{fig:1contours}), an unperturbed trajectory circulates and returns to
-$(\theta_0, \phi_0 + 2\pi)$ after a single precession period. During this
-period, the effect of the dissipation is a negative $\theta'$ everywhere during
-the cycle. Thus, for initial conditions in Zone I, $\theta$ decreases until the
-trajectory has converged to CS1. This is intuitively reasonable, as CS1 is
-stable. For initial conditions in Zone II, an equivalent calculation to that in
-Section~\ref{sss:cs_stab2} shows that all trajectories converge to CS2.
-
-For illustrative purposes, we fix $\abs{g}t_{\rm s} = 10^{-3}$, and $\eta =
--g / \alpha$ is varied among a few small values (small
-meaning much less than $\eta_{\rm c}$). We specialize to the case where $\eta
-< \eta_{\rm c}$ and there are four CSs.
-
-However, initial conditions in Zone III pose a puzzle. There are no stable CSs
-in Zone III, so the system must evolve through the separatrix to reach one of
-either CS1 or CS2. In Fig.~\ref{fig:toy_phop}, we find see that the outcome for
-initial conditions in Zone III is in fact \emph{probabilistic}. Intuitively,
-this can be understood as probabilistic resonance capture: since $\eta \ll
-\eta_{\rm c}$, $\alpha \gg -g$ (the spin-orbit precession rate,
-Eq.~\ref{eq:dsdt1}, and the orbit precession induced by the perturber,
-Eq.~\ref{eq:dldt1}, respectively), but $\alpha \cos \theta$ can become
-commensurate with $-g$ if $\cos \theta \sim \eta$. This is achieved as $\theta$
-evolves from an initially retrograde obliquity through $90^\circ$ towards
-$0^\circ$ under the influence of the dissipative term in
-Eq.~\eqref{eq:dqdt_toy}.
 \begin{figure}
     \centering
-    %\includegraphics[width=\columnwidth]{../initial/0_eta/3stats3_5_0_2.png}
-    \caption{TODO generate a better plot. Ignore bottom two panels, top two
-    panels show which ICs end up in CS 1 (left) and CS2 (right). Probabilistic
-    behavior in Zone III is evident.}\label{fig:toy_phop}
+    \includegraphics[width=\columnwidth]{../initial/99_misc/2_lambdas_full.png}
+    \caption{$\lambda_0^2$ (Eq.~\ref{eq:def_l0_sq}) as a function of $\eta
+    \equiv \abs{g} / \alpha$ for the four CSs. The solid lines give
+    $\lambda_0^2$ for the unperturbed $\phi_{\rm cs}$, and the dashed lines give
+    the values for $\phi_{\rm cs}$ shifted by $60^\circ$ ($\phi_{\rm cs} =
+    120^\circ$ for CS2 and $\phi_{\rm cs} = 60^\circ$ for CSs 1, 3, and 4).
+    }\label{fig:lambda_full}
 \end{figure}
 
-While similar in behavior to previous studies of probabilistic resonance capture
-\citep{henrard1982, su2020}, the mechanism at play here is necessarily
-different: here, the Hamiltonian and underlying phase structure is kept constant
-while a non-Hamiltonian, dissipative perturbation is introduced. The origin of
-this resonance crossing process is easy to visualize. In the absence of
-dissipative effects, the separatrix is both the set of points that flow into CS4
-and the set of points that flow away CS4, called the \emph{stable} and
-\emph{unstable} manifolds of the saddle point CS4 respectively \citep{g_and_h}.
-When the dissipative term is taken into account, these stable and unstable
-manifolds split and open a visible ``path'' from Zone III into both Zones I and
-II, as shown in Fig.~\ref{fig:toy_hop_manifolds}.
+\subsection{Spin Obliquity Evolution Driven by Alignment
+Torque}\label{ss:toy_outcomes}
+
+With the above results, we are equipped to ask questions about the dynamics of
+Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}): what is the long term behavior for
+a general initial $\uv{s}$? If $\eta > \eta_{\rm c}$, then the only possible
+final spin state is CS2, and all initial conditions will evolve asympotically
+towards it. As such, we consider only $\eta < \eta_{\rm c}$, where an initial
+condition can asymptotically evolve towards either CS1 or CS2. In
+Fig.~\ref{fig:toy_phop}, we show which CS an initial $\theta_0$ and $\phi_0$
+evolves into, where we have taken $\abs{g}t_{\rm s} = 10^{-3}$, $\eta = 0.2$,
+and $I = 20^\circ$. It is clear that initial $\uv{s}$ in zone I (following the
+naming in Fig.~\ref{fig:1contours}) evolve into CS1, those in zone II evolve
+into CS2, while those in zone III have a probabilistic outcome. We aim to
+understand each of these in turn:
 \begin{figure}
     \centering
-    %\includegraphics[width=\columnwidth]{../initial/0_eta/6manifolds0_05.png}
-    \caption{TODO overplot separatrix, remove bad labels, better legend. Stable
-    and unstable manifolds of CS4, showing how the separatrix splrits and gives
-    a ``path'' from Zone III into Zones I/II.}\label{fig:}
+    \includegraphics[width=\columnwidth]{../initial/0_eta/3stats3_5_0_2.png}
+    \caption{Plot illustrating the asymptotic behavior of initial conditions for
+    $\eta = 0.2$ and $I = 20^\circ$. Each dot represents an initial spin
+    orientation, and the coloring of the dot indicates which Cassini State
+    (legend) the system asymptotes towards.}\label{fig:toy_phop}
 \end{figure}
 
-The amount that the stable and unstable manifolds split can be calculated
-perturbatively using \emph{Melnikov's Method} \citep{g_and_h}. The essence of
-Melnikov's method lies at the heart of the perturbative approach used in
-Section~\ref{sss:cs_stab2}, where the evolution of $H$ along the perturbed
-trajectories can be evaluated by integration along their original
-\emph{unperturbed} trajectories. In particular: \textcolor{red}{TODO the rest of
-this section is copy pasted from notes without even notation changes, needs to
-be written up correctly} Now, let's reconsider the Melnikov integral when
-perturbing this finite (non-homoclinic orbit); this may no longer be an exact
-result but should give the correct scaling:
+For initial conditions in zone I, the spin circulates, and $\dot{\theta}$ is
+negative everywhere during the cycle. Thus, for initial conditions in zone I,
+$\theta$ decreases until the trajectory has converged to CS1. This is
+intuitively reasonable, as CS1 is stable.
+
+For initial conditions in zone II, our stability calculation in
+Section~\ref{ss:tidal_equils} shows that initial conditions sufficiently near CS2
+will converge to CS2. In fact, this result can be extended to all initial
+conditions inside the separatrix; see Appendix~\ref{app:cs_stab2}.
+
+For initial conditions in zone III, since there are no stable CSs in zone III,
+the system must evolve through the separatrix to reach one of either CS1 or CS2.
+The outcome of the separatrix encounter is effectively probabilistic and
+determines the final CS\@. Intuitively, this can be understood as probabilistic
+resonance capture: since $\eta \ll \eta_{\rm c}$, $\alpha \gg -g$ (the
+spin-orbit precession rate, Eq.~\ref{eq:dsdt1}, and the orbit precession induced
+by the perturber, Eq.~\ref{eq:dldt1}, respectively), but $\alpha \cos \theta$
+can become commensurate with $-g$ if $\cos \theta \sim \eta$. This is achieved
+as $\theta$ evolves from an initially retrograde obliquity through $90^\circ$
+towards $0^\circ$ under the influence of the dissipative term in
+Eq.~\eqref{eq:dqdt_toy}.
+
+While similar in behavior to previous studies of probabilistic resonance capture
+\citep{henrard1982, su2020}, the underlying mechanism is different: in these
+previous studies, the phase space structure itself evolves and causes systems to
+transition among phase space zones, while in the present scenario, a
+non-Hamiltonian, dissipative perturbation causes systems to transition among
+unchanging phase space zones.
+
+\subsubsection{Analytical Calculation of Resonance Capture Probability}
+
+The specific probabilities of the two outcomes upon separatrix encounter, a zone
+III-II or a zone III-I transition, can be calculated analytically.
+Figure~\ref{fig:toy_hop_manifolds} shows how the perturbative alignment torque
+generates probabilistic outcomes upon separatrix encounter. We present the
+interpretation of Figure~\ref{fig:toy_hop_manifolds} and the calculation of the
+resonance capture probability by first giving a qualitative description of the
+intuition behind the method, then presenting a calculation in good agreement with
+numerical results.
+
+We first describe the origin of the boundaries between regions of phase space
+that shown in Fig.~\ref{fig:toy_hop_manifolds}. They are calculated numerically
+by integrating a point infinitesimally close to CS4 forward and backward in
+time. In the absence of the alignment torque, these trajectories would evolve
+along the separatrix, but in the presence of the alignment torque they are
+perturbed slightly and cease to overlap. It can be seen in
+Fig.~\ref{fig:toy_hop_manifolds} that this splitting opens a path from zone III
+into both zones I and II\@.
+
+To understand this process quantitatively, as well as associate probabilities to
+the two possible outcomes, it is important to be more quantitative. The correct
+approach is to consider the evolution of the value of the \emph{unperturbed}
+Hamiltonian (Eq.~\ref{eq:H}) as the spin evolves with the alignment torque. A
+point in zone III evolves such that $H$ is increasing until $H \approx H_{\rm
+sep}$ where $H_{\rm sep}$ is the value of $H$ along the separatrix, given by
+\begin{align}
+    H_{\rm sep} &\equiv H\p{\cos \theta_{\rm 4}, \phi_{\rm 4}},\nonumber\\
+        &\approx -\alpha\sin I - g\cos^2 I +
+            \mathcal{O}\p{\eta^2},\label{eq:def_Hsep}
+\end{align}
+where $\theta_4$ and $\phi_4$ are the coordinates of CS4. As the system evolves
+closer to the separatrix, the change in $H$ over each circulation cycle can be
+approximated by $\Delta H_-$, the change in $H$ along $\mathcal{C}_-$ (see
+Fig.~\ref{fig:1contours}). In general, we can compute $\Delta H_{\pm}$ the
+change over both legs of the separatrix with
 \begin{equation}
-    M_c = \int\limits_0^T \pd{\phi}{t}\epsilon \p{1 - \mu^2}\;\mathrm{d}t.
+    \Delta H_{\pm} \equiv \oint\limits_{\mathcal{C}_{\pm}}
+        \rd{H}{t}\;\mathrm{d}t.\label{eq:def_dHpm}
 \end{equation}
-Naively, we might claim that, since $\pd{\phi}{t}$ changes signs halfway through
-the interval of integration, that the only surviving component is $2\epsilon
-\bar{\mu}\mu'$, where $\bar{\mu} = \mu_4$ is the average value of $\mu$ and
-$\mu'$ is the fluctuation. This gives
+This can be simplified by using:
+\begin{align}
+    \rd{H}{t} &=
+            \pd{H}{(\cos \theta)}\rd{(\cos \theta)}{t}
+            + \pd{H}{\phi}\rd{\phi}{t},\nonumber\\
+        &= \p{\rd{(\cos\theta)}{t}}_{\rm tide} \rd{\phi}{t},\\
+    \Delta H_{\pm} &= \mp\frac{1}{t_{\rm s}}
+        \int\limits_0^{2\pi} \sin^2\theta\;\mathrm{d}\phi.
+\end{align}
+Thus, if we evaluate $H$ every time that a trajectory crosses $\phi = 0$, we see
+that it will initially be negative and increase for each circulation cycle until
+the system encounters the separatrix where $H - H_{\rm sep} < \Delta H_-$.
+
+When the system begins its separatrix-crossing orbit, $H$ at $\phi = 0$ is in
+the range $\s{H_{\rm sep} - \Delta H_-, H_{\rm sep}}$; call this value $H_{\rm
+i}$, as it is the initial value of the Hamiltonian on the separatrix-crossing
+orbit. The two endpoints of this range are denoted in Fig.~\ref{fig:6equils} by
+the black dot and cross at the left and right edges of the plot. Upon entering
+this range, the trajectory encounters the separatrix, and first traverses the
+vicinity of $\mathcal{C}_-$ then of $\mathcal{C}_+$, after which two possible
+outcomes can occur:
+\begin{itemize}
+    \item If the final value of $H$ at the end of this separatrix traversal,
+        denoted $H_{\rm f}$, satisfies $H_{\rm f} > H_{\rm sep}$, then the
+        trajectory enters the separatrix, following the red shaded region in
+        Fig.~\ref{fig:6equils}, and executes a zone III $\to$ II transition.
+
+    \item If $H_{\rm f} < H_{\rm sep}$, then the trajectory exits the separatrix
+        above CS4, following the yellow shaded region in Fig.~\ref{fig:6equils}
+        and executes a zone III $\to$ I transition.
+\end{itemize}
+Since $H_{\rm f} = H_{\rm i} + \Delta H_+ + \Delta H_-$, we find that if $H_{\rm
+i}$ is in the interval $\s{H_{\rm sep} - \Delta H_-, H_{\rm sep} - \Delta H_{-}
+- \Delta H_+}$, then the system executes a III $\to$ I transition, and if it
+is in the interval $\s{H_{\rm sep} - \Delta H_- - \Delta H_+, H_{\rm sep}}$,
+then the system executes a III $\to$ II transition. The values of $\cos
+\theta$ for which $H$ is equal to $H_{\rm sep} - \Delta H_-$, $H_{\rm sep} - \Delta
+H_- - \Delta H_+$, and $H_{\rm sep}$ (CS4) for $\phi = 0$ are shown in
+Fig.~\ref{fig:6equils} as the black cross, star, and dot at $\phi = 0$
+respectively. Finally, if the alignment torque is weak, then $\Delta H_- \sim
+\mathcal{O}\p{t_{\rm s}^{-1}}$ is small compared to the characteristic values of
+$H$, and $H_{\rm i}$ can be effectively considered as uniformly distributed over
+$\s{H_{\rm sep} - \Delta H_-, H_{\rm sep}}$. As such, we obtain that
 \begin{equation}
-    M_c = 2\int\limits_0^{2\pi}2\epsilon \frac{\eta \cos I}{1 + \eta \sin I}
-        \sqrt{2\eta \sin I \p{1 - \cos \phi}}\;\mathrm{d}\phi.
+    P_{\rm III \to II} = \frac{\Delta H_- + \Delta H_+}{\Delta H_-}.
+        \label{eq:def_P32_toy}
 \end{equation}
-Note that $M_c \propto \eta^{3/2}$, and since the gap opened $\Delta_c =
-\frac{M_c}{\pd{\phi}{t}} \propto \eta$, it seems like we're on the right track.
-Specifically:
-\begin{align}
-    M_c &\approx \epsilon 2\eta \cos I A_{sep},\\
-    \Delta_c &\approx 2\epsilon \eta \cos I \p{16 \sqrt{\eta \sin I}}
-        \frac{1}{\sqrt{4\eta \sin I}},\\
-        &\approx 16\epsilon \eta \cos I.
-\end{align}
-This also agrees exceedingly well with our simulations This then gives us
-hopping probability
-\begin{equation}
-    P_{hop} = \frac{\Delta_c}{\Delta_M} \approx
-        \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi}.
-\end{equation}
-This agrees perfectly with the cases we've run.
-
-\textbf{Note:} The full formula, by actually evaluating all the terms, comes out
-to be
-\begin{equation}
-    P_{hop} = \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi
-        \p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
-        + 8\eta^{3/2}\cos I \sqrt{\sin I}}.
-\end{equation}
-
-\section{Spin Evolution with Weak Tidal Friction}\label{ss:full_tide_prob}
 
@@
     \centering
-    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils0_06.png}
+    \includegraphics[width=\columnwidth]{../initial/0_eta/6manifolds0_20.png}
+    \caption{Plot illustrating the probabilistic origin of separatrix capture
+    for $\eta = 0.2$ and $\abs{gt_{\rm s}} = 10^3$. Yellow regions converge to CS1,
+    and red to CS2. The separatrix of the unperturbed system is shown as the
+    green line and splits due to the perturbative torque. To calculate the
+    boundaries (legend) separating the CS1 and CS2-approaching regions, points
+    near either the left or right copy of CS4 (L/R subscript) are evolved either
+    forwards or backwards ($\pm$ superscript). Within zone III, the regions of
+    phase space reaching CS1 and CS2 both become very thin (shown qualitatively
+    as the red dotted lines of decreasing width), reflecting the fact that the
+    outcome for a particular initial condition can be approximated as
+    probabilistic sufficiently far from the separatrix. Labeled in the black
+    cross, star, and dot at the left and right edges of the plot are where $H$
+    is equal to $H_{\rm sep} - \Delta H_-$, $H_{\rm sep} - \Delta H_- - \Delta
+    H_+$, and $H_{\rm sep}$ (Eqs.~\ref{eq:def_Hsep} and~\ref{eq:def_dHpm}).
+    }\label{fig:toy_hop_manifolds}
+\end{figure}
+
+To actually evaluate Eq.~\eqref{eq:def_P32_toy}, we use the parameterization for
+the separatrix \citep{su2020} for $\eta \ll 1$:
+\begin{equation}
+    \p{\cos \theta}_{\mathcal{C}_{\pm}} \approx
+        \eta \cos I \pm \sqrt{2\eta\sin I\p{1 - \cos \phi}}.
+        \label{eq:sep_theta}
+\end{equation}
+It can then be shown that
+\begin{align}
+    \Delta H_- &\approx \frac{2\pi}{t_{\rm s}} + \mathcal{O}(\eta),\\
+    \Delta H_+ + \Delta H_- &\approx
+        \frac{32 \eta^{3/2}\cos I \sqrt{\sin I}}{t_{\rm s}},\\
+    P_{\rm III \to II} &\approx
+        \frac{16 \eta^{3/2} \cos I \sqrt{\sin I}}{\pi}.\label{eq:P32_toy}
+\end{align}
+Figure~\ref{fig:1hist_toy} displays the agreement of Eq.~\eqref{eq:P32_toy} with
+direct numerical simulations of
+Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide_toy}), where good agreement is
+observed.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/3_toy3/1hist_toy.png}
+    \caption{Plot of $P_{\rm III \to II}$ as a function of $\eta$ for the toy
+    model. For each $\eta$, $150$ initial $\theta_0$ in zone III are evolved
+    until separatrix encounter, where their outcome is recorded. Shown in red is
+    Eq.~\eqref{eq:P32_toy}.}\label{fig:1hist_toy}
+\end{figure}
+
+Finally, we remark that the calculation above is just a more descriptive
+application of \emph{Melnikov's Method} \citep{g_and_h}. Melnikov's Method is a
+general integral that gives the degree of splitting of a ``homoclinic orbit''
+(here, the separatrix) induced by a small, possibly periodic, perturbation. The
+explicit connection between the evolution of the unperturbed Hamiltonian and
+distances between curves in phase space (as depicted in Fig.~\ref{fig:6equils})
+is provided by Melnikov's Method.
+
+\section{Spin Evolution with Weak Tidal Friction}\label{s:full_tide_prob}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils0_20.png}
     \caption{Schematic illustrating the evolution of the planet's spin due to
-    tidal friction. The green lines illustrate the directions of
+    tidal friction for $I = 5^\circ$ and $\eta_{\rm sync} = 0.2$. The green
+    lines illustrate the directions of
     Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}), while the black and blue
-    lines denote where the tidal $\Omega_{\rm s}'$ and $\theta'$ change signs
-    respectively. Overlaid are the obliquities of Cassini States 1 and 2, the
-    two Cassini States that are stable under tidal dissipation (see
-    Section~\ref{ss:tidal_eqs}). The points that are both Cassini States and
-    satisfy $\Omega_{\rm s}' = 0$ are the tidal Cassini Equilibria (tCE),
+    lines denote where the tidal $\dot{\Omega}_{\rm s}$ and $\dot{\theta}$
+    change signs respectively. Overlaid are the obliquities of Cassini States 1
+    and 2, the two Cassini States that are stable under tidal dissipation (see
+    Section~\ref{ss:tidal_equils}). The points that are both Cassini States and
+    satisfy $\dot{\Omega}_{\rm s} = 0$ are the tidal Cassini Equilibria (tCE),
     circled in green. Finally, the vertical red lines illustrate the
     $\Omega_{\rm s}$ below which tides causes tCE2 to become unstable; the
-    dashed and dotted lines correspond to values of $\epsilon = 10^{-2}$ and
-    $10^{-1}$ respectively.
-    }\label{fig:6equils}
+    dashed and dotted vertical red lines lines correspond to values of $\abs{gt_{\rm
+    a}}^{-1} = 10^{-2}$ and $10^{-1}$ respectively. }\label{fig:6equils}
 \end{figure}
 
-\subsection{Tidal Model: Equilibrium Tides}\label{sss:weaktide}
+\subsection{Tidal Model: Equilibrium Tides}\label{ss:weaktide}
 
@@
 equilibrium tides \citep{lai2012}. In this model, tides cause both $\uv{s}$ and
-$\Omega_{\rm s}$ to evolve following:
+$\Omega_{\rm s}$ to evolve on the characteristic tidal timescale $t_{\rm a}$:
 \begin{align}
-    \p{\rd{\uv{s}}{\tau}}_{\rm tide} &= \epsilon
+    \p{\rd{\uv{s}}{t}}_{\rm tide} &= \frac{1}{t_{\rm a}}
                 \s{\frac{2n}{\Omega_{\rm s}} - \p{\uv{s} \cdot \uv{l}}}
                     \uv{s} \times \p{\uv{l} \times \uv{s}}\label{eq:dsdt_tide},\\
-    \frac{1}{\Omega_{\rm s}}\p{\rd{\Omega_{\rm s}}{\tau}}_{\rm tide}
-        &= \epsilon \s{\frac{2n}{\Omega_{\rm s}}\p{\uv{s} \cdot
-            \uv{l}} - \p{1 + \p{\uv{s} \cdot \uv{l}}^2}},\label{eq:dWsdt_tide}
+    \frac{1}{\Omega_{\rm s}}\p{\rd{\Omega_{\rm s}}{t}}_{\rm tide}
+        &= \frac{1}{t_{\rm a}} \s{\frac{2n}{\Omega_{\rm s}}\p{\uv{s} \cdot
+            \uv{l}} - 1 - \p{\uv{s} \cdot \uv{l}}^2},\label{eq:dWsdt_tide}
 \end{align}
+where $t_{\rm a}$ is given by
+\begin{equation}
+    \frac{1}{t_{\rm a}} \equiv -\frac{L}{2S} \frac{\Omega_{\rm
+        s}}{2n}\frac{3k_2}{Q}\p{\frac{m}{M}}\p{\frac{R}{a}}^5 n.
+\end{equation}
+Here, $L = ma^2n$ and $S = kmR^2 \approx mR^2/4$ are the orbital and spin
+angular momenta of the inner planet, respectively. We neglect orbital evolution
+in this section since the time scale is longer than $t_{\rm a}$ by a factor of
+$\sim L / S \gg 1$, and so $t_{\rm a}$ is a constant. We will continue mostly
+consider the case where $\abs{gt_{\rm a}} \gg 1$.
+
+To understand the long-term behaviors of the system, we first consider its
+behavior near a CS\@. Specifically, we wish to understand whether initial
+conditions near a CS stay near the CS as the evolution of $\Omega_{\rm s}$
+causes the CSs to evolve. We first note that the evolution of
+$\Omega_{\rm s}$ does not drive spins towards or away from CSs: as long as it
+evolves sufficiently slowly \citep[adiabatically,][]{su2020}, conservation of
+phase space area ensures that trajectories will remain at a roughly fixed
+distance to stable equilibria of the system. Thus, Eq.~\eqref{eq:dsdt_tide}
+alone determines whether a point evolves towards or away from a nearby CS as
+$\Omega_{\rm s}$ evolves. Then, evaluating Eq.~\eqref{eq:lambda_approx} with
+$t_{\rm s} = t_{\rm a} / \p{2n / \Omega_{\rm s} - \cos \theta}$ (compare
+Eqs.~\ref{eq:dsdt_tide_toy} and~Eq.~\eqref{eq:dsdt_tide}), we see that CS2 is
+still always stable, while CS1 is becomes unstable for $\Omega_{\rm s} > 2n$.
+
+Using this result, we can then identify the long-term equilibria of the system
+(i.e.\ when including the evolution of $\Omega_{\rm s}$), as the long-term
+equilibria of the system must both satisfy $\dot{\Omega}_{\rm s} = 0$ and be a
+stable CS\@. Figure~\ref{fig:6equils} shows the behavior of
+Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) qualitatively in the coordinates
+$(\Omega_{\rm s}, \theta)$, along with the locations of CS1 and CS2. The two
+points circled in green in Fig.~\ref{fig:6equils} satisfy the criteria to be
+long-term equilibria, and we call them \emph{tidal Cassini Equilibria} (tCE). We
+number tCE1 and tCE2 the tCE that are in CSs 1 and 2 respectively.
+
+There are two important caveats that may change the existence and stability of
+the tCE\@. First, if $\eta \geq \eta_{\rm c}$ (Eq.~\eqref{eq:def_etac}) when
+$\Omega_{\rm s} \approx n$\footnote{Strictly, if $\eta$ is very close to
+$\eta_{\rm c}$, the planet's spin is slightly subsynchronous at tCE1, see
+Fig.~\ref{fig:6equils}.}, then tCE1 will not exist. We can define the constant
+parameter
+\begin{equation}
+    \eta_{\rm sync} \equiv \big(\eta\big)_{\Omega_{\rm s} = n},
+        \label{eq:def_etasync}
+\end{equation}
+where the existence of tCE1 then requires $\eta_{\rm sync} \leq \eta_{\rm
+c}$. Secondly, tCE2 may not be stable if the tidal phase shift is too large, as
+discussed in Section~\ref{ss:tidal_equils}. This threshold is shown as the
+vertical red lines in Fig.~\ref{fig:6equils} for a few choices of $t_{\rm a}$.
+
+\subsection{Spin Obliquity Evolution as a Function of Initial Spin Orientation}
+
+With this result, we can now consider the final fate of the inner planet's spin.
+We assume that the planet is initially rotating supersynchronously and adopt the
+fiducial initial spin frequency $\Omega_{\rm s, i} = 10n$. The final results are
+not sensitive on the specific initial spin as long as $\Omega_{\rm s, i} \gg n$.
+Then, for a given initial $\theta_0$ and $\phi_0$, the final outcome (either tCE1 and
+tCE2) of the system can be calculated by direct integration of
+Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}). In
+Fig.~\ref{fig:Hhists_0_06}, we show the final outcome for many randomly chosen
+$\theta_0$ and $\phi_0$ for $\eta_{\rm sync} = 0.06$ and $I = 5^\circ$. We see
+that tCE1 is generally reached for spins initially in zone I, tCE2 is generally
+reached for spins initially in zone II, and a probabilistic outcome is observed
+for spins initially in zone III, very similar to the results found for the toy
+model in Section~\ref{s:toy_model}. Figures~\ref{fig:Hhists_0_20}
+and~\ref{fig:Hhists_0_70} show the same results but for $\eta_{\rm sync} = 0.2$
+and $\eta_{\rm sync} = 0.7$. As $\eta_{\rm sync}$ is increased, more initial
+conditions reach tCE2. This is both because there are more systems initially in
+zone II and because more systems initially in zone III execute a III $\to$ II
+transition upon separatrix encounter.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
+    \caption{\emph{Left:} Each dot indicates which tCE a given initial condition
+    $(\theta_{\rm i}, \phi_{\rm i})$ evolve towards (labeled in legend), for
+    $\eta_{\rm sync} = 0.06$ and $I = 5^\circ$. The
+    separatrix is shown as the black line. Note that points above the
+    separatrix evolve towards tCE1, points inside the separatrix evolve towards
+    tCE2, and points below the separatrix have a probabilistic outcome.
+    \emph{Right:} Histogram of which tCE a given initial obliquity $\theta_{\rm
+    i}$ evolves towards.}\label{fig:Hhists_0_06}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
+    \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\eta_{\rm sync} =
+    0.2$.}\label{fig:Hhists_0_20}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_70_5.png}
+    \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\eta_{\rm sync} =
+    0.7$. Note that even points above the separatrix can evolve towards tCE2
+    here.}\label{fig:Hhists_0_70}
+\end{figure}
+
+\subsubsection{Analytical Calculation of Resonance Capture Probability
+}\label{ss:phop_weaktide}
+
+Even when including the evolution of $\Omega_{\rm s}$, and therefore the
+spin-orbit precession frequency $\alpha$, the probabilities of the III $\to$ I
+and III $\to$ II transitions upon separatrix encounter can be computed. The
+calculation is more involved than that presented in
+Section~\ref{ss:toy_outcomes}, and also incorporates the seminal resonance
+capture theory of \citet{henrard1982}. In the interest of clarity, we give an
+overview of the approach, and present the analytical results of the calculation
+in Appendix~\ref{app:sep_crossing_dynamics}.
+
+In Section~\ref{ss:toy_outcomes}, we found that keeping track of the value of
+$H$, the value of the
+unperturbed Hamiltonian, allowed us to calculate the probabilities of the
+various outcomes of separatrix encounter. Specifically, the outcome upon separatrix
+encounter is determined by the value of $H$ at the start of the
+separatrix-crossing orbit relative to $H_{\rm sep}$, the value of $H$ along the
+separatrix. When the spin is also evolving, $H_{\rm sep}$ is also
+changing during the separatrix-crossing orbit, and the discussion in
+Section~\ref{ss:toy_outcomes} must be generalized to account for this. Instead
+of focusing on the evolution of $H$ along a trajectory, we instead follow the
+evolution of
+\begin{equation}
+    K \equiv H - H_{\rm sep}.
+\end{equation}
+Note that $K > 0$ inside the separatrix, and $K < 0$ outside. Then, the outcome
+of the separatrix-crossing orbit is largely the same as discussed in
+Section~\ref{ss:toy_outcomes}. First, we must compute the change in $K$ along
+the legs of the separatrix. We define $\Delta K_{\pm}$ by generalizing
+Eq.~\eqref{eq:def_dHpm} very naturally:
+\begin{align}
+    \Delta K_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}
+        - \rd{H_{\rm sep}}{t}\;\mathrm{d}t.\label{eq:def_dK_weaktide}
+\end{align}
+Here, however, note that $\mathcal{C}_{\pm}$ depends on the value of
+$\Omega_{\rm s}$ upon separatrix encounter! Since there is no closed form
+solution for $\Omega_{\rm s}(t)$, the probabilities of the various outcomes can
+only be determined as a function of the system properties at separatrix
+encounter, and not as a simple function of the initial conditions.
+
+Then, if we call $K_i$ the value of $K$ at the start ($\phi = 0$) of the
+separatrix-crossing orbit, $K_i > -\Delta K_+ - \Delta K_-$ gives a III
+$\to$ II transition and eventual evolution towards tCE2 while $-\Delta K_- < K_i
+< -\Delta K_- - \Delta K_+$ gives a III $\to$ I transition and ultimate
+evolution towards tCE1. Thus, we find that the probability of a III $\to$ II
+transition is given by
+\begin{equation}
+    P_{\rm III \to II} = \frac{\Delta K_+ + \Delta K_-}{\Delta
+        K_-}.\label{eq:def_pc_weaktide}
+\end{equation}
+The analytical approximate forms for $\Delta K_{\pm}$ are given in by
+Eq.~\eqref{eq:app_deltaK}. Note that
+Eqs.~(\ref{eq:def_dK_weaktide},~\ref{eq:def_pc_weaktide}) are equivalent to the
+separatrix capture result of \citet{henrard1982} when $\cos \theta$ is not
+evolving \citep{henrard1987}. Here, we argue that this classic calculation can
+be unified with the calculation given in Section~\ref{ss:toy_outcomes} to give
+an accurate prediction of separatrix encounter outcome probabilities in the
+presence of both a dissipative perturbation and a parametric variation of the
+Hamiltonian.
+
+To compare Eq.~\eqref{eq:def_pc_weaktide} with numerical simulations, we can
+integrate Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) for
+many initial conditions in Zone III while evaluating $P_{\rm III \to II}$ (and
+thus also obtaining $P_{\rm III \to I} = 1 - P_{\rm III \to II}$) for
+each simulation at the moment it encounters the separatrix. If the theory is
+correct, the total numbers of systems converging to each of tCE1 and tCE2
+should be equal to those predicted by the sums of the calculated probabilities.
+In Fig.~\ref{fig:pc_fits_0_06}, we show the agreement of this semi-analytic
+procedure with the numerical results displayed earlier in the right
+panel of Fig.~\ref{fig:Hhists_0_06}. Good agreement is observed.
+Figs.~\ref{fig:pc_fits_0_20} and~\ref{fig:pc_fits_0_70} show the same for
+Figs.~\ref{fig:Hhists_0_20} and~\ref{fig:Hhists_0_70}. Mostly satisfactory
+agreement is observed. Thus, we conclude that the outcomes of separatrix
+encounter are accurately predicted by Eq.~\eqref{eq:def_pc_weaktide}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_06_5.png}
+    \caption{Comparison of the right hand panel of Fig.~\ref{fig:Hhists_0_06}
+    (red dots) with a semi-analytic calculation (blue line). The semi-analytic
+    calculation is performed by numerically integrating
+    Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) on a grid of initial
+    conditions uniform in $\cos \theta_{\rm i}$ and $\phi_{\rm i}$ until
+    separatrix encounter, then using the $\Omega_{\rm s}$ at separatrix
+    encounter to evaluate (TODO) to analytically compute the probability of
+    evolution into tCE2.}\label{fig:pc_fits_0_06}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_20_5.png}
+    \caption{Same as Fig.~\ref{fig:pc_fits_0_06} but for $Omega_{\rm c} =
+    0.2$, shown in Fig.~\ref{fig:Hhists_0_20}.}\label{fig:pc_fits_0_20}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_70_5.png}
+    \caption{Same as Fig.~\ref{fig:pc_fits_0_06} but for $\eta_{\rm sync} =
+    0.7$, shown in Fig.~\ref{fig:Hhists_0_70}.}\label{fig:pc_fits_0_70}
+\end{figure}
+
+\subsection{Spin Obliquity Evolution as a Function of Precession Strength}
+
+In the previous section, we considered the outcome as a function of the initial
+spin orientation, specified by $\theta_0$ and $\phi_0$. In this section, we
+consider the distribution of outcomes when averaging over a distribution of
+initial spin orientations. For simplicity, we just consider $\uv{s}$ being
+isotropically distributed. Figure~\ref{fig:probs} shows this for $I
+= 5^\circ$ as a function of $\eta_{\rm sync}$.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5probs_5.png}
+    \caption{\emph{Top:} Total probability of ending up in tCE2 (red dots) for
+    $I = 5^\circ$ for a range of $\eta_{\rm sync}$. \emph{Bottom:}
+    obliquities of the two possible tCE.}\label{fig:probs}
+\end{figure}
 where $\epsilon$ is the dimensionless tidal evolution rate, given by
@@
     \epsilon \equiv{}& -\frac{1}{gt_a}\frac{L}{2S} \frac{\Omega_{\rm s}}{2n},\\
-        % = \frac{1}{\cos I} \frac{2k_2}{Q} \frac{n}{\Omega_{\rm c}},\\
     \frac{1}{t_a} ={}& \frac{3k_2}{Q}\p{\frac{m}{M}}\p{\frac{R}{a}}^5 n,\\
@@
 \end{align}
-Here, $L = ma^2n$ and $S = kmR^2 \approx mR^2/4$ are the orbital and spin
-angular momenta of the inner planet, respectively. In Eq.~\eqref{eq:dsdt_tide},
-it is clear that tides only acts on the polar component of $\uv{s}$,
-i.e.\ $\theta$, and not the azimuthal component $\phi$. As such,
-the effect of tides on the dynamics of the system can be qualitatively
-understood in $(\Omega_{\rm s}, \theta)$ space. Figure~\ref{fig:6equils} shows
-the behavior of Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) in a few
-characteristic regions of $(\Omega_{\rm s}, \theta)$ space.
 
-Component form
+\section{Applications}
+
+\subsection{Application to SE+HJ Systems}\label{ss:disc_sehj}
+
+Consider a system consisting of an inner Super-Earth (SE) and an exterior cold
+Jupiter (CJ). For this system, Eq.~\eqref{eq:def_etasync} can be evaluated
 \begin{align}
-    \rd{\theta}{t} &= g\sin I \sin \phi -
-        \epsilon \sin \theta,\label{eq:ds_fullq}\\
-    \rd{\phi}{t} &= -\alpha\cos\theta
-        - g\p{\cos I + \sin I \cot \theta \cos \phi}\label{eq:ds_fullphi},\\
-    \rd{\Omega_{\rm s}}{t}
-        &= \epsilon \s{2n \cos \theta
-            - \Omega_{\rm s}\p{1 + \cos^2\theta}}\label{eq:ds_fulls}.
-\end{align}
-
-For the parameters considered here, the tidal evolution in $\Omega_{\rm s}$ and
-$\theta$ occurs over characteristic time scale $2 \times 10^8\;\mathrm{yr}$.
-Note that while the semimajor axis $a$ is not strictly constant under the
-influence of tidal dissipation, $\dot{a} / \dot{\theta} \sim S / L \ll 1$
-\citep{lai2012} and the evolution of $a$ can be safely neglected in this paper.
-
-Armed with the intuition provided by the toy model in
-Section~\ref{ss:toy_model}, we now study the equations of motion including the
-full weak tidal friction theory, given by
-Eqs.~(\ref{eq:ds_fullq}--\ref{eq:ds_fulls}). We imagine that the inner planet is
-born rapidly spinning, but for computational reasons, we restrict the initial
-spin to be $\Omega_{\rm s, i} = 10n$. The final results are not sensitive on the
-specific initial spin as long as $\Omega_{\rm s, i} \gg n$. The hierarchy of the
-system is determined by the parameter $\Omega_{\rm c}$, given by
-Eq.~\eqref{eq:def_Wc}, for which we choose a few representative values. Then,
-for a given initial $\theta_0$ and $\phi_0$, the final outcome (between tCE1 and
-tCE2) of the system can
-be calculated. In Fig.~\ref{fig:Hhists_0_06}, we show the final outcome for many
-randomly chosen $\theta_0$ and $\phi_0$ for $\Omega_{\rm c} = 0.06$ and $I =
-5^\circ$. We see that tCE1 is generally reached for spins initially in Zone I,
-tCE2 is generally reached for spins initially in Zone II, and a probabilistic
-outcome is observed for spins initially in Zone III, very similar to the results
-found for the toy model in Section~\ref{ss:toy_model}.
-Figures~\ref{fig:Hhists_0_20,fig:Hhists_0_70} show the same results but for
-$\Omega_{\rm c} = 0.2$ and $\Omega_{\rm c} = 0.7$. We see that more initial
-conditions are able to end up in tCE2, mostly because the initial Zone II is
-larger. In all three examples, probabilistic resonance capture for initial
-conditions in Zone III is responsible for a significant fraction of systems that
-end up in tCE2.
-\begin{figure}
-    \centering
-    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
-    \caption{\emph{Left:} Each dot indicates which tCE a given initial condition
-    $(\theta_{\rm i}, \phi_{\rm i})$ evolve towards (labeled in legend), for
-    $\Omega_{\rm c} = 0.06n$ and $I = 5^\circ$. The
-    separatrix is shown as the black line. Note that points above the
-    separatrix evolve towards tCE1, points inside the separatrix evolve towards
-    tCE2, and points below the separatrix have a probabilistic outcome.
-    \emph{Right:} Histogram of which tCE a given initial obliquity $\theta_{\rm
-    i}$ evolves towards.}\label{fig:Hhists_0_06}
-\end{figure}
-\begin{figure}
-    \centering
-    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
-    \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\Omega_{\rm c} =
-    0.2n$.}\label{fig:Hhists_0_20}
-\end{figure}
-\begin{figure}
-    \centering
-    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_70_5.png}
-    \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\Omega_{\rm c} =
-    0.7n$. Note that even points above the separatrix can evolve towards tCE2
-    here.}\label{fig:Hhists_0_70}
-\end{figure}
-
-Similarly to \citet{su2020}, these probabilities are the result of separatrix
-crossings. However, the calculation differs from \citet{su2020}: since the
-perturbation is dissipative in phase space (i.e.\ it does not conserve phase
-space area), analysis following \citet{henrard1982} is not sufficient. A more
-general theory of separatrix crossing is still able to predict the outcome
-probabilities, extending the results in Section~\ref{ss:toy_model}.
-Appendix~\ref{app:probs} gives the appropriate generalization, which gives the
-resonance capture probability $P_{\rm III \to II}$ as a function of $\eta$ upon
-separatrix encounter.
-
-We can apply this probability to calculate the probabilities of the two outcomes
-when a numerically-integrated trajectory encounters the separatrix, and from
-this obtain a semi-analytical prediction of the distribution of outcomes. In
-Fig.~\ref{fig:pc_fits_0_06}, we show the same histogram as the vertical panel of
-Fig.~\ref{fig:Hhists_0_06} alongside the semi-analytical prediction. Good
-qualitative agreement is observed. Figs.~\ref{fig:pc_fits_0_20,fig:pc_fits_0_70}
-show the same for Figs.~\ref{fig:Hhists_0_20, fig:Hhists_0_70}.
-\begin{figure}
-    \centering
-    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_06_5.png}
-    \caption{Comparison of the right hand panel of Fig.~\ref{fig:Hhists_0_06}
-    (red dots) with a semi-analytic calculation (blue line). The semi-analytic
-    calculation is performed by numerically integrating
-    Eqs.(~\ref{eq:ds_fullq}--\ref{eq:ds_fulls}) on a grid of initial
-    conditions uniform in $\cos \theta_{\rm i}$ and $\phi_{\rm i}$ until
-    separatrix encounter, then using the $\Omega_{\rm s}$ at separatrix
-    encounter to evaluate (TODO) to analytically compute the probability of
-    evolution into tCE2.}\label{fig:pc_fits_0_06}
-\end{figure}
-\begin{figure}
-    \centering
-    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_20_5.png}
-    \caption{Same as Fig.~\ref{fig:pc_fits_0_06} but for $\Omega_{\rm c} =
-    0.2n$, shown in Fig.~\ref{fig:Hhists_0_20}.}\label{fig:pc_fits_0_20}
-\end{figure}
-\begin{figure}
-    \centering
-    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_70_5.png}
-    \caption{Same as Fig.~\ref{fig:pc_fits_0_06} but for $\Omega_{\rm c} =
-    0.7n$, shown in Fig.~\ref{fig:Hhists_0_70}.}\label{fig:pc_fits_0_70}
-\end{figure}
-
-\subsection{Outcomes for Distribution of Initial Spin Orientations
-}\label{ss:s_c_dist}
-
-Here, we define $\Omega_{\rm c}$ to be the critical spin where the
-precession frequencies are equal, i.e.
-% ((3 Mjup) / (4 Msun) * (0.4 / 5)^3) /
-%   (1.5 * Msun / (4 * pi / 3 * (3 g\cm#3)) / (0.4 AU)^3)
-\begin{align}
-    \Omega_{\rm c} \equiv{}& -\frac{g}{\alpha}\Omega_{\rm s},\\
-    \frac{\Omega_{\rm c}}{n} ={}& 0.33 \p{\frac{k}{k_{\rm q}}}
+    \eta_{\rm sync} ={}& 0.33 \p{\frac{k}{k_{\rm q}}}
             \p{\frac{m_{\rm p}}{M_{\rm J}}}
@@
             \p{\frac{\rho}{3 \; \mathrm{g/cm}^3}}
-            \p{\frac{M_\star}{M_{\odot}}}^{-2}.\label{eq:def_Wc}
+            \p{\frac{M_\star}{M_{\odot}}}^{-2}.\label{eq:sehj_etasync}
 \end{align}
@@
 the tidal equilibrium.
-
-In the previous section, we considered the outcome as a function of the initial
-spin orientation, specified by $\theta_0$ and $\phi_0$. In this section, we
-consider the distribution of outcomes when averaging over a distribution of
-initial spin orientations. For simplicity, we just consider $\uv{s}$ being
-isotropically distributed. Figure~\ref{fig:probs} shows this for $I
-= 5^\circ$ as a function of $\Omega_{\rm c}$.
-\begin{figure}
-    \centering
-    %\includegraphics[width=\columnwidth]{../initial/1_weaktide/5probs_5.png}
-    \caption{\emph{Top:} Total probability of ending up in tCE2 (red dots) for
-    $I = 5^\circ$ for a range of $\Omega_{\rm c}$. \emph{Bottom:}
-    obliquities of the two possible tCEs.}\label{fig:probs}
-\end{figure}
 
@@
 
-\section{Convergence of Initial Conditions Inside the Separatrix to tCE2
-}\label{sss:cs_stab2}
+\section{Convergence of Initial Conditions Inside the Separatrix to CS2
+}\label{app:cs_stab2}
 
-Based on the results from the previous section, we intuitively expect that all
-initial conditions in Zone II, i.e.\ inside the separatrix, will remain near
-CS2, and eventually converge to tCE2. However, this is not immediately
-justified, since not all points in Zone II are necessarily close enough to CS2
-for the linear analysis in Section~\ref{ss:tidal_eqs} to be valid. We present an
-alternative calculation illustrating that all points in Zone II remain near CS2.
-For simplicity, we neglect the evolution of $\Omega_{\rm s}$ here and take
-$\eta$ to be constant; the full calculation presented in
-Appendix~\ref{app:sep_crossing_dynamics} includes the evolution of $\Omega_{\rm
-s}$ and reproduces this result.
+In Section~\ref{ss:tidal_equils}, we studied the stability of the CSs under of
+tidal alignment torque given by Eq.~\eqref{eq:dsdt_tide_toy}, finding that CS2
+is locally stable. Later, in Section~\ref{ss:toy_outcomes}, we found that all
+initial conditions within the separatrix converge to CS2, which is not
+guaranteed by local stability of CS2. In this section, we give an analytic
+demonstration that all points inside the separatrix indeed converge to CS2,
+focusing on the case where $\eta \ll 1$.
 
-The objective is to determine the change in $H$, the value of the unperturbed
-Hamiltonian, over a single libration cycle. If the system's has initial $H_0
-\equiv H\p{\theta_0, \phi_0} = H_{\rm sep} + \Delta H$ where
+Similarly to the analytic calculation in Section~\ref{ss:toy_outcomes}, we seek
+to compute the change in the unperturbed Hamiltonian over a single libration
+cycle. To calculate the evolution of $H$, we first parameterize the unperturbed
+trajectory (similarly to Eq.~\ref{eq:sep_theta}). For initial conditions inside
+the separatrix, the value of $H$ can be written $H = H_{\rm sep} + \Delta H$
+where $\Delta H > 0$, and the two legs of the libration trajectory can be
+written:
 \begin{align}
-    H_{\rm sep} &\equiv H\p{\cos \theta_{\rm 4}, \phi_{\rm 4}},\\
-        &\approx -\sin I + \frac{\eta}{2}\cos^2 I +
-            \mathcal{O}\p{\eta^2},\label{eq:def_Hsep}
-\end{align}
-is the value of $H$ along the separatrix, and $\Delta H > 0$ for initial
-conditions inside the separatrix, then the unperturbed trajectory $\theta(\phi)$
-can then be written explicitly via:
-\begin{align}
-    H_{\rm sep} + \Delta H &= -\frac{\cos^2\theta}{2\eta} + \cos\theta \cos I
-            - \sin I \cos \phi,\\
-    % \cos \theta &=
-    %     \eta \cos I \pm \eta\sqrt{\cos^2 I - 2
-    %         \p{H_{\rm sep} + \Delta H + \sin I \cos \phi} / \eta},\\
     \cos \theta_{\pm} &\approx
@@
 \end{align}
-We have taken $\sin \theta \approx 1$, a good approximation in Zone II since
-$\eta \ll 1$. When $\Delta H = 0$, this reproduces Eq.~(B5) of \citet{su2020}.
-When $\Delta H > 0$, there are some values of $\phi$ for which no solutions of
-$\theta$ exist, reflecting the fact that the libration does not extend over the
-full interval $\phi \in [0, 2\pi]$. During a libration cycle, $\theta_-$
-[$\theta_+$] is traversed while $\phi' > 0$ [$\phi' < 0$], i.e.\ the trajectory
-librates counterclockwise in $(\cos \theta, \phi)$ phase space (see
+We have taken $\sin \theta \approx 1$, a good approximation in zone II since
+$\eta \ll 1$. Note that there are some values of $\phi$ for which no solutions
+of $\theta$ exist, reflecting the fact that the libration cycle does not extend
+over the full interval $\phi \in [0, 2\pi]$. During a libration cycle,
+$\theta_-$ [$\theta_+$] is traversed while $\phi' > 0$ [$\phi' < 0$], i.e.\ the
+trajectory librates counterclockwise in $(\cos \theta, \phi)$ phase space (see
 Fig.~\ref{fig:1contours}).
 
-The above calculation assumes $H$ is constant, yielding the unperturbed
-trajectory. The leading order change to $H$ can be computed by integrating
-$\rdil{H}{\tau}$ along this trajectory, where $\rdil{H}{\tau}$ is given by
+The leading order change to $H$ over a single libration cycle can then computed by
+integrating $\rdil{H}{t}$ along this trajectory, yielding:
 \begin{align}
-    \rd{H}{\tau} &=
-            \pd{H}{(\cos \theta)}\rd{(\cos \theta)}{\tau}
-            + \pd{H}{\phi}\rd{\phi}{\tau},\nonumber\\
-        &= -\p{\rd{(\cos\theta)}{\tau}}_{\rm tide} \rd{\phi}{\tau}.
-            \label{eq:dHdt_toyf}
+    \oint \rd{H}{t}\;\mathrm{d}t
+        &= \oint \p{\rd{(\cos \theta)}{t}}_{\rm tide}
+            \;\mathrm{d}\phi,\nonumber\\
+        &= \int\limits_{\phi_{\min}}^{\phi_{\max}}
+                \frac{1}{t_{\rm s}}
+                \p{\sin^2\theta_- - \sin^2\theta_+} \;\mathrm{d}\phi\nonumber\\
+        &= \frac{1}{t_{\rm s}}
+            \int\limits_{\phi_{\min}}^{\phi_{\max}}
+                4\eta \cos I \sqrt{2\eta\s{\sin I\p{1 - \cos \phi} - \Delta H}}
+                \;\mathrm{d}\phi > 0.
 \end{align}
-We have used Hamilton's equations for the canonically conjugate variables $\cos
-\theta$ and $\phi$ to eliminate the non-tidal contributions. The total change in
-$H$ over a single cycle is then:
+Here, $\phi_{\min} > 0$ and $\phi_{\max} < 2\pi$ are defined such that the
+trajectory librates over $\phi \in \s{\phi_{\min}, \phi_{\max}}$. Thus, $H$ is
+strictly increasing for all initial conditions inside the separatrix, and they
+all converge to CS2.
+
+\section{Separatrix Crossing Probability with Weak Tidal Friction
+}\label{app:sep_crossing_dynamics}
+
+In this appendix, we analytically calculate $\Delta K_{\pm}$ for use in
+Eq.~\eqref{eq:def_pc_weaktide} to calculate the probabilities of the two
+possible transitions upon separatrix encounter. We first rewrite the full
+equations of motion for the planet's spin including weak tidal friction in
+component form:
 \begin{align}
-    \oint \rd{H}{\tau}\;\mathrm{d}\tau ={}& \oint \rd{H}{\tau}
-        \rd{\tau}{\phi}\;\mathrm{d}\phi,\nonumber\\
-        ={}& \oint -\p{\rd{(\cos \theta)}{\tau}}_{\rm tide}
-            \;\mathrm{d}\phi,\nonumber\\
-        ={}&
-            \int\limits_{\phi_{\min}}^{\phi_{\max}}
-                \epsilon \p{\frac{2n}{\Omega_{\rm s}} - \cos \theta_-}
-                \sin^2\theta_- \;\mathrm{d}\phi\nonumber\\
-            &+ \int\limits_{\phi_{\min}}^{\phi_{\max}}
-                \epsilon \p{\frac{2n}{\Omega_{\rm s}} - \cos \theta_+}
-                \sin^2\theta_+ \;\mathrm{d}\phi,\nonumber\\
-        \approx{}&
-            \int\limits_{\phi_{\min}}^{\phi_{\max}}
-                \epsilon \p{\frac{2n}{\Omega_{\rm s}}\sin^2\theta_- - \cos \theta_-}
-                 \;\mathrm{d}\phi\nonumber\\
-            &+ \int\limits_{\phi_{\min}}^{\phi_{\max}}
-                \epsilon \p{\frac{2n}{\Omega_{\rm s}}\sin^2\theta_+ - \cos \theta_+}
-                \;\mathrm{d}\phi.
-\end{align}
-Finally, for every $\phi$, $\sin \theta_- \geq \sin \theta_+$ and $\cos \theta_-
-\leq \cos \theta_+$ with equality only at the endpoints of the libration cycle
-where $\theta_- = \theta_+$. As such, the total change in $H$ over a libration
-cycle is positive, and we conclude that every trajectory starting in Zone II
-remains near CS2 under the effect of tidal dissipation even when not
-infinitesimally close to CS2 initially.
-
-\section{Separatrix Crossing Theory}\label{app:sep_crossing_dynamics}
-
-Thus, the natural extension of the two above results should be
-\begin{align}
-    \Delta_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}\;\mathrm{d}t,\\
-        &= \oint_{\mathcal{C}_{\pm}}
-            \dot{\mu}^{(1)} + \frac{\dot{s}^{(1)}}{\dot{\phi}^{(0)}}
-                \p{\pd{H}{s} - \pd{H_4}{s}}\;\mathrm{d}\phi.
+    \rd{\theta}{t} &= g\sin I \sin \phi -
+        \frac{1}{t_{\rm a}} \sin \theta,\label{eq:ds_fullq}\\
+    \rd{\phi}{t} &= -\alpha\cos\theta
+        - g\p{\cos I + \sin I \cot \theta \cos \phi}\label{eq:ds_fullphi},\\
+    \rd{\Omega_{\rm s}}{t}
+        &= \frac{1}{t_{\rm a}} \s{2n \cos \theta
+            - g\Omega_{\rm s}\p{1 + \cos^2\theta}}\label{eq:ds_fulls}.
 \end{align}
 
-\subsection{Separatrix Crossing Probability: Tidal Friction}\label{app:probs}
+Note that Eq.~\eqref{eq:def_dK_weaktide} can be rewritten
 \begin{align}
-    \rd{\p{\Delta H}}{\tau} &=
-            \pd{H}{(\cos \theta)}\rd{(\cos \theta)}{\tau}
-            + \pd{H}{\phi}\rd{\phi}{\tau}
-            + \pd{H}{\Omega_{\rm s}}\rd{\Omega_{\rm s}}{\tau}
-            - \pd{H_{\rm sep}}{\Omega_{\rm s}}\rd{\Omega_{\rm s}}{\tau}
-                    ,\nonumber\\
-        &= -\p{\rd{(\cos\theta)}{\tau}}_{\rm tide} \rd{\phi}{\tau}
-            + \p{\pd{H}{\Omega_{\rm s}} - \pd{H_{\rm sep}}{\Omega_{\rm s}}}
-            \rd{\Omega_{\rm s}}{\tau},\label{eq:dHdt_schematic}\\
-    \frac{1}{\epsilon}\rd{(\Delta H)}{\tau} &\approx
-            \sin^2\theta\p{\frac{2n}{\Omega_{\rm s}} - \cos\theta}
-                \rd{\phi}{\tau} +
-                \s{\frac{\cos^2\theta}{2\Omega_{\rm c}} - \frac{\Omega_{\rm
-                c}}{2\Omega_{\rm s}^2}\cos^2 I}\rd{\Omega_{\rm
-                s}}{\tau}.\label{eq:dHdt_final}
+    \Delta K_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}
+        - \rd{H_{\rm sep}}{t}\;\mathrm{d}t
+        \nonumber\\
+        &= \oint_{\mathcal{C}_{\pm}}
+           \p{\rd{(\cos\theta)}{t}}_{\rm tide}
+            + \frac{\dot{\Omega}_{\rm s}}{\dot{\phi}}
+            \p{\pd{H}{s} - \pd{H_{\rm sep}}{s}}\;\mathrm{d}\phi
+                \label{eq:app_dhpm}.
 \end{align}
 
-Application of the full formula presented in
-Section~\ref{app:sep_crossing_dynamics}. The key result is that one integrates
-\begin{equation}
-    \rd{(\Delta H)}{(\epsilon t)} \approx
-            (1 - \mu^2)\p{\frac{2\Omega}{s} - \mu}
-                \dot{\phi}^{(0)} + 2\Omega\p{1 + \frac{s}{2\Omega}(1 + \mu^2)}
-                \s{\frac{\mu^2}{2s_c} - \frac{s_c}{2s^2}\cos^2 I}.
-\end{equation}
-
-An analytical form that holds when $s \gg s_c$ is:
+We then evaluate $\Delta K_{\pm}$ by integrating along the separatrix, using the
+parameterized form for $\p{\cos \theta}_{\mathcal{C}_\pm}$ given by
+Eq.~\eqref{eq:sep_theta}. Note that we must use the value of $\eta$ at the
+moment of separatrix encounter, as the evolution of $\Omega_{\rm s}$ changes the
+spin-orbit precession frequency $\alpha$ \textcolor{red}{NB\@: I haven't analytically
+recalculated this formula recently, only compared numerically, so there may be
+small typos, though nothing that changes the accuracy of the result}:
 \begin{align}
-    \frac{\Delta_{\pm}}{\epsilon} ={}&
+    \Delta K_{\pm} ={}& \oint_{\mathcal{C}_{\pm}}
+        \frac{1}{t_{\rm s}}\sin^2\theta
+            \p{\frac{2n}{\Omega_{\rm s}} - \cos\theta}
+         +
+            \s{\alpha\frac{\cos^2\theta}{2} + g\frac{\Omega_{\rm
+            c}}{2\Omega_{\rm s}^2}\cos^2 I}\rd{\Omega_{\rm
+            s}}{t}\rd{t}{\phi}\;\mathrm{d}\phi\\
+     \approx{}& \oint_{\mathcal{C}_{\pm}}
+        \frac{1}{t_{\rm s}}\sin^2\theta
+            \p{\frac{2n}{\Omega_{\rm s}} - \cos\theta}
+        + \frac{1}{t_{\rm s}}\frac{n}{\Omega_{\rm s}\eta}
+            \s{\p{\cos \theta}_{\mathcal{C}_{\pm}} - \frac{\Omega_{\rm s}}{2n}}
+            \s{2 \cos I \pm \sqrt{2 \sin I\p{1 - \cos \phi} / \eta}}
+            \;\mathrm{d}\phi,\\
+    t_{\rm s} \Delta K_{\pm} \approx{}&
         -2\cos I\p{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
-        \pm 2\pi s\cos I
-        + \eta \cos I \p{-8\sqrt{\sin I / \eta}}
-            + \frac{s}{2}8\sqrt{\sin I/\eta}\nonumber\\
-        &+ \frac{2\Omega}{s}\p{\mp 2\pi\p{1 - 2\eta \sin I}
+        \pm 2\pi \frac{\Omega_{\rm s}}{n}\cos I
+        - 8\eta \cos I \sqrt{\sin I / \eta}
+            + \frac{4\Omega_{\rm s}}{n}\sqrt{\sin I/\eta}\nonumber\\
+        &+ \frac{2n}{\Omega_{\rm s}}\p{\mp 2\pi\p{1 - 2\eta \sin I}
             + 16\cos I \eta^{3/2}\sqrt{\sin I}}
@@
             \pm 2 \pi \eta \cos I
-            - \frac{64}{3} \p{\eta \sin I}^{3/2}.
+            - \frac{64}{3} \p{\eta \sin I}^{3/2}.\label{eq:app_deltaK}
 \end{align}
-The capture probability is then just
-\begin{equation}
-    P_c = \frac{\Delta_+ + \Delta_-}{\Delta_-}.
-\end{equation}
+This is used in Eq.~\eqref{eq:def_pc_weaktide} to semi-analytically compute the
+tCE2 probabilities (blue curves) in
+Figs.~\ref{fig:pc_fits_0_06}--\ref{fig:pc_fits_0_70}.
 
@@
 \end{document}
-% chktex 17

### 2021-04-26 initial/99_misc/2_rand_plots.py

@@ -43,14 +43,14 @@ def roots(I, eta):
             roots.append(opt.bisect(f, qi - dq, qi + dq))
         return np.array(roots)
 
-def get_cs(I):
+def get_cs(I, num_pts=100):
     ''' gets list of cassini states at an uneven grid of etas '''
     etac = get_etac(I)
     eps = 1e-5
     min_eta, max_eta = etac / 30, etac * 30
     etas = np.concatenate((
-        np.log(np.linspace(np.exp(min_eta), np.exp(etac - eps), 100)),
-        np.exp(np.linspace(np.log(etac + eps), np.log(max_eta), 100)),
+        np.log(np.linspace(np.exp(min_eta), np.exp(etac - eps), num_pts)),
+        np.exp(np.linspace(np.log(etac + eps), np.log(max_eta), num_pts)),
     ))
     cs_vals = [[], [], [], []]
 
@@ -107,7 +107,7 @@ def plot_cs(I=np.radians(5)):
     plt.clf()
 
 def plot_eigens(I=np.radians(5)):
-    etas, cs_vals, etas_four, etac = get_cs(I)
+    etas, cs_vals, etas_four, etac = get_cs(I, num_pts=200)
     def lambda2(eta, q, sign):
         # note that the 4 CSs are 0, pi/2, -pi, -pi/2 by convention, which
         # correspond to sign choices of -1 for all of them.
@@ -133,7 +133,7 @@ def plot_eigens(I=np.radians(5)):
     # plt.yscale('symlog', linthreshy=1e-5)
     plt.xlabel(r'$\eta$')
     plt.ylabel(r'$\lambda^2/ (1 + \eta^2)$')
-    plt.legend(loc='upper left', fontsize=14,
+    legend = plt.legend(loc='upper left', fontsize=14,
                bbox_to_anchor=(0.5, 0.7))
     plt.xlim([min(etas), max(etas)])
     plt.axhline(0, lw=0.8, c='k', ls='dashed')
@@ -141,6 +141,48 @@ def plot_eigens(I=np.radians(5)):
     # plt.title(r'$I = %d^\circ$' % np.degrees(I))
     plt.tight_layout()
     plt.savefig('2_lambdas.png', dpi=400)
+
+    # add plots for other values of phi
+    legend.remove()
+    plt.legend(loc='upper right', fontsize=12, ncol=2,
+               bbox_to_anchor=(plt.xlim()[1], 0),
[…]

### 2021-05-03 initial/notes.tex
stash 05/03 bit more before meeting to do

@@
 % in paper 1, s_c = 2.04e4, for m_p = 0.01 Msun, a1=5AU, rho1=1g/cm^3, ap=30AU
+% NB: ta has masses flipped compared to Lai 2012, like Millholland 2020
 \begin{align}
@@
 
+\subsubsection{Physical Numbers}
+
+We focus on the USP regime. In the notation of the paper, we need
+\begin{align}
+    1
+        &\approx \frac{2n / \Omega_{\rm s} - \cos \theta
+            }{\abs{g}t_{\rm a}\sin I}.
+\end{align}
+One tricky thing about this calculation is that $\eta$ depends on $\Omega_{\rm
+s}$ which depends on $\cos \theta$ which depends on $\eta$:
+\begin{align}
+    \eta &= \eta_{\rm sync} \frac{n}{\Omega_{\rm s}},\\
+    \frac{n}{\Omega_{\rm s}} &= \frac{1 + \cos^2\theta}{2 \cos \theta},\\
+    \cos \theta &\approx \frac{\eta \cos I}{1 + \eta \sin I}.
+\end{align}
+This requires that
+\begin{align}
+    \frac{\eta}{\eta_{\rm sync}} &\approx \frac{1 + \eta \sin I
+        }{2\eta \cos I},\\
+    2\eta^2 \cos I &\approx \eta_{\rm sync} + \eta_{\rm sync}\eta \sin I,\\
+    \eta &= \frac{\eta_{\rm sync}\sin I + \sqrt{
+        \eta_{\rm sync}^2 \sin^2 I + 8\cos I \eta_{\rm sync}}}{
+            4 \cos I}.
+\end{align}
+It proves sufficient to use the simpler form of this:
+\begin{align}
+    \eta &\approx \sqrt{\frac{\eta_{\rm sync}}{2\cos I}},\\
+    t_{\rm a, c} &= \frac{2n / \Omega_{\rm s}}{\abs{g}\sin I},\\
+        &= \frac{2}{\abs{g}\sin I\sqrt{2\eta_{\rm sync} \cos I}}.
+\end{align}
+Thus, we can continue to evaluate
+\begin{align}
+    1
+        &\approx \frac{2\eta / \eta_{\rm sync} - \eta \cos I
+            }{\abs{g}t_{\rm a}\sin I},\\
+        &\approx \frac{1}{\sin I\sqrt{\eta_{\rm sync}\cos I}}
+            0.003 \frac{1}{\cos I}\p{\frac{2 k_2 / Q}{10^{-3}}}
+                \p{\frac{m_{\rm p}}{M_{\rm J}}}^{-1}
+                \p{\frac{a_{\rm p}}{5\;\mathrm{AU}}}^{3}
+                \p{\frac{a}{0.4\;\mathrm{AU}}}^{-6}
+                \p{\frac{\rho}{3\;\mathrm{g/cm^3}}}^{-1}
+                \p{\frac{M_{\star}}{M_{\odot}}}^2,\\
+        &\approx \frac{0.005}{\sin I \cos^{3/2}I}
+            \p{\frac{k}{k_q}}^{-1/2}
+            \p{\frac{2 k_2 / Q}{10^{-3}}}
+            \p{\frac{m_{\rm p}}{M_{\rm J}}}^{-3/2}
+            \p{\frac{a_{\rm p}}{5\;\mathrm{AU}}}^{9/2}
+            \p{\frac{a}{0.4\;\mathrm{AU}}}^{-9}
+            \p{\frac{\rho}{3\;\mathrm{g/cm^3}}}^{-3/2}
+            \p{\frac{M_{\star}}{M_{\odot}}}^3,\\
+        &\approx \frac{3 \times 10^{-7}}{\sin I \cos^{3/2}I}
+            \p{\frac{k}{k_q}}^{-1/2}
+            \p{\frac{2 k_2 / Q}{10^{-3}}}
+            % 1/5000
+            \p{\frac{m_{\rm p}}{M_{\rm \oplus}}}^{-3/2}
+            % 1e-9
+            \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{9/2}
+            % 1e9
+            \p{\frac{a}{0.04\;\mathrm{AU}}}^{-9}
+            % 1/3
+            \p{\frac{\rho}{6\;\mathrm{g/cm^3}}}^{-3/2}
+            \p{\frac{M_{\star}}{M_{\odot}}}^3,\\
+    a_{\rm break}
+        &\approx 0.01\;\mathrm{AU}
+            \p{\frac{k}{k_q}}^{-1/18}
+            \p{\frac{2 k_2 / Q}{10^{-3}}}^{1/9}
+            \p{\frac{m_{\rm p}}{M_{\rm \oplus}}}^{-1/6}
+            \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{1/2}
+            \p{\frac{\rho}{6\;\mathrm{g/cm^3}}}^{-1/6}
+            \p{\frac{M_{\star}}{M_{\odot}}}^{1/3}.
+\end{align}
+for $I = 5^\circ$. This seems a little bit on the low end.
+
 \subsection{Dissipating Disk: $\theta_f$ Distribution}

### 2021-05-03 writeups/Su_weak_tides.tex
stash 05/03 bit more before meeting to do

@@
+% vim 0_eta/1*.py 0_eta/3*.py 0_eta/6*.py 3_toy3/1sim.py 99_misc/0*.py 99_misc/2*.py 99_misc/5*.py 1_weaktide/5*.py 1_weaktide/6*.py
+% cd 0_eta && python 1*.py && python 3*.py && python 6*.py && cd ..
+&& cd 3_toy3 && python 1sim.py && cd ..
+&& cd 99_misc && python 0*.py && python 2*.py && python 5*.py && cd ..
+&& cd 1_weaktide && python 5*.py && python 6*.py
     \documentclass[
@@
             \label{eq:wsl}\\
-    \omega_{\rm lp} &= \frac{3m_p}{4M_\star}\p{\frac{a}{a_{\rm p}}}^3
+    \omega_{\rm lp} &= \frac{3m_{\rm p}}{4M_\star}\p{\frac{a}{a_{\rm p}}}^3
         n.\label{eq:wlp}
@@
 of which require $\uv{s}$ lie in the plane of $\uv{l}$ and $\uv{l}_{\rm p}$.
-Following the standard convention and nomenclature, CSs 1, 3, and 4 have $\phi =
-0$ and $\theta < 0$, while CS2 has $\phi = \pi$ and $\theta > 0$.
-Figure~\ref{fig:cs_locs} shows the CS obliquities as a function of $\eta$, each
-of which satisfies
-\begin{equation}
-    \sin \theta \cos \theta - \eta \sin\p{\theta - I} = 0.\label{eq:cs_zero}
-\end{equation}
-Note that there are four CSs when $\eta < \eta_{\rm c}$ and only two when $\eta
-> \eta_{\rm c}$, where
-\begin{equation}
-    \eta_{\rm c} \equiv \p{\sin^{2/3}\!I + \cos^{2/3}\!I}^{-3/2}.\label{eq:def_etac}
-\end{equation}
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs.png}
+Following the standard nomenclature, $\uv{s}$ and
+$\uv{l}_{\rm p}$ are on opposite sides of $\uv{l}$ for CSs 1, 3, and 4, and are
+on the same side for CS2. We depart from the standard convention
+and simply label the CSs in spherical coordinates: figure~\ref{fig:cs_locs}
+shows the CS obliquities as a function of $\eta$. CS1 and CS4 do not exist when
+$\eta > \eta_{\rm c}$, where
+\begin{equation}
+    \eta_{\rm c} \equiv \p{\sin^{2/3}\!I + \cos^{2/3}\!I}^{-3/2}.
+        \label{eq:def_etac}
+\end{equation}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs_phi.png}
     \caption{Cassini State obliquities $\theta$ as a function of $\eta \equiv
-    -g/\alpha$ (Eq.~\ref{eq:def_eta}) for $I = 5^\circ$. The vertical dashed
+    -g/\alpha$ (Eq.~\ref{eq:def_eta}) for $I = 20^\circ$. The vertical dashed
     line denotes $\eta_{\rm c}$, where the number of Cassini States changes from
-    four to just two (Eq.~\ref{eq:def_etac}). The horizontal dashed line gives
-    $\theta = I$, the asymptotic value of Cassini State 2's obliquity when $\eta
-    \to \infty$.}\label{fig:cs_locs}
+    four to just two (Eq.~\ref{eq:def_etac}). The y-axis labels on the right of
+    the plot show the asymptotic obliquities for CS2 and CS3, $I$ and $180^\circ
+    - I$ respectively. Note that $\theta$ does not follow the standard
+    convention \citep[e.g.][]{colombo1966} and is simply the angle between
+    $\uv{s}$ and $\uv{l}$.}\label{fig:cs_locs}
 \end{figure}
@@
 Figure~\ref{fig:1contours} shows the level curves of this Hamiltonian for $I =
-20^\circ$, for which $\eta_{\rm c} \approx 0.77$ (Eq.~\ref{eq:def_etac}). When $\eta
+20^\circ$, for which $\eta_{\rm c} \approx 0.574$ (Eq.~\ref{eq:def_etac}). When $\eta
 < \eta_{\rm c}$, CS4 exists and is a saddle point. The two trajectories
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/0_eta/1contours.png}
+    \includegraphics[width=\columnwidth]{../initial/0_eta/1contours20.png}
     \caption{Level curves of the Cassini State Hamiltonian (Eq.~\ref{eq:H}) for
-    $I = 5^\circ$, for which $\eta_{\rm c} \approx 0.77$ (Eq.~\ref{eq:def_etac}).
-    For $\eta < \eta_{\rm c}$, there are four Cassini States (labeled), while
-    for $\eta > \eta_{\rm c}$ there are only two. In the former case, the
-    existence of a \emph{separatrix} (solid black lines) separates phase space
-    into three numbered zones (I/II/III, labeled). Finally, we denote the upper
-    and lower legs of the separatrix by $\mathcal{C}_{\pm}$ respectively, as
-    shown in the upper two panels.}\label{fig:1contours}
+    $I = 20^\circ$, for which $\eta_{\rm c} \approx 0.57$
+    (Eq.~\ref{eq:def_etac}). For $\eta < \eta_{\rm c}$, there are four Cassini
+    States (labeled), while for $\eta > \eta_{\rm c}$ there are only two. In the
+    former case, the existence of a \emph{separatrix} (solid black lines)
+    separates phase space into three numbered zones (I/II/III, labeled). We
+    denote the upper and lower legs of the separatrix by $\mathcal{C}_{\pm}$
+    respectively, as shown in the upper two panels. }\label{fig:1contours}
 \end{figure}
@@
 \begin{align}
-    t_{\rm s, c} &= \frac{1}{\abs{g}\sin I},
+    t_{\rm s, c} &= \frac{1}{\abs{g}\sin I},\label{eq:mcs_shift_crit}
 \end{align}
@@
 CSs in the $\eta \ll 1$ case, where it can be seen that CS2 and CS4 collide and
-annihilate.. For the remainder of this section, we will consider the case where
-$t_{\rm s} \gg t_{\rm s, c}$ and the CSs only differ slightly from their
+annihilate. The phase shift $\phi_{\rm cs}$ for CS2 and CS4 for $t_{\rm s} >
+t_{\rm s, c}$ can be predicted to good accuracy using Eq.~\eqref{eq:mcs_shift}
+using $\theta_{\rm cs} \approx \pi/2 - \eta \cos (I) \approx 79^\circ$
+\citep{su2020} for both, shown as the dashed lines in the bottom panel of
+Fig.~\ref{fig:mcs}. For the remainder of this section, we will consider the case
+where $t_{\rm s} \gg t_{\rm s, c}$ and the CSs only differ slightly from their
 unperturbed locations.
@@
     \includegraphics[width=\columnwidth]{../initial/99_misc/0_stab.png}
-    \caption{Modified CSs for $I = 5^\circ$ and $\eta = 0.2$, and the CS1 and
-    CS3 obliquities have been offset (labeled in legend) to improve clarity of
-    the plot.}\label{fig:mcs}
+    \caption{Modified CS obliquities (top) and azimuthal angles (bottom) for $I
+    = 20^\circ$ and $\eta = 0.2$, where the CS1 and CS3 obliquities have been
+    offset (labeled in top legend) to improve clarity of the plot. In both
+    panels, the solid lines give the result when applying a numerical root
+    finding algorithm to the full equations of motion,
+    Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}), while the dotted lines in the
+    bottom panel give the CS2 and CS4 azimuthal angles according to
+    Eq.~\eqref{eq:mcs_shift}. At $\abs{gt_{\rm s} \sin I} = 1$, CS2 and CS4
+    collide and annihilate (Eq.~\ref{eq:mcs_shift_crit}).}\label{fig:mcs}
 \end{figure}
@@
 $\lambda$ of Eq.~\eqref{eq:dsdt_hessian} satisfy the equation
-\begin{align}
-    0 &= \p{\lambda + \frac{\cos \theta_{\rm cs}}{t_{\rm s}}}\lambda - \lambda_0^2,\\
-    \lambda_0^2 &\equiv \p{\alpha
+\begin{equation}
+    0 = \p{\lambda + \frac{\cos \theta_{\rm cs}}{t_{\rm s}}}\lambda
+        - \lambda_0^2,\label{eq:lambda_orig}
+\end{equation}
+where
+\begin{equation}
+    \lambda_0^2 \equiv \p{\alpha
         \sin \theta_{\rm cs} + g\sin I \csc^2\theta_{\rm cs}\cos \phi_{\rm cs}}
-            \p{- g \sin I \cos \phi_{\rm cs}},\label{eq:def_l0_sq}\\
-    \lambda &\approx -\frac{\cos \theta_{\rm cs}}{t_{\rm s}} \pm \sqrt{\lambda_0^2}.
-        \label{eq:lambda_approx}
-\end{align}
+            \p{- g \sin I \cos \phi_{\rm cs}}\label{eq:def_l0_sq}.
+\end{equation}
+When $t_{\rm s}$ is large, we can simplify Eq.~\eqref{eq:lambda_orig} to
+\begin{equation}
+    \lambda \approx -\frac{\cos \theta_{\rm cs}}{t_{\rm s}}
+        \pm \sqrt{\lambda_0^2}. \label{eq:lambda_approx}
+\end{equation}
 The stability depends only on the real part of $\lambda$ in
@@
 $\lambda$, and the stability of CSs 1--3 are solely determined by the sign of
-$\cos \theta_{\rm cs}$. From Figs.~\ref{fig:cs_locs}, we thus see that CSs 1 and
-2 are stable while CS3 is unstable under the alignment torque. These
+$\cos \theta_{\rm cs}$. Evaluating at each of the CSs (see
+Fig.~\ref{fig:cs_locs}), we conclude that CS1 and CS2 are stable and attracting
+while CS3, stable in the absence of the torque, becomes unstable. These
 calculations justify results long used in CS literature
-\citep[e.g.][]{ward1975tidal}.
+\citep[e.g.][]{ward1975tidal, fabrycky_otides}.
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{../initial/99_misc/2_lambdas_full.png}
-    \caption{$\lambda_0^2$ (Eq.~\ref{eq:def_l0_sq}) as a function of $\eta
-    \equiv \abs{g} / \alpha$ for the four CSs. The solid lines give
-    $\lambda_0^2$ for the unperturbed $\phi_{\rm cs}$, and the dashed lines give
-    the values for $\phi_{\rm cs}$ shifted by $60^\circ$ ($\phi_{\rm cs} =
-    120^\circ$ for CS2 and $\phi_{\rm cs} = 60^\circ$ for CSs 1, 3, and 4).
+    \caption{$\lambda_0^2$ (Eq.~\ref{eq:def_l0_sq}) as a function of $\eta$ for
+    the four CSs. The solid lines give $\lambda_0^2$ for the unperturbed
+    $\phi_{\rm cs}$, and the dashed lines give the values for $\phi_{\rm cs}$
+    shifted by $60^\circ$ ($\phi_{\rm cs} = 120^\circ$ for CS2 and $\phi_{\rm
+    cs} = 60^\circ$ for CSs 1, 3, and 4).
     }\label{fig:lambda_full}
@@
 towards it. As such, we consider only $\eta < \eta_{\rm c}$, where an initial
-condition can asymptotically evolve towards either CS1 or CS2. In
-Fig.~\ref{fig:toy_phop}, we show which CS an initial $\theta_0$ and $\phi_0$
-evolves into, where we have taken $\abs{g}t_{\rm s} = 10^{-3}$, $\eta = 0.2$,
-and $I = 20^\circ$. It is clear that initial $\uv{s}$ in zone I (following the
-naming in Fig.~\ref{fig:1contours}) evolve into CS1, those in zone II evolve
-into CS2, while those in zone III have a probabilistic outcome. We aim to
-understand each of these in turn:
+condition can asymptotically evolve towards either CS1 or CS2. We numerically
+integrate Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) for many random initial
+conditions uniformly distributed in $\p{\cos \theta, \phi}$ with $\abs{g}t_{\rm
+s} = 10^{-3}$ and record the nearest CS for each integration after $10t_{\rm
+s}$. In Fig.~\ref{fig:toy_phop}, we show the results of this procedure for $\eta
+= 0.2$, and $I = 20^\circ$. It is clear that initial conditions in zone I evolve
+into CS1, those in zone II evolve into CS2, while those in zone III have a
+probabilistic outcome. We aim to understand each of these in turn:
 \begin{figure}
@@
     H_{\rm sep} &\equiv H\p{\cos \theta_{\rm 4}, \phi_{\rm 4}},\nonumber\\
-        &\approx -\alpha\sin I - g\cos^2 I +
+        &\approx g\sin I + \frac{g^2}{2\alpha}\cos^2 I +
             \mathcal{O}\p{\eta^2},\label{eq:def_Hsep}
@@
 that it will initially be negative and increase for each circulation cycle until
-the system encounters the separatrix where $H - H_{\rm sep} < \Delta H_-$.
-
-When the system begins its separatrix-crossing orbit, $H$ at $\phi = 0$ is in
-the range $\s{H_{\rm sep} - \Delta H_-, H_{\rm sep}}$; call this value $H_{\rm
-i}$, as it is the initial value of the Hamiltonian on the separatrix-crossing
-orbit. The two endpoints of this range are denoted in Fig.~\ref{fig:6equils} by
-the black dot and cross at the left and right edges of the plot. Upon entering
-this range, the trajectory encounters the separatrix, and first traverses the
-vicinity of $\mathcal{C}_-$ then of $\mathcal{C}_+$, after which two possible
-outcomes can occur:
+the system encounters the separatrix. At the beginning of the
+separatrix-crossing orbit, the initial value of $H$, denoted $H_{\rm i}$,
+satisfies $H_{\rm sep} - \Delta H_- \leq H_{\rm i} \leq H_{\rm sep}$: if it is
+less than the lower bound, it will not cross the separatrix on this orbit, and
+if it is greater than the upper bound then it is already inside the separatrix.
+The two endpoints of this range are denoted in Fig.~\ref{fig:6equils} by the
+black dot and cross at the left and right edges of the plot.
+
+During the separatrix-crossing orbit, the trajectory first evolves
+approximately along $\mathcal{C}_-$ then along $\mathcal{C}_+$, after which two
+possible outcomes can occur:
 \begin{itemize}
@@
     \caption{Plot illustrating the probabilistic origin of separatrix capture
-    for $\eta = 0.2$ and $\abs{gt_{\rm s}} = 10^3$. Yellow regions converge to CS1,
-    and red to CS2. The separatrix of the unperturbed system is shown as the
-    green line and splits due to the perturbative torque. To calculate the
-    boundaries (legend) separating the CS1 and CS2-approaching regions, points
-    near either the left or right copy of CS4 (L/R subscript) are evolved either
-    forwards or backwards ($\pm$ superscript). Within zone III, the regions of
-    phase space reaching CS1 and CS2 both become very thin (shown qualitatively
-    as the red dotted lines of decreasing width), reflecting the fact that the
-    outcome for a particular initial condition can be approximated as
-    probabilistic sufficiently far from the separatrix. Labeled in the black
-    cross, star, and dot at the left and right edges of the plot are where $H$
-    is equal to $H_{\rm sep} - \Delta H_-$, $H_{\rm sep} - \Delta H_- - \Delta
-    H_+$, and $H_{\rm sep}$ (Eqs.~\ref{eq:def_Hsep} and~\ref{eq:def_dHpm}).
+    for $\eta = 0.2$, $I = 20^\circ$, and $\abs{gt_{\rm s}} = 10^{-3}$. Orange
+    regions converge to CS1, and green to CS2, while CS4 is labeled with the
+    purple dots. The boundaries separating the CS1 and CS2-approaching regions
+    consist of the critical trajectories (labeled in the legend) that, when
+    evolved either forwards or backwards in time (superscripts in the legend
+    labels), asymptotically approach CS4 where either $\phi = 0^\circ$ or $\phi
+    = 360^\circ$ (subscripts in the legend labels). Within zone III, the regions
+    of phase space reaching CS1 and CS2 both become very thin (shown
+    qualitatively as the light green lines of decreasing width), reflecting the
+    fact that the outcome for a particular initial condition can be approximated
+    as probabilistic sufficiently far from the separatrix. Labeled in the blue
+    and black dots at the left edge of the plot are the two backwards-in-time
+    critical trajectories intersect $\phi = 0$, and are where $H$ is equal to
+    $H_{\rm sep} - \Delta H_- - \Delta H_+$ and $H_{\rm sep} - \Delta H_-$
+    respectively (Eqs.~\ref{eq:def_Hsep} and~\ref{eq:def_dHpm}).
     }\label{fig:toy_hop_manifolds}
@@
 \begin{align}
-    \Delta H_- &\approx \frac{2\pi}{t_{\rm s}} + \mathcal{O}(\eta),\\
+    \Delta H_- &\approx \frac{2\pi}{t_{\rm s}}\p{1
+        - 2\eta \sin I} + \mathcal{O}(\eta^{3/2}),\\
     \Delta H_+ + \Delta H_- &\approx
-        \frac{32 \eta^{3/2}\cos I \sqrt{\sin I}}{t_{\rm s}},\\
+        \frac{32 \eta^{3/2}\cos I \sqrt{\sin I}}{t_{\rm s}}
+            + \mathcal{O}\p{\eta^{5/2}},\\
     P_{\rm III \to II} &\approx
-        \frac{16 \eta^{3/2} \cos I \sqrt{\sin I}}{\pi}.\label{eq:P32_toy}
-\end{align}
-Figure~\ref{fig:1hist_toy} displays the agreement of Eq.~\eqref{eq:P32_toy} with
-direct numerical simulations of
-Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide_toy}), where good agreement is
-observed.
+        \frac{16 \eta^{3/2} \cos I \sqrt{\sin I}}{\pi
+            \p{1  - 2\eta \sin I}}.\label{eq:P32_toy}
+\end{align}
+
+To directly compare Eq.~\eqref{eq:P32_toy} with numerical simulation, we
+perform integrations of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) while
+restricting our attention to only outcomes of initial conditions in zone III\@.
+In Fig.~\ref{fig:1hist_toy}, we display Eq.~\eqref{eq:P32_toy} alongside the
+computed $P_{\rm III \to II}$ using $1000$ initial conditions in zone III for
+each of $60$ values of $\eta$. Excellent agreement is observed.
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{../initial/3_toy3/1hist_toy.png}
-    \caption{Plot of $P_{\rm III \to II}$ as a function of $\eta$ for the toy
-    model. For each $\eta$, $150$ initial $\theta_0$ in zone III are evolved
-    until separatrix encounter, where their outcome is recorded. Shown in red is
-    Eq.~\eqref{eq:P32_toy}.}\label{fig:1hist_toy}
-\end{figure}
-
-Finally, we remark that the calculation above is just a more descriptive
-application of \emph{Melnikov's Method} \citep{g_and_h}. Melnikov's Method is a
-general integral that gives the degree of splitting of a ``homoclinic orbit''
-(here, the separatrix) induced by a small, possibly periodic, perturbation. The
+    \caption{Plot of $P_{\rm III \to II}$ as a function of $\eta$ for the
+    constant alignment torque model considered in Section~\ref{s:toy_model}. For
+    each $\eta$, $1000$ initial $\theta_0$ in zone III are evolved until just
+    after separatrix encounter, where the outcome of the encounter is recorded.
+    Shown in red is Eq.~\eqref{eq:P32_toy}.}\label{fig:1hist_toy}
+\end{figure}
+
+Finally, we remark that the calculation above is just a descriptive application
+of \emph{Melnikov's Method} \citep{g_and_h}. Melnikov's Method is a general
+calculation that gives the degree of splitting of a ``homoclinic orbit'' (here,
+the separatrix) induced by a small, possibly time-dependent, perturbation. The
 explicit connection between the evolution of the unperturbed Hamiltonian and
-distances between curves in phase space (as depicted in Fig.~\ref{fig:6equils})
+distances between curves in phase space (as seen in Fig.~\ref{fig:6equils})
 is provided by Melnikov's Method.
@@
 \section{Spin Evolution with Weak Tidal Friction}\label{s:full_tide_prob}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils0_20.png}
-    \caption{Schematic illustrating the evolution of the planet's spin due to
-    tidal friction for $I = 5^\circ$ and $\eta_{\rm sync} = 0.2$. The green
-    lines illustrate the directions of
-    Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}), while the black and blue
-    lines denote where the tidal $\dot{\Omega}_{\rm s}$ and $\dot{\theta}$
-    change signs respectively. Overlaid are the obliquities of Cassini States 1
-    and 2, the two Cassini States that are stable under tidal dissipation (see
-    Section~\ref{ss:tidal_equils}). The points that are both Cassini States and
-    satisfy $\dot{\Omega}_{\rm s} = 0$ are the tidal Cassini Equilibria (tCE),
-    circled in green. Finally, the vertical red lines illustrate the
-    $\Omega_{\rm s}$ below which tides causes tCE2 to become unstable; the
-    dashed and dotted vertical red lines lines correspond to values of $\abs{gt_{\rm
-    a}}^{-1} = 10^{-2}$ and $10^{-1}$ respectively. }\label{fig:6equils}
-\end{figure}
 
@@
 \begin{equation}
-    \frac{1}{t_{\rm a}} \equiv -\frac{L}{2S} \frac{\Omega_{\rm
-        s}}{2n}\frac{3k_2}{Q}\p{\frac{m}{M}}\p{\frac{R}{a}}^5 n.
-\end{equation}
-Here, $L = ma^2n$ and $S = kmR^2 \approx mR^2/4$ are the orbital and spin
+    \frac{1}{t_{\rm a}} \equiv \frac{L}{2S} \frac{\Omega_{\rm
+        s}}{2n}\frac{3k_2}{Q}\p{\frac{M_\star}{m}}\p{\frac{R}{a}}^5 n.
+\end{equation}
+Here, $L = ma^2n$ and $S = kmR^2 \Omega_{\rm s}$ are the orbital and spin
 angular momenta of the inner planet, respectively. We neglect orbital evolution
@@
 $\sim L / S \gg 1$, and so $t_{\rm a}$ is a constant. We will continue mostly
-consider the case where $\abs{gt_{\rm a}} \gg 1$.
+consider the case where $\abs{gt_{\rm a}} \gg 1$. The full equations of motion
+including weak tidal friction are
+\begin{align}
+    \rd{\theta}{t} &= g\sin I \sin \phi -
+        \frac{1}{t_{\rm a}}\sin \theta\p{\frac{2n}{\Omega_{\rm s}} - \cos \theta}
+            ,\label{eq:ds_fullq}\\
+    \rd{\phi}{t} &= -\alpha\cos\theta
+        - g\p{\cos I + \sin I \cot \theta \cos \phi}\label{eq:ds_fullphi},\\
+    \frac{1}{\Omega_{\rm s}}\rd{\Omega_{\rm s}}{t}
+        &= \frac{1}{t_{\rm a}} \s{\frac{2n}{\Omega_{\rm s}} \cos \theta
+            - \p{1 + \cos^2\theta}}\label{eq:ds_fulls}.
+\end{align}
+The conditions for which the two tidal terms vanish can be respectively
+expressed as:
+\begin{align}
+    \dot{\theta}_{\rm tide} = 0 &: \quad \frac{2n}{\Omega_{\rm s}} = \cos \theta,
+        \label{eq:weaktide_dqzero}\\
+    \dot{\Omega}_{\rm s} = 0 &: \quad \frac{n}{\Omega_{\rm s}}
+        = \frac{1 + \cos^2\theta}{2\cos \theta}.\label{eq:weaktide_dWszero}
+\end{align}
 
@@
 $t_{\rm s} = t_{\rm a} / \p{2n / \Omega_{\rm s} - \cos \theta}$ (compare
-Eqs.~\ref{eq:dsdt_tide_toy} and~Eq.~\eqref{eq:dsdt_tide}), we see that CS2 is
+Eqs.~\ref{eq:dsdt_tide_toy} and~Eq.~\ref{eq:dsdt_tide}), we see that CS2 is
 still always stable, while CS1 is becomes unstable for $\Omega_{\rm s} > 2n$.
@@
 equilibria of the system must both satisfy $\dot{\Omega}_{\rm s} = 0$ and be a
-stable CS\@. Figure~\ref{fig:6equils} shows the behavior of
+stable CS\@. Figure~\ref{fig:6equils} describes
 Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) qualitatively in the coordinates
 $(\Omega_{\rm s}, \theta)$, along with the locations of CS1 and CS2. The two
-points circled in green in Fig.~\ref{fig:6equils} satisfy the criteria to be
-long-term equilibria, and we call them \emph{tidal Cassini Equilibria} (tCE). We
-number tCE1 and tCE2 the tCE that are in CSs 1 and 2 respectively.
-
-There are two important caveats that may change the existence and stability of
-the tCE\@. First, if $\eta \geq \eta_{\rm c}$ (Eq.~\eqref{eq:def_etac}) when
-$\Omega_{\rm s} \approx n$\footnote{Strictly, if $\eta$ is very close to
-$\eta_{\rm c}$, the planet's spin is slightly subsynchronous at tCE1, see
-Fig.~\ref{fig:6equils}.}, then tCE1 will not exist. We can define the constant
+circled points in Fig.~\ref{fig:6equils} satisfy the criteria to be long-term
+equilibria, and we call them \emph{tidal Cassini Equilibria} (tCE). We number
+tCE1 and tCE2 the tCE that are in CSs 1 and 2 respectively. The obliquities of
+the tCE depend on the system architecture, which can be quantified using the
 parameter
@@
 \end{equation}
-where the existence of tCE1 then requires $\eta_{\rm sync} \leq \eta_{\rm
-c}$. Secondly, tCE2 may not be stable if the tidal phase shift is too large, as
-discussed in Section~\ref{ss:tidal_equils}. This threshold is shown as the
-vertical red lines in Fig.~\ref{fig:6equils} for a few choices of $t_{\rm a}$.
+The tCE obliquity as a function of $\eta_{\rm sync}$ are shown for $I =
+20^\circ$ in the top panel of Fig.~\ref{fig:probs20} and for $I = 5^\circ$ in
+the top panel of Fig.~\ref{fig:probs5}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils0_20.png}
+    \caption{Schematic depiction of the effect of tidal friction on the planet's
+    spin for $I = 20^\circ$ and $\eta_{\rm sync} = 0.2$. The black and blue lines
+    denote where the tidal $\dot{\Omega}_{\rm s}$ and $\dot{\theta}$ change
+    signs (Eqs.~\ref{eq:weaktide_dqzero}--\ref{eq:weaktide_dWszero}). The orange
+    and green lines give the CS1 and CS2 obliquities respectively, which are the
+    two CSs that are stable under the effect of tidal dissipation. Note that
+    when $\dot{\theta}_{\rm tide} > 0$, CS1 becomes unstable, denoted by the
+    dashed orange line. The points that are both CSs and satisfy
+    $\dot{\Omega}_{\rm s} = 0$ are the tidal Cassini Equilibria (tCE), which are
+    circled and labeled. }\label{fig:6equils}
+\end{figure}
+
+There are two important conditions that change the existence and stability of
+the tCE\@. First, if $\eta_{\rm sync} > \eta_{\rm c}$, then tCE1 will not
+exist\footnote{Strictly speaking, $\eta_{\rm sync}$ can be slightly smaller than
+$\eta_{\rm c}$, as the planet's spin is slightly subsynchronous at tCE1 when
+$\eta \approx \eta_{\rm c}$, see Fig.~\ref{fig:6equils}.}. Secondly, tCE2 may
+not be stable if the tidal phase shift is too large. Applying the results of
+Section~\ref{ss:tidal_equils}, we find that tCE2 is stable as long as $t_{\rm a}
+\geq t_{\rm a, c}$ where
+\begin{align}
+    t_{\rm a, c} &\equiv \frac{\sin \theta_{\rm tCE2}}{\abs{g} \sin I}.
+        \label{eq:def_ta_crit}
+\end{align}
+The tCE2 subscripts denote evaluation at tCE2. This can be further simplified
+using that Eq.~\eqref{eq:weaktide_dWszero} and $\cos \theta \approx
+\eta \cos I$ are satisfied at tCE2, giving:
+\begin{equation}
+    t_{\rm a,c} \approx \frac{1}{\abs{g}\sin I}\sqrt{\frac{2}{\eta_{\rm sync}
+        \cos I}}.
+\end{equation}
 
@@
 Fig.~\ref{fig:Hhists_0_06}, we show the final outcome for many randomly chosen
-$\theta_0$ and $\phi_0$ for $\eta_{\rm sync} = 0.06$ and $I = 5^\circ$. We see
+$\theta_0$ and $\phi_0$ for $\eta_{\rm sync} = 0.06$ and $I = 20^\circ$. We see
 that tCE1 is generally reached for spins initially in zone I, tCE2 is generally
 reached for spins initially in zone II, and a probabilistic outcome is observed
-for spins initially in zone III, very similar to the results found for the toy
-model in Section~\ref{s:toy_model}. Figures~\ref{fig:Hhists_0_20}
+for spins initially in zone III, very similar to the results found for the
+alignment torque in Section~\ref{s:toy_model}. Figures~\ref{fig:Hhists_0_20}
 and~\ref{fig:Hhists_0_70} show the same results but for $\eta_{\rm sync} = 0.2$
-and $\eta_{\rm sync} = 0.7$. As $\eta_{\rm sync}$ is increased, more initial
+and $\eta_{\rm sync} = 0.5$. As $\eta_{\rm sync}$ is increased, more initial
 conditions reach tCE2. This is both because there are more systems initially in
 zone II and because more systems initially in zone III execute a III $\to$ II
-transition upon separatrix encounter.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
+transition upon separatrix encounter. Note also that in
+Fig.~\ref{fig:Hhists_0_70}, even initial conditions in zone I are able to reach
+tCE2; we comment on the origin of this behavior in the next section.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_06_20.png}
     \caption{\emph{Left:} Each dot indicates which tCE a given initial condition
     $(\theta_{\rm i}, \phi_{\rm i})$ evolve towards (labeled in legend), for
-    $\eta_{\rm sync} = 0.06$ and $I = 5^\circ$. The
+    $\eta_{\rm sync} = 0.06$ and $I = 20^\circ$. The
     separatrix is shown as the black line. Note that points above the
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_20_20.png}
     \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\eta_{\rm sync} =
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_70_5.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_50_20.png}
     \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\eta_{\rm sync} =
@@
 Section~\ref{ss:toy_outcomes}, and also incorporates the seminal resonance
-capture theory of \citet{henrard1982}. In the interest of clarity, we give an
-overview of the approach, and present the analytical results of the calculation
-in Appendix~\ref{app:sep_crossing_dynamics}.
+capture theory of \citet{henrard1982}. In this section, we give an
+overview of the approach.
 
@@
 Here, however, note that $\mathcal{C}_{\pm}$ depends on the value of
-$\Omega_{\rm s}$ upon separatrix encounter! Since there is no closed form
+$\Omega_{\rm s}$ upon separatrix encounter. Since there is no closed form
 solution for $\Omega_{\rm s}(t)$, the probabilities of the various outcomes can
@@
 \end{equation}
-The analytical approximate forms for $\Delta K_{\pm}$ are given in by
-Eq.~\eqref{eq:app_deltaK}. Note that
-Eqs.~(\ref{eq:def_dK_weaktide},~\ref{eq:def_pc_weaktide}) are equivalent to the
-separatrix capture result of \citet{henrard1982} when $\cos \theta$ is not
-evolving \citep{henrard1987}. Here, we argue that this classic calculation can
-be unified with the calculation given in Section~\ref{ss:toy_outcomes} to give
-an accurate prediction of separatrix encounter outcome probabilities in the
-presence of both a dissipative perturbation and a parametric variation of the
-Hamiltonian.
-
-To compare Eq.~\eqref{eq:def_pc_weaktide} with numerical simulations, we can
-integrate Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) for
-many initial conditions in Zone III while evaluating $P_{\rm III \to II}$ (and
-thus also obtaining $P_{\rm III \to I} = 1 - P_{\rm III \to II}$) for
-each simulation at the moment it encounters the separatrix. If the theory is
-correct, the total numbers of systems converging to each of tCE1 and tCE2
-should be equal to those predicted by the sums of the calculated probabilities.
-In Fig.~\ref{fig:pc_fits_0_06}, we show the agreement of this semi-analytic
-procedure with the numerical results displayed earlier in the right
-panel of Fig.~\ref{fig:Hhists_0_06}. Good agreement is observed.
-Figs.~\ref{fig:pc_fits_0_20} and~\ref{fig:pc_fits_0_70} show the same for
-Figs.~\ref{fig:Hhists_0_20} and~\ref{fig:Hhists_0_70}. Mostly satisfactory
-agreement is observed. Thus, we conclude that the outcomes of separatrix
-encounter are accurately predicted by Eq.~\eqref{eq:def_pc_weaktide}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_06_5.png}
-    \caption{Comparison of the right hand panel of Fig.~\ref{fig:Hhists_0_06}
-    (red dots) with a semi-analytic calculation (blue line). The semi-analytic
-    calculation is performed by numerically integrating
-    Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) on a grid of initial
-    conditions uniform in $\cos \theta_{\rm i}$ and $\phi_{\rm i}$ until
-    separatrix encounter, then using the $\Omega_{\rm s}$ at separatrix
-    encounter to evaluate (TODO) to analytically compute the probability of
-    evolution into tCE2.}\label{fig:pc_fits_0_06}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_20_5.png}
-    \caption{Same as Fig.~\ref{fig:pc_fits_0_06} but for $Omega_{\rm c} =
-    0.2$, shown in Fig.~\ref{fig:Hhists_0_20}.}\label{fig:pc_fits_0_20}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_70_5.png}
+Since $\Delta K_{\pm}$ are evaluated at resonance encounter, and
+$\Omega_{\rm s}$ is evolving, there is no way to express $\Delta K_{\pm}$ as a
+closed form of initial conditions. In fact, since many resonance encounters
+occur when $\eta$ is substantial, even an approximate calculation using
+Eq.~\eqref{eq:sep_theta} is inaccurate, and we instead calculate $\Delta
+K_{\pm}$ along the two legs of the separatrix obtained numerically via a root
+finding algorithm. Note that Eqs.~(\ref{eq:def_dK_weaktide},~\ref{eq:def_pc_weaktide}) are
+equivalent to the separatrix capture result of \citet{henrard1982} when $\cos
+\theta$ is not evolving \citep{henrard1987}. Here, we have argued that this
+classic calculation can be unified with the calculation given in
+Section~\ref{ss:toy_outcomes} to give an accurate prediction of separatrix
+encounter outcome probabilities in the presence of both a dissipative
+perturbation and a parametric variation of the Hamiltonian.
+
+To validate the accuracy of Eq.~\eqref{eq:def_pc_weaktide}, we can compare with
+the numerical integration of
+Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) for many
+initial conditions in zone III while evaluating $P_{\rm III \to II}$ (and thus
+also obtaining $P_{\rm III \to I} = 1 - P_{\rm III \to II}$) for each simulation
+at the moment it encounters the separatrix. If the theory is correct, the total
+numbers of systems converging to each of tCE1 and tCE2 should be equal to those
+predicted by the sums of the calculated probabilities. In
+Fig.~\ref{fig:pc_fits_0_06}, we show the agreement of this semi-analytic
+procedure with the numerical results displayed earlier in the right panel of
+Fig.~\ref{fig:Hhists_0_06}. Good agreement is observed.
+Figs.~\ref{fig:pc_fits_0_20} shows the same for Figs.~\ref{fig:Hhists_0_20}.
+Mostly satisfactory agreement is observed. Thus, we conclude that the outcomes
+of separatrix encounter are accurately predicted by
+Eq.~\eqref{eq:def_pc_weaktide}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_06_20.png}
+    \caption{Comparison of the fraction of systems converging to tCE2 obtained
+    via numerical simulation (red dots) and obtained via a semi-analytic
+    calculation (blue line) for $\eta_{\rm sync} = 0.06$ and $I = 20^\circ$ (see
+    right panel of Fig.~\ref{fig:Hhists_0_06}). The semi-analytic calculation is
+    performed by numerically integrating
+    Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) on a grid
+    of initial conditions uniform in $\cos \theta_{\rm i}$ and $\phi_{\rm i}$
+    until the system reaches the separatrix, then calculating the probability of
+    reaching tCE2 for each integration using
+    Eq.~\eqref{eq:def_pc_weaktide}.}\label{fig:pc_fits_0_06}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_20_20.png}
     \caption{Same as Fig.~\ref{fig:pc_fits_0_06} but for $\eta_{\rm sync} =
-    0.7$, shown in Fig.~\ref{fig:Hhists_0_70}.}\label{fig:pc_fits_0_70}
-\end{figure}
+    0.2$, corresponding to the right panel of
+    Fig.~\ref{fig:Hhists_0_20}.}\label{fig:pc_fits_0_20}
+\end{figure}
+
+With the above calculation, we can understand why even initial conditions in
+zone I can converge to tCE2. As long as the inital spin is sufficiently large
+($\geq 2n$), Eq.~\eqref{eq:dsdt_tide} shows that sufficiently large initial
+obliquities are \emph{increased} by weak tidal friction (see the bottom right
+region of Fig.~\ref{fig:6equils}). This increase means that even initial
+conditions in zone I can sometimes be driven by weak tidal friction to
+experience separatrix encounter. When this is the case, it can be shown that
+both $\Delta K_+ > 0$ and $\Delta K_- > 0$. This implies that both III $\to$ II
+and I $\to$ II outcomes are guaranteed, and thus initial conditions in all three
+zones can evolve into tCE2.
 
@@
 initial spin orientations. For simplicity, we just consider $\uv{s}$ being
-isotropically distributed. Figure~\ref{fig:probs} shows this for $I
-= 5^\circ$ as a function of $\eta_{\rm sync}$.
+isotropically distributed. Figure~\ref{fig:probs20} shows this for $I
+= 20^\circ$ as a function of $\eta_{\rm sync}$. It can be seen that tCE2 is
+reached with substantial probability ($\sim 50^\circ$) while it is also at a
+substantial obliquity ($\sim 60^\circ$) for $\eta_{\rm sync} \approx 0.4$.
+Furthermore, the bottom panel illustrates that initial conditions other than
+those beginning in zone II generate a significant fraction of systems that
+converge to tCE2.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5probs_20.png}
+    \caption{\emph{Top:} Obliquities of the two tCE where $I = 20^\circ$ for a
+    range of $\eta_{\rm sync}$ (Eq.~\ref{eq:def_etasync}), averaged over an
+    isotropic initial spin orientation. \emph{Bottom:} Total probability of
+    ending up in tCE2 (red dots). The red shaded region denotes the contribution
+    of initial conditions in zone II that converge to tCE2 directly, and the
+    yellow shaded region denotes the contribution of initial conditions in zone
+    III that converge to tCE2 after a separatrix encounter. The vertical dashed
+    line denotes $\eta_{\rm c}$ (Eq.~\ref{eq:def_etac}).}\label{fig:probs20}
+\end{figure}
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{../initial/1_weaktide/5probs_5.png}
-    \caption{\emph{Top:} Total probability of ending up in tCE2 (red dots) for
-    $I = 5^\circ$ for a range of $\eta_{\rm sync}$. \emph{Bottom:}
-    obliquities of the two possible tCE.}\label{fig:probs}
-\end{figure}
-where $\epsilon$ is the dimensionless tidal evolution rate, given by
-\begin{align}
-    \epsilon \equiv{}& -\frac{1}{gt_a}\frac{L}{2S} \frac{\Omega_{\rm s}}{2n},\\
-    \frac{1}{t_a} ={}& \frac{3k_2}{Q}\p{\frac{m}{M}}\p{\frac{R}{a}}^5 n,\\
-    \epsilon \approx{}& 0.003\frac{1}{\cos I}\p{\frac{2k_2/Q}{10^{-3}}}
+    \caption{Same as Fig.~\ref{fig:probs20} but for $I =
+    5^\circ$.}\label{fig:probs5}
+\end{figure}
+
+\section{Applications}
+
+\subsection{Application to Warm + Cold Jupiter Systems
+}\label{ss:disc_sehj}
+
+Consider a system consisting of an inner Super-Earth (SE) and an exterior cold
+Jupiter (CJ); such systems are expected to be abundant \citep{zhu2018super}. For
+this system, the relative tidal dissipation rate $\abs{gt_{\rm a}}^{-1}$ can be
+computed
+\begin{align}
+    \frac{1}{\abs{g t_{\rm a}}}
+        \approx{}& 0.003\frac{1}{\cos I}\p{\frac{2k_2/Q}{10^{-3}}}
             \p{\frac{m_{\rm p}}{M_{\rm J}}}^{-1}
@@
 \end{align}
-
-\section{Applications}
-
-\subsection{Application to SE+HJ Systems}\label{ss:disc_sehj}
-
-Consider a system consisting of an inner Super-Earth (SE) and an exterior cold
-Jupiter (CJ). For this system, Eq.~\eqref{eq:def_etasync} can be evaluated
+In physical units, $t_{\rm a} \sim 2 \times 10^8\;\mathrm{yr}$ for the
+parameters adopted above, and $\dot{a} / a \sim 10^{14}\;\mathrm{yr}$, so the
+spin evolution of the inner planet occurs within the characteristic age of most
+planetary systems, while the orbital evolution of the inner planet can indeed by
+safely neglected. Thus, the approximations of slow tidal dissipation and
+constant $a$ used throughout Section~\ref{s:full_tide_prob} is valid.
+For the same fiducial parameters, Eq.~\eqref{eq:def_etasync} can be evaluated
 \begin{align}
@@
 Here, $\rho = m / \p{4\pi R^3/3}$ is the average density of the inner planet,
-and $M_{\rm J}$ is the mass of Jupiter. Tides tend to drive $\Omega_{\rm s}$ to
-spin-orbit synchronization, where $\Omega_{\rm s} = n$ and thus $-g / \alpha =
-\Omega_{\rm c} / n$. As such, we see that the ratio $\Omega_{\rm c} / n$
-quantifies the strength of the perturber relative to the spin-orbit coupling at
-the tidal equilibrium.
+and $M_{\rm J}$ is the mass of Jupiter. From Figs.~\ref{fig:probs20}
+and~\ref{fig:probs5}, we see that this value of $\eta_{\rm sync}$ gives a
+high-obliquity tCE2 with significant probability. Thus, we predict that a
+sizable fraction of SEs with exterior CJ companions can have significant
+obliquities ($\sim \gtrsim 30^\circ$).
+
+\subsection{Application to Ultra-short-period Planet Formation
+}\label{ss:disc_usp}
+
+In \citet{millholland2020formation}, the authors consider capture into the CS2
+resonance as part of a mechanism to induce ultra-short period planet (USP)
+formation. They envision a process consisting of three stages: (i) capture into
+CS2, (ii) simultaneous inward tidal migration and increase of the obliquity of
+CS2, and (iii) destruction of CS2 due to strong tidal dissipation and stalling
+of inward migration. Below, we revisit this process and show that the parameter
+space for this obliquity-driven tidal runaway formation channel of USPs is
+larger than is given in their work.
+
+First, we verify agreement of our criterion for breaking of CS2 with theirs.
+Evaluating Eq.~\eqref{eq:mcs_shift_crit} for the weak tidal friction torque
+given by Eq.~\eqref{eq:mcs_shift}, we find that tCE2 breaks when the semi-major
+axis is smaller than $a_{\rm break}$ where \textcolor{red}{I haven't double
+checked this calculation\dots}
+\begin{align}
+    a_{\rm break}
+        \approx{}& 0.01\;\mathrm{AU}
+            \p{\frac{k}{k_q}}^{-1/18}
+            \p{\frac{2 k_2 / Q}{10^{-3}}}^{1/9}
+            \p{\frac{m_{\rm p}}{M_{\rm \oplus}}}^{-1/6}\nonumber\\
+            &\times \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{1/2}
+            \p{\frac{\rho}{6\;\mathrm{g/cm^3}}}^{-1/6}
+            \p{\frac{M_{\star}}{M_{\odot}}}^{1/3}.
+\end{align}
+We have calculated this for a mutual inclination of $I = 5^\circ$. This
+corresponds to an orbital period of about half a day, qualifying as a USP\@.
+
+Second, we note that \citet{millholland2020formation} focus on system
+architectures for which $\eta_{\rm sync} \gtrsim \eta_{\rm c}$ (where CS1 does
+not exist at spin-orbit synchronization; see Eqs.~\ref{eq:def_etac}
+and~\ref{eq:def_etasync}), finding that architectures for which $\eta_{\rm sync}
+\lesssim \eta_{\rm c}$ always generate evolution towards CS1. However, they
+assumed an initial obliquity $\theta_{0} = 0^\circ$, while broader distributions
+of initial planet obliquities will give some probability of evolution towards
+CS2 and tCE2 (see Figs.~\ref{fig:Hhists_0_06}--\ref{fig:Hhists_0_70}). Thus, it
+is not necessary to restrict formation of USPs via tidal runaway to system
+architectures for which $\eta_{\rm sync} \gtrsim \eta_{\rm c}$. In fig
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/99_misc/5millholland_actives.png}
+    \caption{Plot showing allowable parameter space for USP formation for the
+    fiducial parameters: $P_{j + 1} / P_j = 1.3$ and $M_\star = M_{\odot}$,
+    mirroring Figure~5 of \citet{millholland2020formation}. Shaded in blue is
+    their region of allowable parameter space for USP formation ($\eta_{\rm
+    sync} \geq 1$ and $\dot{a} / a < \;\mathrm{Gyr}$), while shaded in
+    green is the region where $\eta_{\rm sync} \geq 1/3$, for which the tCE2
+    probability is $> 50\%$ for $I = 20^\circ$ (see Fig.~\ref{fig:probs20}).
+    \textcolor{red}{I added a few fudge factors temporarily to be a little bit
+    to be closer to the Millholland plot; I will double check their validity and
+    update this plot to better reflect our actual numbers / parameters.}
+    }\label{fig:millholland_actives}
+\end{figure}
+
+In particular, architectures with larger period ratios $P_{j + 1} / P_j$ (and
+thus, semi-major axis ratios; see Eq.~\ref{eq:def_etasync}) are still able to
+undergo tidal runaway. Such architectures can be advantageous for USP formation
+as more of their total angular momentum budget is in the outer planet's orbit,
+allowing for additional migration \citep{fabrycky_otides,
+millholland2020formation}.
+
+\subsection{Application to WASP-12b}\label{ss:disc_wasp12b}
+
+Thoughts:
+\begin{itemize}
+    \item Significantly limited by conservation of angular momentum (spin of the
+        star is a reservoir?).
+
+    \item Initial conditions are solidly in the $\eta_{\rm sync} \gg 1$ regime
+        (CS2 obliquity goes to near zero when $a$ is increased by $\sim30\%$),
+        probably not a very useful application of our theory. For systems where
+        the perturber is \emph{strong}, our theory produces extra tCE2 systems
+        compared to neglecting the effect of resonance capture, but where the
+        perturber is weak, everybody knows that CS2 is guaranteed.
+\end{itemize}
 
 \section{Summary and Discussion}\label{s:summary}
+
+\section{Acknowledgements}
+
+We thank Sarah Millholland for useful discussions. This work has been supported
+in part by NSF grant AST1715246. YS is supported by the NASA FINESST grant
+19-ASTRO19-0041.%chktex 8
 
@@
 \end{align}
-We have taken $\sin \theta \approx 1$, a good approximation in zone II since
+We have taken $\sin \theta \approx 1$, a good approximation in zone II when
 $\eta \ll 1$. Note that there are some values of $\phi$ for which no solutions
@@
 
-\section{Separatrix Crossing Probability with Weak Tidal Friction
-}\label{app:sep_crossing_dynamics}
-
-In this appendix, we analytically calculate $\Delta K_{\pm}$ for use in
-Eq.~\eqref{eq:def_pc_weaktide} to calculate the probabilities of the two
-possible transitions upon separatrix encounter. We first rewrite the full
-equations of motion for the planet's spin including weak tidal friction in
-component form:
-\begin{align}
-    \rd{\theta}{t} &= g\sin I \sin \phi -
-        \frac{1}{t_{\rm a}} \sin \theta,\label{eq:ds_fullq}\\
-    \rd{\phi}{t} &= -\alpha\cos\theta
-        - g\p{\cos I + \sin I \cot \theta \cos \phi}\label{eq:ds_fullphi},\\
-    \rd{\Omega_{\rm s}}{t}
-        &= \frac{1}{t_{\rm a}} \s{2n \cos \theta
-            - g\Omega_{\rm s}\p{1 + \cos^2\theta}}\label{eq:ds_fulls}.
-\end{align}
-
-Note that Eq.~\eqref{eq:def_dK_weaktide} can be rewritten
-\begin{align}
-    \Delta K_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}
-        - \rd{H_{\rm sep}}{t}\;\mathrm{d}t
-        \nonumber\\
-        &= \oint_{\mathcal{C}_{\pm}}
-           \p{\rd{(\cos\theta)}{t}}_{\rm tide}
-            + \frac{\dot{\Omega}_{\rm s}}{\dot{\phi}}
-            \p{\pd{H}{s} - \pd{H_{\rm sep}}{s}}\;\mathrm{d}\phi
-                \label{eq:app_dhpm}.
-\end{align}
-
-We then evaluate $\Delta K_{\pm}$ by integrating along the separatrix, using the
-parameterized form for $\p{\cos \theta}_{\mathcal{C}_\pm}$ given by
-Eq.~\eqref{eq:sep_theta}. Note that we must use the value of $\eta$ at the
-moment of separatrix encounter, as the evolution of $\Omega_{\rm s}$ changes the
-spin-orbit precession frequency $\alpha$ \textcolor{red}{NB\@: I haven't analytically
-recalculated this formula recently, only compared numerically, so there may be
-small typos, though nothing that changes the accuracy of the result}:
-\begin{align}
-    \Delta K_{\pm} ={}& \oint_{\mathcal{C}_{\pm}}
-        \frac{1}{t_{\rm s}}\sin^2\theta
-            \p{\frac{2n}{\Omega_{\rm s}} - \cos\theta}
-         +
-            \s{\alpha\frac{\cos^2\theta}{2} + g\frac{\Omega_{\rm
-            c}}{2\Omega_{\rm s}^2}\cos^2 I}\rd{\Omega_{\rm
-            s}}{t}\rd{t}{\phi}\;\mathrm{d}\phi\\
-     \approx{}& \oint_{\mathcal{C}_{\pm}}
-        \frac{1}{t_{\rm s}}\sin^2\theta
-            \p{\frac{2n}{\Omega_{\rm s}} - \cos\theta}
-        + \frac{1}{t_{\rm s}}\frac{n}{\Omega_{\rm s}\eta}
-            \s{\p{\cos \theta}_{\mathcal{C}_{\pm}} - \frac{\Omega_{\rm s}}{2n}}
-            \s{2 \cos I \pm \sqrt{2 \sin I\p{1 - \cos \phi} / \eta}}
-            \;\mathrm{d}\phi,\\
-    t_{\rm s} \Delta K_{\pm} \approx{}&
-        -2\cos I\p{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
-        \pm 2\pi \frac{\Omega_{\rm s}}{n}\cos I
-        - 8\eta \cos I \sqrt{\sin I / \eta}
-            + \frac{4\Omega_{\rm s}}{n}\sqrt{\sin I/\eta}\nonumber\\
-        &+ \frac{2n}{\Omega_{\rm s}}\p{\mp 2\pi\p{1 - 2\eta \sin I}
-            + 16\cos I \eta^{3/2}\sqrt{\sin I}}
-            + 8\sqrt{\eta \sin I}
-            \pm 2 \pi \eta \cos I
-            - \frac{64}{3} \p{\eta \sin I}^{3/2}.\label{eq:app_deltaK}
-\end{align}
-This is used in Eq.~\eqref{eq:def_pc_weaktide} to semi-analytically compute the
-tCE2 probabilities (blue curves) in
-Figs.~\ref{fig:pc_fits_0_06}--\ref{fig:pc_fits_0_70}.
+% \section{Separatrix Crossing Probability with Weak Tidal Friction
+% }\label{app:sep_crossing_dynamics}
+
+% In this appendix, we analytically calculate $\Delta K_{\pm}$ for use in
+% Eq.~\eqref{eq:def_pc_weaktide} to calculate the probabilities of the two
+% possible transitions upon separatrix encounter. We first rewrite the full
+% equations of motion for the planet's spin including weak tidal friction in
+% component form:
+% \begin{align}
+%     \rd{\theta}{t} &= g\sin I \sin \phi -
+%         \frac{1}{t_{\rm a}} \sin \theta,\label{eq:ds_fullq}\\
+%     \rd{\phi}{t} &= -\alpha\cos\theta
+%         - g\p{\cos I + \sin I \cot \theta \cos \phi}\label{eq:ds_fullphi},\\
+%     \rd{\Omega_{\rm s}}{t}
+%         &= \frac{1}{t_{\rm a}} \s{2n \cos \theta
+%             - g\Omega_{\rm s}\p{1 + \cos^2\theta}}\label{eq:ds_fulls}.
+% \end{align}
+
+% Note that Eq.~\eqref{eq:def_dK_weaktide} can be rewritten
+% \begin{align}
+%     \Delta K_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}
+%         - \rd{H_{\rm sep}}{t}\;\mathrm{d}t
+%         \nonumber\\
+%         &= \oint_{\mathcal{C}_{\pm}}
+%            \p{\rd{(\cos\theta)}{t}}_{\rm tide}
+%             + \frac{\dot{\Omega}_{\rm s}}{\dot{\phi}}
+%             \p{\pd{H}{s} - \pd{H_{\rm sep}}{s}}\;\mathrm{d}\phi
+%                 \label{eq:app_dhpm}.
+% \end{align}
+
+% We then evaluate $\Delta K_{\pm}$ by integrating along the two legs of the
+% separatrix $\mathcal{C}_{\pm}$ (see Fig.~\ref{fig:1contours}). Note that we must
+% use the value of $\eta$ at the moment of separatrix encounter, as the evolution
+% of $\Omega_{\rm s}$ changes the spin-orbit precession frequency $\alpha$
+% \begin{align}
+%     \Delta K_{\pm} ={}& \oint_{\mathcal{C}_{\pm}}
+%         \frac{1}{t_{\rm s}}\sin^2\theta
+%             \p{\frac{2n}{\Omega_{\rm s}} - \cos\theta}
+%          +
+%             \s{\frac{\alpha}{\Omega_{\rm s}}
+%                 \frac{\cos^2\theta}{2} + g\frac{\Omega_{\rm
+%             c}}{2\Omega_{\rm s}^2}\cos^2 I}\rd{\Omega_{\rm
+%             s}}{t}\rd{t}{\phi}\;\mathrm{d}\phi\\
+%      \approx{}& \oint_{\mathcal{C}_{\pm}}
+%         \frac{1}{t_{\rm s}}\sin^2\theta
+%             \p{\frac{2n}{\Omega_{\rm s}} - \cos\theta}
+%         + \frac{1}{t_{\rm s}}\frac{n}{\Omega_{\rm s}\eta}
+%             \s{\p{\cos \theta}_{\mathcal{C}_{\pm}} - \frac{\Omega_{\rm s}}{2n}}
+%             \s{2 \cos I \pm \sqrt{2 \sin I\p{1 - \cos \phi} / \eta}}
+%             \;\mathrm{d}\phi.\label{eq:app_deltaK}
+%     t_{\rm s} \Delta K_{\pm} \approx{}&
+%         -2\cos I\p{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
+%         \pm 2\pi \frac{\Omega_{\rm s}}{n}\cos I
+%         - 8\eta \cos I \sqrt{\sin I / \eta}
+%             + \frac{4\Omega_{\rm s}}{n}\sqrt{\sin I/\eta}\nonumber\\
+%         &+ \frac{2n}{\Omega_{\rm s}}\p{\mp 2\pi\p{1 - 2\eta \sin I}
+%             + 16\cos I \eta^{3/2}\sqrt{\sin I}}
+%             + 8\sqrt{\eta \sin I}
+%             \pm 2 \pi \eta \cos I
+%             - \frac{64}{3} \p{\eta \sin I}^{3/2}.\label{eq:app_deltaK}
+% \end{align}
+% At this point, since $\eta$ often is not small, it is necessary to integrate
+% along the numerically computed $\mathcal{C}_{\pm}$ (instead of the approximate
+% solution given by Eq.~\ref{eq:sep_theta}) to obtain sufficiently accurate values
+% for $\Delta K_{\pm}$. These numerically integrated values are used in
+% Eq.~\eqref{eq:def_pc_weaktide} to semi-analytically compute the tCE2
+% probabilities (blue curves) in
+% Figs.~\ref{fig:pc_fits_0_06}--\ref{fig:pc_fits_0_20}.
 

### 2021-05-03 initial/0_eta/3stats.py

@@ -117,7 +117,8 @@ def run_for_tide(tide=1e-3,
 
     # points below the separatrix, where do they converge to?
     below_convs = []
-    colors = ['y', 'r', 'y', 'c']
+    # HACK HACK everything but CS1/2 are green as well
+    colors = ['orange', 'tab:green', 'orange', 'tab:purple']
     for q, phi, conv_pts, c in zip(qs, phis, conv_data, colors):
         if conv_pts:
             q_plot, phi_plot = np.array(conv_pts).T
@@ -125,19 +126,27 @@ def run_for_tide(tide=1e-3,
             phis_plot = get_phis(q_plot, phi_plot)
             plt.plot(phis_plot,
                      np.cos(q_plot),
-                     '%so' % c,
-                     markersize=1)
+                     mfc=c, mec=c, marker='o', ls='',
+                     markersize=2)
         else:
             below_convs.append(0)
         # plot_point(plt.gca(), q, '%so' % c, markersize=8)
     for idx, c in enumerate(colors[ :2]):
-        plt.plot(0, -10, '%so' % c, markersize=3, label='CS%d' % (idx + 1))
+        plt.plot(0, -10, c=c, marker='o', ls='',
+                 markersize=5, label='CS%d' % (idx + 1))
     plt.ylim([-1, 1])
-    plt.legend(fontsize=12, loc='center left', bbox_to_anchor=(1, 0.5))
+    plt.legend(fontsize=16, loc='center left', bbox_to_anchor=(1, 0.5))
     plt.ylabel(r'$\cos \theta_0$')
-    plt.xlabel(r'$\phi_0$')
+    plt.xlabel(r'$\phi_0$ (deg)')
     plt.xticks([0, np.pi, 2 * np.pi],
-               ['0', r'$\pi$', r'$2\pi$'])
+               ['0', r'$180$', r'$360$'])
+    plt.text(np.pi, np.cos(qs[1]), 'II', backgroundcolor=(1, 1, 1, 0.9),
+             ha='center', va='center')
+    sepwidth = 2 * np.sqrt(eta * np.sin(I))
+    plt.text(np.pi, np.cos(qs[1]) + 1.2 * sepwidth, 'I',
+             backgroundcolor=(1, 1, 1, 0.9), ha='center', va='center')
+    plt.text(np.pi, np.cos(qs[1]) - 1.2 * sepwidth, 'III',
[…]

### 2021-05-03 initial/0_eta/6manifolds.py

@@ -54,7 +54,7 @@ def plot_manifolds(eta):
     phi1 = np.unwrap(_phi1 + np.pi) - 2 * np.pi
     term1 = np.where(phi1 < 0)[0][0]
     plt.plot(phi1[ :term1], s1[2, :term1], 'b--',
-             label=r'CS4$_{\rm L}^-$', linewidth=1.5, alpha=0.7)
+             label=r'CS4$_{\phi=0}^-$', linewidth=1.5, alpha=0.7)
 
     # forwards from CS4^0
     init = get_displaced(-1, 1)
@@ -67,7 +67,7 @@ def plot_manifolds(eta):
         phi2 < 1,
     ))[0][0]
     plt.plot(phi2[ :term2], s2[2, :term2], 'b',
-             label=r'CS4$_{\rm L}^+$', linewidth=1.5, alpha=0.7)
+             label=r'CS4$_{\phi=0}^+$', linewidth=1.5, alpha=0.7)
 
     # backwards from CS4^1
     init = get_displaced(-1, -1)
@@ -76,7 +76,7 @@ def plot_manifolds(eta):
     phi3 = np.unwrap(_phi3 + np.pi)
     term3 = np.where(phi3 < 0)[0][0]
     plt.plot(phi3[ :term3], s3[2, :term3], 'k--',
-             label=r'CS4$_{\rm R}^-$', linewidth=1.5, alpha=0.7)
+             label=r'CS4$_{\phi=360}^-$', linewidth=1.5, alpha=0.7)
 
     # forwards from CS4^1
     init = get_displaced(1, -1)
@@ -85,22 +85,22 @@ def plot_manifolds(eta):
     phi4 = np.unwrap(_phi4 + np.pi)
     term4 = np.where(phi4 < 0)[0][0]
     plt.plot(phi4[ :term4], s4[2, :term4], 'k',
-             label=r'CS4$_{\rm R}^-$', linewidth=1.5, alpha=0.7)
+             label=r'CS4$_{\phi=360}^+$', linewidth=1.5, alpha=0.7)
 
     plt.xlim([0, 2 * np.pi])
     plt.xticks([0, np.pi, 2 * np.pi],
-               ['0', r'$\pi$', r'$2\pi$'])
+               ['0', r'$180$', r'$360$'])
 
     ylim = plt.ylim()
     a1 = 0.4 # inner alpha
     a2 = 0.2 # Z3 alpha
     # fill Zone I with yellow
[…]

### 2021-05-03 initial/1_weaktide/6misc.py

@@ -36,7 +36,7 @@ def get_cs_val(I, s_c, s):
 
 def plot_equils(I, s_c, verbose=True, fn_str='6equils%s'):
     ''' plot in (s, mu) space showing how the tCS arise '''
-    fig = plt.figure(figsize=(6, 6))
+    fig = plt.figure(figsize=(5, 5))
     s_lt = np.linspace(s_c / 10, 1, 200) # max eta = 10
     s_gt = np.linspace(1, 3, 200) # other interesting part of the interval
     s_tot = np.concatenate((s_lt, s_gt))
@@ -50,40 +50,59 @@ def plot_equils(I, s_c, verbose=True, fn_str='6equils%s'):
     plt.xlabel(r'$\Omega_{\rm s} / n$')
     plt.ylabel(r'$\theta$ (deg)')
     plt.ylim([0, 180])
-    if verbose:
-        plt.plot(s_tot, np.degrees(cs2_qs), 'r', label='CS2', lw=2.5)
-        plt.plot(s_tot[cs1_exist_idx], np.degrees(-cs1_qs[cs1_exist_idx]),
-                 'y', label='CS1', lw=2.5)
 
-        # overplot where CS2 gets destroyed by tides? Just do for a representative
-        # epsilon, want to see the scaling
-
-        eta_crit = lambda eps_val: (
-            -np.sin(I) + np.sqrt(np.sin(I)**2 + 4 * eps_val**2 * np.cos(I)**2)
-        ) / (2 * eps_val * np.cos(I)**2)
-        xlims = plt.xlim()
-        plt.axvline(s_c / eta_crit(1e-2), c='r', ls=':', lw=1.5)
-        plt.axvline(s_c / eta_crit(1e-1), c='r', ls='--', lw=1.5)
-        plt.xlim(xlims)
-    plt.plot(s_lt, mu_equil_lt, 'k', label=r'$\dot{\Omega}_{\rm s} = 0$', lw=4)
-    plt.plot(s_dq, np.degrees(np.arccos(2 / s_dq)), 'b',
-             label=r'$\dot{\theta} = 0$', lw=4)
-    plt.annotate('', xy=(1.5, 90), xytext=(2.5, 120),
-                 arrowprops={'fc': 'g', 'width': 10, 'headwidth': 25})
-    plt.annotate('', xy=(0.8, 10), xytext=(0.3, 30),
-                 arrowprops={'fc': 'g', 'width': 10, 'headwidth': 25})
[…]

### 2021-05-03 initial/1_weaktide/utils.py

@@ -260,6 +260,8 @@ def get_mu_equil(s):
     '''
     solve quadratic mu / (1 + mu^2) = s / 2
     assumes s <= 1 everywhere, else will fail
+
+    1 + mu^2 - 2mu / s = 0
     '''
     if s > 1:
         raise ValueError('Cannot get equil mu for s > 1')
@@ -279,7 +281,7 @@ def get_crit_mus(I, s_c):
         mu_cs = np.cos(roots(I, s_c, s))
         mu_equil = get_mu_equil(s)
         return mu_cs[0] - mu_equil
-    cs2_equil_mu = opt.bisect(dmu_cs2_equil, 0.1, 1)
+    cs2_equil_mu = get_mu_equil(opt.bisect(dmu_cs2_equil, 0.1, 1))
     # if CS1 just before disappearing is below mu_equil, we won't have an
     # intersection
     s_etac = s_c / (0.9999 * s_c_crit)
@@ -288,7 +290,10 @@ def get_crit_mus(I, s_c):
         cs1_crit_mu = np.cos(roots(I, s_c, s_etac)[0])
         mu_equil_etac = get_mu_equil(s_etac)
         if cs1_crit_mu > mu_equil_etac:
-            return opt.bisect(dmu_cs1_equil, s_etac, 1), cs2_equil_mu
+            return (
+                get_mu_equil(opt.bisect(dmu_cs1_equil, s_etac, 1)),
+                cs2_equil_mu,
+            )
     return None, cs2_equil_mu
 
 def get_eta_cutoff(I):

### 2021-05-03 initial/99_misc/0_stab.py

@@ -14,10 +14,10 @@ plt.rc('lines', lw=2.5)
 plt.rc('xtick', direction='in', top=True, bottom=True)
 plt.rc('ytick', direction='in', left=True, right=True)
 
-I = np.radians(5)
+I = np.radians(20)
 eta = 0.2
-mu2 = eta * np.cos(I) / (1 + eta * np.sin(I))
-mu4 = eta * np.cos(I) / (1 - eta * np.sin(I))
+mu2 = eta * np.cos(I)# / (1 + eta * np.sin(I))
+mu4 = eta * np.cos(I)# / (1 - eta * np.sin(I))
 eps_crit = eta * np.sin(I) / (1 - (eta * np.cos(I))**2)
 
 def get_dydt(tide):
@@ -94,7 +94,7 @@ def get_cs3(eps, tol=1e-10, log=False, method='hybr'):
     return ret
 
 def get_cs4(eps, tol=1e-10, log=False, method='hybr'):
-    cs4 = [-np.sqrt(1 - mu4**2), 0, mu4]
+    cs4 = [-np.sqrt(1 - mu4**2), 0, mu4 + 0.02]
     ret = opt.root(get_dydt(eps), cs4, tol=tol, method=method)
     if log and not ret.success:
         print('get_cs4 did not succeed')
@@ -131,10 +131,10 @@ def plot_cs_pts():
     plot the locations of CS2/4 for increasingly large tides
     '''
     eps_crit = eps_crit_num
-    offsets = 0.9 * eps_crit * np.exp(np.linspace(0, -5, 40))
+    offsets = eps_crit * np.geomspace(0.9, 1e-3, 100)
     eps_vals = np.concatenate((
         eps_crit - offsets + min(offsets),
-        (eps_crit + 10 * (offsets - min(offsets)))[1: ],
+        (eps_crit + 10 * (offsets - min(offsets)))[1:][::-1],
     ))
     rets = []
     for eps in eps_vals:
@@ -146,44 +146,51 @@ def plot_cs_pts():
         figsize=(6, 6),
         gridspec_kw={'height_ratios': [1, 1]},
         sharex=True)
-    for ax in [ax1, ax2]:
[…]

### 2021-05-04 initial/notes.tex
can't decide on color but technically have a draft

--- 2020-05-11 initial/notes.tex
@@
 
+\subsubsection{Physical Numbers}
+
+We focus on the USP regime. In the notation of the paper, we need
+\begin{align}
+    1
+        &\approx \frac{2n / \Omega_{\rm s} - \cos \theta
+            }{\abs{g}t_{\rm a}\sin I}.
+\end{align}
+One tricky thing about this calculation is that $\eta$ depends on $\Omega_{\rm
+s}$ which depends on $\cos \theta$ which depends on $\eta$:
+\begin{align}
+    \eta &= \eta_{\rm sync} \frac{n}{\Omega_{\rm s}},\\
+    \frac{n}{\Omega_{\rm s}} &= \frac{1 + \cos^2\theta}{2 \cos \theta},\\
+    \cos \theta &\approx \frac{\eta \cos I}{1 + \eta \sin I}.
+\end{align}
+This requires that
+\begin{align}
+    \frac{\eta}{\eta_{\rm sync}} &\approx \frac{1 + \eta \sin I
+        }{2\eta \cos I},\\
+    2\eta^2 \cos I &\approx \eta_{\rm sync} + \eta_{\rm sync}\eta \sin I,\\
+    \eta &= \frac{\eta_{\rm sync}\sin I + \sqrt{
+        \eta_{\rm sync}^2 \sin^2 I + 8\cos I \eta_{\rm sync}}}{
+            4 \cos I}.
+\end{align}
+It proves sufficient to use the simpler form of this:
+\begin{align}
+    \eta &\approx \sqrt{\frac{\eta_{\rm sync}}{2\cos I}},\\
+    t_{\rm a, c} &= \frac{2n / \Omega_{\rm s}}{\abs{g}\sin I},\\
+        &= \frac{2}{\abs{g}\sin I\sqrt{2\eta_{\rm sync} \cos I}}.
+\end{align}
+Thus, we can continue to evaluate laboriously:
+\begin{align}
+    \frac{1}{t_{\rm s, c}} &= \abs{g}\sin I \sqrt{\frac{\eta_{\rm sync} \cos
+        I}{2}},\\
+    g &= \frac{3m_p}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^3 n,\\
+    \frac{1}{t_{\rm s}} &= \frac{1}{4k}\frac{3k_2}{Q} \frac{M_{\star}}{m}
+        \p{\frac{R}{a}}^3 n,\\
+    \eta_{\rm sync} &= \s{\frac{3m_p}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^3 n}
+        \Bigg/ \s{\frac{3k_q}{2k} \frac{M_\star}{m}\p{\frac{R}{a}}^3 n},\\
+        &= \frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
+            \p{\frac{a}{R}}^3,\\
+    \frac{1}{4k}\frac{3k_2}{Q}\frac{M_\star}{m}\p{\frac{R}{a}}^3
+        &= \frac{3m_{\rm p}}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^3
+            \sin I \sqrt{\frac{\cos I}{2}}
+            \sqrt{\frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
+                \p{\frac{a}{R}}^3 \frac{k}{k_q}},\\
+    a^9 &= 4\frac{2k_2}{Q} \frac{M_\star^3}{(mm_{\rm p})^{3/2}}
+        \p{Ra_{\rm p}}^{9/2}\frac{1}{\sin I \sqrt{\cos I}}
+        \p{\frac{k}{k_{\rm q}}}^{-1/2},\\
+% (4 * 1e-3 * (Msun / (8 Mearth))^3 * ((2 Rearth) * (0.05 AU))^(9/2))^(1/9) / (1 AU)
+% = 0.0387
+    a_{\rm break} &\approx 0.038 \;\mathrm{AU}
+        \p{\frac{2k_2/Q}{10^{-3}}}^{1/9}
+        \p{\frac{M_\star}{M_{\odot}}}^{1/3}
+        \p{\frac{8M_{\oplus}}{m}}^{-1/3}
+        \p{\frac{R}{2R_{\oplus}}}^{1/2}
+        \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{1/2}
+        \p{\frac{1}{\sin I \sqrt{\cos I}}}^{1/9},\\
+% ((8 Mearth)^2 / (Msun)^2) / 2 * (1.3)^(-2) * ((0.035 AU) / (2 Rearth))^3
+% = 0.011845
+    \eta_{\rm sync} &= \frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
+            \p{\frac{a}{R}}^3,\\
+        &= 0.012 \p{\frac{k}{k_{\rm q}}}
+                \p{\frac{m}{8 M_{\oplus}}}^2
+                \p{\frac{M_\star}{M_{\odot}}}^{-2}
+            \p{\frac{a}{0.035 \;\mathrm{AU}}}^{3}
+                \p{\frac{P_{j + 1} / P_j}{1.5}}^{-2}
+                \p{\frac{R}{2R_{\oplus}}}^{-3}.
+\end{align}
+For WASP-12b, we instead can solve for
+\begin{align}
+    \frac{m_{\rm p}^{3/2}}{a_{\rm p}^{9/2}}
+        &= 4\frac{2k_2}{Q} \frac{M_\star^3}{m^{3/2}}
+        \p{\frac{R}{a^2}}^{9/2}\frac{1}{\sin I \sqrt{\cos I}}
+        \p{\frac{k}{k_{\rm q}}}^{-1/2},\\
+    \frac{m_{\rm p}}{a_{\rm p}^3}
+        &\gtrsim 0.0002 \;\mathrm{kg/m^3}
+            \p{\frac{2k_2/Q}{10^{-7}}}^{2/3}
+            \p{\frac{M_\star}{1.36 M_{\odot}}}^{2}
+            \p{\frac{m}{1.41 M_{\rm J}}}^{-1}
+            \p{\frac{R}{1.89R_{\rm J}}}^{3}
+            \p{\frac{a}{0.023\;\mathrm{AU}}}^{-6}
+            \p{\frac{1}{\sin I \sqrt{\cos I}}}^{2/3}.
+\end{align}
+If WASP-12b is in tCE2, then this must be satisfied by the perturber.
+
+However, recall here that $I$ should really be the angle between $\bm{L}$ and
+$\bm{L}_{\rm tot} = \bm{L} + \bm{L}_{\rm out}$. When $L \gg L_{\rm out}$ as in
+this case, we must reduce $\sin I = (L_{\rm out} / L) \sin I_{\rm tot}$, where
+$I_{\rm tot}$ is the mutual inclination between the orbits. For circular orbits
+and small $I_{\rm tot}$, we can write
+\begin{align}
+    \frac{L_{\rm out}}{L} \approx{}& \frac{m_{\rm p}}{m}
+            \sqrt{\frac{a_{\rm p}}{a}}\nonumber\\
+        &= 0.132,\\
+    \p{\frac{m_{\rm p}}{40 M_{\oplus}}}\p{\frac{a_{\rm
+        p}}{0.05\;\mathrm{AU}}}^{-3} \gtrsim {}& 0.4
+            \p{\frac{2k_2/Q}{10^{-7}}}^{2/3}
+            \p{\frac{M_\star}{1.36 M_{\odot}}}^{2}
+            \p{\frac{m}{1.41 M_{\rm J}}}^{-1}
+            \p{\frac{R}{1.89R_{\rm J}}}^{3}\nonumber\\
+        &\times \p{\frac{a}{0.023\;\mathrm{AU}}}^{-6}
+            \p{\frac{m}{m_{\rm p}} \sqrt{\frac{a}{a_{\rm p}}}
+                \frac{1}{\sin I_{\rm tot}}}^{2/3},\\
+    \p{\frac{m_{\rm p}}{40 M_{\oplus}}}^{5/3}\p{\frac{a_{\rm
+        p}}{0.05\;\mathrm{AU}}}^{-8/3} \gtrsim {}& 1.5
+            \p{\frac{2k_2/Q}{10^{-7}}}^{2/3}
+            \p{\frac{M_\star}{1.36 M_{\odot}}}^{2}
+            \p{\frac{m}{1.41 M_{\rm J}}}^{-1}
+            \p{\frac{R}{1.89R_{\rm J}}}^{3}\nonumber\\
+        &\times \p{\frac{a}{0.023\;\mathrm{AU}}}^{-6}
+            \p{\frac{1}{\sin I_{\rm tot}}}^{2/3}.
+\end{align}
+
+What is the corresponding RV signal of such a planet? The RV signal in the star
+is given as a velocity, which is just $n_{\rm p} \times a_{\rm p}\frac{m_{\rm
+p}}{M_{\star}}$. Including the projection effect by an angle $i$, we should find
+that
+\begin{align}
+    \text{RV semi-amplitude} &\approx
+            n_{\rm p}a_{\rm p}\frac{m_{\rm p}}{M_{\star}} \sin i,\\
+        &\approx 10\;\mathrm{m/s} \frac{\sin i}{1/\sqrt{2}}
+\end{align}
+This is in agreement with Fig 3 of Millholland's plot.
+
 \subsection{Dissipating Disk: $\theta_f$ Distribution}

### 2021-05-04 writeups/Su_weak_tides.tex
can't decide on color but technically have a draft

@@
 fixed, while the spin orientation $\uv{s}$ experiences an alignment torque
-towards $\uv{l}$ on the alignment timescale $t_{\rm s}$:
+towards $\uv{l}$ on the alignment timescale $t_{\rm al}$:
 \begin{equation}
     \p{\rd{\uv{s}}{t}}_{\rm tide}
-        = \frac{1}{t_{\rm s}} \uv{s} \times \p{\uv{l} \times \uv{s}}.
+        = \frac{1}{t_{\rm al}} \uv{s} \times \p{\uv{l} \times \uv{s}}.
         \label{eq:dsdt_tide_toy}
@@
 \begin{align}
-    \rd{\theta}{t} &= -g\sin I \sin \phi - \frac{1}{t_{\rm s}} \sin \theta,
+    \rd{\theta}{t} &= -g\sin I \sin \phi - \frac{1}{t_{\rm al}} \sin \theta,
         \label{eq:dqdt_toy}\\
@@
 
-If the alignment torque is weak ($\abs{gt_{\rm s}} \gg 1$), then the fixed points of
-Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) are just slightly shifted CSs. This
-shift can be calculated cleanly to leading order: all of the CS obliquities
-$\theta_{\rm cs}$ are unchanged while the azimuthal angle $\phi_{\rm cs}$ for
-each CS now satisfies
-\begin{equation}
-    \sin \phi_{\rm cs} = \frac{\sin\theta_{\rm cs}}{\sin I \abs{g}t_{\rm s}}.
+If the alignment torque is weak ($\abs{g}t_{\rm al} \gg 1$), then the fixed
+points of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) are just slightly shifted
+CSs. This shift can be calculated cleanly to leading order: all of the CS
+obliquities $\theta_{\rm cs}$ are unchanged while the azimuthal angle $\phi_{\rm
+cs}$ for each CS now satisfies
+\begin{equation}
+    \sin \phi_{\rm cs} = \frac{\sin\theta_{\rm cs}}{\sin I \abs{g}t_{\rm al}}.
         \label{eq:mcs_shift}
 \end{equation}
-We can see that if $t_{\rm s} > t_{\rm s, c}$, where
-\begin{align}
-    t_{\rm s, c} &= \frac{1}{\abs{g}\sin I},\label{eq:mcs_shift_crit}
+We can see that if $t_{\rm al} > t_{\rm al, c}$, where
+\begin{align}
+    t_{\rm al, c} &= \frac{1}{\abs{g}\sin I},\label{eq:mcs_shift_crit}
 \end{align}
@@
 and the alignment torque never changes the number of fixed points of the system.
-If $t_{\rm s}$ is decreased below $t_{\rm s, c}$, CS2 and CS4 cease to be
+If $t_{\rm al}$ is decreased below $t_{\rm al, c}$, CS2 and CS4 cease to be
 fixed points if $\eta \ll 1$ \citep[as first noted in][]{fabrycky_otides}, as
@@
 CSs in the $\eta \ll 1$ case, where it can be seen that CS2 and CS4 collide and
-annihilate. The phase shift $\phi_{\rm cs}$ for CS2 and CS4 for $t_{\rm s} >
-t_{\rm s, c}$ can be predicted to good accuracy using Eq.~\eqref{eq:mcs_shift}
+annihilate. The phase shift $\phi_{\rm cs}$ for CS2 and CS4 for $t_{\rm al} >
+t_{\rm al, c}$ can be predicted to good accuracy using Eq.~\eqref{eq:mcs_shift}
 using $\theta_{\rm cs} \approx \pi/2 - \eta \cos (I) \approx 79^\circ$
@@
 Fig.~\ref{fig:mcs}. For the remainder of this section, we will consider the case
-where $t_{\rm s} \gg t_{\rm s, c}$ and the CSs only differ slightly from their
+where $t_{\rm al} \gg t_{\rm al, c}$ and the CSs only differ slightly from their
 unperturbed locations.
@@
     bottom panel give the CS2 and CS4 azimuthal angles according to
-    Eq.~\eqref{eq:mcs_shift}. At $\abs{gt_{\rm s} \sin I} = 1$, CS2 and CS4
+    Eq.~\eqref{eq:mcs_shift}. At $\abs{gt_{\rm al} \sin I} = 1$, CS2 and CS4
     collide and annihilate (Eq.~\ref{eq:mcs_shift_crit}).}\label{fig:mcs}
@@
     \end{bmatrix} &= \begin{bmatrix}
-        -\frac{\cos \theta}{t_{\rm s}} &
+        -\frac{\cos \theta}{t_{\rm al}} &
         -g\sin I \cos \phi \\
@@
 \begin{equation}
-    0 = \p{\lambda + \frac{\cos \theta_{\rm cs}}{t_{\rm s}}}\lambda
+    0 = \p{\lambda + \frac{\cos \theta_{\rm cs}}{t_{\rm al}}}\lambda
         - \lambda_0^2,\label{eq:lambda_orig}
@@
 \end{equation}
-When $t_{\rm s}$ is large, we can simplify Eq.~\eqref{eq:lambda_orig} to
-\begin{equation}
-    \lambda \approx -\frac{\cos \theta_{\rm cs}}{t_{\rm s}}
+When $t_{\rm al}$ is large, we can simplify Eq.~\eqref{eq:lambda_orig} to
+\begin{equation}
+    \lambda \approx -\frac{\cos \theta_{\rm cs}}{t_{\rm al}}
         \pm \sqrt{\lambda_0^2}. \label{eq:lambda_approx}
@@
 conditions uniformly distributed in $\p{\cos \theta, \phi}$ with $\abs{g}t_{\rm
-s} = 10^{-3}$ and record the nearest CS for each integration after $10t_{\rm
-s}$. In Fig.~\ref{fig:toy_phop}, we show the results of this procedure for $\eta
+al}= 10^{-3}$ and record the nearest CS for each integration after $10t_{\rm al}$. In Fig.~\ref{fig:toy_phop}, we show the results of this procedure for $\eta
 = 0.2$, and $I = 20^\circ$. It is clear that initial conditions in zone I evolve
@@
         &= \p{\rd{(\cos\theta)}{t}}_{\rm tide} \rd{\phi}{t},\\
-    \Delta H_{\pm} &= \mp\frac{1}{t_{\rm s}}
+    \Delta H_{\pm} &= \mp\frac{1}{t_{\rm al}}
         \int\limits_0^{2\pi} \sin^2\theta\;\mathrm{d}\phi.
@@
 respectively. Finally, if the alignment torque is weak, then $\Delta H_- \sim
-\mathcal{O}\p{t_{\rm s}^{-1}}$ is small compared to the characteristic values of
+\mathcal{O}\p{t_{\rm al}^{-1}}$ is small compared to the characteristic values of
 $H$, and $H_{\rm i}$ can be effectively considered as uniformly distributed over
@@
     \caption{Plot illustrating the probabilistic origin of separatrix capture
-    for $\eta = 0.2$, $I = 20^\circ$, and $\abs{gt_{\rm s}} = 10^{-3}$. Orange
+    for $\eta = 0.2$, $I = 20^\circ$, and $\abs{gt_{\rm al}} = 10^{-3}$. Orange
     regions converge to CS1, and green to CS2, while CS4 is labeled with the
@@
 \begin{align}
-    \Delta H_- &\approx \frac{2\pi}{t_{\rm s}}\p{1
+    \Delta H_- &\approx \frac{2\pi}{t_{\rm al}}\p{1
         - 2\eta \sin I} + \mathcal{O}(\eta^{3/2}),\\
     \Delta H_+ + \Delta H_- &\approx
-        \frac{32 \eta^{3/2}\cos I \sqrt{\sin I}}{t_{\rm s}}
+        \frac{32 \eta^{3/2}\cos I \sqrt{\sin I}}{t_{\rm al}}
             + \mathcal{O}\p{\eta^{5/2}},\\
@@
 equilibrium tides \citep{lai2012}. In this model, tides cause both $\uv{s}$ and
-$\Omega_{\rm s}$ to evolve on the characteristic tidal timescale $t_{\rm a}$:
-\begin{align}
-    \p{\rd{\uv{s}}{t}}_{\rm tide} &= \frac{1}{t_{\rm a}}
+$\Omega_{\rm s}$ to evolve on the characteristic tidal timescale $t_{\rm s}$:
+\begin{align}
+    \p{\rd{\uv{s}}{t}}_{\rm tide} &= \frac{1}{t_{\rm s}}
                 \s{\frac{2n}{\Omega_{\rm s}} - \p{\uv{s} \cdot \uv{l}}}
@@
     \frac{1}{\Omega_{\rm s}}\p{\rd{\Omega_{\rm s}}{t}}_{\rm tide}
-        &= \frac{1}{t_{\rm a}} \s{\frac{2n}{\Omega_{\rm s}}\p{\uv{s} \cdot
+        &= \frac{1}{t_{\rm s}} \s{\frac{2n}{\Omega_{\rm s}}\p{\uv{s} \cdot
             \uv{l}} - 1 - \p{\uv{s} \cdot \uv{l}}^2},\label{eq:dWsdt_tide}
 \end{align}
-where $t_{\rm a}$ is given by
-\begin{equation}
-    \frac{1}{t_{\rm a}} \equiv \frac{L}{2S} \frac{\Omega_{\rm
+where $t_{\rm s}$ is given by
+\begin{equation}
+    \frac{1}{t_{\rm s}} \equiv \frac{L}{2S} \frac{\Omega_{\rm
         s}}{2n}\frac{3k_2}{Q}\p{\frac{M_\star}{m}}\p{\frac{R}{a}}^5 n.
@@
 angular momenta of the inner planet, respectively. We neglect orbital evolution
-in this section since the time scale is longer than $t_{\rm a}$ by a factor of
-$\sim L / S \gg 1$, and so $t_{\rm a}$ is a constant. We will continue mostly
-consider the case where $\abs{gt_{\rm a}} \gg 1$. The full equations of motion
+in this section since the time scale is longer than $t_{\rm s}$ by a factor of
+$\sim L / S \gg 1$, and so $t_{\rm s}$ is a constant. We will continue mostly
+consider the case where $\abs{gt_{\rm s}} \gg 1$. The full equations of motion
 including weak tidal friction are
@@
     \rd{\theta}{t} &= g\sin I \sin \phi -
-        \frac{1}{t_{\rm a}}\sin \theta\p{\frac{2n}{\Omega_{\rm s}} - \cos \theta}
+        \frac{1}{t_{\rm s}}\sin \theta\p{\frac{2n}{\Omega_{\rm s}} - \cos \theta}
             ,\label{eq:ds_fullq}\\
@@
     \frac{1}{\Omega_{\rm s}}\rd{\Omega_{\rm s}}{t}
-        &= \frac{1}{t_{\rm a}} \s{\frac{2n}{\Omega_{\rm s}} \cos \theta
+        &= \frac{1}{t_{\rm s}} \s{\frac{2n}{\Omega_{\rm s}} \cos \theta
             - \p{1 + \cos^2\theta}}\label{eq:ds_fulls}.
@@
 $\Omega_{\rm s}$ evolves. Then, evaluating Eq.~\eqref{eq:lambda_approx} with
-$t_{\rm s} = t_{\rm a} / \p{2n / \Omega_{\rm s} - \cos \theta}$ (compare
+$t_{\rm al} = t_{\rm s} / \p{2n / \Omega_{\rm s} - \cos \theta}$ (compare
 Eqs.~\ref{eq:dsdt_tide_toy} and~Eq.~\ref{eq:dsdt_tide}), we see that CS2 is
@@
 parameter
-\begin{equation}
-    \eta_{\rm sync} \equiv \big(\eta\big)_{\Omega_{\rm s} = n},
-        \label{eq:def_etasync}
-\end{equation}
+\begin{align}
+    \eta_{\rm sync} &\equiv \big(\eta\big)_{\Omega_{\rm s} = n}
+        = \eta \frac{\Omega_{\rm s}}{n}\nonumber\\
+        &= \textcolor{red}{\frac{m_{\rm p}m}{2M_\star^2}\p{\frac{a}{a_{\rm
+            p}}}^3 \p{\frac{a}{R}}^3}. \label{eq:def_etasync}
+\end{align}
 The tCE obliquity as a function of $\eta_{\rm sync}$ are shown for $I =
 20^\circ$ in the top panel of Fig.~\ref{fig:probs20} and for $I = 5^\circ$ in
-the top panel of Fig.~\ref{fig:probs5}.
+the top panel of Fig.~\ref{fig:probs5}. In fact, an analytical expression for
+the tCE2 obliquity for $\eta_{\rm sync} \ll \eta_{\rm c}$ can be computed using
+Eqs.~(\ref{eq:weaktide_dWszero}--\ref{eq:def_etasync}) and that $\cos \theta_2
+\approx \eta \cos I$ to yield:
+\begin{align}
+    \cos \theta_{\rm tCE2} &\approx \sqrt{\frac{\eta_{\rm sync} \cos I}{2}},
+        &
+    \frac{\Omega_{\rm s, tCE2}}{n} &\approx
+        \sqrt{2\cos I \eta_{\rm sync}}. \label{eq:def_tce2_approx}
+\end{align}
+This approximation for $\theta_{\rm tCE2}$ is shown as the black dashed line in
+the top panels of Fig.~\ref{fig:probs20} and~\ref{fig:probs5}.
 \begin{figure}
@@
 not be stable if the tidal phase shift is too large. Applying the results of
-Section~\ref{ss:tidal_equils}, we find that tCE2 is stable as long as $t_{\rm a}
-\geq t_{\rm a, c}$ where
-\begin{align}
-    t_{\rm a, c} &\equiv \frac{\sin \theta_{\rm tCE2}}{\abs{g} \sin I}.
-        \label{eq:def_ta_crit}
-\end{align}
-The tCE2 subscripts denote evaluation at tCE2. This can be further simplified
-using that Eq.~\eqref{eq:weaktide_dWszero} and $\cos \theta \approx
-\eta \cos I$ are satisfied at tCE2, giving:
-\begin{equation}
-    t_{\rm a,c} \approx \frac{1}{\abs{g}\sin I}\sqrt{\frac{2}{\eta_{\rm sync}
-        \cos I}}.
+Section~\ref{ss:tidal_equils}, we find that tCE2 is stable as long as $t_{\rm s}
+\geq t_{\rm s, c}$ where
+\begin{equation}
+    t_{\rm s, c} \equiv \frac{\sin \theta_{\rm tCE2}}{\abs{g} \sin
+            I}\p{\frac{2n}{\Omega_{\rm s, tCE2}} - \cos \theta_{\rm tCE2}}.
+\end{equation}
+The tCE2 subscripts denote evaluation at tCE2. When $\eta_{\rm sync} \ll
+\eta_{\rm c}$, we can use Eq.~\eqref{eq:def_tce2_approx} to further simplify:
+\begin{equation}
+    t_{\rm s, c}\approx \frac{1}{\abs{g}\sin I}\sqrt{\frac{2}{\eta_{\rm sync}
+        \cos I}}. \label{eq:def_ta_crit}
 \end{equation}
@@
 the legs of the separatrix. We define $\Delta K_{\pm}$ by generalizing
-Eq.~\eqref{eq:def_dHpm} very naturally:
+Eq.~\eqref{eq:def_dHpm} in the natural way:
 \begin{align}
@@
 $\Omega_{\rm s}$ upon separatrix encounter. Since there is no closed form
-solution for $\Omega_{\rm s}(t)$, the probabilities of the various outcomes can
-only be determined as a function of the system properties at separatrix
-encounter, and not as a simple function of the initial conditions.
+solution for $\Omega_{\rm s}(t)$, the probabilities of the various outcomes
+cannot be expressed as a simple function of the initial conditions.
 
@@
 K_{\pm}$ along the two legs of the separatrix obtained numerically via a root
-finding algorithm. Note that Eqs.~(\ref{eq:def_dK_weaktide},~\ref{eq:def_pc_weaktide}) are
-equivalent to the separatrix capture result of \citet{henrard1982} when $\cos
-\theta$ is not evolving \citep{henrard1987}. Here, we have argued that this
-classic calculation can be unified with the calculation given in
-Section~\ref{ss:toy_outcomes} to give an accurate prediction of separatrix
-encounter outcome probabilities in the presence of both a dissipative
-perturbation and a parametric variation of the Hamiltonian.
+finding algorithm. Note that
+Eqs.~(\ref{eq:def_dK_weaktide},~\ref{eq:def_pc_weaktide}) are equivalent to the
+separatrix capture result of \citet{henrard1982} when $\dot{\theta}_{\rm tide} =
+0$ \citep{henrard1987}. Here, we have argued that this classic calculation can
+be unified with the calculation given in Section~\ref{ss:toy_outcomes} to give
+an accurate prediction of separatrix encounter outcome probabilities in the
+presence of both a dissipative perturbation and a parametric variation of the
+Hamiltonian.
 
@@
     \caption{\emph{Top:} Obliquities of the two tCE where $I = 20^\circ$ for a
-    range of $\eta_{\rm sync}$ (Eq.~\ref{eq:def_etasync}), averaged over an
-    isotropic initial spin orientation. \emph{Bottom:} Total probability of
-    ending up in tCE2 (red dots). The red shaded region denotes the contribution
-    of initial conditions in zone II that converge to tCE2 directly, and the
-    yellow shaded region denotes the contribution of initial conditions in zone
-    III that converge to tCE2 after a separatrix encounter. The vertical dashed
-    line denotes $\eta_{\rm c}$ (Eq.~\ref{eq:def_etac}).}\label{fig:probs20}
+    range of $\eta_{\rm sync}$ (Eq.~\ref{eq:def_etasync}); the blue dashed line
+    denotes the analytical approximation Eq.~\eqref{eq:def_tce2_approx} valid
+    for $\eta_{\rm sync} \ll \eta_{\rm c}$ (vertical dashed line;
+    Eq.~\ref{eq:def_etac}). \emph{Bottom:} Total probability of ending up in
+    tCE2 (red dots), averaged over an isotropic initial spin orientation. The
+    red shaded region denotes the contribution of initial conditions in zone II
+    that converge to tCE2 directly, and the yellow shaded region denotes the
+    contribution of initial conditions in zone III that converge to tCE2 after a
+    separatrix encounter. }\label{fig:probs20}
 \end{figure}
@@
 
-\subsection{Application to Warm + Cold Jupiter Systems
+\subsection{Application to Super Earth + Cold Jupiter Systems
 }\label{ss:disc_sehj}
@@
 Jupiter (CJ); such systems are expected to be abundant \citep{zhu2018super}. For
-this system, the relative tidal dissipation rate $\abs{gt_{\rm a}}^{-1}$ can be
+this system, the relative tidal dissipation rate $\abs{gt_{\rm s}}^{-1}$ can be
 computed
 \begin{align}
-    \frac{1}{\abs{g t_{\rm a}}}
+    \frac{1}{\abs{g} t_{\rm s}}
         \approx{}& 0.003\frac{1}{\cos I}\p{\frac{2k_2/Q}{10^{-3}}}
@@
 \end{align}
-In physical units, $t_{\rm a} \sim 2 \times 10^8\;\mathrm{yr}$ for the
+In physical units, $t_{\rm s} \sim 2 \times 10^8\;\mathrm{yr}$ for the
 parameters adopted above, and $\dot{a} / a \sim 10^{14}\;\mathrm{yr}$, so the
@@
 safely neglected. Thus, the approximations of slow tidal dissipation and
-constant $a$ used throughout Section~\ref{s:full_tide_prob} is valid.
+constant $a$ used throughout Section~\ref{s:full_tide_prob} are valid.
 For the same fiducial parameters, Eq.~\eqref{eq:def_etasync} can be evaluated
@@
 Here, $\rho = m / \p{4\pi R^3/3}$ is the average density of the inner planet,
-and $M_{\rm J}$ is the mass of Jupiter. From Figs.~\ref{fig:probs20}
-and~\ref{fig:probs5}, we see that this value of $\eta_{\rm sync}$ gives a
-high-obliquity tCE2 with significant probability. Thus, we predict that a
-sizable fraction of SEs with exterior CJ companions can have significant
-obliquities ($\sim \gtrsim 30^\circ$).
+and $M_{\rm J}$ is the mass of Jupiter. Evaluating Eq.~\eqref{eq:def_ta_crit},
+we find that $\abs{g}t_{\rm s, c} \approx 2 / \sin I$, which shows that tidal
+friction is many orders of magnitude too weak to destroy tCE2. Additionally,
+we see from Figs.~\ref{fig:probs20} and~\ref{fig:probs5} that this value of
+$\eta_{\rm sync}$ gives a high-obliquity tCE2 with significant probability.
+Thus, we predict that a sizable fraction of SEs with exterior CJ companions can
+have significant obliquities ($\sim \gtrsim 60^\circ$).
 
@@
 CS2, and (iii) destruction of CS2 due to strong tidal dissipation and stalling
-of inward migration. Below, we revisit this process and show that the parameter
-space for this obliquity-driven tidal runaway formation channel of USPs is
-larger than is given in their work.
+of inward migration. They consider an inner proto-USP with two external
+perturbing planets. In this section, we apply our results above to a system
+architecture containing just a single planet, for simplicity.
 
 First, we verify agreement of our criterion for breaking of CS2 with theirs.
-Evaluating Eq.~\eqref{eq:mcs_shift_crit} for the weak tidal friction torque
-given by Eq.~\eqref{eq:mcs_shift}, we find that tCE2 breaks when the semi-major
-axis is smaller than $a_{\rm break}$ where \textcolor{red}{I haven't double
-checked this calculation\dots}
-\begin{align}
-    a_{\rm break}
-        \approx{}& 0.01\;\mathrm{AU}
-            \p{\frac{k}{k_q}}^{-1/18}
-            \p{\frac{2 k_2 / Q}{10^{-3}}}^{1/9}
-            \p{\frac{m_{\rm p}}{M_{\rm \oplus}}}^{-1/6}\nonumber\\
-            &\times \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{1/2}
-            \p{\frac{\rho}{6\;\mathrm{g/cm^3}}}^{-1/6}
-            \p{\frac{M_{\star}}{M_{\odot}}}^{1/3}.
-\end{align}
-We have calculated this for a mutual inclination of $I = 5^\circ$. This
-corresponds to an orbital period of about half a day, qualifying as a USP\@.
+Evaluating Eq.~\eqref{eq:def_ta_crit}, we find that tCE2 breaks when the
+semi-major axis is smaller than $a_{\rm break}$ where:
+\begin{align}
+    a_{\rm break} \approx{}& 0.038 \;\mathrm{AU}
+        \p{\frac{Q'}{10^{3}}}^{-1/9}
+        \p{\frac{M_\star}{M_{\odot}}}^{1/3}
+        \p{\frac{m}{8M_{\oplus}}}^{-1/3}\nonumber\\
+        &\times \p{\frac{R}{2R_{\oplus}}}^{1/2}
+        \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{1/2}
+        \p{\frac{1}{\sin I \sqrt{\cos I}}}^{1/9}.
+\end{align}
+Here, we have assumed the planets are the same mass ($m_{\rm p} = m$) and have
+used the reduced tidal parameter $Q' = 3Q / 2k_2$. This corresponds to a 2.7-day
+orbit and does \emph{not} qualify to be a USP\@.
 
@@
 of initial planet obliquities will give some probability of evolution towards
-CS2 and tCE2 (see Figs.~\ref{fig:Hhists_0_06}--\ref{fig:Hhists_0_70}). Thus, it
-is not necessary to restrict formation of USPs via tidal runaway to system
-architectures for which $\eta_{\rm sync} \gtrsim \eta_{\rm c}$. In fig
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{../initial/99_misc/5millholland_actives.png}
-    \caption{Plot showing allowable parameter space for USP formation for the
-    fiducial parameters: $P_{j + 1} / P_j = 1.3$ and $M_\star = M_{\odot}$,
-    mirroring Figure~5 of \citet{millholland2020formation}. Shaded in blue is
-    their region of allowable parameter space for USP formation ($\eta_{\rm
-    sync} \geq 1$ and $\dot{a} / a < \;\mathrm{Gyr}$), while shaded in
-    green is the region where $\eta_{\rm sync} \geq 1/3$, for which the tCE2
-    probability is $> 50\%$ for $I = 20^\circ$ (see Fig.~\ref{fig:probs20}).
-    \textcolor{red}{I added a few fudge factors temporarily to be a little bit
-    to be closer to the Millholland plot; I will double check their validity and
-    update this plot to better reflect our actual numbers / parameters.}
-    }\label{fig:millholland_actives}
-\end{figure}
-
-In particular, architectures with larger period ratios $P_{j + 1} / P_j$ (and
-thus, semi-major axis ratios; see Eq.~\ref{eq:def_etasync}) are still able to
-undergo tidal runaway. Such architectures can be advantageous for USP formation
-as more of their total angular momentum budget is in the outer planet's orbit,
-allowing for additional migration \citep{fabrycky_otides,
-millholland2020formation}.
+CS2 and tCE2 (see Figs.~\ref{fig:Hhists_0_06}--\ref{fig:Hhists_0_70}). To
+understand qualitatively the likelihood of this happening, we calculate the
+parameter
+\begin{align}
+    \eta_{\rm sync} ={}& 0.012 \p{\frac{k}{k_{\rm q}}}
+            \p{\frac{m}{8 M_{\oplus}}}^2
+            \p{\frac{M_\star}{M_{\odot}}}^{-2}\nonumber\\
+        &\times \p{\frac{a}{0.035 \;\mathrm{AU}}}^{3}
+            \p{\frac{P_{j + 1} / P_j}{1.5}}^{-2}
+            \p{\frac{R}{2R_{\oplus}}}^{-3}.
+\end{align}
+Thus, we see that capture into CS2 is not only not guaranteed but has quite low
+probability (see Figs.~\ref{fig:probs20}--\ref{fig:probs5}). Thus, we conclude
+that the presence of the third planet in their scenario significantly improves
+the formation rate of USPs, likely by significantly enhancing the precession
+rate $g$ compared to the two-planet case.
+
+At a more qualitative level, our result shows that it is not necessary to
+restrict formation of USPs via tidal runaway to system architectures for which
+$\eta_{\rm sync} \gtrsim \eta_{\rm c}$. In particular, architectures with larger
+period ratios $P_{j + 1} / P_j$ can still have substantial probability of
+generating an inner planet occupying tCE2 even if $\eta_{\rm sync} < \eta_{\rm
+c}$. Such architectures can be advantageous for USP formation as more of their
+total angular momentum budget is in the outer planet's orbit, allowing for more
+migration \citep{fabrycky_otides, millholland2020formation}.
 
@@
 
-Thoughts:
-\begin{itemize}
-    \item Significantly limited by conservation of angular momentum (spin of the
-        star is a reservoir?).
-
-    \item Initial conditions are solidly in the $\eta_{\rm sync} \gg 1$ regime
-        (CS2 obliquity goes to near zero when $a$ is increased by $\sim30\%$),
-        probably not a very useful application of our theory. For systems where
-        the perturber is \emph{strong}, our theory produces extra tCE2 systems
-        compared to neglecting the effect of resonance capture, but where the
-        perturber is weak, everybody knows that CS2 is guaranteed.
-\end{itemize}
+Applying our calculation for $a_{\rm break}$, we can calculate the required
+perturber properties if tCE2 is not to be destroyed by tides. This requires
+\begin{align}
+    \p{\frac{m_{\rm p}}{50 M_{\oplus}}}^{5/3}\p{\frac{a_{\rm
+        p}}{0.05\;\mathrm{AU}}}^{-8/3} \gtrsim {}&
+            \p{\frac{2k_2/Q}{10^{-7}}}^{2/3}
+            \p{\frac{M_\star}{1.36 M_{\odot}}}^{2}\nonumber\\
+        &\times \p{\frac{m}{1.41 M_{\rm J}}}^{-1}
+            \p{\frac{R}{1.89R_{\rm J}}}^{3}\nonumber\\
+        &\times \p{\frac{a}{0.023\;\mathrm{AU}}}^{-6}
+            \p{\frac{1}{\sin I_{\rm tot}}}^{2/3}.
+\end{align}
+The residuals of the published RVs (\textcolor{red}{TODO grab citations from
+Millholland, any updates?}) are $\sim 16\;\mathrm{m/s}$. Using a line-of-sight
+angle of $45^\circ$, we find that a planet with $m_{\rm p} = 50M_{\oplus}$ and
+$a_{\rm p} = 0.05\;\mathrm{AU}$ has an RV semi-amplitude of $12\;\mathrm{m/s}$,
+which cannot be ruled out. Thus, we reproduce the result of
+\citet{millholland_wasp12b}, that tCE2 remains stable under the dissipative
+tidal torque, and obliquity tides cannot be ruled out as a mechanism for
+WASP-12b's rapid orbital decay.
 

### 2021-05-04 initial/0_eta/3stats.py

@@ -118,7 +118,7 @@ def run_for_tide(tide=1e-3,
     # points below the separatrix, where do they converge to?
     below_convs = []
     # HACK HACK everything but CS1/2 are green as well
-    colors = ['orange', 'tab:green', 'orange', 'tab:purple']
+    colors = ['darkorange', 'tab:green', 'darkorange', 'tab:purple']
     for q, phi, conv_pts, c in zip(qs, phis, conv_data, colors):
         if conv_pts:
             q_plot, phi_plot = np.array(conv_pts).T
@@ -127,7 +127,7 @@ def run_for_tide(tide=1e-3,
             plt.plot(phis_plot,
                      np.cos(q_plot),
                      mfc=c, mec=c, marker='o', ls='',
-                     markersize=2)
+                     markersize=2, alpha=0.7)
         else:
             below_convs.append(0)
         # plot_point(plt.gca(), q, '%so' % c, markersize=8)

### 2021-05-04 initial/99_misc/2_rand_plots.py

@@ -113,13 +113,13 @@ def plot_cs_phi(I=np.radians(5)):
         if rads[0] < 0:
             return -np.degrees(rads)
         return np.degrees(rads)
-    plt.semilogx(etas_four, fix_d(cs_vals[0]), 'orange', lw=LW)
+    plt.semilogx(etas_four, fix_d(cs_vals[0]), 'darkorange', lw=LW)
     plt.semilogx(etas, fix_d(cs_vals[1]), 'tab:green', lw=LW)
     plt.semilogx(etas, fix_d(cs_vals[2]), 'tab:blue', lw=LW)
     plt.semilogx(etas_four, fix_d(cs_vals[3]), 'tab:purple', lw=LW)
     fs = 16
     plt.text(etas_four[0] * 1.1, fix_d(cs_vals[0])[0] + 5, r'CS1 ($\phi = 0$)',
-             fontsize=fs, color='orange', va='bottom')
+             fontsize=fs, color='darkorange', va='bottom')
     plt.text(etas_four[0] * 1.1, fix_d(cs_vals[3])[0], r'CS4 ($\phi = 0$)',
              fontsize=fs, color='tab:purple', va='bottom')
     plt.text(etas[-1] / 1.1, fix_d(cs_vals[1])[-1] + 8, r'CS2 ($\phi = \pi$)',
@@ -156,7 +156,7 @@ def plot_eigens(I=np.radians(5)):
     plt.semilogx(etas_four,
                  [lambda2(e, q, -1)
                   for e, q in zip(etas_four, cs_vals[0])],
-                 'orange', label='CS1', lw=LW)
+                 'darkorange', label='CS1', lw=LW)
     plt.semilogx(etas,
                  [lambda2(e, q, -1)
                   for e, q in zip(etas, cs_vals[1])],
@@ -190,7 +190,7 @@ def plot_eigens(I=np.radians(5)):
     plt.semilogx(etas_four,
                  [lambda2(e, q, -1 / 2)
                   for e, q in zip(etas_four, cs_vals[0])],
-                 color='orange', ls='--', lw=lw, alpha=0.5)
+                 color='darkorange', ls='--', lw=lw, alpha=0.5)
     plt.semilogx(etas,
                  [lambda2(e, q, -1 / 2)
                   for e, q in zip(etas, cs_vals[1])],

### 2021-05-10 initial/notes.tex
stash 0512

--- 2020-05-11 initial/notes.tex
@@
     \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
+    \newcommand*{\rdil}[2]{\mathrm{d}#1 / \mathrm{d}#2}
+    \newcommand*{\pdil}[2]{\partial#1 / \partial#2}
     \newcommand*{\rtd}[2]{\frac{\mathrm{d}^2#1}{\mathrm{d}#2^2}}
@@
     \newcommand*{\z}[1]{\left\{#1\right\}}
+    \newcommand*{\uv}[1]{\hat{\bm{#1}}}
 
@@
 
-\def\Snospace~{\S{}} % hack to remove the space left after autorefs
 \renewcommand*{\sectionautorefname}{\Snospace}
@@
 noting that $\mu_4 = \frac{\cos I}{\alpha - \sin I}, \phi_4 = 0$ is exact (where
-$\alpha = s/s_c$ for brevity and compatibility with \autoref{s:p2}).
+$\alpha = s/s_c$ for brevity and compatibility with Section~\ref{s:p2}).
 \begin{align*}
@@
 
+\section{Paper Discussion Section Calculations}
+
+\subsection{Compact Multi-Planet Systems}
+
+\subsubsection{Our calculation}
+
+We focus on the USP regime. In the notation of the paper, we need
+\begin{align}
+    1
+        &\approx \frac{2n / \Omega_{\rm s} - \cos \theta
+            }{\abs{g}t_{\rm s}\sin I}.
+\end{align}
+One tricky thing about this calculation is that $\eta$ depends on $\Omega_{\rm
+s}$ which depends on $\cos \theta$ which depends on $\eta$:
+\begin{align}
+    \eta &= \eta_{\rm sync} \frac{n}{\Omega_{\rm s}},\\
+    \frac{n}{\Omega_{\rm s}} &= \frac{1 + \cos^2\theta}{2 \cos \theta},\\
+    \cos \theta &\approx \frac{\eta \cos I}{1 + \eta \sin I}.
+\end{align}
+This requires that
+\begin{align}
+    \frac{\eta}{\eta_{\rm sync}} &\approx \frac{1 + \eta \sin I
+        }{2\eta \cos I},\\
+    2\eta^2 \cos I &\approx \eta_{\rm sync} + \eta_{\rm sync}\eta \sin I,\\
+    \eta &= \frac{\eta_{\rm sync}\sin I + \sqrt{
+        \eta_{\rm sync}^2 \sin^2 I + 8\cos I \eta_{\rm sync}}}{
+            4 \cos I}.
+\end{align}
+It proves sufficient to use the simpler form of this:
+\begin{align}
+    \eta &\approx \sqrt{\frac{\eta_{\rm sync}}{2\cos I}},\\
+    t_{\rm s, c} &= \frac{2n / \Omega_{\rm s}}{\abs{g}\sin I},\\
+        &= \frac{2}{\abs{g}\sin I\sqrt{2\eta_{\rm sync} \cos I}}.
+\end{align}
+Thus, we can continue to evaluate laboriously:
+\begin{align}
+    \frac{1}{t_{\rm s, c}} &= \abs{g}\sin I \sqrt{\frac{\eta_{\rm sync} \cos
+        I}{2}},\\
+    g &= \frac{3m_p}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^3 n\cos I,\\
+    \frac{1}{t_{\rm s}} &= \frac{1}{4k}\frac{3k_2}{Q} \frac{M_{\star}}{m}
+        \p{\frac{R}{a}}^3 n,\\
+    \eta_{\rm sync} &= \s{\frac{3m_p}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^3 n
+        \cos I}
+        \Bigg/ \s{\frac{3k_q}{2k} \frac{M_\star}{m}\p{\frac{R}{a}}^3 n},\\
+        &= \frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
+            \p{\frac{a}{R}}^3 \cos I,\\
+    \frac{1}{4k}\frac{3k_2}{Q}\frac{M_\star}{m}\p{\frac{R}{a}}^3
+        &= \frac{3m_{\rm p}}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^3
+            \cos I \sin I \sqrt{\frac{\cos I}{2}}
+            \sqrt{\frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
+                \p{\frac{a}{R}}^3 \frac{k}{k_q}\cos I},\\
+        &= \frac{3}{8}\sqrt{\frac{m_{\rm p}^3m}{M_\star^4}
+            \frac{a^{12}}{a_{\rm p}^9 R^3}
+            \frac{k}{k_{\rm q}}}
+            \sin I \cos^2 I,\\
+    a^9 &= \frac{2k_2}{Q} \frac{M_\star^3}{(mm_{\rm p})^{3/2}}
+        \p{Ra_{\rm p}}^{9/2}\frac{1}{\sin I \cos^2 I}
+        \p{\frac{k}{k_{\rm q}}}^{-1/2},\\
+% (1e-3 * (Msun / (8 Mearth))^3 * ((2 Rearth) * (0.05 AU))^(9/2))^(1/9) / (1 AU)
+% = 0.033198
+    a_{\rm break} &\approx 0.033 \;\mathrm{AU}
+        \p{\frac{2k_2/Q}{10^{-3}}}^{1/9}
+        \p{\frac{M_\star}{M_{\odot}}}^{1/3}
+        \p{\frac{8M_{\oplus}}{m}}^{-1/3}
+        \p{\frac{R}{2R_{\oplus}}}^{1/2}
+        \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{1/2}
+        \p{\frac{1}{\sin I \cos^2 I}}^{1/9},\\
+% ((8 Mearth)^2 / (Msun)^2) / 2 * (1.3)^(-2) * ((0.035 AU) / (2 Rearth))^3
+% = 0.011845
+    \eta_{\rm sync} &= \frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
+            \p{\frac{a}{R}}^3,\\
+        &= 0.012 \p{\frac{k}{k_{\rm q}}}
+                \p{\frac{m}{8 M_{\oplus}}}^2
+                \p{\frac{M_\star}{M_{\odot}}}^{-2}
+            \p{\frac{a}{0.035 \;\mathrm{AU}}}^{3}
+                \p{\frac{P_{j + 1} / P_j}{1.3}}^{-2}
+                \p{\frac{R}{2R_{\oplus}}}^{-3}.
+\end{align}
+
+\subsubsection{Revised Calculation following Millholland more closely}
+
+We consider a detailed calculation of the $\eta_{\rm sync}$ for an inner planet
+of a compact, multi-planet system, with an eye towards applying it to the
+Millholland runaway USP formation scenario. In this scenario, $\rdil{\uv{s}}{t}$
+does not change, and is still given by
+\begin{align}
+    \rd{\uv{s}}{t} &= \omega_{\rm sl}\p{\uv{s} \cdot \uv{l}}
+            \p{\uv{s} \times \uv{l}},\\
+    \omega_{\rm sl} \equiv \alpha &= \frac{3k_q}{2k}\frac{M_\star}{m}
+        \p{\frac{R}{a}}^3 \Omega_{\rm s},\\
+        &\approx n10^{-3} \p{\frac{M_{\star}}{M_{\odot}}}
+            \p{\frac{m}{8 M_{\oplus}}}^{-1}
+            \p{\frac{R}{2 R_{\oplus}}}^3
+            \p{\frac{a}{0.035\;\mathrm{AU}}}^3
+            \p{\frac{\Omega_{\rm s}}{n}}.
+\end{align}
+Note, for future reference, $3k_q = k_2$.
+
+On the other hand, the evolution of $\uv{l}$ must be done more carefully, using
+secular L-L theory. If we follow Millholland's formulation (which basically
+includes a $J_2$ precession term from the star on top of the LL theory), we find
+that the angular momentum vectors (inclination vectors) evolve by the matrix
+$\bm{B}$, which has entries
+\begin{align}
+    B_{jj} ={}& -n_j\s{
+        \frac{3}{2}J_{2\star} \p{\frac{R_\star}{a_j}}^2
+        - \frac{27}{8}J_{2\star}^2\p{\frac{R_\star}{a_j}}^4
+        + \frac{1}{4}\sum\limits_{k \neq j}
+            \frac{M_{p, k}}{M_\star + M_{p, j}}
+            \alpha_{jk} \bar{\alpha}_{jk}
+            b_{3/2}^{(1)}\p{\alpha_{jk}}},\\
+        \approx{}&
+            -n_{j}\Bigg(\frac{3}{2}10^{-3}\frac{1}{60}
+                \p{\frac{k_{2\star}}{0.2}}
+                \p{\frac{P_{\star}}{\mathrm{day}}}^{-2}
+                \p{\frac{R_{\star}}{R_{\odot}}}^5
+                \p{\frac{M_\star}{M_{\odot}}}^{-1}
+                \p{\frac{a_j}{0.035\;\mathrm{AU}}}^2\nonumber\\
+            &+ \frac{1}{4} \p{2 \times 10^{-5}}
+                \sum\limits_{k \neq j}
+                \p{\frac{M_{p, k}}{8 M_{\oplus}}}
+                \p{\frac{M_\star}{M_{\odot}}}^{-1}
+                \alpha_{jk}\bar{\alpha}_{jk}b_{3/2}^{(1)}\p{\alpha_{jk}}
+            \Bigg).
+            &\\
+    B_{jk} ={}& \frac{1}{4}n_j
+            \frac{M_{p, k}}{M_\star + M_{p, j}}
+            \alpha_{jk} \bar{\alpha}_{jk}
+            b_{3/2}^{(1)}\p{\alpha_{jk}},\\
+        ={}& n_j\frac{1}{4} \p{2 \times 10^{-5}}
+                \p{\frac{M_{p, k}}{8 M_{\oplus}}}
+                \p{\frac{M_\star}{M_{\odot}}}^{-1}
+                \alpha_{jk}\bar{\alpha}_{jk}b_{3/2}^{(1)}\p{\alpha_{jk}}.
+\end{align}
+Above, $\alpha_{jk} = a_{\min} / a_{\max}$, $\bar{a}_{jk} = \min(\alpha_{jk},
+1)$, and, in the case of $j < k$:
+\begin{equation}
+    \alpha_{jk}\bar{\alpha}_{jk}b_{3/2}^{(1)}
+        \approx 3\p{\frac{a_j}{a_k}}^3 + \frac{43}{8}\p{\frac{a_j}{a_k}}^5
+            + \dots
+\end{equation}
+
+For the fiducial values, the $J_2$ term is mildly dominant in the diagonal
+terms, but as the Millholland paper uses $J_2 = 10^{-4}$ intsead, we see that it
+is mildly subdominant, and we will ignore it here. Calling $n \equiv n_0$ the
+mean motion of the innermost planet, we can express
+\begin{align}
+    \frac{B_{jj}}{n \p{2 \times 10^{-5}}}
+        \p{\frac{m}{8 M_{\oplus}}}^{-1}
+        \p{\frac{M_\star}{M_{\odot}}}
+        &= -\p{\frac{P_j}{P_{j + 1}}}^{j} \sum\limits_{k \neq j}
+            \frac{3}{4}\p{\frac{P_j}{P_{j+1}}}^{2(k - j)q/3},\\
+    \frac{B_{jk}}{n \p{2 \times 10^{-5}}}
+        \p{\frac{m}{8 M_{\oplus}}}^{-1}
+        \p{\frac{M_\star}{M_{\odot}}}
+        &= \p{\frac{P_j}{P_{j + 1}}}^{j}
+            \frac{3}{4}\p{\frac{P_j}{P_{j+1}}}^{2|k - j|q/3}.
+\end{align}
+Here, $q = 3$ when $j < k$ else $2$. For instance, for a 3 planet system,
+defining the period ratio $< 1$ to be $\gamma$:
+\begin{equation}
+    \bm{B} = n\p{1.5 \times 10^{-5}}
+        \p{\frac{m}{8 M_{\oplus}}}
+        \p{\frac{M_\star}{M_{\odot}}}^{-1}
+        \begin{bmatrix}
+            -(\gamma^2 + \gamma^4) & \gamma^2 & \gamma^{4}\\
+            \gamma^{7/3} & -(\gamma^{7/3} + \gamma^3) & \gamma^3\\
+            \gamma^{14/3} & \gamma^{10/3} & -\p{\gamma^{14/3} - \gamma^{10/3}}
+    \end{bmatrix}
+\end{equation}
+Empirically, we find that the most negative eigenvalue of the matrix scales with
+$\gamma^{2}$, or $\p{a / a_{\rm p}}^{3}$, indeed, as expected. Approximately the
+maximum eigenvalue is $2\p{\frac{a_j}{a_{j + 1}}}^3$. Thus, we arrive at
+\begin{equation}
+    g_{\max} \approx \cos I 10^{-5}n\p{\frac{m}{8M_{\oplus}}}
+        \p{\frac{M_{\star}}{M_{\odot}}}^{-1}\p{\frac{P_{j + 1} /
+        P_j}{1.5}}^{-2}.
+\end{equation}
+Indeed, we thus see that $\eta_{\rm sync} \sim 10^{-2}$, as we calculated
+before.
+
+\subsection{WASP-12b}
+
+\subsubsection{$\eta_{\rm sync}$}
+
+First, we calculate the $g$ precession frequency correctly. Let's just use
+vector notation for now, and consider the mutual precession of $\uv{l}$ and
+$\uv{l}_{\rm p}$:
+\begin{align}
+    \rd{\uv{l}}{t} &= \omega_{\rm lp}\p{\uv{l} \cdot \uv{l}_{\rm p}}
+        \p{\uv{l} \times \uv{l}_{\rm p}},\\
+    \rd{\uv{l}_{\rm p}}{t} &= -\frac{L}{L_{\rm p}}\omega_{\rm lp}\p{\uv{l} \cdot
+        \uv{l}_{\rm p}} \p{\uv{l} \times \uv{l}_{\rm p}}.
+\end{align}
+It is clear that the conserved quantity is $\bm{J} = \bm{L} + \bm{L}_{\rm p}$,
+so we rewrite
+\begin{align}
+    \rd{\uv{l}}{t} &= \omega_{\rm lp} \cos I\p{\uv{l} \times
+            \frac{\bm{L} + \bm{L}_{\rm p}}{L_{\rm p}}}\nonumber\\
+        &= \omega_{\rm lp} \cos I
+            \frac{J}{L_{\rm p}}\p{\uv{l} \times \uv{j}}.
+\end{align}
+Thus, the actual precession frequency to be used should be $g = \omega_{\rm lp}
+\cos I \p{J / L_{\rm p}}$. For future reference, we also have that $\sin i /
+L_{\rm p} = \sin i_{\rm p} / L = \sin I / J$, note from Fig.~\ref{fig:angles}.
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \filldraw (0,0) circle(1pt);
+        \draw[->] (0, 0)--(-1.2, 5);
+        \node[above left] at (-1.2, 5) {$L$};
+        \draw[->] (0, 0)--(1.2, 0.2);
+        \node[above right] at (1.2, 0.2) {$L_{\rm p}$};
+        \draw[->] (0, 0)--(0, 5.2);
+        \node[above] at (0, 5.2) {$J$};
+        \draw[->, dashed] (-1.2, 5) -- (0, 5.2);
+        \node[above] at (-0.2, 1.6) {$i$};
+        \node[above right] at (0, 0) {$i_{\rm p}$};
+        \node[below left] at (0, 5.2) {$i_{\rm p}$};
+        \node[right] at (-1.2, 4.8) {$I$};
+    \end{tikzpicture}
+    \caption{Picture of angles.}\label{fig:angles}
+\end{figure}
+
+What then is $\eta_{\rm sync}$? Well, in the case of WASP-12b, $J / L_{\rm p}
+\approx L / L_{\rm p} \approx (m/m_{\rm p})\sqrt{a / a_{\rm p}}$
+\begin{align}
+    \eta_{\rm sync} &\approx
+            \frac{k}{k_q}\frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
+            \p{\frac{a}{R}}^3\frac{L}{L_{\rm p}}\cos I\nonumber\\
+        &\approx
+            \frac{k}{k_q}\frac{m^2}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^{7/2}
+            \p{\frac{a}{R}}^3\cos I\nonumber\\
+        &\approx
+% 1/2 * (1.41 Mjup)^2 / (1.36 Msun)^2 * ((0.023 AU) / (1.89 Rjup))^3 * (0.023 / 0.05)^(3.5)
+            \scinot{5}{-4} \cos I\p{\frac{m}{1.41M_J}}^2
+                \p{\frac{M_\star}{1.36M_{\odot}}}^{-2}
+                \p{\frac{a}{0.023\;\mathrm{AU}}}^{13/2}
+                \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{-7/2}
+                \p{\frac{R}{1.89R_{J}}}^{-3}.
+\end{align}
+
+\subsubsection{Constraint: Tidal Decay Rate}
+
+We compute $\dot{a} / a$ for tidal dissipation in the HJ\@. Note here that
+$M_\odot R_{\rm J}^5/M_J \approx 10 M_{\rm J} / M_\odot R_{\rm J}^5$, and so if
+$Q \lesssim Q_\star$ then this is the dominant source of orbital decay.
+According to the Millholland paper, $Q / Q_\star \approx 0.1$, and so planetary
+tides can dominate if the planetary obliquity is substantial compared to the
+stellar obliquity (and indeed, the stellar tidal dissipation alone struggles to
+explain the boserved orbital decay). We thus obtain:
+\begin{align}
+    \frac{\dot{a}}{a} &= \frac{3k_2}{Q}\frac{M_\star}{m} \p{\frac{R}{a}}^5n
+            \p{1 - \frac{\Omega_{\rm s}}{n}\cos \theta},\\
+% 1 / (1.5 * 1e-7 * (1.36 Msun) / (1.41 Mjup) * ((1.89 Rjup) / (0.023 AU))^5 * (G * (1.36 Msun) / (0.023 AU)^3)^(1/2) * (1 yr))
+        &= \frac{1}{\scinot{3.8}{6}\;\mathrm{yr}}
+            \p{\frac{2k_2/Q}{10^{-6}}}
+            \p{\frac{M_\star}{1.36 M_{\odot}}}^{3/2}
+            \p{\frac{m}{1.41M_J}}^{-1}
+            \p{\frac{R}{1.89R_j}}^5
+            \p{\frac{a}{0.023\;\mathrm{AU}}}^{-13/2}
+            \p{1 - \frac{\Omega_{\rm s}}{n}\cos \theta}.
+\end{align}
+Note that for $a = 0.038\;\mathrm{AU}$, the tidal decay rate is $\sim
+\mathrm{Gyr}$. Since $\dot{a} \propto a^{-11/2}$, $a(t) \sim (C - t\dot{a} /
+a)^{2/13}$ for some constant $C$, so we see that we really can't start afford to
+start with the HJ any further out than $\sim 0.038\;\mathrm{AU}$
+
+\subsection{RV Constraint}
+
+What is the corresponding RV signal of a perturber? The RV signal in the star
+is given as a velocity, which is just $n_{\rm p} \times a_{\rm p}\frac{m_{\rm
+p}}{M_{\star}}$. Including the projection effect by an angle $i$, we should find
+that
+\begin{align}
+    \text{RV semi-amplitude} &\approx
+            n_{\rm p}a_{\rm p}\frac{m_{\rm p}}{M_{\star}} \sin i,\\
+%(G * (1.36 Msun) / (0.05 AU))^(1/2) * (50 Mearth) / (1.36 Msun) / 2^(1/2)
+        &\approx 12\;\mathrm{m/s}
+            \p{\frac{M_\star}{1.36M_{\odot}}}^{-1/2}
+            \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{-1/2}
+            \p{\frac{m_{\rm p}}{50M_{\oplus}}}
+            \frac{\sin i}{1/\sqrt{2}}
+\end{align}
+
+\subsubsection{Constraint of being in tCE2}
+
+In order for WASP-12b to be in tCE2, we require that:
+
+\begin{align}
+    \frac{1}{t_{\rm s}} &\lesssim \abs{g} \sin I
+        \sqrt{\frac{\eta_{\rm sync}\cos I}{2}},\\
+    \frac{1}{4k}\frac{3k_2}{Q}\frac{M_\star}{m}\p{\frac{R}{a}}^3
+        &\lesssim \frac{L}{L_{\rm p}}
+            \frac{3m_{\rm p}}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^3
+            \sin I \cos I\sqrt{\frac{\cos I}{2}}
+            \sqrt{\frac{m^2}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^{7/2}
+                \p{\frac{a}{R}}^3 \frac{k}{k_q}\cos I}\nonumber\\
+        &\lesssim \frac{3m}{4M_{\star}}\p{\frac{a}{a_{\rm p}}}^{7/2}
+            \sin I \cos I\sqrt{\frac{\cos I}{2}}
+            \sqrt{\frac{m^2}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^{7/2}
+                \p{\frac{a}{R}}^3 \frac{k}{k_q}\cos I}\nonumber\\
+    \p{\frac{a_{\rm p}}{a}}^{21/4} &\lesssim
+        \frac{3m}{4M_{\star}}
+            \frac{4k}{3}\p{\frac{2k_2}{Q}}^{-1}
+            \frac{m}{M_{\star}}
+            \p{\frac{a}{R}}^3
+            \sin I \cos^2 I
+            \sqrt{\frac{m^2}{M_\star^2}
+                \p{\frac{a}{R}}^3 \frac{k}{k_q}}\nonumber\\
+% (3/4 * ((1.41 * Mjup) / (1.36 * Msun))^3 * (1/3) * 1e6 * ((0.023 AU) / (1.89 Rjup))^(9/2))^(4/21)
+% = 3.3469
+    \frac{a_{\rm p}}{a} &\lesssim 3.3
+            \p{\frac{m}{1.41 M_J}}^{12/21}
+            \p{\frac{M_\star}{1.36 M_{\odot}}}^{-12/21}
+            \p{\frac{2k_2/Q}{10^{-6}}}^{-4/21}
+            \p{\frac{a}{0.023\;\mathrm{AU}}}^{6/7}
+            \p{\frac{R}{1.89 R_J}}^{-6/7}.
+\end{align}
+Indeed, this is not a very difficult constraint to satisfy. If anything, it is
+harder to satisfy the angular momentum constraint, that
+\begin{equation}
+    \frac{L}{L_{\rm p}} = \frac{m}{m_{\rm p}}\sqrt{\frac{a}{a_{\rm p}}} \gg 1.
+\end{equation}
+
+\subsubsection{Constraint: Initial Orbital Stability}
+
+With the constraint of being in tCE2 seeming relatively easy to satisfy, we also
+require that the system be initially stable, which sets a minimum $a_{\rm p}$.
+If the Hill radius criterion is used:
+\begin{equation}
+    a_2 - a_1 > 2\sqrt{3}\frac{a_1 + a_2}{2}\p{\frac{m_1 + m_2}{3m_0}}^{1/3},
+\end{equation}
+then we can calculate in the regime $m_2 \ll m_1$ to find:
+\begin{equation}
+    a_{\rm p} \gtrsim 0.049\;\mathrm{AU}.
+\end{equation}
+
+\subsubsection{Putting it all together}
+
+Thus, the system must satisfy all of: (i) starts with an initial tidal decay
+rate $\lesssim \;\mathrm{Gyr}$, (ii) the present-day tCE2 must be stable to
+tidal dissipation, and (iii) cannot have a perturber above the RV noise
+threshold. These constraints together give that: (i) the initial $a_{\rm i}
+\lesssim 0.038\;\mathrm{AU}$, (ii) the perturber $a_{\rm p} \lesssim
+0.076\;\mathrm{AU}$, and, if the perturber distance is maximal, (iii) $m_{\rm p}
+\lesssim 80 M_{\oplus}$.
+
+We verify that the angular momentum ratio of the perturber is indeed negligible:
+$L / L_{\rm p} \approx 3$, which is marginally satisfied (and is better
+satisfied if $a_{\rm p}$ is smaller).
+
+Finally, re-evaluating $\eta_{\rm sync}$ at the start of the orbital decay for
+the most optimistic initial conditions, where $a_{\rm p} = 0.049\;\mathrm{AU}$
+and $a = 0.038\;\mathrm{AU}$, we find:
+% 1/2 * (1.41 Mjup)^2 / (1.36 Msun)^2 * ((0.038 AU) / (1.89 Rjup))^3 * (0.038 / 0.049)^(3.5)
+% 0.016
+\begin{equation}
+    \eta_{\rm sync} = 0.016 \cos I\p{\frac{m}{1.41M_J}}^2
+            \p{\frac{M_\star}{1.36M_{\odot}}}^{-2}
+            \p{\frac{a}{0.038\;\mathrm{AU}}}^{13/2}
+            \p{\frac{a_{\rm p}}{0.049\;\mathrm{AU}}}^{-7/2}
+            \p{\frac{R}{1.89R_{J}}}^{-3}.
+\end{equation}
+% 1/2 * (Mjup)^2 / (Msun)^2 * ((0.04 AU) / Rjup)^3 * (0.04 / 0.08)^(3.5)
+Note, if we use Dong's values that we indeed get $\eta_{\rm sync} = 0.025$, in
+agreement. Note that if the HJ was initially less inflated, the tidal decay rate
+constraint implies that $R^5 / a^{13/2}$ must be a constant, thus, using a
+smaller $R$ actually even \emph{further} decreases $\eta_{\rm sync}$ Thus, even
+with the most optimistic parameter choices, we see that the formation
+probability of WASP-12b due to weak tidal friction out of an initially isotropic
+spin is quite improbable.
+
 \end{document}

### 2021-05-10 writeups/Su_weak_tides.tex
stash 0512

@@
 
-\begin{itemize}
-    \item Studying planetary obliquities (define) is important. Cassini States
-        are key. More introduction.
-
-    \item Resonance capture via separatrix crossing was first considered by
-        \citep{henrard1982} for non-dissipative perturbations
-        \citep[e.g.][]{su2020}. However, tidal friction is dissipative, so this
-        formalism does not apply. We generalize this calculation and show that
-        it reproduces results.
-\end{itemize}
-
-In Section XXX\dots
+% (i) What is obliquity? Why is it important, esp in exoplanetary systems?
+% (ii) what are the dynamics of obliquity?
+% (iii) Introduce Paper I
+
+It is well recognized that the obliquity of a planet, the angle between the spin
+and orbital axes, likely reflects its dynamical history. In our Solar
+System, planetary obliquities (hereafter just ``obliquities'') range from
+$3.1^\circ$ for Jupiter to $26.7^\circ$ for Saturn to $98^\circ$ for Uranus. The
+obliquities of exoplanets are challinging to measure, and so far only loose
+constraints have been obtained for the obliquity of a faraway ($\gtrsim
+50\;\mathrm{AU}$) planetary-mass companion \citep{bryan2020obliquity}.
+Nevertheless, there are prospects for better constraints on exoplanetary
+obliquities in the coming years, such as using high-resolution spectroscopy to
+measure $v\sin i$ for a planet \citep{snellen2014fast, bryan2018constraints} and
+using high-precision photometry to measure the asphericity of a planet
+\citep{seager2002constraining}. Substantial obliquities are of increasing
+theoretical interest for their proposed role in explaining peculiar thermal
+phase curves \citep[see e.g.][]{millholland_signatures, ohno_infer_obl}, in
+enhancing tidal dissipation in hot Jupiters \citep{millholland_wasp12b} and
+super-Earths \citep{millholland2019obliquity}, and in the formation of
+ultra-short-period planets \citep[USPs;][]{millholland2020formation} .
+
+While nonzero obliquities are sometimes attributed to one or many giant impacts
+\citep[e.g.]{original_gi, benz1989tilting, korycansky1990one, morbidelli_gi},
+some studies suggest that large planetary obliquities may be due to encountering
+spin-orbit resonances. In this scenario, a rotating planet is subjected to a
+gravitational torque from its host star, making its spin axis precess around its
+orbital (angular momentum) axis. At the same time, the orbital axis precesses
+around another fixed axis under the gravitational influence of other masses in
+the system, e.g.\ additional planets or a protoplanetary disk. When the two
+precession frequencies become commensurate, a resonance can occur that excites
+the obliquity to large values. This model is known as ``Colombo's Top'' after
+the seminal work of \citet{colombo1966}, and subsequent works have investigated
+the rich dynamics of this system \citep{peale1969, peale1974possible,
+ward1975tidal, henrard1987}. Such resonances have been invoked to explain the
+obliquities of both the Solar System gas giants \citep{ward2004I, ward2004II,
+ward_jupiter, vokrouhlicky2015tilting, saillenfest2020future,
+saillenfest2021large} and the ice giants \citep{hamilton_tilting_ice}.
+
+In a previous paper \citep[hereafter Paper I]{su2020}, we presented a systematic
+and general investigation of the dynamics of Colombo's Top when the two
+precession frequencies of the system evolve through a commensurability. We
+applied our results to investigate the generation of exoplanetary obliquities
+via a dissipating protoplanetary disk. However, our model did not consider the
+effect of additional torques in the system. Often, tidal dissipation in the
+planet both causes the planet's spin frequency to approach its orbital frequency
+and drives the planet's spin axis towards its orbital axis, complicating the
+evolution of Colombo's Top \citep{fabrycky_otides, peale2008obliquity}. In this
+paper, we extend the approach of Paper I to include tidal dissipation. Our new
+results include a simplified formulation of the effect of tidal dissipation on
+the equilibria of the system (Cassini States) and a novel, complete description
+of the resonance encounter process.
+
+In Section~\ref{s:theory}, we briefly review Colombo's Top. In
+Section~\ref{s:toy_model}, we investigate the effect of adding a simple
+alignment torque to Colombo's Top. The resulting dynamics are illustrative of
+the new behavior that emerges due to tidal dissipation. In
+Section~\ref{s:full_tide_prob}, we solve for the dynamics of the system
+including a realistic model of tidal dissipation. In Section~\ref{s:summary}, we
+apply our results to three astrophysical scenarios of interest: (i) a super
+Earth with a cold Jupiter companion, (ii) the formation of USPs, and (iii) the
+rapid orbital decay of WASP-12b. We summarize and discuss in
+Section~\ref{s:summary}.
 
@@
 
-In this section, we first briefly lay out the spin dynamics of the planet,
-introducing the Cassini State spin-orbit resonance \citep[for more details,
-see][]{su2020}. We then introduce the weak friction theory of equilibrium tides
-used in this work \citep{lai2012}. While many different tidal effects may
-dominate in different planetary systems, our qualitative conclusions do not
-depend on the specific form of the tidal dissipation, so we use the classic weak
-friction theory for simplicity.
-
-\subsection{Spin Dynamics in the Absence of Tides}\label{ss:theory_spin}
-
-\subsubsection{Equations of Motion}
-
-We consider a star of mass $M_\star$ hosting an inner oblate planet of mass $m$
-and radius $R$ on a circular orbit with semi-major axis $a$ and an outer
-perturber of mass $m_{\rm p}$ on a circular orbit with semi-major axis $a_{\rm
-p}$. We assume that the two orbits are mildly misaligned with mutual inclination
-$I$. Denote $\bm{S}$ the spin angular momentum and $\bm{L}$ the orbital angular
-momentum of the planet, and $\bm{L}_{\rm p}$ the angular momentum of the
-perturber. The corresponding unit vectors are $\uv{s} \equiv \bm{S} / S$,
-$\uv{l} \equiv \bm{L} / L$, and $\uv{l}_{\rm p} \equiv \bm{L}_{\rm p} / L_{\rm
-p}$. The spin axis $\uv{s}$ of the planet tends to precess around its orbital
-(angular momentum) axis $\uv{l}$, driven by the gravitational torque from the
-host star acting on the planet's rotational bulge. On the other hand, $\uv{l}$
-and the disk axis $\uv{l}_{\rm p}$ precess around each other due to
-gravitational interactions. We assume $S \ll L \ll L_{\rm p}$, so $\uv{l}_{\rm
-p}$ and $\uv{l}$ are nearly constant. The equations of motion for $\uv{s}$ and
-$\uv{l}$ in this limit are \citep{anderson2018teeter, su2020}
+In this section, we briefly introduce the spin dynamics of the planet (for a
+more detailed treatment, see Paper I). We consider a star of mass $M_\star$
+hosting an inner oblate planet of mass $m$ and radius $R$ on a circular orbit
+with semi-major axis $a$ and an outer perturber of mass $m_{\rm p}$ on a
+circular orbit with semi-major axis $a_{\rm p}$. We assume that the two orbits
+are mutually inclined by the angle $I$. Denote $\bm{S}$ the spin angular
+momentum and $\bm{L}$ the orbital angular momentum of the planet, and
+$\bm{L}_{\rm p}$ the angular momentum of the perturber. The corresponding unit
+vectors are $\uv{s} \equiv \bm{S} / S$, $\uv{l} \equiv \bm{L} / L$, and
+$\uv{l}_{\rm p} \equiv \bm{L}_{\rm p} / L_{\rm p}$. The spin axis $\uv{s}$ of
+the planet tends to precess around its orbital (angular momentum) axis $\uv{l}$,
+driven by the gravitational torque from the host star acting on the planet's
+rotational bulge. On the other hand, $\uv{l}$ and the disk axis $\uv{l}_{\rm p}$
+precess around each other due to gravitational interactions. We assume $S \ll L
+\ll L_{\rm p}$, so $\uv{l}_{\rm p}$ and $\uv{l}$ are nearly constant. The
+equations of motion for $\uv{s}$ and $\uv{l}$ in this limit are
+(\citealp{anderson2018teeter}, Paper I)
 \begin{align}
@@
 In Eq.~\eqref{eq:wsl}, $\Omega_{\rm s}$ is the spin frequency of the inner
-planet, $I = k mR^2$ (with $k$ a constant) is its moment of inertia and $J_2 =
-k_{\rm q}\Omega_{\rm s}^2 (R^3/Gm)$ (with $k_{q}$ a constant) is its rotation-induced
-(dimensionless) quadrupole moment [for a body with uniform density, $k=0.4,
-k_{\rm q}=0.5$; for rocky planets, $k\simeq 0.2$ and $k_{\rm q}\simeq 0.17$
-\citep[e.g.][]{lainey2016quantification} \textcolor{red}{? not sure}]. In other
-studies, $3k_{\rm q} / 2 k$ is often notated as $k_2 / 2C$
+planet, $\mathcal{I} = k mR^2$ (with $k$ a constant) is its moment of inertia
+and $J_2 = k_{\rm q}\Omega_{\rm s}^2 (R^3/Gm)$ (with $k_{q}$ a constant) is its
+rotation-induced (dimensionless) quadrupole moment [for a body with uniform
+density, $k=0.4, k_{\rm q}=0.5$; for rocky planets, $k\simeq 0.2$ and $k_{\rm
+q}\simeq 0.17$ \citep[e.g.][]{lainey2016quantification}]. In other studies,
+$3k_{\rm q} / 2 k$ is often notated as $k_2 / 2C$
 \citep[e.g.][]{millholland_disk}. In Eq.~\eqref{eq:wlp}, $n \equiv
@@
 
-As in \citet{su2020}, we combine Eqs.~(\ref{eq:dsdt1}--\ref{eq:dldt1}) into a
+As in Paper I, we combine Eqs.~(\ref{eq:dsdt1}--\ref{eq:dldt1}) into a
 single equation by transforming into a frame rotating about $\uv{l}_{\rm p}$
@@
 $\uv{s}$ in spherical coordinates using the polar angle $\theta$, the planet's
-obliquity, and $\phi$, the precessional phase of $\uv{s}$ about $\uv{l}$.
+obliquity, and $\phi$, the precessional phase of $\uv{s}$ about $\uv{l}$,
+defined so that when $\phi = 0^\circ$, $\uv{l}_{\rm p}$ and $\uv{s}$ are on
+opposide sides of $\uv{l}$.
 
@@
 States} \citep[CSs;][]{colombo1966, peale1969}. We follow the notation of
-\citet{su2020}, where the parameter
+Paper I, where the parameter
 \begin{equation}
@@
 \end{equation}
-is used. For a given value of $\eta$, there can be either two or four CSs, all
-of which require $\uv{s}$ lie in the plane of $\uv{l}$ and $\uv{l}_{\rm p}$.
-Following the standard nomenclature, $\uv{s}$ and
-$\uv{l}_{\rm p}$ are on opposite sides of $\uv{l}$ for CSs 1, 3, and 4, and are
-on the same side for CS2. We depart from the standard convention
-and simply label the CSs in spherical coordinates: figure~\ref{fig:cs_locs}
-shows the CS obliquities as a function of $\eta$. CS1 and CS4 do not exist when
-$\eta > \eta_{\rm c}$, where
+is introduced. For a given value of $\eta$, there can be either two or four CSs,
+all of which require $\uv{s}$ lie in the plane of $\uv{l}$ and $\uv{l}_{\rm p}$.
+Following the standard nomenclature, $\uv{s}$ and $\uv{l}_{\rm p}$ are on
+opposite sides of $\uv{l}$ for CSs 1, 3, and 4, and are on the same side for
+CS2. We depart from the standard convention and simply label the CSs in
+spherical coordinates: Figure~\ref{fig:cs_locs} shows the CS obliquities as a
+function of $\eta$. CS1 and CS4 do not exist when $\eta > \eta_{\rm c}$, where
 \begin{equation}
@@
 20^\circ$, for which $\eta_{\rm c} \approx 0.574$ (Eq.~\ref{eq:def_etac}). When $\eta
-< \eta_{\rm c}$, CS4 exists and is a saddle point. The two trajectories
-originating and ending at CS4 are the only two infinite-period orbits in the
-phase space. Together, these two critical trajectories are referred to as the
-\emph{separatrix} and divide phase space into three zones. Trajectories in zone
-II librate about CS2 while those in zones I and III circulate. On the other
-hand, when $\eta > \eta_{\rm c}$, all trajectories circulate. When the
+< \eta_{\rm c}$, CS4 exists and is a saddle point. The infinite-period orbits
+originating and ending at CS4 form the \emph{separatrix} and divide phase space
+into three zones. $\phi$ librates for trajectories in zone II and circulates for
+trajectories in zones I and III\@. On the other hand, when $\eta > \eta_{\rm
+c}$, the separatrix is absent and all trajectories circulate. When the
 separatrix exists, we divide it into two curves: $\mathcal{C}_+$, the boundary
@@
 
-In this section, we consider a simplified model of equilibrium tides that
-isolates the important new phenomenon presented in this paper. We assume that
-the spin magnitude of the planet is constant, so $\alpha$ and $g$ are both
-fixed, while the spin orientation $\uv{s}$ experiences an alignment torque
-towards $\uv{l}$ on the alignment timescale $t_{\rm al}$:
+In this section, we consider a simplified dissipative torque that isolates the
+important new phenomenon presented in this paper. We assume that the spin
+magnitude of the planet is constant, so $\alpha$ and $g$ are both fixed, while
+the spin orientation $\uv{s}$ experiences an alignment torque towards $\uv{l}$
+on the alignment timescale $t_{\rm al}$:
 \begin{equation}
@@
 
-\subsection{Shifted Cassini States and Linear Stability
+\subsection{Modified Cassini States and Linear Stability
 Analysis}\label{ss:tidal_equils}
@@
 If the alignment torque is weak ($\abs{g}t_{\rm al} \gg 1$), then the fixed
-points of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) are just slightly shifted
-CSs. This shift can be calculated cleanly to leading order: all of the CS
-obliquities $\theta_{\rm cs}$ are unchanged while the azimuthal angle $\phi_{\rm
-cs}$ for each CS now satisfies
+points of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) are slightly modified CSs.
+To leading order, all of the CS obliquities $\theta_{\rm cs}$ are unchanged
+while the azimuthal angle $\phi_{\rm cs}$ for each CS now satisfies
 \begin{equation}
@@
 \end{equation}
-We can see that if $t_{\rm al} > t_{\rm al, c}$, where
-\begin{align}
-    t_{\rm al, c} &= \frac{1}{\abs{g}\sin I},\label{eq:mcs_shift_crit}
+We can see that if $t_{\rm al}$ is longer than some critical alignment
+timescale $t_{\rm al, c}$, given by
+\begin{align}
+    t_{\rm al, c} &\equiv \frac{1}{\abs{g}\sin I},\label{eq:mcs_shift_crit}
 \end{align}
 then Eq.~\eqref{eq:mcs_shift} will always have solutions for $\phi_{\rm cs}$,
-and the alignment torque never changes the number of fixed points of the system.
-If $t_{\rm al}$ is decreased below $t_{\rm al, c}$, CS2 and CS4 cease to be
-fixed points if $\eta \ll 1$ \citep[as first noted in][]{fabrycky_otides}, as
-$\theta_{\rm cs} \approx 90^\circ$ for these (see Fig.~\ref{fig:cs_locs}), while
-the other CSs have small $\sin \theta_{\rm cs}$ and are only slightly perturbed.
-Figure~\ref{fig:mcs} shows the obliquity and azimuthal angles for each of the
-CSs in the $\eta \ll 1$ case, where it can be seen that CS2 and CS4 collide and
-annihilate. The phase shift $\phi_{\rm cs}$ for CS2 and CS4 for $t_{\rm al} >
+and the alignment torque does not change the number of fixed points of the
+system. If $t_{\rm al}$ is decreased below $t_{\rm al, c}$, CS2 and CS4 cease to
+be fixed points when $\eta \ll 1$ \citep[as first noted in][]{fabrycky_otides},
+as $\theta_{\rm cs} \approx 90^\circ$ for these (see Fig.~\ref{fig:cs_locs}). On
+the other hand, the other CSs have small $\sin \theta_{\rm cs}$ and are only
+slightly perturbed. Figure~\ref{fig:mcs} shows the obliquity and azimuthal
+angles for each of the CSs in the $\eta \ll 1$ case obtained via numerical
+root finding of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}), where it can be
+seen that CS2 and CS4 collide and annihilate when $t_{\rm al}$ reaches $t_{\rm
+al, c}$. The phase shift $\phi_{\rm cs}$ for CS2 and CS4 for $t_{\rm al} >
 t_{\rm al, c}$ can be predicted to good accuracy using Eq.~\eqref{eq:mcs_shift}
@@
 We next seek to characterize the stability of small perturbations about each of
-the CSs in the presence of the weak tidal alignment torque. We can linearize
+the CSs in the presence of the weak alignment torque. We can linearize
 Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) about a shifted CS, yelding
@@
 Eq.~\eqref{eq:lambda_approx}. $\lambda_0^2$ is a generalization of Eq.~(A4)
-in, \citet{su2020} and generally has the same behavior: it is negative for CSs
+in Paper I and generally has the same behavior: it is negative for CSs
 1--3 and positive for CS4, as shown in Fig.~\ref{fig:lambda_full}. Thus, CS4 is
@@
 $\lambda$, and the stability of CSs 1--3 are solely determined by the sign of
-$\cos \theta_{\rm cs}$. Evaluating at each of the CSs (see
-Fig.~\ref{fig:cs_locs}), we conclude that CS1 and CS2 are stable and attracting
-while CS3, stable in the absence of the torque, becomes unstable. These
-calculations justify results long used in CS literature
+$\cos \theta_{\rm cs}$. Using Fig.~\ref{fig:cs_locs}, we conclude that CS1 and
+CS2 are stable and attracting while trajectories near CS3 are driven away by the
+alignment torque. These calculations justify results long used in CS literature
 \citep[e.g.][]{ward1975tidal, fabrycky_otides}.
@@
     \caption{$\lambda_0^2$ (Eq.~\ref{eq:def_l0_sq}) as a function of $\eta$ for
-    the four CSs. The solid lines give $\lambda_0^2$ for the unperturbed
-    $\phi_{\rm cs}$, and the dashed lines give the values for $\phi_{\rm cs}$
-    shifted by $60^\circ$ ($\phi_{\rm cs} = 120^\circ$ for CS2 and $\phi_{\rm
-    cs} = 60^\circ$ for CSs 1, 3, and 4).
-    }\label{fig:lambda_full}
+    the four CSs, for three different values of the shift in $\phi_{\rm cs}$
+    (e.g.\ for $\Delta \phi_{\rm cs} = 60^\circ$, $\phi_{\rm cs} = 120^\circ$
+    for CS2 and $\phi_{\rm cs} = 60^\circ$ for CSs 1, 3, and 4). The values of
+    $\Delta \phi_{\rm cs}$ are labeled. }\label{fig:lambda_full}
 \end{figure}
@@
 Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}): what is the long term behavior for
-a general initial $\uv{s}$? If $\eta > \eta_{\rm c}$, then the only possible
+a general initial $\uv{s}$? If $\eta > \eta_{\rm c}$, then the only stable
 final spin state is CS2, and all initial conditions will evolve asympotically
 towards it. As such, we consider only $\eta < \eta_{\rm c}$, where an initial
-condition can asymptotically evolve towards either CS1 or CS2. We numerically
-integrate Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) for many random initial
-conditions uniformly distributed in $\p{\cos \theta, \phi}$ with $\abs{g}t_{\rm
-al}= 10^{-3}$ and record the nearest CS for each integration after $10t_{\rm al}$. In Fig.~\ref{fig:toy_phop}, we show the results of this procedure for $\eta
-= 0.2$, and $I = 20^\circ$. It is clear that initial conditions in zone I evolve
-into CS1, those in zone II evolve into CS2, while those in zone III have a
+condition can asymptotically evolve towards either CS1 or CS2. Additionally, we
+restrict our attention to the regime where the alignment torque is weak and CS2
+remains stable; specifically, we use $\abs{g}t_{\rm al}= 10^{3}$. We
+numerically integrate Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) for many
+random initial conditions uniformly distributed in $\p{\cos \theta, \phi}$ and
+record the nearest CS for each integration after $10t_{\rm al}$. In
+Fig.~\ref{fig:toy_phop}, we show the results of this procedure for $\eta = 0.2$,
+and $I = 20^\circ$. It is clear that initial conditions in zone I evolve into
+CS1, those in zone II evolve into CS2, while those in zone III have a
 probabilistic outcome. We aim to understand each of these in turn:
@@
 will converge to CS2. In fact, this result can be extended to all initial
-conditions inside the separatrix; see Appendix~\ref{app:cs_stab2}.
+conditions inside the separatrix, shown in Appendix~\ref{app:cs_stab2}.
 
@@
 determines the final CS\@. Intuitively, this can be understood as probabilistic
-resonance capture: since $\eta \ll \eta_{\rm c}$, $\alpha \gg -g$ (the
-spin-orbit precession rate, Eq.~\ref{eq:dsdt1}, and the orbit precession induced
-by the perturber, Eq.~\ref{eq:dldt1}, respectively), but $\alpha \cos \theta$
-can become commensurate with $-g$ if $\cos \theta \sim \eta$. This is achieved
+resonance capture, as first studied in the seminal work of \citet{henrard1982}:
+since $\eta \ll \eta_{\rm c}$, $\alpha \gg -g$, but $\alpha \cos \theta$ can
+become commensurate with $-g$ if $\cos \theta$ becomes small. This is achieved
 as $\theta$ evolves from an initially retrograde obliquity through $90^\circ$
@@
 non-Hamiltonian, dissipative perturbation causes systems to transition among
-unchanging phase space zones.
+unchanging phase space zones. In the following section, we present a calculation
+to understand analytically the probability distribution of outcomes upon
+separatrix encounter in this new scenario.
 
@@
 
-The specific probabilities of the two outcomes upon separatrix encounter, a zone
-III-II or a zone III-I transition, can be calculated analytically.
+Before discussing quantitative calculations, we first present a graphical
+understanding of the separatrix encounter process.
 Figure~\ref{fig:toy_hop_manifolds} shows how the perturbative alignment torque
-generates probabilistic outcomes upon separatrix encounter. We present the
-interpretation of Figure~\ref{fig:toy_hop_manifolds} and the calculation of the
-resonance capture probability by first giving a qualitative description of the
-intuition behind the method, then presenting a calculation in good agreement with
-numerical results.
-
-We first describe the origin of the boundaries between regions of phase space
-that shown in Fig.~\ref{fig:toy_hop_manifolds}. They are calculated numerically
-by integrating a point infinitesimally close to CS4 forward and backward in
-time. In the absence of the alignment torque, these trajectories would evolve
-along the separatrix, but in the presence of the alignment torque they are
-perturbed slightly and cease to overlap. It can be seen in
-Fig.~\ref{fig:toy_hop_manifolds} that this splitting opens a path from zone III
-into both zones I and II\@.
-
-To understand this process quantitatively, as well as associate probabilities to
-the two possible outcomes, it is important to be more quantitative. The correct
+generates the two outcomes upon separatrix encounter, a zone III-II or a zone
+III-I transition. The critical trajectories in Fig.~\ref{fig:toy_hop_manifolds}
+are calculated numerically by integrating a point infinitesimally close to CS4
+forward and backward in time. In the absence of the alignment torque, these
+trajectories would evolve along the separatrix, but in the presence of the
+alignment torque, they are perturbed slightly and cease to overlap. It can be
+seen in Fig.~\ref{fig:toy_hop_manifolds} that this splitting opens a path from
+zone III into both zones I and II\@.
+
+To understand this process more concretely, as well as associate probabilities
+to the two possible outcomes, it is important to be quantitative. The correct
 approach is to consider the evolution of the value of the \emph{unperturbed}
-Hamiltonian (Eq.~\ref{eq:H}) as the spin evolves with the alignment torque. A
+Hamiltonian (Eq.~\ref{eq:H}) as the spin evolves due to the alignment torque. A
 point in zone III evolves such that $H$ is increasing until $H \approx H_{\rm
@@
 approximated by $\Delta H_-$, the change in $H$ along $\mathcal{C}_-$ (see
-Fig.~\ref{fig:1contours}). In general, we can compute $\Delta H_{\pm}$ the
-change over both legs of the separatrix with
+Fig.~\ref{fig:1contours}). In general, we define the quantities $\Delta H_{\pm}$
 \begin{equation}
@@
 \end{align}
-Thus, if we evaluate $H$ every time that a trajectory crosses $\phi = 0$, we see
-that it will initially be negative and increase for each circulation cycle until
-the system encounters the separatrix. At the beginning of the
-separatrix-crossing orbit, the initial value of $H$, denoted $H_{\rm i}$,
-satisfies $H_{\rm sep} - \Delta H_- \leq H_{\rm i} \leq H_{\rm sep}$: if it is
-less than the lower bound, it will not cross the separatrix on this orbit, and
-if it is greater than the upper bound then it is already inside the separatrix.
-The two endpoints of this range are denoted in Fig.~\ref{fig:6equils} by the
-black dot and cross at the left and right edges of the plot.
+In the first line, Hamilton's equations ensure that the non-tidal contributions
+to $\rdil{H}{t}$ vanish. Thus, if we evaluate $H$ every time that a trajectory
+originating in zone III crosses $\phi = 0$, we see that it will initially be $<
+H_{\rm sep}$ and increase for each circulation cycle until the system encounters
+the separatrix. At the beginning of the separatrix-crossing orbit, the initial
+value of $H$, denoted $H_{\rm i}$, must be greater than $H_{\rm sep} - \Delta H$
+to encounter the separatrix on the current orbit, and must be less than $H_{\rm
+sep}$, otherwise the trajectory will be in zone II already. We thus have
+\begin{equation}
+    H_{\rm i} \in \s{ H_{\rm sep} - \Delta H_-,  H_{\rm sep} }
+        \label{eq:Hi_range},
+\end{equation}
+The values of $\cos \theta$ corresponding to the lower and upper bounds on this
+range are shown as the black and red dots on the left of Fig.~\ref{fig:6equils}
+respectively.
 
 During the separatrix-crossing orbit, the trajectory first evolves
-approximately along $\mathcal{C}_-$ then along $\mathcal{C}_+$, after which two
-possible outcomes can occur:
+approximately along $\mathcal{C}_-$ and then along $\mathcal{C}_+$, after which
+the final value of $H$, denoted $H_{\rm f}$ is approximately equal to
+\begin{equation}
+    H_{\rm f} = H_{\rm i} + \Delta H_+ + \Delta H_-.
+\end{equation}
+There can then be two outcomes depending on the value of $H_{\rm f}$:
 \begin{itemize}
-    \item If the final value of $H$ at the end of this separatrix traversal,
-        denoted $H_{\rm f}$, satisfies $H_{\rm f} > H_{\rm sep}$, then the
-        trajectory enters the separatrix, following the red shaded region in
-        Fig.~\ref{fig:6equils}, and executes a zone III $\to$ II transition.
+    \item If $H_{\rm f} > H_{\rm sep}$, then the trajectory enters the
+        separatrix, following the red shaded region in Fig.~\ref{fig:6equils},
+        and executes a zone III $\to$ II transition.
 
@@
 \end{itemize}
-Since $H_{\rm f} = H_{\rm i} + \Delta H_+ + \Delta H_-$, we find that if $H_{\rm
-i}$ is in the interval $\s{H_{\rm sep} - \Delta H_-, H_{\rm sep} - \Delta H_{-}
-- \Delta H_+}$, then the system executes a III $\to$ I transition, and if it
-is in the interval $\s{H_{\rm sep} - \Delta H_- - \Delta H_+, H_{\rm sep}}$,
-then the system executes a III $\to$ II transition. The values of $\cos
-\theta$ for which $H$ is equal to $H_{\rm sep} - \Delta H_-$, $H_{\rm sep} - \Delta
-H_- - \Delta H_+$, and $H_{\rm sep}$ (CS4) for $\phi = 0$ are shown in
-Fig.~\ref{fig:6equils} as the black cross, star, and dot at $\phi = 0$
-respectively. Finally, if the alignment torque is weak, then $\Delta H_- \sim
-\mathcal{O}\p{t_{\rm al}^{-1}}$ is small compared to the characteristic values of
-$H$, and $H_{\rm i}$ can be effectively considered as uniformly distributed over
-$\s{H_{\rm sep} - \Delta H_-, H_{\rm sep}}$. As such, we obtain that
+These two possibilites can be re-expressed in terms of $H_{\rm i}$: we find that
+if $H_{\rm i}$ is in the interval $\s{H_{\rm sep} - \Delta H_-, H_{\rm sep} -
+\Delta H_{-} - \Delta H_+}$, then the system executes a III $\to$ I transition,
+and if it is in the interval $\s{H_{\rm sep} - \Delta H_- - \Delta H_+, H_{\rm
+sep}}$, then the system executes a III $\to$ II transition. We see that there is
+a critical value of $H_{\rm i}$ in the interval given by
+Eq.~\eqref{eq:Hi_range}, where $H_{\rm i} = H_{\rm sep} - \Delta H_{-} - \Delta
+H_+$, that separates the two possible outcomes of the separatrix encounter
+within the interval given by Eq.~\eqref{eq:Hi_range}. The value of $\cos \theta$
+for which $H$ is equal to $H_{\rm sep} - \Delta H_{-} - \Delta H_+$ is shown as
+the blue dot on the left of Fig.~\ref{fig:6equils}. Finally, if the alignment
+torque is weak, then $\Delta H_- \sim \mathcal{O}\p{t_{\rm al}^{-1}}$ is small
+compared to any variation in the value of $H$ (e.g.\ when changing $\phi_0$ or
+$\theta_0$ by a small amount), and $H_{\rm i}$ can be effectively considered as
+randomly chosen from a uniform distribution over $\s{H_{\rm sep} - \Delta H_-,
+H_{\rm sep}}$. As a consequence we obtain the probability of a III $\to$ II
+transition:
 \begin{equation}
@@
     \caption{Plot illustrating the probabilistic origin of separatrix capture
-    for $\eta = 0.2$, $I = 20^\circ$, and $\abs{gt_{\rm al}} = 10^{-3}$. Orange
+    for $\eta = 0.2$, $I = 20^\circ$, and $\abs{gt_{\rm al}} = 10^{3}$. Orange
     regions converge to CS1, and green to CS2, while CS4 is labeled with the
@@
 
-To actually evaluate Eq.~\eqref{eq:def_P32_toy}, we use the parameterization for
-the separatrix \citep{su2020} for $\eta \ll 1$:
+To actually evaluate Eq.~\eqref{eq:def_P32_toy}, we can use the parameterization
+for the separatrix given in Paper I for $\eta \ll 1$:
 \begin{equation}
@@
 
-To directly compare Eq.~\eqref{eq:P32_toy} with numerical simulation, we
-perform integrations of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) while
-restricting our attention to only outcomes of initial conditions in zone III\@.
+To directly compare Eq.~\eqref{eq:P32_toy} with numerical simulation, we perform
+numerical integrations of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) while
+restricting our attention only initial conditions in zone III\@.
 In Fig.~\ref{fig:1hist_toy}, we display Eq.~\eqref{eq:P32_toy} alongside the
@@
 
-Finally, we remark that the calculation above is just a descriptive application
-of \emph{Melnikov's Method} \citep{g_and_h}. Melnikov's Method is a general
-calculation that gives the degree of splitting of a ``homoclinic orbit'' (here,
-the separatrix) induced by a small, possibly time-dependent, perturbation. The
-explicit connection between the evolution of the unperturbed Hamiltonian and
-distances between curves in phase space (as seen in Fig.~\ref{fig:6equils})
-is provided by Melnikov's Method.
+Finally, we remark that the calculation above is just an of \emph{Melnikov's
+Method} \citep{g_and_h}. Melnikov's Method is a general calculation that gives
+the degree of splitting of a ``homoclinic orbit'' (here, the separatrix) induced
+by a small, possibly time-dependent, perturbation. The explicit connection
+between the evolution of the unperturbed Hamiltonian and distances between
+curves in phase space (as seen in Fig.~\ref{fig:6equils}) is provided by
+Melnikov's Method.
 
@@
 
-To model the dissipative effect of times, we use the weak friction theory of
-equilibrium tides \citep{lai2012}. In this model, tides cause both $\uv{s}$ and
-$\Omega_{\rm s}$ to evolve on the characteristic tidal timescale $t_{\rm s}$:
+Having understood the effect of introducing an additional dissipative torque to
+the Colombo's Top system, we now implement a realistic model of tidal
+dissipation. We use the weak friction theory of equilibrium tides
+\citep{lai2012}. In this model, tides cause both the spin orientation $\uv{s}$
+and frequency $\Omega_{\rm s}$ to evolve on the characteristic tidal timescale
+$t_{\rm s}$ following:
 \begin{align}
@@
 $\sim L / S \gg 1$, and so $t_{\rm s}$ is a constant. We will continue mostly
-consider the case where $\abs{gt_{\rm s}} \gg 1$. The full equations of motion
-including weak tidal friction are
+consider the case where tidal dissipation is slow, i.e.\ $\abs{g}t_{\rm s} \gg
+1$. The full equations of motion including weak tidal friction can be written in
+component form as
 \begin{align}
@@
 \end{align}
-The conditions for which the two tidal terms vanish can be respectively
-expressed as:
+The conditions for which the two tidal terms vanish are given respectively by:
 \begin{align}
@@
 
-To understand the long-term behaviors of the system, we first consider its
+To understand the long-term behaviors of this system, we first consider its
 behavior near a CS\@. Specifically, we wish to understand whether initial
@@
 causes the CSs to evolve. We first note that the evolution of
-$\Omega_{\rm s}$ does not drive spins towards or away from CSs: as long as it
-evolves sufficiently slowly \citep[adiabatically,][]{su2020}, conservation of
+$\Omega_{\rm s}$ does not drive spins towards or away from CSs: As long as it
+evolves sufficiently slowly (adiabatically, Paper I), conservation of
 phase space area ensures that trajectories will remain at a roughly fixed
@@
 Using this result, we can then identify the long-term equilibria of the system
-(i.e.\ when including the evolution of $\Omega_{\rm s}$), as the long-term
-equilibria of the system must both satisfy $\dot{\Omega}_{\rm s} = 0$ and be a
-stable CS\@. Figure~\ref{fig:6equils} describes
+when $\Omega_{\rm s}$ is also evolving: these equilibria of the system must both
+satisfy $\dot{\Omega}_{\rm s} = 0$ and be a CS that is stable in the presence of
+tidal dissipation (i.e.\ satisfying $\rdil{\uv{s}}{t} = 0$).
+The panels of Fig.~\ref{fig:6equils} describes the evolution of
 Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) qualitatively in the coordinates
-$(\Omega_{\rm s}, \theta)$, along with the locations of CS1 and CS2. The two
-circled points in Fig.~\ref{fig:6equils} satisfy the criteria to be long-term
-equilibria, and we call them \emph{tidal Cassini Equilibria} (tCE). We number
-tCE1 and tCE2 the tCE that are in CSs 1 and 2 respectively. The obliquities of
-the tCE depend on the system architecture, which can be quantified using the
-parameter
+$(\Omega_{\rm s}, \theta)$, along with the locations of CS1 and CS2, for a few
+different system parameters. The circled points in the panels of
+Fig.~\ref{fig:6equils} satisfy the criteria to be long-term equilibria, and we
+call them \emph{tidal Cassini Equilibria} (tCE). We number tCE1 and tCE2 the tCE
+that are in CSs 1 and 2 respectively. The obliquities of the tCE depend on the
+system architecture, which can be quantified using the parameter
 \begin{align}
@@
         = \eta \frac{\Omega_{\rm s}}{n}\nonumber\\
-        &= \textcolor{red}{\frac{m_{\rm p}m}{2M_\star^2}\p{\frac{a}{a_{\rm
-            p}}}^3 \p{\frac{a}{R}}^3}. \label{eq:def_etasync}
+        &= \frac{1}{2}\frac{k}{k_{\rm q}}
+            \frac{m_{\rm p}m}{M_\star^2}
+            \p{\frac{a}{a_{\rm p}}}^3 \p{\frac{a}{R}}^3\cos(I).
+            \label{eq:def_etasync}
 \end{align}
@@
 This approximation for $\theta_{\rm tCE2}$ is shown as the black dashed line in
-the top panels of Fig.~\ref{fig:probs20} and~\ref{fig:probs5}.
+the top panels of Fig.~\ref{fig:probs20} and~\ref{fig:probs5}, where good
+agreement is observed.
 \begin{figure}
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils0_20.png}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils.png}
     \caption{Schematic depiction of the effect of tidal friction on the planet's
-    spin for $I = 20^\circ$ and $\eta_{\rm sync} = 0.2$. The black and blue lines
-    denote where the tidal $\dot{\Omega}_{\rm s}$ and $\dot{\theta}$ change
-    signs (Eqs.~\ref{eq:weaktide_dqzero}--\ref{eq:weaktide_dWszero}). The orange
-    and green lines give the CS1 and CS2 obliquities respectively, which are the
-    two CSs that are stable under the effect of tidal dissipation. Note that
-    when $\dot{\theta}_{\rm tide} > 0$, CS1 becomes unstable, denoted by the
-    dashed orange line. The points that are both CSs and satisfy
-    $\dot{\Omega}_{\rm s} = 0$ are the tidal Cassini Equilibria (tCE), which are
-    circled and labeled. }\label{fig:6equils}
+    spin for $I = 20^\circ$ and three values of $\eta_{\rm sync}$ (labeled). The
+    black and blue lines denote where the tidal $\dot{\Omega}_{\rm s}$ and
+    $\dot{\theta}$ change signs
+    (Eqs.~\ref{eq:weaktide_dqzero}--\ref{eq:weaktide_dWszero}). The orange and
+    green lines give the CS1 and CS2 obliquities respectively, which are the two
+    CSs that are stable under the effect of tidal dissipation. Note that when
+    $\dot{\theta}_{\rm tide} > 0$, CS1 becomes unstable, denoted by the dashed
+    orange line. The points that are both CSs and satisfy $\dot{\Omega}_{\rm s}
+    = 0$ are the tidal Cassini Equilibria (tCE), which are circled and labeled.
+    }\label{fig:6equils}
 \end{figure}
 
-There are two important conditions that change the existence and stability of
-the tCE\@. First, if $\eta_{\rm sync} > \eta_{\rm c}$, then tCE1 will not
-exist\footnote{Strictly speaking, $\eta_{\rm sync}$ can be slightly smaller than
-$\eta_{\rm c}$, as the planet's spin is slightly subsynchronous at tCE1 when
-$\eta \approx \eta_{\rm c}$, see Fig.~\ref{fig:6equils}.}. Secondly, tCE2 may
-not be stable if the tidal phase shift is too large. Applying the results of
-Section~\ref{ss:tidal_equils}, we find that tCE2 is stable as long as $t_{\rm s}
-\geq t_{\rm s, c}$ where
+There are two important conditions that can change the existence and stability
+of the tCE\@. First, if $\eta_{\rm sync} > \eta_{\rm c}$, then tCE1 will not
+exist, as can be seen in the bottom panel of
+Fig.~\ref{fig:6equils}\footnote{Strictly speaking, $\eta_{\rm sync}$ can be
+slightly smaller than $\eta_{\rm c}$, as the planet's spin is slightly
+subsynchronous at tCE1 when $\eta \approx \eta_{\rm c}$, see the middle panel of
+Fig.~\ref{fig:6equils}.}. Secondly, tCE2 may not be stable if the tidal phase
+shift is too large. Applying the results of Section~\ref{ss:tidal_equils}, we
+find that tCE2 is stable as long as $t_{\rm s} \geq t_{\rm s, c}$ where
 \begin{equation}
@@
     t_{\rm s, c}\approx \frac{1}{\abs{g}\sin I}\sqrt{\frac{2}{\eta_{\rm sync}
-        \cos I}}. \label{eq:def_ta_crit}
+        \cos I}}. \label{eq:def_ts_crit}
 \end{equation}
@@
 fiducial initial spin frequency $\Omega_{\rm s, i} = 10n$. The final results are
-not sensitive on the specific initial spin as long as $\Omega_{\rm s, i} \gg n$.
-Then, for a given initial $\theta_0$ and $\phi_0$, the final outcome (either tCE1 and
-tCE2) of the system can be calculated by direct integration of
+not sensitive to the specific initial spin as long as $\Omega_{\rm s, i} \gg n$.
+Then, for a given initial $\theta_0$ and $\phi_0$, the final outcome (either
+tCE1 and tCE2) of the system can be calculated by direct integration of
 Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}). In
@@
 reached for spins initially in zone II, and a probabilistic outcome is observed
-for spins initially in zone III, very similar to the results found for the
-alignment torque in Section~\ref{s:toy_model}. Figures~\ref{fig:Hhists_0_20}
-and~\ref{fig:Hhists_0_70} show the same results but for $\eta_{\rm sync} = 0.2$
-and $\eta_{\rm sync} = 0.5$. As $\eta_{\rm sync}$ is increased, more initial
-conditions reach tCE2. This is both because there are more systems initially in
-zone II and because more systems initially in zone III execute a III $\to$ II
-transition upon separatrix encounter. Note also that in
-Fig.~\ref{fig:Hhists_0_70}, even initial conditions in zone I are able to reach
-tCE2; we comment on the origin of this behavior in the next section.
+for spins initially in zone III, similarly to Fig.~\ref{fig:toy_phop}.
+Figures~\ref{fig:Hhists_0_20} and~\ref{fig:Hhists_0_70} show the same results
+but for $\eta_{\rm sync} = 0.2$ and $\eta_{\rm sync} = 0.5$. As $\eta_{\rm
+sync}$ is increased, more initial conditions reach tCE2. This is both because
+there are more systems initially in zone II and because systems initially
+in zone III have a higher probability of executing a III $\to$ II transition
+upon separatrix encounter. Note also that in Fig.~\ref{fig:Hhists_0_70}, even
+initial conditions in zone I are able to reach tCE2; we comment on the origin of
+this behavior in the next section.
 \begin{figure}
@@
     $(\theta_{\rm i}, \phi_{\rm i})$ evolve towards (labeled in legend), for
-    $\eta_{\rm sync} = 0.06$ and $I = 20^\circ$. The
-    separatrix is shown as the black line. Note that points above the
-    separatrix evolve towards tCE1, points inside the separatrix evolve towards
-    tCE2, and points below the separatrix have a probabilistic outcome.
-    \emph{Right:} Histogram of which tCE a given initial obliquity $\theta_{\rm
-    i}$ evolves towards.}\label{fig:Hhists_0_06}
+    $\eta_{\rm sync} = 0.06$ and $I = 20^\circ$. The planet's initial spin is
+    chosen to be $\Omega_{\rm s, i} = 10n$, and the three zones of phase space
+    (see Fig.~\ref{fig:1contours}) for the initial conditions are labeled,
+    separated by the separatrix (black line). Note that initial conditions in
+    zone I evolve towards tCE1, initial conditions in zone II evolve towards
+    tCE2, and initial conditions in zone III have an effectively probabilistic
+    outcome. \emph{Right:} Histogram of which tCE a given initial obliquity
+    $\theta_{\rm i}$ evolves towards, averaged over $\phi_{\rm
+    i}$.}\label{fig:Hhists_0_06}
 \end{figure}
@@
     \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\eta_{\rm sync} =
-    0.7$. Note that even points above the separatrix can evolve towards tCE2
+    0.5$. Note that even points above the separatrix can evolve towards tCE2
     here.}\label{fig:Hhists_0_70}
@@
 spin-orbit precession frequency $\alpha$, the probabilities of the III $\to$ I
-and III $\to$ II transitions upon separatrix encounter can be computed. The
-calculation is more involved than that presented in
-Section~\ref{ss:toy_outcomes}, and also incorporates the seminal resonance
-capture theory of \citet{henrard1982}. In this section, we give an
-overview of the approach.
-
-In Section~\ref{ss:toy_outcomes}, we found that keeping track of the value of
-$H$, the value of the
-unperturbed Hamiltonian, allowed us to calculate the probabilities of the
-various outcomes of separatrix encounter. Specifically, the outcome upon separatrix
-encounter is determined by the value of $H$ at the start of the
+and III $\to$ II transitions upon separatrix encounter can still be computed.
+The calculation resembles that presented in Section~\ref{ss:toy_outcomes} but is
+more involved. We describe the calculation below.
+
+In Section~\ref{ss:toy_outcomes}, we found that the evolution of $H$, the value
+of the unperturbed Hamiltonian, allowed us to calculate the probabilities of the
+various outcomes of separatrix encounter. Specifically, the outcome upon
+separatrix encounter is determined by the value of $H$ at the start of the
 separatrix-crossing orbit relative to $H_{\rm sep}$, the value of $H$ along the
-separatrix. When the spin is also evolving, $H_{\rm sep}$ is also
+separatrix. However, when the spin is also evolving, $H_{\rm sep}$ is also
 changing during the separatrix-crossing orbit, and the discussion in
@@
 \end{align}
-Here, however, note that $\mathcal{C}_{\pm}$ depends on the value of
-$\Omega_{\rm s}$ upon separatrix encounter. Since there is no closed form
+Here, however, note that the contours $\mathcal{C}_{\pm}$ depends on the value
+of $\Omega_{\rm s}$ at separatrix encounter. Since there is no closed form
 solution for $\Omega_{\rm s}(t)$, the probabilities of the various outcomes
@@
 
-Then, if we call $K_i$ the value of $K$ at the start ($\phi = 0$) of the
-separatrix-crossing orbit, $K_i > -\Delta K_+ - \Delta K_-$ gives a III
-$\to$ II transition and eventual evolution towards tCE2 while $-\Delta K_- < K_i
-< -\Delta K_- - \Delta K_+$ gives a III $\to$ I transition and ultimate
-evolution towards tCE1. Thus, we find that the probability of a III $\to$ II
-transition is given by
+Continuing the argument presented in Section~\ref{ss:toy_outcomes}, we consider
+the outcome of the separatrix-crossing orbit as a function of $K_i$, the value
+of $K$ at the start ($\phi = 0$) of the separatrix-crossing orbit. We find that
+if $K_i > -\Delta K_+ - \Delta K_-$, then the system undergoes a III $\to$ II
+transition and eventual evolution towards tCE2; while if $-\Delta K_- < K_i <
+-\Delta K_- - \Delta K_+$, then the system undergoes a III $\to$ I transition
+and ultimate evolution towards tCE1. Thus, we find that the probability of a III
+$\to$ II transition is given by
 \begin{equation}
@@
 \end{equation}
-Since $\Delta K_{\pm}$ are evaluated at resonance encounter, and
+Again, since $\Delta K_{\pm}$ are evaluated at resonance encounter, and
 $\Omega_{\rm s}$ is evolving, there is no way to express $\Delta K_{\pm}$ as a
 closed form of initial conditions. In fact, since many resonance encounters
-occur when $\eta$ is substantial, even an approximate calculation using
-Eq.~\eqref{eq:sep_theta} is inaccurate, and we instead calculate $\Delta
-K_{\pm}$ along the two legs of the separatrix obtained numerically via a root
-finding algorithm. Note that
-Eqs.~(\ref{eq:def_dK_weaktide},~\ref{eq:def_pc_weaktide}) are equivalent to the
-separatrix capture result of \citet{henrard1982} when $\dot{\theta}_{\rm tide} =
-0$ \citep{henrard1987}. Here, we have argued that this classic calculation can
-be unified with the calculation given in Section~\ref{ss:toy_outcomes} to give
-an accurate prediction of separatrix encounter outcome probabilities in the
-presence of both a dissipative perturbation and a parametric variation of the
-Hamiltonian.
+occur when $\eta$ is substantial, even an approximate calculation of $\Delta
+K_{\pm}$ using Eq.~\eqref{eq:sep_theta} is inaccurate, and we instead calculate
+$\Delta K_{\pm}$ along the numerically-calculated $\Delta K_{\pm}$ for arbitrary
+$\eta$. Note that Eqs.~(\ref{eq:def_dK_weaktide},~\ref{eq:def_pc_weaktide}) are
+equivalent to the separatrix capture result of \citet{henrard1982} when
+$\dot{\theta}_{\rm tide} = 0$ \citep{henrard1987}. Here, we have argued that
+this classic calculation can be unified with the calculation given in
+Section~\ref{ss:toy_outcomes} to give an accurate prediction of separatrix
+encounter outcome probabilities in the presence of both a dissipative
+perturbation and a parametric evolution of the Hamiltonian.
 
 To validate the accuracy of Eq.~\eqref{eq:def_pc_weaktide}, we can compare with
-the numerical integration of
+direct numerical integration of
 Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) for many
-initial conditions in zone III while evaluating $P_{\rm III \to II}$ (and thus
-also obtaining $P_{\rm III \to I} = 1 - P_{\rm III \to II}$) for each simulation
-at the moment it encounters the separatrix. If the theory is correct, the total
-numbers of systems converging to each of tCE1 and tCE2 should be equal to those
-predicted by the sums of the calculated probabilities. In
+initial conditions while evaluating $P_{\rm III \to II}$ (and thus also
+obtaining $P_{\rm III \to I} = 1 - P_{\rm III \to II}$) for each simulation at
+the moment it encounters the separatrix, if it does so. If the theory is
+correct, the total numbers of systems converging to each of tCE1 and tCE2 should
+be equal to those predicted by the sums of the calculated probabilities. In
 Fig.~\ref{fig:pc_fits_0_06}, we show the agreement of this semi-analytic
@@
 With the above calculation, we can understand why even initial conditions in
-zone I can converge to tCE2. As long as the inital spin is sufficiently large
+zone I can converge to tCE2. As long as the initial spin is sufficiently large
 ($\geq 2n$), Eq.~\eqref{eq:dsdt_tide} shows that sufficiently large initial
@@
 region of Fig.~\ref{fig:6equils}). This increase means that even initial
-conditions in zone I can sometimes be driven by weak tidal friction to
-experience separatrix encounter. When this is the case, it can be shown that
-both $\Delta K_+ > 0$ and $\Delta K_- > 0$. This implies that both III $\to$ II
-and I $\to$ II outcomes are guaranteed, and thus initial conditions in all three
-zones can evolve into tCE2.
-
-\subsection{Spin Obliquity Evolution as a Function of Precession Strength}
+conditions in zone I can sometimes be driven by tidal dissipation into the
+separatrix. When this is the case, it can be shown that both $\Delta K_+ > 0$
+and $\Delta K_- > 0$. This implies that both III $\to$ II and I $\to$ II
+outcomes are guaranteed, and thus initial conditions in all three zones can
+evolve into tCE2.
+
+\subsection{Spin Obliquity Evolution as a Function of Precession Strength
+}\label{ss:tce2_etasync}
 
@@
 spin orientation, specified by $\theta_0$ and $\phi_0$. In this section, we
-consider the distribution of outcomes when averaging over a distribution of
-initial spin orientations. For simplicity, we just consider $\uv{s}$ being
-isotropically distributed. Figure~\ref{fig:probs20} shows this for $I
-= 20^\circ$ as a function of $\eta_{\rm sync}$. It can be seen that tCE2 is
-reached with substantial probability ($\sim 50^\circ$) while it is also at a
-substantial obliquity ($\sim 60^\circ$) for $\eta_{\rm sync} \approx 0.4$.
-Furthermore, the bottom panel illustrates that initial conditions other than
-those beginning in zone II generate a significant fraction of systems that
-converge to tCE2.
+consider the probability of evolution into tCE2 when averaging over a
+distribution of initial spin orientations. For simplicity, we just consider
+$\uv{s}$ to be isotropically distributed; we discuss the impact of more
+physically realistic distributions of $\uv{s}$ in Section~\ref{s:summary}. The
+bottom panel of Fig.~\ref{fig:probs20} shows the probability of evolution into
+tCE2 for $I = 20^\circ$ as a function of $\eta_{\rm sync}$. It can be seen that
+tCE2 is reached with substantial probability ($\sim 50\%$) while it is also
+at a substantial obliquity ($\sim 60^\circ$) for $\eta_{\rm sync} \approx 0.4$.
+Furthermore, we note that initial conditions other than those beginning in zone
+II are responsible for a significant fraction of systems that converge to tCE2.
 \begin{figure}
@@
     range of $\eta_{\rm sync}$ (Eq.~\ref{eq:def_etasync}); the blue dashed line
-    denotes the analytical approximation Eq.~\eqref{eq:def_tce2_approx} valid
-    for $\eta_{\rm sync} \ll \eta_{\rm c}$ (vertical dashed line;
-    Eq.~\ref{eq:def_etac}). \emph{Bottom:} Total probability of ending up in
-    tCE2 (red dots), averaged over an isotropic initial spin orientation. The
-    red shaded region denotes the contribution of initial conditions in zone II
-    that converge to tCE2 directly, and the yellow shaded region denotes the
-    contribution of initial conditions in zone III that converge to tCE2 after a
-    separatrix encounter. }\label{fig:probs20}
+    denotes the analytical approximation Eq.~\eqref{eq:def_tce2_approx} and is
+    only displayed in its regime of validity, $\eta_{\rm sync} \ll \eta_{\rm c}$
+    (vertical dashed line; Eq.~\ref{eq:def_etac}). \emph{Bottom:} Total
+    probability of ending up in tCE2 (red dots), averaged over an isotropic
+    initial spin orientation. The three shaded regions denote the contribution
+    of initial conditions in zones I/II/III (labeled) to the total tCE2
+    probability in the isotropic average. For example, among systems that
+    converge to tCE2 for $\eta_{\rm sync} = 0.06$, more originate in zone III
+    than zone II, and none originate in zone I.}\label{fig:probs20}
 \end{figure}
@@
 
-\section{Applications}
+\section{Applications}\label{s:applications}
 
@@
 Consider a system consisting of an inner Super-Earth (SE) and an exterior cold
-Jupiter (CJ); such systems are expected to be abundant \citep{zhu2018super}. For
-this system, the relative tidal dissipation rate $\abs{gt_{\rm s}}^{-1}$ can be
-computed
-\begin{align}
-    \frac{1}{\abs{g} t_{\rm s}}
-        \approx{}& 0.003\frac{1}{\cos I}\p{\frac{2k_2/Q}{10^{-3}}}
-            \p{\frac{m_{\rm p}}{M_{\rm J}}}^{-1}
-            \p{\frac{a_{\rm p}}{5 \;\mathrm{AU}}}^{3}\nonumber\\
-        &\times \p{\frac{a}{0.4\;\mathrm{AU}}}^{-6}
-            \p{\frac{\rho}{3 \; \mathrm{g/cm}^3}}^{-1}
-            \p{\frac{M_\star}{M_{\odot}}}^{2}.
-\end{align}
-In physical units, $t_{\rm s} \sim 2 \times 10^8\;\mathrm{yr}$ for the
-parameters adopted above, and $\dot{a} / a \sim 10^{14}\;\mathrm{yr}$, so the
-spin evolution of the inner planet occurs within the characteristic age of most
-planetary systems, while the orbital evolution of the inner planet can indeed by
-safely neglected. Thus, the approximations of slow tidal dissipation and
-constant $a$ used throughout Section~\ref{s:full_tide_prob} are valid.
-For the same fiducial parameters, Eq.~\eqref{eq:def_etasync} can be evaluated
-\begin{align}
-    \eta_{\rm sync} ={}& 0.33 \p{\frac{k}{k_{\rm q}}}
+Jupiter (CJ); such systems are expected to be abundant \citep{zhu2018super}. A
+phase of giant impacts may occur in the formation of such SEs
+\citep{inamdar2015formation, izidoro2017breaking}, which can scramble the
+initial obliquity distribution into one resembling the isotropic distribution
+considered in Section~\ref{ss:tce2_etasync}. For this system, the spin of the
+planet approaches a tCE on the timescale
+% 1 / (1.5 * 1e-3 * (Msun / (4 Mearth)) * ((2 Rearth) / (0.4 AU))^3 * 2 * pi / (0.4)^(3/2))
+% = 3.34e7
+\begin{align}
+    \frac{1}{t_{\rm s}} ={}& \frac{1}{3 \times 10^7\;\mathrm{yr}}
+            \p{\frac{1}{4k}}
+            \p{\frac{2k_2/Q}{10^{-3}}}
+            \p{\frac{M_\star}{M_{\odot}}}^{3/2}
+            \p{\frac{m}{4M_{\oplus}}}^{-1}\nonumber\\
+        &\times \p{\frac{R}{2R_{\oplus}}}^3
+            \p{\frac{a}{0.4\;\mathrm{AU}}}^{-9/2}.
+\end{align}
+This occurs well within the age of most SE-CJ systems. On the other hand,
+the orbital evolution of the SE occurs on the timescale \citep{lai2012}
+% 1 / (1.5 * 1e-3 * (Msun / (4 Mearth)) * ((2 Rearth) / (0.4 AU))^5 * 2 * pi / (0.4)^(3/2))
+% = 7.36e14
+\begin{align}
+    -\frac{\dot{a}}{a} ={}& \frac{3k_2}{Q}\frac{M_\star}{m}
+            \p{\frac{R}{a}}^5n \p{1 - \frac{\Omega_{\rm s}}{n}\cos \theta}\nonumber\\
+        ={}& \frac{1}{7 \times 10^{14}\;\mathrm{yr}}
+            \p{1 - \frac{\Omega_{\rm s}}{n}\cos \theta}
+            \p{\frac{2k_2/Q}{10^{-3}}}
+            \p{\frac{M_\star}{M_{\odot}}}^{3/2}\nonumber\\
+        &\times \p{\frac{m}{4M_{\oplus}}}^{-1}
+            \p{\frac{R}{2R_{\oplus}}}^5
+            \p{\frac{a}{0.4\;\mathrm{AU}}}^{-13/2}.
+\end{align}
+Thus, $a$ does not evolve within the age of the SE-CJ system, and the
+approximation where $a$ is held constant is valid. For the same fiducial
+parameters, Eq.~\eqref{eq:def_etasync} can be evaluated
+% 1/2 * Mjup * (4 * Mearth) / (Msun)^2 * ((0.4 AU) / (2 Rearth))^3 * (0.4 / 5)^3
+% = 0.303884
+\begin{align}
+    \eta_{\rm sync} ={}& 0.303 \cos I
+            \p{\frac{k}{k_{\rm q}}}
             \p{\frac{m_{\rm p}}{M_{\rm J}}}
-            \p{\frac{a_{\rm p}}{5 \;\mathrm{AU}}}^{-3}\nonumber\\
-        &\times \p{\frac{a}{0.4\;\mathrm{AU}}}^{6}
-            \p{\frac{\rho}{3 \; \mathrm{g/cm}^3}}
-            \p{\frac{M_\star}{M_{\odot}}}^{-2}.\label{eq:sehj_etasync}
-\end{align}
-Here, $\rho = m / \p{4\pi R^3/3}$ is the average density of the inner planet,
-and $M_{\rm J}$ is the mass of Jupiter. Evaluating Eq.~\eqref{eq:def_ta_crit},
-we find that $\abs{g}t_{\rm s, c} \approx 2 / \sin I$, which shows that tidal
-friction is many orders of magnitude too weak to destroy tCE2. Additionally,
-we see from Figs.~\ref{fig:probs20} and~\ref{fig:probs5} that this value of
-$\eta_{\rm sync}$ gives a high-obliquity tCE2 with significant probability.
-Thus, we predict that a sizable fraction of SEs with exterior CJ companions can
-have significant obliquities ($\sim \gtrsim 60^\circ$).
+            \p{\frac{m}{4M_{\oplus}}}
+            \p{\frac{M_\star}{M_{\odot}}}^{-2}
+            \p{\frac{a}{0.4\;\mathrm{AU}}}^{6}\nonumber\\
+        &\times \p{\frac{a_{\rm p}}{5\;\mathrm{AU}}}^{-3}
+            \p{\frac{R}{2R_{\oplus}}}^{-3}.\label{eq:sehj_etasync}
+\end{align}
+Here, $M_{\rm J}$ is the mass of Jupiter. We see from Figs.~\ref{fig:probs20}
+and~\ref{fig:probs5} that this value of $\eta_{\rm sync}$ gives a high-obliquity
+tCE2 with significant probability. Eq.~\eqref{eq:def_ts_crit} shows that tCE2 is
+only unstable if $t_{\rm s} \lesssim t_{\rm s, c}$ where
+% 1 / (3/8 * ((Mjup^3 * 4 * Mearth) / Msun^4 * (0.4 AU)^12 / ((5 AU)^9 * (2 Rearth)^3))^(1/2) * 2 * pi / (0.4)^(3/2))
+% = 2.8189e5
+\begin{align}
+    \frac{1}{t_{\rm s, c}} ={}& \frac{\sin I \cos^2 I}{3 \times
+        10^5\;\mathrm{yr}}
+            \frac{k}{k_{\rm q}}
+            \p{\frac{m_{\rm p}}{M_{\rm J}}}^{3/2}
+            \p{\frac{m}{4 M_{\oplus}}}^{1/2}\nonumber\\
+        &\times \p{\frac{m_\star}{M_{\odot}}}^{-3/2}
+            \p{\frac{a}{0.4\;\mathrm{AU}}}^6
+            \p{\frac{a_{\rm p}}{5\;\mathrm{AU}}}^{-9/2}
+            \p{\frac{R}{2 R_{\oplus}}}^{-3/2}.
+\end{align}
+Since $t_{\rm s} \gg t_{\rm s, c}$, we see that tCE2 is stable. Thus, we predict
+that a significant fraction of SEs with exterior CJ companions can have
+long-lived, significant obliquities ($\gtrsim 60^\circ$) due to being trapped in
+tCE2.
+
+% \textcolor{red}{Just a brief investigation:} Finally, we briefly consider the
+% possibility of tidal heating. Coarsely, we have that
+% \begin{align}
+%     \frac{\dot{a}}{a} &\sim -\frac{1}{10^{14}\;\mathrm{yr}}\p{1 -
+%         \frac{\Omega_{\rm s}}{n}\cos \theta},\\
+%     \dot{E}_{\rm orb} = \frac{GM_{\star}m}{2a}\frac{\dot{a}}{a}
+%         &\approx 10^{20}\;\mathrm{erg/s}\p{1 -
+%         \frac{\Omega_{\rm s}}{n}\cos \theta}.
+% \end{align}
+% The black body luminosity of the planet is expected to be $4 \times
+% 10^{25}\;\mathrm{erg/s}$ for the fiducial parameters, and so can probably be
+% ignored.
 
@@
 In \citet{millholland2020formation}, the authors consider capture into the CS2
-resonance as part of a mechanism to induce ultra-short period planet (USP)
-formation. They envision a process consisting of three stages: (i) capture into
-CS2, (ii) simultaneous inward tidal migration and increase of the obliquity of
-CS2, and (iii) destruction of CS2 due to strong tidal dissipation and stalling
-of inward migration. They consider an inner proto-USP with two external
-perturbing planets. In this section, we apply our results above to a system
-architecture containing just a single planet, for simplicity.
-
-First, we verify agreement of our criterion for breaking of CS2 with theirs.
-Evaluating Eq.~\eqref{eq:def_ta_crit}, we find that tCE2 breaks when the
-semi-major axis is smaller than $a_{\rm break}$ where:
-\begin{align}
-    a_{\rm break} \approx{}& 0.038 \;\mathrm{AU}
-        \p{\frac{Q'}{10^{3}}}^{-1/9}
+resonance as part of a mechanism to form ultra-short period planets (USPs). They
+envision a process consisting of three stages:
+\begin{itemize}
+    \item Rapid initial guaranteed capture into CS2.
+
+    \item Runaway inward tidal migration due to the simultaneous increase of the
+        CS2 obliquity during migration.
+
+    \item Stalling of inward migration when tidal dissipation becomes
+        sufficiently strong to destroy CS2.
+\end{itemize}
+They consider an inner proto-USP with two external perturbing planets, and
+imagine that the spin of the planet quickly evolves to its equilibrium value,
+i.e.\ satisfying Eq.~\eqref{eq:weaktide_dWszero}. In our language, this
+corresponds to immediate evolution into tCE2. In this section, we revisit this
+mechanism with the results presented earlier in this paper.
+
+First, a proto-USP evolves from its initial condition into one of the tCE on the
+timescale
+% 1 / (1.5 * 1e-3 * (Msun / (8 Mearth)) * ((2 Rearth) / (0.035 AU))^3 * 2 * pi / (0.035)^(3/2))
+% = 1157
+\begin{align}
+    \frac{1}{t_{\rm s}} ={}& \frac{1}{1200\;\mathrm{yr}}
+            \p{\frac{1}{4k}}
+            \p{\frac{2k_2/Q}{10^{-3}}}
+            \p{\frac{M_\star}{M_{\odot}}}^{3/2}
+            \p{\frac{m}{8 M_{\oplus}}}^{-1}\nonumber\\
+        &\times \p{\frac{R}{2R_{\oplus}}}^3
+            \p{\frac{a}{0.035\;\mathrm{AU}}}^{-9/2}.
+\end{align}
+This is much shorter than the age of the system, and so the proto-USP can be
+treated as starting in one of the tCE\@.
+
+Next, we investigate the outcome of the initial, rapid spin evolution. First,
+due to the small semi-major axis ratio, we must generalize Eq.~\eqref{eq:wlp}
+\citep{lai_2017}:
+\begin{equation}
+    \omega_{\rm lp} = \frac{3m_{\rm p}}{4M_{\star}}
+        \alpha^3 n f(\alpha),
+        \label{eq:def_g_usp}
+\end{equation}
+where $\alpha = a / a_{\rm p}$ and \citep{murray1999solar}
+\begin{equation}
+    f(\alpha) \equiv \frac{b_{\rm 3/2}^{(1)}(\alpha)}{3\alpha}
+        \approx 1 + \frac{15}{8}\alpha^2 + \frac{175}{64}\alpha^4 + \dots,
+\end{equation}
+where $b_{\rm 3/2}^{(1)}$ is a Laplace coefficient. With this modification,
+$\eta_{\rm sync}$ (Eq.~\ref{eq:def_etasync}) can be computed:
+% (1 + 15/8 * (1.3)^(-4/3) + 175/64 * 1.3^(-8/3)) * 0.012
+\begin{align}
+    \eta_{\rm sync} ={}& 0.027 \cos I
+            \p{\frac{k}{k_{\rm q}}}
+            \p{\frac{m m_{\rm p}}{\p{8 M_{\oplus}}^2}}
+            \p{\frac{M_\star}{M_{\odot}}}^{-2}
+            \p{\frac{a}{0.035 \;\mathrm{AU}}}^{3}\nonumber\\
+        &\times \p{\frac{\alpha^3 f(\alpha)}{0.016}}
+            \p{\frac{R}{2R_{\oplus}}}^{-3}.
+            \label{eq:etasync_usp}
+\end{align}
+We have evaluated using an $\alpha$ corresponding to a period ratio $P_{\rm p} /
+P = 1.5$. For $I = 5^\circ$, roughly consistent with typical proto-USP systems
+\citep{dai2018larger}, Eq.~\eqref{eq:def_etac} shows that $\eta_{\rm sync} \ll
+\eta_{\rm c}$, and thus there are four CSs at spin-orbit synchronization. If,
+following \citet{millholland2020formation}, we take the initial planetary
+obliquity to be zero, the planet is guaranteed to evolve into tCE1, and not tCE2
+(see Fig.~\ref{fig:Hhists_0_06}). If we assume instead a randomly oriented
+initial planetary spin, perhaps again due to early giant impacts,
+Fig.~\ref{fig:probs5} suggests that the probability of capture into tCE2 is
+still only modest ($\lesssim 10\%$). A more sophisticated calculation including
+the effect of a third planet does not greatly modify these results. Note that
+this calculation is in tension with Fig.~4 of \citet{millholland2020formation},
+where they find that $\eta \sim 1$ for the same physical parameters when
+$\Omega_{\rm s}$ is at its equilibrium value (i.e.\ satisfying
+Eq.~\ref{eq:weaktide_dWszero}, or $\Omega_{\rm s} \approx n$ when the obliquity
+is small).
+
+The second stage of the proposed mechanism, runaway inward migration after
+attaining tCE2, requires that the initial orbital decay time scale be
+sufficiently fast. We find that:
+% 1 / (1.5 * 1e-3 * (Msun / (8 Mearth)) * ((2 Rearth) / (0.035 AU))^5 * 2 * pi / (0.035)^(3/2))
+% = 1.955e8
+\begin{align}
+    -\frac{\dot{a}}{a} ={}& \frac{1}{2 \times 10^8\;\mathrm{yr}}
+            \p{1 - \frac{\Omega_{\rm s}}{n}\cos \theta}
+            \p{\frac{2k_2/Q}{10^{-3}}}
+            \p{\frac{M_\star}{M_{\odot}}}^{3/2}\nonumber\\
+        &\times \p{\frac{m}{8M_{\oplus}}}^{-1}
+            \p{\frac{R}{2R_{\oplus}}}^5
+            \p{\frac{a}{0.035\;\mathrm{AU}}}^{-13/2}.
+            \label{eq:adot_usp}
+\end{align}
+For $\eta_{\rm sync} \ll \eta_{\rm c}$, we can show that $\p{1 - \Omega_{\rm
+s}\cos \theta / n} \approx 1$ in tCE2 by using Eqs.~\eqref{eq:def_tce2_approx},
+so indeed the orbit of the proto-USP is able to decay within the lifetime of the
+system. On the other hand, in tCE1, $\omega_{\rm s} \approx n$ and $\cos \theta
+\approx 1 - \eta_{\rm sync}^2 \sin^2 I / 2$, so $\dot{a} / a$ is suppressed by a
+factor of $\sim \eta_{\rm sync}^2 \sin^2 I$. This shows that a proto-USP in tCE1
+is unable to initiate runaway orbital decay within the age of the system.
+Note that this constraint also implies $\eta_{\rm sync}$
+(Eq.~\ref{eq:etasync_usp}) cannot be increased by considering proto-USPs with
+larger values of $a$, as the initial orbital decay will become too slow.
+
+Finally, we compute the orbital separation at which tCE2 becomes unstable due to
+sufficiently strong tidal dissipation. Evaluating Eq.~\eqref{eq:def_ts_crit}, we
+find that tCE2 breaks ($t_{\rm s} \lesssim t_{\rm s, c}$) when the semi-major
+axis is smaller than $a_{\rm break}$, where
+% (1e-3 * (Msun / (8 Mearth))^3 * ((2 Rearth) * (0.05 AU))^(9/2))^(1/9) / (1 AU)
+% = 0.033198
+\begin{align}
+    a_{\rm break} \approx{}& 0.033 \;\mathrm{AU}
+        \p{\frac{2k_2/Q}{10^{3}}}^{-1/9}
         \p{\frac{M_\star}{M_{\odot}}}^{1/3}
-        \p{\frac{m}{8M_{\oplus}}}^{-1/3}\nonumber\\
+        \p{\frac{mm_{\rm p}}{\p{8M_{\oplus}}^2}}^{-1/6}\nonumber\\
         &\times \p{\frac{R}{2R_{\oplus}}}^{1/2}
         \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{1/2}
-        \p{\frac{1}{\sin I \sqrt{\cos I}}}^{1/9}.
-\end{align}
-Here, we have assumed the planets are the same mass ($m_{\rm p} = m$) and have
-used the reduced tidal parameter $Q' = 3Q / 2k_2$. This corresponds to a 2.7-day
-orbit and does \emph{not} qualify to be a USP\@.
-
-Second, we note that \citet{millholland2020formation} focus on system
-architectures for which $\eta_{\rm sync} \gtrsim \eta_{\rm c}$ (where CS1 does
-not exist at spin-orbit synchronization; see Eqs.~\ref{eq:def_etac}
-and~\ref{eq:def_etasync}), finding that architectures for which $\eta_{\rm sync}
-\lesssim \eta_{\rm c}$ always generate evolution towards CS1. However, they
-assumed an initial obliquity $\theta_{0} = 0^\circ$, while broader distributions
-of initial planet obliquities will give some probability of evolution towards
-CS2 and tCE2 (see Figs.~\ref{fig:Hhists_0_06}--\ref{fig:Hhists_0_70}). To
-understand qualitatively the likelihood of this happening, we calculate the
-parameter
-\begin{align}
-    \eta_{\rm sync} ={}& 0.012 \p{\frac{k}{k_{\rm q}}}
-            \p{\frac{m}{8 M_{\oplus}}}^2
-            \p{\frac{M_\star}{M_{\odot}}}^{-2}\nonumber\\
-        &\times \p{\frac{a}{0.035 \;\mathrm{AU}}}^{3}
-            \p{\frac{P_{j + 1} / P_j}{1.5}}^{-2}
-            \p{\frac{R}{2R_{\oplus}}}^{-3}.
-\end{align}
-Thus, we see that capture into CS2 is not only not guaranteed but has quite low
-probability (see Figs.~\ref{fig:probs20}--\ref{fig:probs5}). Thus, we conclude
-that the presence of the third planet in their scenario significantly improves
-the formation rate of USPs, likely by significantly enhancing the precession
-rate $g$ compared to the two-planet case.
-
-At a more qualitative level, our result shows that it is not necessary to
-restrict formation of USPs via tidal runaway to system architectures for which
-$\eta_{\rm sync} \gtrsim \eta_{\rm c}$. In particular, architectures with larger
-period ratios $P_{j + 1} / P_j$ can still have substantial probability of
-generating an inner planet occupying tCE2 even if $\eta_{\rm sync} < \eta_{\rm
-c}$. Such architectures can be advantageous for USP formation as more of their
-total angular momentum budget is in the outer planet's orbit, allowing for more
-migration \citep{fabrycky_otides, millholland2020formation}.
+        \p{\frac{1}{\sin I \cos^2 I}}^{1/9}.
+\end{align}
+This corresponds to a 2.7-day orbit. Once the system exits tCE2, it rapidly
+evolves to tCE1, which suppresses its orbital decay (Eq.~\ref{eq:adot_usp}).
+This final orbital separation does not qualify as a USP ($P \lesssim
+\mathrm{day}$).
+
+In summary, our results for the formation of USPs via runaway tidal migration
+are in tension with those of \citet{millholland2020formation}. In particular, we
+find that only proto-USPs with a large primordial obliquity have a probability
+of evolving into tCE2 initially. Furthermore, proto-USPs that successfully
+initiate runaway tidal migration after reaching tCE2 will cease their inward
+migration before becoming a USP\@.
 
@@
 
-Applying our calculation for $a_{\rm break}$, we can calculate the required
-perturber properties if tCE2 is not to be destroyed by tides. This requires
-\begin{align}
-    \p{\frac{m_{\rm p}}{50 M_{\oplus}}}^{5/3}\p{\frac{a_{\rm
-        p}}{0.05\;\mathrm{AU}}}^{-8/3} \gtrsim {}&
-            \p{\frac{2k_2/Q}{10^{-7}}}^{2/3}
-            \p{\frac{M_\star}{1.36 M_{\odot}}}^{2}\nonumber\\
-        &\times \p{\frac{m}{1.41 M_{\rm J}}}^{-1}
-            \p{\frac{R}{1.89R_{\rm J}}}^{3}\nonumber\\
-        &\times \p{\frac{a}{0.023\;\mathrm{AU}}}^{-6}
-            \p{\frac{1}{\sin I_{\rm tot}}}^{2/3}.
-\end{align}
-The residuals of the published RVs (\textcolor{red}{TODO grab citations from
-Millholland, any updates?}) are $\sim 16\;\mathrm{m/s}$. Using a line-of-sight
-angle of $45^\circ$, we find that a planet with $m_{\rm p} = 50M_{\oplus}$ and
-$a_{\rm p} = 0.05\;\mathrm{AU}$ has an RV semi-amplitude of $12\;\mathrm{m/s}$,
-which cannot be ruled out. Thus, we reproduce the result of
-\citet{millholland_wasp12b}, that tCE2 remains stable under the dissipative
-tidal torque, and obliquity tides cannot be ruled out as a mechanism for
-WASP-12b's rapid orbital decay.
+In \citet{millholland2019obliquity}, the authors consider the possibility that
+the measured orbital decay of the HJ WASP-12b \citep[$P / \dot{P} = -3.2
+\;\mathrm{Myr}$; ][]{maciejewski2016departure, patra2017apparently} is caused by
+tidal dissipation in the HJ enhanced by being trapped in a high-obliquity CS due
+to an undetected exterior planet. In order for this scenario to be achieved,
+many conditions are necessary:
+\begin{itemize}
+    \item The HJ must have had a sufficiently small initial semimajor axis such
+        that its orbital decay timescale is less than the age of the system.
+
+    \item The exterior planet must be sufficiently massive to keep the HJ in a
+        high-obliquity tCE today.
+
+    \item The RV signal of the exterior planet must be smaller than the
+        residuals of the published RVs, $\sim 16\;\mathrm{m/s}$
+        \citep{hebb2009wasp, husnoo2011orbital, knutson2014friends,
+        bonomo2017gaps}.
+
+    \item The initial configuration of the HJ and exterior planet must be
+        dynamically stable.
+\end{itemize}
+Finally, if all four of these conditions are satisfied, the $\eta_{\rm sync}$ of
+the initial configuration can be used to estimate the likelihood of the spin of
+the HJ initally evolving into tCE2. We use the following current-day system
+parameters \citet{hebb2009wasp, maciejewski2013multi, millholland_wasp12b}:
+$R_\star = 1.63R_{\odot}$, $M_\star = 1.36M_{\odot}$, $R = 1.89R_{\rm J}$,
+$M_{\rm p} = 1.41M_{\rm J}$, and $a = 0.023 \;\mathrm{AU}$.
+
+First, we require that the initial HJ semimajor axis, denoted $a_{\rm i}$, is
+sufficiently small that decay occurs within the age of the system. The semimajor
+axis decay rate can be expressed as
+% 1 / (1.5 * 1e-7 * (1.36 Msun) / (1.41 Mjup) * ((1.89 Rjup) / (0.038 AU))^5 * (G * (1.36 Msun) / (0.038 AU)^3)^(1/2) * (1 yr))
+% = 9.82e8
+\begin{align}
+    \frac{\dot{a}}{a_{\rm i}}
+        =& -\frac{1}{\mathrm{Gyr}}
+            \p{\frac{2k_2/Q}{10^{-6}}}
+            \p{\frac{M_\star}{1.36 M_{\odot}}}^{3/2}
+            \p{\frac{m}{1.41M_J}}^{-1}\nonumber\\
+        &\times \p{\frac{R}{1.89R_j}}^5
+            \p{\frac{a_{\rm i}}{0.038\;\mathrm{AU}}}^{-13/2}
+            \p{1 - \frac{\Omega_{\rm s}}{n}\cos \theta}.
+            \label{eq:hj_adot}
+\end{align}
+Again, $t_{\rm s} \ll a_{\rm i} / \dot{a}$, so we can treat the HJ as
+immediately evolving into a tCE\@. Thus, we see that the initial semimajor axis
+for the HJ cannot exceed $0.038\;\mathrm{AU}$ even when $\p{1 - \Omega_{\rm
+s}\cos \theta/n} \approx 1$, as is the case for rapid evolution into tCE2 while
+$\eta_{\rm sync} \ll 1$.
+
+Next, we address the constraint that tCE2 is stable under the influence of the
+exterior planet. Due to the fact that the angular momentum of the HJ greatly
+exceeds that of the exterior planet ($L \gg L_{\rm p}$; we will verify this
+retroactively), Eq.~\eqref{eq:dldt1} needs to be modified. The precession of
+$\uv{l}$ about $\bm{J} = J\uv{j} \equiv \bm{L} + \bm{L}_{\rm p}$, the total
+angular momentum axis, can be written as
+\begin{equation}
+    \rd{\uv{l}}{t} = \omega_{\rm lp}\cos I \frac{J}{L_{\rm p}}
+        \p{\uv{l} \times \uv{j}},
+\end{equation}
+where $\omega_{\rm lp}$ is still given by Eq.~\eqref{eq:wlp}. Thus, we see that
+the precession frequency $\abs{g}$ is enhanced by a factor of $J / L_{\rm p}
+\approx L / L_{\rm p}$. With this modification, the stability of tCE2 requires
+\begin{equation}
+    \frac{1}{t_{\rm s}} \lesssim \omega_{\rm lp}\cos I \frac{L}{L_{\rm p}}
+        \sin I \sqrt{\frac{\eta_{\rm sync}\cos I}{2}}.
+\end{equation}
+This then yields that
+\begin{align}
+    \frac{a_{\rm p}}{a}
+        \lesssim{}& 3.3 \p{\sin I \cos^2 I}^{4/21}
+            \p{\frac{m}{1.41 M_J}}^{12/21}
+            \p{\frac{M_\star}{1.36 M_{\odot}}}^{-12/21}\nonumber\\
+        &\times \p{\frac{2k_2/Q}{10^{-6}}}^{-4/21}
+            \p{\frac{a}{0.023\;\mathrm{AU}}}^{6/7}
+            \p{\frac{R}{1.89 R_J}}^{-6/7}.\label{eq:hj_tce2_stab}
+\end{align}
+Notably, this expression does not depend on the perturber mass but only on
+$a_{\rm p}$.
+
+Next, we address the constraint that the RV signal of the exterior planet be
+smaller than $16\;\mathrm{m/s}$, which requires
+% (G * (1.36 Msun) / (0.125 AU))^(1/2) * (105 Mearth) / (1.36 Msun) / 2^(1/2)
+% 16.106 m/s
+\begin{equation}
+    \p{\frac{a_{\rm p}}{0.125\;\mathrm{AU}}}^{-1/2}
+    \p{\frac{m_{\rm p}}{105M_{\oplus}}}
+    \p{\frac{M_\star}{1.36M_{\odot}}}^{-1/2}
+    \p{\frac{\sin i}{1 / \sqrt{2}}} \lesssim 1,
+    \label{eq:hj_rv}
+\end{equation}
+where $i$ is the line-of-sight inclination angle. Here, we have taken $a_{\rm
+p}$ to be the maximum value permitted by the combination of
+Eqs.~(\ref{eq:hj_adot},~\ref{eq:hj_tce2_stab}). For these values of $a_{\rm p}$
+and $m_{\rm p}$, we still have $L / L_{\rm p} \sim 0.4$, and so $L \gg L_{\rm
+p}$ is be well satisfied for the permitted parameter space.
+
+Finally, we require that the initial orbital configuration be dynamically
+stable. We use the Hill stability criterion \citep[e.g.][]{petit2020path}:
+\begin{equation}
+    \frac{a_{\rm p} - a_{\rm i}}{a_{\rm i}} > 2\sqrt{3}\frac{a_{\rm p} + a_{\rm
+        i}}{2a_{\rm i}} \p{\frac{m + m_{\rm p}}{3M_{\star}}}^{1/3}.
+\end{equation}
+Assuming $m_{\rm p} \ll m$, this yields:
+\begin{equation}
+    \frac{a_{\rm p}}{a_{\rm i}} > 1.29.\label{eq:hj_orbstab}
+\end{equation}
+
+By using the constraints given by Eqs.~(\ref{eq:hj_adot},~\ref{eq:hj_orbstab}),
+the initial $\eta_{\rm sync, i}$ can be constrained:
+\begin{align}
+    \eta_{\rm sync, i} <{}& 0.016 \cos I\p{\frac{m}{1.41M_J}}^2
+            \p{\frac{M_\star}{1.36M_{\odot}}}^{-2}
+            \p{\frac{a_{\rm i}}{0.038\;\mathrm{AU}}}^{3}\nonumber\\
+        &\times \p{\frac{a_{\rm p} / a_{\rm i}}{1.29}}^{-7/2}
+            \p{\frac{R}{1.89R_{\rm J}}}^{-3}.\label{eq:hj_etasync}
+\end{align}
+It is possible that $R$ is larger today than its primordial value due to
+inflation induced by increased stellar irradiation. However, if a smaller value
+of $R$ is used in Eq.~\eqref{eq:hj_etasync}, the value of $a_{\rm i}$ must also
+be decreased such that $R^5 / a_{\rm i}^{13/2}$ is constant
+(Eq.~\ref{eq:hj_adot}), which further decreases $\eta_{\rm sync, i}$.
+
+For $\eta_{\rm sync} = 0.016$, we find that there are four CSs unless $I$ is
+extremely small. From Fig.~\ref{fig:Hhists_0_06}, we can infer that prograde
+primordial obliquities will evolve towards tCE1 in the regime where $\eta_{\rm
+sync} \ll \eta_{\rm c}$. On the other hand, if the primordial obliquity of the
+HJ is assumed to be isotropically distributed, then Fig.~\ref{fig:probs20}
+suggests that the probability of entry into tCE2 is still $\lesssim 2\%$ even if
+the perturbing planet is misaligned by $I = 20^\circ$.
+
+In summary, the joint constraints we have placed on the WASP-12b \& perturber
+system imply that the initial $\eta_{\rm sync, i}$ is unlikely to have been
+large. This suggests that early capture into tCE2 is unlikely from either an
+isotropic or prograde-favoring initial obliquity distribution. However, it is
+possible that additional mechanisms can generate a favorable initial obliquity
+distribution, such as the presence of a dissipating protoplanetary disk in the
+early lifetime of the system quickly driving the obliquity of WASP-12b to $\sim
+90^\circ$ \citep{millholland_disk, su2020}.
 
 \section{Summary and Discussion}\label{s:summary}
+
+In this work, we have studied the evolution of an interior planet's spin due to
+the joint effect of tidal dissipation and gravitational interactions with an
+exterior perturber. Our results extend our study of Colombo's Top in a previous
+paper \citep{su2020} to include a dissipative torque, for which we have adopted
+the weak friction theory of the equilibrium tide \citep{lai2012}. Our primary
+esults are as follows:
+\begin{itemize}
+    \item We calculate the modification of the equilibria of Colombo's Top
+        (Cassini States; CSs) due to tidal dissipation and evaluate the
+        stability of the CSs in the presence of the tidal dissipation.
+
+    \item We show that, for a given orbital architecture, the spin of the inner
+        planet has at most two spin configurations (spin frequency and
+        orientation) that are stable under the effect of tidal dissipation. We
+        call these equilibria \emph{tidal Cassini Equilibria} (tCE\@; see
+        Fig.~\ref{fig:6equils}). The locations of these equilibria are
+        determined by the system architecture and are parameterized by
+        $\eta_{\rm sync}$ (Eq.~\ref{eq:def_etasync}).
+
+    \item We show that which tCE a given initial planetary spin configuration
+        reaches can be probabilistic for certain initial conditions. For these
+        initial conditions, the probabilities of approaching either tCE can be
+        determined by careful study of the dynamics upon separatrix encounter
+        (Sections~\ref{ss:toy_outcomes} and~\ref{ss:phop_weaktide}). As an
+        example, if the initial spin orientation is assumed to be isotropically
+        distributed, the probabilities of entering tCE1 and tCE2 are given in
+        Figs.~\ref{fig:probs20} and~\ref{fig:probs5} as a function of $\eta_{\rm
+        sync}$ for two different mutual inclinations $I$.
+
+    \item In three exoplanetary scenarios of interest, application of our
+        results yields the following conclusions: (i) a super-Earth with an
+        exterior cold Jupiter has substantial probability of being trapped in a
+        high-obliquity tCE\@; (ii) formation of ultra-short-period planets via
+        tidal runaway is unlikely due to low probability of capture into a
+        high-obliquity tCE\@; and (iii) WASP-12b is unlikely to be undergoing
+        enhanced orbital decay due to obliquity tides, as the probability of
+        entry into tCE2 is also low.
+\end{itemize}
+
+Above, we have studied tidal dissipation in the planet via the weak friction
+theory of the equilibrium tide \citep{lai2012}. However, other mechanisms of
+tidal dissipation may be dominant, depending on the system parameters
+\citep[e.g.][]{papaloizou_ivanov_inertial, teyssandier2019formation}. While the
+detailed outcomes may change, a different tidal mechanism is amenable to the
+same analysis presented in this paper: The tCE can still be found by an analysis
+mirroring that shown in Fig.~\ref{fig:6equils}, and the probabilistic outcome of
+a separatrix encounter can still be solved using the techniques of
+Sections~\ref{ss:toy_outcomes} and~\ref{ss:phop_weaktide}.
+
+Additionally, we have primarily focused on an isotropic distribution of initial
+spin orientation, assuming that giant impacts will effectively randomize a
+planet's spin. More physically accurate distributions can be used in the case of
+planetary mergers \citep{li2020planetary} or many smaller impacts
+\citep{dones1993does}. Figures~\ref{fig:probs20}--\ref{fig:probs5} can be
+updated accordingly by convolving the distributions in the right panels of
+Figs.~\ref{fig:Hhists_0_06}--\ref{fig:Hhists_0_70} with any initial obliquity
+distribution. The qualitative results are unlikely to change, while the detailed
+probabilities for tCE2 capture can increase [decrease] if the initial obliquity
+distribution favors [disfavors] $\theta_{\rm i} \approx 90^\circ$ compared to
+the isotropic distribution.
 

### 2021-05-10 initial/1_weaktide/6misc.py

@@ -34,79 +34,89 @@ def get_cs_val(I, s_c, s):
             cs2_qs[idx] = cs_qs[0]
     return cs1_qs, cs2_qs
 
-def plot_equils(I, s_c, verbose=True, fn_str='6equils%s'):
+def plot_equils(I, s_cs, fn_str='6equils'):
     ''' plot in (s, mu) space showing how the tCS arise '''
-    fig = plt.figure(figsize=(5, 5))
-    s_lt = np.linspace(s_c / 10, 1, 200) # max eta = 10
-    s_gt = np.linspace(1, 3, 200) # other interesting part of the interval
-    s_tot = np.concatenate((s_lt, s_gt))
-
-    cs1_qs, cs2_qs = get_cs_val(I, s_c, s_tot)
-    cs1_exist_idx = np.where(cs1_qs > -1)[0]
-    mu_equil_lt = [np.degrees(np.arccos(get_mu_equil(s))) for s in s_lt]
 
     s_dq = np.linspace(2, 3, 200)
 
-    plt.xlabel(r'$\Omega_{\rm s} / n$')
-    plt.ylabel(r'$\theta$ (deg)')
-    plt.ylim([0, 180])
+    fig, axs = plt.subplots(
+        len(s_cs), 1,
+        figsize=(6, 2 + 3 * len(s_cs)),
+        sharex=True)
+    axs[-1].set_xlabel(r'$\Omega_{\rm s} / n$')
 
-    s_search_min = np.min(s_tot[cs1_exist_idx])
-    dS_interp = interp1d(s_lt, mu_equil_lt)
-    CS2_interp = interp1d(s_tot, np.degrees(cs2_qs))
-    CS1_interp = interp1d(s_tot[cs1_exist_idx],
-                          np.degrees(-cs1_qs[cs1_exist_idx]))
-    tce2_s = brenth(lambda s: dS_interp(s) - CS2_interp(s), s_search_min, 1)
-    tce1_s = brenth(lambda s: dS_interp(s) - CS1_interp(s), s_search_min, 1)
+    for ax, s_c, in zip(axs, s_cs):
+        s_lt = np.linspace(s_c / 10, 1, 200) # max eta = 10
+        s_gt = np.linspace(1, 3, 200) # other interesting part of the interval
+        s_tot = np.concatenate((s_lt, s_gt))
 
-    if verbose:
-        plt.plot(s_tot, np.degrees(cs2_qs), 'tab:green', label='CS2', lw=2.5)
[…]

### 2021-05-10 initial/99_misc/2_rand_plots.py

@@ -169,7 +169,6 @@ def plot_eigens(I=np.radians(5)):
                  [lambda2(e, q, -1)
                   for e, q in zip(etas_four, cs_vals[3])],
                  'tab:purple', label='CS4', lw=LW)
-    # plt.yscale('symlog', linthreshy=1e-5)
     plt.xlabel(r'$\eta$')
     plt.ylabel(r'$\lambda_0^2/ (1 + \eta^2)$')
     legend = plt.legend(loc='upper left', fontsize=14,
@@ -180,30 +179,54 @@ def plot_eigens(I=np.radians(5)):
     # plt.title(r'$I = %d^\circ$' % np.degrees(I))
     plt.tight_layout()
     plt.savefig('2_lambdas.png', dpi=400)
+    plt.close()
+
+def plot_eigens_phi(I=np.radians(5)):
+    etas, cs_vals, etas_four, etac = get_cs(I, num_pts=200)
+    def lambda2(eta, q, sign):
+        # note that the 4 CSs are 0, pi/2, -pi, -pi/2 by convention, which
+        # correspond to sign choices of -1 for all of them.
+        return (
+            (np.sin(q) - sign * eta * np.sin(I) / (np.sin(q)**2)) *
+            (sign * eta * np.sin(I))) / (1 + eta**2)
+    fig, axs = plt.subplots(
+        3, 1,
+        figsize=(6, 8),
+        sharex=True)
+    shifts_deg = [0, 20, 60]
+    shifts = [-np.cos(np.radians(d)) for d in shifts_deg]
+    for ax, shift, shift_deg in zip(axs, shifts, shifts_deg):
+        ax.semilogx(etas_four,
+                     [lambda2(e, q, shift)
+                      for e, q in zip(etas_four, cs_vals[0])],
+                     'darkorange', label='CS1', lw=LW)
+        ax.semilogx(etas,
+                     [lambda2(e, q, shift)
+                      for e, q in zip(etas, cs_vals[1])],
+                     'tab:green', label='CS2', lw=LW)
+        ax.semilogx(etas,
+                     [lambda2(e, q, shift)
+                      for e, q in zip(etas, cs_vals[2])],
+                     'tab:blue', label='CS3', lw=LW)
+        ax.semilogx(etas_four,
+                     [lambda2(e, q, shift)
+                      for e, q in zip(etas_four, cs_vals[3])],
[…]

### 2021-05-10 initial/99_misc/5discussion_plots.py

@@ -11,31 +11,58 @@ plt.rc('ytick', direction='in', left=True, right=True)
 # (3 * (8 Mearth) / (2.4 Msun) * (1.5)^3) / (3/2 * (0.6 Msun) / (8 Mearth) * ((2 Rearth) / (0.035 AU))^3 * 0.5)
 eta = 0.38 / 2 # kq / k?
 
-ain = np.linspace(0.02, 0.05, 50)
-fig = plt.figure(figsize=(6, 5))
-# heuristic (TODO), fixed spin = n / 2
-eta_1 = 1 / (eta * (ain / 0.035)**(3))
-plt.plot(ain, eta_1, 'b', label=r'$\eta_{\rm sync} = 1$')
-eta_3 = 1/3 / (eta * (ain / 0.035)**(3))
-plt.plot(ain, eta_3, 'g', label=r'$\eta_{\rm sync} = 1/3$')
-# 2 / (3 * 1e-3 * Msun / (8 Mearth) * ((2 Rearth) / (0.045 AU))^5 * 2 * pi / ((0.045)^(3/2)))
-adot_gyr = 3 / (ain / 0.045)**(13/2)
-plt.plot(ain, adot_gyr, 'b--', label=r'$\dot{a} = \mathrm{Gyr}$')
+def plot_actives():
+    ain = np.linspace(0.02, 0.05, 50)
+    fig = plt.figure(figsize=(6, 5))
+    # heuristic (TODO), fixed spin = n / 2
+    eta_1 = 1 / (eta * (ain / 0.035)**(3))
+    plt.plot(ain, eta_1, 'b', label=r'$\eta_{\rm sync} = 1$')
+    eta_3 = 1/3 / (eta * (ain / 0.035)**(3))
+    plt.plot(ain, eta_3, 'g', label=r'$\eta_{\rm sync} = 1/3$')
+    # 2 / (3 * 1e-3 * Msun / (8 Mearth) * ((2 Rearth) / (0.045 AU))^5 * 2 * pi / ((0.045)^(3/2)))
+    adot_gyr = 3 / (ain / 0.045)**(13/2)
+    plt.plot(ain, adot_gyr, 'b--', label=r'$\dot{a} = \mathrm{Gyr}$')
 
-fill_blue = np.where(adot_gyr > eta_1)[0]
-plt.fill_between(ain[fill_blue], eta_1[fill_blue], adot_gyr[fill_blue],
-                 facecolor='b', alpha=0.2)
[…]

### 2021-05-16 initial/YS_usp.tex
check in USP calcs + writeup

    \documentclass[11pt,
        usenames, % allows access to some tikz colors
        dvipsnames % more colors: https://en.wikibooks.org/wiki/LaTeX/Colors
    ]{article}
    \usepackage{
        amsmath,
        amssymb,
        fouriernc, % fourier font w/ new century book
        fancyhdr, % page styling
        lastpage, % footer fanciness
        hyperref, % various links
        setspace, % line spacing
        amsthm, % newtheorem and proof environment
        mathtools, % \Aboxed for boxing inside aligns, among others
        float, % Allow [H] figure env alignment
        enumerate, % Allow custom enumerate numbering
        graphicx, % allow includegraphics with more filetypes
        wasysym, % \smiley!
        upgreek, % \upmu for \mum macro
        listings, % writing TrueType fonts and including code prettily
        tikz, % drawing things
        booktabs, % \bottomrule instead of hline apparently
        xcolor, % colored text
        cancel % can cancel things out!
    }
    \usepackage[margin=1in]{geometry} % page geometry
    \usepackage[
        labelfont=bf, % caption names are labeled in bold
        font=scriptsize % smaller font for captions
    ]{caption}
    \usepackage[font=scriptsize]{subcaption} % subfigures

    \newcommand*{\scinot}[2]{#1\times10^{#2}}
    \newcommand*{\dotp}[2]{\left<#1\,\middle|\,#2\right>}
    \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
    \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
    \newcommand*{\rdil}[2]{\mathrm{d}#1 / \mathrm{d}#2}
    \newcommand*{\pdil}[2]{\partial#1 / \partial#2}
    \newcommand*{\rtd}[2]{\frac{\mathrm{d}^2#1}{\mathrm{d}#2^2}}
    \newcommand*{\ptd}[2]{\frac{\partial^2 #1}{\partial#2^2}}
    \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
    \newcommand*{\pvec}[1]{\vec{#1}^{\,\prime}}
    \newcommand*{\svec}[1]{\vec{#1}\;\!}
    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
    \newcommand*{\uv}[1]{\hat{\bm{#1}}}
    \newcommand*{\ang}[0]{\;\text{\AA}}
    \newcommand*{\mum}[0]{\;\upmu \mathrm{m}}
    \newcommand*{\at}[1]{\left.#1\right|}
    \newcommand*{\bra}[1]{\left<#1\right|}
    \newcommand*{\ket}[1]{\left|#1\right>}
    \newcommand*{\abs}[1]{\left|#1\right|}
    \newcommand*{\ev}[1]{\left\langle#1\right\rangle}
    \newcommand*{\p}[1]{\left(#1\right)}
    \newcommand*{\s}[1]{\left[#1\right]}
    \newcommand*{\z}[1]{\left\{#1\right\}}

    \newtheorem{theorem}{Theorem}[section]

    \let\Re\undefined
    \let\Im\undefined
    \DeclareMathOperator{\Res}{Res}
    \DeclareMathOperator{\Re}{Re}
    \DeclareMathOperator{\Im}{Im}
    \DeclareMathOperator{\Log}{Log}
    \DeclareMathOperator{\Arg}{Arg}
    \DeclareMathOperator{\Tr}{Tr}
    \DeclareMathOperator{\E}{E}
    \DeclareMathOperator{\Var}{Var}
    \DeclareMathOperator*{\argmin}{argmin}
    \DeclareMathOperator*{\argmax}{argmax}
    \DeclareMathOperator{\sgn}{sgn}
    \DeclareMathOperator{\diag}{diag\;}

    \colorlet{Corr}{red}

    % \everymath{\displaystyle} % biggify limits of inline sums and integrals
    \tikzstyle{circ} % usage: \node[circ, placement] (label) {text};
        = [draw, circle, fill=white, node distance=3cm, minimum height=2em]
    \definecolor{commentgreen}{rgb}{0,0.6,0}
    \lstset{
        basicstyle=\ttfamily\footnotesize,
        frame=single,
        numbers=left,
        showstringspaces=false,
        keywordstyle=\color{blue},
        stringstyle=\color{purple},
        commentstyle=\color{commentgreen},
        morecomment=[l][\color{magenta}]{\#}
    }

\begin{document}

\onehalfspacing

\section{Two Planet Mutual Precession}

Consider two planets mutually precessing. We calculate this in two ways below,
which are equivalent: the vector formulation, and as the eigenvalue of
Laplace-Lagrange theory. We compare these to the output of the RINGS code as a
third calculation.

\subsection{Vector Formulation}

We have
\begin{align}
    \rd{\uv{l}_1}{t} &= \omega_{21}\p{\uv{l}_1 \cdot \uv{l}_2}
            \p{\uv{l}_1 \times \uv{l}_2}\nonumber\\
        &= \omega_{21}\cos I_{12}
            \p{\uv{l}_1 \times \uv{l}_2},\\
    \rd{\uv{l}_2}{t} &= \frac{L_1}{L_2}\omega_{21}\cos I_{12}
        \p{\uv{l}_2 \times \uv{l}_1},\\
    \omega_{21}
        &= \frac{3 m_2}{4 M_\star}\p{\frac{a_1}{a_2}}^3 n_1
            f\p{\frac{a_1}{a_2}}\label{eq:w21},\\
    f\p{\alpha} &= \frac{b_{3/2}^{(1)}}{3\alpha}\nonumber\\
        &= \frac{1}{3\alpha}
            \frac{1}{\pi}\int\limits_0^{2\pi}
                \frac{\cos \p{t}}{
                \p{\alpha^2 + 1 - 2\alpha \cos t}^{3/2}}\;\mathrm{d}t\nonumber\\
        &\approx 1 + \frac{15}{8}\alpha^2 + \mathcal{O}\p{\alpha^4}.
\end{align}
In all numerical work, we calculate $f(\alpha)$ numerically, via direct
integration.

To get the precession rate of $\uv{l}_1$, we have shown many times that it
precesses around $\uv{j}$ with $\bm{J} = J\uv{j} = \bm{L}_1 + \bm{L}_2$ such
that
\begin{align}
    \rd{\uv{l}_1}{t} &= \omega_{21}\cos I_{21}
            \p{\uv{l}_1 \times \frac{\bm{L}_1 + \bm{L}_2}{L_2}}\nonumber\\
        &= \frac{J}{L_2}
            \omega_{21}\p{\uv{l}_1 \cdot \uv{l}_2}
                \p{\uv{l}_1 \times \uv{j}}\label{eq:2p_vec},
\end{align}
where again $\omega_{21}$ is given by Eq.~\eqref{eq:w21}.

\subsection{Laplace-Lagrange Formulation}\label{ss:LL}

Defining $\mathcal{I}_i = \abs{I_i} e^{i\Omega_i}$, the Laplace-Lagrange secular
theory says that:
\begin{align}
    \rd{}{t}\begin{bmatrix}
        \mathcal{I}_1\\\dots\\\mathcal{I}_N
    \end{bmatrix}
        &= \tilde{\bm{B}} \begin{bmatrix}
            \mathcal{I}_1\\\dots\\\mathcal{I}_N
        \end{bmatrix},\\
    B_{jk} &=
        -\frac{3 m_k}{4 M_\star}\p{\frac{a_i}{a_j}}^2
            \min\p{\frac{a_i}{a_j}, 1}
            n_j f\p{\frac{a_i}{a_j}},\\
    B_{jj} &= \sum\limits_{k \neq j}
        -B_{jk}.\label{eq:2p_LL}
\end{align}
In the two-planet case, $\tilde{\bm{M}}$ is just a $2 \times 2$ matrix, and the
only nonzero eigenvalue is the precession frequency (the other has eigenvalue
zero and corresponds to the total angular momentum). It is believable that this
is in agreement with Eq.~\eqref{eq:2p_vec} if we construct the corresponding
eigenvector and calculate its eigenvalue, and this appears to be the case.

\subsection{RINGS calculation}

For a given set of two-planet parameters, we can use RINGS to calculate their
dynamical evolution. The fiducial parameters we choose are:
\begin{align}
    a_1 &= 0.035\;\mathrm{AU} & m_1 &= M_{\oplus} & I_1 &= 1^\circ\\
    && m_2 &= 10M_\oplus & I_2 &= 5^\circ.
\end{align}
We choose $\Omega_i = \omega_i = 0$ for simplicity. We can then run RINGS and
try to extract the precession frequencies. To do this, I took the Fourier
Transform of $I_1(t)$ and found the frequency with the largest amplitude.

The results of the comparison among these three methods where $a_2$ is varied is
shown in Fig.~\ref{fig:scan}.
\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{4_usp_rings/scan_alpha.png}
    \caption{(Top \& middle) plot of precession frequencies obtained using three
    methods as a function of $a_2$ for two and three-planet systems. Good
    agreement is observed in two-planet cases, while the three-planet systems
    have some interesting behavior. The bottom panel shows the quotient of the
    largest vector-calculated frequency and the numerical value for the 3-planet
    case; convincing agreement is observed. Frequencies are }\label{fig:scan}
\end{figure}

\section{Three-Planet Case}

\subsection{Vector Calculation}

We now add a third planet. For simplicity, we will neglect the precession
induced on $\bm{L}_2$ and $\bm{L}_3$ by $\bm{L}_1$, then:
\begin{align}
    \rd{\uv{l}_1}{t} &= \omega_{21}\cos I_{12} \p{\uv{l}_1 \times \uv{l}_2}
        + \omega_{31}\cos I_{13} \p{\uv{l}_1 \times \uv{l}_3}
        \nonumber\\
    \rd{\uv{l}_2}{t} &= \omega_{32}\cos I_{23} \p{\uv{l}_2 \times \uv{l}_3},\\
    \rd{\uv{l}_3}{t} &= \frac{L_2}{L_3}
        \omega_{32}\cos I_{23} \p{\uv{l}_3 \times \uv{l}_2},\\
    \omega_{jk}
        &= \frac{3 m_k}{4 M_\star}\p{\frac{a_j}{a_k}}^3 n_j
            f\p{\frac{a_j}{a_k}}.
\end{align}
We expect two eigenvectors, one where $\uv{l}_1$ is evolving and one where the
other two are evolving. The latter has the precession frequency
\begin{equation}
    \Omega_{\rm 32} = \frac{J_{23}}{L_3}\omega_{32}.
\end{equation}
The former has the precession frequency:
\begin{align}
    \rd{\uv{l}_1}{t} &= -\s{
        \omega_{21}\cos I_{12} \uv{l}_2 + \omega_{31}\cos I_{13} \uv{l}_3
    } \times \uv{l}_1 \nonumber\\
        &\equiv \bm{\Omega}_{32,1} \times \uv{l}_1,\\
    \Omega_{32, 1}
        &\approx \omega_{21} \cos I_{12}
            + \omega_{31}\cos I_{13}
            + \mathcal{O}\p{\cos I_{23}}.
\end{align}
Here, we have simply assmued that $\uv{l}_2$ is approximately aligned with
$\uv{l}_3$; by the law of cosines, the deviation scales with $\cos I_{23} \sim
2^\circ$ for compact architectures excepting the innermost planet.

We want to know which of $\Omega_{32}$ and $\Omega_{32, 1}$ are larger. To
calculate scalings, let's approximate $I_{12} \approx I_{13} \approx I_{23}
\approx 0$. If we assume the semimajor axis ratios are constant, $a_3 / a_2 =
a_2 / a_1 = \alpha$, then
\begin{align}
    \frac{\Omega_{32, 1}}{\Omega_{32}}
        &= \frac{m_2 \alpha^3 n_1 f(\alpha)
            + m_3 \alpha^6 n_1 f(\alpha^2)}{m_3 \alpha^3 n_2
            f(\alpha)}\frac{L_3}{J_{23}}\nonumber\\
        &= \frac{L_3}{J_{23}}\p{
            \frac{m_2}{m_3}\alpha^{-3/2}
                + \alpha^{3/2}\frac{f\p{\alpha^2}}{f(\alpha)}}.
\end{align}
Note that $J_{23} / L_3 \approx (m_2/m_3)\alpha^{1/2} + 1$. There are thus two
ways to obtain $\Omega_{32, 1} < \Omega_{32}$:
\begin{itemize}
    \item If we have $\alpha \approx m_2/m_3 \approx f\p{\alpha^2} / f(\alpha)
        \approx 1$, then $J_{23} / L_3 \approx 2$ and $\Omega_{32, 1} /
        \Omega_{32} \approx 0.5$, so not a very large ratio.

    \item A much larger ratio can be obtained if $m_2/m_3 \ll \alpha^{3/2} \ll
        1$.
\end{itemize}
Thus, in general, we find that the $\Omega_{32, 1}$ precession frequency should
generally be larger or comparable except for very small $a_{j + 1} / a_j$.

\subsection{Comparison with Other Results}

The LL results follow straightforwardly from Section~\ref{ss:LL}. The RINGS
simulations can yield two precession frequencies if we seek the first two
non-commensurate, non-adjacent frequencies in the FT of $I_1(t)$; note that
choosing $\Omega_{i} = \omega_i = 0$ means that $\uv{l}_2 = \uv{l}_3$ initially,
but due to different backreaction torques from $\uv{l}_1$ they eventually
misalign and give rise to the $\Omega_{32}$ mode. This is shown in the middle
panel of Fig.~\ref{fig:scan}. Finally, in the bottom panel, we show the quotient
of $\Omega_{32, 1}$ and the numerically-determined maximum precession frequency.
We see fractional deviations, showing that $\Omega_{32, 1}$ is a good estimate
of $g_{\max}$.

\subsection{Inner Mass Dependence}

In the above, we have considered the case where $m_1 = M_{\odot}$ and $m_2 = m_3
= 10M_{\odot}$, satisfying our ``no backreaction'' assumption. However, we can
also consider the case closer to the Millholland paper, where $m_i =
5M_{\odot}$. These results are shown in Fig.~\ref{fig:scan5}. For some reason,
the agreement \emph{improves}?
\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{4_usp_rings/scan_alpha5.png}
    \caption{Same as Fig.~\ref{fig:scan} but for equal masses $m_i =
    5M_{\odot}$.}\label{fig:scan5}
\end{figure}

\section{Resulting Impact on USP Formation Story}

In the 3p systems, we see that $\abs{g_{\max}} \lesssim 0.2 \;\mathrm{yr^{-1}}$.
At the same time, we can calculate the spin-orbit precession frequency:
\begin{align}
    \alpha &= \frac{3k_q}{2k}\frac{M_\star}{m}
        \p{\frac{R}{a}}^3 \Omega_{\rm s},\\
        &\approx 0.86\;\mathrm{yr^{-1}}
            \frac{k_q}{k}
            \p{\frac{M_{\star}}{M_{\odot}}}^{3/2}
            \p{\frac{m}{M_{\oplus}}}^{-1}
            \p{\frac{R}{R_{\oplus}}}^3
            \p{\frac{a}{0.035\;\mathrm{AU}}}^{-9/2}
            \p{\frac{\Omega_{\rm s}}{n}}.
\end{align}
This shows that $\eta_{\rm sync} \equiv \abs{g_{\max}} / \alpha \lesssim 0.15$
very optimistically.

Using Millholland's formula, we have yet another small correction. They use
$3k_q = 0.4$ and $k = 0.35$, so their $\alpha$ is depressed by a factor of
$8/21$, leaving $\eta_{\rm sync} \sim 0.4$ for extremal values (note that $a_2 /
a_1 = 1.2$ corresponds to a period ratio of $1.3$). So indeed, we should expect
that $\eta_{\rm sync}$ is only $\gtrsim 1$ if $a_2 / a_1 \lesssim 1.2$.

\subsection{Double Checking $\eta_{\rm sync}$ for 2p}

Recall that we had:
\begin{align}
    \eta_{\rm sync} &= \frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
            \p{\frac{a}{R}}^3,\\
% (8 * (Mearth)^2 / (Msun)^2) / 2 * (2)^(-3) * ((0.04 AU) / (2 Rearth))^3
% 0.00467
        &= 4.67 \times 10^{-4}
            \cos I \frac{k}{k_{\rm q}}f\p{\frac{1}{2}}
            \frac{m_pm}{8(M_{\odot}^2)}
            \p{\frac{M_\star}{M_{\odot}}}^{-2}
            \p{\frac{a/a_{\rm p}}{1/2}}^3
            \p{\frac{a}{0.04\;\mathrm{AU}}}^3
            \p{\frac{R}{2R_{\oplus}}}^{-3},\\
% (10 * (Mearth)^2 / (Msun)^2) / 2 * (1.2)^(-3) * ((0.035 AU) / (Rearth))^3
% 0.014480
        &= 0.0145
            \cos I \frac{k}{k_{\rm q}}f\p{\frac{1}{1.2}}
            \p{\frac{m_p}{10M_{\odot}}}
            \p{\frac{\rho}{\rho_{\oplus}}}
            \p{\frac{M_\star}{M_{\odot}}}^{-2}
            \p{\frac{a/a_{\rm p}}{1/1.2}}^3
            \p{\frac{a}{0.035\;\mathrm{AU}}}^3.
\end{align}
Note that $f(0.5) = 1.72$ while $f(1/1.2) = 9.69$ (NB\@: the power series for
$\alpha$ converges way too slowly for the latter result, have to evaluate
numerically), so this is already a bit more promising.

\subsection{Towards $\eta_{\rm sync}$ for 3p? No}

We showed above that
\begin{align}
    \abs{g_{\max}} &\approx \Omega_{\rm 32, 1}\nonumber\\
        &\approx \omega_{21}\cos I_{12}
            \p{1 + \frac{m_3}{m_2}\alpha^3\frac{f\p{\alpha^2}}{f(\alpha)}
                \frac{\cos I_{13}}{\cos I_{12}}}.
\end{align}
Trying to express this in any sort of scaling way is difficult since $f(\alpha)$
cannot be expressed analytically for sufficiently large $\alpha$. Nevertheless,
for the fiducial $\alpha = 1/1.2$ and $m_3 = m_2$, we find that this enhancement
is only $1.2\times$, and if we account for the fact that our naive prediction
is small by about $15\%$, the third planet only contributes $40\%$ of the
precession rate of the inner. This is unsurprising, and is not enough to lift
$\eta_{\rm sync}$ to values of order unity; it raises it only to $\sim 0.2
k/k_{\rm q}$, which is in line with our calculation above. So everything seems
consistent!

\end{document}

### 2021-05-16 initial/1_weaktide/5pop.py

@@ -402,20 +402,23 @@ def plot_cum_probs(I, s_c_vals, s0, counts):
 def run():
     s_c_vals_20 = [
         # 0.7,
-        0.2,
-        0.06,
+        # 0.2,
+        # 0.06,
         # 2.0,
         # 1.2,
         # 1.0,
         # 0.65,
         # 0.6,
         # 0.55,
-        0.5,
+        # 0.5,
         # 0.45,
         # 0.4,
         # 0.35,
         # 0.3,
         # 0.25,
+        0.1,
+        0.03,
+        0.01,
     ]
     s_c_vals_5 = [
         # 0.7,
@@ -436,6 +439,9 @@ def run():
         # 0.35,
         # 0.3,
         # 0.25,
+        0.1,
+        0.03,
+        0.01,
     ]
     eps = 1e-3
     s0 = 10
@@ -582,7 +588,7 @@ def plot_anal_cs_equils(I=np.radians(20), s_c=0.2):
 
 if __name__ == '__main__':
     run()
-    plot_all_cumprobs()
+    # plot_all_cumprobs()
     # plot_anal_cs_equils()
 
     # bunch of debugging cases...

### 2021-05-16 writeups/Su_weak_tides.tex
investigated scaling relation for tCE2 probability at small eta_sync

@@
 
-% \section{Separatrix Crossing Probability with Weak Tidal Friction
-% }\label{app:sep_crossing_dynamics}
-
-% In this appendix, we analytically calculate $\Delta K_{\pm}$ for use in
-% Eq.~\eqref{eq:def_pc_weaktide} to calculate the probabilities of the two
-% possible transitions upon separatrix encounter. We first rewrite the full
-% equations of motion for the planet's spin including weak tidal friction in
-% component form:
-% \begin{align}
-%     \rd{\theta}{t} &= g\sin I \sin \phi -
-%         \frac{1}{t_{\rm a}} \sin \theta,\label{eq:ds_fullq}\\
-%     \rd{\phi}{t} &= -\alpha\cos\theta
-%         - g\p{\cos I + \sin I \cot \theta \cos \phi}\label{eq:ds_fullphi},\\
-%     \rd{\Omega_{\rm s}}{t}
-%         &= \frac{1}{t_{\rm a}} \s{2n \cos \theta
-%             - g\Omega_{\rm s}\p{1 + \cos^2\theta}}\label{eq:ds_fulls}.
-% \end{align}
-
-% Note that Eq.~\eqref{eq:def_dK_weaktide} can be rewritten
-% \begin{align}
-%     \Delta K_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}
-%         - \rd{H_{\rm sep}}{t}\;\mathrm{d}t
-%         \nonumber\\
-%         &= \oint_{\mathcal{C}_{\pm}}
-%            \p{\rd{(\cos\theta)}{t}}_{\rm tide}
-%             + \frac{\dot{\Omega}_{\rm s}}{\dot{\phi}}
-%             \p{\pd{H}{s} - \pd{H_{\rm sep}}{s}}\;\mathrm{d}\phi
-%                 \label{eq:app_dhpm}.
-% \end{align}
-
-% We then evaluate $\Delta K_{\pm}$ by integrating along the two legs of the
-% separatrix $\mathcal{C}_{\pm}$ (see Fig.~\ref{fig:1contours}). Note that we must
-% use the value of $\eta$ at the moment of separatrix encounter, as the evolution
-% of $\Omega_{\rm s}$ changes the spin-orbit precession frequency $\alpha$
-% \begin{align}
+\section{Approximate TCE2 Probability for Small $\eta_{\rm sync}$
+}\label{app:sep_crossing_dynamics}
+
+In this appendix, we seek a tentative analytic understanding for the
+probability of convergence to tCE2 when $\eta_{\rm sync}$ is small, i.e.\ the
+left extremes of Figs.~\ref{fig:probs20} and~\ref{fig:probs5}. In this regime,
+following the discussions in Sections~\ref{ss:toy_outcomes}
+and~\ref{ss:phop_weaktide}, we understand that initial conditions in zone I
+always converge to tCE1, initial conditions in zone II always converge to tCE2,
+and initial conditions in zone III experience separatrix encounter and
+probabilistically converge to either one of the tCE\@. To further proceed, we
+will assume an isotropic distribution of initial spin orientations; different
+distributions again will only change the quantitative but not qualitative
+character of the discussion.
+
+To express the contribution of initial conditions in zone II to the total tCE2
+probability (green shaded region in Figs.~\ref{fig:probs20}
+and~\ref{fig:probs5}), we need only to know the probability an arbitrary
+initial condition is in zone II\@, which can be obtained by the phase space
+area of zone II\@. An exact analytic form for this area is known
+(\citealp{ward2004I}, Paper I), but an accurate approximation can be obtained
+using Eq.~\eqref{eq:sep_theta} since $\eta_{\rm i} \ll 1$:
+\begin{align}
+    \frac{A_{\rm II}}{4\pi} = \frac{4}{\pi}\sqrt{\eta_{\rm i} \sin I}.
+\end{align}
+where $A_{\rm II}$ is the phase space area (in $\cos \theta$ and $\phi$
+coordinates) of zone II\@.
+
+To express the contribution of initial conditions in zone III to the totac tCE2
+probability (blue shaded region in Figs.~\ref{fig:probs20}
+and~\ref{fig:probs5}), we need both the area of zone III and the distribution of
+outcomes upon separatrix encounter. The area of zone III can again be estimated
+quite simply using Eq.~\eqref{eq:sep_theta}, and we obtain
+\begin{align}
+    \frac{A_{\rm III}}{4\pi}
+        = \frac{1 + \eta_{\rm i} \cos I}{2} -
+            \frac{2}{\pi}\sqrt{\eta_{\rm i} \sin I}.
+\end{align}
+where $A_{\rm III}$ is the phase space area of zone III\@. Next, we need to
+understand the outcomes of the separatrix encounters that initial conditions in
+zone III experience.. We analytically calculate $\Delta K_{\pm}$
+(Eq.~\ref{eq:def_dK_weaktide}) for use in Eq.~\eqref{eq:def_pc_weaktide} to
+obtain the probabilities of the outcomes of separatrix encounter. We first
+rewrite Eq.~\eqref{eq:def_dK_weaktide} as:
+\begin{align}
+    \Delta K_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}
+        - \rd{H_{\rm sep}}{t}\;\mathrm{d}t
+        \nonumber\\
+        &= \oint_{\mathcal{C}_{\pm}}
+           \p{\rd{(\cos\theta)}{t}}_{\rm tide}
+            + \frac{\dot{\Omega}_{\rm s}}{\dot{\phi}}
+            \p{\pd{H}{s} - \pd{H_{\rm sep}}{s}}\;\mathrm{d}\phi
+                \label{eq:app_dhpm}.
+\end{align}
+Then, using the full equations of motion for the planet's spin including weak
+tidal friction in component form, given by
+Eqs.~(\ref{eq:ds_fullq}--\ref{eq:ds_fulls}), we can evaluate $\Delta K_{\pm}$ by
+integrating along the two legs of the separatrix $\mathcal{C}_{\pm}$ (see
+Fig.~\ref{fig:1contours}). Note that we must use the value of $\eta$ at the
+moment of separatrix encounter, which we denote $\eta_{\rm cross}$, as the
+evolution of $\Omega_{\rm s}$ changes the spin-orbit precession frequency
+$\alpha$ and thus $\eta$ itself:
+\begin{align}
     % \Delta K_{\pm} ={}& \oint_{\mathcal{C}_{\pm}}
@@
     %         c}}{2\Omega_{\rm s}^2}\cos^2 I}\rd{\Omega_{\rm
-%             s}}{t}\rd{t}{\phi}\;\mathrm{d}\phi\\
+    %         s}}{t}\rd{t}{\phi}\;\mathrm{d}\phi\nonumber\\
     %  \approx{}& \oint_{\mathcal{C}_{\pm}}
@@
     %         \p{\frac{2n}{\Omega_{\rm s}} - \cos\theta}
-%         + \frac{1}{t_{\rm s}}\frac{n}{\Omega_{\rm s}\eta}
+    %     + \frac{1}{t_{\rm s}}\frac{n}{\Omega_{\rm s}\eta_{\rm cross}}
     %         \s{\p{\cos \theta}_{\mathcal{C}_{\pm}} - \frac{\Omega_{\rm s}}{2n}}
-%             \s{2 \cos I \pm \sqrt{2 \sin I\p{1 - \cos \phi} / \eta}}
-%             \;\mathrm{d}\phi.\label{eq:app_deltaK}
-%     t_{\rm s} \Delta K_{\pm} \approx{}&
-%         -2\cos I\p{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
-%         \pm 2\pi \frac{\Omega_{\rm s}}{n}\cos I
-%         - 8\eta \cos I \sqrt{\sin I / \eta}
-%             + \frac{4\Omega_{\rm s}}{n}\sqrt{\sin I/\eta}\nonumber\\
-%         &+ \frac{2n}{\Omega_{\rm s}}\p{\mp 2\pi\p{1 - 2\eta \sin I}
-%             + 16\cos I \eta^{3/2}\sqrt{\sin I}}
-%             + 8\sqrt{\eta \sin I}
-%             \pm 2 \pi \eta \cos I
-%             - \frac{64}{3} \p{\eta \sin I}^{3/2}.\label{eq:app_deltaK}
-% \end{align}
-% At this point, since $\eta$ often is not small, it is necessary to integrate
-% along the numerically computed $\mathcal{C}_{\pm}$ (instead of the approximate
-% solution given by Eq.~\ref{eq:sep_theta}) to obtain sufficiently accurate values
-% for $\Delta K_{\pm}$. These numerically integrated values are used in
-% Eq.~\eqref{eq:def_pc_weaktide} to semi-analytically compute the tCE2
-% probabilities (blue curves) in
-% Figs.~\ref{fig:pc_fits_0_06}--\ref{fig:pc_fits_0_20}.
+    %         \s{2 \cos I \pm \sqrt{2 \sin I\p{1 - \cos \phi} / \eta_{\rm cross}}}
+    %         \;\mathrm{d}\phi,\\
+    t_{\rm s} \Delta K_{\pm} \approx{}&
+        \frac{\eta_{\rm cross}^2}{\eta_{\rm sync}}\s{
+            -2\cos I\p{\pm 2\pi \eta_{\rm cross} \cos I
+                + 8\sqrt{\eta_{\rm cross} \sin I}}
+            \mp 4\pi \sin I
+            - 8 \cos I \sqrt{\eta_{\rm cross}\sin I}
+                + \frac{4\eta_{\rm sync}}{\eta_{\rm cross}}
+                    \sqrt{\sin I/\eta_{\rm cross}}}\nonumber\\
+        &+ \frac{2\eta_{\rm cross}}{\eta_{\rm sync}}
+            \p{\mp 2\pi\p{1 - 2\eta_{\rm cross} \sin I}
+            + 16\cos I \eta_{\rm cross}^{3/2}\sqrt{\sin I}}
+            + 8\sqrt{\eta_{\rm cross} \sin I}
+            \pm 2 \pi \eta_{\rm cross} \cos I
+            - \frac{64}{3} \p{\eta_{\rm cross} \sin I}^{3/2}.
+                \label{eq:app_deltaK}
+\end{align}
+The resulting $P_{\rm III \to II}$ obtained using this analytic $\Delta K_{\pm}$
+in Eq.~\eqref{eq:def_pc_weaktide} is shown as the green dashed line in the top
+panel of Fig.~\ref{fig:pc_fits_0_06}, where it can be seen that agreement is
+reasonable for $\eta_{\rm cross} \lesssim 0.05$. For the purposes of this
+section, we drop all but the leading order terms in both the numerator and
+denominator of Eq.~\eqref{eq:def_pc_weaktide} and obtain:
+% proof:
+% from utils import *; I = np.radians(20); s_c = 0.01; s = np.linspace(1, 10, 100); top, bottom = get_ps_anal(I, s_c, s); plt.plot(s_c/s, (bottom + top) / bottom, 'k'); plt.plot(s_c/s, 6 * s_c / np.pi * np.sqrt(np.sin(I) / (s_c / s)), 'g')
+\begin{equation}
+    P_{\rm III \to II} \approx
+        \frac{6\eta_{\rm sync}}{\pi} \sqrt{\frac{\sin I}{\eta_{\rm cross}}}.
+\end{equation}
+Finally, based on the bottom panel of Fig.~\ref{fig:pc_fits_0_06}, we make the
+approximation that $\eta_{\rm cross}$ is uniformly distributed between
+$\eta_{\rm i}$ and $\eta_{\rm sync}$. This approximation is mildly justifiable
+as $\eta_{\rm cross}$ favors smaller values in the interval $\s{\eta_{\rm i},
+\eta_{\rm sync}}$, but also extends beyond $\eta_{\rm sync}$ for $\cos
+\theta_{\rm i}$ close to $-1$, so we hope these two effects cancel out to some
+extent. Thus,
+\begin{align}
+    \ev{P_{\rm III \to II}}
+        &\sim \frac{1}{\eta_{\rm sync} - \eta_{\rm i}}
+            \int\limits_{\eta_{\rm i}}^{\eta_{\rm sync}}
+            P_{\rm III \to II}\;\mathrm{d}\eta_{\rm cross}\nonumber\\
+        &= \frac{12 \sqrt{\eta_{\rm sync}\sin I}}{\pi
+            \p{1 + \sqrt{n / \Omega_{\rm s, i}}}}.
+\end{align}
+
+Finally, returning to the aggregate tCE2 probability, we can evaluate it as:
+\begin{align}
+    \text{tCE2 Probability}
+        &= \frac{A_{\rm II}}{4\pi}
+            + \frac{A_{\rm III}}{4\pi}\ev{P_{\rm III \to II}}\nonumber\\
+        &\simeq
+            \frac{4\sqrt{\eta _{\rm sync} \sin I}}{\pi}\p{
+                \sqrt{n / \Omega_{\rm s, i}}
+                + \frac{3}{2\p{1
+                + \sqrt{n / \Omega_{\rm s, i}}}}}
+            + \mathcal{O}\p{\eta_{\rm sync}}.\label{eq:app_tce2_p_tot}
+\end{align}
 

### 2021-05-16 initial/1_weaktide/5pop.py

@@ -291,26 +291,51 @@ def plot_eq_dists(I, s_c, s0, IC_eq1, IC_eq2):
     # try to overplot the semi-analytical simulations I ran
     pkl_fn = '6pc_dist%s.pkl' % s_c_str(s_c)
     if os.path.exists(pkl_fn):
-        fig = plt.figure(figsize=(6, 4))
         n_mu = 501
         n_phi = 50
         mu_vals =  np.linspace(-0.99, 0.99, n_mu)
         with open(pkl_fn, 'rb') as f:
             cross_dat = pickle.load(f)
-        # p_caps = get_anal_caps(I, s_c, cross_dat, mu_vals)
         p_caps = get_num_caps(I, s_c, cross_dat, mu_vals)
         tot_probs = np.sum(p_caps / n_phi, axis=1)
-        plt.plot(mu_vals, tot_probs, 'b', alpha=0.8, lw=3.5)
+        if s_c < 0.1:
+            fig, (ax1, ax2) = plt.subplots(
+                2, 1,
+                figsize=(6, 6),
+                gridspec_kw={'height_ratios': [2, 1]},
+                sharex=True)
+        else:
+            fig = plt.figure(figsize=(6, 4))
+            ax1 = plt.gca()
+        ax1.plot(mu_vals, tot_probs, 'b', alpha=0.8, lw=3.5)
+
+        # try anal prob
+        p_caps_al = get_anal_caps(I, s_c, cross_dat, mu_vals)
+        s_crosses = np.max(cross_dat[:, :, 0], axis=1)
+        tot_probs_al = np.sum(p_caps_al / n_phi, axis=1)
 
         bin_cents = (bins[ :-1] + bins[1: ]) / 2
         bin_probs = np.array(n[0]) / np.array(n[1])
-        plt.plot(bin_cents, bin_probs, 'ro', ms=3)
-        plt.xlabel(r'$\cos \theta_{\rm i}$')
-        plt.ylabel(r'tCE2 Probability')
-        plt.tight_layout()
+        ax1.plot(bin_cents, bin_probs, 'ro', ms=3)
+        ax1.set_ylabel(r'tCE2 Probability')
         s_c_text = '%.1f' % s_c if s_c > 0.1 else '%.2f' % s_c
-        plt.text(1, 1, r'$\eta_{\rm sync} = %s$' % s_c_text,
+        ax1.text(1, 1, r'$\eta_{\rm sync} = %s$' % s_c_text,
[…]

### 2021-05-16 initial/99_misc/6etacross_dist.py

@@ -1,0 +1,50 @@
+'''
+try to semi-analytically estimate the distribution of eta @ crossing as a
+function of initial conditions, assuming sep crossing occurs when theta = 90
+degrees (which is where theta_dot, tide = 0 if spin is large)
+
+Conclusion: due to flatness of theta_dot,tide as theta grows close to 90
+degrees, most systems will spin down significantly before separatrix encounter.
+Thus, approximate crossing probability by evaluation at eta_sync
+'''
+from scipy.interpolate import interp1d
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif', size=20)
+plt.rc('lines', lw=2.5)
+plt.rc('xtick', direction='in', top=True, bottom=True)
+plt.rc('ytick', direction='in', left=True, right=True)
+
+def integrand(q):
+    return -(1 + np.cos(q)**2) / (np.cos(q) * np.sin(q))
+
+def get_integrals(q_vals):
+    '''
+    get the value of int(integrand, {q, 90, q_val in q_vals}) by interpolating a
+    densely-evaluated integral
+    '''
+    q_vals_dense = np.linspace(np.min(q_vals), np.max(q_vals), 10000)
+    int_vals = np.cumsum(integrand(q_vals_dense)) * (
+        np.max(q_vals) - np.min(q_vals)) / len(q_vals_dense)
+    int_orig = interp1d(q_vals_dense, int_vals)(q_vals)
+    return int_orig
+
+def plot_Ws_cross(Wsi=10):
+    '''
+    \Omega_s normalized to units of n
+    '''
+    q_vals = np.linspace(np.radians(100), np.radians(175), 100)
+    integrals = get_integrals(q_vals)
+    # solve 1/Ws,cross - 1 / Wsi = integrals
+    plt.plot(np.degrees(q_vals), integrals, 'r')
+    plt.xlabel(r'$\theta_{\rm i}$')
+    plt.ylabel(r'Integral')
+    plt.tight_layout()
+    plt.savefig('6etacross_dist', dpi=300)
+    plt.close()
+
+if __name__ == '__main__':
+    plot_Ws_cross()

### 2021-05-17 weeklies/YS_210518.tex
05/18 meeting

--- 2021-05-16 initial/YS_usp.tex
@@
     B_{jk} &=
-        -\frac{3 m_k}{4 M_\star}\p{\frac{a_i}{a_j}}^2
-            \min\p{\frac{a_i}{a_j}, 1}
-            n_j f\p{\frac{a_i}{a_j}},\\
+        -\frac{3 m_k}{4 M_\star}\p{\frac{a_j}{a_k}}^2
+            \min\p{\frac{a_j}{a_k}, 1}
+            n_j f\p{\frac{a_j}{a_k}},\\
     B_{jj} &= \sum\limits_{k \neq j}
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{4_usp_rings/scan_alpha.png}
+    \includegraphics[width=0.7\columnwidth]{../initial/4_usp_rings/scan_alpha.png}
     \caption{(Top \& middle) plot of precession frequencies obtained using three
@@
             + \omega_{31}\cos I_{13}
-            + \mathcal{O}\p{\cos I_{23}}.
+            + \mathcal{O}\p{\cos I_{23}^2}.
 \end{align}
 Here, we have simply assmued that $\uv{l}_2$ is approximately aligned with
-$\uv{l}_3$; by the law of cosines, the deviation scales with $\cos I_{23} \sim
-2^\circ$ for compact architectures excepting the innermost planet.
+$\uv{l}_3$; by the law of cosines, the deviation scales with $\cos I_{23}^2 \sim
+2^\circ$ for compact architectures excepting the innermost planet. We have
+neglected the angular momentum ratio factor for simplicity.
 
-We want to know which of $\Omega_{32}$ and $\Omega_{32, 1}$ are larger. To
-calculate scalings, let's approximate $I_{12} \approx I_{13} \approx I_{23}
-\approx 0$. If we assume the semimajor axis ratios are constant, $a_3 / a_2 =
-a_2 / a_1 = \alpha$, then
+We want to know which of $\Omega_{32}$ and $\Omega_{32, 1}$ is responsible for
+the largest precession frequency. To calculate scalings, let's approximate
+$I_{12} \approx I_{13} \approx I_{23} \approx 0$. If we assume the semimajor
+axis ratios are constant, $a_3 / a_2 = a_2 / a_1 = \alpha$, then
 \begin{align}
@@
 Thus, in general, we find that the $\Omega_{32, 1}$ precession frequency should
-generally be larger or comparable except for very small $a_{j + 1} / a_j$.
+generally be larger or comparable except for $a_{j + 1} / a_j$ quite close to
+unity.
 
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{4_usp_rings/scan_alpha5.png}
+    \includegraphics[width=0.7\columnwidth]{../initial/4_usp_rings/scan_alpha5.png}
     \caption{Same as Fig.~\ref{fig:scan} but for equal masses $m_i =
@@
 \begin{align}
-    \alpha &= \frac{3k_q}{2k}\frac{M_\star}{m}
+    \alpha &= \frac{3k_{\rm q}}{2k}\frac{M_\star}{m}
         \p{\frac{R}{a}}^3 \Omega_{\rm s},\\
         &\approx 0.86\;\mathrm{yr^{-1}}
-            \frac{k_q}{k}
+            \frac{k_{\rm q}}{k}
             \p{\frac{M_{\star}}{M_{\odot}}}^{3/2}
@@
 Using Millholland's formula, we have yet another small correction. They use
-$3k_q = 0.4$ and $k = 0.35$, so their $\alpha$ is depressed by a factor of
+$3k_{\rm q} = 0.4$ and $k = 0.35$, so their $\alpha$ is depressed by a factor of
 $8/21$, leaving $\eta_{\rm sync} \sim 0.4$ for extremal values (note that $a_2 /
@@
             \p{\frac{a/a_{\rm p}}{1/1.2}}^3
-            \p{\frac{a}{0.035\;\mathrm{AU}}}^3.
+            \p{\frac{a}{0.035\;\mathrm{AU}}}^3.\label{eq:etasync_2p}
 \end{align}
@@
 
-\subsection{Towards $\eta_{\rm sync}$ for 3p? No}
+\subsection{Three Planets \& Comparison to Millholland}
 
@@
 is small by about $15\%$, the third planet only contributes $40\%$ of the
-precession rate of the inner. This is unsurprising, and is not enough to lift
-$\eta_{\rm sync}$ to values of order unity; it raises it only to $\sim 0.2
-k/k_{\rm q}$, which is in line with our calculation above. So everything seems
-consistent!
+precession rate of the inner. This is unsurprising.
+
+To compare to Millholland, we not that this raises $\eta_{\rm sync}$ by about
+$1.2\times$ from Eq.~\eqref{eq:etasync_2p} or to $\sim 0.2 k/k_{\rm q}$.
+Finally, they have one further amendment: they use the mass radius relation:
+\begin{align}
+    \frac{R}{R_{\oplus}} = 1.015\p{\frac{m}{M_{\oplus}}}^{1/3.7}.
+\end{align}
+Thus, for $m = 8M_{\oplus}$, as they use, $\rho = 1.4\rho_{\oplus}$. Thus, they
+finally would have obtained $\eta_{\rm sync} = 0.59$. For reference, $\eta_{\rm
+c} = 0.74$ for $I = 5^\circ$ and $\eta_{\rm c} = 0.54$ for $I = 20^\circ$, so we
+are quite close to reproducing their result to within a factor of 2. However,
+many generous assumptions are required.
+
+\clearpage
+
+\section{Effect of Stellar $J_2$}
+
+The orbit precession induced by a stellar $J_2$ is given by Anderson \& Lai
+2018:
+\begin{align}
+    \abs{\rd{\uv{l}}{t}}_{\star} &= \frac{S_\star}{L}
+            \frac{3 k_{\rm q\star}}{2k_\star}
+            \p{\frac{m}{M_\star}}
+            \p{\frac{R_\star}{a}}^3
+            \Omega_{\star} \cos I_\star,\\
+        &= \frac{3k_{\rm q \star}}{2} \p{\frac{R_\star}{a}}^5
+            \frac{\Omega_{\rm \star}^2}{n} \cos I_\star.
+            \label{eq:lai_starprec}
+\end{align}
+Note that $k_{\rm q\star} \simeq 0.01$ according to Lai, Anderson \& Pu 2018
+(Mecheri 2004). What is the ratio of this precession rate to the
+perturber-induced rate?
+\begin{align}
+    \frac{\p{\rdil{\uv{l}}{t}}_\star}{\p{\rdil{\uv{l}}{t}}_{\rm p}}
+        &= \frac{3k_{\rm q\star}}{2}\p{\frac{R_\star}{a}}^5
+            \frac{\Omega_\star^2}{n} \frac{4 M_\star}{3m_{\rm p}}
+                \p{\frac{a_{\rm p}}{a}}^3 \frac{1}{n}
+                \frac{\cos I_\star}{\cos I},\\
+        &= 2k_{\rm q \star} \frac{R_\star^5 a_{\rm p}^3}{a^8}
+            \frac{M_\star}{m_{\rm p}}\frac{\Omega_{\rm \star}^2}{n^2}
+            \frac{\cos I_\star}{\cos I},\\
+% 0.02 * (Rsun / (0.035 AU))^5 * (1.2)^3 * Msun / (10 Mearth)
+% = 0.04759
+        &= 0.048
+            \p{\frac{k_{\rm q \star}}{0.01}}
+            \p{\frac{R_\star}{R_{\odot}}}^5
+            \p{\frac{a}{0.035\;\mathrm{AU}}}^{-5}
+            \p{\frac{a_{\rm p} / a}{1.2}}^3
+            \p{\frac{M_\star}{M_{\odot}}}
+            \p{\frac{m_{\rm p}}{10 M_{\oplus}}}^{-1}
+            \p{\frac{\Omega_{\star}}{n}}^2
+            \frac{\cos I_\star}{\cos I}.
+\end{align}
+Since the star is probably rotating slightly faster than $n$ (by maybe a factor
+$3$--$6\times$), the $J_2$ of the star is responsible for maintaining the tidal
+decay rate at smaller separations.
+
+Let's repeat the $a_{\rm break}$ calculation using the $J_2$ precession laws.
+Let's assume $S \gg L$ for now, for illustrative purposes:
+\begin{align}
+    \frac{1}{t_{\rm s, c}} &= \abs{g}\sin I_\star \sqrt{\frac{\eta_{\rm sync}
+        \cos I_\star}{2}},\\
+    \abs{g}_\star &= \frac{3k_{\rm q \star}}{2} \p{\frac{R_\star}{a}}^5
+            \frac{\Omega_{\rm \star}^2}{n} \cos I_\star,\\
+    \frac{1}{t_{\rm s}} &= \frac{1}{4k}\frac{3k_2}{Q} \frac{M_{\star}}{m}
+        \p{\frac{R}{a}}^3 n,\\
+    \eta_{\rm sync} &= \s{\frac{3k_{\rm q \star}}{2} \p{\frac{R_\star}{a}}^5
+            \frac{\Omega_{\rm \star}^2}{n} \cos I_\star}
+        \Bigg/ \s{\frac{3k_{\rm q}}{2k} \frac{M_\star}{m}\p{\frac{R}{a}}^3 n},\\
+        &= \frac{k k_{\rm q \star}}{k_{\rm q}}
+            \frac{m}{M_\star}
+            \frac{R_\star^5}{a^2R^3}
+            \p{\frac{\Omega_{\star}}{n}}^2
+            \cos I_\star,\\
+% unused, but:
+% 0.35 * 0.01 * 3 / 0.4 * Mearth / Msun * Rsun^5 / ((0.035 AU)^2 * Rearth^3)
+% = 0.001809
+    \frac{1}{4k}\frac{3k_2}{Q} \frac{M_\star}{m} \p{\frac{R}{a_{\rm break}}}^3
+        &= \frac{3k_{\rm q \star}}{2} \p{\frac{R_\star}{a_{\rm break}}}^5
+            \frac{\Omega_{\rm \star}^2}{n} \cos I_\star
+            \sin I_\star
+            \sqrt{\frac{k k_{\rm q \star}}{2k_{\rm q}}
+            \frac{m}{M_\star}
+            \frac{R_\star^5}{a_{\rm break}^2R^3}
+            \p{\frac{\Omega_{\star}}{n}}^2
+            \cos^2 I_\star},\\
+    a_{\rm break}^{-3/2}
+        &= \frac{Q}{3k_2}\frac{1}{4k^{3/2}}
+            \frac{k_{\rm q\star}^{3/2}}{2\sqrt{2k_{\rm q}}}
+            \p{\frac{m}{M_\star}}^{3/2}
+            \frac{R_\star^{3}}{R^{9/2}}
+            \hat{\Omega}_{\star}^3
+            \cos^2 I_\star \sin I_\star,\\
+% (2/3 * 1e3 * 1 / (4 * 0.35^(3/2)) * 0.001 / (2 * (2 * 0.4/3)^(1/2)) * (Mearth / Msun)^(3/2) * Rsun^3 / Rearth^(9/2) * 1/27)^(-2/3) / AU
+% 0.012648
+    a_{\rm break} &= 0.013 \;\mathrm{AU}
+            \p{\frac{2k_2/Q}{10^{-3}}}^{2/3}
+            \p{\frac{M_\star}{M_{\odot}}}
+            \p{\frac{\rho}{\rho_{\oplus}}}^{-1}
+            \p{\frac{R_\star}{R_\odot}}^{-2}
+            \p{\frac{\hat{\Omega}_{\star}}{1/3}}^{-2}
+            \cos^2 I_\star \sin I_\star.
+\end{align}
+I've used $k = 0.35$, $k_{\rm q} = 0.4/3$, and $k_{\rm q\star} = 0.01$ in the
+above. This corresponds to a $0.52\;\mathrm{day}$ orbit and has an even shorter
+$a$ than in Millholland.
+
+% \subsection{Millholland Version}
+
+% The orbit precession induced by a stellar $J_2$ modifies $\tilde{\bm{B}}$ in
+% Eq.~\eqref{eq:2p_LL} as:
+% \begin{align}
+%     B_{jj} &= -n_j\s{
+%         \frac{3}{2}J_2 \p{\frac{R_\star}{a_j}}^2
+%         + \mathcal{O}\p{\frac{R_\star}{a_j}}^4
+%         + \frac{1}{4} \sum\limits_{k \neq j}B_{jk}},\\
+%     B_{jk} &=
+%         -\frac{3 m_k}{4 M_\star}\p{\frac{a_j}{a_k}}^2
+%             \min\p{\frac{a_j}{a_k}, 1}
+%             n_j f\p{\frac{a_j}{a_k}}.
+% \end{align}
+% Thus, the relative strength of $g_\star / g_{\rm p}$, for the 2p case, can be
+% expressed as:
+% \begin{align}
+%     \frac{g_\star}{g_{\rm p}}
+%         &= 2J_2\p{\frac{R_\star}{a}}^2 \frac{M_\star}{m_{\rm p}}
+%             \p{\frac{a_{\rm p}}{a}}^3 \frac{1}{f(\alpha)},\\
+% % 2 * 1e-3 * (Rsun / (0.035 AU))^2 * (Msun / (10 Mearth)) * (1.2)^3 / 9.7
+% % 0.209369
+%         &\approx 0.21
+%             \p{\frac{R_\star}{R_{\odot}}}^2
+%             \p{\frac{a}{0.035\;\mathrm{AU}}}^{-2}
+%             \p{\frac{M_{\star}}{M_{\odot}}}
+%             \p{\frac{m_{\rm p}}{10M_{\oplus}}}^{-1}
+%             \p{\frac{a_{\rm p} / a}{1.2}}^3
+%             \frac{1}{f(\alpha)}.
+% \end{align}
+% We see that the stellar precession can be stronger for some parameters but is
+% slightly weaker for fiducial parameters. A useful formula for $J_2$ is
+% (Millholland, Spalding \& Batygin 2016):
+% \begin{align}
+%     J_2 \approx \frac{1}{3}k_{2\star}\frac{\omega_\star^2}{GM_\star/R_\star^3}
+%         \approx 10^{-3}\p{\frac{k_{2\star}}{0.2}}
+%             \p{\frac{P_\star}{\mathrm{day}}}^{-2}
+%             \p{\frac{R_\star}{R_\odot}}^3
+%             \p{\frac{M_\star}{M_{\odot}}}^{-1}.
+% \end{align}
+% This is in agreement with the Lai result.
+
+\section{Analytic tCE2 Probability}
+
+See Figs.~14--15 of the draft: I have added simulations for $\eta_{\rm sync} =
+0.1, 0.03, 0.01$ (except for $I = 20^\circ$ and $\eta_{\rm sync} = 0.01$, which
+is still running). The probability can be predicted analytically, the red line;
+see Appendix~B of the draft.
+
+\section{Evolutionary Trajectories}
+
+For each of the three $\eta_{\rm sync}$ values in Fig.~8 of the draft, I have
+run 6 simulations using identical initial conditions, and their evolution in
+$\theta, \Omega_{\rm s}$ space is shown in the draft. I've also taken a first
+stab at plotting these, shown below:
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_0.png}
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_1.png}
+    \caption{$\eta_{\rm c} = 0.06$, zone I and zone II ICs.}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_2.png}
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_3.png}
+    \caption{$\eta_{\rm c} = 0.06$, two cases of zone III ICs.}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_4.png}
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_5.png}
+    \caption{$\eta_{\rm c} = 0.06$, small spin ICs.}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_50_0.png}
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_50_1.png}
+    \caption{$\eta_{\rm c} = 0.50$, zone I and zone II ICs.}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_50_2.png}
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_50_3.png}
+    \caption{$\eta_{\rm c} = 0.50$, two cases of zone III ICs.}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_50_4.png}
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_50_5.png}
+    \caption{$\eta_{\rm c} = 0.50$, small spin ICs.}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_70_0.png}
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_70_1.png}
+    \caption{$\eta_{\rm c} = 0.70$, zone I and zone II ICs.}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_70_2.png}
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_70_3.png}
+    \caption{$\eta_{\rm c} = 0.70$, two cases of zone III ICs.}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_70_4.png}
+    \includegraphics[width=0.49\columnwidth]{../initial/1_weaktide/6equils_sims/0_70_5.png}
+    \caption{$\eta_{\rm c} = 0.70$, small spin ICs.}
+\end{figure}
 

### 2021-05-17 writeups/Su_weak_tides.tex
05/18 meeting

@@
     \rd{}{t}\begin{bmatrix}
-        \theta\\ \phi
+        \Delta \theta\\ \Delta \phi
     \end{bmatrix} &= \begin{bmatrix}
@@
     = 0$ are the tidal Cassini Equilibria (tCE), which are circled and labeled.
+    \textcolor{red}{The various colored lines indicate sample evolutionary
+    trajectories that are started at the same $\theta$ and $\Omega_{\rm s}$
+    across all three panels, with different outcomes upon separatrix encounter.}
     }\label{fig:6equils}
@@
 \end{equation}
+\textcolor{red}{Note that this result differs in form from that given in
+\citet{fabrycky_otides}. Our formulation is more appropriate and transparent
+when the orbital precession of the inner planet is dominated by the outer planet
+rather than the star.}
 
@@
     reaching tCE2 for each integration using
-    Eq.~\eqref{eq:def_pc_weaktide}.}\label{fig:pc_fits_0_06}
+    Eq.~\eqref{eq:def_pc_weaktide}.
+    \textcolor{red}{The green dashed line in the top panel shows the result of
+    using the analytical expression (Eq.~\ref{eq:app_deltaK}) for $\Delta
+    K_{\pm}$, and the bottom panel shows the distribution of values of
+    $\eta_{\rm cross}$, the value of $\eta$ when a trajectory starting at
+    $\theta_{\rm i}$ encounters the separatrix. }}\label{fig:pc_fits_0_06}
 \end{figure}

### 2021-05-17 initial/1_weaktide/5pop.py

@@ -311,7 +311,7 @@ def plot_eq_dists(I, s_c, s0, IC_eq1, IC_eq2):
 
         # try anal prob
         p_caps_al = get_anal_caps(I, s_c, cross_dat, mu_vals)
-        s_crosses = np.max(cross_dat[:, :, 0], axis=1)
+        s_crosses = cross_dat[:, :, 0]
         tot_probs_al = np.sum(p_caps_al / n_phi, axis=1)
 
         bin_cents = (bins[ :-1] + bins[1: ]) / 2
@@ -324,9 +324,12 @@ def plot_eq_dists(I, s_c, s0, IC_eq1, IC_eq2):
 
         if s_c < 0.1:
             ax1.plot(mu_vals, tot_probs_al, 'g--', alpha=0.8, lw=1.0)
-            cross_idx = np.where(s_crosses > 0)[0]
-            ax2.plot(mu_vals[cross_idx], s_c / s_crosses[cross_idx],
-                     'b', alpha=0.8, lw=2.5)
+            for mu, crosses in zip(mu_vals, s_crosses):
+                cross_idx = np.where(crosses > 0)[0]
+                all_crosses = crosses[cross_idx]
+                ax2.plot(np.full_like(crosses[cross_idx], mu),
+                         s_c / all_crosses,
+                         'bo', alpha=0.8, markersize=0.8)
 
             ax2.set_ylabel(r'$\eta_{\rm cross}$')
             ax2.set_xlabel(r'$\cos \theta_{\rm i}$')
@@ -437,7 +440,7 @@ def plot_cum_probs(I, s_c_vals, s0, counts):
 def run():
     s_c_vals_20 = [
         # 0.7,
-        0.2,
+        # 0.2,
         0.06,
         # 2.0,
         # 1.2,
@@ -445,7 +448,7 @@ def run():
         # 0.65,
         # 0.6,
         # 0.55,
-        0.5,
+        # 0.5,
         # 0.45,
         # 0.4,
         # 0.35,
@@ -457,8 +460,8 @@ def run():
     ]
     s_c_vals_5 = [
         # 0.7,
-        0.2,
-        0.06,
+        # 0.2,
+        # 0.06,
         # 2.0,
         # 1.2,
         # 1.0,
@@ -468,7 +471,7 @@ def run():
         # 0.65,
         # 0.6,
         # 0.55,
-        0.5,
+        # 0.5,
         # 0.45,
         # 0.4,
[…]

### 2021-05-25 writeups/Su_weak_tides.tex
check in new paper draft

--- 2021-05-10 writeups/Su_weak_tides.tex
@@
     \newcommand*{\bm}[1]{\mathbf{#1}}
-    \newcommand*{\uv}[1]{\hat{\mathbf{#1}}}
+    \newcommand*{\uv}[1]{\hat{\boldsymbol{\mathbf{#1}}}}
     \newcommand*{\md}[0]{\mathrm{d}}
@@
 
-In Section~\ref{s:theory}, we briefly review Colombo's Top. In
-Section~\ref{s:toy_model}, we investigate the effect of adding a simple
-alignment torque to Colombo's Top. The resulting dynamics are illustrative of
-the new behavior that emerges due to tidal dissipation. In
+Our paper is organized as follows. In Section~\ref{s:theory}, we briefly review
+Colombo's Top. In Section~\ref{s:toy_model}, we investigate the effect of adding
+a simple alignment torque to Colombo's Top. The resulting dynamics are
+illustrative of the new behavior that emerges due to tidal dissipation. In
 Section~\ref{s:full_tide_prob}, we solve for the dynamics of the system
@@
 The values of $\cos \theta$ corresponding to the lower and upper bounds on this
-range are shown as the black and red dots on the left of Fig.~\ref{fig:6equils}
-respectively.
+range are shown as the black and red dots on the left of
+Fig.~\ref{fig:toy_hop_manifolds} respectively.
 
@@
     \item If $H_{\rm f} > H_{\rm sep}$, then the trajectory enters the
-        separatrix, following the red shaded region in Fig.~\ref{fig:6equils},
-        and executes a zone III $\to$ II transition.
+        separatrix, following the red shaded region in
+        Fig.~\ref{fig:toy_hop_manifolds}, and executes a zone III $\to$ II
+        transition.
 
     \item If $H_{\rm f} < H_{\rm sep}$, then the trajectory exits the separatrix
-        above CS4, following the yellow shaded region in Fig.~\ref{fig:6equils}
-        and executes a zone III $\to$ I transition.
+        above CS4, following the yellow shaded region in
+        Fig.~\ref{fig:toy_hop_manifolds} and executes a zone III $\to$ I
+        transition.
 \end{itemize}
@@
 for which $H$ is equal to $H_{\rm sep} - \Delta H_{-} - \Delta H_+$ is shown as
-the blue dot on the left of Fig.~\ref{fig:6equils}. Finally, if the alignment
-torque is weak, then $\Delta H_- \sim \mathcal{O}\p{t_{\rm al}^{-1}}$ is small
-compared to any variation in the value of $H$ (e.g.\ when changing $\phi_0$ or
-$\theta_0$ by a small amount), and $H_{\rm i}$ can be effectively considered as
-randomly chosen from a uniform distribution over $\s{H_{\rm sep} - \Delta H_-,
-H_{\rm sep}}$. As a consequence we obtain the probability of a III $\to$ II
-transition:
+the blue dot on the left of Fig.~\ref{fig:toy_hop_manifolds}. Finally, if the
+alignment torque is weak, then $\Delta H_- \sim \mathcal{O}\p{t_{\rm al}^{-1}}$
+is small compared to any variation in the value of $H$ (e.g.\ when changing
+$\phi_0$ or $\theta_0$ by a small amount), and $H_{\rm i}$ can be effectively
+considered as randomly chosen from a uniform distribution over $\s{H_{\rm sep} -
+\Delta H_-, H_{\rm sep}}$. As a consequence we obtain the probability of a III
+$\to$ II transition:
 \begin{equation}
@@
 between the evolution of the unperturbed Hamiltonian and distances between
-curves in phase space (as seen in Fig.~\ref{fig:6equils}) is provided by
+curves in phase space (as seen in Fig.~\ref{fig:toy_hop_manifolds}) is provided by
 Melnikov's Method.
@@
 \begin{equation}
-    \frac{1}{t_{\rm s}} \equiv \frac{L}{2S} \frac{\Omega_{\rm
-        s}}{2n}\frac{3k_2}{Q}\p{\frac{M_\star}{m}}\p{\frac{R}{a}}^5 n.
-\end{equation}
-Here, $L = ma^2n$ and $S = kmR^2 \Omega_{\rm s}$ are the orbital and spin
-angular momenta of the inner planet, respectively. We neglect orbital evolution
-in this section since the time scale is longer than $t_{\rm s}$ by a factor of
-$\sim L / S \gg 1$, and so $t_{\rm s}$ is a constant. We will continue mostly
-consider the case where tidal dissipation is slow, i.e.\ $\abs{g}t_{\rm s} \gg
-1$. The full equations of motion including weak tidal friction can be written in
-component form as
+    \frac{1}{t_{\rm s}} \equiv \frac{1}{4k}
+        \frac{3k_2}{Q}\p{\frac{M_\star}{m}}\p{\frac{R}{a}}^3 n.
+\end{equation}
+In this section, we neglect orbital evolution in this section since the time
+scale is longer than $t_{\rm s}$ by a factor of $\sim L / S \gg 1$, and so
+$t_{\rm s}$ is a constant. We will continue mostly consider the case where tidal
+dissipation is slow, i.e.\ $\abs{g}t_{\rm s} \gg 1$. The full equations of
+motion including weak tidal friction can be written in component form as
 \begin{align}
@@
 tidal dissipation (i.e.\ satisfying $\rdil{\uv{s}}{t} = 0$).
-The panels of Fig.~\ref{fig:6equils} describes the evolution of
+Figure~\ref{fig:6equilssingle} describes the evolution of
 Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) qualitatively in the coordinates
-$(\Omega_{\rm s}, \theta)$, along with the locations of CS1 and CS2, for a few
-different system parameters. The circled points in the panels of
-Fig.~\ref{fig:6equils} satisfy the criteria to be long-term equilibria, and we
-call them \emph{tidal Cassini Equilibria} (tCE). We number tCE1 and tCE2 the tCE
-that are in CSs 1 and 2 respectively. The obliquities of the tCE depend on the
-system architecture, which can be quantified using the parameter
+$(\Omega_{\rm s}, \theta)$, along with the locations of CS1 and CS2. The circled
+points in the panels of Fig.~\ref{fig:6equils} satisfy the criteria to be
+long-term equilibria, and we call them \emph{tidal Cassini Equilibria} (tCE). We
+number tCE1 and tCE2 the tCE that are in CSs 1 and 2 respectively. The
+obliquities of the tCE depend on the system architecture, which can be
+quantified using the parameter
 \begin{align}
@@
 \end{align}
+In Fig.~\ref{fig:6equilssingle}, $\eta_{\rm sync} = 0.06$; the two panels of
+Fig.~\ref{fig:6equils} illustrate the change to the tCE when $\eta_{\rm sync} =
+0.5$ and $0.7$ respectively.
+
 The tCE obliquity as a function of $\eta_{\rm sync}$ are shown for $I =
@@
 agreement is observed.
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{../initial/1_weaktide/6equilssingle.png}
+    \caption{Schematic depiction of the effect of tidal friction on the planet's
+    spin for $I = 20^\circ$, corresponding to $\eta_{\rm c} \approx 0.574$
+    (Eq.~\ref{eq:def_etac}), and $\eta_{\rm sync} = 0.06$. The black and blue
+    lines denote where the tidal $\dot{\Omega}_{\rm s}$ and $\dot{\theta}$
+    change signs (Eqs.~\ref{eq:weaktide_dqzero}--\ref{eq:weaktide_dWszero}). The
+    orange and green lines give the CS1 and CS2 obliquities respectively, which
+    are the two CSs that are stable under the effect of tidal dissipation. Note
+    that when $\dot{\theta}_{\rm tide} > 0$, CS1 becomes unstable, denoted by
+    the dashed orange line. The points that are both CSs and satisfy
+    $\dot{\Omega}_{\rm s} = 0$ are the tidal Cassini Equilibria (tCE), which are
+    circled and labeled. The various colored crosses and their associated
+    colored lines represent a few characteristic examples of the evolution of
+    Colombo's Top under weak tidal friction (for illustrative purposes, we have
+    used $\abs{g}t_{\rm s} = 10^2$). The phase space evolution of the two
+    thicker evolutionary trajectories (cyan and pink; those beginning at
+    $\theta_{\rm i} = 120^\circ$) are shown in
+    Figs.~\ref{fig:trajs1}--\ref{fig:trajs2}.
+    }\label{fig:6equilssingle}
+\end{figure*}
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils.png}
-    \caption{Schematic depiction of the effect of tidal friction on the planet's
-    spin for $I = 20^\circ$ and three values of $\eta_{\rm sync}$ (labeled). The
-    black and blue lines denote where the tidal $\dot{\Omega}_{\rm s}$ and
-    $\dot{\theta}$ change signs
-    (Eqs.~\ref{eq:weaktide_dqzero}--\ref{eq:weaktide_dWszero}). The orange and
-    green lines give the CS1 and CS2 obliquities respectively, which are the two
-    CSs that are stable under the effect of tidal dissipation. Note that when
-    $\dot{\theta}_{\rm tide} > 0$, CS1 becomes unstable, denoted by the dashed
-    orange line. The points that are both CSs and satisfy $\dot{\Omega}_{\rm s}
-    = 0$ are the tidal Cassini Equilibria (tCE), which are circled and labeled.
-    }\label{fig:6equils}
+    \caption{Same as Fig.~\ref{fig:6equilssingle} but for $\eta_{\rm sync} =
+    0.5$ and $\eta_{\rm sync} = 0.7$ in the two panels (labeled). Note in the
+    bottom panel that $\eta_{\rm sync} = 0.7 > \eta_{\rm c}$ and tCE1 does not
+    exist. In both panels, the light-colored crosses and lines correspond to
+    evolutionary trajectories using the same initial conditions as those shown
+    in Fig.~\ref{fig:6equilssingle}. The phase space evolution of the thick
+    purple trajectory in the bottom panel (starting at $\theta_{\rm i} \approx
+    10^\circ$) is shown in Fig.~\ref{fig:trajs3}. }\label{fig:6equils}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_2.png}
+    \caption{Phase space evolution of the trajectory in
+    Fig.~\ref{fig:6equilssingle} colored in pink, for which $\eta_{\rm sync} =
+    0.06$ and $I = 20^\circ$. In the
+    left-most panel, the trajectory's evolution in $\p{\Omega_{\rm s}, \theta}$
+    coordinates along with the curves indicating CS1, 2, and $\dot{\Omega}_{\rm
+    s} = 0$ are re-displayed from Fig.~\ref{fig:6equilssingle}. The vertical
+    dashed lines denote the values of $\Omega_{\rm s}$ for which the phase space
+    evolution of the system is displayed in the right four panels. In each of
+    these right four panels, the trajectory's evolution for a single
+    circulation/libration cycle is displayed in $\p{\cos \theta, \phi}$ phase
+    space for the labeled value of $\Omega_{\rm s}$. The system encounters the
+    separatrix, undergoes a III $\to$ I transition, and converges to tCE1.
+    }\label{fig:trajs1}
+\end{figure}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_3.png}
+    \caption{Same as Fig.~\ref{fig:trajs1} but for the trajectory in
+    Fig.~\ref{fig:6equilssingle} colored in cyan, for which $\eta_{\rm sync} =
+    0.06$ and $I = 20^\circ$. The system encounters the
+    separatrix, undergoes a III $\to$ II transition, and converges to tCE2. Note
+    that the initial condition of this system and that displayed in
+    Fig.~\ref{fig:trajs1} have the same initial $\theta_{\rm i}$ and
+    $\Omega_{\rm s, i}$ and only different precessional phases $\phi_{\rm i}$.
+    }\label{fig:trajs2}
+\end{figure}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils_sims/0_70_0.png}
+    \caption{Same as Fig.~\ref{fig:trajs1} but for the purple trajectory
+    shown in the bottom panel of Fig.~\ref{fig:6equils}, for which $\eta_{\rm
+    sync} = 0.7$ and $I = 20^\circ$. Here, the system
+    evolves along CS1 until the separatrix disappears, upon which it experiences
+    large obliquity variations that damp due to tidal dissipation. The system
+    finally converges to tCE2, the only tCE that exists for this value of
+    $\eta_{\rm sync}$ (see bottom panel of Fig.~\ref{fig:6equils}).}\label{fig:trajs3}
 \end{figure}
@@
 slightly smaller than $\eta_{\rm c}$, as the planet's spin is slightly
-subsynchronous at tCE1 when $\eta \approx \eta_{\rm c}$, see the middle panel of
+subsynchronous at tCE1 when $\eta \approx \eta_{\rm c}$, see the top panel of
 Fig.~\ref{fig:6equils}.}. Secondly, tCE2 may not be stable if the tidal phase
@@
 \end{equation}
+Note that this result differs in form from that given in
+\citet{fabrycky_otides}, which assume that the orbital precession of $\uv{l}$ is
+driven by the central star. Our expression is simpler and is applicable to
+systems where the orbital precession of the inner planet is dominated by an
+exterior planet.
 
@@
 With this result, we can now consider the final fate of the inner planet's spin.
-We assume that the planet is initially rotating supersynchronously and adopt the
-fiducial initial spin frequency $\Omega_{\rm s, i} = 10n$. The final results are
-not sensitive to the specific initial spin as long as $\Omega_{\rm s, i} \gg n$.
-Then, for a given initial $\theta_0$ and $\phi_0$, the final outcome (either
-tCE1 and tCE2) of the system can be calculated by direct integration of
-Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}). In
-Fig.~\ref{fig:Hhists_0_06}, we show the final outcome for many randomly chosen
-$\theta_0$ and $\phi_0$ for $\eta_{\rm sync} = 0.06$ and $I = 20^\circ$. We see
-that tCE1 is generally reached for spins initially in zone I, tCE2 is generally
-reached for spins initially in zone II, and a probabilistic outcome is observed
-for spins initially in zone III, similarly to Fig.~\ref{fig:toy_phop}.
-Figures~\ref{fig:Hhists_0_20} and~\ref{fig:Hhists_0_70} show the same results
+We begin by qualitatively examining the example trajectories shown in
+Figs.~\ref{fig:6equilssingle}, for which we have integrated
+Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}). We discuss
+each of the six trajectories in turn:
+\begin{itemize}
+    \item The trajectory with initial conditions $\Omega_{\rm s, i} = 2.5n$ and
+        $\theta_{\rm i} = 10^\circ$ (purple) has an initially prograde spin
+        (i.e.\ in zone I, see FIg.~\ref{fig:1contours}) and directly evolves to
+        tCE1 as the obliquity damps to zero.
+
+    \item The trajectory with initial conditions $\Omega_{\rm s, i} = 2.5n$ and
+        $\theta_{\rm i} = 90^\circ$ (red) has an initial condition inside the
+        resonance (zone II) and evolves to tCE2. Note that the obliquity is
+        trapped in a high value due to the stability of CS2 under weak tidal
+        friction, as discussed in Section~\ref{ss:weaktide}.
+
+    \item We have chosen two trajectories, both with initial conditions
+        $\Omega_{\rm s, i} = 2.5n$ and $\theta_{\rm i} = 120^\circ$ but with
+        different initial precessional phases $\phi_{\rm i}$; we first discuss
+        the pink trajectory. This trajectory originates in zone III, evolves
+        towards the separatrix as tidal friction damps the obliquity, and
+        crosses the resonance without being captured, upon which the obliquity
+        continues to damp until the system converges to tCE1. The detailed phase
+        space evolution of this trajectory is shown in Fig.~\ref{fig:trajs1},
+        where the outcome of the separatrix encounter is very visible.
+
+    \item The other trajectory with initial conditions $\Omega_{\rm s, i} = 2.5n$
+        and $\theta_{\rm i} = 120^\circ$ (light blue) only differs from the pink
+        trajectory in its value of $\phi_{\rm i}$. Nevertheless, this trajectory
+        originates in zone III, encounters the separatrix and is captured into
+        the resonance (zone II), upon which tidal friction drives the system
+        towards tCE2. The detailed phase space evolution of this trajectory is
+        shown in Fig.~\ref{fig:trajs2}, where the resonance capture is
+        displayed.
+
+    \item For completeness, we also examine some trajectories for initially
+        subsynchronous spin rates. The trajectory with initial conditions
+        $\Omega_{\rm s, i} = 0.1n$ and $\theta_{\rm i} = 35^\circ$ (blue) has its
+        obliquity rapidly damped to zero by tidal friction as it spins up to
+        spin-orbit synchronization, eventually converging to tCE1.
+
+    \item The trajectory with initial conditions $\Omega_{\rm s, i} = 0.1n$ and
+        $\theta_{\rm i} = 100^\circ$ (teal) also has its obliquity rapidly
+        damped to zero as it approaches spin-orbit synchronization and tCE1.
+        However, we remark that this initial condition converges to tCE2 when a
+        tidal dissipation rate of $\abs{g}t_{\rm s} = 10^3$ is used.
+\end{itemize}
+For each of these six initial conditions, we also display their evolutionary
+trajectories for $\eta_{\rm sync} = 0.5$ and $\eta_{\rm sync} = 0.7$ in the two
+panels of Fig.~\ref{fig:6equils}. Of particular interest is the purple initial
+condition ($\Omega_{\rm s, i} = 2.5n$ and $\theta_{\rm i} = 10^\circ$) when
+$\eta_{\rm sync} = 0.7$. Figure~\ref{fig:trajs3} shows the detailed phase space
+evolution of this system, where it can be seen that the system initially evolves
+along the stable CS1, but is ejected when $\Omega_{\rm s}$ is sufficiently small
+that CS1 ceases to exist, upon which large obliquity variations eventually lead
+to convergence to tCE2, the only tCE that exists.
+
+It can be seen that the dynamics are complex and can vary greatly depending on
+the parameters used. For tractability, we restrict our attention to initial
+conditions satisfying $\Omega_{\rm s, i} \gg n$, and we adopt the fiducial value
+$\Omega_{\rm s, i} = 10n$. Then, for many initial $\theta_0$ and $\phi_0$, we
+can perform the same integration as above and verify which tCE a given initial
+condition evolves into. In Fig.~\ref{fig:Hhists_0_06}, we show the final outcome
+for many randomly chosen $\theta_0$ and $\phi_0$ for $\eta_{\rm sync} = 0.06$
+and $I = 20^\circ$. We see that the behavior seen in the example trajectories in
+Fig.~\ref{fig:6equilssingle} are general: tCE1 is generally reached for spins
+initially in zone I (like the purple trajectory in
+Fig.~\ref{fig:6equilssingle}), tCE2 is generally reached for spins initially in
+zone II (like the red trajectory in Fig.~\ref{fig:6equilssingle}), and a
+probabilistic outcome is observed for spins initially in zone III (like the
+light blue and pink trajectories in Fig.~\ref{fig:6equilssingle}).
+Figures~\ref{fig:Hhists_0_20} and~\ref{fig:Hhists_0_50} show the same results
 but for $\eta_{\rm sync} = 0.2$ and $\eta_{\rm sync} = 0.5$. As $\eta_{\rm
 sync}$ is increased, more initial conditions reach tCE2. This is both because
-there are more systems initially in zone II and because systems initially
-in zone III have a higher probability of executing a III $\to$ II transition
-upon separatrix encounter. Note also that in Fig.~\ref{fig:Hhists_0_70}, even
-initial conditions in zone I are able to reach tCE2; we comment on the origin of
-this behavior in the next section.
+there are more systems initially in zone II and because systems initially in
+zone III have a higher probability of executing a III $\to$ II transition upon
+separatrix encounter. Note also that in Fig.~\ref{fig:Hhists_0_50}, even initial
+conditions in zone I are able to reach tCE2; we comment on the origin of this
+behavior in the next section.
 \begin{figure}
@@
     $\theta_{\rm i}$ evolves towards, averaged over $\phi_{\rm
-    i}$.}\label{fig:Hhists_0_06}
+    i}$.
+    \textcolor{red}{NB\@: the excess of tCE2 initial conditions at $\cos
+    \theta_{\rm i} \approx -1$ is likely an artifact of loss of numerical
+    precision, I am working on fixing this.}
+    }\label{fig:Hhists_0_06}
 \end{figure}
@@
     \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\eta_{\rm sync} =
-    0.2$.}\label{fig:Hhists_0_20}
+    0.2$.
+    \textcolor{red}{NB\@: the excess of tCE2 initial conditions at $\cos
+    \theta_{\rm i} \approx -1$ is likely an artifact of loss of numerical
+    precision, I am working on fixing this.}
+    }\label{fig:Hhists_0_20}
 \end{figure}
@@
     0.5$. Note that even points above the separatrix can evolve towards tCE2
-    here.}\label{fig:Hhists_0_70}
+    here.}\label{fig:Hhists_0_50}
 \end{figure}
@@
     via numerical simulation (red dots) and obtained via a semi-analytic
-    calculation (blue line) for $\eta_{\rm sync} = 0.06$ and $I = 20^\circ$ (see
-    right panel of Fig.~\ref{fig:Hhists_0_06}). The semi-analytic calculation is
-    performed by numerically integrating
+    calculation (blue line) for $\eta_{\rm sync} = 0.06$, $I = 20^\circ$, and
+    $\Omega_{\rm s, i} = 10n$ (see right panel of Fig.~\ref{fig:Hhists_0_06}).
+    The semi-analytic calculation is performed by numerically integrating
     Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) on a grid
@@
     until the system reaches the separatrix, then calculating the probability of
-    reaching tCE2 for each integration using
-    Eq.~\eqref{eq:def_pc_weaktide}.}\label{fig:pc_fits_0_06}
+    reaching tCE2 for each integration using Eq.~\eqref{eq:def_pc_weaktide}. The
+    green dashed line in the top panel shows the result of using the analytical
+    expression (Eq.~\ref{eq:app_deltaK}) for $\Delta K_{\pm}$, and the bottom
+    panel shows the distribution of values of $\eta_{\rm cross}$, the value of
+    $\eta$ when a trajectory starting at $\theta_{\rm i}$ encounters the
+    separatrix.
+    \textcolor{red}{NB\@: the spike in tCE2 probability at at $\cos
+    \theta_{\rm i} \approx -1$, as well as the large $\eta_{\rm cross}$ values,
+    is likely an artifact of loss of numerical precision, I am working on fixing
+    this.}
+    }\label{fig:pc_fits_0_06}
 \end{figure}
@@
 ($\geq 2n$), Eq.~\eqref{eq:dsdt_tide} shows that sufficiently large initial
-obliquities are \emph{increased} by weak tidal friction (see the bottom right
-region of Fig.~\ref{fig:6equils}). This increase means that even initial
-conditions in zone I can sometimes be driven by tidal dissipation into the
-separatrix. When this is the case, it can be shown that both $\Delta K_+ > 0$
-and $\Delta K_- > 0$. This implies that both III $\to$ II and I $\to$ II
+obliquities are \emph{increased} by weak tidal friction (the bottom right
+region of panels of Fig.~\ref{fig:6equilssingle}). This increase means that even
+initial conditions in zone I can sometimes be driven by tidal dissipation into
+the separatrix. When this is the case, it can be shown that both $\Delta K_+ >
+0$ and $\Delta K_- > 0$. This implies that both III $\to$ II and I $\to$ II
 outcomes are guaranteed, and thus initial conditions in all three zones can
@@
     probability of ending up in tCE2 (red dots), averaged over an isotropic
-    initial spin orientation. The three shaded regions denote the contribution
-    of initial conditions in zones I/II/III (labeled) to the total tCE2
-    probability in the isotropic average. For example, among systems that
-    converge to tCE2 for $\eta_{\rm sync} = 0.06$, more originate in zone III
-    than zone II, and none originate in zone I.}\label{fig:probs20}
+    initial spin orientation and taking $\Omega_{\rm s, i} = 10n$. The three
+    shaded regions denote the contribution of initial conditions in zones
+    I/II/III (labeled) to the total tCE2 probability in the isotropic average.
+    For example, among systems that converge to tCE2 for $\eta_{\rm sync} =
+    0.06$, more originate in zone III than zone II, and none originate in zone
+    I.}\label{fig:probs20}
 \end{figure}
@@
             \p{\frac{R}{2R_{\oplus}}}^5
-            \p{\frac{a}{0.4\;\mathrm{AU}}}^{-13/2}.
+            \p{\frac{a}{0.4\;\mathrm{AU}}}^{-13/2}.\label{eq:sehj_adot}
 \end{align}
@@
             \p{\frac{M_\star}{M_{\odot}}}^{3/2}
-            \p{\frac{m}{8 M_{\oplus}}}^{-1}\nonumber\\
-        &\times \p{\frac{R}{2R_{\oplus}}}^3
+            \p{\frac{\rho}{\rho_{\oplus}}}^{-1}
             \p{\frac{a}{0.035\;\mathrm{AU}}}^{-9/2}.
@@
 due to the small semi-major axis ratio, we must generalize Eq.~\eqref{eq:wlp}
-\citep{lai_2017}:
+\citep[see e.g.][]{lai_2017}:
 \begin{equation}
     \omega_{\rm lp} = \frac{3m_{\rm p}}{4M_{\star}}
-        \alpha^3 n f(\alpha),
+        \p{\frac{a}{a_{\rm p}}}^3 n f(\alpha),
         \label{eq:def_g_usp}
 \end{equation}
-where $\alpha = a / a_{\rm p}$ and \citep{murray1999solar}
+where $\alpha = a / a_{\rm p}$ and
 \begin{equation}
     f(\alpha) \equiv \frac{b_{\rm 3/2}^{(1)}(\alpha)}{3\alpha}
-        \approx 1 + \frac{15}{8}\alpha^2 + \frac{175}{64}\alpha^4 + \dots,
+        \approx 1 + \frac{15}{8}\alpha^2 + \dots
 \end{equation}
@@
 $\eta_{\rm sync}$ (Eq.~\ref{eq:def_etasync}) can be computed:
-% (1 + 15/8 * (1.3)^(-4/3) + 175/64 * 1.3^(-8/3)) * 0.012
-\begin{align}
-    \eta_{\rm sync} ={}& 0.027 \cos I
+% (10 * (Mearth)^2 / (Msun)^2) / 2 * (1.3)^(-3) * ((0.035 AU) / (Rearth))^3
+% 0.011389
+\begin{align}
+    \eta_{\rm sync} ={}& 0.011 \cos I f(\alpha)
             \p{\frac{k}{k_{\rm q}}}
-            \p{\frac{m m_{\rm p}}{\p{8 M_{\oplus}}^2}}
+            \p{\frac{\rho}{\rho_{\oplus}}}
+            \p{\frac{a}{0.035 \;\mathrm{AU}}}^{3}\nonumber\\
+        &\times
+            \p{\frac{m_{\rm p}}{10 M_{\oplus}}}
+            \p{\frac{a / a_{\rm p}}{1/1.3}}^{3}
             \p{\frac{M_\star}{M_{\odot}}}^{-2}
-            \p{\frac{a}{0.035 \;\mathrm{AU}}}^{3}\nonumber\\
-        &\times \p{\frac{\alpha^3 f(\alpha)}{0.016}}
-            \p{\frac{R}{2R_{\oplus}}}^{-3}.
-            \label{eq:etasync_usp}
-\end{align}
-We have evaluated using an $\alpha$ corresponding to a period ratio $P_{\rm p} /
-P = 1.5$. For $I = 5^\circ$, roughly consistent with typical proto-USP systems
-\citep{dai2018larger}, Eq.~\eqref{eq:def_etac} shows that $\eta_{\rm sync} \ll
-\eta_{\rm c}$, and thus there are four CSs at spin-orbit synchronization. If,
-following \citet{millholland2020formation}, we take the initial planetary
-obliquity to be zero, the planet is guaranteed to evolve into tCE1, and not tCE2
-(see Fig.~\ref{fig:Hhists_0_06}). If we assume instead a randomly oriented
-initial planetary spin, perhaps again due to early giant impacts,
-Fig.~\ref{fig:probs5} suggests that the probability of capture into tCE2 is
-still only modest ($\lesssim 10\%$). A more sophisticated calculation including
-the effect of a third planet does not greatly modify these results. Note that
-this calculation is in tension with Fig.~4 of \citet{millholland2020formation},
-where they find that $\eta \sim 1$ for the same physical parameters when
-$\Omega_{\rm s}$ is at its equilibrium value (i.e.\ satisfying
-Eq.~\ref{eq:weaktide_dWszero}, or $\Omega_{\rm s} \approx n$ when the obliquity
-is small).
+            .\label{eq:etasync_usp}
+\end{align}
+We have evaluated using $a / a_{\rm p}$ corresponding to a period ratio $P_{\rm
+p} / P = 1.5$, for which $f(\alpha) \approx 5.5$. For $I = 5^\circ$, roughly
+consistent with typical proto-USP systems \citep{dai2018larger},
+Eq.~\eqref{eq:def_etac} shows that $\eta_{\rm sync} \ll \eta_{\rm c}$, and thus
+there are four CSs at spin-orbit synchronization. If, following
+\citet{millholland2020formation}, we take the initial planetary obliquity to be
+zero, the planet is guaranteed to evolve into tCE1, and not tCE2 (see
+Fig.~\ref{fig:Hhists_0_06}). If we assume instead a randomly oriented initial
+planetary spin, perhaps again due to early giant impacts, Fig.~\ref{fig:probs5}
+suggests that the probability of capture into tCE2 is still only modest
+($\lesssim 10\%$). A more sophisticated calculation including the effect of a
+third planet does not greatly modify these results. Note that this calculation
+is in tension with Fig.~4 of \citet{millholland2020formation}, where they find
+that $\eta \sim 1$ for the same physical parameters when $\Omega_{\rm s}$ is at
+its equilibrium value (i.e.\ satisfying Eq.~\ref{eq:weaktide_dWszero}, or
+$\Omega_{\rm s} \approx n$ when the obliquity is small).
 
@@
 attaining tCE2, requires that the initial orbital decay time scale be
-sufficiently fast. We find that:
+sufficiently fast. Evaluating Eq.~\eqref{eq:sehj_adot} for the relevant physical
+parameters, we find that:
 % 1 / (1.5 * 1e-3 * (Msun / (8 Mearth)) * ((2 Rearth) / (0.035 AU))^5 * 2 * pi / (0.035)^(3/2))
-% = 1.955e8
-\begin{align}
-    -\frac{\dot{a}}{a} ={}& \frac{1}{2 \times 10^8\;\mathrm{yr}}
+% = 7.8e8
+\begin{align}
+    -\frac{\dot{a}}{a} ={}& \frac{1}{8 \times 10^8\;\mathrm{yr}}
             \p{1 - \frac{\Omega_{\rm s}}{n}\cos \theta}
@@
             \p{\frac{M_\star}{M_{\odot}}}^{3/2}\nonumber\\
-        &\times \p{\frac{m}{8M_{\oplus}}}^{-1}
-            \p{\frac{R}{2R_{\oplus}}}^5
+        &\times \p{\frac{m}{M_{\oplus}}}^{-1}
+            \p{\frac{R}{R_{\oplus}}}^5
             \p{\frac{a}{0.035\;\mathrm{AU}}}^{-13/2}.
@@
 axis is smaller than $a_{\rm break}$, where
-% (1e-3 * (Msun / (8 Mearth))^3 * ((2 Rearth) * (0.05 AU))^(9/2))^(1/9) / (1 AU)
-% = 0.033198
-\begin{align}
-    a_{\rm break} \approx{}& 0.033 \;\mathrm{AU}
+% (1e-3 * (Msun / (3.16 Mearth))^3 * ((Rearth) * (0.05 AU))^(9/2))^(1/9) / (1 AU)
+% = 0.031994
+\begin{align}
+    a_{\rm break} \approx{}& 0.032 \;\mathrm{AU}
         \p{\frac{2k_2/Q}{10^{3}}}^{-1/9}
         \p{\frac{M_\star}{M_{\odot}}}^{1/3}
-        \p{\frac{mm_{\rm p}}{\p{8M_{\oplus}}^2}}^{-1/6}\nonumber\\
-        &\times \p{\frac{R}{2R_{\oplus}}}^{1/2}
+        \p{\frac{m}{10M_{\oplus}}}^{-1/6}\nonumber\\
+        &\times \p{\frac{\rho}{\rho_{\oplus}}}^{-1/6}
         \p{\frac{a_{\rm p}}{0.05\;\mathrm{AU}}}^{1/2}
@@
 \begin{align}
-    \frac{\dot{a}}{a_{\rm i}}
-        =& -\frac{1}{\mathrm{Gyr}}
+    -\frac{\dot{a}}{a_{\rm i}}
+        =& \frac{1}{\mathrm{Gyr}}
             \p{\frac{2k_2/Q}{10^{-6}}}
@@
 retroactively), Eq.~\eqref{eq:dldt1} needs to be modified. The precession of
-$\uv{l}$ about $\bm{J} = J\uv{j} \equiv \bm{L} + \bm{L}_{\rm p}$, the total
+$\uv{l}$ about $\bm{J} = J\uv{\jmath} \equiv \bm{L} + \bm{L}_{\rm p}$, the total
 angular momentum axis, can be written as
@@
     \rd{\uv{l}}{t} = \omega_{\rm lp}\cos I \frac{J}{L_{\rm p}}
-        \p{\uv{l} \times \uv{j}},
+        \p{\uv{l} \times \uv{\jmath}},
 \end{equation}
@@
 \begin{equation}
-    \frac{1}{t_{\rm s}} \lesssim \omega_{\rm lp}\cos I \frac{L}{L_{\rm p}}
-        \sin I \sqrt{\frac{\eta_{\rm sync}\cos I}{2}}.
-\end{equation}
-This then yields that
+    \frac{1}{t_{\rm s}} \lesssim \omega_{\rm lp}\cos i \frac{L}{L_{\rm p}}
+        \sin I \sqrt{\frac{\eta_{\rm sync}\cos i}{2}}.
+\end{equation}
+Here, $\cos i \equiv \uv{l} \cdot \uv{\jmath}$. This then yields that
 \begin{align}
     \frac{a_{\rm p}}{a}
-        \lesssim{}& 3.3 \p{\sin I \cos^2 I}^{4/21}
+        \lesssim{}& 3.3 \p{\sin i \cos^{1/2} i \cos^{3/2} I}^{4/21}
             \p{\frac{m}{1.41 M_J}}^{12/21}
@@
 and $m_{\rm p}$, we still have $L / L_{\rm p} \sim 0.4$, and so $L \gg L_{\rm
-p}$ is be well satisfied for the permitted parameter space.
+p}$ is well satisfied for the permitted parameter space.
 
@@
 the initial $\eta_{\rm sync, i}$ can be constrained:
-\begin{align}
-    \eta_{\rm sync, i} <{}& 0.016 \cos I\p{\frac{m}{1.41M_J}}^2
+% 1/2 * (1.41 Mjup)^2 / (1.36 Msun)^2 * ((0.038 AU) / (1.89 Rjup))^3 * (0.038 / 0.05)^(3.5)
+% 0.014916
+\begin{align}
+    \eta_{\rm sync, i} <{}& 0.015 \cos I f(\alpha)
+            \p{\frac{m}{1.41M_J}}^2
             \p{\frac{M_\star}{1.36M_{\odot}}}^{-2}
-            \p{\frac{a_{\rm i}}{0.038\;\mathrm{AU}}}^{3}\nonumber\\
-        &\times \p{\frac{a_{\rm p} / a_{\rm i}}{1.29}}^{-7/2}
+            \nonumber\\
+        &\times
+            \p{\frac{a_{\rm i}}{0.038\;\mathrm{AU}}}^{3}
+            \p{\frac{a_{\rm p} / a_{\rm i}}{1.29}}^{-7/2}
             \p{\frac{R}{1.89R_{\rm J}}}^{-3}.\label{eq:hj_etasync}
 \end{align}
-It is possible that $R$ is larger today than its primordial value due to
-inflation induced by increased stellar irradiation. However, if a smaller value
-of $R$ is used in Eq.~\eqref{eq:hj_etasync}, the value of $a_{\rm i}$ must also
-be decreased such that $R^5 / a_{\rm i}^{13/2}$ is constant
-(Eq.~\ref{eq:hj_adot}), which further decreases $\eta_{\rm sync, i}$.
-
-For $\eta_{\rm sync} = 0.016$, we find that there are four CSs unless $I$ is
+For these values of $a_{\rm i}$ and $a_{\rm p}$, $f(\alpha) \approx 5$. It is
+possible that $R$ is larger today than its primordial value due to inflation
+induced by increased stellar irradiation. However, if a smaller value of $R$ is
+used in Eq.~\eqref{eq:hj_etasync}, the value of $a_{\rm i}$ must also be
+decreased such that $R^5 / a_{\rm i}^{13/2}$ is constant (Eq.~\ref{eq:hj_adot}),
+which further decreases $\eta_{\rm sync, i}$.
+
+For $\eta_{\rm sync} = 0.075$, we find that there are four CSs unless $i$ is
 extremely small. From Fig.~\ref{fig:Hhists_0_06}, we can infer that prograde
@@
 HJ is assumed to be isotropically distributed, then Fig.~\ref{fig:probs20}
-suggests that the probability of entry into tCE2 is still $\lesssim 2\%$ even if
+suggests that the probability of entry into tCE2 is $\lesssim 25\%$ even if
 the perturbing planet is misaligned by $I = 20^\circ$.
@@
         call these equilibria \emph{tidal Cassini Equilibria} (tCE\@; see
-        Fig.~\ref{fig:6equils}). The locations of these equilibria are
+        Fig.~\ref{fig:6equilssingle}). The locations of these equilibria are
         determined by the system architecture and are parameterized by
@@
 same analysis presented in this paper: The tCE can still be found by an analysis
-mirroring that shown in Fig.~\ref{fig:6equils}, and the probabilistic outcome of
-a separatrix encounter can still be solved using the techniques of
+similar to that shown in Fig.~\ref{fig:6equilssingle}, and the probabilistic
+outcome of a separatrix encounter can still be solved using the techniques of
 Sections~\ref{ss:toy_outcomes} and~\ref{ss:phop_weaktide}.
@@
 \citep{dones1993does}. Figures~\ref{fig:probs20}--\ref{fig:probs5} can be
-updated accordingly by convolving the distributions in the right panels of
-Figs.~\ref{fig:Hhists_0_06}--\ref{fig:Hhists_0_70} with any initial obliquity
-distribution. The qualitative results are unlikely to change, while the detailed
-probabilities for tCE2 capture can increase [decrease] if the initial obliquity
-distribution favors [disfavors] $\theta_{\rm i} \approx 90^\circ$ compared to
-the isotropic distribution.
+updated accordingly by convolving any initial obliquity distribution with the
+tCE2 probability distributions, such as those shown in the right panels of
+Figs.~\ref{fig:Hhists_0_06}--\ref{fig:Hhists_0_50}. The qualitative results are
+unlikely to change, though the detailed probabilities for tCE2 capture can
+increase [decrease] if the initial obliquity distribution favors [disfavors]
+$\theta_{\rm i} \approx 90^\circ$ compared to the isotropic distribution.
 
@@
                 \p{\sin^2\theta_- - \sin^2\theta_+} \;\mathrm{d}\phi\nonumber\\
-        &= \frac{1}{t_{\rm s}}
+        &\approx \frac{1}{t_{\rm s}}
             \int\limits_{\phi_{\min}}^{\phi_{\max}}
@@
 
-% \section{Separatrix Crossing Probability with Weak Tidal Friction
-% }\label{app:sep_crossing_dynamics}
-
-% In this appendix, we analytically calculate $\Delta K_{\pm}$ for use in
-% Eq.~\eqref{eq:def_pc_weaktide} to calculate the probabilities of the two
-% possible transitions upon separatrix encounter. We first rewrite the full
-% equations of motion for the planet's spin including weak tidal friction in
-% component form:
-% \begin{align}
-%     \rd{\theta}{t} &= g\sin I \sin \phi -
-%         \frac{1}{t_{\rm a}} \sin \theta,\label{eq:ds_fullq}\\
-%     \rd{\phi}{t} &= -\alpha\cos\theta
-%         - g\p{\cos I + \sin I \cot \theta \cos \phi}\label{eq:ds_fullphi},\\
-%     \rd{\Omega_{\rm s}}{t}
-%         &= \frac{1}{t_{\rm a}} \s{2n \cos \theta
-%             - g\Omega_{\rm s}\p{1 + \cos^2\theta}}\label{eq:ds_fulls}.
-% \end{align}
-
-% Note that Eq.~\eqref{eq:def_dK_weaktide} can be rewritten
-% \begin{align}
-%     \Delta K_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}
-%         - \rd{H_{\rm sep}}{t}\;\mathrm{d}t
-%         \nonumber\\
-%         &= \oint_{\mathcal{C}_{\pm}}
-%            \p{\rd{(\cos\theta)}{t}}_{\rm tide}
-%             + \frac{\dot{\Omega}_{\rm s}}{\dot{\phi}}
-%             \p{\pd{H}{s} - \pd{H_{\rm sep}}{s}}\;\mathrm{d}\phi
-%                 \label{eq:app_dhpm}.
-% \end{align}
-
-% We then evaluate $\Delta K_{\pm}$ by integrating along the two legs of the
-% separatrix $\mathcal{C}_{\pm}$ (see Fig.~\ref{fig:1contours}). Note that we must
-% use the value of $\eta$ at the moment of separatrix encounter, as the evolution
-% of $\Omega_{\rm s}$ changes the spin-orbit precession frequency $\alpha$
-% \begin{align}
+\section{Approximate TCE2 Probability for Small $\eta_{\rm sync}$
+}\label{app:sep_crossing_dynamics}
+
+In this appendix, we seek a tentative analytic understanding for the
+probability of convergence to tCE2 when $\eta_{\rm sync}$ is small, i.e.\ the
+left extremes of Figs.~\ref{fig:probs20} and~\ref{fig:probs5}. In this regime,
+following the discussions in Sections~\ref{ss:toy_outcomes}
+and~\ref{ss:phop_weaktide}, we understand that initial conditions (ICs) in zone I
+always converge to tCE1, ICs in zone II always converge to tCE2,
+and ICs in zone III experience separatrix encounter and
+probabilistically converge to either one of the tCE\@. To further proceed, we
+will assume an isotropic distribution of initial spin orientations; different
+distributions again will only change the quantitative but not qualitative
+character of the discussion. Then the tCE2 probability, which we denote by
+$P_{\rm tCE2}$, can be expressed as the sum of: (i) the probability that an IC
+is in zone II, and (ii) the probability that an IC is both in zone III and
+undergoes a III $\to$ II transition. To simplify the discussion, we will
+approximate that $P_{\rm tCE2}$ can be calculated as
+\begin{equation}
+    P_{\rm tCE2} \sim \frac{A_{\rm II}}{4\pi}
+            + \frac{A_{\rm III}}{4\pi}\ev{P_{\rm III \to II}},
+            \label{eq:app_ptce2_schematic}
+\end{equation}
+where $A_{\rm II}$ and $A_{\rm III}$ are the phase space areas of zones II and
+III respectively, and $\ev{P_{\rm III \to II}}$ is the \emph{average} III $\to$
+II transition probability for a random IC in zone III\@. Next, we evaluate each
+of the expressions in Eq.~\eqref{eq:app_ptce2_schematic}.
+
+We first consider $A_{\rm II}$ and $A_{\rm III}$. Exact analytic forms for both
+$A_{\rm II}$ and $A_{\rm III}$ is known (\citealp{ward2004I}, Paper I), but an
+accurate approximation can be obtained using Eq.~\eqref{eq:sep_theta} since
+$\eta_{\rm i} \ll 1$. We obtain that:
+\begin{align}
+    \frac{A_{\rm II}}{4\pi} &= \frac{4}{\pi}\sqrt{\eta_{\rm i} \sin I},\\
+    \frac{A_{\rm III}}{4\pi}
+        &= \frac{1 + \eta_{\rm i} \cos I}{2} -
+            \frac{2}{\pi}\sqrt{\eta_{\rm i} \sin I}.
+\end{align}
+
+Next, we need to evaluate $\ev{P_{\rm III \to II}}$, for which we must
+understand the outcomes of the separatrix encounters that ICs in zone III
+experience. We proceed by analytically calculating $\Delta K_{\pm}$
+(Eq.~\ref{eq:def_dK_weaktide}) for use in Eq.~\eqref{eq:def_pc_weaktide} to
+obtain the probabilities of the outcomes of separatrix encounter. We first
+rewrite Eq.~\eqref{eq:def_dK_weaktide} as:
+\begin{align}
+    \Delta K_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}
+        - \rd{H_{\rm sep}}{t}\;\mathrm{d}t
+        \nonumber\\
+        &= \oint_{\mathcal{C}_{\pm}}
+           \p{\rd{(\cos\theta)}{t}}_{\rm tide}
+            + \frac{\dot{\Omega}_{\rm s}}{\dot{\phi}}
+            \p{\pd{H}{\Omega_{\rm s}} - \pd{H_{\rm sep}}{\Omega_{\rm s}}}\;\mathrm{d}\phi
+                \label{eq:app_dhpm}.
+\end{align}
+Then, using the full equations of motion for the planet's spin including weak
+tidal friction in component form, given by
+Eqs.~(\ref{eq:ds_fullq}--\ref{eq:ds_fulls}), we can evaluate $\Delta K_{\pm}$ by
+integrating along the two legs of the separatrix $\mathcal{C}_{\pm}$ (see
+Fig.~\ref{fig:1contours}). Note that we must use the value of $\eta$ at the
+moment of separatrix encounter, which we denote $\eta_{\rm cross}$, as the
+evolution of $\Omega_{\rm s}$ changes the spin-orbit precession frequency
+$\alpha$ and thus $\eta$ itself:
+\begin{align}
     % \Delta K_{\pm} ={}& \oint_{\mathcal{C}_{\pm}}
@@
     %         \p{\frac{2n}{\Omega_{\rm s}} - \cos\theta}
-%         + \frac{1}{t_{\rm s}}\frac{n}{\Omega_{\rm s}\eta}
+    %     + \frac{1}{t_{\rm s}}\frac{n}{\Omega_{\rm s}\eta_{\rm cross}}
     %         \s{\p{\cos \theta}_{\mathcal{C}_{\pm}} - \frac{\Omega_{\rm s}}{2n}}
-%             \s{2 \cos I \pm \sqrt{2 \sin I\p{1 - \cos \phi} / \eta}}
-%             \;\mathrm{d}\phi.\label{eq:app_deltaK}
-%     t_{\rm s} \Delta K_{\pm} \approx{}&
-%         -2\cos I\p{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
-%         \pm 2\pi \frac{\Omega_{\rm s}}{n}\cos I
-%         - 8\eta \cos I \sqrt{\sin I / \eta}
-%             + \frac{4\Omega_{\rm s}}{n}\sqrt{\sin I/\eta}\nonumber\\
-%         &+ \frac{2n}{\Omega_{\rm s}}\p{\mp 2\pi\p{1 - 2\eta \sin I}
-%             + 16\cos I \eta^{3/2}\sqrt{\sin I}}
-%             + 8\sqrt{\eta \sin I}
-%             \pm 2 \pi \eta \cos I
-%             - \frac{64}{3} \p{\eta \sin I}^{3/2}.\label{eq:app_deltaK}
-% \end{align}
-% At this point, since $\eta$ often is not small, it is necessary to integrate
-% along the numerically computed $\mathcal{C}_{\pm}$ (instead of the approximate
-% solution given by Eq.~\ref{eq:sep_theta}) to obtain sufficiently accurate values
-% for $\Delta K_{\pm}$. These numerically integrated values are used in
-% Eq.~\eqref{eq:def_pc_weaktide} to semi-analytically compute the tCE2
-% probabilities (blue curves) in
-% Figs.~\ref{fig:pc_fits_0_06}--\ref{fig:pc_fits_0_20}.
+    %         \s{2 \cos I \pm \sqrt{2 \sin I\p{1 - \cos \phi} / \eta_{\rm cross}}}
+    %         \;\mathrm{d}\phi,\\
+    t_{\rm s} \Delta K_{\pm} \approx{}&
+        \frac{\eta_{\rm cross}^2}{\eta_{\rm sync}}\s{
+            -2\cos I\p{\pm 2\pi \eta_{\rm cross} \cos I
+                + 8\sqrt{\eta_{\rm cross} \sin I}}
+            \mp 4\pi \sin I
+            - 8 \cos I \sqrt{\eta_{\rm cross}\sin I}
+                + \frac{4\eta_{\rm sync}}{\eta_{\rm cross}}
+                    \sqrt{\sin I/\eta_{\rm cross}}}\nonumber\\
+        &+ \frac{2\eta_{\rm cross}}{\eta_{\rm sync}}
+            \p{\mp 2\pi\p{1 - 2\eta_{\rm cross} \sin I}
+            + 16\cos I \eta_{\rm cross}^{3/2}\sqrt{\sin I}}
+            + 8\sqrt{\eta_{\rm cross} \sin I}
+            \pm 2 \pi \eta_{\rm cross} \cos I
+            - \frac{64}{3} \p{\eta_{\rm cross} \sin I}^{3/2}.
+                \label{eq:app_deltaK}
+\end{align}
+The resulting $P_{\rm III \to II}$ obtained using this analytic $\Delta K_{\pm}$
+in Eq.~\eqref{eq:def_pc_weaktide} is shown as the green dashed line in the top
+panel of Fig.~\ref{fig:pc_fits_0_06}, where it can be seen that agreement is
+reasonable for $\eta_{\rm cross} \lesssim 0.05$. For the purposes of this
+section, we drop all but the leading order terms in both the numerator and
+denominator of Eq.~\eqref{eq:def_pc_weaktide} and obtain:
+% proof:
+% from utils import *; I = np.radians(20); s_c = 0.01; s = np.linspace(1, 10, 100); top, bottom = get_ps_anal(I, s_c, s); plt.plot(s_c/s, (bottom + top) / bottom, 'k'); plt.plot(s_c/s, 6 * s_c / np.pi * np.sqrt(np.sin(I) / (s_c / s)), 'g')
+\begin{equation}
+    P_{\rm III \to II} \approx
+        \frac{6\eta_{\rm sync}}{\pi} \sqrt{\frac{\sin I}{\eta_{\rm cross}}}.
+\end{equation}
+
+However, $\eta_{\rm cross}$ cannot be expressed in closed form as a function of
+the ICs. Based on the bottom panel of Fig.~\ref{fig:pc_fits_0_06}, we make the
+crude approximation that $\eta_{\rm cross}$ is uniformly distributed between
+$\eta_{\rm i}$ and $\eta_{\rm sync}$. We thus obtain:
+\begin{align}
+    \ev{P_{\rm III \to II}}
+        &\sim \frac{1}{\eta_{\rm sync} - \eta_{\rm i}}
+            \int\limits_{\eta_{\rm i}}^{\eta_{\rm sync}}
+            P_{\rm III \to II}\;\mathrm{d}\eta_{\rm cross}\nonumber\\
+        &= \frac{12 \sqrt{\eta_{\rm sync}\sin I}}{\pi
+            \p{1 + \sqrt{n / \Omega_{\rm s, i}}}}.
+\end{align}
+
+With this result, we can finally express Eq.~\eqref{eq:app_ptce2_schematic} as:
+\begin{align}
+    P_{\rm tCE2} &\simeq
+            \frac{4\sqrt{\eta _{\rm sync} \sin I}}{\pi}\p{
+                \sqrt{n / \Omega_{\rm s, i}}
+                + \frac{3}{2\p{1
+                + \sqrt{n / \Omega_{\rm s, i}}}}}
+            + \mathcal{O}\p{\eta_{\rm sync}}.\label{eq:app_tce2_p_tot}
+\end{align}
 

### 2021-05-25 initial/1_weaktide/5pop.py

@@ -18,38 +18,13 @@ plt.rc('ytick', direction='in', left=True, right=True)
 
 from utils import solve_ic, to_ang, to_cart, get_etac, get_mu4, get_mu2,\
     stringify, H, roots, get_H4, s_c_str, get_mu_equil, get_anal_caps,\
-    get_num_caps, get_crit_mus, get_areas_ward
+    get_num_caps, get_crit_mus, get_areas_ward, solve_with_events5, TIMES, TF
 PKL_FILE = '5dat%s_%d.pkl'
+# PKL_FILE = '5dat_hightol%s_%d.pkl'
 # N_PTS = 1 # TEST
 N_PTS_TOTAL = 20000
-N_THREADS = 50
+N_THREADS = 64
 N_PTS = N_PTS_TOTAL // N_THREADS
-TF = 8000
-TIMES = np.exp(np.linspace(0, np.log(TF), 100))
-
-def solve_with_events(I, s_c, eps, mu0, phi0, s0):
-    '''
-    solves IVP then returns (mu, s, t) at phi=0, pi + others
-    '''
-    init = [*to_cart(np.arccos(mu0), phi0), s0]
-    event = lambda t, y: y[1]
-    t, _, _, ret = solve_ic(I, s_c, eps, init, TF,
-                            rtol=1e-4,
-                            events=[event], dense_output=True)
-    sol_times = ret.sol(TIMES)
-    q, phi = to_ang(*sol_times[0:3])
-    s = sol_times[3]
-
-    [t_events] = ret.t_events
-    x_events, _, mu_events, s_events = ret.sol(t_events)
-    # phi = 0 means x < 0
-    idxs_0 = np.where(x_events < 0)
-    idxs_pi = np.where(x_events > 0)
-    mu_0, s_0, t_0 = mu_events[idxs_0], s_events[idxs_0], t_events[idxs_0]
-    mu_pi, s_pi, t_pi = mu_events[idxs_pi], s_events[idxs_pi], t_events[idxs_pi]
-
-    shat_f = np.sqrt(np.sum(ret.y[ :3, -1]**2))
-    return (mu_0, s_0, t_0, mu_pi, s_pi, t_pi), np.cos(q), phi, s
 
 def get_sep_hop(t_0, s_0, mu_0, t_pi, s_pi, mu_pi):
     '''
@@ -94,7 +69,8 @@ def _run_sim_thread(I, eps, s_c, s0, num_threads, thread_idx):
[…]

### 2021-05-25 initial/1_weaktide/6misc.py

@@ -1,5 +1,7 @@
 '''
 misc little plots
+
+python 6*.py, check the mu_finals
 '''
 import numpy as np
 from multiprocessing import Pool
@@ -11,12 +13,16 @@ plt.rc('text', usetex=True)
 plt.rc('font', family='serif', size=16)
 from scipy.optimize import brenth
 from scipy.interpolate import interp1d
+plt.rc('xtick', direction='in', top=True, bottom=True)
+plt.rc('ytick', direction='in', left=True, right=True)
 
 POOL_SIZE = 50
+TRAJ_COLORS = ['darkorchid', 'red', 'fuchsia',
+               'deepskyblue', 'blue', 'teal', 'k']
 
 from utils import roots, s_c_str, get_mu_equil, solve_ic, to_cart, to_ang,\
     get_H4, H, get_mu4, get_ps_anal, get_anal_caps, get_num_caps, get_etac,\
-    solve_with_events
+    solve_with_events5
 
 def get_cs_val(I, s_c, s):
     '''
@@ -34,7 +40,8 @@ def get_cs_val(I, s_c, s):
             cs2_qs[idx] = cs_qs[0]
     return cs1_qs, cs2_qs
 
-def equils_plot(I, s_c, eps, mu0, phi0, s0, tf, fn_str, idx):
+def equils_plot(I, s_c, eps, mu0, phi0, s0, tf, fn_str, idx, rtol=1e-9,
+                time_idxbase=[100, 300, 600, 4600]):
     plotdir = '%s_sims' % fn_str
     if not os.path.exists(plotdir):
         os.mkdir(plotdir)
@@ -43,7 +50,7 @@ def equils_plot(I, s_c, eps, mu0, phi0, s0, tf, fn_str, idx):
 
     if not os.path.exists(pkl_fn):
         print('Running %s' % pkl_fn)
-        solve_ret = solve_with_events(I, s_c, eps, mu0, phi0, s0, tf)
+        solve_ret = solve_with_events5(I, s_c, eps, mu0, phi0, s0, tf, rtol=rtol)
         with lzma.open(pkl_fn, 'wb') as f:
             pickle.dump(solve_ret, f)
     else:
@@ -51,25 +58,47 @@ def equils_plot(I, s_c, eps, mu0, phi0, s0, tf, fn_str, idx):
             print('Loading %s' % pkl_fn)
[…]

### 2021-05-26 notes/np_notes.tex
stash

--- 2021-05-16 initial/YS_usp.tex
@@
         amssymb,
-        fouriernc, % fourier font w/ new century book
         fancyhdr, % page styling
@@
 
-\onehalfspacing
+\tableofcontents
 
-\section{Two Planet Mutual Precession}
+\section{05/25/21}
 
-Consider two planets mutually precessing. We calculate this in two ways below,
-which are equivalent: the vector formulation, and as the eigenvalue of
-Laplace-Lagrange theory. We compare these to the output of the RINGS code as a
-third calculation.
+TODO Fill in the calculation of the inclination.
 
-\subsection{Vector Formulation}
+We start with the solution for the inner orbit's inclination
+\begin{equation}
+    \mathcal{I}(t) = Ae^{ig_It} + Be^{ig_{II} t},
+\end{equation}
+where $A$ and $B$ are generally complex ($A$ can be chosen to be real by
+choosing the initial phase). If we seek a CS with the frequency $g_I$, then we
+can go to the corotating frame, in which case
+\begin{equation}
+    \mathcal{I}_{\rm rot}(t) = I_0 + Be^{i\p{g_{II} - g_I}t}.
+\end{equation}
+With appropriate choice of initial time/phase, $B$ can be chosen to be real as
+well. Define $g' = g_{II} - g_I$. Intuitively, there are four cases near CS2:
+\begin{itemize}
+    \item If $I_0 > B$ and $g' \gg \omega_{\rm lib}$, we should see small
+        oscillations about CS2 (as $\uv{l}_{\rm p}$ effectively is
+        ``vibrating''), which average out.
 
-We have
-\begin{align}
-    \rd{\uv{l}_1}{t} &= \omega_{21}\p{\uv{l}_1 \cdot \uv{l}_2}
-            \p{\uv{l}_1 \times \uv{l}_2}\nonumber\\
-        &= \omega_{21}\cos I_{12}
-            \p{\uv{l}_1 \times \uv{l}_2},\\
-    \rd{\uv{l}_2}{t} &= \frac{L_1}{L_2}\omega_{21}\cos I_{12}
-        \p{\uv{l}_2 \times \uv{l}_1},\\
-    \omega_{21}
-        &= \frac{3 m_2}{4 M_\star}\p{\frac{a_1}{a_2}}^3 n_1
-            f\p{\frac{a_1}{a_2}}\label{eq:w21},\\
-    f\p{\alpha} &= \frac{b_{3/2}^{(1)}}{3\alpha}\nonumber\\
-        &= \frac{1}{3\alpha}
-            \frac{1}{\pi}\int\limits_0^{2\pi}
-                \frac{\cos \p{t}}{
-                \p{\alpha^2 + 1 - 2\alpha \cos t}^{3/2}}\;\mathrm{d}t\nonumber\\
-        &\approx 1 + \frac{15}{8}\alpha^2 + \mathcal{O}\p{\alpha^4}.
-\end{align}
-In all numerical work, we calculate $f(\alpha)$ numerically, via direct
-integration.
+    \item If $I_0 > B$ and $g' \ll \omega_{\rm lib}$, then adiabatic resonance
+        advection means that the trajectory should encircle CS2 with constant
+        phase space area as CS2 moves around slightly.
 
-To get the precession rate of $\uv{l}_1$, we have shown many times that it
-precesses around $\uv{j}$ with $\bm{J} = J\uv{j} = \bm{L}_1 + \bm{L}_2$ such
-that
-\begin{align}
-    \rd{\uv{l}_1}{t} &= \omega_{21}\cos I_{21}
-            \p{\uv{l}_1 \times \frac{\bm{L}_1 + \bm{L}_2}{L_2}}\nonumber\\
-        &= \frac{J}{L_2}
-            \omega_{21}\p{\uv{l}_1 \cdot \uv{l}_2}
-                \p{\uv{l}_1 \times \uv{j}}\label{eq:2p_vec},
-\end{align}
-where again $\omega_{21}$ is given by Eq.~\eqref{eq:w21}.
+    \item If $I_0 < B$ and $g' \gg \omega_{\rm lib}$, note that $\uv{l}_{\rm p}$
+        is \emph{circulating}; probably precesses about average.
 
-\subsection{Laplace-Lagrange Formulation}\label{ss:LL}
-
-Defining $\mathcal{I}_i = \abs{I_i} e^{i\Omega_i}$, the Laplace-Lagrange secular
-theory says that:
-\begin{align}
-    \rd{}{t}\begin{bmatrix}
-        \mathcal{I}_1\\\dots\\\mathcal{I}_N
-    \end{bmatrix}
-        &= \tilde{\bm{B}} \begin{bmatrix}
-            \mathcal{I}_1\\\dots\\\mathcal{I}_N
-        \end{bmatrix},\\
-    B_{jk} &=
-        -\frac{3 m_k}{4 M_\star}\p{\frac{a_i}{a_j}}^2
-            \min\p{\frac{a_i}{a_j}, 1}
-            n_j f\p{\frac{a_i}{a_j}},\\
-    B_{jj} &= \sum\limits_{k \neq j}
-        -B_{jk}.\label{eq:2p_LL}
-\end{align}
-In the two-planet case, $\tilde{\bm{M}}$ is just a $2 \times 2$ matrix, and the
-only nonzero eigenvalue is the precession frequency (the other has eigenvalue
-zero and corresponds to the total angular momentum). It is believable that this
-is in agreement with Eq.~\eqref{eq:2p_vec} if we construct the corresponding
-eigenvector and calculate its eigenvalue, and this appears to be the case.
-
-\subsection{RINGS calculation}
-
-For a given set of two-planet parameters, we can use RINGS to calculate their
-dynamical evolution. The fiducial parameters we choose are:
-\begin{align}
-    a_1 &= 0.035\;\mathrm{AU} & m_1 &= M_{\oplus} & I_1 &= 1^\circ\\
-    && m_2 &= 10M_\oplus & I_2 &= 5^\circ.
-\end{align}
-We choose $\Omega_i = \omega_i = 0$ for simplicity. We can then run RINGS and
-try to extract the precession frequencies. To do this, I took the Fourier
-Transform of $I_1(t)$ and found the frequency with the largest amplitude.
-
-The results of the comparison among these three methods where $a_2$ is varied is
-shown in Fig.~\ref{fig:scan}.
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{4_usp_rings/scan_alpha.png}
-    \caption{(Top \& middle) plot of precession frequencies obtained using three
-    methods as a function of $a_2$ for two and three-planet systems. Good
-    agreement is observed in two-planet cases, while the three-planet systems
-    have some interesting behavior. The bottom panel shows the quotient of the
-    largest vector-calculated frequency and the numerical value for the 3-planet
-    case; convincing agreement is observed. Frequencies are }\label{fig:scan}
-\end{figure}
-
-\section{Three-Planet Case}
-
-\subsection{Vector Calculation}
-
-We now add a third planet. For simplicity, we will neglect the precession
-induced on $\bm{L}_2$ and $\bm{L}_3$ by $\bm{L}_1$, then:
-\begin{align}
-    \rd{\uv{l}_1}{t} &= \omega_{21}\cos I_{12} \p{\uv{l}_1 \times \uv{l}_2}
-        + \omega_{31}\cos I_{13} \p{\uv{l}_1 \times \uv{l}_3}
-        \nonumber\\
-    \rd{\uv{l}_2}{t} &= \omega_{32}\cos I_{23} \p{\uv{l}_2 \times \uv{l}_3},\\
-    \rd{\uv{l}_3}{t} &= \frac{L_2}{L_3}
-        \omega_{32}\cos I_{23} \p{\uv{l}_3 \times \uv{l}_2},\\
-    \omega_{jk}
-        &= \frac{3 m_k}{4 M_\star}\p{\frac{a_j}{a_k}}^3 n_j
-            f\p{\frac{a_j}{a_k}}.
-\end{align}
-We expect two eigenvectors, one where $\uv{l}_1$ is evolving and one where the
-other two are evolving. The latter has the precession frequency
-\begin{equation}
-    \Omega_{\rm 32} = \frac{J_{23}}{L_3}\omega_{32}.
-\end{equation}
-The former has the precession frequency:
-\begin{align}
-    \rd{\uv{l}_1}{t} &= -\s{
-        \omega_{21}\cos I_{12} \uv{l}_2 + \omega_{31}\cos I_{13} \uv{l}_3
-    } \times \uv{l}_1 \nonumber\\
-        &\equiv \bm{\Omega}_{32,1} \times \uv{l}_1,\\
-    \Omega_{32, 1}
-        &\approx \omega_{21} \cos I_{12}
-            + \omega_{31}\cos I_{13}
-            + \mathcal{O}\p{\cos I_{23}}.
-\end{align}
-Here, we have simply assmued that $\uv{l}_2$ is approximately aligned with
-$\uv{l}_3$; by the law of cosines, the deviation scales with $\cos I_{23} \sim
-2^\circ$ for compact architectures excepting the innermost planet.
-
-We want to know which of $\Omega_{32}$ and $\Omega_{32, 1}$ are larger. To
-calculate scalings, let's approximate $I_{12} \approx I_{13} \approx I_{23}
-\approx 0$. If we assume the semimajor axis ratios are constant, $a_3 / a_2 =
-a_2 / a_1 = \alpha$, then
-\begin{align}
-    \frac{\Omega_{32, 1}}{\Omega_{32}}
-        &= \frac{m_2 \alpha^3 n_1 f(\alpha)
-            + m_3 \alpha^6 n_1 f(\alpha^2)}{m_3 \alpha^3 n_2
-            f(\alpha)}\frac{L_3}{J_{23}}\nonumber\\
-        &= \frac{L_3}{J_{23}}\p{
-            \frac{m_2}{m_3}\alpha^{-3/2}
-                + \alpha^{3/2}\frac{f\p{\alpha^2}}{f(\alpha)}}.
-\end{align}
-Note that $J_{23} / L_3 \approx (m_2/m_3)\alpha^{1/2} + 1$. There are thus two
-ways to obtain $\Omega_{32, 1} < \Omega_{32}$:
-\begin{itemize}
-    \item If we have $\alpha \approx m_2/m_3 \approx f\p{\alpha^2} / f(\alpha)
-        \approx 1$, then $J_{23} / L_3 \approx 2$ and $\Omega_{32, 1} /
-        \Omega_{32} \approx 0.5$, so not a very large ratio.
-
-    \item A much larger ratio can be obtained if $m_2/m_3 \ll \alpha^{3/2} \ll
-        1$.
+    \item If $I_0 < B$ and $g' \ll \omega_{\rm lib}$, then there should be no
+        resonance, as CS2 itself is circulating; there is no librating resonant
+        angle.
 \end{itemize}
-Thus, in general, we find that the $\Omega_{32, 1}$ precession frequency should
-generally be larger or comparable except for very small $a_{j + 1} / a_j$.
-
-\subsection{Comparison with Other Results}
-
-The LL results follow straightforwardly from Section~\ref{ss:LL}. The RINGS
-simulations can yield two precession frequencies if we seek the first two
-non-commensurate, non-adjacent frequencies in the FT of $I_1(t)$; note that
-choosing $\Omega_{i} = \omega_i = 0$ means that $\uv{l}_2 = \uv{l}_3$ initially,
-but due to different backreaction torques from $\uv{l}_1$ they eventually
-misalign and give rise to the $\Omega_{32}$ mode. This is shown in the middle
-panel of Fig.~\ref{fig:scan}. Finally, in the bottom panel, we show the quotient
-of $\Omega_{32, 1}$ and the numerically-determined maximum precession frequency.
-We see fractional deviations, showing that $\Omega_{32, 1}$ is a good estimate
-of $g_{\max}$.
-
-\subsection{Inner Mass Dependence}
-
-In the above, we have considered the case where $m_1 = M_{\odot}$ and $m_2 = m_3
-= 10M_{\odot}$, satisfying our ``no backreaction'' assumption. However, we can
-also consider the case closer to the Millholland paper, where $m_i =
-5M_{\odot}$. These results are shown in Fig.~\ref{fig:scan5}. For some reason,
-the agreement \emph{improves}?
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{4_usp_rings/scan_alpha5.png}
-    \caption{Same as Fig.~\ref{fig:scan} but for equal masses $m_i =
-    5M_{\odot}$.}\label{fig:scan5}
-\end{figure}
-
-\section{Resulting Impact on USP Formation Story}
-
-In the 3p systems, we see that $\abs{g_{\max}} \lesssim 0.2 \;\mathrm{yr^{-1}}$.
-At the same time, we can calculate the spin-orbit precession frequency:
-\begin{align}
-    \alpha &= \frac{3k_q}{2k}\frac{M_\star}{m}
-        \p{\frac{R}{a}}^3 \Omega_{\rm s},\\
-        &\approx 0.86\;\mathrm{yr^{-1}}
-            \frac{k_q}{k}
-            \p{\frac{M_{\star}}{M_{\odot}}}^{3/2}
-            \p{\frac{m}{M_{\oplus}}}^{-1}
-            \p{\frac{R}{R_{\oplus}}}^3
-            \p{\frac{a}{0.035\;\mathrm{AU}}}^{-9/2}
-            \p{\frac{\Omega_{\rm s}}{n}}.
-\end{align}
-This shows that $\eta_{\rm sync} \equiv \abs{g_{\max}} / \alpha \lesssim 0.15$
-very optimistically.
-
-Using Millholland's formula, we have yet another small correction. They use
-$3k_q = 0.4$ and $k = 0.35$, so their $\alpha$ is depressed by a factor of
-$8/21$, leaving $\eta_{\rm sync} \sim 0.4$ for extremal values (note that $a_2 /
-a_1 = 1.2$ corresponds to a period ratio of $1.3$). So indeed, we should expect
-that $\eta_{\rm sync}$ is only $\gtrsim 1$ if $a_2 / a_1 \lesssim 1.2$.
-
-\subsection{Double Checking $\eta_{\rm sync}$ for 2p}
-
-Recall that we had:
-\begin{align}
-    \eta_{\rm sync} &= \frac{m_pm}{2M_\star^2}\p{\frac{a}{a_{\rm p}}}^3
-            \p{\frac{a}{R}}^3,\\
-% (8 * (Mearth)^2 / (Msun)^2) / 2 * (2)^(-3) * ((0.04 AU) / (2 Rearth))^3
-% 0.00467
-        &= 4.67 \times 10^{-4}
-            \cos I \frac{k}{k_{\rm q}}f\p{\frac{1}{2}}
-            \frac{m_pm}{8(M_{\odot}^2)}
-            \p{\frac{M_\star}{M_{\odot}}}^{-2}
-            \p{\frac{a/a_{\rm p}}{1/2}}^3
-            \p{\frac{a}{0.04\;\mathrm{AU}}}^3
-            \p{\frac{R}{2R_{\oplus}}}^{-3},\\
-% (10 * (Mearth)^2 / (Msun)^2) / 2 * (1.2)^(-3) * ((0.035 AU) / (Rearth))^3
-% 0.014480
-        &= 0.0145
-            \cos I \frac{k}{k_{\rm q}}f\p{\frac{1}{1.2}}
-            \p{\frac{m_p}{10M_{\odot}}}
-            \p{\frac{\rho}{\rho_{\oplus}}}
-            \p{\frac{M_\star}{M_{\odot}}}^{-2}
-            \p{\frac{a/a_{\rm p}}{1/1.2}}^3
-            \p{\frac{a}{0.035\;\mathrm{AU}}}^3.
-\end{align}
-Note that $f(0.5) = 1.72$ while $f(1/1.2) = 9.69$ (NB\@: the power series for
-$\alpha$ converges way too slowly for the latter result, have to evaluate
-numerically), so this is already a bit more promising.
-
-\subsection{Towards $\eta_{\rm sync}$ for 3p? No}
-
-We showed above that
-\begin{align}
-    \abs{g_{\max}} &\approx \Omega_{\rm 32, 1}\nonumber\\
-        &\approx \omega_{21}\cos I_{12}
-            \p{1 + \frac{m_3}{m_2}\alpha^3\frac{f\p{\alpha^2}}{f(\alpha)}
-                \frac{\cos I_{13}}{\cos I_{12}}}.
-\end{align}
-Trying to express this in any sort of scaling way is difficult since $f(\alpha)$
-cannot be expressed analytically for sufficiently large $\alpha$. Nevertheless,
-for the fiducial $\alpha = 1/1.2$ and $m_3 = m_2$, we find that this enhancement
-is only $1.2\times$, and if we account for the fact that our naive prediction
-is small by about $15\%$, the third planet only contributes $40\%$ of the
-precession rate of the inner. This is unsurprising, and is not enough to lift
-$\eta_{\rm sync}$ to values of order unity; it raises it only to $\sim 0.2
-k/k_{\rm q}$, which is in line with our calculation above. So everything seems
-consistent!
 

### 2021-05-29 writeups/Su_weak_tides.tex
added some more plots, send dong draft

@@
 rotation-induced (dimensionless) quadrupole moment [for a body with uniform
-density, $k=0.4, k_{\rm q}=0.5$; for rocky planets, $k\simeq 0.2$ and $k_{\rm
-q}\simeq 0.17$ \citep[e.g.][]{lainey2016quantification}]. In other studies,
-$3k_{\rm q} / 2 k$ is often notated as $k_2 / 2C$
-\citep[e.g.][]{millholland_disk}. In Eq.~\eqref{eq:wlp}, $n \equiv
-\sqrt{GM_\star/a^3}$ is the inner planet's orbital mean motion,  and we have
-assumed $a_{\rm p}\gg a$ and included only the leading-order (quadrupole)
-interaction between the inner planet and perturber. Following standard notation,
-we define $\alpha = \omega_{\rm sl}$ and $g \equiv -\omega_{\rm 1p} \cos I$
-\citep[e.g.][]{colombo1966}.
+density, $k=0.4, k_{\rm q}=0.5$; for the Earth, $k \simeq 0.331$ and $k_{\rm q}
+\equiv k_2 / 3 \simeq 0.1$ \citep[e.g.][]{groten2004fundamental,
+lainey2016quantification}]. In other studies, $3k_{\rm q} / 2 k$ is often
+notated as $k_2 / 2C$ \citep[e.g.][]{millholland_disk}. In Eq.~\eqref{eq:wlp},
+$n \equiv \sqrt{GM_\star/a^3}$ is the inner planet's orbital mean motion,  and
+we have assumed $a_{\rm p}\gg a$ and included only the leading-order
+(quadrupole) interaction between the inner planet and perturber. Following
+standard notation, we define $\alpha = \omega_{\rm sl}$ and $g \equiv
+-\omega_{\rm 1p} \cos I$ \citep[e.g.][]{colombo1966}.
 
@@
 tidal dissipation (i.e.\ satisfying $\rdil{\uv{s}}{t} = 0$).
-Figure~\ref{fig:6equilssingle} describes the evolution of
+Figure~\ref{fig:6equils006} describes the evolution of
 Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) qualitatively in the coordinates
 $(\Omega_{\rm s}, \theta)$, along with the locations of CS1 and CS2. The circled
-points in the panels of Fig.~\ref{fig:6equils} satisfy the criteria to be
-long-term equilibria, and we call them \emph{tidal Cassini Equilibria} (tCE). We
-number tCE1 and tCE2 the tCE that are in CSs 1 and 2 respectively. The
-obliquities of the tCE depend on the system architecture, which can be
-quantified using the parameter
+points in Fig.~\ref{fig:6equils006} satisfy the criteria to be long-term
+equilibria, and we call them \emph{tidal Cassini Equilibria} (tCE). We number
+tCE1 and tCE2 the tCE that are in CSs 1 and 2 respectively. The obliquities of
+the tCE depend on the system architecture, which can be quantified using the
+parameter
 \begin{align}
@@
 \end{align}
-In Fig.~\ref{fig:6equilssingle}, $\eta_{\rm sync} = 0.06$; the two panels of
-Fig.~\ref{fig:6equils} illustrate the change to the tCE when $\eta_{\rm sync} =
-0.5$ and $0.7$ respectively.
+In Fig.~\ref{fig:6equils006}, $\eta_{\rm sync} = 0.06$;
+Figs.~\ref{fig:6equils050}--\ref{fig:6equils070} illustrate the change to the
+tCE when $\eta_{\rm sync} = 0.5$ and $0.7$ respectively.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{../initial/1_weaktide/6equilssingle.png}
+    \includegraphics[width=\textwidth]{../initial/1_weaktide/6equils0_06.png}
     \caption{Schematic depiction of the effect of tidal friction on the planet's
@@
     Colombo's Top under weak tidal friction (for illustrative purposes, we have
-    used $\abs{g}t_{\rm s} = 10^2$). The phase space evolution of the two
-    thicker evolutionary trajectories (cyan and pink; those beginning at
-    $\theta_{\rm i} = 120^\circ$) are shown in
+    used $\abs{g}t_{\rm s} = 10^2$ and evolved each example for $5t_{\rm s}$).
+    The phase space evolution of the two thicker evolutionary trajectories (cyan
+    and pink; those beginning at $\theta_{\rm i} = 120^\circ$) are shown in
     Figs.~\ref{fig:trajs1}--\ref{fig:trajs2}.
-    }\label{fig:6equilssingle}
+    }\label{fig:6equils006}
+\end{figure*}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{../initial/1_weaktide/6equils0_50.png}
+    \caption{Same as Fig.~\ref{fig:6equils006} but for $\eta_{\rm sync} = 0.5$.
+    The light-colored crosses and lines correspond to evolutionary trajectories
+    using the same initial conditions as those shown in
+    Fig.~\ref{fig:6equils006}.}\label{fig:6equils050}
+\end{figure*}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{../initial/1_weaktide/6equils0_70.png}
+    \caption{Same as Figs.~\ref{fig:6equils006} and~\ref{fig:6equils050} but for
+    $\eta_{\rm sync} = 0.7$. Note that $\eta_{\rm sync} = 0.7 > \eta_{\rm c}
+    \approx 0.574$ and tCE1 does not exist. The phase space evolution of the
+    thick purple trajectory in the bottom panel (starting at $\theta_{\rm i}
+    = 10^\circ$) is shown in Fig.~\ref{fig:trajs3}. }\label{fig:6equils070}
 \end{figure*}
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils.png}
-    \caption{Same as Fig.~\ref{fig:6equilssingle} but for $\eta_{\rm sync} =
-    0.5$ and $\eta_{\rm sync} = 0.7$ in the two panels (labeled). Note in the
-    bottom panel that $\eta_{\rm sync} = 0.7 > \eta_{\rm c}$ and tCE1 does not
-    exist. In both panels, the light-colored crosses and lines correspond to
-    evolutionary trajectories using the same initial conditions as those shown
-    in Fig.~\ref{fig:6equilssingle}. The phase space evolution of the thick
-    purple trajectory in the bottom panel (starting at $\theta_{\rm i} \approx
-    10^\circ$) is shown in Fig.~\ref{fig:trajs3}. }\label{fig:6equils}
-\end{figure}
-\begin{figure}
-    \centering
     \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_2.png}
     \caption{Phase space evolution of the trajectory in
-    Fig.~\ref{fig:6equilssingle} colored in pink, for which $\eta_{\rm sync} =
-    0.06$ and $I = 20^\circ$. In the
-    left-most panel, the trajectory's evolution in $\p{\Omega_{\rm s}, \theta}$
-    coordinates along with the curves indicating CS1, 2, and $\dot{\Omega}_{\rm
-    s} = 0$ are re-displayed from Fig.~\ref{fig:6equilssingle}. The vertical
-    dashed lines denote the values of $\Omega_{\rm s}$ for which the phase space
-    evolution of the system is displayed in the right four panels. In each of
-    these right four panels, the trajectory's evolution for a single
-    circulation/libration cycle is displayed in $\p{\cos \theta, \phi}$ phase
-    space for the labeled value of $\Omega_{\rm s}$. The system encounters the
-    separatrix, undergoes a III $\to$ I transition, and converges to tCE1.
+    Fig.~\ref{fig:6equils006} colored in pink, for which $\eta_{\rm sync} =
+    0.06$ and $I = 20^\circ$ (for which $\eta_{\rm c} = 0.574$). The initial
+    conditions are $\Omega_{\rm s, i} = 2.5n$, $\theta_{\rm i} = 120^\circ$, and
+    $\phi_{\rm i} = 0^\circ$, and we have used $\abs{g}t_{\rm s} = 10^2$ and
+    have evolved the system for $5t_{\rm s}$. In the left-most panel, the
+    trajectory's evolution in $\p{\Omega_{\rm s}, \theta}$ coordinates along
+    with the curves indicating CS1, 2, and $\dot{\Omega}_{\rm s} = 0$ are
+    re-displayed from Fig.~\ref{fig:6equils006}. The vertical dashed lines
+    denote the values of $\Omega_{\rm s}$ for which the phase space evolution of
+    the system is displayed in the right four panels. In each of these right
+    four panels, the trajectory's evolution for a single circulation/libration
+    cycle is displayed in $\p{\cos \theta, \phi}$ phase space for the labeled
+    value of $\Omega_{\rm s}$. The system encounters the separatrix, undergoes a
+    III $\to$ I transition, and converges to tCE1.
     }\label{fig:trajs1}
@@
     \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_3.png}
-    \caption{Same as Fig.~\ref{fig:trajs1} but for the trajectory in
-    Fig.~\ref{fig:6equilssingle} colored in cyan, for which $\eta_{\rm sync} =
-    0.06$ and $I = 20^\circ$. The system encounters the
-    separatrix, undergoes a III $\to$ II transition, and converges to tCE2. Note
-    that the initial condition of this system and that displayed in
-    Fig.~\ref{fig:trajs1} have the same initial $\theta_{\rm i}$ and
-    $\Omega_{\rm s, i}$ and only different precessional phases $\phi_{\rm i}$.
+    \caption{Same as Fig.~\ref{fig:trajs1} but for $\phi_{\rm i} = 286^\circ$,
+    corresponding to the trajectory in Fig.~\ref{fig:6equils006} colored in
+    cyan. The system encounters the separatrix, undergoes a III $\to$ II
+    transition, and converges to tCE2. The small $\phi$ offset of tCE2 is
+    visible (see Fig.~\ref{fig:mcs}). Note that the initial condition of this
+    system and that displayed in Fig.~\ref{fig:trajs1} have the same initial
+    $\theta_{\rm i}$ and $\Omega_{\rm s, i}$ and only different precessional
+    phases $\phi_{\rm i}$.
     }\label{fig:trajs2}
@@
     \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils_sims/0_70_0.png}
-    \caption{Same as Fig.~\ref{fig:trajs1} but for the purple trajectory
-    shown in the bottom panel of Fig.~\ref{fig:6equils}, for which $\eta_{\rm
-    sync} = 0.7$ and $I = 20^\circ$. Here, the system
-    evolves along CS1 until the separatrix disappears, upon which it experiences
-    large obliquity variations that damp due to tidal dissipation. The system
-    finally converges to tCE2, the only tCE that exists for this value of
-    $\eta_{\rm sync}$ (see bottom panel of Fig.~\ref{fig:6equils}).}\label{fig:trajs3}
+    \caption{Same as Fig.~\ref{fig:trajs1} but for $\eta_{\rm sync} = 0.7$ and
+    $\theta_{\rm i} = 10^\circ$, corresponding to the purple trajectory shown in
+    the bottom panel of Fig.~\ref{fig:6equils070}. Here, the system evolves
+    along CS1 until the separatrix disappears, upon which it experiences large
+    obliquity variations that damp due to tidal dissipation. The highly
+    asymmetric shape in the third panel arises due to the strong tidal
+    dissipation used in this simulation. The system finally converges to tCE2,
+    the only tCE that exists for this value of $\eta_{\rm sync}$ (see bottom
+    panel of Fig.~\ref{fig:6equils070}).}\label{fig:trajs3}
 \end{figure}
@@
 of the tCE\@. First, if $\eta_{\rm sync} > \eta_{\rm c}$, then tCE1 will not
-exist, as can be seen in the bottom panel of
-Fig.~\ref{fig:6equils}\footnote{Strictly speaking, $\eta_{\rm sync}$ can be
-slightly smaller than $\eta_{\rm c}$, as the planet's spin is slightly
-subsynchronous at tCE1 when $\eta \approx \eta_{\rm c}$, see the top panel of
-Fig.~\ref{fig:6equils}.}. Secondly, tCE2 may not be stable if the tidal phase
-shift is too large. Applying the results of Section~\ref{ss:tidal_equils}, we
-find that tCE2 is stable as long as $t_{\rm s} \geq t_{\rm s, c}$ where
+exist, as can be seen in Fig.~\ref{fig:6equils070}\footnote{Strictly speaking,
+$\eta_{\rm sync}$ can be slightly smaller than $\eta_{\rm c}$, as the planet's
+spin is slightly subsynchronous at tCE1 when $\eta \approx \eta_{\rm c}$, e.g.\
+see Fig.~\ref{fig:6equils050}.}. Secondly, tCE2 may not be stable if the tidal
+phase shift is too large. Applying the results of Section~\ref{ss:tidal_equils},
+we find that tCE2 is stable as long as $t_{\rm s} \geq t_{\rm s, c}$ where
 \begin{equation}
@@
 We begin by qualitatively examining the example trajectories shown in
-Figs.~\ref{fig:6equilssingle}, for which we have integrated
-Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}). We discuss
-each of the six trajectories in turn:
+Figs.~\ref{fig:6equils006}, for which we have integrated
+Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) and set $I =
+20^\circ$. We discuss each of the six trajectories in turn:
 \begin{itemize}
@@
         $\theta_{\rm i} = 10^\circ$ (purple) has an initially prograde spin
-        (i.e.\ in zone I, see FIg.~\ref{fig:1contours}) and directly evolves to
+        (i.e.\ in zone I, see Fig.~\ref{fig:1contours}) and directly evolves to
         tCE1 as the obliquity damps to zero.
@@
         different initial precessional phases $\phi_{\rm i}$; we first discuss
-        the pink trajectory. This trajectory originates in zone III, evolves
-        towards the separatrix as tidal friction damps the obliquity, and
-        crosses the resonance without being captured, upon which the obliquity
-        continues to damp until the system converges to tCE1. The detailed phase
-        space evolution of this trajectory is shown in Fig.~\ref{fig:trajs1},
-        where the outcome of the separatrix encounter is very visible.
+        the pink trajectory, for which $\phi_{\rm i} = 0^\circ$. This trajectory
+        originates in zone III, evolves towards the separatrix as tidal friction
+        damps the obliquity, and crosses the resonance without being captured,
+        upon which the obliquity continues to damp until the system converges to
+        tCE1. The detailed phase space evolution of this trajectory is shown in
+        Fig.~\ref{fig:trajs1}, where the outcome of the separatrix encounter is
+        very visible.
 
@@
         and $\theta_{\rm i} = 120^\circ$ (light blue) only differs from the pink
-        trajectory in its value of $\phi_{\rm i}$. Nevertheless, this trajectory
-        originates in zone III, encounters the separatrix and is captured into
-        the resonance (zone II), upon which tidal friction drives the system
-        towards tCE2. The detailed phase space evolution of this trajectory is
-        shown in Fig.~\ref{fig:trajs2}, where the resonance capture is
-        displayed.
+        trajectory as its initial precessional phase is $\phi_{\rm i} \approx
+        286^\circ$. Nevertheless, this trajectory originates in zone III,
+        encounters the separatrix and is captured into the resonance (zone II),
+        upon which tidal friction drives the system towards tCE2. The detailed
+        phase space evolution of this trajectory is shown in
+        Fig.~\ref{fig:trajs2}, where the resonance capture is displayed. Also
+        visible in the final panel of Fig.~\ref{fig:trajs2} is the slight phase
+        offset of CS2, i.e.\ $\phi_{\rm cs} < 180^\circ$, in agreement with the
+        discussion in Section~\ref{ss:tidal_equils} (see Fig.~\ref{fig:mcs}).
 
@@
 
+        A subtlety of initially subsynchronous spins can be seen here: note that
+        the initial $\eta_{\rm i} = 0.6$ here, so the separatrix and CS1 do not
+        exist initially ($\eta_{\rm c} = 0.574$). As such, naively, one expects
+        initial convergence to CS2 and subsequent obliquity along with CS2 as
+        the spin increases. However, due to the strong tidal dissipation and the
+        proximity of $\eta_{\rm i}$ to $\eta_{\rm c}$, CS1 appears within a
+        single circulation cycle, and the obliquity quickly damps to, and
+        continues to evolve along, CS1.
+
     \item The trajectory with initial conditions $\Omega_{\rm s, i} = 0.1n$ and
         $\theta_{\rm i} = 100^\circ$ (teal) also has its obliquity rapidly
-        damped to zero as it approaches spin-orbit synchronization and tCE1.
-        However, we remark that this initial condition converges to tCE2 when a
-        tidal dissipation rate of $\abs{g}t_{\rm s} = 10^3$ is used.
+        damped to zero as it approaches spin-orbit synchronization and tCE1. For
+        these initial conditions, we remark that this initial condition
+        converges to tCE2 when a tidal dissipation rate of $\abs{g}t_{\rm s} =
+        10^3$ is used, satisfying the intuitive analysis given in the previous
+        paragraph.
 \end{itemize}
 For each of these six initial conditions, we also display their evolutionary
-trajectories for $\eta_{\rm sync} = 0.5$ and $\eta_{\rm sync} = 0.7$ in the two
-panels of Fig.~\ref{fig:6equils}. Of particular interest is the purple initial
-condition ($\Omega_{\rm s, i} = 2.5n$ and $\theta_{\rm i} = 10^\circ$) when
-$\eta_{\rm sync} = 0.7$. Figure~\ref{fig:trajs3} shows the detailed phase space
-evolution of this system, where it can be seen that the system initially evolves
-along the stable CS1, but is ejected when $\Omega_{\rm s}$ is sufficiently small
-that CS1 ceases to exist, upon which large obliquity variations eventually lead
-to convergence to tCE2, the only tCE that exists.
-
+trajectories for $\eta_{\rm sync} = 0.5$ and $\eta_{\rm sync} = 0.7$ in
+Figs.~\ref{fig:6equils050}--\ref{fig:6equils070}. The qualitative evolution of
+these six examples only changes in a few important ways, so we will discuss just
+a few points of interest:
+\begin{itemize}
+    \item For both $\eta_{\rm sync} = 0.5$ and $\eta_{\rm sync} = 0.7$, we see
+        that both initial conditions with $\theta_{\rm i} = 120^\circ$ converge
+        to tCE2. In fact, for these values of $\eta_{\rm sync}$, all initial
+        conditions with $\theta_{\rm i} = 120^\circ$ will converge to tCE2
+        regardless of $\phi_{\rm i}$.
+
+    \item The two subsynchronous initial conditions both evolve to tCE2 for both
+        $\eta_{\rm sync} = 0.5$ and $\eta_{\rm sync} = 0.7$, as in both cases
+        $\eta_{\rm i} \gg \eta_{\rm c}$ and CS2 is the only low-obliquity spin
+        equilibrium. The system then continues to evolve along CS2 until
+        reaching a state satisfying $\dot{\Omega}_{\rm s} = 0$ as well.
+
+    \item Of particular interest is the evolution starting from the initial
+        conditions $\Omega_{\rm s, i} = 2.5n$ and $\theta_{\rm i} = 10^\circ$
+        (purple) when $\eta_{\rm sync} = 0.7$. Figure~\ref{fig:trajs3} shows the
+        detailed phase space evolution of this system, where it can be seen that
+        the system initially evolves along the stable CS1, but is ejected when
+        $\Omega_{\rm s}$ is sufficiently small that CS1 ceases to exist, upon
+        which large obliquity variations eventually lead to convergence to tCE2,
+        the only tCE that exists.
+\end{itemize}
 It can be seen that the dynamics are complex and can vary greatly depending on
-the parameters used. For tractability, we restrict our attention to initial
-conditions satisfying $\Omega_{\rm s, i} \gg n$, and we adopt the fiducial value
-$\Omega_{\rm s, i} = 10n$. Then, for many initial $\theta_0$ and $\phi_0$, we
-can perform the same integration as above and verify which tCE a given initial
-condition evolves into. In Fig.~\ref{fig:Hhists_0_06}, we show the final outcome
-for many randomly chosen $\theta_0$ and $\phi_0$ for $\eta_{\rm sync} = 0.06$
-and $I = 20^\circ$. We see that the behavior seen in the example trajectories in
-Fig.~\ref{fig:6equilssingle} are general: tCE1 is generally reached for spins
-initially in zone I (like the purple trajectory in
-Fig.~\ref{fig:6equilssingle}), tCE2 is generally reached for spins initially in
-zone II (like the red trajectory in Fig.~\ref{fig:6equilssingle}), and a
+the parameters used. In the case where the initial spin is subsynchronous, the
+detailed outcome depends sensitively on $\eta_{\rm i}$ and the tidal dissipation
+rate. For tractability, we restrict our subsequent discussion to the more
+astrophysically common regime $\Omega_{\rm s, i} \gg n$, and we adopt the
+fiducial value $\Omega_{\rm s, i} = 10n$.
+
+Having developed an intuition for a few different possible evolutionary
+histories, we can next attempt to draw general conclusions about the final fate
+of the inner planet's spin as a function as a function of its initial
+conditions. We do this by again integrating
+Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) for many
+initial $\theta_0$ and $\phi_0$ and examining which tCE a given initial
+condition evolves into. For this study, we use a more gradual tidal dissipation
+rate of $\abs{gt_{\rm s}} = 10^3$. In Fig.~\ref{fig:Hhists_0_06}, we show the
+final outcome for many randomly chosen $\theta_0$ and $\phi_0$ for $\eta_{\rm
+sync} = 0.06$ and $I = 20^\circ$. We see that the behavior seen in the example
+trajectories in Fig.~\ref{fig:6equils006} are general: tCE1 is generally reached
+for spins initially in zone I (like the purple trajectory in
+Fig.~\ref{fig:6equils006}), tCE2 is generally reached for spins initially in
+zone II (like the red trajectory in Fig.~\ref{fig:6equils006}), and a
 probabilistic outcome is observed for spins initially in zone III (like the
-light blue and pink trajectories in Fig.~\ref{fig:6equilssingle}).
+light blue and pink trajectories in Fig.~\ref{fig:6equils006}).
 Figures~\ref{fig:Hhists_0_20} and~\ref{fig:Hhists_0_50} show the same results
@@
 obliquities are \emph{increased} by weak tidal friction (the bottom right
-region of panels of Fig.~\ref{fig:6equilssingle}). This increase means that even
+region of panels of Fig.~\ref{fig:6equils006}). This increase means that even
 initial conditions in zone I can sometimes be driven by tidal dissipation into
@@
 consider the probability of evolution into tCE2 when averaging over a
-distribution of initial spin orientations. For simplicity, we just consider
-$\uv{s}$ to be isotropically distributed; we discuss the impact of more
-physically realistic distributions of $\uv{s}$ in Section~\ref{s:summary}. The
-bottom panel of Fig.~\ref{fig:probs20} shows the probability of evolution into
-tCE2 for $I = 20^\circ$ as a function of $\eta_{\rm sync}$. It can be seen that
-tCE2 is reached with substantial probability ($\sim 50\%$) while it is also
-at a substantial obliquity ($\sim 60^\circ$) for $\eta_{\rm sync} \approx 0.4$.
-Furthermore, we note that initial conditions other than those beginning in zone
-II are responsible for a significant fraction of systems that converge to tCE2.
+distribution of initial spin orientations, which we denote $P_{\rm tCE2}$. For
+simplicity, we just consider $\uv{s}$ to be isotropically distributed; we
+discuss the impact of more physically realistic distributions of $\uv{s}$ in
+Section~\ref{s:summary}. The bottom panel of Fig.~\ref{fig:probs20} shows
+$P_{\rm tCE2}$ for $I = 20^\circ$ as a function of $\eta_{\rm sync}$. It can be
+seen that tCE2 is reached with substantial probability ($\sim 50\%$) while it is
+also at a substantial obliquity ($\sim 60^\circ$) for $\eta_{\rm sync} \approx
+0.4$.
 \begin{figure}
@@
     (vertical dashed line; Eq.~\ref{eq:def_etac}). \emph{Bottom:} Total
-    probability of ending up in tCE2 (red dots), averaged over an isotropic
-    initial spin orientation and taking $\Omega_{\rm s, i} = 10n$. The three
-    shaded regions denote the contribution of initial conditions in zones
-    I/II/III (labeled) to the total tCE2 probability in the isotropic average.
-    For example, among systems that converge to tCE2 for $\eta_{\rm sync} =
-    0.06$, more originate in zone III than zone II, and none originate in zone
-    I.}\label{fig:probs20}
+    probability of ending up in tCE2 ($P_{\rm tCE2}$; red dots), averaged over
+    an isotropic initial spin orientation and taking $\Omega_{\rm s, i} = 10n$.
+    The three shaded regions denote the contribution of initial conditions in
+    zones I/II/III (labeled) to the total tCE2 probability in the isotropic
+    average. For example, among systems that converge to tCE2 for $\eta_{\rm
+    sync} = 0.06$, more originate in zone III than zone II, and none originate
+    in zone I.}\label{fig:probs20}
 \end{figure}
@@
     5^\circ$.}\label{fig:probs5}
+\end{figure}
+
+When $\eta_{\rm sync} \ll 1$ and $\Omega_{\rm s} \gtrsim n$, an approximate
+analytical formula for $P_{\rm tCE2}$ can be obtained (see
+Appendix~\ref{app:ptce2}):
+\begin{align}
+    P_{\rm tCE2} &\simeq
+            \frac{4\sqrt{\eta _{\rm sync} \sin I}}{\pi}\s{
+                \sqrt{n / \Omega_{\rm s, i}}
+                + \frac{3}{2\p{1
+                + \sqrt{n / \Omega_{\rm s, i}}}}}.\label{eq:app_tce2_p_tot}
+\end{align}
+Eq.~\eqref{eq:app_tce2_p_tot} is shown in
+Figs.~\ref{fig:probs20}--\ref{fig:probs5} as the red dashed lines, where it
+agrees well with the numerical results (red dots) for $\eta_{\rm sync} \lesssim
+0.4$. To illustrate the predicted values of $P_{\rm tCE2}$ for small $\eta_{\rm
+sync}$, we display $P_{\rm tCE2}$ for $\eta_{\rm sync} \in \s{10^{-4}, 0.4}$ for
+both $I = 20^\circ$ and $I = 5^\circ$ in Fig.~\ref{fig:anal_ptce}. Note that no
+numerical results are presented for $\eta_{\rm sync} \leq 10^{-2}$, as the
+spin-orbit coupling becomes very strong and the integration slows dramatically
+due to the rapid precession of $\uv{s}$ about $\uv{l}$.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/1_weaktide/7anal_ptce.png}
+    \caption{Plot of $P_{\rm tCE2}$ for $I = 5^\circ$ and $I = 20^\circ$
+    (legend) shown on a log-log plot, to emphasize the scaling at small
+    $\eta_{\rm sync}$. The crosses are the results of numerical simulations as
+    shown in Figs.~\ref{fig:probs20}--\ref{fig:probs5}, the solid lines are
+    Eq.~\eqref{eq:app_tce2_p_tot} for $\Omega_{\rm s, i} = 10n$ and the dashed
+    lines are for $\Omega_{\rm s, i} = 3n$. \textcolor{red}{Note: The agreement
+    with the data are will change slightly once the numerical
+    precision issue is resolved.}}\label{fig:anal_ptce}
 \end{figure}
@@
             \p{\frac{a}{0.4\;\mathrm{AU}}}^{-9/2}.
+            \label{eq:sehj_ts}
 \end{align}
@@
             \p{\frac{m}{4 M_{\oplus}}}^{1/2}\nonumber\\
-        &\times \p{\frac{m_\star}{M_{\odot}}}^{-3/2}
+        &\times \p{\frac{M_\star}{M_{\odot}}}^{-3/2}
             \p{\frac{a}{0.4\;\mathrm{AU}}}^6
@@
             \p{\frac{R}{2 R_{\oplus}}}^{-3/2}.
-\end{align}
-Since $t_{\rm s} \gg t_{\rm s, c}$, we see that tCE2 is stable. Thus, we predict
-that a significant fraction of SEs with exterior CJ companions can have
-long-lived, significant obliquities ($\gtrsim 60^\circ$) due to being trapped in
-tCE2.
-
-% \textcolor{red}{Just a brief investigation:} Finally, we briefly consider the
-% possibility of tidal heating. Coarsely, we have that
-% \begin{align}
-%     \frac{\dot{a}}{a} &\sim -\frac{1}{10^{14}\;\mathrm{yr}}\p{1 -
-%         \frac{\Omega_{\rm s}}{n}\cos \theta},\\
-%     \dot{E}_{\rm orb} = \frac{GM_{\star}m}{2a}\frac{\dot{a}}{a}
-%         &\approx 10^{20}\;\mathrm{erg/s}\p{1 -
-%         \frac{\Omega_{\rm s}}{n}\cos \theta}.
-% \end{align}
-% The black body luminosity of the planet is expected to be $4 \times
-% 10^{25}\;\mathrm{erg/s}$ for the fiducial parameters, and so can probably be
-% ignored.
+            \label{eq:sehj_tsc}
+\end{align}
+Since $t_{\rm s} \gg t_{\rm s, c}$, we see that tCE2 is stable. In
+Fig.~\ref{fig:sehj_region}, we show the value of $\eta_{\rm sync}$ in the
+regions of $\p{a, a_{\rm p}}$ parameter space that satisfy the stability
+condition for tCE2. It can be seen that a generous portion of parameter space is
+able to generate and sustain inclined SEs. In summary, we predict that a
+significant fraction of SEs with exterior CJ companions can have long-lived,
+significant obliquities ($\gtrsim 60^\circ$) due to being trapped in tCE2.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{../initial/99_misc/5sehj_region.png}
+    \caption{Depiction of the values of $\eta_{\rm sync}$ for the Super Earth +
+    Cold Jupiter systems as a function of $a$ and $a_{\rm p}$ for $I = 20^\circ$
+    (top) and $I = 5^\circ$ (bottom). The SE is taken to have
+    $m = 4M_{\oplus}$ and $R = 2R_{\oplus}$ while the HJ is taken to have
+    $m_{\rm p} = M_{\rm J}$, and we have taken $k \approx k_{\rm q}$. We only
+    show the regions satisfying $t_{\rm s} \geq t_{\rm s, c}$ (the stability
+    condition for tCE2; Eqs.~\ref{eq:sehj_ts}--\ref{eq:sehj_tsc}). The line
+    satisfying $\eta_{\rm sync} = \eta_{\rm c}$ (Eq.~\ref{eq:def_etac}) is shown
+    as the black dashed line.}\label{fig:sehj_region}
+\end{figure}
 
@@
 In \citet{millholland2020formation}, the authors consider capture into the CS2
-resonance as part of a mechanism to form ultra-short period planets (USPs). They
-envision a process consisting of three stages:
+resonance as part of a mechanism to form ultra-short period planets (USPs).
+Their proposed mechanism consists of three stages:
 \begin{itemize}
@@
 
-Next, we investigate the outcome of the initial, rapid spin evolution. First,
-due to the small semi-major axis ratio, we must generalize Eq.~\eqref{eq:wlp}
-\citep[see e.g.][]{lai_2017}:
+Next, we investigate the outcome of the initial, rapid spin evolution. For
+simplicity, we will first consider the case with a single external perturber.
+First, since the considered systems are very compact, we must generalize
+Eq.~\eqref{eq:wlp} to small semi-major axis ratios \citep[see e.g.][]{lai_2017}:
 \begin{equation}
@@
 We have evaluated using $a / a_{\rm p}$ corresponding to a period ratio $P_{\rm
-p} / P = 1.5$, for which $f(\alpha) \approx 5.5$. For $I = 5^\circ$, roughly
+p} / P = 1.5$, for which $f(\alpha) \approx 5.5$. Note furthermore that $k /
+k_{\rm q} \approx 3$ for Earth-like planets \citep{groten2004fundamental,
+lainey2016quantification}. For $I = 5^\circ$, roughly
 consistent with typical proto-USP systems \citep{dai2018larger},
 Eq.~\eqref{eq:def_etac} shows that $\eta_{\rm sync} \ll \eta_{\rm c}$, and thus
-there are four CSs at spin-orbit synchronization. If, following
-\citet{millholland2020formation}, we take the initial planetary obliquity to be
-zero, the planet is guaranteed to evolve into tCE1, and not tCE2 (see
-Fig.~\ref{fig:Hhists_0_06}). If we assume instead a randomly oriented initial
-planetary spin, perhaps again due to early giant impacts, Fig.~\ref{fig:probs5}
-suggests that the probability of capture into tCE2 is still only modest
-($\lesssim 10\%$). A more sophisticated calculation including the effect of a
-third planet does not greatly modify these results. Note that this calculation
-is in tension with Fig.~4 of \citet{millholland2020formation}, where they find
-that $\eta \sim 1$ for the same physical parameters when $\Omega_{\rm s}$ is at
-its equilibrium value (i.e.\ satisfying Eq.~\ref{eq:weaktide_dWszero}, or
-$\Omega_{\rm s} \approx n$ when the obliquity is small).
+there are four CSs at spin-orbit synchronization. As such, if we take the
+initial planetary obliquity to be zero, the planet is guaranteed to evolve into
+tCE1, and not tCE2 (see Fig.~\ref{fig:Hhists_0_06}). If we assume instead a
+randomly oriented initial planetary spin, Fig.~\ref{fig:anal_ptce} suggests that
+the probability of capture into tCE2 is still only modest ($\lesssim 20\%$). A
+more sophisticated calculation including the effect of a third planet does not
+greatly modify these results.
+% Note that this calculation is in tension with
+% Fig.~4 of \citet{millholland2020formation}, where they find that $\eta \sim 1$
+% for the same physical parameters when $\Omega_{\rm s}$ is at its equilibrium
+% value (i.e.\ satisfying Eq.~\ref{eq:weaktide_dWszero}, or $\Omega_{\rm s}
+% \approx n$ when the obliquity is small).
 
@@
 \end{align}
-For $\eta_{\rm sync} \ll \eta_{\rm c}$, we can show that $\p{1 - \Omega_{\rm
-s}\cos \theta / n} \approx 1$ in tCE2 by using Eqs.~\eqref{eq:def_tce2_approx},
-so indeed the orbit of the proto-USP is able to decay within the lifetime of the
-system. On the other hand, in tCE1, $\omega_{\rm s} \approx n$ and $\cos \theta
-\approx 1 - \eta_{\rm sync}^2 \sin^2 I / 2$, so $\dot{a} / a$ is suppressed by a
-factor of $\sim \eta_{\rm sync}^2 \sin^2 I$. This shows that a proto-USP in tCE1
-is unable to initiate runaway orbital decay within the age of the system.
-Note that this constraint also implies $\eta_{\rm sync}$
-(Eq.~\ref{eq:etasync_usp}) cannot be increased by considering proto-USPs with
-larger values of $a$, as the initial orbital decay will become too slow.
+For $\eta_{\rm sync} \ll \eta_{\rm c}$, Eqs.~\eqref{eq:def_tce2_approx} imply
+that $\Omega_{\rm s}\cos \theta / n \ll 1$ in tCE2, so indeed the orbit of the
+proto-USP is able to decay within the lifetime of the system. On the other hand,
+in tCE1, $\omega_{\rm s} \approx n$ and $\cos \theta \approx 1 - \eta_{\rm
+sync}^2 \sin^2 I / 2$, so $\dot{a} / a$ is suppressed by a factor of $\sim
+\eta_{\rm sync}^2 \sin^2 I$. This shows that a proto-USP in tCE1 is unable to
+initiate runaway orbital decay within the age of the system. Note that this
+constraint also implies $\eta_{\rm sync}$ (Eq.~\ref{eq:etasync_usp}) cannot be
+increased by considering proto-USPs with larger values of $a$, as the initial
+orbital decay will become too slow.
 
@@
 
-In summary, our results for the formation of USPs via runaway tidal migration
-are in tension with those of \citet{millholland2020formation}. In particular, we
-find that only proto-USPs with a large primordial obliquity have a probability
-of evolving into tCE2 initially. Furthermore, proto-USPs that successfully
-initiate runaway tidal migration after reaching tCE2 will cease their inward
-migration before becoming a USP\@.
+In summary, our results suggest that only proto-USPs with a large primordial
+obliquity have a probability of evolving into tCE2 initially. Furthermore,
+proto-USPs that successfully initiate runaway tidal migration after reaching
+tCE2 will cease their inward migration before becoming a USP\@.
 
@@
 tidal dissipation in the HJ enhanced by being trapped in a high-obliquity CS due
-to an undetected exterior planet. In order for this scenario to be achieved,
-many conditions are necessary:
+to an undetected exterior planet. We validate the plausibility of this scenario
+by the relevant physical parameters as was done in the previous sections using
+the following current-day system parameters \citet{hebb2009wasp,
+maciejewski2013multi, millholland_wasp12b}: $R_\star = 1.63R_{\odot}$, $M_\star
+= 1.36M_{\odot}$, $R = 1.89R_{\rm J}$, $m = 1.41M_{\rm J}$, and $a = 0.023
+\;\mathrm{AU}$. We begin with the spin evolution timescale, which is given by:
+% 1 / (1.5 * 1e-6 * ((1.36 Msun) / (1.41 Mjup)) * ((1.89 Rjup) / (0.023 AU))^3 * 2 * pi / (0.023)^(3/2))
+% 6466.022710
+\begin{align}
+    \frac{1}{t_{\rm s}} ={}& \frac{1}{6000\;\mathrm{yr}}
+            \p{\frac{1}{4k}}
+            \p{\frac{2k_2/Q}{10^{-6}}}
+            \p{\frac{M_\star}{1.36 M_{\odot}}}^{3/2}\nonumber\\
+        &\times \p{\frac{m}{1.41 M_{\rm J}}}^{-1}
+            \p{\frac{R}{1.89 R_{\rm J}}}^{3}
+            \p{\frac{a}{0.023\;\mathrm{AU}}}^{-9/2}.
+\end{align}
+Thus, the spin of WASP-12b has plenty of time to find a tCE\@. We also wish to
+calculate $\eta_{\rm sync}$, but there are three complications: (i) the system
+likely instead has angular momentum hierarchy $L \gg L_{\rm p}$ (to be verified
+after the fact), opposite to that considered in the paper thus far; (ii) the
+properties of the hypothetical perturber are unknown; and (iii) we should
+evaluate $\eta_{\rm sync}$ using the value of $a$ for WASP-12b at the start of
+its orbital migration, not its present day value. Towards resolving complication
+(i), we express the precession of $\uv{l}$ about $\bm{J} = J\uv{\jmath} \equiv
+\bm{L} + \bm{L}_{\rm p}$, the total angular momentum axis, as
+\begin{equation}
+    \rd{\uv{l}}{t} = \omega_{\rm lp}\cos I \frac{J}{L_{\rm p}}
+        \p{\uv{l} \times \uv{\jmath}},
+        \label{eq:wasp12b_g}
+\end{equation}
+where $\omega_{\rm lp}$ is still given by Eq.~\eqref{eq:wlp}. Thus, we see that
+the precession frequency $\abs{g}$ is enhanced by a factor of $J / L_{\rm p}
+\approx L / L_{\rm p}$. Towards addressing complications (ii--iii),% chktex 8
+we use the fiducial values for the initial semi-major axis $a_{\rm i} =
+0.038\;\mathrm{AU}$ and initial semi-major axis ratio $a_{\rm p} / a_{\rm i} =
+1.29$, to be justified after the fact. We obtain:
+% 1/2 * (1.41 Mjup)^2 / (1.36 Msun)^2 * ((0.038 AU) / (1.89 Rjup))^3 * (0.038 / 0.05)^(3.5)
+% 0.014916
+\begin{align}
+    \eta_{\rm sync, i} ={}& 0.015 \cos I f(\alpha)
+            \p{\frac{m}{1.41M_J}}^2
+            \p{\frac{M_\star}{1.36M_{\odot}}}^{-2}
+            \nonumber\\
+        &\times
+            \p{\frac{a_{\rm i}}{0.038\;\mathrm{AU}}}^{3}
+            \p{\frac{a_{\rm p} / a_{\rm i}}{1.29}}^{-7/2}
+            \p{\frac{R}{1.89R_{\rm J}}}^{-3}.\label{eq:hj_etasync}
+\end{align}
+For these values of $a_{\rm i}$ and $a_{\rm p}$, $f(\alpha) \approx 5$.
+
+We next work towards justifying these choices of fiducial parameters. There are
+four physical and observational constraints on the WASP-12b + perturber system:
 \begin{itemize}
@@
 \end{itemize}
-Finally, if all four of these conditions are satisfied, the $\eta_{\rm sync}$ of
-the initial configuration can be used to estimate the likelihood of the spin of
-the HJ initally evolving into tCE2. We use the following current-day system
-parameters \citet{hebb2009wasp, maciejewski2013multi, millholland_wasp12b}:
-$R_\star = 1.63R_{\odot}$, $M_\star = 1.36M_{\odot}$, $R = 1.89R_{\rm J}$,
-$M_{\rm p} = 1.41M_{\rm J}$, and $a = 0.023 \;\mathrm{AU}$.
 
@@
 
-Next, we address the constraint that tCE2 is stable under the influence of the
-exterior planet. Due to the fact that the angular momentum of the HJ greatly
-exceeds that of the exterior planet ($L \gg L_{\rm p}$; we will verify this
-retroactively), Eq.~\eqref{eq:dldt1} needs to be modified. The precession of
-$\uv{l}$ about $\bm{J} = J\uv{\jmath} \equiv \bm{L} + \bm{L}_{\rm p}$, the total
-angular momentum axis, can be written as
-\begin{equation}
-    \rd{\uv{l}}{t} = \omega_{\rm lp}\cos I \frac{J}{L_{\rm p}}
-        \p{\uv{l} \times \uv{\jmath}},
-\end{equation}
-where $\omega_{\rm lp}$ is still given by Eq.~\eqref{eq:wlp}. Thus, we see that
-the precession frequency $\abs{g}$ is enhanced by a factor of $J / L_{\rm p}
-\approx L / L_{\rm p}$. With this modification, the stability of tCE2 requires
-\begin{equation}
-    \frac{1}{t_{\rm s}} \lesssim \omega_{\rm lp}\cos i \frac{L}{L_{\rm p}}
-        \sin I \sqrt{\frac{\eta_{\rm sync}\cos i}{2}}.
+Second, we address the constraint that tCE2 is stable under the influence of the
+exterior planet. Using the amended precession frequency $\abs{g}$ given by
+Eq.~\eqref{eq:wasp12b_g}, we compute that the stability of tCE2 requires
+\begin{equation}
+    \frac{1}{t_{\rm s}} \lesssim \omega_{\rm lp}\cos I \frac{L}{L_{\rm p}}
+        \sin i \sqrt{\frac{\eta_{\rm sync}\cos i}{2}}.
 \end{equation}
@@
 
-Next, we address the constraint that the RV signal of the exterior planet be
+Third, we address the constraint that the RV signal of the exterior planet be
 smaller than $16\;\mathrm{m/s}$, which requires
-% (G * (1.36 Msun) / (0.125 AU))^(1/2) * (105 Mearth) / (1.36 Msun) / 2^(1/2)
-% 16.106 m/s
-\begin{equation}
-    \p{\frac{a_{\rm p}}{0.125\;\mathrm{AU}}}^{-1/2}
-    \p{\frac{m_{\rm p}}{105M_{\oplus}}}
+% (G * (1.36 Msun) / (0.076 AU))^(1/2) * (80 Mearth) / (1.36 Msun) / 2^(1/2)
+% 15.737236 m\s
+\begin{equation}
+    \p{\frac{a_{\rm p}}{0.076\;\mathrm{AU}}}^{-1/2}
+    \p{\frac{m_{\rm p}}{80M_{\oplus}}}
     \p{\frac{M_\star}{1.36M_{\odot}}}^{-1/2}
@@
 where $i$ is the line-of-sight inclination angle. Here, we have taken $a_{\rm
-p}$ to be the maximum value permitted by the combination of
-Eqs.~(\ref{eq:hj_adot},~\ref{eq:hj_tce2_stab}). For these values of $a_{\rm p}$
-and $m_{\rm p}$, we still have $L / L_{\rm p} \sim 0.4$, and so $L \gg L_{\rm
-p}$ is well satisfied for the permitted parameter space.
+p}$ to be the maximum value permitted by Eq.~\eqref{eq:hj_tce2_stab}. For these
+values of $a_{\rm p}$ and $m_{\rm p}$, we still have $L / L_{\rm p} \sim 0.4$,
+and so $L \gg L_{\rm p}$ is well satisfied for the permitted parameter space as
+claimed.
 
@@
 \end{equation}
-
-By using the constraints given by Eqs.~(\ref{eq:hj_adot},~\ref{eq:hj_orbstab}),
-the initial $\eta_{\rm sync, i}$ can be constrained:
-% 1/2 * (1.41 Mjup)^2 / (1.36 Msun)^2 * ((0.038 AU) / (1.89 Rjup))^3 * (0.038 / 0.05)^(3.5)
-% 0.014916
-\begin{align}
-    \eta_{\rm sync, i} <{}& 0.015 \cos I f(\alpha)
-            \p{\frac{m}{1.41M_J}}^2
-            \p{\frac{M_\star}{1.36M_{\odot}}}^{-2}
-            \nonumber\\
-        &\times
-            \p{\frac{a_{\rm i}}{0.038\;\mathrm{AU}}}^{3}
-            \p{\frac{a_{\rm p} / a_{\rm i}}{1.29}}^{-7/2}
-            \p{\frac{R}{1.89R_{\rm J}}}^{-3}.\label{eq:hj_etasync}
-\end{align}
-For these values of $a_{\rm i}$ and $a_{\rm p}$, $f(\alpha) \approx 5$. It is
-possible that $R$ is larger today than its primordial value due to inflation
-induced by increased stellar irradiation. However, if a smaller value of $R$ is
-used in Eq.~\eqref{eq:hj_etasync}, the value of $a_{\rm i}$ must also be
-decreased such that $R^5 / a_{\rm i}^{13/2}$ is constant (Eq.~\ref{eq:hj_adot}),
-which further decreases $\eta_{\rm sync, i}$.
+The combination of the two constraints in
+Eqs.~(\ref{eq:hj_adot},~\ref{eq:hj_orbstab}) justify the fiducial parameters
+used in Eq.~\eqref{eq:hj_tce2_stab}.
+
+We next address the implications of the $\eta_{\rm sync}$ value found. When
+evaulating $\eta_{\rm sync}$ in Eq.~\eqref{eq:hj_tce2_stab}, it is possible
+that $R$ is larger today than its primordial value due to inflation induced by
+increased stellar irradiation. However, if a smaller value of $R$ is used in
+Eq.~\eqref{eq:hj_etasync}, the value of $a_{\rm i}$ must also be decreased such
+that $R^5 / a_{\rm i}^{13/2}$ is constant (Eq.~\ref{eq:hj_adot}), which further
+decreases $\eta_{\rm sync, i}$.
 
@@
         call these equilibria \emph{tidal Cassini Equilibria} (tCE\@; see
-        Fig.~\ref{fig:6equilssingle}). The locations of these equilibria are
+        Fig.~\ref{fig:6equils006}). The locations of these equilibria are
         determined by the system architecture and are parameterized by
@@
 
-    \item We show that which tCE a given initial planetary spin configuration
-        reaches can be probabilistic for certain initial conditions. For these
-        initial conditions, the probabilities of approaching either tCE can be
-        determined by careful study of the dynamics upon separatrix encounter
-        (Sections~\ref{ss:toy_outcomes} and~\ref{ss:phop_weaktide}). As an
-        example, if the initial spin orientation is assumed to be isotropically
-        distributed, the probabilities of entering tCE1 and tCE2 are given in
+    \item We show that if tCE1 exists ($\eta_{\rm sync} < \eta_{\rm c}$,
+        Eqs.~\ref{eq:def_etasync} and~\ref{eq:def_etac}; see discussion in
+        Section~\ref{ss:weaktide}), which tCE a given initial planetary spin
+        configuration asymptotically evolves towards depends on which of the
+        phase space zones (see Fig.~\ref{fig:1contours}) the initial spin
+        orientation belongs to: (i) If the spin originates in zone I, then it
+        generally evolves towards tCE1 (unless $\eta_{\rm sync}$ very near
+        $\eta_{\rm c}$, e.g.\ see Fig.~\ref{fig:Hhists_0_50}); (ii) if the spin
+        originates in zone II, then it evolves towards tCE2; and (iii) if the
+        spin originates in zone III, the outcome is generally probabilistic.
+
+    \item For initial conditions in zone III, the probabilities of approaching
+        either tCE can be determined by careful study of the dynamics upon
+        separatrix encounter (Sections~\ref{ss:toy_outcomes}
+        and~\ref{ss:phop_weaktide}). As an example, if the initial spin
+        orientation is assumed to be isotropically distributed, the
+        probabilities of entering tCE1 and tCE2 are given in
         Figs.~\ref{fig:probs20} and~\ref{fig:probs5} as a function of $\eta_{\rm
@@
 same analysis presented in this paper: The tCE can still be found by an analysis
-similar to that shown in Fig.~\ref{fig:6equilssingle}, and the probabilistic
+similar to that shown in Fig.~\ref{fig:6equils006}, and the probabilistic
 outcome of a separatrix encounter can still be solved using the techniques of
@@
 \section{Approximate TCE2 Probability for Small $\eta_{\rm sync}$
-}\label{app:sep_crossing_dynamics}
+}\label{app:ptce2}
 
@@
 crude approximation that $\eta_{\rm cross}$ is uniformly distributed between
-$\eta_{\rm i}$ and $\eta_{\rm sync}$. We thus obtain:
+$\eta_{\rm i}$ and $\eta_{\rm sync}$. Note that if $\Omega_{\rm s} \simeq n$,
+then this approximation is invalid: since nearly antialigned spins ($\theta_{\rm
+i} \approx 180^\circ$) will undergo significant spin-down before tidal friction
+can realign the spin orientation, $\Omega_{\rm s, i}$ being too close to $n$
+results in $\eta_{\rm cross} \ll \eta_{\rm sync}$. We thus obtain:
 \begin{align}
@@
     P_{\rm tCE2} &\simeq
-            \frac{4\sqrt{\eta _{\rm sync} \sin I}}{\pi}\p{
+            \frac{4\sqrt{\eta _{\rm sync} \sin I}}{\pi}\s{
                 \sqrt{n / \Omega_{\rm s, i}}
@@
                 + \sqrt{n / \Omega_{\rm s, i}}}}}
-            + \mathcal{O}\p{\eta_{\rm sync}}.\label{eq:app_tce2_p_tot}
-\end{align}
+            + \mathcal{O}\p{\eta_{\rm sync}}.
+\end{align}
+This is exactly Eq.~\eqref{eq:app_tce2_p_tot}. We remark again that this is
+valid in the regime where $\eta_{\rm sync} \ll 1$ and $\Omega_{\rm s} \gtrsim
+n$.
 

### 2021-05-29 initial/1_weaktide/6misc.py

@@ -16,7 +16,7 @@ from scipy.interpolate import interp1d
 plt.rc('xtick', direction='in', top=True, bottom=True)
 plt.rc('ytick', direction='in', left=True, right=True)
 
-POOL_SIZE = 50
+POOL_SIZE = 4
 TRAJ_COLORS = ['darkorchid', 'red', 'fuchsia',
                'deepskyblue', 'blue', 'teal', 'k', 'k']
 
@@ -76,7 +76,7 @@ def equils_plot(I, s_c, eps, mu0, phi0, s0, tf, fn_str, idx, rtol=1e-9,
     # axs[0].plot(s[last_idx], np.degrees(q)[last_idx], 'ko', markersize=2.0)
     axs[0].set_xlim(0, 3)
     axs[0].set_ylim(0, 135)
-    axs[0].set_xlabel(r'$\Omega_{\rm s}$')
+    axs[0].set_xlabel(r'$\Omega_{\rm s} / n$')
     axs[0].set_ylabel(r'$\theta$ (deg)')
     if s_c < 0.1:
         axs[0].set_title(r'$\eta_{\rm sync} = %.2f$' % s_c)
@@ -140,8 +140,9 @@ def equils_plot(I, s_c, eps, mu0, phi0, s0, tf, fn_str, idx, rtol=1e-9,
             H_grid = H(I, s_c, s[t_idx], mu_grid, phi_grid)
             ax.contour(phi_grid, mu_grid, H_grid, levels=[H4], colors='k')
 
-        ax.text(0.1, -1 + 0.03, r'$\Omega_{\rm s} = %.1f$' % s[t_idx],
-                ha='left', va='bottom', color='k', fontsize=14)
+        ax.text(0.1, -1 + 0.05, r'$\Omega_{\rm s} = %.1f n$, $\eta = %.2f$'
+                % (s[t_idx], s_c / s[t_idx]),
+                ha='left', va='bottom', color='k', fontsize=11)
 
         if np.min(mu_plt) < -0.9:
             ylim_bot =-1.1
@@ -172,124 +173,46 @@ def plot_equils(I, s_cs, fn_str='6equils', tf=5000):
 
     s_dq = np.linspace(2, 3, 200)
 
-    fig = plt.figure(figsize=(8, 6))
-    ax = plt.gca()
+    for s_c in s_cs:
+        fig = plt.figure(figsize=(8, 6))
+        ax = plt.gca()
 
[…]

### 2021-05-29 initial/99_misc/5discussion_plots.py

@@ -2,6 +2,7 @@ import numpy as np
 import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
+import matplotlib.cm as cm
 plt.rc('text', usetex=True)
 plt.rc('font', family='serif', size=20)
 plt.rc('lines', lw=2.5)
@@ -42,12 +43,6 @@ def plot_actives():
     plt.close()
 
 def plot_eigens():
-    # for j in range(3):
-    #     for k in range(3):
-    #         if j != k:
-    #             q = 3 if k > j else 2
-    #             print(j, k, ':', j + (2 * np.abs(k - j) * q / 3))
-    # return
     gamma = 1 / np.linspace(1.1, 2.0, 20)
     eigs = []
     for g in gamma:
@@ -64,5 +59,59 @@ def plot_eigens():
     plt.savefig('5eigs', dpi=300)
     plt.close()
 
+def get_etac(I):
+    return (np.sin(I)**(2/3) + np.cos(I)**(2/3))**(-3/2)
+
+def plot_sehj_region():
+    a_vals = np.geomspace(0.2, 0.6, 101)
+    ap_vals = np.geomspace(2, 20, 101)
+    a_grid = np.outer(a_vals, np.ones_like(ap_vals))
+    ap_grid = np.outer(np.ones_like(a_vals), ap_vals)
+
+    fig = plt.figure(figsize=(6, 8))
+    ax1 = plt.axes([0.12, 0.55, 0.65, 0.42])
+    ax2 = plt.axes([0.12, 0.1, 0.65, 0.42])
+    cax = plt.axes([0.79, 0.1, 0.03, 0.87])
+    for ax, Id in zip([ax1, ax2], [20, 5]):
+        I = np.radians(Id)
+        etasync = 0.303 * np.cos(I) * (a_grid / 0.4)**6 / (ap_grid / 5)
+        etasync_min = np.floor(np.log10(etasync[0, 0]))
+        etasync_max = np.ceil(np.log10(etasync.max()))
+        etasync_norm = np.minimum(
+                         np.maximum(etasync_min - 0.05, np.log10(etasync)),
+                         etasync_max,
+                     )
+        cf = ax.contourf(a_grid, ap_grid, etasync_norm)
+
+        aout_tsc_crit = (
+            (100 * (a_vals / 0.4)**(21/2) * np.sin(I) *
+                 np.cos(I)**2)**(2/9) * 5)
[…]

### 2021-05-30 writeups/Su_weak_tides.tex
double spaced, rename

@@
         usenatbib,
-        % referee,
+        referee,
     ]{mnras}
@@
 
+    \newlength{\colummwidth}
+    \setlength{\colummwidth}{246.0pt} % columnwidth for reprint
+
 \title[Weak Tides and Cassini States]{Dynamics of Colombo's Top: Tidal
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/99_misc/2_cs_locs_phi.png}
+    \includegraphics[width=\colummwidth]{../initial/99_misc/2_cs_locs_phi.png}
     \caption{Cassini State obliquities $\theta$ as a function of $\eta \equiv
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/0_eta/1contours20.png}
+    \includegraphics[width=\colummwidth]{../initial/0_eta/1contours20.png}
     \caption{Level curves of the Cassini State Hamiltonian (Eq.~\ref{eq:H}) for
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/99_misc/0_stab.png}
+    \includegraphics[width=\colummwidth]{../initial/99_misc/0_stab.png}
     \caption{Modified CS obliquities (top) and azimuthal angles (bottom) for $I
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/99_misc/2_lambdas_full.png}
+    \includegraphics[width=\colummwidth]{../initial/99_misc/2_lambdas_full.png}
     \caption{$\lambda_0^2$ (Eq.~\ref{eq:def_l0_sq}) as a function of $\eta$ for
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/0_eta/3stats3_5_0_2.png}
+    \includegraphics[width=\colummwidth]{../initial/0_eta/3stats3_5_0_2.png}
     \caption{Plot illustrating the asymptotic behavior of initial conditions for
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/0_eta/6manifolds0_20.png}
+    \includegraphics[width=\colummwidth]{../initial/0_eta/6manifolds0_20.png}
     \caption{Plot illustrating the probabilistic origin of separatrix capture
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/3_toy3/1hist_toy.png}
+    \includegraphics[width=\colummwidth]{../initial/3_toy3/1hist_toy.png}
     \caption{Plot of $P_{\rm III \to II}$ as a function of $\eta$ for the
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_2.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/6equils_sims/0_06_2.png}
     \caption{Phase space evolution of the trajectory in
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils_sims/0_06_3.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/6equils_sims/0_06_3.png}
     \caption{Same as Fig.~\ref{fig:trajs1} but for $\phi_{\rm i} = 286^\circ$,
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/6equils_sims/0_70_0.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/6equils_sims/0_70_0.png}
     \caption{Same as Fig.~\ref{fig:trajs1} but for $\eta_{\rm sync} = 0.7$ and
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_06_20.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/5Hhists0_06_20.png}
     \caption{\emph{Left:} Each dot indicates which tCE a given initial condition
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_20_20.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/5Hhists0_20_20.png}
     \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\eta_{\rm sync} =
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5Hhists0_50_20.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/5Hhists0_50_20.png}
     \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\eta_{\rm sync} =
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_06_20.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/5pc_fits0_06_20.png}
     \caption{Comparison of the fraction of systems converging to tCE2 obtained
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5pc_fits0_20_20.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/5pc_fits0_20_20.png}
     \caption{Same as Fig.~\ref{fig:pc_fits_0_06} but for $\eta_{\rm sync} =
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5probs_20.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/5probs_20.png}
     \caption{\emph{Top:} Obliquities of the two tCE where $I = 20^\circ$ for a
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/5probs_5.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/5probs_5.png}
     \caption{Same as Fig.~\ref{fig:probs20} but for $I =
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/1_weaktide/7anal_ptce.png}
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/7anal_ptce.png}
     \caption{Plot of $P_{\rm tCE2}$ for $I = 5^\circ$ and $I = 20^\circ$
@@
     \centering
-    \includegraphics[width=\columnwidth]{../initial/99_misc/5sehj_region.png}
+    \includegraphics[width=\colummwidth]{../initial/99_misc/5sehj_region.png}
     \caption{Depiction of the values of $\eta_{\rm sync}$ for the Super Earth +

### 2021-06-01 weeklies/YS_210601.tex
nplanet weekly

    \documentclass[11pt,
        usenames, % allows access to some tikz colors
        dvipsnames % more colors: https://en.wikibooks.org/wiki/LaTeX/Colors
    ]{article}
    \usepackage{
        amsmath,
        amssymb,
        fouriernc, % fourier font w/ new century book
        fancyhdr, % page styling
        lastpage, % footer fanciness
        hyperref, % various links
        setspace, % line spacing
        amsthm, % newtheorem and proof environment
        mathtools, % \Aboxed for boxing inside aligns, among others
        float, % Allow [H] figure env alignment
        enumerate, % Allow custom enumerate numbering
        graphicx, % allow includegraphics with more filetypes
        wasysym, % \smiley!
        upgreek, % \upmu for \mum macro
        listings, % writing TrueType fonts and including code prettily
        tikz, % drawing things
        booktabs, % \bottomrule instead of hline apparently
        xcolor, % colored text
        cancel % can cancel things out!
    }
    \usepackage[margin=1in]{geometry} % page geometry
    \usepackage[
        labelfont=bf, % caption names are labeled in bold
        font=scriptsize % smaller font for captions
    ]{caption}
    \usepackage[font=scriptsize]{subcaption} % subfigures

    \newcommand*{\scinot}[2]{#1\times10^{#2}}
    \newcommand*{\dotp}[2]{\left<#1\,\middle|\,#2\right>}
    \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
    \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
    \newcommand*{\rdil}[2]{\mathrm{d}#1 / \mathrm{d}#2}
    \newcommand*{\pdil}[2]{\partial#1 / \partial#2}
    \newcommand*{\rtd}[2]{\frac{\mathrm{d}^2#1}{\mathrm{d}#2^2}}
    \newcommand*{\ptd}[2]{\frac{\partial^2 #1}{\partial#2^2}}
    \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
    \newcommand*{\pvec}[1]{\vec{#1}^{\,\prime}}
    \newcommand*{\svec}[1]{\vec{#1}\;\!}
    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
    \newcommand*{\uv}[1]{\hat{\bm{#1}}}
    \newcommand*{\ang}[0]{\;\text{\AA}}
    \newcommand*{\mum}[0]{\;\upmu \mathrm{m}}
    \newcommand*{\at}[1]{\left.#1\right|}
    \newcommand*{\bra}[1]{\left<#1\right|}
    \newcommand*{\ket}[1]{\left|#1\right>}
    \newcommand*{\abs}[1]{\left|#1\right|}
    \newcommand*{\ev}[1]{\left\langle#1\right\rangle}
    \newcommand*{\p}[1]{\left(#1\right)}
    \newcommand*{\s}[1]{\left[#1\right]}
    \newcommand*{\z}[1]{\left\{#1\right\}}

    \newtheorem{theorem}{Theorem}[section]

    \let\Re\undefined
    \let\Im\undefined
    \DeclareMathOperator{\Res}{Res}
    \DeclareMathOperator{\Re}{Re}
    \DeclareMathOperator{\Im}{Im}
    \DeclareMathOperator{\Log}{Log}
    \DeclareMathOperator{\Arg}{Arg}
    \DeclareMathOperator{\Tr}{Tr}
    \DeclareMathOperator{\E}{E}
    \DeclareMathOperator{\Var}{Var}
    \DeclareMathOperator*{\argmin}{argmin}
    \DeclareMathOperator*{\argmax}{argmax}
    \DeclareMathOperator{\sgn}{sgn}
    \DeclareMathOperator{\diag}{diag\;}

    \colorlet{Corr}{red}

    % \everymath{\displaystyle} % biggify limits of inline sums and integrals
    \tikzstyle{circ} % usage: \node[circ, placement] (label) {text};
        = [draw, circle, fill=white, node distance=3cm, minimum height=2em]
    \definecolor{commentgreen}{rgb}{0,0.6,0}
    \lstset{
        basicstyle=\ttfamily\footnotesize,
        frame=single,
        numbers=left,
        showstringspaces=false,
        keywordstyle=\color{blue},
        stringstyle=\color{purple},
        commentstyle=\color{commentgreen},
        morecomment=[l][\color{magenta}]{\#}
    }

\begin{document}

\section{3-Planet Cassini State Modeling}

\subsection{Code Description}

I have a code that solves the following equations for $N$ planets, $1 \leq i
\leq N$:
\begin{align}
    \rd{\uv{s}_i}{t}
        &= \alpha_i \p{\uv{s}_i \cdot \uv{l}_i}\p{\uv{s}_i \times \uv{l}_i}
            + \epsilon_{\rm tide}\p{\uv{s}_i \times \p{\uv{l}_i \times \uv{s}_i}
                },\\
    \rd{\uv{l}_i}{t}
        &= \sum\limits_{j \neq i}
            \omega_{ji} \p{\uv{l}_j \cdot \uv{l}_i}
                \p{\uv{l}_j \cdot \uv{l}_i},\\
    \alpha_i &= \frac{3k_{\rm q}}{2k}
        \frac{M_\star}{m_i}
        \p{\frac{R_i}{a_i}}^3
        \Omega_{\rm s, i},\\
    \omega_{ji} &= \frac{3m_>}{4M_\star}
        \p{\frac{a_<}{a_>}}^3
        n_<
        f(\alpha) \times
        \begin{cases}
            1 & j > i\\
            \frac{L_j}{L_i} & j < i.
        \end{cases},\\
    \rd{\Omega_{\rm s, i}}{t} &= \epsilon_{\rm spin} \Omega_{\rm s, i}.
\end{align}
These vector+spin equations are evolved in an inertial frame. Define $\uv{j}$ to
be aligned with the total angular momentum axis, then we define the coordinate
system for each possible CS of each spin:
\begin{align}
    \uv{Z}_i &= \uv{l}_i,\\
    \uv{X}_i &\propto \uv{j} - \p{\uv{j} \cdot \uv{l}_i}\uv{l}_i,\\
    \uv{Y}_i &= \uv{Z}_i \times \uv{X}_i,\\
    \cos \theta_i &= \uv{s}_i \cdot \uv{Z}_i,\\
    \tan \phi_i &= \frac{\uv{s}_i \cdot \uv{X}_i}{\uv{s}_i \cdot \uv{Y}_i}.
\end{align}
In other words, $\phi_i$ is defined in the frame \emph{corotating} with
$\uv{l}_i$ about $\uv{j}$.

\subsection{Dynamics}

Note that there are two options to introduce dynamics: either $\epsilon_{\rm
spin}$ (not a physical model; we will use both spinup and spindown), or
$\epsilon_{\rm tide}$, an alignment torque. For each set of parameters, we will
show four groups of panels: one with no dynamics, one with only $\epsilon_{\rm
spin}$, one with only $\epsilon_{\rm tide}$, then one with both an
$\epsilon_{\rm spin}$ and an $\epsilon_{\rm tide}$. In all cases, the $\epsilon
\sim 10^{-3}\;\mathrm{/yr}$.
\begin{figure}
    \centering
    \includegraphics[width=0.48\columnwidth]{../initial/4nplanet/2_3p_mode1.png}
    \includegraphics[width=0.48\columnwidth]{../initial/4nplanet/2_dissipative1.png}

    \includegraphics[width=0.48\columnwidth]{../initial/4nplanet/2_dynamical1.png}
    \includegraphics[width=0.48\columnwidth]{../initial/4nplanet/2_dynamicaltide1.png}
    \caption{Case 1. Modes are as labeled in Panel 4. Corresponding CS2
    obliquities are labeled in Panel 2.}\label{fig:1}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.48\columnwidth]{../initial/4nplanet/2_3p_mode1_2.png}
    \includegraphics[width=0.48\columnwidth]{../initial/4nplanet/2_dissipative1_2.png}

    \includegraphics[width=0.48\columnwidth]{../initial/4nplanet/2_dynamical1_2.png}
    \includegraphics[width=0.48\columnwidth]{../initial/4nplanet/2_dynamicaltide1_2.png}
    \caption{Case 2, offset from Case 1 by $\phi_{\rm i} = 180^\circ$.}\label{fig:2}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_3p_mode2.png}
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_dynamical2.png}
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_dynamicaltide2.png}
    \caption{Case 3; dissipative case is missing.}\label{fig:5}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_3p_mode3.png}
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_dynamical3.png}
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_dynamicaltide3.png}
    \caption{Case 4, offset from case 3 by $\phi_{\rm i} = 180^\circ$;
    dissipative case is missing.}\label{fig:6}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_no_spinup3.png}
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_spinup3.png}
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_spinupdisp3.png}
    \caption{Spinup case; pure dissipative case is missing}\label{fig:3}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_no_spinup4.png}
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_spinup4.png}
    \includegraphics[width=0.32\columnwidth]{../initial/4nplanet/2_spinupdisp4.png}
    \caption{Another spinup case; pure dissipative case is missing}\label{fig:4}
\end{figure}

Among these, there are a few major takeaways:
\begin{itemize}
    \item There is a limit cycle where the angle $\phi_{\rm inertial} + g_>t =
        \phi_{\rm rot} - g_<t$ is circulating (see e.g.\ third group of panels
        in Fig.~\ref{fig:1}). I suspect that this is an interesting limit cycle,
        but may not strictly be a ``resonance''? I'm not sure.

    \item It seems to be hard to be caught in the $g_<$ resonance when both
        $\eta$'s are initially small: compare Figs.~\ref{fig:1}--\ref{fig:2}. On
        the other hand, when the large $\eta$ is already large, the resonances
        are well separated, and it's possible to be advected along, see
        Fig.~\ref{fig:5}.

    \item During spinup, parameters can be finely tuned to be ``caught'' by
        either resonance (Figs.~\ref{fig:3}--\ref{fig:4}).
\end{itemize}
However, no resonant angle appears during these resonance advection phases\dots
why is that? Only the ``limit cycle'' seems to have a resonant angle, but it
doesn't seem to advect at all.

\end{document}

### 2021-06-01 initial/1_weaktide/7anal_ptce.py

@@ -51,7 +51,7 @@ s_c_vals = {
         0.25,
         0.1,
         0.03,
-        0.01,
+        # 0.01,
     ]
 }
 

### 2021-06-01 initial/4nplanet/2sim.py

@@ -1,0 +1,1253 @@
+import os, pickle, lzma
+import scipy.optimize as opt
+import time
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif', size=20)
+plt.rc('lines', lw=2.5)
+plt.rc('xtick', direction='in', top=True, bottom=True)
+plt.rc('ytick', direction='in', left=True, right=True)
+
+from scipy.integrate import solve_ivp
+
+k = 39.4751488
+MEARTH = 3e-6
+REARTH = 4.7e-5
+# length = AU
+# unit of time = 499s * 6.32e4 = 1yr
+# unit of mass = solar mass, solve for M using N1 + distance in correct units
+
+def roots(I, eta):
+    ''' returns theta roots from EOM '''
+    eta_c = get_etac(I)
+
+    # function to minimize and derivatives
+    f = lambda q: -eta * np.sin(q - I) + np.sin(q) * np.cos(q)
+    fp = lambda q: -eta * np.cos(q - I) + np.cos(2 * q)
+
+    if eta < eta_c:
+        roots = []
+        inits = [0, np.pi / 2, -np.pi, -np.pi / 2]
+        for qi in inits:
+            roots.append(opt.newton(f, qi, fprime=fp))
+        return np.array(roots)
+    elif eta > 5: # buggy case, vanishing gradient?
+        return np.array([I, np.pi - I])
+    else:
+        roots = []
+        inits = [np.pi / 2 - I, -np.pi + I]
+        for qi in inits:
+            roots.append(opt.newton(f, qi, fprime=fp))
+        return np.array(roots)
+
+def get_etac(I):
+    return (np.sin(I)**(2/3) + np.cos(I)**(2/3))**(-3/2)
+
+def reg(z):
+    return np.minimum(np.maximum(z, -1), 1)
+
+def ts_dot(x, y):
+    ''' dot product of two time series (is there a better way?) '''
+    z = np.zeros(np.shape(x)[1])
+    for x1, y1 in zip(x, y):
+        z += x1 * y1
+    return reg(z)
+
+def ts_dot_hat(x, yhat):
+    ''' dot product of time series w/ const vec '''
+    z = np.zeros(np.shape(x)[1])
[…]

### 2021-06-01 initial/4nplanet/calc.py

@@ -1,274 +1,0 @@
-import os, pickle, lzma
-from scipy.fft import fft, fftfreq
-from scipy.interpolate import interp1d
-import numpy as np
-import matplotlib
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-plt.rc('text', usetex=True)
-plt.rc('font', family='serif', size=20)
-plt.rc('lines', lw=2.5)
-plt.rc('xtick', direction='in', top=True, bottom=True)
-plt.rc('ytick', direction='in', left=True, right=True)
-
-MEARTH = 3e-6
-REARTH = 4.7e-5
-
-def generate_txt(mps=[1, 10], p_rat=1.5, Is=[1, 5], prefix='', ain=0.035,
-                 **kwargs):
-    with open('rings_usp/in%s.txt' % prefix, 'w') as f:
-        sun_line = [1e9, 0, 1, 0, 0, 0, 0] # tV k I R Spin0 Spin1 Spin2
-        f.write(' '.join(['%e' % l for l in sun_line]))
-        f.write('\n')
-        for idx, (mp, I) in enumerate(zip(mps, Is)):
-            planet_dat = [
-                mp * MEARTH, # m
-                ain * (p_rat)**(idx * 2/3), # a
-                1e-3, # e
-                I, # I
-                0, 0, 1e9, 0, 0, 0, # Omega omega tV k I R
-                0, 0, 0 # spin
-            ]
-            f.write(' '.join(['%e' % l for l in planet_dat]))
-            f.write('\n')
-
-def get_laplace(a, j=1):
-    '''
-    b_{3/2}^1(a) / 3 * a, determined numerically
-    '''
-    psi = np.linspace(0, 2 * np.pi, 10000)
-    integrand = np.cos(j * psi) / (
-        1 - 2 * a * np.cos(psi) + a**2)**(3/2)
-    return np.mean(integrand) * 2 / (3 * a)
-
-def run_txt(t='1e6', prefix='', tol='1e-10', **kwargs):
-    cmd = (
-        'rings --input rings_usp/in{p}.txt --output rings_usp/out{p}.txt --time {t} '
-        '--epsint {tol}'
-        .format(p=prefix, t=t, tol=tol)
-    )
-    print(cmd)
-    os.system(cmd)
-
-def get_peaks(powers, npeaks=1):
-    p_idxs = np.argsort(powers)[::-1]
[…]

### 2021-06-04 notes/np_notes.tex
GM210603

@@
 
-\section{05/25/21}
+\section{06/02/21---Simple Parameterized Model}
 
-TODO Fill in the calculation of the inclination.
+\subsection{Orbital Dynamics}
 
-We start with the solution for the inner orbit's inclination
+We consider the 3-planet case with an inner test mass, as Dong did, for
+simplicity. This is not quantitatively exact but gives us an intuitive
+parameterization (to leading order) of realistic dynamics.
+
+Consider the mutual precession of an inner test particle and two outer planets.
+Define the complex inclination $\mathcal{I}_j = I_j\exp\p{i\Omega_j}$, then
+these evolve following
+\begin{align}
+    \rd{}{t}\begin{bmatrix}
+        \mathcal{I}_1\\
+        \mathcal{I}_2\\
+        \mathcal{I}_3
+    \end{bmatrix} &=
+        \begin{bmatrix}
+            -\omega_{21} - \omega_{31} & \omega_{21} & \omega_{31}\\
+            0 & -\omega_{32} & \omega_{32}\\
+            0 & \omega_{23} & -\omega_{23}
+        \end{bmatrix}
+    \begin{bmatrix}
+        \mathcal{I}_1\\
+        \mathcal{I}_2\\
+        \mathcal{I}_3
+    \end{bmatrix},\label{eq:06/02/21.LL_matrix}\\
+    \omega_{kj}
+        &= -\frac{3 m_>}{4 M_\star}\p{\frac{a_>}{a_<}}^3 n_<
+            f\p{\frac{a_<}{a_>}}
+            \times \min\p{\frac{L_k}{L_j}, 1},\\
+    f\p{\alpha} &= \frac{b_{3/2}^{(1)}}{3\alpha}\nonumber\\
+        &= \frac{1}{3\alpha}
+            \frac{1}{\pi}\int\limits_0^{2\pi}
+                \frac{\cos \p{t}}{
+                \p{\alpha^2 + 1 - 2\alpha \cos t}^{3/2}}\;\mathrm{d}t\nonumber\\
+        &\approx 1 + \frac{15}{8}\alpha^2 + \mathcal{O}\p{\alpha^4}.
+\end{align}
+Note that this $\min$ term means e.g.\ that $\omega_{23} =
+\omega_{32}\frac{L_2}{L_3}$.
+
+We seek the eigenmodes of Eq.~\eqref{eq:06/02/21.LL_matrix}. It is expected that
+there will only be two: a third is if $\mathcal{I}_i = 0$, i.e.\ if everything
+is aligned with the total angular momentum. Otherwise:
+\begin{itemize}
+    \item The first obvious, non-trivial eigenmode is $\mathcal{I}_2 =
+        \mathcal{I}_3 = 0$, then $\mathcal{I}_1$ executes free precession with
+        the precession frequency $g_1 \equiv -\omega_{21} - \omega_{31}$.
+
+    \item We expect the second eigenmode to describe precession of
+        $\mathcal{I}_2$ and $\mathcal{I}_3$ about their total angular momentum
+        axis. Upon inspection, we find that the second eigenvector must indeed
+        satisfy:
         \begin{equation}
-    \mathcal{I}(t) = Ae^{ig_It} + Be^{ig_{II} t},
+            \mathcal{I}_2 = -\frac{L_3}{L_2}\mathcal{I}_3.
         \end{equation}
-where $A$ and $B$ are generally complex ($A$ can be chosen to be real by
-choosing the initial phase). If we seek a CS with the frequency $g_I$, then we
-can go to the corotating frame, in which case
+        The eigenvalue can also be directly read off in this case to be
+        $\omega_{32}\p{-1 - L_2/L_3} \approx -\omega_{32}(J / L_3) \equiv g_2$,
+        where $J \approx L_2 + L_3$. Then, we can find that the corresponding
+        component of $\mathcal{I}_1$ must satisfy
+        \begin{align}
+            g_1\mathcal{I}_1
+                + \omega_{21}\mathcal{I}_2 + \omega_{31}\mathcal{I}_3
+                &= g_2\mathcal{I}_1,\\
+            \p{g_2 - g_1}\mathcal{I}_1 &=
+                \p{\omega_{21}\frac{L_3}{J}
+                    + \omega_{31}\frac{L_2}{J}}\mathcal{I}_{23},\\
+            \mathcal{I}_1 &= \frac{\p{\omega_{21}L_3
+                    + \omega_{31}L_2} / J}{g_2 - g_1}\mathcal{I}_{23}.
+        \end{align}
+\end{itemize}
+Here, $\mathcal{I}_{23} = \mathcal{I}_3 - \mathcal{I}_2$ and corresponds to the
+complexified mutual inclination. Thus, the general solution to
+$\mathcal{I}_1(t)$ is given by:
 \begin{equation}
-    \mathcal{I}_{\rm rot}(t) = I_0 + Be^{i\p{g_{II} - g_I}t}.
+    \mathcal{I}_1(t) = i_1e^{ig_1t} + i_{\rm 1f}e^{i(g_2t + \phi_0)},
 \end{equation}
-With appropriate choice of initial time/phase, $B$ can be chosen to be real as
-well. Define $g' = g_{II} - g_I$. Intuitively, there are four cases near CS2:
+where $i_1$, $i_{\rm 1f}$, and $\phi_0$ are real. Then, of course, we can
+construct the vector solution to $\uv{l}_1$ via:
+\begin{align}
+    \uv{l}_1 &= \Re \mathcal{I}_1\uv{x}
+            + \Im \mathcal{I}_1 \uv{y}
+            + \sqrt{1 - \abs{\mathcal{I}_1}^2}
+            \uv{z},\label{eq:06/02/21.l1param}\\
+        &= \begin{bmatrix}
+            i_1 \cos (g_1t) + i_{\rm 1f} \cos\p{g_2 t + \phi_0}\\
+            i_1 \sin (g_1t) + i_{\rm 1f} \sin\p{g_2 t + \phi_0}\\
+            \cos\abs{\mathcal{I}_1}.\nonumber
+        \end{bmatrix}
+\end{align}
+Note that $i_{\rm 1f}$ is effectively set by the initial $\mathcal{I}_{23}$
+(overlap with the eigenvector), and $i_{1}$ is set by whatever remaining IC is
+not described by the forced component.
+
+\subsection{Spin Dynamics}
+
+We now have the parameterized form for $\uv{l}_1$ following
+Eq.~\eqref{eq:06/02/21.l1param} and the solution for $\mathcal{I}_1$, and the
+spin evolves following
+\begin{equation}
+    \rd{\uv{s}}{t} = \alpha\p{\uv{s} \cdot \uv{l}_1}\p{\uv{s} \times \uv{l}_1}.
+\end{equation}
+
+\subsubsection{Numerical Approach}
+
+We seek to understand the stability of CS2 in the regime $\alpha \gg g_1, g_2$.
+WLOG, we choose to perturb about the initial condition where $\uv{s}$ points
+exactly along CS2, and $i_{\rm 1f} = 0$ (as is in the case of aligned outer
+planets; note that if the inner planet is not a perfect test mass, aligned outer
+planets does not completely suppress this mode). There are then three
+perturbations we can make:
 \begin{itemize}
-    \item If $I_0 > B$ and $g' \gg \omega_{\rm lib}$, we should see small
-        oscillations about CS2 (as $\uv{l}_{\rm p}$ effectively is
-        ``vibrating''), which average out.
+    \item We can increase $i_{\rm 1f}$; the two relevant regimes are expected to
+        be where $i_{\rm 1f} \ll i_1$ and $i_{\rm 1f} \gg i_1$.
 
-    \item If $I_0 > B$ and $g' \ll \omega_{\rm lib}$, then adiabatic resonance
-        advection means that the trajectory should encircle CS2 with constant
-        phase space area as CS2 moves around slightly.
+    \item We can change $g_2$; the two relevant regimes are expected to be where
+        $g_2 \gg g_1$ and $g_2 \ll g_1$, with possible resonance when they are
+        close (since $i_{\rm 1f}$ is prescribed explicitly and held constant, we
+        can imagine that the mutual inclination is decreased in proportion to
+        $g_{2} - g_1$ such that $i_{\rm 1f}$ is constant).
 
-    \item If $I_0 < B$ and $g' \gg \omega_{\rm lib}$, note that $\uv{l}_{\rm p}$
-        is \emph{circulating}; probably precesses about average.
-
-    \item If $I_0 < B$ and $g' \ll \omega_{\rm lib}$, then there should be no
-        resonance, as CS2 itself is circulating; there is no librating resonant
-        angle.
+    \item We can perturb the initial system about the initial CS2; we do this by
+        adding an angle offset $\Delta \theta_{\rm i}$ to the IC, so that there
+        is a nonzero initial libration amplitude.
 \end{itemize}
 
+\subsubsection{Analytical Approach}
+
+It seems like we are seeing some resonances when $g_2 / g_1$ hits half-integer
+multiples. For convenience, we go to the co-rotating frame with $g_1$ where we
+then have
+\begin{equation}
+    \p{\rd{\uv{s}}{t}}_{\rm rot, 1}
+        = \alpha\p{\uv{s} \cdot \uv{l}_1}\p{\uv{s} \times \uv{l}_1}
+            + g_1\p{\uv{s} \cdot \uv{J}}.
+\end{equation}
+Here, now, the mode frequencies are $g_1 \Rightarrow 0$ and $g_2 \Rightarrow g_2
+- g_1$. Decompose then $\uv{l}$ (we drop the subscript) into a mean and fluctuating
+piece $\bar{\bm{l}}$ and $\bm{l}'$ (where the former is still a vector of unit
+length), then:
+\begin{equation}
+    \p{\rd{\uv{s}}{t}}_{\rm rot, 1}
+        = \alpha\p{\uv{s} \cdot \bar{\bm{l}}}\p{\uv{s} \times \bar{\bm{l}}}
+            + g_1\p{\uv{s} \cdot \uv{J}}
+            + \alpha\s{
+                \p{\uv{s} \cdot \bar{\bm{l}}}
+                \p{\uv{s} \times \bm{l}'} +
+                \p{\uv{s} \cdot \bm{l}'}
+                \p{\uv{s} \times \bar{\bm{l}}}
+            }.
+\end{equation}
+This is already looking painful. Let's write down the Hamiltonian to have a
+faster path to EOM in coordinates:
+\begin{align}
+    H_{\rm rot, 1} ={}& -\frac{\alpha}{2}\p{\uv{s} \cdot \uv{l}}^2
+            - g\p{\uv{s} \cdot \uv{J}},\\
+        ={}& -\frac{\alpha}{2}\p{\uv{s} \cdot \bar{\bm{l}}}^2
+            - \alpha\p{\uv{s} \cdot \bar{\bm{l}}}
+                \p{\uv{s} \cdot \bm{l}'}
+            - g\p{\uv{s} \cdot \uv{J}},\\
+        \approx{}& -\frac{\alpha}{2}\cos^2\theta
+            - g\p{\cos \theta \cos I - \sin I \sin \theta \cos \phi}\nonumber\\
+        & - \alpha \cos \theta\p{
+            \cos \theta \cos i_{\rm 1f}
+            - \sin i_{\rm 1f} \sin \theta \cos \p{\phi - \phi_0 - \p{g_2 -
+            g_1}t}}.
+\end{align}
+Is this right, or is $i_{\rm 1f}$ also changing?
+
 \end{document}

### 2021-06-04 initial/1_weaktide/6misc.py

@@ -182,38 +182,6 @@ def plot_equils(I, s_cs, fn_str='6equils', tf=5000):
         s_gt = np.linspace(1, 3, 200) # other interesting part of the interval
         s_tot = np.concatenate((s_lt, s_gt))
 
-        if s_c == 0.06:
-            ax.text(2.55, 123, '(Fig.~11)',
-                    c=TRAJ_COLORS[2], fontsize=12, ha='left')
-            ax.text(2.55, 117, '(Fig.~12)',
-                    c=TRAJ_COLORS[3], fontsize=12, ha='left')
-        if s_c == 0.7:
-            ax.text(2.5, 13, '(Fig.~13)', c=TRAJ_COLORS[0], fontsize=12)
-
-        for idx, c in enumerate(TRAJ_COLORS[ :6]):
-            pkl_fn = '%s_sims/%s_%d.pkl' % (fn_str, s_c_str(s_c), idx)
-            with lzma.open(pkl_fn, 'rb') as f:
-                solve_ret = pickle.load(f)
-            (mu_0, s_0, t_0, mu_pi, s_pi, t_pi), mu, phi, _s, ret_solveivp = solve_ret
-            svec = ret_solveivp.y[0:3, :]
-            s = ret_solveivp.y[3, :]
-            t = ret_solveivp.t
-            q, phi = to_ang(*svec)
-            if (
-                    (idx == 2 and s_c == 0.06) or
-                    (idx == 3 and s_c == 0.06) or
-                    (idx == 0 and s_c == 0.7)
-            ):
-                _lw = 1.5
-                _al = 0.8
-            else:
-                _lw = 0.8
-                _al = 0.4
-            ax.plot(s, np.degrees(q), alpha=_al, c=c, lw=_lw)
-            offset = 0.5 if idx == 3 else (-0.5 if idx == 2 else 0)
-            ax.plot(s[0], np.degrees(q)[0] + offset, ms=10,
-                    c=c, marker='x')
-
         cs1_qs, cs2_qs = get_cs_val(I, s_c, s_tot)
         cs1_exist_idx = np.where(cs1_qs > -1)[0]
         mu_equil_lt = [np.degrees(np.arccos(get_mu_equil(s))) for s in s_lt]
@@ -289,6 +257,39 @@ def plot_equils(I, s_cs, fn_str='6equils', tf=5000):
[…]

### 2021-06-09 weeklies/YS_210608.tex
begin trying the experiment w/ 2 CSs + alignment torque

    \documentclass[11pt,
        usenames, % allows access to some tikz colors
        dvipsnames % more colors: https://en.wikibooks.org/wiki/LaTeX/Colors
    ]{article}
    \usepackage{
        amsmath,
        amssymb,
        fouriernc, % fourier font w/ new century book
        fancyhdr, % page styling
        lastpage, % footer fanciness
        hyperref, % various links
        setspace, % line spacing
        amsthm, % newtheorem and proof environment
        mathtools, % \Aboxed for boxing inside aligns, among others
        float, % Allow [H] figure env alignment
        enumerate, % Allow custom enumerate numbering
        graphicx, % allow includegraphics with more filetypes
        wasysym, % \smiley!
        upgreek, % \upmu for \mum macro
        listings, % writing TrueType fonts and including code prettily
        tikz, % drawing things
        booktabs, % \bottomrule instead of hline apparently
        xcolor, % colored text
        cancel % can cancel things out!
    }
    \usepackage[margin=1in]{geometry} % page geometry
    \usepackage[
        labelfont=bf, % caption names are labeled in bold
        font=scriptsize % smaller font for captions
    ]{caption}
    \usepackage[font=scriptsize]{subcaption} % subfigures

    \newcommand*{\scinot}[2]{#1\times10^{#2}}
    \newcommand*{\dotp}[2]{\left<#1\,\middle|\,#2\right>}
    \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
    \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
    \newcommand*{\rdil}[2]{\mathrm{d}#1 / \mathrm{d}#2}
    \newcommand*{\pdil}[2]{\partial#1 / \partial#2}
    \newcommand*{\rtd}[2]{\frac{\mathrm{d}^2#1}{\mathrm{d}#2^2}}
    \newcommand*{\ptd}[2]{\frac{\partial^2 #1}{\partial#2^2}}
    \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
    \newcommand*{\pvec}[1]{\vec{#1}^{\,\prime}}
    \newcommand*{\svec}[1]{\vec{#1}\;\!}
    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
    \newcommand*{\uv}[1]{\hat{\bm{#1}}}
    \newcommand*{\ang}[0]{\;\text{\AA}}
    \newcommand*{\mum}[0]{\;\upmu \mathrm{m}}
    \newcommand*{\at}[1]{\left.#1\right|}
    \newcommand*{\bra}[1]{\left<#1\right|}
    \newcommand*{\ket}[1]{\left|#1\right>}
    \newcommand*{\abs}[1]{\left|#1\right|}
    \newcommand*{\ev}[1]{\left\langle#1\right\rangle}
    \newcommand*{\p}[1]{\left(#1\right)}
    \newcommand*{\s}[1]{\left[#1\right]}
    \newcommand*{\z}[1]{\left\{#1\right\}}

    \newtheorem{theorem}{Theorem}[section]

    \let\Re\undefined
    \let\Im\undefined
    \DeclareMathOperator{\Res}{Res}
    \DeclareMathOperator{\Re}{Re}
    \DeclareMathOperator{\Im}{Im}
    \DeclareMathOperator{\Log}{Log}
    \DeclareMathOperator{\Arg}{Arg}
    \DeclareMathOperator{\Tr}{Tr}
    \DeclareMathOperator{\E}{E}
    \DeclareMathOperator{\Var}{Var}
    \DeclareMathOperator*{\argmin}{argmin}
    \DeclareMathOperator*{\argmax}{argmax}
    \DeclareMathOperator{\sgn}{sgn}
    \DeclareMathOperator{\diag}{diag\;}

    \colorlet{Corr}{red}

    % \everymath{\displaystyle} % biggify limits of inline sums and integrals
    \tikzstyle{circ} % usage: \node[circ, placement] (label) {text};
        = [draw, circle, fill=white, node distance=3cm, minimum height=2em]
    \definecolor{commentgreen}{rgb}{0,0.6,0}
    \lstset{
        basicstyle=\ttfamily\footnotesize,
        frame=single,
        numbers=left,
        showstringspaces=false,
        keywordstyle=\color{blue},
        stringstyle=\color{purple},
        commentstyle=\color{commentgreen},
        morecomment=[l][\color{magenta}]{\#}
    }

\begin{document}

\onehalfspacing

\pagestyle{fancy}
\rfoot{Yubo Su}
\rhead{}
\cfoot{\thepage/\pageref{LastPage}}

\title{Yubo Weekly June 8, 2021}

\maketitle

We analyze Dong's equations, where:
\begin{align}
    \rd{\uv{s}}{t} &= \alpha\p{\uv{s} \cdot \uv{l}_1}\p{\uv{s} \times
        \uv{l}_1},\\
    \uv{l}_1 &= \Re \mathcal{I}_1\uv{x}
            + \Im \mathcal{I}_1 \uv{y}
            + \sqrt{1 - \abs{\mathcal{I}_1}^2}
            \uv{z},\label{eq:06/02/21.l1param}\\
        &= \begin{bmatrix}
            i_1 \cos (g_1t) + i_{\rm 1f} \cos\p{g_2 t + \phi_0}\\
            i_1 \sin (g_1t) + i_{\rm 1f} \sin\p{g_2 t + \phi_0}\\
            \cos\abs{\mathcal{I}_1}
        \end{bmatrix}.
\end{align}
I've taken $\phi_0 = 0$ for simplicity. We take $\alpha / g_1 = 10$
consistently. We permit $i_{\rm 1f}$ and $g_{1,2}$ to vary independently for
now, even though $i_{\rm 1f} \propto \p{g_2 - g_1}^{-1}$.

\section{Preliminary Numerical Work}

We analyze the dynamics of $\phi_{\rm rot}$, the azimuthal angle in the
co-rotating frame. This lets us both understand the locations of equilibria
($\phi_{\rm rot} \approx \phi_{\rm rot, 0}$) and the distortion of the
separatrix (circulation-libration transition). We suppress the suffix. In
particular, we consider the quantity:
\begin{equation}
    \Delta \phi\p{i_{\rm 1f}; g_2; \Delta \theta_{\rm i}}
        \equiv \phi_{\max} - \phi_{\min}.
\end{equation}
Here, we fix the initial $\phi_{\rm rot} = 180^\circ$, and $\Delta \theta_{\rm
i}$ is the angular distance from CS2. For instance, $\Delta \phi\p{0, 0, 0} =
0$. We show a few plots in Figs.~\ref{fig:scan_I2}--\ref{fig:scan_dq_res}.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\columnwidth]{../initial/4nplanet/3paramsim/scan_I2.png}
    \caption{Scanning $\Delta \phi$ over $i_{\rm 1f}$. Note that $i_1 =
    10^\circ$ for all of these.}\label{fig:scan_I2}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\columnwidth]{../initial/4nplanet/3paramsim/scan_frequency.png}
    \caption{Scanning $\Delta \phi$ over $g_2$.}\label{fig:scan_dq_res}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\columnwidth]{../initial/4nplanet/3paramsim/scan_dq.png}
    \caption{Scanning $\Delta \phi$ over $\Delta \theta_{\rm
    i}$.}\label{fig:scan_dq}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\columnwidth]{../initial/4nplanet/3paramsim/scan_dq_res.png}
    \caption{Scanning $\Delta \phi$ over $\Delta \theta_{\rm
    i}$ for many frequencies near the $g_2 = 2g_1$ resonance.}\label{fig:scan_dq_res}
\end{figure}

It is clear that there are some resonances for $g_1 \simeq g_2$! In fact, there
are some interesting behaviors. If we examine the phase space evolution (in
$\cos \theta, \phi$ space as usual) of ICs near CS2 as we vary $g_2 / g_1$, we
obtain:
\begin{figure}
    \centering
    \includegraphics[width=0.45\columnwidth]{../initial/4nplanet/3paramsim/phase_portrait0.png}
    \includegraphics[width=0.45\columnwidth]{../initial/4nplanet/3paramsim/phase_portrait01.png}

    \includegraphics[width=0.45\columnwidth]{../initial/4nplanet/3paramsim/phase_portrait1.png}
    \includegraphics[width=0.45\columnwidth]{../initial/4nplanet/3paramsim/phase_portrait2.png}

    \includegraphics[width=0.45\columnwidth]{../initial/4nplanet/3paramsim/phase_portrait3.png}
    \includegraphics[width=0.45\columnwidth]{../initial/4nplanet/3paramsim/phase_portrait10.png}
    \caption{Evolution of some ICs for $g_2 / g_1 = \z{0, 0.1, 1, 2, 3, 10}$.
    Note that for $g_2 = 0$, we've set $i_{\rm 1f} = 0^\circ$, else we set
    $i_{\rm f} = 1^\circ$, and $i_1 = 10^\circ$.
    }\label{fig:phase_portraits}
\end{figure}

\section{Analytical Approach}

It is clear that there are some resonance behaviors, and in particular that $g_2
/ g_1 = 1$ is \emph{not} a resonance; it is suspiciously quiet (see
Fig.~\ref{fig:phase_portraits}). Here is a simple explanation:

Consider the Hamiltonian
\begin{equation}
    H = - \frac{\alpha}{2}\p{\uv{s} \cdot \uv{l}}^2.
\end{equation}
Decompose $\uv{l} = \bar{\bm{l}} + \bm{l}'$ where:
\begin{align}
    \bar{\bm{l}} &= \begin{bmatrix}
        i_1 \cos (g_1t)
        i_1 \sin (g_1t)
        \cos i_1
    \end{bmatrix},\\
    \bm{l}' &\equiv \uv{l} - \bar{\bm{l}},\\
        &\approx \begin{bmatrix}
        i_{\rm 1f} \cos\p{g_2 t + \phi_0}\\
        i_{\rm 1f} \sin\p{g_2 t + \phi_0}\\
        -\frac{i_{\rm 1f}i_1}{\cos^2 i_1} \cos\p{g_2t + \phi_0}
    \end{bmatrix}.
\end{align}
Note that $l'_z \approx 0$.

We next go to the corotating frame with $g_1$ about $\uv{\jmath}$, so that
\begin{align}
    H_{\rm rot} &= - \frac{\alpha}{2}\p{\uv{s} \cdot \uv{l}}^2
        - g\p{\uv{s} \cdot \uv{\jmath}},\\
        &\equiv H_0 + H_1,\\
    H_0 &\equiv - \frac{\alpha}{2}\p{\uv{s} \cdot \bar{\bm{l}}}^2
        - g\p{\uv{s} \cdot \uv{\jmath}},\\
    H_1 &\approx -\alpha\p{\uv{s} \cdot \bar{\bm{l}}}
        \p{\uv{s} \cdot \bm{l}'} + \mathcal{O}\p{(l')^2}.
\end{align}
In the corotating frame, we find that
\begin{equation}
    \p{\bm{l}'}_{\rm rot} \approx \begin{bmatrix}
        i_{\rm 1f} \cos\p{(g_2 - g_1) t + \phi_0}\\
        i_{\rm 1f} \sin\p{(g_2 - g_1) t + \phi_0}\\
        0
    \end{bmatrix}.
\end{equation}
Thus, in the corotating frame, when $g_2 = g_1$, CS2 is simply \emph{shifted},
since $\bm{l}'_{\rm rot}$ is fixed in space. This isn't entirely realistic, as
$i_{\rm 1f} \propto \p{g_2 - g_1}^{-1}$.

\section{Numerical Searching for Resonant Behavior (WIP)}

We look for resonances by fixing all frequencies of the system and varying
$\Delta \theta_{\rm i}$, proximity to CS2.

\textbf{What are the origin of any resonances?} My hypothesis was that if $g_2 -
g_1 \simeq \omega_{\rm lib}$, the libration frequency about CS2, then resonances
can appear. Thus, we calculate $\omega_{\rm lib}$ as a function of $\Delta
\theta_{\rm i}$ numerically.

\textbf{Separately, is evolution chaotic?} For every $\Delta \theta_{\rm i}$, we
can compute the evolution for $\phi_{\rm i} = 0$ and $\phi_{\rm i} = 10^{-5}$,
then record
\begin{equation}
    \max \Delta \uv{s} \equiv \max_t \abs{\uv{s}_1 - \uv{s}_2}.
\end{equation}
If $\max \Delta \uv{s} \simeq 1$, then chaos is likely (I spot checked that
these seemed to correspond to the case of exponential growth).

We can plot both of these criteria in Fig.~\ref{fig:resonances}. It seems like a
plausible explanation that resonances occur when $g_2 - g_1 \simeq \omega_{\rm
lib}$, and that these resonances give rise to chaotic behavior (likely when
interacting with the separatrix).
\begin{figure}
    \centering
    \includegraphics[width=0.4\columnwidth]{../initial/4nplanet/3paramsim/resonances.png}
    \includegraphics[width=0.4\columnwidth]{../initial/4nplanet/3paramsim/resonances13.png}

    \includegraphics[width=0.4\columnwidth]{../initial/4nplanet/3paramsim/resonances15.png}
    \includegraphics[width=0.4\columnwidth]{../initial/4nplanet/3paramsim/resonances3.png}
    \caption{Top panels: $\omega_{\rm lib}$ (in the absence of any perturbation)
    as a function of distance to CS2. Horizontal line is the naive $2\pi /
    \p{g_2 - g_1}$. Bottom: $\max \Delta \uv{s}$, where large values suggest
    chaos. $i_1 = 10^\circ$ and $i_{\rm 1f} = 1^\circ$ as usual.}\label{fig:resonances}
\end{figure}

\end{document}

### 2021-06-09 notes/np_notes.tex
stash 0608
run sims for longer

@@
 
-It seems like we are seeing some resonances when $g_2 / g_1$ hits half-integer
-multiples. For convenience, we go to the co-rotating frame with $g_1$ where we
-then have
+It seems like we might be seeing some resonance type behaviors. For convenience,
+we go to the co-rotating frame with $g_1$ where we then have
 \begin{equation}
@@
 
+\section{06/09/21}
+
+\subsection{Analytical Time-Dependent Hamiltonian Perturbation Theory Setup
+(Abandoned)}
+
+We came up with at least a possible way to do this perturbatively, though it
+might not be useful, since we haven't included the effect of tidal dissipation
+yet. I'm going to just mostly copy this from my weekly update, since I don't
+want to retype the scratch work. We analyze Dong's equations, where:
+\begin{align}
+    \rd{\uv{s}}{t} &= \alpha\p{\uv{s} \cdot \uv{l}_1}\p{\uv{s} \times
+        \uv{l}_1},\\
+    \uv{l}_1 &= \Re \mathcal{I}_1\uv{x}
+            + \Im \mathcal{I}_1 \uv{y}
+            + \sqrt{1 - \abs{\mathcal{I}_1}^2}
+            \uv{z},\label{eq:06/02/21.l1param}\\
+        &= \begin{bmatrix}
+            i_1 \cos (g_1t) + i_{\rm 1f} \cos\p{g_2 t + \phi_0}\\
+            i_1 \sin (g_1t) + i_{\rm 1f} \sin\p{g_2 t + \phi_0}\\
+            \cos\abs{\mathcal{I}_1}
+        \end{bmatrix}.
+\end{align}
+I've taken $\phi_0 = 0$ for simplicity. We take $\alpha / g_1 = 10$
+consistently. We permit $i_{\rm 1f}$ and $g_{1,2}$ to vary independently for
+now, even though $i_{\rm 1f} \propto \p{g_2 - g_1}^{-1}$.
+
+Consider the Hamiltonian
+\begin{equation}
+    H = - \frac{\alpha}{2}\p{\uv{s} \cdot \uv{l}}^2.
+\end{equation}
+Decompose $\uv{l} = \bar{\bm{l}} + \bm{l}'$ where:
+\begin{align}
+    \bar{\bm{l}} &= \begin{bmatrix}
+        i_1 \cos (g_1t)
+        i_1 \sin (g_1t)
+        \cos i_1
+    \end{bmatrix},\\
+    \bm{l}' &\equiv \uv{l} - \bar{\bm{l}},\\
+        &\approx \begin{bmatrix}
+        i_{\rm 1f} \cos\p{g_2 t + \phi_0}\\
+        i_{\rm 1f} \sin\p{g_2 t + \phi_0}\\
+        -\frac{i_{\rm 1f}i_1}{\cos^2 i_1} \cos\p{g_2t + \phi_0}
+    \end{bmatrix}.
+\end{align}
+Note that $l'_z \approx 0$.
+
+We next go to the corotating frame with $g_1$ about $\uv{\jmath}$, so that
+\begin{align}
+    H_{\rm rot} &= - \frac{\alpha}{2}\p{\uv{s} \cdot \uv{l}}^2
+        - g\p{\uv{s} \cdot \uv{\jmath}},\\
+        &\equiv H_0 + H_1,\\
+    H_0 &\equiv - \frac{\alpha}{2}\p{\uv{s} \cdot \bar{\bm{l}}}^2
+        - g\p{\uv{s} \cdot \uv{\jmath}},\\
+    H_1 &\approx -\alpha\p{\uv{s} \cdot \bar{\bm{l}}}
+        \p{\uv{s} \cdot \bm{l}'} + \mathcal{O}\p{(l')^2}.
+\end{align}
+In the corotating frame, we find that
+\begin{equation}
+    \p{\bm{l}'}_{\rm rot} \approx \begin{bmatrix}
+        i_{\rm 1f} \cos\p{(g_2 - g_1) t + \phi_0}\\
+        i_{\rm 1f} \sin\p{(g_2 - g_1) t + \phi_0}\\
+        0
+    \end{bmatrix}.
+\end{equation}
+Thus, in the corotating frame, when $g_2 = g_1$, CS2 is simply \emph{shifted},
+since $\bm{l}'_{\rm rot}$ is fixed in space. This isn't entirely realistic, as
+$i_{\rm 1f} \propto \p{g_2 - g_1}^{-1}$, but also gives us a chance at using
+time-dependent perturbation theory.
+
+\textbf{NB:} Per Dong's recommendation, I'm going to mostly stay away from this,
+as the dynamics are already reasonably well understood in the absence of tidal
+dissipation due to resonance overlap. I suspect that there might be some other
+interesting behavior, like chaotic behavior near the separatrix due to another
+Melnikov's Method calculation, but it's a little bit difficult to justify doing
+too much work on this when there's a lot of canonical work on the subject
+already.
+
+I do have a concern about resonance overlap: the resonances are only formally
+defined in their respective corotating frames (i.e.\ they don't share resonance
+angles $\phi_i = \phi_{\rm inertial} + g_it$), so I'm not exactly sure the
+picture of ``don't know which resonance a point belongs to'' is entirely valid.
+
 \end{document}

### 2021-06-09 initial/4nplanet/3paramsim.py

@@ -509,19 +509,20 @@ def nondisp_explore():
 
 TIDE_FLDR = '3paramtide/'
 def disp_run_ex(I2=0, g2=0, fn='/tmp/foo', dq=0.05, tf=300, eps_tide=5e-2,
-                plot=False):
+                plot=False, q0=None, phi0=np.pi):
     '''
     run an example of dissipation
     '''
     alpha0 = 10
     eta = 1 / alpha0
     I1 = np.radians(10)
-    phi_args = 0
     eps_alpha = 0
+    phi_args = 0
     q_cs2 = roots(I1, eta)[1]
-    q0 = q_cs2 + dq
-    svec = [-np.sin(q0 - I1),
-            0,
+    if q0 is None:
+        q0 = q_cs2 + dq
+    svec = [np.sin(q0 - I1) * np.cos(phi0),
+            np.sin(q0 - I1) * np.sin(phi0),
             np.cos(q0 - I1)]
     args = [I1, I2, g2, phi_args, eps_alpha, eps_tide]
     pkl_fn = fn + '.pkl'
@@ -543,15 +544,16 @@ def disp_run_ex(I2=0, g2=0, fn='/tmp/foo', dq=0.05, tf=300, eps_tide=5e-2,
     if not plot:
         return obliquities, phirot_arr, ret
     # phi = np.degrees(np.unwrap(np.arctan2(ret.y[1], ret.y[0])))
-    fig, (ax1, ax2) = plt.subplots(
-        2, 1,
-        figsize=(8, 8),
-        sharex=True)
-    ax1.plot(ret.t, obliquities)
-    ax2.plot(ret.t, phirot_arr)
-    ax2.set_xlabel(r'$g_1t$')
-    ax1.set_ylabel(r'$\theta$')
-    ax2.set_ylabel(r'$\phi_{\rm rot}$')
+    # fig, (ax1, ax2) = plt.subplots(
+    #     2, 1,
+    #     figsize=(8, 8),
+    #     sharex=True)
+    # ax1.plot(ret.t, obliquities)
+    # ax2.plot(ret.t, phirot_arr)
+    # ax2.set_xlabel(r'$g_1t$')
+    # ax1.set_ylabel(r'$\theta$')
+    # ax2.set_ylabel(r'$\phi_{\rm rot}$')
+    plt.plot(phirot_arr % 360, np.cos(np.radians(obliquities)), 'ko')
     plt.tight_layout()
     plt.savefig(fn, dpi=200)
     plt.close()
[…]

### 2021-07-13 writeups/Su_weak_tides.tex
stash 7/12

@@
         usenatbib,
-        referee,
+        referee
     ]{mnras}
@@
 
-In this section, we briefly introduce the spin dynamics of the planet (for a
-more detailed treatment, see Paper I). We consider a star of mass $M_\star$
-hosting an inner oblate planet of mass $m$ and radius $R$ on a circular orbit
-with semi-major axis $a$ and an outer perturber of mass $m_{\rm p}$ on a
-circular orbit with semi-major axis $a_{\rm p}$. We assume that the two orbits
-are mutually inclined by the angle $I$. Denote $\bm{S}$ the spin angular
-momentum and $\bm{L}$ the orbital angular momentum of the planet, and
-$\bm{L}_{\rm p}$ the angular momentum of the perturber. The corresponding unit
-vectors are $\uv{s} \equiv \bm{S} / S$, $\uv{l} \equiv \bm{L} / L$, and
-$\uv{l}_{\rm p} \equiv \bm{L}_{\rm p} / L_{\rm p}$. The spin axis $\uv{s}$ of
-the planet tends to precess around its orbital (angular momentum) axis $\uv{l}$,
-driven by the gravitational torque from the host star acting on the planet's
-rotational bulge. On the other hand, $\uv{l}$ and the disk axis $\uv{l}_{\rm p}$
-precess around each other due to gravitational interactions. We assume $S \ll L
-\ll L_{\rm p}$, so $\uv{l}_{\rm p}$ and $\uv{l}$ are nearly constant. The
-equations of motion for $\uv{s}$ and $\uv{l}$ in this limit are
-(\citealp{anderson2018teeter}, Paper I)
+In this section, we briefly review the spin dynamics of the planet and introduce
+our notations; see Paper I for more details. We consider a star of mass
+$M_\star$ hosting an inner oblate planet of mass $m$ and radius $R$ on a
+circular orbit with semi-major axis $a$ and an outer perturber of mass $m_{\rm
+p}$ on a circular orbit with semi-major axis $a_{\rm p}$. The two orbits are
+mutually inclined by the angle $I$. Denote $\bm{S}$ the spin angular momentum
+and $\bm{L}$ the orbital angular momentum of the planet, and $\bm{L}_{\rm p}$
+the angular momentum of the perturber. The corresponding unit vectors are
+$\uv{s} \equiv \bm{S} / S$, $\uv{l} \equiv \bm{L} / L$, and $\uv{l}_{\rm p}
+\equiv \bm{L}_{\rm p} / L_{\rm p}$. The spin axis $\uv{s}$ of the planet tends
+to precess around its orbital (angular momentum) axis $\uv{l}$, driven by the
+gravitational torque from the host star acting on the planet's rotational bulge.
+On the other hand, $\uv{l}$ and $\uv{l}_{\rm p}$ precess around
+each other due to gravitational interactions. Assuming $S \ll L$,
+the equations of motion for $\uv{s}$ and $\uv{l}$ are
 \begin{align}
@@
 \begin{align}
-    \omega_{\rm sl} &\equiv \frac{3GJ_2 mR^2 M_\star}{2a^3 I\Omega_{\rm s}}
+    \omega_{\rm sl} &\equiv \alpha =
+        \frac{3GJ_2 mR^2 M_\star}{2a^3 \mathcal{I}\Omega_{\rm s}}
         = \frac{3k_q}{2k}\frac{M_\star}{m}\p{\frac{R}{a}}^3 \Omega_{\rm s},
             \label{eq:wsl}\\
-    \omega_{\rm lp} &= \frac{3m_{\rm p}}{4M_\star}\p{\frac{a}{a_{\rm p}}}^3
-        n.\label{eq:wlp}
+    \omega_{\rm lp} &\equiv -\frac{g}{\cos I}
+        = \frac{3m_{\rm p}}{4M_\star}\p{\frac{a}{a_{\rm p}}}^3 n.\label{eq:wlp}
 \end{align}
 In Eq.~\eqref{eq:wsl}, $\Omega_{\rm s}$ is the spin frequency of the inner
-planet, $\mathcal{I} = k mR^2$ (with $k$ a constant) is its moment of inertia
-and $J_2 = k_{\rm q}\Omega_{\rm s}^2 (R^3/Gm)$ (with $k_{q}$ a constant) is its
-rotation-induced (dimensionless) quadrupole moment [for a body with uniform
-density, $k=0.4, k_{\rm q}=0.5$; for the Earth, $k \simeq 0.331$ and $k_{\rm q}
-\equiv k_2 / 3 \simeq 0.1$ \citep[e.g.][]{groten2004fundamental,
-lainey2016quantification}]. In other studies, $3k_{\rm q} / 2 k$ is often
-notated as $k_2 / 2C$ \citep[e.g.][]{millholland_disk}. In Eq.~\eqref{eq:wlp},
-$n \equiv \sqrt{GM_\star/a^3}$ is the inner planet's orbital mean motion,  and
-we have assumed $a_{\rm p}\gg a$ and included only the leading-order
-(quadrupole) interaction between the inner planet and perturber. Following
-standard notation, we define $\alpha = \omega_{\rm sl}$ and $g \equiv
--\omega_{\rm 1p} \cos I$ \citep[e.g.][]{colombo1966}.
-
-As in Paper I, we combine Eqs.~(\ref{eq:dsdt1}--\ref{eq:dldt1}) into a
+planet, $\mathcal{I} = k mR^2$ (with $k$ the normalized moment of inertia, often
+notated as $C_{\rm N}$) is its moment of inertia and $J_2 = k_{\rm q}\Omega_{\rm
+s}^2 (R^3/Gm)$ (with $k_{q}$ a constant) is its rotation-induced (dimensionless)
+quadrupole moment [for a fluid body with uniform density, $k=0.4, k_{\rm
+q} = k_2/3 = 0.5$; for the Earth, $k \simeq 0.331$ and $k_{\rm q} \simeq 0.1$;
+for Jupiter, $k \simeq 0.27$ whle $k_{\rm q} \simeq 0.18$
+\citep[e.g.][]{groten2004fundamental, lainey2016quantification}]\footnote{Note
+that for the Earth, $k / k_{\rm q} \approx 3$ since its $k_{\rm q}$ is reduced
+by its appreciable rigidity, while for ``fluid'' bodies, $k / k_{\rm q} \sim
+1$.}. In other studies, $3k_{\rm q} / 2 k$ is often notated as $k_2 / 2C_{\rm
+N}$ \citep[e.g.][]{millholland_disk}. In Eq.~\eqref{eq:wlp}, $n \equiv
+\sqrt{GM_\star/a^3}$ is the inner planet's orbital mean motion,  and we have
+assumed $a_{\rm p}\gg a$ and included only the leading-order (quadrupole)
+interaction between the inner planet and perturber
+(Section~\ref{ss:disc_usp} discusses modifications to Eq.~\ref{eq:wlp}
+when $a_{\rm p} \gtrsim a$). Eq.~\eqref{eq:dldt1} neglects the back-reaction
+torque on $\uv{l}$ from $\uv{s}$; this is justified since $L \gg S$ (see
+\citealp{anderson2018teeter} for the case when $L \simeq S$). In
+Eq.~\eqref{eq:wsl} (and throughout
+Sections~\ref{s:theory}--\ref{s:full_tide_prob}), we assume $L_{\rm p} \gg L$
+so that $\uv{l}_{\rm p}$ is a constant (Section~\ref{ss:disc_wasp12b} discusses
+the case of $L \simeq L_{\rm p}$). Following standard notation, we have defined
+$\alpha = \omega_{\rm sl}$ and $g \equiv -\omega_{\rm 1p} \cos I$
+\citep[e.g.][]{colombo1966}.
+
+As in Paper I, we combine Eqs.~\eqref{eq:dsdt1}--\eqref{eq:dldt1} into a
 single equation by transforming into a frame rotating about $\uv{l}_{\rm p}$
 with frequency $g$. In this frame, $\uv{l}_{\rm p}$ and $\uv{l}$ are both fixed,
-and $\uv{s}$ evolves as:
+and $\uv{s}$ evolves as
 \begin{equation}
@@
 \end{equation}
-In this reference frame, we choose the coordinate system such that $\uv{z} =
-\uv{l}$ and $\uv{l}_{\rm p}$ lies in the $\uv{x}$-$\uv{z}$ plane. We describe
-$\uv{s}$ in spherical coordinates using the polar angle $\theta$, the planet's
-obliquity, and $\phi$, the precessional phase of $\uv{s}$ about $\uv{l}$,
-defined so that when $\phi = 0^\circ$, $\uv{l}_{\rm p}$ and $\uv{s}$ are on
-opposide sides of $\uv{l}$.
+We choose the coordinate system such that $\uv{z} = \uv{l}$ and $\uv{l}_{\rm p}$
+lies in the $\uv{x}$-$\uv{z}$ plane. We describe $\uv{s}$ in spherical
+coordinates using the polar angle $\theta$, the planet's obliquity, and $\phi$,
+the precessional phase of $\uv{s}$ about $\uv{l}$, defined so that when $\phi =
+0^\circ$, $\uv{l}_{\rm p}$ and $\uv{s}$ are on opposide sides of $\uv{l}$.
 
@@
 States} \citep[CSs;][]{colombo1966, peale1969}. We follow the notation of
-Paper I, where the parameter
-\begin{equation}
-    \eta \equiv -\frac{g}{\alpha},\label{eq:def_eta}
-\end{equation}
-is introduced. For a given value of $\eta$, there can be either two or four CSs,
-all of which require $\uv{s}$ lie in the plane of $\uv{l}$ and $\uv{l}_{\rm p}$.
-Following the standard nomenclature, $\uv{s}$ and $\uv{l}_{\rm p}$ are on
-opposite sides of $\uv{l}$ for CSs 1, 3, and 4, and are on the same side for
-CS2. We depart from the standard convention and simply label the CSs in
-spherical coordinates: Figure~\ref{fig:cs_locs} shows the CS obliquities as a
-function of $\eta$. CS1 and CS4 do not exist when $\eta > \eta_{\rm c}$, where
+Paper I and introduce the parameter
+\begin{equation}
+    \eta \equiv -\frac{g}{\alpha} =
+        \frac{1}{2}\frac{k}{k_{\rm q}}
+            \frac{m_{\rm p}m}{M_\star^2}
+            \p{\frac{a}{a_{\rm p}}}^3
+            \p{\frac{a}{R}}^3\cos(I)
+            \frac{n}{\Omega_{\rm s}}.\label{eq:def_eta}
+\end{equation}
+For a given value of $\eta$, there can be either two or four CSs, all of which
+require $\uv{s}$ lie in the plane of $\uv{l}$ and $\uv{l}_{\rm p}$. In
+the standard nomenclature CSs 1, 3, and 4 have $\theta < 0$, implying that $\uv{s}$ and $\uv{l}_{\rm p}$ are on opposite sides
+of $\uv{l}$, while CS2 has $\theta > 0$, implying that $\uv{s}$ and $\uv{l}$ are
+on the same side of $\uv{l}$. We depart from the standard convention and simply
+label the CSs using the polar angles $\theta$ and $\phi$ (with $\theta \in \s{0,
+\pi}$): Figure~\ref{fig:cs_locs} shows the CS obliquities as a function of
+$\eta$. CS1 and CS4 do not exist when $\eta > \eta_{\rm c}$, where
 \begin{equation}
@@
     line denotes $\eta_{\rm c}$, where the number of Cassini States changes from
-    four to just two (Eq.~\ref{eq:def_etac}). The y-axis labels on the right of
+    four to two (Eq.~\ref{eq:def_etac}). The y-axis labels on the right of
     the plot show the asymptotic obliquities for CS2 and CS3, $I$ and $180^\circ
@@
     convention \citep[e.g.][]{colombo1966} and is simply the angle between
-    $\uv{s}$ and $\uv{l}$.}\label{fig:cs_locs}
+    $\uv{s}$ and $\uv{l}$, while $\phi = 0$ corresponds to $\uv{s}$ and
+    $\uv{l}_{\rm p}$ being on opposite sides of $\uv{l}$. Only CS1 and CS2 are
+    stable in the presence of the spin-orbit alignment torque (see
+    Section~\ref{ss:linear_stab}).}\label{fig:cs_locs}
 \end{figure}
@@
     H &= -\frac{\alpha}{2}\p{\uv{s} \cdot \uv{l}}^2
-            - g\p{\uv{s} \cdot \uv{l}_{\rm d}}\nonumber\\
+            - g\p{\uv{s} \cdot \uv{l}_{\rm p}}\nonumber\\
         &= -\frac{\alpha}{2} \cos^2\theta
@@
 Figure~\ref{fig:1contours} shows the level curves of this Hamiltonian for $I =
-20^\circ$, for which $\eta_{\rm c} \approx 0.574$ (Eq.~\ref{eq:def_etac}). When $\eta
-< \eta_{\rm c}$, CS4 exists and is a saddle point. The infinite-period orbits
-originating and ending at CS4 form the \emph{separatrix} and divide phase space
-into three zones. $\phi$ librates for trajectories in zone II and circulates for
-trajectories in zones I and III\@. On the other hand, when $\eta > \eta_{\rm
-c}$, the separatrix is absent and all trajectories circulate. When the
-separatrix exists, we divide it into two curves: $\mathcal{C}_+$, the boundary
-between zones I and II, and $\mathcal{C}_-$, the boundary between zones II and
-III\@.
+20^\circ$, for which $\eta_{\rm c} \approx 0.574$ (Eq.~\ref{eq:def_etac}). When
+$\eta < \eta_{\rm c}$, CS4 exists and is a saddle point. The infinite-period
+orbits originating and ending at CS4 form the \emph{separatrix} and divide phase
+space into three zones. The angle $\phi$ librates for trajectories in zone II
+and circulates for trajectories in zones I and III\@. On the other hand, when
+$\eta > \eta_{\rm c}$, the separatrix is absent and all trajectories circulate.
+When the separatrix exists, we divide it into two curves: $\mathcal{C}_+$, the
+boundary between zones I and II, and $\mathcal{C}_-$, the boundary between zones
+II and III\@.
 \begin{figure}
@@
     \includegraphics[width=\colummwidth]{../initial/0_eta/1contours20.png}
-    \caption{Level curves of the Cassini State Hamiltonian (Eq.~\ref{eq:H}) for
-    $I = 20^\circ$, for which $\eta_{\rm c} \approx 0.57$
-    (Eq.~\ref{eq:def_etac}). For $\eta < \eta_{\rm c}$, there are four Cassini
-    States (labeled), while for $\eta > \eta_{\rm c}$ there are only two. In the
-    former case, the existence of a \emph{separatrix} (solid black lines)
-    separates phase space into three numbered zones (I/II/III, labeled). We
-    denote the upper and lower legs of the separatrix by $\mathcal{C}_{\pm}$
-    respectively, as shown in the upper two panels. }\label{fig:1contours}
+    \caption{Level curves of the Hamiltonian (Eq.~\ref{eq:H}) for $I =
+    20^\circ$, for which $\eta_{\rm c} \approx 0.57$ (Eq.~\ref{eq:def_etac}).
+    For $\eta < \eta_{\rm c}$, there are four Cassini States (labeled), while
+    for $\eta > \eta_{\rm c}$ there are only two. In the former case, the
+    existence of a \emph{separatrix} (solid black lines) separates phase space
+    into three numbered zones (I/II/III, labeled). We denote the upper and lower
+    legs of the separatrix by $\mathcal{C}_{\pm}$ respectively, as shown in the
+    upper two panels. }\label{fig:1contours}
 \end{figure}
@@
 The full equations of motion for $\uv{s}$ in the coordinates $\theta$ and $\phi$
-can be written:
+can be written as
 \begin{align}
@@
 
-\subsection{Modified Cassini States and Linear Stability
-Analysis}\label{ss:tidal_equils}
+\subsection{Modified Cassini States}\label{ss:mcs}
 
 If the alignment torque is weak ($\abs{g}t_{\rm al} \gg 1$), then the fixed
-points of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) are slightly modified CSs.
-To leading order, all of the CS obliquities $\theta_{\rm cs}$ are unchanged
+points of Eqs.~\eqref{eq:dqdt_toy}--\eqref{eq:dfdt_toy} are slightly modified
+CSs. To leading order, all of the CS obliquities $\theta_{\rm cs}$ are unchanged
 while the azimuthal angle $\phi_{\rm cs}$ for each CS now satisfies
@@
 \end{equation}
-We can see that if $t_{\rm al}$ is longer than some critical alignment
+We can see that if $t_{\rm al}$ is longer than the critical alignment
 timescale $t_{\rm al, c}$, given by
@@
 the other hand, the other CSs have small $\sin \theta_{\rm cs}$ and are only
-slightly perturbed. Figure~\ref{fig:mcs} shows the obliquity and azimuthal
-angles for each of the CSs in the $\eta \ll 1$ case obtained via numerical
-root finding of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}), where it can be
-seen that CS2 and CS4 collide and annihilate when $t_{\rm al}$ reaches $t_{\rm
-al, c}$. The phase shift $\phi_{\rm cs}$ for CS2 and CS4 for $t_{\rm al} >
-t_{\rm al, c}$ can be predicted to good accuracy using Eq.~\eqref{eq:mcs_shift}
-using $\theta_{\rm cs} \approx \pi/2 - \eta \cos (I) \approx 79^\circ$
-\citep{su2020} for both, shown as the dashed lines in the bottom panel of
-Fig.~\ref{fig:mcs}. For the remainder of this section, we will consider the case
-where $t_{\rm al} \gg t_{\rm al, c}$ and the CSs only differ slightly from their
-unperturbed locations.
+slightly modified. Figure~\ref{fig:mcs} shows the obliquity and azimuthal
+angle for each of the CSs when $\eta = 0.2$ obtained via numerical root finding
+of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}), where it can be seen that CS2
+and CS4 collide and annihilate when $t_{\rm al}$ reaches $t_{\rm al, c}$. The
+phase shifts $\phi_{\rm cs}$ for CS2 and CS4 for $t_{\rm al} > t_{\rm al, c}$ can
+be predicted to good accuracy using Eq.~\eqref{eq:mcs_shift} using $\theta_{\rm
+cs} \approx \pi/2 - \eta \cos I \approx 79^\circ$ \citep{su2020} for both and
+are shown as the dashed lines in the bottom panel of Fig.~\ref{fig:mcs}. For the
+remainder of this section, we will consider the case where $t_{\rm al} \gg
+t_{\rm al, c}$ and the CSs only differ slightly from their unmodified
+locations.
 \begin{figure}
@@
     Eq.~\eqref{eq:mcs_shift}. At $\abs{gt_{\rm al} \sin I} = 1$, CS2 and CS4
-    collide and annihilate (Eq.~\ref{eq:mcs_shift_crit}).}\label{fig:mcs}
-\end{figure}
+    collide and annihilate (see Eq.~\ref{eq:mcs_shift_crit}).}\label{fig:mcs}
+\end{figure}
+
+\subsection{Linear Stability Analysis}\label{ss:linear_stab}
 
@@
 \end{equation}
-The stability depends only on the real part of $\lambda$ in
+
+The stability of a CS depends on the real part of $\lambda$ in
 Eq.~\eqref{eq:lambda_approx}. $\lambda_0^2$ is a generalization of Eq.~(A4)
@@
 1--3 and positive for CS4, as shown in Fig.~\ref{fig:lambda_full}. Thus, CS4 is
-always unstable, as there will always be at least one positive solution for
-$\lambda$, and the stability of CSs 1--3 are solely determined by the sign of
-$\cos \theta_{\rm cs}$. Using Fig.~\ref{fig:cs_locs}, we conclude that CS1 and
-CS2 are stable and attracting while trajectories near CS3 are driven away by the
-alignment torque. These calculations justify results long used in CS literature
-\citep[e.g.][]{ward1975tidal, fabrycky_otides}.
+always ``dynamically'' unstable (i.e.\ unstable even in the limit of $t_{\rm al}
+\to \infty$), as there will always be at least one positive solution for
+$\lambda$. On the other hand, CSs 1--3 are dynamically stable, and their overall
+stabilities in the presence of the alignment torque are determined by the
+sign of $\cos \theta_{\rm cs}$. Using Fig.~\ref{fig:cs_locs}, we conclude that
+CS1 and CS2 are stable and attracting while trajectories near CS3 are driven
+away by the alignment torque. These calculations quantify the results long used
+in the literature \citep[e.g.][]{ward1975tidal, fabrycky_otides}.
 \begin{figure}
@@
     the four CSs, for three different values of the shift in $\phi_{\rm cs}$
-    (e.g.\ for $\Delta \phi_{\rm cs} = 60^\circ$, $\phi_{\rm cs} = 120^\circ$
-    for CS2 and $\phi_{\rm cs} = 60^\circ$ for CSs 1, 3, and 4). The values of
-    $\Delta \phi_{\rm cs}$ are labeled. }\label{fig:lambda_full}
+    (e.g.\ for $\Delta \phi_{\rm cs} = 60^\circ$, the phase angles are
+    $\phi_{\rm cs} = 120^\circ$ for CS2 and $\phi_{\rm cs} = 60^\circ$ for CSs
+    1, 3, and 4). The values of $\Delta \phi_{\rm cs}$ are labeled ($\Delta
+    \phi_{\rm cs} = 0$ corresponds to the unmodified CSs).
+    }\label{fig:lambda_full}
 \end{figure}
@@
 With the above results, we are equipped to ask questions about the dynamics of
-Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}): what is the long term behavior for
-a general initial $\uv{s}$? If $\eta > \eta_{\rm c}$, then the only stable
-final spin state is CS2, and all initial conditions will evolve asympotically
-towards it. As such, we consider only $\eta < \eta_{\rm c}$, where an initial
-condition can asymptotically evolve towards either CS1 or CS2. Additionally, we
-restrict our attention to the regime where the alignment torque is weak and CS2
-remains stable; specifically, we use $\abs{g}t_{\rm al}= 10^{3}$. We
-numerically integrate Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) for many
-random initial conditions uniformly distributed in $\p{\cos \theta, \phi}$ and
-record the nearest CS for each integration after $10t_{\rm al}$. In
+Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}): what is the long term evolution of
+$\uv{s}$for a general initial $\uv{s}_{\rm i}$?
+
+For $\eta > \eta_{\rm c}$, the only stable (and attracting) spin state is CS2,
+and all initial conditions will evolve asympotically towards it.
+
+For $\eta < \eta_{\rm c}$, both CS1 and CS2 are stable (assuming the alignment
+torque is sufficiently that CS2 remains a fixed point; see
+Section~\ref{ss:mcs}), and spin evolution may involve separatrix crossing. To
+explore the fate of various initial $\uv{s}$ orientations, we numerically
+integrate Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) for many random initial
+conditions uniformly distributed in $\p{\cos \theta_{\rm i}, \phi_{\rm i}}$ and
+determine the nearest CS for each integration after $10t_{\rm al}$. In
 Fig.~\ref{fig:toy_phop}, we show the results of this procedure for $\eta = 0.2$,
-and $I = 20^\circ$. It is clear that initial conditions in zone I evolve into
-CS1, those in zone II evolve into CS2, while those in zone III have a
-probabilistic outcome. We aim to understand each of these in turn:
+and $I = 20^\circ$ (we use $t_{\rm al} = 10^3 / \abs{g}$, but the results are
+unchanged as long as $t_{\rm al} \gg \abs{g}^{-1}$). It is clear that initial
+conditions in zone I evolve into CS1, those in zone II evolve into CS2, while
+those in zone III have a probabilistic outcome. These can be understood as
+follows:
 \begin{figure}
@@
     \includegraphics[width=\colummwidth]{../initial/0_eta/3stats3_5_0_2.png}
-    \caption{Plot illustrating the asymptotic behavior of initial conditions for
-    $\eta = 0.2$ and $I = 20^\circ$. Each dot represents an initial spin
-    orientation, and the coloring of the dot indicates which Cassini State
-    (legend) the system asymptotes towards.}\label{fig:toy_phop}
-\end{figure}
-
-For initial conditions in zone I, the spin circulates, and $\dot{\theta}$ is
-negative everywhere during the cycle. Thus, for initial conditions in zone I,
-$\theta$ decreases until the trajectory has converged to CS1. This is
-intuitively reasonable, as CS1 is stable.
-
-For initial conditions in zone II, our stability calculation in
-Section~\ref{ss:tidal_equils} shows that initial conditions sufficiently near CS2
-will converge to CS2. In fact, this result can be extended to all initial
-conditions inside the separatrix, shown in Appendix~\ref{app:cs_stab2}.
+    \caption{Asymptotic outcomes of spin evolution driven by an alignment torque
+    for different initial spin orientations ($\theta_{\rm i}$ and $\phi_{\rm
+    i}$) for a system with $\eta = 0.2$ and $I = 20^\circ$. Each dot represents
+    an initial spin orientation, and the coloring of the dot indicates which
+    stable Cassini State (legend) the system evolves into: initial conditions in
+    Zone I evolve into CS1, those in Zone II evolve into CS2, and those in Zone
+    III have a probabilistic outcome.}\label{fig:toy_phop}
+\end{figure}
+
+For initial conditions in zone I, the spin orientation circulates, and
+$\dot{\theta}$ is negative everywhere during the cycle. Thus $\theta$ decreases
+until the trajectory has converged to CS1. This is intuitively reasonable, as
+CS1 is stable and attracting (see Section~\ref{ss:linear_stab}).
+
+For initial conditions in zone II, our stability analysis in
+Section~\ref{ss:linear_stab} shows that when $\uv{s}$ is sufficiently near CS2,
+it will converge to CS2 since CS2 is stable and attracting. In fact, this result
+can be extended to all initial conditions inside the separatrix, as shown in
+Appendix~\ref{app:cs_stab2}.
 
 For initial conditions in zone III, since there are no stable CSs in zone III,
-the system must evolve through the separatrix to reach one of either CS1 or CS2.
-The outcome of the separatrix encounter is effectively probabilistic and
-determines the final CS\@. Intuitively, this can be understood as probabilistic
-resonance capture, as first studied in the seminal work of \citet{henrard1982}:
-since $\eta \ll \eta_{\rm c}$, $\alpha \gg -g$, but $\alpha \cos \theta$ can
-become commensurate with $-g$ if $\cos \theta$ becomes small. This is achieved
-as $\theta$ evolves from an initially retrograde obliquity through $90^\circ$
-towards $0^\circ$ under the influence of the dissipative term in
-Eq.~\eqref{eq:dqdt_toy}.
+the system must evolve through the separatrix to reach either CS1 or CS2.
+The outcome of the separatrix encounter is probabilistic and determines the
+final CS\@. Intuitively, this can be understood as probabilistic resonance
+capture, as first studied in the seminal work of \citet{henrard1982}: for
+$\eta \lesssim \eta_{\rm c} \sim 1$, we have that $\alpha \gg -g$, but $\alpha
+\cos \theta$ can become commensurate with $-g$ if $\cos \theta$ becomes small.
+This is achieved as $\theta$ evolves from an initially retrograde obliquity
+through $90^\circ$ towards $0^\circ$ under the influence of the alignment
+torque.
 
 While similar in behavior to previous studies of probabilistic resonance capture
-\citep{henrard1982, su2020}, the underlying mechanism is different: in these
+\citep{henrard1982, su2020}, the underlying mechanism is different: In these
 previous studies, the phase space structure itself evolves and causes systems to
-transition among phase space zones, while in the present scenario, a
-non-Hamiltonian, dissipative perturbation causes systems to transition among
-unchanging phase space zones. In the following section, we present a calculation
-to understand analytically the probability distribution of outcomes upon
-separatrix encounter in this new scenario.
-
-\subsubsection{Analytical Calculation of Resonance Capture Probability}
-
-Before discussing quantitative calculations, we first present a graphical
+transition among different phase space zones; here in the problem at hand, a
+non-Hamiltonian, dissipative perturbation causes the system to transition among
+fixed phase space zones. In the following subsection, we present an analytic
+calculation to determine the probability distribution of outcomes upon
+separatrix encounter. Readers not interested in the technical details can simply
+examine the resulting Fig.~\ref{fig:1hist_toy}.
+
+\subsection{Analytical Calculation of Resonance Capture
+Probability}\label{ss:analytic_calculation}
+
+Before discussing our quantitative calculation, we first present a graphical
 understanding of the separatrix encounter process.
 Figure~\ref{fig:toy_hop_manifolds} shows how the perturbative alignment torque
-generates the two outcomes upon separatrix encounter, a zone III-II or a zone
-III-I transition. The critical trajectories in Fig.~\ref{fig:toy_hop_manifolds}
-are calculated numerically by integrating a point infinitesimally close to CS4
-forward and backward in time. In the absence of the alignment torque, these
-trajectories would evolve along the separatrix, but in the presence of the
-alignment torque, they are perturbed slightly and cease to overlap. It can be
-seen in Fig.~\ref{fig:toy_hop_manifolds} that this splitting opens a path from
-zone III into both zones I and II\@.
+generates the two outcomes upon separatrix encounter, i.e.\ the zone III to zone
+II and the zone III to zone I transition. The critical trajectories in
+Fig.~\ref{fig:toy_hop_manifolds} are calculated numerically by integrating from
+a point infinitesimally close to CS4 forward and backward in time. In the
+absence of the alignment torque, these trajectories would evolve along the
+separatrix, but in the presence of the alignment torque, they are perturbed
+slightly and cease to overlap. It can be seen in
+Fig.~\ref{fig:toy_hop_manifolds} that this splitting opens a path from zone III
+into both zones I and II\textcolor{red}{: the coloring denotes that trajectories
+within the orange and green colored regions of phase space stay within their
+respective colored regions of phase space.}
 
 To understand this process more concretely, as well as associate probabilities
-to the two possible outcomes, it is important to be quantitative. The correct
-approach is to consider the evolution of the value of the \emph{unperturbed}
-Hamiltonian (Eq.~\ref{eq:H}) as the spin evolves due to the alignment torque. A
-point in zone III evolves such that $H$ is increasing until $H \approx H_{\rm
-sep}$ where $H_{\rm sep}$ is the value of $H$ along the separatrix, given by
-\begin{align}
-    H_{\rm sep} &\equiv H\p{\cos \theta_{\rm 4}, \phi_{\rm 4}},\nonumber\\
+to the two possible outcomes, it is important to be quantitative. To this end,
+we consider the evolution of the value of the \emph{unperturbed} Hamiltonian
+(Eq.~\ref{eq:H}) as the spin evolves due to the alignment torque. A point in
+zone III evolves such that $H$ is increasing until $H \approx H_{\rm sep}$ where
+$H_{\rm sep}$ is the value of $H$ along the separatrix, given by
+\begin{align}
+    H_{\rm sep} &\equiv H\p{\cos \theta_{\rm 4}, \phi_{\rm 4}}\nonumber\\
         &\approx g\sin I + \frac{g^2}{2\alpha}\cos^2 I +
@@
 \end{align}
-where $\theta_4$ and $\phi_4$ are the coordinates of CS4. As the system evolves
-closer to the separatrix, the change in $H$ over each circulation cycle can be
-approximated by $\Delta H_-$, the change in $H$ along $\mathcal{C}_-$ (see
-Fig.~\ref{fig:1contours}). In general, we define the quantities $\Delta H_{\pm}$
+where
+\begin{equation}
+    \theta_4 \simeq \pi/2 - \eta \cos I
+\end{equation}
+(see Section~A.1 of Paper I) and $\phi_4 = 0$ are the coordinates of CS4. As the
+system evolves closer to the separatrix, the change in $H$ over each circulation
+cycle can be approximated by $\Delta H_-$, the change in $H$ along
+$\mathcal{C}_-$ (see Fig.~\ref{fig:1contours}). In general, we define the
+quantities $\Delta H_{\pm}$
 \begin{equation}
@@
 \end{equation}
-This can be simplified by using:
+Using
 \begin{align}
@@
             \pd{H}{(\cos \theta)}\rd{(\cos \theta)}{t}
-            + \pd{H}{\phi}\rd{\phi}{t},\nonumber\\
-        &= \p{\rd{(\cos\theta)}{t}}_{\rm tide} \rd{\phi}{t},\\
+            + \pd{H}{\phi}\rd{\phi}{t}\nonumber\\
+        &= \p{\rd{(\cos\theta)}{t}}_{\rm tide} \rd{\phi}{t}
+\end{align}
+and Eq.~\eqref{eq:dqdt_toy}, we find
+\begin{align}
     \Delta H_{\pm} &= \mp\frac{1}{t_{\rm al}}
-        \int\limits_0^{2\pi} \sin^2\theta\;\mathrm{d}\phi.
-\end{align}
-In the first line, Hamilton's equations ensure that the non-tidal contributions
-to $\rdil{H}{t}$ vanish. Thus, if we evaluate $H$ every time that a trajectory
-originating in zone III crosses $\phi = 0$, we see that it will initially be $<
-H_{\rm sep}$ and increase for each circulation cycle until the system encounters
-the separatrix. At the beginning of the separatrix-crossing orbit, the initial
-value of $H$, denoted $H_{\rm i}$, must be greater than $H_{\rm sep} - \Delta H$
-to encounter the separatrix on the current orbit, and must be less than $H_{\rm
-sep}$, otherwise the trajectory will be in zone II already. We thus have
-\begin{equation}
-    H_{\rm i} \in \s{ H_{\rm sep} - \Delta H_-,  H_{\rm sep} }
-        \label{eq:Hi_range},
-\end{equation}
-The values of $\cos \theta$ corresponding to the lower and upper bounds on this
-range are shown as the black and red dots on the left of
+        \int\limits_0^{2\pi} \sin^2\theta\;\mathrm{d}\phi,
+        \label{eq:deltaH_pm_toy}
+\end{align}
+where $\theta = \theta\p{\phi}$ is evolved along $\mathcal{C}_{\pm}$. Thus, if
+we evaluate $H$ every time that a trajectory originating in zone III crosses
+$\phi = 0$, we see that will initially be $< H_{\rm sep}$ and increase for
+each circulation cycle until the system encounters the separatrix. At the
+beginning of the separatrix-crossing orbit, the initial value of $H$, denoted
+by $H_{\rm i}$, must be greater than $H_{\rm sep} - \Delta H_-$ to encounter the
+separatrix on the current orbit, and must be less than $H_{\rm sep}$, otherwise
+the trajectory will be in zone II already. We thus require
+\begin{equation}
+    H_{\rm i} \in \s{ H_{\rm sep} - \Delta H_-,  H_{\rm sep}}
+        \label{eq:Hi_range}.
+\end{equation}
+The values of $\cos \theta$ corresponding to the lower and upper bounds in this
+range are shown as the black and purple dots on the left of
 Fig.~\ref{fig:toy_hop_manifolds} respectively.
@@
 approximately along $\mathcal{C}_-$ and then along $\mathcal{C}_+$, after which
-the final value of $H$, denoted $H_{\rm f}$ is approximately equal to
+the final value of $H$, denoted by $H_{\rm f}$, is approximately equal to
 \begin{equation}
@@
 \end{equation}
-There can then be two outcomes depending on the value of $H_{\rm f}$:
+There are two outcomes depending on the value of $H_{\rm f}$:
 \begin{itemize}
-    \item If $H_{\rm f} > H_{\rm sep}$, then the trajectory enters the
-        separatrix, following the red shaded region in
-        Fig.~\ref{fig:toy_hop_manifolds}, and executes a zone III $\to$ II
-        transition.
-
-    \item If $H_{\rm f} < H_{\rm sep}$, then the trajectory exits the separatrix
-        above CS4, following the yellow shaded region in
-        Fig.~\ref{fig:toy_hop_manifolds} and executes a zone III $\to$ I
-        transition.
+    \item If $H_{\rm f} < H_{\rm sep}$, then\textcolor{red}{, since $H < H_{\rm
+        sep}$ corresponds to the exterior of the separatrix, this implies that
+        the trajectory has ended its separatrix-crossing orbit outside of the
+        separatrix. This outcome thus corresponds to a zone III to zone I
+        transition, and corresponds to evolution within the orange shaded
+        regions in Fig.~\ref{fig:toy_hop_manifolds}.}
+
+    \item If $H_{\rm f} > H_{\rm sep}$, then \textcolor{red}{the trajectory has
+        instead ended its separatrix-crossing orbit inside of the separatrix and
+        has executed a zone III to zone II transition. This corresponds to
+        evolution within the green shaded regions in
+        Fig.~\ref{fig:toy_hop_manifolds}}.
 \end{itemize}
-These two possibilites can be re-expressed in terms of $H_{\rm i}$: we find that
+These two possibilites can be re-expressed in terms of $H_{\rm i}$:
 if $H_{\rm i}$ is in the interval $\s{H_{\rm sep} - \Delta H_-, H_{\rm sep} -
@@
 sep}}$, then the system executes a III $\to$ II transition. We see that there is
-a critical value of $H_{\rm i}$ in the interval given by
-Eq.~\eqref{eq:Hi_range}, where $H_{\rm i} = H_{\rm sep} - \Delta H_{-} - \Delta
-H_+$, that separates the two possible outcomes of the separatrix encounter
-within the interval given by Eq.~\eqref{eq:Hi_range}. The value of $\cos \theta$
-for which $H$ is equal to $H_{\rm sep} - \Delta H_{-} - \Delta H_+$ is shown as
-the blue dot on the left of Fig.~\ref{fig:toy_hop_manifolds}. Finally, if the
-alignment torque is weak, then $\Delta H_- \sim \mathcal{O}\p{t_{\rm al}^{-1}}$
-is small compared to any variation in the value of $H$ (e.g.\ when changing
-$\phi_0$ or $\theta_0$ by a small amount), and $H_{\rm i}$ can be effectively
-considered as randomly chosen from a uniform distribution over $\s{H_{\rm sep} -
-\Delta H_-, H_{\rm sep}}$. As a consequence we obtain the probability of a III
-$\to$ II transition:
+a critical value of $H_{\rm i}$,
+\begin{equation}
+    \p{H_{\rm i}}_{\rm crit} = H_{\rm sep} - \Delta H_{-} - \Delta H_+,
+        \label{eq:def_Hicrit}
+\end{equation}
+that separates the two possible outcomes of the separatrix encounter within the
+interval given by Eq.~\eqref{eq:Hi_range}. The value of $\cos \theta$ for which
+$H$ is equal to $H_{\rm sep} - \Delta H_{-} - \Delta H_+$ is shown as the blue
+dot on the left of Fig.~\ref{fig:toy_hop_manifolds}. Finally, if the alignment
+torque is weak, then $\abs{\Delta H_{\pm}} \propto t_{\rm al}^{-1}$ is small
+compared to any variation in the value of $H$ (e.g.\ when changing the initial
+$\phi_{\rm i}$ or $\theta_{\rm i}$ by a small amount), and $H_{\rm i}$ can be
+effectively considered as randomly chosen from a uniform distribution over
+the range $\s{H_{\rm sep} - \Delta H_-, H_{\rm sep}}$. As a consequence we
+obtain the probability of the III $\to$ II transition:
 \begin{equation}
@@
     \includegraphics[width=\colummwidth]{../initial/0_eta/6manifolds0_20.png}
-    \caption{Plot illustrating the probabilistic origin of separatrix capture
-    for $\eta = 0.2$, $I = 20^\circ$, and $\abs{gt_{\rm al}} = 10^{3}$. Orange
-    regions converge to CS1, and green to CS2, while CS4 is labeled with the
-    purple dots. The boundaries separating the CS1 and CS2-approaching regions
-    consist of the critical trajectories (labeled in the legend) that, when
-    evolved either forwards or backwards in time (superscripts in the legend
-    labels), asymptotically approach CS4 where either $\phi = 0^\circ$ or $\phi
-    = 360^\circ$ (subscripts in the legend labels). Within zone III, the regions
-    of phase space reaching CS1 and CS2 both become very thin (shown
-    qualitatively as the light green lines of decreasing width), reflecting the
-    fact that the outcome for a particular initial condition can be approximated
-    as probabilistic sufficiently far from the separatrix. Labeled in the blue
-    and black dots at the left edge of the plot are the two backwards-in-time
-    critical trajectories intersect $\phi = 0$, and are where $H$ is equal to
-    $H_{\rm sep} - \Delta H_- - \Delta H_+$ and $H_{\rm sep} - \Delta H_-$
-    respectively (Eqs.~\ref{eq:def_Hsep} and~\ref{eq:def_dHpm}).
+    \caption{Plot illustrating the probabilistic origin of separatrix
+    (resonance) capture for a system with $\eta = 0.2$ and $I = 20^\circ$. The
+    orange regions converge to CS1, and the green to CS2. The purple dots denote
+    CS4, a saddle point. The boundaries separating the CS1 and CS2-approaching
+    regions consist of four critical trajectories (labeled in the legend)
+    \textcolor{red}{that are evolved starting from infinitesimal displacements
+    from CS4 along its stable and unstable axes going forwards and backwards in
+    time: e.g.\ the trajectory labeled CS4$_{\phi=0}^+$ starts at $\phi =
+    \epsilon$ (for some small, positive $\epsilon$) and evolves forwards in time
+    (with $t_{\rm al} = 10^3 \abs{g}^{-1}$), while the trajectory labeled
+    CS4$_{\phi=360}^-$ starts at $\phi = 360^\circ - \epsilon$ and evolves
+    backwards in time. The blue and black dots denote the intersections of
+    CS4$_{\phi = 0}^-$ and CS4$_{\phi = 360}^-$ critical trajectories with the
+    vertical line $\phi = 0$. These critical trajectories can be used to
+    understand the probabilistic outcomes that trajectories originating in zone
+    III experience upon separatrix encounter, illustrated by the tightly spaced
+    orange and green bands in zone III\@; see
+    Section~\ref{ss:analytic_calculation} for additional details.}
     }\label{fig:toy_hop_manifolds}
@@
 
-To actually evaluate Eq.~\eqref{eq:def_P32_toy}, we can use the parameterization
-for the separatrix given in Paper I for $\eta \ll 1$:
+To actually evaluate Eq.~\eqref{eq:def_P32_toy} analytically, we use the
+approximate expression for the separatrix $\eta \ll 1$ (see Eq.~B5 of Paper I):
 \begin{equation}
@@
 \end{equation}
-It can then be shown that
+Using Eq.~\eqref{eq:deltaH_pm_toy}, we find
 \begin{align}
@@
         \frac{32 \eta^{3/2}\cos I \sqrt{\sin I}}{t_{\rm al}}
-            + \mathcal{O}\p{\eta^{5/2}},\\
+            + \mathcal{O}\p{\eta^{5/2}},
+\end{align}
+and thus
+\begin{align}
     P_{\rm III \to II} &\approx
@@
 
-To directly compare Eq.~\eqref{eq:P32_toy} with numerical simulation, we perform
-numerical integrations of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) while
-restricting our attention only initial conditions in zone III\@.
-In Fig.~\ref{fig:1hist_toy}, we display Eq.~\eqref{eq:P32_toy} alongside the
-computed $P_{\rm III \to II}$ using $1000$ initial conditions in zone III for
-each of $60$ values of $\eta$. Excellent agreement is observed.
+To compare Eq.~\eqref{eq:P32_toy} with numerical results, we perform numerical
+integrations of Eqs.~(\ref{eq:dqdt_toy}--\ref{eq:dfdt_toy}) while restricting
+the initial conditions to those in zone III\@. In Fig.~\ref{fig:1hist_toy}, we
+display Eq.~\eqref{eq:P32_toy} alongside the computed $P_{\rm III \to II}$ using
+$1000$ initial conditions in zone III for each of $60$ values of $\eta$.
+Excellent agreement is observed.
 \begin{figure}
@@
     \includegraphics[width=\colummwidth]{../initial/3_toy3/1hist_toy.png}
-    \caption{Plot of $P_{\rm III \to II}$ as a function of $\eta$ for the
-    constant alignment torque model considered in Section~\ref{s:toy_model}. For
-    each $\eta$, $1000$ initial $\theta_0$ in zone III are evolved until just
-    after separatrix encounter, where the outcome of the encounter is recorded.
-    Shown in red is Eq.~\eqref{eq:P32_toy}.}\label{fig:1hist_toy}
-\end{figure}
-
-Finally, we remark that the calculation above is just an of \emph{Melnikov's
-Method} \citep{g_and_h}. Melnikov's Method is a general calculation that gives
-the degree of splitting of a ``homoclinic orbit'' (here, the separatrix) induced
-by a small, possibly time-dependent, perturbation. The explicit connection
-between the evolution of the unperturbed Hamiltonian and distances between
-curves in phase space (as seen in Fig.~\ref{fig:toy_hop_manifolds}) is provided by
-Melnikov's Method.
+    \caption{Zone III to Zone II transition probability $P_{\rm III \to II}$
+    upon separatrix encounter as a function of $\eta$ driven by an alignment
+    torque. For each $\eta$, $1000$ initial random $\theta_{\rm i}$ values in
+    zone III are evolved until just after separatrix encounter, where the
+    outcome of the encounter is recorded. The red line shows the analytical
+    result, Eq.~\eqref{eq:P32_toy}.}\label{fig:1hist_toy}
+\end{figure}
+
+\textcolor{red}{The rigorous connection between the above calculation, focusing
+on the evolution of $H$ along the two legs of the separatrix
+$\mathcal{C}_{\pm}$, and the graphical picture illustrated in
+Fig.~\ref{fig:toy_hop_manifolds} is provided by \emph{Melnikov's Method}
+\citep{g_and_h}.} Melnikov's Method is a general calculation that gives the
+degree of splitting of a ``homoclinic orbit'' (here, the separatrix) of a
+Hamiltonian system induced by a small, possibly time-dependent, perturbation.
+\textcolor{red}{At a qualitative level, we can state the connection succinctly:}
+\begin{itemize}
+    \item \textcolor{red}{The trajectory labeled CS4$_{\phi = 360}^-$ is evolved
+        backwards in time from CS4 (where the Hamiltonian has the value $H_{\rm
+        sep}$) along $\mathcal{C}_-$, and thus the black dot labels the start of
+        a separatrix-crossing orbit with the initial value of the Hamiltonian
+        $H_{\rm i} = H_{\rm sep} - H_-$. According to Eq.~\eqref{eq:Hi_range},
+        this is exactly the minimum $H_{\rm i}$ such that a trajectory
+        experiences a separatrix-crossing orbit. This is consistent with
+        Fig.~\ref{fig:toy_hop_manifolds}, where it is clear that any
+        trajectories below the black dot at $\phi = 0$ will not experience a
+        separatrix encounter on its current circulation cycle.}
+
+    \item \textcolor{red}{The trajectory labeled CS4$_{\phi = 0}^-$ is the one
+        evolving backwards in time from CS4 along first $\mathcal{C}_+$ then
+        $\mathcal{C}_-$, and thus the blue dot labels the start of a
+        separatrix-crossing orbit with $H_{\rm i} = H_{\rm sep} - \Delta H_{-} -
+        \Delta H_+$. According to Eq.~\eqref{eq:def_Hicrit}, this is exactly the
+        critical value of $H_{\rm i}$ that separates trajectories executing a
+        III$\to$II transition and a III$\to$I transition. This is also
+        consistent with Fig.~\ref{fig:toy_hop_manifolds}, where the region above
+        CS4$_{\phi = 0}^-$ is colored green while the region below is colored
+        orange.}
+\end{itemize}
 
@@
 
-\subsection{Tidal Model: Equilibrium Tides}\label{ss:weaktide}
-
-Having understood the effect of introducing an additional dissipative torque to
-the Colombo's Top system, we now implement a realistic model of tidal
-dissipation. We use the weak friction theory of equilibrium tides
-\citep{lai2012}. In this model, tides cause both the spin orientation $\uv{s}$
-and frequency $\Omega_{\rm s}$ to evolve on the characteristic tidal timescale
-$t_{\rm s}$ following:
+\subsection{Tidal Cassini Equilibria (tCE)}\label{ss:tce}
+
+Having understood the effect of the alignment torque on the spin evolution
+(Section~\ref{s:toy_model}), we now implement the full effect of tidal
+dissipation, including both tidal alignment and spin synchronization. We use the
+weak friction theory of equilibrium tides \citep[e.g.][]{alexander1973weak,
+hut1981tidal}. In this model, tides cause both the spin orientation $\uv{s}$ and
+frequency $\Omega_{\rm s}$ to evolve on the characteristic tidal timescale
+$t_{\rm s}$ following \citep[see][]{lai2012}:
 \begin{align}
@@
     \frac{1}{t_{\rm s}} \equiv \frac{1}{4k}
-        \frac{3k_2}{Q}\p{\frac{M_\star}{m}}\p{\frac{R}{a}}^3 n.
-\end{equation}
-In this section, we neglect orbital evolution in this section since the time
-scale is longer than $t_{\rm s}$ by a factor of $\sim L / S \gg 1$, and so
-$t_{\rm s}$ is a constant. We will continue mostly consider the case where tidal
-dissipation is slow, i.e.\ $\abs{g}t_{\rm s} \gg 1$. The full equations of
-motion including weak tidal friction can be written in component form as
+        \frac{3k_2}{Q}\p{\frac{M_\star}{m}}\p{\frac{R}{a}}^3 n,
+\end{equation}
+with $k_2 = 3k_{\rm q}$ and $Q$ the tidal Love number and tidal quality factor,
+respectively. We neglect orbital evolution (thus, $t_{\rm s}$ is a constant) in
+this section since the time scale is longer than $t_{\rm s}$ by a factor of
+$\sim L / S \gg 1$ (but see Section~\ref{ss:disc_wasp12b}). We will continue
+to consider the case where tidal dissipation is slow, i.e.\ $\abs{g}t_{\rm
+s} \gg 1$. The full equations of motion including weak tidal friction can be
+written in component form as
 \begin{align}
@@
 \end{align}
-The conditions for which the two tidal terms vanish are given respectively by:
-\begin{align}
-    \dot{\theta}_{\rm tide} = 0 &: \quad \frac{2n}{\Omega_{\rm s}} = \cos \theta,
-        \label{eq:weaktide_dqzero}\\
-    \dot{\Omega}_{\rm s} = 0 &: \quad \frac{n}{\Omega_{\rm s}}
-        = \frac{1 + \cos^2\theta}{2\cos \theta}.\label{eq:weaktide_dWszero}
-\end{align}
-
-To understand the long-term behaviors of this system, we first consider its
+
+Equation~\eqref{eq:ds_fulls} shows that, at a given obliquity, tides tend to
+drive $\Omega_{\rm s}$ towards the pseudosynchronous equilibrium value
+\begin{equation}
+     \frac{n}{\Omega_{\rm s}}
+        = \frac{1 + \cos^2\theta}{2\cos \theta} \quad
+        \p{\dot{\Omega}_{\rm s} = 0}.\label{eq:weaktide_dWszero}
+\end{equation}
+On the other hand, Eq.~\eqref{eq:ds_fullq} shows that the spin-orbit alignment
+timescale $t_{\rm al}$ is related to $t_{\rm s}$ by
+\begin{equation}
+    t_{\rm al}^{-1} = t_{\rm s}^{-1}\p{\frac{2n}{\Omega_{\rm s}} - \cos \theta}.
+        \label{eq:tal_ts_relation}
+\end{equation}
+Thus, $\dot{\theta}_{\rm tide} < 0$ for $2n / \Omega_{\rm s} > \cos \theta$ and
+$\theta_{\rm tide} > 0$ for $2n / \Omega_{\rm s} < \cos \theta$.
+
+To understand the long-term evolution of this system, we first consider its
 behavior near a CS\@. Specifically, we wish to understand whether initial
 conditions near a CS stay near the CS as the evolution of $\Omega_{\rm s}$
-causes the CSs to evolve. We first note that the evolution of
-$\Omega_{\rm s}$ does not drive spins towards or away from CSs: As long as it
-evolves sufficiently slowly (adiabatically, Paper I), conservation of
-phase space area ensures that trajectories will remain at a roughly fixed
-distance to stable equilibria of the system. Thus, Eq.~\eqref{eq:dsdt_tide}
-alone determines whether a point evolves towards or away from a nearby CS as
-$\Omega_{\rm s}$ evolves. Then, evaluating Eq.~\eqref{eq:lambda_approx} with
-$t_{\rm al} = t_{\rm s} / \p{2n / \Omega_{\rm s} - \cos \theta}$ (compare
-Eqs.~\ref{eq:dsdt_tide_toy} and~Eq.~\ref{eq:dsdt_tide}), we see that CS2 is
-still always stable, while CS1 is becomes unstable for $\Omega_{\rm s} > 2n$.
-
-Using this result, we can then identify the long-term equilibria of the system
-when $\Omega_{\rm s}$ is also evolving: these equilibria of the system must both
-satisfy $\dot{\Omega}_{\rm s} = 0$ and be a CS that is stable in the presence of
-tidal dissipation (i.e.\ satisfying $\rdil{\uv{s}}{t} = 0$).
-Figure~\ref{fig:6equils006} describes the evolution of
-Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) qualitatively in the coordinates
-$(\Omega_{\rm s}, \theta)$, along with the locations of CS1 and CS2. The circled
-points in Fig.~\ref{fig:6equils006} satisfy the criteria to be long-term
-equilibria, and we call them \emph{tidal Cassini Equilibria} (tCE). We number
-tCE1 and tCE2 the tCE that are in CSs 1 and 2 respectively. The obliquities of
-the tCE depend on the system architecture, which can be quantified using the
-parameter
+causes the CSs (and separatrix) to evolve. We first note that the evolution of
+$\Omega_{\rm s}$ alone does not drive $\uv{s}$ towards or away from CSs: As long
+as it evolves sufficiently slowly (adiabatically, see Paper I), conservation of
+phase space area ensures that trajectories will remain at fixed distances to
+stable equilibria of the system. Thus, Eq.~\eqref{eq:dsdt_tide}
+or~\eqref{eq:ds_fullq} alone determine whether the system evolves towards or
+away from a nearby CS as $\Omega_{\rm s}$ evolves. Then, from
+Eq.~\eqref{eq:tal_ts_relation}, we see that CS2 is still always stable, while
+CS1 is becomes unstable for \textcolor{red}{$\Omega_{\rm s} > 2n \cos \theta_1
+\approx 2n$ where $\theta_1 \approx \eta \sin I$ (Paper I) is the obliquity of
+CS1}.
+
+Using this consideration, we can then identify the long-term equilibria of the
+system when tcidal torques drive the evolution of both the obliquity and
+$\Omega_{\rm s}$ (and thus $\eta$): these equilibria must both satisfy
+$\dot{\Omega}_{\rm s} = 0$ and be a CS that is stable in the presence of the
+tidal torque (i.e.\ satisfying $\rdil{\uv{s}}{t} = 0$); we call the long term
+equilibria \emph{tidal Cassini Equilibria} (tCE). Figure~\ref{fig:6equils006}
+depicts the evolution of the system following
+Eqs.~(\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) in the coordinates $(\Omega_{\rm
+s}, \theta)$ starting from several representative initial conditions, along with
+the locations of CS1 and CS2. The circled points in Fig.~\ref{fig:6equils006}
+denote the two tCEs (tCE1 and tCE2, depending on whether it lies on CS1 or CS2).
+
+The obliquities of the tCE and the evolutionary track in the
+$\theta$-$\Omega_{\rm s}$ plane depend on the parameter
 \begin{align}
@@
         = \eta \frac{\Omega_{\rm s}}{n}\nonumber\\
-        &= \frac{1}{2}\frac{k}{k_{\rm q}}
+        &= \frac{k}{2k_{\rm q}}
             \frac{m_{\rm p}m}{M_\star^2}
-            \p{\frac{a}{a_{\rm p}}}^3 \p{\frac{a}{R}}^3\cos(I).
+            \p{\frac{a}{a_{\rm p}}}^3 \p{\frac{a}{R}}^3\cos I.
             \label{eq:def_etasync}
@@
 In Fig.~\ref{fig:6equils006}, $\eta_{\rm sync} = 0.06$;
-Figs.~\ref{fig:6equils050}--\ref{fig:6equils070} illustrate the change to the
-tCE when $\eta_{\rm sync} = 0.5$ and $0.7$ respectively.
-
-The tCE obliquity as a function of $\eta_{\rm sync}$ are shown for $I =
-20^\circ$ in the top panel of Fig.~\ref{fig:probs20} and for $I = 5^\circ$ in
-the top panel of Fig.~\ref{fig:probs5}. In fact, an analytical expression for
-the tCE2 obliquity for $\eta_{\rm sync} \ll \eta_{\rm c}$ can be computed using
-Eqs.~(\ref{eq:weaktide_dWszero}--\ref{eq:def_etasync}) and that $\cos \theta_2
-\approx \eta \cos I$ to yield:
+Figs.~\ref{fig:6equils050}--\ref{fig:6equils070} illustrate the cases with
+$\eta_{\rm sync} = 0.5$ and $0.7$ respectively.
+
+The tCE obliquities as a function of $\eta_{\rm sync}$ are shown in
+Fig.~\ref{fig:tCEs} for $I = 20^\circ$ and $I = 5^\circ$. In fact, an analytical
+expression for the tCE2 obliquity for $\eta_{\rm sync} \ll 1$ can be obtained
+using Eqs.~\eqref{eq:weaktide_dWszero}--\eqref{eq:def_etasync} and $\cos
+\theta_2 \approx \eta \cos I$ (valid for $\eta \ll 1$; see Appendix of Paper I):
 \begin{align}
     \cos \theta_{\rm tCE2} &\approx \sqrt{\frac{\eta_{\rm sync} \cos I}{2}},
-        &
+        \\
     \frac{\Omega_{\rm s, tCE2}}{n} &\approx
-        \sqrt{2\cos I \eta_{\rm sync}}. \label{eq:def_tce2_approx}
-\end{align}
-This approximation for $\theta_{\rm tCE2}$ is shown as the black dashed line in
-the top panels of Fig.~\ref{fig:probs20} and~\ref{fig:probs5}, where good
-agreement is observed.
+        \sqrt{2 \eta_{\rm sync}\cos I}. \label{eq:def_tce2_approx}
+\end{align}
+This approximation for $\theta_{\rm tCE2}$ is shown as the blue dashed line in
+Fig.~\ref{fig:tCEs}, indicating good agreement with the numerical results
+\textcolor{red}{obtained via root finding of
+Eqs.~\eqref{eq:ds_fullq}--\eqref{eq:ds_fulls} while assuming that $\abs{g}t_{\rm
+s} \gg 1$}.
 \begin{figure*}
@@
     \caption{Schematic depiction of the effect of tidal friction on the planet's
-    spin for $I = 20^\circ$, corresponding to $\eta_{\rm c} \approx 0.574$
-    (Eq.~\ref{eq:def_etac}), and $\eta_{\rm sync} = 0.06$. The black and blue
-    lines denote where the tidal $\dot{\Omega}_{\rm s}$ and $\dot{\theta}$
-    change signs (Eqs.~\ref{eq:weaktide_dqzero}--\ref{eq:weaktide_dWszero}). The
-    orange and green lines give the CS1 and CS2 obliquities respectively, which
-    are the two CSs that are stable under the effect of tidal dissipation. Note
-    that when $\dot{\theta}_{\rm tide} > 0$, CS1 becomes unstable, denoted by
-    the dashed orange line. The points that are both CSs and satisfy
-    $\dot{\Omega}_{\rm s} = 0$ are the tidal Cassini Equilibria (tCE), which are
-    circled and labeled. The various colored crosses and their associated
-    colored lines represent a few characteristic examples of the evolution of
-    Colombo's Top under weak tidal friction (for illustrative purposes, we have
-    used $\abs{g}t_{\rm s} = 10^2$ and evolved each example for $5t_{\rm s}$).
-    The phase space evolution of the two thicker evolutionary trajectories (cyan
-    and pink; those beginning at $\theta_{\rm i} = 120^\circ$) are shown in
+    spin evolution in the $\theta$-$\Omega_{\rm s}$ plane for a system with $I =
+    20^\circ$ (corresponding to $\eta_{\rm c} \approx 0.574$; see
+    Eq.~\ref{eq:def_etac}) and $\eta_{\rm sync} = 0.06$ (see
+    Eq.~\ref{eq:def_etasync}). The black and blue lines denote where the tidal
+    $\dot{\Omega}_{\rm s}$ and $\dot{\theta}$ change signs
+    (Eqs.~\ref{eq:weaktide_dqzero}--\ref{eq:weaktide_dWszero}). The orange and
+    green lines give the CS1 and CS2 obliquities respectively (these are the two
+    CSs that can be stable in the presence of tidal dissipation). Note that when
+    $\dot{\theta}_{\rm tide} > 0$, CS1 becomes unstable, denoted by the dashed
+    orange line. The points that lie on CSs and satisfy $\dot{\Omega}_{\rm s}
+    = 0$ are called tidal Cassini Equilibria (tCE), which are circled and labeled.
+    The various colored crosses and their associated colored lines represent a
+    few characteristic examples of the spin evolution under weak
+    tidal friction (for illustrative purposes, we have used $\abs{g}t_{\rm s} =
+    10^2$ and evolved each example for $5t_{\rm s}$). The phase space evolution
+    of the two thicker evolutionary trajectories (cyan and pink; those beginning
+    at $\theta_{\rm i} = 120^\circ$) are shown in
     Figs.~\ref{fig:trajs1}--\ref{fig:trajs2}.
@@
     \caption{Same as Fig.~\ref{fig:6equils006} but for $\eta_{\rm sync} = 0.5$.
-    The light-colored crosses and lines correspond to evolutionary trajectories
-    using the same initial conditions as those shown in
+    The crosses and lines correspond to evolutionary trajectories using the same
+    initial conditions as those shown in
     Fig.~\ref{fig:6equils006}.}\label{fig:6equils050}
@@
     \includegraphics[width=\textwidth]{../initial/1_weaktide/6equils0_70.png}
-    \caption{Same as Figs.~\ref{fig:6equils006} and~\ref{fig:6equils050} but for
-    $\eta_{\rm sync} = 0.7$. Note that $\eta_{\rm sync} = 0.7 > \eta_{\rm c}
-    \approx 0.574$ and tCE1 does not exist. The phase space evolution of the
-    thick purple trajectory in the bottom panel (starting at $\theta_{\rm i}
-    = 10^\circ$) is shown in Fig.~\ref{fig:trajs3}. }\label{fig:6equils070}
+    \caption{Same as Figs.~\ref{fig:6equils006} but for $\eta_{\rm sync} = 0.7$.
+    Note that $\eta_{\rm sync} = 0.7 > \eta_{\rm c} \approx 0.574$ and tCE1 does
+    not exist. The phase space evolution of the thick purple trajectory
+    (starting at $\theta_{\rm i} = 10^\circ$) is shown in Fig.~\ref{fig:trajs3}.
+    }\label{fig:6equils070}
 \end{figure*}
@@
     \includegraphics[width=\colummwidth]{../initial/1_weaktide/6equils_sims/0_06_2.png}
-    \caption{Phase space evolution of the trajectory in
-    Fig.~\ref{fig:6equils006} colored in pink, for which $\eta_{\rm sync} =
-    0.06$ and $I = 20^\circ$ (for which $\eta_{\rm c} = 0.574$). The initial
-    conditions are $\Omega_{\rm s, i} = 2.5n$, $\theta_{\rm i} = 120^\circ$, and
-    $\phi_{\rm i} = 0^\circ$, and we have used $\abs{g}t_{\rm s} = 10^2$ and
-    have evolved the system for $5t_{\rm s}$. In the left-most panel, the
-    trajectory's evolution in $\p{\Omega_{\rm s}, \theta}$ coordinates along
-    with the curves indicating CS1, 2, and $\dot{\Omega}_{\rm s} = 0$ are
-    re-displayed from Fig.~\ref{fig:6equils006}. The vertical dashed lines
-    denote the values of $\Omega_{\rm s}$ for which the phase space evolution of
-    the system is displayed in the right four panels. In each of these right
-    four panels, the trajectory's evolution for a single circulation/libration
-    cycle is displayed in $\p{\cos \theta, \phi}$ phase space for the labeled
-    value of $\Omega_{\rm s}$. The system encounters the separatrix, undergoes a
-    III $\to$ I transition, and converges to tCE1.
+    \caption{Phase space evolution of the pink trajectory in
+    Fig.~\ref{fig:6equils006}, for which $\eta_{\rm sync} = 0.06$ and $I =
+    20^\circ$ (corresponding to $\eta_{\rm c} = 0.574$). The initial conditions
+    are $\Omega_{\rm s, i} = 2.5n$, $\theta_{\rm i} = 120^\circ$, and $\phi_{\rm
+    i} = 0^\circ$, and we have used $\abs{g}t_{\rm s} = 10^2$ and have evolved
+    the system for $5t_{\rm s}$. In the left-most panel, the trajectory's
+    evolution in the $\theta$-$\Omega_{\rm s}$ plane along with the curves
+    indicating CS1, CS2, and $\dot{\Omega}_{\rm s} = 0$ are re-displayed from
+    Fig.~\ref{fig:6equils006}. The vertical dashed lines denote the values of
+    $\Omega_{\rm s} / n$ for which a few phase space snapshots of the system are
+    displayed in the right four panels. In each of these right four panels, the
+    trajectory's evolution for a single circulation/libration cycle is displayed
+    in the $\theta$-$\Omega_{\rm s}$ plane for the labeled value of $\Omega_{\rm
+    s}$ (and the corresponding value of $\eta$). The system encounters the
+    separatrix, undergoes a III $\to$ I transition, and converges to tCE1.
     }\label{fig:trajs1}
@@
     \caption{Same as Fig.~\ref{fig:trajs1} but for $\phi_{\rm i} = 286^\circ$,
-    corresponding to the trajectory in Fig.~\ref{fig:6equils006} colored in
-    cyan. The system encounters the separatrix, undergoes a III $\to$ II
-    transition, and converges to tCE2. The small $\phi$ offset of tCE2 is
-    visible (see Fig.~\ref{fig:mcs}). Note that the initial condition of this
-    system and that displayed in Fig.~\ref{fig:trajs1} have the same initial
-    $\theta_{\rm i}$ and $\Omega_{\rm s, i}$ and only different precessional
-    phases $\phi_{\rm i}$.
+    corresponding to the cyan trajectory in Fig.~\ref{fig:6equils006}. The
+    system encounters the separatrix, undergoes a III $\to$ II transition, and
+    converges to tCE2. The small $\phi$ offset of tCE2 from $180^\circ$ arises
+    from the alignment torque (see Fig.~\ref{fig:mcs}). Note that the initial
+    condition of this trajectory and that displayed in Fig.~\ref{fig:trajs1}
+    have the same initial $\theta_{\rm i}$ and $\Omega_{\rm s, i}$ but different
+    precessional phases $\phi_{\rm i}$.
     }\label{fig:trajs2}
@@
     $\theta_{\rm i} = 10^\circ$, corresponding to the purple trajectory shown in
-    the bottom panel of Fig.~\ref{fig:6equils070}. Here, the system evolves
-    along CS1 until the separatrix disappears, upon which it experiences large
-    obliquity variations that damp due to tidal dissipation. The highly
-    asymmetric shape in the third panel arises due to the strong tidal
-    dissipation used in this simulation. The system finally converges to tCE2,
-    the only tCE that exists for this value of $\eta_{\rm sync}$ (see bottom
-    panel of Fig.~\ref{fig:6equils070}).}\label{fig:trajs3}
-\end{figure}
-
-There are two important conditions that can change the existence and stability
-of the tCE\@. First, if $\eta_{\rm sync} > \eta_{\rm c}$, then tCE1 will not
-exist, as can be seen in Fig.~\ref{fig:6equils070}\footnote{Strictly speaking,
+    Fig.~\ref{fig:6equils070}. Here, the system evolves along CS1 until the
+    separatrix disappears, upon which it experiences large obliquity variations
+    that damp due to tidal dissipation. The highly asymmetric shape in the third
+    panel arises due to the strong tidal dissipation used in this simulation
+    ($\abs{g}t_{\rm s} = 10^2$). The system finally converges to tCE2, the only
+    tCE that exists for this value of $\eta_{\rm sync}$.}\label{fig:trajs3}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=\colummwidth]{../initial/1_weaktide/5tces.png}
+    \caption{\textcolor{red}{Obliquities of the two tCE as a function of
+    $\eta_{\rm sync}$ (defined in Eq.~\ref{eq:def_etasync}) for $I = 20^\circ$
+    (top) and $I = 5^\circ$ (bottom). The blue dashed lines denote the
+    analytical approximation given by Eq.~\eqref{eq:def_tce2_approx} and is only
+    valid for $\eta_{\rm sync} \ll 1$. The vertical dashed lines denote where
+    $\eta_{\rm sync} = \eta_{\rm c}(I)$, above which tCE1 ceases to
+    exist.}}\label{fig:tCEs}
+\end{figure}
+
+There are two important conditions that can influence the existence and stability
+of the tCE\@. First, if $\eta_{\rm sync} > \eta_{\rm c}$ (where $\eta_{\rm c}$ is
+given by Eq.~\ref{eq:def_etac}), then tCE1 will not
+exist (Fig.~\ref{fig:6equils070} gives an example)\footnote{Strictly speaking,
 $\eta_{\rm sync}$ can be slightly smaller than $\eta_{\rm c}$, as the planet's
-spin is slightly subsynchronous at tCE1 when $\eta \approx \eta_{\rm c}$, e.g.\
-see Fig.~\ref{fig:6equils050}.}. Secondly, tCE2 may not be stable if the tidal
-phase shift is too large. Applying the results of Section~\ref{ss:tidal_equils},
-we find that tCE2 is stable as long as $t_{\rm s} \geq t_{\rm s, c}$ where
+spin is slightly subsynchronous at tCE1 (see Eq.~\ref{eq:weaktide_dWszero}).}.
+Secondly, tCE2 may not be stable if the phase shift due to the alignment torque
+(see Section~\ref{ss:mcs}) is too large. Applying
+the results of Section~\ref{ss:linear_stab}, we find that tCE2 is stable as long
+as $t_{\rm s} \geq t_{\rm s, c}$ where
 \begin{equation}
@@
 \end{equation}
-The tCE2 subscripts denote evaluation at tCE2. When $\eta_{\rm sync} \ll
-\eta_{\rm c}$, we can use Eq.~\eqref{eq:def_tce2_approx} to further simplify:
+When $\eta_{\rm sync} \ll 1$, we can use Eq.~\eqref{eq:def_tce2_approx} to
+further simplify $t_{\rm s, c}$ to:
 \begin{equation}
@@
 \end{equation}
-Note that this result differs in form from that given in
-\citet{fabrycky_otides}, which assume that the orbital precession of $\uv{l}$ is
-driven by the central star. Our expression is simpler and is applicable to
-systems where the orbital precession of the inner planet is dominated by an
-exterior planet.
-
-\subsection{Spin Obliquity Evolution as a Function of Initial Spin Orientation}
-
-With this result, we can now consider the final fate of the inner planet's spin.
-We begin by qualitatively examining the example trajectories shown in
+
+\subsection{Spin and Obliquity Evolution as a Function of Initial Spin
+Orientation}
+
+We can now study the final fate of the planet's spin as a function of the
+initial condition.
+We begin by examining the example trajectories shown in
 Figs.~\ref{fig:6equils006}, for which we have integrated
-Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) and set $I =
-20^\circ$. We discuss each of the six trajectories in turn:
+the equations of motion (combining Eqs.~\ref{eq:dsdt_rot}
+and~\ref{eq:dsdt_tide} to give $\rdil{\uv{s}}{t}$, and Eq.~\ref{eq:dWsdt_tide})
+and set $I = 20^\circ$, $t_{\rm s} = 100 \abs{g}^{-1}$. We discuss each of the
+six trajectories in turn:
 \begin{itemize}
-    \item The trajectory with initial conditions $\Omega_{\rm s, i} = 2.5n$ and
-        $\theta_{\rm i} = 10^\circ$ (purple) has an initially prograde spin
+    \item The trajectory with the initial condition $\Omega_{\rm s, i} = 2.5n$
+        and $\theta_{\rm i} = 10^\circ$ (purple) has an initially prograde spin
         (i.e.\ in zone I, see Fig.~\ref{fig:1contours}) and directly evolves to
-        tCE1 as the obliquity damps to zero.
-
-    \item The trajectory with initial conditions $\Omega_{\rm s, i} = 2.5n$ and
+        tCE1, with the final $\Omega_{\rm s} / n \simeq 1$ and $\theta =
+        \theta_{\rm CS1} \simeq \eta_{\rm sync} \sin I$ (for $\eta_{\rm sync}
+        \ll 1$; see Appendix~A of paper I).
+
+    \item The trajectory with $\Omega_{\rm s, i} = 2.5n$ and
         $\theta_{\rm i} = 90^\circ$ (red) has an initial condition inside the
-        resonance (zone II) and evolves to tCE2. Note that the obliquity is
-        trapped in a high value due to the stability of CS2 under weak tidal
-        friction, as discussed in Section~\ref{ss:weaktide}.
-
-    \item We have chosen two trajectories, both with initial conditions
-        $\Omega_{\rm s, i} = 2.5n$ and $\theta_{\rm i} = 120^\circ$ but with
-        different initial precessional phases $\phi_{\rm i}$; we first discuss
-        the pink trajectory, for which $\phi_{\rm i} = 0^\circ$. This trajectory
-        originates in zone III, evolves towards the separatrix as tidal friction
-        damps the obliquity, and crosses the resonance without being captured,
-        upon which the obliquity continues to damp until the system converges to
-        tCE1. The detailed phase space evolution of this trajectory is shown in
-        Fig.~\ref{fig:trajs1}, where the outcome of the separatrix encounter is
-        very visible.
-
-    \item The other trajectory with initial conditions $\Omega_{\rm s, i} = 2.5n$
-        and $\theta_{\rm i} = 120^\circ$ (light blue) only differs from the pink
-        trajectory as its initial precessional phase is $\phi_{\rm i} \approx
-        286^\circ$. Nevertheless, this trajectory originates in zone III,
-        encounters the separatrix and is captured into the resonance (zone II),
-        upon which tidal friction drives the system towards tCE2. The detailed
-        phase space evolution of this trajectory is shown in
-        Fig.~\ref{fig:trajs2}, where the resonance capture is displayed. Also
-        visible in the final panel of Fig.~\ref{fig:trajs2} is the slight phase
-        offset of CS2, i.e.\ $\phi_{\rm cs} < 180^\circ$, in agreement with the
-        discussion in Section~\ref{ss:tidal_equils} (see Fig.~\ref{fig:mcs}).
+        resonance / separatrix (zone II) and evolves to tCE2. Note that the
+        obliquity is trapped in a high value due to the stability of CS2 under
+        the alignment torque, as shown in Section~\ref{ss:tce}.
+
+    \item We have chosen two trajectories, both with the initial condition
+        $\Omega_{\rm s, i} = 2.5n$ and $\theta_{\rm i} = 120^\circ$, but with
+        different initial precessional phases $\phi_{\rm i}$: consider first
+        the pink trajectory, for which $\phi_{\rm i} = 0^\circ$. It originates
+        in zone III, evolves towards the separatrix as tidal friction damps the
+        obliquity, and crosses the resonance (separatrix) without being
+        captured, upon which the obliquity continues to damp until the system
+        converges to tCE1. The detailed phase space evolution of this trajectory
+        is shown in Fig.~\ref{fig:trajs1}, where the outcome of the separatrix
+        encounter is very visible.
+
+    \item The light blue trajectory also has $\Omega_{\rm s, i} =
+        2.5n$ and $\theta_{\rm i} = 120^\circ$ (like the pink trajectory) but
+        with the initial precessional phase $\phi_{\rm i} \approx 286^\circ$.
+        It also originates in zone III, encounters the separatrix but is
+        captured into the resonance (zone II), upon which tidal friction drives
+        the system towards tCE2. The detailed phase space evolution of this
+        trajectory is shown in Fig.~\ref{fig:trajs2}, where the resonance
+        capture is displayed. Also visible in the final panel of
+        Fig.~\ref{fig:trajs2} is the slight phase offset of CS2, i.e.\
+        $\phi_{\rm cs} < 180^\circ$, in agreement with the result of
+        Section~\ref{ss:mcs} (see Fig.~\ref{fig:mcs}).
 
     \item For completeness, we also examine some trajectories for initially
-        subsynchronous spin rates. The trajectory with initial conditions
-        $\Omega_{\rm s, i} = 0.1n$ and $\theta_{\rm i} = 35^\circ$ (blue) has its
-        obliquity rapidly damped to zero by tidal friction as it spins up to
-        spin-orbit synchronization, eventually converging to tCE1.
-
-        A subtlety of initially subsynchronous spins can be seen here: note that
-        the initial $\eta_{\rm i} = 0.6$ here, so the separatrix and CS1 do not
-        exist initially ($\eta_{\rm c} = 0.574$). As such, naively, one expects
-        initial convergence to CS2 and subsequent obliquity along with CS2 as
-        the spin increases. However, due to the strong tidal dissipation and the
-        proximity of $\eta_{\rm i}$ to $\eta_{\rm c}$, CS1 appears within a
-        single circulation cycle, and the obliquity quickly damps to, and
-        continues to evolve along, CS1.
-
-    \item The trajectory with initial conditions $\Omega_{\rm s, i} = 0.1n$ and
-        $\theta_{\rm i} = 100^\circ$ (teal) also has its obliquity rapidly
-        damped to zero as it approaches spin-orbit synchronization and tCE1. For
-        these initial conditions, we remark that this initial condition
-        converges to tCE2 when a tidal dissipation rate of $\abs{g}t_{\rm s} =
-        10^3$ is used, satisfying the intuitive analysis given in the previous
+        subsynchronous spin rates. The trajectory with $\Omega_{\rm s, i} =
+        0.1n$ and $\theta_{\rm i} = 35^\circ$ (blue) has its obliquity rapidly
+        damped to zero by tidal friction as it spins up to spin-orbit
+        synchronization, eventually converging to tCE1.
+
+        A subtlety of initially subsynchronous spins can be seen here: since the
+        initial $\eta_{\rm i} = 0.6 > \eta_{\rm c}$ ($= 0.574$) here, the
+        separatrix and CS1 do not exist initially. As such, naively, one expects
+        initial convergence to CS2 and subsequent obliquity evolution along CS2
+        as the spin increases. However, due to the strong tidal dissipation
+        adapted in the calculation and the proximity of $\eta_{\rm i}$ to
+        $\eta_{\rm c}$, CS1 appears within a single circulation cycle, and the
+        obliquity quickly damps to, and continues to evolve along CS1.
+
+    \item The trajectory with $\Omega_{\rm s, i} = 0.1n$ and $\theta_{\rm i} =
+        100^\circ$ (teal) also has its obliquity damped toward tCE1 as it
+        approaches spin-orbit synchronization. We note that if we adopt $t_{\rm
+        s} = 10^3\abs{g}^{-1}$, the same initial condition will converge to
+        tCE2, agreeing with the intuitive analysis given in the previous
         paragraph.
@@
 trajectories for $\eta_{\rm sync} = 0.5$ and $\eta_{\rm sync} = 0.7$ in
-Figs.~\ref{fig:6equils050}--\ref{fig:6equils070}. The qualitative evolution of
-these six examples only changes in a few important ways, so we will discuss just
-a few points of interest:
+Figs.~\ref{fig:6equils050}--\ref{fig:6equils070}. The qualitative behaviors of
+these six examples change in several important ways, so we will discuss a few
+points of interest:
 \begin{itemize}
     \item For both $\eta_{\rm sync} = 0.5$ and $\eta_{\rm sync} = 0.7$, we see
-        that both initial conditions with $\theta_{\rm i} = 120^\circ$ converge
-        to tCE2. In fact, for these values of $\eta_{\rm sync}$, all initial
-        conditions with $\theta_{\rm i} = 120^\circ$ will converge to tCE2
-        regardless of $\phi_{\rm i}$.
+        that the initial conditions with $\theta_{\rm i} = 120^\circ$
+        ($\phi_{\rm i} = 0$, pink; and $\phi_{\rm i} = 286^\circ$, blue)
+        converge to tCE2. In fact, for these values of $\eta_{\rm sync}$, all
+        initial conditions with $\theta_{\rm i} = 120^\circ$ will converge to
+        tCE2 regardless of $\phi_{\rm i}$.
 
@@
         $\eta_{\rm i} \gg \eta_{\rm c}$ and CS2 is the only low-obliquity spin
-        equilibrium. The system then continues to evolve along CS2 until
-        reaching a state satisfying $\dot{\Omega}_{\rm s} = 0$ as well.
-
-    \item Of particular interest is the evolution starting from the initial
-        conditions $\Omega_{\rm s, i} = 2.5n$ and $\theta_{\rm i} = 10^\circ$
-        (purple) when $\eta_{\rm sync} = 0.7$. Figure~\ref{fig:trajs3} shows the
-        detailed phase space evolution of this system, where it can be seen that
-        the system initially evolves along the stable CS1, but is ejected when
-        $\Omega_{\rm s}$ is sufficiently small that CS1 ceases to exist, upon
-        which large obliquity variations eventually lead to convergence to tCE2,
-        the only tCE that exists.
+        equilibrium. The system then continues to evolve along CS2 toward tCE2.
+
+    \item Of particular interest is the trajectory starting from the initial
+        condition $\Omega_{\rm s, i} = 2.5n$ and $\theta_{\rm i} = 10^\circ$
+        (purple) in the case of $\eta_{\rm sync} = 0.7$. Figure~\ref{fig:trajs3}
+        shows the detailed phase space evolution of this trajectory, where it
+        can be seen that the system initially evolves along the stable CS1, but
+        is ejected when $\Omega_{\rm s}$ becomes sufficiently small that CS1 ceases
+        to exist, upon which large obliquity variations eventually lead to
+        convergence to tCE2, the only tCE that exists.
 \end{itemize}
-It can be seen that the dynamics are complex and can vary greatly depending on
-the parameters used. In the case where the initial spin is subsynchronous, the
+From the above examples, we see that the spin evolution driven by tides can be
+complex and varies greatly depending on the various system parameters and
+initial conditions. In the case where the initial spin is subsynchronous, the
 detailed outcome depends sensitively on $\eta_{\rm i}$ and the tidal dissipation
 rate. For tractability, we restrict our subsequent discussion to the more
-astrophysically common regime $\Omega_{\rm s, i} \gg n$, and we adopt the
+astrophysically common regime of $\Omega_{\rm s, i} \gg n$, and we adopt the
 fiducial value $\Omega_{\rm s, i} = 10n$.
@@
 Having developed an intuition for a few different possible evolutionary
-histories, we can next attempt to draw general conclusions about the final fate
-of the inner planet's spin as a function as a function of its initial
-conditions. We do this by again integrating
-Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide}) for many
-initial $\theta_0$ and $\phi_0$ and examining which tCE a given initial
-condition evolves into. For this study, we use a more gradual tidal dissipation
-rate of $\abs{gt_{\rm s}} = 10^3$. In Fig.~\ref{fig:Hhists_0_06}, we show the
-final outcome for many randomly chosen $\theta_0$ and $\phi_0$ for $\eta_{\rm
-sync} = 0.06$ and $I = 20^\circ$. We see that the behavior seen in the example
-trajectories in Fig.~\ref{fig:6equils006} are general: tCE1 is generally reached
-for spins initially in zone I (like the purple trajectory in
-Fig.~\ref{fig:6equils006}), tCE2 is generally reached for spins initially in
+trajectories, we can attempt to draw general conclusions about the final fate of
+the planet's spin as a function of its initial conditions. We do this by again
+integrating Eqs.~(\ref{eq:dsdt_rot},~\ref{eq:dsdt_tide}--\ref{eq:dWsdt_tide})
+for many initial $\theta_{\rm i}$ and $\phi_{\rm i}$ and examining the final
+outcomes. In contrast to the exmaples shown in
+Figs.~\ref{fig:6equils006}--\ref{fig:trajs3}, we use a more gradual tidal
+dissipation rate of $\abs{gt_{\rm s}} = 10^3$. In Fig.~\ref{fig:Hhists_0_06}, we
+show the final outcome for many randomly chosen $\theta_{\rm i}$ and $\phi_{\rm
+i}$ for $\eta_{\rm sync} = 0.06$ and $I = 20^\circ$. We see that the behaviors
+seen in the example trajectories of Fig.~\ref{fig:6equils006} are general: tCE1
+is generally reached for spins initially in zone I (like the purple trajectory
+in Fig.~\ref{fig:6equils006}), tCE2 is generally reached for spins initially in
 zone II (like the red trajectory in Fig.~\ref{fig:6equils006}), and a
@@
 light blue and pink trajectories in Fig.~\ref{fig:6equils006}).
-Figures~\ref{fig:Hhists_0_20} and~\ref{fig:Hhists_0_50} show the same results
-but for $\eta_{\rm sync} = 0.2$ and $\eta_{\rm sync} = 0.5$. As $\eta_{\rm
-sync}$ is increased, more initial conditions reach tCE2. This is both because
-there are more systems initially in zone II and because systems initially in
-zone III have a higher probability of executing a III $\to$ II transition upon
-separatrix encounter. Note also that in Fig.~\ref{fig:Hhists_0_50}, even initial
-conditions in zone I are able to reach tCE2; we comment on the origin of this
-behavior in the next section.
+Figures~\ref{fig:Hhists_0_20} and~\ref{fig:Hhists_0_50} show similar results for
+$\eta_{\rm sync} = 0.2$ and $\eta_{\rm sync} = 0.5$. As $\eta_{\rm sync}$ is
+increased, more initial conditions reach tCE2. This is both because there are
+more systems initially in zone II and because systems initially in zone III have
+a higher probability of executing a III $\to$ II transition upon separatrix
+encounter. Note also that in Fig.~\ref{fig:Hhists_0_50}, even initial conditions
+in zone I are able to reach tCE2; we comment on the origin of this behavior in
+the next section.
 \begin{figure}
@@
     \includegraphics[width=\colummwidth]{../initial/1_weaktide/5Hhists0_06_20.png}
-    \caption{\emph{Left:} Each dot indicates which tCE a given initial condition
-    $(\theta_{\rm i}, \phi_{\rm i})$ evolve towards (labeled in legend), for
-    $\eta_{\rm sync} = 0.06$ and $I = 20^\circ$. The planet's initial spin is
-    chosen to be $\Omega_{\rm s, i} = 10n$, and the three zones of phase space
-    (see Fig.~\ref{fig:1contours}) for the initial conditions are labeled,
-    separated by the separatrix (black line). Note that initial conditions in
-    zone I evolve towards tCE1, initial conditions in zone II evolve towards
-    tCE2, and initial conditions in zone III have an effectively probabilistic
-    outcome. \emph{Right:} Histogram of which tCE a given initial obliquity
-    $\theta_{\rm i}$ evolves towards, averaged over $\phi_{\rm
-    i}$.
-    \textcolor{red}{NB\@: the excess of tCE2 initial conditions at $\cos
-    \theta_{\rm i} \approx -1$ is likely an artifact of loss of numerical
-    precision, I am working on fixing this.}
+    \caption{\emph{Left:} Asymptotic outcomes of spin evolution in the presence
+    of weak tidal friction for different initial spin orientations ($\theta_{\rm
+    i}$ and $\phi_{\rm i}$) for a system with $\eta_{\rm sync} = 0.06$ and $I =
+    20^\circ$. Each dot represents an initial spin orientation, and the coloring
+    of the dot indicates which tCE (legend) the system evolves into. Similarly
+    to Fig.~\ref{fig:1hist_toy} initial conditions in Zone I evolve into CS1,
+    those in Zone II evolve into CS2, and those in Zone III \emph{Right:}
+    Histogram of the final tCE that a given initial obliquity $\theta_{\rm i}$
+    evolves into, averaged over $\phi_{\rm i}$.
     }\label{fig:Hhists_0_06}
@@
     \caption{Same as Fig.~\ref{fig:Hhists_0_06} but for $\eta_{\rm sync} =
-    0.2$.
-    \textcolor{red}{NB\@: the excess of tCE2 initial conditions at $\cos
-    \theta_{\rm i} \approx -1$ is likely an artifact of loss of numerical
-    precision, I am working on fixing this.}
-    }\label{fig:Hhists_0_20}
+    0.2$. }\label{fig:Hhists_0_20}
 \end{figure}
@@
 
-\subsubsection{Analytical Calculation of Resonance Capture Probability
+\subsection{Semi-analytical Calculation of Resonance Capture Probability
 }\label{ss:phop_weaktide}
@@
 Even when including the evolution of $\Omega_{\rm s}$, and therefore the
-spin-orbit precession frequency $\alpha$, the probabilities of the III $\to$ I
-and III $\to$ II transitions upon separatrix encounter can still be computed.
-The calculation resembles that presented in Section~\ref{ss:toy_outcomes} but is
-more involved. We describe the calculation below.
-
-In Section~\ref{ss:toy_outcomes}, we found that the evolution of $H$, the value
-of the unperturbed Hamiltonian, allowed us to calculate the probabilities of the
-various outcomes of separatrix encounter. Specifically, the outcome upon
-separatrix encounter is determined by the value of $H$ at the start of the
-separatrix-crossing orbit relative to $H_{\rm sep}$, the value of $H$ along the
-separatrix. However, when the spin is also evolving, $H_{\rm sep}$ is also
-changing during the separatrix-crossing orbit, and the discussion in
-Section~\ref{ss:toy_outcomes} must be generalized to account for this. Instead
-of focusing on the evolution of $H$ along a trajectory, we instead follow the
-evolution of
+parameter $\eta$ (see Eq.~\ref{eq:def_eta}), the probabilities of the III $\to$ I
+and III $\to$ II transitions upon separatrix encounter can still be obtained
+semi-analytically. The calculation resembles that presented in
+Section~\ref{ss:analytic_calculation} but involves several new ingredients. We
+describe the calculation below.
+
+In Section~\ref{ss:analytic_calculation}, we found that the evolution of $H$,
+the value of the unperturbed Hamiltonian, allowed us to calculate the
+probabilities of the various outcomes of separatrix encounter. Specifically, the
+outcome upon separatrix encounter is determined by the value of $H$ at the start
+of the separatrix-crossing orbit relative to $H_{\rm sep}$, the value of $H$
+along the separatrix. However, when the spin $\Omega_{\rm s}$ is also evolving,
+$H_{\rm sep}$ also changes during the separatrix-crossing orbit, and the
+calculation in Section~\ref{ss:analytic_calculation} must be generalized to
+account for this. Instead of focusing on the evolution of $H$ along a
+trajectory, we instead follow the evolution of
 \begin{equation}
@@
 \end{equation}
-Note that $K > 0$ inside the separatrix, and $K < 0$ outside. Then, the outcome
-of the separatrix-crossing orbit is largely the same as discussed in
-Section~\ref{ss:toy_outcomes}. First, we must compute the change in $K$ along
-the legs of the separatrix. We define $\Delta K_{\pm}$ by generalizing
-Eq.~\eqref{eq:def_dHpm} in the natural way:
-\begin{align}
-    \Delta K_{\pm} &= \oint_{\mathcal{C}_{\pm}} \rd{H}{t}
-        - \rd{H_{\rm sep}}{t}\;\mathrm{d}t.\label{eq:def_dK_weaktide}
+Note that $K > 0$ inside the separatrix, and $K < 0$ outside. With this
+modification, the outcome of the separatrix-crossing orbit can be determined in
+the same way as in Section~\ref{ss:analytic_calculation}. First, we must compute
+the change in $K$ along the legs of the separatrix. We define $\Delta K_{\pm}$
+by generalizing Eq.~\eqref{eq:def_dHpm} in the natural way:
+\begin{align}
+    \Delta K_{\pm} &= \oint_{\mathcal{C}_{\pm}} \s{\rd{H}{t}
+        - \rd{H_{\rm sep}}{t}}\;\mathrm{d}t.\label{eq:def_dK_weaktide}
 \end{align}
 Here, however, note that the contours $\mathcal{C}_{\pm}$ depends on the value
-of $\Omega_{\rm s}$ at separatrix encounter. Since there is no closed form
-solution for $\Omega_{\rm s}(t)$, the probabilities of the various outcomes
-cannot be expressed as a simple function of the initial conditions.
-
-Continuing the argument presented in Section~\ref{ss:toy_outcomes}, we consider
-the outcome of the separatrix-crossing orbit as a function of $K_i$, the value
-of $K$ at the start ($\phi = 0$) of the separatrix-crossing orbit. We find that
-if $K_i > -\Delta K_+ - \Delta K_-$, then the system undergoes a III $\to$ II
-transition and eventual evolution towards tCE2; while if $-\Delta K_- < K_i <
--\Delta K_- - \Delta K_+$, then the system undergoes a III $\to$ I transition
-and ultimate evolution towards tCE1. Thus, we find that the probability of a III
-$\to$ II transition is given by
+of $\Omega_{\rm s}$ at separatrix encounter (or the corresponding value $\eta =
+\eta_{\rm cross}$). Since there is no closed form solution for $\Omega_{\rm
+s}(t)$, the probabilities of the various outcomes cannot be expressed as a
+simple function of the initial conditions.
+
+Continuing the argument presented in Section~\ref{ss:analytic_calculation}, we
+consider the outcome of the separatrix-crossing orbit as a function of $K_i$,
+the value of $K$ at the start ($\phi = 0$) of the separatrix-crossing orbit. We
+find that if $-\Delta K_+ - \Delta K_- < I_{\rm i} < 0$, then the system
+undergoes a III $\to$ II transition and eventually evolves towards tCE2, and
+if $-\Delta K_- < K_i < -\Delta K_- - \Delta K_+$, then the system undergoes a
+III $\to$ I transition and ultimately evolves towards tCE1. Thus, we find that
+the probability of a III $\to$ II transition is given by
 \begin{equation}
@@
 $\Omega_{\rm s}$ is evolving, there is no way to express $\Delta K_{\pm}$ as a
-closed form of initial conditions. In fact, since many resonance encounters
-occur when $\eta$ is substantial, even an approximate calculation of $\Delta
-K_{\pm}$ using Eq.~\eqref{eq:sep_theta} is inaccurate, and we instead calculate
-$\Delta K_{\pm}$ along the numerically-calculated $\Delta K_{\pm}$ for arbitrary
-$\eta$. Note that Eqs.~(\ref{eq:def_dK_weaktide},~\ref{eq:def_pc_weaktide}) are
-equivalent to the separatrix capture result of \citet{henrard1982} when
-$\dot{\theta}_{\rm tide} = 0$ \citep{henrard1987}. Here, we have argued that
-this classic calculation can be unified with the calculation given in
-Section~\ref{ss:toy_outcomes} to give an accurate prediction of separatrix
-encounter outcome probabilities in the presence of both a dissipative
-perturbation and a parametric evolution of the Hamiltonian.
+closed form of the initial conditions. In fact, since many resonance encounters
+occur when $\eta = \eta_{\rm cross}$ is substantial, even an approximate
+calculation of $\Delta K_{\pm}$ using Eq.~\eqref{eq:sep_theta} (which is valid
+only for $\eta \ll 1$) is inaccurate, and we instead calculate $\Delta K_{\pm}$
+along the numerically-computed $\mathcal{C}_{\pm}$ for arbitrary $\eta$. Note
+that Eqs.~(\ref{eq:def_dK_weaktide},~\ref{eq:def_pc_weaktide}) are equivalent to
+the separatrix capture result of \citet{henrard1982} when $\dot{\theta}_{\rm
+tide} = 0$ (see \citealp{henrard1987}, Paper I). Here, we have argued that this
+classic calculation can be unified with the calculation given in
+Section~\ref{ss:analytic_calculation} to give an accurate prediction of
+separatrix encounter outcome probabilities in the presence of both dissipative
+perturbation and parametric evolution of the Hamiltonian.
 
@@
 Fig.~\ref{fig:pc_fits_0_06}, we show the agreement of this semi-analytic
-procedure with the numerical results displayed earlier in the right panel of
-Fig.~\ref{fig:Hhists_0_06}. Good agreement is observed.
-Figs.~\ref{fig:pc_fits_0_20} shows the same for Figs.~\ref{fig:Hhists_0_20}.
-Mostly satisfactory agreement is observed. Thus, we conclude that the outcomes
-of separatrix encounter are accurately predicted by
-Eq.~\eqref{eq:def_pc_weaktide}.
+procedure with the numerical result displayed in the right panel of
+Fig.~\ref{fig:Hhists_0_06}. Figure~\ref{fig:pc_fits_0_20} depicts the same for
+the parameters of Figs.~\ref{fig:Hhists_0_20}, also showing satisfactory
+agreement. Thus, we conclude that the outcomes of separatrix encounter are
+accurately predicted by Eq.~\eqref{eq:def_pc_weaktide}.
 \begin{figure}
@@
     $\eta$ when a trajectory starting at $\theta_{\rm i}$ encounters the
-    separatrix.
-    \textcolor{red}{NB\@: the spike in tCE2 probability at at $\cos
-    \theta_{\rm i} \approx -1$, as well as the large $\eta_{\rm cross}$ values,
-    is likely an artifact of loss of numerical precision, I am working on fixing
-    this.}
-    }\label{fig:pc_fits_0_06}
+    separatrix. }\label{fig:pc_fits_0_06}
 \end{figure}
@@
     0.2$, corresponding to the right panel of
-    Fig.~\ref{fig:Hhists_0_20}.}\label{fig:pc_fits_0_20}
-\end{figure}
-
-With the above calculation, we can understand why even initial conditions in
-zone I can converge to tCE2. As long as the initial spin is sufficiently large
-($\geq 2n$), Eq.~\eqref{eq:dsdt_tide} shows that sufficiently large initial
-obliquities are \emph{increased} by weak tidal friction (the bottom right
-region of panels of Fig.~\ref{fig:6equils006}). This increase means that even
-initial conditions in zone I can sometimes be driven by tidal dissipation into
-the separatrix. When this is the case, it can be shown that both $\Delta K_+ >
-0$ and $\Delta K_- > 0$. This implies that both III $\to$ II and I $\to$ II
-outcomes are guaranteed, and thus initial conditions in all three zones can
-evolve into tCE2.
+    Fig.~\ref{fig:Hhists_0_20}. \textcolor{red}{Note that the analytical result
+    (green dashed line) exhibits significantly poorer agreement than in
+    Fig.~\ref{fig:pc_fits_0_06} when $\eta_{\rm cross} \gtrsim 0.2$.}
+    }\label{fig:pc_fits_0_20}
+\end{figure}
+
+With the above calculation, we can understand why even some initial conditions
+in zone I may converge to tCE2 in certain situations (see
+Fig.~\ref{fig:Hhists_0_50}). As long as the initial spin is sufficiently large
+($\geq 2n$), Eq.~\eqref{eq:ds_fullq} shows that when $\cos \theta > 2n /
+\Omega_{\rm s}$, the obliquity can increase. \textcolor{red}{In particular, when
+the critical obliquity $\cos \theta = 2n / \Omega_{\rm s}$ is inside the
+separatrix, tidal alignment acts to drive initial conditions in both zones I and
+III towards the critical obliquity and into the separatrix, and also towards
+larger $H$. As such, when this effect is sufficiently strong,
+Eq.~\eqref{eq:def_dK_weaktide} shows that both $\Delta K_\pm > 0$, and both III
+$\to$ II and I $\to$ II transitions are guaranteed upon separatrix encounter
+(Eq.~\ref{eq:def_pc_weaktide})}.
 
@@
 
-In the previous section, we considered the outcome as a function of the initial
-spin orientation, specified by $\theta_0$ and $\phi_0$. In this section, we
-consider the probability of evolution into tCE2 when averaging over a
-distribution of initial spin orientations, which we denote $P_{\rm tCE2}$. For
-simplicity, we just consider $\uv{s}$ to be isotropically distributed; we
-discuss the impact of more physically realistic distributions of $\uv{s}$ in
-Section~\ref{s:summary}. The bottom panel of Fig.~\ref{fig:probs20} shows
-$P_{\rm tCE2}$ for $I = 20^\circ$ as a function of $\eta_{\rm sync}$. It can be
-seen that tCE2 is reached with substantial probability ($\sim 50\%$) while it is
-also at a substantial obliquity ($\sim 60^\circ$) for $\eta_{\rm sync} \approx
-0.4$.
+In the previous section, we considered the outcome of the spin evolution driven
+by tidal torque as a function of the initial spin orientation, specified by
+$\theta_{\rm i}$ and $\phi_{\rm i}$. Here, we calculate the probability of
+evolution into tCE2 when averaging over a distribution of initial spin
+orientations, which we denote by $P_{\rm tCE2}$. For simplicity, we assume
+$\uv{s}$ to be isotropically distributed (see Section~\ref{s:summary} for
+discussions concerning impact of more physically realistic distributions of
+$\uv{s}$). The bottom panel of Fig.~\ref{fig:probs20} shows $P_{\rm tCE2}$ for
+$I = 20^\circ$ as a function of $\eta_{\rm sync}$. We see that, e.g., tCE2 with
+a large obliquity ($\sim 70^\circ$) can be reached reached with substantial
+probability ($\sim 50\%$).
 \begin{figure}
@@
     \includegraphics[width=\colummwidth]{../initial/1_weaktide/5probs_20.png}
-    \caption{\emph{Top:} Obliquities of the two tCE where $I = 20^\circ$ for a
-    range of $\eta_{\rm sync}$ (Eq.~\ref{eq:def_etasync}); the blue dashed line
-    denotes the analytical approximation Eq.~\eqref{eq:def_tce2_approx} and is
-    only displayed in its regime of validity, $\eta_{\rm sync} \ll \eta_{\rm c}$
-    (vertical dashed line; Eq.~\ref{eq:def_etac}). \emph{Bottom:} Total
-    probability of ending up in tCE2 ($P_{\rm tCE2}$; red dots), averaged over
-    an isotropic initial spin orientation and taking $\Omega_{\rm s, i} = 10n$.
-    The three shaded regions denote the contribution of initial conditions in
-    zones I/II/III (labeled) to the total tCE2 probability in the isotropic
-    average. For example, among systems that converge to tCE2 for $\eta_{\rm
-    sync} = 0.06$, more originate in zone III than zone II, and none originate
-    in zone I.}\label{fig:probs20}
+    \caption{\emph{Top:} Same as top panel of Fig.~\ref{fig:tCEs}.
+    \emph{Bottom:} Total probability of ending up in tCE2 ($P_{\rm tCE2}$; red
+    dots), averaged over an isotropic initial spin orientation and taking
+    $\Omega_{\rm s, i} = 10n$. The three shaded regions denote the contribution
+    of initial conditions in zones I/II/III (labeled) to the total tCE2
+    probability in the isotropic average. For example, among systems that
+    converge to tCE2 for $\eta_{\rm sync} = 0.06$, more originate in zone III
+    than zone II, and none originate in zone I.}\label{fig:probs20}
 \end{figure}
@@
 Eq.~\eqref{eq:app_tce2_p_tot} is shown in
-Figs.~\ref{fig:probs20}--\ref{fig:probs5} as the red dashed lines, where it
+Figs.~\ref{fig:probs20}--\ref{fig:probs5} as the red dashed lines; it
 agrees well with the numerical results (red dots) for $\eta_{\rm sync} \lesssim
@@
 sync}$, we display $P_{\rm tCE2}$ for $\eta_{\rm sync} \in \s{10^{-4}, 0.4}$ for
-both $I = 20^\circ$ and $I = 5^\circ$ in Fig.~\ref{fig:anal_ptce}. Note that no
-numerical results are presented for $\eta_{\rm sync} \leq 10^{-2}$, as the
-spin-orbit coupling becomes very strong and the integration slows dramatically
-due to the rapid precession of $\uv{s}$ about $\uv{l}$.
+both $I = 20^\circ$ and $I = 5^\circ$ in Fig.~\ref{fig:anal_ptce}. Note that
+for $\eta_{\rm sync} \leq 10^{-2}$, numerical results for $P_{\rm tCE2}$ are
+difficult to obtain, as the integration of
+Eqs.~\eqref{eq:ds_fullq}--\eqref{eq:ds_fulls} slows down dramatically due to the
+rapid precession of $\uv{s}$ about $\uv{l}$.
 \begin{figure}
@@
     \includegraphics[width=\colummwidth]{../initial/1_weaktide/7anal_ptce.png}
-    \caption{Plot of $P_{\rm tCE2}$ for $I = 5^\circ$ and $I = 20^\circ$
-    (legend) shown on a log-log plot, to emphasize the scaling at small
-    $\eta_{\rm sync}$. The crosses are the results of numerical simulations as
-    shown in Figs.~\ref{fig:probs20}--\ref{fig:probs5}, the solid lines are
-    Eq.~\eqref{eq:app_tce2_p_tot} for $\Omega_{\rm s, i} = 10n$ and the dashed
-    lines are for $\Omega_{\rm s, i} = 3n$. \textcolor{red}{Note: The agreement
-    with the data are will change slightly once the numerical
-    precision issue is resolved.}}\label{fig:anal_ptce}
+    \caption{$P_{\rm tCE2}$ as a function of $\eta_{\rm sync}$ for $I = 5^\circ$
+    and $I = 20^\circ$ shown on a log-log plot, to emphasize the scaling at
+    small $\eta_{\rm sync}$. The crosses are the results of numerical
+    integrations as shown in Figs.~\ref{fig:probs20}--\ref{fig:probs5}, the solid
+    lines are Eq.~\eqref{eq:app_tce2_p_tot} for $\Omega_{\rm s, i} = 10n$ and
+    the dashed lines are for $\Omega_{\rm s, i} = 3n$.}\label{fig:anal_ptce}
 \end{figure}
@@
 
-\subsection{Application to Super Earth + Cold Jupiter Systems
+\subsection{Obliquities of Super Earths with Companions
 }\label{ss:disc_sehj}
 
-Consider a system consisting of an inner Super-Earth (SE) and an exterior cold
-Jupiter (CJ); such systems are expected to be abundant \citep{zhu2018super}. A
-phase of giant impacts may occur in the formation of such SEs
-\citep{inamdar2015formation, izidoro2017breaking}, which can scramble the
-initial obliquity distribution into one resembling the isotropic distribution
-considered in Section~\ref{ss:tce2_etasync}. For this system, the spin of the
-planet approaches a tCE on the timescale
+Consider a system consisting of an inner Super-Earth (SE) with semimajor axis $a
+\lesssim 0.5\;\mathrm{AU}$ and an exterior companion. For concreteness, we
+assume the companion (with mass $m_{\rm p}$) to be a cold
+Jupiter (CJ) with $a_{\rm p} \gtrsim 1\;\mathrm{AU}$. Such systems are quite
+abundant \citep{zhu2018super}. A phase of giant impacts may occur in the
+formation of such SEs \citep{inamdar2015formation, izidoro2017breaking}, leading
+to a wide range of initial obliquities for the SEs. We are interested in the
+``final'' obliquities of the SEs driven by tidal disispation.
+
+For typical SE parameters, the spin evolution timescale due to tidal dissipation
 % 1 / (1.5 * 1e-3 * (Msun / (4 Mearth)) * ((2 Rearth) / (0.4 AU))^3 * 2 * pi / (0.4)^(3/2))
@@
 \begin{align}
-    \frac{1}{t_{\rm s}} ={}& \frac{1}{3 \times 10^7\;\mathrm{yr}}
+    \frac{1}{t_{\rm s}} \simeq{}& \frac{1}{3 \times 10^7\;\mathrm{yr}}
             \p{\frac{1}{4k}}
@@
 \end{align}
-This occurs well within the age of most SE-CJ systems. On the other hand,
-the orbital evolution of the SE occurs on the timescale \citep{lai2012}
+This occurs well within the age of SE-CJ systems. On the other hand,
+the orbital evolution of the SE occurs on the timescale \citep[e.g.][]{lai2012}
 % 1 / (1.5 * 1e-3 * (Msun / (4 Mearth)) * ((2 Rearth) / (0.4 AU))^5 * 2 * pi / (0.4)^(3/2))
@@
             \p{\frac{R}{a}}^5n \p{1 - \frac{\Omega_{\rm s}}{n}\cos \theta}\nonumber\\
-        ={}& \frac{1}{7 \times 10^{14}\;\mathrm{yr}}
+        \simeq{}& \frac{1}{7 \times 10^{14}\;\mathrm{yr}}
             \p{1 - \frac{\Omega_{\rm s}}{n}\cos \theta}
@@
 \end{align}
-Thus, $a$ does not evolve within the age of the SE-CJ system, and the
-approximation where $a$ is held constant is valid. For the same fiducial
-parameters, Eq.~\eqref{eq:def_etasync} can be evaluated
+Thus, $a$ does not evolve within the age of the SE-CJ system (for $a \gtrsim
+0.06\;\mathrm{AU}$), and we shall treat $a$ as a constant. With typical
+parameters for CJ parameters, Eq.~\eqref{eq:def_etasync} can be evaluated
 % 1/2 * Mjup * (4 * Mearth) / (Msun)^2 * ((0.4 AU) / (2 Rearth))^3 * (0.4 / 5)^3
@@
 \end{align}
-Here, $M_{\rm J}$ is the mass of Jupiter. We see from Figs.~\ref{fig:probs20}
+We see from Figs.~\ref{fig:probs20}
 and~\ref{fig:probs5} that this value of $\eta_{\rm sync}$ gives a high-obliquity
-tCE2 with significant probability. Eq.~\eqref{eq:def_ts_crit} shows that tCE2 is
-only unstable if $t_{\rm s} \lesssim t_{\rm s, c}$ where
+tCE2 with significant probability, assuming the SE has a wide range of initial
+obliquities. In addition, Eq.~\eqref{eq:def_ts_crit} shows that tCE2 is stable
+if $t_{\rm s} \gtrsim t_{\rm s, c}$, where
 % 1 / (3/8 * ((Mjup^3 * 4 * Mearth) / Msun^4 * (0.4 AU)^12 / ((5 AU)^9 * (2 Rearth)^3))^(1/2) * 2 * pi / (0.4)^(3/2))
@@
 \end{align}
-Since $t_{\rm s} \gg t_{\rm s, c}$, we see that tCE2 is stable. In
-Fig.~\ref{fig:sehj_region}, we show the value of $\eta_{\rm sync}$ in the
+In Fig.~\ref{fig:sehj_region}, we show the value of $\eta_{\rm sync}$ in the
 regions of $\p{a, a_{\rm p}}$ parameter space that satisfy the stability
-condition for tCE2. It can be seen that a generous portion of parameter space is
-able to generate and sustain inclined SEs. In summary, we predict that a
-significant fraction of SEs with exterior CJ companions can have long-lived,
-significant obliquities ($\gtrsim 60^\circ$) due to being trapped in tCE2.
+condition for tCE2. We see that a generous portion of parameter space is
+able to generate and sustain SEs in stable tCE2 with significant obliquities. In
+summary, we predict that a large fraction of SEs with exterior CJ
+companions can have long-lived, significant obliquities ($\gtrsim 60^\circ$) due
+to being trapped in tCE2.
 \begin{figure}
@@
     (top) and $I = 5^\circ$ (bottom). The SE is taken to have
-    $m = 4M_{\oplus}$ and $R = 2R_{\oplus}$ while the HJ is taken to have
+    $m = 4M_{\oplus}$ and $R = 2R_{\oplus}$ while the CJ is taken to have
     $m_{\rm p} = M_{\rm J}$, and we have taken $k \approx k_{\rm q}$. We only
@@
 
-\subsection{Application to Ultra-short-period Planet Formation
+\subsection{Formation of Ultra-short-period Planet Formation via Obliquity Tides
 }\label{ss:disc_usp}
 
-In \citet{millholland2020formation}, the authors consider capture into the CS2
-resonance as part of a mechanism to form ultra-short period planets (USPs).
-Their proposed mechanism consists of three stages:
+Ultra-short period planets (USPs), Earth-sized planets with sub-day periods,
+constitute a statistically distinct subsample of Kepler planets
+\citep[e.g.][]{winn2018kepler}. It is generally thought that USPs evolved from
+close-in SE- through orbital decay, driven by tidal dissipation in their host
+stars \citep{lee2017magnetospheric} or in the planets \citep{petrovich2019ultra,
+pu2019low}. In particular, \citet{pu2019low} showed that a ``low-eccentricity
+migration'' mechanism, in which a low-mass planet with an initial period of a
+few days maintains a small but finite eccentricity due to secular forcings from
+exterior companion planets and undergoes orbital decay and tidal dissipation,
+can produce USPs with the observed properties.
+
+\citet{millholland2020formation} proposed a new formation mechanism of USPs
+based on obliquity tides. This mechanism consists of three stages:
 \begin{itemize}
-    \item Rapid initial guaranteed capture into CS2.
-
-    \item Runaway inward tidal migration due to the simultaneous increase of the
-        CS2 obliquity during migration.
-
-    \item Stalling of inward migration when tidal dissipation becomes
-        sufficiently strong to destroy CS2.
+    \item A proto-USP (with two external companions) is assumed to be rapidly
+        captured into CS2 with appreciable obliquity and a pseudo-synchronous
+        spin rate (see Eq.~\ref{eq:dWsdt_tide}).
+
+    \item The inner planet undergoes runaway tidal migration as a result of the
+        decreasing semi-major axis and increasing obliquity while following CS2.
+
+    \item The inward migration stalls when the orbital decay becomes
+        sufficiently fast to destroy CS2.
 \end{itemize}
-They consider an inner proto-USP with two external perturbing planets, and
-imagine that the spin of the planet quickly evolves to its equilibrium value,
-i.e.\ satisfying Eq.~\eqref{eq:weaktide_dWszero}. In our language, this
-corresponds to immediate evolution into tCE2. In this section, we revisit this
-mechanism with the results presented earlier in this paper.
-
-First, a proto-USP evolves from its initial condition into one of the tCE on the
-timescale
+
+Here, we evaluate the visibility of the obliquity-driven migration scenario for
+USPs using the general results presented earlier in this paper.
+
+First, the spin evolution timescale for typical proto-USP parameters is
 % 1 / (1.5 * 1e-3 * (Msun / (8 Mearth)) * ((2 Rearth) / (0.035 AU))^3 * 2 * pi / (0.035)^(3/2))
@@
 \end{align}
-This is much shorter than the age of the system, and so the proto-USP can be
-treated as starting in one of the tCE\@.
-
-Next, we investigate the outcome of the initial, rapid spin evolution. For
-simplicity, we will first consider the case with a single external perturber.
-First, since the considered systems are very compact, we must generalize
-Eq.~\eqref{eq:wlp} to small semi-major axis ratios \citep[see e.g.][]{lai_2017}:
+where $\rho$ is the density of the proto-USP and $\rho_{\oplus}$ is the density
+of the Earth. This is much shorter than the age of the system, and so the
+proto-USP can quickly evolve into one of the stable tCE (either tCE1 or tCE2).
+
+Next, to determine which tCE the planet evolves into, we need to evaluate
+$\eta_{\rm sync}$ (see Eq.~\ref{eq:def_etasync}). For simplicity, we consider
+the case where the proto-USP is surrounded by a single external planetary
+companion with $a_{\rm p} \gtrsim a$ (typical of Kepler multiplanet systems) but
+with $L_{\rm p} \gg L$ (this condition can easily be relaxed; see
+Section~\ref{ss:disc_wasp12b}). To acount for such a close-by companion,
+Eq.~\eqref{eq:wlp} must be modified to \citep[see e.g.][]{lai_2017}:
 \begin{equation}
@@
 \end{equation}
-where $b_{\rm 3/2}^{(1)}$ is a Laplace coefficient. With this modification,
-$\eta_{\rm sync}$ (Eq.~\ref{eq:def_etasync}) can be computed:
+with $b_{\rm 3/2}^{(1)}$ the Laplace coefficient. With this modification,
+$\eta_{\rm sync}$ (Eq.~\ref{eq:def_etasync}) is given by
 % (10 * (Mearth)^2 / (Msun)^2) / 2 * (1.3)^(-3) * ((0.035 AU) / (Rearth))^3
@@
             \p{\frac{m_{\rm p}}{10 M_{\oplus}}}
-            \p{\frac{a / a_{\rm p}}{1/1.3}}^{3}
+            \p{\frac{1.3 a}{a_{\rm p}}}^{3}
             \p{\frac{M_\star}{M_{\odot}}}^{-2}
-            .\label{eq:etasync_usp}
-\end{align}
-We have evaluated using $a / a_{\rm p}$ corresponding to a period ratio $P_{\rm
-p} / P = 1.5$, for which $f(\alpha) \approx 5.5$. Note furthermore that $k /
-k_{\rm q} \approx 3$ for Earth-like planets \citep{groten2004fundamental,
-lainey2016quantification}. For $I = 5^\circ$, roughly
-consistent with typical proto-USP systems \citep{dai2018larger},
-Eq.~\eqref{eq:def_etac} shows that $\eta_{\rm sync} \ll \eta_{\rm c}$, and thus
-there are four CSs at spin-orbit synchronization. As such, if we take the
-initial planetary obliquity to be zero, the planet is guaranteed to evolve into
-tCE1, and not tCE2 (see Fig.~\ref{fig:Hhists_0_06}). If we assume instead a
-randomly oriented initial planetary spin, Fig.~\ref{fig:anal_ptce} suggests that
-the probability of capture into tCE2 is still only modest ($\lesssim 20\%$). A
-more sophisticated calculation including the effect of a third planet does not
-greatly modify these results.
+            ,\label{eq:etasync_usp}
+\end{align}
+where we have normalized $a / a_{\rm p}$ to $1.3$ (corresponding to a period
+ratio $P_{\rm p} / P = 1.5$), for which $f(\alpha) \approx 5.5$. As $k / k_{\rm
+q} \sim 1$ for the close-in proto-USP, we have $\eta_{\rm sync} \lesssim 0.06$,
+much less than $\eta_{\rm c} \sim 1$\footnote{One can make $\eta_{\rm sync}$
+larger by choosing a larger initial value for $a$, e.g.\ $a =
+0.05\;\mathrm{AU}$. However, the planet would not be able to experience orbital
+decay for such a large value, see Eq.~\eqref{eq:adot_usp}.}. As such, if the
+initial planetary obliquity is prograde, the planet is guaranteed to evolve into
+tCE1, and not tCE2 (see
+Figs.~\ref{fig:Hhists_0_06},~\ref{fig:pc_fits_0_06}--\ref{fig:pc_fits_0_20}). If
+we assume instead a randomly oriented initial planetary spin,
+Figs.~\ref{fig:anal_ptce}--\ref{fig:probs20} suggest that the probability of
+capture into tCE2 is small ($\lesssim 20\%$). A more sophisticated calculation
+including the effect of a third planet does not greatly modify these results.
 % Note that this calculation is in tension with
@@
 The second stage of the proposed mechanism, runaway inward migration after
-attaining tCE2, requires that the initial orbital decay time scale be
+attaining tCE2, requires that the initial orbital decay timescale be
 sufficiently fast. Evaluating Eq.~\eqref{eq:sehj_adot} for the relevant physical
-parameters, we find that:
+parameters, we find
 % 1 / (1.5 * 1e-3 * (Msun / (8 Mearth)) * ((2 Rearth) / (0.035 AU))^5 * 2 * pi / (0.035)^(3/2))
@@
 
-Finally, we compute the orbital separation at which tCE2 becomes unstable due to
-sufficiently strong tidal dissipation. Evaluating Eq.~\eqref{eq:def_ts_crit}, we
-find that tCE2 breaks ($t_{\rm s} \lesssim t_{\rm s, c}$) when the semi-major
+Finally, we compute the orbital separation at which tCE2 becomes unstable when
+the tidal alignment torque is too strong. Evaluating Eq.~\eqref{eq:def_ts_crit},
+we find that tCE2 breaks ($t_{\rm s} \lesssim t_{\rm s, c}$) when the semi-major
 axis is smaller than $a_{\rm break}$, where
@@
         \p{\frac{M_\star}{M_{\odot}}}^{1/3}
-        \p{\frac{m}{10M_{\oplus}}}^{-1/6}\nonumber\\
+        \p{\frac{m_{\rm p}}{10M_{\oplus}}}^{-1/6}\nonumber\\
         &\times \p{\frac{\rho}{\rho_{\oplus}}}^{-1/6}
@@
 This corresponds to a 2.7-day orbit. Once the system exits tCE2, it rapidly
-evolves to tCE1, which suppresses its orbital decay (Eq.~\ref{eq:adot_usp}).
-This final orbital separation does not qualify as a USP ($P \lesssim
-\mathrm{day}$).
-
-In summary, our results suggest that only proto-USPs with a large primordial
-obliquity have a probability of evolving into tCE2 initially. Furthermore,
+evolves to tCE1, in which orbital decay is severely suppressed
+(Eq.~\ref{eq:adot_usp}). This final orbital separation does not qualify as a USP
+($P \lesssim \mathrm{day}$).
+
+In summary, our results suggest that only proto-USPs with large primordial
+obliquitiies have a probability of evolving into tCE2 initially. Furthermore,
 proto-USPs that successfully initiate runaway tidal migration after reaching
@@
 
-\subsection{Application to WASP-12b}\label{ss:disc_wasp12b}
-
-In \citet{millholland2019obliquity}, the authors consider the possibility that
-the measured orbital decay of the HJ WASP-12b \citep[$P / \dot{P} = -3.2
-\;\mathrm{Myr}$; ][]{maciejewski2016departure, patra2017apparently} is caused by
-tidal dissipation in the HJ enhanced by being trapped in a high-obliquity CS due
-to an undetected exterior planet. We validate the plausibility of this scenario
-by the relevant physical parameters as was done in the previous sections using
-the following current-day system parameters \citet{hebb2009wasp,
-maciejewski2013multi, millholland_wasp12b}: $R_\star = 1.63R_{\odot}$, $M_\star
-= 1.36M_{\odot}$, $R = 1.89R_{\rm J}$, $m = 1.41M_{\rm J}$, and $a = 0.023
-\;\mathrm{AU}$. We begin with the spin evolution timescale, which is given by:
+\subsection{Orbital decay of WASP-12b Driven by Obliquity Tides}\label{ss:disc_wasp12b}
+
+WASP-12b is a hot Jupiter (HJ) with mass $m = 1.41M_{\rm J}$ and radius $R =
+1.89R_{\rm J}$ orbiting a main sequence star (with mass $M_\star
+= 1.36M_{\odot}$ and radius $R_\star = 1.63R_{\odot}$) on a $P =
+1.09\;\mathrm{day}$ ($a = 0.023 \;\mathrm{AU}$) orbit \citet{hebb2009wasp,
+maciejewski2013multi}. Long-term observations have revealed
+that its orbit is undergoing decay with $P / \dot{P} = -3.2\;\mathrm{Myr}$
+\citep{maciejewski2016departure, patra2017apparently}. Such a rapid orbital
+decay puts useful constraints on the physics of tidal dissipation in the host
+star \citep[e.g.][]{weinberg2017tidal, barker2020tidal}.
+
+\citet{millholland2019obliquity} considered the attractive possibility that the
+measured orbital decay of WASP-12b is caused by tidal dissipation in the HJ
+trapped in a high-obliquity CS due to an undetected planetary companion. We now
+evaluate the plausibility of this scenario. We begin with the spin evolution
+timescale, which is given by:
 % 1 / (1.5 * 1e-6 * ((1.36 Msun) / (1.41 Mjup)) * ((1.89 Rjup) / (0.023 AU))^3 * 2 * pi / (0.023)^(3/2))
@@
 Thus, the spin of WASP-12b has plenty of time to find a tCE\@. We also wish to
-calculate $\eta_{\rm sync}$, but there are three complications: (i) the system
-likely instead has angular momentum hierarchy $L \gg L_{\rm p}$ (to be verified
-after the fact), opposite to that considered in the paper thus far; (ii) the
-properties of the hypothetical perturber are unknown; and (iii) we should
-evaluate $\eta_{\rm sync}$ using the value of $a$ for WASP-12b at the start of
-its orbital migration, not its present day value. Towards resolving complication
-(i), we express the precession of $\uv{l}$ about $\bm{J} = J\uv{\jmath} \equiv
-\bm{L} + \bm{L}_{\rm p}$, the total angular momentum axis, as
+calculate $\eta_{\rm sync}$, but there are two complications: (i) the
+properties of the hypothetical planet companion (mass $m_{\rm p}$) to WASP-12b
+are unknown, and it is likely that $L_{\rm p}$ is smaller than $L$; and (ii) we
+should evaluate $\eta_{\rm sync}$ using the value of $a$ for WASP-12b at the
+start of its orbital migration, not its present day value. Towards resolving
+complication (i), we express the precession of $\uv{l}$ about $\bm{J} =
+J\uv{\jmath} \equiv \bm{L} + \bm{L}_{\rm p}$, the total angular momentum axis,
+as
 \begin{equation}
@@
 \end{equation}
-where $\omega_{\rm lp}$ is still given by Eq.~\eqref{eq:wlp}. Thus, we see that
-the precession frequency $\abs{g}$ is enhanced by a factor of $J / L_{\rm p}
-\approx L / L_{\rm p}$. Towards addressing complications (ii--iii),% chktex 8
-we use the fiducial values for the initial semi-major axis $a_{\rm i} =
-0.038\;\mathrm{AU}$ and initial semi-major axis ratio $a_{\rm p} / a_{\rm i} =
-1.29$, to be justified after the fact. We obtain:
+where $\omega_{\rm lp}$ is still given by Eq.~\eqref{eq:def_g_usp}. Thus, we see
+that the precession frequency $\abs{g}$ in
+Sections~\ref{s:theory}--\ref{s:full_tide_prob} is changed to
+\begin{equation}
+    g = -\omega_{\rm lp}\frac{J}{L_{\rm p}} \cos I
+        = \frac{3m_{\rm p}}{4M_{\star}}
+        \p{\frac{a}{a_{\rm p}}}^3 n f(\alpha) \frac{J}{L_{\rm p}}\label{eq:hj_g}.
+\end{equation}
+Towards addressing (ii), we use the fiducial values for the initial semi-major
+axis $a_{\rm i} = 0.038\;\mathrm{AU}$ and initial semi-major axis ratio $a_{\rm
+p} / a_{\rm i} = 1.29$, to be justified \emph{a posteriori}. Assuming $J /
+L_{\rm p} \simeq L / L_{\rm p}$, we have
 % 1/2 * (1.41 Mjup)^2 / (1.36 Msun)^2 * ((0.038 AU) / (1.89 Rjup))^3 * (0.038 / 0.05)^(3.5)
@@
             \p{\frac{a_{\rm i}}{0.038\;\mathrm{AU}}}^{3}
-            \p{\frac{a_{\rm p} / a_{\rm i}}{1.29}}^{-7/2}
+            \p{\frac{a_{\rm p}}{1.29 a_{\rm i}}}^{-7/2}
             \p{\frac{R}{1.89R_{\rm J}}}^{-3}.\label{eq:hj_etasync}
@@
 We next work towards justifying these choices of fiducial parameters. There are
-four physical and observational constraints on the WASP-12b + perturber system:
-\begin{itemize}
-    \item The HJ must have had a sufficiently small initial semimajor axis such
-        that its orbital decay timescale is less than the age of the system.
-
-    \item The exterior planet must be sufficiently massive to keep the HJ in a
-        high-obliquity tCE today.
-
-    \item The RV signal of the exterior planet must be smaller than the
-        residuals of the published RVs, $\sim 16\;\mathrm{m/s}$
-        \citep{hebb2009wasp, husnoo2011orbital, knutson2014friends,
-        bonomo2017gaps}.
-
-    \item The initial configuration of the HJ and exterior planet must be
-        dynamically stable.
-\end{itemize}
-
-First, we require that the initial HJ semimajor axis, denoted $a_{\rm i}$, is
-sufficiently small that decay occurs within the age of the system. The semimajor
-axis decay rate can be expressed as
+four physical and observational constraints on the WASP-12b + companion system:
+
+(i) The HJ must have had a sufficiently small initial semimajor axis such that
+its orbital decay timescale is less than the age of the system. The orbital
+decay rate is given by
 % 1 / (1.5 * 1e-7 * (1.36 Msun) / (1.41 Mjup) * ((1.89 Rjup) / (0.038 AU))^5 * (G * (1.36 Msun) / (0.038 AU)^3)^(1/2) * (1 yr))
@@
 \end{align}
-Again, $t_{\rm s} \ll a_{\rm i} / \dot{a}$, so we can treat the HJ as
-immediately evolving into a tCE\@. Thus, we see that the initial semimajor axis
-for the HJ cannot exceed $0.038\;\mathrm{AU}$ even when $\p{1 - \Omega_{\rm
-s}\cos \theta/n} \approx 1$, as is the case for rapid evolution into tCE2 while
-$\eta_{\rm sync} \ll 1$.
-
-Second, we address the constraint that tCE2 is stable under the influence of the
+Thus, the initial semimajor axis for the HJ cannot exceed $0.038\;\mathrm{AU}$
+even when $\p{1 - \Omega_{\rm s}\cos \theta/n} \approx 1$.
+
+(ii) The exterior planet must be sufficiently massive to keep the HJ in a
+high-obliquity tCE today, i.e.\ the tCE2 must be stable under the influence of the
 exterior planet. Using the amended precession frequency $\abs{g}$ given by
-Eq.~\eqref{eq:wasp12b_g}, we compute that the stability of tCE2 requires
+Eq.~\eqref{eq:hj_g}, we compute that the stability of tCE2 requires (see
+Eq.~\ref{eq:def_ts_crit})
 \begin{equation}
     \frac{1}{t_{\rm s}} \lesssim \omega_{\rm lp}\cos I \frac{L}{L_{\rm p}}
-        \sin i \sqrt{\frac{\eta_{\rm sync}\cos i}{2}}.
-\end{equation}
-Here, $\cos i \equiv \uv{l} \cdot \uv{\jmath}$. This then yields that
+        \sin I_{\rm J} \sqrt{\frac{\eta_{\rm sync}\cos I_{\rm J}}{2}},
+\end{equation}
+where $\cos I_{\rm J} \equiv \uv{l} \cdot \uv{\jmath}$. This then yields
 \begin{align}
     \frac{a_{\rm p}}{a}
-        \lesssim{}& 3.3 \p{\sin i \cos^{1/2} i \cos^{3/2} I}^{4/21}
+        \lesssim{}& 3.3 \p{\sin I_{\rm J} \cos^{1/2} I_{\rm J}
+            \cos^{3/2} I}^{4/21} \nonumber\\
+        &\times
             \p{\frac{m}{1.41 M_J}}^{12/21}
@@
 Notably, this expression does not depend on the perturber mass but only on
-$a_{\rm p}$.
-
-Third, we address the constraint that the RV signal of the exterior planet be
-smaller than $16\;\mathrm{m/s}$, which requires
+$a_{\rm p}$. Note that $\sin I_{\rm J} = \p{L_{\rm p} / J} \sin I \ll 1$ for $L
+\gg L_{\rm p}$, so Eq.~\eqref{eq:hj_tce2_stab} provides a stringent constraint
+on $a_{\rm p} / a$.
+
+(iii) The RV signal of the exterior planet must be smaller than the residuals of
+the published RVs, $\sim 16\;\mathrm{m/s}$ \citep{hebb2009wasp,
+husnoo2011orbital, knutson2014friends, bonomo2017gaps}. This requires
 % (G * (1.36 Msun) / (0.076 AU))^(1/2) * (80 Mearth) / (1.36 Msun) / 2^(1/2)
@@
     \p{\frac{M_\star}{1.36M_{\odot}}}^{-1/2}
-    \p{\frac{\sin i}{1 / \sqrt{2}}} \lesssim 1,
+    \p{\frac{\sin i_{\rm p}}{1 / \sqrt{2}}} \lesssim 1,
     \label{eq:hj_rv}
 \end{equation}
-where $i$ is the line-of-sight inclination angle. Here, we have taken $a_{\rm
-p}$ to be the maximum value permitted by Eq.~\eqref{eq:hj_tce2_stab}. For these
-values of $a_{\rm p}$ and $m_{\rm p}$, we still have $L / L_{\rm p} \sim 0.4$,
-and so $L \gg L_{\rm p}$ is well satisfied for the permitted parameter space as
-claimed.
-
-Finally, we require that the initial orbital configuration be dynamically
-stable. We use the Hill stability criterion \citep[e.g.][]{petit2020path}:
-\begin{equation}
-    \frac{a_{\rm p} - a_{\rm i}}{a_{\rm i}} > 2\sqrt{3}\frac{a_{\rm p} + a_{\rm
-        i}}{2a_{\rm i}} \p{\frac{m + m_{\rm p}}{3M_{\star}}}^{1/3}.
+where $i_{\rm p}$ is the line-of-sight inclination angle of $m_{\rm p}$. Here,
+we have taken $a_{\rm p}$ to be the maximum value permitted by
+Eq.~\eqref{eq:hj_tce2_stab}. For these values of $a_{\rm p}$ and $m_{\rm p}$, we
+still have $L / L_{\rm p} \simeq 0.4$, and so $L \gg L_{\rm p}$ is well satisfied
+for the permitted parameter space.
+
+(iv) Finally, we require that the initial orbital configuration of the two
+planets be dynamically stable. We use the Hill stability criterion
+\citep[e.g.][]{petit2020path},
+\begin{equation}
+    a_{\rm p} - a_{\rm i} > 2\sqrt{3} \frac{a_{\rm p} + a_{\rm
+        i}}{2} \p{\frac{m + m_{\rm p}}{3M_{\star}}}^{1/3}.
 \end{equation}
@@
 
-For $\eta_{\rm sync} = 0.075$, we find that there are four CSs unless $i$ is
-extremely small. From Fig.~\ref{fig:Hhists_0_06}, we can infer that prograde
-primordial obliquities will evolve towards tCE1 in the regime where $\eta_{\rm
-sync} \ll \eta_{\rm c}$. On the other hand, if the primordial obliquity of the
-HJ is assumed to be isotropically distributed, then Fig.~\ref{fig:probs20}
-suggests that the probability of entry into tCE2 is $\lesssim 25\%$ even if
-the perturbing planet is misaligned by $I = 20^\circ$.
-
-In summary, the joint constraints we have placed on the WASP-12b \& perturber
-system imply that the initial $\eta_{\rm sync, i}$ is unlikely to have been
-large. This suggests that early capture into tCE2 is unlikely from either an
-isotropic or prograde-favoring initial obliquity distribution. However, it is
-possible that additional mechanisms can generate a favorable initial obliquity
-distribution, such as the presence of a dissipating protoplanetary disk in the
-early lifetime of the system quickly driving the obliquity of WASP-12b to $\sim
-90^\circ$ \citep{millholland_disk, su2020}.
+For $\eta_{\rm sync} \sim 0.075$, we can infer that prograde primordial
+obliquities will evolve towards tCE1 (see
+Figs.~\ref{fig:Hhists_0_06},~\ref{fig:probs20}--\ref{fig:probs5}). On the other
+hand, if the primordial obliquity of the HJ is assumed to be isotropically
+distributed, then Fig.~\ref{fig:probs20} suggests that the probability of entry
+into tCE2 is $\lesssim 25\%$ even if the perturbing planet is misaligned by
+$I_{\rm J} \sim I \sim 20^\circ$. In reality, $\sin I_{\rm J} = \p{L_{\rm p} /
+J}\sin I \ll \sin I$ for $L_{\rm p} \ll L$, further decreasing the probability.
+
+In summary, the joint constraints we have placed on the WASP-12b \& companion
+system imply that the initial $\eta_{\rm sync, i}$ is unlikely to be large.
+\textcolor{red}{Figure~\ref{fig:wasp12b_constr} illustrates the joint effect of
+these constraints and the resulting range of possible $\eta_{\rm sync, i}$
+values.} These $\eta_{\rm sync, i}$ values suggest that early capture into tCE2
+is unlikely from either an isotropic or prograde-favoring initial obliquity
+distribution. However, dynamical effects when the WASP-12b system was young may
+have preferentially generated tCE2-producing systems, i.e.\ systems with
+$\theta_{\rm i} \simeq 90^\circ$ \citep[e.g.\ the presence of an exterior
+protoplanetary disk][]{millholland_disk, su2020}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\colummwidth]{../initial/99_misc/5wasp12b_region.png}
+    \caption{\textcolor{red}{The values of $\eta_{\rm sync, i}$
+    (Eq.~\ref{eq:hj_etasync}) for the WASP-12b system. The permitted parameter
+    space is constrained by
+    Eqs.~(\ref{eq:hj_tce2_stab},~\ref{eq:hj_rv},~\ref{eq:hj_orbstab}).
+    }}\label{fig:wasp12b_constr}
+\end{figure}
 
@@
         Eqs.~\ref{eq:def_etasync} and~\ref{eq:def_etac}; see discussion in
-        Section~\ref{ss:weaktide}), which tCE a given initial planetary spin
+        Section~\ref{ss:tce}), which tCE a given initial planetary spin
         configuration asymptotically evolves towards depends on which of the
@@
         either tCE can be determined by careful study of the dynamics upon
-        separatrix encounter (Sections~\ref{ss:toy_outcomes}
+        separatrix encounter (Sections~\ref{ss:analytic_calculation}
         and~\ref{ss:phop_weaktide}). As an example, if the initial spin
@@
 outcome of a separatrix encounter can still be solved using the techniques of
-Sections~\ref{ss:toy_outcomes} and~\ref{ss:phop_weaktide}.
+Sections~\ref{ss:analytic_calculation} and~\ref{ss:phop_weaktide}.
 
@@
 
-In Section~\ref{ss:tidal_equils}, we studied the stability of the CSs under of
+In Section~\ref{ss:linear_stab}, we studied the stability of the CSs under of
 tidal alignment torque given by Eq.~\eqref{eq:dsdt_tide_toy}, finding that CS2
@@
 
-Similarly to the analytic calculation in Section~\ref{ss:toy_outcomes}, we seek
+Similarly to the analytic calculation in Section~\ref{ss:analytic_calculation}, we seek
 to compute the change in the unperturbed Hamiltonian over a single libration
@@
 left extremes of Figs.~\ref{fig:probs20} and~\ref{fig:probs5}. In this regime,
-following the discussions in Sections~\ref{ss:toy_outcomes}
+following the discussions in Sections~\ref{ss:analytic_calculation}
 and~\ref{ss:phop_weaktide}, we understand that initial conditions (ICs) in zone I

### 2021-07-13 initial/0_eta/3stats.py

@@ -133,11 +133,11 @@ def run_for_tide(tide=1e-3,
         # plot_point(plt.gca(), q, '%so' % c, markersize=8)
     for idx, c in enumerate(colors[ :2]):
         plt.plot(0, -10, c=c, marker='o', ls='',
-                 markersize=5, label='CS%d' % (idx + 1))
+                 markersize=5, label='CS%d' % (idx + 1), zorder=2)
     plt.ylim([-1, 1])
     plt.legend(fontsize=16, loc='center left', bbox_to_anchor=(1, 0.5))
-    plt.ylabel(r'$\cos \theta_0$')
-    plt.xlabel(r'$\phi_0$ (deg)')
+    plt.ylabel(r'$\cos \theta_{\rm i}$')
+    plt.xlabel(r'$\phi_{\rm i}$ (deg)')
     plt.xticks([0, np.pi, 2 * np.pi],
                ['0', r'$180$', r'$360$'])
     plt.text(np.pi, np.cos(qs[1]), 'II', backgroundcolor=(1, 1, 1, 0.9),
@@ -156,7 +156,7 @@ def run_for_tide(tide=1e-3,
                 levels=[H(I, eta, np.cos(qs[3]), phis[3])],
                 colors=['k'],
                 linewidths=3,
-                linestyles='solid')
+                linestyles='solid', zorder=3)
 
     plt.tight_layout()
     plt.savefig('3stats%s.png' % prefix, dpi=400)

### 2021-07-13 initial/1_weaktide/5pop.py

@@ -192,7 +192,7 @@ def plot_eq_dists(I, s_c, s0, IC_eq1, IC_eq2):
     # set up axes
     left, width = 0.22, 0.53
     bottom, height = 0.12, 0.76
-    spacing = 0.05
+    spacing = 0.08
     rect_scatter = [left, bottom, width, height]
     rect_histy = [left + width + spacing, bottom,
                   0.98 - (left + width + spacing), height]
@@ -274,15 +274,11 @@ def plot_eq_dists(I, s_c, s0, IC_eq1, IC_eq2):
         mu_vals =  np.linspace(-0.99, 0.99, n_mu)
         p_caps = get_num_caps(I, s_c, cross_dat, mu_vals)
         tot_probs = np.sum(p_caps / n_phi, axis=1)
-        if s_c < 0.1:
-            fig, (ax1, ax2) = plt.subplots(
-                2, 1,
-                figsize=(6, 6),
-                gridspec_kw={'height_ratios': [2, 1]},
-                sharex=True)
-        else:
-            fig = plt.figure(figsize=(6, 4))
-            ax1 = plt.gca()
+        fig, (ax1, ax2) = plt.subplots(
+            2, 1,
+            figsize=(6, 6),
+            gridspec_kw={'height_ratios': [2, 1]},
+            sharex=True)
         ax1.plot(mu_vals, tot_probs, 'b', alpha=0.8, lw=3.5)
 
         # try anal prob
@@ -298,23 +294,24 @@ def plot_eq_dists(I, s_c, s0, IC_eq1, IC_eq2):
         ax1.text(1, 1, r'$\eta_{\rm sync} = %s$' % s_c_text,
                  ha='right', va='top', fontsize=16)
 
-        if s_c < 0.1:
-            ax1.plot(mu_vals, tot_probs_al, 'g--', alpha=0.8, lw=1.0)
-            for mu, crosses in zip(mu_vals, s_crosses):
-                cross_idx = np.where(crosses > 0)[0]
-                all_crosses = crosses[cross_idx]
-                ax2.plot(np.full_like(crosses[cross_idx], mu),
-                         s_c / all_crosses,
-                         'bo', alpha=0.8, markersize=0.8)
+        ax1.plot(mu_vals, tot_probs_al, 'g--', alpha=0.8, lw=1.0)
[…]

### 2021-07-13 initial/1_weaktide/7anal_ptce.py

@@ -29,7 +29,7 @@ s_c_vals = {
         0.25,
         0.1,
         0.03,
-        # 0.01,
+        0.01,
     ],
     5: [
         0.7,
@@ -111,5 +111,5 @@ def pcaps_compare():
     plt.close()
 
 if __name__ == '__main__':
-    # plot_anal()
+    plot_anal()
     pcaps_compare()

### 2021-07-13 initial/99_misc/2_rand_plots.py

@@ -118,12 +118,15 @@ def plot_cs_phi(I=np.radians(5)):
     plt.semilogx(etas, fix_d(cs_vals[2]), 'tab:blue', lw=LW)
     plt.semilogx(etas_four, fix_d(cs_vals[3]), 'tab:purple', lw=LW)
     fs = 16
-    plt.text(etas_four[0] * 1.1, fix_d(cs_vals[0])[0] + 5, r'CS1 ($\phi = 0$)',
+    plt.text(etas_four[0] * 1.1, fix_d(cs_vals[0])[0] + 8,
+             r'CS1 ($\phi = 0$; stable)',
              fontsize=fs, color='darkorange', va='bottom')
     plt.text(etas_four[0] * 1.1, fix_d(cs_vals[3])[0], r'CS4 ($\phi = 0$)',
              fontsize=fs, color='tab:purple', va='bottom')
-    plt.text(etas[-1] / 1.1, fix_d(cs_vals[1])[-1] + 8, r'CS2 ($\phi = \pi$)',
-             fontsize=fs, ha='right', color='tab:green', va='bottom')
+    plt.text(etas[-1] / 1.1, fix_d(cs_vals[1])[-1] + 5,
+             r'CS2 ($\phi = \pi$; stable)',
+             fontsize=fs, ha='right', color='tab:green', va='bottom',
+             rotation=-15)
     plt.text(etas[-1] / 1.1, fix_d(cs_vals[2])[-1] + 5, r'CS3 ($\phi = 0$)',
              fontsize=fs, ha='right', color='tab:blue', va='bottom')
     plt.xlabel(r'$\eta$', fontsize=22)
@@ -217,7 +220,7 @@ def plot_eigens_phi(I=np.radians(5)):
         ax.text(np.max(etas), 0 + 0.05 * ax.get_ylim()[0],
                 r'$\Delta \phi_{\rm cs} = %d^\circ$' % shift_deg,
                 ha='right', va='top', fontsize=16)
-        ax.set_ylabel(r'$\lambda_0^2/ (1 + \eta^2)$')
+        ax.set_ylabel(r'$\lambda_0^2/ (g^2 + \alpha^2)$')
     axs[2].set_xlabel(r'$\eta$')
     axs[2].set_xlim([min(etas), max(etas)])
 
@@ -490,5 +493,5 @@ if __name__ == '__main__':
     # plot_nonad_diagram()
 
     # plot_cs_phi(np.radians(20))
[…]
